### 2014-01-26 figure_table.tex
intermediate version

the width of band gap is a measure of chemical bond strength

Fig.~\ref{fig4}(c) illustrated the XRD spectrum of one typical sample.The peaks under circular symbol were identified to be the monoclinic \ce{WO3} phase (ICDD PDF 01-083-0950,\emph{a}=7.30084\AA, \emph{b}=7.53889\AA, \emph{c}=7.6896\AA , $\beta$=90.8920$^\circ$), while the peak under the triangular symbol was indexed to cubic tungsten phase (ICDD PDF 04--16-3405,\emph{a}=3.157\AA).

\si{W/in^2}
\si{\degreeCelsius}

 WO3: dielectrics constants: $\epsilon_\alpha = 6.52,\epsilon_\infty > 50$. \cite{Deb2008}
\begin{figure}[htb]
\centering
\subfloat[tw2]{\label{fig:tw2}\includegraphics[width=5cm]{Tangwei2}}\hspace{0.04\textwidth}
\subfloat[tw3]{\label{fig:tw3}\includegraphics[width=5cm]{Tangwei3}}

\subfloat[tw4]{\label{fig:tw4}\includegraphics[width=10cm]{Tangwei4}}
\caption{snapshot of Late Autumn}
\label{fig:tw}
\end{figure}

\begin{figure}[htb]
\centering
\subcaptionbox{\label{fig:moind}}{\includegraphics{n_MoO3}}%
\subcaptionbox{\label{fig:mocon}}{\includegraphics{Graph20}}
\caption[Refractive indices of \ce{MoO3}]{(a) Refractive indices of \ce{MoO3} Dashed line is n along $a$ axis while solid line is along $c$ axis. (b) optical contrast mapping of 1L \ce{MoO3} on \ce{SiO2}-Si. The x axis is \ce{SiO2} thickness, y axis is wavelength.It is assumed that the incident light is polarized along c axis of \ce{MoO3}.}
\label{fig:mofl}
\end{figure}

\begin{align}
\cee{WO3(V) &-> W(S) + 3/2O2 \qquad T= 1150 \si{\degreeCelsius}\\
        WO3(V) &-> WO2(S) + 1/2O2}
\end{align}

\begin{align}
W + xSiO{_2} &\rightarrow WO{_x} + xSiO{_2},\\
W + SiO{_2}   &\rightarrow WO{_x} + WSi{_2},
\end{align}

\begin{align}
x\ce{M+} + x\ce{e-} +  \ce{$\alpha \hyphen$WO$_{3-y}$}= \ce{$\alpha \hyphen$M$_x$WO$_{3-y}$},
\end{align}

\begin{align}
h\nu +\ce{W^{5+}(A)} +  \ce{W^{6+}(B)} &\rightarrow \ce{W^{5+}(B)} + \ce{W^{6+}(A)} \label{eq:cl_bl1}\\
h\nu +\ce{W^{5+}(A)} +  \ce{W^{4+}(B)} &\rightarrow \ce{W^{5+}(B)} + \ce{W^{4+}(A)} \label{eq:cl_bl2}
\end{align}

\begin{figure}[htb]
\centering
\includegraphics[width=0.8\textwidth]{CVD_and_temp_MoO3.jpg}
\caption[CVD system]{Chemical vapor system and its temperature profile.The length of heating zone is 6 inches. On the horizontal axis of temperature, zero inch is defined at the upstream edge of furnace.The triangular labels $\blacktriangledown$ were measured points at ambient pressure.The nominal substrates temperature were estimated from interpolation data.}
\label{fig:s1}
\end{figure}

\begin{table}[htb]
\centering
\caption{Source of figures }\label{tab:sof}
\begin{tabular}{lcccr}
\toprule
\multicolumn{2}{c}{Flow} \\
\cmidrule(l){4-5}
         & Temperature & Pressure & Ar & \ce{O2}  \\
\midrule
Range      & RT-1100    & 10mTorr-1atm & 0 - 100 & 0-30  \\
Resolution & $\pm1$  & correlated to flow & 1   & 0.1  \\
\bottomrule
\end{tabular}
\end{table}

Adding notes to tables can be complicated.

\begin{table}
  \caption{A table with notes}
  \label{tbl:notes}
  \begin{tabular}{ll}
    \toprule
    Header one                            & Header two \\
    \midrule
    Entry one\textsuperscript{\emph{a}}   & Entry two  \\
    Entry three\textsuperscript{\emph{b}} & Entry four \\
    \bottomrule
  \end{tabular}

  \textsuperscript{\emph{a}} Some text;
  \textsuperscript{\emph{b}} Some more text.
\end{table}

%\newgeometry{margin=1in}
%\begin{landscape}
\begin{sidewaystable}
\begin{table}[htb]
\centering \small
\caption{Tungsten Oxides Growth and Application}\label{tab:wox}
\begin{tabular}{lccr}
\toprule
composition  &  methods & highlights &  reference  \\
\midrule
\ce{WO3}     & \ce{Na2WO4.2H2O} mixed with \ce{(NH4)2Fe(SO4)2.6H2O} or%
 \ce{CoCl2.6H2O} followed by hydrothermal heating  & 3 different morphologies and photodegradation  & \cite{Rajagopal2009}  \\
Resolution & $\pm1$  & correlated to flow & 1     \\

\bottomrule
\end{tabular}
\end{table}
\end{sidewaystable}
%\end{landscape}
%\restoregeometry

the electrical conductivity is given by $\sigma = n e \mu$, where $n$ is the density of free carriers, $\mu$ is their mobility and $e$ is electronic charge. The mobility is given by $\mu = e\tau/m^*$ with $\tau$ is carrier resistivity relaxation time and $m^*$ is the carrier effective mass.

The degree of \ce{H^+} intercalation, $x$, is determined by integrating cathodic current, and given by
\begin{equation}
x = \frac{Q}{F}\frac{M_\ce{WO3}}{m_f}
\end{equation}
where $m_f$ is the mass of film, $M_\ce{WO3}$ is the molar mass of \ce{WO3*1/3H2O}, and F is Faraday's constant.
The color center density, $c$, is then obtained using formula
\begin{equation}
c= \frac{x M_\ce{WO3}N_A}{\rho}
\end{equation}
where $N_A$ is Avogadro number, $\rho$ is density of film.

In second state, the one with smaller droplet probably would exhibit faster growth rate in $\langle001\rangle$ direction due to its shortest lattice constant, while the other one endures more growth along$\langle010\rangle$ direction. We suspect that the liquid size that induce the tower growth is much larger than that of belts. From the final morphology of as-synthesized sample, we find that the above proposed two growth approaches could change into each other, that is belt growth could be initiated on the top of tower growth and vice visa. We assume this phenomena arise from the interaction between vapor supply, temperature and the shape of liquid catalyst. Or it may just come from the vapor transport of \ce{NaxMoO3}.
It had been shown by actively engineering the shape of catalysis, the growth direction of  InP NW could be switched between [111] and [100].\cite{Wang2013c} The same mechanism might exist in our case as well. For instance, when a belt is sufficient long and it could extend into the low temperature part, where the supply of MoOx vapor is reduced due to the consumption, and the shape of liquid might vary as well. Both will result in different absorption and subsequent diffusion rate along and inside the liquid catalyst. We also observed that belt growth could initiate from tower growth in reduced time growth. Actually this may be one possible mechanism of belts formation.

(The presence of \ce{Na6MoO33} phase is an indirect evidence for the formation of eutectic \ce{Na2MoO4}- \ce{MoO3} binary compounds at growth temperature. The bulk phase diagram may not accurately represent the phase transition occurring in catalyst droplet and solid interface. And it will usually lead to a significant temperature decrease of eutectic point from the bulk value. Nanoparticles do not completely melt and instead act as an active site for reactant absorption and diffusion, leading to a vapor-solid-solid growth mechanism. )

### 2014-01-26 main.tex
intermediate version

\documentclass[12pt,oneside]{book}
 %
   \usepackage{uncc-thesis} % uncc format specification seems this style should be loaded before other packages

   \input{package.tex} % additonal packages and tweaking
   \input{./FrontMatter/abbre}

   \makeglossaries

   \begin{document}

%    \input{./FrontMatter/FrontMatter}

%   \include{./ch-intro/ch-intro}
%   \include{./ch-wox/ch-wox}
   \include{./ch-moox/moox}

\appendix
   %\glsaddallunused
%    \include{./BackMatter/app1}

\renewcommand{\bibname}{REFERENCES}
   \begin{singlespace}
   \printbibliography
   \end{singlespace}

\end{document}

### 2014-01-26 FrontMatter/Abstract.tex
add rest of tex

\begin{abstract}

Transition metal oxides and dichacolgenides.

\end{abstract}

### 2014-01-26 FrontMatter/FrontMatter.tex
add rest of tex

  \title{Controlled Growth and Properties Measurement of One-Dimensional Nanostructures: Nanowires and Hybrids}
  \author{Tao Sheng}
  \university{The University of North Carolina at Charlotte}
  \location{Charlotte}
  \thesisyear{\the\year}
  \degree{Doctor of Philosophy}
  \department{Physics and Optical Science}

  \committeemember{Dr. Haitao Zhang} % First sets the \advisor default.
  \committeemember{Dr. Tsinghua Her}
  \committeemember{Dr. Michael Fiddy}
  \committeemember{Dr. Stuart Smith}
  \committeemember{Last  person} % Maximum of 10 can be specified.

%  \advisor{Dr. Haitao Zhang}

\maketitle

\input{./FrontMatter/Abstract}

\begin{dedication}
This mis my appear in the named sectional unit, otherwise each glossary will
appear in a chapter, if chapters exist, otherwise in a section. Unnumbered
sectional units will be used by default.
\end{dedication}

%\pagebreak{}

\begin{ackn}
This work is supported by National Science Foundation (DMR-1006547) and the start-up fund from the Department of Mechanical Engineering and Engineering Science(MEES) and Charlotte Research Institute at the University of North Carolina at Charlotte (UNC Charlotte). We appreciate the Department of MEES and the Center for Optoelectronics and Optical Communications at UNC Charlotte for the support of multiuser facilities.
\end{ackn}
%\pagebreak{}
%% --- Work around some bugs due to babel package---
% for more, see http://tex.stackexchange.com/questions/82993/how-to-change-the-name-of-document-elements-like-figure-contents-bibliogr?lq=1
\setcounter{tocdepth}{1}
% ----- end of work around--------

\clearpage
\tableofcontents
\clearpage
\listoftables
\clearpage
\listoffigures
\begin{singlespace}
%\thispagestyle{myheadings}
\renewcommand{\glossarypreamble}{\thispagestyle{myheadings}}
\printglossary[type=\acronymtype]
\clearpage
\end{singlespace}
%\listofabbre

\pagebreak{}

### 2014-01-26 ch-intro/ch-intro.tex
add rest of tex

%\input{../header.tex} %  comment out when assembling

\chapter{introduction: nanomaterials for energy applications}

\section{Background and Motivation}

TMO as electrochromic device and TMDC as newly 2D semiconductor, and some VLS.

Materials that human can make define the age they live in. From Stone Age to Bronze Age and Iron Age, people evolve as mastering more and more sophisticated techniques of manipulating metals, such as alloying and annealing. Obtaining extreme high purity of silicon brings us into Information Age. Future is difficult to predict. But nanotechnology is one direction that we can not ignore. According to \gls{nni}, \gls{nanotechnology}. This definition alludes that dimension comes before compositions. It is often related to the quantum confinement or surface area in nanomaterials, which we will later revisit with specific scenario.

There are three states of matter under usual conditions: solid,liquid and gas. Solids materials could be further categorized into five groups: metals, ceramics, polymers, semiconductors, and composites.\cite{William2009} This classification is based on both composition and mechanical, electrical, and thermal properties as well as the associated functionality(i.e., \gls{ceramics} are typically hard yet brittle, insulating to electricity and resistant to heating).

\section{Dissertation Outline}

The materials studied in this work/dissertation are tungsten oxides (\ce{WO3}), molybdenum oxides (\ce{MoO3}),and their chalcogenide counterparts (\ce{WS2} and \ce{MoS2}). Both tungsten (W) and molybdenum (Mo) belong to Group VIB transition metal, with outer shell electrons configuration as $4d^55s^1$ and $5d^46s^2$ respectively. Therefore we refer their oxides and chalcogenides as \gls{tmo} and \gls{tmdc}.\footnote{Obviously transition metals include many other elements, all of which have partially filled $d$-electron shell. But here we use TM to denote W and Mo exclusively.} We have synthesized \gls{tmo} and \gls{tmdc} at nanoscale, measured their crystalline structures and optical properties and demonstrated some devices assembled using as-synthesized nanomaterials. We aim to illustrate that by nanoengineering these \gls{tmo} and \gls{tmdc}, enhanced performances over their bulk states could be expected and new properties will arise. In the remaining sections of this chapter, we will discuss some general perspectives of nanomaterials, the growth apparatus and characterization methods that apply to all experiments done in this work. Then chapter 2 will focus on growth of \ce{WO3} and its derivative. We employed thermal \gls{cvd} to synthesize \ce{WO3} \gls{nw}, and we investigated the role of impurity in tungsten metallic powders, during which we observed a new state of sodium tungsten oxides: \ce{Na5W14O44} nanowires. We also found a method to potentially obtain large yield of \ce{WO3} \gls{nw}. Chapter 3 will concentrate on \ce{MoO3}. We explored two different growth mechanism of \ce{MoO3}:\gls{vs} and \gls{vls}. We discovered that alkaline oxides can be used as catalyst to grow two distinct \ce{MoO3} morphologies: nanobelts and towers. We further demonstrated the application of as-synthesized \ce{MoO3} nanomaterials in electrochromic devices.  In chapter 4 we discuss the growth of \gls{tmdc} and associated heterostructures. We synthesized \ce{WO3}-\ce{WS2} core-shell \gls{nw} and inspected the growth of \gls{fl} \ce{WS2}. Chapter 5 will conclude with an overall summary.

\section{Nanomaterials for Energy Applications}

why nano? surface-to-volume ratio, more surface area for catalytic reaction; surface energy state: tuned by dimension; quantum confinement effects: exciton size vs physical dimension. easy for dopant diffusion, thereby band structure modification; charge-separation and transport mechanism may also differ from bulk.

\section{Crystal Structures and Electronic Properties}

Solid and orderliness.

Two theories arise to describe the outer shell electrons and to correlate the structure and physical properties: \gls{cft} and band theory.\cite{Goodenough1971} \gls{cft} assumes weak interaction between neighboring atoms and localization of electron towards parent atom, whereas band theory assumes that electron is shared equally by all nuclei and therefore a many-electron problems follows. Description of a single electron in periodic potential fail to treat the electron correlations adequately, as the interaction between atoms becomes weaker.For transition metals, $s$ and $p$ electrons are well described by a collective-electron model, while the 4f or 5f electrons are tightly bound to nuclei and screened from the neighboring atoms by 5s, 5p or 6s, 6p core electrons, hence it matches well with a localized-electron model. d electrons show intermediate character.

\section{Growth Apparatus and Characterization Methods}
\subsection{CVD System}

The synthesis was accomplished in a home-made hot-wall CVD system, as visualized in Fig.~\ref{fig:ch1cvd}. The furnace is made by two semi-cylindrical ceramic fiber heaters (WATLOW inc.) with power density from 0.8 to 4.6 \si{W/cm^2}. Quartz tube (Quartz Sci inc.) of 1 inch diameter was primarily used as reaction chamber. A mechanical pump was connected to maintain the low pressure environment inside the chamber. The length of uniform heating zone is 6 inches, with cooling zone extending outward. Carriers gas argon (Ar) and reactant gas oxygen (\ce{O2}) was regulated by two mass flow controllers respectively.

\begin{figure}[htb]
\centering
\subfloat[]{\includegraphics[width=0.8\textwidth]{CVD_d346.jpg}}

\subfloat[]{\includegraphics[width=0.8\textwidth]{CVD_model.jpg}}
\caption[CVD system]{Home-built low-pressure chemical vapor system.}
\label{fig:ch1cvd}
\end{figure}

Silicon and silicon dioxides on Si wafer ($p$-Si(100),Unversity Wafer inc.) were primarily used as receiving substrates, and other substrates (i.e. Mica\footnote{ \ce{K(Al2)(Si3Al)O10(OH)2}}, glass (Fisher Scientific, microscope slide, 12-549),\footnote{Typical composition is 72.6\% \ce{SiO2}, 0.8\% \ce{B2O3}, 1.7\% \ce{Al2O3}, 4.6\% \ce{CaO}, 3.6\% \ce{MgO} and 15.2\% \ce{Na2O}} stainless steel) were occasionally adapted. The preparation procedure was illustrated in Fig. Substrates were first cut into rectangular pieces of certain size and then ultrasonically bathed (Branson 1510R-MTH) with acetone and alcohol for about 15 minutes each followed by blow-drying with nitrogen gas. After solution cleaning, the Si surface is hydrophobic. Depending on the specific experimental requirement, sometimes a hydrophilic surface is desired. We use plasma cleaning (Kurt J Lesker: Plasma-Preen 862) under 2Torr \ce{O2} for 3 minutes to render a hydrophilic Si surface. In addition, substrates can be coated with a thin layer of metal before sent into reaction chamber. This process details will be covered later in the \emph{Characterization} session. The controllable parameters of our CVD system includes central heating temperature, absolute gas flow and relative ratio of (Ar/\ce{O2}), amount of source material and the location of receiving substrates. The operation capability was summarized in Table.~\ref{tab:cvd}.

\begin{table}[htb]
\centering
\caption{CVD parameters map}\label{tab:cvd}
    \begin{tabular}{lcccr}
    \toprule
     &&&\multicolumn{2}{c}{Flow} \\
    \cmidrule(l){4-5}
             & Temperature & Pressure & Ar & \ce{O2}  \\
    \midrule
             & \si{\degreeCelsius} & mTorr & sccm & sccm\\
    \midrule
    Range      & RT-1100    & 10mTorr-1atm & 0 - 100 & 0-30  \\
    Resolution & $\pm1$  & correlated to flow & 1   & 0.1  \\
    \bottomrule
    \end{tabular}
\end{table}

The substrates were mostly positioned in downstream cooling zone since within this region, the vapor undergoes a rapid temperature gradient and precipitation occurs. The source material placed in the central heating zone is oxidized and then evaporated. The growth species, transported by carrier gas, bombard both substrate and chamber wall. Some will be adsorbed by the substrate and become adatoms while some may remain as gas molecules, waiting for another event. On the hot substrate, adatoms diffuse and do not settle down until finding a appropriate location where equilibrium is favorable.

Nucleation is a process of generating a new phase from a metastable old phase, where the Gibbs energy per molecule of the bulk of the emerging new phase is less than that of the old phase.

  General CVD knowledge, substrate preparation, and\cite{MichealK.Zuraw2003}

\subsection{Measurement}
sample/specimen preparation, data processing,

\textbf{Magnetic Sputtering} Sputtering, a process in which atoms are ejected from a solid target material by bombarding it with energetic particles, is a well established PVD process with a high degree of controllability. The high energy and controllable parameters of sputtering can result in the growth of well-structured and crystalline films. Further, sputtering can be easily implemented as a roll-to-roll process for large-scale manufacturing. It is widely utilized for deposition of \ce{WO_x} in industry.

The morphology and composition of the as-synthesized samples were analyzed by scanning electron microscopy (SEM,JEOL JSM-6480) and energy dispersive X-ray spectroscopy (EDS,Oxford Instrument INCA). Crystal structures were characterized using X-ray diffraction (XRD, PANXpert X’pert Pro MRD with Cu $K\alpha$ radiation at $\lambda$=1.5418\AA) and transmission electron microscopy (TEM, JEOL JEM-2100 \ce{LaB6} operated at 200kV). Optical measurements were performed by Micro-Raman spectroscopy (Horiba Scientific, Labram HR800 with 532 nm excitation laser) in a confocal microscope backscattering configuration with spectral resolution about 1 cm$^{-1}$. Optical absorption spectra was recorded using UV-Vis-NIR spectrophotometer(Schimadzu, UV2600Plus) in transmission mode. When necessary, the as-synthesized sample was removed from substrates by light sonication(Branson 1510R-MTH, 70W) in ethanol for 15 seconds. The dispersion was left for 12 hrs to enable the possible sedimentation, after which became transparent under the unaided eye. Then the dispersion was transferred into one 10 mm quartz cuvette (Thorlabs, W005654) for absorption measurement with another paired cuvette containing ethanol only.

%\printbibliography  %  comment out when assembling

%\input{../end.tex} %  comment out when assembling

### 2014-01-26 ch-moox/moox.tex
add rest of tex

\chapter{Molybdenum Oxides}

\section{Introduction}

Molybdenum oxides \ce{MoO3} crystallizes in three phases, orthorhombic $\alpha$-\ce{MoO3}, monoclinic $\beta$-\ce{MoO3} and the metastable hexagonal h-\ce{MoO3}.\citep{Deb1968,Fibers2007} $\alpha$-\ce{MoO3} phase exhibits anisotropic structure with strong bonding along [001] and [100] direction while Van der Waals interaction along [010] direction.\cite{He2003} Due to this unique structure, \ce{MoO3} was found to have several important properties and a wide range of technological applications, such as electrochromism and photochromism,\cite{Yao1992} lubricants,\cite{Sheehan1996} photocatalysts,\cite{Chen2010} and gas sensor, including \ce{CO},\cite{Comini2005} \ce{NO2},\cite{Taurino2006} \ce{H2}\cite{Sha2009} and ethanol.\cite{Choopun} Moreover, other features arise when nanoscale \ce{MoO3} is specifically prepared, for instance, field emission.\citep{Li2002d,Zhou2003b}  As a layered hosting material, \ce{MoO3} can be further modified by intercalating with alkaline ions\citep{Spahr1995,Li2006b,Hu2011} and even divalent ion\cite{Sian2005}. This structural richness have enabled improved performance in Li-ion\cite{Mai2007} and sodium-ion battery.\cite{Hariharan2013} In combination with \ce{TiO2} forming a core-shell structure, these nanoparitcles are reported to lower the photoabsorption energy of \ce{TiO2}.\cite{Elder2000} When combined with Ag as layered structure, transparent conducting behavior was observed.\cite{Nguyen2012} In addition, \ce{MoO3} is a good precursor for preparing other useful materials, such as \ce{MoS2} fullerenes\cite{Li2003c}, and few layer \ce{MoS2}.\cite{Lin2012}  It will also be an important member of the Van der Waals heterostructures.\cite{Geim2013}

It may be considered as built up of chains of \ce{MoO4} tetrahedra connected by the sharing of two oxygen corners with two neighbouring tetrahedra in $c$ axis. The infinite chains of \ce{MoO4} tetrahedra from half-layers in the $ac$ plane. Two half-layers, which are stapled along $b$ axis, build up one \ce{MoO3} layer. When the two more distant oxygen are included for one molybdenum atom, the coordination can be regards a sixfold, i.e,, the layered structure consisting of zig-zag rows of edge-sharing \ce{MoO6} octahedra, while the rows are mutually connected by corners.\cite{Itoh2001a}

on \ce{MoO3} reviews.\cite{He2003}

\citeauthor{Chithambararaj2013} prepared hexagonal \ce{MoO3} nanocrystal via hydrothermal method  and demonstrated the photodegradation of MB under visible light.\cite{Chithambararaj2013} The efficiency dependence on catalysis/dye ratio, light intensity and temperature was studied. h-\ce{MoO3} was mostly synthesized using solution methods, where \ce{NH4+} and \ce{OH.} were possible structure directing and stable agents. The band gap of h-\ce{MoO3} estimated from diffusion reflection spectrum is $2.8\sim3.0eV$.

Hexagonal phase \ce{MoO3} is readily identified by the XRD pattern (strong peak at $2\theta=20^{\circ}$).

\section{Syntheses Methods}
\subsection{literature review}

\subsection{this work}
\textbf{Substrate treatment.} Silicon substrates(p-$\langle100\rangle$, University Wafers) were first cut into 10mm by 25mm pieces and ultrasonically cleaned with acetone and ethanol for 15 minutes(Branson 1510R-MTH), each followed by blow-drying with nitrogen gas. Then the substrates were selectively treated in an oxygen plasma cleaning apparatus(Kurt J Lesker: Plasma-Preen 862, 2Torr) for 3 minutes to increase the wettability. The substrates without plasma cleaning were rendered as hydrophobic. Finally, the substrate was drop-cast 54 $\mu$L 10 mM \ce{NaOH} (or \ce{KI}, \ce{Na2CO3}) and naturally left dry in a convection hood with a flask cover above. Other alkaline ions-containing substrates, such as glass (Fisher Scientific, microscope slide, 12-549) and indium tin oxide (ITO) coated glass(Delta Technologies, 25\si{\ohm}), were cleaned by the same routine except the absence of plasma cleaning and subsequent aqueous solution dipping. Mica was cleaved right before growth without other treatment.

\textbf{Synthesis.} In a typical synthesis, molybdenum powders were loaded into the uniform heating zone and the sealed chamber was first pumped down to 10 mTorr. Then oxygen flow varying between 0.1 sccm to 10 sccm (standard cubic centimeter per minute) was admitted from upstream inlet. With 10 sccm UHP Ar(99.999\%)as carrier gas, the overall pressure reached about 200 mTorr. The heating temperature was ramped up to 800 \si{\degreeCelsius} in 30 minutes and lasted for 15 to 120 minutes. Then the heating power was turned off and the chamber was allowed to naturally cool down to room temperature. The receiving substrate was placed in downstream location where the temperature was about 400 to 670 \si{\degreeCelsius} according to open air temperature profile. To observe the formation of droplets, clean silicon substrate was coated with 9 nm molybdenum film using a magnetron sputter(Desk IV TSC, Denton Vacuum), followed by \ce{NaOH} dipping as described before. Then the substrate was placed into chamber for growth, where all the parameters remained unchanged except the absence of Mo powder source.

\section{Discussion}

In vapor synthesis process, two growth mechanism exists: VS and VLS. VS process is widely accepted for the growth of \ce{MoO3}. Yet we caution that synthesis conditions should be scrutinized to determine the exact mechanism. \citeauthor{Li2002c} suggested a VS mechanism at 700 \si{\degreeCelsius} and VLS at 750 \si{\degreeCelsius} and higher.\cite{Li2002c} \citeauthor{Fibers2007} proposed a modified VS mechanism probably because the deposition occurs on \ce{Al2SiO5} with possible \ce{Al_{0.95}SiNa_{0.06}O_x} involved. Therefore temperature and possible impurity could potentially alter the growth mechanism. We divide the growth results into two categories: on Si substrate and on non-Si substrate to describe them respectively.

\subsection{Growth on Si substrates}

Mo began to be oxidized into \ce{MoO3} at 500 \si{\degreeCelsius}, \ce{MoO3} vapor pressure began to increase rapidly above 700 \si{\degreeCelsius}. \cite{Margrave1967} And the MP of \ce{MoO3} is reported as 795 \si{\degreeCelsius}. With these facts in mind, we design the experimental parameters as listed in Table.~\ref{tab:mooxsi}. We should point out that these parameters are selected and optimized from a wide range of combinations. And when we discuss the influence of one parameter with different values, one should assume other parameters still adapt those listed in Table.~\ref{tab:mooxsi}.

\begin{table}[htb]
\centering
\caption{Growth conditions of \ce{MoO3} on Si}\label{tab:mooxsi}
\begin{tabular}{lcccr}
\toprule
&&&\multicolumn{2}{c}{Flow (sccm)} \\
\cmidrule(l){4-5}
 & Temperature $T_h$ (\si{\degreeCelsius}) & Pressure  & Ar & \ce{O2}  \\
\midrule
typical values  & 800    & 200mTorr & 10 & 10  \\
\end{tabular}
\end{table}

The growth layout is schematically shown in Fig.~\ref{fig:mooxgrowth}. Notice that on the horizontal axis of temperature, zero inch is defined at the upstream edge of furnace. To facilitate discussion and provide a tight context, we define the position of substrate as the coordinate of its upper-stream edge along this temperature axis (i.e. the substrate location is 7 inch in Fig.~\ref{fig:mooxgrowth}). The usual length of Si substrate is 1 inch. When positioned at 7 inch, it is then located in a temperature range of $650 \sim 350$ \si{\degreeCelsius}.

\begin{figure}[htb]
\centering
\includegraphics[width=0.8\textwidth]{CVD_and_temp_MoO3.jpg}
\caption[Growth setup of \ce{MoO3}]{Chemical vapor system and its temperature profile. The triangular labels $\blacktriangledown$ were measured points at ambient pressure. The nominal substrates temperature were estimated from interpolation data.}
\label{fig:mooxgrowth}
\end{figure}

From previous works,\cite{predeep2011} we found that with $T_h = 600$ and substrate placed at 6.5 inches, microflakes was found at the high temperature edge of Si, suggesting the nucleation already started.\footnote{020510 batch} When flow of oxygen was gradually reduced, diminished size of micro-flake was observed at the same location of substrates. This results indicated the rate-determining step is diffusion when oxygen flow was in the range of 2 sccm to 0.5 sccm.\footnote{(31210-31510 batches)} We also found the deposition amount on a particular location of the substrate is not linearly proportional to the growth time, i.e., the growth at upper stream edge first increase then decrease. This is not surprising when considering the temperature field requires some time to become synchronized as depicted in Fig.~\ref{fig:mooxgrowth}. Using conditions in Table.~\ref{tab:mooxsi} and 1 hr growth, we observed the typical micro-flakes morphologies as shown in Fig.~\ref{fig:mosisem}. Most flakes exhibit rectangular shape, with average thickness of one micron, standard deviation $\sigma_D=0.34\mu m$.

\begin{figure}[htb]
\centering
\subfloat[]{\label{fig:mosem1}\includegraphics[width=0.45\textwidth]{mosemsi_a}}\hspace{0.04\textwidth}
\subfloat[]{\label{fig:mosem2}\includegraphics[width=0.45\textwidth]{mosemsi_b}}
\caption[Representative morphologies of \ce{MoO3} on Si]{SEM images of representative depositions of \ce{MoO3} on Si. (a)Low magnification. (b) High magnification. }
\label{fig:mosisem}
\end{figure}

This rectangular shape implies the boundary plane along growth direction (long axis) is (001), in consistency with previous experimental\cite{Zeng1998,Li2002b} and theoretical\cite{Firment1983,Cora1997} studies. We also observed different shapes, i.e., elongated hexagonal using similar growth conditions. This is not an indication of different growth mode. It is a normal thermodynamic fluctuation. In fact, (201), (101) and (102) planes have all been observed as terminating planes.\cite{Zeng1998} The stacking rate of \ce{MoO6} octahedra along a and c axis could develop some other ratio. And the coexistence of different planes in one growth suggests the similarity of free surface energies.

\begin{figure}[htb]
\centering
\subfloat[]{\label{fig:moxrd}\includegraphics[width=0.45\textwidth]{xrd_moo3}}\hspace{0.04\textwidth}
\subfloat[]{\label{fig:moram}\includegraphics[width=0.45\textwidth]{raman_moo3}}
\caption[Crystalline phase characterization of \ce{MoO3} on Si]{(a) XRD pattern and (b) Raman spectrum of typical \ce{MoO3} on Si, $\lambda_{ex} = 532nm$.}
\label{fig:mooxch}
\end{figure}

As shown in Fig.~\ref{fig:mooxch}, the crystal structures and phase of as-synthesized samples were examined by XRD and Raman. The XRD pattern (Fig.~\ref{fig:moxrd}) is readily indexed to the orthorhombic phase of \ce{MoO3} (ICDD PDF 05-0508, \emph{a}=3.9628\AA, \emph{b}=13.855\AA, \emph{c}=3.6964\AA). The space group is $D_{2h}^{16}(Pbnm)$. This crystal structure is indeed a unique example among transition metal oxides, representing a transitional stage between tetrahedra and octahedral coordination.\cite{Itoh2001a} The strongest peak index is (110), suggesting the orientation of \ce{MoO3} is not parallel to the substrate, which is consistent with the morphology displayed in Fig.~\ref{fig:mosem1}. In contrast, we shall see a different scenario in Section.~\ref{sec:nasi}, where the orientation is changed. The Raman spectrum of as-synthesized specimens also closely matches \ce{MoO3} features in previous studies.\cite{Dixit1986,Silveira2012} During m-Raman measurement, the laser spot was carefully focused onto the plates and several inspections on different positions were observed to ensure the reproductivity of spectra data. As shown in Fig.~\ref{fig:moram}, 14 distinct bands were well resolved. The 284 \si{cm^{-1}} peak represents the wagging mode for double bond \ce{O=Mo=O}. The 337 and 380  \si{cm^{-1}} peaks are assigned to \ce{O-Mo-O} bending and scissoring modes. The 199 \si{cm^{-1}} peak and two other weaker peaks at 218 and 247 \si{cm^{-1}} represent \ce{O=Mo=O} $B_{2g}$ twist, $A_g$ chain mode and \ce{O=Mo=O} $B_{3g}$ twist mode, respectively.    667 \si{cm^{-1}} peak is assigned to triply coordinated oxygen stretching model resulting from edge-shared oxygen in common to three octahedral. The 819 \si{cm^{-1}} peak is from doubly coordinated oxygen stretching mode arising from corner-shared oxygen between two octahedral. The 996 \si{cm^{-1}} peak comes from unshared oxygen stretching mode.\cite{Siciliano2009} The assignment is summarized in Table.~\ref{tab:moram}.

\begin{table}[htb]
\centering
\caption{Experimental Raman peaks (\si{cm^{-1}}) assignment of \ce{MoO3} on Si.\cite{Eda1992,Siciliano2009}}\label{tab:moram}
\begin{tabular}{llcll}
\toprule
this work & Sym.       &          & Assignment &   \\
\midrule
117      & $B_{2g}$    &           & $T_c$  & RCM  \\
129      & $B_{3g}$    &           & $T_c$  & RCM  \\
158      & $A_g/B_{1g}$&           & $T_b$  & RCM  \\
199      & $B_{2g}$    & $\tau$    & \ce{O=Mo=O}  & twist  \\
218      & $A_g$       &           & $R_c$     & RCM  \\
247      & $B_{3g}$    & $\tau$    & \ce{O=Mo=O}  & twist  \\
284      & $B_{2g}$    &           & \ce{O=Mo=O}  & wag  \\
292      & $B_{3g}$     & $\delta$ & \ce{O=Mo=O}  & wag  \\
337      & $A_g,B_{1g}$ & $\delta$ & \ce{O-Mo-O} & bend  \\
380      & $B_{1g}$     & $\delta$ & \ce{O-Mo-O}  & scissor  \\
474      & $A_g$        & $\nu_{as}$ & \ce{O-Mo-O}  & stretch,bend  \\
667      & $B_{2g},B_{3g}$ & $\nu_{as}$  & \ce{O-Mo-O}  & stretch  \\
819      & $A_g$        & $\nu_{as}$  & \ce{O=Mo}  & stretch  \\
996      & $A_g$         & $\nu_{as}$  & \ce{O=Mo}  & stretch  \\
\bottomrule
\end{tabular}
\end{table}

The growth rates along different crystalline direction of \ce{MoO3} are presumably determined by the free surface energy. In other words, the migration barrier of adatoms on (010) plane is presumably much lower than that on other low index planes due to the Van der Waals interaction nature along [010] direction.

\subsection{FL}

FL materials attracts intensive research efforts recently. We first use liquid exfoliation method to prepare FL \ce{MoO3}. We then characterized the absorption feature and crystalline structures of the exfoliated \ce{MoO3} using UV-Vis and TEM. Then we calculate the optical contrast of FL \ce{MoO3} on \ce{SiO2}-Si, which serves as a guideline to identify FL \ce{MoO3} using optical microscope.

The exfoliation solution is 30\% isopropanol (IPA) in DI water, which has been proved to work well on other layered compounds.\cite{Halim2013} After 20 minutes sonication, the dispersion is milky. We measured the transmission spectra of this dispersion immediately upon sonication and after 40 hrs for gravity sedimentation, as illustrated in Fig.~\ref{fig:moabs}. The t0 line mainly arises from the scattering of flakes in the dispersion. There are two scattering mechanisms: Rayleigh scattering and Tyndall scattering. Rayleigh scattering, which occurs when particles are comparable to wavelength, is inversely proportional to the fourth power of wavelength; While Tyndall scattering, which occurs when the particles are larger, is inversely proportional to the square of the wavelength. To fully evaluate the true absorbance of the sample itself, one needs to decouple the scattering part from apparent absorbance. Generally we select one part of spectrum and assume it is only caused by scattering. Then a empirical dependence shown in Eq.~\ref{eq:sca2} is used as polynomial fitting model.

\begin{align}
Abs_{sca}  & = a\times \lambda^{n}  \label{eq:sca1}\\
\log{Abs_{sca}} & = \log{a} + n*\log{\lambda} \label{eq:sca2}
\end{align}

After least-squares fitting, the coefficients $a$ and $n$ can be used to estimated the scattering in other wavelengths. The fitting of n usually falls between -2 and -4. We examined the t40h line in Fig.~\ref{fig:moabs} and found the scattering part is almost zero. Therefore we did not perform aforementioned fitting. This is not always the case. In chapter on the \ce{WS2} section, we do need to do so.

\begin{figure}[htb]
\centering
\subfloat[]{\label{fig:moabs}\includegraphics[width=0.45\textwidth]{MoO3-abs}}\hspace{0.04\textwidth}
\subfloat[]{\label{fig:mobg}\includegraphics[width=0.45\textwidth]{MoO3-bg}}
\caption[UV-Vis spectra of exfoliated \ce{MoO3}]{(a) UV-Vis absorbance spectra of exfoliated \ce{MoO3}. Dashed line (t0) represents measurement immediately after sonication, and solid line (t40h) is obtained after sitting for 40 hours. The dot dashed line is reference spectrum of the 30\% IPA. (b) Band gap estimation}
\label{fig:mouv}
\end{figure}

According to the corrected absorbance spectrum, optical band gap can be deduced, which is known as Tauc Plot.\cite{Tauc1972} The procedure is recapitulated here.

\begin{equation}\label{eq:tauc}
 (h\nu \alpha)^{\frac{1}{n}} = B(h\nu - E_g^{opt}),
\end{equation}
where B is a proportional coefficient, $\alpha$ is absorption\footnote{The absorbance $A = 0.4343\alpha*l$, where l is the optical path} and $E_g^{opt}$ is defined as optical band gap. The value n is correlated to the nature of optical transition. For direct allowed transition, n = 1/2; For direct forbidden transition, n = 3/2; For indirect allowed transition, n = 2; And for indirect forbidden transition, n = 3. When the transition nature of sample is not well known, one should apply each to check which one provide the best fit. Depending on the synthesis methods and \ce{MoO3} morphologies, the transition phenomena might vary. On the \ce{MoO3} films, \citeauthor{Bouzidi2003} assumed a direct gap (n = 1/2)\cite{Bouzidi2003} while \citeauthor{Szekeres2002} not.\cite{Szekeres2002} We use n = 2 in this work. We plot $\sqrt{(h\nu \alpha)}$ versus photon energy, and extrapolate the linear part onto $h\nu$ axis. The intercept is used as $E_g^{opt}$ then. Our evaluation and some previous studies is summarized in Table.~\ref{tab:mobg}.

\begin{table}[htb]
\centering
\caption{Optical band gaps of \ce{MoO3}}\label{tab:mobg}
\begin{tabular}{lccr}
\toprule
&\multicolumn{2}{c}{Band gap} \\
\cmidrule(l){2-3}
Reference & value(eV) & orientation & material states\\
\midrule
\cite{Deb1968}   & 2.96  & $E\parallel c_0$ & single crystal\\
\cite{Deb1968}   & 2.80  & $E\perp c_0$ & single crystal \\
\cite{Julien1995} & 2.8$\sim$ 3.2 & NA & films\\
 this work  & 3.1  & NA & nanoflakes\\
\bottomrule
\end{tabular}
\end{table}

An alternative way is a) define $Y = \alpha E=\alpha h\nu$, and obtain $Y' = \frac{\partial Y}{\partial E}$, then b) plot $Y'/Y$ versus $h\nu$. The band gap value can be obtained from the intercept of extrapolated line on photo energy axis.\cite{Choopun} This approach is not difficult to comprehend as long as we notice from Eq.~\ref{eq:tauc}, $Y = B (h\nu - E_g^{opt})^n$ and $Y' = B n(h\nu - E_g^{opt})^{n-1}$.

The dielectric constants\footnote{Not a constant at all, instead, it has complicated dependence on photon energy} ($\epsilon = \epsilon_1 + i*\epsilon_2$) of \ce{MoO3} have been studied in several reports.\cite{Deb1968,Sabhapathi1995,Miyata1996,Abdellaoui1997,Mondragon1999} We extracted $\epsilon_1$ from Ref\cite{Itoh2001a} due to the wide photon energy range utilized. We also notice that $\epsilon_2$ is approximately zero when $h\nu$ is less than 4 eV. Since we are primarily concerned with the optical contrast of FL \ce{MoO3} in visible wavelength region($h\nu < 3$ eV), we obtained refractive indices $n$ from $n = \sqrt{\epsilon_1}$. Due to the orthorhombic phase, \ce{MoO3} exhibit birefringence, that is there are two refractive indices, $n_c$ and $n_a$, as shown in Fig.~\ref{fig:moind}. The refractive index is between $ 2.2\sim 2.4$ along a axis, and $ 2.5\sim 2.8$ along c axis. Comparison to the low frequency dielectric constant ($18.0\pm1$) implies a primarily ionic bonding in \ce{MoO3}.\cite{He2003}

\begin{figure}[htb]
\centering
\subfloat[]{\label{fig:moind}\includegraphics[width=0.45\textwidth]{n_MoO3}}\hspace{0.04\textwidth}
\subfloat[]{\label{fig:mocon}\includegraphics[width=0.45\textwidth]{Graph20}}
\caption[Refractive indices of \ce{MoO3}]{(a) Refractive indices of \ce{MoO3} Dashed line is n along $a$ axis while solid line is along $c$ axis. (b) optical contrast mapping of 1L \ce{MoO3} on \ce{SiO2}-Si. The x axis is \ce{SiO2} thickness, y axis is wavelength.It is assumed that the incident light is polarized along c axis of \ce{MoO3}.}
\label{fig:mofl}
\end{figure}

Fig.~\ref{fig:mocon} illustrates the optical contrast mapping of 1L \ce{MoO3} on \ce{SiO2}-Si when the incident light is polarized along c axis of \ce{MoO3}. One can see that .
The refractive indices of Si and \ce{SiO2} within visible wavelengths and MATLAB source code for optical contrast calculation is included in Appendix.

The dimension and phase of exfoliated \ce{MoO3} is examined using TEM. Fig.~\ref{fig:motem} shows the size of exfoliated \ce{MoO3} is about 500 nm. High-resolution TEM (HRTEM) image was taken to assess the \ce{MoO3}. The clearly resolved lattices indicate high crystal quality of \ce{MoO3}.

\begin{figure}[htb]
\centering
\includegraphics[width=0.8\textwidth]{exf_moo3.jpg}
\caption[TEM images of exfoliated \ce{MoO3}]{(a) TEM image and (b) HRTEM image of FL \ce{MoO3} obtained by liquid sonication method.}
\label{fig:motem}
\end{figure}

\subsection{Growth on non-Si substrates}\label{sec:nasi}

In previous works, \ce{MoO3} deposition on ITO/glass exhibits new morphologies that were not observed on Si substrates, yet the mechanism is not well investigated.\cite{predeep2011} We first repeated the previous growth on ITO/glass, and then found similar deposition phenomena on glass and mica substrates. We suspected that the morphology difference on the substrates employed in this study arises from the compositions difference. Both mica and glass contains alkaline elements which are absent in Si and \ce{SiO2}/Si substrates. We primarily verify this hypothesis by utilizing \ce{NaOH} treated Si substrates and found that the overall morphology almost reproduces that on ITO and mica substrates. We then propose a new growth mechanism based on the VLS process to explain the deposition of \ce{MoO3} on alkaline-ions-containing substrates.

ITO versus NaOH images.

\subsubsection{Na transport}
We estimated the mass transport of sodium ions in silica glass. The driving force could be external field or concentration gradient. And the dynamics is governed by diffusion equation

\begin{align}
\frac{\partial C}{\partial t} = D \frac{\partial^2 C}{\partial x^2},
\end{align}

where C is concentration in unit of \si{mol\per cm^3}, and D is diffusion coefficient in unit of \si{cm^2\per\second}. Diffusion coefficient highly depends on the overall environments in which the ions resides. Typical values of D for Na ions are listed in Table.~\ref{tab:mona}

\begin{table}[htb]
\centering
\caption{Na diffusion coefficient ($cm^2/sec$), R is molar gas constant (8.315 \si{\joule\per mol\per K}), and T is temperature in K}\label{tab:mona}
\begin{tabular}{lcr}
\toprule
 Composition & Value  & Reference  \\
\midrule
Quartz      & $3.8\times10^{-2}exp(\frac{-24500}{RT})$  & \cite{Rybach1967a}  \\
Sodalite      & $6.6exp(\frac{-42500}{RT})$  & \cite{Sippel1963}  \\
Obsidian     & $4.4\times10^{-2}exp(\frac{-22900}{RT})$  & \cite{Sippel1963}  \\
silicate glass & $3.1\times10^{-8}$ at 420\si{\degreeCelsius} & \cite{Jbara1995} \\
\ce{SiO2} glass & $1.1\times10^{-7}$ at 670\si{\degreeCelsius} &  \cite{FRISCHAT1968}\\
\bottomrule
\end{tabular}
\end{table}

We also would like to mention the gradient of Gibbs free enthalpy overruled the concentration of a particular species, and higher \ce{OH^-} contents tend to reduce Na diffusivity.\cite{Materials2012}  The substrates used in this work are glass and ITO/glass. Related parameters is as following:
\begin{itemize}
\item dimension: $25mm\times10mm\times1mm$
\item density: 2.567 \si{g\per cm^3}
\item Na concentration: 0.01 \si{mol\per cm^3}
\item D: $1.1\times10^{-7}$ \si{cm^2\per\second}
\end{itemize}

Then the net flux $J$ is estimated as
\begin{align}
J = -D \frac{\Delta C}{\Delta x} = 2.0e^{-8} mol/cm^2/sec,
\end{align}

for a typical 2hrs growth, the net amount of Na diffusing out of substrate is then 144$\mu mol$, about 10\% of total Na ions. The diffusion length $\sqrt{Dt}$ is 190 $\mu m$. We noticed this result overestimate since the flux will reduce gradually. Meanwhile the molar amount of \ce{NaOH} applied on Si substrate is about 1$\mu mol$. Considering the adjusted ratio, Na contents should be much more when using glass substrate than when using NaOH-Si substrate.

Another important factor is the evaporation of sodium molybdates. However, few report could be found in literature. We only find one by \citeauthor{Kazenas2010}.\cite{Kazenas2010} The partial pressure\footnote{$logP(atm)= -13794/T + 6.19$} of \ce{Na2MoO4} is calculated to be 0.2 mTorr at 800 \si{\degreeCelsius} and $3.5\times 10^{-3}$ mTorr at 670 \si{\degreeCelsius}.

\begin{table}[htb]
\centering
\caption{Reactants list}\label{tb:source}
\begin{tabular}{lcccr}
\toprule
Material & Stock No & LOT &Purity & Vendor\\
\midrule
\ce{NaOH}        & S318-500 & 070241 & 99.8\% & Fisher Scientific \\
\ce{NaI}        & 11665 & K11W054 & 99.9\% &  Alfa Aesar \\
\ce{KI}        & 42857 & H06Z051 & 99.9\% &  Alfa Aesar \\
\ce{Na2CO3}        & 33377 & 114X012 & 99.95\% &  Alfa Aesar \\
\ce{Molybdenum}        & 00932 & I07S024 & 99.9\% &  Alfa Aesar\\
\bottomrule
\end{tabular}
\end{table}

\textbf{tower-like structure}

Nanotower is a less common morphology in the structures of nanomaterials.\cite{Kharissova2010} We have not found report on  \ce{MoO3} nanotower structures, although there are several studies on \ce{In2O3},\cite{Jean2010,Yan2007}, GaN\cite{Xiao2012} and ZnO\cite{Zhang2013c}. \citeauthor{Jean2010} investigated the growth mechanism of \ce{In2O3} nanotowers and attributed it to the periodical axial and continuous lateral growth interaction, where the former was first guided by Au-In alloy liquid, and subsequent by self-catalytic In droplets (MP 156C) while the latter due to VS process. In contrast, \citeauthor{Yan2007} observed similar \ce{In2O3} nanotower growth and proposed that the axial growth is controlled by Au-catalytic VLS process. \citeauthor{Xiao2012} reported the GaN nanotower grown on Ni-coated Si(111) substrates and explained the growth as asymmetric self-copy process based on VLS mechanism. \citeauthor{Zhang2013c} studied the growth of ZnO nanotower and provided a competitive model between axial and lateral growth controlled by Zn vapor to explain the as-synthesized structures. (When ZnO and carbon mixture was used as source instead of ZnO alone, nanorods array results, presumably due to the stable supply of Zn vapor owing to the gentle carbothermal reduction.) Therefore the fluctuation of reagents is probably responsible for tapering and periodical modification, which is absent in the coin roll style growth of \ce{MoO3} tower on Si. The occasionally observed tapering or enlarging on \ce{MoO3} tower can be attributed to the cooling down growth.  An oxygen regulated growth will be conducted to reveal the role of vapor pressure during the formation of tower.

long belts  is also found on Mica(\ce{K(Al2)(Si3Al)O10(OH)2}), the formation probably arise from Potassium-catalyzed VLS mechanism.\cite{Hu2011}

\subsubsection{time stepwise growth}

With time stepwise growth, the following results were obtained:

\begin{enumerate}
\item When no Mo powder is used, NaOH still hold onto substrate with some locations exhibiting etching.
\item When no Mo powder is used while growth is performed in an old tube or oxygen flow is limited to a extreme small value, circular droplet-like solid were found and Mo, Na and O were detected, suggesting the existence of VLS mechanism. Using Moly coated substrate and subsequent NaOH treatment, similar droplets formation was repeated. No discernible XRD pattern emerged, illustrating the amorphous nature of liquid catalyst.
\item 1mins growth shows plates in high temp end and irregular shapes in low temp end.
\item 15mins growth shows \ce{MoO3} plates parallel to substrate, with some belts emerging and growing out of the substrate plane. This is presumably due to the growth direction mismatch between different plates. Morphology will also depend on local NaOH concentration. NaOH trace mark turns into connected plates at the original locations, showing the high concentration mediated the morphology evolution. The possible catalyst solid was sitting on the top of plate layer. Also some belt-like growth is visible on reaction chamber walls, suggesting the evaporation and transport of \ce{NaxMoO3} vapor phase;
\item 30mins growth:  belts growth begin (500 microns long, grow rate is estimated to be 0.5 $\mu m/s$), tower structures show up as well, but much less than belt. Two kinds of belts found, tapering and non-tapering. The former one seems to have droplets mostly associated with sidewalls of the top part.
\item In reduced time or less oxygen supply growth, Na-containing site was found located onto the sidewall of belts instead of the usual expected tip. XRD pattern indicated the existence of \ce{NaxMoO3} phase. And MoO3 XRD pattern is dominated by (0k0) peaks, indicating a 2D layer-by-layer growth with lateral rate exceeding that of axial direction.
\item 2hr growth: there are crossed tapering belts at downstream boundary, with more than one droplet located along the interface of two perpendicular belts, EDX confirmed high Na content.
\item The tower is paled along $\langle010\rangle$ direction, and the belt growth direction is $\langle001\rangle$.
\item Using NaOH treated hydrophobic substrates, dense tower array growth was found along the edge areas or molten periphery of droplets, where 5 mins growth already show the initial stage of tower with diameter about 1 $\mu m$, which increase to 10 $\mu m$ in prolonged growth.
\end{enumerate}

We divide the growth into two stages according to the emerging time of long belts and towers. In first stage the growth is dominated by lateral growth, as illustrated in . In the second stage, \ce{NaxMoO3} is evaporated and recondensed in the low temperature region, and some droplet will form, and when at proper locations, introduce secondary VLS growth.

In first stage, the Na-Mo-O liquid is formed and have much more higher absorption rate than that of bare substrate. The absorbed species will diffuse along the surface and inside the liquid. It was difficult to estimate which diffusion path one is faster. When the size of liquid is smaller than some critical size, there is no preferred growth direction. This changed when the precipitated solid exceeds certain critical dimension, and the morphology evolution is then determined by the relative size of already formed solid and its liquid catalyst.

The overall reactions probably occur in the following sequences.
First, Mo powder is oxidized and \ce{MoO3} vapor is produced and transported to downstream by Ar carrier gas. Then,
\begin{align}
\cee{NaOH(l) + MoO3(g) -> Na2MoO4(l) + H2O(g)}
\end{align}

The melting point of \ce{Na2MoO4} is 687 \si{\degreeCelsius}. Based on the open air temperature profile (Fig.~\ref{fig:mooxgrowth}), the substrate is locate in temperature zone between 650 and 400 \si{\degreeCelsius}. The temperature distribution is different due to both the sealed condition and thermal conduction along the Si substrate. It will be difficult to acquire the accurate values along the substrate. However by considering the flow rate, the actual temperature will be higher than predicted by open air measurement.\cite{Subannajui2010} The melting of \ce{Na2MoO4} is highly possible when taking into account of its size as well. \cite{Bruggemann1997}

\begin{figure}[htb]
\centering
\includegraphics[width=0.6\textwidth]{Na2MoO4_Phase}
\caption[Phase diagram of Na-Mo-O]{Phase diagram of \ce{Na2MoO4} and \ce{MoO3} reproduced from ref.~\cite{Hoermann1929}}
\label{fig:pd}
\end{figure}

According to the phase diagram shown in Fig.~\ref{fig:pd}, \ce{Na2MoO4} - \ce{MoO3} phase above 800 \si{\degreeCelsius} are \ce{Na2MoO4}(l) + \ce{MoO3}(l), More discussion should follow $\ldots$.

Each site of \ce{Na2MoO4} will continue absorb incoming \ce{MoO3}, forming a swelling droplet. \ce{MoO3} will precipitate from these seeds when a critical supersaturation concentration is reached, which is about 75\% according to Fig.~\ref{fig:pd}.\footnote{This ratio considerably exceeds that of the usual metal catalyst scenario. This high solubility accounts for several observations in our experiments: the dimensions of individual deposit is much larger than that of initial droplet, the concentration of sodium in final products is extremely low.}

As shown in Fig, we found several solid clusters with diameter about 1 $\mu m$ on the top part of long belts. According to the \ce{Na2MoO4}-\ce{MoO3} binary compounds phase diagram, we expect the terminating solid clusters have a Na:Mo ratio close to 0.6. The experimental results match well with this predictions. EDX analysis reveal the presence of Na on the solid cluster but not at about 1$\mu m$ away from previous location.\footnote{the sensitivity of our instrument is estimated to be 1\% atomic leve} Quantitative atomic ratio derived from the solid cluster is not close to the one predicted by phase diagram probably due to the high Mo content in adjacent area. However, XRD examinations on a short time growth sample revealed a possible \ce{Na2Mo4O13} phase(PDF 028-1112), providing an indirection evidence of the droplet composition.

We also suspect that the growth will become different below 500 \si{\degreeCelsius} since no liquid would remain. Substrate placed at low temp end show.

We can also deduce that other sodium compounds can be employed as substrate treatment agent. This argument is confirmed by \ce{Na2CO3} and \ce{KI} assisted growth.

Nanotower is a less common morphology in the structures of nanomaterials.\cite{Kharissova2010} We have not found report on  \ce{MoO3} nanotower structures, although there are several studies on \ce{In2O3},\citep{Jean2010,Yan2007}, GaN\cite{Xiao2012} and ZnO\cite{Zhang2013c}. \citeauthor{Jean2010} investigated the growth mechanism of \ce{In2O3} nanotowers and attributed it to the periodical axial and continuous lateral growth interaction, where the former was first guided by Au-In alloy liquid, and subsequent by self-catalytic In droplets (MP 156C) while the latter due to VS process. In contrast, \citeauthor{Yan2007} observed similar \ce{In2O3} nanotower growth and proposed that the axial growth is controlled by Au-catalytic VLS process. \citeauthor{Xiao2012} reported the GaN nanotower grown on Ni-coated Si(111) substrates and explained the growth as asymmetric self-copy process based on VLS mechanism. \citeauthor{Zhang2013c} studied the growth of ZnO nanotower and provided a competitive model between axial and lateral growth controlled by Zn vapor to explain the as-synthesized structures. (When ZnO and carbon mixture was used as source instead of ZnO alone, nanorods array results, presumably due to the stable supply of Zn vapor owing to the gentle carbothermal reduction.) Therefore the fluctuation of reagents is probably responsible for tapering and periodical modification, which is absent in the coin roll style growth of \ce{MoO3} tower on Si. The occasionally observed tapering or enlarging on \ce{MoO3} tower can be attributed to the cooling down growth.  An oxygen regulated growth will be conducted to reveal the role of vapor pressure during the formation of tower.

\textbf{open questions}
\begin{itemize}
\item Is the liquid consumed? if so, how? : evaporation
\item How the size of liquid is related to the morphology evolution?
\item Possible doping level of alkaline ions
\item other lateral growth mode such as Ni-W-S system
\item VLS-VS interaction, or possible solution-liquid-solid, VSS,
\item the interpretation of phase diagram
\item the overall molar amount of NaOH and MoO3 deposition
\item Young's parameters, contact angle informations, Gibbs free energy calculation
\item catalyst composition variation during growth
\end{itemize}

### 2014-01-26 ch-wox/ch-wox.tex
add rest of tex

%\input{../header.tex} %  comment out when assembling

\chapter{tungsten oxides}

\section{Introduction}

Tungsten oxide (\ce{WO_x}) is an important functional materials with distinctive properties and technology applications. Intense research interest was rekindled by the discovery of \gls{ec} effect in \citeyear{Granqvist1993}.\cite{Granqvist1993}  Nano-engineering \ce{WO_x} bring more possibility and flexibility to its already rich characteristics, therefore resulting research efforts spanning multiple fields of scientific community. Besides smart window based on EC effect, \ce{WO_x} is also well investigated for several other significant applications: photoelectrochemical cell for solar energy conversion and storage, photocatalysis for hydrogen evolution reaction, chemical and biological sensing based on gasochromic effect. In addition, a few young fields are not thoroughly explored: field emission, optical storage, thermoelectrcity, ferroelectricity, and superconductivity.

In this chapter, we will first review the literature to date for both \ce{WO_x} and \ce{Na_xWO3}, then divide the summaries into a) technological application, b) crystal structure and electronic properties and c) synthesis approaches. Then we present our growth methods and results. And we conclude with a brief summary.

\subsection{Rich and useful technological appeals}

Electrochromic effect of tungsten oxide means the coloration (deep blue) and bleaching (transparent) states of \ce{WO3} are reversibly switched upon forward and backward voltage, and the coloration or bleached states remain after disconnecting the voltage. On basis of this property, \gls{ecd} of tremendous energy saving potential is conceptualized and some products have already been commercialized (i.e. smart window\footnote{``We did a case study in five cities, and the average savings in commercial buildings are about 25 percent of the heating, ventilation, and air-conditioning energy use annually," says CEO of View, Inc.}).

In the past decades, tons of works have been devoted to understanding the chromogenic phenomena in \ce{WO3}. We highlight several key results as reviewed by ,
\begin{itemize}
    \item coloration and bleaching can also be stimulated by other routes, such as by UV irradiation, thermal treating, heating in vacuum, reducing atmosphere etc
    \item no electrical coloration occurs in vacuum, but other routes still works
    \item coloration is associated with a proportional increase in conductivity
    \item coloration spectrum is essentially similar in all cases except small variation in peak position and FWHM
    \item coloration is structure sensitive and most efficient in amorphous films
\end{itemize}

Sofar there is no unifying model that could reconcile these contradictory experimental observations. Among all the developed models, polaronic absorption is the most widely accepted mechanism for coloration. In polaron model\footnote{When a free electron travels through a polar solid, it creates a local lattice displacement (longitudinal optical phonon clouds) due to the coulombic interaction with neighboring ions. This local distortion and the electron together is equivalent to a new elementary exciton of the crystal, and is named as polaron}, the intercalation of \ce{M^+} (M = H, \ce{Li}, or Na) ions into \ce{WO3} films is accompanied with the formation of small polarons ($r_p$ comparable to unit cell size) and formal reduction of some \ce{W^{6+}} sites to \ce{W^{5+}}, as depicted in Eq.~\ref{eq:ec}. During the intercalation process, the \ce{M^+} ions enter into these vacant sites.\cite{Hepel2008} Coloration occurs when the polaron band .

\begin{align}\label{eq:ec}
x\ce{M+} + x\ce{e-} +  \ce{$\alpha \hyphen$WO$_{3-y}$}= \ce{$\alpha \hyphen$M$_x$WO$_{3-y}$},
\end{align}

And the polaron binding energy ($E_p$) is given by
\begin{align}
E_p = - \frac{e^2}{2r_p} (\epsilon_\infty^{-1} - \epsilon_{st}^{-1}),
\end{align}

where $\epsilon_\infty$ and $\epsilon_{st}$ are optical and static dielectric constants respectively, and polaron radius $r_p$, which specifies how far the lattice distortion extends, is related to polaron density $N_p$ by $r_p = \frac{1}{2}\sqrt[3]{\pi/6N_p}$. However, the polaron model has difficulty in estimating $r_p$. The asymmetric optical absorption spectrum are often characteristic of large polarons, and dielectric constants ($\epsilon_\infty = 6.52,\epsilon_{st} > 50$,\cite{Deb2008}) suggests the formation of bipolaron. Moreover, polaron model does not take oxygen vacancy into account, which plays a vital role in the nonstoichiometric tungsten oxides. For instance, it is observed that \ce{WO_{3-y}} films are metallic and conductive for $y > 0.5$, blue and conductive for $y = 0.3 \sim 0.5$, and transparent and resistive when $y < 0.3$, regardless of the preparation methods.\cite{Chatten2005}

Therefore another model in analogy to the F-color center is proposed. Color center model assumes the presence of oxygen vacancy $V_O^0$ is associated with \ce{W^{4+}} or 2\ce{W^{5+}} states. This defect level is expected to be inside or near the valence band. When one electron is removed from this level, $V_O^0$ is converted to $V_O^+$.The positively charged vacancy exerts coulombic repulsion to the nearest W-ions, which results in a displacement of the neighboring W-ions and an upward shift of the defect level into the bandgap, thereby creating a color center. The optical transition from $V_O^+$ to $V_O^{2+}$ (a state within the conduction band)
contributes to coloration.\cite{Deb2008}

So the polaron and color center models both agree on that \ce{W^{5+}} and its transition is responsible for the coloration, but disagree on how this \ce{W^{5+}} state is created (foreign ion reduction in polaron model and oxygen vacancy in color center model) and the corresponding energy levels. A modified polaron model is proposed to include \ce{W^{4+}} states in host lattice. Coloration mechanism is represented by Eq.~\ref{eq:cl_bl1} and \ref{eq:cl_bl2}, which described the polaron hopping from one site to another.\cite{Chatten2005}

\begin{align}
h\nu +\ce{W^{5+}(A)} +  \ce{W^{6+}(B)} &\rightarrow \ce{W^{5+}(B)} + \ce{W^{6+}(A) + E_{phonon}} \label{eq:cl_bl1}\\
h\nu +\ce{W^{5+}(A)} +  \ce{W^{4+}(B)} &\rightarrow \ce{W^{5+}(B)} + \ce{W^{4+}(A) + E_{phonon}} \label{eq:cl_bl2}
\end{align}

Similar scenarios occurs in the gasochromic effect. Two models, double injection and color center, arise to account for the coloration upon exposure to certain gases. Both consents to Eq.~\ref{eq:cl_bl1}. But there is a disagreement on the final states. Double injection supports the formation of tungsten bronze \ce{H_xWO3} while color center insists on the inward diffusion of oxygen vacancy and outward diffusion of water molecules. Both have been substantiated experimentally. Therefore the exact mechanism in \ce{WO_x} still requires further investigation. The author believes the resolution to a large extent depends on the phase transitions, as discussed in Section.~\ref{sec:wonawo}.

photocatalytic applications in solar hydrogen generation and organic pollutant degradation.

photocatalyst\cite{Macphee2010}, photoelectrochemical energy application \cite{Su2010}

Photocatalytic activity occurs when a semiconductor in aqueous solution is illuminated by photons of energy larger than the band gap, then electron-hole pairs generate free radicals, (i.e. \ce{OH.}) which enable further reactions. For water splitting using solar energy, the band gap should be within $2.0 \sim 3.0 $ eV, and CB edge should be more negative than reduction potential of \ce{H^+/H2}, whereas the VB top should be more positive than the oxidation potential of \ce{H2O/O2)}.\cite{Wang2012} The valence band holes (\ce{h^+}) oxidize water to oxygen and conduction band electrons propel hydrogen generation, as depicted in Eq.~\ref{eq:hervb} and \ref{eq:hercb}.

\begin{align}
4\ce{h^+} +  \ce{H2O} &\rightarrow \ce{O2} + 4\ce{H^+} \label{eq:hervb}\\
4\ce{H^+} +  4e^- &\rightarrow 2\ce{H2} \label{eq:hercb}
\end{align}

As shown in Fig.~\ref{fig:woxnhe}, \ce{WO3} has CB edge positioned slightly more positive than reduction potential of \ce{H^+/H2}(versus \gls{nhe}), and VB edge much more positive than the oxidation potential of \ce{H2O/O2}. So the photo-cleavage of water cannot be accomplished by \ce{WO3} alone. Nevertheless, a tandem cell approach by \ce{WO3} film and dye-sensitized \ce{TiO2} has been demonstrated with an efficiency of 4.5\%.\cite{Michael1999} It is worth noting that green plants also have two photosynthetic systems connected in series, one for oxidation of water into oxygen and the other for fixation of carbon dioxide.

% wo3 vs NHE 
\begin{figure}[htb]
\centering
\includegraphics[width=0.7\textwidth]{woxnhe.jpg}
\caption[Bands positions of \ce{WO3} versus NHE]{Bands positions of \ce{WO3} in contact with aqueous electolyte at pH 1. adapted from Ref\cite{Gratzel2001}}
\label{fig:woxnhe}
\end{figure}

Moreover, favorable oxygen evolution of \ce{WO3} brings good performance in degradation of organic compounds\cite{Hepel2001,Luo2001,Watcharenwong2008}. The formation of long-lived holes is recognized as a key requirement.\cite{Pesci2011} Besides, \ce{WO3} is remarkably stable in acid, making it a significant candidate for treating water pollutant caused by organic acids.\cite{Monllor-Satoca2006}

the ubiquity of \ce{WO6} octahedra is essential for not only the optical properties but the ability to insert and extract ions in the EC oxides, due to the tunnels in three dimensions serving as path for transport of small ions.
The intercalation of hydrogen or alkali ions into \ce{WO3} created electron donor level. By absorbing the red part of incident spectrum, electrons at donor level make transition to the conduction band, causing the blue coloration in \ce{H_xWO3}.

\citeauthor{Wang2009a} mentioned that amorphous \ce{WO3} can only be used in lithium-based electrolytes due to its
in-compact structure and high dissolution rate in acidic electrolyte solutions. Electrochromic materials that can endure acidic electrolytes without degradation should be developed. Crystalline \ce{WO3} nanostructures with their much denser structures and small particle sizes are promising to be used as suitable electrochromic material in acidic electrolytes.

Characterization of ECD (work like a thin-film batteries) includes transmission measurement and associated EC calculation, charge-discharge time, current-time curve and the fitting of obtained data.

The coloration efficiency (CE) represents the change in the optical density (OD) per unit charge density ($Q/A$, in units of \si{\cm^2\per\coulomb}) during switching and can be calculated according to the formula:
\begin{equation}
CE = \frac{\Delta~OD}{(Q/A)} [cm^2/C],
\end{equation}
where OD = $log(T_{bleach}/T_{color})$. The EC and optical density depend on the wavelength and are usually higher in the near IR than in the visible region.
Using Ohm's law($U_s = IR = RQ/t_s$) with switch voltage $U_s$, resistance R and surface area A, switching time $t_s$ could be estimated as
\begin{equation}
t_s = \Delta~OD\cdot A \cdot R /(CE\cdot U_s).
\end{equation}

its one dimensional (1D) nanostructure has attained intensive research efforts in recent years due to the potential applications in advanced nano-electric and nano-optoelectronic devices.

\begin{quote}
a viable electrochromic smart window must exhibit a cycling life time \textgreater $10^5$ cycles, corresponding to an operation life at 10 - 20 years.
\end{quote}

\subsection{Crystal structures and properties of tungsten oxides and sodium tungsten oxides}\label{sec:wonawo}

\textbf{\ce{WO3}} Tungsten trioxides crystalize in multiple phases. The basic building block is \ce{WO6} octahedra.\footnote{Tungsten, with its electronic configuration as \ce{(Xe)4f^{14}5d^{4}6s^{2}}, has empty 5d and 6s orbitals in its +6 oxidation state.} \ce{WO3} crystal structure consists of \ce{WO6} octahedra joined at their corners, which may be considered as a perovskite structure of \ce{CaTiO3} with all \ce{Ca^{2+}} sites vacant. A representative lattice structures is illustrated in Fig.~\ref{fig:wo3oct}. These distorted \ce{WO6} octahedra adapts different tilting angles in different phases and edge-sharing octahedra also arises. The temperature-dependent phase transition and corresponding lattice constants in bulk form is summarized in Table.~\ref{tab:wo3phase}.\cite{Zheng2011} And a firm assignation of space group to monoclinic phases are still in debate.\cite{Chatten2005} It is noticed that the lattice parameters obtained via \emph{ab initio} calculation closely match the experimental values.\cite{Migas2010a} The phase transition scenarios in nanostructured \ce{WO3} are supposed to be much more sophisticated. Within Gibbs-Thomson frame work, one can generally expect lower transition temperature than their bulk counterparts due to enhanced surface energy. Temperature-dependent Raman spectroscopy provided support for this deduction.\cite{Boulova2002}

% wo3 phases
\begin{table}[htb]
\centering
\caption{\ce{WO3} phases}\label{tab:wo3phase}
\begin{tabular}{lccccc}
\toprule
\multicolumn{5}{c}{Lattice constants \AA} \\
\cmidrule(l){4-6}
 Symbol    & Temperature (\si{\degreeCelsius}) & Phase & a & b & c   \\
\midrule
$\epsilon$-\ce{WO3} & $ -140 \sim -50$  & monoclinic II & 7.378 & 7.378 & 7.664  \\
$\delta$-\ce{WO3} & $-50 \sim 17$  & triclinic & 7.309 & 7.522 & 7.686  \\
$\gamma$-\ce{WO3} & $17 \sim 330$  & monoclinic I & 7.306 & 7.540 & 7.692  \\
$\beta$-\ce{WO3} & $330 \sim 740$  & orthorhombic & 7.384 & 7.512 & 3.846  \\
$\alpha$-\ce{WO3} & $> 740$  & tetragonal & 5.25 & NA & 3.91  \\
$h$-\ce{WO3} &  $<400$  & hexagonal & 7.298 & NA & 3.899  \\
\bottomrule
\end{tabular}
\end{table}

\begin{figure}[htb]
\centering
\includegraphics[width=0.4\textwidth]{octwo3.jpg}
\caption[Octahedra model of \ce{WO3}]{Octahedra model of \ce{WO3}}
\label{fig:wo3oct}
\end{figure}

\ce{WO3} is wide gap n-type semiconductor with valence band top featuring $2p$ states of oxygen and conduction band bottom arising primarily from $5d$ states of tungsten with some mixing of oxygen $2p$ states.\cite{Gillet2004} \citeauthor{Migas2010a} maintained there is essentially identical band dispersion near the gap region in case of $\epsilon$-\ce{WO3}, $\delta$-\ce{WO3}, $\gamma$-\ce{WO3} and $\beta$-\ce{WO3}.\cite{Migas2010a} When there is oxygen vacancy, the Fermi level moves into the conduction band and the gap shrinks by about 0.5 eV. \citeauthor{Migas2010a} also pointed out the flat bands at VBM and CBM could lead to poor transport of holes and electrons, thus may compromising the function in photoelectrochemical cells.

 \citeauthor{Chatten2005} also studied the oxygen vacancy in different phases of \ce{WO3}.\cite{Chatten2005}

Nonstoichiometric tungsten oxides \ce{WO_x} (i.e. \ce{WO_{2.92}}, \ce{WO_{2.87}}) are known as Magn$\acute{e}$li phases.

We do not discuss tungsten oxide hydrates (\ce{WO3.nH2O}) in this work since the product of thermal CVD approach is not plagued with this complexity. It's necessary, however, to deal with hydrated \ce{WO3} in the liquid synthesis routes, as indicated in Section.~\ref{sec:woxgrowth}.

Theoretical computation of electronic band structures for \ce{WO_x} proves difficult due to the aforementioned phase transition.

 oxygen deficiency, structure change, electronic properties vary according.

% band gap table
\begin{table}[htb]
\centering
\caption{Tungsten oxides band gap }\label{tab:wo3eg}
\begin{tabular}{lccr}
\toprule
Phase & Experimental (eV) & Theory (eV) & Remarks  \\
\midrule
amorphous \ce{WO3} & 3.2  & NA &    \\
monoclinic bulk \ce{WO3} &  2.6   & 1.73\cite{Migas2010a}  &    \\
tetragonal bulk \ce{WO3} &     & 0.66 \cite{Migas2010a}&    \\
nano-\ce{WO3} & 2.6$\sim$3.2  & NA &    \\
nano-\ce{WO_{3-x}} & NA  & NA &    \\
\bottomrule
\end{tabular}
\end{table}

Tungsten bronzes was coined by Wohler in 1837.\cite{Deb2008} \ce{Na_{x}WO3}

\subsection{Synthesis strategies}\label{sec:woxgrowth}

We will first give a brief review on the synthesis of \ce{WO3}. As the chemical formula suggested, the most straightforward way is heating metallic tungsten in various forms (i.e. powders,\cite{Zhou2005a,Cao2009,Hsieh2010} foils and wires). Actually \ce{WO_x}\footnote{$x$ is between 2 and 3.} NWs was observed when directly heating W wires.\cite{Gu2002a} Due to the extreme high melting point of W, it requires very high temperature (say, above 1100 \si{\degreeCelsius}) to produce large amount of growth species. Therefore scalable growth seems difficult. The DC current heating proved to be a route with potential large yield. Tungsten wire or filament is connected to a voltage source, and substrate is positioned in proximity to the heated W wire. \cite{Lingfei2006,Thangala2007,Chang2007}

Tungsten oxides powder can also been used as precursor to prepare \ce{WO_{x}} \glspl{nw}.\cite{Huang2008a,Wang2009} Hydrogen-containing agents (i.e. water, \ce{H2},or methane\cite{Klinke2005}) were often involved into the reaction.\cite{Baek2007,Karuppanan2007} The potential benefit is \ce{WO3} has a much lower melting point ($\approx 1470$\si{\degreeCelsius}) than that of W.

Direct oxidation and \ce{WO3} conversion could be grouped as addition approach. In contrast, decomposition method is also feasible.
\citeauthor{Pol2005} obtained \ce{W18O49} nanorods by thermal dissociation of \ce{WO(OMe)4} at 700 \si{\degreeCelsius}, and \ce{WO3} by the annealing at 500 \si{\degreeCelsius} at air atmosphere.\cite{Pol2005}

Spray pyrolysis is a typical aerosol-assisted CVD technique. Typical process flow is: the precursor solution is pumped to an atomizer, and then sprayed through the carrier gas as a fine mist of very small droplets onto heated substrates. Subsequently the droplets undergo evaporation, solute condensation, and thermal decomposition, which then result in film formation.\cite{Zheng2011}

Main reactions include: \cee{W + O2 -> WO_{3-x}} \cee{W + H2O -> W_{3-x} + H2}

the energetic sources are ion bombardment, electron beam, laser ablation, and combustion flame\cite{Rao2011}.

The sol–gel process is a well-known, intensively studied wetchemical technique that is widely used in materials synthesis. This method generally starts with a precursor solution (the ``sol") to form discrete particles or a networked gel structure. During the course of gelation (aging process), various forms of hydrolysis and polycondensation take place.

Hydrothermal method has been an important route to synthesize a diversity of nanomaterials (i.e. ). Preparation of \ce{WO_{3-x}} has also been demonstrated hydrothermally.\cite{Lee2003,Gu2007} Usually, the precursor (\ce{H2WO4}) is mixed with other reactants (sulfides or certain organic acid) in solution and pH value is adjusted as another control degree of freedom. Then the solution is transferred into a sealed container (i.e. Teflon autoclave) and maintained at elevated temperature ($120 \sim 300$ \si{\degreeCelsius}) for tens of hours. Finally the product is separated from the solution and dried, layered \ce{WO3.nH2O} flakes are usual products.

In addition, doped \ce{WO3} was also demonstrated

 The composition and phase of final product highly depend on the synthesis conditions.

%\newgeometry{margin=1in}
\begin{landscape}
\begin{table}[htb]
\centering
\caption{Tungsten Oxides Growth and Application}\label{tab:wox}
{\footnotesize
\begin{tabular}{lp{3.5in}p{2.5in}c}
\toprule
composition  &  methods & highlights &  reference  \\
\midrule
\ce{WO3} & hot W filament (above 1500 \si{\degreeCelsius}) in Ar/\ce{O2} flow  & Cubic phase, PL, resistivity measured & \cite{Thangala2007} \\
\addlinespace[0.5em]
& W filament DC heating in \ce{NH3} or \ce{N2}/\ce{H2} flow  & multi phases, 100mg per batch, stable dispersion in both organic and aqueous solvents & \cite{Chang2007} \\
\addlinespace[0.5em]
& W powder heating Ar/\ce{O2} flow  & triclinic phase, CL at 370,415nm, UV-Vis, 3eV & \cite{Hsieh2010} \\
\cmidrule(l){2-4}
& \ce{WOx} film in \ce{H2} and \ce{CH4} flow  & monoclinic phase, tungsten carbide is the key & \cite{Klinke2005} \\
\cmidrule(l){2-4}
& \ce{Na2WO4.2H2O} by hydrothermal heating to test for line break & 3 different morphologies and photodegradation & \cite{Rajagopal2009}  \\
& \ce{H2WO4.2H2O}, \ce{H2O2} and poly(vinyl alcohol) etc by solvothermal  & multi phases deposition of FTO with varied bandgaps  & \cite{Su2010}  \\

\midrule
\ce{W18O49} & \ce{KOH} etching of W tips followed by heating in Ar flow  & oxygen from leakage, VS process& \textcite{Gu2002a} \\
\addlinespace[0.5em]
& \ce{NW(CO)6}, \ce{Me3NO.2H2O} and oleylamine by hydrothermal  &  RT PL at 350nm and 440nm & \cite{Lee2003}  \\
\bottomrule
\end{tabular}
}
\end{table}
\end{landscape}
%\restoregeometry

\section{growth method and results discussion}

Tungsten powder were used as source material, and named as W3N (Alfa, -325 mesh, 99.9\%, metal basis) by the author. The sodium concentration was 20ppm.\footnote{detection of sodium by EDS is possible although the concentration is below the limit of typical EDS capacity due to the non-uniform distribution of foreign elements} The substrates were p-type, boron-doped and [100]-orientated silicon with about 1 $\mu$m thermally-grown silicon oxide layer on the polished side (U.Wafer). The one-side polished substrates were first cut into rectangular pieces of 10mm by 35mm, and then ultrasonically cleaned with acetone and alcohol for about ten minutes, each followed by the blow drying with nitrogen.

In a typical growth experiment, about 2g tungsten powder was positioned in the upstream of the quartz boat and downstream about 2.5 inches the substrate was stationed. The boat was then loaded into a 1-inch diameter quartz tube in a way that the powder source was placed in the middle, and the substrate low temperature end was aligned with tube edge. After pumping down, 1 \gls{sccm} (SCCM denotes cubic centimeter per minute at STP) \ce{O2} and 10 sccm Ar were admitted into the tube respectively, after which the overall pressure read approximately 110 mTorr. The temperature ramped to 1000 \si{\degreeCelsius} in half an hour and lasted for 4 hours, and subsequently the system was allowed to naturally cool down to room temperature.

\subsection{Results on Sodium Tungsten Oxides}

The SEM images of powder a) before growth and b) after growth.

\subsection{Results on Seeded Growth}

\section{summary}

%\printbibliography  %  comment out when assembling
%\input{../end.tex} %  comment out when assembling

### 2014-01-26 misc/mwe.tex
add rest of tex

--- 2014-01-26 ch-moox/moox.tex
@@
-\chapter{Molybdenum Oxides}
+\documentclass[12pt,oneside]{book}
+ %
+   \usepackage{uncc-thesis} % some format specifications define page number in up right corner
+   \input{package.tex} % additonal packages and tweaking
 
-\section{Introduction}
+   \newacronym{cvd}{CVD}{chemical vapor deposition}
+   \newacronym{cft}{CFT}{crystal-field theory}
 
-Molybdenum oxides \ce{MoO3} crystallizes in three phases, orthorhombic $\alpha$-\ce{MoO3}, monoclinic $\beta$-\ce{MoO3} and the metastable hexagonal h-\ce{MoO3}.\citep{Deb1968,Fibers2007} $\alpha$-\ce{MoO3} phase exhibits anisotropic structure with strong bonding along [001] and [100] direction while Van der Waals interaction along [010] direction.\cite{He2003} Due to this unique structure, \ce{MoO3} was found to have several important properties and a wide range of technological applications, such as electrochromism and photochromism,\cite{Yao1992} lubricants,\cite{Sheehan1996} photocatalysts,\cite{Chen2010} and gas sensor, including \ce{CO},\cite{Comini2005} \ce{NO2},\cite{Taurino2006} \ce{H2}\cite{Sha2009} and ethanol.\cite{Choopun} Moreover, other features arise when nanoscale \ce{MoO3} is specifically prepared, for instance, field emission.\citep{Li2002d,Zhou2003b}  As a layered hosting material, \ce{MoO3} can be further modified by intercalating with alkaline ions\citep{Spahr1995,Li2006b,Hu2011} and even divalent ion\cite{Sian2005}.
-This structural richness have enabled improved performance in Li-ion\cite{Mai2007} and sodium-ion battery.\cite{Hariharan2013} In combination with \ce{TiO2} forming a core-shell structure, these nanoparitcles are reported to lower the photoabsorption energy of \ce{TiO2}.\cite{Elder2000} When combined with Ag as layered structure, transparent conducting behavior was observed.\cite{Nguyen2012} In addition, \ce{MoO3} is a good precursor for preparing other useful materials, such as \ce{MoS2} fullerenes\cite{Li2003c}, and few layer \ce{MoS2}.\cite{Lin2012}  It will also be an important member of the Van der Waals heterostructures.\cite{Geim2013}
+   \makeglossaries
 
-It may be considered as built up of chains of \ce{MoO4} tetrahedra connected by the sharing of two oxygen corners with two neighbouring tetrahedra in $c$ axis.
-The infinite chains of \ce{MoO4} tetrahedra from half-layers in the $ac$ plane.
-Two half-layers, which are stapled along $b$ axis, build up one \ce{MoO3} layer.
-When the two more distant oxygen are included for one molybdenum atom, the coordination can be regards a sixfold, i.e,, the layered structure consisting of zig-zag rows of edge-sharing \ce{MoO6} octahedra, while the rows are mutually connected by corners.\cite{Itoh2001a}
+\begin{document}
 
-on \ce{MoO3} reviews.\cite{He2003}
+  \title{\LaTeX is great}
+  \author{me}
+  \maketitle
 
-\citeauthor{Chithambararaj2013} prepared hexagonal \ce{MoO3} nanocrystal via hydrothermal method  and demonstrated the photodegradation of MB under visible light.\cite{Chithambararaj2013} The efficiency dependence on catalysis/dye ratio, light intensity and temperature was studied.
-h-\ce{MoO3} was mostly synthesized using solution methods, where \ce{NH4+} and \ce{OH.} were possible structure directing and stable agents.
-The band gap of h-\ce{MoO3} estimated from diffusion reflection spectrum is $2.8\sim3.0eV$.
+    \clearpage
+    \tableofcontents
+    \clearpage
+    \listoftables
+    \clearpage
+    \listoffigures
 
-Hexagonal phase \ce{MoO3} is readily identified by the XRD pattern (strong peak at $2\theta=20^{\circ}$).
+    \begin{singlespace}
+    %\thispagestyle{myheadings} % before, this does not work
+    \renewcommand{\glossarypreamble}{\thispagestyle{myheadings}} % after, this works.
+    \printglossary[type=\acronymtype]
+    \clearpage
+    \end{singlespace}
 
-\section{Syntheses Methods}
-\subsection{literature review}
+ %   \include{./ch-intro/ch-intro}
 
-\subsection{this work}
-\textbf{Substrate treatment.} Silicon substrates(p-$\langle100\rangle$, University Wafers) were first cut into 10mm by 25mm pieces and ultrasonically cleaned with acetone and ethanol for 15 minutes(Branson 1510R-MTH), each followed by blow-drying with nitrogen gas.
-Then the substrates were selectively treated in an oxygen plasma cleaning apparatus(Kurt J Lesker: Plasma-Preen 862, 2Torr) for 3 minutes to increase the wettability.
-The substrates without plasma cleaning were rendered as hydrophobic.
-Finally, the substrate was drop-cast 54 $\mu$L 10 mM \ce{NaOH} (or \ce{KI}, \ce{Na2CO3}) and naturally left dry in a convection hood with a flask cover above.
-Other alkaline ions-containing substrates, such as glass (Fisher Scientific, microscope slide, 12-549) and indium tin oxide (ITO) coated glass(Delta Technologies, 25\si{\ohm}), were cleaned by the same routine except the absence of plasma cleaning and subsequent aqueous solution dipping.
-Mica was cleaved right before growth without other treatment.
-
-\textbf{Synthesis.} In a typical synthesis, molybdenum powders were loaded into the uniform heating zone and the sealed chamber was first pumped down to 10 mTorr.
-Then oxygen flow varying between 0.1 sccm to 10 sccm (standard cubic centimeter per minute) was admitted from upstream inlet.
-With 10 sccm UHP Ar(99.999\%)as carrier gas, the overall pressure reached about 200 mTorr.
-The heating temperature was ramped up to 800 \si{\degreeCelsius} in 30 minutes and lasted for 15 to 120 minutes.
-Then the heating power was turned off and the chamber was allowed to naturally cool down to room temperature.
-The receiving substrate was placed in downstream location where the temperature was about 400 to 670 \si{\degreeCelsius} according to open air temperature profile.
-To observe the formation of droplets, clean silicon substrate was coated with 9 nm molybdenum film using a magnetron sputter(Desk IV TSC, Denton Vacuum), followed by \ce{NaOH} dipping as described before.
-Then the substrate was placed into chamber for growth, where all the parameters remained unchanged except the absence of Mo powder source.
-
-\section{Discussion}
-
-In vapor synthesis process, two growth mechanism exists: VS and VLS.
-VS process is widely accepted for the growth of \ce{MoO3}.
-Yet we caution that synthesis conditions should be scrutinized to determine the exact mechanism.
-\citeauthor{Li2002c} suggested a VS mechanism at 700 \si{\degreeCelsius} and VLS at 750 \si{\degreeCelsius} and higher.\cite{Li2002c} \citeauthor{Fibers2007} proposed a modified VS mechanism probably because the deposition occurs on \ce{Al2SiO5} with possible \ce{Al_{0.95}SiNa_{0.06}O_x} involved.
-Therefore temperature and possible impurity could potentially alter the growth mechanism.
-We divide the growth results into two categories: on Si substrate and on non-Si substrate to describe them respectively.
-
-\subsection{Growth on Si substrates}
-
-Mo began to be oxidized into \ce{MoO3} at 500 \si{\degreeCelsius}, \ce{MoO3} vapor pressure began to increase rapidly above 700 \si{\degreeCelsius}.
-\cite{Margrave1967} And the MP of \ce{MoO3} is reported as 795 \si{\degreeCelsius}.
-With these facts in mind, we design the experimental parameters as listed in Table.~\ref{tab:mooxsi}.
-We should point out that these parameters are selected and optimized from a wide range of combinations.
-And when we discuss the influence of one parameter with different values, one should assume other parameters still adapt those listed in Table.~\ref{tab:mooxsi}.
-
-\begin{table}[htb]
-\centering
-\caption{Growth conditions of \ce{MoO3} on Si}\label{tab:mooxsi}
-\begin{tabular}{lcccr}
-\toprule
-&&&\multicolumn{2}{c}{Flow (sccm)} \\
-\cmidrule(l){4-5}
- & Temperature $T_h$ (\si{\degreeCelsius}) & Pressure  & Ar & \ce{O2}  \\
-\midrule
-typical values  & 800    & 200mTorr & 10 & 10  \\
-\end{tabular}
-\end{table}
-
-The growth layout is schematically shown in Fig.~\ref{fig:mooxgrowth}.
-Notice that on the horizontal axis of temperature, zero inch is defined at the upstream edge of furnace.
-To facilitate discussion and provide a tight context, we define the position of substrate as the coordinate of its upper-stream edge along this temperature axis (i.e.
-the substrate location is 7 inch in Fig.~\ref{fig:mooxgrowth}).
-The usual length of Si substrate is 1 inch.
-When positioned at 7 inch, it is then located in a temperature range of $650 \sim 350$ \si{\degreeCelsius}.
-
-\begin{figure}[htb]
-\centering
-\includegraphics[width=0.8\textwidth]{CVD_and_temp_MoO3.jpg}
-\caption[Growth setup of \ce{MoO3}]{Chemical vapor system and its temperature profile.
-The triangular labels $\blacktriangledown$ were measured points at ambient pressure.
-The nominal substrates temperature were estimated from interpolation data.}
-\label{fig:mooxgrowth}
-\end{figure}
-
-From previous works,\cite{predeep2011} we found that with $T_h = 600$ and substrate placed at 6.5 inches, microflakes was found at the high temperature edge of Si, suggesting the nucleation already started.\footnote{020510 batch} When flow of oxygen was gradually reduced, diminished size of micro-flake was observed at the same location of substrates.
-This results indicated the rate-determining step is diffusion when oxygen flow was in the range of 2 sccm to 0.5 sccm.\footnote{(31210-31510 batches)} We also found the deposition amount on a particular location of the substrate is not linearly proportional to the growth time, i.e., the growth at upper stream edge first increase then decrease.
-This is not surprising when considering the temperature field requires some time to become synchronized as depicted in Fig.~\ref{fig:mooxgrowth}.
-Using conditions in Table.~\ref{tab:mooxsi} and 1 hr growth, we observed the typical micro-flakes morphologies as shown in Fig.~\ref{fig:mosisem}.
-Most flakes exhibit rectangular shape, with average thickness of one micron, standard deviation $\sigma_D=0.34\mu m$.
-
-\begin{figure}[htb]
-\centering
-\subfloat[]{\label{fig:mosem1}\includegraphics[width=0.45\textwidth]{mosemsi_a}}\hspace{0.04\textwidth}
-\subfloat[]{\label{fig:mosem2}\includegraphics[width=0.45\textwidth]{mosemsi_b}}
-\caption[Representative morphologies of \ce{MoO3} on Si]{SEM images of representative depositions of \ce{MoO3} on Si. (a)Low magnification. (b) High magnification. }
-\label{fig:mosisem}
-\end{figure}
-
-This rectangular shape implies the boundary plane along growth direction (long axis) is (001), in consistency with previous experimental\cite{Zeng1998,Li2002b} and theoretical\cite{Firment1983,Cora1997} studies.
-We also observed different shapes, i.e., elongated hexagonal using similar growth conditions.
-This is not an indication of different growth mode.
-It is a normal thermodynamic fluctuation.
-In fact, (201), (101) and (102) planes have all been observed as terminating planes.\cite{Zeng1998} The stacking rate of \ce{MoO6} octahedra along a and c axis could develop some other ratio.
-And the coexistence of different planes in one growth suggests the similarity of free surface energies.
-
-\begin{figure}[htb]
-\centering
-\subfloat[]{\label{fig:moxrd}\includegraphics[width=0.45\textwidth]{xrd_moo3}}\hspace{0.04\textwidth}
-\subfloat[]{\label{fig:moram}\includegraphics[width=0.45\textwidth]{raman_moo3}}
-\caption[Crystalline phase characterization of \ce{MoO3} on Si]{(a) XRD pattern and (b) Raman spectrum of typical \ce{MoO3} on Si, $\lambda_{ex} = 532nm$.}
-\label{fig:mooxch}
-\end{figure}
-
-As shown in Fig.~\ref{fig:mooxch}, the crystal structures and phase of as-synthesized samples were examined by XRD and Raman.
-The XRD pattern (Fig.~\ref{fig:moxrd}) is readily indexed to the orthorhombic phase of \ce{MoO3} (ICDD PDF 05-0508, \emph{a}=3.9628\AA, \emph{b}=13.855\AA, \emph{c}=3.6964\AA).
-The space group is $D_{2h}^{16}(Pbnm)$.
-This crystal structure is indeed a unique example among transition metal oxides, representing a transitional stage between tetrahedra and octahedral coordination.\cite{Itoh2001a} The strongest peak index is (110), suggesting the orientation of \ce{MoO3} is not parallel to the substrate, which is consistent with the morphology displayed in Fig.~\ref{fig:mosem1}.
-In contrast, we shall see a different scenario in Section.~\ref{sec:nasi}, where the orientation is changed.
-The Raman spectrum of as-synthesized specimens also closely matches \ce{MoO3} features in previous studies.\cite{Dixit1986,Silveira2012} During m-Raman measurement, the laser spot was carefully focused onto the plates and several inspections on different positions were observed to ensure the reproductivity of spectra data.
-As shown in Fig.~\ref{fig:moram}, 14 distinct bands were well resolved.
-The 284 \si{cm^{-1}} peak represents the wagging mode for double bond \ce{O=Mo=O}.
-The 337 and 380  \si{cm^{-1}} peaks are assigned to \ce{O-Mo-O} bending and scissoring modes.
-The 199 \si{cm^{-1}} peak and two other weaker peaks at 218 and 247 \si{cm^{-1}} represent \ce{O=Mo=O} $B_{2g}$ twist, $A_g$ chain mode and \ce{O=Mo=O} $B_{3g}$ twist mode, respectively.
-667 \si{cm^{-1}} peak is assigned to triply coordinated oxygen stretching model resulting from edge-shared oxygen in common to three octahedral.
-The 819 \si{cm^{-1}} peak is from doubly coordinated oxygen stretching mode arising from corner-shared oxygen between two octahedral.
-The 996 \si{cm^{-1}} peak comes from unshared oxygen stretching mode.\cite{Siciliano2009} The assignment is summarized in Table.~\ref{tab:moram}.
-
-\begin{table}[htb]
-\centering
-\caption{Experimental Raman peaks (\si{cm^{-1}}) assignment of \ce{MoO3} on Si.\cite{Eda1992,Siciliano2009}}\label{tab:moram}
-\begin{tabular}{llcll}
-\toprule
-this work & Sym.       &          & Assignment &   \\
-\midrule
-117      & $B_{2g}$    &           & $T_c$  & RCM  \\
-129      & $B_{3g}$    &           & $T_c$  & RCM  \\
-158      & $A_g/B_{1g}$&           & $T_b$  & RCM  \\
-199      & $B_{2g}$    & $\tau$    & \ce{O=Mo=O}  & twist  \\
-218      & $A_g$       &           & $R_c$     & RCM  \\
-247      & $B_{3g}$    & $\tau$    & \ce{O=Mo=O}  & twist  \\
-284      & $B_{2g}$    &           & \ce{O=Mo=O}  & wag  \\
-292      & $B_{3g}$     & $\delta$ & \ce{O=Mo=O}  & wag  \\
-337      & $A_g,B_{1g}$ & $\delta$ & \ce{O-Mo-O} & bend  \\
-380      & $B_{1g}$     & $\delta$ & \ce{O-Mo-O}  & scissor  \\
-474      & $A_g$        & $\nu_{as}$ & \ce{O-Mo-O}  & stretch,bend  \\
-667      & $B_{2g},B_{3g}$ & $\nu_{as}$  & \ce{O-Mo-O}  & stretch  \\
-819      & $A_g$        & $\nu_{as}$  & \ce{O=Mo}  & stretch  \\
-996      & $A_g$         & $\nu_{as}$  & \ce{O=Mo}  & stretch  \\
-\bottomrule
-\end{tabular}
-\end{table}
-
-The growth rates along different crystalline direction of \ce{MoO3} are presumably determined by the free surface energy.
-In other words, the migration barrier of adatoms on (010) plane is presumably much lower than that on other low index planes due to the Van der Waals interaction nature along [010] direction.
-
-\subsection{FL}
-
-FL materials attracts intensive research efforts recently.
-We first use liquid exfoliation method to prepare FL \ce{MoO3}.
-We then characterized the absorption feature and crystalline structures of the exfoliated \ce{MoO3} using UV-Vis and TEM.
-Then we calculate the optical contrast of FL \ce{MoO3} on \ce{SiO2}-Si, which serves as a guideline to identify FL \ce{MoO3} using optical microscope.
-
-The exfoliation solution is 30\% isopropanol (IPA) in DI water, which has been proved to work well on other layered compounds.\cite{Halim2013} After 20 minutes sonication, the dispersion is milky.
+After 20 minutes sonication, the dispersion is milky.
 We measured the transmission spectra of this dispersion immediately upon sonication and after 40 hrs for gravity sedimentation, as illustrated in Fig.~\ref{fig:moabs}.
@@
 
-\begin{figure}[htb]
-\centering
-\subfloat[]{\label{fig:moabs}\includegraphics[width=0.45\textwidth]{MoO3-abs}}\hspace{0.04\textwidth}
-\subfloat[]{\label{fig:mobg}\includegraphics[width=0.45\textwidth]{MoO3-bg}}
-\caption[UV-Vis spectra of exfoliated \ce{MoO3}]{(a) UV-Vis absorbance spectra of exfoliated \ce{MoO3}.
-Dashed line (t0) represents measurement immediately after sonication, and solid line (t40h) is obtained after sitting for 40 hours.
-The dot dashed line is reference spectrum of the 30\% IPA.
-(b) Band gap estimation}
-\label{fig:mouv}
-\end{figure}
-
-According to the corrected absorbance spectrum, optical band gap can be deduced, which is known as Tauc Plot.\cite{Tauc1972} The procedure is recapitulated here.
-
-\begin{equation}\label{eq:tauc}
- (h\nu \alpha)^{\frac{1}{n}} = B(h\nu - E_g^{opt}),
-\end{equation}
-where B is a proportional coefficient, $\alpha$ is absorption\footnote{The absorbance $A = 0.4343\alpha*l$, where l is the optical path} and $E_g^{opt}$ is defined as optical band gap.
-The value n is correlated to the nature of optical transition.
-For direct allowed transition, n = 1/2; For direct forbidden transition, n = 3/2; For indirect allowed transition, n = 2; And for indirect forbidden transition, n = 3.
-When the transition nature of sample is not well known, one should apply each to check which one provide the best fit.
-Depending on the synthesis methods and \ce{MoO3} morphologies, the transition phenomena might vary.
-On the \ce{MoO3} films, \citeauthor{Bouzidi2003} assumed a direct gap (n = 1/2)\cite{Bouzidi2003} while \citeauthor{Szekeres2002} not.\cite{Szekeres2002} We use n = 2 in this work.
-We plot $\sqrt{(h\nu \alpha)}$ versus photon energy, and extrapolate the linear part onto $h\nu$ axis.
-The intercept is used as $E_g^{opt}$ then.
-Our evaluation and some previous studies is summarized in Table.~\ref{tab:mobg}.
-
-\begin{table}[htb]
-\centering
-\caption{Optical band gaps of \ce{MoO3}}\label{tab:mobg}
-\begin{tabular}{lccr}
-\toprule
-&\multicolumn{2}{c}{Band gap} \\
-\cmidrule(l){2-3}
-Reference & value(eV) & orientation & material states\\
-\midrule
-\cite{Deb1968}   & 2.96  & $E\parallel c_0$ & single crystal\\
-\cite{Deb1968}   & 2.80  & $E\perp c_0$ & single crystal \\
-\cite{Julien1995} & 2.8$\sim$ 3.2 & NA & films\\
- this work  & 3.1  & NA & nanoflakes\\
-\bottomrule
-\end{tabular}
-\end{table}
-
-An alternative way is a) define $Y = \alpha E=\alpha h\nu$, and obtain $Y' = \frac{\partial Y}{\partial E}$, then b) plot $Y'/Y$ versus $h\nu$.
-The band gap value can be obtained from the intercept of extrapolated line on photo energy axis.\cite{Choopun} This approach is not difficult to comprehend as long as we notice from Eq.~\ref{eq:tauc}, $Y = B (h\nu - E_g^{opt})^n$ and $Y' = B n(h\nu - E_g^{opt})^{n-1}$.
-
-The dielectric constants\footnote{Not a constant at all, instead, it has complicated dependence on photon energy} ($\epsilon = \epsilon_1 + i*\epsilon_2$) of \ce{MoO3} have been studied in several reports.\cite{Deb1968,Sabhapathi1995,Miyata1996,Abdellaoui1997,Mondragon1999} We extracted $\epsilon_1$ from Ref\cite{Itoh2001a} due to the wide photon energy range utilized.
-We also notice that $\epsilon_2$ is approximately zero when $h\nu$ is less than 4 eV.
-Since we are primarily concerned with the optical contrast of FL \ce{MoO3} in visible wavelength region($h\nu < 3$ eV), we obtained refractive indices $n$ from $n = \sqrt{\epsilon_1}$.
-Due to the orthorhombic phase, \ce{MoO3} exhibit birefringence, that is there are two refractive indices, $n_c$ and $n_a$, as shown in Fig.~\ref{fig:moind}.
-The refractive index is between $ 2.2\sim 2.4$ along a axis, and $ 2.5\sim 2.8$ along c axis.
-Comparison to the low frequency dielectric constant ($18.0\pm1$) implies a primarily ionic bonding in \ce{MoO3}.\cite{He2003}
+\begin{itemize}
+\item s inversely proportional to the fourth
+\item  inversely proportional to the fourth
+\item s inversely proportional to the fourth
+\end{itemize}
 
@@
 \centering
-\subfloat[]{\label{fig:moind}\includegraphics[width=0.45\textwidth]{n_MoO3}}\hspace{0.04\textwidth}
-\subfloat[]{\label{fig:mocon}\includegraphics[width=0.45\textwidth]{Graph20}}
+\subcaptionbox{\label{fig:moind}}{\includegraphics[width=0.35\linewidth]{n_MoO3}}%
+\subcaptionbox{\label{fig:mocon}}{\includegraphics[width=0.55\linewidth]{Graph20}}
 \caption[Refractive indices of \ce{MoO3}]{(a) Refractive indices of \ce{MoO3} Dashed line is n along $a$ axis while solid line is along $c$ axis.
@@
 \end{figure}
+%[width=0.45\textwidth]
 
-Fig.~\ref{fig:mocon} illustrates the optical contrast mapping of 1L \ce{MoO3} on \ce{SiO2}-Si when the incident light is polarized along c axis of \ce{MoO3}. One can see that .
-The refractive indices of Si and \ce{SiO2} within visible wavelengths and MATLAB source code for optical contrast calculation is included in Appendix.
+Rayleigh scattering and Tyndall scattering.
+Rayleigh scattering, which occurs when particles are comparable to wavelength, is inversely proportional to the fourth power of wavelength; While Tyndall scattering, which occurs when the particles are larger, is inversely proportional to the square of the wavelength.
+To fully evaluate the true absorbance of the sample itself, one needs to decouple the scattering part from apparent absorbance.
+Generally we select one part of spectrum and assume it is only caused by scattering.
+Then a empirical dependence shown in Eq.~\ref{eq:sca2} is used as polynomial fitting model.
 
-The dimension and phase of exfoliated \ce{MoO3} is examined using TEM.
-Fig.~\ref{fig:motem} shows the size of exfoliated \ce{MoO3} is about 500 nm.
-High-resolution TEM (HRTEM) image was taken to assess the \ce{MoO3}.
-The clearly resolved lattices indicate high crystal quality of \ce{MoO3}.
+   %\glsaddallunused
+    \appendix
+    \chapter{math}
+    \renewcommand{\bibname}{REFERENCES}
+    \begin{singlespace}
+    \printbibliography
+    \end{singlespace}
 
-\begin{figure}[htb]
-\centering
-\includegraphics[width=0.8\textwidth]{exf_moo3.jpg}
-\caption[TEM images of exfoliated \ce{MoO3}]{(a) TEM image and (b) HRTEM image of FL \ce{MoO3} obtained by liquid sonication method.}
-\label{fig:motem}
-\end{figure}
-
-\subsection{Growth on non-Si substrates}\label{sec:nasi}
-
-In previous works, \ce{MoO3} deposition on ITO/glass exhibits new morphologies that were not observed on Si substrates, yet the mechanism is not well investigated.\cite{predeep2011} We first repeated the previous growth on ITO/glass, and then found similar deposition phenomena on glass and mica substrates.
-We suspected that the morphology difference on the substrates employed in this study arises from the compositions difference.
-Both mica and glass contains alkaline elements which are absent in Si and \ce{SiO2}/Si substrates.
-We primarily verify this hypothesis by utilizing \ce{NaOH} treated Si substrates and found that the overall morphology almost reproduces that on ITO and mica substrates.
-We then propose a new growth mechanism based on the VLS process to explain the deposition of \ce{MoO3} on alkaline-ions-containing substrates.
-
-ITO versus NaOH images.
-
-\subsubsection{Na transport}
-We estimated the mass transport of sodium ions in silica glass. The driving force could be external field or concentration gradient. And the dynamics is governed by diffusion equation
-
-\begin{align}
-\frac{\partial C}{\partial t} = D \frac{\partial^2 C}{\partial x^2},
-\end{align}
-
-where C is concentration in unit of \si{mol\per cm^3}, and D is diffusion coefficient in unit of \si{cm^2\per\second}.
-Diffusion coefficient highly depends on the overall environments in which the ions resides.
-Typical values of D for Na ions are listed in Table.~\ref{tab:mona}
-
-\begin{table}[htb]
-\centering
-\caption{Na diffusion coefficient ($cm^2/sec$), R is molar gas constant (8.315 \si{\joule\per mol\per K}), and T is temperature in K}\label{tab:mona}
-\begin{tabular}{lcr}
-\toprule
- Composition & Value  & Reference  \\
-\midrule
-Quartz      & $3.8\times10^{-2}exp(\frac{-24500}{RT})$  & \cite{Rybach1967a}  \\
-Sodalite      & $6.6exp(\frac{-42500}{RT})$  & \cite{Sippel1963}  \\
-Obsidian     & $4.4\times10^{-2}exp(\frac{-22900}{RT})$  & \cite{Sippel1963}  \\
-silicate glass & $3.1\times10^{-8}$ at 420\si{\degreeCelsius} & \cite{Jbara1995} \\
-\ce{SiO2} glass & $1.1\times10^{-7}$ at 670\si{\degreeCelsius} &  \cite{FRISCHAT1968}\\
-\bottomrule
-\end{tabular}
-\end{table}
-
-We also would like to mention the gradient of Gibbs free enthalpy overruled the concentration of a particular species, and higher \ce{OH^-} contents tend to reduce Na diffusivity.\cite{Materials2012}  The substrates used in this work are glass and ITO/glass.
-Related parameters is as following:
-\begin{itemize}
-\item dimension: $25mm\times10mm\times1mm$
-\item density: 2.567 \si{g\per cm^3}
-\item Na concentration: 0.01 \si{mol\per cm^3}
-\item D: $1.1\times10^{-7}$ \si{cm^2\per\second}
-\end{itemize}
-
-Then the net flux $J$ is estimated as
-\begin{align}
-J = -D \frac{\Delta C}{\Delta x} = 2.0e^{-8} mol/cm^2/sec,
-\end{align}
-
-for a typical 2hrs growth, the net amount of Na diffusing out of substrate is then 144$\mu mol$, about 10\% of total Na ions.
-The diffusion length $\sqrt{Dt}$ is 190 $\mu m$.
-We noticed this result overestimate since the flux will reduce gradually.
-Meanwhile the molar amount of \ce{NaOH} applied on Si substrate is about 1$\mu mol$.
-Considering the adjusted ratio, Na contents should be much more when using glass substrate than when using NaOH-Si substrate.
-
-Another important factor is the evaporation of sodium molybdates.
-However, few report could be found in literature.
-We only find one by \citeauthor{Kazenas2010}.\cite{Kazenas2010} The partial pressure\footnote{$logP(atm)= -13794/T + 6.19$} of \ce{Na2MoO4} is calculated to be 0.2 mTorr at 800 \si{\degreeCelsius} and $3.5\times 10^{-3}$ mTorr at 670 \si{\degreeCelsius}.
-
-\begin{table}[htb]
-\centering
-\caption{Reactants list}\label{tb:source}
-\begin{tabular}{lcccr}
-\toprule
-Material & Stock No & LOT &Purity & Vendor\\
-\midrule
-\ce{NaOH}        & S318-500 & 070241 & 99.8\% & Fisher Scientific \\
-\ce{NaI}        & 11665 & K11W054 & 99.9\% &  Alfa Aesar \\
-\ce{KI}        & 42857 & H06Z051 & 99.9\% &  Alfa Aesar \\
-\ce{Na2CO3}        & 33377 & 114X012 & 99.95\% &  Alfa Aesar \\
-\ce{Molybdenum}        & 00932 & I07S024 & 99.9\% &  Alfa Aesar\\
-\bottomrule
-\end{tabular}
-\end{table}
-
-\textbf{tower-like structure}
-
-Nanotower is a less common morphology in the structures of nanomaterials.\cite{Kharissova2010} We have not found report on  \ce{MoO3} nanotower structures, although there are several studies on \ce{In2O3},\cite{Jean2010,Yan2007}, GaN\cite{Xiao2012} and ZnO\cite{Zhang2013c}.
-\citeauthor{Jean2010} investigated the growth mechanism of \ce{In2O3} nanotowers and attributed it to the periodical axial and continuous lateral growth interaction, where the former was first guided by Au-In alloy liquid, and subsequent by self-catalytic In droplets (MP 156C) while the latter due to VS process.
-In contrast, \citeauthor{Yan2007} observed similar \ce{In2O3} nanotower growth and proposed that the axial growth is controlled by Au-catalytic VLS process.
-\citeauthor{Xiao2012} reported the GaN nanotower grown on Ni-coated Si(111) substrates and explained the growth as asymmetric self-copy process based on VLS mechanism.
-\citeauthor{Zhang2013c} studied the growth of ZnO nanotower and provided a competitive model between axial and lateral growth controlled by Zn vapor to explain the as-synthesized structures.
-(When ZnO and carbon mixture was used as source instead of ZnO alone, nanorods array results, presumably due to the stable supply of Zn vapor owing to the gentle carbothermal reduction.) Therefore the fluctuation of reagents is probably responsible for tapering and periodical modification, which is absent in the coin roll style growth of \ce{MoO3} tower on Si.
-The occasionally observed tapering or enlarging on \ce{MoO3} tower can be attributed to the cooling down growth.
-An oxygen regulated growth will be conducted to reveal the role of vapor pressure during the formation of tower.
-
-long belts  is also found on Mica(\ce{K(Al2)(Si3Al)O10(OH)2}), the formation probably arise from Potassium-catalyzed VLS mechanism.\cite{Hu2011}
-
-\subsubsection{time stepwise growth}
-
-With time stepwise growth, the following results were obtained:
-
-\begin{enumerate}
-\item When no Mo powder is used, NaOH still hold onto substrate with some locations exhibiting etching.
-\item When no Mo powder is used while growth is performed in an old tube or oxygen flow is limited to a extreme small value, circular droplet-like solid were found and Mo, Na and O were detected, suggesting the existence of VLS mechanism.
-Using Moly coated substrate and subsequent NaOH treatment, similar droplets formation was repeated.
-No discernible XRD pattern emerged, illustrating the amorphous nature of liquid catalyst.
-\item 1mins growth shows plates in high temp end and irregular shapes in low temp end.
-\item 15mins growth shows \ce{MoO3} plates parallel to substrate, with some belts emerging and growing out of the substrate plane.
-This is presumably due to the growth direction mismatch between different plates.
-Morphology will also depend on local NaOH concentration.
-NaOH trace mark turns into connected plates at the original locations, showing the high concentration mediated the morphology evolution.
-The possible catalyst solid was sitting on the top of plate layer.
-Also some belt-like growth is visible on reaction chamber walls, suggesting the evaporation and transport of \ce{NaxMoO3} vapor phase;
-\item 30mins growth:  belts growth begin (500 microns long, grow rate is estimated to be 0.5 $\mu m/s$), tower structures show up as well, but much less than belt.
-Two kinds of belts found, tapering and non-tapering.
-The former one seems to have droplets mostly associated with sidewalls of the top part.
-\item In reduced time or less oxygen supply growth, Na-containing site was found located onto the sidewall of belts instead of the usual expected tip.
-XRD pattern indicated the existence of \ce{NaxMoO3} phase.
-And MoO3 XRD pattern is dominated by (0k0) peaks, indicating a 2D layer-by-layer growth with lateral rate exceeding that of axial direction.
-\item 2hr growth: there are crossed tapering belts at downstream boundary, with more than one droplet located along the interface of two perpendicular belts, EDX confirmed high Na content.
-\item The tower is paled along $\langle010\rangle$ direction, and the belt growth direction is $\langle001\rangle$.
-\item Using NaOH treated hydrophobic substrates, dense tower array growth was found along the edge areas or molten periphery of droplets, where 5 mins growth already show the initial stage of tower with diameter about 1 $\mu m$, which increase to 10 $\mu m$ in prolonged growth.
-\end{enumerate}
-
-We divide the growth into two stages according to the emerging time of long belts and towers.
-In first stage the growth is dominated by lateral growth, as illustrated in .
-In the second stage, \ce{NaxMoO3} is evaporated and recondensed in the low temperature region, and some droplet will form, and when at proper locations, introduce secondary VLS growth.
-
-In first stage, the Na-Mo-O liquid is formed and have much more higher absorption rate than that of bare substrate.
-The absorbed species will diffuse along the surface and inside the liquid.
-It was difficult to estimate which diffusion path one is faster.
-When the size of liquid is smaller than some critical size, there is no preferred growth direction.
-This changed when the precipitated solid exceeds certain critical dimension, and the morphology evolution is then determined by the relative size of already formed solid and its liquid catalyst.
-
-The overall reactions probably occur in the following sequences.
-First, Mo powder is oxidized and \ce{MoO3} vapor is produced and transported to downstream by Ar carrier gas. Then,
-\begin{align}
-\cee{NaOH(l) + MoO3(g) -> Na2MoO4(l) + H2O(g)}
-\end{align}
-
-The melting point of \ce{Na2MoO4} is 687 \si{\degreeCelsius}.
-Based on the open air temperature profile (Fig.~\ref{fig:mooxgrowth}), the substrate is locate in temperature zone between 650 and 400 \si{\degreeCelsius}.
-The temperature distribution is different due to both the sealed condition and thermal conduction along the Si substrate.
-It will be difficult to acquire the accurate values along the substrate.
-However by considering the flow rate, the actual temperature will be higher than predicted by open air measurement.\cite{Subannajui2010} The melting of \ce{Na2MoO4} is highly possible when taking into account of its size as well.
-\cite{Bruggemann1997}
-
-\begin{figure}[htb]
-\centering
-\includegraphics[width=0.6\textwidth]{Na2MoO4_Phase}
-\caption[Phase diagram of Na-Mo-O]{Phase diagram of \ce{Na2MoO4} and \ce{MoO3} reproduced from ref.~\cite{Hoermann1929}}
-\label{fig:pd}
-\end{figure}
-
-According to the phase diagram shown in Fig.~\ref{fig:pd}, \ce{Na2MoO4} - \ce{MoO3} phase above 800 \si{\degreeCelsius} are \ce{Na2MoO4}(l) + \ce{MoO3}(l), More discussion should follow $\ldots$.
-
-Each site of \ce{Na2MoO4} will continue absorb incoming \ce{MoO3}, forming a swelling droplet.
-\ce{MoO3} will precipitate from these seeds when a critical supersaturation concentration is reached, which is about 75\% according to Fig.~\ref{fig:pd}.\footnote{This ratio considerably exceeds that of the usual metal catalyst scenario.
-This high solubility accounts for several observations in our experiments: the dimensions of individual deposit is much larger than that of initial droplet, the concentration of sodium in final products is extremely low.}
-
-As shown in Fig, we found several solid clusters with diameter about 1 $\mu m$ on the top part of long belts.
-According to the \ce{Na2MoO4}-\ce{MoO3} binary compounds phase diagram, we expect the terminating solid clusters have a Na:Mo ratio close to 0.6.
-The experimental results match well with this predictions.
-EDX analysis reveal the presence of Na on the solid cluster but not at about 1$\mu m$ away from previous location.\footnote{the sensitivity of our instrument is estimated to be 1\% atomic leve} Quantitative atomic ratio derived from the solid cluster is not close to the one predicted by phase diagram probably due to the high Mo content in adjacent area.
-However, XRD examinations on a short time growth sample revealed a possible \ce{Na2Mo4O13} phase(PDF 028-1112), providing an indirection evidence of the droplet composition.
-
-We also suspect that the growth will become different below 500 \si{\degreeCelsius} since no liquid would remain. Substrate placed at low temp end show.
-
-We can also deduce that other sodium compounds can be employed as substrate treatment agent. This argument is confirmed by \ce{Na2CO3} and \ce{KI} assisted growth.
-
-Nanotower is a less common morphology in the structures of nanomaterials.\cite{Kharissova2010} We have not found report on  \ce{MoO3} nanotower structures, although there are several studies on \ce{In2O3},\citep{Jean2010,Yan2007}, GaN\cite{Xiao2012} and ZnO\cite{Zhang2013c}.
-\citeauthor{Jean2010} investigated the growth mechanism of \ce{In2O3} nanotowers and attributed it to the periodical axial and continuous lateral growth interaction, where the former was first guided by Au-In alloy liquid, and subsequent by self-catalytic In droplets (MP 156C) while the latter due to VS process.
-In contrast, \citeauthor{Yan2007} observed similar \ce{In2O3} nanotower growth and proposed that the axial growth is controlled by Au-catalytic VLS process.
-\citeauthor{Xiao2012} reported the GaN nanotower grown on Ni-coated Si(111) substrates and explained the growth as asymmetric self-copy process based on VLS mechanism.
-\citeauthor{Zhang2013c} studied the growth of ZnO nanotower and provided a competitive model between axial and lateral growth controlled by Zn vapor to explain the as-synthesized structures.
-(When ZnO and carbon mixture was used as source instead of ZnO alone, nanorods array results, presumably due to the stable supply of Zn vapor owing to the gentle carbothermal reduction.) Therefore the fluctuation of reagents is probably responsible for tapering and periodical modification, which is absent in the coin roll style growth of \ce{MoO3} tower on Si.
-The occasionally observed tapering or enlarging on \ce{MoO3} tower can be attributed to the cooling down growth.
-An oxygen regulated growth will be conducted to reveal the role of vapor pressure during the formation of tower.
-
-\textbf{open questions}
-\begin{itemize}
-\item Is the liquid consumed? if so, how? : evaporation
-\item How the size of liquid is related to the morphology evolution?
-\item Possible doping level of alkaline ions
-\item other lateral growth mode such as Ni-W-S system
-\item VLS-VS interaction, or possible solution-liquid-solid, VSS,
-\item the interpretation of phase diagram
-\item the overall molar amount of NaOH and MoO3 deposition
-\item Young's parameters, contact angle informations, Gibbs free energy calculation
-\item catalyst composition variation during growth
-\end{itemize}
+\end{document}

### 2014-01-26 foo.tex
learning note foo.tex added

\documentclass[12pt,letterpaper]{article}
\usepackage{listings}
\lstset{
frame = single,
language = bash,
breaklines = true,
postbreak=\raisebox{0ex}[0ex][0ex]{\ensuremath{\color{red}\hookrightarrow\space}}
}

\title{Git Learning Notes}
\author{tao}
\date{\today}

\begin{document}

\maketitle
\section{New tracking project}
Minimum working sample is:
\begin{lstlisting}
Git init
Git add */*.tex
Git add *.tex
Git add readme
Git commit -m 'comments'
% on a specific file after editing
 git add xx.tex

% to Reset a staged file
Git reset HEAD xxx.tex

\end{lstlisting}

\section{Commands}

\begin{table}
  \caption{Commands}
  \label{tbl:notes}
  \begin{tabular}{ll}
    \toprule
    Command                            & Function \\
    \midrule
    gitk\textsuperscript{\emph{a}}   & Visualization versioning history  \\
    git status\textsuperscript{\emph{b}} & current working flow state \\

    \bottomrule
  \end{tabular}

  \textsuperscript{\emph{a}} Some text;
  \textsuperscript{\emph{b}} Some more text.
\end{table}

\end{document}

### 2014-01-26 foo.tex
more tutorial note

@@
 
+ssh-keygen -t rsa -C "qisaiman@gmail.com"
+
+% checkout from github 
+git add remote hw https://github.com/qisaiman/hw.git
+git fetch hw master or develop 
+git push hw master
 \end{lstlisting}
+
+Git protocol 9148 port.
 
@@
     git status\textsuperscript{\emph{b}} & current working flow state \\
+    ssh key   & zgcss627\\
 

### 2014-01-27 ch-moox/moox.tex
moo3 012714

@@
+% git version control added 012614
 \chapter{Molybdenum Oxides}
@@
 \subsection{literature review}
+crystal-chemical principles.
+Due to the weak cation-oxygen bonding, alkali metal cations only introduce small perturbations into the energies of Mo-O or W-O ensembles in comparison to cations of other elements.
+And no mixing of vibrations of the cationic sublattices with that of \ce{Mo-O} or \ce{W-O} lattices.
+So the structural features of \ce{Mo-O} or \ce{W-O} polyhedra are dominating factors affecting the vibration frequencies and thermodynamic values of the molybdates and tungstates.\cite{Fomichev1992}
+
+\begin{table}[htb]
+\centering
+\caption{Crystal structures of alkali metal molybdates and tungstates}\label{tab:naxmow}
+\begin{tabular}{lcr}
+\toprule
+formula & structure  & remarks  \\
+\midrule
+\ce{A2O:MO3}\textsuperscript{\emph{a}} & isolated tetrahedral \ce{MO4} anions& \\
+\ce{A2O:2MO3} & chain-type anions of \ce{MO4} and \ce{MO6} & \\
+\ce{A2O:3MO3} & chain-type anions of \ce{MO5} and \ce{MO6} & \\
+\ce{A2O:4MO3} & chain-type anions of \ce{MO6} & \\
+\bottomrule
+
+\textsuperscript{\emph{a}} A = Li, Na, K, Rb, Cs; M = Mo, W;
+\end{tabular}
+\end{table}
+
+Assignment for \ce{A2MO4} is well grounded.
+Alkali metal cations with octahedral coordination occur below 230 $cm^{-1}$.
+For \ce{A2M_nO_{3n+1}}, exact assignment is not available yet due to the complicated \ce{MO6} octahedra.
 
@@
 After least-squares fitting, the coefficients $a$ and $n$ can be used to estimated the scattering in other wavelengths.
-The fitting of n usually falls between -2 and -4.
+The fitting of $n$ usually falls between -2 and -4.
 We examined the t40h line in Fig.~\ref{fig:moabs} and found the scattering part is almost zero.
@@
 \subfloat[]{\label{fig:moind}\includegraphics[width=0.45\textwidth]{n_MoO3}}\hspace{0.04\textwidth}
-\subfloat[]{\label{fig:mocon}\includegraphics[width=0.45\textwidth]{Graph20}}
+\subfloat[]{\label{fig:mocon}\includegraphics[width=0.45\textwidth]{MoO3_1L}}
 \caption[Refractive indices of \ce{MoO3}]{(a) Refractive indices of \ce{MoO3} Dashed line is n along $a$ axis while solid line is along $c$ axis.
@@
 
-Fig.~\ref{fig:mocon} illustrates the optical contrast mapping of 1L \ce{MoO3} on \ce{SiO2}-Si when the incident light is polarized along c axis of \ce{MoO3}. One can see that .
-The refractive indices of Si and \ce{SiO2} within visible wavelengths and MATLAB source code for optical contrast calculation is included in Appendix.
+Fig.~\ref{fig:mocon} illustrates the optical contrast mapping of 1L \ce{MoO3} on \ce{SiO2}-Si when the incident light is polarized along c axis of \ce{MoO3}.
+One can see that there is a pseudo-periodical trend with either wavelength or \ce{SiO2} thickness fixed.
+The positive extreme occur at around 80nm and 240nm \ce{SiO2} layer, slightly less than the optimum for observing graphene.
+The refractive indices of Si and \ce{SiO2} within visible wavelengths and MATLAB source code for optical contrast calculation is included in Appendix, with which one can readily evaluate the few layers \ce{MoO3} scenarios and the circumstance when incident light is polarized along a axis.
 
@@
 Fig.~\ref{fig:motem} shows the size of exfoliated \ce{MoO3} is about 500 nm.
-High-resolution TEM (HRTEM) image was taken to assess the \ce{MoO3}.
-The clearly resolved lattices indicate high crystal quality of \ce{MoO3}.
+High-resolution TEM (HRTEM) image was taken to assess the \ce{MoO3} crystallinity.
+The clearly resolved lattices indicate high crystal quality of these exfoliated \ce{MoO3}.
 
@@
 \end{figure}
+
+Nevertheless, identifying these few layer \ce{MoO3} under optical microscope is still difficult due to both the small flake size and low contrast.\footnote{Human eye threshold contrast (contrast sensitivity)$^{-1}$ is about}
 
@@
 The experimental results match well with this predictions.
-EDX analysis reveal the presence of Na on the solid cluster but not at about 1$\mu m$ away from previous location.\footnote{the sensitivity of our instrument is estimated to be 1\% atomic leve} Quantitative atomic ratio derived from the solid cluster is not close to the one predicted by phase diagram probably due to the high Mo content in adjacent area.
+EDX analysis reveal the presence of Na on the solid cluster but not at about 1$\mu m$ away from previous location.\footnote{the sensitivity of our instrument is estimated to be 1\% atomic level} Quantitative atomic ratio derived from the solid cluster is not close to the one predicted by phase diagram probably due to the high Mo content in adjacent area.
 However, XRD examinations on a short time growth sample revealed a possible \ce{Na2Mo4O13} phase(PDF 028-1112), providing an indirection evidence of the droplet composition.
@@
 We can also deduce that other sodium compounds can be employed as substrate treatment agent. This argument is confirmed by \ce{Na2CO3} and \ce{KI} assisted growth.
-
-Nanotower is a less common morphology in the structures of nanomaterials.\cite{Kharissova2010} We have not found report on  \ce{MoO3} nanotower structures, although there are several studies on \ce{In2O3},\citep{Jean2010,Yan2007}, GaN\cite{Xiao2012} and ZnO\cite{Zhang2013c}.
-\citeauthor{Jean2010} investigated the growth mechanism of \ce{In2O3} nanotowers and attributed it to the periodical axial and continuous lateral growth interaction, where the former was first guided by Au-In alloy liquid, and subsequent by self-catalytic In droplets (MP 156C) while the latter due to VS process.
-In contrast, \citeauthor{Yan2007} observed similar \ce{In2O3} nanotower growth and proposed that the axial growth is controlled by Au-catalytic VLS process.
-\citeauthor{Xiao2012} reported the GaN nanotower grown on Ni-coated Si(111) substrates and explained the growth as asymmetric self-copy process based on VLS mechanism.
-\citeauthor{Zhang2013c} studied the growth of ZnO nanotower and provided a competitive model between axial and lateral growth controlled by Zn vapor to explain the as-synthesized structures.
-(When ZnO and carbon mixture was used as source instead of ZnO alone, nanorods array results, presumably due to the stable supply of Zn vapor owing to the gentle carbothermal reduction.) Therefore the fluctuation of reagents is probably responsible for tapering and periodical modification, which is absent in the coin roll style growth of \ce{MoO3} tower on Si.
-The occasionally observed tapering or enlarging on \ce{MoO3} tower can be attributed to the cooling down growth.
-An oxygen regulated growth will be conducted to reveal the role of vapor pressure during the formation of tower.
 

### 2014-01-27 foo.tex
foo on develop
moo3 012714

@@
 \documentclass[12pt,letterpaper]{article}
+\usepackage{booktabs}
+\usepackage{xcolor}
 \usepackage{listings}
@@
 git fetch hw master or develop 
-git push hw master
+git merge hw/master
+git push hw master:master
+% or 
+git push hw master:hw/master % use my master branch to update remote
+
+% view current remote
+git remote -v
+% remove origin remote
+git remote rm origin
+
+%create a branch develop and switch to it
+git checkout -b develop
+{some editing }
+git commit -m ''
+git checkout master 
+git merge develop % into current branch 
+% inspect the branch status 
+git branch --merged % show merged branch 
+git branch --no-merge % show unmerged works
+
+% delete a branch
+git branch -d develop
+
 \end{lstlisting}
 
+\begin{lstlisting}
+% initialization
+touch README.md
+git init
+git add README.md
+git commit -m "first commit"
+git remote add origin git@github.com:qisaiman/cv.git
+git push -u origin master
+
+% view current remote 
+git remote -v 
+% remove origin remote 
+git remote rm origin
+
+% to view current config
+git config --list
+
+\end{lstlisting}
 Git protocol 9148 port.
@@
 
-\begin{table}
-  \caption{Commands}
-  \label{tbl:notes}
-  \begin{tabular}{ll}
+\begin{table}[htb]
+  \caption{Commands}\label{tbl:notes}
+  \centering
+  \begin{tabular}{lr}
     \toprule

### 2014-01-29 ch-wox/ch-wox.tex
wox 012814

@@
 
-\section{Introduction}
+% \input{./ch-wox/part1}
 
-Tungsten oxide (\ce{WO_x}) is an important functional materials with distinctive properties and technology applications.
-Intense research interest was rekindled by the discovery of \gls{ec} effect in \citeyear{Granqvist1993}.\cite{Granqvist1993}  Nano-engineering \ce{WO_x} bring more possibility and flexibility to its already rich characteristics, therefore resulting research efforts spanning multiple fields of scientific community.
-Besides smart window based on EC effect, \ce{WO_x} is also well investigated for several other significant applications: photoelectrochemical cell for solar energy conversion and storage, photocatalysis for hydrogen evolution reaction, chemical and biological sensing based on gasochromic effect.
-In addition, a few young fields are not thoroughly explored: field emission, optical storage, thermoelectrcity, ferroelectricity, and superconductivity.
+\section{growth method and results discussion}
 
-In this chapter, we will first review the literature to date for both \ce{WO_x} and \ce{Na_xWO3}, then divide the summaries into a) technological application, b) crystal structure and electronic properties and c) synthesis approaches.
-Then we present our growth methods and results.
-And we conclude with a brief summary.
-
-\subsection{Rich and useful technological appeals}
-
-Electrochromic effect of tungsten oxide means the coloration (deep blue) and bleaching (transparent) states of \ce{WO3} are reversibly switched upon forward and backward voltage, and the coloration or bleached states remain after disconnecting the voltage.
-On basis of this property, \gls{ecd} of tremendous energy saving potential is conceptualized and some products have already been commercialized (i.e.
-smart window\footnote{``We did a case study in five cities, and the average savings in commercial buildings are about 25 percent of the heating, ventilation, and air-conditioning energy use annually," says CEO of View, Inc.}).
-
-In the past decades, tons of works have been devoted to understanding the chromogenic phenomena in \ce{WO3}. We highlight several key results as reviewed by ,
-\begin{itemize}
-    \item coloration and bleaching can also be stimulated by other routes, such as by UV irradiation, thermal treating, heating in vacuum, reducing atmosphere etc
-    \item no electrical coloration occurs in vacuum, but other routes still works
-    \item coloration is associated with a proportional increase in conductivity
-    \item coloration spectrum is essentially similar in all cases except small variation in peak position and FWHM
-    \item coloration is structure sensitive and most efficient in amorphous films
-\end{itemize}
-
-Sofar there is no unifying model that could reconcile these contradictory experimental observations.
-Among all the developed models, polaronic absorption is the most widely accepted mechanism for coloration.
-In polaron model\footnote{When a free electron travels through a polar solid, it creates a local lattice displacement (longitudinal optical phonon clouds) due to the coulombic interaction with neighboring ions.
-This local distortion and the electron together is equivalent to a new elementary exciton of the crystal, and is named as polaron}, the intercalation of \ce{M^+} (M = H, \ce{Li}, or Na) ions into \ce{WO3} films is accompanied with the formation of small polarons ($r_p$ comparable to unit cell size) and formal reduction of some \ce{W^{6+}} sites to \ce{W^{5+}}, as depicted in Eq.~\ref{eq:ec}.
-During the intercalation process, the \ce{M^+} ions enter into these vacant sites.\cite{Hepel2008} Coloration occurs when the polaron band .
-
-\begin{align}\label{eq:ec}
-x\ce{M+} + x\ce{e-} +  \ce{$\alpha \hyphen$WO$_{3-y}$}= \ce{$\alpha \hyphen$M$_x$WO$_{3-y}$},
-\end{align}
-
-And the polaron binding energy ($E_p$) is given by
-\begin{align}
-E_p = - \frac{e^2}{2r_p} (\epsilon_\infty^{-1} - \epsilon_{st}^{-1}),
-\end{align}
-
-where $\epsilon_\infty$ and $\epsilon_{st}$ are optical and static dielectric constants respectively, and polaron radius $r_p$, which specifies how far the lattice distortion extends, is related to polaron density $N_p$ by $r_p = \frac{1}{2}\sqrt[3]{\pi/6N_p}$.
-However, the polaron model has difficulty in estimating $r_p$.
-The asymmetric optical absorption spectrum are often characteristic of large polarons, and dielectric constants ($\epsilon_\infty = 6.52,\epsilon_{st} > 50$,\cite{Deb2008}) suggests the formation of bipolaron.
-Moreover, polaron model does not take oxygen vacancy into account, which plays a vital role in the nonstoichiometric tungsten oxides.
-For instance, it is observed that \ce{WO_{3-y}} films are metallic and conductive for $y > 0.5$, blue and conductive for $y = 0.3 \sim 0.5$, and transparent and resistive when $y < 0.3$, regardless of the preparation methods.\cite{Chatten2005}
-
-Therefore another model in analogy to the F-color center is proposed.
-Color center model assumes the presence of oxygen vacancy $V_O^0$ is associated with \ce{W^{4+}} or 2\ce{W^{5+}} states.
-This defect level is expected to be inside or near the valence band.
-When one electron is removed from this level, $V_O^0$ is converted to $V_O^+$.The positively charged vacancy exerts coulombic repulsion to the nearest W-ions, which results in a displacement of the neighboring W-ions and an upward shift of the defect level into the bandgap, thereby creating a color center.
-The optical transition from $V_O^+$ to $V_O^{2+}$ (a state within the conduction band)
-contributes to coloration.\cite{Deb2008}
-
-So the polaron and color center models both agree on that \ce{W^{5+}} and its transition is responsible for the coloration, but disagree on how this \ce{W^{5+}} state is created (foreign ion reduction in polaron model and oxygen vacancy in color center model) and the corresponding energy levels.
-A modified polaron model is proposed to include \ce{W^{4+}} states in host lattice.
-Coloration mechanism is represented by Eq.~\ref{eq:cl_bl1} and \ref{eq:cl_bl2}, which described the polaron hopping from one site to another.\cite{Chatten2005}
-
-\begin{align}
-h\nu +\ce{W^{5+}(A)} +  \ce{W^{6+}(B)} &\rightarrow \ce{W^{5+}(B)} + \ce{W^{6+}(A) + E_{phonon}} \label{eq:cl_bl1}\\
-h\nu +\ce{W^{5+}(A)} +  \ce{W^{4+}(B)} &\rightarrow \ce{W^{5+}(B)} + \ce{W^{4+}(A) + E_{phonon}} \label{eq:cl_bl2}
-\end{align}
-
-Similar scenarios occurs in the gasochromic effect.
-Two models, double injection and color center, arise to account for the coloration upon exposure to certain gases.
-Both consents to Eq.~\ref{eq:cl_bl1}.
-But there is a disagreement on the final states.
-Double injection supports the formation of tungsten bronze \ce{H_xWO3} while color center insists on the inward diffusion of oxygen vacancy and outward diffusion of water molecules.
-Both have been substantiated experimentally.
-Therefore the exact mechanism in \ce{WO_x} still requires further investigation.
-The author believes the resolution to a large extent depends on the phase transitions, as discussed in Section.~\ref{sec:wonawo}.
-
-photocatalytic applications in solar hydrogen generation and organic pollutant degradation.
-
-photocatalyst\cite{Macphee2010}, photoelectrochemical energy application \cite{Su2010}
-
-Photocatalytic activity occurs when a semiconductor in aqueous solution is illuminated by photons of energy larger than the band gap, then electron-hole pairs generate free radicals, (i.e.
-\ce{OH.}) which enable further reactions.
-For water splitting using solar energy, the band gap should be within $2.0 \sim 3.0 $ eV, and CB edge should be more negative than reduction potential of \ce{H^+/H2}, whereas the VB top should be more positive than the oxidation potential of \ce{H2O/O2)}.\cite{Wang2012} The valence band holes (\ce{h^+}) oxidize water to oxygen and conduction band electrons propel hydrogen generation, as depicted in Eq.~\ref{eq:hervb} and \ref{eq:hercb}.
-
-\begin{align}
-4\ce{h^+} +  \ce{H2O} &\rightarrow \ce{O2} + 4\ce{H^+} \label{eq:hervb}\\
-4\ce{H^+} +  4e^- &\rightarrow 2\ce{H2} \label{eq:hercb}
-\end{align}
-
-As shown in Fig.~\ref{fig:woxnhe}, \ce{WO3} has CB edge positioned slightly more positive than reduction potential of \ce{H^+/H2}(versus \gls{nhe}), and VB edge much more positive than the oxidation potential of \ce{H2O/O2}.
-So the photo-cleavage of water cannot be accomplished by \ce{WO3} alone.
-Nevertheless, a tandem cell approach by \ce{WO3} film and dye-sensitized \ce{TiO2} has been demonstrated with an efficiency of 4.5\%.\cite{Michael1999} It is worth noting that green plants also have two photosynthetic systems connected in series, one for oxidation of water into oxygen and the other for fixation of carbon dioxide.
-
-% wo3 vs NHE 
-\begin{figure}[htb]
-\centering
-\includegraphics[width=0.7\textwidth]{woxnhe.jpg}
-\caption[Bands positions of \ce{WO3} versus NHE]{Bands positions of \ce{WO3} in contact with aqueous electolyte at pH 1. adapted from Ref\cite{Gratzel2001}}
-\label{fig:woxnhe}
-\end{figure}
-
-Moreover, favorable oxygen evolution of \ce{WO3} brings good performance in degradation of organic compounds\cite{Hepel2001,Luo2001,Watcharenwong2008}.
-The formation of long-lived holes is recognized as a key requirement.\cite{Pesci2011} Besides, \ce{WO3} is remarkably stable in acid, making it a significant candidate for treating water pollutant caused by organic acids.\cite{Monllor-Satoca2006}
-
-the ubiquity of \ce{WO6} octahedra is essential for not only the optical properties but the ability to insert and extract ions in the EC oxides, due to the tunnels in three dimensions serving as path for transport of small ions.
-The intercalation of hydrogen or alkali ions into \ce{WO3} created electron donor level.
-By absorbing the red part of incident spectrum, electrons at donor level make transition to the conduction band, causing the blue coloration in \ce{H_xWO3}.
-
-\citeauthor{Wang2009a} mentioned that amorphous \ce{WO3} can only be used in lithium-based electrolytes due to its
-in-compact structure and high dissolution rate in acidic electrolyte solutions.
-Electrochromic materials that can endure acidic electrolytes without degradation should be developed.
-Crystalline \ce{WO3} nanostructures with their much denser structures and small particle sizes are promising to be used as suitable electrochromic material in acidic electrolytes.
-
-Characterization of ECD (work like a thin-film batteries) includes transmission measurement and associated EC calculation, charge-discharge time, current-time curve and the fitting of obtained data.
-
-The coloration efficiency (CE) represents the change in the optical density (OD) per unit charge density ($Q/A$, in units of \si{\cm^2\per\coulomb}) during switching and can be calculated according to the formula:
-\begin{equation}
-CE = \frac{\Delta~OD}{(Q/A)} [cm^2/C],
-\end{equation}
-where OD = $log(T_{bleach}/T_{color})$. The EC and optical density depend on the wavelength and are usually higher in the near IR than in the visible region.
-Using Ohm's law($U_s = IR = RQ/t_s$) with switch voltage $U_s$, resistance R and surface area A, switching time $t_s$ could be estimated as
-\begin{equation}
-t_s = \Delta~OD\cdot A \cdot R /(CE\cdot U_s).
-\end{equation}
-
-its one dimensional (1D) nanostructure has attained intensive research efforts in recent years due to the potential applications in advanced nano-electric and nano-optoelectronic devices.
-
-\begin{quote}
-a viable electrochromic smart window must exhibit a cycling life time \textgreater $10^5$ cycles, corresponding to an operation life at 10 - 20 years.
-\end{quote}
-
-\subsection{Crystal structures and properties of tungsten oxides and sodium tungsten oxides}\label{sec:wonawo}
-
-\textbf{\ce{WO3}} Tungsten trioxides crystalize in multiple phases.
-The basic building block is \ce{WO6} octahedra.\footnote{Tungsten, with its electronic configuration as \ce{(Xe)4f^{14}5d^{4}6s^{2}}, has empty 5d and 6s orbitals in its +6 oxidation state.} \ce{WO3} crystal structure consists of \ce{WO6} octahedra joined at their corners, which may be considered as a perovskite structure of \ce{CaTiO3} with all \ce{Ca^{2+}} sites vacant.
-A representative lattice structures is illustrated in Fig.~\ref{fig:wo3oct}.
-These distorted \ce{WO6} octahedra adapts different tilting angles in different phases and edge-sharing octahedra also arises.
-The temperature-dependent phase transition and corresponding lattice constants in bulk form is summarized in Table.~\ref{tab:wo3phase}.\cite{Zheng2011} And a firm assignation of space group to monoclinic phases are still in debate.\cite{Chatten2005} It is noticed that the lattice parameters obtained via \emph{ab initio} calculation closely match the experimental values.\cite{Migas2010a} The phase transition scenarios in nanostructured \ce{WO3} are supposed to be much more sophisticated.
-Within Gibbs-Thomson frame work, one can generally expect lower transition temperature than their bulk counterparts due to enhanced surface energy.
-Temperature-dependent Raman spectroscopy provided support for this deduction.\cite{Boulova2002}
-
-% wo3 phases
+Tungsten powders were used as source in this work.
+We used four kinds of W powder in total, as summarized in Table.~\ref{tab:powder}.
+Three growth configurations were explored, namely ordinary transport (OT), seeded growth (SG) and flow growth (FG).
+% Tungsten powders size and purity
 \begin{table}[htb]
 \centering
-\caption{\ce{WO3} phases}\label{tab:wo3phase}
-\begin{tabular}{lccccc}
+\caption{Tungsten powders size and purity}\label{tab:powder}
+\begin{tabular}{lccr}
 \toprule
-\multicolumn{5}{c}{Lattice constants \AA} \\
-\cmidrule(l){4-6}
- Symbol    & Temperature (\si{\degreeCelsius}) & Phase & a & b & c   \\
+Name & purity & average size & vendor info\\
 \midrule
-$\epsilon$-\ce{WO3} & $ -140 \sim -50$  & monoclinic II & 7.378 & 7.378 & 7.664  \\
-$\delta$-\ce{WO3} & $-50 \sim 17$  & triclinic & 7.309 & 7.522 & 7.686  \\
-$\gamma$-\ce{WO3} & $17 \sim 330$  & monoclinic I & 7.306 & 7.540 & 7.692  \\
-$\beta$-\ce{WO3} & $330 \sim 740$  & orthorhombic & 7.384 & 7.512 & 3.846  \\
-$\alpha$-\ce{WO3} & $> 740$  & tetragonal & 5.25 & NA & 3.91  \\
-$h$-\ce{WO3} &  $<400$  & hexagonal & 7.298 & NA & 3.899  \\
+3N   &  99.9\% & 17 $\mu$m & Alfa Aesar \#39749\\
+3N5   &  99.95\% & 32 $\mu$m  & Alfa Aesar \#42477\\
+4N5   &  99.995\% & 3.3 $\mu$m  & Materion T-2049 \\
+5N   &  99.999\% & 1.5 $\mu$m & Alfa Aesar \#12973\\
 \bottomrule
@@
 
+In a typical OT experiment (Fig.~\ref{fig:wogrow}), about 2g tungsten powder was positioned in the upstream end of a quartz boat and downstream about 2.5 inches the substrate was stationed.
+The substrates were p-type, boron-doped and [100]-orientated silicon with about 1 $\mu m$ thermally-grown silicon oxide layer on the polished side.
+The cleaning procedures have been elucidated in Chapter 1 section.
+The boat was then loaded into reaction chamber in a way that the powder source was placed in the center of heating zone, and the substrate upstream end was aligned at 6.5in.\footnote{As defined in Fig.~\ref{fig:wogrow}} After pumping down, 1 sccm \ce{O2} and 10 sccm Ar were admitted into the chamber, respectively, after which the overall pressure read approximately 110 mTorr.
+The temperature ramped up to 1000 \si{\degreeCelsius} in 30 minutes and lasted for 4 hours, and subsequently the apparatus was allowed to naturally cool down to room temperature.
+% cvd NW growth
 \begin{figure}[htb]
 \centering
-\includegraphics[width=0.4\textwidth]{octwo3.jpg}
-\caption[Octahedra model of \ce{WO3}]{Octahedra model of \ce{WO3}}
-\label{fig:wo3oct}
+\includegraphics[width=0.7\textwidth]{CVD_and_temp.jpg}
+\caption[\ce{WO3} NW growth: OT]{Chemical vapor system and its temperature profile.
+The nominal NWs growth temperature were estimated according to the interpolation data.
+The zero inch location is defined at the upstream edge of furnace.}
+\label{fig:wogrow}
 \end{figure}
 
-\ce{WO3} is wide gap n-type semiconductor with valence band top featuring $2p$ states of oxygen and conduction band bottom arising primarily from $5d$ states of tungsten with some mixing of oxygen $2p$ states.\cite{Gillet2004} \citeauthor{Migas2010a} maintained there is essentially identical band dispersion near the gap region in case of $\epsilon$-\ce{WO3}, $\delta$-\ce{WO3}, $\gamma$-\ce{WO3} and $\beta$-\ce{WO3}.\cite{Migas2010a} When there is oxygen vacancy, the Fermi level moves into the conduction band and the gap shrinks by about 0.5 eV.
-\citeauthor{Migas2010a} also pointed out the flat bands at VBM and CBM could lead to poor transport of holes and electrons, thus may compromising the function in photoelectrochemical cells.
+SG and FG experiments remain essentially the same as that of OT growth, except that in SG additional tungsten powders were distributed onto the receiving substrate, and in FG more than one piece of substrate was employed.
+The modification is schematically illustrated in Fig.~\ref{fig:wogrowsf}.
+More details will be provided when it comes to the discussion.
+% sg fg 
+\begin{figure}[htb]
+\centering
+\includegraphics[width=0.5\textwidth]{sg_and_fg.jpg}
+\caption[\ce{WO3} NW growth: SG and FG]{\ce{WO3} NW growth: SG and FG. (a) Seeded growth with additional powders on substrate (b) Flow growth with multiple substrates}
+\label{fig:wogrowsf}
+\end{figure}
 
- \citeauthor{Chatten2005} also studied the oxygen vacancy in different phases of \ce{WO3}.\cite{Chatten2005}
-
-Nonstoichiometric tungsten oxides \ce{WO_x} (i.e. \ce{WO_{2.92}}, \ce{WO_{2.87}}) are known as Magn$\acute{e}$li phases.
-
-We do not discuss tungsten oxide hydrates (\ce{WO3.nH2O}) in this work since the product of thermal CVD approach is not plagued with this complexity.
-It's necessary, however, to deal with hydrated \ce{WO3} in the liquid synthesis routes, as indicated in Section.~\ref{sec:woxgrowth}.
-
-Theoretical computation of electronic band structures for \ce{WO_x} proves difficult due to the aforementioned phase transition.
-
- oxygen deficiency, structure change, electronic properties vary according.
-
-% band gap table
+With four kinds of W powders and three layouts, we designed the experimental matrix as illustrated in Table.~\ref{tab:matrix}.
+The symbol $\times$ means this combination is covered in this work, and NA means otherwise.
+% Tungsten powders growth design
 \begin{table}[htb]
 \centering
-\caption{Tungsten oxides band gap }\label{tab:wo3eg}
+\caption{Tungsten powders growth design}\label{tab:matrix}
 \begin{tabular}{lccr}
 \toprule
-Phase & Experimental (eV) & Theory (eV) & Remarks  \\
+ & Ordinary Transport & Seeded growth & Flow growth \\
 \midrule
-amorphous \ce{WO3} & 3.2  & NA &    \\
-monoclinic bulk \ce{WO3} &  2.6   & 1.73\cite{Migas2010a}  &    \\
-tetragonal bulk \ce{WO3} &     & 0.66 \cite{Migas2010a}&    \\
-nano-\ce{WO3} & 2.6$\sim$3.2  & NA &    \\
-nano-\ce{WO_{3-x}} & NA  & NA &    \\
+3N   &  $\times$ & NA &  NA   \\
+3N5  &  $\times$ & NA &  NA   \\
+4N5  &  $\times$ & $\times$ & $\times$ \\
+5N   &  $\times$ & $\times$ &  $\times$ \\
 \bottomrule
@@
 
-Tungsten bronzes was coined by Wohler in 1837.\cite{Deb2008} \ce{Na_{x}WO3}
+We will first present the OT growth results in section~\ref{sec:nawox}, and discuss the other two in section~\ref{sec:sgfg}.
 
-\subsection{Synthesis strategies}\label{sec:woxgrowth}
+\subsection{Tungsten Oxides by OT}\label{sec:nawox}
 
-We will first give a brief review on the synthesis of \ce{WO3}.
-As the chemical formula suggested, the most straightforward way is heating metallic tungsten in various forms (i.e.
-powders,\cite{Zhou2005a,Cao2009,Hsieh2010} foils and wires).
-Actually \ce{WO_x}\footnote{$x$ is between 2 and 3.} NWs was observed when directly heating W wires.\cite{Gu2002a} Due to the extreme high melting point of W, it requires very high temperature (say, above 1100 \si{\degreeCelsius}) to produce large amount of growth species.
-Therefore scalable growth seems difficult.
-The DC current heating proved to be a route with potential large yield.
-Tungsten wire or filament is connected to a voltage source, and substrate is positioned in proximity to the heated W wire.
-\cite{Lingfei2006,Thangala2007,Chang2007}
-
-Tungsten oxides powder can also been used as precursor to prepare \ce{WO_{x}} \glspl{nw}.\cite{Huang2008a,Wang2009} Hydrogen-containing agents (i.e.
-water, \ce{H2},or methane\cite{Klinke2005}) were often involved into the reaction.\cite{Baek2007,Karuppanan2007} The potential benefit is \ce{WO3} has a much lower melting point ($\approx 1470$\si{\degreeCelsius}) than that of W.
-
-Direct oxidation and \ce{WO3} conversion could be grouped as addition approach. In contrast, decomposition method is also feasible.
-\citeauthor{Pol2005} obtained \ce{W18O49} nanorods by thermal dissociation of \ce{WO(OMe)4} at 700 \si{\degreeCelsius}, and \ce{WO3} by the annealing at 500 \si{\degreeCelsius} at air atmosphere.\cite{Pol2005}
-
-Spray pyrolysis is a typical aerosol-assisted CVD technique.
-Typical process flow is: the precursor solution is pumped to an atomizer, and then sprayed through the carrier gas as a fine mist of very small droplets onto heated substrates.
-Subsequently the droplets undergo evaporation, solute condensation, and thermal decomposition, which then result in film formation.\cite{Zheng2011}
-
-Main reactions include: \cee{W + O2 -> WO_{3-x}} \cee{W + H2O -> W_{3-x} + H2}
-
-the energetic sources are ion bombardment, electron beam, laser ablation, and combustion flame\cite{Rao2011}.
-
-The sol–gel process is a well-known, intensively studied wetchemical technique that is widely used in materials synthesis.
-This method generally starts with a precursor solution (the ``sol") to form discrete particles or a networked gel structure.
-During the course of gelation (aging process), various forms of hydrolysis and polycondensation take place.
-
-Hydrothermal method has been an important route to synthesize a diversity of nanomaterials (i.e.
-).
-Preparation of \ce{WO_{3-x}} has also been demonstrated hydrothermally.\cite{Lee2003,Gu2007} Usually, the precursor (\ce{H2WO4}) is mixed with other reactants (sulfides or certain organic acid) in solution and pH value is adjusted as another control degree of freedom.
-Then the solution is transferred into a sealed container (i.e.
-Teflon autoclave) and maintained at elevated temperature ($120 \sim 300$ \si{\degreeCelsius}) for tens of hours.
-Finally the product is separated from the solution and dried, layered \ce{WO3.nH2O} flakes are usual products.
-
-In addition, doped \ce{WO3} was also demonstrated
-
- The composition and phase of final product highly depend on the synthesis conditions.
-
-%\newgeometry{margin=1in}
-\begin{landscape}
+We have investigated the growth dynamics of each source in OT configuration.
+In each experiments, we control the temperature, flow rate and source and substrate locations.
+Another parameter we found important is the growth number\footnote{Defined as the order of growth performed in the same reaction chamber} in the same reaction chamber.
+Usually one will conduct several runs in the same chamber, and different results may arise with respect to the growth number.
+With this degree of freedom included, we first summarized the primary features of deposition and the associated parameters in Table~\ref{tab:wot}.
+% \ce{WO_x} ordinary transport results
 \begin{table}[htb]
 \centering
-\caption{Tungsten Oxides Growth and Application}\label{tab:wox}
-{\footnotesize
-\begin{tabular}{lp{3.5in}p{2.5in}c}
+\caption{\ce{WO_x} ordinary transport results}\label{tab:wot}
+\begin{tabular}{lp{2in}p{2in}r}
 \toprule
-composition  &  methods & highlights &  reference  \\
+\multicolumn{2}{c}{Growth Number} \\
+\cmidrule(l){2-3}
+ Source   & First & Second and more & Sodium(ppm)   \\
 \midrule
-\ce{WO3} & hot W filament (above 1500 \si{\degreeCelsius}) in Ar/\ce{O2} flow  & Cubic phase, PL, resistivity measured & \cite{Thangala2007} \\
-\addlinespace[0.5em]
-& W filament DC heating in \ce{NH3} or \ce{N2}/\ce{H2} flow  & multi phases, 100mg per batch, stable dispersion in both organic and aqueous solvents & \cite{Chang2007} \\
-\addlinespace[0.5em]
-& W powder heating Ar/\ce{O2} flow  & triclinic phase, CL at 370,415nm, UV-Vis, 3eV & \cite{Hsieh2010} \\
-\cmidrule(l){2-4}
-& \ce{WOx} film in \ce{H2} and \ce{CH4} flow  & monoclinic phase, tungsten carbide is the key & \cite{Klinke2005} \\
-\cmidrule(l){2-4}
-& \ce{Na2WO4.2H2O} by hydrothermal heating to test for line break & 3 different morphologies and photodegradation & \cite{Rajagopal2009}  \\
-& \ce{H2WO4.2H2O}, \ce{H2O2} and poly(vinyl alcohol) etc by solvothermal  & multi phases deposition of FTO with varied bandgaps  & \cite{Su2010}  \\
-
-\midrule
-\ce{W18O49} & \ce{KOH} etching of W tips followed by heating in Ar flow  & oxygen from leakage, VS process& \textcite{Gu2002a} \\
-\addlinespace[0.5em]
-& \ce{NW(CO)6}, \ce{Me3NO.2H2O} and oleylamine by hydrothermal  &  RT PL at 350nm and 440nm & \cite{Lee2003}  \\
+3N      & Morphology from high to low temperature: islands, dense layer and a few NWs & Dense wires become more and more, \ce{NaxWO3} phase dominates & 20  \\
+3N5     & $\pm1$  & correlated to flow &      NA\\
+4N5  & dense islands, some tiny wires in low temperature end & NA & 0.065 \\
+5N  & dense islands, some tiny wires in low temperature end  & NA & 0.05\\
 \bottomrule
 \end{tabular}
+\end{table}
+
+We found the growth using 3N source show distinctive features in comparison to the rest.
+This mainly arise from the higher sodium concentration in 3N source than that in others.
+Therefore we focus on 3N source first, and move on to other latter.
+
+Before diving into the complex interaction of \ce{WO3} and \ce{Na_xWO3} nanostructures, we would like to examine the metallic W source itself and its changes after growth.
+The SEM images of all powders before and  after growth are shown in Fig.~\ref{fig:pdbefore} and Fig.~\ref{fig:pdafter}, respectively.
+% powder before growth
+\begin{figure}[htb]
+\centering
+\includegraphics[width=0.7\textwidth]{pd_before.jpg}
+\caption[SEM images of W powder before growth]{SEM images of W powder before growth.(a) 3N, (b) 3N5, (c) 4N5 and (d) 5N. }
+\label{fig:pdbefore}
+\end{figure}
+
+% powder after growth
+\begin{figure}[htb]
+\centering
+\includegraphics[width=0.7\textwidth]{pd_after.jpg}
+\caption[SEM images of W powder after growth]{SEM images of W powder after growth.(a) 3N, (b) 3N5, (c) 4N5 and (d) 5N. }
+\label{fig:pdafter}
+\end{figure}
+
+Typical morphologies of the as-synthesized nanostructures grown on a \ce{SiO2}-Si substrate was shown in Fig.~\ref{fig:nawoxsemedx}(a).
+The nanostructures are NWs with lengths from tens microns up to several hundred microns and diameters about 40 to 500 nm.
+The deposition of nanowires was generally located on the substrates with a growth temperature range from 660 to 420 \si{\degreeCelsius}.
+Close-up observations at high magnification revealed some nanowires were cylinder-shaped and some were belt-shaped.
+At some locations, microplate structures with a regular rectangular shape grew among the nanowires as demonstrated in Fig.~\ref{fig:nawoxsemedx}(b) and its inset.
+The chemical compositions of the deposition were identified by EDX.
+A representative EDX spectrum in Fig.~\ref{fig:nawoxsemedx}(c) shows the existence of W, Na, O, and Si signals in the specimen, where the Si signal is from the substrate.
+The crystal structures of the as-synthesized specimens were examined using XRD.
+The diffraction peaks were carefully indexed and the deposition was identified as two phases of sodium tungsten oxides and one phase of tungsten oxide as indicated on Fig.~\ref{fig:nawoxsemedx}(d).
+The two sodium tungsten oxide phases are the triclinic \ce{Na5W_{14}O_{44}} phase\footnote{ICDD PDF 04-012-4449,\emph{a}=7.2740\AA, \emph{b}=7.2911\AA, \emph{c}=18.5510\AA, $\alpha$=96.3750$^\circ$, $\beta$=90.8920$^\circ$, $\gamma$=119.6560$^\circ$} and the triclinic \ce{Na2W4O_{13}} phase.\footnote{ICDD PDF 04-012-7108,\emph{a}=11.1630\AA, \emph{b}=3.8940\AA, \emph{c}=8.2550\AA, $\alpha$=90.60$^\circ$, $\beta$=131.36$^\circ$, $\gamma$=79.70$^\circ$} The tungsten oxide is the monoclinic \ce{WO3} phase.\footnote{ICDD PDF 01-083-0950,\emph{a}=7.30084\AA, \emph{b}=7.53889\AA, \emph{c}=7.6896\AA, $\beta$=90.8920$^\circ$}
+
+% nawox sem edx
+\begin{figure}[htb]
+\centering
+\includegraphics[width=0.7\textwidth]{nawox_semedx.jpg}
+\caption[SEM and EDX on \ce{Na_xWO3}]{SEM images of (a) dense array of as-synthesized ultra-long nanowires on SiO2-Si substrate and (b) rectangular microplates grow among the nanowires.
+(c) EDS and (d) XRD spectra showing the chemical compositions and phases of the deposition.}
+\label{fig:nawoxsemedx}
+\end{figure}
+
+The XRD measurements revealed the overall structure of the depositions on the substrates.
+To obtain detailed information on the crystallinity, composition, and growth direction of the nanostructures, TEM analyses with imaging, electron diffraction, and EDX were performed on more than 20 nanowires.
+The majority of the nanowires were identified as the \ce{Na5W_{14}O_{44}} phase.
+(Fig.~\ref{fig:nawoxtem}(a-c)) The HRTEM image in Fig.~\ref{fig:nawoxtem}(b) reveals that the nanowire has a single-crystalline structure.
+The corresponding diffraction pattern in the inset of Fig.~\ref{fig:nawoxtem}(b) was recorded in $[\bar{1}10]$ axis.
+Based on the analyses on a series of diffraction patterns and HRTEM images, the nanowire was confirmed as the triclinic \ce{Na5W_{14}O_{44}}.
+The growth direction of \ce{Na5W_{14}O_{44}} NWs was determined to be parallel to the (001) plane.
+The chemical composition of the nanowire was revealed by EDX.
+Fig.~\ref{fig:nawoxtem}(c) shows the nanowire consisted of W, Na, and O.
+No other impurities were detected.\footnote{The Cu and C signals come from the supporting Cu grid with lacey carbon and the Cr signal from the tip of JEOL double tilt holder.
+They are not compositions from the nanowires and other structures studied here.} small fraction of nanowires were found to be the monoclinic \ce{WO3} phase.
+(Fig.~\ref{fig:nawoxtem}(d-f)) The SAED shown in the inset of Fig.~\ref{fig:nawoxtem}(e) was recorded in [100] zone.
+
+\begin{figure}[htb]
+\centering
+\includegraphics[width=0.8\textwidth]{nawox_tem.jpg}
+\caption[SEM images of morphology evolution]{TEM images at low-magnification, HRTEM images, and EDS spectra of a \ce{Na5W_{14}O_{44}} NW (a, b, c), a \ce{WO3} NW (d, e, f), and a \ce{Na2W4O_{13}} microplate (g, h, i).
 }
-\end{table}
-\end{landscape}
-%\restoregeometry
+\label{fig:nawoxtem}
+\end{figure}
 
-\section{growth method and results discussion}
+Using 3N source and with increasing growth number from 1 to 5, we found dramatic morphology variation of as-synthesized nanostructures.
+The typical morphologies evolution as to the growth numbers is illustrated in Fig.~\ref{fig:nawoxsemall}.
 
-Tungsten powder were used as source material, and named as W3N (Alfa, -325 mesh, 99.9\%, metal basis) by the author.
-The sodium concentration was 20ppm.\footnote{detection of sodium by EDS is possible although the concentration is below the limit of typical EDS capacity due to the non-uniform distribution of foreign elements} The substrates were p-type, boron-doped and [100]-orientated silicon with about 1 $\mu$m thermally-grown silicon oxide layer on the polished side (U.Wafer).
-The one-side polished substrates were first cut into rectangular pieces of 10mm by 35mm, and then ultrasonically cleaned with acetone and alcohol for about ten minutes, each followed by the blow drying with nitrogen.
+\begin{figure}[htb]
+\centering
+\includegraphics[width=0.8\textwidth]{nawox_sem_series.jpg}
+\caption[SEM images of morphology evolution]{Low magnification SEM images of the NWs at different growth zones showing morphology changes with the increase of growth number.
+The insets show detailed structures of the NWs.}
+\label{fig:nawoxsemall}
+\end{figure}
 
-In a typical growth experiment, about 2g tungsten powder was positioned in the upstream of the quartz boat and downstream about 2.5 inches the substrate was stationed.
-The boat was then loaded into a 1-inch diameter quartz tube in a way that the powder source was placed in the middle, and the substrate low temperature end was aligned with tube edge.
-After pumping down, 1 \gls{sccm} (SCCM denotes cubic centimeter per minute at STP) \ce{O2} and 10 sccm Ar were admitted into the tube respectively, after which the overall pressure read approximately 110 mTorr.
-The temperature ramped to 1000 \si{\degreeCelsius} in half an hour and lasted for 4 hours, and subsequently the system was allowed to naturally cool down to room temperature.
+The sodium concentration was 20ppm as provided by vendor.\footnote{Due to the non-uniform distribution of foreign elements, detection of sodium by EDX is possible although the concentration is below the limit of typical EDX capacity.}
+% 3N5 powder growth
+\begin{figure}[htb]
+\centering
+\includegraphics[width=0.9\textwidth]{wox3n5.jpg}
+\caption[SEM images of \ce{WO3} growth using 3N5 powder]{SEM images of \ce{WO3} growth using 3N5 powder showing the morphology variation from (a) high temperature and (b) intermediate temperature, to (c) low temperature.}
+\label{fig:wox3n5}
+\end{figure}
 
-\subsection{Results on Sodium Tungsten Oxides}
+% 4N5 powder growth
+\begin{figure}[htb]
+\centering
+\includegraphics[width=0.9\textwidth]{wox4n5.jpg}
+\caption[SEM images of \ce{WO3} growth using 4N5 powder]{SEM images of \ce{WO3} growth using 4N5 powder showing the morphology variation from (a) high temperature and (b) intermediate temperature, to (c) low temperature.}
+\label{fig:wox4n5}
+\end{figure}
 
-The SEM images of powder a) before growth and b) after growth.
+\subsection{Tungsten Oxides by SG and FG}\label{sec:sgfg}
 
-\subsection{Results on Seeded Growth}
+As mentioned in Section.~\ref{sec:nawox}, growth using higher purity tungsten powders primarily produce dense layer deposition, and growth using 3N powder is plagued with the impurity effect.
+New growth method is required to obtain \ce{WO3} NWs.
+Here we figured out two alternatives to address this issue: seeded growth (SG) and flow growth (FG).
+In seeded growth, additional tungsten powders on the substrate serves as local seed.
+This approach is essentially the same as previous studies where tungsten foils was used as substrate.
+The advantage of our method is W powder cost much less than a whole piece of foil, and provide more surface area than W foil in the same volume.
+The FG method utilizes the flow dynamics of our CVD apparatus.
+We will discuss both of them in details.
+
+Understanding the oxidation of tungsten powder is the key to obtain high yield in seeded growth.
+Oxidation of tungsten have been investigated under diverse conditions, such as at elevated temperature (\textgreater 1100 \si{\degreeCelsius} ) and oxygen pressure on the order of Torr,\cite{Base1965} and at temperatures ranging from 20 to 500 \si{\degreeCelsius} under atmosphere pressure.\cite{Warren1996} \ce{WO_x} NWs were readily found when tungsten (foil, wire, or powder) is oxidized under various conditions.\cite{Zhu1999,Karuppanan2007,Hsieh2010} However the study on tungsten powder oxidation behavior between intermediate temperature range and under low pressure is still rare.
+In this work, we studied the oxidation of tungsten powders with diverse size within temperature range from 500 to 1000 \si{\degreeCelsius} and under several mTorr oxygen partial pressure.
+Using tungsten powder as seed, we further illustrate an economic approach to obtain large yield of \ce{WO3} nanowires at relatively lower temperature than previous efforts.
+We also demonstrate that there is an optimal tungsten powder size under our experimental conditions for seeded growth.
+This will provide some insight on the role of tungsten powder as source material in CVD growth of \ce{WO_x}.
+
+Commercial available tungsten powders with different size are usually associated with purity variation as well.
+We investigated four kinds of tungsten powder as already summarized in Table~\ref{tab:powder}.
+The dimensions of tungsten powder were obtained by measuring the average size in SEM graphs.
+
+We performed a systematic investigation on the oxidation behavior of tungsten powder.
+In a typical oxidation experiment, tungsten powders were loaded into the uniform heating zone and the sealed chamber was first pumped down to 5--8 mTorr.
+Then oxygen flow varying between 1 sccm to 10 sccm was admitted from upstream inlet.
+With 10 sccm Ar as carrier gas, the overall pressure was about 100 mTorr.
+The heating temperature was in the range of 500 to 750 \si{\degreeCelsius}.
+We present the temperature effect, size-dependence and influence of oxygen partial pressure as following.
+% seed optimal
+\begin{figure}[htb]
+\centering
+\includegraphics[width=0.8\textwidth]{JAP-2column_Fig1.jpg}
+\caption[W powder oxidation: temperature effect]{SEM graphs of 99.9\% (3N) tungsten powder oxidization at different temperatures of a) 500\si{\degreeCelsius}, b) 600\si{\degreeCelsius}, c) 650\si{\degreeCelsius}, d) 750\si{\degreeCelsius}, showing the optimal temperature for local formation of nanowires is between 600--650\si{\degreeCelsius}.
+Oxygen flow rate is 1 sccm.}
+\label{fig:pdtemp}
+\end{figure}
+
+Fig.~\ref{fig:pdtemp} illustrated the effect of temperature on the morphological change and surface nanowires formation of 3N powder.
+At 500 \si{\degreeCelsius}, most tungsten powder retained its original shape and a layer of tiny dense NWs begun to grow.
+When temperature was increased to 600 \si{\degreeCelsius}, 3N powder started to crack with longer NWs on the isolated surface.
+Further increase of temperature lead to irregular shapes of tungsten power and aggregation of NWs, giving rise to the nanorods and bunched or bundled structures.
+It could be determined from the morphology variation that the optimal seeded growth temperature for 3N powder was in the range of 600 to 650 \si{\degreeCelsius}.
+% seed optimal
+\begin{figure}[htb]
+\centering
+\includegraphics[width=0.8\textwidth]{JAP-2column_Fig3.jpg}
+\caption[W powder oxidation: size effect]{SEM graphs illustrating the oxidization of four different size of tungsten powders at 600~\si{\degreeCelsius} and 1 sccm oxygen flow.
+a) $17\mu m$, b) $32\mu m$, c) $3.3\mu m$, d) $1.5\mu m$.}
+\label{fig:pdsize}
+\end{figure}
+
+Fig.~\ref{fig:pdsize} depicted the oxidation of different sizes of tungsten powder under the same experimental conditions.
+In contrast to the morphology of 3N powder shown in Fig.~\ref{fig:pdtemp}, 3N5 powder surface is primarily covered with sub-micro particles as well as some short tiny NWs, whereas 4N5 and 5N powder were thoroughly oxidized, showing branched flowers feature.
+This dramatic difference could be explained in terms of surface energy and oxygen diffusion.
+With smaller dimension, the increased surface-to-volume ratio and short diffusion path both lower the energy barrier of oxidation.\cite{tungsten1999} It was logical to deduce that higher temperature or increased oxygen level might favor the NWs formation on 3N5 powder.
+When it comes to seeded growth, however, the powder size distribution was an important factor to give uniform NWs deposition.
+Since the size distribution of 3N powder is more uniform than that of 3N5 powder, we only employed the former as seeds.
+% seed optimal
+\begin{figure}[htb]
+\centering
+\includegraphics[width=0.8\textwidth]{JAP-2column_Fig2.jpg}
+\caption[W powder oxidation: oxygen pressure]{SEM graphs of 3N tungsten powder oxidization at 600 \si{\degreeCelsius} under different rates of oxygen flow: a) 1 sccm, b) 2 sccm, c) 3 sccm, d) 10 sccm.
+The oxygen partial pressures were 13 mTorr, 23 mTorr, 32 mTorr, and 82 mTorr, respectively with background pressure subtracted.}
+\label{fig:pdoxy}
+\end{figure}
+
+Fig.~\ref{fig:pdoxy} depicted the morphology change of 3N powder with respect to varied oxygen partial pressure.
+When the oxygen flow is lower than 3 sccm, 3N powder almost stayed as the same, with cracks separating the dense layer of NWs.
+When oxygen flow is increased to 10 sccm, the 3N powder exemplified an enlarged version of that for 4N5 or 5N powder under 1 sccm oxygen flow.
+This observation again supported the surface energy explanation.
+
+With all above oxidation experiments, favorable conditions for local growth of NWs were extracted to perform seeded growth.
+The seeded growth was performed by placing high purity tungsten powders (4N5 or 5N) in heating zone and receiving substrate with 3N tungsten powders in downstream location where the temperature was about 600 \si{\degreeCelsius}.
+The temperature profile and source and substrate locations remain essentially the same as in Fig.~\ref{fig:wogrow} except the presence of 3N powder on receiving substrate.
+In all experiments, tungsten powders were uniformly distributed by sliding two pieces of substrates and the growth time was kept at 4 hours.
+% sg sem
+\begin{figure}[htb]
+\centering
+\subfloat[]{\label{fig:sga}\includegraphics[width=0.4\textwidth]{wox_sg_a.jpg}}\hspace{0.04\textwidth}
+\subfloat[]{\label{fig:sgb}\includegraphics[width=0.4\textwidth]{wox_sg_b.jpg}}
+\caption[Characterization of seeded growth \ce{WO3}: SEM]{Characterizations of seeded growth.
+(a) SEM graphs of \ce{WO3} NWs on \ce{SiO2/Si} substrate.
+(b) A high magnification view showing uniform NW growth and close-up view of one NW.
+}
+\label{fig:woseedsem}
+\end{figure}
+
+As shown in Fig.~\ref{fig:sgb}, dense NWs array was obtained on tungsten powder seeds with individual wires of length up to 5 $\mu$m and diameter about 50 to 200 nm, according to the estimation made in the close-up view.
+Each tungsten powder stood as independent growth site (Fig.~\ref{fig:sga}) with island-layer growth on the substrates, a common feature without using tungsten powder as seed under current experimental conditions.
+It was occasionally observed that NWs growth was initiated adjacent some tungsten powders.
+We suspect that this phenomenon was correlated to the local trap of vapor flow since it was more often found among the enclosed area by tungsten powders.
+We also found that the diameter of NWs decrease as the distance between powders and upstream edge increases.
+This is a combination effect of lower temperature and reduced \ce{WOx} growth species supply.
+Similar phenomena were observed in other studies.
+\citeauthor{Thangala2007} reported that a decrease in NW density with increasing substrate temperature, and an increase of NW density with increasing partial pressure of oxygen.\cite{Thangala2007}
+% sg raman xrd
+\begin{figure}[htb]
+\centering
+\subfloat[]{\label{fig:sgxrd}\includegraphics[width=0.45\textwidth]{wox_xrd_1}}\hspace{0.04\textwidth}
+\subfloat[]{\label{fig:sgram}\includegraphics[width=0.45\textwidth]{wox_raman_1}}
+\caption[Characterization of seeded growth \ce{WO3}: XRD and Raman]{ (a) XRD pattern of as-prepared sample indicating the \ce{WO3} phase and the presence of metallic core.
+(b) Raman spectrum on NWs region showing the feature of \ce{WO3}.}
+\label{fig:woseedxrd}
+\end{figure}
+
+Fig.~\ref{fig:sgxrd} is the XRD spectrum of one typical sample.
+The peaks under circular symbol were identified to be the monoclinic \ce{WO3} phase (ICDD PDF 01-083-0950,\emph{a}=7.30084\AA, \emph{b}=7.53889\AA, \emph{c}=7.6896\AA, $\beta$=90.8920$^\circ$), while the peak under the triangular symbol was indexed to cubic tungsten phase (ICDD PDF 04-16-3405, \emph{a}=3.157\AA).
+This metallic core was anticipated considering the oxygen flow levels in previous oxidation experiment and the seeded growth (Fig.~\ref{fig:pdoxy}).
+Micro-Raman scattering spectroscopy was performed on as-synthesized sample as well.
+During Raman examination, the laser spot was carefully focused onto the NWs on powders and several inspections on different positions were observed to ensure the reproductivity of spectra data.
+As shown in Fig.~\ref{fig:sgram}, five distinct bands were well resolved, with its peaks located at 131, 265, 327, 711 and 803 \si{cm^{-1}}, respectively.
+This pattern was typical features of \ce{WO3}, consistent with previous study.\cite{Salje1975a,Dixit1986} The high background level probably arise from the metallic core.
+% sg tem
+\begin{figure}[htb]
+\centering
+\includegraphics[width=0.9\textwidth]{JAP-2column_Fig5.jpg}
+\caption[Characterization of \ce{WO3}: TEM]{TEM graphs of as-prepared NWs.
+Left: TEM image of one nanowire, the diameter is about 40 nm.
+Right: HRTEM images showing the spacing is 0.38 nm, corresponding to (002) plane distance.}
+\label{fig:woseedtem}
+\end{figure}
+
+We also examine the as-synthesized NWs using TEM.
+TEM specimen was prepared by using carbon grid to slightly scratch the as-grown sample.
+One can also disperse the NWs into acetone and then drop cast onto TEM grids.
+As shown in Fig.~\ref{fig:woseedtem}, the growth direction is determined to be [001], similar to previous reports.
+The streakings in SEAD pattern presumably arise from stacking defaults.
+
+We would like to discuss a little more on the dispersion of \ce{WO3} NWs, since the stability of \ce{WO3} dispersion is important for its applications.
+\citeauthor{Kozan2008} studied the stability of \ce{WO3} in various polar solvents such as acetone, isopropanol(IPA), ethanol, 1-methoxy-2-propanol (1M-2P) and N-dimethylformamide(DMF).\cite{Kozan2008} High power ultra-sonication was applied for about 2 minutes followed by a low power ultrasonic bath for 15 minutes.
+The the solvent was left to sedimentation.
+Samples was drawn out with pipette and transferred to clean substrate for observation.
+It is suggested that bundled NWs aggregates in 1M-2P seem to breakup at the outer branches to a small extent and turn into slightly more compact aggregate, providing well-dispersed stable suspension.
+Subsequently, this suggests we could harvest the as-grown nanowires by a solution ultra-sonication method.
+Generally there will be metallic tungsten in the core region of powder particles.
+The separation of NWs could be done via the route reported by \citeauthor{Kumar2008}, where separation by sonication in 1-methoxy 2-propanol followed by gravity sedimentation.\cite{Kozan2008}
+
+%\textbf{Growth mechanism}
+
+In regarding to the formation of NWs on tungsten powder itself, we assume the driving force is related to interfacial strain between W and \ce{WOx}.
+Oxidation of tungsten proceed slowly at room temperature and an oxide layer of $100 \AA$  was found.\cite{Warren1996} The tungsten powder used in current study would be covered by a thin oxide layer as well.
+During oxidation, different oxidation rates exist for different crystallographic orientations on the tungsten powder.
+Oxidation occurring at boundaries and defects are preferred.\cite{You2010} Compressive strain will gradually accumulate at the tungsten oxide/tungsten interface, which might limit the diffusion rate of oxygen at temperature lower than 500 \si{\degreeCelsius}.\cite{tungsten1999} At elevated temperature, cracks will primarily occur, as observed in Fig.~\ref{fig:pdtemp}.
+When heated up, tungsten and the oxide shell will probably relax the strain by converting into substoichiometric NWs, a similar process as suggested by \citeauthor{Klinke2005} in the chemically induced strain growth of tungsten oxide NWs.\cite{Klinke2005} It is worth noting that tungsten oxide nanowires could also formed when \ce{WO3} is reduced.\cite{Sarin1975} We speculate that the elongation of \ce{WOx} is thermodynamically favorable during the conversion from metallic tungsten to tungsten oxide as well.
+Another possible formation  mechanism of NWs on tungsten powder is a local evaporation-condensation process.
+
+The enhanced yield of NWs obtained via seeded growth could be explained by a vapor-solid (VS) mechanism.
+External supply of growth species will condense onto the powders and substrate simultaneously, promoting the elongation of NWs on power as well as resulting island-layer growth on substrate.
+We found that the local NW density in oxidation experiment was much higher than that of seeded growth.
+It is reasonable to presume that during seeded growth, several NWs in a small region on powder will coalescence, as evidenced by the bundled structures.
+At last, we point out that when low purity tungsten powder (3N) in our stock was used as source, sodium tungsten oxide nanowires were found to be dominant in the final product.
+The details have been discussed in Section.~\ref{sec:nawox}.
+It seems surprising that when 3N powder was used as seeds, only \ce{WO3} nanowires was obtained.
+We attribute this result to the lower temperature and significantly reduced amount of 3N powder used in the seeded growth, compared with the conditions in another study.
+The source material in seeded growth is not limited to high purity tungsten powder.
+Instead, any material that could produce appropriate growth vapor could be employed, indicating the versatility of our approach.
+
+%FG
+
+% fg sem 
+\begin{figure}[htb]
+\centering
+\subfloat[]{\label{fig:sg1}\includegraphics[width=0.45\textwidth]{wox_flow1}}\hspace{0.04\textwidth}
+\subfloat[]{\label{fig:sg2}\includegraphics[width=0.45\textwidth]{wox_flow2}}
+\caption[Characterization of flow growth \ce{WO3}: SEM]{ (a) Low magnification SEM image showing dense array of NWs (b) High magnification SEM image of NWs grew out of layer and close-up view on individual wire.}
+\label{fig:fgsem}
+\end{figure}
+
+% fg tem
+\begin{figure}[htb]
+\centering
+\includegraphics[width=0.8\textwidth]{wo3_tem.jpg}
+\caption[Flow growth of \ce{wo3}:TEM]{TEM characterization of FG \ce{WO3} NWs. }
+\label{fig:fgtem}
+\end{figure}
 

### 2014-01-29 ch-wox/part1.tex
wox 012814

\section{Introduction}

Tungsten oxide (\ce{WO_x}) is an important functional materials with distinctive properties and technology applications. Intense research interest was rekindled by the discovery of \gls{ec} effect in \citeyear{Granqvist1993}.\cite{Granqvist1993}  Nano-engineering \ce{WO_x} bring more possibility and flexibility to its already rich characteristics, therefore resulting research efforts spanning multiple fields of scientific community. Besides smart window based on EC effect, \ce{WO_x} is also well investigated for several other significant applications: photoelectrochemical cell for solar energy conversion and storage, photocatalysis for hydrogen evolution reaction, chemical and biological sensing based on gasochromic effect. In addition, a few young fields are not thoroughly explored: field emission, optical storage, thermoelectrcity, ferroelectricity, and superconductivity.

In this chapter, we will first review the literature to date for both \ce{WO_x} and \ce{Na_xWO3}, then divide the summaries into a) technological application, b) crystal structure and electronic properties and c) synthesis approaches. Then we present our growth methods and results. And we conclude with a brief summary.

\subsection{Rich and useful technological appeals}

Electrochromic effect of tungsten oxide means the coloration (deep blue) and bleaching (transparent) states of \ce{WO3} are reversibly switched upon forward and backward voltage, and the coloration or bleached states remain after disconnecting the voltage. On basis of this property, \gls{ecd} of tremendous energy saving potential is conceptualized and some products have already been commercialized (i.e. smart window\footnote{``We did a case study in five cities, and the average savings in commercial buildings are about 25 percent of the heating, ventilation, and air-conditioning energy use annually," says CEO of View, Inc.}).

In the past decades, tons of works have been devoted to understanding the chromogenic phenomena in \ce{WO3}. We highlight several key results as reviewed by ,
\begin{itemize}
    \item coloration and bleaching can also be stimulated by other routes, such as by UV irradiation, thermal treating, heating in vacuum, reducing atmosphere etc
    \item no electrical coloration occurs in vacuum, but other routes still works
    \item coloration is associated with a proportional increase in conductivity
    \item coloration spectrum is essentially similar in all cases except small variation in peak position and FWHM
    \item coloration is structure sensitive and most efficient in amorphous films
\end{itemize}

Sofar there is no unifying model that could reconcile these contradictory experimental observations. Among all the developed models, polaronic absorption is the most widely accepted mechanism for coloration. In polaron model\footnote{When a free electron travels through a polar solid, it creates a local lattice displacement (longitudinal optical phonon clouds) due to the coulombic interaction with neighboring ions. This local distortion and the electron together is equivalent to a new elementary exciton of the crystal, and is named as polaron}, the intercalation of \ce{M^+} (M = H, \ce{Li}, or Na) ions into \ce{WO3} films is accompanied with the formation of small polarons ($r_p$ comparable to unit cell size) and formal reduction of some \ce{W^{6+}} sites to \ce{W^{5+}}, as depicted in Eq.~\ref{eq:ec}. During the intercalation process, the \ce{M^+} ions enter into these vacant sites.\cite{Hepel2008} Coloration occurs when the polaron band .

\begin{align}\label{eq:ec}
x\ce{M+} + x\ce{e-} +  \ce{$\alpha \hyphen$WO$_{3-y}$}= \ce{$\alpha \hyphen$M$_x$WO$_{3-y}$},
\end{align}

And the polaron binding energy ($E_p$) is given by
\begin{align}
E_p = - \frac{e^2}{2r_p} (\epsilon_\infty^{-1} - \epsilon_{st}^{-1}),
\end{align}

where $\epsilon_\infty$ and $\epsilon_{st}$ are optical and static dielectric constants respectively, and polaron radius $r_p$, which specifies how far the lattice distortion extends, is related to polaron density $N_p$ by $r_p = \frac{1}{2}\sqrt[3]{\pi/6N_p}$. However, the polaron model has difficulty in estimating $r_p$. The asymmetric optical absorption spectrum are often characteristic of large polarons, and dielectric constants ($\epsilon_\infty = 6.52,\epsilon_{st} > 50$,\cite{Deb2008}) suggests the formation of bipolaron. Moreover, polaron model does not take oxygen vacancy into account, which plays a vital role in the nonstoichiometric tungsten oxides. For instance, it is observed that \ce{WO_{3-y}} films are metallic and conductive for $y > 0.5$, blue and conductive for $y = 0.3 \sim 0.5$, and transparent and resistive when $y < 0.3$, regardless of the preparation methods.\cite{Chatten2005}

Therefore another model in analogy to the F-color center is proposed. Color center model assumes the presence of oxygen vacancy $V_O^0$ is associated with \ce{W^{4+}} or 2\ce{W^{5+}} states. This defect level is expected to be inside or near the valence band. When one electron is removed from this level, $V_O^0$ is converted to $V_O^+$.The positively charged vacancy exerts coulombic repulsion to the nearest W-ions, which results in a displacement of the neighboring W-ions and an upward shift of the defect level into the bandgap, thereby creating a color center. The optical transition from $V_O^+$ to $V_O^{2+}$ (a state within the conduction band)
contributes to coloration.\cite{Deb2008}

So the polaron and color center models both agree on that \ce{W^{5+}} and its transition is responsible for the coloration, but disagree on how this \ce{W^{5+}} state is created (foreign ion reduction in polaron model and oxygen vacancy in color center model) and the corresponding energy levels. A modified polaron model is proposed to include \ce{W^{4+}} states in host lattice. Coloration mechanism is represented by Eq.~\ref{eq:cl_bl1} and \ref{eq:cl_bl2}, which described the polaron hopping from one site to another.\cite{Chatten2005}

\begin{align}
h\nu +\ce{W^{5+}(A)} +  \ce{W^{6+}(B)} &\rightarrow \ce{W^{5+}(B)} + \ce{W^{6+}(A) + E_{phonon}} \label{eq:cl_bl1}\\
h\nu +\ce{W^{5+}(A)} +  \ce{W^{4+}(B)} &\rightarrow \ce{W^{5+}(B)} + \ce{W^{4+}(A) + E_{phonon}} \label{eq:cl_bl2}
\end{align}

Similar scenarios occurs in the gasochromic effect. Two models, double injection and color center, arise to account for the coloration upon exposure to certain gases. Both consents to Eq.~\ref{eq:cl_bl1}. But there is a disagreement on the final states. Double injection supports the formation of tungsten bronze \ce{H_xWO3} while color center insists on the inward diffusion of oxygen vacancy and outward diffusion of water molecules. Both have been substantiated experimentally. Therefore the exact mechanism in \ce{WO_x} still requires further investigation. The author believes the resolution to a large extent depends on the phase transitions, as discussed in Section.~\ref{sec:wonawo}.

photocatalytic applications in solar hydrogen generation and organic pollutant degradation.

photocatalyst\cite{Macphee2010}, photoelectrochemical energy application \cite{Su2010}

Photocatalytic activity occurs when a semiconductor in aqueous solution is illuminated by photons of energy larger than the band gap, then electron-hole pairs generate free radicals, (i.e. \ce{OH.}) which enable further reactions. For water splitting using solar energy, the band gap should be within $2.0 \sim 3.0 $ eV, and CB edge should be more negative than reduction potential of \ce{H^+/H2}, whereas the VB top should be more positive than the oxidation potential of \ce{H2O/O2)}.\cite{Wang2012} The valence band holes (\ce{h^+}) oxidize water to oxygen and conduction band electrons propel hydrogen generation, as depicted in Eq.~\ref{eq:hervb} and \ref{eq:hercb}.

\begin{align}
4\ce{h^+} +  \ce{H2O} &\rightarrow \ce{O2} + 4\ce{H^+} \label{eq:hervb}\\
4\ce{H^+} +  4e^- &\rightarrow 2\ce{H2} \label{eq:hercb}
\end{align}

As shown in Fig.~\ref{fig:woxnhe}, \ce{WO3} has CB edge positioned slightly more positive than reduction potential of \ce{H^+/H2}(versus \gls{nhe}), and VB edge much more positive than the oxidation potential of \ce{H2O/O2}. So the photo-cleavage of water cannot be accomplished by \ce{WO3} alone. Nevertheless, a tandem cell approach by \ce{WO3} film and dye-sensitized \ce{TiO2} has been demonstrated with an efficiency of 4.5\%.\cite{Michael1999} It is worth noting that green plants also have two photosynthetic systems connected in series, one for oxidation of water into oxygen and the other for fixation of carbon dioxide.

% wo3 vs NHE
\begin{figure}[htb]
\centering
\includegraphics[width=0.7\textwidth]{woxnhe.jpg}
\caption[Bands positions of \ce{WO3} versus NHE]{Bands positions of \ce{WO3} in contact with aqueous electolyte at pH 1. adapted from Ref\cite{Gratzel2001}}
\label{fig:woxnhe}
\end{figure}

Moreover, favorable oxygen evolution of \ce{WO3} brings good performance in degradation of organic compounds\cite{Hepel2001,Luo2001,Watcharenwong2008}. The formation of long-lived holes is recognized as a key requirement.\cite{Pesci2011} Besides, \ce{WO3} is remarkably stable in acid, making it a significant candidate for treating water pollutant caused by organic acids.\cite{Monllor-Satoca2006}

the ubiquity of \ce{WO6} octahedra is essential for not only the optical properties but the ability to insert and extract ions in the EC oxides, due to the tunnels in three dimensions serving as path for transport of small ions.
The intercalation of hydrogen or alkali ions into \ce{WO3} created electron donor level. By absorbing the red part of incident spectrum, electrons at donor level make transition to the conduction band, causing the blue coloration in \ce{H_xWO3}.

\citeauthor{Wang2009a} mentioned that amorphous \ce{WO3} can only be used in lithium-based electrolytes due to its
in-compact structure and high dissolution rate in acidic electrolyte solutions. Electrochromic materials that can endure acidic electrolytes without degradation should be developed. Crystalline \ce{WO3} nanostructures with their much denser structures and small particle sizes are promising to be used as suitable electrochromic material in acidic electrolytes.

Characterization of ECD (work like a thin-film batteries) includes transmission measurement and associated EC calculation, charge-discharge time, current-time curve and the fitting of obtained data.

The coloration efficiency (CE) represents the change in the optical density (OD) per unit charge density ($Q/A$, in units of \si{\cm^2\per\coulomb}) during switching and can be calculated according to the formula:
\begin{equation}
CE = \frac{\Delta~OD}{(Q/A)} [cm^2/C],
\end{equation}
where OD = $log(T_{bleach}/T_{color})$. The EC and optical density depend on the wavelength and are usually higher in the near IR than in the visible region.
Using Ohm's law($U_s = IR = RQ/t_s$) with switch voltage $U_s$, resistance R and surface area A, switching time $t_s$ could be estimated as
\begin{equation}
t_s = \Delta~OD\cdot A \cdot R /(CE\cdot U_s).
\end{equation}

its one dimensional (1D) nanostructure has attained intensive research efforts in recent years due to the potential applications in advanced nano-electric and nano-optoelectronic devices.

\begin{quote}
a viable electrochromic smart window must exhibit a cycling life time \textgreater $10^5$ cycles, corresponding to an operation life at 10 - 20 years.
\end{quote}

\subsection{Crystal structures and properties of tungsten oxides and sodium tungsten oxides}\label{sec:wonawo}

\textbf{\ce{WO3}} Tungsten trioxides crystalize in multiple phases. The basic building block is \ce{WO6} octahedra.\footnote{Tungsten, with its electronic configuration as \ce{(Xe)4f^{14}5d^{4}6s^{2}}, has empty 5d and 6s orbitals in its +6 oxidation state.} \ce{WO3} crystal structure consists of \ce{WO6} octahedra joined at their corners, which may be considered as a perovskite structure of \ce{CaTiO3} with all \ce{Ca^{2+}} sites vacant. A representative lattice structures is illustrated in Fig.~\ref{fig:wo3oct}. These distorted \ce{WO6} octahedra adapts different tilting angles in different phases and edge-sharing octahedra also arises. The temperature-dependent phase transition and corresponding lattice constants in bulk form is summarized in Table.~\ref{tab:wo3phase}.\cite{Zheng2011} And a firm assignation of space group to monoclinic phases are still in debate.\cite{Chatten2005} It is noticed that the lattice parameters obtained via \emph{ab initio} calculation closely match the experimental values.\cite{Migas2010a} The phase transition scenarios in nanostructured \ce{WO3} are supposed to be much more sophisticated. Within Gibbs-Thomson frame work, one can generally expect lower transition temperature than their bulk counterparts due to enhanced surface energy. Temperature-dependent Raman spectroscopy provided support for this deduction.\cite{Boulova2002}

% wo3 phases
\begin{table}[htb]
\centering
\caption{\ce{WO3} phases}\label{tab:wo3phase}
\begin{tabular}{lccccc}
\toprule
&&&\multicolumn{3}{c}{Lattice constants \AA} \\
\cmidrule(l){4-6}
 Symbol    & Temperature (\si{\degreeCelsius}) & Phase & a & b & c   \\
\midrule
$\epsilon$-\ce{WO3} & $ -140 \sim -50$  & monoclinic II & 7.378 & 7.378 & 7.664  \\
$\delta$-\ce{WO3} & $-50 \sim 17$  & triclinic & 7.309 & 7.522 & 7.686  \\
$\gamma$-\ce{WO3} & $17 \sim 330$  & monoclinic I & 7.306 & 7.540 & 7.692  \\
$\beta$-\ce{WO3} & $330 \sim 740$  & orthorhombic & 7.384 & 7.512 & 3.846  \\
$\alpha$-\ce{WO3} & $> 740$  & tetragonal & 5.25 & NA & 3.91  \\
$h$-\ce{WO3} &  $<400$  & hexagonal & 7.298 & NA & 3.899  \\
\bottomrule
\end{tabular}
\end{table}

\begin{figure}[htb]
\centering
\includegraphics[width=0.4\textwidth]{octwo3.jpg}
\caption[Octahedra model of \ce{WO3}]{Octahedra model of \ce{WO3}}
\label{fig:wo3oct}
\end{figure}

\ce{WO3} is wide gap n-type semiconductor with valence band top featuring $2p$ states of oxygen and conduction band bottom arising primarily from $5d$ states of tungsten with some mixing of oxygen $2p$ states.\cite{Gillet2004} \citeauthor{Migas2010a} maintained there is essentially identical band dispersion near the gap region in case of $\epsilon$-\ce{WO3}, $\delta$-\ce{WO3}, $\gamma$-\ce{WO3} and $\beta$-\ce{WO3}.\cite{Migas2010a} When there is oxygen vacancy, the Fermi level moves into the conduction band and the gap shrinks by about 0.5 eV. \citeauthor{Migas2010a} also pointed out the flat bands at VBM and CBM could lead to poor transport of holes and electrons, thus may compromising the function in photoelectrochemical cells.

 \citeauthor{Chatten2005} also studied the oxygen vacancy in different phases of \ce{WO3}.\cite{Chatten2005}

Nonstoichiometric tungsten oxides \ce{WO_x} (i.e. \ce{WO_{2.92}}, \ce{WO_{2.87}}) are known as Magn$\acute{e}$li phases.

We do not discuss tungsten oxide hydrates (\ce{WO3.nH2O}) in this work since the product of thermal CVD approach is not plagued with this complexity. It's necessary, however, to deal with hydrated \ce{WO3} in the liquid synthesis routes, as indicated in Section.~\ref{sec:woxgrowth}.

Theoretical computation of electronic band structures for \ce{WO_x} proves difficult due to the aforementioned phase transition.

 oxygen deficiency, structure change, electronic properties vary according.

% band gap table
\begin{table}[htb]
\centering
\caption{Tungsten oxides band gap }\label{tab:wo3eg}
\begin{tabular}{lccr}
\toprule
Phase & Experimental (eV) & Theory (eV) & Remarks  \\
\midrule
amorphous \ce{WO3} & 3.2  & NA &    \\
monoclinic bulk \ce{WO3} &  2.6   & 1.73\cite{Migas2010a}  &    \\
tetragonal bulk \ce{WO3} &     & 0.66 \cite{Migas2010a}&    \\
nano-\ce{WO3} & 2.6$\sim$3.2  & NA &    \\
nano-\ce{WO_{3-x}} & NA  & NA &    \\
\bottomrule
\end{tabular}
\end{table}

Tungsten bronzes was coined by Wohler in 1837.\cite{Deb2008} \ce{Na_{x}WO3}

\subsection{Synthesis strategies}\label{sec:woxgrowth}

We will first give a brief review on the synthesis of \ce{WO3}. As the chemical formula suggested, the most straightforward way is heating metallic tungsten in various forms (i.e. powders,\cite{Zhou2005a,Cao2009,Hsieh2010} foils and wires). Actually \ce{WO_x}\footnote{$x$ is between 2 and 3.} NWs was observed when directly heating W wires.\cite{Gu2002a} Due to the extreme high melting point of W, it requires very high temperature (say, above 1100 \si{\degreeCelsius}) to produce large amount of growth species. Therefore scalable growth seems difficult. The DC current heating proved to be a route with potential large yield. Tungsten wire or filament is connected to a voltage source, and substrate is positioned in proximity to the heated W wire.\cite{Lingfei2006,Thangala2007,Chang2007}

Tungsten oxides powder can also been used as precursor to prepare \ce{WO_{x}} \glspl{nw}.\cite{Huang2008a,Wang2009} Hydrogen-containing agents (i.e. water, \ce{H2},or methane\cite{Klinke2005}) were often involved into the reaction.\cite{Baek2007,Karuppanan2007} The potential benefit is \ce{WO3} has a much lower melting point ($\approx 1470$\si{\degreeCelsius}) than that of W.

Direct oxidation and \ce{WO3} conversion could be grouped as addition approach. In contrast, decomposition method is also feasible.
\citeauthor{Pol2005} obtained \ce{W18O49} nanorods by thermal dissociation of \ce{WO(OMe)4} at 700 \si{\degreeCelsius}, and \ce{WO3} by the annealing at 500 \si{\degreeCelsius} at air atmosphere.\cite{Pol2005}

Spray pyrolysis is a typical aerosol-assisted CVD technique. Typical process flow is: the precursor solution is pumped to an atomizer, and then sprayed through the carrier gas as a fine mist of very small droplets onto heated substrates. Subsequently the droplets undergo evaporation, solute condensation, and thermal decomposition, which then result in film formation.\cite{Zheng2011}

Main reactions include: \cee{W + O2 -> WO_{3-x}} \cee{W + H2O -> W_{3-x} + H2}

the energetic sources are ion bombardment, electron beam, laser ablation, and combustion flame\cite{Rao2011}.

The sol–gel process is a well-known, intensively studied wetchemical technique that is widely used in materials synthesis. This method generally starts with a precursor solution (the ``sol") to form discrete particles or a networked gel structure. During the course of gelation (aging process), various forms of hydrolysis and polycondensation take place.

Hydrothermal method has been an important route to synthesize a diversity of nanomaterials (i.e. ). Preparation of \ce{WO_{3-x}} has also been demonstrated hydrothermally.\cite{Lee2003,Gu2007} Usually, the precursor (\ce{H2WO4}) is mixed with other reactants (sulfides or certain organic acid) in solution and pH value is adjusted as another control degree of freedom. Then the solution is transferred into a sealed container (i.e. Teflon autoclave) and maintained at elevated temperature ($120 \sim 300$ \si{\degreeCelsius}) for tens of hours. Finally the product is separated from the solution and dried, layered \ce{WO3.nH2O} flakes are usual products.

In addition, doped \ce{WO3} was also demonstrated

 The composition and phase of final product highly depend on the synthesis conditions.

%\newgeometry{margin=1in}
\begin{landscape}
\begin{table}[htb]
\centering
\caption{Tungsten Oxides Growth and Application}\label{tab:wox}
{\footnotesize
\begin{tabular}{lp{3.5in}p{2.5in}c}
\toprule
composition  &  methods & highlights &  reference  \\
\midrule
\ce{WO3} & hot W filament (above 1500 \si{\degreeCelsius}) in Ar/\ce{O2} flow  & Cubic phase, PL, resistivity measured & \cite{Thangala2007} \\
\addlinespace[0.5em]
& W filament DC heating in \ce{NH3} or \ce{N2}/\ce{H2} flow  & multi phases, 100mg per batch, stable dispersion in both organic and aqueous solvents & \cite{Chang2007} \\
\addlinespace[0.5em]
& W powder heating Ar/\ce{O2} flow  & triclinic phase, CL at 370,415nm, UV-Vis, 3eV & \cite{Hsieh2010} \\
\cmidrule(l){2-4}
& \ce{WOx} film in \ce{H2} and \ce{CH4} flow  & monoclinic phase, tungsten carbide is the key & \cite{Klinke2005} \\
\cmidrule(l){2-4}
& \ce{Na2WO4.2H2O} by hydrothermal heating to test for line break & 3 different morphologies and photodegradation & \cite{Rajagopal2009}  \\
& \ce{H2WO4.2H2O}, \ce{H2O2} and poly(vinyl alcohol) etc by solvothermal  & multi phases deposition of FTO with varied bandgaps  & \cite{Su2010}  \\

\midrule
\ce{W18O49} & \ce{KOH} etching of W tips followed by heating in Ar flow  & oxygen from leakage, VS process& \textcite{Gu2002a} \\
\addlinespace[0.5em]
& \ce{NW(CO)6}, \ce{Me3NO.2H2O} and oleylamine by hydrothermal  &  RT PL at 350nm and 440nm & \cite{Lee2003}  \\
\bottomrule
\end{tabular}
}
\end{table}
\end{landscape}
%\restoregeometry

### 2014-01-29 figure_table.tex
tutorial test
moo3 012714
wox 012814

@@
+% art work global settings
+%  origin:
+ all tick in, line color: blue or black, line width: 2; tick : 18pt;
+ layout area(in): left:1, top:0.3; width 10: height 7; total 
+ layout area(in): left:1, top:0.8; width 9.6: height 7; total 12 by 9
+ export: 3in auto
+ text size: 22
+% SEM
+2.5in by 2in, 300dpi; gray scale
+
 the width of band gap is a measure of chemical bond strength
 
-Fig.~\ref{fig4}(c) illustrated the XRD spectrum of one typical sample.The peaks under circular symbol were identified to be the monoclinic \ce{WO3} phase (ICDD PDF 01-083-0950,\emph{a}=7.30084\AA, \emph{b}=7.53889\AA, \emph{c}=7.6896\AA , $\beta$=90.8920$^\circ$), while the peak under the triangular symbol was indexed to cubic tungsten phase (ICDD PDF 04--16-3405,\emph{a}=3.157\AA).
+A low recombination rate is preferred for high photocatalytic efficiency. The simultaneous migration of electrons and holes.
+\textbf{\ce{WS2}-\ce{WO3}}: 1 kW light source(Hg, or Xe lamp), photon flux, phenol (\ce{C6H5OH}, 94.1g/mol, MP 40C)concentration is 20 mg/L, hydroxyl group.
+The quantitative analysis of phenol was performed via a standard colorimetric method.\footnote{\url{http://omlc.ogi.edu/spectra/PhotochemCAD/html/072.html}}
+\citeauthor{DiPaola1999} prepared \ce{WS2}-\ce{WO3} mixture in two methods, sulfurization of \ce{WO3} and oxidation of \ce{WS2},with the latter are more active.
+\citeauthor{DiPaola1999} also concluded that the actual efficiency of mixed \ce{WS2}-\ce{WO3} catalysts depends on the ratio of each composition present of the surface of the particles, and the maximum of photoactivity is obtained with 40-50\% surface molar ratio of \ce{WS2}.
+
+ref 25, 28 and 41.
+
+\textbf{\ce{MoO3}}:
+
+\citeauthor{Sreedhara2013} studied the kinetics of photodegradation of methylene blue\footnote{\ce{C16H18N3SCl},319.8 g/mol, MP: 100C accompanied with decomposition \url{http://en.wikipedia.org/wiki/Methylene_blue}} dye by few layer \ce{MoO3}.
+For the photodegradation method, it was stated that `` the samples were collected after the photoreaction had been centrifuged for 5 min to remove the photocatalyst before UV-Vis measurement.''
 
@@
 
-Adding notes to tables can be complicated.
-
+% Adding notes to tables can be complicated.
 \begin{table}
-  \caption{A table with notes}
-  \label{tbl:notes}
+  \centering
+  \caption{A table with notes}  \label{tbl:notes}
   \begin{tabular}{ll}

### 2014-01-30 ch-wox/ch-wox.tex
nawox initial

@@
 3N      & Morphology from high to low temperature: islands, dense layer and a few NWs & Dense wires become more and more, \ce{NaxWO3} phase dominates & 20  \\
-3N5     & $\pm1$  & correlated to flow &      NA\\
+3N5     & islands in high temperature end and layers in low temperature end & NA &      NA\\
 4N5  & dense islands, some tiny wires in low temperature end & NA & 0.065 \\
-5N  & dense islands, some tiny wires in low temperature end  & NA & 0.05\\
+5N  & similar to those of 4N5  & NA & 0.05\\
 \bottomrule
@@
 
-Before diving into the complex interaction of \ce{WO3} and \ce{Na_xWO3} nanostructures, we would like to examine the metallic W source itself and its changes after growth.
+Before diving into the growth of \ce{WO3} and \ce{Na_xWO3} nanostructures using 3N powders, we would like to examine the metallic W source itself and its changes after growth.
 The SEM images of all powders before and  after growth are shown in Fig.~\ref{fig:pdbefore} and Fig.~\ref{fig:pdafter}, respectively.
@@
 \centering
-\includegraphics[width=0.7\textwidth]{pd_before.jpg}
+\includegraphics[width=0.6\textwidth]{pd_before.jpg}
 \caption[SEM images of W powder before growth]{SEM images of W powder before growth.(a) 3N, (b) 3N5, (c) 4N5 and (d) 5N. }
@@
 \end{figure}
-
+Tungsten metals crystallize in body center cubic (BCC) phase.
+Overall, we can still discern the facets.
+The 4N5 and 5N powders share similar appearance and size distribution (Fig.~\ref{fig:pdbefore}c-d).
+In contrast, 3N powders are almost half the size of 3N5 ones, and have more uniform size distribution as well.
+Absolute size and its distribution play a key role in its usage as seed, which we will talk more in Section~\ref{sec:sgfg}.
 % powder after growth
@@
 \centering
-\includegraphics[width=0.7\textwidth]{pd_after.jpg}
+\includegraphics[width=0.6\textwidth]{pd_after.jpg}
 \caption[SEM images of W powder after growth]{SEM images of W powder after growth.(a) 3N, (b) 3N5, (c) 4N5 and (d) 5N. }
@@
 \end{figure}
+After growth, 4N5 and 5N powder (Fig.~\ref{fig:pdafter}c-d) both develop the round edges, while 3N and 3N5 powders (Fig.~\ref{fig:pdafter}a-b) become bundled rods.
+This difference mainly arise from the average size.
 
-Typical morphologies of the as-synthesized nanostructures grown on a \ce{SiO2}-Si substrate was shown in Fig.~\ref{fig:nawoxsemedx}(a).
+\textbf{OT growth of 3N}
+
+The sodium contents in 3N powders fundamentally change the deposition in OT growth.
+Typical morphologies of the as-synthesized nanostructures grown on a \ce{SiO2}-Si substrate was shown in Fig.~\ref{fig:nawoxsemedx}a.
 The nanostructures are NWs with lengths from tens microns up to several hundred microns and diameters about 40 to 500 nm.
@@
 Close-up observations at high magnification revealed some nanowires were cylinder-shaped and some were belt-shaped.
-At some locations, microplate structures with a regular rectangular shape grew among the nanowires as demonstrated in Fig.~\ref{fig:nawoxsemedx}(b) and its inset.
+At some locations, microplate structures with a regular rectangular shape grew among the nanowires as demonstrated in Fig.~\ref{fig:nawoxsemedx}b and its inset.
 The chemical compositions of the deposition were identified by EDX.
-A representative EDX spectrum in Fig.~\ref{fig:nawoxsemedx}(c) shows the existence of W, Na, O, and Si signals in the specimen, where the Si signal is from the substrate.
+A representative EDX spectrum in Fig.~\ref{fig:nawoxsemedx}c shows the existence of W, Na, O, and Si signals in the specimen, where the Si signal is from the substrate.
 The crystal structures of the as-synthesized specimens were examined using XRD.
-The diffraction peaks were carefully indexed and the deposition was identified as two phases of sodium tungsten oxides and one phase of tungsten oxide as indicated on Fig.~\ref{fig:nawoxsemedx}(d).
+The diffraction peaks were carefully indexed and the deposition was identified as two phases of sodium tungsten oxides and one phase of tungsten oxide as indicated on Fig.~\ref{fig:nawoxsemedx}d.
 The two sodium tungsten oxide phases are the triclinic \ce{Na5W_{14}O_{44}} phase\footnote{ICDD PDF 04-012-4449,\emph{a}=7.2740\AA, \emph{b}=7.2911\AA, \emph{c}=18.5510\AA, $\alpha$=96.3750$^\circ$, $\beta$=90.8920$^\circ$, $\gamma$=119.6560$^\circ$} and the triclinic \ce{Na2W4O_{13}} phase.\footnote{ICDD PDF 04-012-7108,\emph{a}=11.1630\AA, \emph{b}=3.8940\AA, \emph{c}=8.2550\AA, $\alpha$=90.60$^\circ$, $\beta$=131.36$^\circ$, $\gamma$=79.70$^\circ$} The tungsten oxide is the monoclinic \ce{WO3} phase.\footnote{ICDD PDF 01-083-0950,\emph{a}=7.30084\AA, \emph{b}=7.53889\AA, \emph{c}=7.6896\AA, $\beta$=90.8920$^\circ$}
@@
 The majority of the nanowires were identified as the \ce{Na5W_{14}O_{44}} phase.
-(Fig.~\ref{fig:nawoxtem}(a-c)) The HRTEM image in Fig.~\ref{fig:nawoxtem}(b) reveals that the nanowire has a single-crystalline structure.
-The corresponding diffraction pattern in the inset of Fig.~\ref{fig:nawoxtem}(b) was recorded in $[\bar{1}10]$ axis.
+(Fig.~\ref{fig:nawoxtem}a-c) The HRTEM image in Fig.~\ref{fig:nawoxtem}b reveals that the nanowire has a single-crystalline structure.
+The corresponding diffraction pattern in the inset of Fig.~\ref{fig:nawoxtem}b was recorded in $[\bar{1}10]$ axis.
 Based on the analyses on a series of diffraction patterns and HRTEM images, the nanowire was confirmed as the triclinic \ce{Na5W_{14}O_{44}}.
@@
 The chemical composition of the nanowire was revealed by EDX.
-Fig.~\ref{fig:nawoxtem}(c) shows the nanowire consisted of W, Na, and O.
+Fig.~\ref{fig:nawoxtem}c shows the nanowire consisted of W, Na, and O.
 No other impurities were detected.\footnote{The Cu and C signals come from the supporting Cu grid with lacey carbon and the Cr signal from the tip of JEOL double tilt holder.
-They are not compositions from the nanowires and other structures studied here.} small fraction of nanowires were found to be the monoclinic \ce{WO3} phase.
-(Fig.~\ref{fig:nawoxtem}(d-f)) The SAED shown in the inset of Fig.~\ref{fig:nawoxtem}(e) was recorded in [100] zone.
+They are not compositions from the nanowires and other structures studied here.} Small fraction of nanowires were found to be the monoclinic \ce{WO3} phase.
+(Fig.~\ref{fig:nawoxtem}d-f) The SAED shown in the inset of Fig.~\ref{fig:nawoxtem}e was recorded in [100] zone.
+The growth direction of the \ce{WO3} nanowire was determined to be perpendicular to the (002) plane with a d-spacing of 0.38 nm.
+EDX spectrum in Fig.~\ref{fig:nawoxtem}f shows the nanowire consisted of W and O without Na or other impurities.
+The rectangular microplate structures shown in Fig.~\ref{fig:nawoxsemedx}b were also collected for TEM examination.
+These microplate structures were identified to be the triclinic \ce{Na2W4O_{13}} phase.
+The SAED in Fig.~\ref{fig:nawoxtem}h was recorded in [101] axis.
+No high-quality HRTEM images were acquired for the \ce{Na2W4O_{13}} plate due to its thickness.
+The long edge of the plate was identified as parallel to the (010) plane and the short edge parallel to the ($\bar{1}01$) plane.
+From XRD spectra, the long edge of \ce{Na2W4O_{13}} plate can be figured out as the $\vec{c}$ axis ([001]) and the short edge is along the $\vec{b}$ axis ([010]).
+Fig.~\ref{fig:nawoxtem}i shows the plate structure also consisted of W, Na, and O and no other impurities were detected.
+Normalized to the highest W peak, the Na peak intensity in Fig.~\ref{fig:nawoxtem}i is higher than the one in Fig.~\ref{fig:nawoxtem}c.
+This result indicates a higher Na:W ratio for the \ce{Na2W4O_{13}} plate structure than the one for \ce{Na5W_{14}O_{44}} nanowires, in consistent with the compositions of the two phases.
 
@@
 
-Using 3N source and with increasing growth number from 1 to 5, we found dramatic morphology variation of as-synthesized nanostructures.
-The typical morphologies evolution as to the growth numbers is illustrated in Fig.~\ref{fig:nawoxsemall}.
+Micro-Raman spectroscopy was also carried out at room temperature in ambient atmosphere to confirm the phases of the microplates and ultra-long nanowires.
+Fig.~\ref{fig:nawoxram}a shows the mRaman spectrum of the microplates.
+The Raman lines at 949, 794-777, 366-263 \si{cm^{-1}} closely matches the reported \ce{Na2W4O_{13}} Raman shift frequencies.
+\cite{Fomichev1992} The Raman spectrum from the ultra-long nanowires is shown in Fig.~\ref{fig:nawoxram}b.
+The spectrum shows major peaks in 100-150 \si{cm^{-1}}, 650-900 \si{cm^{-1}}, and 900-100 \si{cm^{-1}} regions.
+As compared to the reported peak positions (shown by reference lines in Fig.~\ref{fig:nawoxram}b), the nanowires consist of only little or no amount of \ce{WO3} and \ce{Na2W4O_{13}} phases.
+Major peaks at 107, 695, 765, 913, 943, and 965 \si{cm^{-1}} cannot be fitted.
+According to the TEM results, the nanowires are mainly \ce{Na5W_{14}O_{44}}, therefore these peaks should belong to the \ce{Na5W_{14}O_{44}} phase.
+Sofar no Raman spectrum has been reported this phase, hence we are probably the first to observe the Raman spectrum for \ce{Na5W_{14}O_{44}}.
+
+\begin{figure}[htb]
+\centering
+\includegraphics[width=0.7\textwidth]{nawox_raman_series}
+\caption[Raman spectra on \ce{Na_xWO3}]{Micro-Raman spectra of (a) microplates matching the reported peak positions of the \ce{Na2W4O_{13}} phase, and (b) nanowires with comparisons to the reported major peak positions of \ce{WO3} (shown by black line) and \ce{Na2W4O_{13}} (shown by red line) phases.}
+\label{fig:nawoxram}
+\end{figure}
+
+Heated at elevated temperatures, the W source, quartz tube, and quartz boat were the three possible sources for Na.
+The sodium concentration in 3N source was 20ppm as provided by vendor.\footnote{Due to the non-uniform distribution of foreign elements, detection of sodium by EDX is possible although the concentration is below the limit of typical EDX capacity.} The Na concentrations in quartz tube and quartz boat (GE 214 quartz, Wilmad Labglass) were 1 ppm and 0.7 ppm,  respectively.
+To confirm the major source of Na content coming from 3N powder, control experiments were employed by using W source with higher purities (4N5 or 5N).
+These ultra-high purity W sources produced pure tungsten oxide deposition.
+No Na content was detected.
+These results verified the Na content was mainly from the 3N W powders, not from the quartz tube and boat.
+In the experiments, the W source was first slowly oxidized at 1000 \si{\degreeCelsius} with 1 sccm \ce{O2} and the oxidized source was then evaporated producing \ce{WO3} and other substoichiometric tungsten oxide vapors.
+The tungsten oxide vapors produced this way were limited by the slow oxidation, as indicated by (i) only small amount of the tungsten source was consumed during the growth and (ii) only the top layer of the tungsten source was oxidized with a dark blue color.
+Due to its low concentration, the exact composition of the Na content in the tungsten source is not clear.
+However, the evaporation rate of the Na content is expected to be high as heated at 1000 \si{\degreeCelsius}.
+This assumption is supported by the observation that no Na was found in the deposition along the whole substrate in control experiments using the used 3N W source.
+Put it in another way, this means that the majority of Na content was already evaporated in previous experiment.
+Hence, despite of its low concentration in the source, the total amount of Na-based vapors produced during the growth was comparable to or more than the amount of tungsten oxide vapors and resulted in the dominating deposition of sodium tungsten oxide phases in the nanowire growth region.
+
+\begin{figure}[htb]
+\centering
+\includegraphics[width=0.8\textwidth]{nawox_edx_series.jpg}
+\caption[Photograph of a series of 3N growth]{(a) Photograph of a series of specimens grown in the same reaction chamber with the increase of growth number showing different growth zones and corresponding morphology changes.
+(b) Change of Na/W ratios with the increase of growth number at different growth zones.}
+\label{fig:nawoxser}
+\end{figure}
+
+As shown by the photograph in Fig.~\ref{fig:nawoxser}a, for a series of growth performed in the same reaction chamber, the morphology of the nanowires changes with the increase of growth numbers.
+Three growth zones of nanowires can be identified in basis of the coverage and density of the nanowires, as delimited by the vertical guide line.
+The growth Zone I was located at high temperature end ranging from 660 to 520 \si{\degreeCelsius}, Zone II was from 520 to 470 \si{\degreeCelsius}, and Zone III from 470 to 420 \si{\degreeCelsius}.
+Detailed morphological changes are depicted in Fig.~\ref{fig:nawoxsemall}.
 
@@
 
-The sodium concentration was 20ppm as provided by vendor.\footnote{Due to the non-uniform distribution of foreign elements, detection of sodium by EDX is possible although the concentration is below the limit of typical EDX capacity.}
+For the first growth (Fig.~\ref{fig:nawoxsemall}a-c) in a new clean reaction chamber, there were only a little nanowires scattered in Zone I (Fig.~\ref{fig:nawoxsemall}a), ultra-long nanowires were mostly found in Zone II with higher density and coverage (Fig.~\ref{fig:nawoxsemall}b), and in Zone III the coverage, density, and length of nanowires gradually reduced as the growth location moved downstream (Fig.~\ref{fig:nawoxsemall}c).
+With growth number increased to the third growth (Fig.~\ref{fig:nawoxsemall}d-f) and to the fifth growth (Fig.~\ref{fig:nawoxsemall}g-i), the coverage, density, and length of the nanowires increased in all three zones.
+Zone I had the most significant morphology changes as shown by Fig.~\ref{fig:nawoxser}a and Fig.~\ref{fig:nawoxsemall}g.
+After fifth growth in the same reaction chamber, the deposition of ultra-long nanowires almost covered all three zones.
+For Zones I and II, no significant morphology change was observed with further increase of the growth number up to 8th growth.
+However, for Zone III the microplate structures (shown in inset of Fig.~\ref{fig:nawoxsemall}i) kept increasing significantly with the growth number.
+EDX study revealed the change of Na concentration in the deposition with the growth number.
+Fig.~\ref{fig:nawoxser}b shows the variation of the Na/W ratios with the increase of growth number at different nanowire growth zones.
+Generally, the Na/W ratios at all growth zones increased with the increase of growth number.
+The large fluctuation of Na/W ratio at Zone III was mainly due to the uneven distribution of Na content with different morphologies at Zone III.
+
+\begin{figure}[htb]
+\centering
+\includegraphics[width=0.9\textwidth]{nawox_sch.jpg}
+\caption[Schematic drawings of residual \ce{Na_xWO3} growth]{Schematic drawings showing (a) growth with tungsten source in a new tube, (b) enhanced growth with both residue deposition and tungsten source, and (c) growth with residue deposition only.}
+\label{fig:nawoxsch}
+\end{figure}
+
+A mechanism of residue deposition enhanced growth was proposed to explain the morphology change of the nanowires with the growth number.
+Since the CVD setup employed here is a hot-wall CVD system, deposition formed on the substrate surface as well as on the inner wall of the reaction chamber in the growth area.
+Residue deposition was fund on the quartz tube which can be distinguished by the color change on the quartz tube after each growth.
+With the increase of growth number for the same reaction chamber, the residue deposition on the inner wall of the tube also increased.
+If a clean quartz tube free of any residue deposition is used as the reaction chamber, the vapors are supplied only from the source material forming deposition in the growth area with lower temperature (as shown by the schematics in Fig.~\ref{fig:nawoxsch}a).
+When a quartz tube with residue deposition from previous depositions is used repeatedly as the reaction chamber, the residue deposition heated at growth temperature will also produce vapor locally.
+Therefore, the vapors from both the source materials and the local residue deposition will result in an enhanced growth of nanowires (Fig.~\ref{fig:nawoxsch}b).
+To prove this hypothesis, control experiments were performed utilizing a quartz tube used multiple times previously (e.g., a growth number of 9).
+The experiments were carried out without any source materials while other growth parameters remain unchanged.
+Similar nanowires were found on the substrate in the nanowire growth zones.
+Without the source materials, the residue deposition from the tube surface was the only possible source that could produce vapors forming nanowires on the substrate (Fig.~\ref{fig:nawoxsch}c).
+This result confirmed the nanowire growth could be enhanced by the presence of the residue deposition and explained the morphology changes of the nanowires with the increase of growth number.
+
+\begin{figure}[htb]
+\centering
+\includegraphics[width=0.8\textwidth]{wox_xrd_series}
+\caption[XRD spectra evolution of \ce{Na_xWO3} growth]{XRD spectra of the as-synthesized specimen with the increase of growth number from 1 to 5.}
+\label{fig:nawoxxrd}
+\end{figure}
+
+The general trend of Na/W ratios with the growth number can also be explained by the aforementioned effect of residue deposition.
+The sodium contents from the residue deposition will join the new Na contents from the W source forming deposition.
+Fig.~\ref{fig:nawoxxrd} shows the XRD spectra of a series of specimens with the growth number increases from 1 to 5.
+The XRD spectra also reveal the revolution of the three phases with changes of relative concentrations as the growth number increases.
+Compared to the \ce{WO3} phase, the \ce{Na5W_{14}O_{44}} and the \ce{Na2W4O_{13}} phases increase significantly as the growth number increase from 1 to 5.
+And in the 5th growth, \ce{Na2W4O_{13}} become the dominated phase compared to the other two phases.
+These results are consistent with the SEM observation (Fig.~\ref{fig:nawoxsemall}) and the composition change from the EDS measurements (Fig.~\ref{fig:nawoxser}b).
+
+\textbf{OT growth of 3N5, 4N5 and 5N}
+
+Typical morphologies of OT growth using other powders are shown in Fig.~\ref{fig:wox3n5} and Fig.~\ref{fig:wox4n5}, respectively.
+The common feature is the deposition is dominated by islands in upstream end and layers in downstream end.
+The exact dimension still shows some minor difference, particularly in low temperature region.
+The deposition with 4N5 and 5N have much smaller grain size than that with 3N5 powder.
 % 3N5 powder growth
@@
 \end{figure}
-
+It is worth pointing out that we found some NWs growth in low temperature end associated with 4N5 (Fig.~\ref{fig:wox4n5}c), although the density is not large.
+We managed to enhance the coverage as discussed in Section~\ref{sec:sgfg}.
 % 4N5 powder growth
@@
 \includegraphics[width=0.9\textwidth]{wox4n5.jpg}
-\caption[SEM images of \ce{WO3} growth using 4N5 powder]{SEM images of \ce{WO3} growth using 4N5 powder showing the morphology variation from (a) high temperature and (b) intermediate temperature, to (c) low temperature.}
+\caption[SEM images of \ce{WO3} growth using 4N5 powder]{SEM images of \ce{WO3} growth using 4N5 powder showing the morphology variation from (a) high temperature and (b) intermediate temperature, to (c) low temperature.
+Growth with 5N powders have almost the same morphology with that of 4N5, and is not shown in this work}
 \label{fig:wox4n5}
@@
 The dimensions of tungsten powder were obtained by measuring the average size in SEM graphs.
-
 We performed a systematic investigation on the oxidation behavior of tungsten powder.
@@
 \centering
-\includegraphics[width=0.8\textwidth]{JAP-2column_Fig1.jpg}
+\includegraphics[width=0.7\textwidth]{JAP-2column_Fig1.jpg}
 \caption[W powder oxidation: temperature effect]{SEM graphs of 99.9\% (3N) tungsten powder oxidization at different temperatures of a) 500\si{\degreeCelsius}, b) 600\si{\degreeCelsius}, c) 650\si{\degreeCelsius}, d) 750\si{\degreeCelsius}, showing the optimal temperature for local formation of nanowires is between 600--650\si{\degreeCelsius}.
@@
 \centering
-\includegraphics[width=0.8\textwidth]{JAP-2column_Fig3.jpg}
+\includegraphics[width=0.7\textwidth]{JAP-2column_Fig3.jpg}
 \caption[W powder oxidation: size effect]{SEM graphs illustrating the oxidization of four different size of tungsten powders at 600~\si{\degreeCelsius} and 1 sccm oxygen flow.
@@
 \centering
-\includegraphics[width=0.8\textwidth]{JAP-2column_Fig2.jpg}
+\includegraphics[width=0.7\textwidth]{JAP-2column_Fig2.jpg}
 \caption[W powder oxidation: oxygen pressure]{SEM graphs of 3N tungsten powder oxidization at 600 \si{\degreeCelsius} under different rates of oxygen flow: a) 1 sccm, b) 2 sccm, c) 3 sccm, d) 10 sccm.
@@
 \centering
-\includegraphics[width=0.9\textwidth]{JAP-2column_Fig5.jpg}
+\includegraphics[width=0.9\textwidth]{JAP-2column_Fig5major.jpg}
 \caption[Characterization of \ce{WO3}: TEM]{TEM graphs of as-prepared NWs.
-Left: TEM image of one nanowire, the diameter is about 40 nm.
-Right: HRTEM images showing the spacing is 0.38 nm, corresponding to (002) plane distance.}
-\label{fig:woseedtem}
+(a) TEM image of one nanowire, the diameter is about 40 nm.
+(b) HRTEM images showing the spacing is 0.38 nm, corresponding to (002) plane distance.}
+\label{fig:woseedtem1}
 \end{figure}
@@
 One can also disperse the NWs into acetone and then drop cast onto TEM grids.
-As shown in Fig.~\ref{fig:woseedtem}, the growth direction is determined to be [001], similar to previous reports.
+Fig.~\ref{fig:woseedtem1} shows the feature of majority NWs.
+The growth direction is determined to be perpendicular to (002) plane, similar to previous reports.
 The streakings in SEAD pattern presumably arise from stacking defaults.
+We also find some NWs exhibit high crystalline quality, as revealed by the TEM analysis in Fig.~\ref{fig:woseedtem2}.
+The sharp SEAD pattern and clear phase contrast in HRTEM demonstrated are both strong evidence of good crystallinity.
+This formation indicated our growth parameters have promising potential to obtain highly crystalline \ce{WO3} NWs.
+
+% sg tem
+\begin{figure}[htb]
+\centering
+\includegraphics[width=0.9\textwidth]{JAP-2column_Fig5minor.jpg}
+\caption[Characterization of \ce{WO3}: TEM cont]{TEM graphs of as-prepared NWs.
+(a) TEM image of one nanowire, the diameter is about 70 nm.
+(b) HRTEM images showing the spacing is 0.379 nm, corresponding to (002) plane distance.}
+\label{fig:woseedtem2}
+\end{figure}
 
@@
 %FG
-
+As shown in Fig.~\ref{fig:wogrowsf}b, we use two substrates in flow growth, each of which is approximate 12mm long.
+Substrate 1 (Sub1) is located at 6.75 to 7 inch (See Fig.~\ref{fig:wogrow} horizontal axis), and substrate 2 (sub2) is placed in close vicinity of downstream end of sub1.
+Source (4N5 and 5N powder) is located at 5 inch, and 0.3 sccm \ce{O2} is used to reduce the \ce{WO_x} vapor pressure.
+Deposition on sub1 is characterized by dense layer, similar to those shown in Fig.~\ref{fig:wox4n5}b.
+However, deposition on sub2 (Fig.~\ref{fig:sg1}) is in sharp contrast to that shown in Fig.~\ref{fig:wox4n5}c, although they are both located in the low temperature region of reaction chamber.
+The NW density is dramatically increased in flow growth layout.
+The NWs have length about 1 to 2 $\mu m$ and diameter about 200 nm.
+Close-up view (inset of Fig.~\ref{fig:sg2}) show the NWs have clear facets, implying its high crystalline quality.
 % fg sem
@@
 \end{figure}
+TEM to be done on D8. 
+% fg tem 
+%\begin{figure}[htb]
+%\centering
+%\includegraphics[width=0.8\textwidth]{wo3_tem.jpg}
+%\caption[Flow growth of \ce{wo3}:TEM]{TEM characterization of FG \ce{WO3} NWs. }
+%\label{fig:fgtem}
+%\end{figure}
 
-% fg tem
-\begin{figure}[htb]
-\centering
-\includegraphics[width=0.8\textwidth]{wo3_tem.jpg}
-\caption[Flow growth of \ce{wo3}:TEM]{TEM characterization of FG \ce{WO3} NWs. }
-\label{fig:fgtem}
-\end{figure}
+The growth mechanism stay the same as aforementioned VS process.
+Both local flow and temperature play an vital role in the formation of dense NW array.
+Splitting one substrate into two presumably introduces some fluctuation in the vapor flow.
+It is well known that in lamellar flow region, there is a velocity boundary above the side wall.
 

### 2014-01-31 BackMatter/app2.tex
synchronize 013014

\chapter{CVD gas dynamics}

kinematic viscosity $\nu$ in unit of $m^2/s$. Dynamic viscosity $\eta = \rho*\nu$ in unit of kg/m/s. The relationship between Pascal second and centipoise is 1 Pas = 1 $Ns/m^2$=1 kg/(ms)=103 cP.  laminar flow is considered to exist if the Re numbers are significantly below 1000.

Ideal gas equation
\[
PV = n R T;
\]
where R = 8.3 J/mole K.

\begin{itemize}
\item 1 mole = 22.4 liters at "STP" (0 C, 1 atmosphere)
\item 1 liter = 0.045 moles at STP
\item 1 cm3 = 4.5E-5 moles @ STP
\item 1 cm3 = 6.4E-8 moles @ 1 Torr, 23 C
\item 1 atm = 760 Torr = 101,000 Pa
\item 1 Pa = 7.6 mTorr
\item 1 SLPM = 7.4E-4 moles/second
\item 1 sccm = 7.4E-7 moles/second
\end{itemize}

Maxwellian velocity distribution is given by
\[
\frac{\partial N}{\partial \nu} = N 4\pi \nu^2 (\frac{m}{2\pi k T})^{3/2} exp(-\frac{m\nu^2}{2k T})
\]
with mean velocity $c_m = \sqrt{\frac{8 RT}{\pi M}}$.

pumping ability in unit of $cm^3/s$ is estimated to be.

\begin{table}[htb]
\centering
\caption{CVD parameters}\label{tab:cvd2}
    \begin{tabular}{lccr}
    \toprule
    \cmidrule(l){4-5}
    parameter       & value    & Ar     & \ce{O2}  \\
    \midrule
    Inner Dia       & 25.4mm    &       &      \\
    pressure (mTorr)&           & 100   & 10   \\
    pressure (Pa)   &           & 13.33 & 1.333 \\
    Molar weight (g/mol) &      & 40     & 32  \\
    chamber volume  &           & $7.7e^{-4}m^3$  & 770ml \\
    RT density      & $kg/m^3$  & $2.14e^{-4}$  & $1.71e^{-5}$ \\
    total molar amount&         & $0.004$  & $4.13e^{-4}$ \\
    average velocity (m/s) & 300K & 398   & 445  \\
    average velocity (m/s) & 1200K& 796   & 890  \\    
    $\eta$  kg/(ms) & 300K      &  $2.272e^{-5}$  & $2.063e^{-5}$   \\
    Reynolds number &          & 95.2      & 9.4   \\ 
    MFP  ()         &  & & \\
    \bottomrule
    \end{tabular}
\end{table}

Mean free path of gas in vacuum:
\[
\lambda_p = \frac{5\times10^{-3}}{P} \approx 0.05,
\]
where $\lambda_p$ is in centimeter, and P is pressure in Torr. Gas impingement flux $\Phi$, is a measure of the frequency with which gas molecules impinge on or collide with a surface.
\[
\Phi = 3.513\times10^{22}\frac{P}{\sqrt{M T}},
\]
Gas flow could be divided into three regimes: molecular flow, intermediate flow and viscous flow.
Knudsen number is
\[
K_n = D/\lambda_p \approx 50,
\]
where D is characteristic dimension of the CVD system.

### 2014-02-02 BackMatter/app2.tex
TMDC initial

@@
 
-kinematic viscosity $\nu$ in unit of $m^2/s$.
-Dynamic viscosity $\eta = \rho*\nu$ in unit of kg/m/s.
-The relationship between Pascal second and centipoise is 1 Pas = 1 $Ns/m^2$=1 kg/(ms)=103 cP.
-laminar flow is considered to exist if the Re numbers are significantly below 1000.
+Reynolds number is define for laminar flow as
+\[
+Re = D \cdot \frac{ V_c \rho}{\eta} = D \cdot \frac{ V_c }{\nu}.
+\]
+
+D is inner diameter of pipe, $V_c$ is velocity, $\rho$ is mass density and $\eta$ is dynamic viscosity $\nu$ is and kinematic viscosity.
+
+Reynolds number is the square of the ratio of the system size to the diffusion length for momentum: Re is the Peclet number for momentum.
+We can now see that small Re corresponds to diffusion lengths comparable to system size: just as before, gradients (in this case in velocity) are small, and the system behaves as a single unit.
+When Re is very large (flows with Re \textgreater 10,000 or even \textgreater 1,000,000 are common in the real world, though fortunately not in CVD reactors) diffusion of momentum only proceeds locally within very tiny cells, and huge gradients are possible: i.e.
+recirculating and turbulent flows.
+Laminar flow is considered to exist if the Re numbers are significantly below 1000.
+
+chamber volume estimation.
+We use 30 sccm Ar to fill the sealed chamber.
+At ambient condition, 1 sccm will fill a one liter vessel from zero pressure to 1 atm in a thousand minutes.
+And in 87 sec, the pressure increase to 80 Torr.
+So we estimate the chamber volume to be 410 mL.
+
+kinematic viscosity $\nu$ in unit of $m^2/s$. Dynamic viscosity $\eta = \rho*\nu$ in unit of kg/m/s. The relationship between Pascal second and centipoise is 1 Pas = 1 $Ns/m^2$=1 kg/(ms)=103 cP.
 
@@
     \toprule
-    \cmidrule(l){4-5}
     parameter       & value    & Ar     & \ce{O2}  \\
@@
     Molar weight (g/mol) &      & 40     & 32  \\
-    chamber volume  &           & $7.7e^{-4}m^3$  & 770ml \\
-    RT density      & $kg/m^3$  & $2.14e^{-4}$  & $1.71e^{-5}$ \\
-    total molar amount&         & $0.004$  & $4.13e^{-4}$ \\
+    chamber volume  &           & $4.1e^{-4}m^3$  & 410ml \\
+    molar con       & $mol/cm^3$ & $5.35e^{-9}$  & $5.35e^{-10}$ \\
+    molecular con   & $molecules/cm^3$  & $3.22e^{15}$ & $3.22e^{14}$ \\
     average velocity (m/s) & 300K & 398   & 445  \\
     average velocity (m/s) & 1200K& 796   & 890  \\
+    Flux  &$ molecules/cm^2/s$ & 3.21e19 & 3.58e18 \\
     $\eta$  kg/(ms) & 300K      &  $2.272e^{-5}$  & $2.063e^{-5}$   \\
     Reynolds number &          & 95.2      & 9.4   \\
-    MFP  ()         &  & & \\
+    MFP  ($\mu m$)   &         &           &     \\
     \bottomrule
@@
 \end{table}
+The molar concentration at 1200 K will be only 25\% of that at RT.
+
+Knudsen equation is 
+\[
+J = ($\alpha$)3.51\times10^{22}\frac{P_{torr}}{\sqrt{MT}},
+\]
+Condensation rate $J(\text{atoms}/\text{cm}^2 \text{sec})$, M in grams/mol. 
+This set the upper bound on the rate of deposition. Usually an accommodation coefficient $\alpha$ is used to account for the adsorption.
 

### 2014-02-02 ch-tms/tms.tex
TMDC initial

\chapter{Transition metal dichalcogenides}

\section{literature review}

Shortly after the the discovery of carbon nanotube (CNT) in 1991, its transition metal dichalcogenides (TMDC) counterparts (\ce{WS2}) was synthesized in 1992. In the following decade, other TMDC and several metal oxides nanotubes were demonstrated as well. \citeauthor{Rao2003} did an excellent job to review these inorganic nanotubes.\cite{Rao2003} Here we just recapitulate the main categories of synthesis methods. 
\begin{enumerate}
\item Reducing \ce{MO3} in \ce{H2} and \ce{H2S} atmosphere\footnote{M = Mo, W in this work}
\item Direct decomposition of \ce{MS3}
\item Decomposition of the ammonium salt \ce{(NH4)2MS4}
\item Using CNT as templates, or arc, laser ablation
\end{enumerate}

Except the aforementioned methods, another important reaction in CVD domain is
\[
\cee{MoCl5(WCl6) + S \rightarrow MoS2(WS2) + S2Cl2}.
\]
This reaction has been explored by several authors,\cite{Stoffels1999} and could be used under atmospheric pressure.\cite{Li2004a}

All these methods can be applied to the growth of TMDC few layer structures, either directly or with some modification or combination, as we shall discuss later. Among all the members of TMDC nanotubes, \ce{WS2} NT is probably the one most well investigated.\cite{Tenne1998,Frey1998,Frey1999,Rothschild2000,Zak2000} The reaction mechanism of \ce{WO3} with \ce{H2}/\ce{H2S} has been thoroughly studied \cite{Feldman1998} and high yield synthesis approach has been established.\cite{Margolin2004}
It is worth noting that \ce{MS2} can be prepared by direct sulfurization from its oxides phase, but reaction \cee{MO3 + Se \rightarrow MSe2} will not proceed unless introducing other reducing agents, such as \ce{H2}.\cite{Tsirlina1998} This fact highlights that sulfur is rather a radical element under elevated temperature.

Parallel with the scenario of graphene and CNT, TMDC few layer structures attracts intensive research efforts recently. The unfolded TMDC nanotubes exhibit many appealing features, i.e., indirect-to-direct band gap transition, valley electronics, and become a promising candidate in energy harvesting, optoelectronics.

For scientific research purpose, exfoliation by liquid or mechanics methods can provide plenty materials. Yet considering the integration into current microelectronic process, CVD synthesis of TMDC FL is desired, which hold the greatest potential for high yield production of \ce{MS2}. So in this work we focus on the CVD-based methods, as summarized in Table~\ref{tab:tmsgrowth}.

\begin{table}
  \centering
  \caption{A table with notes}  \label{tbl:notes}
  \begin{tabular}{ll}
    \toprule
    Header one                            & Header two \\
    \midrule
    Entry one\textsuperscript{\emph{a}}   & Entry two  \\
    Entry three\textsuperscript{\emph{b}} & Entry four \\
    \bottomrule
  \end{tabular}

  \textsuperscript{\emph{a}} Some text;
  \textsuperscript{\emph{b}} Some more text.
\end{table}

% CVD TMDC
\begin{landscape}
\begin{table}[htb]
\centering
\caption{TMDC FL methods summary}\label{tab:tmsgrowth}
{\footnotesize
\begin{tabular}{lp{2in}p{4in}}
\toprule
TMDC  &  precursor & growth condition  \\
\midrule
\ce{WS2} & hot W filament (above 1500 \si{\degreeCelsius}) in Ar/\ce{O2} flow  & Cubic phase, PL, resistivity measured  \\
\addlinespace[0.5em]
& W filament DC heating in \ce{NH3} or \ce{N2}/\ce{H2} flow  & multi phases, 100mg per batch, stable dispersion in both organic and aqueous solvents  \\
\bottomrule
\end{tabular}
}
\end{table}
\end{landscape}

\section{Raman spectra and Layer configuration}

\section{paragraph from word files}

Lattice vibration in hexagonal \ce{MoS2} was studied by (Wieting & Verble, 1971) using infrared and Raman spectroscopy. 15 optical modes are allowed assuming 6 atoms in primitive cell. Refractive indices was calculated as n0= 3.9, ne = 2.5. \cite{Wieting1971}

Band structure  of \ce{MoS2} in bulk form was calculated by (Mattheiss, 1973). There is some controversy about the exact value of bandgap. The calculation result is 1.2eV ( indirect gap).\cite{Mattheiss1973}

Alkali metal intercalated \ce{WS2} film was prepared.(Homyonfer et al., 1997) Stage 6 superlattice formation was suggested according to X-ray diffraction, and photoresponse spectra and electron tunneling measurement were done.

(Ballif, Regula, & Lévy, 1999) annealing of W/S/W layer , a thin Ni layer deposition, Ni-W-S phase diagram.

Sulfurizaiton of W film, (Jäger-Waldau, Lux-Steiner, Jäger-Waldau, & Bucher, 1993)

(Splendiani et al., 2010) reported the PL in monolayer \ce{MoS2}.  Calculation indicated the indirect gap become larger when thinning, while the previous direct one almost stays as the same, the value is about 1.85eV (direct gap).\cite{Splendiani2010}

(Ramasubramaniam, Naveh, & Towe, 2011) investigate the band gap tuning in bilayer TMD materials by applying external E field. Similar research has been done for graphene and bilayer boron nitride. Semiconductor-metal transition was suggested for \ce{MoS2} and WS2, with difference on the CBM and VBM evolution. In \ce{MoS2}, the valence-band-splitting cause the A and B excitons in optical absorption measurement. Calculation shows that CB and VB are translated toward the Fermi level with increasing E field.  The external field localized charge along C axis, but delocalized that within the plane normal towards C, thereby driving the semi-metal transition. It was mentioned that this transition is not anticipated in monolayer \ce{MoS2}. It was emphasized that precise band gaps might be different from the author’s results, yet the gap-tuning should be universal.

(Kośmider & Fernández-Rossier, 2013) studied the heterojunction between two monolayers of \ce{MoS2} and WS2. Top of VB in W layer and bottom of CB in Mo layer, forming type II structure. bilayer gap 1.2 eV.

(Shi, Pan, Zhang, & Yakobson, 2013) studied the strained monolayer \ce{MoS2} and WS2. The results show that exciton binding energy is insensitive to the strain, while optical band gap becomes smaller as strain increases. Monolayer WS2 PL maximum located at about 1.95eV. Calculation shows the electron effective mass of WS2 is the smallest, rendering higher mobility in device.

(Zhou et al., 2010) heterojunction is employed to transferred photo-generated carriers. schottky barrier conduction band electron trapping and consequent longer electron-hole pair lifetimes. Numerous studies have suggested that fine particles of transition metals or their oxides, when dispersed on the surface of a photocatalyst matrix, can act as electron traps on n-type semiconductors.

(Ueno, Saiki, et al. 1990) Van der Waals epitaxial growth of transition metal dichalcogenides (TMD) on mica. ( MoSe2, NbSe2,
Method: MBE substrate temp : 500 \si{\degreeCelsius}

CVD of MoS2 by H2S and MoF6/MoCl5; MoS2 deposition temperature: 400-550 degree. (W. Y. Lee, Besmann, and Stott 1994)

thermal decomposition of (NH4)2MoO2S2 and intermediate product MoOS2 was studied. application: hyfrodesulfurization in refinery (Weber et al. 1996)

\cee{MoCl5 + 1/4S8 + 5/2H2 \rightarrow MoS2 + 5HCl} (Stoffels et al. 1999)

(Endler et al. 1999) solid-phase diagram for \ce{Mo-S-Cl-H-Ar} system at 1 kPa.

(M Remskar et al. 1999) WS2 nanotube from WO3-x whisker. heating 840 degree under flow of H2/N2/H2S ,

A detailed study by (Rothschild, Sloan, and Tenne 2000) tungsten filament oxidation by water. then WS2 nanotube from WO3-x whisker. heating 840 degree under flow of H2/N2/H2S ,

IF MoS2 synthesis by MoO3 nanobelt and S.(X. L. Li and Li 2003)

\begin{align}
\cee{WCl6 + S &rightarrow WS2 + Cl2S2}\\
\cee{MoCl5 + S &\rightarrow MoS2 + S2Cl2} \\
\cee{S2Cl2 + NaOH &\rightarrow NaCl + S + Na2SO3 + H2O}
\end{aligh}

WO3 and S by ball-milling (Z. Wu et al. 2010)

Inorganic core –shell nanotube, WS2@MoS2 core-shell NT.(Kreizman et al. 2010)

vdW Epitaxy of MoS2 on graphene. (Y. Shi et al. 2012)

(Zhan et al. 2012) 1-5nm thick Mo coating on SiO2/Si. Mo coating on Si did not work.

WS2 monolayer and intense photoluminescent behavior. Sulfurization of WO3 film( 5-20 angstrom). (Gutiérrez et al. 2012)

MoO3 on sapphire reduction in H2 at 500 and sulfurizatin at 1000 degree. (Lin et al. 2012)

quantitative Raman of MoS2 on insulating subs. intensity difference between supported and suspended was highlighted, detailed model in support info.(S.-L. Li et al. 2012)

MoS2 on SiO2/Si sub pretreated with OTAS, PTCDA solution. (Y.-H. Lee et al. 2012)

WO3-x (1nm) on SiO2/Si sulfurization at 750-950 degree, (Elías et al. 2013)

source MoS2 powder, Ar On sapphire, SiO2/Si, QWP circularly polarized  light (S. Wu et al. 2013)

MoO3 powder and Sulfur powder, pregrow purge, heating 600 degree, (Mann et al. 2013)

(Wang et al. 2013)
MoS2 CVD (tsinghua univ) layer by layer sulfurization of MoO2
MoO3 powder 25mg and MnO2 powder 25 mg, extra sulfur
Ar purging  20mins, heating at 650 degree to produce MoO2 flakes
Further reaction between MoO2 and S was performed at 850-950 degree under Ar flow.

MoS2 on SiO2, sapphire, and graphite by MoCl5 and S. (Yu et al. 2013)
growth time: 10min at 850 degree, P: 2 Torr.

MoO3 nanoribbon (Na2MoO4 hydrothermal method)sulphurization, (Najmaei et al. 2013)

review of inorganic 2D materials, (Chhowalla et al., 2013)

(Ramasubramaniam, 2012) decrease in dielectric screening and thereby enhanced excitonic effect.
DFT is not good at describing photoemission, GW approximation overcome this deficiency but still not enough for photoabsorption process in which ehps are created. BSE equation is used to compensate this discrepancy,
WX2 exhibits larger spin-orbit splitting as compared to MX2 family.

### 2014-02-02 figure_table.tex
TMDC initial

@@
 %\newgeometry{margin=1in}
+\begin{landscape}
+\begin{table}[htb]
+\centering
+\caption{Tungsten Oxides Growth and Application}\label{tab:wox}
+{\footnotesize
+\begin{tabular}{lp{3.5in}p{2.5in}c}
+\toprule
+composition  &  methods & highlights &  reference  \\
+\midrule
+\ce{WO3} & hot W filament (above 1500 \si{\degreeCelsius}) in Ar/\ce{O2} flow  & Cubic phase, PL, resistivity measured & \cite{Thangala2007} \\
+\addlinespace[0.5em]
+& W filament DC heating in \ce{NH3} or \ce{N2}/\ce{H2} flow  & multi phases, 100mg per batch, stable dispersion in both organic and aqueous solvents & \cite{Chang2007} \\
+\bottomrule
+\end{tabular}
+}
+\end{table}
+\end{landscape}
+%\restoregeometry
+
+%\newgeometry{margin=1in}
 %\begin{landscape}

### 2014-02-03 ch-tms/tms.tex
tms reviews

@@
 Parallel with the scenario of graphene and CNT, TMDC few layer structures attracts intensive research efforts recently.
-The unfolded TMDC nanotubes exhibit many appealing features, i.e., indirect-to-direct band gap transition, valley electronics, and become a promising candidate in energy harvesting, optoelectronics.
+The unfolded TMDC nanotubes exhibit many appealing features, i.e., indirect-to-direct band gap transition,\cite{Splendiani2010} valley electronics, and become a promising candidate in energy harvesting, optoelectronics.
 
-For scientific research purpose, exfoliation by liquid or mechanics methods can provide plenty materials.
+For scientific research purpose, exfoliation by liquid \cite{Smith2011} or mechanical methods \cite{Lee2010a} can provide plenty materials.
 Yet considering the integration into current microelectronic process, CVD synthesis of TMDC FL is desired, which hold the greatest potential for high yield production of \ce{MS2}.
 So in this work we focus on the CVD-based methods, as summarized in Table~\ref{tab:tmsgrowth}.
+
+\citeauthor{Lee1994} studied the CVD of \ce{MoS2} by \ce{MoCl5} or \ce{MoF6} and \ce{H2S} in great details.
+Phase diagrams for \ce{Mo-S-Cl-H} and \ce{Mo-S-F-H} system at 1 kPa were simulated.
+\citeauthor{Endler1999} also investigated the solid-phase diagram for \ce{Mo-S-Cl-H-Ar} system.\cite{Endler1999} It was found pure \ce{MoS2} was main product when molar ratio of \ce{H2S}-\ce{MoCl5} exceeds 2.
+More important, \ce{MoS2} basal plane orientation can be parallel to substrate when the thickness was smaller than 50 nm.
+
+\citeauthor{Regula1997} studied the Ni-W-S phase diagram and the role of Ni layer in promoting \ce{WS2} film growth from amorphous \ce{WS3}.\cite{Regula1997} \emph{In-situ} TEM analysis confirmed the formation of \ce{NiS_x} droplets and lateral growth of \ce{WS2} from these droplets.
+\cite{Regula1998}
+
+\citeauthor{Cong2013} prepared monolayer \ce{WS2} on 300nm \ce{SiO2}-Si by sulfurization of \ce{WO3} powders in a one-end sealed tube.\cite{Cong2013} It was suggested that pre-cleaning the inner tube by IPA and DI water could effectively increase the pressure of vapor source.
+This observation probably arise from the reduction of \ce{WO3} assisted by IPA and water residuals, or due to the possible presence of \ce{H2S}.
+Intermediate phase \ce{WO_yS_{2-y}} and \ce{WS_{2+x}} is proposed in the growth mechanism.
+Possible thick \ce{WS_{2+x}} flakes decompose subsequently, leading to ML \ce{WS2}.
+Sulfurization mechanism study of \ce{WO3} suggested \ce{W^{6+}} cannot be directly reduce to \ce{W^{4+}} in \ce{WS2}.\cite{VanderVlies2002,VanderVlies2002a} Tungsten oxysulfides was necessary as the intermediate phase.
+Other chalcogenide has also been synthesized using this one-end sealed layout.\cite{Mukherjee2013}
+
+\citeauthor{Cao2014} studied the layer-dependence \ce{MoS2} electrocatalysis and propose the vertical hopping efficiency of electrons instead of the edge site numbers is a key factor for catalytic reaction.\cite{Cao2014} ref19,20
+
+In studying the growth of TMDC, two issues dominate: one is the reaction of precursor, the other is the surface energy status of receiving substrates.
+For \ce{MoS2}, the reaction mechanism of \ce{MoO3} to \ce{MoS2} was studied by \citeauthor{Weber1996}.\cite{Weber1996} This study provided guideline for the recent syntheses of \ce{MoS2} by sulfurization of \ce{MoO3}.
+\cite{Lin2012,Lee2012b,Liu2012a}
 
@@
 {\footnotesize
-\begin{tabular}{lp{2in}p{4in}}
+\begin{tabular}{lp{2.5in}p{4.5in}}
 \toprule
-TMDC  &  precursor & growth condition  \\
+TMDC  &  precursor & growth condition (default temperature unit \si{\degreeCelsius}) \\
 \midrule
-\ce{WS2} & hot W filament (above 1500 \si{\degreeCelsius}) in Ar/\ce{O2} flow  & Cubic phase, PL, resistivity measured  \\
+\ce{MoS2} films \cite{Lee1994,Endler1999} & \ce{MoCl5}, \ce{H2S} & 1 kPa, temperature: 400-550 \si{\degreeCelsius}, 100/10/2.5 sccm for Ar, \ce{H2S} and \ce{MoCl5} flow\\
 \addlinespace[0.5em]
-& W filament DC heating in \ce{NH3} or \ce{N2}/\ce{H2} flow  & multi phases, 100mg per batch, stable dispersion in both organic and aqueous solvents  \\
+\ce{MoS2} FL \cite{Zhan2012} & 1-5nm Mo films on \ce{SiO2}, Sulfur & purging, RT-550@30mins, 550-750@90mins and hold for 10 mins. Mo coating on Si did not work.\\
+\ce{MoS2} FL \cite{Lin2012,Wang2013} & 4nm \ce{MoO3} coating on sapphire  & reduced to \ce{MoO2} in \ce{H2} and Ar at 500 \si{\degreeCelsius}, sulfurization at 850-1000 \si{\degreeCelsius} \\
+\addlinespace[0.5em]
+\ce{MoS2} FL \cite{Liu2012a} & \ce{(NH4)2MoS4} in DMF solution transport by Ar bubbler or dip-coating onto subs &  annealing under Ar or Ar + Sulfur, total pressure 0.2-2 Torr, \\
+ \addlinespace[0.5em]
+\ce{MoS2} FL \cite{Wu2013} & \ce{MoS2} powder & Ar flow, 900 \si{\degreeCelsius} heating, pressure 20 Torr, 650 \si{\degreeCelsius} growth\\
+ \addlinespace[0.5em]
+\ce{MoS2} FL \cite{Mann2013,Najmaei2013,Ji2013} Rice & \ce{MoO3} powders or ribbons, Sulfur & Ar flow, 530-850\si{\degreeCelsius}, total pressure 0.2-2 Torr, 5-30mins, mica or \ce{SiO2}-Si\\
+ \addlinespace[0.5em]
+\ce{MoS2} FL \cite{Lee2012b,Ling2014} & 18mg \ce{MoO3} powders, Sulfur,various seeding promoter on sub & 5sccm Ar, 650 \si{\degreeCelsius}, 3min growth, atmospheric pressure, quick cooling\\
+
+ \midrule
+\ce{WS2} films\cite{Ballif1999,Brunken2008} & sputtering \ce{WS_{3+x}} on 10nm Ni  & annealing under Ar for 1h at 850 \si{\degreeCelsius} \\
+\addlinespace[0.5em]
+\ce{WS2} FL \cite{Berkdemir2013} & $\sim$1nm \ce{WO3} coating on 285nm \ce{SiO2}-Si, 500mg sulfur & 800 \si{\degreeCelsius} for 30 mins, 100 sccm Ar, atmospheric pressure in \cite{Gutierrez2012} and 450 mTorr in \cite{Elias2013}.
+triangular flakes obtained\\
+\addlinespace[0.5em]
+\ce{WS2} ML \cite{Cong2013} & \ce{WO3} powder on sub1 covered by sub2, sulfur & 750 \si{\degreeCelsius} hold for 5mins, one-end sealed inner tube, 100 sccm Ar\\
+
 \bottomrule
@@
 
+\ce{WS2} NT chirality by TEM SEAD.\cite{Zhu2000}
+
+hydrogen evolution catalysts. \cite{Merki2011}
+
+\ce{WS2} NT FET. \cite{Levi2013}
+
+\ce{WS2} NT transport \cite{Zhang2012c}
+
+Raman substrate dependence \cite{Buscema2013}
+
 \section{paragraph from word files}
 
-Lattice vibration in hexagonal \ce{MoS2} was studied by (Wieting & Verble, 1971) using infrared and Raman spectroscopy.
-15 optical modes are allowed assuming 6 atoms in primitive cell.
-Refractive indices was calculated as n0= 3.9, ne = 2.5.
-\cite{Wieting1971}
-
-Band structure  of \ce{MoS2} in bulk form was calculated by (Mattheiss, 1973).
-There is some controversy about the exact value of bandgap.
-The calculation result is 1.2eV ( indirect gap).\cite{Mattheiss1973}
-
-Alkali metal intercalated \ce{WS2} film was prepared.(Homyonfer et al., 1997) Stage 6 superlattice formation was suggested according to X-ray diffraction, and photoresponse spectra and electron tunneling measurement were done.
-
-(Ballif, Regula, & Lévy, 1999) annealing of W/S/W layer , a thin Ni layer deposition, Ni-W-S phase diagram.
-
-Sulfurizaiton of W film, (Jäger-Waldau, Lux-Steiner, Jäger-Waldau, & Bucher, 1993)
-
-(Splendiani et al., 2010) reported the PL in monolayer \ce{MoS2}.
-Calculation indicated the indirect gap become larger when thinning, while the previous direct one almost stays as the same, the value is about 1.85eV (direct gap).\cite{Splendiani2010}
-
-(Ramasubramaniam, Naveh, & Towe, 2011) investigate the band gap tuning in bilayer TMD materials by applying external E field.
-Similar research has been done for graphene and bilayer boron nitride.
-Semiconductor-metal transition was suggested for \ce{MoS2} and WS2, with difference on the CBM and VBM evolution.
-In \ce{MoS2}, the valence-band-splitting cause the A and B excitons in optical absorption measurement.
-Calculation shows that CB and VB are translated toward the Fermi level with increasing E field.
-The external field localized charge along C axis, but delocalized that within the plane normal towards C, thereby driving the semi-metal transition.
-It was mentioned that this transition is not anticipated in monolayer \ce{MoS2}.
-It was emphasized that precise band gaps might be different from the author’s results, yet the gap-tuning should be universal.
-
-(Kośmider & Fernández-Rossier, 2013) studied the heterojunction between two monolayers of \ce{MoS2} and WS2.
-Top of VB in W layer and bottom of CB in Mo layer, forming type II structure.
-bilayer gap 1.2 eV.
-
-(Shi, Pan, Zhang, & Yakobson, 2013) studied the strained monolayer \ce{MoS2} and WS2.
-The results show that exciton binding energy is insensitive to the strain, while optical band gap becomes smaller as strain increases.
-Monolayer WS2 PL maximum located at about 1.95eV.
-Calculation shows the electron effective mass of WS2 is the smallest, rendering higher mobility in device.
-
-(Zhou et al., 2010) heterojunction is employed to transferred photo-generated carriers.
-schottky barrier conduction band electron trapping and consequent longer electron-hole pair lifetimes.
-Numerous studies have suggested that fine particles of transition metals or their oxides, when dispersed on the surface of a photocatalyst matrix, can act as electron traps on n-type semiconductors.
-
-(Ueno, Saiki, et al. 1990) Van der Waals epitaxial growth of transition metal dichalcogenides (TMD) on mica. ( MoSe2, NbSe2,
-Method: MBE substrate temp : 500 \si{\degreeCelsius}
-
-CVD of MoS2 by H2S and MoF6/MoCl5; MoS2 deposition temperature: 400-550 degree. (W. Y. Lee, Besmann, and Stott 1994)
-
-thermal decomposition of (NH4)2MoO2S2 and intermediate product MoOS2 was studied. application: hyfrodesulfurization in refinery (Weber et al. 1996)
-
-\cee{MoCl5 + 1/4S8 + 5/2H2 \rightarrow MoS2 + 5HCl} (Stoffels et al. 1999)
-
-(Endler et al. 1999) solid-phase diagram for \ce{Mo-S-Cl-H-Ar} system at 1 kPa.
-
-(M Remskar et al. 1999) WS2 nanotube from WO3-x whisker. heating 840 degree under flow of H2/N2/H2S ,
-
-A detailed study by (Rothschild, Sloan, and Tenne 2000) tungsten filament oxidation by water. then WS2 nanotube from WO3-x whisker. heating 840 degree under flow of H2/N2/H2S ,
-
-IF MoS2 synthesis by MoO3 nanobelt and S.(X. L. Li and Li 2003)
-
 \begin{align}
-\cee{WCl6 + S &rightarrow WS2 + Cl2S2}\\
+\cee{WCl6 + S &\rightarrow WS2 + Cl2S2}\\
 \cee{MoCl5 + S &\rightarrow MoS2 + S2Cl2} \\
 \cee{S2Cl2 + NaOH &\rightarrow NaCl + S + Na2SO3 + H2O}
-\end{aligh}
+\end{align}
 
-WO3 and S by ball-milling (Z. Wu et al. 2010)
-
-Inorganic core –shell nanotube, WS2@MoS2 core-shell NT.(Kreizman et al. 2010)
-
-vdW Epitaxy of MoS2 on graphene. (Y. Shi et al. 2012)
-
-(Zhan et al. 2012) 1-5nm thick Mo coating on SiO2/Si. Mo coating on Si did not work.
-
-WS2 monolayer and intense photoluminescent behavior. Sulfurization of WO3 film( 5-20 angstrom). (Gutiérrez et al. 2012)
-
-MoO3 on sapphire reduction in H2 at 500 and sulfurizatin at 1000 degree. (Lin et al. 2012)
-
-quantitative Raman of MoS2 on insulating subs. intensity difference between supported and suspended was highlighted, detailed model in support info.(S.-L. Li et al. 2012)
-
-MoS2 on SiO2/Si sub pretreated with OTAS, PTCDA solution. (Y.-H. Lee et al. 2012)
-
-WO3-x (1nm) on SiO2/Si sulfurization at 750-950 degree, (Elías et al. 2013)
-
-source MoS2 powder, Ar On sapphire, SiO2/Si, QWP circularly polarized  light (S. Wu et al. 2013)
-
-MoO3 powder and Sulfur powder, pregrow purge, heating 600 degree, (Mann et al. 2013)
-
-(Wang et al. 2013)
-MoS2 CVD (tsinghua univ) layer by layer sulfurization of MoO2
-MoO3 powder 25mg and MnO2 powder 25 mg, extra sulfur
-Ar purging  20mins, heating at 650 degree to produce MoO2 flakes
-Further reaction between MoO2 and S was performed at 850-950 degree under Ar flow.
-
-MoS2 on SiO2, sapphire, and graphite by MoCl5 and S. (Yu et al. 2013)
-growth time: 10min at 850 degree, P: 2 Torr.
-
-MoO3 nanoribbon (Na2MoO4 hydrothermal method)sulphurization, (Najmaei et al. 2013)
-
-review of inorganic 2D materials, (Chhowalla et al., 2013)
-
-(Ramasubramaniam, 2012) decrease in dielectric screening and thereby enhanced excitonic effect.
-DFT is not good at describing photoemission, GW approximation overcome this deficiency but still not enough for photoabsorption process in which ehps are created.
-BSE equation is used to compensate this discrepancy,
-WX2 exhibits larger spin-orbit splitting as compared to MX2 family.
+\begin{figure}[htb]
+\centering
+\includegraphics[width=0.7\textwidth]{ws2_ramsch}
+\caption[CVD system]{Chemical vapor system and \cite{Ghorbani-asl}}
+\label{fig:ws2ramsch}
+\end{figure}

### 2014-02-03 figure_table.tex
tms reviews

@@
+\subsection{artwork}
 % art work global settings
 %  origin:
+
  all tick in, line color: blue or black, line width: 2; tick : 18pt;
@@
 
+\subsection{photocatalyst}
 A low recombination rate is preferred for high photocatalytic efficiency. The simultaneous migration of electrons and holes.
@@
 For the photodegradation method, it was stated that `` the samples were collected after the photoreaction had been centrifuged for 5 min to remove the photocatalyst before UV-Vis measurement.''
+\subsection{tms}
+%%%%%%%%%%%% literature tms %%%%%%%%%
 
+(Ramasubramaniam, Naveh, \& Towe, 2011) investigate the band gap tuning in bilayer TMD materials by applying external E field.
+Similar research has been done for graphene and bilayer boron nitride.
+Semiconductor-metal transition was suggested for \ce{MoS2} and WS2, with difference on the CBM and VBM evolution.
+In \ce{MoS2}, the valence-band-splitting cause the A and B excitons in optical absorption measurement.
+Calculation shows that CB and VB are translated toward the Fermi level with increasing E field.
+The external field localized charge along C axis, but delocalized that within the plane normal towards C, thereby driving the semi-metal transition.
+It was mentioned that this transition is not anticipated in monolayer \ce{MoS2}.
+It was emphasized that precise band gaps might be different from the author’s results, yet the gap-tuning should be universal.
+
+(Shi, Pan, Zhang, \& Yakobson, 2013) studied the strained monolayer \ce{MoS2} and WS2.
+The results show that exciton binding energy is insensitive to the strain, while optical band gap becomes smaller as strain increases.
+Monolayer WS2 PL maximum located at about 1.95eV.
+Calculation shows the electron effective mass of WS2 is the smallest, rendering higher mobility in device.
+
+(Kośmider \& Fernández-Rossier, 2013) studied the heterojunction between two monolayers of \ce{MoS2} and WS2.
+Top of VB in W layer and bottom of CB in Mo layer, forming type II structure.
+bilayer gap 1.2 eV.
+
+Lattice vibration in hexagonal \ce{MoS2} was studied by (Wieting & Verble, 1971) using infrared and Raman spectroscopy.
+15 optical modes are allowed assuming 6 atoms in primitive cell.
+Refractive indices was calculated as n0= 3.9, ne = 2.5.
+\cite{Wieting1971}
+
+Band structure  of \ce{MoS2} in bulk form was calculated by (Mattheiss, 1973).
+There is some controversy about the exact value of bandgap.
+The calculation result is 1.2eV ( indirect gap).\cite{Mattheiss1973}
+
+Alkali metal intercalated \ce{WS2} film was prepared.(Homyonfer et al., 1997) Stage 6 superlattice formation was suggested according to X-ray diffraction, and photoresponse spectra and electron tunneling measurement were done.
+
+Sulfurizaiton of W film, (Jäger-Waldau, Lux-Steiner, Jäger-Waldau, & Bucher, 1993)
+
+(Splendiani et al., 2010) reported the PL in monolayer \ce{MoS2}.
+Calculation indicated the indirect gap become larger when thinning, while the previous direct one almost stays as the same, the value is about 1.85eV (direct gap).\cite{Splendiani2010}
+
+(Zhou et al., 2010) heterojunction is employed to transferred photo-generated carriers.
+schottky barrier conduction band electron trapping and consequent longer electron-hole pair lifetimes.
+Numerous studies have suggested that fine particles of transition metals or their oxides, when dispersed on the surface of a photocatalyst matrix, can act as electron traps on n-type semiconductors.
+
+thermal decomposition of (NH4)2MoO2S2 and intermediate product MoOS2 was studied. application: hyfrodesulfurization in refinery (Weber et al. 1996) \cite{Weber1996}
+
+\cee{MoCl5 + 1/4S8 + 5/2H2 \rightarrow MoS2 + 5HCl} (Stoffels et al. 1999)
+
+(M Remskar et al. 1999) WS2 nanotube from WO3-x whisker. heating 840 degree under flow of H2/N2/H2S ,
+
+A detailed study by (Rothschild, Sloan, and Tenne 2000) tungsten filament oxidation by water. then WS2 nanotube from WO3-x whisker. heating 840 degree under flow of H2/N2/H2S ,
+
+IF MoS2 synthesis by MoO3 nanobelt and S.(X. L. Li and Li 2003)
+
+Inorganic core –shell nanotube, WS2@MoS2 core-shell NT.(Kreizman et al. 2010)
+
+vdW Epitaxy of MoS2 on graphene. (Y. Shi et al. 2012)
+
+WS2 monolayer and intense photoluminescent behavior. Sulfurization of WO3 film( 5-20 angstrom). (Gutiérrez et al. 2012)
+
+MoO3 on sapphire reduction in H2 at 500 and sulfurizatin at 1000 degree. (Lin et al. 2012)
+
+quantitative Raman of MoS2 on insulating subs. intensity difference between supported and suspended was highlighted, detailed model in support info.(S.-L. Li et al. 2012)
+
+MoS2 on SiO2/Si sub pretreated with OTAS, PTCDA solution. (Y.-H. Lee et al. 2012)
+
+WO3-x (1nm) on SiO2/Si sulfurization at 750-950 degree, (Elías et al. 2013)\cite{Elias2013}
+
+source MoS2 powder, Ar On sapphire, SiO2/Si, QWP circularly polarized  light (S. Wu et al. 2013)
+
+(Wang et al. 2013)
+MoS2 CVD (tsinghua univ) layer by layer sulfurization of MoO2
+MoO3 powder 25mg and MnO2 powder 25 mg, extra sulfur
+Ar purging  20mins, heating at 650 degree to produce MoO2 flakes
+Further reaction between MoO2 and S was performed at 850-950 degree under Ar flow.
+
+MoS2 on SiO2, sapphire, and graphite by MoCl5 and S. (Yu et al. 2013)
+growth time: 10min at 850 degree, P: 2 Torr.
+
+review of inorganic 2D materials, (Chhowalla et al., 2013)
+
+(Ramasubramaniam, 2012) decrease in dielectric screening and thereby enhanced excitonic effect.
+DFT is not good at describing photoemission, GW approximation overcome this deficiency but still not enough for photoabsorption process in which ehps are created.
+BSE equation is used to compensate this discrepancy,
+WX2 exhibits larger spin-orbit splitting as compared to MX2 family.
+
+reaction mechanism of \ce{MoO3} to \ce{Mo2S}.\cite{Weber1996}
+
+\citeauthor{Ling2014} studied the role of seeding promoters in CVD growth of FL \ce{MoS2}.\cite{Ling2014} PTAS treated substrates provided nucleation site and thus enable uniform deposition of \ce{MS2}.
+This enhancement perhaps arise from the \ce{K+} ions.
+
+%%%%%%%%%%%%%%%%%%%%%%
+\subsection{figure table units}
 \si{W/in^2}
@@
 
+\subsection{chromic}
+
 the electrical conductivity is given by $\sigma = n e \mu$, where $n$ is the density of free carriers, $\mu$ is their mobility and $e$ is electronic charge.

### 2014-02-07 BackMatter/paper.tex
further contents on ws2

\chapter{paper reading}

\section{WO3}

\ce{WOx} and optical electric field enhancement. The enhancement arise from the structure composed of a conductive layer and an insulating layer that are laminated therein.\footnote{US patent 8601610B2} In \ce{WOx} nanorods, the oxygen deficient planes are conductive, each having atomic thickness and separated by several nm \ce{WO3}. Localized surface plasmons could possibly exist on these conductive planes. Therefore SERS applies and single molecule Raman scattering using a tungsten oxide nanorod has been demonstrated. The \ce{W_n_O{3n-1}} ($n \geq 2$) exhibit $\{ 001 \}$ CS structure. Chemical formulae corresponding to n=2, 3, 4, 5 and 6 are \ce{W2O5=WO_{2.5}}, \ce{W3O8=W_{2.67}}, \ce{W4O_{11}=WO_{2.75}}, \ce{W5O_{14}=WO_{2.8}}, and \ce{W6O_{17}=WO_{2.83}}, which indicates the existence of a oxygen deficient plane at every n row. Actually the value x in \ce{WOx} could almost continuously vary within a range of 2.5 to 3. \ce{W_{18}O_{49}=\ce{WO_{2.72}}} is an exception without $\{ 001 \}$ CS structure. Moreover, the oxygen deficient planes could extend along directions other than $\{ 001 \}$. For instance, the $\{ 102 \}$ CS planes appears in \ce{WOx} where x is within 2.93 to 2.98, and  the $\{ 103 \}$ CS planes for x within 2.87 to 2.93. \citeauthor{Shingaya2013} also synthesized \ce{WS2}-\ce{WO_x} structures and found similar Raman scattering enhancement. The x value is estimated by the Raman spectra peaks.\cite{Shingaya2013}(Data not shown in patent)

The Raman spectra of \ce{WO_x} is rare because of the difficulty of preparing pure suboxides phase and the strong shielding of \ce{WS2}. Yet it does exhibit distinct Raman spectra. \cite{Tenne2005} The 870 line is attributed to \ce{W3O8}.\cite{Hardcastle1995}

unzip nanotube. passivate BN ribbons with O and S; another player terrones psu.

\section{MoO3}

\section{TMS}

### 2014-02-07 ch-tms/tms.tex
further contents on ws2

@@
 
-Shortly after the the discovery of carbon nanotube (CNT) in 1991, its transition metal dichalcogenides (TMDC) counterparts (\ce{WS2}) was synthesized in 1992.
-In the following decade, other TMDC and several metal oxides nanotubes were demonstrated as well.
+Shortly after the the discovery of carbon nanotube (CNT) in 1991,\cite{Iijima1991} its transition metal dichalcogenides (TMDC) counterparts (\ce{WS2}) was synthesized in 1992.\cite{Tenne1992} In the following decade, other TMDC and several metal oxides nanotubes were demonstrated as well.
 \citeauthor{Rao2003} did an excellent job to review these inorganic nanotubes.\cite{Rao2003} Here we just recapitulate the main categories of synthesis methods.
@@
 \item Decomposition of the ammonium salt \ce{(NH4)2MS4}
-\item Using CNT as templates, or arc, laser ablation
+\item Using CNT as templates, arc discharge, or laser ablation
 \end{enumerate}
@@
 All these methods can be applied to the growth of TMDC few layer structures, either directly or with some modification or combination, as we shall discuss later.
-Among all the members of TMDC nanotubes, \ce{WS2} NT is probably the one most well investigated.\cite{Tenne1998,Frey1998,Frey1999,Rothschild2000,Zak2000} The reaction mechanism of \ce{WO3} with \ce{H2}/\ce{H2S} has been thoroughly studied \cite{Feldman1998} and high yield synthesis approach has been established.\cite{Margolin2004}
+Among all the members of TMDC nanotubes, \ce{WS2} and \ce{MoS2} NTs are probably the most well investigated.\cite{Homyonfer1997,Tenne1998,Frey1998,Frey1999,Rothschild2000,Zak2000} The reaction mechanism of \ce{WO3} with \ce{H2}/\ce{H2S} has been thoroughly studied \cite{Feldman1998} and high yield synthesis approach has been established.\cite{Margolin2004} For precursor of \ce{WO3} NPs, it was found that the simultaneous reduction and sulfurization is essential for encapsulation of fullerene like \ce{WS2} structures from the oxide nanoparticles.
+During the surfurization process, remaining oxide core is gradually reduced and transformed into an ordered superlattice of $\{ 001 \}$ CS planes.
 It is worth noting that \ce{MS2} can be prepared by direct sulfurization from its oxides phase, but reaction \cee{MO3 + Se \rightarrow MSe2} will not proceed unless introducing other reducing agents, such as \ce{H2}.\cite{Tsirlina1998} This fact highlights that sulfur is rather a radical element under elevated temperature.
 
-Parallel with the scenario of graphene and CNT, TMDC few layer structures attracts intensive research efforts recently.
-The unfolded TMDC nanotubes exhibit many appealing features, i.e., indirect-to-direct band gap transition,\cite{Splendiani2010} valley electronics, and become a promising candidate in energy harvesting, optoelectronics.
+Parallel with the scenario of CNT and graphene, TMDC few layer structures attracts intensive research efforts recently.
+These unfolded TMDC nanotubes exhibit many appealing features, i.e., indirect-to-direct band gap transition,\cite{Splendiani2010} valley electronics, and become a promising candidate in energy harvesting, optoelectronics.
 
@@
 
-\ce{WS2} NT chirality by TEM SEAD.\cite{Zhu2000}
+\citeauthor{Zhu2000} performed a detailed morphological and structural analysis on \ce{WS2} NT synthesized using \ce{WO_{3-x}} NWs and \ce{H2S}.
+\cite{Zhu2000} Sulfur vacancy was found on the outer wall of NT.
+The tips exhibits various structures.
+Open-ended can be observed, more frequently than that in CNT, which is often sealed.
+\citeauthor{Zhu2000} suggested this open-ended tubes resulted from continuous growth on other nanotubes.
+And the closure configuration is rather complicated.
+Flat caps often dominates.
+\citeauthor{Feldman1996} proposed that TMDC nanotubes growth began with the reduced \ce{WO3} phases, in particular \ce{W_{18}O_{49}}.\cite{Feldman1996} \citeauthor{Zhu2000} maintained that this oxide-to-sulfides mechanism might apply to closed caps only, not to those open ended tubes.\cite{Zhu2000} TEM diffraction analysis could distinguish the chirality of NTs, as demonstrated by CNT \cite{Zhang1993} and \ce{MoS2}\cite{MARGULIS1996}.
+\ce{WS2} NT chirality revealed by TEM SEAD show armchair NTs dominates.
+
+\citeauthor{Sloan1999} investigated tungsten oxides structures incorporated in \ce{WS2}.\cite{Sloan1999} The encapsulated \ce{WO_x} cores often exhibit \ce{W3O8} and \ce{W5O14} phases, both of which belong to the \ce{W_nO_{3n-1}} homogenous series, arising as a result of crystallographic shearing (CS) planes.\cite{Miyano} Some \ce{WO_x} cores show oxygen vacancy instead of CS planes, leading to prominent streaking in SEAD patterns.
+and the relations between their microstructures and the growth mechanism of encapsulating shell.
+
+\citeauthor{Rafailov2005} estimated the orientation dependence of resonant raman on one MWNT \ce{WS2} attached to the cantilever tip of AFM.\cite{Rafailov2005} Antenna effect lead to optical transition occurring only for polarization parallel to nanotube axis.
+And therefore resonance Raman intensity of SWNT varies as nanotube orientation.
+This dependence may provide a routine to distinguish different chiral NTs.
+632nm excitation is used.
+Polarized Raman spectra is obtained, showing A1g and E2g sharing the sample polarization behavior.
 
@@
 Raman substrate dependence \cite{Buscema2013}
+
+effect of substrate on WS2 growth\cite{Genut1992}
+
+WO3-x NPs \cite{Frey2001}
+
+stability of TMS NTs \cite{Seifert2002}
+
+growth mechanism \cite{ZAK2009}
 

### 2014-02-07 foo.tex
further contents on ws2

@@
 
+\section{lynda git}
+
+\begin{lstlisting}
+git config --global % to each user level
+git config  % to each project
+
+git config --global core.editor ""
+git config --list % view current config
+ls -la % list hidden files
+git log --since=
+git log --until=
+git log --grep="tms"
+
+three tress: repository, staging, working
+change set into checksum
+
+git diff %
+git diff --staged %
+git diff --color-words filexxx
+
+git mv file1 renamedfile2 % rename a file
+
+git commit -am 'commit comments' % add and commit
+
+git checkout -- filexxx% stay on current branch and restore previous versions from repository
+git reset HEAD filexxx % unstage
+
+git commit --amend -m "" % undo commit
+
+git checkout SHA -- filexxx % checkout previous version
+
+git revert SHA %
+
+\end{lstlisting}
+
 \end{document}

### 2014-02-09 BackMatter/paper.tex
paper reading

@@
 
+\citeauthor{Huang2006} studied the \ce{W3On} cluster with n from 7 to 10.\cite{Huang2006} It was found \ce{W3O9} clusters possess a HOMO-LUMO gap about 3.4eV.
+This closeness to bulk value suggests \ce{W3O9} could be viewed as the smallest molecular unit for bulk \ce{WO3}.
+
+\ce{WO3} indirect gap 2.6eV, direct gap 3.4eV. \cite{Koffyberg1979}
+
+Fingerprint of m-\ce{WO3}, h-\ce{WO3} and \ce{WO3,nH2O} were summarized in ref\cite{Daniel1987}.
+
+ \ce{WO3} on FTO by flame synthesis.\cite{Rao2014} \cite{Xu2006}
+
+ Seeded \ce{W_{18}O_{49}} NWs growth on W foil.\cite{Hong2006a}
+
+ \ce{Na2W4O_{13}} growth and optical properties. \cite{Oishi2001} \cite{Itoh2001}
+
+ For photochemical water reduction to occur, the flat-band potential of the semiconductor (for highly doped semiconductors, this equals the bottom of the conductance band) must exceed the proton reduction potential of 0.0 V vs NHE at pH =0.
+\cite{Osterloh2008} flat-band potentials strongly depend on ion absorption (protonation of surface hydroxyl groups), crystallographic orientation of the exposed surface, surface defects, and surface oxidation processes.
+
+\citeauthor{Salje1984} studied the transport in \ce{WO_{3-x}} ($0\leq x \leq 0.28$).\cite{Salje1984} It was found \ce{WO_{3-x}} show metallic conductivity when $x > 0.1$.
+
+ \ce{WO3} high temperature phase. \cite{Vogt1999}
+
+ tungsten bronzes \cite{Wiseman1976}
+
+ Ge NW growth using Ga as catalyst. \cite{Chandrasekaran2006}
+
+ Phase transformation of \ce{Na2MoO4} and \ce{Na2WO4} by Raman scattering. \cite{Lima2011}
+
+ \ce{WO2} NWs synthesis and raman \cite{Ma2005}.
+
+ \ce{WO_{3-x}} CS planes and conductivity.\cite{Sahle1983}
+
 \section{MoO3}
 
+\citeauthor{Hardcastle1990} summarized an empirical formula to relate the Raman peaks and \ce{Mo-O} bonding lengths.\cite{Hardcastle1990} This correlation assumes general form as
+\begin{equation}\label{eq:mobond}
+\nu = A \exp{B\cdot R},
+\end{equation}
+where $A=32895$ and $B=-2.073$ are fitting parameters, R is bond distance in unit of \AA.
+Given a stretching frequency, the resolution for calculated bond distance is $\pm0.016$\AA.
+The counterpart for \ce{W-O} bond \cite{Hardcastle1995} is
+\begin{equation}\label{eq:wobond}
+\nu = 25823 \exp{-1.902\cdot R},
+\end{equation}
+with standard deviation of estimating \ce{W-O} bond distance from Raman stretching wavenumber is $\pm0.034$\AA.
+Another empirical expression connect the bond valence $s$ and bond distance R: $s(M-O) \approx (R/X)^{-6} $, where X=1.882 when M is Mo, and 1.904 when M is W.
+The valence sum rule could be then used to check the state of Mo cation.
+It should be noticed that not all observed Raman lines could be correlated to a \ce{Mo-O} bond distance by extrapolation of Eq.~\ref{eq:mobond}.
+It is then regarded as a symmetry related vibrational mode, i.e.
+$820 cm^{-1}$ in \ce{MoO3}.
+From the correlation of various Mo compounds, a general conclusion is the lower the stretching frequency for the shortest metal-oxygen bond, the more regular is the structure.
+
+The observed raman lines of \ce{Na5W_{14}O_{44}} phase lies at 965, 943, 913, 808, 786, 778, 765, 695 and 107 cm.
+The calculated \ce{W-O} bond distance using Eq.~\ref{eq:wobond} fit very well with the crystallographic value of \ce{Na5W_{14}O_{44}}.
+\cite{Triantafyllou1999a} The 107 peak probably arise from \ce{Na-O} bond.
+
+The molecular unit in crystal exhibits different vibrational frequencies from that in solution or gas phases.
+
+\ce{Na2Mo4O_{13}} phases monoclinic at RT, solid solubility of \ce{Na2MoO4} in solid \ce{MoO3} is high. vapor pressure of \ce{Na2Mo4O_{13}} over \ce{MoO3}.
+
+melting point of \ce{Na2Mo4O_{13}}
+Mp: \ce{Na2Mo2O7} 960K
+
+\ce{MoO3} vapor pressure:
+
+The real phase diagram is the one between \ce{Na2Mo4O_{13}} and \ce{MoO3}.
+
+the growth temperature could be much lower than the eutectic point.
+
+KI MP:  681 
+NaI MP: 661
+
+NaOH Raman peaks lie at 3633 cm. \cite{walrafen2006} Raman scattering of \ce{Na2SiO3} exhibit major peak at 966 and 589 cm.\cite{Richet1996}
+
 \section{TMS}
+
+multipeak Lorentzian fitting. 270 to 410 cm
+
+In 2H type TMDC, the $A_{1g}$ mode is sensitive to electrostatic doping, while $E_{2g}^1$ mode is sensitive to strain, in which the FWHM of the peaks are indicator of external force quantity.
+
+Raman technique could provide valuable insight into the structures of CNT, i.e., tube diameter by assigning the RBMs ( radial breathing modes) and G peaks position.\cite{Bonaccorso2013}
+
+\citeauthor{Virsek2007} investigated the Raman scattering ($\lambda=632nm$) of \ce{WS2} NTs.\cite{Virsek2007} The silicon peak at 520 cm is used for calibration.
+Up-shift of A1g and E2g modes were observed, attributing to the strain in 3R stacking layers.
+
+\citeauthor{Dobardzic2005} calculated \ce{MoS2} SWNT phonon dispersion.
+The dependence of wavenumbers and their displacement on chirality and diameter were discussed.
+The calculation method enable studying lattice dynamics with NT diameter up to 50nm.
+The chiral vector $(n_1, n_2)$ is defined within the Moly plane.
+Symmetry assignment is zigzag when $(n,0)$, armchair when $(n,n)$ and chiral when $(n_1, n_2), n_1>n_2$.
+
+\begin{enumerate}
+\item WS2 NT phase, 2H or 3R or 1T;
+
+\end{enumerate}
+
+\section{misc}
+
+SOI:
+
+VSS, growth kinetics,

### 2014-02-09 ch-moox/moox.tex
paper reading

@@
 \caption{Crystal structures of alkali metal molybdates and tungstates}\label{tab:naxmow}
-\begin{tabular}{lcr}
+\begin{tabular}{l1r}
 \toprule
@@
 \midrule
-\ce{A2O:MO3}\textsuperscript{\emph{a}} & isolated tetrahedral \ce{MO4} anions& \\
-\ce{A2O:2MO3} & chain-type anions of \ce{MO4} and \ce{MO6} & \\
-\ce{A2O:3MO3} & chain-type anions of \ce{MO5} and \ce{MO6} & \\
-\ce{A2O:4MO3} & chain-type anions of \ce{MO6} & \\
+\ce{A2O}:\ce{MO3}\textsuperscript{\emph{a}} & isolated tetrahedral \ce{MO4} anions& \\
+\ce{A2O}:\ce{2MO3} & chain-type anions of \ce{MO4} and \ce{MO6} & \\
+\ce{A2O}:\ce{3MO3} & chain-type anions of \ce{MO5} and \ce{MO6} & \\
+\ce{A2O}:\ce{4MO3} & chain-type anions of \ce{MO6} & \\
 \bottomrule
@@
 \item catalyst composition variation during growth
+\item \ce{Na2Mo4O_{13}} phases, solid solubility of \ce{Na2MoO4} in solid \ce{MoO3} is high. 
+\item vapor pressure of \ce{Na2Mo4O_{13}} and \ce{MoO3}.
 \end{itemize}

### 2014-02-09 ch-tms/tms.tex
paper reading

@@
 During the surfurization process, remaining oxide core is gradually reduced and transformed into an ordered superlattice of $\{ 001 \}$ CS planes.
-It is worth noting that \ce{MS2} can be prepared by direct sulfurization from its oxides phase, but reaction \cee{MO3 + Se \rightarrow MSe2} will not proceed unless introducing other reducing agents, such as \ce{H2}.\cite{Tsirlina1998} This fact highlights that sulfur is rather a radical element under elevated temperature.
+It is worth noting that \ce{MS2} can be prepared by direct sulfurization from its oxides phase, but reaction \cee{MO3 + Se \rightarrow MSe2} will not proceed unless introducing other reducing agents, such as \ce{H2}.\cite{Tsirlina1998} This fact highlights that sulfur is rather radical at elevated temperature.
 
@@
 Other chalcogenide has also been synthesized using this one-end sealed layout.\cite{Mukherjee2013}
+
+\citeauthor{Zhang2013h} synthesized \ce{WS2} on sapphire using \ce{WO3} powder and sulfur as precursor under 900 C.
+\cite{Zhang2013h} Ar slightly mixed with \ce{H2} is used to tailor the shape of \ce{WS2} flakes.
+\citeauthor{Peimyoo2013} prepared \ce{WS2} on \ce{SiO2}/Si using \ce{WO3} powder and sulfur at 800 C, aiming at the light emission studies to clarify several contradictory reports.\cite{Peimyoo2013} Uniform PL intensity was found on the triangular \ce{WS2} flakes, in contrast to previous edge enhanced PL.\cite{Berkdemir2013} Raman excitation ($\lambda=532nm$)
+It is worth noting that the growth conditions in Ref \cite{Peimyoo2013} and \cite{Zhang2013h} are basically identical except the usage of substrate.
+The flake size on sapphire seem larger than that on \ce{SiO2}/Si, either due to the nucleation barrier difference or the amount of growth vapor and growth time.
+
+\cite{Song2013} ALD \ce{WS2}
 
@@
 \ce{WS2} ML \cite{Cong2013} & \ce{WO3} powder on sub1 covered by sub2, sulfur & 750 \si{\degreeCelsius} hold for 5mins, one-end sealed inner tube, 100 sccm Ar\\
-
+\addlinespace[0.5em]
+\ce{WS2} ML \cite{Zhang2013h} & \ce{WO3} powders, sulfur (separate heating) & 900 \si{\degreeCelsius}, sapphire subs, 225mTorr, Ar 80 sccm and \ce{H2} 10 sccm, growth time 60mins, adjusting precursor and sapphire distance changing the coverage of \ce{WS2} \\
+\addlinespace[0.5em]
+\ce{WS2} ML \cite{Peimyoo2013} & 1mg \ce{WO3} powders, sulfur,  & \ce{SiO2}/Si subs.
+Recipe A: 200mg S,RT-550, Sulfur begin to melt, 550-800, 5K/min, hold 10mins, 200 sccm Ar.
+Recipe B: sulfur separated heated at 250C\\
+  & & \\
 \bottomrule

### 2014-02-10 BackMatter/paper.tex
tms raman part in process

@@
 
+ \ce{Na2W4O_{13}} crystal phase \cite{Viswanathan1974}
+
  For photochemical water reduction to occur, the flat-band potential of the semiconductor (for highly doped semiconductors, this equals the bottom of the conductance band) must exceed the proton reduction potential of 0.0 V vs NHE at pH =0.
@@
 \citeauthor{Salje1984} studied the transport in \ce{WO_{3-x}} ($0\leq x \leq 0.28$).\cite{Salje1984} It was found \ce{WO_{3-x}} show metallic conductivity when $x > 0.1$.
+
+ \ce{WO_{3-x}} \cite{Migas2010}
 
@@
  \ce{WO_{3-x}} CS planes and conductivity.\cite{Sahle1983}
+
+ \ce{W-O} equilibrium diagram \cite{Wriedt1989}
+
+ \ce{W_{18}O_{49}} electrochromic devices.\cite{Liu2013d} should compare with this one \cite{Wang2008}
+
+  nucleation catalysis \cite{Turnbull1952}
+
+  \ce{WO3} NWs aggregates. \cite{Kozan2008a}
+
+  electrochromic films. \cite{Yoshimura1985}
+
+  optical properties of \ce{WO3} gaps\cite{Saygin-Hinczewski2008}
+
+  \ce{WO3} atomic layer by exfoliation and annealing \ce{WO3.H2O}. \cite{Kalantar-zadeh2010a}
+
+  sodium tungstates raman \cite{Redkin2010}
+
+  charge density wave in K-doped \ce{WO3} \cite{Raj2008}
+
+  \ce{W_{18}O_{49}} Raman \cite{Guo2012} \cite{Guo2011}
+
+  ECD \cite{Jiao2012} recent review \cite{Mortimer2011}
+
+  \ce{WnO_{3n-1}} NPs. \cite{Frey2001}
+
+  \ce{WO3} growth hydrothermal.\cite{Moshofsky2012}
+
+  \ce{W_{18}O_{49}} on tungsten foil by thermal growth\cite{VanHieu2012}
+
+  \ce{WO_{3-x}} Raman peak at 778. \cite{Deb2007}
+
+  Cathodoluminescence \cite{Parish2007}
+
+  optical characterization of WOx film.\cite{Valyukh2010a}
+
+  E-beam penetration \cite{Kanaya2002}
+
+  PEC, photoelectrode, WO3 and Si tandem structures.\cite{Coridan2013}
+
+  WO3 photoactivity MB. \cite{Watcharenwong2008}
+
+  optics in electron microscopy. \cite{GarciadeAbajo2010a}
+
+  A low recombination rate is preferred for high photocatalytic efficiency. The simultaneous migration of electrons and holes.
+\textbf{\ce{WS2}-\ce{WO3}}: 1 kW light source(Hg, or Xe lamp), photon flux, phenol (\ce{C6H5OH}, 94.1g/mol, MP 40C)concentration is 20 mg/L, hydroxyl group.
+The quantitative analysis of phenol was performed via a standard colorimetric method.\footnote{\url{http://omlc.ogi.edu/spectra/PhotochemCAD/html/072.html}}
+\citeauthor{DiPaola1999} prepared \ce{WS2}-\ce{WO3} mixture in two methods, sulfurization of \ce{WO3} and oxidation of \ce{WS2},with the latter are more active.
+\citeauthor{DiPaola1999} also concluded that the actual efficiency of mixed \ce{WS2}-\ce{WO3} catalysts depends on the ratio of each composition present of the surface of the particles, and the maximum of photoactivity is obtained with 40-50\% surface molar ratio of \ce{WS2}.
+
+ref 25, 28 and 41.
+
+\textbf{\ce{MoO3}}:
+
+\citeauthor{Sreedhara2013} studied the kinetics of photodegradation of methylene blue\footnote{\ce{C16H18N3SCl},319.8 g/mol, MP: 100C accompanied with decomposition \url{http://en.wikipedia.org/wiki/Methylene_blue}} dye by few layer \ce{MoO3}.
+For the photodegradation method, it was stated that `` the samples were collected after the photoreaction had been centrifuged for 5 min to remove the photocatalyst before UV-Vis measurement.''
 
@@
 
-Raman technique could provide valuable insight into the structures of CNT, i.e., tube diameter by assigning the RBMs ( radial breathing modes) and G peaks position.\cite{Bonaccorso2013}
-
-\citeauthor{Virsek2007} investigated the Raman scattering ($\lambda=632nm$) of \ce{WS2} NTs.\cite{Virsek2007} The silicon peak at 520 cm is used for calibration.
-Up-shift of A1g and E2g modes were observed, attributing to the strain in 3R stacking layers.
-
-\citeauthor{Dobardzic2005} calculated \ce{MoS2} SWNT phonon dispersion.
-The dependence of wavenumbers and their displacement on chirality and diameter were discussed.
-The calculation method enable studying lattice dynamics with NT diameter up to 50nm.
-The chiral vector $(n_1, n_2)$ is defined within the Moly plane.
-Symmetry assignment is zigzag when $(n,0)$, armchair when $(n,n)$ and chiral when $(n_1, n_2), n_1>n_2$.
+Raman technique could provide valuable insight into the structures of CNT, i.e., tube diameter by assigning the RBMs (radial breathing modes) and G peaks position.\cite{Bonaccorso2013}
 
@@
 
+(Ramasubramaniam, Naveh, \& Towe, 2011) investigate the band gap tuning in bilayer TMD materials by applying external E field.
+Similar research has been done for graphene and bilayer boron nitride.
+Semiconductor-metal transition was suggested for \ce{MoS2} and WS2, with difference on the CBM and VBM evolution.
+In \ce{MoS2}, the valence-band-splitting cause the A and B excitons in optical absorption measurement.
+Calculation shows that CB and VB are translated toward the Fermi level with increasing E field.
+The external field localized charge along C axis, but delocalized that within the plane normal towards C, thereby driving the semi-metal transition.
+It was mentioned that this transition is not anticipated in monolayer \ce{MoS2}.
+It was emphasized that precise band gaps might be different from the author’s results, yet the gap-tuning should be universal.
+
+(Shi, Pan, Zhang, \& Yakobson, 2013) studied the strained monolayer \ce{MoS2} and WS2.
+The results show that exciton binding energy is insensitive to the strain, while optical band gap becomes smaller as strain increases.
+Monolayer WS2 PL maximum located at about 1.95eV.
+Calculation shows the electron effective mass of WS2 is the smallest, rendering higher mobility in device.
+
+(Kośmider \& Fernández-Rossier, 2013) studied the heterojunction between two monolayers of \ce{MoS2} and WS2.
+Top of VB in W layer and bottom of CB in Mo layer, forming type II structure.
+bilayer gap 1.2 eV.
+
+Band structure  of \ce{MoS2} in bulk form was calculated by (Mattheiss, 1973).
+There is some controversy about the exact value of bandgap.
+The calculation result is 1.2eV ( indirect gap).\cite{Mattheiss1973}
+
+Alkali metal intercalated \ce{WS2} film was prepared.(Homyonfer et al., 1997) Stage 6 superlattice formation was suggested according to X-ray diffraction, and photoresponse spectra and electron tunneling measurement were done.
+
+Sulfurizaiton of W film, (Jäger-Waldau, Lux-Steiner, Jäger-Waldau, & Bucher, 1993)
+
+(Splendiani et al., 2010) reported the PL in monolayer \ce{MoS2}.
+Calculation indicated the indirect gap become larger when thinning, while the previous direct one almost stays as the same, the value is about 1.85eV (direct gap).\cite{Splendiani2010}
+
+(Zhou et al., 2010) heterojunction is employed to transferred photo-generated carriers.
+schottky barrier conduction band electron trapping and consequent longer electron-hole pair lifetimes.
+Numerous studies have suggested that fine particles of transition metals or their oxides, when dispersed on the surface of a photocatalyst matrix, can act as electron traps on n-type semiconductors.
+
+thermal decomposition of (NH4)2MoO2S2 and intermediate product MoOS2 was studied. application: hyfrodesulfurization in refinery (Weber et al. 1996) \cite{Weber1996}
+
+\cee{MoCl5 + 1/4S8 + 5/2H2 \rightarrow MoS2 + 5HCl} (Stoffels et al. 1999)
+
+(M Remskar et al. 1999) WS2 nanotube from WO3-x whisker. heating 840 degree under flow of H2/N2/H2S ,
+
+A detailed study by (Rothschild, Sloan, and Tenne 2000) tungsten filament oxidation by water. then WS2 nanotube from WO3-x whisker. heating 840 degree under flow of H2/N2/H2S ,
+
+IF MoS2 synthesis by MoO3 nanobelt and S.(X. L. Li and Li 2003)
+
+Inorganic core –shell nanotube, WS2@MoS2 core-shell NT.(Kreizman et al. 2010)
+
+vdW Epitaxy of MoS2 on graphene. (Y. Shi et al. 2012)
+
+WS2 monolayer and intense photoluminescent behavior. Sulfurization of WO3 film( 5-20 angstrom). (Gutiérrez et al. 2012)
+
+MoO3 on sapphire reduction in H2 at 500 and sulfurizatin at 1000 degree. (Lin et al. 2012)
+
+quantitative Raman of MoS2 on insulating subs. intensity difference between supported and suspended was highlighted, detailed model in support info.(S.-L. Li et al. 2012)
+
+MoS2 on SiO2/Si sub pretreated with OTAS, PTCDA solution. (Y.-H. Lee et al. 2012)
+
+WO3-x (1nm) on SiO2/Si sulfurization at 750-950 degree, (Elías et al. 2013)\cite{Elias2013}
+
+source MoS2 powder, Ar On sapphire, SiO2/Si, QWP circularly polarized  light (S. Wu et al. 2013)
+
+(Wang et al. 2013)
+MoS2 CVD (tsinghua univ) layer by layer sulfurization of MoO2
+MoO3 powder 25mg and MnO2 powder 25 mg, extra sulfur
+Ar purging  20mins, heating at 650 degree to produce MoO2 flakes
+Further reaction between MoO2 and S was performed at 850-950 degree under Ar flow.
+
+MoS2 on SiO2, sapphire, and graphite by MoCl5 and S. (Yu et al. 2013)
+growth time: 10min at 850 degree, P: 2 Torr.
+
+review of inorganic 2D materials, (Chhowalla et al., 2013)
+
+(Ramasubramaniam, 2012) decrease in dielectric screening and thereby enhanced excitonic effect.
+DFT is not good at describing photoemission, GW approximation overcome this deficiency but still not enough for photoabsorption process in which ehps are created.
+BSE equation is used to compensate this discrepancy,
+WX2 exhibits larger spin-orbit splitting as compared to MX2 family.
+
+reaction mechanism of \ce{MoO3} to \ce{Mo2S}.\cite{Weber1996}
+
+\citeauthor{Ling2014} studied the role of seeding promoters in CVD growth of FL \ce{MoS2}.\cite{Ling2014} PTAS treated substrates provided nucleation site and thus enable uniform deposition of \ce{MS2}.
+This enhancement perhaps arise from the \ce{K+} ions.
+
+CNT chirality by TEM \cite{Zhang1993} TEM chirality of \ce{MoS2} NTs
+
+arise as a result of, dispersal of Na by electron probe.
+
+%%%%%%%%%%%%%%%%%%%%%%
+
 \section{misc}

### 2014-02-10 ch-tms/tms.tex
tms raman part in process

@@
 
-\section{Raman spectra and Layer configuration}
+\section{ and Layer configuration}
 
@@
 
+\section{Raman spectra}
+
+\subsection{TMS NTs}
+\citeauthor{Virsek2007} investigated the Raman scattering ($\lambda=632nm$) of \ce{WS2} NTs.\cite{Virsek2007} The silicon peak at 520 cm is used for calibration.
+Up-shift of A1g and E2g modes were observed, attributing to the strain in 3R stacking layers.
+
+\citeauthor{Dobardzic2005} calculated \ce{MoS2} SWNT phonon dispersion.
+The dependence of wavenumbers and their displacement on chirality and diameter were discussed.
+The calculation method enable studying lattice dynamics with NT diameter up to 50nm.
+The chiral vector $(n_1, n_2)$ is defined within the Moly plane.
+Symmetry assignment is zigzag when $(n,0)$, armchair when $(n,n)$ and chiral when $(n_1, n_2), n_1>n_2$.
+
+\citeauthor{Seifert2000} investigated the electronic structures of \ce{WS2} nanotube using DFT calculation.\cite{Seifert2000} It was found zigzag (n,0) NTs exhibts a direct gap at $\Gamma$ point, whose size increase monotonically with tube diameter, while armchair (n,n) NTs, unlike its metallic counterpart of (n,n) CNT, show indirect band gap increasing with tube diameter.
+
+\subsection{TMS bulk and FL}
+
+Lattice vibration of natural \ce{MoS2} crystal was studied by \citeauthor{Wieting1971} using infrared and Raman spectroscopy.\cite{Wieting1971} Hexagonal \ce{MoS2} belongs to space group $D_{6h}^4$, and the repeat unit in $c$ axis contains two layers, where sulfur atoms in one layer are directly above the molybdenum atoms in adjacent layers, which is often referred as 2H-\ce{MoS2}.
+The lattices dimensions are summarized in Table~\ref{tab:ms2lattice}, and vibration modes in Table~\ref{tab:tmslattice}.
+Group theory predicts two infrared- and four Raman-active modes for 2H-\ce{MoS2}, which are mutually exclusive when the center of inversion is present.
+It was found the $E_{1u}$ IR mode and one $E_{2g}$ Raman mode are nearly degenerate in energy.
+15 optical modes are allowed assuming 6 atoms in primitive cell.
+Refractive indices from reflectivity measurement were n0= 3.9, ne = 2.5.
+
+\citeauthor{Sourisseau1991} investigated the resonant Raman profiles in 2H-\ce{WS2} using ten different excitation wavelengths.\cite{Sourisseau1991} Dramatic intensity variation at 352 cm was observed, which is of two-phonon signal nature, and corresponds to an overtone or combination band of phonons with non-zero momenta contributing to indirect gap absorption edge.
+The authors assigned this phonon with non-zero momenta as $LA(K_5)$ type.
+
+The symmetry is reduced from $D_{6h}$ to $D_{3h}$ when thinning to monolayer, with the absence of inversion center.
+
+Raman signatures of \ce{WS2} nanotubes show distinct features to the spectra of their bulk counterpart.
+\citeauthor{JMR7990865} observed a new line at 152 cm in \ce{WS2} NT, which is absent in 2H-\ce{WS2}.\cite{JMR7990865} Another feature is a emerging shoulder on the low energy side of $A_{1g}$ mode at about 416 $cm^{-1}$.
+This has been attributed to a combination mode of LA + TA phonons from the $K$ point of Brillouin zone.\cite{Sourisseau1991} A more prominent feature is the resonance profile broadening the shape of $E_{2g}^1$ mode, which is often assigned to 2LA mode.
+Yet there is some different opinion on these assignments.
+\citeauthor{Molina-Sanchez2011} label the 350 $cm^{-1}$ band as \ce{E_{1u}} instead of 2LA, and the 416 $cm^{-1}$ band as inactive $B_{1u}$ mode.\cite{Molina-Sanchez2011} \citeauthor{Staiger2012} adopted these assignments in studying the resonance Raman profile of \ce{WS2} NTs.\cite{Staiger2012} It was found that
+\begin{enumerate}
+\item $B_{1u}$ mode arise from curvature and structural disorder
+\item $B_{1u}/A_{1g}$ intensity ratio strongly depends on excitation, and exceeds unity when excitation energy less than 1.9eV.
+\item  An excitonic transition energy of NT is found have a local minimum at about 50nm, (layer number probably \textgreater 10), and increase either way. Yet all below the bulk value.
+\end{enumerate}
+
+% irreducible representation
+\begin{table}[htb]
+\centering
+\caption{Lattices vibration of \ce{MS2}, adopted from ref\cite{Molina-Sanchez2011}}\label{tab:tmslattice}
+\begin{tabular}{lcccc}
+\toprule
+ $D_{6h}$   & $D_{3h}$ & Character &  Direction & Atoms  \\
+\midrule
+$A_{1g}$    &  $A_1$   & Raman     & (out of plane)  & S  \\
+$E_{2g}^2$  &          &           & (in plane)      & M + S  \\
+$E_{2g}^1$  &  $E'$    &           & (in plane)      & M + S  \\
+$E_{1g}$    &  $E''$    &           & (in plane)      & S  \\
+\midrule
+$A_{2u}$    &  $A_2''$  & Infrared  & (out of plane)  & M + S  \\
+$E_{1u}$    &          &           & (in plane)      & M + S  \\
+\midrule
+$A_{2u}$    &  $A_2$   & Acoustic  & (out of plane)  & M + S  \\
+$E_{1u}$    &          &           &       &    \\
+\midrule
+$B_{2g}^2$  &          & Inactive  & (out of plane)  & M + S  \\
+$B_{2g}^1$  &          &           & (out of plane)  & M + S  \\
+$B_{1u}$    &          &           & (out of plane)  & S  \\
+$E_{2u}$    &          &           & (in plane)      & S  \\
+\bottomrule
+\end{tabular}
+\end{table}
+
+\begin{table}[htb]
+\centering
+\caption{Lattices dimension of \ce{MS2}}\label{tab:ms2lattice}
+\begin{tabular}{lcccr}
+\toprule
+\multicolumn{2}{c}{Flow} \\
+\cmidrule(l){4-5}
+         & Temperature & Pressure & Ar & \ce{O2}  \\
+\midrule
+Range      & RT-1100    & 10mTorr-1atm & 0 - 100 & 0-30  \\
+Resolution & $\pm1$  & correlated to flow & 1   & 0.1  \\
+\bottomrule
+\end{tabular}
+\end{table}
+
+% WS2 Raman assignments
+\begin{table}
+  \centering
+  \caption{\ce{WS2} Raman assignment}  \label{tbl:ws2raman}
+  \begin{tabular}{ccccc}
+    \toprule
+    &&\multicolumn{3}{c}{Wavenumber shift ($cm^{-1}$})\\
+    \cmidrule(l){3-5}
+    Symmetry                & Atoms & \ce{WS2} ML\cite{Cong2013}  & \ce{WS2} NT \cite{JMR7990865}  & \ce{WS2} bulk \cite{Sourisseau1991} \\
+    \midrule
+          $E_{2g}^2(\Gamma)$ &      & 27.5\textsuperscript{\emph{a}}&             &  27.4    \\
+    $LA(M)-E_{2g}^2(\Gamma)$ &      & 148.3                        &              &    \\
+       TBD                   &      &                              & 153          &      \\
+         $E_{2g}^1(M)-LA(M)$ &      &                              & 172          & 173  \\
+    LA(M)                    &      & 174.8                        & 172          &       \\
+    LA(K)                    &      & 192.4                        &              &  193 \\
+    $LA(M)+E_{2g}^2(\Gamma)$ &      & 203                          &              &     \\
+    $LA(K)+E_{2g}^2(\Gamma)$ &      & 213.9                        &              &  212  \\
+    $A_{1g}(M)-LA(M)$        &      & 230.9                        & 230          &  233  \\
+    $2LA(M)-3E_{2g}^2(\Gamma)$ &    & 264.2                        & 262          &  267  \\
+    $2LA(M)-2E_{2g}^2(\Gamma)$ &    & 295.4                        & 294          &  297   \\
+    $2LA(M)-E_{2g}^2(\Gamma)$ &     & 322.9                        &              &  325   \\
+               $E_{2g}^1(M)$ &      & 343.1                        &              &      \\
+    2LA(M)                   &      & 350.8                        & 350          &  352\\
+          $E_{2g}^1(\Gamma)$ &      & 355.4                        & 350          &  356 \\
+    $2LA(M)+2E_{2g}^2(M)$    &      &                              & 381          &  381   \\
+     LA + TA or $B_{1u}$     &      &                              &              &  416 \\
+          $A_{1g}(\Gamma)$   &      & 417.9                        & 416\textsuperscript{\emph{b}} &  421\\
+               3LA(K)        &      & 577                          &              &      \\
+       $ LA(M)+ A_{1g}(M)$   &      & 584                          & 581          &  585 \\
+    4LA(M)                   &      & 704                          &              &  703\\
+    \bottomrule
+  \end{tabular}
+
+  \textsuperscript{\emph{a}} Calculated from column values;
+  \textsuperscript{\emph{b}} \citeauthor{JMR7990865} probably made incorrect assignment of 416 peak.\cite{JMR7990865}
+\end{table}
+
 \section{paragraph from word files}

### 2014-02-10 figure_table.tex
further contents on ws2
tms raman part in process

--- 2014-02-02 figure_table.tex
@@
 
-A low recombination rate is preferred for high photocatalytic efficiency. The simultaneous migration of electrons and holes.
-\textbf{\ce{WS2}-\ce{WO3}}: 1 kW light source(Hg, or Xe lamp), photon flux, phenol (\ce{C6H5OH}, 94.1g/mol, MP 40C)concentration is 20 mg/L, hydroxyl group.
-The quantitative analysis of phenol was performed via a standard colorimetric method.\footnote{\url{http://omlc.ogi.edu/spectra/PhotochemCAD/html/072.html}}
-\citeauthor{DiPaola1999} prepared \ce{WS2}-\ce{WO3} mixture in two methods, sulfurization of \ce{WO3} and oxidation of \ce{WS2},with the latter are more active.
-\citeauthor{DiPaola1999} also concluded that the actual efficiency of mixed \ce{WS2}-\ce{WO3} catalysts depends on the ratio of each composition present of the surface of the particles, and the maximum of photoactivity is obtained with 40-50\% surface molar ratio of \ce{WS2}.
-
-ref 25, 28 and 41.
-
-\textbf{\ce{MoO3}}:
-
-\citeauthor{Sreedhara2013} studied the kinetics of photodegradation of methylene blue\footnote{\ce{C16H18N3SCl},319.8 g/mol, MP: 100C accompanied with decomposition \url{http://en.wikipedia.org/wiki/Methylene_blue}} dye by few layer \ce{MoO3}.
-For the photodegradation method, it was stated that `` the samples were collected after the photoreaction had been centrifuged for 5 min to remove the photocatalyst before UV-Vis measurement.''
-
+\subsection{figure table units}
 \si{W/in^2}

### 2014-02-11 BackMatter/paper.tex
tms continue

@@
 
-(Ramasubramaniam, Naveh, \& Towe, 2011) investigate the band gap tuning in bilayer TMD materials by applying external E field.
-Similar research has been done for graphene and bilayer boron nitride.
-Semiconductor-metal transition was suggested for \ce{MoS2} and WS2, with difference on the CBM and VBM evolution.
-In \ce{MoS2}, the valence-band-splitting cause the A and B excitons in optical absorption measurement.
-Calculation shows that CB and VB are translated toward the Fermi level with increasing E field.
-The external field localized charge along C axis, but delocalized that within the plane normal towards C, thereby driving the semi-metal transition.
-It was mentioned that this transition is not anticipated in monolayer \ce{MoS2}.
-It was emphasized that precise band gaps might be different from the author’s results, yet the gap-tuning should be universal.
-
 (Shi, Pan, Zhang, \& Yakobson, 2013) studied the strained monolayer \ce{MoS2} and WS2.

### 2014-02-11 ch-tms/tms.tex
tms continue

@@
 
-\citeauthor{Zhang2013h} synthesized \ce{WS2} on sapphire using \ce{WO3} powder and sulfur as precursor under 900 C.
+\citeauthor{Zhang2013h} synthesized \ce{WS2} on sapphire using \ce{WO3} powder and sulfur as precursor under 900 \si{\degreeCelsius}.
 \cite{Zhang2013h} Ar slightly mixed with \ce{H2} is used to tailor the shape of \ce{WS2} flakes.
-\citeauthor{Peimyoo2013} prepared \ce{WS2} on \ce{SiO2}/Si using \ce{WO3} powder and sulfur at 800 C, aiming at the light emission studies to clarify several contradictory reports.\cite{Peimyoo2013} Uniform PL intensity was found on the triangular \ce{WS2} flakes, in contrast to previous edge enhanced PL.\cite{Berkdemir2013} Raman excitation ($\lambda=532nm$)
-It is worth noting that the growth conditions in Ref \cite{Peimyoo2013} and \cite{Zhang2013h} are basically identical except the usage of substrate.
+It was found the source substrate distance play an important role in determining the morphology of as-grown flakes.
+\citeauthor{Peimyoo2013} prepared \ce{WS2} on \ce{SiO2}/Si using \ce{WO3} powder and sulfur at 800 \si{\degreeCelsius}, aiming at the light emission studies to clarify several contradictory reports.\cite{Peimyoo2013} Uniform PL intensity was found on the triangular \ce{WS2} flakes, in contrast to previous edge enhanced PL.\cite{Berkdemir2013} It is worth noting that the growth conditions in Ref \cite{Peimyoo2013} and \cite{Zhang2013h} are basically identical except the usage of substrate.
 The flake size on sapphire seem larger than that on \ce{SiO2}/Si, either due to the nucleation barrier difference or the amount of growth vapor and growth time.
@@
 \cite{Lin2012,Lee2012b,Liu2012a}
-
-\begin{table}
-  \centering
-  \caption{A table with notes}  \label{tbl:notes}
-  \begin{tabular}{ll}
-    \toprule
-    Header one                            & Header two \\
-    \midrule
-    Entry one\textsuperscript{\emph{a}}   & Entry two  \\
-    Entry three\textsuperscript{\emph{b}} & Entry four \\
-    \bottomrule
-  \end{tabular}
-
-  \textsuperscript{\emph{a}} Some text;
-  \textsuperscript{\emph{b}} Some more text.
-\end{table}
 
@@
 \addlinespace[0.5em]
-\ce{WS2} ML \cite{Zhang2013h} & \ce{WO3} powders, sulfur (separate heating) & 900 \si{\degreeCelsius}, sapphire subs, 225mTorr, Ar 80 sccm and \ce{H2} 10 sccm, growth time 60mins, adjusting precursor and sapphire distance changing the coverage of \ce{WS2} \\
+\ce{WS2} ML \cite{Zhang2013h} & \ce{WO3} powders, sulfur (separate heating) & 900 \si{\degreeCelsius}, sapphire subs, 225mTorr, Ar 80 sccm and \ce{H2} 10 sccm, growth time 60mins, adjusting precursor and sapphire distance changing the coverage of \ce{WS2}, tube diameter: 1 inch\\
 \addlinespace[0.5em]
@@
 Recipe A: 200mg S,RT-550, Sulfur begin to melt, 550-800, 5K/min, hold 10mins, 200 sccm Ar.
-Recipe B: sulfur separated heated at 250C\\
-  & & \\
+Recipe B: sulfur separated heated at 250 \si{\degreeCelsius}.
+Total pressure: maybe atmospheric, tube diameter: 2 inch \\
+\ce{WS2} FL \cite{Lee2013}  & 1g \ce{WO3} powders, sulfur,subs treated with PTAS and gentle gas blow & substrate facing down, APCVD, 900 \si{\degreeCelsius}, 5mins, 5 sccm Ar, fast heating. \\
 \bottomrule
@@
 \citeauthor{Sloan1999} investigated tungsten oxides structures incorporated in \ce{WS2}.\cite{Sloan1999} The encapsulated \ce{WO_x} cores often exhibit \ce{W3O8} and \ce{W5O14} phases, both of which belong to the \ce{W_nO_{3n-1}} homogenous series, arising as a result of crystallographic shearing (CS) planes.\cite{Miyano} Some \ce{WO_x} cores show oxygen vacancy instead of CS planes, leading to prominent streaking in SEAD patterns.
-and the relations between their microstructures and the growth mechanism of encapsulating shell.
-
-\citeauthor{Rafailov2005} estimated the orientation dependence of resonant raman on one MWNT \ce{WS2} attached to the cantilever tip of AFM.\cite{Rafailov2005} Antenna effect lead to optical transition occurring only for polarization parallel to nanotube axis.
-And therefore resonance Raman intensity of SWNT varies as nanotube orientation.
-This dependence may provide a routine to distinguish different chiral NTs.
-632nm excitation is used.
-Polarized Raman spectra is obtained, showing A1g and E2g sharing the sample polarization behavior.
 
@@
 \subsection{TMS NTs}
-\citeauthor{Virsek2007} investigated the Raman scattering ($\lambda=632nm$) of \ce{WS2} NTs.\cite{Virsek2007} The silicon peak at 520 cm is used for calibration.
-Up-shift of A1g and E2g modes were observed, attributing to the strain in 3R stacking layers.
 
@@
 Symmetry assignment is zigzag when $(n,0)$, armchair when $(n,n)$ and chiral when $(n_1, n_2), n_1>n_2$.
+\citeauthor{Dobardzic2006} theoretically presented Raman scattering of any polarization on SWNT of \ce{WS2} and their dependence on diameter (1-20nm) and chiral angle.
+The author assigned 351 $cm^{-1}$ as $E_u$ for \ce{WS2} NT.\cite{Dobardzic2006}
 
 \citeauthor{Seifert2000} investigated the electronic structures of \ce{WS2} nanotube using DFT calculation.\cite{Seifert2000} It was found zigzag (n,0) NTs exhibts a direct gap at $\Gamma$ point, whose size increase monotonically with tube diameter, while armchair (n,n) NTs, unlike its metallic counterpart of (n,n) CNT, show indirect band gap increasing with tube diameter.
+\citeauthor{Zibouche2012} reached the same conclusion on \ce{WS2} SWNT.\cite{Zibouche2012} It was also found band gaps of armchair and zigzag NTs increase with diameter, going from values close to bulk and approaching that of  monolayer, and for a given tube diameter, $E_g$ of zigzag NTs are larger than those of armchair NTs.
+This difference presumably vanishes when the tube diameter exceeds 100 nm.
 
-\subsection{TMS bulk and FL}
-
-Lattice vibration of natural \ce{MoS2} crystal was studied by \citeauthor{Wieting1971} using infrared and Raman spectroscopy.\cite{Wieting1971} Hexagonal \ce{MoS2} belongs to space group $D_{6h}^4$, and the repeat unit in $c$ axis contains two layers, where sulfur atoms in one layer are directly above the molybdenum atoms in adjacent layers, which is often referred as 2H-\ce{MoS2}.
-The lattices dimensions are summarized in Table~\ref{tab:ms2lattice}, and vibration modes in Table~\ref{tab:tmslattice}.
-Group theory predicts two infrared- and four Raman-active modes for 2H-\ce{MoS2}, which are mutually exclusive when the center of inversion is present.
-It was found the $E_{1u}$ IR mode and one $E_{2g}$ Raman mode are nearly degenerate in energy.
-15 optical modes are allowed assuming 6 atoms in primitive cell.
-Refractive indices from reflectivity measurement were n0= 3.9, ne = 2.5.
-
-\citeauthor{Sourisseau1991} investigated the resonant Raman profiles in 2H-\ce{WS2} using ten different excitation wavelengths.\cite{Sourisseau1991} Dramatic intensity variation at 352 cm was observed, which is of two-phonon signal nature, and corresponds to an overtone or combination band of phonons with non-zero momenta contributing to indirect gap absorption edge.
-The authors assigned this phonon with non-zero momenta as $LA(K_5)$ type.
-
-The symmetry is reduced from $D_{6h}$ to $D_{3h}$ when thinning to monolayer, with the absence of inversion center.
+\citeauthor{Rafailov2005} estimated the orientation dependence of resonant raman on one MWNT \ce{WS2} attached to the cantilever tip of AFM.\cite{Rafailov2005} Antenna effect lead to optical transition occurring only for polarization parallel to nanotube axis.
+And therefore resonance Raman intensity of SWNT varies as nanotube orientation.
+This dependence may provide a routine to distinguish different chiral NTs.
+632nm excitation is used.
+Polarized Raman spectra is obtained, showing $A_{1g}$ and $E_{2g}$ sharing the same polarization behavior.
+\citeauthor{Virsek2007} investigated the Raman scattering ($\lambda=632nm$) of \ce{WS2} NTs.\cite{Virsek2007} The silicon peak at 520 $cm^{-1}$ is used for calibration.
+Up-shift of $A_{1g}$ and $E_{2g}$ modes were observed, attributing to the strain in 3R stacking layers.
 
@@
 \end{enumerate}
+
+\citeauthor{Krause2009} measured the resonant Raman using 632 and 532 nm excitation and found a split within 420 $cm^{-1}$ region, which is labelled as $D-A_{1g}$ mode in analog with the similar defect mode of graphene.\cite{Krause2009} This  $D-A_{1g}$ mode was found enhanced as diameter of \ce{WS2} NTs decrease.
+In this work, we will use $B_{1u}$ mode to interpret this emerging line at about 416 $cm^{-1}$ of \ce{WS2} NTs.
+\citeauthor{Krause2009a} confirmed $B_{1u}$ mode arise from the inherent structure of \ce{WS2} nanomaterials instead of surface layer effect.
+It is also worth noting that $A_{1g}$ is stronger than 2LA under 632nm yet weaker under 532nm, and $B_{1u}$ mode under 532 nm become less prominent than that of 632 nm.\cite{Krause2009a} This is in consistent with our observation of Raman spectra on the \ce{WS2}-\ce{WO_x} structures.
+
+\subsection{TMS bulk and FL}
+
+Lattice vibration of natural \ce{MoS2} crystal was studied by \citeauthor{Wieting1971} using infrared and Raman spectroscopy.\cite{Wieting1971} Hexagonal \ce{MoS2} belongs to space group $D_{6h}^4$, and the repeat unit in $c$ axis contains two layers, where sulfur atoms in one layer are directly above the molybdenum atoms in adjacent layers, which is often referred as 2H-\ce{MoS2}.
+The lattices dimensions are summarized in Table~\ref{tab:ms2lattice}, and vibration modes in Table~\ref{tab:tmslattice}.\footnote{The symmetry is reduced from $D_{6h}$ to $D_{3h}$ when thinning to monolayer, with the absence of inversion center.} Group theory predicts two infrared- and four Raman-active modes for 2H-\ce{MoS2}, which are mutually exclusive when the center of inversion is present.
+It was found the $E_{1u}$ IR mode and one $E_{2g}$ Raman mode are nearly degenerate in energy.
+15 optical modes are allowed assuming 6 atoms in primitive cell.
+Refractive indices from reflectivity measurement were n0= 3.9, ne = 2.5.
+
+\citeauthor{Sourisseau1991} investigated the resonant Raman profiles in 2H-\ce{WS2} using ten different excitation wavelengths.\cite{Sourisseau1991} Dramatic intensity variation at 352 cm was observed, which is of two-phonon signal nature, and corresponds to an overtone or combination band of phonons with non-zero momenta contributing to indirect gap absorption edge.
+The authors assigned this phonon with non-zero momenta as $LA(K_5)$ type.
+\citeauthor{Stacy1985} studied \ce{MoS2} and \ce{WS2} Raman spectra using lasing energy close to the absorption edges.\cite{Stacy1985} Second order scattering from phonon with nonzero momentum is used to explain the rich Raman spectra.
 
@@
 \caption{Lattices dimension of \ce{MS2}}\label{tab:ms2lattice}
-\begin{tabular}{lcccr}
+\begin{tabular}{lccr}
 \toprule
-\multicolumn{2}{c}{Flow} \\
-\cmidrule(l){4-5}
-         & Temperature & Pressure & Ar & \ce{O2}  \\
+         &  & 2H-\ce{MoS2}\cite{Coehoorn1987} & 2H-\ce{WS2}\cite{Albe2002,Schutte1987} \\
 \midrule
-Range      & RT-1100    & 10mTorr-1atm & 0 - 100 & 0-30  \\
-Resolution & $\pm1$  & correlated to flow & 1   & 0.1  \\
+Lattice constant & a(\AA) & 3.1604 & 3.171 \\
+                 & c(\AA) & 12.295 & 12.359 \\
+Within \ce{MS2} layer & M-3S (\AA)&   & 2.405   \\
+                      & S-1S (\AA)&   & 3.14   \\
+Between \ce{MS2} layer& S-3S (\AA)&   & 3.53   \\
 \bottomrule
@@
     \toprule
-    &&\multicolumn{3}{c}{Wavenumber shift ($cm^{-1}$})\\
+    &&\multicolumn{3}{c}{Wavenumber shift ($cm^{-1}$)}\\
     \cmidrule(l){3-5}
@@
     $2LA(M)+2E_{2g}^2(M)$    &      &                              & 381          &  381   \\
-     LA + TA or $B_{1u}$     &      &                              &              &  416 \\
+     LA + TA \cite{Sourisseau1991} or $B_{1u}$\cite{Staiger2012}  &      &       &   &  416 \\
           $A_{1g}(\Gamma)$   &      & 417.9                        & 416\textsuperscript{\emph{b}} &  421\\
@@
 
+\citeauthor{Chung1998} grew \ce{WS2} film using \ce{W(CO)6} and \ce{H2S} precursor.\cite{Chung1998} Raman spectra ($\lambda=632nm$) on films with non-parallel orientation revealed (non-symmetric) the presence of shoulder mode under $A_{1g}$, which is assigned to LA and TA phonon coupling.
+This coupling process stem from disorder-activated zone boundary phonons.
+
+\citeauthor{Ghorbani-asl} discuss the electronic and vibrational properties for large diameter \ce{WS2} NTs\cite{Ghorbani-asl}.
+Single-walled NT is approximated by 1H monolayer and others by 2H bulk structure.
+It was found that large-diameter nanotubes can be approximated with layered systems as their properties should be nearly the same at the scale.
+Only hypothetical SWNTs, and possibly MWNTs with alternating layer compositions, may show direct band gaps.
+Slight mechanical deformation of the SWNTs would result in a change of the direct band gap back to the indirect one, located between $\Gamma$ and $K$ high-symmetry points, similarly to the monolayers.
+As for 2D materials, quantum confinement to single-walled tubes would result in direct band-gap semiconductors with $\Delta$ occurring at the $K$ point.
+Single-walled tubes exhibit slightly softer out-of-plane $A'$ and stronger in-plane $E'$ modes.
+Those results indicate that the weak interlayer interactions in TX$_2$ materials cannot be associated with the van der Waals interactions only, but most probably with Coulomb electrostatic interactions as well.
+Raman spectroscopy qualifies as an excellent tool to monitor tensile tests of TMDs, both in 2D and in tubular forms.
+For 2D materials, strain may be induced by elongation of an appropriate substrate, e.g.
+by uniform mechanical strain, or by using a material with high thermal expansion coefficient and varying the temperature.
+For TMD MWNT, tensile tests have been reported by various groups.
+However, to date, it is not perfectly clear whether inner and outer walls are stretched simultaneously, or rather the outer walls slide on the inner ones.
+The latter hypothesis would result in a broadening of the Raman signals, while the first one would leave the signal widths rather unaffected.
+In any case, there would be a shift of the Raman signals that can serve as precise scale for determining the strain.
+
+As the experimental setup for direct tensile tests of nanotubes is state-of-the-art,\cite{Tang2013} the application of tensile stress on 2D TMD systems is rather difficult due to the excellent lubricating properties of these materials.
+
+The $E$ type phonon branches correspond to the in-plane normal modes, while the $A$ type phonons result from the out-of-plane vibrations. ref 29,
+
+\citeauthor{Zhang2013i} investigated the shear (C) and layer breathing mode (LBM) in the low frequency region of \ce{MoS2}.\cite{Zhang2013i} Even layer \ce{MS2} belong to point group D$_{6h}$ with inversion symmetry, while odd  layer \ce{MS2} correspond to D$_{3h}$ without inversion symmetry.
+The excitation wavelength is 532nm from a diode-pumped solid-state laser.
+A power$\sim$0.23mW is used to avoid sample heating.
+Bulk MoS$_2$ and 2L-MoS$_2$ belong to the space group P6$_3$/$_{mmc}$ (point group D$_{6h}$) There are 18 normal vibration modes.
+The factor group of bulk and 2L-MoS$_2$ at $\vec{\Gamma}$ is D$_{6h}$, the same as the point group.
+The atoms site groups are a subgroup of the crystal factor group.
+The correlation of the Mo site group D$_{3h}$, S site group C$_{3v}$, and factor group D$_{6h}$ allows one to derive the following irreducible representations for the 18 normal vibration modes at $\vec{\Gamma}$: $\vec{\Gamma}$= $A_{1g}+2A_{2u}+2B_{2g}+B_{1u}+E_{1g}+2E_{1u}+2E_{2g}+E_{2u}$, where $A_{2u}$ and $E_{1u}$ are translational acoustic modes, $A_{1g}$, $E_{1g}$ and $E_{2g}$ are Raman active, $A_{2u}$ and $E_{1u}$ are infrared (IR) active.
+1L-MoS$_2$ has $D_{3h}$ symmetry, with three atoms per unit cell.
+The irreducible representation of $D_{3h}$ gives: $\vec{\Gamma}$= $2A_2^{''}$+$A_1^{'}$+$2E^{'}$+$E^{''}$, with $A_2$$^{''}$ and $E^{'}$ acoustic modes, $A_2^{''}$ IR active, $A_1^{'}$ and $E^{''}$ Raman active, and the other $E^{'}$ both Raman and IR active.
+NL-MoS$_2$ has 9N-3 optical modes: 3N-1 are vibrations along the c axis, and 3N-1 are doubly degenerate in-plane vibrations.
+For rigid-layer vibrations, there are N-1 LBMs along the c axis, and N-1 doubly degenerate shear modes perpendicular to it.
+When N is even, there are 0 Raman active LBMs and $\frac{N}{2}$ doubly degenerate shear modes.
+When N is odd, there are $\frac{N-1}{2}$ LBMs and N-1 doubly degenerate shear modes.
+
+direct gap of ML at point K.
+
 \section{paragraph from word files}
+
+nucleation and film growth \cite{Hanbucken1984}
+
+2H and 1T in \ce{MoS2} \cite{Eda2012}
+
+\ce{MoS2} FET statistical study. \cite{Liu2013i}
+
+water splitting review. \cite{B800489G}
+
+\ce{WS2} theory and experimental combined study. \cite{Klein2001}
+
+2D review on oxides \cite{Osada2012}
+
+Pb catalyzed \ce{MoS2} nanotube \cite{Brontvein2012}
+
+\ce{WS2} film by sulfurization of W coating on \ce{SiO2}-Si.\cite{Shanmugam2012a}
+
+8/8/13
+
+\citeauthor{Ramasubramaniam2011} investigated the band gap tuning in bilayer TMDC materials by applying external $E$ field.
+Similar research has been done for graphene and bilayer boron nitride.
+Semiconductor-metal transition was suggested for \ce{MoS2} and \ce{WS2}, with difference on the CBM and VBM evolution.
+In \ce{MoS2}, the valence-band-splitting cause the A and B excitons in optical absorption measurement.
+Calculation shows that CB and VB are translated toward the Fermi level with increasing E field.
+The external field localized charge along $c$ axis, but delocalized that within the plane normal towards $c$, thereby driving the semi-metal transition.
+It was mentioned that this transition is not anticipated in monolayer \ce{MoS2}.
+It was emphasized that precise band gaps might be different from the author’s results, yet the gap-tuning should be universal.\cite{Ramasubramaniam2011}
 

### 2014-02-12 BackMatter/paper.tex
tms chapter structure rebuilt

@@
 
+hydrogen absorption in \ce{MoO3}.\cite{Sha2009}
+
+\ce{Na6Mo_{11}O_{36}} phase. \cite{Bramnik2004}
+
+\ce{Na6Mo_{10}O_{33}} phase, \cite{Gatehouse1983}
+
+\ce{MoO3} thin film. \cite{Carcia1987}
+
+\ce{H_xMoO3} raman.\cite{Hirata1996}
+
+MoO3 spreading \cite{Leyrer1990}
+
+Na2Mo2O7, Na2Mo4O13 phase transition \cite{SinghMudher2005}\cite{Tangri1992}
+
+visibility of FL \cite{Benameur2011}
+
+exfoliation IPA \cite{Halim2013}  \cite{Zhou2011a}
+
 \section{TMS}
@@
 
-In 2H type TMDC, the $A_{1g}$ mode is sensitive to electrostatic doping, while $E_{2g}^1$ mode is sensitive to strain, in which the FWHM of the peaks are indicator of external force quantity.
+Raman technique could provide valuable insight into the structures of CNT, i.e., tube diameter by assigning the RBMs (radial breathing modes) and G peaks position.\cite{Bonaccorso2013}
 
-Raman technique could provide valuable insight into the structures of CNT, i.e., tube diameter by assigning the RBMs (radial breathing modes) and G peaks position.\cite{Bonaccorso2013}
+ Raman spectroscopy qualifies as an excellent tool to monitor tensile tests of TMDs, both in 2D and in tubular forms.
+For 2D materials, strain may be induced by elongation of an appropriate substrate, e.g.
+by uniform mechanical strain, or by using a material with high thermal expansion coefficient and varying the temperature.
+For TMD MWNT, tensile tests have been reported by various groups.
+However, to date, it is not perfectly clear whether inner and outer walls are stretched simultaneously, or rather the outer walls slide on the inner ones.
+The latter hypothesis would result in a broadening of the Raman signals, while the first one would leave the signal widths rather unaffected.
+In any case, there would be a shift of the Raman signals that can serve as precise scale for determining the strain.
+
+As the experimental setup for direct tensile tests of nanotubes is state-of-the-art,\cite{Tang2013} the application of tensile stress on 2D TMD systems is rather difficult due to the excellent lubricating properties of these materials.
 
@@
 \end{enumerate}
+
+\citeauthor{Zhang2013i} investigated the shear (C) and layer breathing mode (LBM) in the low frequency region of \ce{MoS2}.\cite{Zhang2013i} Even layer \ce{MS2} belong to point group D$_{6h}$ with inversion symmetry, while odd layer \ce{MS2} correspond to D$_{3h}$ without inversion symmetry.
+The excitation wavelength is 532nm from a diode-pumped solid-state laser.
+A power$\sim$0.23mW is used to avoid sample heating.
+
+\citeauthor{Cao2014} studied the layer-dependence \ce{MoS2} electrocatalysis and propose the vertical hopping efficiency of electrons instead of the edge site numbers is a key factor for catalytic reaction.\cite{Cao2014} ref19,20
 
@@
 
-(Wang et al. 2013)
-MoS2 CVD (tsinghua univ) layer by layer sulfurization of MoO2
-MoO3 powder 25mg and MnO2 powder 25 mg, extra sulfur
-Ar purging  20mins, heating at 650 degree to produce MoO2 flakes
+(Wang et al. 2013) MoS2 CVD (tsinghua univ) layer by layer sulfurization of MoO2. 
+MoO3 powder 25mg and MnO2 powder 25 mg, extra sulfur Ar purging  20mins, heating at 650 degree to produce MoO2 flakes
 Further reaction between MoO2 and S was performed at 850-950 degree under Ar flow.

### 2014-02-12 ch-tms/tms.tex
tms chapter structure rebuilt

@@
 \chapter{Transition metal dichalcogenides}
+
+In this chapter, we will first review the growth of \ce{MS2} nanotubes and \ce{MS2} few layer structures.
+Then we summarize the Raman spectroscopy results on NTs and FL.
+Finally we present our own results on synthesis and characterization.
 
@@
 
+\citeauthor{Zhu2000} performed a detailed morphological and structural analysis on \ce{WS2} NT synthesized using \ce{WO_{3-x}} NWs and \ce{H2S}.
+\cite{Zhu2000} Sulfur vacancy was found on the outer wall of NT.
+The tips exhibits various structures.
+Open-ended can be observed, more frequently than that in CNT, which is often sealed.
+\citeauthor{Zhu2000} suggested this open-ended tubes resulted from continuous growth on other nanotubes.
+And the closure configuration is rather complicated.
+Flat caps often dominates.
+\citeauthor{Feldman1996} proposed that TMDC nanotubes growth began with the reduced \ce{WO3} phases, in particular \ce{W_{18}O_{49}}.\cite{Feldman1996} \citeauthor{Zhu2000} maintained that this oxide-to-sulfides mechanism might apply to closed caps only, not to those open ended tubes.\cite{Zhu2000} TEM diffraction analysis could distinguish the chirality of NTs, as demonstrated by CNT \cite{Zhang1993} and \ce{MoS2}\cite{MARGULIS1996}.
+\ce{WS2} NT chirality revealed by TEM SEAD show armchair NTs dominates.
+\citeauthor{Sloan1999} investigated tungsten oxides structures incorporated in \ce{WS2}.\cite{Sloan1999} The encapsulated \ce{WO_x} cores often exhibit \ce{W3O8} and \ce{W5O_{14}} phases, both of which belong to the \ce{W_nO_{3n-1}} homogenous series, arising as a result of crystallographic shearing (CS) planes.\cite{Miyano} Some \ce{WO_x} cores show oxygen vacancy instead of CS planes, leading to prominent streaking in SEAD patterns.
+Although high yield growth method of \ce{WS2} has been available, the extent to which one can control the NT configuration is still limited, i.e., single-walled NT has not been routinely synthesized and the electronic properties can only be predicted theoretically.
+\citeauthor{Seifert2000} investigated the electronic structures of \ce{WS2} nanotube using DFT calculation.\cite{Seifert2000} It was found zigzag (n,0) NTs exhibts a direct gap at $\Gamma$ point, whose size increase monotonically with tube diameter, while armchair (n,n) NTs, unlike its metallic counterpart of (n,n) CNT, show indirect band gap increasing with tube diameter.
+\citeauthor{Zibouche2012} reached the same conclusion on \ce{WS2} SWNT.\cite{Zibouche2012} It was also found band gaps of armchair and zigzag NTs increase with diameter, going from values close to bulk and approaching that of  monolayer, and for a given tube diameter, $E_g$ of zigzag NTs are larger than those of armchair NTs.
+This difference presumably vanishes when the tube diameter exceeds 100 nm.
+
 Parallel with the scenario of CNT and graphene, TMDC few layer structures attracts intensive research efforts recently.
 These unfolded TMDC nanotubes exhibit many appealing features, i.e., indirect-to-direct band gap transition,\cite{Splendiani2010} valley electronics, and become a promising candidate in energy harvesting, optoelectronics.
-
 For scientific research purpose, exfoliation by liquid \cite{Smith2011} or mechanical methods \cite{Lee2010a} can provide plenty materials.
 Yet considering the integration into current microelectronic process, CVD synthesis of TMDC FL is desired, which hold the greatest potential for high yield production of \ce{MS2}.
-So in this work we focus on the CVD-based methods, as summarized in Table~\ref{tab:tmsgrowth}.
+So in this work we focus on the CVD-based methods.
+We will review literature to date on both \ce{WS2} films and few layer structures, and highlight several typical investigations using different type synthesis method, as summarized in Table~\ref{tab:tmsgrowth}.
 
-\citeauthor{Lee1994} studied the CVD of \ce{MoS2} by \ce{MoCl5} or \ce{MoF6} and \ce{H2S} in great details.
+\textbf{\ce{MS2} films} \citeauthor{Lee1994} studied the CVD of \ce{MoS2} by \ce{MoCl5} or \ce{MoF6} and \ce{H2S} in great details.
 Phase diagrams for \ce{Mo-S-Cl-H} and \ce{Mo-S-F-H} system at 1 kPa were simulated.
@@
 More important, \ce{MoS2} basal plane orientation can be parallel to substrate when the thickness was smaller than 50 nm.
+\citeauthor{Regula1997} studied the Ni-W-S phase diagram and the role of Ni layer in promoting \ce{WS2} film growth from amorphous \ce{WS3}.\cite{Regula1997} \emph{In-situ} TEM analysis confirmed the formation of \ce{NiS_x} droplets and lateral growth of \ce{WS2} from these droplets.
+\cite{Regula1998} Recently, it has been shown that direct sulfurization of W coating (20nm) at 750 \si{\degreeCelsius} on \ce{SiO2}-Si can also produce \ce{WS2} film.\cite{Shanmugam2012a} However, the film is of bulk in nature.
+This could be explained by the study of \citeauthor{Genut1992} towards \ce{WS2} growth on various substrates.\cite{Genut1992} We summarize the main results in Table~\ref{tab:ws2subs}.
+It was found that the \ce{WS2} nucleate from an amorphous \ce{WS3} phase and the substrate has a critical role in determining both the reaction onset temperature and the texture.
+% WS2 films
+\begin{table}[htb]
+\centering
+\caption{\ce{WS2} growth on different substrates}\label{tab:ws2subs}
+\begin{tabular}{lcp{1in}p{2in}}
+\toprule
+precursor                 & substrate &  conditions & film feature\textsuperscript{\emph{a}}  \\
+\midrule
+sputtered W + \ce{H2S}   & glass      & onset 400 \si{\degreeCelsius} & $\perp c$ at 500 \si{\degreeCelsius}\\
+                          & quartz      & onset 650 \si{\degreeCelsius} & $\parallel c$ below 950 \si{\degreeCelsius}\\
+                          & Mo        & onset NA          & $\parallel c$ at 1000 \si{\degreeCelsius}\\
+                          & W          & onset NA           & random orientation\\
+\midrule
+\ce{WO_x} + \ce{H2S}    & quartz      & onset 500 \si{\degreeCelsius} & predominantly $\perp c$ at 800 \si{\degreeCelsius}\\
+\bottomrule
+\end{tabular}
 
-\citeauthor{Regula1997} studied the Ni-W-S phase diagram and the role of Ni layer in promoting \ce{WS2} film growth from amorphous \ce{WS3}.\cite{Regula1997} \emph{In-situ} TEM analysis confirmed the formation of \ce{NiS_x} droplets and lateral growth of \ce{WS2} from these droplets.
-\cite{Regula1998}
+\textsuperscript{\emph{a}} $\perp c$: the c axis is perpendicular to the substrate, $\parallel c$: the c axis is parallel to the substrate;
 
+\end{table}
+
+\textbf{\ce{MS2} FL} For \ce{MoS2}, the reaction mechanism of \ce{MoO3} to \ce{MoS2} was studied by \citeauthor{Weber1996}.\cite{Weber1996} This study provided guideline for the recent syntheses of \ce{MoS2} by sulfurization of \ce{MoO3}.
+\cite{Lin2012,Lee2012b,Liu2012a} We assume similar insight could be gained from the aforementioned growth of \ce{WS2} films.
 \citeauthor{Cong2013} prepared monolayer \ce{WS2} on 300nm \ce{SiO2}-Si by sulfurization of \ce{WO3} powders in a one-end sealed tube.\cite{Cong2013} It was suggested that pre-cleaning the inner tube by IPA and DI water could effectively increase the pressure of vapor source.
@@
 Sulfurization mechanism study of \ce{WO3} suggested \ce{W^{6+}} cannot be directly reduce to \ce{W^{4+}} in \ce{WS2}.\cite{VanderVlies2002,VanderVlies2002a} Tungsten oxysulfides was necessary as the intermediate phase.
-Other chalcogenide has also been synthesized using this one-end sealed layout.\cite{Mukherjee2013}
-
-\citeauthor{Zhang2013h} synthesized \ce{WS2} on sapphire using \ce{WO3} powder and sulfur as precursor under 900 \si{\degreeCelsius}.
+Other chalcogenide has also been synthesized using this one-end sealed layout.\cite{Mukherjee2013} \citeauthor{Zhang2013h} synthesized \ce{WS2} on sapphire using \ce{WO3} powder and sulfur as precursor under 900 \si{\degreeCelsius}.
 \cite{Zhang2013h} Ar slightly mixed with \ce{H2} is used to tailor the shape of \ce{WS2} flakes.
@@
 
-\cite{Song2013} ALD \ce{WS2}
-
-\citeauthor{Cao2014} studied the layer-dependence \ce{MoS2} electrocatalysis and propose the vertical hopping efficiency of electrons instead of the edge site numbers is a key factor for catalytic reaction.\cite{Cao2014} ref19,20
-
 In studying the growth of TMDC, two issues dominate: one is the reaction of precursor, the other is the surface energy status of receiving substrates.
-For \ce{MoS2}, the reaction mechanism of \ce{MoO3} to \ce{MoS2} was studied by \citeauthor{Weber1996}.\cite{Weber1996} This study provided guideline for the recent syntheses of \ce{MoS2} by sulfurization of \ce{MoO3}.
-\cite{Lin2012,Lee2012b,Liu2012a}
-
 % CVD TMDC
@@
 \ce{WS2} FL \cite{Lee2013}  & 1g \ce{WO3} powders, sulfur,subs treated with PTAS and gentle gas blow & substrate facing down, APCVD, 900 \si{\degreeCelsius}, 5mins, 5 sccm Ar, fast heating. \\
+\addlinespace[0.5em]
+\ce{WS2} films \cite{Shanmugam2012a}   & 20nm W on \ce{SiO2}-Si, sulfur & 750 \si{\degreeCelsius}, 200 sccm Ar, 1Torr. Annealing at 1000 \si{\degreeCelsius}, 25nm thick \ce{WS2} film obtained \\
 \bottomrule
@@
 
-\section{ and Layer configuration}
-
-\citeauthor{Zhu2000} performed a detailed morphological and structural analysis on \ce{WS2} NT synthesized using \ce{WO_{3-x}} NWs and \ce{H2S}.
-\cite{Zhu2000} Sulfur vacancy was found on the outer wall of NT.
-The tips exhibits various structures.
-Open-ended can be observed, more frequently than that in CNT, which is often sealed.
-\citeauthor{Zhu2000} suggested this open-ended tubes resulted from continuous growth on other nanotubes.
-And the closure configuration is rather complicated.
-Flat caps often dominates.
-\citeauthor{Feldman1996} proposed that TMDC nanotubes growth began with the reduced \ce{WO3} phases, in particular \ce{W_{18}O_{49}}.\cite{Feldman1996} \citeauthor{Zhu2000} maintained that this oxide-to-sulfides mechanism might apply to closed caps only, not to those open ended tubes.\cite{Zhu2000} TEM diffraction analysis could distinguish the chirality of NTs, as demonstrated by CNT \cite{Zhang1993} and \ce{MoS2}\cite{MARGULIS1996}.
-\ce{WS2} NT chirality revealed by TEM SEAD show armchair NTs dominates.
-
-\citeauthor{Sloan1999} investigated tungsten oxides structures incorporated in \ce{WS2}.\cite{Sloan1999} The encapsulated \ce{WO_x} cores often exhibit \ce{W3O8} and \ce{W5O14} phases, both of which belong to the \ce{W_nO_{3n-1}} homogenous series, arising as a result of crystallographic shearing (CS) planes.\cite{Miyano} Some \ce{WO_x} cores show oxygen vacancy instead of CS planes, leading to prominent streaking in SEAD patterns.
-
-hydrogen evolution catalysts. \cite{Merki2011}
-
-\ce{WS2} NT FET. \cite{Levi2013}
-
-\ce{WS2} NT transport \cite{Zhang2012c}
-
-Raman substrate dependence \cite{Buscema2013}
-
-effect of substrate on WS2 growth\cite{Genut1992}
-
-WO3-x NPs \cite{Frey2001}
-
-stability of TMS NTs \cite{Seifert2002}
-
-growth mechanism \cite{ZAK2009}
-
 \section{Raman spectra}
-
-\subsection{TMS NTs}
-
-\citeauthor{Dobardzic2005} calculated \ce{MoS2} SWNT phonon dispersion.
-The dependence of wavenumbers and their displacement on chirality and diameter were discussed.
-The calculation method enable studying lattice dynamics with NT diameter up to 50nm.
-The chiral vector $(n_1, n_2)$ is defined within the Moly plane.
-Symmetry assignment is zigzag when $(n,0)$, armchair when $(n,n)$ and chiral when $(n_1, n_2), n_1>n_2$.
-\citeauthor{Dobardzic2006} theoretically presented Raman scattering of any polarization on SWNT of \ce{WS2} and their dependence on diameter (1-20nm) and chiral angle.
-The author assigned 351 $cm^{-1}$ as $E_u$ for \ce{WS2} NT.\cite{Dobardzic2006}
-
-\citeauthor{Seifert2000} investigated the electronic structures of \ce{WS2} nanotube using DFT calculation.\cite{Seifert2000} It was found zigzag (n,0) NTs exhibts a direct gap at $\Gamma$ point, whose size increase monotonically with tube diameter, while armchair (n,n) NTs, unlike its metallic counterpart of (n,n) CNT, show indirect band gap increasing with tube diameter.
-\citeauthor{Zibouche2012} reached the same conclusion on \ce{WS2} SWNT.\cite{Zibouche2012} It was also found band gaps of armchair and zigzag NTs increase with diameter, going from values close to bulk and approaching that of  monolayer, and for a given tube diameter, $E_g$ of zigzag NTs are larger than those of armchair NTs.
-This difference presumably vanishes when the tube diameter exceeds 100 nm.
-
-\citeauthor{Rafailov2005} estimated the orientation dependence of resonant raman on one MWNT \ce{WS2} attached to the cantilever tip of AFM.\cite{Rafailov2005} Antenna effect lead to optical transition occurring only for polarization parallel to nanotube axis.
-And therefore resonance Raman intensity of SWNT varies as nanotube orientation.
-This dependence may provide a routine to distinguish different chiral NTs.
-632nm excitation is used.
-Polarized Raman spectra is obtained, showing $A_{1g}$ and $E_{2g}$ sharing the same polarization behavior.
-\citeauthor{Virsek2007} investigated the Raman scattering ($\lambda=632nm$) of \ce{WS2} NTs.\cite{Virsek2007} The silicon peak at 520 $cm^{-1}$ is used for calibration.
-Up-shift of $A_{1g}$ and $E_{2g}$ modes were observed, attributing to the strain in 3R stacking layers.
-
-Raman signatures of \ce{WS2} nanotubes show distinct features to the spectra of their bulk counterpart.
-\citeauthor{JMR7990865} observed a new line at 152 cm in \ce{WS2} NT, which is absent in 2H-\ce{WS2}.\cite{JMR7990865} Another feature is a emerging shoulder on the low energy side of $A_{1g}$ mode at about 416 $cm^{-1}$.
-This has been attributed to a combination mode of LA + TA phonons from the $K$ point of Brillouin zone.\cite{Sourisseau1991} A more prominent feature is the resonance profile broadening the shape of $E_{2g}^1$ mode, which is often assigned to 2LA mode.
-Yet there is some different opinion on these assignments.
-\citeauthor{Molina-Sanchez2011} label the 350 $cm^{-1}$ band as \ce{E_{1u}} instead of 2LA, and the 416 $cm^{-1}$ band as inactive $B_{1u}$ mode.\cite{Molina-Sanchez2011} \citeauthor{Staiger2012} adopted these assignments in studying the resonance Raman profile of \ce{WS2} NTs.\cite{Staiger2012} It was found that
-\begin{enumerate}
-\item $B_{1u}$ mode arise from curvature and structural disorder
-\item $B_{1u}/A_{1g}$ intensity ratio strongly depends on excitation, and exceeds unity when excitation energy less than 1.9eV.
-\item  An excitonic transition energy of NT is found have a local minimum at about 50nm, (layer number probably \textgreater 10), and increase either way. Yet all below the bulk value.
-\end{enumerate}
-
-\citeauthor{Krause2009} measured the resonant Raman using 632 and 532 nm excitation and found a split within 420 $cm^{-1}$ region, which is labelled as $D-A_{1g}$ mode in analog with the similar defect mode of graphene.\cite{Krause2009} This  $D-A_{1g}$ mode was found enhanced as diameter of \ce{WS2} NTs decrease.
-In this work, we will use $B_{1u}$ mode to interpret this emerging line at about 416 $cm^{-1}$ of \ce{WS2} NTs.
-\citeauthor{Krause2009a} confirmed $B_{1u}$ mode arise from the inherent structure of \ce{WS2} nanomaterials instead of surface layer effect.
-It is also worth noting that $A_{1g}$ is stronger than 2LA under 632nm yet weaker under 532nm, and $B_{1u}$ mode under 532 nm become less prominent than that of 632 nm.\cite{Krause2009a} This is in consistent with our observation of Raman spectra on the \ce{WS2}-\ce{WO_x} structures.
 
@@
 
-Lattice vibration of natural \ce{MoS2} crystal was studied by \citeauthor{Wieting1971} using infrared and Raman spectroscopy.\cite{Wieting1971} Hexagonal \ce{MoS2} belongs to space group $D_{6h}^4$, and the repeat unit in $c$ axis contains two layers, where sulfur atoms in one layer are directly above the molybdenum atoms in adjacent layers, which is often referred as 2H-\ce{MoS2}.
-The lattices dimensions are summarized in Table~\ref{tab:ms2lattice}, and vibration modes in Table~\ref{tab:tmslattice}.\footnote{The symmetry is reduced from $D_{6h}$ to $D_{3h}$ when thinning to monolayer, with the absence of inversion center.} Group theory predicts two infrared- and four Raman-active modes for 2H-\ce{MoS2}, which are mutually exclusive when the center of inversion is present.
-It was found the $E_{1u}$ IR mode and one $E_{2g}$ Raman mode are nearly degenerate in energy.
-15 optical modes are allowed assuming 6 atoms in primitive cell.
-Refractive indices from reflectivity measurement were n0= 3.9, ne = 2.5.
-
-\citeauthor{Sourisseau1991} investigated the resonant Raman profiles in 2H-\ce{WS2} using ten different excitation wavelengths.\cite{Sourisseau1991} Dramatic intensity variation at 352 cm was observed, which is of two-phonon signal nature, and corresponds to an overtone or combination band of phonons with non-zero momenta contributing to indirect gap absorption edge.
-The authors assigned this phonon with non-zero momenta as $LA(K_5)$ type.
-\citeauthor{Stacy1985} studied \ce{MoS2} and \ce{WS2} Raman spectra using lasing energy close to the absorption edges.\cite{Stacy1985} Second order scattering from phonon with nonzero momentum is used to explain the rich Raman spectra.
+Before discussing the Raman spectra features, we briefly recapitulate some symmetry notations and vibration modes.
+We will use \ce{MoS2} as an example, and those definitions apply to \ce{WS2} as well.
+Hexagonal \ce{MoS2} belongs to space group $D_{6h}^4$, and the repeat unit in $c$ axis contains two layers, where sulfur atoms in one layer are directly above the molybdenum atoms in adjacent layers, which is often referred as 2H-\ce{MoS2}.
+Group theory predicts two infrared- and four Raman-active modes for 2H-\ce{MoS2}, which are mutually exclusive when the center of inversion is present.
+First we want to emphasize that in few layer structures, \ce{MoS2} with odd layers belong to different space group from that of even layers.
+Bulk MoS$_2$ and 2L-MoS$_2$ belong to the space group P6$_3$/$_{mmc}$ (point group D$_{6h}$) There are 18 normal vibration modes.
+The factor group of bulk and 2L-MoS$_2$ at $\vec{\Gamma}$ is D$_{6h}$.
+The atoms site groups are a subgroup of the crystal factor group.
+The correlation of the Mo site group D$_{3h}$, S site group C$_{3v}$, and factor group D$_{6h}$ allows one to derive the following irreducible representations for the 18 normal vibration modes at $\vec{\Gamma}$: $\vec{\Gamma}$= $A_{1g}+2A_{2u}+2B_{2g}+B_{1u}+E_{1g}+2E_{1u}+2E_{2g}+E_{2u}$, where $A_{2u}$ and $E_{1u}$ are translational acoustic modes, $A_{1g}$, $E_{1g}$ and $E_{2g}$ are Raman active, $A_{2u}$ and $E_{1u}$ are infrared (IR) active.
+1L-MoS$_2$ has $D_{3h}$ symmetry, with three atoms per unit cell.
+The irreducible representation of $D_{3h}$ gives: $\vec{\Gamma}$= $2A_2^{''}$+$A_1^{'}$+$2E^{'}$+$E^{''}$, with $A_2$$^{''}$ and $E^{'}$ acoustic modes, $A_2^{''}$ IR active, $A_1^{'}$ and $E^{''}$ Raman active, and the other $E^{'}$ both Raman and IR active.
+(See Fig.~\ref{fig:ws2ramsch}) NL-MoS$_2$ has 9N-3 optical modes: 3N-1 are vibrations along the c axis, and 3N-1 are doubly degenerate in-plane vibrations.
+For rigid-layer vibrations, there are N-1 layer breathing modes (LBMs) along the c axis, and N-1 doubly degenerate shear modes perpendicular to it.
+When N is even, there are 0 Raman active LBMs and $\frac{N}{2}$ doubly degenerate shear modes.
+When N is odd, there are $\frac{N-1}{2}$ LBMs and N-1 doubly degenerate shear modes.\cite{Wieting1971,Zhang2013i} This discussion can be visualized in Table~\ref{tab:tmslattice}.
 
@@
 
-\begin{table}[htb]
+The $E$ type phonon branches correspond to the in-plane normal modes, while the $A$ type phonons result from the out-of-plane vibrations.
+$A_{1g}$ mode is an out-of-plane vibration involving only the S atoms while the $E_{2g}^1$ mode involves in-plane displacement of transition metal and S atoms.
+The $E_{2g}^2$ mode is a shear mode corresponding to the vibration of two rigid layers against
+each other and appears at very low frequencies ($<50 cm^{-1}$ \cite{Zhang2013i}).
+The $E_{1g}$ mode, which is an in-plane vibration of only the S atoms, is forbidden in the backscattering Raman configuration.
+In 2H type TMDC, the $A_{1g}$ mode is sensitive to electrostatic doping, while $E_{2g}^1$ mode is sensitive to strain, in which the FWHM of the peaks are indicator of external force quantity.
+
+\begin{figure}[htb]
 \centering
-\caption{Lattices dimension of \ce{MS2}}\label{tab:ms2lattice}
-\begin{tabular}{lccr}
-\toprule
-         &  & 2H-\ce{MoS2}\cite{Coehoorn1987} & 2H-\ce{WS2}\cite{Albe2002,Schutte1987} \\
-\midrule
-Lattice constant & a(\AA) & 3.1604 & 3.171 \\
-                 & c(\AA) & 12.295 & 12.359 \\
-Within \ce{MS2} layer & M-3S (\AA)&   & 2.405   \\
-                      & S-1S (\AA)&   & 3.14   \\
-Between \ce{MS2} layer& S-3S (\AA)&   & 3.53   \\
-\bottomrule
-\end{tabular}
-\end{table}
+\includegraphics[width=0.7\textwidth]{ws2_ramsch}
+\caption[\ce{MS2} vibration symmetry]{\ce{MS2} vibration symmetry in bulk and monalyer, adopted from REF\cite{Ghorbani-asl}}
+\label{fig:ws2ramsch}
+\end{figure}
+
+Lattice vibration of natural \ce{MoS2} crystal was studied by \citeauthor{Wieting1971} using infrared and Raman spectroscopy.\cite{Wieting1971} It was found the $E_{1u}$ IR mode and one $E_{2g}$ Raman mode are nearly degenerate in energy.
+15 optical modes are allowed assuming 6 atoms in primitive cell.
+Refractive indices from reflectivity measurement were n0= 3.9, ne = 2.5.
+\citeauthor{Stacy1985} studied \ce{MoS2} and \ce{WS2} Raman spectra using lasing energy close to the absorption edges.\cite{Stacy1985} Second order scattering from phonon with nonzero momentum is used to explain the rich Raman spectra.
+\citeauthor{Sourisseau1991} investigated the resonant Raman profiles in 2H-\ce{WS2} using ten different excitation wavelengths.\cite{Sourisseau1991} Dramatic intensity variation at 352 $cm^{-1}$ was observed, which is of two-phonon signal nature, and corresponds to an overtone or combination band of phonons with non-zero momenta contributing to indirect gap absorption edge.
+The authors assigned this phonon with non-zero momenta as $LA(K_5)$ type.
+The enhancement of the total Raman cross section at excitonic resonance in which excitons serve as the intermediate state is stronger compared to that of interband resonance.
+The strong enhancement at excitonic resonance is attributed to the characteristics of excitons in layered materials such as large binding energy, enhanced oscillator strength, and small damping constant.\cite{Zhao2013} \citeauthor{Chung1998} grew \ce{WS2} film using \ce{W(CO)6} and \ce{H2S} precursor.\cite{Chung1998} Raman spectra ($\lambda=632nm$) on films with non-parallel orientation revealed the presence of shoulder mode under $A_{1g}$, which is assigned to LA and TA phonon coupling.
+This coupling process stem from disorder-activated zone boundary phonons.
+We will further discuss this non-symmetric feature of $A_{1g}$ mode in section~\ref{sec:ntram}.
 
@@
 
-\citeauthor{Chung1998} grew \ce{WS2} film using \ce{W(CO)6} and \ce{H2S} precursor.\cite{Chung1998} Raman spectra ($\lambda=632nm$) on films with non-parallel orientation revealed (non-symmetric) the presence of shoulder mode under $A_{1g}$, which is assigned to LA and TA phonon coupling.
-This coupling process stem from disorder-activated zone boundary phonons.
+Raman technique has also provided much insight into the few layer \ce{MS2}.
 
-\citeauthor{Ghorbani-asl} discuss the electronic and vibrational properties for large diameter \ce{WS2} NTs\cite{Ghorbani-asl}.
+\subsection{TMS NTs}\label{sec:ntram}
+
+\citeauthor{Dobardzic2005} calculated \ce{MoS2} SWNT phonon dispersion.
+The dependence of wavenumbers and their displacement on chirality and diameter were discussed.
+The calculation method enables studying lattice dynamics with NT diameter up to 50nm.
+The chiral vector $(n_1, n_2)$ is defined within the molybdenum plane.
+Symmetry assignment is zigzag when $(n,0)$, armchair when $(n,n)$ and chiral when $(n_1, n_2), n_1>n_2$.
+\citeauthor{Dobardzic2006} theoretically presented Raman scattering of any polarization on SWNT of \ce{WS2} and their dependence on diameter (1-20nm) and chiral angle.
+The author assigned 351 $cm^{-1}$ as $E_u$ for \ce{WS2} NT.\cite{Dobardzic2006} \citeauthor{Ghorbani-asl} discuss the electronic and vibrational properties for large diameter \ce{WS2} NTs\cite{Ghorbani-asl}.
 Single-walled NT is approximated by 1H monolayer and others by 2H bulk structure.
@@
 Single-walled tubes exhibit slightly softer out-of-plane $A'$ and stronger in-plane $E'$ modes.
-Those results indicate that the weak interlayer interactions in TX$_2$ materials cannot be associated with the van der Waals interactions only, but most probably with Coulomb electrostatic interactions as well.
-Raman spectroscopy qualifies as an excellent tool to monitor tensile tests of TMDs, both in 2D and in tubular forms.
-For 2D materials, strain may be induced by elongation of an appropriate substrate, e.g.
-by uniform mechanical strain, or by using a material with high thermal expansion coefficient and varying the temperature.
-For TMD MWNT, tensile tests have been reported by various groups.
-However, to date, it is not perfectly clear whether inner and outer walls are stretched simultaneously, or rather the outer walls slide on the inner ones.
-The latter hypothesis would result in a broadening of the Raman signals, while the first one would leave the signal widths rather unaffected.
-In any case, there would be a shift of the Raman signals that can serve as precise scale for determining the strain.
+Those results indicate that the weak interlayer interactions in MS$_2$ materials cannot be associated with the van der Waals interactions only, but most probably with Coulomb electrostatic interactions as well.
 
-As the experimental setup for direct tensile tests of nanotubes is state-of-the-art,\cite{Tang2013} the application of tensile stress on 2D TMD systems is rather difficult due to the excellent lubricating properties of these materials.
+Raman signatures of \ce{WS2} nanotubes show distinct features to the spectra of their bulk counterpart.
+\citeauthor{JMR7990865} observed a new line at 152 cm in \ce{WS2} NT, which is absent in 2H-\ce{WS2}.\cite{JMR7990865} Another feature is a emerging shoulder on the low energy side of $A_{1g}$ mode at about 416 $cm^{-1}$.
+This has been attributed to a combination mode of LA + TA phonons from the $K$ point of Brillouin zone.\cite{Sourisseau1991} A more prominent feature is the resonance profile broadening the shape of $E_{2g}^1$ mode, which is often assigned to 2LA mode.
+Yet there is some different opinion on these assignments.
+\citeauthor{Molina-Sanchez2011} label the 350 $cm^{-1}$ band as \ce{E_{1u}} instead of 2LA, and the 416 $cm^{-1}$ band as inactive $B_{1u}$ mode.\cite{Molina-Sanchez2011} \citeauthor{Staiger2012} adopted these assignments in studying the resonance Raman profile of \ce{WS2} NTs.\cite{Staiger2012} It was found that
+\begin{enumerate}
+\item $B_{1u}$ mode arise from curvature and structural disorder
+\item $B_{1u}/A_{1g}$ intensity ratio strongly depends on excitation, and exceeds unity when excitation energy less than 1.9eV.
+\item  An excitonic transition energy of NT is found have a local minimum at about 50nm, (layer number probably \textgreater 10), and increase either way. Yet all below the bulk value.
+\end{enumerate}
 
-The $E$ type phonon branches correspond to the in-plane normal modes, while the $A$ type phonons result from the out-of-plane vibrations. ref 29,
+\citeauthor{Krause2009} measured the resonant Raman using 632 and 532 nm excitation and found a split within 420 $cm^{-1}$ region, which is labelled as $D-A_{1g}$ mode in analog with the similar defect mode of graphene.\cite{Krause2009} This  $D-A_{1g}$ mode was found enhanced as diameter of \ce{WS2} NTs decrease.
+In this work, we will use $B_{1u}$ mode to interpret this emerging line at about 416 $cm^{-1}$ of \ce{WS2} NTs.
+\citeauthor{Krause2009a} confirmed $B_{1u}$ mode arise from the inherent structure of \ce{WS2} nanomaterials instead of surface layer effect.
+It is also worth noting that $A_{1g}$ is stronger than 2LA under 632nm yet weaker under 532nm, and $B_{1u}$ mode under 532 nm become less prominent than that of 632 nm.\cite{Krause2009a} This is in consistent with our observation of Raman spectra on the \ce{WS2}-\ce{WO_x} structures.
+\citeauthor{Rafailov2005} estimated the orientation dependence of resonant raman on one MWNT \ce{WS2} attached to the cantilever tip of AFM.\cite{Rafailov2005} Antenna effect lead to optical transition occurring only for polarization parallel to nanotube axis.
+And therefore resonance Raman intensity of SWNT varies as nanotube orientation.
+This dependence may provide a routine to distinguish different chiral NTs.
+Polarized Raman spectra (632nm excitation) is obtained, showing $A_{1g}$ and $E_{2g}$ sharing the same polarization behavior.
+\citeauthor{Virsek2007} investigated the Raman scattering ($\lambda=632nm$) of \ce{WS2} NTs.\cite{Virsek2007} The silicon peak at 520 $cm^{-1}$ is used for calibration.
+Up-shift of $A_{1g}$ and $E_{2g}$ modes (i.e.
+420 to 423 $cm^{-1}$ at $A_{1g}$ mode) were observed, which is attributed to the strain in 3R stacking layers.
 
-\citeauthor{Zhang2013i} investigated the shear (C) and layer breathing mode (LBM) in the low frequency region of \ce{MoS2}.\cite{Zhang2013i} Even layer \ce{MS2} belong to point group D$_{6h}$ with inversion symmetry, while odd  layer \ce{MS2} correspond to D$_{3h}$ without inversion symmetry.
-The excitation wavelength is 532nm from a diode-pumped solid-state laser.
-A power$\sim$0.23mW is used to avoid sample heating.
-Bulk MoS$_2$ and 2L-MoS$_2$ belong to the space group P6$_3$/$_{mmc}$ (point group D$_{6h}$) There are 18 normal vibration modes.
-The factor group of bulk and 2L-MoS$_2$ at $\vec{\Gamma}$ is D$_{6h}$, the same as the point group.
-The atoms site groups are a subgroup of the crystal factor group.
-The correlation of the Mo site group D$_{3h}$, S site group C$_{3v}$, and factor group D$_{6h}$ allows one to derive the following irreducible representations for the 18 normal vibration modes at $\vec{\Gamma}$: $\vec{\Gamma}$= $A_{1g}+2A_{2u}+2B_{2g}+B_{1u}+E_{1g}+2E_{1u}+2E_{2g}+E_{2u}$, where $A_{2u}$ and $E_{1u}$ are translational acoustic modes, $A_{1g}$, $E_{1g}$ and $E_{2g}$ are Raman active, $A_{2u}$ and $E_{1u}$ are infrared (IR) active.
-1L-MoS$_2$ has $D_{3h}$ symmetry, with three atoms per unit cell.
-The irreducible representation of $D_{3h}$ gives: $\vec{\Gamma}$= $2A_2^{''}$+$A_1^{'}$+$2E^{'}$+$E^{''}$, with $A_2$$^{''}$ and $E^{'}$ acoustic modes, $A_2^{''}$ IR active, $A_1^{'}$ and $E^{''}$ Raman active, and the other $E^{'}$ both Raman and IR active.
-NL-MoS$_2$ has 9N-3 optical modes: 3N-1 are vibrations along the c axis, and 3N-1 are doubly degenerate in-plane vibrations.
-For rigid-layer vibrations, there are N-1 LBMs along the c axis, and N-1 doubly degenerate shear modes perpendicular to it.
-When N is even, there are 0 Raman active LBMs and $\frac{N}{2}$ doubly degenerate shear modes.
-When N is odd, there are $\frac{N-1}{2}$ LBMs and N-1 doubly degenerate shear modes.
+The lattices dimensions are summarized in Table~\ref{tab:ms2lattice},
+%lattice
+\begin{table}[htb]
+\centering
+\caption{Lattices dimension of \ce{MS2}}\label{tab:ms2lattice}
+\begin{tabular}{lccr}
+\toprule
+         &  & 2H-\ce{MoS2}\cite{Coehoorn1987,Ataca2012} & 2H-\ce{WS2}\cite{Albe2002,Schutte1987} \\
+\midrule
+Lattice constant & a(\AA) & 3.1604 & 3.171 \\
+                 & c(\AA) & 12.295 & 12.359 \\
+Within \ce{MS2} layer & M-3S (\AA)& 2.37  & 2.405   \\
+                      & S-1S (\AA)& 3.11  & 3.14   \\
+Between \ce{MS2} layer& S-3S (\AA)&   & 3.53   \\
+\bottomrule
+\end{tabular}
+\end{table}
 
-direct gap of ML at point K.
+\section{literature to read}
 
-\section{paragraph from word files}
+hydrogen evolution catalysts. \cite{Merki2011}
+
+\ce{WS2} NT FET. \cite{Levi2013}
+
+\ce{WS2} NT transport \cite{Zhang2012c}
+
+Raman substrate dependence \cite{Buscema2013}
+
+WO3-x NPs \cite{Frey2001}
+
+stability of TMS NTs \cite{Seifert2002}
+
+growth mechanism \cite{ZAK2009}
+
+\citeauthor{Ramasubramaniam2011} investigated the band gap tuning in bilayer TMDC materials by applying external $E$ field.
+Similar research has been done for graphene and bilayer boron nitride.
+Semiconductor-metal transition was suggested for \ce{MoS2} and \ce{WS2}, with difference on the CBM and VBM evolution.
+In \ce{MoS2}, the valence-band-splitting cause the A and B excitons in optical absorption measurement.
+Calculation shows that CB and VB are translated toward the Fermi level with increasing E field.
+The external field localized charge along $c$ axis, but delocalized that within the plane normal towards $c$, thereby driving the semi-metal transition.
+It was mentioned that this transition is not anticipated in monolayer \ce{MoS2}.
+It was emphasized that precise band gaps might be different from the author’s results, yet the gap-tuning should be universal.\cite{Ramasubramaniam2011}
+
+Raman conditions: 0.3 mW, 532 nm, 200 sec acquisition time.
 
@@
 
-\ce{WS2} film by sulfurization of W coating on \ce{SiO2}-Si.\cite{Shanmugam2012a}
+\cite{Song2013} ALD \ce{WS2}
 
-8/8/13
+\ce{WS2} Raman.\cite{Zhao2013} \cite{Sekine1980}
 
-\citeauthor{Ramasubramaniam2011} investigated the band gap tuning in bilayer TMDC materials by applying external $E$ field.
-Similar research has been done for graphene and bilayer boron nitride.
-Semiconductor-metal transition was suggested for \ce{MoS2} and \ce{WS2}, with difference on the CBM and VBM evolution.
-In \ce{MoS2}, the valence-band-splitting cause the A and B excitons in optical absorption measurement.
-Calculation shows that CB and VB are translated toward the Fermi level with increasing E field.
-The external field localized charge along $c$ axis, but delocalized that within the plane normal towards $c$, thereby driving the semi-metal transition.
-It was mentioned that this transition is not anticipated in monolayer \ce{MoS2}.
-It was emphasized that precise band gaps might be different from the author’s results, yet the gap-tuning should be universal.\cite{Ramasubramaniam2011}
+phonon dispersion \cite{Ataca2012}
+
+MoS2 optical properties.\cite{Search1979}
+
+FL heterostructure. \cite{Yu2013a}
+
+10/13/13
+
+direct gap of ML at point K.
 
@@
 \end{align}
-
-\begin{figure}[htb]
-\centering
-\includegraphics[width=0.7\textwidth]{ws2_ramsch}
-\caption[CVD system]{Chemical vapor system and \cite{Ghorbani-asl}}
-\label{fig:ws2ramsch}
-\end{figure}

### 2014-02-14 BackMatter/paper.tex
moly articles skim finished

@@
 
+\ce{MoO3} good style. \cite{Siciliano2009} \cite{Abdellaoui1997}
+
+\ce{MoO3}  DFT study \cite{B511044K} \cite{Cora1997} \cite{Sayede2005}
+
+\ce{MoO3} raman \cite{Lee2002}
+
+Charge-density-wave states\footnote{In CDW states, conductivity is non-Ohmic above a threshold electric field} was found in blue bronze \ce{K_{0.3}MoO3}, which can be prepared by electrolytic reduction of \ce{K2MoO4} and \ce{MoO3} melt.\cite{Dumas1983} \ce{K_{0.3}MoO3} is side=centered monoclinic phase, with lattice parameter $a=18.249$\AA, $b=7.561$\AA, $c=9.856$\AA, and $\beta=117.54^\{circ}$ at RT.
+\ce{K_{0.3}MoO3} presents a semiconductor-to-metal transition at 180 K.
+Electrical transport measurements yield an highly anisotropic ratio of DC conductivities of 1:10:1000.
+Along this high conducting axis, metallic reflection behavior is confirmed by optical measurements.
+Therefore, this blue bronze \ce{K_{0.3}MoO3} is known as quasi-1D metal.\cite{Sing1999}
+
+\ce{MoO3}, an alternative interpretation in terms of tetrahedral coordination of Mo atoms is also proposed.
+This is caused by the fact that four of the six surrounding O atom are at distances from 1.67\AA to 1.95\AA, while the remaining two are as far as 2.25 and 2.33\AA.
+This also stress that the \ce{MOO6} octahedra are rather distorted.
+
+visibility of mica thin layer on \ce{SiO2}-Si.
+\cite{Castellanos-gomez2011} 1.5\% contrast is almost at the threshold of human eye sensitivity.
+When the thickness is below 60nm, Raman could not detect mica.
+
+\ce{MoO3} photocatalytic \cite{Chithambararaj2013}
+\ce{MoO3} (010) surface defect. \cite{Chen2001}
+
+photocatalytic experimental setup.\cite{Hupka2006}
+
+mass spectrometry data to extract vapor pressure of \ce{NaxMoO3}.
+
+\ce{MoO3} pseudocapacitor  \cite{Brezesinski2010}
+
+\ce{MoO3} SWNT by hydrothermal method.\cite{Hu2008a} Raman spectra is off compared to single crystal \ce{MoO3}.  Van der Waals interaction and layered structure make NT possible.
+
+TMO review.\cite{Goodenough2013}
+
+\cite{Matar2011} Using electronegativity $\chi$ and chemical hardness $\eta$ to assess electron affinity $E_a$, work function $W_f$, Fermi energy $E_f$ and band gap $E_g$.
+\begin{align}
+\chi &= 0.5(W_f + E_a)\\
+\eta & = 0.5(W_f - E_a)\\
+\end{aligh}
+where I is ionization potential and $E_a$ is electron affinity.
+
+Correlation between optical band gap and formation enthalpy; reaction occurs in order to form compounds with a larger gap.
+$E_g = A \exp(0.34E_{\Delta H^0})$, and A adopts different values depending on the metal elements:
+\begin{itemize}
+\item A=0.8 for s and f block elements,
+\item A = 1 for d block elements,
+\item A = 1.35 for p block elements.
+\end{itemize}
+
+h-\ce{MoO3} \cite{Lunk2010} \cite{Zheng2009}
+
+\ce{MoOx} few layer as hole selective contact in solar cell.\cite{Battaglia2014} 
+\ce{MoO_x} on n-type Si acts as a high workfunction metal (6.6eV), enabling a dopant-free contact and thus junctionless devices.
+
 \section{TMS}
@@
 
-\section{misc}
+\section{CNT}
 
@@
 VSS, growth kinetics,
+BN nanotube capping, zigzag is more stable than armchair. \cite{Menon1999}

### 2014-02-14 ch-tms/tms.tex
moly articles skim finished

@@
 
-\cite{Song2013} ALD \ce{WS2}
+\cite{Song2013} \ce{WO3} by ALD, and sulfurized in Ar and \ce{H2S} (10:1) at 1000 C.
+\ce{WS2} layer No and peak intensities ratio under 633nm excitation is correlated.
+It was found the 2LA/A1g is less than 1 for 1L.
+In supporting info 532 nm Raman spectra, the 2LA/A1g is presumably larger than 1 for 1L.
+\ce{WS2} NT on Si NWs is also demonstrated.
 
@@
 
-phonon dispersion \cite{Ataca2012}
+phonon dispersion $E_{2g}^1(M)$? \cite{Ataca2012}
 
@@
 
-10/13/13
+Water splitting materials should process a band gap larger than 1.4eV, considering both the NHE potential distance and practical application.
+The monolayer \ce{WS2} exhibits direct gap of 1.98 eV.
+Quantum confinement could push the gap separation farther away.
+\cite{wilcoxon1997} \citeauthor{Notley2013} use liquid exfoliation to prepare \ce{WS2} NPs.\cite{Notley2013} Non-ionic surfactant concentration is about 0.1\%w/w.
+Continuously adding surfactant during sonication improves the yield.
+Optimum surface tension is found at about 40 mJ/m$^2$.
+
+\ce{WS2} thin film growth motivated by solar cell.
+\cite{Ennaoui1995a} grew tungsten disulfides film using sulfurization of \ce{WO3} under \ce{N2}/\ce{H2} gas flow.
+The composition was found to be \ce{WS_{2.13}}, and the excess of sulfur lead to p-type conductivity.
+XRD peaks ratio is used as a measure of film orientation, which was found higher for film prepared without an intermediate Ni coating.
+\ce{Ni3S2} phase was found and surfactant-mediated epitaxy is proposed.
+
+\cite{Kang2013} TMDC alloy DFT.
+
+thermoelectric TMDC \cite{Wickramaratne2014}
+
+\ce{CH4N2S} thiourea + \ce{WOx} to \ce{WS2} \cite{Leonard-Deepak2011}
+
+\ce{WS2} by \ce{WCl_n} and \ce{H2S}, raman (632nm) show bulk features\cite{Tenne2008}.
+
+inorganic nanotubes review \cite{Tenne2004} , unsaturated bonds number increases as the size of MS2 sheet decreases.
+
+\cite{Tenne2010} chemical modification of NTs.
+Functional ligand consists of an anchor group that attaches to the NTs surface and a tail which render them soluble in various solvents.
+PTAS functionalized BN nanotube lead to the formation of stable suspensions in aqueous solutions.
+The strong attachment is formed through $\pi-\pi$ interactions.
+ref 49, 416 cm raman on WS2.
+B1u is pressure sensitive.
+
+A1g mode using resonance Raman excitation shows upshift, which is presumably caused by folding induced strains.
+And TEM SEAD reveal 3R symmetry.
+We did not observed this upshift of A1g probably due to the large diameter and few layer involved.
+
+Nanotube growth is relatively independent of substrates and FL layer is closely related to substrate. Film growth could provide some insight into the latter scenario.
 

### 2014-02-15 BackMatter/paper.tex
daily works

@@
 \section{WO3}
+
+An empirical formula to relate the Raman peaks and \ce{W-O} bonding lengths \cite{Hardcastle1995} is
+\begin{equation}\label{eq:wobond}
+\nu = 25823 \exp{-1.902\cdot R}.
+\end{equation}
+And the standard deviation of estimating \ce{W-O} bond distance from Raman stretching wavenumber is $\pm0.034$\AA.
+The observed Raman peaks of \ce{Na5W_{14}O_{44}} phase lies at 965, 943, 913, 808, 786, 778, 765, 695 and 107 cm.
+Multi-peaks Lorentzian fitting is preformed to precisely determine the central maximum.
+Good fitting is obtained, as shown in Fig.~\ref{fig:naworamfit}.
+We then calculated \ce{W-O} bond distance using Eq.~\ref{eq:wobond}, as illustrated in Table~\ref{tab:nawobond}.
+The predicted \ce{W-O} bond length comply very well with the crystallographic value of \ce{Na5W_{14}O_{44}} phase.\cite{Triantafyllou1999a} The 107 peak probably is caused by \ce{Na-O} bond.
+% Na5 raman fitting
+\begin{figure}[htb]
+\centering
+\includegraphics[width=0.6\textwidth]{naxwo_ramfit}
+\caption[\ce{Na5W_{14}O_{44}} Raman fitting]{Multi-peaks Lorentzian fitting on two major peaks region of \ce{Na5W_{14}O_{44}}.
+The peaks sum height difference is caused by different baseline value adopted in each fitting.}
+\label{fig:naworamfit}
+\end{figure}
+
+% W-O bond length
+\begin{table}[htb]
+\centering
+\caption{\ce{W-O} bond length predication}\label{tab:nawobond}
+\begin{tabular}{lccr}
+\toprule
+peak center & length (\AA) & peak center & length (\AA) \\
+\midrule
+694.6 & 1.900 &  808.6 &  1.821 \\
+745.4 & 1.863 &  911.5 &  1.758 \\
+764.4 & 1.850 &  933.0 &  1.745 \\
+778.7 & 1.840 &   943.5 & 1.740 \\
+788.4 & 1.834 &   965.4 & 1.728 \\
+\bottomrule
+\end{tabular}
+\end{table}
 
@@
 
-The observed raman lines of \ce{Na5W_{14}O_{44}} phase lies at 965, 943, 913, 808, 786, 778, 765, 695 and 107 cm.
-The calculated \ce{W-O} bond distance using Eq.~\ref{eq:wobond} fit very well with the crystallographic value of \ce{Na5W_{14}O_{44}}.
-\cite{Triantafyllou1999a} The 107 peak probably arise from \ce{Na-O} bond.
-
 The molecular unit in crystal exhibits different vibrational frequencies from that in solution or gas phases.
@@
 \ce{MoO_x} on n-type Si acts as a high workfunction metal (6.6eV), enabling a dopant-free contact and thus junctionless devices.
+
+We studied the effect of temperature, oxygen partial pressure and growth time towards \ce{MoO3} deposition on glass substrates.
+Each factor is divided into two levels, with T at 700 and 800, \ce{O2} at 1 and 10 sccm, and growth time of 15 and 60 mins.
+We will assign $+$ and $-$ to higher and lower levels, respectively.
+And the morphological variation is summarized in Table~\ref{tab:mo3glass}.
+% glass growth matrix 
+\begin{table}[htb]
+\centering
+\caption{\ce{MoO3} growth on glass}\label{tab:mo3glass}
+\begin{tabular}{lccp{3in}}
+\toprule
+\multicolumn{3}{c}{Growth Conditions} \\
+\cmidrule(l){1-3}
+ Temperature & \ce{O2} & Time & Morphology  \\
+\midrule
+-    &  +   & -  &   \\
+-    &  -   & +  &   \\
++    &  +   & -  &   \\
++    &  +   & -  &   \\
++    &  +   & -  &   \\
++    &  +   & -  &   \\
+\bottomrule
+\end{tabular}
+\end{table}
+
+% droplet position statistics
+\begin{figure}[htb]
+\centering
+\includegraphics[width=0.6\textwidth]{droplets_sta}
+\caption[Droplet position statistics]{Droplet position statistics. On-tip and not-on-tip counts variation with respect to growth time. }
+\label{fig:mo3dropsta}
+\end{figure}
 
@@
 BN nanotube capping, zigzag is more stable than armchair. \cite{Menon1999}
+
+\cite{Chen2013j} To develop large-size single-crystal graphene on dielectric substrates.
+small carbon flow near-equilibrium CVD process.
+Grain size about 10 microns, precursor \ce{CH4} and \ce{H2} (ratio 2.3:50) at 1180 C.
+\ce{SiO2}-Si surface roughness.
+Although the growth substrates (quartz,\ce{SiO2}-Si and \ce{Si3N4}-\ce{SiO2}-Si ) have a complicated stereo network similar to diamond, regular hexagonal G growth is obtained, which indicates the deposition is determined by equilibrium kinetics, and this should be applicable to other 2D materials as well.
+I2D/IG exceeds two on \ce{SiO2}-Si subs (514.5nm), indicating monolayer G.
+armchair (AC) G edge grows faster than zigzag (ZZ) edge.
+
+\cite{Weatherup2013} catalytic graphitization of solid carbon sources.
+catalytic transformation, the source is in solid state, low temperature (less than 600C), 2nm  \ce{Al2O3} by ALD as carbon diffusion barrier.
+amorphous silicon (a-Si), Ni lower the activation barrier ,  tetrahedral amorphous carbon (ta-C).
+
+\cite{Bangert2013} low energy (50eV) ion implantation doping in G.
+Ions penetrate pristine G at energy larger than 100eV.
+Individual substitutional incorporation of B into G lattice is demonstrated.
+1\% doping level was obtained.
+
+\cite{Wu2013b} CVD G on copper. Size of single crystal domain and nucleation site density.

### 2014-02-15 ch-tms/tms.tex
daily works

@@
 The $E_{1g}$ mode, which is an in-plane vibration of only the S atoms, is forbidden in the backscattering Raman configuration.
-In 2H type TMDC, the $A_{1g}$ mode is sensitive to electrostatic doping, while $E_{2g}^1$ mode is sensitive to strain, in which the FWHM of the peaks are indicator of external force quantity.
+In 2H-type TMDC, the $A_{1g}$ mode is sensitive to electrostatic doping, while $E_{2g}^1$ mode is sensitive to strain, in which the FWHM of the peaks are indicator of external force quantity.
 
@@
 
-Raman conditions: 0.3 mW, 532 nm, 200 sec acquisition time.
+Raman conditions: 0.3 mW, 532 nm, 200 sec acquisition time. photon flux = $0.3E-3\times6.242E+18/1.2398/0.532=2.84E15$
 
@@
 The strong attachment is formed through $\pi-\pi$ interactions.
-ref 49, 416 cm raman on WS2.
-B1u is pressure sensitive.
+
+416 cm raman on WS2. B1u is pressure sensitive. \cite{Staiger2012} also studied pressure dependence.
+
+\cite{Zou2007} prepared W/\ce{WS2} core-shell NPs by reaction of tungsten and sulfur under hydrogen atmosphere.
+The shoulder mode under A1g is attributed to LA+TA.
+As pressure increase from 0GPa to 18GPa, these two bands, both shifting to higher wavenumbers, first separate and then recombine.
+It was assumed the compression mainly occurs in c axis, so the stiffening of A1g is anticipated.
 
@@
 
-direct gap of ML at point K.
+\cite{M2013} temperature dependent of ML \ce{WS2}.
+Interestingly in this report 2LA/A1g (514 nm) seems less than unit.
+The spectra were obtain from mechanically exfoliated \ce{WS2} lying on 300 \ce{SiO2}-Si substrate.
+When the temperature increase from 77K to 623K, A1g shift from 420 to 416.5 cm.
+
+direct gap of ML at corner of BZ, point K.
 

### 2014-02-16 foo.tex
git lynda

@@
 
+git clean % remove untracked files
+
+navigating commit tree
+tree-ish
+
+parent commit: HEAD^, HEAD~1, HEAD~2,
+
+git ls-tree master or HEAD %list commit tree
+
+git log --oneline 
+git log --author=""
+git log --since=
+git log --graph --all --decorate --oneline
+
+git show SHA
+
+git diff HEAD~3..HEAD % -b ignore space changes,
+
+%use branch to try new ideas, and isolate features
+compare branches
+git diff --color-words master..develop
+
+git branch --merged % to see if current branch include previous contents
+
+rename branches:
+
+git branch -m develop newname
+
+git merge --no-ff branch % no fast-forward merge
+
+true merge  %recursive strategy
+
+resolving conflicts: 
+abort: git merge --abort
+manually: 
+merge tool:
+
+stashing: store temporally 
+git stash save ""
+git stash list 
+git stash show -p stash@{0}
+git stash apply or pop stash@{0}% pop, no longer in drawer, apply, make a copy from the drawer
+
+git stash drop stash@{0} 
+git stash clear % clear all stashes
+
+% remotes 
+git push -u %
+
 \end{lstlisting}

### 2014-02-16 foo.tex
finish lynda tutorial on git

@@
 % remotes 
-git push -u %
+git push -u % -u = --set-upstream
+git branch -r % show remote branch
+git branch -a % show all branches
+
+fetch % synch origin/master with remote 
+fetch does not merge origin/master into local master branch
+
+git pull = git fetch + git merge
+
+git branch no_track origin/nontrakcing % starting a new branch from origin/nontracking
+
+git show HEAD
+git show branch
+
+git log -p onebranch..another
 

### 2014-02-18 BackMatter/paper.tex
tms FL detail reading

@@
 
+Raman spectra arise from the inelastic light scattering of optical phonons. In back scattering geometry, the phonon wavevector
+$q = 4\pi\frac{n}{\lambda}$.
+The refractive index of \ce{WS2} at 532nm is about.
+Compared to the size of Brillouin zone ($\pi/a = 10^{10}m^{-1}$), resonant Raman could or could not probe phonon at $M$ point.
+
+In centrosymmetric crystals, the vibrational modes must either have even (Raman-active) or odd (IR-active) parity under inversion, which is known as rule of mutual exclusion.
+When this symmetry is broken, some modes may be simultaneously IR and Raman active.
+
+inelastic neutron scattering to study the non-zone center LA mode.
+Zone-edge scattering can occur due to zone-folding process.
+The formation of superlattice could activate formerly inactive zone-edge phonons.
+The folding of BZ along $\Gamma-M$ would cause the M point to coincide with $\Gamma$ point, so LA(M) phonons would become Raman active in a first-order process.
+
 multipeak Lorentzian fitting. 270 to 410 cm

### 2014-02-18 ch-tms/tms.tex
git lynda
tms FL detail reading

@@
 
-In this chapter, we will first review the growth of \ce{MS2} nanotubes and \ce{MS2} few layer structures.
+In this chapter, we will first review the growth of \ce{MS2} nanotubes and few layer structures.
 Then we summarize the Raman spectroscopy results on NTs and FL.
@@
 
-\section{literature review}
+\section{Literature review}
 
 Shortly after the the discovery of carbon nanotube (CNT) in 1991,\cite{Iijima1991} its transition metal dichalcogenides (TMDC) counterparts (\ce{WS2}) was synthesized in 1992.\cite{Tenne1992} In the following decade, other TMDC and several metal oxides nanotubes were demonstrated as well.
-\citeauthor{Rao2003} did an excellent job to review these inorganic nanotubes.\cite{Rao2003} Here we just recapitulate the main categories of synthesis methods.
+\citeauthor{Rao2003} did an excellent work to review these inorganic nanotubes.\cite{Rao2003} Here we just recapitulate the main categories of synthesis methods.
 \begin{enumerate}
@@
 Except the aforementioned methods, another important reaction in CVD domain is
-\[
+\begin{equation}\label{eq:mclns}
 \cee{MoCl5(WCl6) + S \rightarrow MoS2(WS2) + S2Cl2}.
-\]
+\end{equation}
 This reaction has been explored by several authors,\cite{Stoffels1999} and could be used under atmospheric pressure.\cite{Li2004a}
 
-All these methods can be applied to the growth of TMDC few layer structures, either directly or with some modification or combination, as we shall discuss later.
+All these methods can be applied to the growth of TMDC few layer structures, either directly or with some modification, as we shall discuss later.
 Among all the members of TMDC nanotubes, \ce{WS2} and \ce{MoS2} NTs are probably the most well investigated.\cite{Homyonfer1997,Tenne1998,Frey1998,Frey1999,Rothschild2000,Zak2000} The reaction mechanism of \ce{WO3} with \ce{H2}/\ce{H2S} has been thoroughly studied \cite{Feldman1998} and high yield synthesis approach has been established.\cite{Margolin2004} For precursor of \ce{WO3} NPs, it was found that the simultaneous reduction and sulfurization is essential for encapsulation of fullerene like \ce{WS2} structures from the oxide nanoparticles.
 During the surfurization process, remaining oxide core is gradually reduced and transformed into an ordered superlattice of $\{ 001 \}$ CS planes.
-It is worth noting that \ce{MS2} can be prepared by direct sulfurization from its oxides phase, but reaction \cee{MO3 + Se \rightarrow MSe2} will not proceed unless introducing other reducing agents, such as \ce{H2}.\cite{Tsirlina1998} This fact highlights that sulfur is rather radical at elevated temperature.
+Further reaction will consume up the \ce{WO_x} core, leaving multi-walled \ce{WS2} NTs only.
+For precursor of \ce{WO3} nanowires, \citeauthor{Feldman1996} proposed that TMDC nanotubes growth began with the reduced \ce{WO3} phases, in particular \ce{W_{18}O_{49}}.\cite{Feldman1996} It is worth noting that \ce{MS2} can be prepared by direct sulfurization from its oxides phase, but reaction \cee{MO3 + Se \rightarrow MSe2} will not proceed unless introducing other reducing agents, such as \ce{H2}.\cite{Tsirlina1998} This fact highlights that sulfur is rather radical at elevated temperature.
 
-\citeauthor{Zhu2000} performed a detailed morphological and structural analysis on \ce{WS2} NT synthesized using \ce{WO_{3-x}} NWs and \ce{H2S}.
-\cite{Zhu2000} Sulfur vacancy was found on the outer wall of NT.
+\citeauthor{Zhu2000} performed a detailed morphological and structural analysis on \ce{WS2} NT synthesized using \ce{WO_{3-x}} NWs and \ce{H2S}.\cite{Zhu2000} Sulfur vacancy was found on the outer wall of NT.
 The tips exhibits various structures.
-Open-ended can be observed, more frequently than that in CNT, which is often sealed.
+Open-ended can be observed, more frequently than that in carbon nanotubes (CNTs), which is often sealed.
 \citeauthor{Zhu2000} suggested this open-ended tubes resulted from continuous growth on other nanotubes.
@@
 Flat caps often dominates.
-\citeauthor{Feldman1996} proposed that TMDC nanotubes growth began with the reduced \ce{WO3} phases, in particular \ce{W_{18}O_{49}}.\cite{Feldman1996} \citeauthor{Zhu2000} maintained that this oxide-to-sulfides mechanism might apply to closed caps only, not to those open ended tubes.\cite{Zhu2000} TEM diffraction analysis could distinguish the chirality of NTs, as demonstrated by CNT \cite{Zhang1993} and \ce{MoS2}\cite{MARGULIS1996}.
-\ce{WS2} NT chirality revealed by TEM SEAD show armchair NTs dominates.
-\citeauthor{Sloan1999} investigated tungsten oxides structures incorporated in \ce{WS2}.\cite{Sloan1999} The encapsulated \ce{WO_x} cores often exhibit \ce{W3O8} and \ce{W5O_{14}} phases, both of which belong to the \ce{W_nO_{3n-1}} homogenous series, arising as a result of crystallographic shearing (CS) planes.\cite{Miyano} Some \ce{WO_x} cores show oxygen vacancy instead of CS planes, leading to prominent streaking in SEAD patterns.
+\citeauthor{Zhu2000} maintained that this oxide-to-sulfides mechanism might apply to closed caps only, not to those open ended tubes.\cite{Zhu2000} TEM diffraction analysis could distinguish the chirality of NTs, as demonstrated by CNT \cite{Zhang1993} and \ce{MoS2}\cite{MARGULIS1996}.
+\ce{WS2} NT chirality revealed by TEM SAED show armchair NTs dominates.
+\citeauthor{Sloan1999} investigated tungsten oxides structures incorporated in \ce{WS2}.\cite{Sloan1999} The encapsulated \ce{WO_x} cores often exhibit \ce{W3O8} and \ce{W5O_{14}} phases, both of which belong to the \ce{W_nO_{3n-1}} homogenous series, arising as a result of crystallographic shearing (CS) planes.\cite{Miyano} Some \ce{WO_x} cores show oxygen vacancy instead of CS planes, leading to prominent streaking in SAED patterns.
 Although high yield growth method of \ce{WS2} has been available, the extent to which one can control the NT configuration is still limited, i.e., single-walled NT has not been routinely synthesized and the electronic properties can only be predicted theoretically.
@@
 \citeauthor{Zibouche2012} reached the same conclusion on \ce{WS2} SWNT.\cite{Zibouche2012} It was also found band gaps of armchair and zigzag NTs increase with diameter, going from values close to bulk and approaching that of  monolayer, and for a given tube diameter, $E_g$ of zigzag NTs are larger than those of armchair NTs.
-This difference presumably vanishes when the tube diameter exceeds 100 nm.
+This difference presumably vanishes when nanotube diameter exceeds 100 nm.
 
 Parallel with the scenario of CNT and graphene, TMDC few layer structures attracts intensive research efforts recently.
-These unfolded TMDC nanotubes exhibit many appealing features, i.e., indirect-to-direct band gap transition,\cite{Splendiani2010} valley electronics, and become a promising candidate in energy harvesting, optoelectronics.
-For scientific research purpose, exfoliation by liquid \cite{Smith2011} or mechanical methods \cite{Lee2010a} can provide plenty materials.
-Yet considering the integration into current microelectronic process, CVD synthesis of TMDC FL is desired, which hold the greatest potential for high yield production of \ce{MS2}.
+These unfolded TMDC nanotubes exhibit many appealing features, i.e., indirect-to-direct band gap transition,\cite{Splendiani2010} valley electronics, and become a promising candidate in energy harvesting, optoelectronics and photocatalytic activity.
+For scientific research purpose, exfoliation by liquid \cite{Smith2011} or mechanical methods \cite{Lee2010a} can provide sufficient materials.
+Yet considering the integration into current microelectronic process, CVD synthesis of TMDC FL is highly desired, which stills hold the greatest potential for high yield production of \ce{MS2}.
 So in this work we focus on the CVD-based methods.
 We will review literature to date on both \ce{WS2} films and few layer structures, and highlight several typical investigations using different type synthesis method, as summarized in Table~\ref{tab:tmsgrowth}.
+We stress that the synthesis of NTs is relevantly independent of substrates, which is in sharp contrast to the scenario of few layer growth.
+The \ce{WS2} nucleation and interaction with substrates play dominant roles in the growth of FL structures.
+This lead us to focus on the \ce{WS2} films growth, which presumably could provide valuable insight into the nucleation process on various substrates.
 
@@
 More important, \ce{MoS2} basal plane orientation can be parallel to substrate when the thickness was smaller than 50 nm.
-\citeauthor{Regula1997} studied the Ni-W-S phase diagram and the role of Ni layer in promoting \ce{WS2} film growth from amorphous \ce{WS3}.\cite{Regula1997} \emph{In-situ} TEM analysis confirmed the formation of \ce{NiS_x} droplets and lateral growth of \ce{WS2} from these droplets.
-\cite{Regula1998} Recently, it has been shown that direct sulfurization of W coating (20nm) at 750 \si{\degreeCelsius} on \ce{SiO2}-Si can also produce \ce{WS2} film.\cite{Shanmugam2012a} However, the film is of bulk in nature.
+\citeauthor{Regula1997} studied the Ni-W-S phase diagram and the role of Ni layer in promoting \ce{WS2} film growth from amorphous \ce{WS3}.\cite{Regula1997} \emph{In-situ} TEM analysis confirmed the formation of \ce{NiS_x} droplets and lateral growth of \ce{WS2} from these droplets.\cite{Regula1998} Recently, it has been shown that direct sulfurization of W coating (20nm) at 750 \si{\degreeCelsius} on \ce{SiO2}-Si can also produce \ce{WS2} film.\cite{Shanmugam2012a} However, the film is of bulk in nature.
 This could be explained by the study of \citeauthor{Genut1992} towards \ce{WS2} growth on various substrates.\cite{Genut1992} We summarize the main results in Table~\ref{tab:ws2subs}.
@@
 
-\textbf{\ce{MS2} FL} For \ce{MoS2}, the reaction mechanism of \ce{MoO3} to \ce{MoS2} was studied by \citeauthor{Weber1996}.\cite{Weber1996} This study provided guideline for the recent syntheses of \ce{MoS2} by sulfurization of \ce{MoO3}.
-\cite{Lin2012,Lee2012b,Liu2012a} We assume similar insight could be gained from the aforementioned growth of \ce{WS2} films.
+\textbf{\ce{MS2} FL} For \ce{MoS2}, the reaction mechanism of \ce{MoO3} to \ce{MoS2} was studied by \citeauthor{Weber1996}.\cite{Weber1996} This study provided guidelines for the recent syntheses of \ce{MoS2} by sulfurization of \ce{MoO3}.\cite{Lin2012,Lee2012b,Liu2012a,Najmaei2013} Similar studies on sulfurization of \ce{WO3.H2O} to \ce{WS2} and decomposition of \ce{(NH4)2WO2S2} were also reported.\cite{VanderVlies2002,VanderVlies2002a} In combination with the knowledge from \ce{WS2}, we compare those insight with several recent reports on \ce{WS2} FL.
 \citeauthor{Cong2013} prepared monolayer \ce{WS2} on 300nm \ce{SiO2}-Si by sulfurization of \ce{WO3} powders in a one-end sealed tube.\cite{Cong2013} It was suggested that pre-cleaning the inner tube by IPA and DI water could effectively increase the pressure of vapor source.
@@
 Sulfurization mechanism study of \ce{WO3} suggested \ce{W^{6+}} cannot be directly reduce to \ce{W^{4+}} in \ce{WS2}.\cite{VanderVlies2002,VanderVlies2002a} Tungsten oxysulfides was necessary as the intermediate phase.
-Other chalcogenide has also been synthesized using this one-end sealed layout.\cite{Mukherjee2013} \citeauthor{Zhang2013h} synthesized \ce{WS2} on sapphire using \ce{WO3} powder and sulfur as precursor under 900 \si{\degreeCelsius}.
-\cite{Zhang2013h} Ar slightly mixed with \ce{H2} is used to tailor the shape of \ce{WS2} flakes.
+Other chalcogenide has also been synthesized using this one-end sealed layout.\cite{Mukherjee2013}
+
+\citeauthor{Peimyoo2013} prepared \ce{WS2} on \ce{SiO2}-Si using \ce{WO3} powder and sulfur at 800 \si{\degreeCelsius}, aiming at the light emission studies to clarify several contradictory reports.\cite{Peimyoo2013} Uniform PL intensity was found on the triangular \ce{WS2} flakes, in contrast to previous edge enhanced PL.\cite{Berkdemir2013} Raman spectra (532nm) fit includes $E_{2g}^1(M)$ mode at 343 cm$^{-1}$, according to the phonon dispersion calculation \cite{Molina-Sanchez2011} and experimental observation\cite{Zeng2013,Zhao2013,Lee2013}.
+However, none of these experimental reports specifically mentioned $E_{2g}^1(M)$ mode.
+Tentative assignments of multi-phonon bands are summarized in supporting discussion of Ref\cite{Zhao2013}.
+As to the growth setup, similar tube furnace as in Ref \cite{VanderZande2013} and \cite{Najmaei2013} was used.
+To gain additional wisdom on \ce{MoS2} growth, we thus summarize the growth strategies in Ref \cite{VanderZande2013} and \cite{Najmaei2013} as following.
+\citeauthor{VanderZande2013} prepared \ce{MoS2} on 285nm \ce{SiO2}-Si using \ce{MoO3} and S as precursors.\cite{VanderZande2013} In contrast to the seeding method adopted in ref\cite{Lee2013,Lee2012b}, the author stress the importance of carefully cleaned substrates\footnote{acetone, 2hrs in \ce{H2SO4} and \ce{H2O2} (3:1) and 5 mins oxygen plasma} and minimum exposure of precursor to air.\footnote{APCVD, 105 \si{\degreeCelsius} for 4hrs, 700 \si{\degreeCelsius} hold for 5mins, and 10 sccm \ce{N2} within 2 inch tube.
+rapid cooling from 570 \si{\degreeCelsius}} Dirty substrates or old precursors will lead to hexagonal, 3-point star or irregular polycrystalline structures.
+The growth setup is similar to those in Ref\cite{Lee2012b}.
+The substrate and \ce{MoO3} source distance is critical in determining the growth density.
+As a comparison, we briefly mention the synthesis strategy in Ref\cite{Lee2013,Lee2012b} as well, where PTAS treated substrate is found to promote the deposition, while KCl treated substrates did not, and small carrier gas flow is preferred (1 sccm \ce{N2}).
+We also notice that the \ce{MoS2} flakes morphology seems more uniform in Ref\cite{VanderZande2013} than that in Ref\cite{Lee2012b}.
+On the other hand, \citeauthor{Najmaei2013} also demostrated \ce{MoS2} FL growth by sulfurization of \ce{MoO3} nanoribbons.\cite{Najmaei2013} The ribbons is applied by dispersion and meant to control the source amount.
+It was found the diffusion of vapor \ce{MoO_{3-x}} is rate-limiting step in \ce{MoS2} growth.
+This means the amount of source is critical in successful synthesis.
+The nucleation event is more frequently observed at subs edges, scratches or rough surface.
+Step edges is then intentionally created to facilitate the nucleation.
+As to the growth dynamics, it was postulated the oxisulfides(\ce{MoOS2} Raman spectra found), as intermediate phase, diffuse across the bare substrates and form triangular domains upon further sulfurization.
+The optimal growth conditions are 800-850 C, 700Torr, and sufficient sulfur.
+We then conjecture that the substrate cleaning in ref\cite{Peimyoo2013} should be similar to that in ref\cite{VanderZande2013}, yet the source-to-substrate layout and growth pressure are still needed to be optimized with respect to our current apparatus.
+
+\citeauthor{Zhang2013h} synthesized \ce{WS2} on sapphire (0001) using \ce{WO3} powder and sulfur as precursor under 900 \si{\degreeCelsius}.\cite{Zhang2013h} Ar slightly mixed with \ce{H2} is used to tailor the shape of \ce{WS2} flakes.
 It was found the source substrate distance play an important role in determining the morphology of as-grown flakes.
-\citeauthor{Peimyoo2013} prepared \ce{WS2} on \ce{SiO2}/Si using \ce{WO3} powder and sulfur at 800 \si{\degreeCelsius}, aiming at the light emission studies to clarify several contradictory reports.\cite{Peimyoo2013} Uniform PL intensity was found on the triangular \ce{WS2} flakes, in contrast to previous edge enhanced PL.\cite{Berkdemir2013} It is worth noting that the growth conditions in Ref \cite{Peimyoo2013} and \cite{Zhang2013h} are basically identical except the usage of substrate.
+The lattice mismatch between \ce{Al2O3} and \ce{WS2} is .
+The edge termination is not well studied.
+Raman spectra indicate a universal down-shift of $A_{1g}$ peak (1L from 418 on \ce{SiO2}-Si to 416.4 on sapphire).
+PL signal on \ce{SiO2}-Si is stronger than on sapphire.
+The visibility of \ce{WS2} on \ce{Al2O3} is poor.
+No 1L vs nL statistic is available.
+FET on/off ratio is about 100, indicating low mobility.
+The other conditions includes 880C, 90mm source-to-substrate distance, 1 inch quartz tube, and LBM furnace.
+The growth conditions are probably adopted from ref\cite{Huanga2013}(arxiv:1304.7365).
+
+\cite{Cong2013} A direct gap of $\sim 2eV$ at the corners of BZ is formed in 1L \ce{WS2}, The subs are thoroughly cleaned.
+It was mentioned that separate sulfur heating improved the PL uniformity.
+The apex of triangles could be active site of nucleation, \ce{WS_{2+x}} formation is confirmed by secondary ion mass spectrometry.
+Growth on bottom piece show the multiple domain flakes occurs at initial stage of the growth, starting from \ce{WO3} particles.
+
+It is worth noting that the growth conditions in Ref \cite{Peimyoo2013} and \cite{Zhang2013h} are basically identical except the usage of substrate.
 The flake size on sapphire seem larger than that on \ce{SiO2}/Si, either due to the nucleation barrier difference or the amount of growth vapor and growth time.
-
 In studying the growth of TMDC, two issues dominate: one is the reaction of precursor, the other is the surface energy status of receiving substrates.
@@
 \addlinespace[0.5em]
-\ce{WS2} ML \cite{Cong2013} & \ce{WO3} powder on sub1 covered by sub2, sulfur & 750 \si{\degreeCelsius} hold for 5mins, one-end sealed inner tube, 100 sccm Ar\\
+\ce{WS2} ML \cite{Cong2013} & 1mg \ce{WO3} powder on \ce{SiO2}-Si covered by another sub, $d\sim3mm$, sulfur & 750 \si{\degreeCelsius}, slow heating, hold for 5mins, one-end sealed inner tube, 100 sccm Ar\\
 \addlinespace[0.5em]
-\ce{WS2} ML \cite{Zhang2013h} & \ce{WO3} powders, sulfur (separate heating) & 900 \si{\degreeCelsius}, sapphire subs, 225mTorr, Ar 80 sccm and \ce{H2} 10 sccm, growth time 60mins, adjusting precursor and sapphire distance changing the coverage of \ce{WS2}, tube diameter: 1 inch\\
+\ce{WS2} ML \cite{Zhang2013h} & \ce{WO3} powders, sulfur (separate heating) & 900 \si{\degreeCelsius}, sapphire subs, 225mTorr, Ar 80 sccm and \ce{H2} 10 sccm, growth time 60mins, adjusting precursor and sapphire distance changing the coverage of \ce{WS2}, tube diameter: 1 inch.
+55 $\mu m$ triangular flakes\\
 \addlinespace[0.5em]
-\ce{WS2} ML \cite{Peimyoo2013} & 1mg \ce{WO3} powders, sulfur,  & \ce{SiO2}/Si subs.
+\ce{WS2} ML \cite{Peimyoo2013} & 1mg \ce{WO3} powders, sulfur  & \ce{SiO2}/Si subs.
 Recipe A: 200mg S,RT-550, Sulfur begin to melt, 550-800, 5K/min, hold 10mins, 200 sccm Ar.
 Recipe B: sulfur separated heated at 250 \si{\degreeCelsius}.
-Total pressure: maybe atmospheric, tube diameter: 2 inch \\
-\ce{WS2} FL \cite{Lee2013}  & 1g \ce{WO3} powders, sulfur,subs treated with PTAS and gentle gas blow & substrate facing down, APCVD, 900 \si{\degreeCelsius}, 5mins, 5 sccm Ar, fast heating. \\
+Total pressure: maybe atmospheric, tube diameter: 2 inch.
+5 $\mu m$ triangular flakes \\
+\ce{WS2} FL \cite{Lee2013}  & 1g \ce{WO3} powders, sulfur, \ce{SiO2}-Si subs treated with PTAS \ce{C24H12K4O8} and gentle gas blow & substrate facing down, APCVD, 800 \si{\degreeCelsius}, 5mins, 5 sccm Ar, fast heating.
+\\
 \addlinespace[0.5em]
@@
 \end{landscape}
+
+In Ref\cite{Zeng2013}, single crystal \ce{WS2} growth using \ce{I2} transport was described in supporting info.
+
+\cite{Lee2013} PTAS \ce{C24H12K4O8}\footnote{http://www.chemspider.com/Chemical-Structure.24771386.html} treated substrates.
+Tiny ($\sim 200$nm) seeds is found on treated surfaces.
+Layer growth and nucleation.
 
@@
     $2LA(M)+2E_{2g}^2(M)$    &      &                              & 381          &  381   \\
-     LA + TA \cite{Sourisseau1991} or $B_{1u}$\cite{Staiger2012}  &      &       &   &  416 \\
+     LA + TA \cite{Sourisseau1991} or $B_{1u}(\Gamma)$\cite{Staiger2012}  &      &       &   &  416 \\
           $A_{1g}(\Gamma)$   &      & 417.9                        & 416\textsuperscript{\emph{b}} &  421\\
@@
 
+The $A_{1g}$ and $E_{2g}^1$ intensities ratio exhibit reverse behaviors under 532 and 632 nm excitation.
+This is caused by the different cross-section enhancement for a specific excitation condition.
+The A and B excitonic absorption in \ce{WS2} mainly arise from the $d_{xy}$ and $d_{x^2 - y^2}$ states to $d_{z^2}$ states of tungsten atoms.
+Thus, electrons excited by 633 nm laser have a character of tungsten $d_{z^2}$ orbitals aligned along the c axis perpendicular to \ce{WS2} basal plane.
+Since $A_{1g}$ mode involve out of plane displacement along c axis, $A_{1g}$ phonons could couple more strongly with $d_{z^2}$ states than that of $E_{2g}^1$ phonons.
+As a result, $A_{1g}$ mode is stronger than $E_{2g}^1$ mode at 633 nm resonance.\cite{Zhao2013} However, the reverse effect for 532 nm excitation could not be well explained using above argument.
+This may be caused by electron-phonon coupling with other inter-band transition electrons.
+416 peak was prevously assumed to be a combination of LA and TA phonons at K points.
+recent theoretical investigation suggest this peak is $B_{1u}$ mode\cite{Molina-Sanchez2011,Ataca2012}, which is the Davydov doublet with  $A_{1g}$ mode.
+
 Raman conditions: 0.3 mW, 532 nm, 200 sec acquisition time. photon flux = $0.3E-3\times6.242E+18/1.2398/0.532=2.84E15$

### 2014-02-18 BackMatter/paper.tex
tms further adjusted

@@
 \section{TMS}
+\cite{Cong2013} A direct gap of $\sim 2eV$ at the corners of BZ is formed in 1L \ce{WS2}, Growth on bottom piece show the multiple domain flakes occurs at initial stage of the growth, starting from \ce{WO3} particles.
 
-Raman spectra arise from the inelastic light scattering of optical phonons. In back scattering geometry, the phonon wavevector
-$q = 4\pi\frac{n}{\lambda}$.
-The refractive index of \ce{WS2} at 532nm is about.
-Compared to the size of Brillouin zone ($\pi/a = 10^{10}m^{-1}$), resonant Raman could or could not probe phonon at $M$ point.
+In Ref\cite{Zeng2013}, single crystal \ce{WS2} growth using \ce{I2} transport was described in supporting info.
+\ce{C24H12K4O8}\footnote{http://www.chemspider.com/Chemical-Structure.24771386.html}
 
@@
 
-Raman technique could provide valuable insight into the structures of CNT, i.e., tube diameter by assigning the RBMs (radial breathing modes) and G peaks position.\cite{Bonaccorso2013}
-
- Raman spectroscopy qualifies as an excellent tool to monitor tensile tests of TMDs, both in 2D and in tubular forms.
 For 2D materials, strain may be induced by elongation of an appropriate substrate, e.g.

### 2014-02-18 ch-tms/tms.tex
tms further adjusted

@@
 So in this work we focus on the CVD-based methods.
-We will review literature to date on both \ce{WS2} films and few layer structures, and highlight several typical investigations using different type synthesis method, as summarized in Table~\ref{tab:tmsgrowth}.
+We will review literatures to date on both \ce{WS2} films and few layer structures, and highlight several typical investigations using different type synthesis method, as summarized in Table~\ref{tab:tmsgrowth}.
 We stress that the synthesis of NTs is relevantly independent of substrates, which is in sharp contrast to the scenario of few layer growth.
@@
 More important, \ce{MoS2} basal plane orientation can be parallel to substrate when the thickness was smaller than 50 nm.
+\cite{Ennaoui1995a} grew tungsten disulfides film using sulfurization of \ce{WO3} under \ce{N2}/\ce{H2} gas flow.
+The composition was found to be \ce{WS_{2.13}}, and the excess of sulfur lead to p-type conductivity.
+XRD peaks ratio is used as a measure of film orientation, which was found higher for film prepared without an intermediate Ni coating.
+\ce{Ni3S2} phase was found and surfactant-mediated epitaxy is proposed.
 \citeauthor{Regula1997} studied the Ni-W-S phase diagram and the role of Ni layer in promoting \ce{WS2} film growth from amorphous \ce{WS3}.\cite{Regula1997} \emph{In-situ} TEM analysis confirmed the formation of \ce{NiS_x} droplets and lateral growth of \ce{WS2} from these droplets.\cite{Regula1998} Recently, it has been shown that direct sulfurization of W coating (20nm) at 750 \si{\degreeCelsius} on \ce{SiO2}-Si can also produce \ce{WS2} film.\cite{Shanmugam2012a} However, the film is of bulk in nature.
@@
 Intermediate phase \ce{WO_yS_{2-y}} and \ce{WS_{2+x}} is proposed in the growth mechanism.
+The apex of triangles could be active site of nucleation, \ce{WS_{2+x}} formation is confirmed by secondary ion mass spectrometry.
 Possible thick \ce{WS_{2+x}} flakes decompose subsequently, leading to ML \ce{WS2}.
+The subs are thoroughly cleaned.
+It was mentioned that separate sulfur heating improved the PL uniformity.
 Sulfurization mechanism study of \ce{WO3} suggested \ce{W^{6+}} cannot be directly reduce to \ce{W^{4+}} in \ce{WS2}.\cite{VanderVlies2002,VanderVlies2002a} Tungsten oxysulfides was necessary as the intermediate phase.
@@
 It was found the source substrate distance play an important role in determining the morphology of as-grown flakes.
-The lattice mismatch between \ce{Al2O3} and \ce{WS2} is .
+The lattice mismatch between \ce{Al2O3} (4.785\AA) and \ce{WS2} (3.153 \AA) is .
 The edge termination is not well studied.
@@
 
-\cite{Cong2013} A direct gap of $\sim 2eV$ at the corners of BZ is formed in 1L \ce{WS2}, The subs are thoroughly cleaned.
-It was mentioned that separate sulfur heating improved the PL uniformity.
-The apex of triangles could be active site of nucleation, \ce{WS_{2+x}} formation is confirmed by secondary ion mass spectrometry.
-Growth on bottom piece show the multiple domain flakes occurs at initial stage of the growth, starting from \ce{WO3} particles.
+It is worth noting the flake sizes on sapphire \cite{Zhang2013h} seems larger than that on \ce{SiO2}/Si\cite{Peimyoo2013}, either due to the nucleation barrier difference or the amount of growth vapor and growth time.
+The flake sizes in ref \cite{Cong2013} is not quite uniform, though it could be even larger than that on sapphire \cite{Zhang2013h}.
+One common feature of aforementioned investigations is growth occurs on bare substrates and no catalyst or seeding promoter is employed.
+While there is another synthesis approach \cite{Lee2013,Ling2014} exclusively focusing on using seeding promoter.
+\citeauthor{Lee2013} obtained \ce{MoS2} and \ce{WS2} FL on PTAS-treated substrates (\ce{C24H12K4O8}), where tiny ($\sim 200$nm) seeds were found under AFM.
+More recently, \citeauthor{Ling2014} systemically investigated the role of seeding promoter in facilitating the nucleation of \ce{MoS2} monolayers.\cite{Ling2014} It was found various aromatic molecules are effective yet inorganic nanoparticles are not.
+The mechanism of thin film growth depends on the surface energy and chemical potentials of the deposited layers and their substrates.
+Layer growth is preferred when surface adhesive force is stronger than adatoms cohesive force.
+Seeding promoter probably lowered the surface energy by wetting, thus provided heterogenous nucleation sites.
+Continuous \ce{MoS2} monolayer is obtained by evaporating 2 \AA  \ce{F16CuPc} on desired receiving substrates.
+In each growth, about $10^{-10}$mol PTAS was applied onto \ce{SiO2}-Si, which was rendered hydrophilic and gentle gas blow to distribute the solution evenly.
 
-It is worth noting that the growth conditions in Ref \cite{Peimyoo2013} and \cite{Zhang2013h} are basically identical except the usage of substrate.
-The flake size on sapphire seem larger than that on \ce{SiO2}/Si, either due to the nucleation barrier difference or the amount of growth vapor and growth time.
-In studying the growth of TMDC, two issues dominate: one is the reaction of precursor, the other is the surface energy status of receiving substrates.
+In short summary, we stress that there are several key factors in successfully synthesizing \ce{WS2} FL: 
+\begin{itemize}
+\item \ce{WO3} powder size distribution and absolute amount (0.69g \ce{WO3} in 10mL acetone or IPA, inspired by the \ce{MoO3} nanoribbons usage)
+\item Sulfur amount and heating method to ensure a constant sulfur-rich environment
+\item \ce{WO3} powder source to substrate distance, which is coupled to pressure and carrier gas flow in determining the transport (atmospheric, 3-5mm)
+\item temperature ramping and growth time (750-800C, 3-10mins)
+\item 300nm-\ce{SiO2}-Si substrate to make OM flakes identification easier
+\end{itemize}
+
 % CVD TMDC
@@
 
-In Ref\cite{Zeng2013}, single crystal \ce{WS2} growth using \ce{I2} transport was described in supporting info.
+\section{Raman spectra}
 
-\cite{Lee2013} PTAS \ce{C24H12K4O8}\footnote{http://www.chemspider.com/Chemical-Structure.24771386.html} treated substrates.
-Tiny ($\sim 200$nm) seeds is found on treated surfaces.
-Layer growth and nucleation.
+In this section, we will discuss previous studies using Raman to characterize \ce{MS2} films, nanotubes, and FL structures.
+In each morphology, one or two key points that we are interested will be highlighted for study in this thesis.
+The previous Raman efforts on \ce{MS2} film, especially the one using resonant conditions, provided critical insight into the electronic structure and lattice dynamics of these TMDC layered materials.
+We will then gather the Raman knowledge and compare it to the one obtained on nanotube and FL structures.
+For \ce{WS2} NTs, we will focus on the asymmetry of $A_{1g}$ mode and its origin.
+And for \ce{WS2} FL structures, we will summarize the finger print of Raman spectra on layer number dependence, and make some attempts on analysis the resonant Raman profiles of \ce{WS2}.
 
-\section{Raman spectra}
+We notice that Raman technique already proves to be extreme useful in characterizing CNT and graphene, i.e., tube diameter by assigning the RBMs (radial breathing modes) and G peaks position.\cite{Bonaccorso2013} And Raman spectroscopy also qualifies as an excellent tool to monitor tensile features of TMDCs in both 2D and tubular forms.\cite{Tang2013} Nevertheless, we will not exhaust these progress in this work.
+
+Raman spectra arise from the inelastic light scattering of optical phonons. In back scattering geometry, the phonon wavevector
+$q = 4\pi\frac{n}{\lambda}$.
+The refractive index of \ce{WS2} at 532nm is about.
+Compared to the size of Brillouin zone ($\pi/a = 10^{10}m^{-1}$), resonant Raman could or could not probe phonon at $M$ point.
 
@@
 First we want to emphasize that in few layer structures, \ce{MoS2} with odd layers belong to different space group from that of even layers.
-Bulk MoS$_2$ and 2L-MoS$_2$ belong to the space group P6$_3$/$_{mmc}$ (point group D$_{6h}$) There are 18 normal vibration modes.
+Bulk MoS$_2$ and 2L-MoS$_2$ belong to the space group P6$_3$/$_{mmc}$ (point group D$_{6h}$).
+There are 18 normal vibration modes.
 The factor group of bulk and 2L-MoS$_2$ at $\vec{\Gamma}$ is D$_{6h}$.
@@
 1L-MoS$_2$ has $D_{3h}$ symmetry, with three atoms per unit cell.
-The irreducible representation of $D_{3h}$ gives: $\vec{\Gamma}$= $2A_2^{''}$+$A_1^{'}$+$2E^{'}$+$E^{''}$, with $A_2$$^{''}$ and $E^{'}$ acoustic modes, $A_2^{''}$ IR active, $A_1^{'}$ and $E^{''}$ Raman active, and the other $E^{'}$ both Raman and IR active.
+The irreducible representation of $D_{3h}$ gives: $\vec{\Gamma}$= $2A_2^{''}$+$A_1^{'}$+$2E^{'}$+$E^{''}$, with $A_2^{''}$ and $E^{'}$ acoustic modes, $A_2^{''}$ IR active, $A_1^{'}$ and $E^{''}$ Raman active, and the other $E^{'}$ both Raman and IR active.
 (See Fig.~\ref{fig:ws2ramsch}) NL-MoS$_2$ has 9N-3 optical modes: 3N-1 are vibrations along the c axis, and 3N-1 are doubly degenerate in-plane vibrations.
@@
 \midrule
-$A_{1g}$    &  $A_1$   & Raman     & (out of plane)  & S  \\
+$A_{1g}$    &  $A_1^{'}$   & Raman     & (out of plane)  & S  \\
 $E_{2g}^2$  &          &           & (in plane)      & M + S  \\
@@
 \midrule
-$A_{2u}$    &  $A_2$   & Acoustic  & (out of plane)  & M + S  \\
+$A_{2u}$    &  $A_2^{''}$   & Acoustic  & (out of plane)  & M + S  \\
 $E_{1u}$    &          &           &       &    \\
@@
 
-The $E$ type phonon branches correspond to the in-plane normal modes, while the $A$ type phonons result from the out-of-plane vibrations.
+The $E$ type phonon branches correspond to in-plane normal modes, while the $A$ type phonons result from out-of-plane vibrations.
 $A_{1g}$ mode is an out-of-plane vibration involving only the S atoms while the $E_{2g}^1$ mode involves in-plane displacement of transition metal and S atoms.
@@
 The $E_{1g}$ mode, which is an in-plane vibration of only the S atoms, is forbidden in the backscattering Raman configuration.
-In 2H-type TMDC, the $A_{1g}$ mode is sensitive to electrostatic doping, while $E_{2g}^1$ mode is sensitive to strain, in which the FWHM of the peaks are indicator of external force quantity.
+In 2H-type TMDC, the $A_{1g}$ mode is sensitive to electrostatic doping, while $E_{2g}^1$ mode is sensitive to strain, in which the FWHM of the peaks are indicator of external force quantity.\cite{Zhao2013}
 
@@
 15 optical modes are allowed assuming 6 atoms in primitive cell.
-Refractive indices from reflectivity measurement were n0= 3.9, ne = 2.5.
+Refractive indices from reflectivity measurement were $n_0$= 3.9, $n_e$ = 2.5.
 \citeauthor{Stacy1985} studied \ce{MoS2} and \ce{WS2} Raman spectra using lasing energy close to the absorption edges.\cite{Stacy1985} Second order scattering from phonon with nonzero momentum is used to explain the rich Raman spectra.
-\citeauthor{Sourisseau1991} investigated the resonant Raman profiles in 2H-\ce{WS2} using ten different excitation wavelengths.\cite{Sourisseau1991} Dramatic intensity variation at 352 $cm^{-1}$ was observed, which is of two-phonon signal nature, and corresponds to an overtone or combination band of phonons with non-zero momenta contributing to indirect gap absorption edge.
-The authors assigned this phonon with non-zero momenta as $LA(K_5)$ type.
+\citeauthor{Sourisseau1991} investigated the resonant Raman profiles in 2H-\ce{WS2} using ten different excitation wavelengths.\cite{Sourisseau1991} Dramatic intensity variation at 352 $cm^{-1}$ was observed, which is assume to be of two-phonon signal nature, and correspond to an overtone or combination band of phonons with non-zero momenta contributing to indirect gap absorption edge.
+\citeauthor{Sourisseau1991} assigned this phonon with non-zero momenta as $LA(K_5)$ type.
 The enhancement of the total Raman cross section at excitonic resonance in which excitons serve as the intermediate state is stronger compared to that of interband resonance.
@@
 Raman technique has also provided much insight into the few layer \ce{MS2}.
+\ce{MS2} layer numbers are readily identified by the wavenumber distance between $A_{1g}$ and $E_{2g}^1$ mode for \ce{MoS2}\cite{Buscema2013} and \ce{WS2}\cite{Berkdemir2013}.
+Yet due to the relative small shift of $A_{1g}$ mode and little shift of $E_{2g}^1$ mode in \ce{WS2} FL, the frequencies distance might not qualify as an unambiguous way to distinguish layer numbers.
+Yet the resonant Raman profile on \ce{WS2} exhibit unique features between the intensity of 2LA and $A_{1g}$ mode,\cite{Berkdemir2013,Zhao2013} which provide another routine to assure the monolayer presence.
+However, we notice some discrepancy in de-convolution of \ce{WS2} resonant profile between 300 and 400 cm$^{-1}$, i.e., the presence of $E_{2g}^1(M)$ mode at about 344 cm$^{-1}$.\cite{Peimyoo2013,Cong2013,Berkdemir2013} Rigid assignments of this mode still requires further theoretical\cite{Ataca2012} and experimental efforts.
+In addition, \citeauthor{M2013} reported temperature dependent of 1L \ce{WS2}.\cite{M2013} When the temperature increase from 77K to 623K, A1g shift from 420 to 416.5 cm.
+Interestingly in this report 2LA/$A_{1g}$ (514 nm excitation) seems less than unit.
+The spectra were obtain from mechanically exfoliated \ce{WS2} lying on 300 nm \ce{SiO2}-Si substrate.
+Moreover, The $A_{1g}$ and $E_{2g}^1$ intensities ratio exhibit reverse behaviors under 532 and 632 nm excitation.
+This is caused by the different cross-section enhancement for a specific excitation condition.
+The A and B excitonic absorption in \ce{WS2} mainly arise from the $d_{xy}$ and $d_{x^2 - y^2}$ states to $d_{z^2}$ states of tungsten atoms.
+Thus, electrons excited by 633 nm laser have a character of tungsten $d_{z^2}$ orbitals aligned along the c axis perpendicular to \ce{WS2} basal plane.
+Since $A_{1g}$ mode involve out of plane displacement along c axis, $A_{1g}$ phonons could couple more strongly with $d_{z^2}$ states than that of $E_{2g}^1$ phonons.
+As a result, $A_{1g}$ mode is stronger than $E_{2g}^1$ mode at 633 nm resonance.\cite{Zhao2013} However, the reverse effect for 532 nm excitation could not be well explained using the above argument.
+This may be caused by electron-phonon coupling with other inter-band transition electrons.
 
@@
 \citeauthor{JMR7990865} observed a new line at 152 cm in \ce{WS2} NT, which is absent in 2H-\ce{WS2}.\cite{JMR7990865} Another feature is a emerging shoulder on the low energy side of $A_{1g}$ mode at about 416 $cm^{-1}$.
-This has been attributed to a combination mode of LA + TA phonons from the $K$ point of Brillouin zone.\cite{Sourisseau1991} A more prominent feature is the resonance profile broadening the shape of $E_{2g}^1$ mode, which is often assigned to 2LA mode.
-Yet there is some different opinion on these assignments.
-\citeauthor{Molina-Sanchez2011} label the 350 $cm^{-1}$ band as \ce{E_{1u}} instead of 2LA, and the 416 $cm^{-1}$ band as inactive $B_{1u}$ mode.\cite{Molina-Sanchez2011} \citeauthor{Staiger2012} adopted these assignments in studying the resonance Raman profile of \ce{WS2} NTs.\cite{Staiger2012} It was found that
+This has been attributed to a combination mode of LA + TA phonons from the $K$ point of Brillouin zone.\cite{Sourisseau1991} \citeauthor{Zou2007} prepared W/\ce{WS2} core-shell NPs by reaction of tungsten and sulfur under hydrogen atmosphere.\cite{Zou2007} The shoulder mode associated with $A_{1g}$ is attributed to LA + TA.
+As pressure increase from 0GPa to 18GPa, these two bands, both shifting to higher wavenumbers, first separate and then recombine.
+It was assumed the compression mainly occurs in c axis, so the stiffening of $A_{1g}$ is anticipated.
+A more prominent feature is the resonance profile broadening the shape of $E_{2g}^1$ mode, which is often assigned to 2LA mode.
+Yet there is different opinion on these assignments.
+\citeauthor{Molina-Sanchez2011} label the 350 $cm^{-1}$ band as \ce{E_{1u}} instead of 2LA.\cite{Molina-Sanchez2011} And recent theoretical investigations suggest 416 $cm^{-1}$ peak is inactive$B_{1u}$ mode\cite{Molina-Sanchez2011,Ataca2012}, which is the Davydov doublet with $A_{1g}$ mode.
+\citeauthor{Staiger2012} adopted these assignments in studying the resonance Raman profile of \ce{WS2} NTs.\cite{Staiger2012} It was found that
 \begin{enumerate}
@@
 
-\citeauthor{Krause2009} measured the resonant Raman using 632 and 532 nm excitation and found a split within 420 $cm^{-1}$ region, which is labelled as $D-A_{1g}$ mode in analog with the similar defect mode of graphene.\cite{Krause2009} This  $D-A_{1g}$ mode was found enhanced as diameter of \ce{WS2} NTs decrease.
-In this work, we will use $B_{1u}$ mode to interpret this emerging line at about 416 $cm^{-1}$ of \ce{WS2} NTs.
+\citeauthor{Krause2009} also measured the resonant Raman on \ce{WS2} nanotubes and found a split within 420 $cm^{-1}$ region, which is labelled as $D-A_{1g}$ mode in analog with the similar defect mode of graphene.\cite{Krause2009} This  $D-A_{1g}$ mode was found enhanced as diameter of \ce{WS2} NTs decrease.
+In this work, we will use $B_{1u}({\Gamma})$ mode to interpret this emerging line at about 416 $cm^{-1}$ of \ce{WS2} NTs, and we adopt the 350 $cm^{-1}$ as 2LA(M).
 \citeauthor{Krause2009a} confirmed $B_{1u}$ mode arise from the inherent structure of \ce{WS2} nanomaterials instead of surface layer effect.
-It is also worth noting that $A_{1g}$ is stronger than 2LA under 632nm yet weaker under 532nm, and $B_{1u}$ mode under 532 nm become less prominent than that of 632 nm.\cite{Krause2009a} This is in consistent with our observation of Raman spectra on the \ce{WS2}-\ce{WO_x} structures.
+It is also worth noting that $A_{1g}$ is stronger than 2LA under 632nm yet weaker under 532nm, similar to previous discussion of FL scenarios.
+And $B_{1u}$ mode under 532 nm become less prominent than that of 632 nm.\cite{Krause2009a} This is in consistent with our observation of Raman spectra on the \ce{WS2}-\ce{WO_x} structures.
 \citeauthor{Rafailov2005} estimated the orientation dependence of resonant raman on one MWNT \ce{WS2} attached to the cantilever tip of AFM.\cite{Rafailov2005} Antenna effect lead to optical transition occurring only for polarization parallel to nanotube axis.
@@
 
+The difference of B1u and LA + TA.
+
 \section{literature to read}
@@
 
-The $A_{1g}$ and $E_{2g}^1$ intensities ratio exhibit reverse behaviors under 532 and 632 nm excitation.
-This is caused by the different cross-section enhancement for a specific excitation condition.
-The A and B excitonic absorption in \ce{WS2} mainly arise from the $d_{xy}$ and $d_{x^2 - y^2}$ states to $d_{z^2}$ states of tungsten atoms.
-Thus, electrons excited by 633 nm laser have a character of tungsten $d_{z^2}$ orbitals aligned along the c axis perpendicular to \ce{WS2} basal plane.
-Since $A_{1g}$ mode involve out of plane displacement along c axis, $A_{1g}$ phonons could couple more strongly with $d_{z^2}$ states than that of $E_{2g}^1$ phonons.
-As a result, $A_{1g}$ mode is stronger than $E_{2g}^1$ mode at 633 nm resonance.\cite{Zhao2013} However, the reverse effect for 532 nm excitation could not be well explained using above argument.
-This may be caused by electron-phonon coupling with other inter-band transition electrons.
  416 peak was prevously assumed to be a combination of LA and TA phonons at K points.
-recent theoretical investigation suggest this peak is $B_{1u}$ mode\cite{Molina-Sanchez2011,Ataca2012}, which is the Davydov doublet with  $A_{1g}$ mode.
 
@@
 
-\ce{WS2} thin film growth motivated by solar cell.
-\cite{Ennaoui1995a} grew tungsten disulfides film using sulfurization of \ce{WO3} under \ce{N2}/\ce{H2} gas flow.
-The composition was found to be \ce{WS_{2.13}}, and the excess of sulfur lead to p-type conductivity.
-XRD peaks ratio is used as a measure of film orientation, which was found higher for film prepared without an intermediate Ni coating.
-\ce{Ni3S2} phase was found and surfactant-mediated epitaxy is proposed.
-
 \cite{Kang2013} TMDC alloy DFT.
@@
 
-\cite{Zou2007} prepared W/\ce{WS2} core-shell NPs by reaction of tungsten and sulfur under hydrogen atmosphere.
-The shoulder mode under A1g is attributed to LA+TA.
-As pressure increase from 0GPa to 18GPa, these two bands, both shifting to higher wavenumbers, first separate and then recombine.
-It was assumed the compression mainly occurs in c axis, so the stiffening of A1g is anticipated.
-
 A1g mode using resonance Raman excitation shows upshift, which is presumably caused by folding induced strains.
-And TEM SEAD reveal 3R symmetry.
+And TEM SAED reveal 3R symmetry.
 We did not observed this upshift of A1g probably due to the large diameter and few layer involved.
@@
 Nanotube growth is relatively independent of substrates and FL layer is closely related to substrate. Film growth could provide some insight into the latter scenario.
-
-\cite{M2013} temperature dependent of ML \ce{WS2}.
-Interestingly in this report 2LA/A1g (514 nm) seems less than unit.
-The spectra were obtain from mechanically exfoliated \ce{WS2} lying on 300 \ce{SiO2}-Si substrate.
-When the temperature increase from 77K to 623K, A1g shift from 420 to 416.5 cm.
 

### 2014-02-19 ch-wox/ch-wox.tex
lortenzian fitting on naxwo3 added

@@
 \end{figure}
+
+An empirical formula to relate the Raman peaks and \ce{W-O} bonding lengths\cite{Hardcastle1995} is
+\begin{equation}\label{eq:wobond}
+\nu = 25823 e^{-1.902\cdot R}.
+\end{equation}
+And the standard deviation of estimating \ce{W-O} bond distance from Raman stretching wavenumber is $\pm0.034$\AA.
+The observed Raman peaks of \ce{Na5W_{14}O_{44}} phase lies at 965, 943, 913, 808, 786, 778, 765, 695 and 107 cm.
+Multi-peaks Lorentzian fitting is preformed to precisely determine the central maximum.
+Good fitting is obtained, as shown in Fig.~\ref{fig:naworamfit}.
+We then calculated \ce{W-O} bond distance using Eq.~\ref{eq:wobond}, as illustrated in Table~\ref{tab:nawobond}.
+The predicted \ce{W-O} bond length comply very well with the crystallographic value of \ce{Na5W_{14}O_{44}} phase.\cite{Triantafyllou1999a} The 107 peak probably is caused by \ce{Na-O} bond.
+% Na5 raman fitting
+\begin{figure}[htb]
+\centering
+\includegraphics[width=0.6\textwidth]{naxwo_ramfit}
+\caption[\ce{Na5W_{14}O_{44}} Raman fitting]{Multi-peaks Lorentzian fitting on two major peaks region of \ce{Na5W_{14}O_{44}}.
+The peaks sum height difference is caused by different baseline value adopted in each fitting.}
+\label{fig:naworamfit}
+\end{figure}
+
+% W-O bond length
+\begin{table}[htb]
+\centering
+\caption{\ce{W-O} bond length predication}\label{tab:nawobond}
+\begin{tabular}{lccr}
+\toprule
+peak center & length (\AA) & peak center & length (\AA) \\
+\midrule
+694.6 & 1.900 &  808.6 &  1.821 \\
+745.4 & 1.863 &  911.5 &  1.758 \\
+764.4 & 1.850 &  933.0 &  1.745 \\
+778.7 & 1.840 &   943.5 & 1.740 \\
+788.4 & 1.834 &   965.4 & 1.728 \\
+\bottomrule
+\end{tabular}
+\end{table}
 

### 2014-02-19 ch-tms/Seeded_growth_draft.tex
coreshell draft initial

% !TEX TS-program = pdflatex
% !TEX encoding = UTF-8 Unicode

% This is a simple template for a LaTeX document using the "article" class.
% See "book", "report", "letter" for other types of document.

\documentclass[11pt]{article} % use larger type; default would be 10pt

\usepackage[utf8]{inputenc} % set input encoding (not needed with XeLaTeX)

%%% Examples of Article customizations
% These packages are optional, depending whether you want the features they provide.
% See the LaTeX Companion or other references for full information.

%%% PAGE DIMENSIONS
\usepackage{geometry} % to change the page dimensions
\geometry{a4paper} % or letterpaper (US) or a5paper or....
% \geometry{margin=2in} % for example, change the margins to 2 inches all round
% \geometry{landscape} % set up the page for landscape
%   read geometry.pdf for detailed page layout information

\usepackage{graphicx} % support the \includegraphics command and options

% \usepackage[parfill]{parskip} % Activate to begin paragraphs with an empty line rather than an indent

%%% PACKAGES
\usepackage{booktabs} % for much better looking tables
\usepackage{array} % for better arrays (eg matrices) in maths
\usepackage{paralist} % very flexible & customisable lists (eg. enumerate/itemize, etc.)
\usepackage{verbatim} % adds environment for commenting out blocks of text & for better verbatim
\usepackage{subfig} % make it possible to include more than one captioned figure/table in a single float
% These packages are all incorporated in the memoir class to one degree or another...

%%% HEADERS & FOOTERS
\usepackage{fancyhdr} % This should be set AFTER setting up the page geometry
\pagestyle{fancy} % options: empty , plain , fancy
\renewcommand{\headrulewidth}{0pt} % customise the layout...
\lhead{}\chead{}\rhead{}
\lfoot{}\cfoot{\thepage}\rfoot{}

%%% SECTION TITLE APPEARANCE
\usepackage{sectsty}
\allsectionsfont{\sffamily\mdseries\upshape} % (See the fntguide.pdf for font help)
% (This matches ConTeXt defaults)

%%% ToC (table of contents) APPEARANCE
\usepackage[nottoc,notlof,notlot]{tocbibind} % Put the bibliography in the ToC
\usepackage[titles,subfigure]{tocloft} % Alter the style of the Table of Contents
\renewcommand{\cftsecfont}{\rmfamily\mdseries\upshape}
\renewcommand{\cftsecpagefont}{\rmfamily\mdseries\upshape} % No bold!

%%% END Article customizations
%%---added by tao sheng
\usepackage{subfig}
\usepackage{float}
\graphicspath{{../gallery/}} %--added by authior

\usepackage{xcolor}

\usepackage{amsmath}
%\numberwithin{equation}{section} % reset counters at each start of section
%\numberwithin{figure}{section}
\providecommand*{\ud}{\mathrm{d}}

\usepackage[font=small, labelfont=bf]{caption}

\usepackage{pdfpages}
\usepackage{placeins}
\usepackage{siunitx}
\usepackage[version=3]{mhchem}
\usepackage{mathpazo}

\usepackage[affil-it]{authblk}

\usepackage[super, comma,sort&compress]{natbib}
\providecommand*{\bibpath}{E:/spring2012/Ubuntu/Latex/Mendeley_Bib_lib}

\usepackage{hyperref} % put this package at the last of all other packages
\hypersetup{
colorlinks,%
citecolor=black,%
filecolor=black,%
linkcolor=black,%
urlcolor=black
} % make all links black

%%% The "real" document content comes below...

\begin{document}
\title{Tungsten Disulfides and Tungsten Oxides Core-Shell NWs}
\author{Tao Sheng}
%\date{} % Activate to display a given date or no date (if empty),
         % otherwise the current date is printed
\affil{Department of Physics and Optical Science\\}
\author{Youfei Jiang}
\author{Haitao Zhang%
\thanks{Email address:hzhang3@uncc.edu; Corresponding author}}
\affil{Department of Mechanical Engineering and Engineering Science\\
The University of North Carolina at Charlotte\\
9201 University City Boulevard, Charlotte NC 28223}

\maketitle

\section{Introduction}
% phtotcatalytic activity

\section{Experimental}

\textbf{Synthesis}

\ce{WS2}-\ce{WO_x} core-shell NWs were synthesized using direct sulfurization of \ce{WO3} NWs (Fig.~\ref{fig0}). Tungsten trioxides NWs were synthesized by a seeded growth approach in a home-built CVD apparatus, which has been successfully employed to prepare \ce{TiO2}, \ce{WO3}\cite{Zhang2010}, \ce{MoO3} etc nanomaterials. The seeded growth details are provided in supporting information. The as-grown \ce{WO3} NWs were loaded into the center of heating furnace, and $\sim100$mg sulfur (99.5\%) was positioned just outside the upstream edge of furnace, where the maximum temperature was about 240 \si{\degreeCelsius}. After pumping down, the reaction chamber was flushed two times to expel residual air. Then the furnace was heated to 750 \si{\degreeCelsius} in 30 minutes, held for 15 minutes, and allowed to naturally cool down to room temperature. During entire growth process, 30 sccm Ar was used as carrier flow.

\begin{figure}[htb]
\centering
\includegraphics[width=0.7\textwidth]{ws2_coreshell_setup}
\caption{Schematic illustration of sulfurization process.}
\label{fig0}
\end{figure}

\textbf{Characterization}

The morphology and composition of the as-synthesized samples were analyzed by scanning electron microscopy (SEM, JEOL JSM-6480) and the associated energy dispersive X-ray spectroscopy unit(EDS, Oxford Instrument INCA). Crystal structures were characterized using X-ray diffraction (PANXpertX’pert Pro MRD with Cu K$\alpha$ line at $\lambda$=1.5418\AA) and transmission electron microscopy (TEM, JEOL JEM-2100 LaB6 operated at 200kV). A Raman microscope setup (Horiba Scientific, Labram HR800) were used to detect Raman spectra.

To perform TEM-Raman integrated study, the core-shell specimen was first dispersed into acetone solution, and dipped onto PDMS () support. A micromanipulator was used to pick up the longer core-shell NWs and to transfer them onto TEM grids. The NWs were first examined using TEM to identify the \ce{WS2} layers configuration and the associated geometrical orientation. Then the core-shell NWs on TEM grids were examined under Raman.

\FloatBarrier

\section{Results and Discussion}

\textbf{Seeded growth}

% sg sem
\begin{figure}[htb]
\centering
\subfloat[]{\label{fig:sga}\includegraphics[width=0.4\textwidth]{wox_sg_a.jpg}}\hspace{0.04\textwidth}
\subfloat[]{\label{fig:sgb}\includegraphics[width=0.4\textwidth]{wox_sg_b.jpg}}
\caption[Characterization of seeded growth \ce{WO3}: SEM]{Characterizations of seeded growth. (a) SEM graphs of \ce{WO3} NWs on \ce{SiO2/Si} substrate. (b) A high magnification view showing uniform NW growth and close-up view of one NW. }
\label{fig:woseedsem}
\end{figure}

As shown in Fig.~\ref{fig:sgb}, dense NWs array was obtained on tungsten powder seeds with individual wires of length up to 5 $\mu$m and diameter about 50 to 200 nm, according to the estimation made in the close-up view. Each tungsten powder stood as independent growth site (Fig.~\ref{fig:sga}) with island-layer growth on the substrates, a common feature without using tungsten powder as seed under current experimental conditions. It was occasionally observed that NWs growth was initiated adjacent some tungsten powders. We suspect that this phenomenon was correlated to the local trap of vapor flow since it was more often found among the enclosed area by tungsten powders. We also found that the diameter of NWs decrease as the distance between powders and upstream edge increases. This is a combination effect of lower temperature and reduced \ce{WOx} growth species supply. Similar phenomena were observed in other studies.\cite{Thangala2007}

% sg raman xrd
\begin{figure}[htb]
\centering
\subfloat[]{\label{fig:sgxrd}\includegraphics[width=0.45\textwidth]{wox_xrd_1}}\hspace{0.04\textwidth}
\subfloat[]{\label{fig:sgram}\includegraphics[width=0.45\textwidth]{wox_raman_1}}
\caption[Characterization of seeded growth \ce{WO3}: XRD and Raman]{ (a) XRD pattern of as-prepared sample indicating the \ce{WO3} phase and the presence of metallic core. (b) Raman spectrum on NWs region showing the feature of \ce{WO3}.}
\label{fig:woseedxrd}
\end{figure}

Fig.~\ref{fig:sgxrd} is the XRD spectrum of one typical sample. The peaks under circular symbol were identified to be the monoclinic \ce{WO3} phase (ICDD PDF 01-083-0950,\emph{a}=7.30084\AA, \emph{b}=7.53889\AA, \emph{c}=7.6896\AA, $\beta$=90.8920$^\circ$), while the peak under the triangular symbol was indexed to cubic tungsten phase (ICDD PDF 04-16-3405, \emph{a}=3.157\AA). This metallic core was anticipated considering the oxygen flow levels (Supporting info for oxidation experiment). Micro-Raman scattering spectroscopy was performed on as-synthesized sample as well. During Raman examination, the laser spot was carefully focused onto the NWs on powders and several inspections on different positions were observed to ensure the reproductivity of spectra data. As shown in Fig.~\ref{fig:sgram}, five distinct bands were well resolved, with its peaks located at 131, 265, 327, 711 and 803 \si{cm^{-1}}, respectively. This pattern closely matches previous studies on \ce{WO3} lattice dynamics.\cite{Salje1975a,Dixit1986} The high background level probably arises from the metallic core.

\textbf{core shell phase and composition}

\begin{figure}[htb]
\centering
\includegraphics[width=0.7\textwidth]{WS2_sem_edx.jpg}
\caption{ Morphology and composition analysis on as-synthesized core-shell structures. (a) SEM images showing the NWs almost retain their original shapes after sulfurization, and (b) EDX spectroscopy revealing the presence of sulfur element after sulfurization.}
\label{fig:ws2sem}
\end{figure}

%fig TEM showing CS planes

% fig Raman TEM

%

\subsection{Photocatalytic}

\clearpage
\bibliographystyle{unsrtnat}
\bibliography{\bibpath/ECD,\bibpath/tungsten_newandgood,\bibpath/ACSnano,\bibpath/tungsten_old,\bibpath/Raman,\bibpath/Molybdenum,\bibpath/tungsten_cl}

\end{document}

\si{\degreeCelsius}
\AA

\clearpage
\begin{table}[htb]
\centering
\caption{Source of figures }\label{tab:sof}
\begin{tabular}{l|c|c|r}
\hline
No of Fig & sub index & sample date & remarks\\
\hline
1        & a & 013113 & 500 \\
1        & b & 012913 & 600 \\
1        & c & 020413 & 650 \\
1        & d & 013013 & 750 \\
\hline
2       & a & 012913 & 1sccm \\
2       & b & 020513 & 2sccm \\
2       & c & 020613 & 3sccm \\
2       & d & 021113 & 10sccm \\
\hline
3       & a & 012913 &  3N\\
3       & b & 042313 &  3N5\\
3       & c & 041013 &  4N5\\
3       & d & 041113 &  5N\\
\hline
4       & a & 021513 &  8mm-x500\\
4       & a inset & 021513 &  8mm-x10k\\
4       & b & 021513 &  13mm-x500\\
4       & b inset & 021513 &  13mm-x10ka\\
\hline
5   &   xrd & 021513 & \\
\hline
6  & raman & 060313 or 021513 & \\
\hline
7 & TEM & 060413 &
\end{tabular}
\end{table}

A low recombination rate is preferred for high photocatalytic efficiency. The simultaneous migration of electrons and holes.
\textbf{\ce{WS2}-\ce{WO3}}: 1 kW light source(Hg, or Xe lamp), photon flux, phenol (\ce{C6H5OH}, 94.1g/mol, MP 40C)concentration is 20 mg/L, hydroxyl group. The quantitative analysis of phenol was performed via a standard colorimetric method.\footnote{\url{http://omlc.ogi.edu/spectra/PhotochemCAD/html/072.html}}
\citeauthor{DiPaola1999} prepared \ce{WS2}-\ce{WO3} mixture in two methods, sulfurization of \ce{WO3} and oxidation of \ce{WS2},with the latter are more active.
\citeauthor{DiPaola1999} also concluded that the actual efficiency of mixed \ce{WS2}-\ce{WO3} catalysts depends on the ratio of each composition present of the surface of the particles, and the maximum of photoactivity is obtained with 40-50\% surface molar ratio of \ce{WS2}.

ref 25, 28 and 41.

\textbf{\ce{MoO3}}:

\citeauthor{Sreedhara2013} studied the kinetics of photodegradation of methylene blue\footnote{\ce{C16H18N3SCl},319.8 g/mol, MP: 100C accompanied with decomposition \url{http://en.wikipedia.org/wiki/Methylene_blue}} dye by few layer \ce{MoO3}.
For the photodegradation method, it was stated that `` the samples were collected after the photoreaction had been centrifuged for 5 min to remove the photocatalyst before UV-Vis measurement.''

### 2014-02-21 BackMatter/paper.tex
daily works on Raman and seeded growth

@@
 \cite{Wu2013b} CVD G on copper. Size of single crystal domain and nucleation site density.
+
+Concentration of charge carrier $n$ is related to gate voltage $V_g$ by:
+\[
+n = \frac{\epsilon_0 \epsilon V_g}{ed}
+\[
+where $\epsilon_r = \epsilon_0 \epsilon$ is dielectric constant of gate materials.
+
+massless relativistic chiral particles, Klein paradox, 100\% tunneling and extreme high mobility.
+
+\ce{SiO_x}-Si, \ce{WS2} absorption coefficient $10^{-7}m^{-1}$, mean free path of photo-excited charge carriers 1 $\mu m$.
+the wave vector of photon is considerably small than size of BZ, therefore The wave vector of phonon in Raman scattering usually close to zero.
+
+ref M. Cardona. Light Scattering in Solids II,. Springer, Berlin, 1982
+
+Multiple phonon scattering, For two identical phonons, the corresponding Raman peak in the spectrum is called an overtone of the peak from the corresponding one-phonon process.
+And the wave vector conservation rule is automatically filled, therefore the phonon involved is not limited to BZ center anymore.
+\[
+I(G) \approx \sum_k \frac{\langle f|H_M|b\rangle \langle b|H_{ep}|a\rangle \langle a|H_M|i\rangle}{(E_p - E_k^{\pi *}- E_k^{\pi}-i\gamma)(E_p - E_k^{\pi *}- E_k^{\pi}-i\gamma- \hbar\Omega_{G})}
+\]
+
+the average distance travelled by an excited electron-hole pair before combination $l=\nu_F/\omega_D=4nm$.
+
+Confocal Raman spectrometer:to obtain Raman spectrum in a specific depth of sample. Edge filter to cut off Rayleigh emission.
+
+resolution $d= 1.22 \lambda/NA$,
+
+\section{vocabulary}
+
+in reciprocal space, primitive cell, a sketch of device, a decisive role. anchors,

### 2014-02-21 ch-tms/Seeded_growth_draft.tex
daily works on Raman and seeded growth

@@
 \ce{WS2}-\ce{WO_x} core-shell NWs were synthesized using direct sulfurization of \ce{WO3} NWs (Fig.~\ref{fig0}).
-Tungsten trioxides NWs were synthesized by a seeded growth approach in a home-built CVD apparatus, which has been successfully employed to prepare \ce{TiO2}, \ce{WO3}\cite{Zhang2010}, \ce{MoO3} etc nanomaterials.
+Tungsten trioxides NWs were synthesized by a seeded growth approach in a home-built CVD apparatus, which has been successfully employed to prepare borides\cite{Amin2009a}, titanium oxide\cite{Amin2007}, tungsten oxides\cite{Zhang2010} and \ce{MoO3}.
 The seeded growth details are provided in supporting information.
-The as-grown \ce{WO3} NWs were loaded into the center of heating furnace, and $\sim100$mg sulfur (99.5\%) was positioned just outside the upstream edge of furnace, where the maximum temperature was about 240 \si{\degreeCelsius}.
+The as-grown \ce{WO3} NWs were loaded into the center of heating furnace, and $\sim200$mg sulfur (Alfa Aesar 10785, 99.5\%) was positioned just outside the upstream edge of furnace, where the maximum temperature was about 240 \si{\degreeCelsius}.
 After pumping down, the reaction chamber was flushed two times to expel residual air.
+A cold trap filled with liquid nitrogen in downstream was used to collect possible sulfur precipitation.
 Then the furnace was heated to 750 \si{\degreeCelsius} in 30 minutes, held for 15 minutes, and allowed to naturally cool down to room temperature.
@@
 The morphology and composition of the as-synthesized samples were analyzed by scanning electron microscopy (SEM, JEOL JSM-6480) and the associated energy dispersive X-ray spectroscopy unit(EDS, Oxford Instrument INCA).
-Crystal structures were characterized using X-ray diffraction (PANXpertX’pert Pro MRD with Cu K$\alpha$ line at $\lambda$=1.5418\AA) and transmission electron microscopy (TEM, JEOL JEM-2100 LaB6 operated at 200kV).
+Crystal structures were characterized using X-ray diffraction (PANXpertX’pert Pro MRD with Cu K$\alpha$ line at $\lambda$=1.5418\AA) and transmission electron microscopy (TEM, JEOL JEM-2100 \ce{LaB6} operated at 200kV).
 A Raman microscope setup (Horiba Scientific, Labram HR800) were used to detect Raman spectra.
+The spectra was acquired using 532 nm laser (0.3 mW) and 200 seconds acquisition time.
 
-To perform TEM-Raman integrated study, the core-shell specimen was first dispersed into acetone solution, and dipped onto PDMS () support.
+To perform TEM-Raman integrated study, the core-shell specimen was first dispersed into acetone solution, and dipped onto polydimethylsiloxane (PDMS) support.
 A micromanipulator was used to pick up the longer core-shell NWs and to transfer them onto TEM grids.
@@
 
-\FloatBarrier
+To perform TEM-Raman integrated study, the core-shell nanowires need to be transferred to TEM grid first.
+So the core-shell specimens were dispersed into acetone, and then dipped onto polydimethylsiloxane (PDMS) substrate.
+Some long core-shell nanowires on PDMS substrate were picked up and transferred to TEM grids by using a home-built micromanipulator under optical microscope
 
@@
 %fig TEM showing CS planes
+\begin{figure}[htb]
+\centering
+\includegraphics[width=0.7\textwidth]{ws2_coreshell_tem.jpg}
+\caption{HRTEM images on one core-shell nanowires showing (a) the multilayer capping and void formation in \ce{WO_x} core, and (b) uniform \ce{WS2} layers on nanowire body and CS planes formation in core region.}
+\label{fig:ws2tem}
+\end{figure}
+% fig Raman TEM
+\begin{figure}[htb]
+\centering
+\includegraphics[width=0.7\textwidth]{ws2_coreshell_integ.jpg}
+\caption{TEM-Raman integrated results on one core-shell nanowires.
+(a)-(c) \ce{WS2} layer number variation from bulk to 2L.
+(d) Associated Raman spectra with site1-3 corresponding to HRTEM images (a)-(c), respectively.
+(e) Multi-peak Lorentzian fitting on Raman spectrum site 3 with inset showing layer number dependent intensiteis ratio of $I_{2LA}/I_{A_{1g}}$ under 532 nm excitation.}
+\label{fig:ws2ram}
+\end{figure}
 
-% fig Raman TEM
-
-%
-
+\FloatBarrier
 \subsection{Photocatalytic}
@@
 \bibliographystyle{unsrtnat}
-\bibliography{\bibpath/ECD,\bibpath/tungsten_newandgood,\bibpath/ACSnano,\bibpath/tungsten_old,\bibpath/Raman,\bibpath/Molybdenum,\bibpath/tungsten_cl}
+\bibliography{\bibpath/Titanium,\bibpath/VLS,\bibpath/ECD,\bibpath/tungsten_newandgood,\bibpath/ACSnano,\bibpath/tungsten_old,\bibpath/Raman,\bibpath/Molybdenum,\bibpath/tungsten_cl}
 
@@
 \hline
-7 & TEM & 060413 &
+7 & TEM & B10, B6 &
 \end{tabular}

### 2014-02-21 ch-tms/tms.tex
daily works on Raman and seeded growth

@@
 It was found that the \ce{WS2} nucleate from an amorphous \ce{WS3} phase and the substrate has a critical role in determining both the reaction onset temperature and the texture.
+The adhesion of tungsten to quartz was found to be much stronger than to glass.
+And oxygen-containing species such as \ce{H2O} or OH tend to cause \ce{WS2} basal plane perpendicular to substrate.
 % WS2 films
@@
 \midrule
-sputtered W + \ce{H2S}   & glass      & onset 400 \si{\degreeCelsius} & $\perp c$ at 500 \si{\degreeCelsius}\\
+sputtered W + \ce{H2S}   & glass      & onset 400 \si{\degreeCelsius} & $\perp c$ at 500 \si{\degreeCelsius}, metastable \ce{WS3} found\\
                           & quartz      & onset 650 \si{\degreeCelsius} & $\parallel c$ below 950 \si{\degreeCelsius}\\
@@
 \midrule
-\ce{WO_x} + \ce{H2S}    & quartz      & onset 500 \si{\degreeCelsius} & predominantly $\perp c$ at 800 \si{\degreeCelsius}\\
+\ce{WO_x} + \ce{H2S}    & quartz      & onset 500 \si{\degreeCelsius} & predominantly $\perp c$ after 800 \si{\degreeCelsius}\\
+                        & Mo        & onset NA          & $\parallel c$ dominant\\
+                        & W       & onset NA          & random orientation\\
 \bottomrule

### 2014-02-23 BackMatter/paper.tex
core-shell paper

@@
 \ce{MoOx} few layer as hole selective contact in solar cell.\cite{Battaglia2014}
-\ce{MoO_x} on n-type Si acts as a high workfunction metal (6.6eV), enabling a dopant-free contact and thus junctionless devices.
+\ce{MoO_x} on n-type Si acts as a high work function metal (6.6eV), enabling a dopant-free contact and thus junctionless devices.
 
@@
 \section{TMS}
+
+\cite{Najmaei2014} Self-assembled monolayer (SAM) on \ce{SiO2} and its effect on \ce{MoS2} 1L.
+
+\cite{Ma2011} \ce{WS2} 1L doping calculation.
+
+\cite{Britnell2013} G/\ce{WS2}/G stacked solar cell. For lubricant, and surface protection. Absorption $\sim 10^7 m^{-1}$.
+
 \cite{Cong2013} A direct gap of $\sim 2eV$ at the corners of BZ is formed in 1L \ce{WS2}, Growth on bottom piece show the multiple domain flakes occurs at initial stage of the growth, starting from \ce{WO3} particles.
@@
 
-ref M. Cardona. Light Scattering in Solids II,. Springer, Berlin, 1982
-
 Multiple phonon scattering, For two identical phonons, the corresponding Raman peak in the spectrum is called an overtone of the peak from the corresponding one-phonon process.
@@
 
+Light Scattering in Solids II,. Springer, Berlin, 1982
+
+influence of core WOx, Raman scattering by plasma-LO coupling to determine carrier concentration. measure resonant cross sections in absolute units.
+
+disorder-induced light scattering, Van Hove critical points,
+In resonant second-order scattering:
+overtone: the same phonon,
+combination: two different phonons;
+
+\[
+\frac{\ud\sigma}{\ud\Omega}= \omega_s^4 cm^6 Sr^{-1}
+\]
+
+scattering volume V in number of unit cells can be considered as one big molecule.
+
+\ce{CaF2} a material suitable for scattering efficiency S comparison measurement due to its large band gap ($S\times \omega_L^4$ is constant below 5eV).
+
+symmetry-breaking mechanism,
+
+\cite{Ahlgren2011}  low energy ion doping of graphene.
+
+\section{misc}
+
+\cite{Habib2010} oxygen plasma treatment on HF-etched Si (001). reaction among $e$, \ce{O^+}, \ce{O2^+}, \ce{O^-},\ce{O2}. \ce{OH}-terminated surface obtained.
+
+\cite{Wang2014a} MB is a heterocyclic aromatic dye which is blue colored in oxidizing environment.
+Upon reduction, MB is turned into colorless leuco MB.
+This can be used as an oxygen indicator in food industry.
+Photo-bleaching of MB can be also due to its leuco formation rather than total decomposition.
+Photocatalytic decomposition can be minimized by keeping the solution at acidic condition (PH = 4), which will limit the formation of oxidative hydroxyl radicals (E = 2.8eV vs normal hydrogen electrode).
+Oxygen dissolved in the solution play a key role in conversion of LMB to MB under visible light.
+Purging with \ce{N2} for 20mins can remove dissolved oxygen.
+
 \section{vocabulary}
 
-in reciprocal space, primitive cell, a sketch of device, a decisive role. anchors,
+experience an enormous development, principles underlying, scarce.
+heavily engaged, extensively used, become aware of, a great deal of, consistently used, lift the restriction, changed profoundly, denominator, a situation which often arises as ...
+in a manner similar to its counterpart.
+
+in reciprocal space, primitive cell, a sketch of device, a decisive role. anchors,angular brackets, thermodynamical average over the equilibrium configuration at temperature T.
+
+equation embodies the law of conservation
+
+become varied, laptop not hammer it hand, bubble pop, crash and burns.

### 2014-02-23 ch-tms/Seeded_growth_draft.tex
core-shell paper

@@
 So the core-shell specimens were dispersed into acetone, and then dipped onto polydimethylsiloxane (PDMS) substrate.
-Some long core-shell nanowires on PDMS substrate were picked up and transferred to TEM grids by using a home-built micromanipulator under optical microscope
+Some long core-shell nanowires on PDMS substrate were picked up and transferred to TEM grids by using a home-built micromanipulator under optical microscope.
+
+$6\mu L$ Methylene Blue\footnote{\ce{C16H18N3SCl} molar mass 319.85g/mol.} (Alfa Aesar 42771, 1\%w/v = 31.26 mM) in diluted into 20 mL DI water, giving ultimate concentration as $9.38 \mu M$.
+The measured absorbance spectrum is shown in supporting information, with maximum absorbance 0.42 at 664nm.
+Taking the \ce{MB^+} molar extinction coefficient $\epsilon$ as 95000 $M^{-1}cm^{-1}$,\cite{Cenens1988} then the measured concentration is $c = \frac{A}{\epsilon l}$ is $4.37 \mu M$.
 
@@
 (d) Associated Raman spectra with site1-3 corresponding to HRTEM images (a)-(c), respectively.
-(e) Multi-peak Lorentzian fitting on Raman spectrum site 3 with inset showing layer number dependent intensiteis ratio of $I_{2LA}/I_{A_{1g}}$ under 532 nm excitation.}
+(e) Multi-peak Lorentzian fitting on Raman spectrum site 3 with inset showing layer number dependent intensities ratio of $I_{2LA}/I_{A_{1g}}$ under 532 nm excitation.}
 \label{fig:ws2ram}

### 2014-02-23 BackMatter/app3.tex
process applendix added

\chapter{Processes developed during Ph.D. study}

\section{Growth recipes}

\section{Characterization and data processing}

\subsection{UV-Vis measurements}

\subsection{TEM-Raman integrated measurements}

\subsection{data processing}

\textbf{Multipeaks fitting}

\textbf{3D pdf}

### 2014-02-25 BackMatter/paper.tex
paper.tex u8 issue

@@
 
-Charge-density-wave states\footnote{In CDW states, conductivity is non-Ohmic above a threshold electric field} was found in blue bronze \ce{K_{0.3}MoO3}, which can be prepared by electrolytic reduction of \ce{K2MoO4} and \ce{MoO3} melt.\cite{Dumas1983} \ce{K_{0.3}MoO3} is side=centered monoclinic phase, with lattice parameter $a=18.249$\AA, $b=7.561$\AA, $c=9.856$\AA, and $\beta=117.54^\{circ}$ at RT.
-\ce{K_{0.3}MoO3} presents a semiconductor-to-metal transition at 180 K.
+Charge-density-wave states\footnote{In CDW states, conductivity is non-Ohmic above a threshold electric field} was found in blue bronze \ce{K_{0.3}MoO3}, which can be prepared by electrolytic reduction of \ce{K2MoO4} and \ce{MoO3} melt.\cite{Dumas1983} \ce{K_{0.3}MoO3} is side=centered monoclinic phase, with lattice parameter $a=18.249$\AA, $b=7.561$\AA, $c=9.856$\AA, and $\beta=117.54$ at RT.
+\ce{K0.3MoO3} presents a semiconductor-to-metal transition at 180 K.
 Electrical transport measurements yield an highly anisotropic ratio of DC conductivities of 1:10:1000.
 Along this high conducting axis, metallic reflection behavior is confirmed by optical measurements.
-Therefore, this blue bronze \ce{K_{0.3}MoO3} is known as quasi-1D metal.\cite{Sing1999}
+Therefore, this blue bronze $\ce{K_{0.3}MoO3}$ is known as quasi-1D metal.\cite{Sing1999}
 
@@
 \eta & = 0.5(W_f - E_a)\\
-\end{aligh}
+\end{align}
 where I is ionization potential and $E_a$ is electron affinity.
@@
 
-Sulfurizaiton of W film, (Jäger-Waldau, Lux-Steiner, Jäger-Waldau, & Bucher, 1993)
+Sulfurizaiton of W film, (Jäger-Waldau, Lux-Steiner, Jäger-Waldau, \& Bucher, 1993)
 
@@
 n = \frac{\epsilon_0 \epsilon V_g}{ed}
-\[
+\]
 where $\epsilon_r = \epsilon_0 \epsilon$ is dielectric constant of gate materials.
@@
 
+\cite{Yoneyama1972} MB to LMB (\ce{C16H19N3S}) in aqueous solution upon illumination of \ce{TiO2}.
+The colorimetric analysis was performed in a glove box under nitrogen atmosphere.
+The absence of oxygen is important to prevent the oxidation of LMB to blue MB.
+\[
+\cee{MB^+ H2O + H^+ \rightarrow MBH3^{2+} + 1/2O2}
+\]
+where MB represents the uncharged center of MB molecule.
+
+\cite{Takizawa1978} common wisdom expect that a dye incapable of injecting an electron at the excited state to CdS.
+MB, which process N-methyl groups in its molecular structure and does not sensitize CdS is an exemplary candidate.
+quantum efficiency is defined as probability of MB converted to azure B per incident photon.
+QE of CdS to MB decomposition is reduced in nitrogen bubbling treated solutions, indicating the necessity of oxygen.
+Two possible mechanisms: a) adsorbed oxygen acts as a trap for the conduction electron and prevent the accumulation of negative charge within space charge region of CdS, supported by the formation of \ce{O2^-} in excitation of CdS in aqueous suspension.
+
+ref 16, MB aqueous solution stability. Liquid chromatogram, azure B (trimethylthionine), and thionine. Electrochemical measurement,
+
+\cite{Matthews1989} MB adsorption.
+photocatalytic oxidation of MB by \ce{TiO2} film.
+photo-oxidation reaction occurs at the surface of photocatalyst.
+Mb molar extinction coefficient was found to be 66700 1/cm 1/M.
+Langmuir adsorption isotherm
+\[
+[MB]_{ads} = \frac{k_1 k_2 [MB]}{1 + k_1[MB]}
+\]
+and integrated form of Langmuir adsorption isotherm
+\[
+t = \frac{1}{k_1K} In\frac{[S]^0}{[S]} + \frac{1}{K}([S]^0 - [S])
+\]
+where $K = k_2 \phi N T_r$, with $\phi$ as quantum yield, N as total absorbed photons, and $T_r$ as rate of transport.
+\[
+\cee{C16H18N3SCl + 25.5O2 \rightarrow 16CO2 + 6H2O + 3HNO3 + H2SO4 +HCl}
+\]
+which indicates the total oxidation of $10 \mu M$ MB would exhause the ambient oxygen concentration of initially air-equilibrated solutions (about $250 \mu M$ ).
+ref 28 Thus the transport of both oxygen and MB to the photocatalyst surface are anticipated to be key factors.
+
+\cite{DeTacconi1997} photoelectrochromism at \ce{TiO2}/MB interface and its control.
+Efficient capture of photogenerated holes by a reducing agent is crucial to the reversibility of bleach-recoloration transition.
+This transition is kinetically dictated by electron transfer.
+Holes transfer is not desired.
+
+256 nm band is associated to the presence of LMB.
+LMB formation is not favored at alkaline pH values in aqueous solution.
+The OH radicals are generated either with the surface hydroxyl groups on \ce{TiO2} or with water, and its high oxidizing powder cause photocatalytic decomposition of the dye.
+
+An elementary step in decomposition of MB is N-dealkylation, which is preceded by radical cation formation.\cite{Takizawa1978} This radical cation can be spectroscopically monitored by the presence of 520nm band for MB.
+In MB absorption spectrum, 664 and 614 nm band ratio is related to monomer and dimer relaxation.
+\begin{align}
+\cee{TiO2 &\rightarrow e_{CB}^- + h_{VB}^+ \\
+h_{VB}^+ + red &\rightarrow ox\\
+MB^+ + 2e_{CB}^ + H^+ &\rightarrow LMB}
+\end{align}
+
+Measure the ratio between 614 and 663 nm before and after adding WS2 can indicate the adsorption of monomer and dimer MB.
+
+\cite{Mills1999} MB can act as sacrificial electron acceptor in the reduction to leuco form.
+The decomposition is favored under oxygen-rich environment.
+MB feature peaks at 663, 614 and 292 nm.
+The doubly reduced form of MB, LMB has feature peak at 256 nm.
+The singly reduced form of MB, \ce{MB.^-} is pale yellow, with peak at 420nm.
+\[
+\cee{2MB.^- \rightarrow MB + LMB}
+\]
+The oxidized form of MB, \ce{MB.^+} has peak at 520nm, which is stable in acidic solution, but decomposes irreversibly in slight alkaline solution(pH = 9).
+thionine peaks at 600nm.
+\[
+\cee{2LMB + O2 \rightarrow 2MB + 2H2O}
+\]
+
+S.L. Murov, I. Carmichael, G.L. Hug, Handbook of Photochemistry, 2nd revised ed. Marcel Dekker, New York, 1993.
+
+aerobic or anaerobic, dimerise, photominerlization, gas to liquid transfer.
+
+\cite{Lee2003a}
+\begin{align}
+\cee{ 2LMB &\rightarrow LMB^*\\
+2LMB^* + O2 &\rightarrow 2MB^+ + 2OH^-}
+\end{align}
+
+\[
+\cee{2LMB -> [\alpha] LMB^*}
+\cee{2LMB -> [\text{above}] LMB^*}
+\]
+
 \section{vocabulary}
@@
 
-become varied, laptop not hammer it hand, bubble pop, crash and burns.
+become varied, laptop not hammer it hand, bubble pop, crash and burns. exert a marked influence

### 2014-02-27 BackMatter/paper.tex
coreshell growth cont

@@
 
-\cite{Habib2010} oxygen plasma treatment on HF-etched Si (001). reaction among $e$, \ce{O^+}, \ce{O2^+}, \ce{O^-},\ce{O2}. \ce{OH}-terminated surface obtained.
+oxygen plasma treatment on HF-etched Si (001). reaction among $e$, \ce{O^+}, \ce{O2^+}, \ce{O^-},\ce{O2}. \ce{OH}-terminated surface obtained.\cite{Habib2010}
 
@@
 
-\cite{Yoneyama1972} MB to LMB (\ce{C16H19N3S}) in aqueous solution upon illumination of \ce{TiO2}.
+Liquid
+
+solar energy harvesting representative study.\cite{Yoneyama1972} MB to LMB (\ce{C16H19N3S}) in aqueous solution upon illumination of \ce{TiO2}.
 The colorimetric analysis was performed in a glove box under nitrogen atmosphere.
@@
 \]
-which indicates the total oxidation of $10 \mu M$ MB would exhause the ambient oxygen concentration of initially air-equilibrated solutions (about $250 \mu M$ ).
+which indicates the total oxidation of $10 \mu M$ MB would exhaust the ambient oxygen concentration of initially air-equilibrated solutions (about $250 \mu M$ ).
 ref 28 Thus the transport of both oxygen and MB to the photocatalyst surface are anticipated to be key factors.
@@
 LMB formation is not favored at alkaline pH values in aqueous solution.
-The OH radicals are generated either with the surface hydroxyl groups on \ce{TiO2} or with water, and its high oxidizing powder cause photocatalytic decomposition of the dye.
+The OH radicals are generated either with the surface hydroxyl groups on \ce{TiO2} or with water, and its high oxidizing power cause photocatalytic decomposition of the dye.
 
@@
 The decomposition is favored under oxygen-rich environment.
-MB feature peaks at 663, 614 and 292 nm.
+MB feature peaks at 663, 614 and 292 nm, and $\epsilon_{660}=10^5 M^{-1}cm^{-1}$.
 The doubly reduced form of MB, LMB has feature peak at 256 nm.
@@
 \[
+\cee{MB + e_{CB}^- ->[pH<7] MB.^-}
 \cee{2MB.^- \rightarrow MB + LMB}
+\cee{O2 + e_{CB}^- \rightarrow O2.^-}
 \]
+
 The oxidized form of MB, \ce{MB.^+} has peak at 520nm, which is stable in acidic solution, but decomposes irreversibly in slight alkaline solution(pH = 9).
 thionine peaks at 600nm.
+MB forms dimers in aqueous solution, 
+\ce{
+2MB <=>[K_D] (MB)_2
+}
+A typical value of $K_D$ is 3970 1/M. A quadratic equation can be solved to obtain the monomer concentration: 
 \[
-\cee{2LMB + O2 \rightarrow 2MB + 2H2O}
+2K_D [MB]^2 + [MB] - [MB]_{total} = 0
+\]
+MB adsorption on metal oxides. Monomer size is less than 1.5nm. 
+Logarithmic acid dissociation constant $pK_a= -\log_10 \frac{[A^-][H^+]}{[HA]}$. The oxidation potential for \ce{H2O}-\ce{O2} couple is 1.23V and 0.817V versus NHE at pH 0 and pH 7, respectively.
+
+\[
+\cee{MB + SED &->[TiO2][h\nu \leq 3.2eV] LMB + SED^{2+}\\
+2LMB + O2 &\rightarrow 2MB + 2H2O\\
+
+}
 \]
@@
 
+\cite{Galagan2008} Mb to LMB transition as visual time monitor. commercial colorimetric oxygen indicators. radical-bearing carbon with unpaired electrons. MB = \ce{MB^+Cl^-}.
+
+\cite{Spencer1979} monomer MB and dimer MB kinetics.
+
 \cite{Lee2003a}
 \begin{align}
-\cee{ 2LMB &\rightarrow LMB^*\\
+\cee{ 2LMB &->[\text{UV}] LMB^*\\
 2LMB^* + O2 &\rightarrow 2MB^+ + 2OH^-}
@@
 \[
-\cee{2LMB -> [\alpha] LMB^*}
-\cee{2LMB -> [\text{above}] LMB^*}
+\cee{2LMB ->[\alpha] LMB^*}
+\cee{2LMB ->[\text{above}] LMB^*}
 \]

### 2014-02-27 ch-tms/Seeded_growth_draft.tex
coreshell growth cont

@@
 \usepackage[version=3]{mhchem}
+%\usepackage{mhchem}
 \usepackage{mathpazo}
@@
 
-\FloatBarrier
 \subsection{Photocatalytic}
+
+ oxygen plasma treatment on HF-etched Si (001). reaction among $e$, \ce{O^+}, \ce{O2^+}, \ce{O^-},\ce{O2}. \ce{OH}-terminated surface obtained.\cite{Habib2010}
+
+MB is a heterocyclic aromatic dye which is blue colored in oxidizing environment.
+Upon reduction, MB is turned into colorless leuco MB.
+This can be used as an oxygen indicator in food industry.
+Photo-bleaching of MB can be also due to its leuco formation rather than total decomposition.
+Photocatalytic decomposition can be minimized by keeping the solution at acidic condition (PH = 4), which will limit the formation of oxidative hydroxyl radicals (E = 2.8 eV vs normal hydrogen electrode).
+Oxygen dissolved in the solution play a key role in conversion of LMB to MB under visible light.
+Purging with \ce{N2} for 20mins can remove dissolved oxygen.\cite{Wang2014a}
+
+\cite{Yoneyama1972} MB to LMB (\ce{C16H19N3S}) in aqueous solution upon illumination of \ce{TiO2}.
+The colorimetric analysis was performed in a glove box under nitrogen atmosphere.
+The absence of oxygen is important to prevent the oxidation of LMB to blue MB.
+\[
+\cee{MB^+ + H2O + H^+ \rightarrow MBH3^{2+} + 1/2O2}
+\]
+where MB represents the uncharged center of MB molecule.
+
+\cite{Takizawa1978} common wisdom expect that a dye incapable of injecting an electron at the excited state to CdS.
+MB, which process N-methyl groups in its molecular structure and does not sensitize CdS is an exemplary candidate.
+quantum efficiency is defined as probability of MB converted to azure B per incident photon.
+QE of CdS to MB decomposition is reduced in nitrogen bubbling treated solutions, indicating the necessity of oxygen.
+Two possible mechanisms: a) adsorbed oxygen acts as a trap for the conduction electron and prevent the accumulation of negative charge within space charge region of CdS, supported by the formation of \ce{O2^-} in excitation of CdS in aqueous suspension.
+
+ref 16, MB aqueous solution stability. Liquid chromatogram, azure B (trimethylthionine), and thionine. Electrochemical measurement,
+
+\cite{Matthews1989} MB adsorption.
+photocatalytic oxidation of MB by \ce{TiO2} film.
+photo-oxidation reaction occurs at the surface of photocatalyst.
+Mb molar extinction coefficient was found to be 66700 1/cm 1/M.
+Langmuir adsorption isotherm
+\[
+[MB]_{ads} = \frac{k_1 k_2 [MB]}{1 + k_1[MB]}
+\]
+and integrated form of Langmuir adsorption isotherm
+\[
+t = \frac{1}{k_1K} In\frac{[S]^0}{[S]} + \frac{1}{K}([S]^0 - [S])
+\]
+where $K = k_2 \phi N T_r$, with $\phi$ as quantum yield, N as total absorbed photons, and $T_r$ as rate of transport.
+\[
+\cee{C16H18N3SCl + 25.5O2 \rightarrow 16CO2 + 6H2O + 3HNO3 + H2SO4 +HCl}
+\]
+which indicates the total oxidation of $10 \mu M$ MB would exhause the ambient oxygen concentration of initially air-equilibrated solutions (about $250 \mu M$ ).
+ref 28 Thus the transport of both oxygen and MB to the photocatalyst surface are anticipated to be key factors.
+
+\cite{DeTacconi1997} photoelectrochromism at \ce{TiO2}/MB interface and its control.
+Efficient capture of photogenerated holes by a reducing agent is crucial to the reversibility of bleach-recoloration transition.
+This transition is kinetically dictated by electron transfer.
+Holes transfer is not desired.
+
+256 nm band is associated to the presence of LMB.
+LMB formation is not favored at alkaline pH values in aqueous solution.
+The OH radicals are generated either with the surface hydroxyl groups on \ce{TiO2} or with water, and its high oxidizing powder cause photocatalytic decomposition of the dye.
+
+An elementary step in decomposition of MB is N-dealkylation, which is preceded by radical cation formation.\cite{Takizawa1978} This radical cation can be spectroscopically monitored by the presence of 520nm band for MB.
+In MB absorption spectrum, 664 and 614 nm band ratio is related to monomer and dimer relaxation.
+\begin{align}
+\cee{TiO2 &\rightarrow e_{CB}^- + h_{VB}^+ \\
+h_{VB}^+ + red &\rightarrow ox\\
+MB^+ + 2e_{CB}^ + H^+ &\rightarrow LMB}
+\end{align}
+
+Measure the ratio between 614 and 663 nm before and after adding WS2 can indicate the adsorption of monomer and dimer MB.
+
+\cite{Mills1999} MB can act as sacrificial electron acceptor in the reduction to leuco form.
+The decomposition is favored under oxygen-rich environment.
+MB feature peaks at 663, 614 and 292 nm, and $\epsilon_{660}=10^5 M^{-1}cm^{-1}$.
+The doubly reduced form of MB, LMB has feature peak at 256 nm.
+The singly reduced form of MB, \ce{MB.^-} is pale yellow, with peak at 420nm.
+\begin{align}
+\cee{MB + e_{CB}^- &->[pH<7] MB^{.-} \\
+2MB^{.-} &\rightarrow MB + LMB\\
+O2 + e_{CB}^- &\rightarrow O2^{.-}}
+\end{align}
+
+The oxidized form of MB, \ce{MB.^+} has peak at 520nm, which is stable in acidic solution, but decomposes irreversibly in slight alkaline solution(pH = 9).
+thionine peaks at 600nm.
+MB forms dimers in aqueous solution,
+\ce{
+2MB <=>[K_D] (MB)_2
+}
+A typical value of $K_D$ is 3970 1/M. A quadratic equation can be solved to obtain the monomer concentration:
+\[
+2K_D [MB]^2 + [MB] - [MB]_{total} = 0
+\]
+MB adsorption on metal oxides. Monomer size is less than 1.5nm.
+Logarithmic acid dissociation constant $pK_a= -\log_10 \frac{[A^-][H^+]}{[HA]}$. The oxidation potential for \ce{H2O}-\ce{O2} couple is 1.23V and 0.817V versus NHE at pH 0 and pH 7, respectively.
+
+\ce{MB + SED ->[TiO2][h\nu \geq 3.2eV] LMB + SED^{2+}}
+
+\ce{2LMB + O2 \rightarrow 2MB + 2H2O}
+
+\cite{Lee2003a}
+\begin{align}
+\cee{ 2LMB &->[UV] LMB^*\\
+2LMB^* + O2 &\rightarrow 2MB^+ + 2OH^-}
+\end{align}
+
+\ce{2LMB ->[\ce{H2O}][ed] LMB^* }
+
+\ce{Zn^2+
+<=>[\ce{+ 2OH-}][\ce{+ 2H+}]
+$\underset{\text{amphoteres Hydroxid}}{\ce{Zn(OH)2 v}}$
+<=>C[+2OH-][{+ 2H+}]
+$\underset{\text{Hydroxozikat}}{\cf{[Zn(OH)4]^2-}}$
+}
+
+\ce{CO2 + C ->[hv][\beta] 2CO}
+
+\ce{$A$ ->[\ce{+H2O}] $B$}
+
+\ce{Hg^2+ ->[\ce{I-}]
+$\underset{\mathrm{red}}{\ce{HgI2}}$
+->C[I-]
+$\underset{\mathrm{red}}{\ce{[Hg^{II}I4]^2-}}$
+}
 

### 2014-02-28 BackMatter/paper.tex
moo3 and coreshell works

@@
 \midrule
--    &  +   & -  &   \\
--    &  -   & +  &   \\
-+    &  +   & -  &   \\
-+    &  +   & -  &   \\
-+    &  +   & -  &   \\
-+    &  +   & -  &   \\
+-    &  +   & -  &   about 50 $\mu m$ belts, some towers \\
+-    &  -   & +  &   irregular shape, not too much growth\\
+-    &  +   & +  &   droplet almost all on tip of belts, many towers \\
++    &  -   & -  &   tens $\mu m$ belt with sharp edge(100 nm thick, and 1micro wide) dominates\\
++    &  -   & +  &   exhibit ITO features, droplets on tips of belt, many tower like structures\\
++    &  +   & -  &   rounded edge flakes dominate, modest density tapering belt, and some possible tower\\
++    &  +   & +  &   ITO/glass features, aggregated belts, some towers\\
 \bottomrule
@@
 \end{figure}
+
+\begin{table}[htb]
+\centering
+\renewcommand*{\thetable}{S\arabic{table}}
+\caption{physical constants of reactants }\label{tb:thermo}
+\begin{tabular}{lccr}
+\toprule
+Material & MP(\si{\degreeCelsius}) & BP(\si{\degreeCelsius}) & reference\\
+\midrule
+\ce{NaOH}        & 318 & 1388 & handbook  \\
+\ce{NaI}        & 651 & 1300 & MSDS    \\
+\ce{KI}        & 681 & 1330 & MSDS   \\
+\ce{Na2CO3}        & 851 & Not determined & MSDS    \\
+\ce{Na2MoO4}        & 687 & Not available & handbook   \\
+\ce{MoO3}    & 795 & 1155 & MSDS   \\
+\ce{MoO2}    & 1100(decomp) & Not available & MSDS   \\
+\bottomrule
+\end{tabular}
+\end{table}
 

### 2014-02-28 ch-moox/moox.tex
moo3 and coreshell works

@@
 \caption{Crystal structures of alkali metal molybdates and tungstates}\label{tab:naxmow}
-\begin{tabular}{l1r}
+\begin{tabular}{llr}
 \toprule
@@
 \subsection{this work}
+
+The reactants used in this study were listed in Table.~\ref{tb:mosource}. All reactants were used as received without further processing.
+
+\begin{table}[htb]
+\centering
+\caption{Reactants list}\label{tb:mosource}
+\begin{tabular}{lcccr}
+\toprule
+Material & Stock No & LOT &Purity & Vendor\\
+\midrule
+\ce{NaOH}        & S318-500 & 070241 & 99.8\% & Fisher Scientific \\
+\ce{NaI}        & 11665 & K11W054 & 99.9\% &  Alfa Aesar \\
+\ce{KI}        & 42857 & H06Z051 & 99.9\% &  Alfa Aesar \\
+\ce{Na2CO3}        & 33377 & 114X012 & 99.95\% &  Alfa Aesar \\
+\ce{Molybdenum}        & 00932 & I07S024 & 99.9\% &  Alfa Aesar\\
+\bottomrule
+\end{tabular}
+\end{table}
+
 \textbf{Substrate treatment.} Silicon substrates(p-$\langle100\rangle$, University Wafers) were first cut into 10mm by 25mm pieces and ultrasonically cleaned with acetone and ethanol for 15 minutes(Branson 1510R-MTH), each followed by blow-drying with nitrogen gas.
@@
 Then oxygen flow varying between 0.1 sccm to 10 sccm (standard cubic centimeter per minute) was admitted from upstream inlet.
-With 10 sccm UHP Ar(99.999\%)as carrier gas, the overall pressure reached about 200 mTorr.
+With 10 sccm UHP Ar as carrier gas, the overall pressure reached about 200 mTorr.
 The heating temperature was ramped up to 800 \si{\degreeCelsius} in 30 minutes and lasted for 15 to 120 minutes.
@@
 Then the substrate was placed into chamber for growth, where all the parameters remained unchanged except the absence of Mo powder source.
+
+\textbf{Materials characterization.} The morphology and composition of the as-synthesized samples were analyzed by scanning electron microscopy (SEM,JEOL JSM-6480) and energy dispersive X-ray spectroscopy (EDS,Oxford Instrument INCA).
+Crystal structures were characterized using X-ray diffraction (XRD, PANXpert X’pert Pro MRD with Cu $K\alpha$ radiation at $\lambda$=1.5418\AA) and transmission electron microscopy (TEM, JEOL JEM-2100 \ce{LaB6} operated at 200kV).
+Optical measurements were performed by Micro-Raman spectroscopy (Horiba Scientific, Labram HR800 with 532 nm excitation laser) in a confocal microscope backscattering configuration with spectral resolution about 1 cm$^{-1}$.
+Optical absorption spectra was recorded using UV-Vis-NIR spectrophotometer(Schimadzu, UV2600Plus) in transmission mode.
+The as-synthesized sample was removed from substrates by light sonication(Branson 1510R-MTH, 70W) in ethanol for 15 seconds.
+The dispersion was left for 12 hrs to enable the possible sedimentation, after which became transparent under the unaided eye.
+Then the dispersion was transferred into one 10 mm quartz cuvette (Thorlabs, W005654) for absorption measurement with another paired cuvette containing ethanol only.
 
@@
 
-\begin{table}[htb]
-\centering
-\caption{Reactants list}\label{tb:source}
-\begin{tabular}{lcccr}
-\toprule
-Material & Stock No & LOT &Purity & Vendor\\
-\midrule
-\ce{NaOH}        & S318-500 & 070241 & 99.8\% & Fisher Scientific \\
-\ce{NaI}        & 11665 & K11W054 & 99.9\% &  Alfa Aesar \\
-\ce{KI}        & 42857 & H06Z051 & 99.9\% &  Alfa Aesar \\
-\ce{Na2CO3}        & 33377 & 114X012 & 99.95\% &  Alfa Aesar \\
-\ce{Molybdenum}        & 00932 & I07S024 & 99.9\% &  Alfa Aesar\\
-\bottomrule
-\end{tabular}
-\end{table}
-
 \textbf{tower-like structure}
@@
 \end{itemize}
+
+\subsection{glass growth}
+
+We studied the effect of temperature, oxygen partial pressure and growth time towards \ce{MoO3} deposition on glass substrates.
+Each factor is divided into two levels, with T at 700 and 800, \ce{O2} at 1 and 10 sccm, and growth time of 15 and 60 mins.
+We will assign $+$ and $-$ to higher and lower levels, respectively.
+And the morphological variation is summarized in Table~\ref{tab:mo3glass}.
+% glass growth matrix
+\begin{table}[htb]
+\centering
+\caption{\ce{MoO3} growth on glass}\label{tab:mo3glass}
+\begin{tabular}{lccp{3in}}
+\toprule
+\multicolumn{3}{c}{Growth Conditions} \\
+\cmidrule(l){1-3}
+ Temperature & \ce{O2} & Time & Morphology  \\
+\midrule
+-    &  +   & -  &   about 50 $\mu m$ belts, some towers \\
+-    &  -   & +  &   irregular shape, not too much growth\\
+-    &  +   & +  &   droplet almost all on tip of belts, many towers \\
++    &  -   & -  &   tens $\mu m$ belt with sharp edge(100 nm thick, and 1micro wide) dominates\\
++    &  -   & +  &   exhibit ITO features, droplets on tips of belt, many tower like structures\\
++    &  +   & -  &   rounded edge flakes dominate, modest density tapering belt, and some possible tower\\
++    &  +   & +  &   ITO/glass features, aggregated belts, some towers\\
+\bottomrule
+\end{tabular}
+\end{table}
+
+% droplet position statistics
+\begin{figure}[htb]
+\centering
+\includegraphics[width=0.6\textwidth]{droplets_sta}
+\caption[Droplet position statistics]{Droplet position statistics. On-tip and not-on-tip counts variation with respect to growth time. }
+\label{fig:mo3dropsta}
+\end{figure}

### 2014-02-28 ch-tms/Seeded_growth_draft.tex
moo3 and coreshell works

@@
 
-\ce{2LMB ->[\ce{H2O}][ed] LMB^* }
+\cite{Breault2013} \ce{TiO2} on MB degradation rate.
+aliquots, adsorption and desorption equilibrium and how to measure it.
+Discuss the distinguish of MB and LMB by nitrogen and oxygen purging.
+The author also mention the pH value change is an indictor of complete mineralization.
+The formatin of superoxide and hydroxyl radicals has been experimentally determined by radical quenchers.
+\ce{I^-} is a scavenger for VB holes, and \ce{.OH}. Adding 2mM KI will reduce the rate.
 
-\ce{Zn^2+
-<=>[\ce{+ 2OH-}][\ce{+ 2H+}]
-$\underset{\text{amphoteres Hydroxid}}{\ce{Zn(OH)2 v}}$
-<=>C[+2OH-][{+ 2H+}]
-$\underset{\text{Hydroxozikat}}{\cf{[Zn(OH)4]^2-}}$
+\begin{align}
+\cee{ WS2-WO3 + h\nu &-> e^- + h^+\\
+O2 + e^- &-> O2^{.-}\\
+OH_{surface}^- + h^+ &-> .OH\\
+MB^+ + O2^{.-} + .OH-> \text{degradation phases}
 }
+\end{align}
 
-\ce{CO2 + C ->[hv][\beta] 2CO}
-
-\ce{$A$ ->[\ce{+H2O}] $B$}
-
-\ce{Hg^2+ ->[\ce{I-}]
-$\underset{\mathrm{red}}{\ce{HgI2}}$
-->C[I-]
-$\underset{\mathrm{red}}{\ce{[Hg^{II}I4]^2-}}$
-}
+Energy diagram level alignment
 

### 2014-03-02 BackMatter/paper.tex
fix subsubsection numbering issus

@@
 \]
+\section{solar cell}
+
+DSC, ref 5, 10, 3, 2, 11.
+
+\ce{TiO2} NPs for high loading of sensitizing dye. Hole conducting electrolyte with \ce{I^-} and \ce{I3^-} concentration close to $10^19 cm^3$. chemical anchoring groups.
+
+electron injection rate. e transfer rate is several order faster than hole. 1 M = $6\times10^{20} cm^{-3}$. \ce{I^-} is known to coordinate with the sulfur atoms on NCS ligand. ref 31.
+
+FRET: dipole-dipole coupling, energy relay dye to sentisizing dye and then to \ce{TiO2}. analogous to photosynthesis bacteria. Time-resolved PL to measure FRET $R_0$.
 

### 2014-03-09 BackMatter/paper.tex
a low productivity week

@@
 
+Electronic structure of \ce{MoS2}.\cite{Eknapakul2014} K intercalating into bulk to create quasi-standing 1L.
+Large effective mass 0.6 $m_e$ found, implying low mobility.
+Direct gap 1.88eV is measured.
+
 \cite{Najmaei2014} Self-assembled monolayer (SAM) on \ce{SiO2} and its effect on \ce{MoS2} 1L.
@@
 
+a single nanowire tends to minimize its surface. 2D isoperimetric quotient or circularity $C= \frac{4\pi A}{P^2}$, where A is area and P is perimeter of the cross-section.
+
 oxygen plasma treatment on HF-etched Si (001). reaction among $e$, \ce{O^+}, \ce{O2^+}, \ce{O^-},\ce{O2}. \ce{OH}-terminated surface obtained.\cite{Habib2010}
@@
 
+photocatalyst review.\cite{Mills1997} Definition: catalysis should not be used unless it can be demonstrated that the turnover number\footnote{the number of product molecules per number of active sites.} is greater than unity.
+Otherwise, semiconductor-assisted photoreaction is more appropriate.
+aerated, flush with air; nitrogen-purged.
+Deggussa P25 \ce{TiO2} high temperature flame hydrolysis of \ce{TiCl4} in presence of hydrogen and oxygen.
+Oxidization of organic species is presumably obtained by \ce{Ti^{IV}OH^{.-}}, rather than direct hole transfer.
+carrier decay pathways.
+deactivation of catalyst by intermediate product.
+
+MB natural decoloration under sunlight is found to be about 18\%.\cite{Nogueira1993} Latitude: 24 south, $3.4mW/cm^2$. natural evaporation should be prevented or corrected.
+
+\section{dissertation}
+
+WS2 surface hydrophilic or hydrophobic.
+\[
+\cee{Ti(IV)-OCH3 + h^+ -> Ti(IV)-O^+CH3}
+\]
+
+\ce{WO3} photoanode should be a n-type semiconductor, stable in acidic aqueous solution.
+
+Swagelok TM. List of equipments,
+
 \section{vocabulary}
@@
 
-equation embodies the law of conservation
+equation embodies the law of conservation, excess, set in consequentially.
 
-become varied, laptop not hammer it hand, bubble pop, crash and burns. exert a marked influence
+become varied, laptop not hammer it hand, bubble pop, crash and burns. exert a marked influence, detrimental impact.
+
+theoretical interest, phase transition, water droplets, water vapor cools, supersaturates and nucleates. aerosol, sulfuric acid, subsaturated, corrosion. union, cross, T. moisture,

### 2014-03-09 ch-tms/Seeded_growth_draft.tex
a low productivity week

@@
 
+ Transition metal anchored to \ce{TiO2} review.\cite{Ardo2009} molecular approach, chemical bonds afford large energy storage capacities. 
+\begin{enumerate}
+   \item photo excitation of dye sensitizer to form a molecular excited state;
+   \item electron injection from HOMO to CB of semiconductor to cause e-h separation;
+   \item oxidized(loss of electron) sensitized is compensated by external donor;
+   \item external donor is compensated by the CB electron after performing useful works;
+   \item this is a typical operation of Gratzel cell. 
+\end{enumerate}
+
+Metal-to-ligand charge transfer (MLCT) ($d \rightarrow \pi^*$)
+
 \clearpage

### 2014-03-11 BackMatter/paper.tex
moox structure adjusted

@@
 
-\citeauthor{Hardcastle1990} summarized an empirical formula to relate the Raman peaks and \ce{Mo-O} bonding lengths.\cite{Hardcastle1990} This correlation assumes general form as
-\begin{equation}\label{eq:mobond}
-\nu = A \exp{B\cdot R},
-\end{equation}
-where $A=32895$ and $B=-2.073$ are fitting parameters, R is bond distance in unit of \AA.
-Given a stretching frequency, the resolution for calculated bond distance is $\pm0.016$\AA.
-The counterpart for \ce{W-O} bond \cite{Hardcastle1995} is
-\begin{equation}\label{eq:wobond}
-\nu = 25823 \exp{-1.902\cdot R},
-\end{equation}
-with standard deviation of estimating \ce{W-O} bond distance from Raman stretching wavenumber is $\pm0.034$\AA.
-Another empirical expression connect the bond valence $s$ and bond distance R: $s(M-O) \approx (R/X)^{-6} $, where X=1.882 when M is Mo, and 1.904 when M is W.
-The valence sum rule could be then used to check the state of Mo cation.
-It should be noticed that not all observed Raman lines could be correlated to a \ce{Mo-O} bond distance by extrapolation of Eq.~\ref{eq:mobond}.
-It is then regarded as a symmetry related vibrational mode, i.e.
-$820 cm^{-1}$ in \ce{MoO3}.
-From the correlation of various Mo compounds, a general conclusion is the lower the stretching frequency for the shortest metal-oxygen bond, the more regular is the structure.
-
 The molecular unit in crystal exhibits different vibrational frequencies from that in solution or gas phases.
@@
 
-Charge-density-wave states\footnote{In CDW states, conductivity is non-Ohmic above a threshold electric field} was found in blue bronze \ce{K_{0.3}MoO3}, which can be prepared by electrolytic reduction of \ce{K2MoO4} and \ce{MoO3} melt.\cite{Dumas1983} \ce{K_{0.3}MoO3} is side=centered monoclinic phase, with lattice parameter $a=18.249$\AA, $b=7.561$\AA, $c=9.856$\AA, and $\beta=117.54$ at RT.
-\ce{K0.3MoO3} presents a semiconductor-to-metal transition at 180 K.
-Electrical transport measurements yield an highly anisotropic ratio of DC conductivities of 1:10:1000.
-Along this high conducting axis, metallic reflection behavior is confirmed by optical measurements.
-Therefore, this blue bronze $\ce{K_{0.3}MoO3}$ is known as quasi-1D metal.\cite{Sing1999}
-
 \ce{MoO3}, an alternative interpretation in terms of tetrahedral coordination of Mo atoms is also proposed.
@@
 \ce{MoO_x} on n-type Si acts as a high work function metal (6.6eV), enabling a dopant-free contact and thus junctionless devices.
-
-We studied the effect of temperature, oxygen partial pressure and growth time towards \ce{MoO3} deposition on glass substrates.
-Each factor is divided into two levels, with T at 700 and 800, \ce{O2} at 1 and 10 sccm, and growth time of 15 and 60 mins.
-We will assign $+$ and $-$ to higher and lower levels, respectively.
-And the morphological variation is summarized in Table~\ref{tab:mo3glass}.
-% glass growth matrix
-\begin{table}[htb]
-\centering
-\caption{\ce{MoO3} growth on glass}\label{tab:mo3glass}
-\begin{tabular}{lccp{3in}}
-\toprule
-\multicolumn{3}{c}{Growth Conditions} \\
-\cmidrule(l){1-3}
- Temperature & \ce{O2} & Time & Morphology  \\
-\midrule
--    &  +   & -  &   about 50 $\mu m$ belts, some towers \\
--    &  -   & +  &   irregular shape, not too much growth\\
--    &  +   & +  &   droplet almost all on tip of belts, many towers \\
-+    &  -   & -  &   tens $\mu m$ belt with sharp edge(100 nm thick, and 1micro wide) dominates\\
-+    &  -   & +  &   exhibit ITO features, droplets on tips of belt, many tower like structures\\
-+    &  +   & -  &   rounded edge flakes dominate, modest density tapering belt, and some possible tower\\
-+    &  +   & +  &   ITO/glass features, aggregated belts, some towers\\
-\bottomrule
-\end{tabular}
-\end{table}
-
-% droplet position statistics
-\begin{figure}[htb]
-\centering
-\includegraphics[width=0.6\textwidth]{droplets_sta}
-\caption[Droplet position statistics]{Droplet position statistics. On-tip and not-on-tip counts variation with respect to growth time. }
-\label{fig:mo3dropsta}
-\end{figure}
 

### 2014-03-11 ch-moox/moox.tex
fix subsubsection numbering issus
moox structure adjusted

@@
 
-Molybdenum oxides \ce{MoO3} crystallizes in three phases, orthorhombic $\alpha$-\ce{MoO3}, monoclinic $\beta$-\ce{MoO3} and the metastable hexagonal h-\ce{MoO3}.\citep{Deb1968,Fibers2007} $\alpha$-\ce{MoO3} phase exhibits anisotropic structure with strong bonding along [001] and [100] direction while Van der Waals interaction along [010] direction.\cite{He2003} Due to this unique structure, \ce{MoO3} was found to have several important properties and a wide range of technological applications, such as electrochromism and photochromism,\cite{Yao1992} lubricants,\cite{Sheehan1996} photocatalysts,\cite{Chen2010} and gas sensor, including \ce{CO},\cite{Comini2005} \ce{NO2},\cite{Taurino2006} \ce{H2}\cite{Sha2009} and ethanol.\cite{Choopun} Moreover, other features arise when nanoscale \ce{MoO3} is specifically prepared, for instance, field emission.\citep{Li2002d,Zhou2003b}  As a layered hosting material, \ce{MoO3} can be further modified by intercalating with alkaline ions\citep{Spahr1995,Li2006b,Hu2011} and even divalent ion\cite{Sian2005}.
+Molybdenum oxides \ce{MoO3} crystallizes in three phases, orthorhombic $\alpha$-\ce{MoO3}, monoclinic $\beta$-\ce{MoO3} and the metastable hexagonal h-\ce{MoO3}.\citep{Deb1968,Fibers2007} $\alpha$-\ce{MoO3} phase (hereafter \ce{MoO3})exhibits anisotropic structure with strong bonding along [001] and [100] direction while Van der Waals interaction along [010] direction.\cite{He2003} Due to this unique structure, \ce{MoO3} was found to have several important properties and a wide range of technological applications, such as electrochromism and photochromism,\cite{Yao1992} lubricants,\cite{Sheehan1996} photocatalysts,\cite{Chen2010} and gas sensor, including \ce{CO},\cite{Comini2005} \ce{NO2},\cite{Taurino2006} \ce{H2}\cite{Sha2009} and ethanol.\cite{Choopun} Moreover, other features arise when nanoscale \ce{MoO3} is specifically prepared, for instance, field emission.\citep{Li2002d,Zhou2003b}  As a layered hosting material, \ce{MoO3} can be further modified by intercalating with alkaline ions\citep{Spahr1995,Li2006b,Hu2011} and even divalent ion\cite{Sian2005}.
 This structural richness have enabled improved performance in Li-ion\cite{Mai2007} and sodium-ion battery.\cite{Hariharan2013} In combination with \ce{TiO2} forming a core-shell structure, these nanoparitcles are reported to lower the photoabsorption energy of \ce{TiO2}.\cite{Elder2000} When combined with Ag as layered structure, transparent conducting behavior was observed.\cite{Nguyen2012} In addition, \ce{MoO3} is a good precursor for preparing other useful materials, such as \ce{MoS2} fullerenes\cite{Li2003c}, and few layer \ce{MoS2}.\cite{Lin2012} It will also be an important member of the Van der Waals heterostructures.\cite{Geim2013}
 
-It may be considered as built up of chains of \ce{MoO4} tetrahedra connected by the sharing of two oxygen corners with two neighbouring tetrahedra in $c$ axis.
+In this thesis, we developed a new method to prepare \ce{MoO3} by using alkaline oxides as catalysts.
+This newly discovered a vapor-liquid-solid growth mechanism produced two new \ce{MoO3} structures: long nanoribbons and microscale towers.
+We then investigated the phase and crystalline structures of these new morphologies, and demonstrated the application in photocatalyst and electrochromic devices.
+
+\section{Synthesis and Properties of Molybdenum Oxides}
+
+\subsection{Growth of molybdenum oxides}
+
+Researchers have been exploring a variety of methods to synthesized different \ce{MoO3} nanostructures.
+We will not try to exhaust these efforts since it has been well summarized in several review articles.\cite{He2003} So we only gave a brief introduction here.
+Most of these methods can be categorized into two groups: solution-based hydrothermal procedures \citep{Li2002b,Xia2006,Li2006a,Camacho-Bragado2006} and chemical vapor transport and deposition approaches.
+\citep{Zeng1998,Li2002c,Li2002d,Zhou2003b,Fibers2007,Yan2009}.
+Both methods have its own merits.
+Hydrothermal process usually need lower temperature(\textless 300 \si{\degreeCelsius}), but the duration is usually long and requires several post-growth processing steps; while vapor deposition demands relatively high temperature (\textgreater 500 \si{\degreeCelsius}) yet with a shorter time.
+Both methods are scalable for industrial applications.
+However the hydrothermal treatment seems to allow more  nanostructures control than do the vapor deposition method.
+Nanobelts,\cite{Li2002b} helical nanosheets, nanoflowers, prims-like rods\cite{Li2006a} and nanoribbons\cite{Camacho-Bragado2006} were obtained by the former one while nanoflakes,\cite{Chen2009} nanobelts\cite{Hu2009} and nanowires\citep{Zhou2003b,Chen2011b} dominated the product morphology for the latter one.
+The assistance of Au catalyst in vapor deposition only altered the orientation\cite{Yan2009} or served as preferred nucleation sites\cite{Cai2011} without producing new \ce{MoO3} structures.
+\citeauthor{Chithambararaj2013} prepared hexagonal \ce{MoO3} nanocrystal via hydrothermal method and demonstrated the photodegradation of MB under visible light.\cite{Chithambararaj2013} The efficiency dependence on catalysis/dye ratio, light intensity and temperature was studied.
+h-\ce{MoO3} was mostly synthesized using solution methods, where \ce{NH4+} and \ce{OH-} were possible structure directing and stable agents.
+The band gap of h-\ce{MoO3} estimated from diffusion reflection spectrum is $2.8\sim3.0eV$.
+Hexagonal phase of \ce{MoO3} is readily identified by the XRD pattern (strong peak at $2\theta=20^{\circ}$).
+
+In spite of these numerous growth of \ce{MoO3}, we point out that reports on VLS mechanism and other than Si substrates are still scarce.
+We will explore these relative new domains and present our results in Sec.~\ref{sec:result}.
+
+\subsection{Crystal structures and chemical features of molybdenum oxides}
+
+The coordination number of Mo in \ce{MoO3} is six, so usually \ce{MoO6} octahedra are considered as the building blocks.
+As shown in Fig, the layered structure consisting of zig-zag rows of edge-sharing \ce{MoO6} octahedra, while the rows are mutually connected by corners.
+
+While considering the fact that four of the six surrounding O atom are at distances from 1.67\AA to 1.95\AA, while the remaining two are as far as 2.25 and 2.33\AA, \ce{MoO3} could be considered as built up of chains of \ce{MoO4} tetrahedra connected by the sharing of two oxygen corners with two neighbouring tetrahedra in $c$ axis.
 The infinite chains of \ce{MoO4} tetrahedra from half-layers in the $ac$ plane.
-Two half-layers, which are stapled along $b$ axis, build up one \ce{MoO3} layer.
-When the two more distant oxygen are included for one molybdenum atom, the coordination can be regards a sixfold, i.e,, the layered structure consisting of zig-zag rows of edge-sharing \ce{MoO6} octahedra, while the rows are mutually connected by corners.\cite{Itoh2001a}
+Two half-layers, which are stapled along $b$ axis, build up one \ce{MoO3} layer.\cite{Itoh2001a} This also stress that the \ce{MoO6} octahedra are rather distorted.
 
-on \ce{MoO3} reviews.\cite{He2003}
-
-\citeauthor{Chithambararaj2013} prepared hexagonal \ce{MoO3} nanocrystal via hydrothermal method  and demonstrated the photodegradation of MB under visible light.\cite{Chithambararaj2013} The efficiency dependence on catalysis/dye ratio, light intensity and temperature was studied.
-h-\ce{MoO3} was mostly synthesized using solution methods, where \ce{NH4+} and \ce{OH.} were possible structure directing and stable agents.
-The band gap of h-\ce{MoO3} estimated from diffusion reflection spectrum is $2.8\sim3.0eV$.
-
-Hexagonal phase \ce{MoO3} is readily identified by the XRD pattern (strong peak at $2\theta=20^{\circ}$).
-
-\section{Syntheses Methods}
-\subsection{literature review}
-crystal-chemical principles.
 Due to the weak cation-oxygen bonding, alkali metal cations only introduce small perturbations into the energies of Mo-O or W-O ensembles in comparison to cations of other elements.
@@
 
-Assignment for \ce{A2MO4} is well grounded.
+Raman band assignment for \ce{A2MO4} is well grounded.
 Alkali metal cations with octahedral coordination occur below 230 $cm^{-1}$.
@@
 
-\subsection{this work}
+Molybdenum bronze also exhibits intriguing features, for instance, charge-density-wave states\footnote{In CDW states, conductivity is non-Ohmic above a threshold electric field} was found in blue bronze \ce{K_{0.3}MoO3}, which can be prepared by electrolytic reduction of \ce{K2MoO4} and \ce{MoO3} melt.\cite{Dumas1983} \ce{K_{0.3}MoO3} is side=centered monoclinic phase, with lattice parameter $a=18.249$\AA, $b=7.561$\AA, $c=9.856$\AA, and $\beta=117.54$ at RT.
+\ce{K0.3MoO3} presents a semiconductor-to-metal transition at 180 K.
+Electrical transport measurements yield an highly anisotropic ratio of DC conductivities of 1:10:1000.
+Along this high conducting axis, metallic reflection behavior is confirmed by optical measurements.
+Therefore, this blue bronze $\ce{K_{0.3}MoO3}$ is known as quasi-1D metal.\cite{Sing1999}
+
+\subsection{Synthesis methods in this theis}
 
@@
 
-\textbf{Synthesis.} In a typical synthesis, molybdenum powders were loaded into the uniform heating zone and the sealed chamber was first pumped down to 10 mTorr.
+\textbf{Synthesis.} In a typical synthesis (Fig.~\ref{fig:mooxgrowth}), molybdenum powders were loaded into the uniform heating zone and the sealed chamber was first pumped down to 10 mTorr.
 Then oxygen flow varying between 0.1 sccm to 10 sccm (standard cubic centimeter per minute) was admitted from upstream inlet.
@@
 
-\section{Discussion}
+\section{Discussion on molybdenum oxides}\label{sec:result}
 
@@
 Therefore temperature and possible impurity could potentially alter the growth mechanism.
-We divide the growth results into two categories: on Si substrate and on non-Si substrate to describe them respectively.
+We divide the growth results into two categories: on Si substrate and on non-Si substrate, and describe them respectively.
+We also briefly mention using liquid exfoliation to prepare few layer \ce{MoO3}.
 
@@
 Mo began to be oxidized into \ce{MoO3} at 500 \si{\degreeCelsius}, \ce{MoO3} vapor pressure began to increase rapidly above 700 \si{\degreeCelsius}.
-\cite{Margrave1967} And the MP of \ce{MoO3} is reported as 795 \si{\degreeCelsius}.
+\cite{Margrave1967} And the melting point of \ce{MoO3} is reported as 795 \si{\degreeCelsius}.
 With these facts in mind, we design the experimental parameters as listed in Table.~\ref{tab:mooxsi}.
@@
 
-This rectangular shape implies the boundary plane along growth direction (long axis) is (001), in consistency with previous experimental\cite{Zeng1998,Li2002b} and theoretical\cite{Firment1983,Cora1997} studies.
-We also observed different shapes, i.e., elongated hexagonal using similar growth conditions.
+This rectangular shape implies the boundary plane along growth direction (long axis) is (001), in consistency with previous experimental reports\cite{Zeng1998,Li2002b} and theoretical studies.\cite{Firment1983,Cora1997} We also observed different shapes, i.e., elongated hexagonal using similar growth conditions.
 This is not an indication of different growth mode.
 It is a normal thermodynamic fluctuation.
-In fact, (201), (101) and (102) planes have all been observed as terminating planes.\cite{Zeng1998} The stacking rate of \ce{MoO6} octahedra along a and c axis could develop some other ratio.
-And the coexistence of different planes in one growth suggests the similarity of free surface energies.
+The growth rates along different crystalline direction of \ce{MoO3} are determined by the free surface energy.
+In fact, (201), (101) and (102) planes have all been observed as terminating planes.\cite{Zeng1998} The stacking rate of \ce{MoO6} octahedra along $a$ and $c$ axis could develop some other ratio.
+And the coexistence of different planes in one growth suggests the similarity of free surface energies between these surfaces.
+In other words, the migration barrier of adatoms on (010) plane is presumably much lower than that on other low index planes due to the Van der Waals interaction nature along [010] direction.
 
@@
 In contrast, we shall see a different scenario in Section.~\ref{sec:nasi}, where the orientation is changed.
-The Raman spectrum of as-synthesized specimens also closely matches \ce{MoO3} features in previous studies.\cite{Dixit1986,Silveira2012} During m-Raman measurement, the laser spot was carefully focused onto the plates and several inspections on different positions were observed to ensure the reproductivity of spectra data.
-As shown in Fig.~\ref{fig:moram}, 14 distinct bands were well resolved.
-The 284 \si{cm^{-1}} peak represents the wagging mode for double bond \ce{O=Mo=O}.
-The 337 and 380  \si{cm^{-1}} peaks are assigned to \ce{O-Mo-O} bending and scissoring modes.
-The 199 \si{cm^{-1}} peak and two other weaker peaks at 218 and 247 \si{cm^{-1}} represent \ce{O=Mo=O} $B_{2g}$ twist, $A_g$ chain mode and \ce{O=Mo=O} $B_{3g}$ twist mode, respectively.
-667 \si{cm^{-1}} peak is assigned to triply coordinated oxygen stretching model resulting from edge-shared oxygen in common to three octahedral.
-The 819 \si{cm^{-1}} peak is from doubly coordinated oxygen stretching mode arising from corner-shared oxygen between two octahedral.
-The 996 \si{cm^{-1}} peak comes from unshared oxygen stretching mode.\cite{Siciliano2009} The assignment is summarized in Table.~\ref{tab:moram}.
 
@@
 \centering
-\caption{Experimental Raman peaks (\si{cm^{-1}}) assignment of \ce{MoO3} on Si.\cite{Eda1992,Siciliano2009}}\label{tab:moram}
+\caption{Experimental Raman peaks assignment of \ce{MoO3} on Si.\cite{Eda1992,Siciliano2009}}\label{tab:moram}
 \begin{tabular}{llcll}
 \toprule
-this work & Sym.       &          & Assignment &   \\
+this work(\si{cm^{-1}}) & Sym.       &          & Assignment &   \\
 \midrule
@@
 
-The growth rates along different crystalline direction of \ce{MoO3} are presumably determined by the free surface energy.
-In other words, the migration barrier of adatoms on (010) plane is presumably much lower than that on other low index planes due to the Van der Waals interaction nature along [010] direction.
+The Raman spectrum of as-synthesized specimens also closely matches \ce{MoO3} features in previous studies.\cite{Dixit1986,Silveira2012} During m-Raman measurement, the laser spot was carefully focused onto the plates and several inspections on different positions were observed to ensure the reproductivity of spectra data.
+As shown in Fig.~\ref{fig:moram}, 14 distinct bands were well resolved.
+The 284 \si{cm^{-1}} peak represents the wagging mode for double bond \ce{O=Mo=O}.
+The 337 and 380  \si{cm^{-1}} peaks are assigned to \ce{O-Mo-O} bending and scissoring modes.
+The 199 \si{cm^{-1}} peak and two other weaker peaks at 218 and 247 \si{cm^{-1}} represent \ce{O=Mo=O} $B_{2g}$ twist, $A_g$ chain mode and \ce{O=Mo=O} $B_{3g}$ twist mode, respectively.
+667 \si{cm^{-1}} peak is assigned to triply coordinated oxygen stretching model resulting from edge-shared oxygen in common to three octahedral.
+The 819 \si{cm^{-1}} peak is from doubly coordinated oxygen stretching mode arising from corner-shared oxygen between two octahedral.
+The 996 \si{cm^{-1}} peak comes from unshared oxygen stretching mode.\cite{Siciliano2009} The assignment is summarized in Table.~\ref{tab:moram}.
 
-\subsection{FL}
+\subsection{Liquid exfoliation on as-grown molybdenum oxides}
 
-FL materials attracts intensive research efforts recently.
-We first use liquid exfoliation method to prepare FL \ce{MoO3}.
+Few layer (FL) materials attracts intensive research efforts recently.
+We studied using liquid exfoliation method to prepare FL \ce{MoO3}.
 We then characterized the absorption feature and crystalline structures of the exfoliated \ce{MoO3} using UV-Vis and TEM.
@@
 This is not always the case.
-In chapter on the \ce{WS2} section, we do need to do so.
+In Chapter on the \ce{WS2} section, we do need to do so.
 
@@
 According to the corrected absorbance spectrum, optical band gap can be deduced, which is known as Tauc Plot.\cite{Tauc1972} The procedure is recapitulated here.
+Eq.~\ref{eq:tauc} is given to empirically relate optical band gap to absorption.
 
@@
 The value n is correlated to the nature of optical transition.
-For direct allowed transition, n = 1/2; For direct forbidden transition, n = 3/2; For indirect allowed transition, n = 2; And for indirect forbidden transition, n = 3.
+\begin{itemize}
+\item For direct allowed transition, n = 1/2;
+\item For direct forbidden transition, n = 3/2;
+\item For indirect allowed transition, n = 2; 
+\item And for indirect forbidden transition, n = 3.
+\end{itemize}
+
 When the transition nature of sample is not well known, one should apply each to check which one provide the best fit.
 Depending on the synthesis methods and \ce{MoO3} morphologies, the transition phenomena might vary.
-On the \ce{MoO3} films, \citeauthor{Bouzidi2003} assumed a direct gap (n = 1/2)\cite{Bouzidi2003} while \citeauthor{Szekeres2002} not.\cite{Szekeres2002} We use n = 2 in this work.
-We plot $\sqrt{(h\nu \alpha)}$ versus photon energy, and extrapolate the linear part onto $h\nu$ axis.
+On the \ce{MoO3} films, \citeauthor{Bouzidi2003} assumed a direct gap (n = 1/2)\cite{Bouzidi2003} while \citeauthor{Szekeres2002} not.\cite{Szekeres2002} We use n = 2 in this work, plot $\sqrt{(h\nu \alpha)}$ versus photon energy, and extrapolate the linear part onto $h\nu$ axis.
 The intercept is used as $E_g^{opt}$ then.
@@
 
-An alternative way is a) define $Y = \alpha E=\alpha h\nu$, and obtain $Y' = \frac{\partial Y}{\partial E}$, then b) plot $Y'/Y$ versus $h\nu$.
+An alternative apporach is a) define $Y = \alpha E=\alpha h\nu$, and obtain $Y' = \frac{\partial Y}{\partial E}$, then b) plot $Y'/Y$ versus $h\nu$.
 The band gap value can be obtained from the intercept of extrapolated line on photo energy axis.\cite{Choopun} This approach is not difficult to comprehend as long as we notice from Eq.~\ref{eq:tauc}, $Y = B (h\nu - E_g^{opt})^n$ and $Y' = B n(h\nu - E_g^{opt})^{n-1}$.
+The advantage is one can also estimate n without using assumption.
 
@@
 
-Nevertheless, identifying these few layer \ce{MoO3} under optical microscope is still difficult due to both the small flake size and low contrast.\footnote{Human eye threshold contrast (contrast sensitivity)$^{-1}$ is about}
+Nevertheless, identifying these few layer \ce{MoO3} under optical microscope is still difficult due to both the small flake size and low contrast.\footnote{Human eye threshold contrast (contrast sensitivity)$^{-1}$ is about 10\%.} One need to improve the liquid exfoliation process to obtain larger dimension and high yield.
+This is however beyond the scope of current study.
 
@@
 \includegraphics[width=0.6\textwidth]{Na2MoO4_Phase}
-\caption[Phase diagram of Na-Mo-O]{Phase diagram of \ce{Na2MoO4} and \ce{MoO3} reproduced from ref.~\cite{Hoermann1929}}
+\caption[Phase diagram of Na-Mo-O system]{Phase diagram of \ce{Na2MoO4} and \ce{MoO3} reproduced from ref.~\cite{Hoermann1929}}
 \label{fig:pd}
@@
 \end{itemize}
+
+\subsubsection{Phase evolution probing by Raman}
+
+\citeauthor{Hardcastle1990} summarized an empirical formula to relate the Raman peaks and \ce{Mo-O} bonding lengths.\cite{Hardcastle1990} This correlation assumes general form as
+\begin{equation}\label{eq:mobond}
+\nu = A \exp{B\cdot R},
+\end{equation}
+where $A=32895$ and $B=-2.073$ are fitting parameters, R is bond distance in unit of \AA.
+Given a stretching frequency, the resolution for calculated bond distance is $\pm0.016$\AA.
+Another empirical expression connect the bond valence $s$ and bond distance R: $s(M-O) \approx (R/X)^{-6} $, where X=1.882 when M is Mo, and 1.904 when M is W.
+The valence sum rule could be then used to check the state of Mo cation.
+It should be noticed that not all observed Raman lines could be correlated to a \ce{Mo-O} bond distance by extrapolation of Eq.~\ref{eq:mobond}.
+It is then regarded as a symmetry related vibrational mode, i.e.
+$820 cm^{-1}$ in \ce{MoO3}.
+From the correlation of various Mo compounds, a general conclusion is the lower the stretching frequency for the shortest metal-oxygen bond, the more regular is the structure.
+
+\textbf{Fundamental of VLS}
+
+Vapor-Liquid-Solid (VLS) process is first proposed by Wagner,\cite{Wagner1964} and further developed by \citeauthor{Givargizov1975}.\cite{Givargizov1975} This method has become an important strategy for synthesizing one-dimensional nanostructures.\cite{Lieber1998} Conventionally, a liquid eutectic droplet is formed by catalyst itself or by alloying with the growth material, acting as a trap of growth species.
+The growth is initialized by supersaturation of the liquid alloy and subsequent precipitation at the solid-liquid interface.
+The choice of catalyst usually is among the several noble metals since they are physically active but chemically stable or inert in most growth scenarios.
+The growth materials span a wide range including group IV,\cite{Hochbaum2005} group III-V,\citep{Dalacu2013, Xiao2012, Dubrovskii2011} group II-VI,\cite{Hao2006} and some metal oxides, such as \ce{ZnO},\citep{Huang2001a,Ramgir2010} \ce{MgO},\citep{HEUER1967, Nagashima2007} \ce{SiO2},\cite{Pan2002} and \ce{TiO2},\cite{Zhuge2012} to name a few.
+The catalysts can be Au, Pd, Pt, Ni,\cite{Xiao2012} Ti, Ga,\cite{Pan2002} and even KI.
+
+Understanding the interaction between liquid droplet and the solid interface allows for a rich engineering space to fine tune the geometry and structures of as-grown nanostructures.
+For instances, the diameter of Si nanowires (NWs) can be controlled by laser ablated catalyst\cite{Morales1998} or well-defined Au nanoparticles.\cite{Cui2001b} Under proper conditions,  axial modulation can produce nanowire superlattices from group IV and III-V materials.\citep{Gudiksen2002,Bjork2002}  Radial composition modulation have also been demonstrated by selectively suppressing VLS process, providing a robust routine for homogeneous or heterogeneous core-shell structures.\cite{Lauhon2002a}  \citeauthor{Wang2013c} changed the NW growth direction by changing the shape of droplets; \citeauthor{Biswas2013} reported enhanced aspect ratio of Ge NWs from bimetallic alloy.
 

### 2014-03-11 ch-tms/Seeded_growth_draft.tex
moox structure adjusted

@@
 
-$6\mu L$ Methylene Blue\footnote{\ce{C16H18N3SCl} molar mass 319.85g/mol.} (Alfa Aesar 42771, 1\%w/v = 31.26 mM) in diluted into 20 mL DI water, giving ultimate concentration as $9.38 \mu M$.
+Photocatalytic performance of as-synthesized core-shell NWs was evaluated by measuring the degradation of MB.
+Xe-Hg lamp ( ) and a liquid filter were used to provide UV and visible irradiation and a glass filter was applied to cut off UV light (below 420 nm).
+All vessel and beaker are of borosilicate glass type (Pyrex), which was reported to adsorb little MB.\cite{Chakrabarti2005} In a typical experiment, 10 mL aqueous solution containing about 1 mg sample was mixed with 50 mL of $10 \mu M$ MB solution.
+The mixture was magnetically stirred in dark for 1 hr to allow for MB adsorption, during which the solution was sampled several times for UV-Vis measurement to confirm the equilibrium and to serve as reference point.
+Then the solution was continuously purged with oxygen or argon (20 sccm) and magnetically stirred (80 rmp) throughout the reaction process.
+No thermal bath was used but the solution temperature was monitored and the variation was found to be less than 3 K.
+Sample of the solution was withdraw regularly with respect to irradiation time, placed into a quartz cuvette and capped with plastic septum to isolate external moisture.
+The UV-Vis absorbance spectra were taken in a two beam configuration, with a paired quartz cuvette containing DI water as reference.
+The catalyst absorbance spectrum only provide a scattering background onto which the MB spectra is superimposed.
+Thus no centrifugation is employed since it does not interfere with evaluating absorbance of MB.
+The extent to which MB is photodecomposed was calculated the absorbance variation at 663nm.
+It has been known that MB can also be reduced to colorless lecuo form with absorption peak at 256 nm in aqueous solution.\cite{Mills1999} This might cause overestimation of the photocatalyst efficiency.
+To avoid this ambiguity, the possible formation of lecuo MB was probed by oxygen purging the solution in dark and measuring the UV-Vis spectrum again.
+
+Methylene Blue\footnote{\ce{C16H18N3SCl} molar mass 319.85g/mol.} (Alfa Aesar 42771, 1\%w/v = 31.26 mM) is diluted into DI water to prepare reaction solution with concentration about $10 \mu M$.
 The measured absorbance spectrum is shown in supporting information, with maximum absorbance 0.42 at 664nm.
@@
 
-\cite{Breault2013} \ce{TiO2} on MB degradation rate.
+ \ce{TiO2} on MB degradation rate.
 aliquots, adsorption and desorption equilibrium and how to measure it.
@@
 The author also mention the pH value change is an indictor of complete mineralization.
-The formatin of superoxide and hydroxyl radicals has been experimentally determined by radical quenchers.
+The formatin of superoxide and hydroxyl radicals has been experimentally determined by radical quenchers.\cite{Breault2013}
 \ce{I^-} is a scavenger for VB holes, and \ce{.OH}. Adding 2mM KI will reduce the rate.

### 2014-03-19 BackMatter/paper.tex
intro contents added

@@
 
-An empirical formula to relate the Raman peaks and \ce{W-O} bonding lengths \cite{Hardcastle1995} is
-\begin{equation}\label{eq:wobond}
-\nu = 25823 \exp{-1.902\cdot R}.
-\end{equation}
-And the standard deviation of estimating \ce{W-O} bond distance from Raman stretching wavenumber is $\pm0.034$\AA.
-The observed Raman peaks of \ce{Na5W_{14}O_{44}} phase lies at 965, 943, 913, 808, 786, 778, 765, 695 and 107 cm.
-Multi-peaks Lorentzian fitting is preformed to precisely determine the central maximum.
-Good fitting is obtained, as shown in Fig.~\ref{fig:naworamfit}.
-We then calculated \ce{W-O} bond distance using Eq.~\ref{eq:wobond}, as illustrated in Table~\ref{tab:nawobond}.
-The predicted \ce{W-O} bond length comply very well with the crystallographic value of \ce{Na5W_{14}O_{44}} phase.\cite{Triantafyllou1999a} The 107 peak probably is caused by \ce{Na-O} bond.
-% Na5 raman fitting
-\begin{figure}[htb]
-\centering
-\includegraphics[width=0.6\textwidth]{naxwo_ramfit}
-\caption[\ce{Na5W_{14}O_{44}} Raman fitting]{Multi-peaks Lorentzian fitting on two major peaks region of \ce{Na5W_{14}O_{44}}.
-The peaks sum height difference is caused by different baseline value adopted in each fitting.}
-\label{fig:naworamfit}
-\end{figure}
+W plasma oxidation.\cite{Romanyuk2005} 200nm W coating on Si (100) sub, temperature at RT, 390, and 490 C, oxygen pressure 0.5 Pa, oxidation time for 10 sec to 3600 sec.
+The resultant thickness of \ce{WO3} at RT  and time of 10 sec and 3600 sec is found to be 0.2nm and 11 nm respectively.
 
-% W-O bond length
-\begin{table}[htb]
-\centering
-\caption{\ce{W-O} bond length predication}\label{tab:nawobond}
-\begin{tabular}{lccr}
-\toprule
-peak center & length (\AA) & peak center & length (\AA) \\
-\midrule
-694.6 & 1.900 &  808.6 &  1.821 \\
-745.4 & 1.863 &  911.5 &  1.758 \\
-764.4 & 1.850 &  933.0 &  1.745 \\
-778.7 & 1.840 &   943.5 & 1.740 \\
-788.4 & 1.834 &   965.4 & 1.728 \\
-\bottomrule
-\end{tabular}
-\end{table}
+\[
+ d = d_0 exp(kt)
+\]
+
+after fitting, $d_0 = 0.19777 nm$, $k = 0.00112 sec^{-1}$, so to oxidize 1nm W coating completely, oxygen plasma time is 1450 sec at 0.5Pa partially pressure; 2 nm for 2000 sec.
 
@@
 
+\ce{WO3} catalyst.\cite{Miyauchi2013}  potential of CB e more negative than redox potential of \ce{O2}-\ce{O2^-} (-0.046 V vs NHE at pH 0).
+Z-scheme two photo absorption.
+photogenerated ele in CB of WO3 can reduce itself by formation of color centers.
+
 \ce{WO3} indirect gap 2.6eV, direct gap 3.4eV. \cite{Koffyberg1979}
 
-Fingerprint of m-\ce{WO3}, h-\ce{WO3} and \ce{WO3,nH2O} were summarized in ref\cite{Daniel1987}.
+Fingerprint of m-\ce{WO3}, h-\ce{WO3} and \ce{WO3.nH2O} were summarized in ref\cite{Daniel1987}.
 
@@
   A low recombination rate is preferred for high photocatalytic efficiency. The simultaneous migration of electrons and holes.
+
+An empirical formula to relate the Raman peaks and \ce{W-O} bonding lengths \cite{Hardcastle1995} is
+\begin{equation}\label{eq:wobond}
+\nu = 25823 \exp{-1.902\cdot R}.
+\end{equation}
+And the standard deviation of estimating \ce{W-O} bond distance from Raman stretching wavenumber is $\pm0.034$\AA.
+The observed Raman peaks of \ce{Na5W_{14}O_{44}} phase lies at 965, 943, 913, 808, 786, 778, 765, 695 and 107 cm.
+Multi-peaks Lorentzian fitting is preformed to precisely determine the central maximum.
+Good fitting is obtained, as shown in Fig.~\ref{fig:naworamfit}.
+We then calculated \ce{W-O} bond distance using Eq.~\ref{eq:wobond}, as illustrated in Table~\ref{tab:nawobond}.
+The predicted \ce{W-O} bond length comply very well with the crystallographic value of \ce{Na5W_{14}O_{44}} phase.\cite{Triantafyllou1999a} The 107 peak probably is caused by \ce{Na-O} bond.
+% Na5 raman fitting
+\begin{figure}[htb]
+\centering
+\includegraphics[width=0.6\textwidth]{naxwo_ramfit}
+\caption[\ce{Na5W_{14}O_{44}} Raman fitting]{Multi-peaks Lorentzian fitting on two major peaks region of \ce{Na5W_{14}O_{44}}.
+The peaks sum height difference is caused by different baseline value adopted in each fitting.}
+\label{fig:naworamfit}
+\end{figure}
+
+% W-O bond length
+\begin{table}[htb]
+\centering
+\caption{\ce{W-O} bond length predication}\label{tab:nawobond}
+\begin{tabular}{lccr}
+\toprule
+peak center & length (\AA) & peak center & length (\AA) \\
+\midrule
+694.6 & 1.900 &  808.6 &  1.821 \\
+745.4 & 1.863 &  911.5 &  1.758 \\
+764.4 & 1.850 &  933.0 &  1.745 \\
+778.7 & 1.840 &   943.5 & 1.740 \\
+788.4 & 1.834 &   965.4 & 1.728 \\
+\bottomrule
+\end{tabular}
+\end{table}
+
 \textbf{\ce{WS2}-\ce{WO3}}: 1 kW light source(Hg, or Xe lamp), photon flux, phenol (\ce{C6H5OH}, 94.1g/mol, MP 40C)concentration is 20 mg/L, hydroxyl group.
@@
 \section{MoO3}
+
+\ce{MoO3} ECD:
+
+piranha clean of FTO.
+50ms switch.\cite{Scherer2012} nanoscale Kirkendall effect: the outward diffusion of metal cations are balanced by an influx of vacancies.
+For example, diffusion coefficient of Ni in NiO is higher than that of oxygen.
+\subsection{EC windows and thin film batteries}
+
+\ce{WO3} as cathodic and either polyaniline(PANI) or Prussian white (PW) as anodic electrochromic half cells. \cite{Heckner2002}
+
+Characterization of ECD includes transmission measurement and associated EC calculation, charge-discharge time, current-time curve and the fitting of obtained data.
+
+\begin{quote}
+a viable electrochromic smart window must exhibit a cycling life time \textgreater $10^5$ cycles, corresponding to an operation life at 10 - 20 years.
+\end{quote}
+
+\citeauthor{Sella1998} studied the optical and structural properties of RF sputtered thin film of \ce{WO3} and \ce{VO2} for electrochromic devices.
+Ionic conductor was built using transparent polymer electrolyte, which was prepared from a solution of 1M \ce{LiClO4} in propylene carbonate which was mixed with methylmetharcylate (MMA).
+The main characteristics of polymer electrolyte were: viscosity at 25 \si{\degreeCelsius} $\approx$ 12920 Pa.s, conductivity $\approx 10^{-2}-10^{-4}$\si{\per\ohm\per cm},non-hygroscopic if PMMA concentration \textgreater 30\%.
+A specific counter-electrode layer was not used since the encapsulated polymer electrolyte processes a very high ion storage capacity.
+
+The device proposed was reproduced as shown in Fig.~\ref{fig:Sella1998ECD}
+\begin{figure}[htb]
+    \centering
+    \includegraphics[angle=270,width=0.8\textwidth]{Sella1998ECD}
+    \caption{citation, see original captions} \label{fig:Sella1998ECD}
+\end{figure}
+
+\subsection{experimental setup}
+
+applications: electrically controlled optical shutters for heat and light modulation, smart windows associated with solar cell to provide dynamical control of incoming illumination.
+
+\begin{table}[htb]
+\caption{Combinations of ECD configuration}\label{tb:ecd}
+\begin{tabular}{lcccr}
+\toprule
+TC(both side) & electrochromic & ion conductor & counter electrode  & reference\\
+\midrule
+ITO &  \ce{WO3} & \ce{H^+\hyphen} polymer & PANI &\citeauthor{Heckner2002}\\
+FTO &  \ce{WO3} & \ce{K^+\hyphen} polymer & PW &\citeauthor{Heckner2002}\\
+ITO & \ce{WO3} NWs & \ce{LiClO4\hyphen}PC & none & author design \\
+\ce{Na_xWO3} NWs &\ce{WO3} NWs & \ce{LiClO4\hyphen}PC & none & author design\\
+\bottomrule
+\end{tabular}
+\end{table}
+
+\begin{table}[htb]
+\centering
+\caption{Comparison of MoOx ECD}\label{tab:moxecd}
+\begin{tabular}{lcccr}
+\toprule
+$\lambda$ & $\Delta T$ & $t_c$ & $t_b$ & $CE$}  \\
+         (nm) & (\%)    & (s) & (s) & ($cm^2/C$)  \\
+\midrule
+Range      & RT-1100    & 10mTorr-1atm & 0 - 100 & 0-30  \\
+\bottomrule
+\end{tabular}
+\end{table}
+
+10nm MoOx as hole extraction layer (HEL).
+Without HEL, Holes accumulates at QD/anode interface, causing increased recombination rate.
+With HEL, hole diffuse into this layer, reducing the recombination.
 
@@
 
+intrinsic silicon equilibrium charge carrier concentration at RT is $n_i = p_i = 1.5 \times 10^{10} cm^{-3}$, much smaller than silicon atoms density as $5\times 10 ^{22} cm^{-3}$.
+
+The average distance between dopant atoms is cubed root of concentration, $d = (10^{18} cm^{-3})^{-1/3} = 10nm$.
+
+The electron mobility $\mu_n = 1500 cm^2/V\cdot sec $ at RT for Si, and hole mobility $\mu_p = 450 cm^2/V\cdot sec$ at RT.
+
+for p-type silicon, when the conductivity $\sigma = 1 (ohm cm )^{-1}$, the doping level is
+$N_A = \frac{\sigma}{q \mu_p}= 1 / (1.6E-19 \times 450) = 1.4E16 cm^{-3}$.
+
+Built-in voltage $V_0 = \frac{kT}{q}ln(N_A N_D/n_i^2)$, depletion region width $W = \sqrt{\frac{2 \epsilon_{Si} V_0}{q}(1/N_A + 1/N_D)}$, where $\epsilon_{Si} = 11.7 \epsilon_0$.
+When applying external field, depletion width $W = \sqrt{\frac{2 \epsilon_{Si} (V_0 - V) }{q}(1/N_A + 1/N_D)}$
+
+The capacitance of p-n junction is $C = A \sqrt{\frac{q \epsilon_{Si}}{2(V_0 -V)}(N_D N_A/(N_A + N_D))}$.
+
 a single nanowire tends to minimize its surface. 2D isoperimetric quotient or circularity $C= \frac{4\pi A}{P^2}$, where A is area and P is perimeter of the cross-section.
@@
 aerated, flush with air; nitrogen-purged.
-Deggussa P25 \ce{TiO2} high temperature flame hydrolysis of \ce{TiCl4} in presence of hydrogen and oxygen.
+Degussa P25 \ce{TiO2} high temperature flame hydrolysis of \ce{TiCl4} in presence of hydrogen and oxygen.
 Oxidization of organic species is presumably obtained by \ce{Ti^{IV}OH^{.-}}, rather than direct hole transfer.
@@
 
+strike the wafer, sputter etching and plasma etching .
+
 experience an enormous development, principles underlying, scarce.
@@
 theoretical interest, phase transition, water droplets, water vapor cools, supersaturates and nucleates. aerosol, sulfuric acid, subsaturated, corrosion. union, cross, T. moisture,
+
+\subsection{pronunciation}
+
+chamber, vias, valve, figure, energetic, managerial, inert, volatile,

### 2014-03-19 ch-intro/ch-intro.tex
intro contents added

@@
 
-\textbf{Magnetic Sputtering} Sputtering, a process in which atoms are ejected from a solid target material by bombarding it with energetic particles, is a well established PVD process with a high degree of controllability.
+\textbf{Magneton Sputtering} Sputtering, a process in which atoms are ejected from a solid target material by bombarding it with energetic particles, is a well established PVD process with a high degree of controllability.
 The high energy and controllable parameters of sputtering can result in the growth of well-structured and crystalline films.
@@
 It is widely utilized for deposition of \ce{WO_x} in industry.
+
+Sputtering is a better PVD technique than e-beam deposition since it alleviates the adverse effects in the latter.
+\ce{Ar+} ions are accelerated to target foils.
+The pressure of \ce{Ar+} has two functions: to sputter off the target ions, and to influence the mean free path.
+These collisions between target ions and \ce{Ar+} leads to almost all arrival angle, thus uniform coverage.
+The sputter yield is No of target ions released per ions hitting on target.
+If \ce{Ar+} ion energy is less than 100eV, the yield is zero; If larger than 10 keV, implantation of \ce{Ar+} into target foils occurs.
+Usually yield between 1 and 2 is desired.
+
+The MFP in sputtering is on order of 3 cm (assuming pressure 30mTorr), with source-to-substrate distance as 5cm, average No of collisions is about 5/3$\sim$2.
 

### 2014-03-21 BackMatter/paper.tex
change to lualatex engine

@@
 \section{WO3}
+
+DFT doped \ce{WO3} for photocatalytic reaction.\cite{Wang2012} CBM arises from W $5d$ states and splits into $t_{2g}$ and $e_g$ states under crystal field.
+VBM comes from O $2p$ states, including $2p_\sigma$ (along \ce{W-O} bonds) and $2p_\pi$ (normal to \ce{W-O} bonds).
+
+oxygen vacancies in \ce{WO_{3-x}}.\cite{Wang2011b}  Coloration and electron conductivity changes.
+\citeauthor{Wang2011b} found strong dependence of WO3-x electronic properties on $V_O$ concentration and the the crystallographic direction on which O is removed.
+DFT band gap calculation is close to experimental value.
+Vacancy levels are found at 2.1eV.
 
@@
 
+battery and ECD.\cite{Granqvist2012} electrolyte: PVB (poly vinyl buteral).
+alternative materials and design: organic, Prussian Blue as EC materials, metal hydrides, suspended particle device, liquid crystal, electroplating,
+challenges: large area nanoporosity, transparent conducting contact, electrolyte with good ionic conductivity and poor electronic conductivity, stable under UV; assembly and large scale manufacturing;
+cathodic coloration:
+anodic coloration:
+The coloration mechanism: \ce{MO6} octahedrons lead to $e_g$ and $t_{2g}$ level and ion channelling.
+ref54,60,65,66,200,209,
+
 \ce{WO3} as cathodic and either polyaniline(PANI) or Prussian white (PW) as anodic electrochromic half cells. \cite{Heckner2002}
@@
 The main characteristics of polymer electrolyte were: viscosity at 25 \si{\degreeCelsius} $\approx$ 12920 Pa.s, conductivity $\approx 10^{-2}-10^{-4}$\si{\per\ohm\per cm},non-hygroscopic if PMMA concentration \textgreater 30\%.
-A specific counter-electrode layer was not used since the encapsulated polymer electrolyte processes a very high ion storage capacity.
+A specific counter-electrode layer was not used since the encapsulated polymer electrolyte processes a very high ion storage capacity.\cite{Sella1998}
 
@@
 ITO &  \ce{WO3} & \ce{H^+\hyphen} polymer & PANI &\citeauthor{Heckner2002}\\
-FTO &  \ce{WO3} & \ce{K^+\hyphen} polymer & PW &\citeauthor{Heckner2002}\\
+FTO &  \ce{WO3} & \ce{K^+\hyphen} polymer & PW &\cite{Heckner2002}\\
 ITO & \ce{WO3} NWs & \ce{LiClO4\hyphen}PC & none & author design \\
@@
 \toprule
-$\lambda$ & $\Delta T$ & $t_c$ & $t_b$ & $CE$}  \\
+$\lambda$ & $\Delta T$ & $t_c$ & $t_b$ & $CE$  \\
          (nm) & (\%)    & (s) & (s) & ($cm^2/C$)  \\
@@
 
-\cite{Najmaei2014} Self-assembled monolayer (SAM) on \ce{SiO2} and its effect on \ce{MoS2} 1L.
+Self-assembled monolayer (SAM) on \ce{SiO2} and its effect on \ce{MoS2} 1L.\cite{Najmaei2014}
 
-\cite{Ma2011} \ce{WS2} 1L doping calculation.
+\ce{WS2} 1L doping calculation. \cite{Ma2011}
 
-\cite{Britnell2013} G/\ce{WS2}/G stacked solar cell. For lubricant, and surface protection. Absorption $\sim 10^7 m^{-1}$.
+G/\ce{WS2}/G stacked solar cell. For lubricant, and surface protection. Absorption $\sim 10^7 m^{-1}$. \cite{Britnell2013}
 
-\cite{Cong2013} A direct gap of $\sim 2eV$ at the corners of BZ is formed in 1L \ce{WS2}, Growth on bottom piece show the multiple domain flakes occurs at initial stage of the growth, starting from \ce{WO3} particles.
+A direct gap of $\sim 2eV$ at the corners of BZ is formed in 1L \ce{WS2}, Growth on bottom piece show the multiple domain flakes occurs at initial stage of the growth, starting from \ce{WO3} particles.
+%\cite{Cong2013}
 
@@
 
-(Shi, Pan, Zhang, \& Yakobson, 2013) studied the strained monolayer \ce{MoS2} and WS2.
+(Shi 2013) studied the strained monolayer \ce{MoS2} and WS2.
 The results show that exciton binding energy is insensitive to the strain, while optical band gap becomes smaller as strain increases.
@@
 
-(Kośmider \& Fernández-Rossier, 2013) studied the heterojunction between two monolayers of \ce{MoS2} and WS2.
-Top of VB in W layer and bottom of CB in Mo layer, forming type II structure.
-bilayer gap 1.2 eV.
+(Rossier, 2013) studied the heterojunction between two monolayers of \ce{MoS2} and WS2. Top of VB in W layer and bottom of CB in Mo layer, forming type II structure. bilayer gap 1.2 eV.
 
@@
 
-Sulfurizaiton of W film, (Jäger-Waldau, Lux-Steiner, Jäger-Waldau, \& Bucher, 1993)
+Sulfurizaiton of W film, (Waldau1993)
 
@@
 
-WS2 monolayer and intense photoluminescent behavior. Sulfurization of WO3 film( 5-20 angstrom). (Gutiérrez et al. 2012)
+WS2 monolayer and intense photoluminescent behavior. Sulfurization of WO3 film( 5-20 angstrom).
+%(Gutiérrez et al. 2012)
 
@@
 
-WO3-x (1nm) on SiO2/Si sulfurization at 750-950 degree, (Elías et al. 2013)\cite{Elias2013}
+WO3-x (1nm) on SiO2/Si sulfurization at 750-950 degree,\cite{Elias2013}
 
@@
 
-\cite{Chen2013j} To develop large-size single-crystal graphene on dielectric substrates.
+To develop large-size single-crystal graphene on dielectric substrates.
 small carbon flow near-equilibrium CVD process.
@@
 I2D/IG exceeds two on \ce{SiO2}-Si subs (514.5nm), indicating monolayer G.
-armchair (AC) G edge grows faster than zigzag (ZZ) edge.
+armchair (AC) G edge grows faster than zigzag (ZZ) edge.\cite{Chen2013j}
 
-\cite{Weatherup2013} catalytic graphitization of solid carbon sources.
+catalytic graphitization of solid carbon sources.
 catalytic transformation, the source is in solid state, low temperature (less than 600C), 2nm  \ce{Al2O3} by ALD as carbon diffusion barrier.
-amorphous silicon (a-Si), Ni lower the activation barrier ,  tetrahedral amorphous carbon (ta-C).
+amorphous silicon (a-Si), Ni lower the activation barrier ,  tetrahedral amorphous carbon (ta-C).\cite{Weatherup2013}
 
-\cite{Bangert2013} low energy (50eV) ion implantation doping in G.
+low energy (50eV) ion implantation doping in G.
 Ions penetrate pristine G at energy larger than 100eV.
@@
 1\% doping level was obtained.
+\cite{Bangert2013}
 
-\cite{Wu2013b} CVD G on copper. Size of single crystal domain and nucleation site density.
+CVD G on copper. Size of single crystal domain and nucleation site density.\cite{Wu2013b}
 
@@
 
-\cite{Ahlgren2011}  low energy ion doping of graphene.
+low energy ion doping of graphene.\cite{Ahlgren2011}
 
@@
 
-\cite{Wang2014a} MB is a heterocyclic aromatic dye which is blue colored in oxidizing environment.
+MB is a heterocyclic aromatic dye which is blue colored in oxidizing environment.
 Upon reduction, MB is turned into colorless leuco MB.
@@
 Purging with \ce{N2} for 20mins can remove dissolved oxygen.
+\cite{Wang2014a}
 
@@
 
-\cite{Takizawa1978} common wisdom expect that a dye incapable of injecting an electron at the excited state to CdS.
+common wisdom expect that a dye incapable of injecting an electron at the excited state to CdS.
 MB, which process N-methyl groups in its molecular structure and does not sensitize CdS is an exemplary candidate.
@@
 QE of CdS to MB decomposition is reduced in nitrogen bubbling treated solutions, indicating the necessity of oxygen.
-Two possible mechanisms: a) adsorbed oxygen acts as a trap for the conduction electron and prevent the accumulation of negative charge within space charge region of CdS, supported by the formation of \ce{O2^-} in excitation of CdS in aqueous suspension.
+Two possible mechanisms: a) adsorbed oxygen acts as a trap for the conduction electron and prevent the accumulation of negative charge within space charge region of CdS, supported by the formation of \ce{O2^-} in excitation of CdS in aqueous suspension.\cite{Takizawa1978}
 
@@
 
-\cite{Matthews1989} MB adsorption.
+MB adsorption.
 photocatalytic oxidation of MB by \ce{TiO2} film.
@@
 Mb molar extinction coefficient was found to be 66700 1/cm 1/M.
-Langmuir adsorption isotherm
+Langmuir adsorption isotherm.\cite{Matthews1989}
+
 \[
@@
 
-\cite{DeTacconi1997} photoelectrochromism at \ce{TiO2}/MB interface and its control.
+photoelectrochromism at \ce{TiO2}/MB interface and its control.
 Efficient capture of photogenerated holes by a reducing agent is crucial to the reversibility of bleach-recoloration transition.
 This transition is kinetically dictated by electron transfer.
-Holes transfer is not desired.
+Holes transfer is not desired.\cite{DeTacconi1997}
 
@@
 
-\cite{Mills1999} MB can act as sacrificial electron acceptor in the reduction to leuco form.
+MB can act as sacrificial electron acceptor in the reduction to leuco form.
 The decomposition is favored under oxygen-rich environment.
@@
 The doubly reduced form of MB, LMB has feature peak at 256 nm.
-The singly reduced form of MB, \ce{MB.^-} is pale yellow, with peak at 420nm.
+The singly reduced form of MB, \ce{MB.^-} is pale yellow, with peak at 420nm.\cite{Mills1999}
 \[
@@
 
-\[
-\cee{MB + SED &->[TiO2][h\nu \leq 3.2eV] LMB + SED^{2+}\\
-2LMB + O2 &\rightarrow 2MB + 2H2O\\
-
-}
-\]
+%\begin{align}
+%\cee{MB + SED &->[TiO2][h\nu \leq 3.2eV] LMB + SED^{2+}\\
+%2LMB + O2 &\rightarrow 2MB + 2H2O}
+%\end{align}
 
@@
 
-\cite{Galagan2008} Mb to LMB transition as visual time monitor. commercial colorimetric oxygen indicators. radical-bearing carbon with unpaired electrons. MB = \ce{MB^+Cl^-}.
+Mb to LMB transition as visual time monitor. commercial colorimetric oxygen indicators. radical-bearing carbon with unpaired electrons. MB = \ce{MB^+Cl^-}.\cite{Galagan2008}
 
-\cite{Spencer1979} monomer MB and dimer MB kinetics.
+monomer MB and dimer MB kinetics.\cite{Spencer1979}
 
-\cite{Lee2003a}
+MB. \cite{Lee2003a}
 \begin{align}
@@
 
-strike the wafer, sputter etching and plasma etching .
+strike the wafer, sputter etching and plasma etching. fenestration, arrangement of windows and doors. sustained research,
 
@@
 
-chamber, vias, valve, figure, energetic, managerial, inert, volatile,
+chamber, vias, valve, figure, energetic, managerial, inert, volatile, chromic,

### 2014-03-24 ch-moox/moox.tex
lualatex packages as alternative in mwe

@@
 \midrule
--    &  +   & -  &   about 50 $\mu m$ belts, some towers \\
--    &  -   & +  &   irregular shape, not too much growth\\
--    &  +   & +  &   droplet almost all on tip of belts, many towers \\
-+    &  -   & -  &   tens $\mu m$ belt with sharp edge(100 nm thick, and 1micro wide) dominates\\
-+    &  -   & +  &   exhibit ITO features, droplets on tips of belt, many tower like structures\\
-+    &  +   & -  &   rounded edge flakes dominate, modest density tapering belt, and some possible tower\\
-+    &  +   & +  &   ITO/glass features, aggregated belts, some towers\\
+700    &  10   & 15  &   about 50 $\mu m$ belts, some towers \\
+700   &  1   & 60  &   irregular shape, not too much growth\\
+700    &  10   & 60  &   droplet almost all on tip of belts, many towers \\
+800    &  1   & 15  &   tens $\mu m$ belt with sharp edge(100 nm thick, and 1micro wide) dominates\\
+800   &  1   & 60  &   exhibit ITO features, droplets on tips of belt, many tower like structures\\
+800    &  10   & 15  &   rounded edge flakes dominate, modest density tapering belt, and some possible tower\\
+800    &  10   & 60  &   ITO/glass features, aggregated belts, some towers\\
 \bottomrule

### 2014-03-24 misc/mwe.tex
moo3 012714
coreshell growth cont
fix subsubsection numbering issus
lualatex packages as alternative in mwe

@@
  %   \include{./ch-intro/ch-intro}
+  %   \include{../BackMatter/paper}
+\chapter{one}
+\section{level one}
 
+\subsection{level two }
+
+\subsubsection{level three}
 After 20 minutes sonication, the dispersion is milky.
-We measured the transmission spectra of this dispersion immediately upon sonication and after 40 hrs for gravity sedimentation, as illustrated in Fig.~\ref{fig:moabs}.
+We measured the transmission spectra of this dispersion immediately upon sonication and after 40 hrs for gravity sedimentation.
 The t0 line mainly arises from the scattering of flakes in the dispersion.
@@
 Then a empirical dependence shown in Eq.~\ref{eq:sca2} is used as polynomial fitting model.
+test.
 
@@
 The fitting of n usually falls between -2 and -4.
-We examined the t40h line in Fig.~\ref{fig:moabs} and found the scattering part is almost zero.
+We examined the t40h line and found the scattering part is almost zero.
 Therefore we did not perform aforementioned fitting.
@@
 \centering
-\subcaptionbox{\label{fig:moind}}{\includegraphics[width=0.35\linewidth]{n_MoO3}}%
-\subcaptionbox{\label{fig:mocon}}{\includegraphics[width=0.55\linewidth]{Graph20}}
+\subcaptionbox{\label{fig:moind}}{\includegraphics[width=0.45\linewidth]{n_MoO3}}%
+\subcaptionbox{\label{fig:mocon}}{\includegraphics[width=0.45\linewidth]{MoO3_1L}}
 \caption[Refractive indices of \ce{MoO3}]{(a) Refractive indices of \ce{MoO3} Dashed line is n along $a$ axis while solid line is along $c$ axis.
@@
 Then a empirical dependence shown in Eq.~\ref{eq:sca2} is used as polynomial fitting model.
+\begin{figure}[htb]
+\centering
+\subcaptionbox{\label{fig:moxrd}}{\includegraphics[width=0.45\linewidth]{xrd_moo3}}%
+\subcaptionbox{\label{fig:moram}}{\includegraphics[width=0.45\linewidth]{xrd_moo3}}
+\caption[Crystalline phase characterization of \ce{MoO3} on Si]{(a) XRD pattern and (b) Raman spectrum of typical \ce{MoO3} on Si, $\lambda_{ex} = 532nm$.}
+\label{fig:mooxch}
+\end{figure}
+
+piranha clean of FTO.
+50ms switch.\cite{Scherer2012} nanoscale Kirkendall effect: the outward diffusion of metal cations are balanced by an influx of vacancies.
+For example, diffusion coefficient of Ni in NiO is higher than that of oxygen.
+\subsection{EC windows and thin film batteries}
+
+battery and ECD.\cite{Granqvist2012} electrolyte: PVB (poly vinyl buteral).
+alternative materials and design: organic, Prussian Blue as EC materials, metal hydrides, suspended particle device, liquid crystal, electroplating,
+challenges: large area nanoporosity, transparent conducting contact, electrolyte with good ionic conductivity and poor electronic conductivity, stable under UV; assembly and large scale manufacturing;
+cathodic coloration:
+anodic coloration:
+The coloration mechanism: \ce{MO6} octahedrons lead to $e_g$ and $t_{2g}$ level and ion channelling.
+ref54,60,65,66,200,209,
+
+\ce{WO3} as cathodic and either polyaniline(PANI) or Prussian white (PW) as anodic electrochromic half cells. \cite{Heckner2002}
+
+Characterization of ECD includes transmission measurement and associated EC calculation, charge-discharge time, current-time curve and the fitting of obtained data.
+
+\begin{quote}
+a viable electrochromic smart window must exhibit a cycling life time \textgreater $10^5$ cycles, corresponding to an operation life at 10 - 20 years.
+\end{quote}
+
+\citeauthor{Sella1998} studied the optical and structural properties of RF sputtered thin film of \ce{WO3} and \ce{VO2} for electrochromic devices.
+Ionic conductor was built using transparent polymer electrolyte, which was prepared from a solution of 1M \ce{LiClO4} in propylene carbonate which was mixed with methylmetharcylate (MMA).
+The main characteristics of polymer electrolyte were: viscosity at 25 \si{\degreeCelsius} $\approx$ 12920 Pa.s, conductivity $\approx 10^{-2}-10^{-4}$\si{\per\ohm\per cm},non-hygroscopic if PMMA concentration \textgreater 30\%.
+A specific counter-electrode layer was not used since the encapsulated polymer electrolyte processes a very high ion storage capacity.\cite{Sella1998}
 

### 2014-04-14 BackMatter/paper.tex
after a long pause

@@
 Therefore SERS applies and single molecule Raman scattering using a tungsten oxide nanorod has been demonstrated.
-The \ce{W_n_O{3n-1}} ($n \geq 2$) exhibit $\{ 001 \}$ CS structure.
+The \ce{W_nO_{3n-1}} ($n \geq 2$) exhibit $\{ 001 \}$ CS structure.
 Chemical formulae corresponding to n=2, 3, 4, 5 and 6 are \ce{W2O5=WO_{2.5}}, \ce{W3O8=W_{2.67}}, \ce{W4O_{11}=WO_{2.75}}, \ce{W5O_{14}=WO_{2.8}}, and \ce{W6O_{17}=WO_{2.83}}, which indicates the existence of a oxygen deficient plane at every n row.
@@
 Moreover, the oxygen deficient planes could extend along directions other than $\{ 001 \}$.
-For instance, the $\{ 102 \}$ CS planes appears in \ce{WOx} where x is within 2.93 to 2.98, and  the $\{ 103 \}$ CS planes for x within 2.87 to 2.93.
-\citeauthor{Shingaya2013} also synthesized \ce{WS2}-\ce{WO_x} structures and found similar Raman scattering enhancement.
+For instance, the $\{ 102 \}$ CS planes appears in \ce{WOx} where x is within 2.93 to 2.98, and  the $\{ 103 \}$ CS planes for x within 2.87 to 2.93.\cite{Sloan1999}  \citeauthor{Shingaya2013} also synthesized \ce{WS2}-\ce{WO_x} structures and found similar Raman scattering enhancement.
 The x value is estimated by the Raman spectra peaks.\cite{Shingaya2013}(Data not shown in patent)
@@
 
-  \ce{W_{18}O_{49}} Raman \cite{Guo2012} \cite{Guo2011}
+  \ce{W_{18}O_{49}} Raman, IR shielding.\cite{Guo2012} \cite{Guo2011}
+broad peak between 750-780 cm-1.
 
@@
   \ce{WnO_{3n-1}} NPs. \cite{Frey2001}
+WO3-x raman info, the encapsulated WOx core has been investigated in depth.
+several stable phase could occur, including \{001\} CS phases, \{103\} CS phases.
+no evidence of $\gamma$-\ce{W_{18}O_{49}} phase is found.
+The cross-section ($\sigma$) for Raman scattering and the absorption coefficient of the WS2 layers are much larger than those of the suboxide phase encapsulated inside.
+
+WO2:168(w),189(w), 286(vs), 345(w), 423(w), 479(m), 512(m), 599(m),
+617(m) cm-1, and a mode at 781(s) cm-1 which tails to higher energies (w-weak; m-medium; s-strong; vs-very strong).
+
+W5O14: 215, 264, 325, 349, 418, 425,707, and 800 cm-1, 900 maybe
+
+WO3: 808, 719, 275;
+
+W3O8: 870;
+
+no 950 peak indicates no hydrated phases.
 
@@
 For example, diffusion coefficient of Ni in NiO is higher than that of oxygen.
+
 \subsection{EC windows and thin film batteries}
@@
 
+\ce{WS2} p-type or n-type.
+Fermi level at the surface of semiconductor is pinned to a fixed position relative to the CBM and VBM by a sufficient density of surface states situated between CBM and VBM.
+\cite{Baglio1983}
+
 Electronic structure of \ce{MoS2}.\cite{Eknapakul2014} K intercalating into bulk to create quasi-standing 1L.
@@
 
-G/\ce{WS2}/G stacked solar cell. For lubricant, and surface protection. Absorption $\sim 10^7 m^{-1}$. \cite{Britnell2013}
-
 A direct gap of $\sim 2eV$ at the corners of BZ is formed in 1L \ce{WS2}, Growth on bottom piece show the multiple domain flakes occurs at initial stage of the growth, starting from \ce{WO3} particles.
 %\cite{Cong2013}
-
-In Ref\cite{Zeng2013}, single crystal \ce{WS2} growth using \ce{I2} transport was described in supporting info.
-\ce{C24H12K4O8}\footnote{http://www.chemspider.com/Chemical-Structure.24771386.html}
 
@@
 
-\citeauthor{Zhang2013i} investigated the shear (C) and layer breathing mode (LBM) in the low frequency region of \ce{MoS2}.\cite{Zhang2013i} Even layer \ce{MS2} belong to point group D$_{6h}$ with inversion symmetry, while odd layer \ce{MS2} correspond to D$_{3h}$ without inversion symmetry.
+\citeauthor{Zhang2013e} investigated the shear (C) and layer breathing mode (LBM) in the low frequency region of \ce{MoS2}.\cite{Zhang2013e} Even layer \ce{MS2} belong to point group D$_{6h}$ with inversion symmetry, while odd layer \ce{MS2} correspond to D$_{3h}$ without inversion symmetry.
 The excitation wavelength is 532nm from a diode-pumped solid-state laser.
@@
 (Zhou et al., 2010) heterojunction is employed to transferred photo-generated carriers.
-schottky barrier conduction band electron trapping and consequent longer electron-hole pair lifetimes.
+Schottky barrier conduction band electron trapping and consequent longer electron-hole pair lifetimes.
 Numerous studies have suggested that fine particles of transition metals or their oxides, when dispersed on the surface of a photocatalyst matrix, can act as electron traps on n-type semiconductors.
@@
 This enhancement perhaps arise from the \ce{K+} ions.
-
-CNT chirality by TEM \cite{Zhang1993} TEM chirality of \ce{MoS2} NTs
 
@@
 \section{misc}
+nucleation and film growth \cite{Hanbucken1984}
 
@@
 chamber, vias, valve, figure, energetic, managerial, inert, volatile, chromic,
+
+\section{job related paper}
+
+OLED with \ce{MoO3} as charge generation layer. \cite{Kanno2006} The PI is stephen forrest, also a cofounder of udc oled.\footnote{http://www.umich.edu/~ocm/research.html}
+
+stacked led, luminescence linearly increase with layer no at fix current density. hole transporting layer by MoO3, and electron transporting layer by Li.
+
+OLED photovoltaic.\cite{Xiao2012a} functionalized squaraines as donor
+
+excitation state management \cite{Zhang2012b}. 
+triplet-triplet annihilation (TTA) and singlet-triplet annihilation (STA). spin number of exciton is either 0 (singlet) or 1 (triplet).
+
+TTA, bound electron-hole pairs, introducing a heavy metal in organic molecule to enhance the spin-orbital coupling, enabling triplet emitters.\cite{Zhang2013i} yet when operating at high current, the efficiency is decreased, and TTA is considered as a intrinsic limit.
+
+ (T. Tsujimura
+OLED Displays: Fundamentals and Applications
+John Wiley & Sons Inc., Hoboken, New Jersey (2012))
+
+\section{The physics of semiconductor}
+
+quantum well devices exploit spatial quantization effects to increase the efficiency as well as alter the lasing threshold, and  novel semiconductor is made to emit light at wavelengths different from those possible when only bulk material is used.
+
+The discontinuity in the CB and CB occurs at the interface.
+The corresponding potential discontinuity create a potential difference, forming a trap in which electron or hole can only have discrete energies.
+
+a material of smaller bandgap is sandwiched between two layers of material of greater bandgap, or vice versa.
+
+transmissivity coupled in multiple quantum well structure.
+
+band structures=potential energy diagrams.
+
+\textbf{junctions}
+p-n homojunctions, p-n or n-n heterojunctions, metal-semi junctions, most important types: Schottky barriers, or ohmic contact.
+
+chemical potential (Fermi level) as a measure of particle concentration.
+Fermi level at 0K is equal to Fermi energy, which is defined as the energy of the topmost filled orbital.
+In equilibrium, the Fermi level $E_f$ is uniform throughout the material.
+n electron carrier, p holes carrier.
+
+band diagram represents the electron's potential energy.
+
+band bending: the electron energies are greater on the p side than on the n side, or the electrostatic potential is greater on the n side than on the p side, since potential $V = E/-q$.
+
+The built-in potential for a homojunction is equal to the full band bending in equilibrium.
+
+heterojunction: bandgap discontinuity, to solve the Poisson's equation for band bending.
+
+Metal-Semi: metal cannot support any potential difference across it. Fermi level in Semi is pinned at the interface. Electron transfer from n-type semi to metal, leaving ionized donors behind.
+
+ohmic contact forms if the work function of the metal is less than that of the semi. net flow of electron from metal into semi, no depletion layer forms.
+
+metal-oxide-semi as MIS structures is capacitive in nature since no dc current flows under bias.
+
+ch11.5 nonequilibrium conditions

### 2014-04-14 FrontMatter/FrontMatter.tex
List of abbreviations fixed
fix subsubsection numbering issus
after a long pause

@@
-  \title{Controlled Growth and Properties Measurement of One-Dimensional Nanostructures: Nanowires and Hybrids}
+  \title{Research plan: Controlled Growth and Property Measurement of One-dimensional Oxide Nanostructures for Energy Applications}
   \author{Tao Sheng}
@@
   \committeemember{Dr. Stuart Smith}
-  \committeemember{Last  person} % Maximum of 10 can be specified.
+  \committeemember{Dr. Yu Wang} % Maximum of 10 can be specified.
 
@@
 \renewcommand{\glossarypreamble}{\thispagestyle{myheadings}}
+\renewcommand{\acronymname}{LIST OF ABBREVIATIONS}
+\glossarystyle{long}
 \printglossary[type=\acronymtype]

### 2014-04-14 ch-tms/tms.tex
after a long pause

@@
 
-\ce{WS2} NT FET. \cite{Levi2013}
-
-\ce{WS2} NT transport \cite{Zhang2012c}
-
 Raman substrate dependence \cite{Buscema2013}
 
-WO3-x NPs \cite{Frey2001}
-
 stability of TMS NTs \cite{Seifert2002}
-
-growth mechanism \cite{ZAK2009}
-
-\citeauthor{Ramasubramaniam2011} investigated the band gap tuning in bilayer TMDC materials by applying external $E$ field.
-Similar research has been done for graphene and bilayer boron nitride.
-Semiconductor-metal transition was suggested for \ce{MoS2} and \ce{WS2}, with difference on the CBM and VBM evolution.
-In \ce{MoS2}, the valence-band-splitting cause the A and B excitons in optical absorption measurement.
-Calculation shows that CB and VB are translated toward the Fermi level with increasing E field.
-The external field localized charge along $c$ axis, but delocalized that within the plane normal towards $c$, thereby driving the semi-metal transition.
-It was mentioned that this transition is not anticipated in monolayer \ce{MoS2}.
-It was emphasized that precise band gaps might be different from the author’s results, yet the gap-tuning should be universal.\cite{Ramasubramaniam2011}
-
- 416 peak was prevously assumed to be a combination of LA and TA phonons at K points.
-
-Raman conditions: 0.3 mW, 532 nm, 200 sec acquisition time. photon flux = $0.3E-3\times6.242E+18/1.2398/0.532=2.84E15$
-
-nucleation and film growth \cite{Hanbucken1984}
 
@@
 
-\cite{Song2013} \ce{WO3} by ALD, and sulfurized in Ar and \ce{H2S} (10:1) at 1000 C.
-\ce{WS2} layer No and peak intensities ratio under 633nm excitation is correlated.
-It was found the 2LA/A1g is less than 1 for 1L.
-In supporting info 532 nm Raman spectra, the 2LA/A1g is presumably larger than 1 for 1L.
-\ce{WS2} NT on Si NWs is also demonstrated.
-
 \ce{WS2} Raman.\cite{Zhao2013} \cite{Sekine1980}
@@
 FL heterostructure. \cite{Yu2013a}
-
-Water splitting materials should process a band gap larger than 1.4eV, considering both the NHE potential distance and practical application.
-The monolayer \ce{WS2} exhibits direct gap of 1.98 eV.
-Quantum confinement could push the gap separation farther away.
-\cite{wilcoxon1997} \citeauthor{Notley2013} use liquid exfoliation to prepare \ce{WS2} NPs.\cite{Notley2013} Non-ionic surfactant concentration is about 0.1\%w/w.
-Continuously adding surfactant during sonication improves the yield.
-Optimum surface tension is found at about 40 mJ/m$^2$.
 
@@
 
-inorganic nanotubes review \cite{Tenne2004} , unsaturated bonds number increases as the size of MS2 sheet decreases.
+direct gap of ML at corner of BZ, point K.
+
+\begin{align}
+\cee{WCl6 + S &\rightarrow WS2 + Cl2S2}\\
+\cee{MoCl5 + S &\rightarrow MoS2 + S2Cl2} \\
+\cee{S2Cl2 + NaOH &\rightarrow NaCl + S + Na2SO3 + H2O}
+\end{align}
+
+\section{literature read}
+
+CNT chirality by TEM \cite{Zhang1993} TEM chirality of \ce{MoS2} NTs
+
+first demonstration of \ce{WS2} NT n-type FET. \cite{Levi2013}
+the importance of contact, and avoiding moisture.
+
+The calculated carrier concentration is about $10^{19}cm^{-3}$, a highly doped semiconductor, possibibly arising from sulfur vacancy.
+
+\ce{WS2} NT transport \cite{Zhang2012c}
+less grain boundary more mobility,
+
+\citeauthor{Ramasubramaniam2011} investigated the band gap tuning in bilayer TMDC materials by applying external $E$ field.
+Similar research has been done for graphene and bilayer boron nitride.
+Semiconductor-metal transition was suggested for \ce{MoS2} and \ce{WS2}, with difference on the CBM and VBM evolution.
+In \ce{MoS2}, the valence-band-splitting cause the A and B excitons in optical absorption measurement.
+Calculation shows that CB and VB are translated toward the Fermi level with increasing E field.
+The external field localized charge along $c$ axis, but delocalized that within the plane normal towards $c$, thereby driving the semi-metal transition.
+It was mentioned that this transition is not anticipated in monolayer \ce{MoS2}.
+It was emphasized that precise band gaps might be different from the author’s results, yet the gap-tuning should be universal.\cite{Ramasubramaniam2011}
+
+\cite{Song2013} \ce{WO3} by ALD, and sulfurized in Ar and \ce{H2S} (10:1) at 1000 C.
+\ce{WS2} layer No and peak intensities ratio under 633nm excitation is correlated.
+It was found the 2LA/A1g is less than 1 for 1L.
+In supporting info 532 nm Raman spectra, the 2LA/A1g is presumably larger than 1 for 1L.
+\ce{WS2} NT on Si NWs is also demonstrated.
 
@@
 The strong attachment is formed through $\pi-\pi$ interactions.
+
+growth mechanism of WS2 NT\cite{ZAK2009} 
+It was found that the critical step in this process is the fast conversion of the oxide nanoparticle surface into a closed monolayer of WS2.
+W18O49 as an intermediate phase is observed.
+XRD peaks shift to monitor strain.
+
+inorganic nanotubes review \cite{Tenne2004} , unsaturated bonds number increases as the size of MS2 sheet decreases.
+
+Water splitting materials should process a band gap larger than 1.4eV, considering both the NHE potential distance and practical application.
+The monolayer \ce{WS2} exhibits direct gap of 1.98 eV.
+Quantum confinement could push the gap separation farther away.
+\cite{wilcoxon1997} \citeauthor{Notley2013} use liquid exfoliation to prepare \ce{WS2} NPs.\cite{Notley2013} Non-ionic surfactant concentration is about 0.1\%w/w.
+Continuously adding surfactant during sonication improves the yield.
+Optimum surface tension is found at about 40 mJ/m$^2$.
+
+G/\ce{WS2}/G stacked solar cell. For lubricant, and surface protection. Absorption $\sim 10^7 m^{-1}$. \cite{Britnell2013}
+
+In Ref\cite{Zeng2013}, single crystal \ce{WS2} growth using \ce{I2} transport was described in supporting info.
+\ce{C24H12K4O8}\footnote{http://www.chemspider.com/Chemical-Structure.24771386.html}
+
+416 peak was prevously assumed to be a combination of LA and TA phonons at K points.
+
+Raman conditions: 0.3 mW, 532 nm, 200 sec acquisition time. photon flux = $0.3E-3\times6.242E+18/1.2398/0.532=2.84E15$
 
@@
 Nanotube growth is relatively independent of substrates and FL layer is closely related to substrate. Film growth could provide some insight into the latter scenario.
-
-direct gap of ML at corner of BZ, point K.
-
-\begin{align}
-\cee{WCl6 + S &\rightarrow WS2 + Cl2S2}\\
-\cee{MoCl5 + S &\rightarrow MoS2 + S2Cl2} \\
-\cee{S2Cl2 + NaOH &\rightarrow NaCl + S + Na2SO3 + H2O}
-\end{align}

### 2014-07-28 BackMatter/paper.tex
before final branch

@@
 \section{WO3}
+
+Raman \cite{Xiao2007}.
+Silver has the strongest SERS enhancement due to the larger imaginary part of the dielectric constant and higher thermal conductivity.
+Milli-Q grade water ((Milli-pore)\textgreater 18.2Mohm).
+
+MB Raman peaks: 445, 1618, ref20. some peak splitting and shift observed on SERS, attributed to chemical adsorption.
+
+definition of Raman enhancement factor (9,26).
+
+SERR MB on Ag. \cite{Nicolai2003}
+MB: the absorption spectrum in VIS is used to infer about different adsorbed forms of MB. the formation of large aggregates. I call attention to the fact that.
+
+WO3: effective mass of bipolaron = 1.9me. for electron, for hole:
 
@@
 
+WS2 photoluminescence spectra of few layer and nanotube:
+NT electrical structures depend on chirality, diameter and layer No as well as strain.
+Theoretical calculation indicates the SWNT with diameter larger than 4nm should approach the single layer limit.\cite{Ghorbani-Asl2013}
+
+Exfoliated WS2 few layer PL.\cite{Zhao2012} excitonic absorption peaks A and B arising from direction transition at K point are found around 625nm (1.98eV) and 550nm, respectively, which are in agreement with results from bulk layers.
+The A, B excitons difference was a result of strong spin-orbital coupling.
+Relative PL quantum yield of WS2 between 1L and 2L is on the order of 2.
+The FWHM of WS2 peak is about 75 meV.
+Narrower than thermal energy at room temperature,
+
+CVD 1L WS2 PL.\cite{Peimyoo2013} (of NTU Yu group) PL peak at 635nm, width 40 meV,
+
+CVD 1L WS2.\cite{Cong2013} (of NTU Yu group) 457 nm excitation, PL at 525nm and 630nm,
+
+\cite{Xiao2014}
+
+1T MoS2: metallic phase a negative temperature coefficient for conductivity, XRD pattern identified. \cite{Wypych1992}
+
+stable 1T WS2 multiwalled NT by Re doping.\cite{Enyashin2011}.
+2H to 1T transition formerly known only for WS2 and MoS2 intercalated by alkali metals.
+3R transition to 2H upon heating since 2H is the most stable one.
+aberration corrected TEM is used.
+
+petroleum oil catalytic refinement, solid lubricants in aerospace industry.
+
+Electro microscopy on stacking sequences of WS2 NT.\cite{Houben2012} The probability of parallel stacking is about 30\%.
+a metal-semi superstructures.
+In NT, the layers are slightly shifted with respect to each other due to the constraints, thus the stacking is not exactly as pure phases of 2H(prismatic antiparallel), 3R(prismatic parallel) or 1T (octahedral parallel) with their perfect translational symmetry.
+
+chevron pattern, contradictory, contradicting, Debye scattering model for XRD.
+
+\begin{quote}
+hexagonal polytype 2Hb with two molecular layers (spacegroup P63/mmc) and a rhombohedral polytype 3R with three molecular layers per unit cell (space group R3m), a high pressure polytype that is stable in plane geometry at pressures above 4 GPa.
+The two prismatic phases are semiconducting, and the octahedral one is metallic-like.
+
+1T phase may be the result of a transformation from the 3R to the 2H phase by an intermediate 1T phase that is trapped by fast quenching
+
+\end{quote}
+
+HRTEM on WS2 NT.\cite{Sadan2008} negative spherical-aberration imaging (NCSI).
+NCSI condiction were achieved at a negative spherical aberration of -20um balanced by an overfocus of +17 nm.
+Focal series reconstruction to retrieve the phase of electron exit plan wavefunction.
+Zigzag, armchair revealed.
+
+1T \ce{MoS2} Raman.
+\cite{Yang1991} strong peaks at 156, 226, and 330 cm-1.
+M point frequencies measured by neutron scattering.
+M point is folded into BZ zone center due to the formation of superlattice.
+
+Electrons and Phonons in Layered Crystal Structures, edited by T. J. Wieting (Reidel, Dordrecht, Holland, 1979).
+
 \ce{WS2} p-type or n-type.
@@
 
+Zheng thesis: \ce{TiO2} anodic nanotube by sputtering Ti on FTO and anodizing in F-organic electrolyte.
+
+heat cure gasket ( ionomer surlyn 1702 Dupont), 125 C for 30s.
+vacuum back filling.
+
 \section{vocabulary}
+
+adjunct to muscle power, computing and reasoning power, zinc-blende similarity, switching time depends on the velocity of the carriers; impact ionization, high field lead to nonlinear behavior, which arise from the major changes in the shape of the carrier distribution function, a far from equilibrium state.\footnote{\url{http://ieeexplore.ieee.org/xpl/tocresult.jsp?isnumber=31617&punumber=16}}
+
+high field 600kV/cm.
+carrier, linear transport, constant relaxation time, mean free path longer than interatomic distances.
+the periodic potential does not cause scattering of the electrons.
+box normalization, wave vector is not a continuous variable.
+in ground state, topmost filled level is the Fermi level, crystal momentum, hk, or Fermi vector k_F depends on the electron density.
+curvature mass, DOS mass in a state countering process,
+
+Heat capacity is dominated by the electrons lying near the Fermi level. quantum effect and the coherence length ( 100nm at RT).
 
@@
 chamber, vias, valve, figure, energetic, managerial, inert, volatile, chromic,
+laminar, palladium, platinum, photovoltaic, acronym, chirality, stoichiometric, cyclic voltammetry,
 
@@
 ch11.5 nonequilibrium conditions
+quasi-fermi level $\phi_n$ or $\phi_p$.

### 2014-07-28 ch-tms/tms.tex
before final branch

@@
 
+The geometrical symmetry groups of WS2 NT.\cite{Milosevic2000} 
+The basis/lattice vectors $a_1$ and $a_2$ are defined in transition metal plane with equal length $a_0 \approx 3$ \AA.
+This monolayered sheet can be rolled up to form a tubular structure when the chiral/translation vector $c = n_1a_1 + n_2a_2$ becomes the circumference of the tube.
+The diameter of a nanotube is given by
+\begin{equation}
+d = \frac{\mid c \mid}{\pi} = \frac{a_0}{\pi}\sqrt{n_1^2 + n_1n_2 + n_2^2}
+\end{equation}
+Notice $a_1 \cdot a_2 = a_1a_2 \cos\pi/3$, where the cosine times 2 is unit. 
+In analog with carbon nanotube, chiral angle $\theta$ is given by
+\begin{equation}
+\theta = \tan^{-1}\frac{\sqrt{3}n_2}{2n_1 + n_2}
+\end{equation}
+
+Chiral angles from the interval $[0,pi/6]$ is sufficient for all possible tubes.
+Tubes $(n,0)$ with zero chiral angle are named zigzag, tubes $(n,n)$ with $\pi/6$ chiral angle are armchair, whereas all others are referred as chiral ones with $\theta \in (0,pi/6)$.
+
 hydrogen evolution catalysts. \cite{Merki2011}

### 2014-07-30 ch-intro/ch-instr.tex
ch2 draft initial

\chapter{experimental tools}

In this study the nanostructures were grown in a home-built chemical vapor deposition system, and characterized using both electron microscopy and optical spectroscopy methods, including SEM, XRD, EDX, TEM, Raman and UV-Vis. Other sample and substrate preparation methods used are also briefly introduced. A detailed introduction will be given to the CVD system. For other mature techniques, the contents will be limited to the extent where experienced material researchers could repeat the experiments performed in this study. This chapter is concluded with data processing and associated software discussion.

\section{Home-built CVD System}

The synthesis was accomplished in a home-made hot-wall CVD system, as visualized in Fig.~\ref{fig:ch2cvd}. The furnace is made by two semi-cylindrical ceramic fiber heaters (WATLOW inc.) with power density from 0.8 to 4.6 \si{W cm^{-2}}. Quartz tube (Quartz Sci inc.) of 1 inch diameter was primarily used as reaction chamber. A mechanical pump was connected to maintain the low pressure environment inside the chamber. The length of uniform heating zone is 6 inches, with cooling zone extending outward. Carriers gas argon (Ar) and reactant gas oxygen (\ce{O2}) was regulated by two mass flow controllers.

\begin{figure}[htb]
\centering
\subfloat[]{\includegraphics[width=0.7\textwidth]{CVD_d346.jpg}}

\subfloat[]{\includegraphics[width=0.9\textwidth]{CVD_model.jpg}}
\caption[CVD system]{Home-built low-pressure chemical vapor system. (a) Photograph of reaction chamber. (b) Sketch of CVD system, where A1: quartz tube; B1: bubbler; C1-2: gas cylinders; E1: mechanical pump; H1-2: ceramic heater; MFC: flow controller; P1: pressure gauge; V1-4: valves; V5-7: butterfly valves.}
\label{fig:ch2cvd}
\end{figure}

The controllable parameters of this CVD system include central heating temperature, absolute gas flow and relative ratio of (Ar/\ce{O2}), amount of source material and location of the substrates. The operation capability is summarized in Table.~\ref{tab:cvd}.

\begin{table}[htb]
\centering
\caption{CVD parameters map}\label{tab:cvd}
    \begin{tabular}{lcccr}
    \toprule
     &&&\multicolumn{2}{c}{Flow} \\
    \cmidrule(l){4-5}
             & Temperature & Pressure & Ar & \ce{O2}  \\
    \midrule
             & \si{\degreeCelsius} & mTorr & sccm & sccm\\
    \midrule
    Range      & RT-1100    & 10mTorr-1atm & 0 - 100 & 0-30  \\
    Resolution & $\pm1$  & correlated to flow & 1   & 0.1  \\
    \bottomrule
    \end{tabular}
\end{table}

The heating temperature $T$ profile measured at different settings in ambient environment was shown in Fig.~\ref{fig:ch2temp}. There exists a uniform heating zone in the center area, spanning over about 2 in. Then $T$ descends gradually within the 6 in heating zone, and decrease rapidly at the rest part. In this study, a zero position is defined at the upstream edge of reaction chamber covered by the furnace.

\begin{figure}[htb]
\centering
\includegraphics[width=0.8\textwidth]{temp_profile.pdf}
\caption[CVD temperature profile]{Temperature profile of home-built low-pressure chemical vapor system.}
\label{fig:ch2temp}
\end{figure}

The substrates were mostly positioned just outside the downstream heating zone since within this region, the vapor undergoes a rapid temperature gradient and precipitation occurs. The source material placed in the furnace center is oxidized and evaporated. The growth species, transported by carrier gas, bombard both substrate and chamber wall. Some will be adsorbed by the substrate and become adatoms while some may remain as gas molecules, waiting for another event. On the hot substrate, adatoms diffuse and do not settle down until finding a appropriate location where equilibrium is favorable. Detailed growth conditions are introduced in corresponding chapters.

\section{Scanning Electron Microscopy (SEM) and Energy Dispersive X-ray Spectroscopy (EDX)}\label{sec:sem}

SEM, as its name suggests, forms images using contrast from the electron-materials interactions. Electron beam (E-beam), generated from either thermionic or field emission of filaments, travels towards the sample underneath, producing rich signals as illustrated in Fig.~\ref{fig:ch2sem}. The out-coming backscattering (BSE) and secondary electrons (SE) arise from elastic and inelastic process, respectively. The X-ray stems from inner shell transition, and cathodoluminescence from band gap transition. In this study, we mainly use SE-formed images to reveal the morphology of the samples, since SE emission is sensitive to the shape and orientation. X-ray, collected by silicon detector cooled by liquid nitrogen, could provide compositional information attaining to the studied sample, because of the characteristic X-ray emission lines from each element.

\begin{figure}[htb]
\centering
\includegraphics[width=0.5\textwidth]{sem_sch.png}
\caption[SEM excitation volume]{schematic drawing of electron materials interaction in SEM, some process is not shown, such as Auger emission.}
\label{fig:ch2sem}
\end{figure}

The SEM instrument used in this study is JEOL JSM-6480 and EDX attachment from Oxford Instrument INCA. Typical observation conditions are listed as following:

\begin{enumerate}
\item SEM
\begin{itemize}

\item Acceleration voltage: 10 kV
\item Working distance: 10 mm
\item Scanning time: 80 sec
\end{itemize}
\item EDX
\begin{itemize}

\item Acceleration voltage: 20 kV
\item Working distance: 10 mm
\item Dead time: $20\sim30$\%
\end{itemize}
\end{enumerate}

\section{X-ray Diffraction (XRD)}

The high energy ($E = 1239.8/0.15148= 8184.5$ eV) photon was generated using accelerated electron beam from tungsten filament to bombard Cu target. When striking onto the crystal, these photons are scattered by the lattices. Since the wavelength of X-ray is similar to the lattice spacing, the scattering events interact coherently. Only at specific angles constructive interference occurs, and a diffraction peak registers when the detector is scanned across that angle.

Crystal structures of the as-synthesized specimens in this study were characterized using PANXpert X’pert Pro MRD with Cu $K\alpha_{avg}$ radiation at $\lambda$=1.5418\AA. The nanostructures in this work usually grew without preferred orientation, and can be treated as powders. So the $\theta-2\theta$ configuration was primarily used, as shown in Fig.~\ref{fig:ch2theta}.

\begin{figure}[htb]
\centering
\includegraphics[width=0.5\textwidth]{xrd_2theta.png}

\caption[XRD configuration]{Bragg-Brentano geometry used in powder diffractometer}
\label{fig:ch2theta}
\end{figure}

The as-synthesized specimens were mounted onto diffractometer in a way that the X-ray will illuminate interested region during the whole scanning. Typical settings used was summarized in Table.~\ref{tab:ch2xrd}.

\begin{table}[htb]
\centering
\caption{XRD settings}\label{tab:ch2xrd}
\begin{tabular}{lp{2in}lp{2in}}
\toprule
Name & Value & Name & Value  \\
\midrule
Voltage   & 45 kV & Current & 40 mA \\
Divergence slit & 1/32$^\circ$(alignment) 1/2$^\circ$(scanning) & Receiving slit& Parallel collimator \\
Soller slit & 0.04 rad & Collimator & Parallel plate 0.27 rad \\
Scan range & $10 \sim 65 ^\circ$ & Step size & 0.05$^\circ$ \\
\bottomrule
\end{tabular}
\end{table}

\section{Transmission Electron Microscopy (TEM)}

TEM qualifies as a powerful and versatile tool for material characterization. JEOL JEM-2100 TEM with a \ce{LaB6} filament operated at 200 kV was used in current thesis. Similar to the photon-lattice interaction in XRD, the process of TEM could be understood as electron scattering events by the same crystal plane. In both processes, the constructive interference is described by $2d\sin\theta = \lambda$, where $d$ is crystal plane distance, $\lambda$ is incident wavelength (photon or electron), and $\theta$ is half of the scattering angle. A numerical comparison in Table.~\ref{tab:ch2tem} demonstrates the origin of difference in these two techniques.

\begin{table}[htb]
\centering
\caption{Scattering angle difference of Si(111)}\label{tab:ch2tem}
\begin{tabular}{lccr}
\toprule
Si(111) spacing & Source & Wavelength & scattering angle($2\theta$) \\
\midrule
3.135\AA & Cu $K\alpha$ & 1.541\AA & 28.45$^\circ$  \\
3.135\AA & 200 kV & 0.0251\AA \textsuperscript{\emph{a}}& 0.45$^\circ$  \\
\bottomrule
\end{tabular}

 \textsuperscript{\emph{a}} with relativistic correction;
\end{table}

This small deviation angle determines the design of TEM column. In analog to the diffraction-limited resolution in conventional lens optics, the ultimate resolved point distance in TEM at 200 kV could be as small as 0.025 \AA. However it is much harder to manipulate electron with magnetic field than photon with dielectric lens, the current resolution in TEM is on the order of 1.0 \AA. The nominal resolution of JEM-2100 is 2.3 \AA. On the other hand, it is much easier to fine tune the power (focal length) of lens in TEM than in conventional optics. This capacity enables other observation approaches that would be rather difficult, if not impossible, to be realized in lens optics, such as selected area electron diffraction pattern (SAED).

Akin to the electron-materials interaction introduced in Sec.~\ref{sec:sem}, X-ray emission and CL also occur in TEM, and these signals could be collected to obtain value insight into specimen at higher spatial resolution. In this study, the TEM specimen was prepared either by directly scratching the as-synthesized sample using TEM grid (Cu, lacy carbon, 300 mesh), or dispersed into aqueous or organic solutions, then drop-cast onto TEM grid. A JEOL double tilt holder was used to rotate the crystal orientation. TEM images and SEADs were acquired using a charge coupled device (CCD) from Gatan, inc. EDX spectroscopy was captured by similar Oxford Instrument INCA attachment.

\section{Raman and UV-Vis Spectroscopy}

Raman spectroscopy, a common vibrational spectroscopy, is based on the inelastic scattering of a monochromatic excitation source in energy range of 100 to 4000 $cm^{-1}$. Being nondestructive and requiring minimal preparation, 
it is an excellent tools to assess lattice dynamics and fingerprint species.\cite{McCreery2000}

In this study, Raman measurement was performed using a confocal micro-Raman system (Horiba Scentific, Labram HR800) with excitation wavelengths of 441, 532 and 632 nm. For nanowire samples, the laser powers were kept between 0.2 and 0.3 mW, and the acquisition time was 100 sec to avoid possible thermal damage. The spectral resolution is about 1 $cm^{-1}$ and the depth resolution about $2\mu m$.

A Raman pattern database can be found at \url{http://wwwobs.univ-bpclermont.fr/sfmc/ramandb2/index.html}.

UV-Vis-NIR spectrophotometer is also a useful tool to obtain absorption and reflectance from various samples. The absorption can be described by Lambert-Beer law: $I = I_0 \exp{-\alpha(\lambda) x}$, where $\alpha$ is the absorption coefficient in unit of $cm^{-1}$, and $x$ is the optical path. When the sample is in liquid form, it is more convenient to use $I = I_0 \exp{-\epsilon(\lambda) C x}$, where $C(M = mol dm^{-3})$ is the molar concentration, and $\epsilon (M^{-1}cm^{-1})$ is the extinction coefficient. For example, $\epsilon$ for methylene blue (MB) is $10^5 M^{-1}cm^{-1}$ at 660 nm.\cite{Mills1999}

In this thesis, optical absorption spectra was recorded using Schimadzu, UV2600Plus in transmission mode. When necessary, the as-synthesized sample was removed from substrates by light sonication(Branson 1510R-MTH, 70W) in ethanol or DI water for 15 seconds. The dispersion was left for 12 hrs to enable the possible sedimentation. Then the dispersion was transferred into one 10 mm quartz cuvette (Thorlabs, W005654) for absorption measurement with another paired cuvette containing pairing liquid only.

\section{Substrates and Pre-growth Treatments}

Silicon and silicon dioxides on Si wafer ($p$-Si(100),Unversity Wafer inc.) were primarily used, and other substrates (i.e. Mica\footnote{ \ce{K(Al2)(Si3Al)O10(OH)2}}, glass (Fisher Scientific, microscope slide, 12-549),\footnote{Typical composition is 72.6\% \ce{SiO2}, 0.8\% \ce{B2O3}, 1.7\% \ce{Al2O3}, 4.6\% \ce{CaO}, 3.6\% \ce{MgO} and 15.2\% \ce{Na2O}} stainless steel) were occasionally adapted. Substrates were first cut into rectangular pieces of certain size and then ultrasonically cleaned (Branson 1510R-MTH) with acetone and alcohol for about 15 minutes each followed by blow-drying with nitrogen gas. After solution cleaning, the Si surface is hydrophobic. Depending on the specific experimental requirement, sometimes a hydrophilic surface is desired. We use plasma cleaning (Kurt J Lesker: Plasma-Preen 862) under 2 Torr \ce{O2} for 3 min to render a hydrophilic Si surface. In addition, substrates can be coated with a thin layer of metal before growth. This process will be covered  in Sec.~\ref{sec:mag}.

\subsection{Magnetron Sputtering}\label{sec:mag}

Sputtering, a process in which atoms are ejected from a solid target material by bombarding it with energetic particles, is a well established physical vapor deposition (PVD) process with a high degree of controllability. The high energy and controllable parameters of sputtering can result in the growth of well-structured and crystalline films. Further, sputtering can be easily implemented as a roll-to-roll process for large-scale manufacturing. It is widely utilized for deposition of \ce{WO_x} in industry.

In this work, magnetron sputtering (Denton Vacuum Desk IV) was used to coat thin layers of metals onto cleaned substrates, such as W, Mo, Au, Ag, Pd, and Pt. As shown in Fig.~\ref{fig:ch2magsp}, a high potential created between the target (cathode) and substrate ionizes the argon molecules. These ions are accelerated to bombard the target foils, knocking out active atoms which subsequently deposit onto the substrates. A magnetic field is applied to confine electrons to the vicinity of the foils. These electrons in turn increase the ionization yield.

\begin{figure}[htb]
\centering
\includegraphics[width=0.8\textwidth]{magsp.jpg}
\caption[magnetron sputtering system]{Schematic drawing of sputtering adopted from ref\cite{Song2008}}
\label{fig:ch2magsp}
\end{figure}

Sputtering is a better PVD technique than e-beam deposition since it alleviates the adverse effects in the latter. \ce{Ar+} ions are accelerated to target foils. The pressure of \ce{Ar+} has two functions: to sputter off the target ions, and to influence the mean free path (MFP). These collisions between target ions and \ce{Ar+} leads to almost all arrival angle, thus uniform coverage. The sputter yield is number of target ions released per ions hitting on target. If \ce{Ar+} ion energy is less than 100 eV, the yield is zero; If larger than 10 keV, implantation of \ce{Ar+} into target foils occurs. Usually yield between 1 and 2 is desired. The MFP in sputtering is on order of 3 cm (assuming pressure 30 mTorr), with source-to-substrate distance as 5 cm, average number of collisions is about 5/3$\sim$2.

\section{data processing tools}

Image J.\cite{Schneider2012} TEM lattice measurement.

Fityk. \cite{Wojdyr2010}

XRD pattern, Spectra(EDX, Raman, UV-Vis) redraw using Origin Pro 8.0.

### 2014-07-30 ch-intro/ch-intro.tex
ch2 draft initial

--- 2014-01-26 ch-intro/ch-intro.tex
@@
 
-The synthesis was accomplished in a home-made hot-wall CVD system, as visualized in Fig.~\ref{fig:ch1cvd}.
-The furnace is made by two semi-cylindrical ceramic fiber heaters (WATLOW inc.) with power density from 0.8 to 4.6 \si{W/cm^2}.
-Quartz tube (Quartz Sci inc.) of 1 inch diameter was primarily used as reaction chamber.
-A mechanical pump was connected to maintain the low pressure environment inside the chamber.
-The length of uniform heating zone is 6 inches, with cooling zone extending outward.
-Carriers gas argon (Ar) and reactant gas oxygen (\ce{O2}) was regulated by two mass flow controllers respectively.
-
-\begin{figure}[htb]
-\centering
-\subfloat[]{\includegraphics[width=0.8\textwidth]{CVD_d346.jpg}}
-
-\subfloat[]{\includegraphics[width=0.8\textwidth]{CVD_model.jpg}}
-\caption[CVD system]{Home-built low-pressure chemical vapor system.}
-\label{fig:ch1cvd}
-\end{figure}
-
-Silicon and silicon dioxides on Si wafer ($p$-Si(100),Unversity Wafer inc.) were primarily used as receiving substrates, and other substrates (i.e.
-Mica\footnote{ \ce{K(Al2)(Si3Al)O10(OH)2}}, glass (Fisher Scientific, microscope slide, 12-549),\footnote{Typical composition is 72.6\% \ce{SiO2}, 0.8\% \ce{B2O3}, 1.7\% \ce{Al2O3}, 4.6\% \ce{CaO}, 3.6\% \ce{MgO} and 15.2\% \ce{Na2O}} stainless steel) were occasionally adapted.
-The preparation procedure was illustrated in Fig.
-Substrates were first cut into rectangular pieces of certain size and then ultrasonically bathed (Branson 1510R-MTH) with acetone and alcohol for about 15 minutes each followed by blow-drying with nitrogen gas.
-After solution cleaning, the Si surface is hydrophobic.
-Depending on the specific experimental requirement, sometimes a hydrophilic surface is desired.
-We use plasma cleaning (Kurt J Lesker: Plasma-Preen 862) under 2Torr \ce{O2} for 3 minutes to render a hydrophilic Si surface.
-In addition, substrates can be coated with a thin layer of metal before sent into reaction chamber.
-This process details will be covered later in the \emph{Characterization} session.
-The controllable parameters of our CVD system includes central heating temperature, absolute gas flow and relative ratio of (Ar/\ce{O2}), amount of source material and the location of receiving substrates.
-The operation capability was summarized in Table.~\ref{tab:cvd}.
-
-\begin{table}[htb]
-\centering
-\caption{CVD parameters map}\label{tab:cvd}
-    \begin{tabular}{lcccr}
-    \toprule
-     &&&\multicolumn{2}{c}{Flow} \\
-    \cmidrule(l){4-5}
-             & Temperature & Pressure & Ar & \ce{O2}  \\
-    \midrule
-             & \si{\degreeCelsius} & mTorr & sccm & sccm\\
-    \midrule
-    Range      & RT-1100    & 10mTorr-1atm & 0 - 100 & 0-30  \\
-    Resolution & $\pm1$  & correlated to flow & 1   & 0.1  \\
-    \bottomrule
-    \end{tabular}
-\end{table}
-
-The substrates were mostly positioned in downstream cooling zone since within this region, the vapor undergoes a rapid temperature gradient and precipitation occurs.
-The source material placed in the central heating zone is oxidized and then evaporated.
-The growth species, transported by carrier gas, bombard both substrate and chamber wall.
-Some will be adsorbed by the substrate and become adatoms while some may remain as gas molecules, waiting for another event.
-On the hot substrate, adatoms diffuse and do not settle down until finding a appropriate location where equilibrium is favorable.
-
 Nucleation is a process of generating a new phase from a metastable old phase, where the Gibbs energy per molecule of the bulk of the emerging new phase is less than that of the old phase.
@@
 
-\textbf{Magnetic Sputtering} Sputtering, a process in which atoms are ejected from a solid target material by bombarding it with energetic particles, is a well established PVD process with a high degree of controllability.
-The high energy and controllable parameters of sputtering can result in the growth of well-structured and crystalline films.
-Further, sputtering can be easily implemented as a roll-to-roll process for large-scale manufacturing.
-It is widely utilized for deposition of \ce{WO_x} in industry.
-
-The morphology and composition of the as-synthesized samples were analyzed by scanning electron microscopy (SEM,JEOL JSM-6480) and energy dispersive X-ray spectroscopy (EDS,Oxford Instrument INCA).
-Crystal structures were characterized using X-ray diffraction (XRD, PANXpert X’pert Pro MRD with Cu $K\alpha$ radiation at $\lambda$=1.5418\AA) and transmission electron microscopy (TEM, JEOL JEM-2100 \ce{LaB6} operated at 200kV).
-Optical measurements were performed by Micro-Raman spectroscopy (Horiba Scientific, Labram HR800 with 532 nm excitation laser) in a confocal microscope backscattering configuration with spectral resolution about 1 cm$^{-1}$.
-Optical absorption spectra was recorded using UV-Vis-NIR spectrophotometer(Schimadzu, UV2600Plus) in transmission mode.
-When necessary, the as-synthesized sample was removed from substrates by light sonication(Branson 1510R-MTH, 70W) in ethanol for 15 seconds.
-The dispersion was left for 12 hrs to enable the possible sedimentation, after which became transparent under the unaided eye.
-Then the dispersion was transferred into one 10 mm quartz cuvette (Thorlabs, W005654) for absorption measurement with another paired cuvette containing ethanol only.
-
 %\printbibliography  %  comment out when assembling

### 2014-08-01 ch-intro/ch-instr.tex
moo3 draft 50%

@@
 The furnace is made by two semi-cylindrical ceramic fiber heaters (WATLOW inc.) with power density from 0.8 to 4.6 \si{W cm^{-2}}.
-Quartz tube (Quartz Sci inc.) of 1 inch diameter was primarily used as reaction chamber.
+Quartz tube (Quartz Sci inc.) of 1 in diameter was primarily used as reaction chamber.
 A mechanical pump was connected to maintain the low pressure environment inside the chamber.
-The length of uniform heating zone is 6 inches, with cooling zone extending outward.
+The length of uniform heating zone is 6 in, with cooling zone extending outward.
 Carriers gas argon (Ar) and reactant gas oxygen (\ce{O2}) was regulated by two mass flow controllers.
@@
     \midrule
-    Range      & RT-1100    & 10mTorr-1atm & 0 - 100 & 0-30  \\
+    Range      & RT-1100    & 10 mTorr-1 atm & 0 - 100 & 0-30  \\
     Resolution & $\pm1$  & correlated to flow & 1   & 0.1  \\
@@
 \item Working distance: 10 mm
-\item Scanning time: 80 sec
+\item Scanning time: 80 s
 \end{itemize}
@@
 
-Crystal structures of the as-synthesized specimens in this study were characterized using PANXpert X’pert Pro MRD with Cu $K\alpha_{avg}$ radiation at $\lambda$=1.5418\AA.
+Crystal structures of the as-synthesized specimens in this study were characterized using PANXpert X’pert Pro MRD with Cu $K\alpha_{avg}$ radiation at $\lambda$=1.5418 \AA.
 The nanostructures in this work usually grew without preferred orientation, and can be treated as powders.
@@
 \midrule
-3.135\AA & Cu $K\alpha$ & 1.541\AA & 28.45$^\circ$  \\
-3.135\AA & 200 kV & 0.0251\AA \textsuperscript{\emph{a}}& 0.45$^\circ$  \\
+3.135 \AA & Cu $K\alpha$ & 1.541 \AA & 28.45$^\circ$  \\
+3.135 \AA & 200 kV & 0.0251 \AA \textsuperscript{\emph{a}}& 0.45$^\circ$  \\
 \bottomrule
@@
 
-Raman spectroscopy, a common vibrational spectroscopy, is based on the inelastic scattering of a monochromatic excitation source in energy range of 100 to 4000 $cm^{-1}$.
+Raman spectroscopy, a common vibrational spectroscopy, is based on the inelastic scattering of a monochromatic excitation source in energy range of 100 to 4000 \si{cm^{-1}}.
 Being nondestructive and requiring minimal preparation,
@@
 In this study, Raman measurement was performed using a confocal micro-Raman system (Horiba Scentific, Labram HR800) with excitation wavelengths of 441, 532 and 632 nm.
-For nanowire samples, the laser powers were kept between 0.2 and 0.3 mW, and the acquisition time was 100 sec to avoid possible thermal damage.
-The spectral resolution is about 1 $cm^{-1}$ and the depth resolution about $2\mu m$.
+For nanowire samples, the laser powers were kept between 0.2 and 0.3 mW, and the acquisition time was 100 s to avoid possible thermal damage.
+The spectral resolution is about 1 \si{cm^{-1}} and the depth resolution about $2 \mu m$.
 
@@
 UV-Vis-NIR spectrophotometer is also a useful tool to obtain absorption and reflectance from various samples.
-The absorption can be described by Lambert-Beer law: $I = I_0 \exp{-\alpha(\lambda) x}$, where $\alpha$ is the absorption coefficient in unit of $cm^{-1}$, and $x$ is the optical path.
-When the sample is in liquid form, it is more convenient to use $I = I_0 \exp{-\epsilon(\lambda) C x}$, where $C(M = mol dm^{-3})$ is the molar concentration, and $\epsilon (M^{-1}cm^{-1})$ is the extinction coefficient.
+The absorption can be described by Lambert-Beer law: $I = I_0 \exp{-\alpha(\lambda) x}$, where $\alpha$ is the absorption coefficient in unit of \si{cm^{-1}}, and $x$ is the optical path.
+When the sample is in liquid form, it is more convenient to use $I = I_0 \exp(-\epsilon_\lambda C x)$, where $C(M = mol dm^{-3})$ is the molar concentration, and $\epsilon (M^{-1}cm^{-1})$ is the extinction coefficient.
 For example, $\epsilon$ for methylene blue (MB) is $10^5 M^{-1}cm^{-1}$ at 660 nm.\cite{Mills1999}
@@
 When necessary, the as-synthesized sample was removed from substrates by light sonication(Branson 1510R-MTH, 70W) in ethanol or DI water for 15 seconds.
-The dispersion was left for 12 hrs to enable the possible sedimentation.
+The dispersion was left for 12 h to enable the possible sedimentation.
 Then the dispersion was transferred into one 10 mm quartz cuvette (Thorlabs, W005654) for absorption measurement with another paired cuvette containing pairing liquid only.
 
-\section{Substrates and Pre-growth Treatments}
+\section{Substrates and Pre-growth Treatments}\label{ch2sub}
 
@@
 Depending on the specific experimental requirement, sometimes a hydrophilic surface is desired.
-We use plasma cleaning (Kurt J Lesker: Plasma-Preen 862) under 2 Torr \ce{O2} for 3 min to render a hydrophilic Si surface.
+A plasma cleaning was used (Kurt J Lesker: Plasma-Preen 862) to render a hydrophilic Si surface.
+The treatment was done at 2 Torr \ce{O2} for 3 minutes.
 In addition, substrates can be coated with a thin layer of metal before growth.

### 2014-08-01 ch-intro/ch-intro.tex
moo3 draft 50%

@@
 
-\chapter{introduction: nanomaterials for energy applications}
+\chapter{introduction}
 
-\section{Background and Motivation}
+\section{Background and Motivation: Nanomaterials for Energy Applications}
 
@@
 
+Energy saving and harvesting.
+
+why nano?
+surface-to-volume ratio, more surface area for catalytic reaction; surface energy state: tuned by dimension; quantum confinement effects: exciton size vs physical dimension.
+easy for dopant diffusion, thereby band structure modification; charge-separation and transport mechanism may also differ from bulk.
+
+\subsection{Electrochromism for Energy Saving}
+
+coloration efficiency, the doping amount,
+
+\subsection{Photocatalysis for Energy Harvesting}
+
+\subsection{Advantage of Nano-engineering}
+
 \section{Dissertation Outline}
@@
 The materials studied in this work/dissertation are tungsten oxides (\ce{WO3}), molybdenum oxides (\ce{MoO3}),and their chalcogenide counterparts (\ce{WS2} and \ce{MoS2}).
-Both tungsten (W) and molybdenum (Mo) belong to Group VIB transition metal, with outer shell electrons configuration as $4d^55s^1$ and $5d^46s^2$ respectively.
-Therefore we refer their oxides and chalcogenides as \gls{tmo} and \gls{tmdc}.\footnote{Obviously transition metals include many other elements, all of which have partially filled $d$-electron shell.
-But here we use TM to denote W and Mo exclusively.} We have synthesized \gls{tmo} and \gls{tmdc} at nanoscale, measured their crystalline structures and optical properties and demonstrated some devices assembled using as-synthesized nanomaterials.
+
+This dissertation work primarily focuses on growth and characterization, and will only present some preliminary tests on device and applications.
+Experimental tools for growth and characterization will be introduced in Chapter 2.
+Chapter 3 will be devoted to tungsten oxides (\ce{WO3}) and sodium tungsten oxides (\ce{Na5W14O44}) nanowires, where the role of sodium compounds in metallic tungsten precursors are thoroughly investigated.
+Chapter 4 will turn to molybdenum oxides (\ce{MoO3}) growth using alkaline metal compounds as catalysts.
+In Chapter 5, the growth of \gls{tmdc} and heterostructures will be discussed.
+Emphasis will be placed on the characterization of individual \ce{WO3}-\ce{WS2} core-shell \gls{nw}.
+The dissertation is then concluded with a summary and future work.
+
+We have synthesized \gls{tmo} and \gls{tmdc} at nanoscale, measured their crystalline structures and optical properties and demonstrated some devices assembled using as-synthesized nanomaterials.
 We aim to illustrate that by nanoengineering these \gls{tmo} and \gls{tmdc}, enhanced performances over their bulk states could be expected and new properties will arise.
@@
 We further demonstrated the application of as-synthesized \ce{MoO3} nanomaterials in electrochromic devices.
-In chapter 4 we discuss the growth of \gls{tmdc} and associated heterostructures.
-We synthesized \ce{WO3}-\ce{WS2} core-shell \gls{nw} and inspected the growth of \gls{fl} \ce{WS2}.
+In chapter 4 we discuss  We synthesized  and inspected the growth of \gls{fl} \ce{WS2}.
 Chapter 5 will conclude with an overall summary.
 
-\section{Nanomaterials for Energy Applications}
-
-why nano?
-surface-to-volume ratio, more surface area for catalytic reaction; surface energy state: tuned by dimension; quantum confinement effects: exciton size vs physical dimension.
-easy for dopant diffusion, thereby band structure modification; charge-separation and transport mechanism may also differ from bulk.
-
-\section{Crystal Structures and Electronic Properties}
-
-Solid and orderliness.
-
-Two theories arise to describe the outer shell electrons and to correlate the structure and physical properties: \gls{cft} and band theory.\cite{Goodenough1971} \gls{cft} assumes weak interaction between neighboring atoms and localization of electron towards parent atom, whereas band theory assumes that electron is shared equally by all nuclei and therefore a many-electron problems follows.
-Description of a single electron in periodic potential fail to treat the electron correlations adequately, as the interaction between atoms becomes weaker.For transition metals, $s$ and $p$ electrons are well described by a collective-electron model, while the 4f or 5f electrons are tightly bound to nuclei and screened from the neighboring atoms by 5s, 5p or 6s, 6p core electrons, hence it matches well with a localized-electron model.
-d electrons show intermediate character.
-
-\section{Growth Apparatus and Characterization Methods}
-\subsection{CVD System}
-
-Nucleation is a process of generating a new phase from a metastable old phase, where the Gibbs energy per molecule of the bulk of the emerging new phase is less than that of the old phase.
-
-  General CVD knowledge, substrate preparation, and\cite{MichealK.Zuraw2003}
-
-\subsection{Measurement}
-sample/specimen preparation, data processing,
-
-%\printbibliography  %  comment out when assembling
-
 %\input{../end.tex} %  comment out when assembling

### 2014-08-01 ch-moox/moox.tex
after a long pause
moo3 draft 50%

@@
 
-Molybdenum oxides \ce{MoO3} crystallizes in three phases, orthorhombic $\alpha$-\ce{MoO3}, monoclinic $\beta$-\ce{MoO3} and the metastable hexagonal h-\ce{MoO3}.\citep{Deb1968,Fibers2007} $\alpha$-\ce{MoO3} phase (hereafter \ce{MoO3})exhibits anisotropic structure with strong bonding along [001] and [100] direction while Van der Waals interaction along [010] direction.\cite{He2003} Due to this unique structure, \ce{MoO3} was found to have several important properties and a wide range of technological applications, such as electrochromism and photochromism,\cite{Yao1992} lubricants,\cite{Sheehan1996} photocatalysts,\cite{Chen2010} and gas sensor, including \ce{CO},\cite{Comini2005} \ce{NO2},\cite{Taurino2006} \ce{H2}\cite{Sha2009} and ethanol.\cite{Choopun} Moreover, other features arise when nanoscale \ce{MoO3} is specifically prepared, for instance, field emission.\citep{Li2002d,Zhou2003b}  As a layered hosting material, \ce{MoO3} can be further modified by intercalating with alkaline ions\citep{Spahr1995,Li2006b,Hu2011} and even divalent ion\cite{Sian2005}.
-This structural richness have enabled improved performance in Li-ion\cite{Mai2007} and sodium-ion battery.\cite{Hariharan2013} In combination with \ce{TiO2} forming a core-shell structure, these nanoparitcles are reported to lower the photoabsorption energy of \ce{TiO2}.\cite{Elder2000} When combined with Ag as layered structure, transparent conducting behavior was observed.\cite{Nguyen2012} In addition, \ce{MoO3} is a good precursor for preparing other useful materials, such as \ce{MoS2} fullerenes\cite{Li2003c}, and few layer \ce{MoS2}.\cite{Lin2012} It will also be an important member of the Van der Waals heterostructures.\cite{Geim2013}
+In this work, a new growth mechanism of molybdenum oxide (\ce{MoO3}) 1D structures was discovered, highlighted by \ce{MoO3} long nanobelts and micro-scale towers.
+The samples were synthesized using a group of alkaline metal based catalysts, including \ce{NaOH}, \ce{KI}, and \ce{Na2CO3}.
+In contrast to the sole axial growth found in the conventional catalyst-assisted growth, two different growth modes were observed for the \ce{MoO3} 1D growth here: transverse growth and axial growth.
+In the transverse mode, the 1D structures grow perpendicularly to the catalyst-deposition interface with catalyst particles on the side surfaces; whereas in the axial mode, the crystal grows along the catalyst-deposition axis.
+The growth modes were explained by a modified vapor-solid-solid (VSS) mechanism, and factors that affect the growth were explored in details.
 
-In this thesis, we developed a new method to prepare \ce{MoO3} by using alkaline oxides as catalysts.
-This newly discovered a vapor-liquid-solid growth mechanism produced two new \ce{MoO3} structures: long nanoribbons and microscale towers.
-We then investigated the phase and crystalline structures of these new morphologies, and demonstrated the application in photocatalyst and electrochromic devices.
+This remaining sections are organized as following: a brief review on previous studies of \ce{MoO3} is given first, followed is the synthesis method in this dissertation.
+Emphasis will be placed on morphological and crystal structure characterization of 1D \ce{MoO3} nanostructures, and the verification of proposed VSS mechanism.
+This chapter is concluded with a summary of VSS growth and some preliminary results of morphology controlled \ce{MoO3} nanostructures.
 
-\section{Synthesis and Properties of Molybdenum Oxides}
+\section{Synthesis and Properties of Molybdenum Oxide}
 
-\subsection{Growth of molybdenum oxides}
+Molybdenum oxide (\ce{MoO3}) crystallizes in three phases, orthorhombic $\alpha$-\ce{MoO3}, monoclinic $\beta$-\ce{MoO3} and the metastable hexagonal h-\ce{MoO3}.\citep{Deb1968,Fibers2007} $\alpha$-\ce{MoO3} phase (hereafter \ce{MoO3}) exhibits anisotropic structure with strong bonding along [001] and [100] direction while van der Waals interaction along [010] direction.\cite{He2003} Due to this unique structure, \ce{MoO3} was found to have several important properties and a wide range of technological applications, such as electrochromism and photochromism,\cite{Yao1992} lubricants,\cite{Sheehan1996} photocatalysts,\cite{Chen2010} and gas sensor, including \ce{CO},\cite{Comini2005} \ce{NO2},\cite{Taurino2006} \ce{H2}\cite{Sha2009} and ethanol.\cite{Choopun} Moreover, other features arise when nanoscale \ce{MoO3} is specifically prepared, for instance, field emission.\citep{Li2002d,Zhou2003b}  As a layered hosting material, \ce{MoO3} can be further modified by intercalating with alkaline ions\citep{Spahr1995,Li2006b,Hu2011} and even divalent ion.\cite{Sian2005} This structural richness have enabled improved performance in Li-ion\cite{Mai2007} and sodium-ion battery.\cite{Hariharan2013} In combination with \ce{TiO2} forming a core-shell structure, these nanoparitcles are reported to lower the photon absorption energy of \ce{TiO2}.\cite{Elder2000} When combined with Ag as layered structure, transparent conducting behavior was observed.\cite{Nguyen2012} In addition, \ce{MoO3} is a good precursor for preparing other useful materials, such as \ce{MoS2} fullerene\cite{Li2003c} and few layer \ce{MoS2}.\cite{Lin2012} It will also be an important member of the van der Waals heterostructures.\cite{Geim2013}
+
+\subsection{Growth of molybdenum oxide}
 
 Researchers have been exploring a variety of methods to synthesized different \ce{MoO3} nanostructures.
-We will not try to exhaust these efforts since it has been well summarized in several review articles.\cite{He2003} So we only gave a brief introduction here.
-Most of these methods can be categorized into two groups: solution-based hydrothermal procedures \citep{Li2002b,Xia2006,Li2006a,Camacho-Bragado2006} and chemical vapor transport and deposition approaches.
-\citep{Zeng1998,Li2002c,Li2002d,Zhou2003b,Fibers2007,Yan2009}.
+Only a brief introduction will be given here, since these efforts has been well documented in several review articles.\cite{He2003} Most of these methods can be categorized into two groups: solution-based hydrothermal procedures \citep{Li2002b,Xia2006,Li2006a,Camacho-Bragado2006} and chemical vapor transport and deposition approaches.\citep{Zeng1998,Li2002c,Li2002d,Zhou2003b,Fibers2007,Yan2009}.
 Both methods have its own merits.
@@
 The assistance of Au catalyst in vapor deposition only altered the orientation\cite{Yan2009} or served as preferred nucleation sites\cite{Cai2011} without producing new \ce{MoO3} structures.
-\citeauthor{Chithambararaj2013} prepared hexagonal \ce{MoO3} nanocrystal via hydrothermal method and demonstrated the photodegradation of MB under visible light.\cite{Chithambararaj2013} The efficiency dependence on catalysis/dye ratio, light intensity and temperature was studied.
+\citeauthor{Chithambararaj2013} prepared hexagonal \ce{MoO3} nanocrystal via hydrothermal method and demonstrated the photodegradation of methylene blue (MB) under visible light.\cite{Chithambararaj2013} The efficiency dependence on catalysis/dye ratio, light intensity and temperature was studied.
 h-\ce{MoO3} was mostly synthesized using solution methods, where \ce{NH4+} and \ce{OH-} were possible structure directing and stable agents.
-The band gap of h-\ce{MoO3} estimated from diffusion reflection spectrum is $2.8\sim3.0eV$.
+The band gap of h-\ce{MoO3} estimated from diffusion reflection spectrum is $2.8\sim3.0$ eV.
 Hexagonal phase of \ce{MoO3} is readily identified by the XRD pattern (strong peak at $2\theta=20^{\circ}$).
+It is worth noting that in spite of these numerous growth of \ce{MoO3}, reports on catalytic growth are still scarce.
 
-In spite of these numerous growth of \ce{MoO3}, we point out that reports on VLS mechanism and other than Si substrates are still scarce.
-We will explore these relative new domains and present our results in Sec.~\ref{sec:result}.
-
-\subsection{Crystal structures and chemical features of molybdenum oxides}
+\subsection{Lattice structures of molybdenum oxide and molybdates}
 
@@
 
-While considering the fact that four of the six surrounding O atom are at distances from 1.67\AA to 1.95\AA, while the remaining two are as far as 2.25 and 2.33\AA, \ce{MoO3} could be considered as built up of chains of \ce{MoO4} tetrahedra connected by the sharing of two oxygen corners with two neighbouring tetrahedra in $c$ axis.
+While considering the fact that four of the six surrounding O atom are at distances from 1.67 to 1.95 \AA, while the remaining two are as far as 2.25 and 2.33 \AA, \ce{MoO3} could also be considered as built up of chains of \ce{MoO4} tetrahedra connected by the sharing of two oxygen corners with two neighbouring tetrahedra in $c$ axis.
 The infinite chains of \ce{MoO4} tetrahedra from half-layers in the $ac$ plane.
-Two half-layers, which are stapled along $b$ axis, build up one \ce{MoO3} layer.\cite{Itoh2001a} This also stress that the \ce{MoO6} octahedra are rather distorted.
+Two half-layers, which are stapled along $b$ axis, build up one \ce{MoO3} layer.\cite{Itoh2001a} This view stresses that the \ce{MoO6} octahedra are rather distorted.
+A brief summary of crystallography, band structure and dielectric function is listed in Appendix.
 
-Due to the weak cation-oxygen bonding, alkali metal cations only introduce small perturbations into the energies of Mo-O or W-O ensembles in comparison to cations of other elements.
-And no mixing of vibrations of the cationic sublattices with that of \ce{Mo-O} or \ce{W-O} lattices.
-So the structural features of \ce{Mo-O} or \ce{W-O} polyhedra are dominating factors affecting the vibration frequencies and thermodynamic values of the molybdates and tungstates.\cite{Fomichev1992}
+It is known that a series of molybdate compound forms when alkali metal ions are incorporated into the \ce{MoO3} lattice, and the structures are summarized in Table.~\ref{tab:naxmow}.
+Due to the weak cation-oxygen bonding, alkali metal cations only introduce small perturbations into the energies of \ce{Mo-O} ensembles in comparison to cations of other elements.
+And no mixing of vibrations of the cationic sublattices with that of \ce{Mo-O} lattices is anticipated.
+So the structural features of \ce{Mo-O} polyhedra are dominating factors affecting the vibration frequencies and thermodynamic values of the molybdates.\cite{Fomichev1992}
 
@@
 \toprule
-formula & structure  & remarks  \\
+formula & structure  &  \\
 \midrule
@@
 Raman band assignment for \ce{A2MO4} is well grounded.
-Alkali metal cations with octahedral coordination occur below 230 $cm^{-1}$.
+Alkali metal cations with octahedral coordination occur below 230 cm$^{-1}$.
 For \ce{A2M_nO_{3n+1}}, exact assignment is not available yet due to the complicated \ce{MO6} octahedra.
 
-Molybdenum bronze also exhibits intriguing features, for instance, charge-density-wave states\footnote{In CDW states, conductivity is non-Ohmic above a threshold electric field} was found in blue bronze \ce{K_{0.3}MoO3}, which can be prepared by electrolytic reduction of \ce{K2MoO4} and \ce{MoO3} melt.\cite{Dumas1983} \ce{K_{0.3}MoO3} is side=centered monoclinic phase, with lattice parameter $a=18.249$\AA, $b=7.561$\AA, $c=9.856$\AA, and $\beta=117.54$ at RT.
-\ce{K0.3MoO3} presents a semiconductor-to-metal transition at 180 K.
+Molybdenum bronze also exhibits intriguing features, for instance, charge-density-wave states\footnote{In CDW states, conductivity is non-Ohmic above a threshold electric field.} was found in blue bronze \ce{K_{0.3}MoO3}, which can be prepared by electrolytic reduction of \ce{K2MoO4} and \ce{MoO3} melt.\cite{Dumas1983} \ce{K_{0.3}MoO3} stay as monoclinic phase at room temperature, with lattice parameter $a=18.249$ \AA, $b=7.561$ \AA, $c=9.856$ \AA, and $\beta=117.54$, and exhibits a semiconductor-to-metal transition at 180 K.
 Electrical transport measurements yield an highly anisotropic ratio of DC conductivities of 1:10:1000.
@@
 
-\subsection{Synthesis methods in this theis}
+\subsection{Synthesis methods in this thesis}\label{sec:grow}
 
@@
 
-\textbf{Substrate treatment.} Silicon substrates(p-$\langle100\rangle$, University Wafers) were first cut into 10mm by 25mm pieces and ultrasonically cleaned with acetone and ethanol for 15 minutes(Branson 1510R-MTH), each followed by blow-drying with nitrogen gas.
-Then the substrates were selectively treated in an oxygen plasma cleaning apparatus(Kurt J Lesker: Plasma-Preen 862, 2Torr) for 3 minutes to increase the wettability.
-The substrates without plasma cleaning were rendered as hydrophobic.
-Finally, the substrate was drop-cast 54 $\mu$L 10 mM \ce{NaOH} (or \ce{KI}, \ce{Na2CO3}) and naturally left dry in a convection hood with a flask cover above.
-Other alkaline ions-containing substrates, such as glass (Fisher Scientific, microscope slide, 12-549) and indium tin oxide (ITO) coated glass(Delta Technologies, 25\si{\ohm}), were cleaned by the same routine except the absence of plasma cleaning and subsequent aqueous solution dipping.
+\textbf{Substrate treatment.} Silicon substrates was first cleaned according to the procedure in Sec.~\ref{ch2sub} on page~\pageref{ch2sub}.
+To apply the catalysts, 54 $\mu$L 10 mM \ce{NaOH} (or \ce{KI}, \ce{Na2CO3}) was drop-cast and then naturally left dry in a convection hood.
+Other alkaline ions-containing substrates, such as glass (Fisher Scientific, microscope slide, 12-549) and indium tin oxide (ITO) coated glass (Delta Technologies, 25\si{\ohm}), were cleaned by the same routine except the absence of plasma cleaning and subsequent aqueous solution dipping.
 Mica was cleaved right before growth without other treatment.
@@
 Then the heating power was turned off and the chamber was allowed to naturally cool down to room temperature.
-The receiving substrate was placed in downstream location where the temperature was about 400 to 670 \si{\degreeCelsius} according to open air temperature profile.
-To observe the formation of droplets, clean silicon substrate was coated with 9 nm molybdenum film using a magnetron sputter(Desk IV TSC, Denton Vacuum), followed by \ce{NaOH} dipping as described before.
+The substrate was placed in downstream location where the temperature was about 350 to 650 \si{\degreeCelsius} according to open air temperature profile.
+To observe the formation of droplets, clean silicon substrate was coated with 9 nm molybdenum film using magnetron sputtering, followed by \ce{NaOH} dipping as described before.
 Then the substrate was placed into chamber for growth, where all the parameters remained unchanged except the absence of Mo powder source.
+Non-catalytic growth shares the same procedure except the Si substrate treatment.
 
-\textbf{Materials characterization.} The morphology and composition of the as-synthesized samples were analyzed by scanning electron microscopy (SEM,JEOL JSM-6480) and energy dispersive X-ray spectroscopy (EDS,Oxford Instrument INCA).
-Crystal structures were characterized using X-ray diffraction (XRD, PANXpert X’pert Pro MRD with Cu $K\alpha$ radiation at $\lambda$=1.5418\AA) and transmission electron microscopy (TEM, JEOL JEM-2100 \ce{LaB6} operated at 200kV).
-Optical measurements were performed by Micro-Raman spectroscopy (Horiba Scientific, Labram HR800 with 532 nm excitation laser) in a confocal microscope backscattering configuration with spectral resolution about 1 cm$^{-1}$.
-Optical absorption spectra was recorded using UV-Vis-NIR spectrophotometer(Schimadzu, UV2600Plus) in transmission mode.
-The as-synthesized sample was removed from substrates by light sonication(Branson 1510R-MTH, 70W) in ethanol for 15 seconds.
-The dispersion was left for 12 hrs to enable the possible sedimentation, after which became transparent under the unaided eye.
-Then the dispersion was transferred into one 10 mm quartz cuvette (Thorlabs, W005654) for absorption measurement with another paired cuvette containing ethanol only.
+\section{Results and Discussion on Molybdenum Oxide}\label{sec:result}
 
-\section{Discussion on molybdenum oxides}\label{sec:result}
+In this section, the growth of \ce{MoO3} on Si was presented first, followed by catalytic growth, both of which were characterized by SEM, XRD, TEM and EDX.
+Then the catalytic growth mechanism was investigated using \ce{NaOH} treated Si substrate.
+\subsection{Growth on Si substrates}\label{sec:nonsi}
 
-In vapor synthesis process, two growth mechanism exists: VS and VLS.
-VS process is widely accepted for the growth of \ce{MoO3}.
-Yet we caution that synthesis conditions should be scrutinized to determine the exact mechanism.
-\citeauthor{Li2002c} suggested a VS mechanism at 700 \si{\degreeCelsius} and VLS at 750 \si{\degreeCelsius} and higher.\cite{Li2002c} \citeauthor{Fibers2007} proposed a modified VS mechanism probably because the deposition occurs on \ce{Al2SiO5} with possible \ce{Al_{0.95}SiNa_{0.06}O_x} involved.
-Therefore temperature and possible impurity could potentially alter the growth mechanism.
-We divide the growth results into two categories: on Si substrate and on non-Si substrate, and describe them respectively.
-We also briefly mention using liquid exfoliation to prepare few layer \ce{MoO3}.
-
-\subsection{Growth on Si substrates}
-
-Mo began to be oxidized into \ce{MoO3} at 500 \si{\degreeCelsius}, \ce{MoO3} vapor pressure began to increase rapidly above 700 \si{\degreeCelsius}.
-\cite{Margrave1967} And the melting point of \ce{MoO3} is reported as 795 \si{\degreeCelsius}.
-With these facts in mind, we design the experimental parameters as listed in Table.~\ref{tab:mooxsi}.
-We should point out that these parameters are selected and optimized from a wide range of combinations.
-And when we discuss the influence of one parameter with different values, one should assume other parameters still adapt those listed in Table.~\ref{tab:mooxsi}.
-
+The oxidization of Mo starts at 500 \si{\degreeCelsius}, and \ce{MoO3} vapor pressure begins to increase rapidly above 700 \si{\degreeCelsius}.\cite{Margrave1967} The melting point of \ce{MoO3} is reported as 795 \si{\degreeCelsius}.
+Based on these data, the growth was designed with parameters listed in Table.~\ref{tab:mooxsi}.
+It is worth mentioning that these parameters are selected and optimized from a wide range of combinations.
+And when the influence of one parameter is studied, the others are fixed.
+%growth parameter
 \begin{table}[htb]
@@
 \cmidrule(l){4-5}
- & Temperature $T_h$ (\si{\degreeCelsius}) & Pressure  & Ar & \ce{O2}  \\
+ & Temperature $T_h$ (\si{\degreeCelsius}) & Pressure (mTorr) & Ar & \ce{O2}  \\
 \midrule
-typical values  & 800    & 200mTorr & 10 & 10  \\
+Typical values  & 800    & 200 & 10 & 10  \\
+\bottomrule
 \end{tabular}
@@
 Notice that on the horizontal axis of temperature, zero inch is defined at the upstream edge of furnace.
-To facilitate discussion and provide a tight context, we define the position of substrate as the coordinate of its upper-stream edge along this temperature axis (i.e.
-the substrate location is 7 inch in Fig.~\ref{fig:mooxgrowth}).
-The usual length of Si substrate is 1 inch.
-When positioned at 7 inch, it is then located in a temperature range of $650 \sim 350$ \si{\degreeCelsius}.
-
+To facilitate discussion and provide a tight context, the author define the position of substrate as the coordinate of its upper-stream edge along this temperature axis (i.e.
+the substrate location is 7 in in Fig.~\ref{fig:mooxgrowth}).
+The usual length of Si substrate is 1 in.
+When positioned at 7 in, it is then located in a temperature range of $650 \sim 350$ \si{\degreeCelsius}.
+% cvd layout
 \begin{figure}[htb]
 \centering
-\includegraphics[width=0.8\textwidth]{CVD_and_temp_MoO3.jpg}
+\includegraphics[width=0.7\textwidth]{CVD_and_temp_MoO3.jpg}
 \caption[Growth setup of \ce{MoO3}]{Chemical vapor system and its temperature profile.
-The triangular labels $\blacktriangledown$ were measured points at ambient pressure.
+The triangular labels $\blacktriangledown$ were measured points at ambient environment.
 The nominal substrates temperature were estimated from interpolation data.}
@@
 
-From previous works,\cite{predeep2011} we found that with $T_h = 600$ and substrate placed at 6.5 inches, microflakes was found at the high temperature edge of Si, suggesting the nucleation already started.\footnote{020510 batch} When flow of oxygen was gradually reduced, diminished size of micro-flake was observed at the same location of substrates.
-This results indicated the rate-determining step is diffusion when oxygen flow was in the range of 2 sccm to 0.5 sccm.\footnote{(31210-31510 batches)} We also found the deposition amount on a particular location of the substrate is not linearly proportional to the growth time, i.e., the growth at upper stream edge first increase then decrease.
+From previous works in our group,\cite{predeep2011} the author found that with $T_h = 600$ \si{\degreeCelsius} and substrate placed at 6.5 in, microflakes grew at the high temperature edge of Si, suggesting the nucleation already started.\footnote{020510 batch} When flow of oxygen was gradually reduced, diminished size of micro-flake was observed at the same location of substrates.
+This results indicated the rate-determining step is diffusion when oxygen flow was in the range of 2 sccm to 0.5 sccm.\footnote{(31210-31510 batches)} The author also found the deposition amount on a particular location of the substrate is not linearly proportional to the growth time, \emph{i.e.}, the growth at upper stream edge first increase then decrease.
 This is not surprising when considering the temperature field requires some time to become synchronized as depicted in Fig.~\ref{fig:mooxgrowth}.
-Using conditions in Table.~\ref{tab:mooxsi} and 1 hr growth, we observed the typical micro-flakes morphologies as shown in Fig.~\ref{fig:mosisem}.
-Most flakes exhibit rectangular shape, with average thickness of one micron, standard deviation $\sigma_D=0.34\mu m$.
-
+Using conditions in Table.~\ref{tab:mooxsi} and 2 h growth, the author observed the typical micro-flakes morphologies as shown in Fig.~\ref{fig:mosisem}.
+Most flakes exhibit rectangular shape, with average thickness of one micron, standard deviation $\sigma_D=0.34$  $\mu m$.
+% sem
 \begin{figure}[htb]
@@
 \subfloat[]{\label{fig:mosem2}\includegraphics[width=0.45\textwidth]{mosemsi_b}}
-\caption[Representative morphologies of \ce{MoO3} on Si]{SEM images of representative depositions of \ce{MoO3} on Si. (a)Low magnification. (b) High magnification. }
+\caption[Representative morphologies of \ce{MoO3} on Si]{(a) Low magnification and (b) high magnification SEM images of representative depositions of \ce{MoO3} on Si for non-catalytic growth.}
 \label{fig:mosisem}
@@
 
-This rectangular shape implies the boundary plane along growth direction (long axis) is (001), in consistency with previous experimental reports\cite{Zeng1998,Li2002b} and theoretical studies.\cite{Firment1983,Cora1997} We also observed different shapes, i.e., elongated hexagonal using similar growth conditions.
-This is not an indication of different growth mode.
-It is a normal thermodynamic fluctuation.
-The growth rates along different crystalline direction of \ce{MoO3} are determined by the free surface energy.
-In fact, (201), (101) and (102) planes have all been observed as terminating planes.\cite{Zeng1998} The stacking rate of \ce{MoO6} octahedra along $a$ and $c$ axis could develop some other ratio.
-And the coexistence of different planes in one growth suggests the similarity of free surface energies between these surfaces.
-In other words, the migration barrier of adatoms on (010) plane is presumably much lower than that on other low index planes due to the Van der Waals interaction nature along [010] direction.
-
+As shown in Fig.~\ref{fig:mooxch}, the crystal structure and phase of as-synthesized samples were examined by XRD and Raman.
+The XRD pattern (Fig.~\ref{fig:moxrd}) is readily indexed to the orthorhombic phase of \ce{MoO3} (ICDD PDF 05-0508, \emph{a}=3.9628 \AA, \emph{b}=13.855 \AA, \emph{c}=3.6964 \AA).
+The space group is $D_{2h}^{16}(Pbnm)$.
+This crystal structure is indeed a unique example among transition metal oxides, representing a transitional stage between tetrahedra and octahedral coordination.\cite{Itoh2001a} The strongest peak index is (110), suggesting the orientation of \ce{MoO3} is not parallel to the substrate, which is consistent with the morphology displayed in Fig.~\ref{fig:mosem1}.
+In contrast, a different XRD peak pattern is observed in Sec.~\ref{sec:nasi}, where the catalytic growth occurs.
+% xrd raman
 \begin{figure}[htb]
@@
 \subfloat[]{\label{fig:moram}\includegraphics[width=0.45\textwidth]{raman_moo3}}
-\caption[Crystalline phase characterization of \ce{MoO3} on Si]{(a) XRD pattern and (b) Raman spectrum of typical \ce{MoO3} on Si, $\lambda_{ex} = 532nm$.}
+\caption[Crystalline phase characterization of \ce{MoO3} on Si]{(a) XRD pattern and (b) Raman spectrum of typical \ce{MoO3} on Si, $\lambda_{ex} = 532$ nm.}
 \label{fig:mooxch}
@@
 
-As shown in Fig.~\ref{fig:mooxch}, the crystal structures and phase of as-synthesized samples were examined by XRD and Raman.
-The XRD pattern (Fig.~\ref{fig:moxrd}) is readily indexed to the orthorhombic phase of \ce{MoO3} (ICDD PDF 05-0508, \emph{a}=3.9628\AA, \emph{b}=13.855\AA, \emph{c}=3.6964\AA).
-The space group is $D_{2h}^{16}(Pbnm)$.
-This crystal structure is indeed a unique example among transition metal oxides, representing a transitional stage between tetrahedra and octahedral coordination.\cite{Itoh2001a} The strongest peak index is (110), suggesting the orientation of \ce{MoO3} is not parallel to the substrate, which is consistent with the morphology displayed in Fig.~\ref{fig:mosem1}.
-In contrast, we shall see a different scenario in Section.~\ref{sec:nasi}, where the orientation is changed.
-
+The Raman spectrum of as-synthesized specimens also closely matches \ce{MoO3} features in previous studies.\cite{Dixit1986,Silveira2012} During m-Raman measurement, the laser spot was carefully focused onto the plates and several inspections on different positions were observed to ensure the reproductivity of spectra data.
+As shown in Fig.~\ref{fig:moram}, 14 distinct bands were well resolved.
+The 284 \si{cm^{-1}} peak represents the wagging mode for double bond \ce{O=Mo=O}.
+The 337 and 380  \si{cm^{-1}} peaks are assigned to \ce{O-Mo-O} bending and scissoring modes.
+The 199 \si{cm^{-1}} peak and two other weaker peaks at 218 and 247 \si{cm^{-1}} represent \ce{O=Mo=O} $B_{2g}$ twist, $A_g$ chain mode and \ce{O=Mo=O} $B_{3g}$ twist mode, respectively.
+The 667 \si{cm^{-1}} peak is assigned to triply coordinated oxygen stretching model resulting from edge-shared oxygen in common to three octahedral.
+The 819 \si{cm^{-1}} peak is from doubly coordinated oxygen stretching mode arising from corner-shared oxygen between two octahedral.
+The 996 \si{cm^{-1}} peak comes from unshared oxygen stretching mode.\cite{Siciliano2009} The assignment is summarized in Table.~\ref{tab:moram}.
+% raman assign
 \begin{table}[htb]
@@
 
-The Raman spectrum of as-synthesized specimens also closely matches \ce{MoO3} features in previous studies.\cite{Dixit1986,Silveira2012} During m-Raman measurement, the laser spot was carefully focused onto the plates and several inspections on different positions were observed to ensure the reproductivity of spectra data.
-As shown in Fig.~\ref{fig:moram}, 14 distinct bands were well resolved.
-The 284 \si{cm^{-1}} peak represents the wagging mode for double bond \ce{O=Mo=O}.
-The 337 and 380  \si{cm^{-1}} peaks are assigned to \ce{O-Mo-O} bending and scissoring modes.
-The 199 \si{cm^{-1}} peak and two other weaker peaks at 218 and 247 \si{cm^{-1}} represent \ce{O=Mo=O} $B_{2g}$ twist, $A_g$ chain mode and \ce{O=Mo=O} $B_{3g}$ twist mode, respectively.
-667 \si{cm^{-1}} peak is assigned to triply coordinated oxygen stretching model resulting from edge-shared oxygen in common to three octahedral.
-The 819 \si{cm^{-1}} peak is from doubly coordinated oxygen stretching mode arising from corner-shared oxygen between two octahedral.
-The 996 \si{cm^{-1}} peak comes from unshared oxygen stretching mode.\cite{Siciliano2009} The assignment is summarized in Table.~\ref{tab:moram}.
+\subsection{Growth on NaOH-Si substrate}\label{sec:naohsi}
 
-\subsection{Liquid exfoliation on as-grown molybdenum oxides}
+All samples in Sec.~\ref{sec:naohsi} were grown for 2 h, too.
+The only difference in growth conditions from Sec.~\ref{sec:nonsi} is the Si substrate treatment.
+When NaOH is applied onto Si, the morphologies change significantly.
+Fig.~\ref{fig:ch4sem2by3} shows a comparison of the morphology difference between the non-catalyst growth (Fig.~\ref{fig:ch4sem2by3}a) and the catalyst-assisted growth (Fig.~\ref{fig:ch4sem2by3}b-f) revealed by SEM.
+The non-catalyst growth morphology has been discussed from Fig.~\ref{fig:mosisem} on page~\pageref{fig:mosisem}.
+Several different structures emerge when catalyst is applied, such as nanobelts in Fig.~\ref{fig:ch4sem2by3}d with length up to hundreds of microns, and microtowers in Fig.~\ref{fig:ch4sem2by3}f with diameter around 10 $\mu m$.
 
-Few layer (FL) materials attracts intensive research efforts recently.
-We studied using liquid exfoliation method to prepare FL \ce{MoO3}.
-We then characterized the absorption feature and crystalline structures of the exfoliated \ce{MoO3} using UV-Vis and TEM.
-Then we calculate the optical contrast of FL \ce{MoO3} on \ce{SiO2}-Si, which serves as a guideline to identify FL \ce{MoO3} using optical microscope.
-
-The exfoliation solution is 30\% isopropanol (IPA) in DI water, which has been proved to work well on other layered compounds.\cite{Halim2013} After 20 minutes sonication, the dispersion is milky.
-We measured the transmission spectra of this dispersion immediately upon sonication and after 40 hrs for gravity sedimentation, as illustrated in Fig.~\ref{fig:moabs}.
-The t0 line mainly arises from the scattering of flakes in the dispersion.
-There are two scattering mechanisms: Rayleigh scattering and Tyndall scattering.
-Rayleigh scattering, which occurs when particles are comparable to wavelength, is inversely proportional to the fourth power of wavelength; While Tyndall scattering, which occurs when the particles are larger, is inversely proportional to the square of the wavelength.
-To fully evaluate the true absorbance of the sample itself, one needs to decouple the scattering part from apparent absorbance.
-Generally we select one part of spectrum and assume it is only caused by scattering.
-Then a empirical dependence shown in Eq.~\ref{eq:sca2} is used as polynomial fitting model.
-
-\begin{align}
-Abs_{sca}  & = a\times \lambda^{n}  \label{eq:sca1}\\
-\log{Abs_{sca}} & = \log{a} + n*\log{\lambda} \label{eq:sca2}
-\end{align}
-
-After least-squares fitting, the coefficients $a$ and $n$ can be used to estimated the scattering in other wavelengths.
-The fitting of $n$ usually falls between -2 and -4.
-We examined the t40h line in Fig.~\ref{fig:moabs} and found the scattering part is almost zero.
-Therefore we did not perform aforementioned fitting.
-This is not always the case.
-In Chapter on the \ce{WS2} section, we do need to do so.
-
+% sem
 \begin{figure}[htb]
 \centering
-\subfloat[]{\label{fig:moabs}\includegraphics[width=0.45\textwidth]{MoO3-abs}}\hspace{0.04\textwidth}
-\subfloat[]{\label{fig:mobg}\includegraphics[width=0.45\textwidth]{MoO3-bg}}
-\caption[UV-Vis spectra of exfoliated \ce{MoO3}]{(a) UV-Vis absorbance spectra of exfoliated \ce{MoO3}.
-Dashed line (t0) represents measurement immediately after sonication, and solid line (t40h) is obtained after sitting for 40 hours.
-The dot dashed line is reference spectrum of the 30\% IPA.
-(b) Band gap estimation}
-\label{fig:mouv}
+\includegraphics[width=0.8\textwidth]{MoO3_SEM_a.jpg}
+\caption[SEM imaging on \ce{MoO3} catalytic growth]{Effect of alkaline metal-based catalysts on the morphology of \ce{MoO3} depositions.
+(a) SEM image of rectangular nanoplates grown without catalysts.
+(b-f) SEM images of different morphologies grown with NaOH catalysts: (b) nanobelts grown on top of dense array of nanoplates,(c) close-up view of the forked nanoplates from an area indicated by the square in Fig.~\ref{fig:ch4sem2by3}, (d) long nanobelts, (e) side-view of ultra-long microbelts, and (f) side-view of microtowers.
+Insets show detailed features of different \ce{MoO3} structures.}
+\label{fig:ch4sem2by3}
 \end{figure}
 
-According to the corrected absorbance spectrum, optical band gap can be deduced, which is known as Tauc Plot.\cite{Tauc1972} The procedure is recapitulated here.
-Eq.~\ref{eq:tauc} is given to empirically relate optical band gap to absorption.
-
-\begin{equation}\label{eq:tauc}
- (h\nu \alpha)^{\frac{1}{n}} = B(h\nu - E_g^{opt}),
-\end{equation}
-where B is a proportional coefficient, $\alpha$ is absorption\footnote{The absorbance $A = 0.4343\alpha*l$, where l is the optical path} and $E_g^{opt}$ is defined as optical band gap.
-The value n is correlated to the nature of optical transition.
-\begin{itemize}
-\item For direct allowed transition, n = 1/2;
-\item For direct forbidden transition, n = 3/2;
-\item For indirect allowed transition, n = 2;
-\item And for indirect forbidden transition, n = 3.
-\end{itemize}
-
-When the transition nature of sample is not well known, one should apply each to check which one provide the best fit.
-Depending on the synthesis methods and \ce{MoO3} morphologies, the transition phenomena might vary.
-On the \ce{MoO3} films, \citeauthor{Bouzidi2003} assumed a direct gap (n = 1/2)\cite{Bouzidi2003} while \citeauthor{Szekeres2002} not.\cite{Szekeres2002} We use n = 2 in this work, plot $\sqrt{(h\nu \alpha)}$ versus photon energy, and extrapolate the linear part onto $h\nu$ axis.
-The intercept is used as $E_g^{opt}$ then.
-Our evaluation and some previous studies is summarized in Table.~\ref{tab:mobg}.
-
+The crystal structures of the as-synthesized specimens were characterized with X-ray diffraction (XRD) for the non-catalyst growth (Fig.~\ref{fig:ch4tem3by3}a) and catalyst-assisted growth (Fig.~\ref{fig:ch4tem3by3}b).
+The calculated lattice parameters and standard database value(ICDD PDF 05-0508), as listed in Table.~\ref{tab:ch4xrd}, matches favorably.
+No other phases were found from XRD spectra for both specimens.
+This result indicates that if there were any catalyst phases present in the catalyst-assisted specimen, they must be of extremely low amount as compared to that of the \ce{MoO3} phase, presumably below the detection limit.
+% xrd 
 \begin{table}[htb]
 \centering
-\caption{Optical band gaps of \ce{MoO3}}\label{tab:mobg}
-\begin{tabular}{lccr}
+\caption{Lattice information of \ce{MoO3}}\label{tab:ch4xrd}
+\begin{tabular}{lccc}
 \toprule
-&\multicolumn{2}{c}{Band gap} \\
-\cmidrule(l){2-3}
-Reference & value(eV) & orientation & material states\\
+           & $a$ (\AA) & $b$ (\AA) & $c$ (\AA)   \\
 \midrule
-\cite{Deb1968}   & 2.96  & $E\parallel c_0$ & single crystal\\
-\cite{Deb1968}   & 2.80  & $E\perp c_0$ & single crystal \\
-\cite{Julien1995} & 2.8$\sim$ 3.2 & NA & films\\
- this work  & 3.1  & NA & nanoflakes\\
+Non-catalytic growth  & 3.963    & 13.882 & 3.701  \\
+Catalytic growth  & 3.967    & 13.865 & 3.701  \\
+PDF 05-0508       & 3.9628    & 13.855 & 3.6964  \\
 \bottomrule
@@
 
-An alternative apporach is a) define $Y = \alpha E=\alpha h\nu$, and obtain $Y' = \frac{\partial Y}{\partial E}$, then b) plot $Y'/Y$ versus $h\nu$.
-The band gap value can be obtained from the intercept of extrapolated line on photo energy axis.\cite{Choopun} This approach is not difficult to comprehend as long as we notice from Eq.~\ref{eq:tauc}, $Y = B (h\nu - E_g^{opt})^n$ and $Y' = B n(h\nu - E_g^{opt})^{n-1}$.
-The advantage is one can also estimate n without using assumption.
+The XRD pattern of catalyst-assisted growth shown in Fig.~\ref{fig:ch4tem3by3}b is dominated by the (0$k$0) family peaks, showing a different preferred orientation from the non-catalytic growth.
+The reason will be discussed in Sec.~\ref{sec:nasi}.
 
-The dielectric constants\footnote{Not a constant at all, instead, it has complicated dependence on photon energy} ($\epsilon = \epsilon_1 + i*\epsilon_2$) of \ce{MoO3} have been studied in several reports.\cite{Deb1968,Sabhapathi1995,Miyata1996,Abdellaoui1997,Mondragon1999} We extracted $\epsilon_1$ from Ref\cite{Itoh2001a} due to the wide photon energy range utilized.
-We also notice that $\epsilon_2$ is approximately zero when $h\nu$ is less than 4 eV.
-Since we are primarily concerned with the optical contrast of FL \ce{MoO3} in visible wavelength region($h\nu < 3$ eV), we obtained refractive indices $n$ from $n = \sqrt{\epsilon_1}$.
-Due to the orthorhombic phase, \ce{MoO3} exhibit birefringence, that is there are two refractive indices, $n_c$ and $n_a$, as shown in Fig.~\ref{fig:moind}.
-The refractive index is between $ 2.2\sim 2.4$ along a axis, and $ 2.5\sim 2.8$ along c axis.
-Comparison to the low frequency dielectric constant ($18.0\pm1$) implies a primarily ionic bonding in \ce{MoO3}.\cite{He2003}
+% tem
+\begin{figure}[htb]
+\centering
+\includegraphics[width=0.8\textwidth]{MoO3_TEM_XRD.jpg}
+\caption[XRD and TEM on \ce{MoO3} catalytic growth]{XRD spectra of (a) a specimen grown without catalysts and (b) a specimen grown with NaOH catalysts.
+(c) Low-magnification TEM image and (d) HRTEM image of nanoplate grown without catalyst.
+Low-magnification TEM images of (e) forked nanoplate, (f) nanobelt, and (h) microtower, and (g) HRTEM image of nanobelt.
+Insets show SAED patterns of different \ce{MoO3} 1D structures}
+\label{fig:ch4tem3by3}
+\end{figure}
+
+Fig.~\ref{fig:ch4tem3by3}c shows low magnification TEM image of a rectangular nanoplate grown without catalysts and the SAED pattern.
+The nanoplate was exfoliated by ultra-sonication in acetone solution to obtain high-resolution TEM (HRTEM) image, hence the nanoplate was broken into a smaller piece.
+The SAED pattern in [010] axis and the HRTEM image (Fig.~\ref{fig:ch4tem3by3}d) show the nanoplate has a (010) top surface and two orthogonal edges along [100] and [001] respectively.
+For the catalyst-assisted growth, Fig.~\ref{fig:ch4tem3by3}e and Fig.~\ref{fig:ch4tem3by3}f-g confirm both the forked nanoplate and the nanobelt have a (010) top surface and a growth direction of [001], while Fig.~\ref{fig:ch4tem3by3}h reveals the microtower grow with (010) layers stacking along a [010] direction.
+Lattice measurements in Fig.~\ref{fig:ch4tem3by3}d and g indicate a planar distance of 0.38 nm for (100) planes and 0.36 nm for (001) planes.
+These values are slightly smaller than the standard data for $\alpha$-\ce{MoO3} and the results from XRD measurements.
+This deviation in lattice parameters may arise from the small error in TEM measurements and the lattice distortion from the electron beam irradiation.
+These results indicate that all the as-synthesized 1D structures have a layered structure.
+Raman scattering measurement on the catalytic growth sample revealed similar \ce{MoO3} bands, as already displayed in Fig.~\ref{fig:mooxch} on page~\pageref{fig:mooxch}.
+
+\subsection{Growth mechanism study}\label{sec:nasi}
+
+To provide a proper context, Vapor-Liquid-Solid (VLS) process is brief introduced.
+VLS is first proposed by Wagner,\cite{Wagner1964} and further developed by \citeauthor{Givargizov1975}.\cite{Givargizov1975} This method has become an important strategy for synthesizing 1D nanostructures.\cite{Lieber1998} Conventionally, a liquid eutectic droplet is formed by catalyst itself or by alloying with the growth material, acting as a trap of growth species.
+The growth is initialized by supersaturation of the liquid alloy and subsequent precipitation at the solid-liquid interface.
+The choice of catalyst usually is among the several noble metals since they are physically active but chemically stable or inert in most growth scenarios.
+The growth materials span a wide range including group IV,\cite{Hochbaum2005} group III-V,\citep{Dalacu2013, Xiao2012, Dubrovskii2011} group II-VI,\cite{Hao2006} and some metal oxides, such as \ce{ZnO},\citep{Huang2001a,Ramgir2010} \ce{MgO},\citep{HEUER1967, Nagashima2007} \ce{SiO2},\cite{Pan2002} and \ce{TiO2},\cite{Zhuge2012} to name a few.
+The catalysts can be Au, Pd, Pt, Ni,\cite{Xiao2012} Ti, Ga,\cite{Pan2002} and even KI.
+
+Understanding the interaction between liquid droplet and the solid interface allows for a rich engineering space to fine tune the geometry and structures of as-grown nanostructures.
+For instances, the diameter of Si nanowires (NWs) can be controlled by laser ablated catalyst\cite{Morales1998} or well-defined Au nanoparticles.\cite{Cui2001b} Under proper conditions, axial modulation can produce nanowire superlattices from group IV and III-V materials.\citep{Gudiksen2002,Bjork2002}  Radial composition modulation have also been demonstrated by selectively suppressing VLS process, providing a robust routine for homogeneous or heterogeneous core-shell structures.\cite{Lauhon2002a}
+
+Previous study in our group has found that \ce{MoO3} deposition on ITO/glass exhibits new morphologies that are not observed on Si substrates, yet the mechanism is not well investigated.\cite{predeep2011} Based on the VLS process, it is known that a eutectic state is the key to promote preferred growth direction.
+A list of composition difference between glass and Si substrate shows the extra elements of Na, K, Ca, etc.
+Since the concentration of Na is highest among these extra elements, it is most likely to induce the new morphology growth.
+A literature search indeed results a Na-Mo-O phase diagram as shown in Fig.~\ref{fig:ch4pd}.\cite{Hoermann1929} Notice the phases of the Na-Mo-O system can be written as \ce{Na2O.nMoO3}, where n = 1, 2, 3, and 4.
+
+%phase diagram
+\begin{figure}[htb]
+\centering
+\includegraphics[width=0.4\textwidth]{Na2MoO4_Phase}
+\caption[Phase diagram of Na-Mo-O system]{Phase diagram of \ce{Na2MoO4} and \ce{MoO3} reproduced from ref.~\cite{Hoermann1929}}
+\label{fig:ch4pd}
+\end{figure}
+
+Based on this phase diagram and the growth conditions adopted in this study, it is predicted that the overall reactions occur in the following sequences.
+First, Mo powder is oxidized and \ce{MoO3} vapor is produced and transported to downstream by Ar carrier gas.
+Then NaOH reacts with incoming \ce{MoO3} according to formula~\ref{eq:pd}.
+
+\begin{align}\label{eq:pd}
+\cee{NaOH(l) + MoO3(g) -> Na2MoO4(l) + H2O(g)}\\
+\cee{Na2MoO4 + nMoO3   -> Na2O.(n+1)MoO3}
+\end{align}
+
+The melting point of \ce{Na2MoO4} is 687 \si{\degreeCelsius}.
+Based on the open air temperature profile (Fig.~\ref{fig:mooxgrowth}), the substrate is locate in temperature zone between 650 and 350 \si{\degreeCelsius}.
+The temperature distribution is different due to both the sealed condition and thermal conduction along the Si substrate.
+It is difficult to acquire the accurate values along the substrate.
+However by considering the flow rate, the actual temperature will be higher than predicted by open air measurement.\cite{Subannajui2010} The melting of \ce{Na2MoO4} is highly possible when taking into account of its size as well.\cite{Bruggemann1997} The continuous supply of \ce{MoO3} growth species will push the phase evolution towards high \ce{MoO3} molar ratio end, with $n$ in \ce{Na2O.nMoO3} increasing from 1 to 4.
+Each site of \ce{Na2MoO4} will continue absorb incoming \ce{MoO3}, forming a swelling droplet.
+\ce{MoO3} will precipitate from these seeds when a critical supersaturation concentration is reached, which is about 75\% according to Fig.~\ref{fig:ch4pd}.\footnote{This ratio considerably exceeds that of the usual metal catalyst scenario.
+This high solubility accounts for several observations in current experiments: the dimensions of individual deposit is much larger than that of initial droplet, the concentration of sodium in final products is extremely low.}
+
+Based on this aforementioned analysis, the author propose a hypothesis as summarized in Assumption~\ref{hypo1}.
+%theorem environment
+\begin{hypothesis}\label{hypo1}
+The reaction on NaOH-Si substrate follow the phase diagram, and \ce{Na2Mo4O13} serves as the catalyst promoting various 1D \ce{MoO3} growth. 
+\end{hypothesis}
+
+In a typical 2 h growth, the \ce{MoO3} weight increase is about 20 mg, which is about $1.4\times 10^{-4}$ mol.
+This amount far exceeds the mole of applied NaOH $5\times 10^{-7}$.\footnote{Sec.~\ref{sec:grow} on page.~\pageref{sec:grow}} To capture the early stage growth, the supply of \ce{MoO3} must be reduced in a controlled way.
+This can be accomplished by tuning two factors: oxygen flow rate and growth time.
+In this thesis, two series of controlled growth were used to probe the evolution of \ce{MoO3} deposition on NaOH-Si substrate.
+The first series regulated \ce{O2} flow at 0.1, 1, 3 and 10 sccm with fixed growth time of 15 min.
+The second series controls growth time at 15, 30, 60, and 90 min with fixed \ce{O2} flow of 10 sccm.
+Two series share one common growth of 10 sccm \ce{O2} for 15 min.
+
+The oxygen regulated growths were characterized using SEM, EDX and Raman, as shown in Fig.~\ref{fig:ch4oxy}.
+When \ce{O2} flow $\leq 1$ sccm, the deposition show micron size plate growth(Fig.~\ref{fig:ch4oxy}a and d).
+As oxygen flow becomes higher, the deposition amount increases dramatically, with a morphology of 1D forked plate decorated by triangular shape particles.
+% sem
+\begin{figure}[htb]
+\centering
+\includegraphics[width=0.8\textwidth]{MoO3_EDX_Raman}
+\caption[Growth evolution of \ce{MoO3}: first stage]{Evolution of the early stage for catalyst-assisted \ce{MoO3} growth: SEM images, micro-Raman spectra, and EDX spectra of the specimens grown for 15 min with different \ce{O2} flows of (a-c) 0.1 sccm, (d-f) 1 sccm, (g-i) 3 sccm, and (j-l) 10 sccm.
+}
+\label{fig:ch4oxy}
+\end{figure}
+
+Micro-Raman scattering was used to probe the phase change during the oxygen regulated growth.
+The Raman spectra of sodium molybdates is featured with multiple strong peaks located between 800 and 1000 \si{cm^{-1}}, which we refer as high-frequency region hereafter.
+\ce{MoO3} phase shows two peaks in this region with the strongest one at about 820 \si{cm^{-1}}; \ce{Na2Mo2O7} phase exhibits four peaks in this region with the strongest one moving to 937 \si{cm^{-1}}, whereas \ce{Na2Mo4O13} phase shows even more peaks in high-frequency region, with a doublet at 962 and 970 \si{cm^{-1}}, respectively.\cite{Schofield2005,Saraiva2011} As predicted by the phase diagram (Fig.~\ref{fig:ch4pd}), Raman spectra identified \ce{Na2Mo2O7} phase in the 0.1 sccm growth (Fig.~\ref{fig:ch4oxy}b), and \ce{Na2Mo4O13} phase on the particles in the rest three growths (Fig.~\ref{fig:ch4oxy}e, h, and k).
+The author would like to point out the existence of \ce{Na2Mo3O10} phase is still open in air, and no Raman fingerprint is ever reported.\cite{Fomichev1992} This observation supports the previous hypothesis about the reaction sequence on NaOH-Si substrate.
+Element analysis performed on the Raman sites also confirm the presence of Na, Mo and O in particles growth, and only Mo and O in the plate growth (Fig.~\ref{fig:ch4oxy}c, f, i, and l).
+It is worth noting that the absence of Na signal in the forked \ce{MoO3} plate indicates the doping level would be lower than the detection limit of 0.01 wt.\% if the Na doping ever occurs.
+
+The morphologies of second series experiment at constant \ce{O2} flow and varied growth time were shown in Fig.~\ref{fig:ch4ev}.
+The 15 min and 30 min growth show that dense arrays of \ce{MoO3} forked nanoplates with a length of hundreds of microns covering the substrate areas at different temperatures.
+With the increase of the growth time, these nanoplates keep growing and become larger, longer, and denser.
+Ultra-long 1D \ce{MoO3} structures start to grow on top of the nanoplate arrays.
+For 60 min growth, ultra-long nanobelts appear on top of the nanoplates.
+For the growth time of 90 min, the nanobelts grow longer, and some grow into microbelts.
+Microtowers start to grow as well.
 
@@
 \centering
-\subfloat[]{\label{fig:moind}\includegraphics[width=0.45\textwidth]{n_MoO3}}\hspace{0.04\textwidth}
-\subfloat[]{\label{fig:mocon}\includegraphics[width=0.45\textwidth]{MoO3_1L}}
-\caption[Refractive indices of \ce{MoO3}]{(a) Refractive indices of \ce{MoO3} Dashed line is n along $a$ axis while solid line is along $c$ axis.
-(b) optical contrast mapping of 1L \ce{MoO3} on \ce{SiO2}-Si.
-The x axis is \ce{SiO2} thickness, y axis is wavelength.It is assumed that the incident light is polarized along c axis of \ce{MoO3}.}
-\label{fig:mofl}
+\includegraphics[width=0.8\textwidth]{mooe_sem_ev}
+\caption[Growth evolution of \ce{MoO3}: second stage]{Growth evolution of the second stage of catalyst-assisted growth of \ce{MoO3} 1D structures: SEM images of the deposition at different growth temperatures with growth time of row 1: 15 min, row 2: 30 min, row 3: 60 min, and row 4: 90 min.
+The estimated temperature for each column from left to right is 525 \si{\degreeCelsius}, 445 \si{\degreeCelsius}, 390 \si{\degreeCelsius} and 340 \si{\degreeCelsius}, respectively.
+}
+\label{fig:ch4ev}
 \end{figure}
 
-Fig.~\ref{fig:mocon} illustrates the optical contrast mapping of 1L \ce{MoO3} on \ce{SiO2}-Si when the incident light is polarized along c axis of \ce{MoO3}.
-One can see that there is a pseudo-periodical trend with either wavelength or \ce{SiO2} thickness fixed.
-The positive extreme occur at around 80nm and 240nm \ce{SiO2} layer, slightly less than the optimum for observing graphene.
-The refractive indices of Si and \ce{SiO2} within visible wavelengths and MATLAB source code for optical contrast calculation is included in Appendix, with which one can readily evaluate the few layers \ce{MoO3} scenarios and the circumstance when incident light is polarized along a axis.
-
-The dimension and phase of exfoliated \ce{MoO3} is examined using TEM.
-Fig.~\ref{fig:motem} shows the size of exfoliated \ce{MoO3} is about 500 nm.
-High-resolution TEM (HRTEM) image was taken to assess the \ce{MoO3} crystallinity.
-The clearly resolved lattices indicate high crystal quality of these exfoliated \ce{MoO3}.
+To reveal the growth mechanisms for the ultra-long 1D structures in the second stage, specimens were carefully examined to locate the catalyst particles.
+Small catalyst particles ranging from several hundred nanometers to several microns were found at different locations of these ultra-long 1D structures.
+As shown in Fig.~\ref{fig:ch4edx1} and Fig.~\ref{fig:ch4edx2}, EDX element analysis confirmed the presence of Na, Mo, and O in these particles, indicating the particles are sodium molybdate catalysts.
 
@@
 \centering
-\includegraphics[width=0.8\textwidth]{exf_moo3.jpg}
-\caption[TEM images of exfoliated \ce{MoO3}]{(a) TEM image and (b) HRTEM image of FL \ce{MoO3} obtained by liquid sonication method.}
-\label{fig:motem}
+\includegraphics[width=0.4\textwidth]{MoO3_SFig_EDX}
+\caption[Growth evolution of \ce{MoO3}: second stage]{SEM images and EDS spectra identifying the location, morphology, and composition of the catalyst particles on the nanobelt structures: (a-b) a catalyst particle (I) in the middle of a nanobelt (II), (c-d) two catalyst particles (I and II) leading the growth of two perpendicular nanobelts, (e-f) a catalyst particle in the middle of a nanobelt, and (g-f) a catalyst particle on the side surface of a nanobelt tip.
+}
+\label{fig:ch4edx1}
 \end{figure}
 
-Nevertheless, identifying these few layer \ce{MoO3} under optical microscope is still difficult due to both the small flake size and low contrast.\footnote{Human eye threshold contrast (contrast sensitivity)$^{-1}$ is about 10\%.} One need to improve the liquid exfoliation process to obtain larger dimension and high yield.
-This is however beyond the scope of current study.
+\begin{figure}[htb]
+\centering
+\includegraphics[width=0.5\textwidth]{MoO3_SFig_EDX_tower}
+\caption[Growth evolution of \ce{MoO3}: second stage]{SEM images and EDS spectra for identifying the location, morphology, and composition of the catalysts on the microtower structures: (a-b) a tiny catalyst particle (I) on top of a small cone shaped microtower (II), and (c-d) a catalyst particle (III) on a large and short microtower (IV).}
+\label{fig:ch4edx2}
+\end{figure}
 
-\subsection{Growth on non-Si substrates}\label{sec:nasi}
+The author would like to stress the difficulty of observing the sodium molybdate particles on as-synthesized belts and tower.
+Two factors are probably responsible for this observation, one is the consumption of catalysts, such as evaporation; the other is the unpredictable location of the catalyst.
+Unlike the conventional VLS growth where the catalysts were predominantly found at the tip of 1D nanostructures, the catalyst in current study were mostly found at the side wall of long nanobelts, and the location could be on the tip, or several microns away from tip.
+As for the microtowers, it is even rare to observe Na element.\footnote{try m-Raman at different depths}
 
-In previous works, \ce{MoO3} deposition on ITO/glass exhibits new morphologies that were not observed on Si substrates, yet the mechanism is not well investigated.\cite{predeep2011} We first repeated the previous growth on ITO/glass, and then found similar deposition phenomena on glass and mica substrates.
-We suspected that the morphology difference on the substrates employed in this study arises from the compositions difference.
-Both mica and glass contains alkaline elements which are absent in Si and \ce{SiO2}/Si substrates.
-We primarily verify this hypothesis by utilizing \ce{NaOH} treated Si substrates and found that the overall morphology almost reproduces that on ITO and mica substrates.
-We then propose a new growth mechanism based on the VLS process to explain the deposition of \ce{MoO3} on alkaline-ions-containing substrates.
+Some observations under similar controlled growth conditions is also listed as following to support the proposed growth model:
 
-ITO versus NaOH images.
+\begin{enumerate}
+\item When no Mo powder is used, NaOH still holds onto substrate with some locations exhibiting etching.
+\item When no Mo powder is used while growth is performed in an old tube or oxygen flow is limited to a extreme small value, circular droplet-like solid were found and Mo, Na and O were detected, suggesting the existence of VLS mechanism.
+Using Mo coated substrate and subsequent NaOH treatment, similar droplets formation was repeated.
+No discernible XRD pattern emerged, illustrating the amorphous nature of liquid catalyst.
+\item 1 min growth shows plates in high temperature end and irregular shapes in low temperature end.
+\item 15 min growth shows \ce{MoO3} plates parallel to substrate, with some belts emerging and growing out of the substrate plane.
+This is presumably due to the growth direction mismatch between different plates.
+Morphology will also depend on local NaOH concentration.
+NaOH trace mark turns into connected plates at the original locations, showing the high concentration mediated the morphology evolution.
+The possible catalyst solid was sitting on the top of plate layer.
+Also some belt-like growth is visible on reaction chamber walls, suggesting the evaporation and transport of \ce{Na_xMoO3} vapor phase;
+\item 30 min growth: belts growth begin (500 microns long, grow rate is estimated to be 0.5 $\mu m/s$), tower structures show up as well, but much less than belt.
+Two kinds of belts found, tapering and non-tapering.
+The former one seems to have droplets mostly associated with sidewalls of the top part.
+\item In reduced time or less oxygen supply growth, Na-containing site was found located onto the sidewall of belts instead of the usual expected tip.
+XRD pattern indicated the existence of \ce{Na_xMoO3} phase.
+And \ce{MoO3} XRD pattern is dominated by (0k0) peaks, indicating a 2D layer-by-layer growth with lateral rate exceeding that of axial direction.
+\item 2 h growth: there are crossed tapering belts at downstream boundary, with more than one droplet located along the interface of two perpendicular belts, EDX confirmed high Na content.
+\item Using NaOH treated hydrophobic substrates, dense tower array growth was found along the edge areas or molten periphery of droplets, where 5 mins growth already show the initial stage of tower with diameter about 1 $\mu m$, which increase to 10 $\mu m$ in prolonged growth.
+\end{enumerate}
+
+A growth model is proposed in hypothesis.
+
+We divide the growth into two stages according to the emerging time of long belts and towers.
+In first stage the growth is dominated by lateral growth, as illustrated in .
+In the second stage, \ce{NaxMoO3} is evaporated and recondensed in the low temperature region, and some droplet will form, and when at proper locations, introduce secondary VLS growth.
+
+In first stage, the Na-Mo-O liquid is formed and have much more higher absorption rate than that of bare substrate.
+The absorbed species will diffuse along the surface and inside the liquid.
+It was difficult to estimate which diffusion path one is faster.
+When the size of liquid is smaller than some critical size, there is no preferred growth direction.
+This changed when the precipitated solid exceeds certain critical dimension, and the morphology evolution is then determined by the relative size of already formed solid and its liquid catalyst.
 
@@
 \centering
-\caption{Na diffusion coefficient ($cm^2/sec$), R is molar gas constant (8.315 \si{\joule\per mol\per K}), and T is temperature in K}\label{tab:mona}
+\caption{Na diffusion coefficient (\si{cm^2\per\second}), R is molar gas constant (8.315 \si{\joule\per mol\per K}), and T is temperature in K}\label{tab:mona}
 \begin{tabular}{lcr}
@@
 \midrule
-Quartz      & $3.8\times10^{-2}exp(\frac{-24500}{RT})$  & \cite{Rybach1967a}  \\
-Sodalite      & $6.6exp(\frac{-42500}{RT})$  & \cite{Sippel1963}  \\
-Obsidian     & $4.4\times10^{-2}exp(\frac{-22900}{RT})$  & \cite{Sippel1963}  \\
+Quartz      & $3.8\times10^{-2}\exp(\frac{-24500}{RT})$  & \cite{Rybach1967a}  \\
+ \addlinespace[0.5em]
+Sodalite      & $6.6\exp(\frac{-42500}{RT})$  & \cite{Sippel1963}  \\
+ \addlinespace[0.5em]
+Obsidian     & $4.4\times10^{-2}\exp(\frac{-22900}{RT})$  & \cite{Sippel1963}  \\
+ \addlinespace[0.5em]
 silicate glass & $3.1\times10^{-8}$ at 420\si{\degreeCelsius} & \cite{Jbara1995} \\
+ \addlinespace[0.5em]
 \ce{SiO2} glass & $1.1\times10^{-7}$ at 670\si{\degreeCelsius} &  \cite{FRISCHAT1968}\\
@@
 
-We also would like to mention the gradient of Gibbs free enthalpy overruled the concentration of a particular species, and higher \ce{OH^-} contents tend to reduce Na diffusivity.\cite{Materials2012}  The substrates used in this work are glass and ITO/glass.
+It is worth mentioning that the gradient of Gibbs free enthalpy overruled the concentration of a particular species, and higher \ce{OH^-} contents tend to reduce Na diffusivity.\cite{Materials2012}  The substrates used in this work are glass and ITO/glass.
 Related parameters is as following:
 \begin{itemize}
-\item dimension: $25mm\times10mm\times1mm$
+\item dimension: $25\times10\times1$ mm
 \item density: 2.567 \si{g\per cm^3}
@@
 \begin{align}
-J = -D \frac{\Delta C}{\Delta x} = 2.0e^{-8} mol/cm^2/sec,
+J = -D \frac{\Delta C}{\Delta x} = 2.0\times 10^{-8} \si{mol\per cm^2\per\second}
 \end{align}
 
-for a typical 2hrs growth, the net amount of Na diffusing out of substrate is then 144$\mu mol$, about 10\% of total Na ions.
+for a typical 2 h growth, the net amount of Na diffusing out of substrate is then 144$\mu mol$, about 10\% of total Na ions.
 The diffusion length $\sqrt{Dt}$ is 190 $\mu m$.
-We noticed this result overestimate since the flux will reduce gradually.
-Meanwhile the molar amount of \ce{NaOH} applied on Si substrate is about 1$\mu mol$.
+Notice this result overestimate since the flux will reduce gradually.
+Meanwhile the molar amount of \ce{NaOH} applied on Si substrate is about 0.5 $\mu mol$.
 Considering the adjusted ratio, Na contents should be much more when using glass substrate than when using NaOH-Si substrate.
@@
 However, few report could be found in literature.
-We only find one by \citeauthor{Kazenas2010}.\cite{Kazenas2010} The partial pressure\footnote{$logP(atm)= -13794/T + 6.19$} of \ce{Na2MoO4} is calculated to be 0.2 mTorr at 800 \si{\degreeCelsius} and $3.5\times 10^{-3}$ mTorr at 670 \si{\degreeCelsius}.
+Only one was reported by \citeauthor{Kazenas2010}.\cite{Kazenas2010} The partial pressure of \ce{Na2MoO4} is calculated to be 0.2 mTorr at 800 \si{\degreeCelsius} and $3.5\times 10^{-3}$ mTorr at 670 \si{\degreeCelsius}.\footnote{$logP(atm)= -13794/T + 6.19$}
 
@@
 \subsubsection{time stepwise growth}
-
-With time stepwise growth, the following results were obtained:
-
-\begin{enumerate}
-\item When no Mo powder is used, NaOH still hold onto substrate with some locations exhibiting etching.
-\item When no Mo powder is used while growth is performed in an old tube or oxygen flow is limited to a extreme small value, circular droplet-like solid were found and Mo, Na and O were detected, suggesting the existence of VLS mechanism.
-Using Moly coated substrate and subsequent NaOH treatment, similar droplets formation was repeated.
-No discernible XRD pattern emerged, illustrating the amorphous nature of liquid catalyst.
-\item 1mins growth shows plates in high temp end and irregular shapes in low temp end.
-\item 15mins growth shows \ce{MoO3} plates parallel to substrate, with some belts emerging and growing out of the substrate plane.
-This is presumably due to the growth direction mismatch between different plates.
-Morphology will also depend on local NaOH concentration.
-NaOH trace mark turns into connected plates at the original locations, showing the high concentration mediated the morphology evolution.
-The possible catalyst solid was sitting on the top of plate layer.
-Also some belt-like growth is visible on reaction chamber walls, suggesting the evaporation and transport of \ce{NaxMoO3} vapor phase;
-\item 30mins growth:  belts growth begin (500 microns long, grow rate is estimated to be 0.5 $\mu m/s$), tower structures show up as well, but much less than belt.
-Two kinds of belts found, tapering and non-tapering.
-The former one seems to have droplets mostly associated with sidewalls of the top part.
-\item In reduced time or less oxygen supply growth, Na-containing site was found located onto the sidewall of belts instead of the usual expected tip.
-XRD pattern indicated the existence of \ce{NaxMoO3} phase.
-And MoO3 XRD pattern is dominated by (0k0) peaks, indicating a 2D layer-by-layer growth with lateral rate exceeding that of axial direction.
-\item 2hr growth: there are crossed tapering belts at downstream boundary, with more than one droplet located along the interface of two perpendicular belts, EDX confirmed high Na content.
-\item The tower is paled along $\langle010\rangle$ direction, and the belt growth direction is $\langle001\rangle$.
-\item Using NaOH treated hydrophobic substrates, dense tower array growth was found along the edge areas or molten periphery of droplets, where 5 mins growth already show the initial stage of tower with diameter about 1 $\mu m$, which increase to 10 $\mu m$ in prolonged growth.
-\end{enumerate}
-
-We divide the growth into two stages according to the emerging time of long belts and towers.
-In first stage the growth is dominated by lateral growth, as illustrated in .
-In the second stage, \ce{NaxMoO3} is evaporated and recondensed in the low temperature region, and some droplet will form, and when at proper locations, introduce secondary VLS growth.
-
-In first stage, the Na-Mo-O liquid is formed and have much more higher absorption rate than that of bare substrate.
-The absorbed species will diffuse along the surface and inside the liquid.
-It was difficult to estimate which diffusion path one is faster.
-When the size of liquid is smaller than some critical size, there is no preferred growth direction.
-This changed when the precipitated solid exceeds certain critical dimension, and the morphology evolution is then determined by the relative size of already formed solid and its liquid catalyst.
-
-The overall reactions probably occur in the following sequences.
-First, Mo powder is oxidized and \ce{MoO3} vapor is produced and transported to downstream by Ar carrier gas. Then,
-\begin{align}
-\cee{NaOH(l) + MoO3(g) -> Na2MoO4(l) + H2O(g)}
-\end{align}
-
-The melting point of \ce{Na2MoO4} is 687 \si{\degreeCelsius}.
-Based on the open air temperature profile (Fig.~\ref{fig:mooxgrowth}), the substrate is locate in temperature zone between 650 and 400 \si{\degreeCelsius}.
-The temperature distribution is different due to both the sealed condition and thermal conduction along the Si substrate.
-It will be difficult to acquire the accurate values along the substrate.
-However by considering the flow rate, the actual temperature will be higher than predicted by open air measurement.\cite{Subannajui2010} The melting of \ce{Na2MoO4} is highly possible when taking into account of its size as well.
-\cite{Bruggemann1997}
-
-\begin{figure}[htb]
-\centering
-\includegraphics[width=0.6\textwidth]{Na2MoO4_Phase}
-\caption[Phase diagram of Na-Mo-O system]{Phase diagram of \ce{Na2MoO4} and \ce{MoO3} reproduced from ref.~\cite{Hoermann1929}}
-\label{fig:pd}
-\end{figure}
-
-According to the phase diagram shown in Fig.~\ref{fig:pd}, \ce{Na2MoO4} - \ce{MoO3} phase above 800 \si{\degreeCelsius} are \ce{Na2MoO4}(l) + \ce{MoO3}(l), More discussion should follow $\ldots$.
-
-Each site of \ce{Na2MoO4} will continue absorb incoming \ce{MoO3}, forming a swelling droplet.
-\ce{MoO3} will precipitate from these seeds when a critical supersaturation concentration is reached, which is about 75\% according to Fig.~\ref{fig:pd}.\footnote{This ratio considerably exceeds that of the usual metal catalyst scenario.
-This high solubility accounts for several observations in our experiments: the dimensions of individual deposit is much larger than that of initial droplet, the concentration of sodium in final products is extremely low.}
 
@@
 \end{itemize}
-
-\subsubsection{Phase evolution probing by Raman}
-
-\citeauthor{Hardcastle1990} summarized an empirical formula to relate the Raman peaks and \ce{Mo-O} bonding lengths.\cite{Hardcastle1990} This correlation assumes general form as
-\begin{equation}\label{eq:mobond}
-\nu = A \exp{B\cdot R},
-\end{equation}
-where $A=32895$ and $B=-2.073$ are fitting parameters, R is bond distance in unit of \AA.
-Given a stretching frequency, the resolution for calculated bond distance is $\pm0.016$\AA.
-Another empirical expression connect the bond valence $s$ and bond distance R: $s(M-O) \approx (R/X)^{-6} $, where X=1.882 when M is Mo, and 1.904 when M is W.
-The valence sum rule could be then used to check the state of Mo cation.
-It should be noticed that not all observed Raman lines could be correlated to a \ce{Mo-O} bond distance by extrapolation of Eq.~\ref{eq:mobond}.
-It is then regarded as a symmetry related vibrational mode, i.e.
-$820 cm^{-1}$ in \ce{MoO3}.
-From the correlation of various Mo compounds, a general conclusion is the lower the stretching frequency for the shortest metal-oxygen bond, the more regular is the structure.
-
-\textbf{Fundamental of VLS}
-
-Vapor-Liquid-Solid (VLS) process is first proposed by Wagner,\cite{Wagner1964} and further developed by \citeauthor{Givargizov1975}.\cite{Givargizov1975} This method has become an important strategy for synthesizing one-dimensional nanostructures.\cite{Lieber1998} Conventionally, a liquid eutectic droplet is formed by catalyst itself or by alloying with the growth material, acting as a trap of growth species.
-The growth is initialized by supersaturation of the liquid alloy and subsequent precipitation at the solid-liquid interface.
-The choice of catalyst usually is among the several noble metals since they are physically active but chemically stable or inert in most growth scenarios.
-The growth materials span a wide range including group IV,\cite{Hochbaum2005} group III-V,\citep{Dalacu2013, Xiao2012, Dubrovskii2011} group II-VI,\cite{Hao2006} and some metal oxides, such as \ce{ZnO},\citep{Huang2001a,Ramgir2010} \ce{MgO},\citep{HEUER1967, Nagashima2007} \ce{SiO2},\cite{Pan2002} and \ce{TiO2},\cite{Zhuge2012} to name a few.
-The catalysts can be Au, Pd, Pt, Ni,\cite{Xiao2012} Ti, Ga,\cite{Pan2002} and even KI.
-
-Understanding the interaction between liquid droplet and the solid interface allows for a rich engineering space to fine tune the geometry and structures of as-grown nanostructures.
-For instances, the diameter of Si nanowires (NWs) can be controlled by laser ablated catalyst\cite{Morales1998} or well-defined Au nanoparticles.\cite{Cui2001b} Under proper conditions,  axial modulation can produce nanowire superlattices from group IV and III-V materials.\citep{Gudiksen2002,Bjork2002}  Radial composition modulation have also been demonstrated by selectively suppressing VLS process, providing a robust routine for homogeneous or heterogeneous core-shell structures.\cite{Lauhon2002a}  \citeauthor{Wang2013c} changed the NW growth direction by changing the shape of droplets; \citeauthor{Biswas2013} reported enhanced aspect ratio of Ge NWs from bimetallic alloy.
 
@@
 
-% droplet position statistics
+\subsection{Liquid exfoliation on as-grown molybdenum oxides}
+
+Few layer (FL) materials attracts intensive research efforts recently.
+The author also made some efforts using liquid exfoliation method to prepare FL \ce{MoO3}.
+The exfoliated \ce{MoO3} was characterized using UV-Vis and TEM.
+The optical contrast of FL \ce{MoO3} on \ce{SiO2}-Si is also calculated, which could serve as a guideline to identify FL \ce{MoO3} using optical microscope.
+
+The exfoliation solution is 30\% isopropanol (IPA) in DI water, which has been proved to work well on other layered compounds.\cite{Halim2013} After 20 minutes sonication, the dispersion is milky.
+The transmission spectra of this dispersion immediately upon sonication and after 40 h for gravity sedimentation was measured, as illustrated in Fig.~\ref{fig:moabs}.
+The t0 line mainly arises from the scattering of flakes in the dispersion.
+There are two scattering mechanisms: Rayleigh scattering and Tyndall scattering.
+Rayleigh scattering, which occurs when particles are comparable to wavelength, is inversely proportional to the fourth power of wavelength; While Tyndall scattering, which occurs when the particles are larger, is inversely proportional to the square of the wavelength.
+To fully evaluate the true absorbance of the sample itself, one needs to decouple the scattering part from apparent absorbance.
+Generally  one part of spectrum is selected and assumed it is only caused by scattering.
+Then a empirical dependence shown in Eq.~\ref{eq:sca2} is used as polynomial fitting model.
+
+\begin{align}
+Abs_{sca}  & = a\times \lambda^{n}  \label{eq:sca1}\\
+\log{Abs_{sca}} & = \log{a} + n*\log{\lambda} \label{eq:sca2}
+\end{align}
+
+After least-squares fitting, the coefficients $a$ and $n$ can be used to estimated the scattering in other wavelengths.
+The fitting of $n$ usually falls between -2 and -4.
+The author examined the t40h line in Fig.~\ref{fig:moabs} and found the scattering part is almost zero.
+Therefore no scattering fitting was performed.
+
 \begin{figure}[htb]
 \centering
-\includegraphics[width=0.6\textwidth]{droplets_sta}
-\caption[Droplet position statistics]{Droplet position statistics. On-tip and not-on-tip counts variation with respect to growth time. }
-\label{fig:mo3dropsta}
+\subfloat[]{\label{fig:moabs}\includegraphics[width=0.45\textwidth]{MoO3-abs}}\hspace{0.04\textwidth}
+\subfloat[]{\label{fig:mobg}\includegraphics[width=0.45\textwidth]{MoO3-bg}}
+\caption[UV-Vis spectra of exfoliated \ce{MoO3}]{(a) UV-Vis absorbance spectra of exfoliated \ce{MoO3}.
+Dashed line (t0) represents measurement immediately after sonication, and solid line (t40h) is obtained after sitting for 40 h.
+The dot dashed line is reference spectrum of the 30\% IPA.
+(b) Band gap estimation}
+\label{fig:mouv}
 \end{figure}
+
+According to the corrected absorbance spectrum, optical band gap can be deduced, which is known as Tauc Plot.\cite{Tauc1972} The procedure is recapitulated here briefly.
+Eq.~\ref{eq:tauc} is given to empirically relate optical band gap to absorption.
+
+\begin{equation}\label{eq:tauc}
+ (h\nu \alpha)^{\frac{1}{n}} = B(h\nu - E_g^{opt}),
+\end{equation}
+where B is a proportional coefficient, $\alpha$ is absorption\footnote{The absorbance $A = 0.4343\alpha*l$, where l is the optical path} and $E_g^{opt}$ is defined as optical band gap.
+The value n is correlated to the nature of optical transition.
+\begin{itemize}
+\item For direct allowed transition, n = 1/2;
+\item For direct forbidden transition, n = 3/2;
+\item For indirect allowed transition, n = 2;
+\item And for indirect forbidden transition, n = 3.
+\end{itemize}
+
+When the transition nature of sample is not well known, one should apply each to check which one provide the best fit.
+Depending on the synthesis methods and \ce{MoO3} morphologies, the transition phenomena might vary.
+On the \ce{MoO3} films, \citeauthor{Bouzidi2003} assumed a direct gap (n = 1/2)\cite{Bouzidi2003} while \citeauthor{Szekeres2002} not.\cite{Szekeres2002} The author use n = 2 in this work, plot $\sqrt{(h\nu \alpha)}$ versus photon energy, and extrapolate the linear part onto $h\nu$ axis.
+The intercept is used as $E_g^{opt}$ then.
+The estimated energy gap and some results from previous studies is summarized in Table.~\ref{tab:mobg}.
+
+\begin{table}[htb]
+\centering
+\caption{Optical band gaps of \ce{MoO3}}\label{tab:mobg}
+\begin{tabular}{lccr}
+\toprule
+&\multicolumn{2}{c}{Band gap} \\
+\cmidrule(l){2-3}
+Reference & value(eV) & orientation & material states\\
+\midrule
+\cite{Deb1968}   & 2.96  & $E\parallel c_0$ & single crystal\\
+\cite{Deb1968}   & 2.80  & $E\perp c_0$ & single crystal \\
+\cite{Julien1995} & 2.8$\sim$ 3.2 & NA & films\\
+ this work  & 3.1  & NA & nanoflakes\\
+\bottomrule
+\end{tabular}
+\end{table}
+
+An alternative apporach is a) define $Y = \alpha E=\alpha h\nu$, and obtain $Y' = \frac{\partial Y}{\partial E}$, then b) plot $Y'/Y$ versus $h\nu$.
+The band gap value can be obtained from the intercept of extrapolated line on photo energy axis.\cite{Choopun} This approach is not difficult to comprehend as long as we notice from Eq.~\ref{eq:tauc}, $Y = B (h\nu - E_g^{opt})^n$ and $Y' = B n(h\nu - E_g^{opt})^{n-1}$.
+The advantage is one can also estimate n without using assumption.
+
+The dielectric constants\footnote{Not a constant at all, instead, it has complicated dependence on photon energy} ($\epsilon = \epsilon_1 + i*\epsilon_2$) of \ce{MoO3} have been studied in several reports.\cite{Deb1968,Sabhapathi1995,Miyata1996,Abdellaoui1997,Mondragon1999} The author extracted $\epsilon_1$ from Ref\cite{Itoh2001a} due to the wide photon energy range utilized there.
+Notice that $\epsilon_2$ is approximately zero when $h\nu$ is less than 4 eV.
+Since this study is primarily concerned with the optical contrast of FL \ce{MoO3} in visible wavelength region($h\nu < 3$ eV), the refractive indices $n$ is calculated from $n = \sqrt{\epsilon_1}$.
+Due to the orthorhombic phase, \ce{MoO3} exhibit birefringence, that is there are two refractive indices, $n_c$ and $n_a$, as shown in Fig.~\ref{fig:moind}.
+The refractive index is between $ 2.2\sim 2.4$ along $a$ axis, and $ 2.5\sim 2.8$ along $c$ axis.
+Comparison to the low frequency dielectric constant ($18.0\pm1$) implies a primarily ionic bonding in \ce{MoO3}.\cite{He2003}
+
+\begin{figure}[htb]
+\centering
+\subfloat[]{\label{fig:moind}\includegraphics[width=0.45\textwidth]{n_MoO3}}\hspace{0.04\textwidth}
+\subfloat[]{\label{fig:mocon}\includegraphics[width=0.45\textwidth]{MoO3_1L}}
+\caption[Refractive indices of \ce{MoO3}]{(a) Refractive indices of \ce{MoO3} Dashed line is n along $a$ axis while solid line is along $c$ axis.
+(b) optical contrast mapping of 1L \ce{MoO3} on \ce{SiO2}-Si.
+The x axis is \ce{SiO2} thickness, y axis is wavelength.It is assumed that the incident light is polarized along c axis of \ce{MoO3}.}
+\label{fig:mofl}
+\end{figure}
+
+Fig.~\ref{fig:mocon} illustrates the optical contrast mapping of 1L \ce{MoO3} on \ce{SiO2}-Si when the incident light is polarized along $c$ axis of \ce{MoO3}.
+One can see that there is a pseudo-periodical trend with either wavelength or \ce{SiO2} thickness fixed.
+The positive extreme occur at around 80 nm and 240 nm \ce{SiO2} layer, slightly less than the optimum for observing graphene.
+The refractive indices of Si and \ce{SiO2} within visible wavelengths and MATLAB source code for optical contrast calculation is included in Appendix, with which one can readily evaluate the few layers \ce{MoO3} scenarios and the circumstance when incident light is polarized along $a$ axis.
+
+The dimension and phase of exfoliated \ce{MoO3} is examined using TEM.
+Fig.~\ref{fig:motem} shows the size of exfoliated \ce{MoO3} is about 500 nm.
+High-resolution TEM (HRTEM) image was taken to assess the \ce{MoO3} crystallinity.
+The clearly resolved lattices indicate high crystal quality of these exfoliated \ce{MoO3}.
+
+\begin{figure}[htb]
+\centering
+\includegraphics[width=0.8\textwidth]{exf_moo3.jpg}
+\caption[TEM images of exfoliated \ce{MoO3}]{(a) TEM image and (b) HRTEM image of FL \ce{MoO3} obtained by liquid sonication method.}
+\label{fig:motem}
+\end{figure}
+
+Nevertheless, identifying these few layer \ce{MoO3} under optical microscope is still difficult due to both the small flake size and low contrast.\footnote{Human eye threshold contrast (contrast sensitivity)$^{-1}$ is about 10\%.} One need to improve the liquid exfoliation process to obtain larger dimension and high yield.
+This is however beyond the scope of current study.
+
+\section{summary}

### 2014-08-01 main.tex
wox 012814
synchronize 013014
TMDC initial
paper reading
lortenzian fitting on naxwo3 added
core-shell paper
paper.tex u8 issue
moo3 and coreshell works
a low productivity week
change to lualatex engine
lualatex packages as alternative in mwe
package adjusted
after a long pause
before final branch
ch2 draft initial
moo3 draft 50%

@@
 
-   \input{package.tex} % additonal packages and tweaking
+   \input{package_iff.tex} % additonal packages and tweaking
    \input{./FrontMatter/abbre}
@@
 % \include{./ch-intro/ch-intro}
+ \include{./ch-intro/ch-instr}
 %   \include{./ch-wox/ch-wox}
-   \include{./ch-moox/moox}
-
+  \include{./ch-moox/moox} % no tex needed, otherwise there is error
+%    \include{./ch-tms/tms}
 \appendix
@@
 %    \include{./BackMatter/app1}
+%     \include{./BackMatter/app2}
+%   \include{./BackMatter/paper}
 
@@
 \end{document}
+
+Both tungsten (W) and molybdenum (Mo) belong to Group VIB transition metal, with outer shell electrons configuration as $4d^55s^1$ and $5d^46s^2$, respectively.
+Therefore we refer their oxides and chalcogenides as \gls{tmo} and \gls{tmdc}.\footnote{Obviously transition metals include many other elements, all of which have partially filled $d$-electron shell.
+But here we use TM to denote W and Mo exclusively.}
+
+Nucleation is a process of generating a new phase from a metastable old phase, where the Gibbs energy per molecule of the bulk of the emerging new phase is less than that of the old phase.
+
+General CVD knowledge, substrate preparation, and\cite{MichealK.Zuraw2003}
+
+\section{Crystal Structures and Electronic Properties}
+
+Solid and orderliness.
+
+Two theories arise to describe the outer shell electrons and to correlate the structure and physical properties: \gls{cft} and band theory.\cite{Goodenough1971} \gls{cft} assumes weak interaction between neighboring atoms and localization of electron towards parent atom, whereas band theory assumes that electron is shared equally by all nuclei and therefore a many-electron problems follows.
+Description of a single electron in periodic potential fail to treat the electron correlations adequately, as the interaction between atoms becomes weaker.For transition metals, $s$ and $p$ electrons are well described by a collective-electron model, while the 4f or 5f electrons are tightly bound to nuclei and screened from the neighboring atoms by 5s, 5p or 6s, 6p core electrons, hence it matches well with a localized-electron model.
+d electrons show intermediate character.
+
+In vapor synthesis process, two growth mechanism exists: VS and VLS.
+VS process is widely accepted for the growth of \ce{MoO3}.
+Yet we caution that synthesis conditions should be scrutinized to determine the exact mechanism.
+\citeauthor{Li2002c} suggested a VS mechanism at 700 \si{\degreeCelsius} and VLS at 750 \si{\degreeCelsius} and higher.\cite{Li2002c} \citeauthor{Fibers2007} proposed a modified VS mechanism probably because the deposition occurs on \ce{Al2SiO5} with possible \ce{Al_{0.95}SiNa_{0.06}O_x} involved.
+Therefore temperature and possible impurity could potentially alter the growth mechanism.
+We divide the growth results into two categories: on Si substrate and on non-Si substrate, and describe them respectively.
+We also briefly mention using liquid exfoliation to prepare few layer \ce{MoO3}.
+
+This rectangular shape implies the boundary plane along growth direction (long axis) is (001), in consistency with previous experimental reports\cite{Zeng1998,Li2002b} and theoretical studies.\cite{Firment1983,Cora1997} We also observed different shapes, i.e., elongated hexagonal using similar growth conditions.
+This is not an indication of different growth mode.
+It is a normal thermodynamic fluctuation.
+The growth rates along different crystalline direction of \ce{MoO3} are determined by the free surface energy.
+In fact, (201), (101) and (102) planes have all been observed as terminating planes.\cite{Zeng1998} The stacking rate of \ce{MoO6} octahedra along $a$ and $c$ axis could develop some other ratio.
+And the coexistence of different planes in one growth suggests the similarity of free surface energies between these surfaces.
+In other words, the migration barrier of adatoms on (010) plane is presumably much lower than that on other low index planes due to the Van der Waals interaction nature along [010] direction.
+
+\citeauthor{Wang2013c} changed the NW growth direction by changing the shape of droplets; \citeauthor{Biswas2013} reported enhanced aspect ratio of Ge NWs from bimetallic alloy.
+
+We first repeated the previous growth on ITO/glass, and then found similar deposition phenomena on glass and mica substrates.
+We suspected that the morphology difference on the substrates employed in this study arises from the compositions difference.
+Both mica and glass contains alkaline elements which are absent in Si and \ce{SiO2}/Si substrates.
+We primarily verify this hypothesis by utilizing \ce{NaOH} treated Si substrates and found that the overall morphology almost reproduces that on ITO and mica substrates.
+We then propose a new growth mechanism based on the VLS process to explain the deposition of \ce{MoO3} on alkaline-ions-containing substrates.
+
+ITO versus NaOH images.
+
+According to the phase diagram shown in Fig.~\ref{fig:pd}, \ce{Na2MoO4} - \ce{MoO3} phase above 800 \si{\degreeCelsius} are \ce{Na2MoO4}(l) + \ce{MoO3}(l), More discussion should follow $\ldots$.
+
+\subsubsection{Phase evolution probing by Raman}
+
+\citeauthor{Hardcastle1990} summarized an empirical formula to relate the Raman peaks and \ce{Mo-O} bonding lengths.\cite{Hardcastle1990} This correlation assumes general form as
+\begin{equation}\label{eq:mobond}
+\nu = A \exp{B\cdot R},
+\end{equation}
+where $A=32895$ and $B=-2.073$ are fitting parameters, R is bond distance in unit of \AA.
+Given a stretching frequency, the resolution for calculated bond distance is $\pm0.016$ \AA.
+Another empirical expression connect the bond valence $s$ and bond distance R: $s(M-O) \approx (R/X)^{-6} $, where X=1.882 when M is Mo, and 1.904 when M is W.
+The valence sum rule could be then used to check the state of Mo cation.
+It should be noticed that not all observed Raman lines could be correlated to a \ce{Mo-O} bond distance by extrapolation of Eq.~\ref{eq:mobond}.
+It is then regarded as a symmetry related vibrational mode, i.e.
+820 \si{cm^{-1} in \ce{MoO3}.
+From the correlation of various Mo compounds, a general conclusion is the lower the stretching frequency for the shortest metal-oxygen bond, the more regular is the structure.
+
+% droplet position statistics
+\begin{figure}[htb]
+\centering
+\includegraphics[width=0.6\textwidth]{droplets_sta}
+\caption[Droplet position statistics]{Droplet position statistics. On-tip and not-on-tip counts variation with respect to growth time. }
+\label{fig:mo3dropsta}
+\end{figure}

### 2014-08-04 ch-moox/moox.tex
moo3 chapter 70 percent

@@
 
-\textbf{Substrate treatment.} Silicon substrates was first cleaned according to the procedure in Sec.~\ref{ch2sub} on page~\pageref{ch2sub}.
+Silicon substrates was first cleaned according to the procedure in Sec.~\ref{ch2sub} on page~\pageref{ch2sub}.
 To apply the catalysts, 54 $\mu$L 10 mM \ce{NaOH} (or \ce{KI}, \ce{Na2CO3}) was drop-cast and then naturally left dry in a convection hood.
@@
 
-\textbf{Synthesis.} In a typical synthesis (Fig.~\ref{fig:mooxgrowth}), molybdenum powders were loaded into the uniform heating zone and the sealed chamber was first pumped down to 10 mTorr.
+In a typical synthesis (Fig.~\ref{fig:mooxgrowth}), molybdenum powders were loaded into the uniform heating zone and the sealed chamber was first pumped down to 10 mTorr.
 Then oxygen flow varying between 0.1 sccm to 10 sccm (standard cubic centimeter per minute) was admitted from upstream inlet.
@@
 
-Previous study in our group has found that \ce{MoO3} deposition on ITO/glass exhibits new morphologies that are not observed on Si substrates, yet the mechanism is not well investigated.\cite{predeep2011} Based on the VLS process, it is known that a eutectic state is the key to promote preferred growth direction.
+Previous study in our group has found that \ce{MoO3} deposition on ITO glass exhibits new morphologies that are not observed on Si substrates, yet the mechanism is not well investigated.\cite{predeep2011} Based on the VLS process, it is known that a eutectic state is the key to promote preferred growth direction.
 A list of composition difference between glass and Si substrate shows the extra elements of Na, K, Ca, etc.
@@
 \cee{NaOH(l) + MoO3(g) -> Na2MoO4(l) + H2O(g)}\\
-\cee{Na2MoO4 + nMoO3   -> Na2O.(n+1)MoO3}
+\cee{Na2MoO4 + nMoO3   -> Na2O.(n + 1)MoO3}
 \end{align}
@@
 Based on the open air temperature profile (Fig.~\ref{fig:mooxgrowth}), the substrate is locate in temperature zone between 650 and 350 \si{\degreeCelsius}.
-The temperature distribution is different due to both the sealed condition and thermal conduction along the Si substrate.
+The temperature distribution is different from ambient measurement due to the pressure change and thermal conduction along the Si substrate.
 It is difficult to acquire the accurate values along the substrate.
@@
 
-Based on this aforementioned analysis, the author propose a hypothesis as summarized in Assumption~\ref{hypo1}.
+Based on this aforementioned analysis, the author propose a hypothesis:
 %theorem environment
@@
 \ce{MoO3} phase shows two peaks in this region with the strongest one at about 820 \si{cm^{-1}}; \ce{Na2Mo2O7} phase exhibits four peaks in this region with the strongest one moving to 937 \si{cm^{-1}}, whereas \ce{Na2Mo4O13} phase shows even more peaks in high-frequency region, with a doublet at 962 and 970 \si{cm^{-1}}, respectively.\cite{Schofield2005,Saraiva2011} As predicted by the phase diagram (Fig.~\ref{fig:ch4pd}), Raman spectra identified \ce{Na2Mo2O7} phase in the 0.1 sccm growth (Fig.~\ref{fig:ch4oxy}b), and \ce{Na2Mo4O13} phase on the particles in the rest three growths (Fig.~\ref{fig:ch4oxy}e, h, and k).
-The author would like to point out the existence of \ce{Na2Mo3O10} phase is still open in air, and no Raman fingerprint is ever reported.\cite{Fomichev1992} This observation supports the previous hypothesis about the reaction sequence on NaOH-Si substrate.
+This observation supports the previous hypothesis about the reaction sequence on NaOH-Si substrate.
 Element analysis performed on the Raman sites also confirm the presence of Na, Mo and O in particles growth, and only Mo and O in the plate growth (Fig.~\ref{fig:ch4oxy}c, f, i, and l).
 It is worth noting that the absence of Na signal in the forked \ce{MoO3} plate indicates the doping level would be lower than the detection limit of 0.01 wt.\% if the Na doping ever occurs.
+It should be pointed out the existence of \ce{Na2Mo3O10} phase is in doubt so far, and no Raman fingerprint is reported.\cite{Fomichev1992}
 
@@
 \centering
-\includegraphics[width=0.4\textwidth]{MoO3_SFig_EDX}
-\caption[Growth evolution of \ce{MoO3}: second stage]{SEM images and EDS spectra identifying the location, morphology, and composition of the catalyst particles on the nanobelt structures: (a-b) a catalyst particle (I) in the middle of a nanobelt (II), (c-d) two catalyst particles (I and II) leading the growth of two perpendicular nanobelts, (e-f) a catalyst particle in the middle of a nanobelt, and (g-f) a catalyst particle on the side surface of a nanobelt tip.
+\includegraphics[width=0.5\textwidth]{MoO3_SFig_EDX}
+\caption[Growth evolution of \ce{MoO3}: second stage]{SEM images and EDS spectra identifying the location, morphology, and composition of the catalyst particles on the nanobelt structures: (a-b) a catalyst particle (I) in the middle of a nanobelt (II), (c-d) two catalyst particles (I and II) leading the growth of two perpendicular nanobelts.
 }
@@
 
-The author would like to stress the difficulty of observing the sodium molybdate particles on as-synthesized belts and tower.
-Two factors are probably responsible for this observation, one is the consumption of catalysts, such as evaporation; the other is the unpredictable location of the catalyst.
+It could be of difficulty to observe the sodium molybdate particles on the as-synthesized belts and towers due to the following two factors, one is the consumption of catalysts, such as evaporation; the other is the unpredictable location of the catalyst.
 Unlike the conventional VLS growth where the catalysts were predominantly found at the tip of 1D nanostructures, the catalyst in current study were mostly found at the side wall of long nanobelts, and the location could be on the tip, or several microns away from tip.
@@
 
-A growth model is proposed in hypothesis.
+The growth of \ce{MoO3} on NaOH-Si can be divided into two stages delimited by the emerging of long nanobelts and microtowers.
+A growth model is proposed to account for the observed morphologies of \ce{MoO3} long nanobelt and tower-like structures.
+\begin{hypothesis}\label{hypo2}
+A transverse growth mode exists with growth direction perpendicular to the catalyst-deposition interface, promoting \ce{MoO3} nanoplate and nanobelt growth.
+A axial growth mode akin to conventional VLS process exists, and is responsible for \ce{MoO3} tower-like growth.
+\end{hypothesis}
 
-We divide the growth into two stages according to the emerging time of long belts and towers.
-In first stage the growth is dominated by lateral growth, as illustrated in .
-In the second stage, \ce{NaxMoO3} is evaporated and recondensed in the low temperature region, and some droplet will form, and when at proper locations, introduce secondary VLS growth.
+The first stage is dominated by transverse growth.
+The atomic steps in proposed growth model are depicted in the upper panel of Fig.~\ref{fig:ch4vls}.
+It has been verified that \ce{Na2Mo4O13} forms during the early stage of growth, and can act as catalysts.
+Although the exact phase (liquid or solid) of \ce{Na2Mo4O13} is not known yet in current study, it can be deduced that the \ce{Na2Mo4O13} exists as an active site for the adsorption of incoming \ce{MoO3} growth species.
+When the catalyst is smaller than some critical size, there is no preferred growth direction.
+This changed when the precipitated solid exceeds certain critical dimension, and the morphology evolution is then determined by the relative size of already formed solid and the associated catalyst.
+Several pathways could occur after the accommodation of \ce{MoO3} vapor and supersaturation.
+\ce{MoO3} could precipitate at catalyst-deposition interface, or propagate along catalyst-environment boundary and spread on the already formed \ce{MoO3} surface.
+Meanwhile, the VS process is not suppressed and \ce{MoO3} adatoms could directly condense on \ce{MoO3} surface.
 
-In first stage, the Na-Mo-O liquid is formed and have much more higher absorption rate than that of bare substrate.
-The absorbed species will diffuse along the surface and inside the liquid.
-It was difficult to estimate which diffusion path one is faster.
-When the size of liquid is smaller than some critical size, there is no preferred growth direction.
-This changed when the precipitated solid exceeds certain critical dimension, and the morphology evolution is then determined by the relative size of already formed solid and its liquid catalyst.
+\begin{figure}[htb]
+\centering
+\includegraphics[width=0.6\textwidth]{vls_mode2}
+\caption[Growth model of \ce{MoO3}]{Schematic drawing on the growth steps of the proposed growth model in hypothesis~\ref{hypo2}.}
+\label{fig:ch4vls}
+\end{figure}
 
-\subsubsection{Na transport}
-We estimated the mass transport of sodium ions in silica glass. The driving force could be external field or concentration gradient. And the dynamics is governed by diffusion equation
+Some unique features of \ce{MoO3} must be taken into consideration to properly evaluate the dominate pathway(s).
+It has been reported that \ce{MoO3} can spontaneously spread over the surface of supports (\emph{e.g.}, \ce{Al2O3}, \ce{SiO2}, and Au) to form a monolayer or submonolayer at a temperature (257 \si{\degreeCelsius}) well below the melting point.\cite{Leyrer1990} This strong spreading behavior can be explained by the solid-solid wetting process, in which the driving force is the decrease in total surface free energy.\cite{Leyrer1988} Although the detailed transport mechanisms of the spreading are still in debate, it is suggested that the high mobility of the Mo oxide species on substrates and \ce{MoO3} islands can promote the spreading and the ambient gases could further enhance the spreading.\cite{Gunther2000, Song2003} Based on above analysis and the final morphology of \ce{MoO3}, the dominance of accommodation and spreading pathway in higher temperature part of the growth sample is most possible in this study.
+Hereby the transverse growth mode is attributed to the strong spreading capability of \ce{MoO3}.
+The final morphology of observed nanoplate and nanobelt is a combined result of VS and VLS growth.
+
+On the other hand, the tower-like structures in the second stage follow the axial growth mode in conventional VLS process.
+The molybdates can be evaporated from the higher temperature end and re-condense onto the lower temperature region.
+As illustrated in the lower panel of Fig.~\ref{fig:ch4vls}, this could initiate either belt growth or tower growth depending on the locations.
+The microtowers in this study primarily grow at the low temperature end of the substrate, where the spreading capability of the Mo oxide species is possibly limited.
+Thus the transverse growth pathway is probably suppressed and axial growth becomes dominant.
+
+\subsection{Verification of Growth Model}
+
+The transport of molybdates in proposed growth model is verified by a side-by-side experiment, as schematically depicted in Fig.~\ref{fig:ch4sbs}a.
+Two substrates, one with NaOH catalyst and one bare substrate, were loaded side-by-side at the same location for the growth.
+To avoid any possible catalyst transports through surface diffusion, the two substrates were separated with several millimeters gap in between.
+
+\begin{figure}[htb]
+\centering
+\includegraphics[width=0.8\textwidth]{MoO3_SFig_sidebyside}
+\caption[side by side growth of \ce{MoO3}]{(a) Schematic drawing of the side-by-side growth with one NaOH catalyst treated substrate and one bare substrate.
+SEM images of the growth on the untreated substrates at different growth times: (b-e) 30 min and (f-i) 120 min.
+For 30 min growth: (b) low magnification SEM image showing labeled growth areas with different morphologies, (c) rectangular nanoplates grown without catalyst, (d) nanobelts grown with catalyst, and (e) forked nanoplates grown with catalyst.
+For 120 min growth: (f) rectangular nanoplates without catalyst, (g) forked nanoplates with catalyst, (h) microbelts with catalyst, and (i) microtowers with catalyst.}
+\label{fig:ch4sbs}
+\end{figure}
+
+After the growth, besides the non-catalyst rectangular plates, catalyst induced 1D structures were also found on the bare substrate (Fig.~\ref{fig:ch4sbs}b-i).
+This result clearly confirms that the catalyst can be evaporated and transferred from the NaOH treated substrate to the untreated one.
+The catalyst vapors can nucleate and form catalyst particles on the \ce{MoO3} deposition promoting the VLS growth of different 1D structures.
+It is worth mentioning that catalyst particles were not observed on all the 1D structures.
+This fact can be explained by following reasons.
+(1) Catalyst particles can nucleate at any locations along the 1D structures.
+Some particles may be invisible hiding on the backside of the 1D structures.
+(2) Because of the evaporation, the catalyst particles may become too small to be detected.
+Some particles could even disappear terminating the catalyzed growth, which may explain the growth of the microtowers with a flat top.
+The evaporation and nucleation of catalyst not only promote the growth of the 1D structures in the second stage growth, they also shape the morphologies of these 1D structures.
+Many 1D structures in the second stage were found to have a tapered shape, such as triangular nanobelts (Figure 2b and 2d) and microbelts (Figure 6k), microtowers with tapered tips (Figure 2f and Figure 7f) and cone-shaped microtowers (Figure 7h).
+Several factors can contribute to the tapering of the 1D structures.
+First, the reduction in catalyst size may induce the tapering.[38] Due to the evaporation, the size of the catalyst particles can shrink during the growth resulting in the tapered growth.
+The VS growth on the side surfaces is another possible mechanism, which promotes the radial growth of the 1D structures forming the tapered shape.
+Another important factor is the gradually reduced growth during the cooling process.
+During the cooling, the \ce{MoO3} vapor supply reduced and the growth temperature gradually decrease.
+Hence the growth rate slows down producing the tapered tips on the top of some 1D structures.
+
+\section{Extension of alkaline metal catalyzed growth}
+
+\subsection{Growth on alkaline metal containing substrate}
+
+In analog with the \ce{Na2MoO4}-\ce{MoO3} binary phase diagram, other alkaline metals, such as Li and K, could also form A-Mo-O alloy at elevated temperature.
+This fact enable the usage of a variety of alkaline metal based material as catalyst to promote VLS or VSS growth of \ce{MoO3}.
+Some experiments have been performed in this study, including growth using KI and \ce{Na2CO3} treated Si substrate, glass and mica.
+Fig.~\ref{fig:ch4al1}a-b show the long belt growth on KI treated Si substrate and towers on ITO glass, respectively.
+Compared to NaOH-Si growth, the belt on KI appears with rough edge, whereas the towers on ITO glass exhibit obvious stacking features.
+
+\begin{figure}[htb]
+\centering
+\includegraphics[width=0.6\textwidth]{Fig7_MoO3_Small}
+\caption[Alternative catalysts for \ce{MoO3} growth 1]{SEM images of \ce{MoO3} 1D structures. (a) nanobelts grown with KI and (b) microtowers grown on ITO glass}
+\label{fig:ch4al1}
+\end{figure}
+
+Fig.~\ref{fig:ch4al2}a-c illustrate the forked plate growth on \ce{Na2CO3} treated Si, sword-shape belts on glass, and nanoblets growth on mica, respectively.
+No long belt or tower was observed on the sample with \ce{Na2CO3}.
+Long belts found on mica(\ce{K(Al2)(Si3Al)O10(OH)2}) probably arise from potassium-catalyzed VLS mechanism.\cite{Hu2011} More detailed results on glass will be presented in Sec.~\ref{sec:glass}.
+
+\begin{figure}[htb]
+\centering
+\includegraphics[width=0.8\textwidth]{SFig5_MoO3_Small}
+\caption[Alternative catalysts for \ce{MoO3} growth 2]{SEM images of MoO3 1D structures: (a) forked nanoplates grown with \ce{Na2CO3}, (b) triangular microbelts grown on glass, and (c) nanobelts and microbelts grown on mica.}
+\label{fig:ch4al2}
+\end{figure}
+
+The various growth morphologies found using alkaline metal based materials as catalysts demonstrate the proposed VLS mechanism and transverse mode is a general phenomenon, and broad engineering space could be explored to control the dimension of \ce{MoO3}.
+
+\subsection{Growth on glass}\label{sec:glass}
+
+The mass transport of sodium ions in silica glass is first estimated to evaluate the amount of catalyst available during the growth of \ce{MoO3}.
+The driving force could be external field or concentration gradient.
+And the dynamics is governed by diffusion equation
 
@@
 
-where C is concentration in unit of \si{mol\per cm^3}, and D is diffusion coefficient in unit of \si{cm^2\per\second}.
+where $C$ is concentration in unit of \si{mol\per cm^3}, and $D$ is diffusion coefficient in unit of \si{cm^2\per\second}.
 Diffusion coefficient highly depends on the overall environments in which the ions resides.
@@
 
-for a typical 2 h growth, the net amount of Na diffusing out of substrate is then 144$\mu mol$, about 10\% of total Na ions.
+In a typical 2 h growth, the net amount of Na diffusing out of substrate is then $1.44\times10^{-4}$mol, about 10\% of total Na ions.
 The diffusion length $\sqrt{Dt}$ is 190 $\mu m$.
 Notice this result overestimate since the flux will reduce gradually.
-Meanwhile the molar amount of \ce{NaOH} applied on Si substrate is about 0.5 $\mu mol$.
+Meanwhile the molar amount of \ce{NaOH} applied on Si substrate is about $5\times10^{-7}$mol.
 Considering the adjusted ratio, Na contents should be much more when using glass substrate than when using NaOH-Si substrate.
-
 Another important factor is the evaporation of sodium molybdates.
@@
 
-\textbf{tower-like structure}
-
-Nanotower is a less common morphology in the structures of nanomaterials.\cite{Kharissova2010} We have not found report on  \ce{MoO3} nanotower structures, although there are several studies on \ce{In2O3},\cite{Jean2010,Yan2007}, GaN\cite{Xiao2012} and ZnO\cite{Zhang2013c}.
-\citeauthor{Jean2010} investigated the growth mechanism of \ce{In2O3} nanotowers and attributed it to the periodical axial and continuous lateral growth interaction, where the former was first guided by Au-In alloy liquid, and subsequent by self-catalytic In droplets (MP 156C) while the latter due to VS process.
-In contrast, \citeauthor{Yan2007} observed similar \ce{In2O3} nanotower growth and proposed that the axial growth is controlled by Au-catalytic VLS process.
-\citeauthor{Xiao2012} reported the GaN nanotower grown on Ni-coated Si(111) substrates and explained the growth as asymmetric self-copy process based on VLS mechanism.
-\citeauthor{Zhang2013c} studied the growth of ZnO nanotower and provided a competitive model between axial and lateral growth controlled by Zn vapor to explain the as-synthesized structures.
-(When ZnO and carbon mixture was used as source instead of ZnO alone, nanorods array results, presumably due to the stable supply of Zn vapor owing to the gentle carbothermal reduction.) Therefore the fluctuation of reagents is probably responsible for tapering and periodical modification, which is absent in the coin roll style growth of \ce{MoO3} tower on Si.
-The occasionally observed tapering or enlarging on \ce{MoO3} tower can be attributed to the cooling down growth.
-An oxygen regulated growth will be conducted to reveal the role of vapor pressure during the formation of tower.
-
-long belts  is also found on Mica(\ce{K(Al2)(Si3Al)O10(OH)2}), the formation probably arise from Potassium-catalyzed VLS mechanism.\cite{Hu2011}
-
-\subsubsection{time stepwise growth}
-
-As shown in Fig, we found several solid clusters with diameter about 1 $\mu m$ on the top part of long belts.
-According to the \ce{Na2MoO4}-\ce{MoO3} binary compounds phase diagram, we expect the terminating solid clusters have a Na:Mo ratio close to 0.6.
-The experimental results match well with this predictions.
-EDX analysis reveal the presence of Na on the solid cluster but not at about 1$\mu m$ away from previous location.\footnote{the sensitivity of our instrument is estimated to be 1\% atomic level} Quantitative atomic ratio derived from the solid cluster is not close to the one predicted by phase diagram probably due to the high Mo content in adjacent area.
-However, XRD examinations on a short time growth sample revealed a possible \ce{Na2Mo4O13} phase(PDF 028-1112), providing an indirection evidence of the droplet composition.
-
-We also suspect that the growth will become different below 500 \si{\degreeCelsius} since no liquid would remain. Substrate placed at low temp end show.
-
-We can also deduce that other sodium compounds can be employed as substrate treatment agent. This argument is confirmed by \ce{Na2CO3} and \ce{KI} assisted growth.
-
-\textbf{open questions}
-\begin{itemize}
-\item Is the liquid consumed? if so, how? : evaporation
-\item How the size of liquid is related to the morphology evolution?
-\item Possible doping level of alkaline ions
-\item other lateral growth mode such as Ni-W-S system
-\item VLS-VS interaction, or possible solution-liquid-solid, VSS,
-\item the interpretation of phase diagram
-\item the overall molar amount of NaOH and MoO3 deposition
-\item Young's parameters, contact angle informations, Gibbs free energy calculation
-\item catalyst composition variation during growth
-\item \ce{Na2Mo4O_{13}} phases, solid solubility of \ce{Na2MoO4} in solid \ce{MoO3} is high.
-\item vapor pressure of \ce{Na2Mo4O_{13}} and \ce{MoO3}.
-\end{itemize}
-
-\subsection{glass growth}
-
-We studied the effect of temperature, oxygen partial pressure and growth time towards \ce{MoO3} deposition on glass substrates.
-Each factor is divided into two levels, with T at 700 and 800, \ce{O2} at 1 and 10 sccm, and growth time of 15 and 60 mins.
-We will assign $+$ and $-$ to higher and lower levels, respectively.
+The author studied the effect of temperature, oxygen partial pressure and growth time towards \ce{MoO3} deposition on glass substrates.
+Each factor is divided into two levels, with T at 700 and 800 \si{\degreeCelsius}, \ce{O2} at 1 and 10 sccm, and growth time of 15 and 60 min.
 And the morphological variation is summarized in Table~\ref{tab:mo3glass}.
@@
 
-\subsection{Liquid exfoliation on as-grown molybdenum oxides}
+\subsection{Liquid exfoliation of molybdenum oxide}
 

### 2014-08-04 main.tex
moo3 chapter 70 percent

@@
 \end{figure}
+
+Nanotower is a less common morphology in the structures of nanomaterials.\cite{Kharissova2010} We have not found report on  \ce{MoO3} nanotower structures, although there are several studies on \ce{In2O3},\cite{Jean2010,Yan2007}, GaN\cite{Xiao2012} and ZnO\cite{Zhang2013c}.
+\citeauthor{Jean2010} investigated the growth mechanism of \ce{In2O3} nanotowers and attributed it to the periodical axial and continuous lateral growth interaction, where the former was first guided by Au-In alloy liquid, and subsequent by self-catalytic In droplets (MP 156C) while the latter due to VS process.
+In contrast, \citeauthor{Yan2007} observed similar \ce{In2O3} nanotower growth and proposed that the axial growth is controlled by Au-catalytic VLS process.
+\citeauthor{Xiao2012} reported the GaN nanotower grown on Ni-coated Si(111) substrates and explained the growth as asymmetric self-copy process based on VLS mechanism.
+\citeauthor{Zhang2013c} studied the growth of ZnO nanotower and provided a competitive model between axial and lateral growth controlled by Zn vapor to explain the as-synthesized structures.
+(When ZnO and carbon mixture was used as source instead of ZnO alone, nanorods array results, presumably due to the stable supply of Zn vapor owing to the gentle carbothermal reduction.) Therefore the fluctuation of reagents is probably responsible for tapering and periodical modification, which is absent in the coin roll style growth of \ce{MoO3} tower on Si.
+The occasionally observed tapering or enlarging on \ce{MoO3} tower can be attributed to the cooling down growth.
+
+We divide the growth into two stages according to the emerging time of long belts and towers.
+In first stage the growth is dominated by lateral growth, as illustrated in .
+In the second stage, \ce{NaxMoO3} is evaporated and recondensed in the low temperature region, and some droplet will form, and when at proper locations, introduce secondary VLS growth.
+
+In first stage, the Na-Mo-O liquid is formed and have much more higher absorption rate than that of bare substrate.
+The absorbed species will diffuse along the surface and inside the liquid.
+It was difficult to estimate which diffusion path one is faster.
+
+\textbf{open questions}
+\begin{itemize}
+\item Is the liquid consumed? if so, how? : evaporation
+\item How the size of liquid is related to the morphology evolution?
+\item Possible doping level of alkaline ions
+\item other lateral growth mode such as Ni-W-S system
+\item VLS-VS interaction, or possible solution-liquid-solid, VSS,
+\item the interpretation of phase diagram
+\item the overall molar amount of NaOH and MoO3 deposition
+\item Young's parameters, contact angle informations, Gibbs free energy calculation
+\item catalyst composition variation during growth
+\item \ce{Na2Mo4O_{13}} phases, solid solubility of \ce{Na2MoO4} in solid \ce{MoO3} is high.
+\item vapor pressure of \ce{Na2Mo4O_{13}} and \ce{MoO3}.
+\end{itemize}
+
+As shown in Fig, we found several solid clusters with diameter about 1 $\mu m$ on the top part of long belts.
+According to the \ce{Na2MoO4}-\ce{MoO3} binary compounds phase diagram, we expect the terminating solid clusters have a Na:Mo ratio close to 0.6.
+The experimental results match well with this predictions.
+EDX analysis reveal the presence of Na on the solid cluster but not at about 1$\mu m$ away from previous location.\footnote{the sensitivity of our instrument is estimated to be 1\% atomic level} Quantitative atomic ratio derived from the solid cluster is not close to the one predicted by phase diagram probably due to the high Mo content in adjacent area.
+However, XRD examinations on a short time growth sample revealed a possible \ce{Na2Mo4O13} phase(PDF 028-1112), providing an indirection evidence of the droplet composition.
+We also suspect that the growth will become different below 500 \si{\degreeCelsius} since no liquid would remain.
+Substrate placed at low temp end show.
+We can also deduce that other sodium compounds can be employed as substrate treatment agent. This argument is confirmed by \ce{Na2CO3} and \ce{KI} assisted growth.

### 2014-08-06 BackMatter/app-tms.tex
tms chapter 50 percentage

\chapter{bulk tungsten disulfide}

Tungsten disulfide (\ce{WS2}) is a group VI dichalcogenide semiconductor compound. The molecular weight is 249.97 \si{g\per \mole}. Almost all natural \ce{WS2} belongs to P63/mmc space group (2H-\ce{WS2}), where $a$ is 3.153 \AA, $c$ is 12.323 \AA (PDF 04-003-4478). Two other crystal structures were found in man-made \ce{WS2}, i.e. 1T and 3R, where 3R can be prepared by bromine chemical vapor transport (CVT) method \cite{Schutte1987} and 1T was generally found in alkaline intercalated \ce{WS2}.\cite{Yang1996a, Enyashin2011}

\section{Crystallography and thermodynamics}

The refined crystallographic data, including bond length, angle is listed in Fig.~\ref{app:bond}.

\begin{figure}[htb]
\centering
\includegraphics[width=0.9\textwidth]{tms_crys}
\caption{Adopted from Ref.\cite{Schutte1987}}
\label{app:bond}
\end{figure}

The melt point of \ce{WS2} is 1523 K (decompose). A phase diagram between W and S is shown in Fig.~\ref{app:pd}.

\begin{figure}[htb]
\centering
\includegraphics[width=0.6\textwidth]{ws_phase}
\caption{Adopted from Ref.\cite{Tenne1995,Tenne1998}}
\label{app:pd}
\end{figure}

\section{Band structures}

A theoretical calculation is shown in Fig.~\ref{app:band} 
\begin{figure}[htb]
\centering
\includegraphics[width=0.7\textwidth]{ws2_bandcal}
\caption{Adopted from Ref.\cite{Kuc2011}}
\label{app:band}
\end{figure}

\section{Dielectric function}

$\epsilon(h\nu)$ is shown in Fig.~\ref{app:nk}. 
\begin{figure}[htb]
\centering
\includegraphics[width=0.5\textwidth]{ws2_nk}
\caption{Adopted from Ref.\cite{Hughes1976}}
\label{app:nk}
\end{figure}

The $n$ and $\kappa$ can be retrieved using other software, such as Tracer 2.0.\footnote{\url{https://sites.google.com/site/kalypsosimulation/Home/data-analysis-software-1}}

### 2014-08-06 BackMatter/paper.tex
tms chapter 50 percentage

@@
 
+plasmon dispersion in 2D materials, plasmon resonances in visible regions by doping induced free carrier density.
+2D plasmonics, depolarization factors, partial reduction of Mo to a lower valence state.
+\cite{Alsaif2014a}
+
+2D wo3.\cite{Kalantar-zadeh2010a}
+
 \ce{MoO3} ECD:
@@
 \begin{quote}
-a viable electrochromic smart window must exhibit a cycling life time \textgreater $10^5$ cycles, corresponding to an operation life at 10 - 20 years.
+a viable electrochromic smart window must exhibit a cycling life time \textgreater $10^5$ cycles, corresponding to an operation life at 10 -- 20 years.
 \end{quote}

### 2014-08-06 ch-tms/tms.tex
tms chapter 50 percentage

@@
 
-In this chapter, we will first review the growth of \ce{MS2} nanotubes and few layer structures.
-Then we summarize the Raman spectroscopy results on NTs and FL.
-Finally we present our own results on synthesis and characterization.
+In this chapter, a TEM-Raman integrated study on \ce{WO3}-\ce{WS2} core-shell nanostructures is presented.
+We leverage a home-built micromanipulator apparatus to transfer the nanostructures between TEM grids and other desired substrates.
+This technique has enabled us to correlate TEM and micro-Raman measurement on individual nanowires, thereby enhancing the understanding of structure-property relations which would otherwise be blurred in conventional ensemble averaged methods.
+\ce{WO3}-\ce{WS2} heterostructure is chosen due to the potential applications in photocatalysis and hydrogen evolution.
 
-\section{Literature review}
+The remaining section is arranged in following order: A review on the growth of \ce{MS2} (M = Mo, W)nanotubes (NTs) and 2D few layer (FL) structures will be introduced first.
+And Raman spectroscopy results on NTs and FL are summarized.
+The thesis will then focus on synthesis of \ce{WO3}-\ce{WS2} heterostructure and various characterizations, including both ensemble averaged and on individual nanowires.
 
+\section{Introduction}
+
+\subsection{Growth of TMDC}
 Shortly after the the discovery of carbon nanotube (CNT) in 1991,\cite{Iijima1991} its transition metal dichalcogenides (TMDC) counterparts (\ce{WS2}) was synthesized in 1992.\cite{Tenne1992} In the following decade, other TMDC and several metal oxides nanotubes were demonstrated as well.
@@
 
-\section{Raman spectra}
+\subsection{Raman on bulk and FL TMDC}
 
@@
 Compared to the size of Brillouin zone ($\pi/a = 10^{10}m^{-1}$), resonant Raman could or could not probe phonon at $M$ point.
-
-\subsection{TMS bulk and FL}
 
@@
 
-\subsection{TMS NTs}\label{sec:ntram}
+\subsection{Raman on TMDC NTs}\label{sec:ntram}
 
@@
 The difference of B1u and LA + TA.
+
+\section{Results and Discussion}
+
+\subsection{synthesis method in this work}
+
+Four kinds of tungsten powders were used as precursor to prepare \ce{WO3} NWs, and sulfur powder was used to fabricate \ce{WO3}-\ce{WS2} core-shell NWs, as summarized in Table.~\ref{tab:ch5pre}.
+All reactants were employed as received without further processing.
+Substrates cleaning precudures have been introduced in Sec.~\ref{ch2sub}.
+
+% Tungsten powders size and purity
+\begin{table}[htb]
+\centering
+\caption{List of reactants}\label{tab:ch5pre}
+\begin{tabular}{lccr}
+\toprule
+Name & purity & average size & vendor info\\
+\midrule
+3N   &  99.9\% & 17 $\mu$m & Alfa Aesar \#39749\\
+3N5   &  99.95\% & 32 $\mu$m  & Alfa Aesar \#42477\\
+4N5   &  99.995\% & 3.3 $\mu$m  & Materion T-2049 \\
+5N   &  99.999\% & 1.5 $\mu$m & Alfa Aesar \#12973\\
+S    &   99.5\%  &  NA  & Alfa Aesar \#10785\\
+\bottomrule
+\end{tabular}
+\end{table}
+
+\ce{WO3} NWs were obtained by a seeded growth with tungsten powders applied onto the Si substrate.
+To find out the optimal conditions, tungsten powder oxidation experimental were carried out.
+Schematic layout of each growth were illustated in Fig.~\ref{fig:ch5grow} including the sulfurization process.
+
+% cvd NW growth
+\begin{figure}[htb]
+\centering
+\includegraphics[width=0.7\textwidth]{cs_sfig1_all}
+\caption[\ce{WO3} NW growth: OT]{Schematic diagrams of (a) tungsten power oxidization, (b) seeded growth of \ce{WO3} NW, and (c) sulfurization process.
+(d) Chemical vapor deposition system temperature profile measured at ambient condition.
+The zero inch location is defined at the upstream edge of furnace.}
+\label{fig:ch5grow}
+\end{figure}
+
+In a typical oxidation experiment shown in Fig.~\ref{fig:ch5grow}a, tungsten powders were loaded into the uniform heating zone and the sealed chamber was pumped down to an ultimate pressure of $5\sim8$ mTorr.
+Then oxygen flow varying between 1 sccm to 10 sccm (standard cubic centimeter per minute) was admitted from upstream inlet.
+With 10 sccm UHP Ar (99.999\%) as carrier gas, the overall pressure reached to about 100 mTorr.
+The heating temperature (500 to 750 \si{\degreeCelsius}) was ramped up in 30 min and lasted for 30 min.
+Then the heating power was turned off and the chamber was allowed to naturally cool down to room temperature.
+
+In a representative seeded growth (Fig.~\ref{fig:ch5grow}b), 4N5 or 5N tungsten source powder (Table.~\ref{tab:ch5pre}) was positioned in the upstream end of a quartz boat and downstream about 2.5 in the substrate was stationed.
+Additional tungsten seed powders (3N) were distributed evenly onto the substrate.
+After pumping down, 1 sccm oxygen and 10 sccm Ar were admitted into the chamber, respectively.
+The heating temperature was ramped up to 1000 \si{\degreeCelsius} in 30 min and lasted for 240 min.
+Subsequently the apparatus was allowed to naturally cool down to room temperature.
+
+\ce{WO3}-\ce{WS2} core-shell NWs were synthesized using direct sulfurization of \ce{WO3} NWs.
+As depicted in Fig.~\ref{fig:ch5grow}c, the as-grown \ce{WO3} NWs were loaded into the center of heating furnace, and $\sim200$mg sulfur (Alfa Aesar 10785, 99.5\%) was positioned just outside the upstream edge of furnace, where the maximum temperature was about 240 \si{\degreeCelsius}.
+After pumping down, the reaction chamber was flushed two times to expel residual air.
+A cold trap filled with liquid nitrogen in downstream was used to collect possible sulfur precipitation.
+Then the furnace was heated to 750 \si{\degreeCelsius} in 30 min, held for 15 min, and allowed to naturally cool down to room temperature.
+During entire growth process, 30 sccm Ar was used as carrier flow.
+
+\subsection{Characterizations}
+
+\subsubsection{Optimization of W powder oxidization}\label{sec:woxd}
+
+Understanding the oxidation of tungsten powder is the key to obtain high yield in seeded growth.
+Oxidation of tungsten have been investigated under diverse conditions, such as at elevated temperature (\textgreater 1100 \si{\degreeCelsius} ) and oxygen pressure on the order of Torr,\cite{Base1965} and at temperatures ranging from 20 to 500 \si{\degreeCelsius} under atmosphere pressure.\cite{Warren1996} \ce{WO_x} NWs were readily found when tungsten (foil, wire, or powder) is oxidized under various conditions.\cite{Zhu1999,Karuppanan2007,Hsieh2010} However the study on tungsten powder oxidation behavior between intermediate temperature range and under low pressure is still rare.
+This work studied the oxidation of tungsten powders with diverse size within temperature range from 500 to 1000 \si{\degreeCelsius} and under several mTorr oxygen partial pressure.
+Using tungsten powder as seed, the author further illustrate an economic approach to obtain large yield of \ce{WO3} nanowires at relatively lower temperature than previous efforts.
+It is demonstrated that there is an optimal tungsten powder size under our experimental conditions for seeded growth.
+This will provide some insight on the role of tungsten powder as source material in CVD growth of \ce{WO_x}.
+
+Commercial available tungsten powders with different size are usually associated with purity variation as well, as already listed in Table.~\ref{tab:ch5pre}.
+The dimensions of tungsten powder were obtained by measuring the average size in SEM graphs.
+A systematic investigation was performed on the oxidation behavior of tungsten powder to evaluate the temperature effect, size-dependence and influence of oxygen partial pressure.
+% seed optimal
+\begin{figure}[htb]
+\centering
+\includegraphics[width=0.7\textwidth]{JAP-2column_Fig1.jpg}
+\caption[W powder oxidation: temperature effect]{SEM graphs of 99.9\% (3N) tungsten powder oxidization at different temperatures of a) 500 \si{\degreeCelsius}, b) 600 \si{\degreeCelsius}, c) 650 \si{\degreeCelsius}, d) 750 \si{\degreeCelsius}, showing the optimal temperature for local formation of nanowires is between 600--650 \si{\degreeCelsius}.
+Oxygen flow rate is 1 sccm.}
+\label{fig:pdtemp}
+\end{figure}
+
+Fig.~\ref{fig:pdtemp} illustrated the effect of temperature on the morphological change and surface nanowires formation of 3N powder.
+At 500 \si{\degreeCelsius}, most tungsten powder retained its original shape and a layer of tiny dense NWs begun to grow.
+When temperature was increased to 600 \si{\degreeCelsius}, 3N powder started to crack with longer NWs on the isolated surface.
+Further increase of temperature lead to irregular shapes of tungsten power and aggregation of NWs, giving rise to the nanorods and bunched or bundled structures.
+It could be determined from the morphology variation that the optimal seeded growth temperature for 3N powder was in the range of 600 to 650 \si{\degreeCelsius}.
+% seed optimal
+\begin{figure}[htb]
+\centering
+\includegraphics[width=0.7\textwidth]{JAP-2column_Fig3.jpg}
+\caption[W powder oxidation: size effect]{SEM graphs illustrating the oxidization of four different size of tungsten powders at 600~\si{\degreeCelsius} and 1 sccm oxygen flow.
+a) 17 $\mu m$, b) 32 $\mu m$, c) 3.3 $\mu m$, d) 1.5 $\mu m$.}
+\label{fig:pdsize}
+\end{figure}
+
+Fig.~\ref{fig:pdsize} depicted the oxidation of different sizes of tungsten powder under the same experimental conditions.
+In contrast to the morphology of 3N powder shown in Fig.~\ref{fig:pdtemp}, 3N5 powder surface is primarily covered with sub-micro particles as well as some short tiny NWs, whereas 4N5 and 5N powder were thoroughly oxidized, showing branched flowers feature.
+This dramatic difference could be explained in terms of surface energy and oxygen diffusion.
+With smaller dimension, the increased surface-to-volume ratio and short diffusion path both lower the energy barrier of oxidation.\cite{tungsten1999} It was logical to deduce that higher temperature or increased oxygen level might favor the NWs formation on 3N5 powder.
+When it comes to seeded growth, however, the powder size distribution was an important factor to give uniform NWs deposition.
+Since the size distribution of 3N powder is more uniform than that of 3N5 powder, the author employed the former as seeds.
+% seed optimal
+\begin{figure}[htb]
+\centering
+\includegraphics[width=0.7\textwidth]{JAP-2column_Fig2.jpg}
+\caption[W powder oxidation: oxygen pressure]{SEM graphs of 3N tungsten powder oxidization at 600 \si{\degreeCelsius} under different rates of oxygen flow: a) 1 sccm, b) 2 sccm, c) 3 sccm, d) 10 sccm.
+The oxygen partial pressures were 13 mTorr, 23 mTorr, 32 mTorr, and 82 mTorr, respectively with background pressure subtracted.}
+\label{fig:pdoxy}
+\end{figure}
+
+Fig.~\ref{fig:pdoxy} depicted the morphology change of 3N powder with respect to varied oxygen partial pressure.
+When the oxygen flow is lower than 3 sccm, 3N powder almost stayed as the same, with cracks separating the dense layer of NWs.
+When oxygen flow is increased to 10 sccm, the 3N powder exemplified an enlarged version of that for 4N5 or 5N powder under 1 sccm oxygen flow.
+This observation again supported the surface energy explanation.
+
+\subsubsection{Seeded growth of tungsten oxide NWs}
+With the oxidation experiments study in Sec.~\ref{sec:woxd}, favorable conditions for local growth of NWs were extracted to perform seeded growth.
+
+\begin{figure}[htb]
+\centering
+\subfloat[]{\label{fig:sga}\includegraphics[width=0.4\textwidth]{wox_sg_a.jpg}}\hspace{0.04\textwidth}
+\subfloat[]{\label{fig:sgb}\includegraphics[width=0.4\textwidth]{wox_sg_b.jpg}}
+\caption[Characterization of seeded growth \ce{WO3}: SEM]{Characterizations of seeded growth.
+(a) SEM graphs of \ce{WO3} NWs on \ce{SiO2/Si} substrate.
+(b) A high magnification view showing uniform NW growth and close-up view of one NW.
+}
+\label{fig:woseedsem}
+\end{figure}
+
+As shown in Fig.~\ref{fig:sgb}, dense NWs array was obtained on tungsten powder seeds with individual wires of length up to 5 $\mu$m and diameter about 50 to 200 nm, according to the estimation made in the close-up view.
+Each tungsten powder stood as independent growth site (Fig.~\ref{fig:sga}) with island-layer growth on the substrates, a common feature without using tungsten powder as seed under current experimental conditions.
+It was occasionally observed that NWs growth was initiated adjacent some tungsten powders.
+This phenomenon was correlated to the local trap of vapor flow since it was more often found among the enclosed area by tungsten powders.
+It is also found that the diameter of NWs decrease as the distance between powders and upstream edge increases.
+This is a combination effect of lower temperature and reduced \ce{WOx} growth species supply.
+Similar phenomena were observed in other studies.
+\citeauthor{Thangala2007} reported that a decrease in NW density with increasing substrate temperature, and an increase of NW density with increasing partial pressure of oxygen.\cite{Thangala2007}
+
+% seeded edx 
+\begin{figure}[htb]
+\centering
+\includegraphics[width=0.7\textwidth]{wo3_seed_edx}
+\caption[Composition analysis on seeded growth \ce{WO3} NWs]{EDX spectroscopy on seeded growth \ce{WO3} NWs.}
+\label{fig:woedx}
+\end{figure}
+Energy-dispersive X-ray spectroscopy (EDX) analysis on the seeded growth \ce{WO3} NWs is shown in Fig.~\ref{fig:woedx}.
+Only W and O elements were detected on the NW array.
+The background level from 3 to 8 keV was a manifestation of the continuous components of W X-ray spectrum.
+
+% sg raman xrd
+\begin{figure}[htb]
+\centering
+\subfloat[]{\label{fig:sgxrd}\includegraphics[width=0.45\textwidth]{xrd_cs_before}}\hspace{0.04\textwidth}
+\subfloat[]{\label{fig:sgram}\includegraphics[width=0.45\textwidth]{wox_raman_1}}
+\caption[Characterization of seeded growth \ce{WO3}: XRD and Raman]{ (a) XRD pattern of as-prepared sample indicating the \ce{WO3} phase and the presence of metallic core.
+(b) Raman spectrum on NWs region showing the feature of \ce{WO3}.}
+\label{fig:woseedxrd}
+\end{figure}
+
+Fig.~\ref{fig:sgxrd} is the XRD spectrum of one typical sample.
+The peaks under circular symbol were identified to be the monoclinic \ce{WO3} phase (ICDD PDF 01-083-0950, \emph{a}=7.30084 \AA, \emph{b}=7.53889 \AA, \emph{c}=7.6896 \AA, $\beta$=90.89$^\circ$), while the peak under the triangular symbol was indexed to cubic tungsten phase (ICDD PDF 04-16-3405, \emph{a}=3.157 \AA), in agreement with the EDX analysis (Fig.~\ref{fig:woedx}).
+This means that during the \ce{WO3} seeded growth of 4 h heating at 1000 \si{\degreeCelsius}, the tungsten powder in downstream low temperature region (600 -- 700 \si{\degreeCelsius}) is not entirely oxidized.
+Micro-Raman scattering spectroscopy was performed on the as-synthesized sample as well.
+During Raman examination, the laser spot was carefully focused onto the NWs on powders and several inspections on different positions were observed to ensure the reproductivity of spectra data.
+As shown in Fig.~\ref{fig:sgram}, five distinct bands were well resolved, with peaks located at 131, 265, 327, 711 and 803 \si{cm^{-1}}, respectively.
+This pattern was typical features of \ce{WO3}, consistent with previous study.\cite{Salje1975a,Dixit1986} The high background level probably arises from the metallic core.
+
+% sg tem
+\begin{figure}[htb]
+\centering
+\includegraphics[width=0.9\textwidth]{JAP-2column_Fig5major.jpg}
+\caption[Characterization of \ce{WO3}: TEM]{TEM graphs of as-prepared NWs.
+(a) TEM image of one nanowire with diameter about 40 nm.
+(b) HRTEM images showing the spacing is 0.38 nm, corresponding to (002) plane distance.}
+\label{fig:woseedtem1}
+\end{figure}
+
+TEM specimen was prepared by using carbon grid to slightly scratch the as-grown sample.
+Fig.~\ref{fig:woseedtem1} shows the feature of majority NWs.
+The growth direction is determined to be perpendicular to (002) plane.
+The streaking in SEAD pattern presumably arises from stacking defaults.
+The author also find some NWs exhibit high crystalline quality, as revealed by the TEM analysis in Fig.~\ref{fig:woseedtem2}.
+The NW grew normal to (002) plane with a measured lattice spacing of 3.79 \AA, which is favorably compared to the XRD peak at $23.07^\circ$ (7.7103 \AA).
+The sharp SEAD pattern and clear phase contrast in HRTEM demonstrated are both strong evidence of good crystallinity.
+This formation indicated current growth parameters have promising potential to obtain highly crystalline \ce{WO3} NWs in large scale.
+
+% sg tem
+\begin{figure}[htb]
+\centering
+\includegraphics[width=0.9\textwidth]{JAP-2column_Fig5minor.jpg}
+\caption[Characterization of \ce{WO3}: TEM cont]{TEM graphs of as-prepared NWs.
+(a) TEM image of one nanowire, the diameter is about 70 nm.
+(b) HRTEM images showing the spacing is 0.379 nm, corresponding to (002) plane distance.}
+\label{fig:woseedtem2}
+\end{figure}
+
+In regarding to the formation of NWs on tungsten powder itself, this study assumes the driving force is related to interfacial strain between W and \ce{WOx}.
+Oxidation of tungsten proceed slowly at room temperature and an oxide layer of 100 \AA was found on the surface of tungsten foils.\cite{Warren1996} The tungsten powder used in current study would be covered by a thin oxide layer as well.
+During oxidation, different oxidation rates exist for different crystallographic orientations on the tungsten powder.
+Oxidation occurring at boundaries and defects are preferred thermodynamically.\cite{You2010} Compressive strain will gradually accumulate at the tungsten oxide/tungsten interface, which might limit the diffusion rate of oxygen at temperature lower than 500 \si{\degreeCelsius}.\cite{tungsten1999} At elevated temperature, cracks will primarily occur, as observed in Fig.~\ref{fig:pdtemp}.
+When heated up, tungsten and the oxide shell will probably relax the strain by converting into substoichiometric NWs, a similar process as suggested by \citeauthor{Klinke2005} in the chemically induced strain growth of tungsten oxide NWs.\cite{Klinke2005} It is worth noting that tungsten oxide nanowires could also formed when \ce{WO3} is reduced.\cite{Sarin1975} The elongation of \ce{WOx} is thermodynamically favorable during the conversion from metallic tungsten to tungsten oxide as well.
+Local evaporation-condensation process might also contribute to the formation of NWs on tungsten powder.
+
+The enhanced yield of NWs obtained via seeded growth could be explained by a vapor-solid (VS) mechanism.
+External supply of growth species will condense onto the powders and substrate simultaneously, promoting the elongation of NWs on power as well as resulting island-layer growth on substrate.
+The local NW density in oxidation experiment was much higher than that of seeded growth.
+It is reasonable to presume that during seeded growth, several NWs in a small region on powder will coalescence, as evidenced by the bundled structures.
+At last, the author would like to point out that when low purity tungsten powder (3N) was used as source, sodium tungsten oxide nanowires were found to be dominant in the final product.
+The details have been published.\cite{Sheng2014} It seems surprising that when 3N powder was used as seeds, only \ce{WO3} nanowires were obtained.
+This result was attributed to the lower temperature and significantly reduced amount of 3N powder used in the seeded growth, compared with the conditions used in Ref.\cite{Sheng2014}.
+The source material in seeded growth is not limited to high purity tungsten powder.
+Instead, any material that could produce appropriate growth vapor could be employed, indicating the versatility of this approach.
+\subsubsection{Ensemble measurements on core-shell NWs}
+
+The morphology of \ce{WO3} NWs in micron scale almost stay the same after sulfurization, as shown in the inset SEM imaging of Fig.~\ref{fig:ch5ws2sem}.
+The length of individual nanowire can be up to 15 $\mu$m and the diameter varies from about 40 to 300 nm.
+The surface of the NWs were rather smooth without other attachments.
+The NWs array grow slightly larger than the W seed ( $\sim 12 \mu$m), mostly due to the elongation of NW.
+
+\begin{figure}[htb]
+\centering
+\includegraphics[width=0.7\textwidth]{ws2_sem_edx}
+\caption[Morphology and composition analysis on \ce{WO3}-\ce{WS2} NWs]{Morphology and composition analysis on the as-synthesized core-shell structures.
+(a) SEM images showing the NWs almost retain their original shapes after sulfurization, and (b) EDX spectroscopy revealing the presence of sulfur element after sulfurization.}
+\label{fig:ch5ws2sem}
+\end{figure}
+
+The EDX spectrum in Fig.~\ref{fig:ch5ws2sem} revealed the presence of sulfur element, indicating the effectiveness of sulfurization.
+Compared to the XRD pattern on seeded growth \ce{WO3} sample, post-sulfurization pattern (Fig.~\ref{fig:ch5ws2xrd}) shows a much reduced \ce{WO3} intensity with W phase becoming relatively prominent.
+Still the peaks at 23.44$^{\circ}$ and 24.36$^{\circ}$ can be indexed to \ce{WO3} (020) and (200) reflection, respectively.
+This result as well as the SEM imaging indicates \ce{WO3} NWs could preserve some long range order after the sulfurization for 15 min at 750 \si{\degreeCelsius}.
+
+%fig xrd ws2 
+\begin{figure}[htb]
+\centering
+\includegraphics[width=0.7\textwidth]{ws2_cs_xrd}
+\caption[XRD on core-shell NWs]{X-ray diffraction spectra before and after sulfurization. The reference spectra for $c$-W, 2H-\ce{WS2} and $m$-\ce{WO3} are included with some major peaks labeled.}
+\label{fig:ch5ws2xrd}
+\end{figure}
+
+This observation can also be used to account for the extreme small peak at 13.87$^{\circ}$ in the post-sulfurization spectrum.
+Compared the reference 2H-\ce{WS2} (002) peak (14.37$^{\circ}$, ICDD PDF 04-003-4478), this redshift indicates an increase of lattice spacing along $c$ axis (from 6.16 \AA to 6.38 \AA).
+The FWHM of this (002) peak is about 1.1$^{\circ}$, giving an estimation on the crystalline size of 7.5 nm according to Scherrer equation.
+
+Due to this small spacing, TEM is primarily utilized to observe the detailed morphology of \ce{WO3}-\ce{WS2} core-shell NWs.
+Fig.~\ref{fig:ch5ws2tem1} shows HRTEM imaging on typical tip and body region of the core-shell NW, respectively.
+A comparison with the pre-sulfurization specimen (Fig.~\ref{fig:woseedtem2}) readily reveals the formation of core-shell morphology after sulfurization.
+The measured layer spacing is 6.4 \AA, slight larger than bulk 2H-\ce{WS2} of 6.16 \AA, but in good agreement with XRD results in Fig.~\ref{fig:ch5ws2xrd}.
+The clear contrast in core region also prove the lattice structure of \ce{WO3} is not seriously distorted.
+
+% tem core shell layer
+\begin{figure}[htb]
+\centering
+\includegraphics[width=0.9\textwidth]{ws2_coreshell_tem}
+\caption[TEM imaging on core-shell NWs: 1]{HRTEM imaging on one core-shell nanowire showing layer number changes.}
+\label{fig:ch5ws2tem1}
+\end{figure}
+
+After examining dozens of core-shell NWs, the author found the \ce{WS2} layer number at NW tip was usually the largest, reaching more than ten, and the layer number could decrease to one along the NW body, but there exist some layer number fluctuation and shape modification.
+Fig.~\ref{fig:ch5ws2tem3} shows a smooth transition of \ce{WS2} layer number on the tip region of one NW.
+The layer number is about 7 on the tip corner, gradually decreases from 4 to 3 along the NW body, and stops at 2.
+Closer observation indicates the layer spacing is not quite uniform in the tip area, probably due to the complex curvature and bending.
+\ce{WS2} fullerene also show similar structures.
+Since the closing of the tip region could be of great complexity and the induced strain could modify Raman signal considerably, the TEM-Raman integrated measurement in this study will focus on the body region only, with those having smooth transition of layer number.
+% coreshell tem
+\begin{figure}[htb]
+\centering
+\includegraphics[width=0.8\textwidth]{ws2_growth3}
+\caption[TEM imaging on core-shell NWs: 2]{HRTEM imaging on the tip area of one core-shell nanowire.}
+\label{fig:ch5ws2tem3}
+\end{figure}
+
+As illustrated in Fig.~\ref{fig:ch5ws2tem4}, complicated \ce{WS2} encapsulation was observed on one tapered core-shell NW.
+This tapering probably arose from the sulfurization process, but could be also due to the parent \ce{WO3} NW.
+The diameter varied from about 200 nm to 15 nm, and the \ce{WS2} layer number also changed in a nonlinear manner.
+On some turning region, the \ce{WS2} seems penetrating into the body of primary \ce{WO3} NW.
+
+% coreshell tem
+\begin{figure}[htb]
+\centering
+\includegraphics[width=0.8\textwidth]{ws2_growth4}
+\caption[TEM imaging on core-shell NWs: 3]{HRTEM imaging on one tapered core-shell nanowire showing fluctuation of layer numbers}
+\label{fig:ch5ws2tem4}
+\end{figure}
+
+A systematic study on the sulfurization must be performed to understand the growth dynamics.
+The growth mechanism of \ce{WS2} nanotubes from oxides were thoroughly studied,\cite{Feldman1998} and it is generally agreed that the sulfurization of \ce{WO3} is a diffusion limited reaction.\cite{Feldman1996} It was also suggested that the core \ce{WO3} NWs will become non-stoichiometric phases upon sulfurization.\cite{Feldman1996,ZAK2009} In this study, the author recognize this possibility but also consider two factors different from previous studies: one is the usage of sulfur as precursor instead of \ce{H2} and/or \ce{H2S} as in previous reports, which will accelerate the reduction of \ce{WO3} significantly due to the formation of \ce{H2O}; the other is the short reaction time and light degree of sulfurization, which probably will not distort the \ce{WO3} lattice significantly, as evidenced by the XRD and HRTEM analysis in this section.
+The sulfurization dynamic is then proposed as following in this thesis: the tips of \ce{WO3} NWs exhibit greater crystalline disorder, and \ce{WS2} layers on tips are folded at least along two axes, resulting a higher density of defects and thus a higher sulfurization rate; while the folding along NW body is quasi-one dimensional, subsequently the sulfurization rate could be lower.
+Besides, sulfurization could also initiated from the NW body, presumably due to the presence of surface defects.
+As a result, this led to the uneven \ce{WS2} layer number distribution along the core-shell NWs.
+
+Among most of the core-shell NWs examined under TEM, the author observed no discernible consumed core region.
+An exception is shown in Fig.~\ref{fig:ch5ws2tem2}.
+It is worth mentioning that some interesting growth behavior around the void region, where a new \ce{WS2} layer pushing through the already formed \ce{WS2} ones, deviating from the diffusion growth model.
+
+% coreshell tem
+\begin{figure}[htb]
+\centering
+\includegraphics[width=0.8\textwidth]{ws2_growth1}
+\caption[TEM imaging on core-shell NWs: 4]{HRTEM imaging on one core-shell nanowire showing consumed core.}
+\label{fig:ch5ws2tem2}
+\end{figure}
+
+\subsection{TEM-Raman integrated study}
+
+To perform TEM-Raman integrated study, the core-shell specimen was first dispersed into ethanol solution and then dipped onto polydimethylsiloxane (PDMS) support.
+A home-built micromanipulator with proble tip (tungsten, 100nm point radius, Micromaipulator) was used to pick up the core-shell NWs and transfer them onto TEM grids (Lacey C, 300 mesh, Cu, 01895-F Ted Pella, Inc) under 100x objective.
+The steps are visualized in Fig.~\ref{fig:ch5ws2trans}.
+% ws2 transfer
+\begin{figure}[htb]
+\centering
+\includegraphics[width=0.6\textwidth]{ws2trans}
+\caption[Manipulating core-shell NWs]{Core-shell nanowires transfer steps. }
+\label{fig:ch5ws2trans}
+\end{figure}
+
+The transferred NWs were first examined using TEM to identify the \ce{WS2} layers configuration and the associated geometrical orientation.
+Then the core-shell NWs on TEM grids were probed under Raman in a location-resolved manner.
+To perform TEM and Raman analysis on individual NWs, only one NW was placed in each cell on the TEM grid (65 $\times$ 65 $\mu$m).
+And the low magnification TEM images and optical images were compared to map the NW location and orientation.
+The carbon film patterns served as a unique background to resolve possible ambiguity.
+An example is given in Fig.~\ref{fig:ch5ws2map}.
+% ws2 map
+\begin{figure}[htb]
+\centering
+\includegraphics[width=0.6\textwidth]{ws2map}
+\caption[Mapping core-shell NWs]{Core-shell nanowires mapping. }
+\label{fig:ch5ws2map}
+\end{figure}
+
+% fig Raman TEM
+\begin{figure}[htb]
+\centering
+\includegraphics[width=0.7\textwidth]{ws2_tem_ram}
+\caption[TEM-Raman integrated characterization on core-shell NWs]{TEM-Raman integrated results on one core-shell nanowires. (}
+\label{fig:ch5ws2ram}
+\end{figure}
+
+a)-(c) \ce{WS2} layer number variation from bulk to 2L.
+(d) Associated Raman spectra with site1-3 corresponding to HRTEM images (a)-(c), respectively.
+(e) Multi-peak Lorentzian fitting on Raman spectrum site 3 with inset showing layer number dependent intensities ratio of $I_{2LA}/I_{A_{1g}}$ under 532 nm excitation.
+
+\section{summary}
 

### 2014-08-07 BackMatter/paper.tex
tms chapter 80/100

@@
 \section{WO3}
+
+2D wo3.\cite{Kalantar-zadeh2010a} 
+WO3 plasmon \cite{Manthiram2012}
 
@@
 
-2D wo3.\cite{Kalantar-zadeh2010a}
-
 \ce{MoO3} ECD:
@@
 \section{TMS}
+
+\subsection{strain}
+
+$E_{2g}$ mode is strain sensitive.
+
+\citeauthor{Ghorbani-Asl2013} studied the strain in tubular TMDC and found a linear dependence of Raman scattering on strain (3 \si{cm^{-1}} per percentage for $E_{2g}$mode).\cite{Ghorbani-Asl2013}
+
+\citeauthor{Virsek2007} performed a Raman-TEM integrated study on multiwalled \ce{WS2} NT with diameter \textgreater 200 nm.
+The tubes were synthesized using chemical transport method.
+Up-shift of Raman is explained by strain in the walls.
+This shift is not observed in the specimen by sulfurization process of oxides.
+Applied hydrostatic pressure is isotropic,\cite{Staiger2012} while the strain is expected to anisotropic.
+Strain can also be relaxed by chirality.\cite{Virsek2007}
+
+strain effect by first-principles calculations. direct gap is only maintain in a narrow strain range (-1.3 -- 0.3 \%), \cite{Yun2012}.
+
+Semiconducting to metallic transition in \ce{MoS2} at compressive strain of 15\% or tensile strain of 8\%; direct-to-indirect gap transition for 1L \ce{MoS2} at about 2\%. \cite{Scalise2012}
+
+strain and Raman theoretical analysis.\cite{Chang2013a}
+
+magnetic properties of ws2.\cite{Zhang2013j}
+
+growth mechanism of WS2 NT:
+
+It was found that the critical step in this process is the fast conversion of the oxide nanoparticle surface into a closed monolayer of WS2.
+W18O49 as an intermediate phase is observed.
+XRD peaks shift to monitor strain.(002) peak of nanotube shifted to lower angles, the interlayer spacing increase by about 2\% as compared to the bulk powder, likely due to the build-in strain.\cite{ZAK2009}
+$\epsilon = (a - a_0)/a_0$ =(6.4-6.16)/6.16 = 3.8\%. tensile strain ($\epsilon > 0$)
+
+`` Nanotubes not fully converted appeared also during short
+runs with higher working pressure. HRTEM observations
+revealed an amorphous phase inside some of the nanotubes’
+hollow cores, generally near the nanotubes tip (Fig. 5a). The
+amorphous phase occupies only a small fraction of the nanotube’s
+core volume. A meniscus is found to form at the contact
+point between the amorphous matter and the nanotube’s walls.
+Fig. 5b displays such a meniscus in the nanotube core (marked
+by arrows). The presence of this meniscus indicates that this
+amorphous material solidified from a molten phase during the
+cool-down period of the sample. The meniscus of the amorphous
+phase suggest that the amorphous matter wets the
+nanotubes’ walls. Since the WS2 nanotubes are hydrophobic,
+this observation indicates that a monomolecular layer of oxide
+is left on the entire hollow core of the nanotubes. The nanotube
+walls near the contact area with the meniscus are quite defective,
+probably due to the large differences between the thermal
+expansion coefficients of the WS2 and the amorphous matter,
+which induces strain during the cool-down period of the
+reaction product. These observations are consistent with the
+notion that the amorphous material inside the core is an oxide
+phase which is hydrophilic and does not wet the hydrophobic
+WS2 layers''\cite{Margolin2004}
+
+\subsection{others}
 

### 2014-08-07 ch-tms/tms.tex
tms chapter 80/100

@@
 \centering
-\includegraphics[width=0.7\textwidth]{JAP-2column_Fig1.jpg}
+\includegraphics[width=0.6\textwidth]{JAP-2column_Fig1.jpg}
 \caption[W powder oxidation: temperature effect]{SEM graphs of 99.9\% (3N) tungsten powder oxidization at different temperatures of a) 500 \si{\degreeCelsius}, b) 600 \si{\degreeCelsius}, c) 650 \si{\degreeCelsius}, d) 750 \si{\degreeCelsius}, showing the optimal temperature for local formation of nanowires is between 600--650 \si{\degreeCelsius}.
@@
 \centering
-\includegraphics[width=0.7\textwidth]{JAP-2column_Fig3.jpg}
+\includegraphics[width=0.6\textwidth]{JAP-2column_Fig3.jpg}
 \caption[W powder oxidation: size effect]{SEM graphs illustrating the oxidization of four different size of tungsten powders at 600~\si{\degreeCelsius} and 1 sccm oxygen flow.
@@
 \centering
-\includegraphics[width=0.7\textwidth]{JAP-2column_Fig2.jpg}
+\includegraphics[width=0.6\textwidth]{JAP-2column_Fig2.jpg}
 \caption[W powder oxidation: oxygen pressure]{SEM graphs of 3N tungsten powder oxidization at 600 \si{\degreeCelsius} under different rates of oxygen flow: a) 1 sccm, b) 2 sccm, c) 3 sccm, d) 10 sccm.
@@
 \centering
-\includegraphics[width=0.7\textwidth]{wo3_seed_edx}
+\includegraphics[width=0.5\textwidth]{wo3_seed_edx}
 \caption[Composition analysis on seeded growth \ce{WO3} NWs]{EDX spectroscopy on seeded growth \ce{WO3} NWs.}
@@
 \centering
-\includegraphics[width=0.6\textwidth]{ws2trans}
+\includegraphics[width=0.5\textwidth]{ws2trans}
 \caption[Manipulating core-shell NWs]{Core-shell nanowires transfer steps. }
@@
 Then the core-shell NWs on TEM grids were probed under Raman in a location-resolved manner.
+Only those core-shell NWs exhibiting relative smooth \ce{WS2} wall number transition was used in subsequent Raman measurement (wall number and layer number were used interchangeably in this work, but 1 wall is not equal to 1 layer due to the tubular structure).
 To perform TEM and Raman analysis on individual NWs, only one NW was placed in each cell on the TEM grid (65 $\times$ 65 $\mu$m).
@@
 
+Fig.~\ref{fig:ch5ws2ram}a-d depict typical \ce{WO3}-\ce{WS2} NWs used in TEM-Raman integrated study.
+The diameter of these core-shell NWs is around 100 nm and the length around 10 $\mu$m, allowing for up to five distinctive Raman scattering sites.
+Fig.~\ref{fig:ch5ws2ram}e shows the associated Raman spectra acquired on core-shell NWs using 532 nm excitation.
+Two strong peaks were observed between 300 and 450 \si{cm^{-1}}.
+The resonant nature\cite{Stacy1985} of Raman shift is recognized by the broad band at about 350 \si{cm^{-1}}.
+Recent theoretical\cite{Molina-Sanchez2011} and experimental\cite{Staiger2012} studies on 2D and tubular \ce{WS2} agree this band consist of first order mode $E_{2g}^1$ and second order mode $2LA(M)$, although there is still discrepancy on the exact symmetry assignment, \emph{i.e.}, the presence of $E_{2g}^1(M)$ mode.\cite{Berkdemir2013,Peimyoo2013}.
+The other peak at about 420 \si{cm^{-1}} is assigned to $A_{1g}$ mode in both bulk\cite{Sekine1980} and few layer \ce{WS2}.
+Tubular \ce{WS2} structure can be viewed as rolling up the planar \ce{WS2} sheet, and new Raman features arise subsequently, \emph{e.g.}, a shoulder mode emerges on the low frequency side of $A_{1g}$ mode.
+Theoretical investigation suggests assigning this mode as $B_{1u}$, the Davydov doublet of $A_{1g}$ mode.\cite{Ataca2012} And experimental study confirmed this $B_{1u}$ mode arise from structural disorder of \ce{WS2} layers, and the intensity ratio between $B_{1u}$ and $A_{1g}$ strongly depended on excitation wavelength.\cite{Staiger2012} This study observed $B_{1u}$ mode under 532 nm is much less prominent than that of 632 nm, in consistent with previous reports.\cite{Krause2009,Krause2009a}
+
 % fig Raman TEM
@@
 \includegraphics[width=0.7\textwidth]{ws2_tem_ram}
-\caption[TEM-Raman integrated characterization on core-shell NWs]{TEM-Raman integrated results on one core-shell nanowires. (}
+\caption[TEM-Raman integrated characterization on core-shell NWs]{(a)-(d) HRTEM images on several NWs showing the \ce{WS2} wall number variation from one to about ten.
+(e) Raman spectra acquired from core-shell NWs supported on TEM grids, indicating a sharp contrast between the in-plane and out-of-plane vibrations.
+Notice that the Raman spectra primarily arise from the outer \ce{WS2} shell, and only weak Raman shift at about 800 \si{cm^{-1}} were observed at some bare core region (not shown here).
+(f) Layer number dependence on averaged intensity ratio between the in-plane and out-of-plane Raman bands.
+}
 \label{fig:ch5ws2ram}
@@
 
-a)-(c) \ce{WS2} layer number variation from bulk to 2L.
-(d) Associated Raman spectra with site1-3 corresponding to HRTEM images (a)-(c), respectively.
-(e) Multi-peak Lorentzian fitting on Raman spectrum site 3 with inset showing layer number dependent intensities ratio of $I_{2LA}/I_{A_{1g}}$ under 532 nm excitation.
+Multi-peak Lorentzian fitting was also attempted on spectra shown in Fig.~\ref{fig:ch5ws2ram}e.
+Similar trend was found between the apparent peak ratio and the de-convolution value, as shown in Fig.~\ref{fig:ch5ws2pr}.
+For a qualitative purpose, the overall intensity ratio $I_{E/A}$ between in-plane E band ($E_{2g}^1+2LA$) and out-of-plane A band ($A_{1g}+B_{1u}$) is sufficient.
+This value is then extracted to correlate with layer number variation.
+Multiple Raman spectra for each layer were averaged, as shown in Fig.~\ref{fig:ch5ws2ram}f.
+
+% fig Raman TEM
+\begin{figure}[htb]
+\centering
+\includegraphics[width=0.4\textwidth]{ws2_peak_ratio}
+\caption[Multi-peak Lorentzian fitting on core-shell NWs]{Comparison of apparent peak ratio and de-convolution value.}
+\label{fig:ch5ws2pr}
+\end{figure}
+
+The intensity ratio $I_{E/A}$ decreases monotonically with the increase of \ce{WS2} wall number, a similar trend as observed on 2D few layer \ce{WS2}.
+The exact value of $I_{E/A}$ shows modest difference with 2D sheet, which is attributed to the suspended configuration of current core-shell NWs specimen and the presence of \ce{WO3} core.
+It has been demonstrated that the optical interference from dielectric environment significantly modified the Raman scattering of layered MoS2, regardless lattice vibration modes.\cite{Li2012} The author calculated the reflectivity of three different stacking scenarios to estimate the influence of \ce{WO3} and insulating substrate, as shown in.
+It can be concluded that under 532 nm excitation, the \ce{WO3} core shows little influence on the Raman intensity when \ce{WS2} tube is suspended in air, whereas the \ce{SiO2}/Si substrates will dramatically enhance the Raman scattering of the core-shell NWs.
+It could be further predicted that current Raman spectra on core-shell NWs can be used to estimate the \ce{WS2} nanotube wall numbers.
 
@@
 
-growth mechanism of WS2 NT\cite{ZAK2009} 
-It was found that the critical step in this process is the fast conversion of the oxide nanoparticle surface into a closed monolayer of WS2.
-W18O49 as an intermediate phase is observed.
-XRD peaks shift to monitor strain.
-
 inorganic nanotubes review \cite{Tenne2004} , unsaturated bonds number increases as the size of MS2 sheet decreases.

### 2014-08-08 ch-wox/part1.tex
before final branch
intro of wo3 modified

@@
 Tungsten oxide (\ce{WO_x}) is an important functional materials with distinctive properties and technology applications.
-Intense research interest was rekindled by the discovery of \gls{ec} effect in \citeyear{Granqvist1993}.\cite{Granqvist1993}  Nano-engineering \ce{WO_x} bring more possibility and flexibility to its already rich characteristics, therefore resulting research efforts spanning multiple fields of scientific community.
+Intense research interest was rekindled by the discovery of \gls{ec} effect in \citeyear{Granqvist1993}.\cite{Granqvist1993}  Nano-engineering \ce{WO_x} bring more possibility and flexibility to its already rich characteristics, therefore resulting in research efforts spanning multiple fields of scientific community.
 Besides smart window based on EC effect, \ce{WO_x} is also well investigated for several other significant applications: photoelectrochemical cell for solar energy conversion and storage, photocatalysis for hydrogen evolution reaction, chemical and biological sensing based on gasochromic effect.
@@
 
-In this chapter, we will first review the literature to date for both \ce{WO_x} and \ce{Na_xWO3}, then divide the summaries into a) technological application, b) crystal structure and electronic properties and c) synthesis approaches.
-Then we present our growth methods and results.
-And we conclude with a brief summary.
+In this chapter, a literature review on \ce{WO_x} and \ce{Na_xWO3} will be given first, with focus on technological application, crystal structure and electronic properties and synthesis approaches.
+Then the growth methods in this study are presented, followed by corresponding characterization and discussion.
+This chanpter is concluded with a brief summary.
 
@@
 
-In the past decades, tons of works have been devoted to understanding the chromogenic phenomena in \ce{WO3}. We highlight several key results as reviewed by ,
+In the past decades, tons of works have been devoted to understanding the chromogenic phenomena in \ce{WO3}. Several key results were highlighted as reviewed in Ref.\cite{Deb2008},
 \begin{itemize}
-    \item coloration and bleaching can also be stimulated by other routes, such as by UV irradiation, thermal treating, heating in vacuum, reducing atmosphere etc
-    \item no electrical coloration occurs in vacuum, but other routes still works
+    \item coloration and bleaching can also be stimulated by other routes, such as by UV irradiation, thermal treating, heating in vacuum, reducing atmosphere, \emph{etc}
+    \item no electrical coloration occurs in vacuum, but other routes still work
     \item coloration is associated with a proportional increase in conductivity
-    \item coloration spectrum is essentially similar in all cases except small variation in peak position and FWHM
-    \item coloration is structure sensitive and most efficient in amorphous films
+    \item coloration spectrum is essentially similar in all cases except small variation in peak position
+    \item coloration is structural sensitive and most efficient in amorphous films
 \end{itemize}
 
-Sofar there is no unifying model that could reconcile these contradictory experimental observations.
+So far there is no unifying model that could reconcile these contradictory experimental observations.
 Among all the developed models, polaronic absorption is the most widely accepted mechanism for coloration.
-In polaron model\footnote{When a free electron travels through a polar solid, it creates a local lattice displacement (longitudinal optical phonon clouds) due to the coulombic interaction with neighboring ions.
-This local distortion and the electron together is equivalent to a new elementary exciton of the crystal, and is named as polaron}, the intercalation of \ce{M^+} (M = H, \ce{Li}, or Na) ions into \ce{WO3} films is accompanied with the formation of small polarons ($r_p$ comparable to unit cell size) and formal reduction of some \ce{W^{6+}} sites to \ce{W^{5+}}, as depicted in Eq.~\ref{eq:ec}.
+In polaron model,\footnote{When a free electron travels through a polar solid, it creates a local lattice displacement (longitudinal optical phonon clouds) due to the coulombic interaction with neighboring ions.
+This local distortion and the electron together is equivalent to a new elementary exciton of the crystal, and is named as polaron} the intercalation of \ce{M^+} (M = H, \ce{Li}, or Na) ions into \ce{WO3} films is accompanied with the formation of small polarons ($r_p$ comparable to unit cell size) and formal reduction of some \ce{W^{6+}} sites to \ce{W^{5+}}, as depicted in Eq.~\ref{eq:ec}.
 During the intercalation process, the \ce{M^+} ions enter into these vacant sites.\cite{Hepel2008} Coloration occurs when the polaron band .
@@
 \begin{align}\label{eq:ec}
-x\ce{M+} + x\ce{e-} +  \ce{$\alpha \hyphen$WO$_{3-y}$}= \ce{$\alpha \hyphen$M$_x$WO$_{3-y}$},
+x\ce{M+} + x\ce{e-} +  \ce{$\alpha \hyphen$WO$_{3-y}$}-> \ce{$\alpha \hyphen$M$_x$WO$_{3-y}$},
 \end{align}
@@
 This defect level is expected to be inside or near the valence band.
-When one electron is removed from this level, $V_O^0$ is converted to $V_O^+$.The positively charged vacancy exerts coulombic repulsion to the nearest W-ions, which results in a displacement of the neighboring W-ions and an upward shift of the defect level into the bandgap, thereby creating a color center.
+When one electron is removed from this level, $V_O^0$ is converted to $V_O^+$.
+The positively charged vacancy exerts coulombic repulsion to the nearest W-ions, which results in a displacement of the neighboring W-ions and an upward shift of the defect level into the bandgap, thereby creating a color center.
 The optical transition from $V_O^+$ to $V_O^{2+}$ (a state within the conduction band)
@@
 
-So the polaron and color center models both agree on that \ce{W^{5+}} and its transition is responsible for the coloration, but disagree on how this \ce{W^{5+}} state is created (foreign ion reduction in polaron model and oxygen vacancy in color center model) and the corresponding energy levels.
+So the polaron and color center models both agree on that \ce{W^{5+}} and its transition is responsible for the coloration, but disagree on how this \ce{W^{5+}} state and the corresponding energy levels are created (foreign ion reduction in polaron model and oxygen vacancy in color center model).
 A modified polaron model is proposed to include \ce{W^{4+}} states in host lattice.
@@
 Two models, double injection and color center, arise to account for the coloration upon exposure to certain gases.
-Both consents to Eq.~\ref{eq:cl_bl1}.
+Both consent to Eq.~\ref{eq:cl_bl1}.
 But there is a disagreement on the final states.
@@
 Therefore the exact mechanism in \ce{WO_x} still requires further investigation.
-The author believes the resolution to a large extent depends on the phase transitions, as discussed in Section.~\ref{sec:wonawo}.
-
-photocatalytic applications in solar hydrogen generation and organic pollutant degradation.
-
-photocatalyst\cite{Macphee2010}, photoelectrochemical energy application \cite{Su2010}
+The author believe the resolution to a large extent depends on the phase transitions, as discussed in Section.~\ref{sec:wonawo}.
 
@@
 \ce{OH.}) which enable further reactions.
-For water splitting using solar energy, the band gap should be within $2.0 \sim 3.0 $ eV, and CB edge should be more negative than reduction potential of \ce{H^+/H2}, whereas the VB top should be more positive than the oxidation potential of \ce{H2O/O2)}.\cite{Wang2012} The valence band holes (\ce{h^+}) oxidize water to oxygen and conduction band electrons propel hydrogen generation, as depicted in Eq.~\ref{eq:hervb} and \ref{eq:hercb}.
+For water splitting using solar energy, the band gap should be within $2.0 \sim 3.0 $ eV, and CB edge should be more negative than reduction potential of \ce{H^+/H2}, whereas the VB top should be more positive than the oxidation potential of \ce{H2O}/\ce{O2}.\cite{Wang2012} The valence band holes (\ce{h^+}) oxidize water to oxygen and conduction band electrons propel hydrogen generation, as depicted in Eq.~\ref{eq:hervb} and \ref{eq:hercb}.
 
@@
 
-As shown in Fig.~\ref{fig:woxnhe}, \ce{WO3} has CB edge positioned slightly more positive than reduction potential of \ce{H^+/H2}(versus \gls{nhe}), and VB edge much more positive than the oxidation potential of \ce{H2O/O2}.
+As shown in Fig.~\ref{fig:woxnhe}, \ce{WO3} has \gls{cb} edge positioned slightly more positive than reduction potential of \ce{H^+/H2}(versus \gls{nhe}), and \gls{vb} edge much more positive than the oxidation potential of \ce{H2O/O2}.
 So the photo-cleavage of water cannot be accomplished by \ce{WO3} alone.
@@
 
-the ubiquity of \ce{WO6} octahedra is essential for not only the optical properties but the ability to insert and extract ions in the EC oxides, due to the tunnels in three dimensions serving as path for transport of small ions.
-The intercalation of hydrogen or alkali ions into \ce{WO3} created electron donor level.
-By absorbing the red part of incident spectrum, electrons at donor level make transition to the conduction band, causing the blue coloration in \ce{H_xWO3}.
-
-\citeauthor{Wang2009a} mentioned that amorphous \ce{WO3} can only be used in lithium-based electrolytes due to its
-in-compact structure and high dissolution rate in acidic electrolyte solutions.
-Electrochromic materials that can endure acidic electrolytes without degradation should be developed.
-Crystalline \ce{WO3} nanostructures with their much denser structures and small particle sizes are promising to be used as suitable electrochromic material in acidic electrolytes.
-
-Characterization of ECD (work like a thin-film batteries) includes transmission measurement and associated EC calculation, charge-discharge time, current-time curve and the fitting of obtained data.
-
-The coloration efficiency (CE) represents the change in the optical density (OD) per unit charge density ($Q/A$, in units of \si{\cm^2\per\coulomb}) during switching and can be calculated according to the formula:
-\begin{equation}
-CE = \frac{\Delta~OD}{(Q/A)} [cm^2/C],
-\end{equation}
-where OD = $log(T_{bleach}/T_{color})$. The EC and optical density depend on the wavelength and are usually higher in the near IR than in the visible region.
-Using Ohm's law($U_s = IR = RQ/t_s$) with switch voltage $U_s$, resistance R and surface area A, switching time $t_s$ could be estimated as
-\begin{equation}
-t_s = \Delta~OD\cdot A \cdot R /(CE\cdot U_s).
-\end{equation}
-
-its one dimensional (1D) nanostructure has attained intensive research efforts in recent years due to the potential applications in advanced nano-electric and nano-optoelectronic devices.
-
-\begin{quote}
-a viable electrochromic smart window must exhibit a cycling life time \textgreater $10^5$ cycles, corresponding to an operation life at 10 - 20 years.
-\end{quote}
-
 \subsection{Crystal structures and properties of tungsten oxides and sodium tungsten oxides}\label{sec:wonawo}
 
-\textbf{\ce{WO3}} Tungsten trioxides crystalize in multiple phases.
+Tungsten trioxide (\ce{WO3}) crystallizes in multiple phases.
 The basic building block is \ce{WO6} octahedra.\footnote{Tungsten, with its electronic configuration as \ce{(Xe)4f^{14}5d^{4}6s^{2}}, has empty 5d and 6s orbitals in its +6 oxidation state.} \ce{WO3} crystal structure consists of \ce{WO6} octahedra joined at their corners, which may be considered as a perovskite structure of \ce{CaTiO3} with all \ce{Ca^{2+}} sites vacant.
-A representative lattice structures is illustrated in Fig.~\ref{fig:wo3oct}.
-These distorted \ce{WO6} octahedra adapts different tilting angles in different phases and edge-sharing octahedra also arises.
-The temperature-dependent phase transition and corresponding lattice constants in bulk form is summarized in Table.~\ref{tab:wo3phase}.\cite{Zheng2011} And a firm assignation of space group to monoclinic phases are still in debate.\cite{Chatten2005} It is noticed that the lattice parameters obtained via \emph{ab initio} calculation closely match the experimental values.\cite{Migas2010a} The phase transition scenarios in nanostructured \ce{WO3} are supposed to be much more sophisticated.
+A representative lattice structure is illustrated in Fig.~\ref{fig:wo3oct}.
+These distorted \ce{WO6} octahedra adapt different tilting angles in different phases and edge-sharing octahedra also arise.
+The temperature-dependent phase transition and corresponding lattice constants in bulk form is summarized in Table.~\ref{tab:wo3phase}.\cite{Zheng2011} And a firm assignation of space group to monoclinic phases are still in debate.\cite{Chatten2005} It is noticed that the lattice parameters obtained via \emph{ab initio} calculation closely match the experimental values.\cite{Migas2010a} The phase transition scenarios in nanostructured \ce{WO3} are supposed to be more sophisticated.
 Within Gibbs-Thomson frame work, one can generally expect lower transition temperature than their bulk counterparts due to enhanced surface energy.
@@
 \centering
-\caption{\ce{WO3} phases}\label{tab:wo3phase}
+\caption{List of \ce{WO3} phases}\label{tab:wo3phase}
 \begin{tabular}{lccccc}
@@
 
- \citeauthor{Chatten2005} also studied the oxygen vacancy in different phases of \ce{WO3}.\cite{Chatten2005}
-
-Nonstoichiometric tungsten oxides \ce{WO_x} (i.e. \ce{WO_{2.92}}, \ce{WO_{2.87}}) are known as Magn$\acute{e}$li phases.
-
-We do not discuss tungsten oxide hydrates (\ce{WO3.nH2O}) in this work since the product of thermal CVD approach is not plagued with this complexity.
-It's necessary, however, to deal with hydrated \ce{WO3} in the liquid synthesis routes, as indicated in Section.~\ref{sec:woxgrowth}.
-
-Theoretical computation of electronic band structures for \ce{WO_x} proves difficult due to the aforementioned phase transition.
-
- oxygen deficiency, structure change, electronic properties vary according.
-
 % band gap table
@@
 \toprule
-Phase & Experimental (eV) & Theory (eV) & Remarks  \\
+Phase & Experimental (eV) & Theory (eV) &  \\
 \midrule
@@
 tetragonal bulk \ce{WO3} &     & 0.66 \cite{Migas2010a}&    \\
-nano-\ce{WO3} & 2.6$\sim$3.2  & NA &    \\
-nano-\ce{WO_{3-x}} & NA  & NA &    \\
 \bottomrule
@@
 
-Tungsten bronzes was coined by Wohler in 1837.\cite{Deb2008} \ce{Na_{x}WO3}
-
 \subsection{Synthesis strategies}\label{sec:woxgrowth}
 
-We will first give a brief review on the synthesis of \ce{WO3}.
 As the chemical formula suggested, the most straightforward way is heating metallic tungsten in various forms (i.e.
 powders,\cite{Zhou2005a,Cao2009,Hsieh2010} foils and wires).
-Actually \ce{WO_x}\footnote{$x$ is between 2 and 3.} NWs was observed when directly heating W wires.\cite{Gu2002a} Due to the extreme high melting point of W, it requires very high temperature (say, above 1100 \si{\degreeCelsius}) to produce large amount of growth species.
+Actually \ce{WO_x} \glspl{nw}\footnote{$x$ is between 2 and 3} were observed when directly heating W wires.\cite{Gu2002a} Due to the extreme high melting point of W, it requires very high temperature (say, above 1100 \si{\degreeCelsius}) to produce large amount of growth species.
 Therefore scalable growth seems difficult.
@@
 Tungsten oxides powder can also been used as precursor to prepare \ce{WO_{x}} \glspl{nw}.\cite{Huang2008a,Wang2009} Hydrogen-containing agents (i.e.
-water, \ce{H2},or methane\cite{Klinke2005}) were often involved into the reaction.\cite{Baek2007,Karuppanan2007} The potential benefit is \ce{WO3} has a much lower melting point ($\approx 1470$\si{\degreeCelsius}) than that of W.
+water, \ce{H2}, or methane\cite{Klinke2005}) were often involved into the reaction.\cite{Baek2007,Karuppanan2007} The potential benefit is \ce{WO3} has a much lower melting point ($\approx 1470$ \si{\degreeCelsius}) than that of W.
 
-Direct oxidation and \ce{WO3} conversion could be grouped as addition approach. In contrast, decomposition method is also feasible.
-\citeauthor{Pol2005} obtained \ce{W18O49} nanorods by thermal dissociation of \ce{WO(OMe)4} at 700 \si{\degreeCelsius}, and \ce{WO3} by the annealing at 500 \si{\degreeCelsius} at air atmosphere.\cite{Pol2005}
+Direct oxidation and \ce{WO3} conversion could be grouped as addition approach.
+In contrast, decomposition method is also feasible.
+\citeauthor{Pol2005} obtained \ce{W18O49} nanorods by thermal dissociation of \ce{WO(OMe)4} at 700 \si{\degreeCelsius}, and \ce{WO3} by further annealing at 500 \si{\degreeCelsius} in air atmosphere.\cite{Pol2005}
 
-Spray pyrolysis is a typical aerosol-assisted CVD technique.
+Spray pyrolysis is a typical aerosol-assisted \gls{cvd} technique.
 Typical process flow is: the precursor solution is pumped to an atomizer, and then sprayed through the carrier gas as a fine mist of very small droplets onto heated substrates.
-Subsequently the droplets undergo evaporation, solute condensation, and thermal decomposition, which then result in film formation.\cite{Zheng2011}
+Subsequently the droplets undergo evaporation, solute condensation, and thermal decomposition, which then result in film formation.\cite{Zheng2011} Main reactions include:
+\begin{align}
+\cee{W + O2 &\rightarrow WO_{3-x}\\
+W + H2O &\rightarrow  W_{3-x} + H2}
+\end{align}
 
-Main reactions include: \cee{W + O2 -> WO_{3-x}} \cee{W + H2O -> W_{3-x} + H2}
-
-the energetic sources are ion bombardment, electron beam, laser ablation, and combustion flame\cite{Rao2011}.
-
-The sol–gel process is a well-known, intensively studied wetchemical technique that is widely used in materials synthesis.
-This method generally starts with a precursor solution (the ``sol") to form discrete particles or a networked gel structure.
-During the course of gelation (aging process), various forms of hydrolysis and polycondensation take place.
-
-Hydrothermal method has been an important route to synthesize a diversity of nanomaterials (i.e.
-).
+Hydrothermal method has been an important route to synthesize a diversity of nanomaterials.
 Preparation of \ce{WO_{3-x}} has also been demonstrated hydrothermally.\cite{Lee2003,Gu2007} Usually, the precursor (\ce{H2WO4}) is mixed with other reactants (sulfides or certain organic acid) in solution and pH value is adjusted as another control degree of freedom.
@@
 Finally the product is separated from the solution and dried, layered \ce{WO3.nH2O} flakes are usual products.
-
-In addition, doped \ce{WO3} was also demonstrated
-
- The composition and phase of final product highly depend on the synthesis conditions.
 

### 2014-08-08 BackMatter/paper.tex
minor changes in supp tex files

@@
 \section{WO3}
+
+The energetic sources are ion bombardment, electron beam, laser ablation, and combustion flame\cite{Rao2011}.
+
+The sol–gel process is a well-known, intensively studied wetchemical technique that is widely used in materials synthesis.
+This method generally starts with a precursor solution (the ``sol") to form discrete particles or a networked gel structure.
+During the course of gelation (aging process), various forms of hydrolysis and polycondensation take place.
+In addition, doped \ce{WO3} was also demonstrated
+
+ The composition and phase of final product highly depend on the synthesis conditions.
+
+Tungsten bronzes was coined by Wohler in 1837.\cite{Deb2008} \ce{Na_{x}WO3}
+
+\citeauthor{Chatten2005} also studied the oxygen vacancy in different phases of \ce{WO3}.\cite{Chatten2005}
+
+Nonstoichiometric tungsten oxides \ce{WO_x} (i.e. \ce{WO_{2.92}}, \ce{WO_{2.87}}) are known as Magn$\acute{e}$li phases.
+
+We do not discuss tungsten oxide hydrates (\ce{WO3.nH2O}) in this work since the product of thermal CVD approach is not plagued with this complexity.
+It's necessary, however, to deal with hydrated \ce{WO3} in the liquid synthesis routes, as indicated in Section.~\ref{sec:woxgrowth}.
+
+Theoretical computation of electronic band structures for \ce{WO_x} proves difficult due to the aforementioned phase transition.
+oxygen deficiency, structure change, electronic properties vary according.
+
+the ubiquity of \ce{WO6} octahedra is essential for not only the optical properties but the ability to insert and extract ions in the EC oxides, due to the tunnels in three dimensions serving as path for transport of small ions.
+The intercalation of hydrogen or alkali ions into \ce{WO3} created electron donor level.
+By absorbing the red part of incident spectrum, electrons at donor level make transition to the conduction band, causing the blue coloration in \ce{H_xWO3}.
+
+\citeauthor{Wang2009a} mentioned that amorphous \ce{WO3} can only be used in lithium-based electrolytes due to its
+in-compact structure and high dissolution rate in acidic electrolyte solutions.
+Electrochromic materials that can endure acidic electrolytes without degradation should be developed.
+Crystalline \ce{WO3} nanostructures with their much denser structures and small particle sizes are promising to be used as suitable electrochromic material in acidic electrolytes.
+
+Characterization of ECD (work like a thin-film batteries) includes transmission measurement and associated EC calculation, charge-discharge time, current-time curve and the fitting of obtained data.
+
+The coloration efficiency (CE) represents the change in the optical density (OD) per unit charge density ($Q/A$, in units of \si{\cm^2\per\coulomb}) during switching and can be calculated according to the formula:
+\begin{equation}
+CE = \frac{\Delta~OD}{(Q/A)} [cm^2/C],
+\end{equation}
+where OD = $log(T_{bleach}/T_{color})$. The EC and optical density depend on the wavelength and are usually higher in the near IR than in the visible region.
+Using Ohm's law($U_s = IR = RQ/t_s$) with switch voltage $U_s$, resistance R and surface area A, switching time $t_s$ could be estimated as
+\begin{equation}
+t_s = \Delta~OD\cdot A \cdot R /(CE\cdot U_s).
+\end{equation}
+
+its one dimensional (1D) nanostructure has attained intensive research efforts in recent years due to the potential applications in advanced nano-electric and nano-optoelectronic devices.
+
+\begin{quote}
+a viable electrochromic smart window must exhibit a cycling life time \textgreater $10^5$ cycles, corresponding to an operation life at 10 - 20 years.
+\end{quote}
+
+photocatalytic applications in solar hydrogen generation and organic pollutant degradation.
+
+photocatalyst\cite{Macphee2010}, photoelectrochemical energy application \cite{Su2010}
 

### 2014-08-08 ch-wox/ch-wox.tex
minor changes in supp tex files

@@
 
-Tungsten powders were used as source in this work.
-We used four kinds of W powder in total, as summarized in Table.~\ref{tab:powder}.
-Three growth configurations were explored, namely ordinary transport (OT), seeded growth (SG) and flow growth (FG).
+Tungsten powders were utilized as source materials in this work.
+Four kinds of W powder were used in total, as summarized in Table.~\ref{tab:powder}.
+Two growth configurations were explored, namely ordinary transport (OT) and seeded growth (SG).
 % Tungsten powders size and purity
-\begin{table}[htb]
 \centering

### 2014-08-09 ch-tms/tms.tex
tms split, intro proofreading done 85/100

@@
 
-The remaining section is arranged in following order: A review on the growth of \ce{MS2} (M = Mo, W)nanotubes (NTs) and 2D few layer (FL) structures will be introduced first.
-And Raman spectroscopy results on NTs and FL are summarized.
+The remaining section is arranged in following order: a review on the growth of \ce{MS2} (M = Mo, W) nanotubes (NTs) and 2D few layer (FL) structures will be introduced first, followed by Raman spectroscopy summary on NTs and FL.
 The thesis will then focus on synthesis of \ce{WO3}-\ce{WS2} heterostructure and various characterizations, including both ensemble averaged and on individual nanowires.
+This chapter is concluded with a brief summary and future work.
 
-\section{Introduction}
-
-\subsection{Growth of TMDC}
-Shortly after the the discovery of carbon nanotube (CNT) in 1991,\cite{Iijima1991} its transition metal dichalcogenides (TMDC) counterparts (\ce{WS2}) was synthesized in 1992.\cite{Tenne1992} In the following decade, other TMDC and several metal oxides nanotubes were demonstrated as well.
-\citeauthor{Rao2003} did an excellent work to review these inorganic nanotubes.\cite{Rao2003} Here we just recapitulate the main categories of synthesis methods.
-\begin{enumerate}
-\item Reducing \ce{MO3} in \ce{H2} and \ce{H2S} atmosphere\footnote{M = Mo, W in this work}
-\item Direct decomposition of \ce{MS3}
-\item Decomposition of the ammonium salt \ce{(NH4)2MS4}
-\item Using CNT as templates, arc discharge, or laser ablation
-\end{enumerate}
-
-Except the aforementioned methods, another important reaction in CVD domain is
-\begin{equation}\label{eq:mclns}
-\cee{MoCl5(WCl6) + S \rightarrow MoS2(WS2) + S2Cl2}.
-\end{equation}
-This reaction has been explored by several authors,\cite{Stoffels1999} and could be used under atmospheric pressure.\cite{Li2004a}
-
-All these methods can be applied to the growth of TMDC few layer structures, either directly or with some modification, as we shall discuss later.
-Among all the members of TMDC nanotubes, \ce{WS2} and \ce{MoS2} NTs are probably the most well investigated.\cite{Homyonfer1997,Tenne1998,Frey1998,Frey1999,Rothschild2000,Zak2000} The reaction mechanism of \ce{WO3} with \ce{H2}/\ce{H2S} has been thoroughly studied \cite{Feldman1998} and high yield synthesis approach has been established.\cite{Margolin2004} For precursor of \ce{WO3} NPs, it was found that the simultaneous reduction and sulfurization is essential for encapsulation of fullerene like \ce{WS2} structures from the oxide nanoparticles.
-During the surfurization process, remaining oxide core is gradually reduced and transformed into an ordered superlattice of $\{ 001 \}$ CS planes.
-Further reaction will consume up the \ce{WO_x} core, leaving multi-walled \ce{WS2} NTs only.
-For precursor of \ce{WO3} nanowires, \citeauthor{Feldman1996} proposed that TMDC nanotubes growth began with the reduced \ce{WO3} phases, in particular \ce{W_{18}O_{49}}.\cite{Feldman1996} It is worth noting that \ce{MS2} can be prepared by direct sulfurization from its oxides phase, but reaction \cee{MO3 + Se \rightarrow MSe2} will not proceed unless introducing other reducing agents, such as \ce{H2}.\cite{Tsirlina1998} This fact highlights that sulfur is rather radical at elevated temperature.
-
-\citeauthor{Zhu2000} performed a detailed morphological and structural analysis on \ce{WS2} NT synthesized using \ce{WO_{3-x}} NWs and \ce{H2S}.\cite{Zhu2000} Sulfur vacancy was found on the outer wall of NT.
-The tips exhibits various structures.
-Open-ended can be observed, more frequently than that in carbon nanotubes (CNTs), which is often sealed.
-\citeauthor{Zhu2000} suggested this open-ended tubes resulted from continuous growth on other nanotubes.
-And the closure configuration is rather complicated.
-Flat caps often dominates.
-\citeauthor{Zhu2000} maintained that this oxide-to-sulfides mechanism might apply to closed caps only, not to those open ended tubes.\cite{Zhu2000} TEM diffraction analysis could distinguish the chirality of NTs, as demonstrated by CNT \cite{Zhang1993} and \ce{MoS2}\cite{MARGULIS1996}.
-\ce{WS2} NT chirality revealed by TEM SAED show armchair NTs dominates.
-\citeauthor{Sloan1999} investigated tungsten oxides structures incorporated in \ce{WS2}.\cite{Sloan1999} The encapsulated \ce{WO_x} cores often exhibit \ce{W3O8} and \ce{W5O_{14}} phases, both of which belong to the \ce{W_nO_{3n-1}} homogenous series, arising as a result of crystallographic shearing (CS) planes.\cite{Miyano} Some \ce{WO_x} cores show oxygen vacancy instead of CS planes, leading to prominent streaking in SAED patterns.
-Although high yield growth method of \ce{WS2} has been available, the extent to which one can control the NT configuration is still limited, i.e., single-walled NT has not been routinely synthesized and the electronic properties can only be predicted theoretically.
-\citeauthor{Seifert2000} investigated the electronic structures of \ce{WS2} nanotube using DFT calculation.\cite{Seifert2000} It was found zigzag (n,0) NTs exhibts a direct gap at $\Gamma$ point, whose size increase monotonically with tube diameter, while armchair (n,n) NTs, unlike its metallic counterpart of (n,n) CNT, show indirect band gap increasing with tube diameter.
-\citeauthor{Zibouche2012} reached the same conclusion on \ce{WS2} SWNT.\cite{Zibouche2012} It was also found band gaps of armchair and zigzag NTs increase with diameter, going from values close to bulk and approaching that of  monolayer, and for a given tube diameter, $E_g$ of zigzag NTs are larger than those of armchair NTs.
-This difference presumably vanishes when nanotube diameter exceeds 100 nm.
-
-Parallel with the scenario of CNT and graphene, TMDC few layer structures attracts intensive research efforts recently.
-These unfolded TMDC nanotubes exhibit many appealing features, i.e., indirect-to-direct band gap transition,\cite{Splendiani2010} valley electronics, and become a promising candidate in energy harvesting, optoelectronics and photocatalytic activity.
-For scientific research purpose, exfoliation by liquid \cite{Smith2011} or mechanical methods \cite{Lee2010a} can provide sufficient materials.
-Yet considering the integration into current microelectronic process, CVD synthesis of TMDC FL is highly desired, which stills hold the greatest potential for high yield production of \ce{MS2}.
-So in this work we focus on the CVD-based methods.
-We will review literatures to date on both \ce{WS2} films and few layer structures, and highlight several typical investigations using different type synthesis method, as summarized in Table~\ref{tab:tmsgrowth}.
-We stress that the synthesis of NTs is relevantly independent of substrates, which is in sharp contrast to the scenario of few layer growth.
-The \ce{WS2} nucleation and interaction with substrates play dominant roles in the growth of FL structures.
-This lead us to focus on the \ce{WS2} films growth, which presumably could provide valuable insight into the nucleation process on various substrates.
-
-\textbf{\ce{MS2} films} \citeauthor{Lee1994} studied the CVD of \ce{MoS2} by \ce{MoCl5} or \ce{MoF6} and \ce{H2S} in great details.
-Phase diagrams for \ce{Mo-S-Cl-H} and \ce{Mo-S-F-H} system at 1 kPa were simulated.
-\citeauthor{Endler1999} also investigated the solid-phase diagram for \ce{Mo-S-Cl-H-Ar} system.\cite{Endler1999} It was found pure \ce{MoS2} was main product when molar ratio of \ce{H2S}-\ce{MoCl5} exceeds 2.
-More important, \ce{MoS2} basal plane orientation can be parallel to substrate when the thickness was smaller than 50 nm.
-\cite{Ennaoui1995a} grew tungsten disulfides film using sulfurization of \ce{WO3} under \ce{N2}/\ce{H2} gas flow.
-The composition was found to be \ce{WS_{2.13}}, and the excess of sulfur lead to p-type conductivity.
-XRD peaks ratio is used as a measure of film orientation, which was found higher for film prepared without an intermediate Ni coating.
-\ce{Ni3S2} phase was found and surfactant-mediated epitaxy is proposed.
-\citeauthor{Regula1997} studied the Ni-W-S phase diagram and the role of Ni layer in promoting \ce{WS2} film growth from amorphous \ce{WS3}.\cite{Regula1997} \emph{In-situ} TEM analysis confirmed the formation of \ce{NiS_x} droplets and lateral growth of \ce{WS2} from these droplets.\cite{Regula1998} Recently, it has been shown that direct sulfurization of W coating (20nm) at 750 \si{\degreeCelsius} on \ce{SiO2}-Si can also produce \ce{WS2} film.\cite{Shanmugam2012a} However, the film is of bulk in nature.
-This could be explained by the study of \citeauthor{Genut1992} towards \ce{WS2} growth on various substrates.\cite{Genut1992} We summarize the main results in Table~\ref{tab:ws2subs}.
-It was found that the \ce{WS2} nucleate from an amorphous \ce{WS3} phase and the substrate has a critical role in determining both the reaction onset temperature and the texture.
-The adhesion of tungsten to quartz was found to be much stronger than to glass.
-And oxygen-containing species such as \ce{H2O} or OH tend to cause \ce{WS2} basal plane perpendicular to substrate.
-% WS2 films
-\begin{table}[htb]
-\centering
-\caption{\ce{WS2} growth on different substrates}\label{tab:ws2subs}
-\begin{tabular}{lcp{1in}p{2in}}
-\toprule
-precursor                 & substrate &  conditions & film feature\textsuperscript{\emph{a}}  \\
-\midrule
-sputtered W + \ce{H2S}   & glass      & onset 400 \si{\degreeCelsius} & $\perp c$ at 500 \si{\degreeCelsius}, metastable \ce{WS3} found\\
-                          & quartz      & onset 650 \si{\degreeCelsius} & $\parallel c$ below 950 \si{\degreeCelsius}\\
-                          & Mo        & onset NA          & $\parallel c$ at 1000 \si{\degreeCelsius}\\
-                          & W          & onset NA           & random orientation\\
-\midrule
-\ce{WO_x} + \ce{H2S}    & quartz      & onset 500 \si{\degreeCelsius} & predominantly $\perp c$ after 800 \si{\degreeCelsius}\\
-                        & Mo        & onset NA          & $\parallel c$ dominant\\
-                        & W       & onset NA          & random orientation\\
-\bottomrule
-\end{tabular}
-
-\textsuperscript{\emph{a}} $\perp c$: the c axis is perpendicular to the substrate, $\parallel c$: the c axis is parallel to the substrate;
-
-\end{table}
-
-\textbf{\ce{MS2} FL} For \ce{MoS2}, the reaction mechanism of \ce{MoO3} to \ce{MoS2} was studied by \citeauthor{Weber1996}.\cite{Weber1996} This study provided guidelines for the recent syntheses of \ce{MoS2} by sulfurization of \ce{MoO3}.\cite{Lin2012,Lee2012b,Liu2012a,Najmaei2013} Similar studies on sulfurization of \ce{WO3.H2O} to \ce{WS2} and decomposition of \ce{(NH4)2WO2S2} were also reported.\cite{VanderVlies2002,VanderVlies2002a} In combination with the knowledge from \ce{WS2}, we compare those insight with several recent reports on \ce{WS2} FL.
-\citeauthor{Cong2013} prepared monolayer \ce{WS2} on 300nm \ce{SiO2}-Si by sulfurization of \ce{WO3} powders in a one-end sealed tube.\cite{Cong2013} It was suggested that pre-cleaning the inner tube by IPA and DI water could effectively increase the pressure of vapor source.
-This observation probably arise from the reduction of \ce{WO3} assisted by IPA and water residuals, or due to the possible presence of \ce{H2S}.
-Intermediate phase \ce{WO_yS_{2-y}} and \ce{WS_{2+x}} is proposed in the growth mechanism.
-The apex of triangles could be active site of nucleation, \ce{WS_{2+x}} formation is confirmed by secondary ion mass spectrometry.
-Possible thick \ce{WS_{2+x}} flakes decompose subsequently, leading to ML \ce{WS2}.
-The subs are thoroughly cleaned.
-It was mentioned that separate sulfur heating improved the PL uniformity.
-Sulfurization mechanism study of \ce{WO3} suggested \ce{W^{6+}} cannot be directly reduce to \ce{W^{4+}} in \ce{WS2}.\cite{VanderVlies2002,VanderVlies2002a} Tungsten oxysulfides was necessary as the intermediate phase.
-Other chalcogenide has also been synthesized using this one-end sealed layout.\cite{Mukherjee2013}
-
-\citeauthor{Peimyoo2013} prepared \ce{WS2} on \ce{SiO2}-Si using \ce{WO3} powder and sulfur at 800 \si{\degreeCelsius}, aiming at the light emission studies to clarify several contradictory reports.\cite{Peimyoo2013} Uniform PL intensity was found on the triangular \ce{WS2} flakes, in contrast to previous edge enhanced PL.\cite{Berkdemir2013} Raman spectra (532nm) fit includes $E_{2g}^1(M)$ mode at 343 cm$^{-1}$, according to the phonon dispersion calculation \cite{Molina-Sanchez2011} and experimental observation\cite{Zeng2013,Zhao2013,Lee2013}.
-However, none of these experimental reports specifically mentioned $E_{2g}^1(M)$ mode.
-Tentative assignments of multi-phonon bands are summarized in supporting discussion of Ref\cite{Zhao2013}.
-As to the growth setup, similar tube furnace as in Ref \cite{VanderZande2013} and \cite{Najmaei2013} was used.
-To gain additional wisdom on \ce{MoS2} growth, we thus summarize the growth strategies in Ref \cite{VanderZande2013} and \cite{Najmaei2013} as following.
-\citeauthor{VanderZande2013} prepared \ce{MoS2} on 285nm \ce{SiO2}-Si using \ce{MoO3} and S as precursors.\cite{VanderZande2013} In contrast to the seeding method adopted in ref\cite{Lee2013,Lee2012b}, the author stress the importance of carefully cleaned substrates\footnote{acetone, 2hrs in \ce{H2SO4} and \ce{H2O2} (3:1) and 5 mins oxygen plasma} and minimum exposure of precursor to air.\footnote{APCVD, 105 \si{\degreeCelsius} for 4hrs, 700 \si{\degreeCelsius} hold for 5mins, and 10 sccm \ce{N2} within 2 inch tube.
-rapid cooling from 570 \si{\degreeCelsius}} Dirty substrates or old precursors will lead to hexagonal, 3-point star or irregular polycrystalline structures.
-The growth setup is similar to those in Ref\cite{Lee2012b}.
-The substrate and \ce{MoO3} source distance is critical in determining the growth density.
-As a comparison, we briefly mention the synthesis strategy in Ref\cite{Lee2013,Lee2012b} as well, where PTAS treated substrate is found to promote the deposition, while KCl treated substrates did not, and small carrier gas flow is preferred (1 sccm \ce{N2}).
-We also notice that the \ce{MoS2} flakes morphology seems more uniform in Ref\cite{VanderZande2013} than that in Ref\cite{Lee2012b}.
-On the other hand, \citeauthor{Najmaei2013} also demostrated \ce{MoS2} FL growth by sulfurization of \ce{MoO3} nanoribbons.\cite{Najmaei2013} The ribbons is applied by dispersion and meant to control the source amount.
-It was found the diffusion of vapor \ce{MoO_{3-x}} is rate-limiting step in \ce{MoS2} growth.
-This means the amount of source is critical in successful synthesis.
-The nucleation event is more frequently observed at subs edges, scratches or rough surface.
-Step edges is then intentionally created to facilitate the nucleation.
-As to the growth dynamics, it was postulated the oxisulfides(\ce{MoOS2} Raman spectra found), as intermediate phase, diffuse across the bare substrates and form triangular domains upon further sulfurization.
-The optimal growth conditions are 800-850 C, 700Torr, and sufficient sulfur.
-We then conjecture that the substrate cleaning in ref\cite{Peimyoo2013} should be similar to that in ref\cite{VanderZande2013}, yet the source-to-substrate layout and growth pressure are still needed to be optimized with respect to our current apparatus.
-
-\citeauthor{Zhang2013h} synthesized \ce{WS2} on sapphire (0001) using \ce{WO3} powder and sulfur as precursor under 900 \si{\degreeCelsius}.\cite{Zhang2013h} Ar slightly mixed with \ce{H2} is used to tailor the shape of \ce{WS2} flakes.
-It was found the source substrate distance play an important role in determining the morphology of as-grown flakes.
-The lattice mismatch between \ce{Al2O3} (4.785\AA) and \ce{WS2} (3.153 \AA) is .
-The edge termination is not well studied.
-Raman spectra indicate a universal down-shift of $A_{1g}$ peak (1L from 418 on \ce{SiO2}-Si to 416.4 on sapphire).
-PL signal on \ce{SiO2}-Si is stronger than on sapphire.
-The visibility of \ce{WS2} on \ce{Al2O3} is poor.
-No 1L vs nL statistic is available.
-FET on/off ratio is about 100, indicating low mobility.
-The other conditions includes 880C, 90mm source-to-substrate distance, 1 inch quartz tube, and LBM furnace.
-The growth conditions are probably adopted from ref\cite{Huanga2013}(arxiv:1304.7365).
-
-It is worth noting the flake sizes on sapphire \cite{Zhang2013h} seems larger than that on \ce{SiO2}/Si\cite{Peimyoo2013}, either due to the nucleation barrier difference or the amount of growth vapor and growth time.
-The flake sizes in ref \cite{Cong2013} is not quite uniform, though it could be even larger than that on sapphire \cite{Zhang2013h}.
-One common feature of aforementioned investigations is growth occurs on bare substrates and no catalyst or seeding promoter is employed.
-While there is another synthesis approach \cite{Lee2013,Ling2014} exclusively focusing on using seeding promoter.
-\citeauthor{Lee2013} obtained \ce{MoS2} and \ce{WS2} FL on PTAS-treated substrates (\ce{C24H12K4O8}), where tiny ($\sim 200$nm) seeds were found under AFM.
-More recently, \citeauthor{Ling2014} systemically investigated the role of seeding promoter in facilitating the nucleation of \ce{MoS2} monolayers.\cite{Ling2014} It was found various aromatic molecules are effective yet inorganic nanoparticles are not.
-The mechanism of thin film growth depends on the surface energy and chemical potentials of the deposited layers and their substrates.
-Layer growth is preferred when surface adhesive force is stronger than adatoms cohesive force.
-Seeding promoter probably lowered the surface energy by wetting, thus provided heterogenous nucleation sites.
-Continuous \ce{MoS2} monolayer is obtained by evaporating 2 \AA  \ce{F16CuPc} on desired receiving substrates.
-In each growth, about $10^{-10}$mol PTAS was applied onto \ce{SiO2}-Si, which was rendered hydrophilic and gentle gas blow to distribute the solution evenly.
-
-In short summary, we stress that there are several key factors in successfully synthesizing \ce{WS2} FL:
-\begin{itemize}
-\item \ce{WO3} powder size distribution and absolute amount (0.69g \ce{WO3} in 10mL acetone or IPA, inspired by the \ce{MoO3} nanoribbons usage)
-\item Sulfur amount and heating method to ensure a constant sulfur-rich environment
-\item \ce{WO3} powder source to substrate distance, which is coupled to pressure and carrier gas flow in determining the transport (atmospheric, 3-5mm)
-\item temperature ramping and growth time (750-800C, 3-10mins)
-\item 300nm-\ce{SiO2}-Si substrate to make OM flakes identification easier
-\end{itemize}
-
-% CVD TMDC
-\begin{landscape}
-\begin{table}[htb]
-\centering
-\caption{TMDC FL methods summary}\label{tab:tmsgrowth}
-{\footnotesize
-\begin{tabular}{lp{2.5in}p{4.5in}}
-\toprule
-TMDC  &  precursor & growth condition (default temperature unit \si{\degreeCelsius}) \\
-\midrule
-\ce{MoS2} films \cite{Lee1994,Endler1999} & \ce{MoCl5}, \ce{H2S} & 1 kPa, temperature: 400-550 \si{\degreeCelsius}, 100/10/2.5 sccm for Ar, \ce{H2S} and \ce{MoCl5} flow\\
-\addlinespace[0.5em]
-\ce{MoS2} FL \cite{Zhan2012} & 1-5nm Mo films on \ce{SiO2}, Sulfur & purging, RT-550@30mins, 550-750@90mins and hold for 10 mins. Mo coating on Si did not work.\\
-\ce{MoS2} FL \cite{Lin2012,Wang2013} & 4nm \ce{MoO3} coating on sapphire  & reduced to \ce{MoO2} in \ce{H2} and Ar at 500 \si{\degreeCelsius}, sulfurization at 850-1000 \si{\degreeCelsius} \\
-\addlinespace[0.5em]
-\ce{MoS2} FL \cite{Liu2012a} & \ce{(NH4)2MoS4} in DMF solution transport by Ar bubbler or dip-coating onto subs &  annealing under Ar or Ar + Sulfur, total pressure 0.2-2 Torr, \\
- \addlinespace[0.5em]
-\ce{MoS2} FL \cite{Wu2013} & \ce{MoS2} powder & Ar flow, 900 \si{\degreeCelsius} heating, pressure 20 Torr, 650 \si{\degreeCelsius} growth\\
- \addlinespace[0.5em]
-\ce{MoS2} FL \cite{Mann2013,Najmaei2013,Ji2013} Rice & \ce{MoO3} powders or ribbons, Sulfur & Ar flow, 530-850\si{\degreeCelsius}, total pressure 0.2-2 Torr, 5-30mins, mica or \ce{SiO2}-Si\\
- \addlinespace[0.5em]
-\ce{MoS2} FL \cite{Lee2012b,Ling2014} & 18mg \ce{MoO3} powders, Sulfur,various seeding promoter on sub & 5sccm Ar, 650 \si{\degreeCelsius}, 3min growth, atmospheric pressure, quick cooling\\
-
- \midrule
-\ce{WS2} films\cite{Ballif1999,Brunken2008} & sputtering \ce{WS_{3+x}} on 10nm Ni  & annealing under Ar for 1h at 850 \si{\degreeCelsius} \\
-\addlinespace[0.5em]
-\ce{WS2} FL \cite{Berkdemir2013} & $\sim$1nm \ce{WO3} coating on 285nm \ce{SiO2}-Si, 500mg sulfur & 800 \si{\degreeCelsius} for 30 mins, 100 sccm Ar, atmospheric pressure in \cite{Gutierrez2012} and 450 mTorr in \cite{Elias2013}.
-triangular flakes obtained\\
-\addlinespace[0.5em]
-\ce{WS2} ML \cite{Cong2013} & 1mg \ce{WO3} powder on \ce{SiO2}-Si covered by another sub, $d\sim3mm$, sulfur & 750 \si{\degreeCelsius}, slow heating, hold for 5mins, one-end sealed inner tube, 100 sccm Ar\\
-\addlinespace[0.5em]
-\ce{WS2} ML \cite{Zhang2013h} & \ce{WO3} powders, sulfur (separate heating) & 900 \si{\degreeCelsius}, sapphire subs, 225mTorr, Ar 80 sccm and \ce{H2} 10 sccm, growth time 60mins, adjusting precursor and sapphire distance changing the coverage of \ce{WS2}, tube diameter: 1 inch.
-55 $\mu m$ triangular flakes\\
-\addlinespace[0.5em]
-\ce{WS2} ML \cite{Peimyoo2013} & 1mg \ce{WO3} powders, sulfur  & \ce{SiO2}/Si subs.
-Recipe A: 200mg S,RT-550, Sulfur begin to melt, 550-800, 5K/min, hold 10mins, 200 sccm Ar.
-Recipe B: sulfur separated heated at 250 \si{\degreeCelsius}.
-Total pressure: maybe atmospheric, tube diameter: 2 inch.
-5 $\mu m$ triangular flakes \\
-\ce{WS2} FL \cite{Lee2013}  & 1g \ce{WO3} powders, sulfur, \ce{SiO2}-Si subs treated with PTAS \ce{C24H12K4O8} and gentle gas blow & substrate facing down, APCVD, 800 \si{\degreeCelsius}, 5mins, 5 sccm Ar, fast heating.
-\\
-\addlinespace[0.5em]
-\ce{WS2} films \cite{Shanmugam2012a}   & 20nm W on \ce{SiO2}-Si, sulfur & 750 \si{\degreeCelsius}, 200 sccm Ar, 1Torr. Annealing at 1000 \si{\degreeCelsius}, 25nm thick \ce{WS2} film obtained \\
-\bottomrule
-\end{tabular}
-}
-\end{table}
-\end{landscape}
-
-\subsection{Raman on bulk and FL TMDC}
-
-In this section, we will discuss previous studies using Raman to characterize \ce{MS2} films, nanotubes, and FL structures.
-In each morphology, one or two key points that we are interested will be highlighted for study in this thesis.
-The previous Raman efforts on \ce{MS2} film, especially the one using resonant conditions, provided critical insight into the electronic structure and lattice dynamics of these TMDC layered materials.
-We will then gather the Raman knowledge and compare it to the one obtained on nanotube and FL structures.
-For \ce{WS2} NTs, we will focus on the asymmetry of $A_{1g}$ mode and its origin.
-And for \ce{WS2} FL structures, we will summarize the finger print of Raman spectra on layer number dependence, and make some attempts on analysis the resonant Raman profiles of \ce{WS2}.
-
-We notice that Raman technique already proves to be extreme useful in characterizing CNT and graphene, i.e., tube diameter by assigning the RBMs (radial breathing modes) and G peaks position.\cite{Bonaccorso2013} And Raman spectroscopy also qualifies as an excellent tool to monitor tensile features of TMDCs in both 2D and tubular forms.\cite{Tang2013} Nevertheless, we will not exhaust these progress in this work.
-
-Raman spectra arise from the inelastic light scattering of optical phonons. In back scattering geometry, the phonon wavevector
-$q = 4\pi\frac{n}{\lambda}$.
-The refractive index of \ce{WS2} at 532nm is about.
-Compared to the size of Brillouin zone ($\pi/a = 10^{10}m^{-1}$), resonant Raman could or could not probe phonon at $M$ point.
-
-Before discussing the Raman spectra features, we briefly recapitulate some symmetry notations and vibration modes.
-We will use \ce{MoS2} as an example, and those definitions apply to \ce{WS2} as well.
-Hexagonal \ce{MoS2} belongs to space group $D_{6h}^4$, and the repeat unit in $c$ axis contains two layers, where sulfur atoms in one layer are directly above the molybdenum atoms in adjacent layers, which is often referred as 2H-\ce{MoS2}.
-Group theory predicts two infrared- and four Raman-active modes for 2H-\ce{MoS2}, which are mutually exclusive when the center of inversion is present.
-First we want to emphasize that in few layer structures, \ce{MoS2} with odd layers belong to different space group from that of even layers.
-Bulk MoS$_2$ and 2L-MoS$_2$ belong to the space group P6$_3$/$_{mmc}$ (point group D$_{6h}$).
-There are 18 normal vibration modes.
-The factor group of bulk and 2L-MoS$_2$ at $\vec{\Gamma}$ is D$_{6h}$.
-The atoms site groups are a subgroup of the crystal factor group.
-The correlation of the Mo site group D$_{3h}$, S site group C$_{3v}$, and factor group D$_{6h}$ allows one to derive the following irreducible representations for the 18 normal vibration modes at $\vec{\Gamma}$: $\vec{\Gamma}$= $A_{1g}+2A_{2u}+2B_{2g}+B_{1u}+E_{1g}+2E_{1u}+2E_{2g}+E_{2u}$, where $A_{2u}$ and $E_{1u}$ are translational acoustic modes, $A_{1g}$, $E_{1g}$ and $E_{2g}$ are Raman active, $A_{2u}$ and $E_{1u}$ are infrared (IR) active.
-1L-MoS$_2$ has $D_{3h}$ symmetry, with three atoms per unit cell.
-The irreducible representation of $D_{3h}$ gives: $\vec{\Gamma}$= $2A_2^{''}$+$A_1^{'}$+$2E^{'}$+$E^{''}$, with $A_2^{''}$ and $E^{'}$ acoustic modes, $A_2^{''}$ IR active, $A_1^{'}$ and $E^{''}$ Raman active, and the other $E^{'}$ both Raman and IR active.
-(See Fig.~\ref{fig:ws2ramsch}) NL-MoS$_2$ has 9N-3 optical modes: 3N-1 are vibrations along the c axis, and 3N-1 are doubly degenerate in-plane vibrations.
-For rigid-layer vibrations, there are N-1 layer breathing modes (LBMs) along the c axis, and N-1 doubly degenerate shear modes perpendicular to it.
-When N is even, there are 0 Raman active LBMs and $\frac{N}{2}$ doubly degenerate shear modes.
-When N is odd, there are $\frac{N-1}{2}$ LBMs and N-1 doubly degenerate shear modes.\cite{Wieting1971,Zhang2013i} This discussion can be visualized in Table~\ref{tab:tmslattice}.
-
-% irreducible representation
-\begin{table}[htb]
-\centering
-\caption{Lattices vibration of \ce{MS2}, adopted from ref\cite{Molina-Sanchez2011}}\label{tab:tmslattice}
-\begin{tabular}{lcccc}
-\toprule
- $D_{6h}$   & $D_{3h}$ & Character &  Direction & Atoms  \\
-\midrule
-$A_{1g}$    &  $A_1^{'}$   & Raman     & (out of plane)  & S  \\
-$E_{2g}^2$  &          &           & (in plane)      & M + S  \\
-$E_{2g}^1$  &  $E'$    &           & (in plane)      & M + S  \\
-$E_{1g}$    &  $E''$    &           & (in plane)      & S  \\
-\midrule
-$A_{2u}$    &  $A_2''$  & Infrared  & (out of plane)  & M + S  \\
-$E_{1u}$    &          &           & (in plane)      & M + S  \\
-\midrule
-$A_{2u}$    &  $A_2^{''}$   & Acoustic  & (out of plane)  & M + S  \\
-$E_{1u}$    &          &           &       &    \\
-\midrule
-$B_{2g}^2$  &          & Inactive  & (out of plane)  & M + S  \\
-$B_{2g}^1$  &          &           & (out of plane)  & M + S  \\
-$B_{1u}$    &          &           & (out of plane)  & S  \\
-$E_{2u}$    &          &           & (in plane)      & S  \\
-\bottomrule
-\end{tabular}
-\end{table}
-
-The $E$ type phonon branches correspond to in-plane normal modes, while the $A$ type phonons result from out-of-plane vibrations.
-$A_{1g}$ mode is an out-of-plane vibration involving only the S atoms while the $E_{2g}^1$ mode involves in-plane displacement of transition metal and S atoms.
-The $E_{2g}^2$ mode is a shear mode corresponding to the vibration of two rigid layers against
-each other and appears at very low frequencies ($<50 cm^{-1}$ \cite{Zhang2013i}).
-The $E_{1g}$ mode, which is an in-plane vibration of only the S atoms, is forbidden in the backscattering Raman configuration.
-In 2H-type TMDC, the $A_{1g}$ mode is sensitive to electrostatic doping, while $E_{2g}^1$ mode is sensitive to strain, in which the FWHM of the peaks are indicator of external force quantity.\cite{Zhao2013}
-
-\begin{figure}[htb]
-\centering
-\includegraphics[width=0.7\textwidth]{ws2_ramsch}
-\caption[\ce{MS2} vibration symmetry]{\ce{MS2} vibration symmetry in bulk and monalyer, adopted from REF\cite{Ghorbani-asl}}
-\label{fig:ws2ramsch}
-\end{figure}
-
-Lattice vibration of natural \ce{MoS2} crystal was studied by \citeauthor{Wieting1971} using infrared and Raman spectroscopy.\cite{Wieting1971} It was found the $E_{1u}$ IR mode and one $E_{2g}$ Raman mode are nearly degenerate in energy.
-15 optical modes are allowed assuming 6 atoms in primitive cell.
-Refractive indices from reflectivity measurement were $n_0$= 3.9, $n_e$ = 2.5.
-\citeauthor{Stacy1985} studied \ce{MoS2} and \ce{WS2} Raman spectra using lasing energy close to the absorption edges.\cite{Stacy1985} Second order scattering from phonon with nonzero momentum is used to explain the rich Raman spectra.
-\citeauthor{Sourisseau1991} investigated the resonant Raman profiles in 2H-\ce{WS2} using ten different excitation wavelengths.\cite{Sourisseau1991} Dramatic intensity variation at 352 $cm^{-1}$ was observed, which is assume to be of two-phonon signal nature, and correspond to an overtone or combination band of phonons with non-zero momenta contributing to indirect gap absorption edge.
-\citeauthor{Sourisseau1991} assigned this phonon with non-zero momenta as $LA(K_5)$ type.
-The enhancement of the total Raman cross section at excitonic resonance in which excitons serve as the intermediate state is stronger compared to that of interband resonance.
-The strong enhancement at excitonic resonance is attributed to the characteristics of excitons in layered materials such as large binding energy, enhanced oscillator strength, and small damping constant.\cite{Zhao2013} \citeauthor{Chung1998} grew \ce{WS2} film using \ce{W(CO)6} and \ce{H2S} precursor.\cite{Chung1998} Raman spectra ($\lambda=632nm$) on films with non-parallel orientation revealed the presence of shoulder mode under $A_{1g}$, which is assigned to LA and TA phonon coupling.
-This coupling process stem from disorder-activated zone boundary phonons.
-We will further discuss this non-symmetric feature of $A_{1g}$ mode in section~\ref{sec:ntram}.
-
-% WS2 Raman assignments
-\begin{table}
-  \centering
-  \caption{\ce{WS2} Raman assignment}  \label{tbl:ws2raman}
-  \begin{tabular}{ccccc}
-    \toprule
-    &&\multicolumn{3}{c}{Wavenumber shift ($cm^{-1}$)}\\
-    \cmidrule(l){3-5}
-    Symmetry                & Atoms & \ce{WS2} ML\cite{Cong2013}  & \ce{WS2} NT \cite{JMR7990865}  & \ce{WS2} bulk \cite{Sourisseau1991} \\
-    \midrule
-          $E_{2g}^2(\Gamma)$ &      & 27.5\textsuperscript{\emph{a}}&             &  27.4    \\
-    $LA(M)-E_{2g}^2(\Gamma)$ &      & 148.3                        &              &    \\
-       TBD                   &      &                              & 153          &      \\
-         $E_{2g}^1(M)-LA(M)$ &      &                              & 172          & 173  \\
-    LA(M)                    &      & 174.8                        & 172          &       \\
-    LA(K)                    &      & 192.4                        &              &  193 \\
-    $LA(M)+E_{2g}^2(\Gamma)$ &      & 203                          &              &     \\
-    $LA(K)+E_{2g}^2(\Gamma)$ &      & 213.9                        &              &  212  \\
-    $A_{1g}(M)-LA(M)$        &      & 230.9                        & 230          &  233  \\
-    $2LA(M)-3E_{2g}^2(\Gamma)$ &    & 264.2                        & 262          &  267  \\
-    $2LA(M)-2E_{2g}^2(\Gamma)$ &    & 295.4                        & 294          &  297   \\
-    $2LA(M)-E_{2g}^2(\Gamma)$ &     & 322.9                        &              &  325   \\
-               $E_{2g}^1(M)$ &      & 343.1                        &              &      \\
-    2LA(M)                   &      & 350.8                        & 350          &  352\\
-          $E_{2g}^1(\Gamma)$ &      & 355.4                        & 350          &  356 \\
-    $2LA(M)+2E_{2g}^2(M)$    &      &                              & 381          &  381   \\
-     LA + TA \cite{Sourisseau1991} or $B_{1u}(\Gamma)$\cite{Staiger2012}  &      &       &   &  416 \\
-          $A_{1g}(\Gamma)$   &      & 417.9                        & 416\textsuperscript{\emph{b}} &  421\\
-               3LA(K)        &      & 577                          &              &      \\
-       $ LA(M)+ A_{1g}(M)$   &      & 584                          & 581          &  585 \\
-    4LA(M)                   &      & 704                          &              &  703\\
-    \bottomrule
-  \end{tabular}
-
-  \textsuperscript{\emph{a}} Calculated from column values;
-  \textsuperscript{\emph{b}} \citeauthor{JMR7990865} probably made incorrect assignment of 416 peak.\cite{JMR7990865}
-\end{table}
-
-Raman technique has also provided much insight into the few layer \ce{MS2}.
-\ce{MS2} layer numbers are readily identified by the wavenumber distance between $A_{1g}$ and $E_{2g}^1$ mode for \ce{MoS2}\cite{Buscema2013} and \ce{WS2}\cite{Berkdemir2013}.
-Yet due to the relative small shift of $A_{1g}$ mode and little shift of $E_{2g}^1$ mode in \ce{WS2} FL, the frequencies distance might not qualify as an unambiguous way to distinguish layer numbers.
-Yet the resonant Raman profile on \ce{WS2} exhibit unique features between the intensity of 2LA and $A_{1g}$ mode,\cite{Berkdemir2013,Zhao2013} which provide another routine to assure the monolayer presence.
-However, we notice some discrepancy in de-convolution of \ce{WS2} resonant profile between 300 and 400 cm$^{-1}$, i.e., the presence of $E_{2g}^1(M)$ mode at about 344 cm$^{-1}$.\cite{Peimyoo2013,Cong2013,Berkdemir2013} Rigid assignments of this mode still requires further theoretical\cite{Ataca2012} and experimental efforts.
-In addition, \citeauthor{M2013} reported temperature dependent of 1L \ce{WS2}.\cite{M2013} When the temperature increase from 77K to 623K, A1g shift from 420 to 416.5 cm.
-Interestingly in this report 2LA/$A_{1g}$ (514 nm excitation) seems less than unit.
-The spectra were obtain from mechanically exfoliated \ce{WS2} lying on 300 nm \ce{SiO2}-Si substrate.
-Moreover, The $A_{1g}$ and $E_{2g}^1$ intensities ratio exhibit reverse behaviors under 532 and 632 nm excitation.
-This is caused by the different cross-section enhancement for a specific excitation condition.
-The A and B excitonic absorption in \ce{WS2} mainly arise from the $d_{xy}$ and $d_{x^2 - y^2}$ states to $d_{z^2}$ states of tungsten atoms.
-Thus, electrons excited by 633 nm laser have a character of tungsten $d_{z^2}$ orbitals aligned along the c axis perpendicular to \ce{WS2} basal plane.
-Since $A_{1g}$ mode involve out of plane displacement along c axis, $A_{1g}$ phonons could couple more strongly with $d_{z^2}$ states than that of $E_{2g}^1$ phonons.
-As a result, $A_{1g}$ mode is stronger than $E_{2g}^1$ mode at 633 nm resonance.\cite{Zhao2013} However, the reverse effect for 532 nm excitation could not be well explained using the above argument.
-This may be caused by electron-phonon coupling with other inter-band transition electrons.
-
-\subsection{Raman on TMDC NTs}\label{sec:ntram}
-
-\citeauthor{Dobardzic2005} calculated \ce{MoS2} SWNT phonon dispersion.
-The dependence of wavenumbers and their displacement on chirality and diameter were discussed.
-The calculation method enables studying lattice dynamics with NT diameter up to 50nm.
-The chiral vector $(n_1, n_2)$ is defined within the molybdenum plane.
-Symmetry assignment is zigzag when $(n,0)$, armchair when $(n,n)$ and chiral when $(n_1, n_2), n_1>n_2$.
-\citeauthor{Dobardzic2006} theoretically presented Raman scattering of any polarization on SWNT of \ce{WS2} and their dependence on diameter (1-20nm) and chiral angle.
-The author assigned 351 $cm^{-1}$ as $E_u$ for \ce{WS2} NT.\cite{Dobardzic2006} \citeauthor{Ghorbani-asl} discuss the electronic and vibrational properties for large diameter \ce{WS2} NTs\cite{Ghorbani-asl}.
-Single-walled NT is approximated by 1H monolayer and others by 2H bulk structure.
-It was found that large-diameter nanotubes can be approximated with layered systems as their properties should be nearly the same at the scale.
-Only hypothetical SWNTs, and possibly MWNTs with alternating layer compositions, may show direct band gaps.
-Slight mechanical deformation of the SWNTs would result in a change of the direct band gap back to the indirect one, located between $\Gamma$ and $K$ high-symmetry points, similarly to the monolayers.
-As for 2D materials, quantum confinement to single-walled tubes would result in direct band-gap semiconductors with $\Delta$ occurring at the $K$ point.
-Single-walled tubes exhibit slightly softer out-of-plane $A'$ and stronger in-plane $E'$ modes.
-Those results indicate that the weak interlayer interactions in MS$_2$ materials cannot be associated with the van der Waals interactions only, but most probably with Coulomb electrostatic interactions as well.
-
-Raman signatures of \ce{WS2} nanotubes show distinct features to the spectra of their bulk counterpart.
-\citeauthor{JMR7990865} observed a new line at 152 cm in \ce{WS2} NT, which is absent in 2H-\ce{WS2}.\cite{JMR7990865} Another feature is a emerging shoulder on the low energy side of $A_{1g}$ mode at about 416 $cm^{-1}$.
-This has been attributed to a combination mode of LA + TA phonons from the $K$ point of Brillouin zone.\cite{Sourisseau1991} \citeauthor{Zou2007} prepared W/\ce{WS2} core-shell NPs by reaction of tungsten and sulfur under hydrogen atmosphere.\cite{Zou2007} The shoulder mode associated with $A_{1g}$ is attributed to LA + TA.
-As pressure increase from 0GPa to 18GPa, these two bands, both shifting to higher wavenumbers, first separate and then recombine.
-It was assumed the compression mainly occurs in c axis, so the stiffening of $A_{1g}$ is anticipated.
-A more prominent feature is the resonance profile broadening the shape of $E_{2g}^1$ mode, which is often assigned to 2LA mode.
-Yet there is different opinion on these assignments.
-\citeauthor{Molina-Sanchez2011} label the 350 $cm^{-1}$ band as \ce{E_{1u}} instead of 2LA.\cite{Molina-Sanchez2011} And recent theoretical investigations suggest 416 $cm^{-1}$ peak is inactive$B_{1u}$ mode\cite{Molina-Sanchez2011,Ataca2012}, which is the Davydov doublet with $A_{1g}$ mode.
-\citeauthor{Staiger2012} adopted these assignments in studying the resonance Raman profile of \ce{WS2} NTs.\cite{Staiger2012} It was found that
-\begin{enumerate}
-\item $B_{1u}$ mode arise from curvature and structural disorder
-\item $B_{1u}/A_{1g}$ intensity ratio strongly depends on excitation, and exceeds unity when excitation energy less than 1.9eV.
-\item  An excitonic transition energy of NT is found have a local minimum at about 50nm, (layer number probably \textgreater 10), and increase either way. Yet all below the bulk value.
-\end{enumerate}
-
-\citeauthor{Krause2009} also measured the resonant Raman on \ce{WS2} nanotubes and found a split within 420 $cm^{-1}$ region, which is labelled as $D-A_{1g}$ mode in analog with the similar defect mode of graphene.\cite{Krause2009} This  $D-A_{1g}$ mode was found enhanced as diameter of \ce{WS2} NTs decrease.
-In this work, we will use $B_{1u}({\Gamma})$ mode to interpret this emerging line at about 416 $cm^{-1}$ of \ce{WS2} NTs, and we adopt the 350 $cm^{-1}$ as 2LA(M).
-\citeauthor{Krause2009a} confirmed $B_{1u}$ mode arise from the inherent structure of \ce{WS2} nanomaterials instead of surface layer effect.
-It is also worth noting that $A_{1g}$ is stronger than 2LA under 632nm yet weaker under 532nm, similar to previous discussion of FL scenarios.
-And $B_{1u}$ mode under 532 nm become less prominent than that of 632 nm.\cite{Krause2009a} This is in consistent with our observation of Raman spectra on the \ce{WS2}-\ce{WO_x} structures.
-\citeauthor{Rafailov2005} estimated the orientation dependence of resonant raman on one MWNT \ce{WS2} attached to the cantilever tip of AFM.\cite{Rafailov2005} Antenna effect lead to optical transition occurring only for polarization parallel to nanotube axis.
-And therefore resonance Raman intensity of SWNT varies as nanotube orientation.
-This dependence may provide a routine to distinguish different chiral NTs.
-Polarized Raman spectra (632nm excitation) is obtained, showing $A_{1g}$ and $E_{2g}$ sharing the same polarization behavior.
-\citeauthor{Virsek2007} investigated the Raman scattering ($\lambda=632nm$) of \ce{WS2} NTs.\cite{Virsek2007} The silicon peak at 520 $cm^{-1}$ is used for calibration.
-Up-shift of $A_{1g}$ and $E_{2g}$ modes (i.e.
-420 to 423 $cm^{-1}$ at $A_{1g}$ mode) were observed, which is attributed to the strain in 3R stacking layers.
-
-The lattices dimensions are summarized in Table~\ref{tab:ms2lattice},
-%lattice
-\begin{table}[htb]
-\centering
-\caption{Lattices dimension of \ce{MS2}}\label{tab:ms2lattice}
-\begin{tabular}{lccr}
-\toprule
-         &  & 2H-\ce{MoS2}\cite{Coehoorn1987,Ataca2012} & 2H-\ce{WS2}\cite{Albe2002,Schutte1987} \\
-\midrule
-Lattice constant & a(\AA) & 3.1604 & 3.171 \\
-                 & c(\AA) & 12.295 & 12.359 \\
-Within \ce{MS2} layer & M-3S (\AA)& 2.37  & 2.405   \\
-                      & S-1S (\AA)& 3.11  & 3.14   \\
-Between \ce{MS2} layer& S-3S (\AA)&   & 3.53   \\
-\bottomrule
-\end{tabular}
-\end{table}
-
-The difference of B1u and LA + TA.
+\input{./ch-tms/tmspart}
 

### 2014-08-09 ch-tms/tmspart.tex
tms split, intro proofreading done 85/100

\section{Introduction}
% \subsection{crystal structure of tmdc}
\subsection{Growth of TMDC}
Shortly after the discovery of carbon nanotube (CNT) in 1991,\cite{Iijima1991} its transition metal dichalcogenides (TMDC) counterparts, \emph{i.e.} \ce{WS2}, was synthesized in 1992.\cite{Tenne1992} In the following decades, other TMDC and several metal oxides nanotubes were demonstrated as well. \citeauthor{Rao2003} did an excellent work to review these inorganic nanotubes.\cite{Rao2003} Here the author just recapitulate the main categories of synthesis methods.
\begin{enumerate}
\item Reducing \ce{MO3} in \ce{H2} and \ce{H2S} atmosphere\footnote{M = Mo, W in this work}
\item Direct decomposition of \ce{MS3}
\item Decomposition of the ammonium salt \ce{(NH4)2MS4}
\item Using CNT as templates, arc discharge, or laser ablation
\end{enumerate}

Except the aforementioned methods, another important reaction in CVD domain is
\begin{equation}\label{eq:mclns}
\cee{MoCl5(WCl6) + S \rightarrow MoS2(WS2) + S2Cl2}.
\end{equation}
This reaction has been explored by several authors,\cite{Stoffels1999} and could be used under atmospheric pressure.\cite{Li2004a}

All these methods can be applied to the growth of TMDC few layer structures, either directly or with some modifications. Among all the members of TMDC nanotubes, \ce{WS2} and \ce{MoS2} NTs are probably the most well investigated.\cite{Homyonfer1997,Tenne1998,Frey1998,Frey1999,Rothschild2000,Zak2000} The reaction mechanism of \ce{WO3} with \ce{H2}/\ce{H2S} has been thoroughly studied \cite{Feldman1998} and high yield synthesis approach has been established.\cite{Margolin2004} For \ce{WO3} nanoparticles precursor, it was found that the simultaneous reduction and sulfurization is essential for encapsulation of fullerene like \ce{WS2} structures from the oxide nanoparticles. During the surfurization process, remaining oxide core is gradually reduced and transformed into an ordered superlattice of $\{ 001 \}$ \gls{cs} planes. Further reaction will consume up the \ce{WO_x} core, leaving multi-walled \ce{WS2} NTs only. For precursor of \ce{WO3} nanowires, \citeauthor{Feldman1996} proposed that TMDC nanotubes growth began with the reduced \ce{WO3} phases, in particular \ce{W_{18}O_{49}}.\cite{Feldman1996} It is worth noting that \ce{MS2} can be prepared by direct sulfurization from its oxides phase, but reaction \cee{MO3 + Se \rightarrow MSe2} will not proceed unless introducing other reducing agents, such as \ce{H2}.\cite{Tsirlina1998} This fact highlights that sulfur is rather radical at elevated temperature.

\citeauthor{Zhu2000} performed a detailed morphological and structural analysis on \ce{WS2} NTs synthesized using \ce{WO_{3-x}} NWs and \ce{H2S}.\cite{Zhu2000} Sulfur vacancy was found on the outer wall of NT. The tips exhibits various structures. Open-ended can be observed, more frequently than that in carbon nanotubes (CNTs), which is often sealed. \citeauthor{Zhu2000} suggested this open-ended tubes resulted from continuous growth on other nanotubes. And the closure configuration is rather complicated. Flat caps often dominates. \citeauthor{Zhu2000} maintained that this oxide-to-sulfides mechanism might apply to closed caps only, not to those open ended tubes.\cite{Zhu2000} TEM diffraction analysis could distinguish the chirality of NTs, as demonstrated by CNT \cite{Zhang1993} and \ce{MoS2}\cite{MARGULIS1996}. \ce{WS2} NT chirality revealed by TEM SAED shows armchair NTs dominates. \citeauthor{Sloan1999} investigated tungsten oxides structures incorporated in \ce{WS2}.\cite{Sloan1999} The encapsulated \ce{WO_x} cores often exhibit \ce{W3O8} and \ce{W5O_{14}} phases, both of which belong to the \ce{W_nO_{3n-1}} homogenous series, arising as a result of \gls{cs} planes.\cite{Miyano} Some \ce{WO_x} cores show oxygen vacancy instead of CS planes, leading to prominent streaking in SAED patterns. Although high yield growth method of \ce{WS2} has been available, the extent to which one can control the NT configuration is still limited, \emph{i.e.}, single-walled NT has not been routinely synthesized and the electronic properties can only be predicted theoretically. \citeauthor{Seifert2000} investigated the electronic structures of \ce{WS2} nanotube using DFT calculation.\cite{Seifert2000} It was found zigzag (n,0) NTs exhibts a direct gap at $\Gamma$ point, whose size increase monotonically with tube diameter, while armchair (n,n) NTs, unlike its metallic counterpart of (n,n) CNT, show indirect band gap increasing with tube diameter. \citeauthor{Zibouche2012} reached the same conclusion on \ce{WS2} SWNT.\cite{Zibouche2012} It was also found band gaps of armchair and zigzag NTs increase with diameter, going from values close to bulk and approaching that of  monolayer, and for a given tube diameter, $E_g$ of zigzag NTs are larger than those of armchair NTs. This difference presumably vanishes when nanotube diameter exceeds 100 nm.

Parallel with the scenario of CNT and graphene, TMDC few layer structures attract intensive research efforts recently. These unfolded TMDC nanotubes exhibit many appealing features, i.e., indirect-to-direct band gap transition,\cite{Splendiani2010} valley electronics, and become a promising candidate in energy harvesting, optoelectronics and photocatalytic activity. For scientific research purpose, exfoliation by liquid \cite{Smith2011} or mechanical methods \cite{Lee2010a} can provide sufficient materials. Yet considering the integration into current microelectronic process, CVD synthesis of thickness controllable 2D TMDC is highly desired, which stills hold the greatest potential for high yield production of \ce{MS2}. So this work focuses on reviewing the CVD based methods. The author will review literatures to date on both \ce{WS2} films and few layer structures, and highlight several typical investigations using different synthesis methods, as summarized in Table~\ref{tab:tmsgrowth}. It is important to note that the synthesis of NTs is relevantly independent of substrates, which is in sharp contrast to the scenario of few layer growth. The \ce{WS2} nucleation and interaction with substrates play dominant roles in the growth of 2D FL structures. This lead us to focus on the \ce{WS2} films growth, which presumably could provide valuable insight into the nucleation process on various substrates.

\textbf{\ce{MS2} films} \citeauthor{Lee1994} studied the CVD of \ce{MoS2} by \ce{MoCl5} or \ce{MoF6} and \ce{H2S} in great details. Phase diagrams for \ce{Mo-S-Cl-H} and \ce{Mo-S-F-H} system at 1 kPa were simulated.\cite{Lee1994} \citeauthor{Endler1999} also investigated the solid-phase diagram for \ce{Mo-S-Cl-H-Ar} system.\cite{Endler1999} It was found pure \ce{MoS2} was main product when molar ratio of \ce{H2S}-\ce{MoCl5} exceeds 2. More important, \ce{MoS2} basal plane orientation can be parallel to substrate when the thickness was smaller than 50 nm. \citeauthor{Ennaoui1995a} grew tungsten disulfide film using sulfurization of \ce{WO3} under \ce{N2}/\ce{H2} gas flow.\cite{Ennaoui1995a} The composition was found to be \ce{WS_{2.13}}, and the excess of sulfur lead to p-type conductivity. XRD peaks ratio is used as a measure of film orientation, which was found higher for film prepared without an intermediate Ni coating. \ce{Ni3S2} phase was found and surfactant-mediated epitaxy is proposed. \citeauthor{Regula1997} studied the Ni-W-S phase diagram and the role of Ni layer in promoting \ce{WS2} film growth from amorphous \ce{WS3}.\cite{Regula1997} \emph{In-situ} TEM analysis confirmed the formation of \ce{NiS_x} droplets and lateral growth of \ce{WS2} from these droplets.\cite{Regula1998} Recently, it has been shown that direct sulfurization of W coating (20nm) at 750 \si{\degreeCelsius} on \ce{SiO2}-Si can also produce \ce{WS2} film.\cite{Shanmugam2012a} However, the film is of bulk in nature. This could be explained by the study of \citeauthor{Genut1992} towards \ce{WS2} growth on various substrates,\cite{Genut1992} as summarized in Table~\ref{tab:ws2subs}. It was found that the \ce{WS2} nucleate from an amorphous \ce{WS3} phase and the substrate has a critical role in determining both the reaction onset temperature and the texture. The adhesion of tungsten to quartz was found to be much stronger than to glass. And oxygen-containing species such as \ce{H2O} or OH tend to cause \ce{WS2} basal plane perpendicular to substrate.
% WS2 films
\begin{table}[htb]
\centering
\caption{\ce{WS2} growth on different substrates}\label{tab:ws2subs}
\begin{tabular}{lcp{1in}p{2in}}
\toprule
precursor                 & substrate &  conditions & film feature\textsuperscript{\emph{a}}  \\
\midrule
sputtered W + \ce{H2S}   & glass      & onset 400 \si{\degreeCelsius} & $\perp c$ at 500 \si{\degreeCelsius}, metastable \ce{WS3} found\\
                          & quartz      & onset 650 \si{\degreeCelsius} & $\parallel c$ below 950 \si{\degreeCelsius}\\
                          & Mo        & onset NA          & $\parallel c$ at 1000 \si{\degreeCelsius}\\
                          & W          & onset NA           & random orientation\\
\midrule
\ce{WO_x} + \ce{H2S}    & quartz      & onset 500 \si{\degreeCelsius} & predominantly $\perp c$ after 800 \si{\degreeCelsius}\\
                        & Mo        & onset NA          & $\parallel c$ dominant\\
                        & W       & onset NA          & random orientation\\
\bottomrule
\end{tabular}

\textsuperscript{\emph{a}} $\perp c$: the c axis is perpendicular to the substrate, $\parallel c$: the c axis is parallel to the substrate;

\end{table}

\textbf{\ce{MS2} FL} For \ce{MoS2}, the reaction mechanism of \ce{MoO3} to \ce{MoS2} was studied by \citeauthor{Weber1996}.\cite{Weber1996} This study provided guidelines for the recent syntheses of \ce{MoS2} by sulfurization of \ce{MoO3}.\cite{Lin2012,Lee2012b,Liu2012a,Najmaei2013} Similar studies on sulfurization of \ce{WO3.H2O} to \ce{WS2} and decomposition of \ce{(NH4)2WO2S2} were also reported.\cite{VanderVlies2002,VanderVlies2002a} In combination with the knowledge from \ce{WS2}, the author compare those insight from several recent reports on \ce{WS2} FL. \citeauthor{Cong2013} prepared monolayer \ce{WS2} on 300 nm \ce{SiO2}-Si by sulfurization of \ce{WO3} powders in a one-end sealed tube.\cite{Cong2013} It was suggested that pre-cleaning the inner tube by IPA and DI water could effectively increase the pressure of vapor source. This observation probably arise from the reduction of \ce{WO3} assisted by IPA and water residuals, or due to the possible presence of \ce{H2S}. Intermediate phase \ce{WO_yS_{2-y}} and \ce{WS_{2+x}} is proposed in the growth mechanism. The apex of triangles could be active site of nucleation, \ce{WS_{2+x}} formation is confirmed by secondary ion mass spectrometry. Possible thick \ce{WS_{2+x}} flakes decompose subsequently, leading to ML \ce{WS2}. The substrates are thoroughly cleaned. It was mentioned that separate sulfur heating improved the PL uniformity. Sulfurization mechanism study of \ce{WO3} suggested \ce{W^{6+}} cannot be directly reduce to \ce{W^{4+}} in \ce{WS2}.\cite{VanderVlies2002,VanderVlies2002a} Tungsten oxysulfides was necessary as the intermediate phase.

\citeauthor{Peimyoo2013} prepared \ce{WS2} on \ce{SiO2}-Si using \ce{WO3} powder and sulfur at 800 \si{\degreeCelsius}, aiming at the light emission studies to clarify several contradictory reports.\cite{Peimyoo2013} Uniform PL intensity was found on the triangular \ce{WS2} flakes, in contrast to previous edge enhanced PL.\cite{Berkdemir2013} Raman spectra (532nm) fit includes $E_{2g}^1(M)$ mode at 343 cm$^{-1}$, according to the phonon dispersion calculation \cite{Molina-Sanchez2011} and experimental observation\cite{Zeng2013a,Zhao2013,Lee2013}. However, none of these experimental reports specifically mentioned $E_{2g}^1(M)$ mode. Tentative assignments of multi-phonon bands are summarized in supporting information of Ref\cite{Zhao2013}. As to the growth setup, similar tube furnace as in Ref \cite{VanderZande2013} and \cite{Najmaei2013} was used. To gain additional wisdom on \ce{MoS2} growth, the author thus summarize the growth strategies in Ref \cite{VanderZande2013} and \cite{Najmaei2013} as following. \citeauthor{VanderZande2013} prepared \ce{MoS2} on 285nm \ce{SiO2}-Si using \ce{MoO3} and S as precursors.\cite{VanderZande2013} In contrast to the seeding method adopted in ref\cite{Lee2013,Lee2012b}, \citeauthor{VanderZande2013} stressed the importance of carefully cleaned substrates\footnote{acetone, 2hrs in \ce{H2SO4} and \ce{H2O2} (3:1) and 5 mins oxygen plasma} and minimum exposure of precursor to air.\footnote{APCVD, 105 \si{\degreeCelsius} for 4hrs, 700 \si{\degreeCelsius} hold for 5mins, and 10 sccm \ce{N2} within 2 inch tube. rapid cooling from 570 \si{\degreeCelsius}} Dirty substrates or old precursors will lead to hexagonal, 3-point star or irregular polycrystalline structures. The growth setup is similar to those in Ref\cite{Lee2012b}. The substrate and \ce{MoO3} source distance is critical in determining the growth density. The synthesis strategy in Ref\cite{Lee2013,Lee2012b} is briefly mentioned as well, where PTAS treated substrate is found to promote the deposition, while KCl treated substrates did not, and small carrier gas flow is preferred (1 sccm \ce{N2}). It was also noted that the \ce{MoS2} flakes morphology seems more uniform in Ref\cite{VanderZande2013} than that in Ref\cite{Lee2012b}. On the other hand, \citeauthor{Najmaei2013} also demostrated \ce{MoS2} FL growth by sulfurization of \ce{MoO3} nanoribbons.\cite{Najmaei2013} The ribbons is applied by dispersion and meant to control the source amount. It was found the diffusion of vapor \ce{MoO_{3-x}} is rate-limiting step in \ce{MoS2} growth. This means the amount of source is critical in successful synthesis. The nucleation event is more frequently observed at subs edges, scratches or rough surface. Step edges is then intentionally created to facilitate the nucleation. As to the growth dynamics, it was postulated the oxisulfides(\ce{MoOS2} Raman spectra found), as intermediate phase, diffuse across the bare substrates and form triangular domains upon further sulfurization. The optimal growth conditions are 800--850 \si{\degreeCelsius}, 700 Torr, and sufficient sulfur. This theis then conjectures that the substrate cleaning in ref\cite{Peimyoo2013} should be similar to that in ref\cite{VanderZande2013}, yet the source-to-substrate layout and growth pressure are still needed to be optimized with respect to our current apparatus.

\citeauthor{Zhang2013h} synthesized \ce{WS2} on sapphire (0001) using \ce{WO3} powder and sulfur as precursor under 900 \si{\degreeCelsius}.\cite{Zhang2013h} Ar slightly mixed with \ce{H2} is used to tailor the shape of \ce{WS2} flakes. It was found the source substrate distance plays an important role in determining the morphology of the as-grown flakes.\footnote{There is a lattice mismatch between \ce{Al2O3} (4.785 \AA) and \ce{WS2} (3.153 \AA)} The edge termination is not well studied. Raman spectra indicate a universal down-shift of $A_{1g}$ peak (1L from 418 on \ce{SiO2}-Si to 416.4 on sapphire). PL signal on \ce{SiO2}-Si is stronger than on sapphire. The visibility of \ce{WS2} on \ce{Al2O3} is poor. No 1L vs nL statistic is available. FET on/off ratio is about 100, indicating low mobility. The other conditions includes 880 \si{\degreeCelsius}, 90 mm source-to-substrate distance, 1 in quartz tube, and LBM furnace. The growth conditions are probably adopted from ref\cite{Huanga2013}.

It is worth noting the flake sizes on sapphire\cite{Zhang2013h} seems larger than that on \ce{SiO2}/Si\cite{Peimyoo2013}, either due to the nucleation barrier difference or the amount of growth vapor and growth time. The flake sizes in ref \cite{Cong2013} is not quite uniform, though it could be even larger than that on sapphire \cite{Zhang2013h}. One common feature of aforementioned investigations is growth occurs on bare substrates and no catalyst or seeding promoter is employed. While there is another synthesis approach \cite{Lee2013,Ling2014} exclusively focusing on using seeding promoter. \citeauthor{Lee2013} obtained \ce{MoS2} and \ce{WS2} FL on PTAS-treated substrates (\ce{C24H12K4O8}), where tiny ($\sim 200$ nm) seeds were found under AFM. More recently, \citeauthor{Ling2014} systemically investigated the role of seeding promoter in facilitating the nucleation of \ce{MoS2} monolayers.\cite{Ling2014} It was found various aromatic molecules are effective yet inorganic nanoparticles are not. The mechanism of thin film growth depends on the surface energy and chemical potentials of the deposited layers and their substrates. Layer growth is preferred when surface adhesive force is stronger than adatoms cohesive force. Seeding promoter probably lowered the surface energy by wetting, thus provided heterogenous nucleation sites. Continuous \ce{MoS2} monolayer is obtained by evaporating \ce{F16CuPc} of 2 \AA on desired receiving substrates. In each growth, about $10^{-10}$ mol PTAS was applied onto \ce{SiO2}-Si, which was rendered hydrophilic and gentle gas blow to distribute the solution evenly.

In short summary, this thesis stresses that there are several key factors in successfully synthesizing \ce{WS2} FL:
\begin{itemize}
\item \ce{WO3} powder size distribution and absolute amount (0.69 g \ce{WO3} in 10 mL acetone or IPA, inspired by the \ce{MoO3} nanoribbons usage)
\item Sulfur amount and heating method to ensure a constant sulfur-rich environment
\item \ce{WO3} powder source to substrate distance, which is coupled to pressure and carrier gas flow in determining the transport (atmospheric, 3-5 mm)
\item temperature ramping and growth time (750-800 \si{\degreeCelsius}, 3-10 min)
\item 300 nm-\ce{SiO2}-Si substrate to make OM flakes identification easier
\end{itemize}

% CVD TMDC
\begin{landscape}
\begin{table}[htb]
\centering
\caption{TMDC FL methods summary}\label{tab:tmsgrowth}
{\footnotesize
\begin{tabular}{lp{2.5in}p{4.5in}}
\toprule
TMDC  &  precursor & growth condition (default temperature unit \si{\degreeCelsius}) \\
\midrule
\ce{MoS2} films \cite{Lee1994,Endler1999} & \ce{MoCl5}, \ce{H2S} & 1 kPa, temperature: 400-550 \si{\degreeCelsius}, 100/10/2.5 sccm for Ar, \ce{H2S} and \ce{MoCl5} flow\\
\addlinespace[0.5em]
\ce{MoS2} FL \cite{Zhan2012} & 1-5 nm Mo films on \ce{SiO2}, Sulfur & purging, RT-550@30 min, 550-750@90 min and hold for 10 min. Mo coating on Si did not work.\\
\ce{MoS2} FL \cite{Lin2012,Wang2013} & 4 nm \ce{MoO3} coating on sapphire  & reduced to \ce{MoO2} in \ce{H2} and Ar at 500 \si{\degreeCelsius}, sulfurization at 850-1000 \si{\degreeCelsius} \\
\addlinespace[0.5em]
\ce{MoS2} FL \cite{Liu2012a} & \ce{(NH4)2MoS4} in DMF solution transport by Ar bubbler or dip-coating onto subs &  annealing under Ar or Ar + Sulfur, total pressure 0.2-2 Torr, \\
 \addlinespace[0.5em]
\ce{MoS2} FL \cite{Wu2013} & \ce{MoS2} powder & Ar flow, 900 \si{\degreeCelsius} heating, pressure 20 Torr, 650 \si{\degreeCelsius} growth\\
 \addlinespace[0.5em]
\ce{MoS2} FL \cite{Mann2013,Najmaei2013,Ji2013} Rice & \ce{MoO3} powders or ribbons, Sulfur & Ar flow, 530-850 \si{\degreeCelsius}, total pressure 0.2-2 Torr, 5-30 min, mica or \ce{SiO2}-Si\\
 \addlinespace[0.5em]
\ce{MoS2} FL \cite{Lee2012b,Ling2014} & 18mg \ce{MoO3} powders, Sulfur,various seeding promoter on sub & 5sccm Ar, 650 \si{\degreeCelsius}, 3 min growth, atmospheric pressure, quick cooling\\

 \midrule
\ce{WS2} films\cite{Ballif1999,Brunken2008} & sputtering \ce{WS_{3+x}} on 10 nm Ni  & annealing under Ar for 1 h at 850 \si{\degreeCelsius} \\
\addlinespace[0.5em]
\ce{WS2} FL \cite{Berkdemir2013} & $\sim$1nm \ce{WO3} coating on 285 nm \ce{SiO2}-Si, 500 mg sulfur & 800 \si{\degreeCelsius} for 30 min, 100 sccm Ar, atmospheric pressure in \cite{Gutierrez2012} and 450 mTorr in \cite{Elias2013}. triangular flakes obtained\\
\addlinespace[0.5em]
\ce{WS2} ML \cite{Cong2013} & 1 mg \ce{WO3} powder on \ce{SiO2}-Si covered by another sub, $d\sim3$ mm, sulfur & 750 \si{\degreeCelsius}, slow heating, hold for 5 min, one-end sealed inner tube, 100 sccm Ar\\
\addlinespace[0.5em]
\ce{WS2} ML \cite{Zhang2013h} & \ce{WO3} powders, sulfur (separate heating) & 900 \si{\degreeCelsius}, sapphire subs, 225 mTorr, Ar 80 sccm and \ce{H2} 10 sccm, growth time 60 min, adjusting precursor and sapphire distance changing the coverage of \ce{WS2}, tube diameter: 1 in. 55 $\mu$m triangular flakes\\
\addlinespace[0.5em]
\ce{WS2} ML \cite{Peimyoo2013} & 1 mg \ce{WO3} powders, sulfur  & \ce{SiO2}/Si subs. Recipe A: 200 mg S,RT-550, Sulfur begin to melt, 550-800 \si{\degreeCelsius}, 5K/min, hold 10mins, 200 sccm Ar. Recipe B: sulfur separated heated at 250 \si{\degreeCelsius}. Total pressure: maybe atmospheric, tube diameter: 2 in. 5 $\mu$m triangular flakes \\
\ce{WS2} FL \cite{Lee2013}  & 1g \ce{WO3} powders, sulfur, \ce{SiO2}-Si subs treated with PTAS \ce{C24H12K4O8} and gentle gas blow & substrate facing down, APCVD, 800 \si{\degreeCelsius}, 5 min, 5 sccm Ar, fast heating. \\
\addlinespace[0.5em]
\ce{WS2} films \cite{Shanmugam2012a}   & 20 nm W on \ce{SiO2}-Si, sulfur & 750 \si{\degreeCelsius}, 200 sccm Ar, 1Torr. Annealing at 1000 \si{\degreeCelsius}, 25 nm thick \ce{WS2} film obtained \\
\bottomrule
\end{tabular}
}
\end{table}
\end{landscape}

\subsection{Raman on bulk and FL TMDC}

This section will discuss previous studies using Raman to characterize \ce{MS2} films, nanotubes, and FL structures. In each morphology, one or two key points will be highlighted for study in this thesis. The previous Raman efforts on \ce{MS2} film, especially the one using resonant conditions, provided critical insight into the electronic structure and lattice dynamics of these TMDC layered materials. Next a comparison of Raman knowledge between TMDC nanotubes and FL structures is given. For \ce{WS2} NTs, focus is on the asymmetry of $A_{1g}$ mode and its origin. And for \ce{WS2} FL structures, layer number dependent fingerprint is summarized, and some attempts on analysis the resonant Raman profiles of \ce{WS2} are made.

It is worth noting that Raman technique proves to be extreme useful in characterizing CNT and graphene, i.e., tube diameter by assigning the RBMs (radial breathing modes) and G peaks position.\cite{Bonaccorso2013} And Raman spectroscopy also qualifies as an excellent tool to monitor tensile features of TMDC in both 2D and tubular forms.\cite{Tang2013}

Raman spectra arise from the inelastic light scattering of optical phonons. In back scattering geometry, the phonon wave-vector stands as $q = 4\pi\frac{n}{\lambda}$. The refractive index $\tilde{n}$ of \ce{WS2} at 532 nm is about $4.726 - 0.737i$. Compared to the size of Brillouin zone ($\pi/a = 10^{10}m^{-1}$), resonant Raman could or could not probe phonon at $M$ point.

Before discussing the Raman spectra features, the author briefly recapitulate some symmetry notations and vibration modes. \ce{MoS2} is used as an example, and those definitions apply to \ce{WS2} as well. Hexagonal \ce{MoS2} belongs to space group $D_{6h}^4$, and the repeat unit in $c$ axis contains two layers, where sulfur atoms in one layer are directly above the molybdenum atoms in adjacent layers, which is often referred as 2H-\ce{MoS2}. Group theory predicts two infrared- and four Raman-active modes for 2H-\ce{MoS2}, which are mutually exclusive when the center of inversion is present. First it should be emphasized that in few layer structures, \ce{MoS2} with odd layers belong to different space group from that of even layers. Bulk MoS$_2$ and 2L-MoS$_2$ belong to the space group P6$_3$/$_{mmc}$ (point group D$_{6h}$). There are 18 normal vibration modes. The factor group of bulk and 2L-MoS$_2$ at $\vec{\Gamma}$ is D$_{6h}$. The atoms site groups are a subgroup of the crystal factor group. The correlation of the Mo site group D$_{3h}$, S site group C$_{3v}$, and factor group D$_{6h}$ allows one to derive the following irreducible representations for the 18 normal vibration modes at $\vec{\Gamma}$: $\vec{\Gamma}$= $A_{1g}+2A_{2u}+2B_{2g}+B_{1u}+E_{1g}+2E_{1u}+2E_{2g}+E_{2u}$, where $A_{2u}$ and $E_{1u}$ are translational acoustic modes, $A_{1g}$, $E_{1g}$ and $E_{2g}$ are Raman active, $A_{2u}$ and $E_{1u}$ are infrared (IR) active. As a contrast, 1L-MoS$_2$ has $D_{3h}$ symmetry with three atoms per unit cell. The irreducible representation of $D_{3h}$ gives: $\vec{\Gamma}$= $2A_2^{''}$+$A_1^{'}$+$2E^{'}$+$E^{''}$, with $A_2^{''}$ and $E^{'}$ acoustic modes, $A_2^{''}$ IR active, $A_1^{'}$ and $E^{''}$ Raman active, and the other $E^{'}$ both Raman and IR active (See Fig.~\ref{fig:ws2ramsch}). NL-MoS$_2$ has 9N-3 optical modes: 3N-1 are vibrations along the c axis, and 3N-1 are doubly degenerate in-plane vibrations. For rigid-layer vibrations, there are N-1 layer breathing modes (LBMs) along the c axis, and N-1 doubly degenerate shear modes perpendicular to it. When N is even, there are 0 Raman active LBMs and $\frac{N}{2}$ doubly degenerate shear modes. When N is odd, there are $\frac{N-1}{2}$ LBMs and N-1 doubly degenerate shear modes.\cite{Wieting1971,Zhang2013e} This discussion can be visualized in Table~\ref{tab:tmslattice}.

% irreducible representation
\begin{table}[htb]
\centering
\caption{Lattices vibration of \ce{MS2}, adopted from ref\cite{Molina-Sanchez2011}}\label{tab:tmslattice}
\begin{tabular}{lcccc}
\toprule
 $D_{6h}$   & $D_{3h}$ & Character &  Direction & Atoms  \\
\midrule
$A_{1g}$    &  $A_1^{'}$   & Raman     & (out of plane)  & S  \\
$E_{2g}^2$  &          &           & (in plane)      & M + S  \\
$E_{2g}^1$  &  $E'$    &           & (in plane)      & M + S  \\
$E_{1g}$    &  $E''$    &           & (in plane)      & S  \\
\midrule
$A_{2u}$    &  $A_2''$  & Infrared  & (out of plane)  & M + S  \\
$E_{1u}$    &          &           & (in plane)      & M + S  \\
\midrule
$A_{2u}$    &  $A_2^{''}$   & Acoustic  & (out of plane)  & M + S  \\
$E_{1u}$    &          &           &       &    \\
\midrule
$B_{2g}^2$  &          & Inactive  & (out of plane)  & M + S  \\
$B_{2g}^1$  &          &           & (out of plane)  & M + S  \\
$B_{1u}$    &          &           & (out of plane)  & S  \\
$E_{2u}$    &          &           & (in plane)      & S  \\
\bottomrule
\end{tabular}
\end{table}

The $E$ type phonon branches correspond to in-plane normal modes, while the $A$ type phonons result from out-of-plane vibrations. $A_{1g}$ mode is an out-of-plane vibration involving only the S atoms while the $E_{2g}^1$ mode involves in-plane displacement of transition metal and S atoms. The $E_{2g}^2$ mode is a shear mode corresponding to the vibration of two rigid layers against
each other and appears at very low frequencies ($<50 cm^{-1}$ \cite{Zhang2013e}). The $E_{1g}$ mode, which is an in-plane vibration of only the S atoms, is forbidden in the backscattering Raman configuration. In 2H-type TMDC, the $A_{1g}$ mode is more sensitive to electrostatic doping, while $E_{2g}^1$ mode is more sensitive to strain, in which the FWHM of the peaks are indicator of external force quantity.\cite{Zhao2013}

\begin{figure}[htb]
\centering
\includegraphics[width=0.7\textwidth]{ws2_ramsch}
\caption[\ce{MS2} vibration symmetry]{\ce{MS2} vibration symmetry in bulk and monalyer, adopted from REF\cite{Ghorbani-asl}}
\label{fig:ws2ramsch}
\end{figure}

Lattice vibration of natural \ce{MoS2} crystal was studied by \citeauthor{Wieting1971} using infrared and Raman spectroscopy.\cite{Wieting1971} It was found the $E_{1u}$ IR mode and one $E_{2g}$ Raman mode are nearly degenerate in energy. 15 optical modes are allowed assuming 6 atoms in primitive cell. Refractive indices from reflectivity measurement were $n_0$= 3.9, $n_e$ = 2.5. \citeauthor{Stacy1985} studied \ce{MoS2} and \ce{WS2} Raman spectra using lasing energy close to the absorption edges.\cite{Stacy1985} Second order scattering from phonon with nonzero momentum is used to explain the rich Raman spectra. \citeauthor{Sourisseau1991} investigated the resonant Raman profiles in 2H-\ce{WS2} using ten different excitation wavelengths.\cite{Sourisseau1991} Dramatic intensity variation at 352 \si{cm^{-1}} was observed, which is assume to be of two-phonon signal nature, and corresponds to an overtone or combination band of phonons with non-zero momenta contributing to indirect gap absorption edge. \citeauthor{Sourisseau1991} assigned this phonon with non-zero momenta as $LA(K_5)$ type. The enhancement of the total Raman cross section at excitonic resonance in which excitons serve as the intermediate state is stronger compared to that of interband resonance. The strong enhancement at excitonic resonance is attributed to the characteristics of excitons in layered materials such as large binding energy, enhanced oscillator strength, and small damping constant.\cite{Zhao2013} \citeauthor{Chung1998} grew \ce{WS2} film using \ce{W(CO)6} and \ce{H2S} precursor.\cite{Chung1998} Raman spectra ($\lambda=632nm$) on films with non-parallel orientation revealed the presence of shoulder mode under $A_{1g}$, which is assigned to LA and TA phonon coupling. This coupling process stems from disorder-activated zone boundary phonons. A further discussion on this non-symmetric feature of $A_{1g}$ mode will be continued in section~\ref{sec:ntram}.

% WS2 Raman assignments
\begin{table}
  \centering
  \caption{\ce{WS2} symmetry assignment}  \label{tbl:ws2raman}
  \begin{tabular}{ccccc}
    \toprule
    &&\multicolumn{3}{c}{Raman Shift (\si{cm^{-1}})}\\
    \cmidrule(l){3-5}
    Symmetry                & Atoms & \ce{WS2} ML\cite{Cong2013}  & \ce{WS2} NT \cite{JMR7990865}  & \ce{WS2} bulk \cite{Sourisseau1991} \\
    \midrule
          $E_{2g}^2(\Gamma)$ &      & 27.5\textsuperscript{\emph{a}}&             &  27.4    \\
    $LA(M)-E_{2g}^2(\Gamma)$ &      & 148.3                        &              &    \\
       TBD                   &      &                              & 153          &      \\
         $E_{2g}^1(M)-LA(M)$ &      &                              & 172          & 173  \\
    LA(M)                    &      & 174.8                        & 172          &       \\
    LA(K)                    &      & 192.4                        &              &  193 \\
    $LA(M)+E_{2g}^2(\Gamma)$ &      & 203                          &              &     \\
    $LA(K)+E_{2g}^2(\Gamma)$ &      & 213.9                        &              &  212  \\
    $A_{1g}(M)-LA(M)$        &      & 230.9                        & 230          &  233  \\
    $2LA(M)-3E_{2g}^2(\Gamma)$ &    & 264.2                        & 262          &  267  \\
    $2LA(M)-2E_{2g}^2(\Gamma)$ &    & 295.4                        & 294          &  297   \\
    $2LA(M)-E_{2g}^2(\Gamma)$ &     & 322.9                        &              &  325   \\
               $E_{2g}^1(M)$ &      & 343.1                        &              &      \\
    2LA(M)                   &      & 350.8                        & 350          &  352\\
          $E_{2g}^1(\Gamma)$ &      & 355.4                        & 350          &  356 \\
    $2LA(M)+2E_{2g}^2(M)$    &      &                              & 381          &  381   \\
     LA + TA \cite{Sourisseau1991} or $B_{1u}(\Gamma)$\cite{Staiger2012}  &      &       &   &  416 \\
          $A_{1g}(\Gamma)$   &      & 417.9                        & 416\textsuperscript{\emph{b}} &  421\\
               3LA(K)        &      & 577                          &              &      \\
       $ LA(M)+ A_{1g}(M)$   &      & 584                          & 581          &  585 \\
    4LA(M)                   &      & 704                          &              &  703\\
    \bottomrule
  \end{tabular}

  \textsuperscript{\emph{a}} Calculated from column values;
  \textsuperscript{\emph{b}} \citeauthor{JMR7990865} probably made incorrect assignment of 416 peak.\cite{JMR7990865}
\end{table}

Raman technique has also provided much insight into the few layer \ce{MS2}. \ce{MS2} layer numbers are readily identified by the wavenumber distance between $A_{1g}$ and $E_{2g}^1$ mode for \ce{MoS2}\cite{Buscema2013} and \ce{WS2}\cite{Berkdemir2013}. Yet due to the relative small shift of $A_{1g}$ mode and little shift of $E_{2g}^1$ mode in \ce{WS2} FL, the frequencies distance might not qualify as an unambiguous way to distinguish layer numbers. Yet the resonant Raman profile on \ce{WS2} exhibit unique features between the intensity of 2LA and $A_{1g}$ mode,\cite{Berkdemir2013,Zhao2013} which provide another routine to assure the monolayer presence. However, the author notice some discrepancy in de-convolution of \ce{WS2} resonant profile between 300 and 400 cm$^{-1}$, i.e., the presence of $E_{2g}^1(M)$ mode at about 344 cm$^{-1}$.\cite{Peimyoo2013,Cong2013,Berkdemir2013} Rigid assignments of this mode still requires further theoretical\cite{Ataca2012} and experimental efforts. In addition, \citeauthor{M2013} reported temperature dependent of 1L \ce{WS2}.\cite{M2013} When the temperature increase from 77 K to 623 K, A1g shift from 420 to 416.5 cm$^{-1}$. Interestingly in this report 2LA/$A_{1g}$ ratio (514 nm excitation) seems less than unit. The spectra were obtain from mechanically exfoliated \ce{WS2} lying on 300 nm \ce{SiO2}-Si substrate. Moreover, The $A_{1g}$ and $E_{2g}^1$ intensities ratio exhibit reverse behaviors under 532 and 632 nm excitation. This is caused by the different cross-section enhancement for a specific excitation condition. The A and B excitonic absorption in \ce{WS2} mainly arise from the $d_{xy}$ and $d_{x^2 - y^2}$ states to $d_{z^2}$ states of tungsten atoms. Thus, electrons excited by 633 nm laser have a character of tungsten $d_{z^2}$ orbitals aligned along the $c$ axis perpendicular to \ce{WS2} basal plane. Since $A_{1g}$ mode involves out of plane displacement along $c$ axis, $A_{1g}$ phonons could couple more strongly with $d_{z^2}$ states than that of $E_{2g}^1$ phonons. As a result, $A_{1g}$ mode is stronger than $E_{2g}^1$ mode at 633 nm resonance.\cite{Zhao2013} However, the reverse effect for 532 nm excitation could not be well explained using the above argument. This may be caused by electron-phonon coupling with other inter-band transition electrons.

\subsection{Raman on TMDC NTs}\label{sec:ntram}

\citeauthor{Dobardzic2005} calculated \ce{MoS2} SWNT phonon dispersion. The dependence of wavenumbers and their displacement on chirality and diameter were discussed. The calculation method enables studying lattice dynamics with NT diameter up to 50 nm. The chiral vector $(n_1, n_2)$ is defined within the molybdenum plane. Symmetry assignment is zigzag when $(n,0)$, armchair when $(n,n)$ and chiral when $(n_1, n_2), n_1>n_2$. \citeauthor{Dobardzic2006} theoretically presented Raman scattering of any polarization on SWNT of \ce{WS2} and their dependence on diameter (1-20 nm) and chiral angle. The author assigned 351 cm$^{-1}$ as $E_u$ for \ce{WS2} NT.\cite{Dobardzic2006} \citeauthor{Ghorbani-Asl2013} discuss the electronic and vibrational properties for large diameter \ce{WS2} NTs\cite{Ghorbani-Asl2013}. Single-walled NT is approximated by 1H monolayer and others by 2H bulk structure. It was found that large-diameter nanotubes can be approximated with layered systems as their properties should be nearly the same at the scale. Only hypothetical SWNTs, and possibly MWNTs with alternating layer compositions, may show direct band gaps. Slight mechanical deformation of the SWNTs would result in a change of the direct band gap back to the indirect one, located between $\Gamma$ and $K$ high-symmetry points, similarly to the monolayers. As for 2D materials, quantum confinement to single-walled tubes would result in direct band-gap semiconductors with $\Delta$ occurring at the $K$ point. Single-walled tubes exhibit slightly softer out-of-plane $A'$ and stronger in-plane $E'$ modes. Those results indicate that the weak interlayer interactions in MS$_2$ materials cannot be associated with the van der Waals interactions only, but most probably with Coulomb electrostatic interactions as well.

Raman signatures of \ce{WS2} nanotubes show distinct features to the spectra of their bulk counterpart. \citeauthor{JMR7990865} observed a new line at 152 cm$^{-1}$ in \ce{WS2} NT, which is absent in 2H-\ce{WS2}.\cite{JMR7990865} Another feature is a emerging shoulder on the low energy side of $A_{1g}$ mode at about 416 cm$^{-1}$. This has been attributed to a combination mode of LA + TA phonons from the $K$ point of Brillouin zone.\cite{Sourisseau1991} The shoulder mode associated with $A_{1g}$ is attributed to LA + TA. As pressure increase from 0 GPa to 18 GPa, these two bands, both shifting to higher wavenumbers, first separate and then recombine. It was assumed the compression mainly occurs in $c$ axis, so the stiffening of $A_{1g}$ is anticipated. A more prominent feature is the resonance profile broadening the shape of $E_{2g}^1$ mode, which is often assigned to 2LA mode. Yet there is different opinion on these assignments. \citeauthor{Molina-Sanchez2011} label the 350 $cm^{-1}$ band as \ce{E_{1u}} instead of 2LA.\cite{Molina-Sanchez2011} And recent theoretical investigations suggest 416 $cm^{-1}$ peak is inactive$B_{1u}$ mode\cite{Molina-Sanchez2011,Ataca2012}, which is the Davydov doublet with $A_{1g}$ mode. \citeauthor{Staiger2012} adopted these assignments in studying the resonance Raman profile of \ce{WS2} NTs.\cite{Staiger2012} It was found that
\begin{enumerate}
\item $B_{1u}$ mode arise from curvature and structural disorder
\item $B_{1u}/A_{1g}$ intensity ratio strongly depends on excitation, and exceeds unity when excitation energy less than 1.9 eV.
\item  An excitonic transition energy of NT is found have a local minimum at about 50 nm, (layer number probably \textgreater 10), and increase either way. Yet all below the bulk value.
\end{enumerate}

\citeauthor{Krause2009} also measured the resonant Raman on \ce{WS2} nanotubes and found a split within 420 cm$^{-1}$ region, which is labelled as $D-A_{1g}$ mode in analog with the similar defect mode of graphene.\cite{Krause2009} This  $D-A_{1g}$ mode was found enhanced as diameter of \ce{WS2} NTs decrease. This thesis work will use $B_{1u}({\Gamma})$ mode to interpret this emerging line at about 416 $cm^{-1}$ of \ce{WS2} NTs, and adopt the 350 $cm^{-1}$ as 2LA(M). \citeauthor{Krause2009a} confirmed $B_{1u}$ mode arise from the inherent structure of \ce{WS2} nanomaterials instead of surface layer effect. It is also worth noting that $A_{1g}$ is stronger than 2LA under 632 nm yet weaker under 532 nm excitation, similar to previous discussion of FL scenarios.\cite{Krause2009a} This is in consistent with our observation of Raman spectra on the \ce{WS2}-\ce{WO3} structures, as discussed later. \citeauthor{Rafailov2005} estimated the orientation dependence of resonant raman on one MWNT \ce{WS2} attached to the cantilever tip of AFM.\cite{Rafailov2005} Antenna effect lead to optical transition occurring only for polarization parallel to nanotube axis. And therefore resonance Raman intensity of SWNT varies as nanotube orientation. This dependence may provide a routine to distinguish different chiral NTs. Polarized Raman spectra (632 nm excitation) is obtained, showing $A_{1g}$ and $E_{2g}$ sharing the same polarization behavior. \citeauthor{Virsek2007} investigated the Raman scattering ($\lambda=632$ nm) of \ce{WS2} NTs.\cite{Virsek2007} The silicon peak at 520 cm$^{-1}$ is used for calibration. Up-shift of $A_{1g}$ and $E_{2g}$ modes (i.e. 420 to 423 cm$^{-1}$ at $A_{1g}$ mode) were observed, which is attributed to the strain in 3R stacking layers.

As a useful reference, the lattices dimensions are summarized in Table~\ref{tab:ms2lattice},
%lattice
\begin{table}[htb]
\centering
\caption{Lattices dimension of \ce{MS2}}\label{tab:ms2lattice}
\begin{tabular}{lccr}
\toprule
         &  & 2H-\ce{MoS2}\cite{Coehoorn1987,Ataca2012} & 2H-\ce{WS2}\cite{Albe2002,Schutte1987} \\
\midrule
Lattice constant & a(\AA) & 3.1604 & 3.171 \\
                 & c(\AA) & 12.295 & 12.359 \\
Within \ce{MS2} layer & M-3S (\AA)& 2.37  & 2.405   \\
                      & S-1S (\AA)& 3.11  & 3.14   \\
Between \ce{MS2} layer& S-3S (\AA)&   & 3.53   \\
\bottomrule
\end{tabular}
\end{table}

### 2014-08-09 BackMatter/paper.tex
citation style to none sorting

@@
 \section{WO3}
+
+SG and FG experiments remain essentially the same as that of OT growth, except that in SG additional tungsten powders were distributed onto the receiving substrate, and in FG more than one piece of substrate was employed.
+The modification is schematically illustrated in Fig.~\ref{fig:wogrowsf}.
+More details will be provided when it comes to the discussion.
+% sg fg
+\begin{figure}[htb]
+\centering
+\includegraphics[width=0.5\textwidth]{sg_and_fg.jpg}
+\caption[\ce{WO3} NW growth: SG and FG]{\ce{WO3} NW growth: SG and FG. (a) Seeded growth with additional powders on substrate (b) Flow growth with multiple substrates}
+\label{fig:wogrowsf}
+\end{figure}
+
+With four kinds of W powders and three layouts, we designed the experimental matrix as illustrated in Table.~\ref{tab:matrix}.
+The symbol $\times$ means this combination is covered in this work, and NA means otherwise.
+% Tungsten powders growth design
+\begin{table}[htb]
+\centering
+\caption{Tungsten powders growth design}\label{tab:matrix}
+\begin{tabular}{lccr}
+\toprule
+ & Ordinary Transport & Seeded growth & Flow growth \\
+\midrule
+3N   &  $\times$ & NA &  NA   \\
+3N5  &  $\times$ & NA &  NA   \\
+4N5  &  $\times$ & $\times$ & $\times$ \\
+5N   &  $\times$ & $\times$ &  $\times$ \\
+\bottomrule
+\end{tabular}
+\end{table}
+
+We will first present the OT growth results in section~\ref{sec:nawox}, and discuss the other two in section~\ref{sec:sgfg}.
+
+We found the growth using 3N source show distinctive features in comparison to the rest.
+This mainly arise from the higher sodium concentration in 3N source than that in others.
+Therefore we focus on 3N source first, and move on to other latter.
 
@@
 \section{TMS}
+Other chalcogenide has also been synthesized using this one-end sealed layout.\cite{Mukherjee2013}
+\citeauthor{Zou2007} prepared W/\ce{WS2} core-shell NPs by reaction of tungsten and sulfur under hydrogen atmosphere.\cite{Zou2007}
 

### 2014-08-09 ch-wox/ch-wox.tex
citation style to none sorting

@@
 
-% \input{./ch-wox/part1}
+ \input{./ch-wox/part1}
 
@@
 % Tungsten powders size and purity
+\begin{table}
 \centering
@@
 
-In a typical OT experiment (Fig.~\ref{fig:wogrow}), about 2g tungsten powder was positioned in the upstream end of a quartz boat and downstream about 2.5 inches the substrate was stationed.
+In a typical OT experiment (Fig.~\ref{fig:wogrow}), about 2 g tungsten powder was positioned in the upstream end of a quartz boat and downstream about 2.5 in the substrate was stationed.
 The substrates were p-type, boron-doped and [100]-orientated silicon with about 1 $\mu m$ thermally-grown silicon oxide layer on the polished side.
-The cleaning procedures have been elucidated in Chapter 1 section.
-The boat was then loaded into reaction chamber in a way that the powder source was placed in the center of heating zone, and the substrate upstream end was aligned at 6.5in.\footnote{As defined in Fig.~\ref{fig:wogrow}} After pumping down, 1 sccm \ce{O2} and 10 sccm Ar were admitted into the chamber, respectively, after which the overall pressure read approximately 110 mTorr.
-The temperature ramped up to 1000 \si{\degreeCelsius} in 30 minutes and lasted for 4 hours, and subsequently the apparatus was allowed to naturally cool down to room temperature.
+The cleaning procedures have been elucidated on page.~\pageref{ch2sub}.
+The boat was then loaded into reaction chamber in a way that the powder source was placed in the center of heating zone, and the substrate upstream end was aligned at 6.5 in.\footnote{As defined in Fig.~\ref{fig:wogrow}} After pumping down, 1 sccm \ce{O2} and 10 sccm Ar were admitted into the chamber, respectively, after which the overall pressure read approximately 110 mTorr.
+The temperature ramped up to 1000 \si{\degreeCelsius} in 30 min and lasted for 4 h, and subsequently the apparatus was allowed to naturally cool down to room temperature.
 % cvd NW growth
@@
 
-SG and FG experiments remain essentially the same as that of OT growth, except that in SG additional tungsten powders were distributed onto the receiving substrate, and in FG more than one piece of substrate was employed.
-The modification is schematically illustrated in Fig.~\ref{fig:wogrowsf}.
-More details will be provided when it comes to the discussion.
-% sg fg
-\begin{figure}[htb]
-\centering
-\includegraphics[width=0.5\textwidth]{sg_and_fg.jpg}
-\caption[\ce{WO3} NW growth: SG and FG]{\ce{WO3} NW growth: SG and FG. (a) Seeded growth with additional powders on substrate (b) Flow growth with multiple substrates}
-\label{fig:wogrowsf}
-\end{figure}
-
-With four kinds of W powders and three layouts, we designed the experimental matrix as illustrated in Table.~\ref{tab:matrix}.
-The symbol $\times$ means this combination is covered in this work, and NA means otherwise.
-% Tungsten powders growth design
-\begin{table}[htb]
-\centering
-\caption{Tungsten powders growth design}\label{tab:matrix}
-\begin{tabular}{lccr}
-\toprule
- & Ordinary Transport & Seeded growth & Flow growth \\
-\midrule
-3N   &  $\times$ & NA &  NA   \\
-3N5  &  $\times$ & NA &  NA   \\
-4N5  &  $\times$ & $\times$ & $\times$ \\
-5N   &  $\times$ & $\times$ &  $\times$ \\
-\bottomrule
-\end{tabular}
-\end{table}
-
-We will first present the OT growth results in section~\ref{sec:nawox}, and discuss the other two in section~\ref{sec:sgfg}.
-
 \subsection{Tungsten Oxides by OT}\label{sec:nawox}
 
-We have investigated the growth dynamics of each source in OT configuration.
-In each experiments, we control the temperature, flow rate and source and substrate locations.
-Another parameter we found important is the growth number\footnote{Defined as the order of growth performed in the same reaction chamber} in the same reaction chamber.
+The growth dynamics of each source were investigated in OT configuration.
+In each experiment, the temperature, flow rate and source and substrate locations were controlled.
+Another parameter the author found important is the growth number\footnote{Defined as the order of growth performed in the same reaction chamber} in the same reaction chamber.
 Usually one will conduct several runs in the same chamber, and different results may arise with respect to the growth number.
-With this degree of freedom included, we first summarized the primary features of deposition and the associated parameters in Table~\ref{tab:wot}.
+With this degree of freedom included, the primary features of the deposition and the associated parameters were summarized in Table~\ref{tab:wot}.
 % \ce{WO_x} ordinary transport results
@@
 
-We found the growth using 3N source show distinctive features in comparison to the rest.
-This mainly arise from the higher sodium concentration in 3N source than that in others.
-Therefore we focus on 3N source first, and move on to other latter.
-
-Before diving into the growth of \ce{WO3} and \ce{Na_xWO3} nanostructures using 3N powders, we would like to examine the metallic W source itself and its changes after growth.
-The SEM images of all powders before and  after growth are shown in Fig.~\ref{fig:pdbefore} and Fig.~\ref{fig:pdafter}, respectively.
+The change of metallic W source after growth carries important information on the growth.
+So before examining the deposition on substrates, the SEM images of all powders before and after growth are presented in Fig.~\ref{fig:pdbefore} and Fig.~\ref{fig:pdafter}, respectively.
 % powder before growth
@@
 \includegraphics[width=0.6\textwidth]{pd_before.jpg}
-\caption[SEM images of W powder before growth]{SEM images of W powder before growth.(a) 3N, (b) 3N5, (c) 4N5 and (d) 5N. }
+\caption[SEM images of W powder before growth]{SEM images of W powder before growth for (a) 3N, (b) 3N5, (c) 4N5 and (d) 5N, respectively.}
 \label{fig:pdbefore}
@@
 Tungsten metals crystallize in body center cubic (BCC) phase.
-Overall, we can still discern the facets.
+Overall, the facets were still discernible.
 The 4N5 and 5N powders share similar appearance and size distribution (Fig.~\ref{fig:pdbefore}c-d).
 In contrast, 3N powders are almost half the size of 3N5 ones, and have more uniform size distribution as well.
-Absolute size and its distribution play a key role in its usage as seed, which we will talk more in Section~\ref{sec:sgfg}.
+Absolute size and its distribution play a key role in its usage as seed, as discussed in Section~\ref{sec:sgfg}.
 % powder after growth
@@
 \includegraphics[width=0.6\textwidth]{pd_after.jpg}
-\caption[SEM images of W powder after growth]{SEM images of W powder after growth.(a) 3N, (b) 3N5, (c) 4N5 and (d) 5N. }
+\caption[SEM images of W powder after growth]{SEM images of W powder after growth for (a) 3N, (b) 3N5, (c) 4N5 and (d) 5N. }
 \label{fig:pdafter}
@@
 After growth, 4N5 and 5N powder (Fig.~\ref{fig:pdafter}c-d) both develop the round edges, while 3N and 3N5 powders (Fig.~\ref{fig:pdafter}a-b) become bundled rods.
-This difference mainly arise from the average size.
+This difference mainly arises from the average size, which will dictate the degree of oxidation.
 
@@
 The sodium contents in 3N powders fundamentally change the deposition in OT growth.
-Typical morphologies of the as-synthesized nanostructures grown on a \ce{SiO2}-Si substrate was shown in Fig.~\ref{fig:nawoxsemedx}a.
-The nanostructures are NWs with lengths from tens microns up to several hundred microns and diameters about 40 to 500 nm.
+Typical morphologies of the as-synthesized nanostructures grown on a \ce{SiO2}-Si substrate were shown in Fig.~\ref{fig:nawoxsemedx}a.
+The nanostructures were \glspl{nw} with lengths up to several hundred microns and diameters about 40 to 500 nm.
 The deposition of nanowires was generally located on the substrates with a growth temperature range from 660 to 420 \si{\degreeCelsius}.
 Close-up observations at high magnification revealed some nanowires were cylinder-shaped and some were belt-shaped.
-At some locations, microplate structures with a regular rectangular shape grew among the nanowires as demonstrated in Fig.~\ref{fig:nawoxsemedx}b and its inset.
-The chemical compositions of the deposition were identified by EDX.
+At lower temperature end of substrate, microplate structures with a rectangular shape grew among the nanowires as displayed in Fig.~\ref{fig:nawoxsemedx}b and inset.
+The chemical compositions of the deposition were analyzed using EDX.
 A representative EDX spectrum in Fig.~\ref{fig:nawoxsemedx}c shows the existence of W, Na, O, and Si signals in the specimen, where the Si signal is from the substrate.
@@
 The diffraction peaks were carefully indexed and the deposition was identified as two phases of sodium tungsten oxides and one phase of tungsten oxide as indicated on Fig.~\ref{fig:nawoxsemedx}d.
-The two sodium tungsten oxide phases are the triclinic \ce{Na5W_{14}O_{44}} phase\footnote{ICDD PDF 04-012-4449,\emph{a}=7.2740\AA, \emph{b}=7.2911\AA, \emph{c}=18.5510\AA, $\alpha$=96.3750$^\circ$, $\beta$=90.8920$^\circ$, $\gamma$=119.6560$^\circ$} and the triclinic \ce{Na2W4O_{13}} phase.\footnote{ICDD PDF 04-012-7108,\emph{a}=11.1630\AA, \emph{b}=3.8940\AA, \emph{c}=8.2550\AA, $\alpha$=90.60$^\circ$, $\beta$=131.36$^\circ$, $\gamma$=79.70$^\circ$} The tungsten oxide is the monoclinic \ce{WO3} phase.\footnote{ICDD PDF 01-083-0950,\emph{a}=7.30084\AA, \emph{b}=7.53889\AA, \emph{c}=7.6896\AA, $\beta$=90.8920$^\circ$}
+The two sodium tungsten oxide phases are the triclinic \ce{Na5W_{14}O_{44}} phase (ICDD PDF 04-012-4449, \emph{a}=7.2740 \AA, \emph{b}=7.2911 \AA, \emph{c}=18.5510 \AA, $\alpha$=96.37$^\circ$, $\beta$=90.89$^\circ$, $\gamma$=119.65$^\circ$) and the triclinic \ce{Na2W4O_{13}} phase.\footnote{ICDD PDF 04-012-7108, \emph{a}=11.1630 \AA, \emph{b}=3.8940 \AA, \emph{c}=8.2550 \AA, $\alpha$=90.60$^\circ$, $\beta$=131.36$^\circ$, $\gamma$=79.70$^\circ$} The tungsten oxide is the monoclinic \ce{WO3} phase.\footnote{ICDD PDF 01-083-0950, \emph{a}=7.30084 \AA, \emph{b}=7.53889 \AA, \emph{c}=7.6896 \AA, $\beta$=90.89$^\circ$}
 
@@
 To obtain detailed information on the crystallinity, composition, and growth direction of the nanostructures, TEM analyses with imaging, electron diffraction, and EDX were performed on more than 20 nanowires.
-The majority of the nanowires were identified as the \ce{Na5W_{14}O_{44}} phase.
-(Fig.~\ref{fig:nawoxtem}a-c) The HRTEM image in Fig.~\ref{fig:nawoxtem}b reveals that the nanowire has a single-crystalline structure.
+The majority of the nanowires were identified as the \ce{Na5W_{14}O_{44}} phase (Fig.~\ref{fig:nawoxtem}a-c).
+The HRTEM image in Fig.~\ref{fig:nawoxtem}b reveals that the nanowire exhibits a single-crystalline structure.
 The corresponding diffraction pattern in the inset of Fig.~\ref{fig:nawoxtem}b was recorded in $[\bar{1}10]$ axis.
@@
 The growth direction of \ce{Na5W_{14}O_{44}} NWs was determined to be parallel to the (001) plane.
-The chemical composition of the nanowire was revealed by EDX.
-Fig.~\ref{fig:nawoxtem}c shows the nanowire consisted of W, Na, and O.
-No other impurities were detected.\footnote{The Cu and C signals come from the supporting Cu grid with lacey carbon and the Cr signal from the tip of JEOL double tilt holder.
-They are not compositions from the nanowires and other structures studied here.} Small fraction of nanowires were found to be the monoclinic \ce{WO3} phase.
+EDX measurement (Fig.~\ref{fig:nawoxtem}c) shows the nanowire consisted of W, Na, and O.
+No other elements were detected.\footnote{The Cu and C signals come from the supporting Cu grid with lacey carbon and the Cr signal from the tip of JEOL double tilt holder.} Small fraction of nanowires were found to be the monoclinic \ce{WO3} phase.
 (Fig.~\ref{fig:nawoxtem}d-f) The SAED shown in the inset of Fig.~\ref{fig:nawoxtem}e was recorded in [100] zone.
@@
 Normalized to the highest W peak, the Na peak intensity in Fig.~\ref{fig:nawoxtem}i is higher than the one in Fig.~\ref{fig:nawoxtem}c.
-This result indicates a higher Na:W ratio for the \ce{Na2W4O_{13}} plate structure than the one for \ce{Na5W_{14}O_{44}} nanowires, in consistent with the compositions of the two phases.
+This result indicates a higher Na:W ratio for the \ce{Na2W4O_{13}} plate structure than that of \ce{Na5W_{14}O_{44}} nanowires, in consistent with the compositions of the two phases.
 
@@
 Micro-Raman spectroscopy was also carried out at room temperature in ambient atmosphere to confirm the phases of the microplates and ultra-long nanowires.
-Fig.~\ref{fig:nawoxram}a shows the mRaman spectrum of the microplates.
-The Raman lines at 949, 794-777, 366-263 \si{cm^{-1}} closely matches the reported \ce{Na2W4O_{13}} Raman shift frequencies.
-\cite{Fomichev1992} The Raman spectrum from the ultra-long nanowires is shown in Fig.~\ref{fig:nawoxram}b.
+Fig.~\ref{fig:nawoxram}a shows the m-Raman spectrum of the microplates.
+The Raman lines at 949, 794-777, 366-263 \si{cm^{-1}} closely matches the reported \ce{Na2W4O_{13}} Raman shift frequencies.\cite{Fomichev1992} The Raman spectrum from the ultra-long nanowires is shown in Fig.~\ref{fig:nawoxram}b.
 The spectrum shows major peaks in 100-150 \si{cm^{-1}}, 650-900 \si{cm^{-1}}, and 900-100 \si{cm^{-1}} regions.
 As compared to the reported peak positions (shown by reference lines in Fig.~\ref{fig:nawoxram}b), the nanowires consist of only little or no amount of \ce{WO3} and \ce{Na2W4O_{13}} phases.
-Major peaks at 107, 695, 765, 913, 943, and 965 \si{cm^{-1}} cannot be fitted.
+Major peaks at 107, 695, 765, 913, 943, and 965 \si{cm^{-1}} cannot be assigned to reference in literatures.
 According to the TEM results, the nanowires are mainly \ce{Na5W_{14}O_{44}}, therefore these peaks should belong to the \ce{Na5W_{14}O_{44}} phase.
-Sofar no Raman spectrum has been reported this phase, hence we are probably the first to observe the Raman spectrum for \ce{Na5W_{14}O_{44}}.
+So far no Raman spectrum has been reported for this phase, hence this is probably the first observed Raman pattern for \ce{Na5W_{14}O_{44}}.
 
@@
 \end{equation}
-And the standard deviation of estimating \ce{W-O} bond distance from Raman stretching wavenumber is $\pm0.034$\AA.
-The observed Raman peaks of \ce{Na5W_{14}O_{44}} phase lies at 965, 943, 913, 808, 786, 778, 765, 695 and 107 cm.
-Multi-peaks Lorentzian fitting is preformed to precisely determine the central maximum.
+And the standard deviation of estimating \ce{W-O} bond distance from Raman stretching wavenumber is $\pm0.034$ \AA.
+The observed Raman peaks of \ce{Na5W_{14}O_{44}} phase lies at 965, 943, 913, 808, 786, 778, 765, 695 and 107 \si{cm^{-1}}.
+Multi-peak Lorentzian fitting is preformed to precisely determine the central maximum.
 Good fitting is obtained, as shown in Fig.~\ref{fig:naworamfit}.
-We then calculated \ce{W-O} bond distance using Eq.~\ref{eq:wobond}, as illustrated in Table~\ref{tab:nawobond}.
-The predicted \ce{W-O} bond length comply very well with the crystallographic value of \ce{Na5W_{14}O_{44}} phase.\cite{Triantafyllou1999a} The 107 peak probably is caused by \ce{Na-O} bond.
+The calculated \ce{W-O} bond distances using Eq.~\ref{eq:wobond} are listed in Table~\ref{tab:nawobond}.
+The predicted \ce{W-O} bond lengths comply very well with the crystallographic value of \ce{Na5W_{14}O_{44}} phase.\cite{Triantafyllou1999a} The 107 \si{cm^{-1}} peak probably is caused by \ce{Na-O} bond.
 % Na5 raman fitting
@@
 \includegraphics[width=0.6\textwidth]{naxwo_ramfit}
-\caption[\ce{Na5W_{14}O_{44}} Raman fitting]{Multi-peaks Lorentzian fitting on two major peaks region of \ce{Na5W_{14}O_{44}}.
+\caption[\ce{Na5W_{14}O_{44}} Raman fitting]{Multi-peak Lorentzian fitting on two major peaks region of \ce{Na5W_{14}O_{44}}.
 The peaks sum height difference is caused by different baseline value adopted in each fitting.}
@@
 \caption{\ce{W-O} bond length predication}\label{tab:nawobond}
-\begin{tabular}{lccr}
+\begin{tabular}{cccc}
 \toprule
-peak center & length (\AA) & peak center & length (\AA) \\
+peak center (\si{cm^{-1}}) & length (\AA) & peak center (\si{cm^{-1}}) & length (\AA) \\
 \midrule
@@
 
-Heated at elevated temperatures, the W source, quartz tube, and quartz boat were the three possible sources for Na.
+Heated at elevated temperatures, the W precursor, quartz tube, and quartz boat were three possible sources for Na.
 The sodium concentration in 3N source was 20ppm as provided by vendor.\footnote{Due to the non-uniform distribution of foreign elements, detection of sodium by EDX is possible although the concentration is below the limit of typical EDX capacity.} The Na concentrations in quartz tube and quartz boat (GE 214 quartz, Wilmad Labglass) were 1 ppm and 0.7 ppm,  respectively.
 To confirm the major source of Na content coming from 3N powder, control experiments were employed by using W source with higher purities (4N5 or 5N).
-These ultra-high purity W sources produced pure tungsten oxide deposition.
-No Na content was detected.
-These results verified the Na content was mainly from the 3N W powders, not from the quartz tube and boat.
+These ultra-high purity W sources produced pure tungsten oxide deposition and no Na content was detected by EDX.
+These results verified the Na content was mainly from the 3N W powders.
 In the experiments, the W source was first slowly oxidized at 1000 \si{\degreeCelsius} with 1 sccm \ce{O2} and the oxidized source was then evaporated producing \ce{WO3} and other substoichiometric tungsten oxide vapors.
-The tungsten oxide vapors produced this way were limited by the slow oxidation, as indicated by (i) only small amount of the tungsten source was consumed during the growth and (ii) only the top layer of the tungsten source was oxidized with a dark blue color.
+The tungsten oxide vapors produced this way were limited by the slow oxidation, as indicated by (i) only small amount of the tungsten source was consumed during the growth and (ii) only the top layer of the tungsten source was oxidized showing a dark blue color after growth.
 Due to its low concentration, the exact composition of the Na content in the tungsten source is not clear.
-However, the evaporation rate of the Na content is expected to be high as heated at 1000 \si{\degreeCelsius}.
+However, the evaporation rate of the Na content is expected to be high when heated at 1000 \si{\degreeCelsius}.
 This assumption is supported by the observation that no Na was found in the deposition along the whole substrate in control experiments using the used 3N W source.
 Put it in another way, this means that the majority of Na content was already evaporated in previous experiment.
-Hence, despite of its low concentration in the source, the total amount of Na-based vapors produced during the growth was comparable to or more than the amount of tungsten oxide vapors and resulted in the dominating deposition of sodium tungsten oxide phases in the nanowire growth region.
+Hence, despite of its low concentration in the source, the total amount of Na-based vapors produced during the growth was significant, resulting in the dominance of sodium tungsten oxide phases in the nanowire growth region.
 
@@
 
-As shown by the photograph in Fig.~\ref{fig:nawoxser}a, for a series of growth performed in the same reaction chamber, the morphology of the nanowires changes with the increase of growth numbers.
-Three growth zones of nanowires can be identified in basis of the coverage and density of the nanowires, as delimited by the vertical guide line.
+As shown by the photograph in Fig.~\ref{fig:nawoxser}a, for a series of growth performed in the same reaction chamber, the morphology of the nanowires changes with the increase of growth number.
+Three growth zones of nanowires can be identified on basis of the coverage and density of the nanowires, as delimited by the vertical guide line.
 The growth Zone I was located at high temperature end ranging from 660 to 520 \si{\degreeCelsius}, Zone II was from 520 to 470 \si{\degreeCelsius}, and Zone III from 470 to 420 \si{\degreeCelsius}.
@@
 For the first growth (Fig.~\ref{fig:nawoxsemall}a-c) in a new clean reaction chamber, there were only a little nanowires scattered in Zone I (Fig.~\ref{fig:nawoxsemall}a), ultra-long nanowires were mostly found in Zone II with higher density and coverage (Fig.~\ref{fig:nawoxsemall}b), and in Zone III the coverage, density, and length of nanowires gradually reduced as the growth location moved downstream (Fig.~\ref{fig:nawoxsemall}c).
-With growth number increased to the third growth (Fig.~\ref{fig:nawoxsemall}d-f) and to the fifth growth (Fig.~\ref{fig:nawoxsemall}g-i), the coverage, density, and length of the nanowires increased in all three zones.
-Zone I had the most significant morphology changes as shown by Fig.~\ref{fig:nawoxser}a and Fig.~\ref{fig:nawoxsemall}g.
-After fifth growth in the same reaction chamber, the deposition of ultra-long nanowires almost covered all three zones.
-For Zones I and II, no significant morphology change was observed with further increase of the growth number up to 8th growth.
+With growth number increased to 3 (Fig.~\ref{fig:nawoxsemall}d-f) and 5 (Fig.~\ref{fig:nawoxsemall}g-i), the coverage, density, and length of the nanowires increased in all three zones.
+Zone I saw the most significant morphology changes as shown by Fig.~\ref{fig:nawoxser}a and Fig.~\ref{fig:nawoxsemall}g.
+After the fifth growth in the same reaction chamber, the deposition of ultra-long nanowires almost covered all three zones.
+For Zones I and II, no significant morphology change was observed with further increase of the growth number up to 8.
 However, for Zone III the microplate structures (shown in inset of Fig.~\ref{fig:nawoxsemall}i) kept increasing significantly with the growth number.
-EDX study revealed the change of Na concentration in the deposition with the growth number.
+EDX study revealed the variation of Na concentration in the deposition with the growth number.
 Fig.~\ref{fig:nawoxser}b shows the variation of the Na/W ratios with the increase of growth number at different nanowire growth zones.
 Generally, the Na/W ratios at all growth zones increased with the increase of growth number.
-The large fluctuation of Na/W ratio at Zone III was mainly due to the uneven distribution of Na content with different morphologies at Zone III.
+The large fluctuation of Na/W ratio at Zone III was presumably due to the uneven distribution of Na content with different morphologies at Zone III.
 
@@
 
-A mechanism of residue deposition enhanced growth was proposed to explain the morphology change of the nanowires with the growth number.
-Since the CVD setup employed here is a hot-wall CVD system, deposition formed on the substrate surface as well as on the inner wall of the reaction chamber in the growth area.
-Residue deposition was fund on the quartz tube which can be distinguished by the color change on the quartz tube after each growth.
+A mechanism of residue deposition enhanced growth was proposed to explain the morphology evolution of the nanowires with the growth number.
+Since the CVD setup employed in this thesis is a hot-wall system, deposition formed on the substrate surface as well as on the inner wall of the reaction chamber in the growth area.
+Residue deposition was found on the quartz tube which can be distinguished by the color change on the quartz tube after each growth.
 With the increase of growth number for the same reaction chamber, the residue deposition on the inner wall of the tube also increased.
@@
 To prove this hypothesis, control experiments were performed utilizing a quartz tube used multiple times previously (e.g., a growth number of 9).
-The experiments were carried out without any source materials while other growth parameters remain unchanged.
+The experiments were carried out without any source materials while other growth parameters remain the same.
 Similar nanowires were found on the substrate in the nanowire growth zones.
@@
 This result confirmed the nanowire growth could be enhanced by the presence of the residue deposition and explained the morphology changes of the nanowires with the increase of growth number.
-
+% xrd na5
 \begin{figure}[htb]
@@
 The sodium contents from the residue deposition will join the new Na contents from the W source forming deposition.
-Fig.~\ref{fig:nawoxxrd} shows the XRD spectra of a series of specimens with the growth number increases from 1 to 5.
-The XRD spectra also reveal the revolution of the three phases with changes of relative concentrations as the growth number increases.
+Fig.~\ref{fig:nawoxxrd} displays the XRD spectra of a series of specimens with the growth number increases from 1 to 5.
+The XRD spectra reveal the relative concentration dynamics of the three phases as the growth number increases.
 Compared to the \ce{WO3} phase, the \ce{Na5W_{14}O_{44}} and the \ce{Na2W4O_{13}} phases increase significantly as the growth number increase from 1 to 5.
 And in the 5th growth, \ce{Na2W4O_{13}} become the dominated phase compared to the other two phases.
-These results are consistent with the SEM observation (Fig.~\ref{fig:nawoxsemall}) and the composition change from the EDS measurements (Fig.~\ref{fig:nawoxser}b).
+These results are consistent with the SEM observation (Fig.~\ref{fig:nawoxsemall}) and the composition change from the EDX measurements (Fig.~\ref{fig:nawoxser}b).
 
@@
 \end{figure}
-It is worth pointing out that we found some NWs growth in low temperature end associated with 4N5 (Fig.~\ref{fig:wox4n5}c), although the density is not large.
-We managed to enhance the coverage as discussed in Section~\ref{sec:sgfg}.
+It is worth pointing out that there are some NWs growth in low temperature end associated with 4N5 (Fig.~\ref{fig:wox4n5}c), although not in large scale.
 % 4N5 powder growth
@@
 \caption[SEM images of \ce{WO3} growth using 4N5 powder]{SEM images of \ce{WO3} growth using 4N5 powder showing the morphology variation from (a) high temperature and (b) intermediate temperature, to (c) low temperature.
-Growth with 5N powders have almost the same morphology with that of 4N5, and is not shown in this work}
+Growth with 5N powders have almost the same morphology with that of 4N5, and is not shown hereby.}
 \label{fig:wox4n5}
@@
 \end{figure}
-TEM to be done on D8.
+%TEM to be done on D8.
 % fg tem

### 2014-08-09 ch-tms/tms.tex
tms pl results added

@@
 
+PL was examined with core-shell NWs on insulating \ce{SiO2}-Si substrates.
+A typical Raman spectrum from 160 to 6000 \si{cm^{-1}} is presented in Fig.~\ref{fig:ws2ramall}.
+This pattern was acquired on the middle spot of the core-shell NW shown as inset.
+Using 532 nm excitation, the multi-phonon resonant feature was clearly resolved.
+A broad PL peak was also observed with center at 628 nm and FWHM of 23 nm, corresponding to a photon energy of 1.974 eV with width of 72 meV.
+
+% ws2/wo3 on sio2,1 
+\begin{figure}[htb]
+\centering
+\includegraphics[width=0.75\textwidth]{ws2_sio2_all}
+\caption[Raman spectrum of \ce{WO3}-\ce{WS2} on \ce{SiO2}-Si 1]{Raman spectrum acquired on the middle spot of core-shell NW (inset) using 532 nm. The $x$ axis is in logarithmic scale.}
+\label{fig:ws2ramall}
+\end{figure}
+
+Another feature is the presence of three peaks centering at 1860, 3695, and 5500 \si{cm^{-1}}, respectively, where the latter two is probably the secondary and third overtone of the first peak.
+The origin of this peak family is still under research.
+A possible candidate points at the hydrocarbon contamination attached onto the core-shell NWs, as already been observed using TEM imaging.
+Interesting the intensity of this three-peak family attenuated significantly when using 441 nm excitation, as shown in Fig.~\ref{fig:ws2ramblue}.
+This comparison suggested there might be some enhancement mechanism from \ce{WS2} resonant Raman vibrations.
+
+\begin{figure}[htb]
+\centering
+\includegraphics[width=0.5\textwidth]{ws2_sio2_all_blue}
+\caption[Raman spectrum of \ce{WO3}-\ce{WS2} on \ce{SiO2}-Si 2]{Raman spectrum acquired on the middle spot of core-shell NW shown in the inset of Fig.~\ref{fig:ws2ramall}.}
+\label{fig:ws2ramblue}
+\end{figure}
+
+Three Raman sites were chosen to probe possible layer variation using both 532 and 441 nm, with the naming displayed in the inset of Fig.~\ref{fig:ws2ramall}.
+The Raman patterns are shown in Fig.~\ref{fig:ws2ram3site}a-b.
+The off-resonance profile in Fig.~\ref{fig:ws2ram3site}b shows only two modes, with $E_{2g}^1$ mode at about 357 \si{cm^{-1}} and $A_{1g}$ mode at $418\sim419$ \si{cm^{-1}}.
+In contrast, the on-resonance profile in Fig.~\ref{fig:ws2ram3site}a exhibits much richer spectra.
+The shoulder mode at tip2 spectrum is a manifestation of $B_{1u}$ mode from curved \ce{WS2} layer.
+According to previous analysis, the apparent ratio between in-plane and out-of-plane vibration indicates site tip2 has multi-wall \ce{WS2}, and the other two possibly have few-wall \ce{WS2}.
+
+\begin{figure}[htb]
+\centering
+\subfloat[]{\label{fig:green}\includegraphics[width=0.45\textwidth]{ws2_sio2_raman_green}}\hspace{0.04\textwidth}
+\subfloat[]{\label{fig:blue}\includegraphics[width=0.45\textwidth]{ws2_sio2_raman_blue}}
+\caption[Raman spectrum of \ce{WO3}-\ce{WS2} on \ce{SiO2}-Si 3]{Raman scattering from (a) 532 nm and (b) 441 nm excitation scanned along the core-shell NW.}
+\label{fig:ws2ram3site}
+\end{figure}
+
+This predication is confirmed by the associated PL measurement as displayed in Fig.~\ref{fig:ws2plgreen}.
+Strong luminescent peaks were found at site mid and tip1, and an extremely weak from site tip2.
+The PL peaks centered at 1958 and 1934 meV for mid and tip1, respectively.
+The second and third order peaks also show up on all three Raman sites.
+
+\begin{figure}[htb]
+\centering
+\includegraphics[width=0.6\textwidth]{core-shell-sio2-pl_green}
+\caption[PL spectra of \ce{WO3}-\ce{WS2} on \ce{SiO2}-Si]{PL spectrum acquired on the core-shell NW shown in the inset of Fig.~\ref{fig:ws2ramall}.}
+\label{fig:ws2plgreen}
+\end{figure}
+
 \section{summary}

### 2014-08-09 figure_table.tex
moo3 draft 50%
minor changes in supp tex files
tms pl results added

@@
+\si{\degreeCelsius}
+
 \subsection{artwork}
@@
 
+\begin{equation}\label{eq:mclns}
+\cee{MoCl5(WCl6) + S \rightarrow MoS2(WS2) + S2Cl2}.
+\end{equation}
+
  WO3: dielectrics constants: $\epsilon_\alpha = 6.52,\epsilon_\infty > 50$. \cite{Deb2008}
@@
 \centering
+\subfloat[]{\label{fig:mosem1}\includegraphics[width=0.45\textwidth]{mosemsi_a}}\hspace{0.04\textwidth}
+\subfloat[]{\label{fig:mosem2}\includegraphics[width=0.45\textwidth]{mosemsi_b}}
+\caption[Representative morphologies of \ce{MoO3} on Si]{(a) Low magnification and (b) high magnification SEM images of representative depositions of \ce{MoO3} on Si for non-catalytic growth.}
+\label{fig:mosisem}
+\end{figure}
+
+\begin{figure}[htb]
+\centering
 \subcaptionbox{\label{fig:moind}}{\includegraphics{n_MoO3}}%
@@
 \end{figure}
+
+\begin{align}
+\cee{MB + e_{CB}^- &->[pH<7] MB^{.-} \\
+2MB^{.-} &\rightarrow MB + LMB\\
+O2 + e_{CB}^- &\rightarrow O2^{.-}}
+\end{align}
+
+\begin{align}
+\cee{ WS2-WO3 + h\nu &-> e^- + h^+\\
+O2 + e^- &-> O2^{.-}\\
+OH_{surface}^- + h^+ &-> .OH\\
+MB^+ + O2^{.-} + .OH-> \text{degradation phases}
+}
+\end{align}
 

### 2014-08-10 BackMatter/paper.tex
wox chapter revising

--- 2014-08-07 BackMatter/paper.tex
@@
 
-2D wo3.\cite{Kalantar-zadeh2010a} 
-WO3 plasmon \cite{Manthiram2012}
+Tungsten bronzes was coined by Wohler in 1837.\cite{Deb2008} \ce{Na_{x}WO3}
+
+\subsection{applications}
+
+\citeauthor{Wang2009a} mentioned that amorphous \ce{WO3} can only be used in lithium-based electrolytes due to its in-compact structure and high dissolution rate in acidic electrolyte solutions.
+Electrochromic materials that can endure acidic electrolytes without degradation should be developed.
+Crystalline \ce{WO3} nanostructures with their much denser structures and small particle sizes are promising to be used as suitable electrochromic material in acidic electrolytes.
+
+photocatalytic applications in solar hydrogen generation and organic pollutant degradation.
+
+photocatalyst\cite{Macphee2010},
+photoelectrochemical energy application \cite{Su2010}
 
@@
 
-MB Raman peaks: 445, 1618, ref20. some peak splitting and shift observed on SERS, attributed to chemical adsorption.
-
-definition of Raman enhancement factor (9,26).
+MB Raman peaks: 445, 1618, ref20. some peak splitting and shift observed on SERS, attributed to chemical adsorption. definition of Raman enhancement factor (9,26).
 
@@
 WO3: effective mass of bipolaron = 1.9me. for electron, for hole:
+unzip nanotube. passivate BN ribbons with O and S; another player terrones psu.
+
+\ce{WO3} catalyst.\cite{Miyauchi2013}  potential of CB e more negative than redox potential of \ce{O2}-\ce{O2^-} (-0.046 V vs NHE at pH 0).
+Z-scheme two photo absorption.
+photogenerated ele in CB of WO3 can reduce itself by formation of color centers.
+
+electrochromic films. \cite{Yoshimura1985}
+
+ECD \cite{Jiao2012} recent review \cite{Mortimer2011}
+
+PEC, photoelectrode, WO3 and Si tandem structures.\cite{Coridan2013}
+
+WO3 photoactivity MB. \cite{Watcharenwong2008}
+A low recombination rate is preferred for high photocatalytic efficiency. The simultaneous migration of electrons and holes.
+
+\subsection{properties}
+
+\citeauthor{Chatten2005} also studied the oxygen vacancy in different phases of \ce{WO3}.\cite{Chatten2005}
+
+2D wo3.\cite{Kalantar-zadeh2010a} 
+WO3 plasmon \cite{Manthiram2012}
 
@@
 
-W plasma oxidation.\cite{Romanyuk2005} 200nm W coating on Si (100) sub, temperature at RT, 390, and 490 C, oxygen pressure 0.5 Pa, oxidation time for 10 sec to 3600 sec.
-The resultant thickness of \ce{WO3} at RT  and time of 10 sec and 3600 sec is found to be 0.2nm and 11 nm respectively.
-
-\[
- d = d_0 exp(kt)
-\]
-
-after fitting, $d_0 = 0.19777 nm$, $k = 0.00112 sec^{-1}$, so to oxidize 1nm W coating completely, oxygen plasma time is 1450 sec at 0.5Pa partially pressure; 2 nm for 2000 sec.
-
-\ce{WOx} and optical electric field enhancement.
-The enhancement arise from the structure composed of a conductive layer and an insulating layer that are laminated therein.\footnote{US patent 8601610B2} In \ce{WOx} nanorods, the oxygen deficient planes are conductive, each having atomic thickness and separated by several nm \ce{WO3}.
-Localized surface plasmons could possibly exist on these conductive planes.
-Therefore SERS applies and single molecule Raman scattering using a tungsten oxide nanorod has been demonstrated.
-The \ce{W_nO_{3n-1}} ($n \geq 2$) exhibit $\{ 001 \}$ CS structure.
-Chemical formulae corresponding to n=2, 3, 4, 5 and 6 are \ce{W2O5=WO_{2.5}}, \ce{W3O8=W_{2.67}}, \ce{W4O_{11}=WO_{2.75}}, \ce{W5O_{14}=WO_{2.8}}, and \ce{W6O_{17}=WO_{2.83}}, which indicates the existence of a oxygen deficient plane at every n row.
-Actually the value x in \ce{WOx} could almost continuously vary within a range of 2.5 to 3.
-\ce{W_{18}O_{49}=\ce{WO_{2.72}}} is an exception without $\{ 001 \}$ CS structure.
-Moreover, the oxygen deficient planes could extend along directions other than $\{ 001 \}$.
-For instance, the $\{ 102 \}$ CS planes appears in \ce{WOx} where x is within 2.93 to 2.98, and  the $\{ 103 \}$ CS planes for x within 2.87 to 2.93.\cite{Sloan1999}  \citeauthor{Shingaya2013} also synthesized \ce{WS2}-\ce{WO_x} structures and found similar Raman scattering enhancement.
-The x value is estimated by the Raman spectra peaks.\cite{Shingaya2013}(Data not shown in patent)
-
 The Raman spectra of \ce{WO_x} is rare because of the difficulty of preparing pure suboxides phase and the strong shielding of \ce{WS2}.
@@
 
-unzip nanotube. passivate BN ribbons with O and S; another player terrones psu.
-
 \citeauthor{Huang2006} studied the \ce{W3On} cluster with n from 7 to 10.\cite{Huang2006} It was found \ce{W3O9} clusters possess a HOMO-LUMO gap about 3.4eV.
@@
 
-\ce{WO3} catalyst.\cite{Miyauchi2013}  potential of CB e more negative than redox potential of \ce{O2}-\ce{O2^-} (-0.046 V vs NHE at pH 0).
-Z-scheme two photo absorption.
-photogenerated ele in CB of WO3 can reduce itself by formation of color centers.
-
 \ce{WO3} indirect gap 2.6eV, direct gap 3.4eV. \cite{Koffyberg1979}
 
-Fingerprint of m-\ce{WO3}, h-\ce{WO3} and \ce{WO3.nH2O} were summarized in ref\cite{Daniel1987}.
+Raman fingerprint of m-\ce{WO3}, h-\ce{WO3} and \ce{WO3.nH2O} were summarized in ref\cite{Daniel1987}.
 
@@
 
-For photochemical water reduction to occur, the flat-band potential of the semiconductor (for highly doped semiconductors, this equals the bottom of the conductance band) must exceed the proton reduction potential of 0.0 V vs NHE at pH =0.
-\cite{Osterloh2008} flat-band potentials strongly depend on ion absorption (protonation of surface hydroxyl groups), crystallographic orientation of the exposed surface, surface defects, and surface oxidation processes.
-
 \citeauthor{Salje1984} studied the transport in \ce{WO_{3-x}} ($0\leq x \leq 0.28$).\cite{Salje1984} It was found \ce{WO_{3-x}} show metallic conductivity when $x > 0.1$.
@@
 \ce{WO3} high temperature phase. \cite{Vogt1999}
-
 tungsten bronzes \cite{Wiseman1976}
-
- Ge NW growth using Ga as catalyst. \cite{Chandrasekaran2006}
 
@@
 
-  electrochromic films. \cite{Yoshimura1985}
-
 optical properties of \ce{WO3} gaps\cite{Saygin-Hinczewski2008}
@@
 
-  ECD \cite{Jiao2012} recent review \cite{Mortimer2011}
-
 \ce{WnO_{3n-1}} NPs. \cite{Frey2001}
-WO3-x raman info, the encapsulated WOx core has been investigated in depth.
-several stable phase could occur, including \{001\} CS phases, \{103\} CS phases.
-no evidence of $\gamma$-\ce{W_{18}O_{49}} phase is found.
-The cross-section ($\sigma$) for Raman scattering and the absorption coefficient of the WS2 layers are much larger than those of the suboxide phase encapsulated inside.
-
-WO2:168(w),189(w), 286(vs), 345(w), 423(w), 479(m), 512(m), 599(m),
-617(m) cm-1, and a mode at 781(s) cm-1 which tails to higher energies (w-weak; m-medium; s-strong; vs-very strong).
-
-W5O14: 215, 264, 325, 349, 418, 425,707, and 800 cm-1, 900 maybe
-
-WO3: 808, 719, 275;
-
-W3O8: 870;
-
-no 950 peak indicates no hydrated phases.
 
@@
 \ce{W_{18}O_{49}} on tungsten foil by thermal growth\cite{VanHieu2012}
-
-  \ce{WO_{3-x}} Raman peak at 778. \cite{Deb2007}
 
@@
 
-  PEC, photoelectrode, WO3 and Si tandem structures.\cite{Coridan2013}
-
-  WO3 photoactivity MB. \cite{Watcharenwong2008}
-
 optics in electron microscopy. \cite{GarciadeAbajo2010a}
 
-  A low recombination rate is preferred for high photocatalytic efficiency. The simultaneous migration of electrons and holes.
+\section{MoO3}
 
-An empirical formula to relate the Raman peaks and \ce{W-O} bonding lengths \cite{Hardcastle1995} is
-\begin{equation}\label{eq:wobond}
-\nu = 25823 \exp{-1.902\cdot R}.
-\end{equation}
-And the standard deviation of estimating \ce{W-O} bond distance from Raman stretching wavenumber is $\pm0.034$\AA.
-The observed Raman peaks of \ce{Na5W_{14}O_{44}} phase lies at 965, 943, 913, 808, 786, 778, 765, 695 and 107 cm.
-Multi-peaks Lorentzian fitting is preformed to precisely determine the central maximum.
-Good fitting is obtained, as shown in Fig.~\ref{fig:naworamfit}.
-We then calculated \ce{W-O} bond distance using Eq.~\ref{eq:wobond}, as illustrated in Table~\ref{tab:nawobond}.
-The predicted \ce{W-O} bond length comply very well with the crystallographic value of \ce{Na5W_{14}O_{44}} phase.\cite{Triantafyllou1999a} The 107 peak probably is caused by \ce{Na-O} bond.
-% Na5 raman fitting
-\begin{figure}[htb]
-\centering
-\includegraphics[width=0.6\textwidth]{naxwo_ramfit}
-\caption[\ce{Na5W_{14}O_{44}} Raman fitting]{Multi-peaks Lorentzian fitting on two major peaks region of \ce{Na5W_{14}O_{44}}.
-The peaks sum height difference is caused by different baseline value adopted in each fitting.}
-\label{fig:naworamfit}
-\end{figure}
-
-% W-O bond length
-\begin{table}[htb]
-\centering
-\caption{\ce{W-O} bond length predication}\label{tab:nawobond}
-\begin{tabular}{lccr}
-\toprule
-peak center & length (\AA) & peak center & length (\AA) \\
-\midrule
-694.6 & 1.900 &  808.6 &  1.821 \\
-745.4 & 1.863 &  911.5 &  1.758 \\
-764.4 & 1.850 &  933.0 &  1.745 \\
-778.7 & 1.840 &   943.5 & 1.740 \\
-788.4 & 1.834 &   965.4 & 1.728 \\
-\bottomrule
-\end{tabular}
-\end{table}
-
-\textbf{\ce{WS2}-\ce{WO3}}: 1 kW light source(Hg, or Xe lamp), photon flux, phenol (\ce{C6H5OH}, 94.1g/mol, MP 40C)concentration is 20 mg/L, hydroxyl group.
-The quantitative analysis of phenol was performed via a standard colorimetric method.\footnote{\url{http://omlc.ogi.edu/spectra/PhotochemCAD/html/072.html}}
-\citeauthor{DiPaola1999} prepared \ce{WS2}-\ce{WO3} mixture in two methods, sulfurization of \ce{WO3} and oxidation of \ce{WS2},with the latter are more active.
-\citeauthor{DiPaola1999} also concluded that the actual efficiency of mixed \ce{WS2}-\ce{WO3} catalysts depends on the ratio of each composition present of the surface of the particles, and the maximum of photoactivity is obtained with 40-50\% surface molar ratio of \ce{WS2}.
-
-ref 25, 28 and 41.
-
-\textbf{\ce{MoO3}}:
-
-\citeauthor{Sreedhara2013} studied the kinetics of photodegradation of methylene blue\footnote{\ce{C16H18N3SCl},319.8 g/mol, MP: 100C accompanied with decomposition \url{http://en.wikipedia.org/wiki/Methylene_blue}} dye by few layer \ce{MoO3}.
-For the photodegradation method, it was stated that `` the samples were collected after the photoreaction had been centrifuged for 5 min to remove the photocatalyst before UV-Vis measurement.''
-
-\section{MoO3}
+VLS:
+Ge NW growth using Ga as catalyst. \cite{Chandrasekaran2006}
 
@@
 
-\ce{MoO3} ECD:
+\subsection{app}
+applications: electrically controlled optical shutters for heat and light modulation, smart windows associated with solar cell to provide dynamical control of incoming illumination.
 
-piranha clean of FTO.
-50ms switch.\cite{Scherer2012} nanoscale Kirkendall effect: the outward diffusion of metal cations are balanced by an influx of vacancies.
-For example, diffusion coefficient of Ni in NiO is higher than that of oxygen.
+piranha clean of FTO. 50ms switch.\cite{Scherer2012} 
+nanoscale Kirkendall effect: the outward diffusion of metal cations are balanced by an influx of vacancies. For example, diffusion coefficient of Ni in NiO is higher than that of oxygen.
 
-\subsection{EC windows and thin film batteries}
+\ce{MoO3} photocatalytic \cite{Chithambararaj2013}
+photocatalytic experimental setup.\cite{Hupka2006}
+\ce{MoO3} pseudocapacitor  \cite{Brezesinski2010}
 
-battery and ECD.\cite{Granqvist2012} electrolyte: PVB (poly vinyl buteral).
-alternative materials and design: organic, Prussian Blue as EC materials, metal hydrides, suspended particle device, liquid crystal, electroplating,
-challenges: large area nanoporosity, transparent conducting contact, electrolyte with good ionic conductivity and poor electronic conductivity, stable under UV; assembly and large scale manufacturing;
-cathodic coloration:
-anodic coloration:
-The coloration mechanism: \ce{MO6} octahedrons lead to $e_g$ and $t_{2g}$ level and ion channelling.
-ref54,60,65,66,200,209,
+\ce{MoOx} few layer as hole selective contact in solar cell.\cite{Battaglia2014}
+\ce{MoO_x} on n-type Si acts as a high work function metal (6.6eV), enabling a dopant-free contact and thus junction-less devices.
 
-\ce{WO3} as cathodic and either polyaniline(PANI) or Prussian white (PW) as anodic electrochromic half cells. \cite{Heckner2002}
-
-Characterization of ECD includes transmission measurement and associated EC calculation, charge-discharge time, current-time curve and the fitting of obtained data.
-
-\begin{quote}
-a viable electrochromic smart window must exhibit a cycling life time \textgreater $10^5$ cycles, corresponding to an operation life at 10 -- 20 years.
-\end{quote}
-
-\citeauthor{Sella1998} studied the optical and structural properties of RF sputtered thin film of \ce{WO3} and \ce{VO2} for electrochromic devices.
-Ionic conductor was built using transparent polymer electrolyte, which was prepared from a solution of 1M \ce{LiClO4} in propylene carbonate which was mixed with methylmetharcylate (MMA).
-The main characteristics of polymer electrolyte were: viscosity at 25 \si{\degreeCelsius} $\approx$ 12920 Pa.s, conductivity $\approx 10^{-2}-10^{-4}$\si{\per\ohm\per cm},non-hygroscopic if PMMA concentration \textgreater 30\%.
-A specific counter-electrode layer was not used since the encapsulated polymer electrolyte processes a very high ion storage capacity.\cite{Sella1998}
-
-The device proposed was reproduced as shown in Fig.~\ref{fig:Sella1998ECD}
-\begin{figure}[htb]
-    \centering
-    \includegraphics[angle=270,width=0.8\textwidth]{Sella1998ECD}
-    \caption{citation, see original captions} \label{fig:Sella1998ECD}
-\end{figure}
-
-\subsection{experimental setup}
-
-applications: electrically controlled optical shutters for heat and light modulation, smart windows associated with solar cell to provide dynamical control of incoming illumination.
+\subsection{properties}
 
@@
 The real phase diagram is the one between \ce{Na2Mo4O_{13}} and \ce{MoO3}.
-
 the growth temperature could be much lower than the eutectic point.
@@
 
-\ce{MoO3}, an alternative interpretation in terms of tetrahedral coordination of Mo atoms is also proposed.
-This is caused by the fact that four of the six surrounding O atom are at distances from 1.67\AA to 1.95\AA, while the remaining two are as far as 2.25 and 2.33\AA.
-This also stress that the \ce{MOO6} octahedra are rather distorted.
-
 visibility of mica thin layer on \ce{SiO2}-Si.
@@
 
-\ce{MoO3} photocatalytic \cite{Chithambararaj2013}
 \ce{MoO3} (010) surface defect. \cite{Chen2001}
 
-photocatalytic experimental setup.\cite{Hupka2006}
-
 mass spectrometry data to extract vapor pressure of \ce{NaxMoO3}.
-
-\ce{MoO3} pseudocapacitor  \cite{Brezesinski2010}
 
@@
 
-\cite{Matar2011} Using electronegativity $\chi$ and chemical hardness $\eta$ to assess electron affinity $E_a$, work function $W_f$, Fermi energy $E_f$ and band gap $E_g$.
-\begin{align}
-\chi &= 0.5(W_f + E_a)\\
-\eta & = 0.5(W_f - E_a)\\
-\end{align}
-where I is ionization potential and $E_a$ is electron affinity.
-
-Correlation between optical band gap and formation enthalpy; reaction occurs in order to form compounds with a larger gap.
-$E_g = A \exp(0.34E_{\Delta H^0})$, and A adopts different values depending on the metal elements:
-\begin{itemize}
-\item A=0.8 for s and f block elements,
-\item A = 1 for d block elements,
-\item A = 1.35 for p block elements.
-\end{itemize}
-
 h-\ce{MoO3} \cite{Lunk2010} \cite{Zheng2009}
 
-\ce{MoOx} few layer as hole selective contact in solar cell.\cite{Battaglia2014}
-\ce{MoO_x} on n-type Si acts as a high work function metal (6.6eV), enabling a dopant-free contact and thus junctionless devices.
+\section{TMS}
 
-\begin{table}[htb]
-\centering
-\renewcommand*{\thetable}{S\arabic{table}}
-\caption{physical constants of reactants }\label{tb:thermo}
-\begin{tabular}{lccr}
-\toprule
-Material & MP(\si{\degreeCelsius}) & BP(\si{\degreeCelsius}) & reference\\
-\midrule
-\ce{NaOH}        & 318 & 1388 & handbook  \\
-\ce{NaI}        & 651 & 1300 & MSDS    \\
-\ce{KI}        & 681 & 1330 & MSDS   \\
-\ce{Na2CO3}        & 851 & Not determined & MSDS    \\
-\ce{Na2MoO4}        & 687 & Not available & handbook   \\
-\ce{MoO3}    & 795 & 1155 & MSDS   \\
-\ce{MoO2}    & 1100(decomp) & Not available & MSDS   \\
-\bottomrule
-\end{tabular}
-\end{table}
+petroleum oil catalytic refinement, solid lubricants in aerospace industry.
 
-\section{TMS}
+heterojunction is employed to transferred photo-generated carriers.
+Schottky barrier conduction band electron trapping and consequent longer electron-hole pair lifetimes.
+Numerous studies have suggested that fine particles of transition metals or their oxides, when dispersed on the surface of a photocatalyst matrix, can act as electron traps on n-type semiconductors.\cite{Zhou2010}
+
+\citeauthor{Cao2014} studied the layer-dependence \ce{MoS2} electrocatalysis and propose the vertical hopping efficiency of electrons instead of the edge site numbers is a key factor for catalytic reaction.\cite{Cao2014} ref19,20
 
@@
 \citeauthor{Ghorbani-Asl2013} studied the strain in tubular TMDC and found a linear dependence of Raman scattering on strain (3 \si{cm^{-1}} per percentage for $E_{2g}$mode).\cite{Ghorbani-Asl2013}
+
+For 2D materials, strain may be induced by elongation of an appropriate substrate, e.g.
+by uniform mechanical strain, or by using a material with high thermal expansion coefficient and varying the temperature.
+For TMD MWNT, tensile tests have been reported by various groups.
+However, to date, it is not perfectly clear whether inner and outer walls are stretched simultaneously, or rather the outer walls slide on the inner ones.
+The latter hypothesis would result in a broadening of the Raman signals, while the first one would leave the signal widths rather unaffected.
+In any case, there would be a shift of the Raman signals that can serve as precise scale for determining the strain.\cite{Ghorbani-Asl2013}
 
@@
 
-\subsection{others}
+\subsection{growth and properties}
 
@@
 
-Exfoliated WS2 few layer PL.\cite{Zhao2012} excitonic absorption peaks A and B arising from direction transition at K point are found around 625nm (1.98eV) and 550nm, respectively, which are in agreement with results from bulk layers.
-The A, B excitons difference was a result of strong spin-orbital coupling.
-Relative PL quantum yield of WS2 between 1L and 2L is on the order of 2.
-The FWHM of WS2 peak is about 75 meV.
-Narrower than thermal energy at room temperature,
+Other chalcogenide has also been synthesized using this one-end sealed layout.\cite{Mukherjee2013}
+
+\citeauthor{Zou2007} prepared W/\ce{WS2} core-shell NPs by reaction of tungsten and sulfur under hydrogen atmosphere.\cite{Zou2007}
 
@@
 
-\cite{Xiao2014}
+\ce{MoS2} sing-walled nanotube.\cite{Xiao2014}
 
@@
 3R transition to 2H upon heating since 2H is the most stable one.
-aberration corrected TEM is used.
-
-petroleum oil catalytic refinement, solid lubricants in aerospace industry.
-
-Electro microscopy on stacking sequences of WS2 NT.\cite{Houben2012} The probability of parallel stacking is about 30\%.
-a metal-semi superstructures.
-In NT, the layers are slightly shifted with respect to each other due to the constraints, thus the stacking is not exactly as pure phases of 2H(prismatic antiparallel), 3R(prismatic parallel) or 1T (octahedral parallel) with their perfect translational symmetry.
-
-chevron pattern, contradictory, contradicting, Debye scattering model for XRD.
-
-\begin{quote}
-hexagonal polytype 2Hb with two molecular layers (spacegroup P63/mmc) and a rhombohedral polytype 3R with three molecular layers per unit cell (space group R3m), a high pressure polytype that is stable in plane geometry at pressures above 4 GPa.
-The two prismatic phases are semiconducting, and the octahedral one is metallic-like.
-
-1T phase may be the result of a transformation from the 3R to the 2H phase by an intermediate 1T phase that is trapped by fast quenching
-
-\end{quote}
-
-HRTEM on WS2 NT.\cite{Sadan2008} negative spherical-aberration imaging (NCSI).
-NCSI condiction were achieved at a negative spherical aberration of -20um balanced by an overfocus of +17 nm.
-Focal series reconstruction to retrieve the phase of electron exit plan wavefunction.
-Zigzag, armchair revealed.
 
@@
 
-A direct gap of $\sim 2eV$ at the corners of BZ is formed in 1L \ce{WS2}, Growth on bottom piece show the multiple domain flakes occurs at initial stage of the growth, starting from \ce{WO3} particles.
-%\cite{Cong2013}
-
-In centrosymmetric crystals, the vibrational modes must either have even (Raman-active) or odd (IR-active) parity under inversion, which is known as rule of mutual exclusion.
-When this symmetry is broken, some modes may be simultaneously IR and Raman active.
-
-inelastic neutron scattering to study the non-zone center LA mode.
-Zone-edge scattering can occur due to zone-folding process.
-The formation of superlattice could activate formerly inactive zone-edge phonons.
-The folding of BZ along $\Gamma-M$ would cause the M point to coincide with $\Gamma$ point, so LA(M) phonons would become Raman active in a first-order process.
-
 multipeak Lorentzian fitting. 270 to 410 cm
 
-For 2D materials, strain may be induced by elongation of an appropriate substrate, e.g.
-by uniform mechanical strain, or by using a material with high thermal expansion coefficient and varying the temperature.
-For TMD MWNT, tensile tests have been reported by various groups.
-However, to date, it is not perfectly clear whether inner and outer walls are stretched simultaneously, or rather the outer walls slide on the inner ones.
-The latter hypothesis would result in a broadening of the Raman signals, while the first one would leave the signal widths rather unaffected.
-In any case, there would be a shift of the Raman signals that can serve as precise scale for determining the strain.
+\citeauthor{Shi2013} studied the strained monolayer \ce{MoS2} and WS2.
+The results show that exciton binding energy is insensitive to the strain, while optical band gap becomes smaller as strain increases.
+Monolayer WS2 PL maximum located at about 1.95 eV.
+Calculation shows the electron effective mass of WS2 is the smallest, rendering higher mobility in device.\cite{Shi2013}
 
-As the experimental setup for direct tensile tests of nanotubes is state-of-the-art,\cite{Tang2013} the application of tensile stress on 2D TMD systems is rather difficult due to the excellent lubricating properties of these materials.
+\citeauthor{Kosmider2013} studied the heterojunction between two monolayers of \ce{MoS2} and WS2.
+Top of VB in W layer and bottom of CB in Mo layer, forming type II structure.
+bilayer gap 1.2 eV.\cite{Kosmider2013}
 
-\begin{enumerate}
-\item WS2 NT phase, 2H or 3R or 1T;
+Band structure  of \ce{MoS2} in bulk form was calculated by \citeauthor{Mattheiss1973}.The calculation result is 1.2eV (indirect gap).\cite{Mattheiss1973}
 
-\end{enumerate}
+Alkali metal intercalated \ce{WS2} film was prepared.\cite{Homyonfer1997} Stage 6 superlattice formation was suggested according to X-ray diffraction, and photoresponse spectra and electron tunneling measurement were done.
 
-\citeauthor{Zhang2013e} investigated the shear (C) and layer breathing mode (LBM) in the low frequency region of \ce{MoS2}.\cite{Zhang2013e} Even layer \ce{MS2} belong to point group D$_{6h}$ with inversion symmetry, while odd layer \ce{MS2} correspond to D$_{3h}$ without inversion symmetry.
-The excitation wavelength is 532nm from a diode-pumped solid-state laser.
-A power$\sim$0.23mW is used to avoid sample heating.
-
-\citeauthor{Cao2014} studied the layer-dependence \ce{MoS2} electrocatalysis and propose the vertical hopping efficiency of electrons instead of the edge site numbers is a key factor for catalytic reaction.\cite{Cao2014} ref19,20
-
-(Shi 2013) studied the strained monolayer \ce{MoS2} and WS2.
-The results show that exciton binding energy is insensitive to the strain, while optical band gap becomes smaller as strain increases.
-Monolayer WS2 PL maximum located at about 1.95eV.
-Calculation shows the electron effective mass of WS2 is the smallest, rendering higher mobility in device.
-
-(Rossier, 2013) studied the heterojunction between two monolayers of \ce{MoS2} and WS2. Top of VB in W layer and bottom of CB in Mo layer, forming type II structure. bilayer gap 1.2 eV.
-
-Band structure  of \ce{MoS2} in bulk form was calculated by (Mattheiss, 1973).
-There is some controversy about the exact value of bandgap.
-The calculation result is 1.2eV ( indirect gap).\cite{Mattheiss1973}
-
-Alkali metal intercalated \ce{WS2} film was prepared.(Homyonfer et al., 1997) Stage 6 superlattice formation was suggested according to X-ray diffraction, and photoresponse spectra and electron tunneling measurement were done.
-
-Sulfurizaiton of W film, (Waldau1993)
-
-(Splendiani et al., 2010) reported the PL in monolayer \ce{MoS2}.
-Calculation indicated the indirect gap become larger when thinning, while the previous direct one almost stays as the same, the value is about 1.85eV (direct gap).\cite{Splendiani2010}
-
-(Zhou et al., 2010) heterojunction is employed to transferred photo-generated carriers.
-Schottky barrier conduction band electron trapping and consequent longer electron-hole pair lifetimes.
-Numerous studies have suggested that fine particles of transition metals or their oxides, when dispersed on the surface of a photocatalyst matrix, can act as electron traps on n-type semiconductors.
-
-thermal decomposition of (NH4)2MoO2S2 and intermediate product MoOS2 was studied. application: hyfrodesulfurization in refinery (Weber et al. 1996) \cite{Weber1996}
-
-\cee{MoCl5 + 1/4S8 + 5/2H2 \rightarrow MoS2 + 5HCl} (Stoffels et al. 1999)
-
-(M Remskar et al. 1999) WS2 nanotube from WO3-x whisker. heating 840 degree under flow of H2/N2/H2S ,
-
-A detailed study by (Rothschild, Sloan, and Tenne 2000) tungsten filament oxidation by water. then WS2 nanotube from WO3-x whisker. heating 840 degree under flow of H2/N2/H2S ,
-
-IF MoS2 synthesis by MoO3 nanobelt and S.(X. L. Li and Li 2003)
-
-Inorganic core –shell nanotube, WS2@MoS2 core-shell NT.(Kreizman et al. 2010)
-
-vdW Epitaxy of MoS2 on graphene. (Y. Shi et al. 2012)
-
-WS2 monolayer and intense photoluminescent behavior. Sulfurization of WO3 film( 5-20 angstrom).
-%(Gutiérrez et al. 2012)
-
-MoO3 on sapphire reduction in H2 at 500 and sulfurizatin at 1000 degree. (Lin et al. 2012)
-
-quantitative Raman of MoS2 on insulating subs. intensity difference between supported and suspended was highlighted, detailed model in support info.(S.-L. Li et al. 2012)
-
-MoS2 on SiO2/Si sub pretreated with OTAS, PTCDA solution. (Y.-H. Lee et al. 2012)
+quantitative Raman of MoS2 on insulating subs. intensity difference between supported and suspended was highlighted, detailed model in support info.Li2013
 
@@
 
-source MoS2 powder, Ar On sapphire, SiO2/Si, QWP circularly polarized  light (S. Wu et al. 2013)
-
-(Wang et al. 2013) MoS2 CVD (tsinghua univ) layer by layer sulfurization of MoO2.
-MoO3 powder 25mg and MnO2 powder 25 mg, extra sulfur Ar purging  20mins, heating at 650 degree to produce MoO2 flakes
-Further reaction between MoO2 and S was performed at 850-950 degree under Ar flow.
-
-MoS2 on SiO2, sapphire, and graphite by MoCl5 and S. (Yu et al. 2013)
-growth time: 10min at 850 degree, P: 2 Torr.
-
-review of inorganic 2D materials, (Chhowalla et al., 2013)
-
-(Ramasubramaniam, 2012) decrease in dielectric screening and thereby enhanced excitonic effect.
+decrease in dielectric screening and thereby enhanced excitonic effect.
 DFT is not good at describing photoemission, GW approximation overcome this deficiency but still not enough for photoabsorption process in which ehps are created.
-BSE equation is used to compensate this discrepancy,
-WX2 exhibits larger spin-orbit splitting as compared to MX2 family.
-
-reaction mechanism of \ce{MoO3} to \ce{Mo2S}.\cite{Weber1996}
-
-\citeauthor{Ling2014} studied the role of seeding promoters in CVD growth of FL \ce{MoS2}.\cite{Ling2014} PTAS treated substrates provided nucleation site and thus enable uniform deposition of \ce{MS2}.
-This enhancement perhaps arise from the \ce{K+} ions.
+BSE equation is used to compensate this discrepancy, WX2 exhibits larger spin-orbit splitting as compared to MX2 family.\cite{Ramasubramaniam2012}
 
 arise as a result of, dispersal of Na by electron probe.
-
-%%%%%%%%%%%%%%%%%%%%%%
 
@@
 
-\ce{SiO_x}-Si, \ce{WS2} absorption coefficient $10^{-7}m^{-1}$, mean free path of photo-excited charge carriers 1 $\mu m$.
-the wave vector of photon is considerably small than size of BZ, therefore The wave vector of phonon in Raman scattering usually close to zero.
-
-Multiple phonon scattering, For two identical phonons, the corresponding Raman peak in the spectrum is called an overtone of the peak from the corresponding one-phonon process.
-And the wave vector conservation rule is automatically filled, therefore the phonon involved is not limited to BZ center anymore.
-\[
-I(G) \approx \sum_k \frac{\langle f|H_M|b\rangle \langle b|H_{ep}|a\rangle \langle a|H_M|i\rangle}{(E_p - E_k^{\pi *}- E_k^{\pi}-i\gamma)(E_p - E_k^{\pi *}- E_k^{\pi}-i\gamma- \hbar\Omega_{G})}
-\]
-
-the average distance travelled by an excited electron-hole pair before combination $l=\nu_F/\omega_D=4nm$.
-
-Confocal Raman spectrometer:to obtain Raman spectrum in a specific depth of sample. Edge filter to cut off Rayleigh emission.
-
-resolution $d= 1.22 \lambda/NA$,
-
-Light Scattering in Solids II,. Springer, Berlin, 1982
-
-influence of core WOx, Raman scattering by plasma-LO coupling to determine carrier concentration. measure resonant cross sections in absolute units.
-
-disorder-induced light scattering, Van Hove critical points,
-In resonant second-order scattering:
-overtone: the same phonon,
-combination: two different phonons;
-
-\[
-\frac{\ud\sigma}{\ud\Omega}= \omega_s^4 cm^6 Sr^{-1}
-\]
-
-scattering volume V in number of unit cells can be considered as one big molecule.
-
 \ce{CaF2} a material suitable for scattering efficiency S comparison measurement due to its large band gap ($S\times \omega_L^4$ is constant below 5eV).
@@
 
-a single nanowire tends to minimize its surface. 2D isoperimetric quotient or circularity $C= \frac{4\pi A}{P^2}$, where A is area and P is perimeter of the cross-section.
-
 oxygen plasma treatment on HF-etched Si (001). reaction among $e$, \ce{O^+}, \ce{O2^+}, \ce{O^-},\ce{O2}. \ce{OH}-terminated surface obtained.\cite{Habib2010}
 
+\subsection{MB}
 MB is a heterocyclic aromatic dye which is blue colored in oxidizing environment.
@@
 \cite{Wang2014a}
-
-Liquid
 
@@
 \]
+
 \section{solar cell}
-
-DSC, ref 5, 10, 3, 2, 11.
 
@@
 box normalization, wave vector is not a continuous variable.
-in ground state, topmost filled level is the Fermi level, crystal momentum, hk, or Fermi vector k_F depends on the electron density.
+in ground state, topmost filled level is the Fermi level, crystal momentum, $hk$, or Fermi vector $k_F$ depends on the electron density.
 curvature mass, DOS mass in a state countering process,
@@
 
+profound effect, multiphonon bands, rich spectrum, Raman-active modes, atomic displacement giving rise to these modes, weaker restoring force in the vibrations.
+Interlayer van der Waals interaction, hydrocarbon contamination, an enlarged view of the boxed area, overlaid, ball-and-stick model fashion, a schematic view along [001].
+Beam stop, in-plane stiffness, $\delta\omega/\epsilon$
+
 \subsection{pronunciation}
@@
 chamber, vias, valve, figure, energetic, managerial, inert, volatile, chromic,
-laminar, palladium, platinum, photovoltaic, acronym, chirality, stoichiometric, cyclic voltammetry,
+laminar, palladium, platinum, photovoltaic, acronym, chirality, stoichiometric, cyclic voltammetry, quasi, pseudo,
 
@@
 
- (T. Tsujimura
-OLED Displays: Fundamentals and Applications
-John Wiley & Sons Inc., Hoboken, New Jersey (2012))
+(T. Tsujimura OLED Displays: Fundamentals and Applications John Wiley \& Sons Inc., Hoboken, New Jersey (2012))
 

### 2014-08-10 ch-wox/ch-wox.tex
wox chapter revising

@@
 
-\subsection{Tungsten Oxides by OT}\label{sec:nawox}
+\subsection{Tungsten Oxides by OT Growth}\label{sec:nawox}
 
@@
 The deposition of nanowires was generally located on the substrates with a growth temperature range from 660 to 420 \si{\degreeCelsius}.
-Close-up observations at high magnification revealed some nanowires were cylinder-shaped and some were belt-shaped.
+Close-up view at higher magnification revealed some nanowires were cylinder-shaped and some were belt-shaped.
 At lower temperature end of substrate, microplate structures with a rectangular shape grew among the nanowires as displayed in Fig.~\ref{fig:nawoxsemedx}b and inset.
@@
 
-The XRD measurements revealed the overall structure of the depositions on the substrates.
+XRD measurements revealed the overall structure of the specimen.
 To obtain detailed information on the crystallinity, composition, and growth direction of the nanostructures, TEM analyses with imaging, electron diffraction, and EDX were performed on more than 20 nanowires.
@@
 This result indicates a higher Na:W ratio for the \ce{Na2W4O_{13}} plate structure than that of \ce{Na5W_{14}O_{44}} nanowires, in consistent with the compositions of the two phases.
-
+% tem
 \begin{figure}[htb]
@@
 
-An empirical formula to relate the Raman peaks and \ce{W-O} bonding lengths\cite{Hardcastle1995} is
+Based on the correlation of Raman spectra and crystallographic data of a variety of tungsten bronze, an empirical formula to relate the Raman peaks and \ce{W-O} bonding lengthshas been found as 
 \begin{equation}\label{eq:wobond}
-\nu = 25823 e^{-1.902\cdot R}.
+\nu = 25823 \exp(-1.902\cdot R)
 \end{equation}
-And the standard deviation of estimating \ce{W-O} bond distance from Raman stretching wavenumber is $\pm0.034$ \AA.
+where $R$ is tungsten-oxygen bond length in \AA, and $\nu$ is Raman stretching wavenumber in \si{cm^{-1}}.\cite{Hardcastle1995} The standard deviation of estimating \ce{W-O} bond distance from Raman stretching wavenumber is $\pm0.034$ \AA.
 The observed Raman peaks of \ce{Na5W_{14}O_{44}} phase lies at 965, 943, 913, 808, 786, 778, 765, 695 and 107 \si{cm^{-1}}.
@@
 
+The \ce{Na5W14O44} phase was further confirmed by a XRD scanning from 4 to 10 degree in $2\theta/\Omega$.
+As shown in Fig.~\ref{fig:naxrdlow}, two peaks at 4.84$^{\circ}$ and 9.65$^{\circ}$ were well resolved, corresponding a lattice spacing of 18.25 and 9.16 \AA, respectively.
+This compares favorably with both HRTEM analysis (Fig.~\ref{fig:nawoxtem}e) and ICDD database results.
+
+% 061212 sample
+\begin{figure}[htb]
+\centering
+\includegraphics[width=0.5\textwidth]{naxwo_xrd_low}
+\caption[low angle scan of XRD pattern]{Low angle scan of XRD pattern on the as-grown sodium tungsten oxide sample}
+\label{fig:naxrdlow}
+\end{figure}
+
 \textbf{OT growth of 3N5, 4N5 and 5N}
@@
 Typical morphologies of OT growth using other powders are shown in Fig.~\ref{fig:wox3n5} and Fig.~\ref{fig:wox4n5}, respectively.
-The common feature is the deposition is dominated by islands in upstream end and layers in downstream end.
+The common feature of these samples is the dominance of islands growth in upstream end and layers growth in downstream end.
 The exact dimension still shows some minor difference, particularly in low temperature region.
@@
 
-\subsection{Tungsten Oxides by SG and FG}\label{sec:sgfg}
+\subsection{Tungsten Oxides by }\label{sec:sgfg}
 
@@
 %FG
-As shown in Fig.~\ref{fig:wogrowsf}b, we use two substrates in flow growth, each of which is approximate 12mm long.
+As shown in Fig.~\ref{fig:wogrowsf}b, we use two substrates in flow growth, each of which is approximate 12 mm long.
 Substrate 1 (Sub1) is located at 6.75 to 7 inch (See Fig.~\ref{fig:wogrow} horizontal axis), and substrate 2 (sub2) is placed in close vicinity of downstream end of sub1.
@@
 
+to be added, NaOH WO3 results.
+
 %\printbibliography  %  comment out when assembling

### 2014-08-10 main.tex
tms chapter 50 percentage
citation style to none sorting
wox chapter revising

@@
 % \include{./ch-intro/ch-intro}
- \include{./ch-intro/ch-instr}
+ %\include{./ch-intro/ch-instr}
   % \include{./ch-wox/ch-wox}
-  \include{./ch-moox/moox} % no tex needed, otherwise there is error
+%  \include{./ch-moox/moox} % no tex needed, otherwise there is error
  %   \include{./ch-tms/tms}
+    \include{./misc/draft}
 \appendix
@@
 %     \include{./BackMatter/app2}
-%   \include{./BackMatter/paper}
+ %   \include{./BackMatter/app-tms}
+   \include{./BackMatter/paper}
 
@@
 
-Both tungsten (W) and molybdenum (Mo) belong to Group VIB transition metal, with outer shell electrons configuration as $4d^55s^1$ and $5d^46s^2$, respectively.
-Therefore we refer their oxides and chalcogenides as \gls{tmo} and \gls{tmdc}.\footnote{Obviously transition metals include many other elements, all of which have partially filled $d$-electron shell.
-But here we use TM to denote W and Mo exclusively.}
-
-Nucleation is a process of generating a new phase from a metastable old phase, where the Gibbs energy per molecule of the bulk of the emerging new phase is less than that of the old phase.
-
-General CVD knowledge, substrate preparation, and\cite{MichealK.Zuraw2003}
-
-\section{Crystal Structures and Electronic Properties}
+%\section{Crystal Structures and Electronic Properties}
 
@@
 
-\subsubsection{Phase evolution probing by Raman}
+%\subsubsection{Phase evolution probing by Raman}
 

### 2014-08-10 misc/draft.tex
wox chapter revising

\chapter{paper draft}
\section{wo3}

\subsection{used}

SG and FG experiments remain essentially the same as that of OT growth, except that in SG additional tungsten powders were distributed onto the receiving substrate, and in FG more than one piece of substrate was employed. The modification is schematically illustrated in Fig.~\ref{fig:wogrowsf}. More details will be provided when it comes to the discussion.
% sg fg
\begin{figure}[htb]
\centering
\includegraphics[width=0.5\textwidth]{sg_and_fg.jpg}
\caption[\ce{WO3} NW growth: SG and FG]{\ce{WO3} NW growth: SG and FG. (a) Seeded growth with additional powders on substrate (b) Flow growth with multiple substrates}
\label{fig:wogrowsf}
\end{figure}

With four kinds of W powders and three layouts, we designed the experimental matrix as illustrated in Table.~\ref{tab:matrix}. The symbol $\times$ means this combination is covered in this work, and NA means otherwise.
% Tungsten powders growth design
\begin{table}[htb]
\centering
\caption{Tungsten powders growth design}\label{tab:matrix}
\begin{tabular}{lccr}
\toprule
 & Ordinary Transport & Seeded growth & Flow growth \\
\midrule
3N   &  $\times$ & NA &  NA   \\
3N5  &  $\times$ & NA &  NA   \\
4N5  &  $\times$ & $\times$ & $\times$ \\
5N   &  $\times$ & $\times$ &  $\times$ \\
\bottomrule
\end{tabular}
\end{table}

We will first present the OT growth results in section~\ref{sec:nawox}, and discuss the other two in section~\ref{sec:sgfg}.

We found the growth using 3N source show distinctive features in comparison to the rest. This mainly arise from the higher sodium concentration in 3N source than that in others. Therefore we focus on 3N source first, and move on to other latter.

% Na5 raman fitting
\begin{figure}[htb]
\centering
\includegraphics[width=0.6\textwidth]{naxwo_ramfit}
\caption[\ce{Na5W_{14}O_{44}} Raman fitting]{Multi-peaks Lorentzian fitting on two major peaks region of \ce{Na5W_{14}O_{44}}. The peaks sum height difference is caused by different baseline value adopted in each fitting.}
\label{fig:naworamfit}
\end{figure}

% W-O bond length
\begin{table}[htb]
\centering
\caption{\ce{W-O} bond length predication}\label{tab:nawobond}
\begin{tabular}{lccr}
\toprule
peak center & length (\AA) & peak center & length (\AA) \\
\midrule
694.6 & 1.900 &  808.6 &  1.821 \\
745.4 & 1.863 &  911.5 &  1.758 \\
764.4 & 1.850 &  933.0 &  1.745 \\
778.7 & 1.840 &   943.5 & 1.740 \\
788.4 & 1.834 &   965.4 & 1.728 \\
\bottomrule
\end{tabular}
\end{table}

An empirical formula to relate the Raman peaks and \ce{W-O} bonding lengths \cite{Hardcastle1995} is
\begin{equation}\label{eq:wobond}
\nu = 25823 \exp{-1.902\cdot R}.
\end{equation}
And the standard deviation of estimating \ce{W-O} bond distance from Raman stretching wavenumber is $\pm0.034$\AA.
The observed Raman peaks of \ce{Na5W_{14}O_{44}} phase lies at 965, 943, 913, 808, 786, 778, 765, 695 and 107 cm. Multi-peaks Lorentzian fitting is preformed to precisely determine the central maximum. Good fitting is obtained, as shown in Fig.~\ref{fig:naworamfit}. We then calculated \ce{W-O} bond distance using Eq.~\ref{eq:wobond}, as illustrated in Table~\ref{tab:nawobond}. The predicted \ce{W-O} bond length comply very well with the crystallographic value of \ce{Na5W_{14}O_{44}} phase.\cite{Triantafyllou1999a} The 107 peak probably is caused by \ce{Na-O} bond.

\subsection{not used}
Both tungsten (W) and molybdenum (Mo) belong to Group VIB transition metal, with outer shell electrons configuration as $4d^55s^1$ and $5d^46s^2$, respectively. Therefore we refer their oxides and chalcogenides as \gls{tmo} and \gls{tmdc}.\footnote{Obviously transition metals include many other elements, all of which have partially filled $d$-electron shell. But here we use TM to denote W and Mo exclusively.}

Nucleation is a process of generating a new phase from a metastable old phase, where the Gibbs energy per molecule of the bulk of the emerging new phase is less than that of the old phase.

General CVD knowledge, substrate preparation, and\cite{MichealK.Zuraw2003}

The energetic sources are ion bombardment, electron beam, laser ablation, and combustion flame\cite{Rao2011}.

The sol–gel process is a well-known, intensively studied wetchemical technique that is widely used in materials synthesis. This method generally starts with a precursor solution (the ``sol") to form discrete particles or a networked gel structure. During the course of gelation (aging process), various forms of hydrolysis and polycondensation take place.
In addition, doped \ce{WO3} was also demonstrated
The composition and phase of final product highly depend on the synthesis conditions.

We do not discuss tungsten oxide hydrates (\ce{WO3.nH2O}) in this work since the product of thermal CVD approach is not plagued with this complexity. It's necessary, however, to deal with hydrated \ce{WO3} in the liquid synthesis routes, as indicated in Section.~\ref{sec:woxgrowth}.

Nonstoichiometric tungsten oxides \ce{WO_x} (i.e. \ce{WO_{2.92}}, \ce{WO_{2.87}}) are known as Magn$\acute{e}$li phases.

Theoretical computation of electronic band structures for \ce{WO_x} proves difficult due to the aforementioned phase transition. oxygen deficiency, structure change, electronic properties vary according.

the ubiquity of \ce{WO6} octahedra is essential for not only the optical properties but the ability to insert and extract ions in the EC oxides, due to the tunnels in three dimensions serving as path for transport of small ions. The intercalation of hydrogen or alkali ions into \ce{WO3} created electron donor level. By absorbing the red part of incident spectrum, electrons at donor level make transition to the conduction band, causing the blue coloration in \ce{H_xWO3}.

its one dimensional (1D) nanostructure has attained intensive research efforts in recent years due to the potential applications in advanced nano-electric and nano-optoelectronic devices.

\begin{quote}
a viable electrochromic smart window must exhibit a cycling life time \textgreater $10^5$ cycles, corresponding to an operation life at 10 - 20 years.
\end{quote}

\subsection{to be used}

W plasma oxidation.\cite{Romanyuk2005} 200nm W coating on Si (100) sub, temperature at RT, 390, and 490 C, oxygen pressure 0.5 Pa, oxidation time for 10 to 3600 s. The resultant thickness of \ce{WO3} at RT  and time of 10 s and 3600 s is found to be 0.2 nm and 11 nm respectively.

\[
 d = d_0 exp(kt)
\]

after fitting, $d_0 = 0.19777$ nm, $k = 0.00112 $ s$^{-1}$, so to oxidize 1nm W coating completely, oxygen plasma time is 1450 s at 0.5 Pa partially pressure; 2 nm for 2000 s.

\ce{WOx} and optical electric field enhancement. The enhancement arise from the structure composed of a conductive layer and an insulating layer that are laminated therein.\footnote{US patent 8601610B2} In \ce{WOx} nanorods, the oxygen deficient planes are conductive, each having atomic thickness and separated by several nm \ce{WO3}. Localized surface plasmons could possibly exist on these conductive planes. Therefore SERS applies and single molecule Raman scattering using a tungsten oxide nanorod has been demonstrated. The \ce{W_nO_{3n-1}} ($n \geq 2$) exhibit $\{ 001 \}$ CS structure. Chemical formulae corresponding to n=2, 3, 4, 5 and 6 are \ce{W2O5=WO_{2.5}}, \ce{W3O8=W_{2.67}}, \ce{W4O_{11}=WO_{2.75}}, \ce{W5O_{14}=WO_{2.8}}, and \ce{W6O_{17}=WO_{2.83}}, which indicates the existence of a oxygen deficient plane at every n row. Actually the value x in \ce{WOx} could almost continuously vary within a range of 2.5 to 3. \ce{W_{18}O_{49}=\ce{WO_{2.72}}} is an exception without $\{ 001 \}$ CS structure. Moreover, the oxygen deficient planes could extend along directions other than $\{ 001 \}$. For instance, the $\{ 102 \}$ CS planes appears in \ce{WOx} where x is within 2.93 to 2.98, and  the $\{ 103 \}$ CS planes for x within 2.87 to 2.93.\cite{Sloan1999}  \citeauthor{Shingaya2013} also synthesized \ce{WS2}-\ce{WO_x} structures and found similar Raman scattering enhancement. The x value is estimated by the Raman spectra peaks.\cite{Shingaya2013}(Data not shown in patent)

For photochemical water reduction to occur, the flat-band potential of the semiconductor (for highly doped semiconductors, this equals the bottom of the conductance band) must exceed the proton reduction potential of 0.0 V vs NHE at pH =0. \cite{Osterloh2008} flat-band potentials strongly depend on ion absorption (protonation of surface hydroxyl groups), crystallographic orientation of the exposed surface, surface defects, and surface oxidation processes.

\ce{W_{18}O_{49}} Raman, IR shielding.\cite{Guo2012} \cite{Guo2011}
broad peak between 750-780 cm-1.

\ce{WnO_{3n-1}} NPs. \cite{Frey2001}

WO3-x raman info, the encapsulated WOx core has been investigated in depth. several stable phase could occur, including \{001\} CS phases, \{103\} CS phases. no evidence of $\gamma$-\ce{W_{18}O_{49}} phase is found. The cross-section ($\sigma$) for Raman scattering and the absorption coefficient of the WS2 layers are much larger than those of the suboxide phase encapsulated inside.

WO2:168(w),189(w), 286(vs), 345(w), 423(w), 479(m), 512(m), 599(m),
617(m) cm-1, and a mode at 781(s) cm-1 which tails to higher energies (w-weak; m-medium; s-strong; vs-very strong).

W5O14: 215, 264, 325, 349, 418, 425,707, and 800 cm-1, 900 maybe

WO3: 808, 719, 275;

W3O8: 870;

no 950 peak indicates no hydrated phases.

\ce{WO_{3-x}} Raman peak at 778. \cite{Deb2007}

% wo3-x phases
\begin{table}[htb]
\centering
\caption{List of \ce{WO_{3-x}} phases}\label{tab:wo3xphase}
\begin{tabular}{lccccc}
\toprule
&&&\multicolumn{3}{c}{Lattice constants \AA} \\
\cmidrule(l){4-6}
 Symbol    & PDF  & Phase & a & b & c   \\
\midrule
\ce{W18O49}  & 00-036-0101 & monoclinic & 18.324 & 3.784 & 14.035  \\
$\delta$-\ce{WO3}   & $-50 \sim 17$  & triclinic & 7.309 & 7.522 & 7.686  \\
$\gamma$-\ce{WO3}   & $17 \sim 330$  & monoclinic I & 7.306 & 7.540 & 7.692  \\
$\beta$-\ce{WO3}    & $330 \sim 740$  & orthorhombic & 7.384 & 7.512 & 3.846  \\
$\alpha$-\ce{WO3}   & $> 740$  & tetragonal & 5.25 & NA & 3.91  \\
$h$-\ce{WO3}        &  $<400$  & hexagonal & 7.298 & NA & 3.899  \\
\bottomrule
\end{tabular}
\end{table}

\section{moo3}

\subsection{used}

\ce{MoO3}, an alternative interpretation in terms of tetrahedral coordination of Mo atoms is also proposed. This is caused by the fact that four of the six surrounding O atom are at distances from 1.67\AA to 1.95\AA, while the remaining two are as far as 2.25 and 2.33\AA. This also stress that the \ce{MOO6} octahedra are rather distorted.

\subsection{to be used}

\cite{Matar2011} Using electronegativity $\chi$ and chemical hardness $\eta$ to assess electron affinity $E_a$, work function $W_f$, Fermi energy $E_f$ and band gap $E_g$.
\begin{align}
\chi &= 0.5(W_f + E_a)\\
\eta & = 0.5(W_f - E_a)
\end{align}
where I is ionization potential and $E_a$ is electron affinity.

Correlation between optical band gap and formation enthalpy; reaction occurs in order to form compounds with a larger gap.  $E_g = A \exp(0.34E_{\Delta H^0})$, and A adopts different values depending on the metal elements:
\begin{itemize}
\item A=0.8 for s and f block elements,
\item A = 1 for d block elements,
\item A = 1.35 for p block elements.
\end{itemize}

\citeauthor{Sreedhara2013} studied the kinetics of photodegradation of methylene blue\footnote{\ce{C16H18N3SCl},319.8 g/mol, MP: 100C accompanied with decomposition \url{http://en.wikipedia.org/wiki/Methylene_blue}} dye by few layer \ce{MoO3}.
For the photodegradation method, it was stated that `` the samples were collected after the photoreaction had been centrifuged for 5 min to remove the photocatalyst before UV-Vis measurement.''

% Melting points 
\begin{table}[htb]
\centering
\renewcommand*{\thetable}{S\arabic{table}}
\caption{physical constants of reactants }\label{tb:thermo}
\begin{tabular}{lccr}
\toprule
Material & MP(\si{\degreeCelsius}) & BP(\si{\degreeCelsius}) & reference\\
\midrule
\ce{NaOH}        & 318 & 1388 & handbook  \\
\ce{NaI}        & 651 & 1300 & MSDS    \\
\ce{KI}        & 681 & 1330 & MSDS   \\
\ce{Na2CO3}        & 851 & Not determined & MSDS    \\
\ce{Na2MoO4}        & 687 & Not available & handbook   \\
\ce{MoO3}    & 795 & 1155 & MSDS   \\
\ce{MoO2}    & 1100(decomp) & Not available & MSDS   \\
\bottomrule
\end{tabular}
\end{table}

\section{ws2}

\textbf{\ce{WS2}-\ce{WO3}}: 1 kW light source(Hg, or Xe lamp), photon flux, phenol (\ce{C6H5OH}, 94.1g/mol, MP 40C)concentration is 20 mg/L, hydroxyl group. The quantitative analysis of phenol was performed via a standard colorimetric method.\footnote{\url{http://omlc.ogi.edu/spectra/PhotochemCAD/html/072.html}}
\citeauthor{DiPaola1999} prepared \ce{WS2}-\ce{WO3} mixture in two methods, sulfurization of \ce{WO3} and oxidation of \ce{WS2},with the latter are more active.
\citeauthor{DiPaola1999} also concluded that the actual efficiency of mixed \ce{WS2}-\ce{WO3} catalysts depends on the ratio of each composition present of the surface of the particles, and the maximum of photoactivity is obtained with 40-50\% surface molar ratio of \ce{WS2}.

ref 25, 28 and 41.

\subsection{used}

As the experimental setup for direct tensile tests of nanotubes is state-of-the-art,\cite{Tang2013} the application of tensile stress on 2D TMD systems is rather difficult due to the excellent lubricating properties of these materials.

\citeauthor{Zhang2013e} investigated the shear (C) and layer breathing mode (LBM) in the low frequency region of \ce{MoS2}.\cite{Zhang2013e} Even layer \ce{MS2} belong to point group D$_{6h}$ with inversion symmetry, while odd layer \ce{MS2} correspond to D$_{3h}$ without inversion symmetry. The excitation wavelength is 532nm from a diode-pumped solid-state laser. A power$\sim$0.23mW is used to avoid sample heating.

reaction mechanism of \ce{MoO3} to \ce{Mo2S}.\cite{Weber1996}

\citeauthor{Ling2014} studied the role of seeding promoters in CVD growth of FL \ce{MoS2}.\cite{Ling2014} PTAS treated substrates provided nucleation site and thus enable uniform deposition of \ce{MS2}.  This enhancement perhaps arise from the \ce{K+} ions.

\citeauthor{Splendiani2010} reported the PL in monolayer \ce{MoS2}.  Calculation indicated the indirect gap become larger when thinning, while the previous direct one almost stays as the same, the value is about 1.85eV (direct gap).\cite{Splendiani2010}

thermal decomposition of (NH4)2MoO2S2 and intermediate product MoOS2 was studied. application: hyfrodesulfurization in refinery \cite{Weber1996}

\cee{MoCl5 + 1/4S8 + 5/2H2 \rightarrow MoS2 + 5HCl} \cite{Stoffels1999}

A direct gap of $\sim 2eV$ at the corners of BZ is formed in 1L \ce{WS2}, Growth on bottom piece show the multiple domain flakes occurs at initial stage of the growth, starting from \ce{WO3} particles.
%\cite{Cong2013}
\subsection{to be used}

Exfoliated WS2 few layer PL.\cite{Zhao2012} excitonic absorption peaks A and B arising from direction transition at K point are found around 625nm (1.98eV) and 550nm, respectively, which are in agreement with results from bulk layers. The A, B excitons difference was a result of strong spin-orbital coupling. Relative PL quantum yield of WS2 between 1L and 2L is on the order of 2. The FWHM of WS2 peak is about 75 meV. wider than thermal energy at room temperature,

Electro microscopy on stacking sequences of WS2 NT.\cite{Houben2012} The probability of parallel stacking is about 30\%. a metal-semi superstructures. In NT, the layers are slightly shifted with respect to each other due to the constraints, thus the stacking is not exactly as pure phases of 2H(prismatic antiparallel), 3R(prismatic parallel) or 1T (octahedral parallel) with their perfect translational symmetry.

chevron pattern, contradictory, contradicting, Debye scattering model for XRD.

\begin{quote}
hexagonal polytype 2Hb with two molecular layers (spacegroup P63/mmc) and a rhombohedral polytype 3R with three molecular layers per unit cell (space group R3m), a high pressure polytype that is stable in plane geometry at pressures above 4 GPa. The two prismatic phases are semiconducting, and the octahedral one is metallic-like.

1T phase may be the result of a transformation from the 3R to the 2H phase by an intermediate 1T phase that is trapped by fast quenching

\end{quote}

aberration corrected TEM is used.

HRTEM on WS2 NT.\cite{Sadan2008} negative spherical-aberration imaging (NCSI). NCSI condiction were achieved at a negative spherical aberration of -20um balanced by an overfocus of +17 nm. Focal series reconstruction to retrieve the phase of electron exit plan wavefunction. Zigzag, armchair revealed.

In centrosymmetric crystals, the vibrational modes must either have even (Raman-active) or odd (IR-active) parity under inversion, which is known as rule of mutual exclusion. When this symmetry is broken, some modes may be simultaneously IR and Raman active.

inelastic neutron scattering to study the non-zone center LA mode. Zone-edge scattering can occur due to zone-folding process. The formation of superlattice could activate formerly inactive zone-edge phonons. The folding of BZ along $\Gamma-M$ would cause the M point to coincide with $\Gamma$ point, so LA(M) phonons would become Raman active in a first-order process.

\ce{SiO_x}-Si, \ce{WS2} absorption coefficient $10^{-7}m^{-1}$, mean free path of photo-excited charge carriers 1 $\mu m$. the wave vector of photon is considerably small than size of BZ, therefore The wave vector of phonon in Raman scattering usually close to zero.

Multiple phonon scattering, For two identical phonons, the corresponding Raman peak in the spectrum is called an overtone of the peak from the corresponding one-phonon process. And the wave vector conservation rule is automatically filled, therefore the phonon involved is not limited to BZ center anymore.
\[
I(G) \approx \sum_k \frac{\langle f|H_M|b\rangle \langle b|H_{ep}|a\rangle \langle a|H_M|i\rangle}{(E_p - E_k^{\pi *}- E_k^{\pi}-i\gamma)(E_p - E_k^{\pi *}- E_k^{\pi}-i\gamma- \hbar\Omega_{G})}
\]

the average distance traveled by an excited electron-hole pair before combination $l=\nu_F/\omega_D=4nm$.

Confocal Raman spectrometer:to obtain Raman spectrum in a specific depth of sample. Edge filter to cut off Rayleigh emission.

resolution $d= 1.22 \lambda/NA$,

Light Scattering in Solids II,. Springer, Berlin, 1982

influence of core WOx, Raman scattering by plasma-LO coupling to determine carrier concentration. measure resonant cross sections in absolute units.

disorder-induced light scattering, Van Hove critical points,
In resonant second-order scattering:
overtone: the same phonon,
combination: two different phonons;

\[
\frac{\ud\sigma}{\ud\Omega}= \omega_s^4 cm^6 Sr^{-1}
\]

scattering volume V in number of unit cells can be considered as one big molecule.

a single nanowire tends to minimize its surface. 2D isoperimetric quotient or circularity $C= \frac{4\pi A}{P^2}$, where A is area and P is perimeter of the cross-section.

\section{ECD}

Characterization of ECD (work like a thin-film batteries) includes transmission measurement and associated EC calculation, charge-discharge time, current-time curve and the fitting of obtained data.

The coloration efficiency (CE) represents the change in the optical density (OD) per unit charge density ($Q/A$, in units of \si{\cm^2\per\coulomb}) during switching and can be calculated according to the formula:
\begin{equation}
CE = \frac{\Delta~OD}{(Q/A)} [cm^2/C],
\end{equation}
where OD = $log(T_{bleach}/T_{color})$. The EC and optical density depend on the wavelength and are usually higher in the near IR than in the visible region.
Using Ohm's law($U_s = IR = RQ/t_s$) with switch voltage $U_s$, resistance R and surface area A, switching time $t_s$ could be estimated as
\begin{equation}
t_s = \Delta~OD\cdot A \cdot R /(CE\cdot U_s).
\end{equation}

battery and ECD.\cite{Granqvist2012} electrolyte: PVB (poly vinyl buteral).
alternative materials and design: organic, Prussian Blue as EC materials, metal hydrides, suspended particle device, liquid crystal, electroplating,
challenges: large area nanoporosity, transparent conducting contact, electrolyte with good ionic conductivity and poor electronic conductivity, stable under UV; assembly and large scale manufacturing;
cathodic coloration:
anodic coloration:
The coloration mechanism: \ce{MO6} octahedrons lead to $e_g$ and $t_{2g}$ level and ion channelling.
ref54,60,65,66,200,209,

\ce{WO3} as cathodic and either polyaniline(PANI) or Prussian white (PW) as anodic electrochromic half cells. \cite{Heckner2002}

Characterization of ECD includes transmission measurement and associated EC calculation, charge-discharge time, current-time curve and the fitting of obtained data.

\begin{quote}
a viable electrochromic smart window must exhibit a cycling life time \textgreater $10^5$ cycles, corresponding to an operation life at 10 -- 20 years.
\end{quote}

\citeauthor{Sella1998} studied the optical and structural properties of RF sputtered thin film of \ce{WO3} and \ce{VO2} for electrochromic devices. Ionic conductor was built using transparent polymer electrolyte, which was prepared from a solution of 1M \ce{LiClO4} in propylene carbonate which was mixed with methylmetharcylate (MMA). The main characteristics of polymer electrolyte were: viscosity at 25 \si{\degreeCelsius} $\approx$ 12920 Pa.s, conductivity $\approx 10^{-2}-10^{-4}$ \si{\per\ohm\per cm},non-hygroscopic if PMMA concentration \textgreater 30\%. A specific counter-electrode layer was not used since the encapsulated polymer electrolyte processes a very high ion storage capacity.\cite{Sella1998}

The device proposed was reproduced as shown in Fig.~\ref{fig:Sella1998ECD}
\begin{figure}[htb]
    \centering
    \includegraphics[angle=270,width=0.8\textwidth]{Sella1998ECD}
    \caption{citation, see original captions} \label{fig:Sella1998ECD}
\end{figure}

### 2014-08-18 ch-intro/ch-instr.tex
wox chapter revising
ch2 instrument 60 percentage

@@
 
-In this study the nanostructures were grown in a home-built chemical vapor deposition system, and characterized using both electron microscopy and optical spectroscopy methods, including SEM, XRD, EDX, TEM, Raman and UV-Vis.
-Other sample and substrate preparation methods used are also briefly introduced.
+In this study, the nanostructures were grown in a home-built chemical vapor deposition system and characterized using both electron microscopy and optical spectroscopy methods, including SEM, XRD, EDX, TEM, Raman and UV-Vis.
+Other sample and substrate preparation methods are also briefly introduced.
 A detailed introduction will be given to the CVD system.
-For other mature techniques, the contents will be limited to the extent where experienced material researchers could repeat the experiments performed in this study.
-This chapter is concluded with data processing and associated software discussion.
+For other mature techniques, the contents will be limited to the extent where experienced material researchers could repeat the experiments performed here.
+Particular attentions will also be mentioned to properly characterize the nanostrucutres synthesized in this work .
+This chapter is concluded with data processing discussion.
 
@@
 Some will be adsorbed by the substrate and become adatoms while some may remain as gas molecules, waiting for another event.
-On the hot substrate, adatoms diffuse and do not settle down until finding a appropriate location where equilibrium is favorable.
+On the hot substrate, adatoms diffuse and do not settle down until finding an appropriate location where equilibrium is favored.
 Detailed growth conditions are introduced in corresponding chapters.
@@
 
-SEM, as its name suggests, forms images using contrast from the electron-materials interactions.
-Electron beam (E-beam), generated from either thermionic or field emission of filaments, travels towards the sample underneath, producing rich signals as illustrated in Fig.~\ref{fig:ch2sem}.
-The out-coming backscattering (BSE) and secondary electrons (SE) arise from elastic and inelastic process, respectively.
-The X-ray stems from inner shell transition, and cathodoluminescence from band gap transition.
-In this study, we mainly use SE-formed images to reveal the morphology of the samples, since SE emission is sensitive to the shape and orientation.
-X-ray, collected by silicon detector cooled by liquid nitrogen, could provide compositional information attaining to the studied sample, because of the characteristic X-ray emission lines from each element.
+The SEM instrument used in this study is JEOL JSM-6480.
+The electron beam (E-beam) source is a tungsten filament heated at about 2800 K.
+The acceleration voltage can be up to 30 kV.
+After acceleration, electron beam strikes the sample mounted on specimen stage, producing rich signals as illustrated in Fig.~\ref{fig:ch2sem}.
+Depending on the energy and scattering angle, the out-coming electrons from specimen can be grouped as backscattering electron (BSE) and secondary electron (SE), respectively.
+SE is generated from the emission of valence band electrons.
+And due to the limited energy ($<50$ eV), the emission from deep region is mostly absorbed again; only those SE that are at the vicinity of specimen surface can escape.
+Hence the SE image is topographical sensitive.
+The emission efficiency is strongly affected by the geometry (tilting angle of specimen surface) and voltage potential (charging effect), so does the contrast in SE image.
+On the other hand, backscattered electron has large energy close to that of incident E-beam.
+The scattering efficiency strongly depends on atomic number (Z), thus allowing for the compositional analysis.
+The X-ray emission stems from inner shell transition of the constitutive atoms, and cathodoluminescence from bandgap transition.
+Other E-beam generated signals, such as Auger electrons, are not shown here.
 
@@
 \includegraphics[width=0.5\textwidth]{sem_sch.png}
-\caption[SEM excitation volume]{schematic drawing of electron materials interaction in SEM, some process is not shown, such as Auger emission.}
+\caption[SEM excitation volume]{schematic drawing of electron materials interaction in SEM. Some process is not shown, such as Auger emission.}
 \label{fig:ch2sem}
 \end{figure}
+
+In this study, SE images were mainly used to reveal the morphology of the samples.
+Energy dispersive X-ray spectroscopy provides compositional information attaining to the studied sample because of the characteristic X-ray lines from each element.
+The X-ray detector (INCA, 7573-M, 10 \si{mm^2} Si cooled by liquid nitrogen) is equipped with a super thin window enabling light element detection such as boron.
+To obtain quantitative results on EDX spectra, special attentions should be paid to the following aspects:
+\begin{itemize}
+\item elemental distribution in an X-ray generation area is uniform,
+\item the specimen surface is flat,
+\item the electron beam enters perpendicular to the specimen. 
+\item a reference sample consisting of identical elements and known ratio is used. 
+\end{itemize}
+
+Even for qualitative analysis, ambiguity exists when the $K$ lines of lighter elements overlap with $L$ lines of heavier elements.
+For instance, Na-$K_\alpha$ (1.041 keV) interferes with $L_\alpha$ lines of Zn (1.009 keV) and Cu (0.928 keV).
+Overall spectra and growth conditions should be weighted against possible wrong assignment.
+
+Charge effect could arise on the samples grown in this study, leading to anomalous contrast on the images.
+Several measures could be taken to alleviate this adverse influence, including adjusting the acceleration voltage, tilting the specimen, and coating a thin layer of metal.
+Sometimes when an area is scanned for a long time at high magnification, the surrounding region could appear brighter after switching to a lower magnification.
+This is a sample contamination, due to the E-beam induced polymerization and deposition of hydrocarbon molecules in the vicinity of that smaller area.
+
+\iffalse
+An eucentric specimen stage is used, thus observation area remain fixed when tilting the specimen.
+The pressure in SEM chamber is on the order of $10^{-3} \sim 10^{-4}$ Pa, which is usually maintained by a diffusion pump, or turbo molecular pump when oil-free operation is needed.
+For a field emission electron source, a sputter ion pump becomes necessary due to the high vacuum requirement.
 
@@
 
+\begin{quotation}
+Since the intensity of characteristic X-rays is proportional to the concentration of the corresponding element, quantitative analysis
+can be performed. In actual experiment, a standard specimen containing elements with known concentrations is used. The
+concentration of a certain element in an unknown specimen can be obtained by comparing the X-ray intensities of the certain element
+between the standard specimen and unknown specimen. However, X-rays generated in the specimen may be absorbed in
+this specimen or excite the X-rays from other elements before they are emitted in vacuum. Thus, quantitative correction is needed.
+In the present EDS and WDS, correction calculation is easily made; however, a prerequisite is required for this correction. That is,
+elemental distribution in an X-ray generation area is uniform, the specimen surface is flat, and the electron probe enters perpendicular to the specimen.
+Actually, many specimens observed with the SEM do not satisfy this prerequisite; therefore, it should be noted that a quantitative analysis result might have appreciable errors.
+\end{quotation}
+
+\fi
+
 \section{X-ray Diffraction (XRD)}
 
-The high energy ($E = 1239.8/0.15148= 8184.5$ eV) photon was generated using accelerated electron beam from tungsten filament to bombard Cu target.
-When striking onto the crystal, these photons are scattered by the lattices.
-Since the wavelength of X-ray is similar to the lattice spacing, the scattering events interact coherently.
-Only at specific angles constructive interference occurs, and a diffraction peak registers when the detector is scanned across that angle.
-
 Crystal structures of the as-synthesized specimens in this study were characterized using PANXpert X’pert Pro MRD with Cu $K\alpha_{avg}$ radiation at $\lambda$=1.5418 \AA.
-The nanostructures in this work usually grew without preferred orientation, and can be treated as powders.
-So the $\theta-2\theta$ configuration was primarily used, as shown in Fig.~\ref{fig:ch2theta}.
-
+The high energy photon ($E = 1239.8/0.15148= 8184.5$ eV) was generated using accelerated electron beam from tungsten filament to bombard Cu target.
+The $\theta-2\theta$ configuration was primarily used, as shown in Fig.~\ref{fig:ch2theta}.
 \begin{figure}[htb]
@@
 \end{figure}
+When striking onto the crystal, these photons are scattered by the lattices.
+Since the wavelength of X-ray is similar to the lattice spacing, the scattering events interact coherently.
+Only at specific angles constructive interference occurs, and a diffraction peak registers when the detector is scanned across that angle.
 
@@
 \caption{XRD settings}\label{tab:ch2xrd}
-\begin{tabular}{lp{2in}lp{2in}}
+\begin{tabular}{lp{1.5in}lp{1.5in}}
 \toprule
@@
 Soller slit & 0.04 rad & Collimator & Parallel plate 0.27 rad \\
-Scan range & $10 \sim 65 ^\circ$ & Step size & 0.05$^\circ$ \\
+Scan range & $10 \sim 65 ^\circ$ & Step size & 0.02$^\circ$ \\
 \bottomrule
@@
 \end{table}
+
+The nanostructures usually grew with preferred orientation; therefore, they cannot be treated as powders.
+The interpretation of XRD patterns could become difficult somehow.
+Two possible approaches could be followed to resolve this problem: one is using grazing angle XRD which could reveal in-plane domain size and orientation;\cite{Tersigni2011,Goorsky2002} the other is combining XRD with alternative techniques, such as Raman, TEM.
+The latter approach was taken in this work.
 
@@
 In analog to the diffraction-limited resolution in conventional lens optics, the ultimate resolved point distance in TEM at 200 kV could be as small as 0.025 \AA.
-However it is much harder to manipulate electron with magnetic field than photon with dielectric lens, the current resolution in TEM is on the order of 1.0 \AA.
+However it is much harder to manipulate electron with magnetic field than photon with dielectric lens, the current resolution in TEM is on the order of 1.0 \AA without correcting the spherical aberration.
 The nominal resolution of JEM-2100 is 2.3 \AA.
@@
 
+The cost of TEM adds up to \$10 per eV.
+seize the public's imaginations.
+One must be just as aware of the instrument's limitations as one is of its advantages.
+Fundamental physics of electrons, how it is controlled by magnetic fields, how it interacts with specimen.
+TEM is essentially a signal-generating and detecting tool.
+TEM is initially developed to overcome the image resolution imposed by light microscopes.
+constitute, draw analogies, resolving power, correction of spherical aberration ($C_s$) and chromatic aberration ($C_c$), $C_s$ is done by , $C_c$ by energy-filtering, which is more useful for thicker specimens.
+E-beam is one type of ionizing radiation, which is capable of removing the tightly bound, inner-shell electrons from attractive field of nucleus (visible light, is non-ionizing radiation to some extent).
+a wide range of secondary signal can be produced, the spectra exhibits characteristic peaks, which identify the elements present in the specimen.
+In analog to laser as a highly coherent source, .
+The diameter of e-beam in TEM is less than 5nm in general, and can be $< 0.1$ nm at best.
+$C_s$ correction permits the generation of smaller electron probes with higher currents, which significantly improves both analytical spatial resolution and sensitivity.
+$C_c$ correction offer the possibility to form band-gap imaging and chemical-bond imaging.
+The limiting apertures increase the depth of field for specimen, and the depth of focus for the image.
+And the specimen is usually in focus from top to bottom surface.\cite{Williams2009}
+
+Point-group and space-group determination from convergent-beam patterns.
+crystal symmetry analysis.
+e-beam wavelength in metal.
+The high-resolution comes at the cost of poor sampling.
+The limitations of TEM include small sampling, interpreting of the image.
+Human eyes and brain understand reflected light image, and not well-trained for the transmission images.
+The images, DPs and spectra are all averaged through the thickness of specimen.
+In other words, single TEM image has no depth sensitivity.
+
+Both wave and particle approach, Electron scattering dictated by Coulomb interaction, Four aspects, the cross section (scattering probability), differential cross section (scattering angle), mean free path, and inelastic or elastic, non-scattering is invisible, backscattered in large angle and secondary electrons are of interest in SEM, where they provide Z contrast and surface-sensitive, topographical images.
+forward scattered is of interest in TEM.
+The spatial distribution of scattering is observed as contrast in images, and angular distribution is viewed in form of diffraction patterns.
+scattering events as billiard balls colliding, coherently scattered are those that remain in step, and incoherently scattered electrons have random phase relationship.
+Assuming single scattering events in TEM,
+
+angle in radians, solid angle in steradians, cross section $\sigma$ in \si{m^2}, which when divided by area of atom, represents a probability that scattering event will occur.
+differential cross section for an isolated atom is $\frac{d\sigma}{d\Omega} = \frac{1}{2\pi \sin\theta} \frac{d\sigma}{d\theta}$.
+The total cross section is just $\sigma$ times atom number in unit volume.
+The mean free path is the inverse of $\sigma_{total}$, that is $\lambda_{MFP} = 1/\sigma_{total}$.
+penetrate electron cloud, spherical wavelets, the cross section for electrons elastically scattered into angles larger than $\theta$ is $\sigma_{nucleus}= 1.62\times10^{-24} (\frac{Z}{E_0})^2\cot^2\frac{\theta}{2}$; scattering factor $f(\theta)$ for low angle ($< \sim 3^{\circ}$).
+The positions of diffracted e-beams determined by size and shape of unit cell, and intensities governed by distribution, number, and types of atoms in the specimen.
+
+XRD: X-ray scattered by electrons, electron scattered by both electrons and nuclei.
+Fresnel vs.
+Fraunhofer, high-angle scattered electron are incoherent; therefore, it can be used to form high-resolution Z-contrast image of a crystalline specimen, regardless of the orientation.
+Auger electron spectroscopy.
+EELS and XEDS constitute analytical electron microscopy (AEM).
+close approach the single-atom level.
+well suited to, energy-loss electrons cause Kikuchi lines to arise in DPs.
+Ionized atom enters excited state,
+
+\begin{itemize}
+\item X-ray: characteristic X-ray for elemental analysis, Bremsstrahlung X-ray also useful for biological sample; $K_\alpha$ line from L to K transition, and $K_\beta$ from M to K transition, $L_\alpha$ line from M to L transition, Inelastic cross section, Bethe expression, X-ray energies are not identical to the ionized energy because after first emission, the atom is not in ground state until a free electron fill the last hole in the outermost shell.
+A cascade of transitions, Coster-Kroning transition, X-ray line shift slightly due to the chemical bonding to another atom.
+XEDS is not good at analyzing light elements due to the low fluorescence yield, which is strongly dependent on Z.
+Bremsstrahlung X-ray emission is strongly forward,
+\item SE: ejected from the conduction or valence bands, weak so only escaping if near the surface, STEM, complex cross section mechanism, 
+\item Auger: Auger electron has specific energy similar to X-Ray, but is much more strongly absorbed than X-ray. Stated another way, Auger electron is hard to escape, so it is a surface sensitive. 
+\item CL: spatial resolution around 100 nm, 
+\item collective interaction, plasmon and phonon, plasmon excitation cross section in Lorenztian form $\frac{d\sigma_\theta}{d\Omega} = \frac{1}{2\pi a_0} \frac{\theta_E}{\theta^2 + \theta_E^2}$, where $\theta_E = E_p/2E_0$,
+\end{itemize}
+
+The cross section of tungsten, moly is
+
+Focused ion beam (FIB) to prepare thin foils of individual gates from one of the many millions of such on a wafer.
+The events of electron passing through one crystal plane, The coherent length of e-beam, collection angle,
+
+detrimental, available means, safety as a primary concern, radiation-leak test, used in isolation, telepresence, increasingly attractive feature, give rise to, worth illustrating, remain unaffected, stated another way, line of thought, reduced and lowered, electron crystallography, interplanar spacing, intrinsic to the specimen,
+
 \section{Raman and UV-Vis Spectroscopy}
+
+\url{http://www.kayelaby.npl.co.uk/chemistry/3_8/3_8_5.html}
 
@@
 
+Some common symbols for symmetry representations are as following:
+\begin{enumerate}
+\item $A$ representation indicates that the functions are symmetric with respect to rotation about the principal axis of rotation.
+\item $B$ representations are asymmetric with respect to rotation about the principal axis.
+\item $E$ representations are doubly degenerate.
+\item $T$ representations are triply degenerate.
+\item Subscripts u and g indicate asymmetric (\emph{ungerade}) or symmetric (\emph{gerade}) with respect to a center of inversion.
+\end{enumerate}
+
 In this study, Raman measurement was performed using a confocal micro-Raman system (Horiba Scentific, Labram HR800) with excitation wavelengths of 441, 532 and 632 nm.
 For nanowire samples, the laser powers were kept between 0.2 and 0.3 mW, and the acquisition time was 100 s to avoid possible thermal damage.
-The spectral resolution is about 1 \si{cm^{-1}} and the depth resolution about $2 \mu m$.
+The spectral resolution is about 1 \si{cm^{-1}} and the depth resolution about 2 $\mu$m.
 
@@
 
-UV-Vis-NIR spectrophotometer is also a useful tool to obtain absorption and reflectance from various samples.
-The absorption can be described by Lambert-Beer law: $I = I_0 \exp{-\alpha(\lambda) x}$, where $\alpha$ is the absorption coefficient in unit of \si{cm^{-1}}, and $x$ is the optical path.
-When the sample is in liquid form, it is more convenient to use $I = I_0 \exp(-\epsilon_\lambda C x)$, where $C(M = mol dm^{-3})$ is the molar concentration, and $\epsilon (M^{-1}cm^{-1})$ is the extinction coefficient.
-For example, $\epsilon$ for methylene blue (MB) is $10^5 M^{-1}cm^{-1}$ at 660 nm.\cite{Mills1999}
+UV-Vis-NIR spectrophotometer is a useful tool to obtain absorption and reflectance from various samples.
+Generally speaking, the UV spectrum ranges from 100 nm to 400 nm, and visible spectrum spans from 400 nm to 750 nm.
+Absorption from atmospheric \ce{CO2} becomes significant below 200 nm; therefore 100 to 200 nm region is usually not measured unless some vacuum technique is applied.
+Near-IR ranges from 0.75 to 3 $\mu$m.
+The cost of fabricating a spectrometer covering the whole NIR region can be quite high.
+The instrument used in this thesis (Schimadzu, UV2600Plus) can measure from 220 nm to 1350 nm (5.6 eV to 0.92 eV) with an integrating sphere.
 
-In this thesis, optical absorption spectra was recorded using Schimadzu, UV2600Plus in transmission mode.
-When necessary, the as-synthesized sample was removed from substrates by light sonication(Branson 1510R-MTH, 70W) in ethanol or DI water for 15 seconds.
+The absorption of materials can be described by Lambert-Beer law: $I = I_0 \exp(-A)=I_0\exp(-\alpha(\lambda) x)$, where $\alpha$ is the absorption coefficient in unit of \si{cm^{-1}}, and $x$ is the optical path in cm.
+When the sample is in liquid form, it is more convenient to use $A =\epsilon_\lambda C x$, where $C$ is the molar concentration (M = \si{\mole dm^{-3}}), and $\epsilon_\lambda$ is the extinction coefficient/molar absorptivity (\si{M^{-1} cm^{-1}}).
+For example, $\epsilon$ for methylene blue (MB) is $10^5 M^{-1}cm^{-1}$ at 660 nm.\cite{Mills1999} So by measuring the maximum absorbance of known sample, its concentration can be estimated accordingly.
+
+In the transmission mode, the reflection from materials phase boundary has been compensated with the usage of paired container and solvent.
+The scattering, however, cannot be eliminated this way.
+Usually scattering is negligible in molecular disperse media, yet should be considered in colloids or solids when the incident wavelength is comparable to the particle dimension.
+The size of nanostructures studied in this work is estimated to be 200 to 400 nm after sonication treatment; therefore, scattering effect should be included in the absorbance spectrum.
+
+In fact, there have been ongoing efforts to retrieve particle size profile from the dynamic light scattering, a technique also known as photon correlation spectroscopy.
+The experimental principle is as following: the sample in liquid solution is illuminated by a laser source and the fluctuations of the scattered light are detected at a known scattering angle $\theta$ by a fast photon detector.
+The fluctuations arise from the Brownian motion of small particles, equivalent to a random variation of scatter distance.
+By auto-correlation analysis, the decay rate of scattering intensity correlation can be related to the diffusion coefficient of small particles in the solvent.\cite{Maret1987} This approach, however, will not be pursued in this work.
+Instead, the scattering effect is partially circumvented by using diffuse reflection technique.
+
+Diffuse reflection spectroscopy (DRS) serves as another tool to estimate the sample band gap using Kubelka-Munk theory (KM).\cite{Tandon1970} The original KM theory was proposed in 1931,\cite{Kubelka1931} and has been popular in the color-related industry, such as painting, pigments, and paper.
+Some key points were recapitulated in this thesis.
+
+The sample is under isotropic diffuse illumination.
+And the upward flux $J$ and downward flux $I$ are characterized by the K-M scattering and absorption coefficients denoted as $S$ and $K$, respectively; that is
+\begin{align}
+\ud I &= - (K + S)I \ud z + SJ\ud z,\\
+\ud J &= + (K + S)J \ud z - SI\ud z.
+\end{align}
+Quantities $S$ and $K$, in unit of percentage of light scattered and absorbed per unit vertical length, have no direct physical meaning.
+For example, $S$ and $K$ depend on illumination geometry: diffuse or collimated.
+In the limit of infinite thick sample, the KM equation is given by
+\begin{equation}
+f(R_\infty) = \frac{(1-R_\infty)^2}{2R_\infty} = K/S,
+\end{equation}
+where $R_\infty$ is relative reflectance between sample and standard.
+In case of dilute species, one can approximate the KM function as $f(R) \propto \frac{\epsilon c}{s}$.
+When the diffuse scattering condition is fulfilled, $K$ can be related to absorption coefficient $\alpha$ by $K = 2\alpha$.
+If the scattering coefficient $S$ is fixed with respect to $\lambda$, one can then obtain
+\begin{equation}
+(f(R_\infty) h \nu)^n \propto (hv - E_g),
+\end{equation}
+where $n$ depends on the nature of electronic transition.
+The diffuse reflection spectroscopy is more proper to characterize nanomaterials because compared with UV-Vis transmission measurement for sample dispersed in liquid media, it takes the scattering effect into consideration.
+Favorable results have been obtained on the comparison of band gaps using KM model and other methods.\cite{Tandon1970,Morales2007}
+
+In this thesis, UV-Vis and diffuse reflectance spectra were recorded using Schimadzu, UV2600Plus.
+For UV-Vis measurement in transmission mode, the as-synthesized sample was removed from substrates by light sonication(Branson 1510R-MTH, 70W) in ethanol or DI water for 15 seconds.
 The dispersion was left for 12 h to enable the possible sedimentation.
 Then the dispersion was transferred into one 10 mm quartz cuvette (Thorlabs, W005654) for absorption measurement with another paired cuvette containing pairing liquid only.
+To carry out diffuse reflectance measurement, integrating sphere (ISR2600Plus) was used with an incident angle of 0 deg.
+The baseline reflectance was first recorded with the standard white plate (barium sulfate powder, \ce{BaSO4}) placed at the exit window on the sample path side, then the target sample was set in for relative reflectance measurement.
+The \ce{BaSO4} powder should be replaced periodically, otherwise the surface might turn yellow.
+To replace the \ce{BaSO4} powder, one should supply new powder into the sample holder for several time, each followed by a compact pressing using the glass rod.
+Chemical wrapping paper can be inserted between the glass rod and \ce{BaSO4} powder to prevent the powder sticking.
+Nanostructured sample could be mounted directly with the growth substrate, or ground and spread evenly onto \ce{BaSO4} surface.
 
@@
 This process will be covered  in Sec.~\ref{sec:mag}.
+
+oxygen plasma treatment on HF-etched Si (001). reaction among $e$, \ce{O^+}, \ce{O2^+}, \ce{O^-},\ce{O2}. \ce{OH}-terminated surface obtained.\cite{Habib2010}
 

### 2014-08-18 misc/draft.tex
ch2 instrument 60 percentage

@@
 \chapter{paper draft}
+
+The KM two-flux model has been extensively used to describe the optical properties of inhomogeneous materials that consist of scattering and absorbing particles in a matrix.\cite{Vargas1997} There are some limitation in the assumptions made in original KM model, e.g., the distribution of scattering on the optical path.
+And revised KM models have been proposed to eliminate these limitations.\cite{Yang2004}
+
+\citeauthor{Morandi2005} studied the absorbance and diffuse reflectin of \ce{MoO3} and \ce{WO3} thin films using FT-IT and UV-Vis spectroscopy.
+The observed absorption in visible and middle IR region were attributed to oxygen defects induced donor levels.\cite{Morandi2005}
+
+The ratio between absorption and scattering, not the absolute value of each quality, determines the reflection features.
+
 \section{wo3}
@@
 \end{figure}
+
+\subsection{polarons}
+
+The concept of polaron was first proposed by Landau in 1933.
+In ionic or highly polar crystals, such as II-VI semiconductors, alkali halides and transition metal oxides, the Coulomb interaction between a conduction electron and the lattice ions results in a strong electron-phonon coupling.
+A new quasi-particle, virtual phonon, can be defined corresponding to the effect of electron pulling nearby positive ions towards it and pushing nearby negative ions away.
+The electron and its virtual phonons, taken together, can be treated as a new composite particle, called an electron polaron; the hole polaron is defined analogously.
+\cite{Devreese1996}
+
+\subsection{NW waveguide}
+
+seriously pursued.

### 2014-08-22 BackMatter/paper.tex
ch2 enhanced

@@
 \section{misc}
+
+E-beam spatial coherence.\cite{Morishita2013} phase contrast transfer function, coherence estimated by the visibility of double slits interference fringes, an effective diameter in specimen plane.
+Image is a result of convolution between object and lens, point source on the focal plane, after lens the EM wavefront intersect image plane at different angle $\theta = d/f$,
+
 nucleation and film growth \cite{Hanbucken1984}
@@
 \section{vocabulary}
-
-adjunct to muscle power, computing and reasoning power, zinc-blende similarity, switching time depends on the velocity of the carriers; impact ionization, high field lead to nonlinear behavior, which arise from the major changes in the shape of the carrier distribution function, a far from equilibrium state.\footnote{\url{http://ieeexplore.ieee.org/xpl/tocresult.jsp?isnumber=31617&punumber=16}}
-
-high field 600kV/cm.
-carrier, linear transport, constant relaxation time, mean free path longer than interatomic distances.
-the periodic potential does not cause scattering of the electrons.
-box normalization, wave vector is not a continuous variable.
-in ground state, topmost filled level is the Fermi level, crystal momentum, $hk$, or Fermi vector $k_F$ depends on the electron density.
-curvature mass, DOS mass in a state countering process,
-
-Heat capacity is dominated by the electrons lying near the Fermi level. quantum effect and the coherence length ( 100nm at RT).
-
-strike the wafer, sputter etching and plasma etching. fenestration, arrangement of windows and doors. sustained research,
-
-experience an enormous development, principles underlying, scarce.
-heavily engaged, extensively used, become aware of, a great deal of, consistently used, lift the restriction, changed profoundly, denominator, a situation which often arises as ...
-in a manner similar to its counterpart.
-
-in reciprocal space, primitive cell, a sketch of device, a decisive role. anchors,angular brackets, thermodynamical average over the equilibrium configuration at temperature T.
-
-equation embodies the law of conservation, excess, set in consequentially.
-
-become varied, laptop not hammer it hand, bubble pop, crash and burns. exert a marked influence, detrimental impact.
-
-theoretical interest, phase transition, water droplets, water vapor cools, supersaturates and nucleates. aerosol, sulfuric acid, subsaturated, corrosion. union, cross, T. moisture,
-
-profound effect, multiphonon bands, rich spectrum, Raman-active modes, atomic displacement giving rise to these modes, weaker restoring force in the vibrations.
-Interlayer van der Waals interaction, hydrocarbon contamination, an enlarged view of the boxed area, overlaid, ball-and-stick model fashion, a schematic view along [001].
-Beam stop, in-plane stiffness, $\delta\omega/\epsilon$
+$\delta\omega/\epsilon$
 

### 2014-08-22 ch-intro/ch-instr.tex
ch2 enhanced

@@
 After acceleration, electron beam strikes the sample mounted on specimen stage, producing rich signals as illustrated in Fig.~\ref{fig:ch2sem}.
-Depending on the energy and scattering angle, the out-coming electrons from specimen can be grouped as backscattering electron (BSE) and secondary electron (SE), respectively.
+Depending on the energy and scattering angle, the out-coming electrons from specimen can be grouped into backscattering electron (BSE) and secondary electron (SE), respectively.
 SE is generated from the emission of valence band electrons.
@@
 The emission efficiency is strongly affected by the geometry (tilting angle of specimen surface) and voltage potential (charging effect), so does the contrast in SE image.
-On the other hand, backscattered electron has large energy close to that of incident E-beam.
-The scattering efficiency strongly depends on atomic number (Z), thus allowing for the compositional analysis.
+On the other hand, backscattered electron could have large energy close to that of incident E-beam.
+The scattering cross section strongly depends on atomic number (Z), thus allowing for the compositional analysis.
 The X-ray emission stems from inner shell transition of the constitutive atoms, and cathodoluminescence from bandgap transition.
-Other E-beam generated signals, such as Auger electrons, are not shown here.
+Other E-beam generated signals, such as Auger electrons, are not useful unless with ultra-high vacuum and clean surface.
 
@@
 
-Crystal structures of the as-synthesized specimens in this study were characterized using PANXpert X’pert Pro MRD with Cu $K\alpha_{avg}$ radiation at $\lambda$=1.5418 \AA.
+Crystal structures of the as-synthesized specimens in this study were characterized using PANXpert Pro MRD with Cu $K\alpha_{avg}$ radiation at $\lambda$=1.5418 \AA.
 The high energy photon ($E = 1239.8/0.15148= 8184.5$ eV) was generated using accelerated electron beam from tungsten filament to bombard Cu target.
@@
 Two possible approaches could be followed to resolve this problem: one is using grazing angle XRD which could reveal in-plane domain size and orientation;\cite{Tersigni2011,Goorsky2002} the other is combining XRD with alternative techniques, such as Raman, TEM.
-The latter approach was taken in this work.
+The latter approach was pursued in this work.
 
@@
 
-TEM qualifies as a powerful and versatile tool for material characterization.
+TEM qualifies as a very powerful and versatile tool for material characterization.
+Akin to the electron-materials interaction introduced in Sec.~\ref{sec:sem}, various signals are generated when the thin specimen was radiated by electron beam.
+Besides the SAED pattern and HRTEM imaging, other TEM based techniques include CBED, EDX, EELS and CL, etc.
+Therefore, TEM is essentially a signal-generating and detecting tool.
+Fundamental physics of electron is needed to obtain a comprehensive understanding of these TEM related techniques.
+Only a brief summary is given here.
+
+Electron scattering was dictated by Coulomb interaction, and can be characterized by the following four aspects: the cross section (scattering probability), differential cross section (scattering angle), mean free path, and inelastic or elastic scattering.
+The cross section $\sigma$ in \si{m^2}, which when divided by area of targeting atom, represents a probability that scattering event will occur.
+Differential cross section for an isolated atom is
+\[
+\frac{d\sigma}{d\Omega} = \frac{1}{2\pi \sin\theta} \frac{d\sigma}{d\theta},
+\] 
+where $\theta$ is scattering angle in radians, $\Omega$ is solid angle in steradians (sr), and $\theta$ is half of the scattering angle.
+The total cross section is just $\sigma$ times atom numbers in unit volume.
+The mean free path is the inverse of $\sigma_{total}$, that is $\lambda_{MFP} = 1/\sigma_{total}$.
+
+The spatial distribution of scattering is observed as contrast in images, and angular distribution is viewed in form of diffraction patterns.
+The positions of diffracted E-beams are determined by size and shape of unit cell, and intensities governed by distribution, number, and types of atoms in the specimen.
+
 JEOL JEM-2100 TEM with a \ce{LaB6} filament operated at 200 kV was used in current thesis.
-Similar to the photon-lattice interaction in XRD, the process of TEM could be understood as electron scattering events by the same crystal plane.
-In both processes, the constructive interference is described by $2d\sin\theta = \lambda$, where $d$ is crystal plane distance, $\lambda$ is incident wavelength (photon or electron), and $\theta$ is half of the scattering angle.
-A numerical comparison in Table.~\ref{tab:ch2tem} demonstrates the origin of difference in these two techniques.
+A numerical comparison between the scattering events in XRD and TEM is provided to visualize the difference.
+In both processes, the constructive interference is described by $2d\sin\theta = \lambda$, where $d$ is crystal plane distance, $\lambda$ is incident wavelength (photon or electron), and $\theta$, again, is half of the scattering angle.
+Table.~\ref{tab:ch2tem} demonstrates the origin of difference in these two techniques.
 
@@
 
-This small deviation angle determines the design of TEM column.
-In analog to the diffraction-limited resolution in conventional lens optics, the ultimate resolved point distance in TEM at 200 kV could be as small as 0.025 \AA.
-However it is much harder to manipulate electron with magnetic field than photon with dielectric lens, the current resolution in TEM is on the order of 1.0 \AA without correcting the spherical aberration.
+This small deviation angle determines the way of secondary signal usage in TEM.
+In analog to the diffraction-limited resolution in conventional lens optics, the ultimate resolved point distance in TEM should be on the order of electron wavelength used, which is 0.025 \AA at 200 kV.
+However, it is generally more difficult to manipulate electron with magnetic field than do photon with dielectric lens.
+The current resolving power in TEM is on the order of 1.0 \AA without correction of spherical aberration.
 The nominal resolution of JEM-2100 is 2.3 \AA.
@@
 
-Akin to the electron-materials interaction introduced in Sec.~\ref{sec:sem}, X-ray emission and CL also occur in TEM, and these signals could be collected to obtain value insight into specimen at higher spatial resolution.
 In this study, the TEM specimen was prepared either by directly scratching the as-synthesized sample using TEM grid (Cu, lacy carbon, 300 mesh), or dispersed into aqueous or organic solutions, then drop-cast onto TEM grid.
@@
 
-The cost of TEM adds up to \$10 per eV.
-seize the public's imaginations.
-One must be just as aware of the instrument's limitations as one is of its advantages.
-Fundamental physics of electrons, how it is controlled by magnetic fields, how it interacts with specimen.
-TEM is essentially a signal-generating and detecting tool.
-TEM is initially developed to overcome the image resolution imposed by light microscopes.
-constitute, draw analogies, resolving power, correction of spherical aberration ($C_s$) and chromatic aberration ($C_c$), $C_s$ is done by , $C_c$ by energy-filtering, which is more useful for thicker specimens.
-E-beam is one type of ionizing radiation, which is capable of removing the tightly bound, inner-shell electrons from attractive field of nucleus (visible light, is non-ionizing radiation to some extent).
-a wide range of secondary signal can be produced, the spectra exhibits characteristic peaks, which identify the elements present in the specimen.
-In analog to laser as a highly coherent source, .
-The diameter of e-beam in TEM is less than 5nm in general, and can be $< 0.1$ nm at best.
+To make the best out of TEM analysis, one also needs to be aware of the limitations of TEM.
+Two aspects were pointed out here, including small sampling and interpreting of the image.
+The former one is inherent and can only be partially overcome by combining TEM with other ensemble characterization tools.
+As to the latter one, it should be noted that the specimen is usually in focus from top to bottom surface; therefore the images, DPs and spectra are all averaged through the thickness of specimen.
+In other words, single TEM image has no depth sensitivity.\cite{Williams2009}
+
+\iffalse
+Similar to the photon-lattice interaction in XRD, the process of TEM could be understood as electron scattering events by the same crystal plane.
+
+\begin{itemize}
+\item X-ray: characteristic X-ray for elemental analysis, Bremsstrahlung X-ray also useful for biological sample; $K_\alpha$ line from L to K transition, and $K_\beta$ from M to K transition, $L_\alpha$ line from M to L transition, Inelastic cross section, Bethe expression, X-ray energies are not identical to the ionized energy because after first emission, the atom is not in ground state until a free electron fill the last hole in the outermost shell.
+A cascade of transitions, Coster-Kroning transition, X-ray line shift slightly due to the chemical bonding to another atom.
+XEDS is not good at analyzing light elements due to the low fluorescence yield, which is strongly dependent on Z.
+Bremsstrahlung X-ray emission is strongly forward,
+\item SE: ejected from the conduction or valence bands, weak so only escaping if near the surface, STEM, complex cross section mechanism, 
+\item Auger: Auger electron has specific energy similar to X-Ray, but is much more strongly absorbed than X-ray. Stated another way, Auger electron is hard to escape, so it is surface sensitive. 
+\item CL: spatial resolution around 100 nm, 
+\item collective interaction, plasmon and phonon, plasmon excitation cross section in Lorenztian form $\frac{d\sigma_\theta}{d\Omega} = \frac{1}{2\pi a_0} \frac{\theta_E}{\theta^2 + \theta_E^2}$, where $\theta_E = E_p/2E_0$,
+\end{itemize}
+
+The diameter of E-beam in TEM is less than 5 nm in general, and can be $< 0.1$ nm at best.
+
+correction of spherical aberration ($C_s$) and chromatic aberration ($C_c$), $C_s$ is done by , $C_c$ by energy-filtering, which is more useful for thicker specimens.
 $C_s$ correction permits the generation of smaller electron probes with higher currents, which significantly improves both analytical spatial resolution and sensitivity.
 $C_c$ correction offer the possibility to form band-gap imaging and chemical-bond imaging.
-The limiting apertures increase the depth of field for specimen, and the depth of focus for the image.
-And the specimen is usually in focus from top to bottom surface.\cite{Williams2009}
+The limiting apertures increase the depth of field for specimen, and the depth of focus for the image.\cite{Williams2009}
 
-Point-group and space-group determination from convergent-beam patterns.
-crystal symmetry analysis.
-e-beam wavelength in metal.
-The high-resolution comes at the cost of poor sampling.
-The limitations of TEM include small sampling, interpreting of the image.
-Human eyes and brain understand reflected light image, and not well-trained for the transmission images.
-The images, DPs and spectra are all averaged through the thickness of specimen.
-In other words, single TEM image has no depth sensitivity.
-
-Both wave and particle approach, Electron scattering dictated by Coulomb interaction, Four aspects, the cross section (scattering probability), differential cross section (scattering angle), mean free path, and inelastic or elastic, non-scattering is invisible, backscattered in large angle and secondary electrons are of interest in SEM, where they provide Z contrast and surface-sensitive, topographical images.
-forward scattered is of interest in TEM.
-The spatial distribution of scattering is observed as contrast in images, and angular distribution is viewed in form of diffraction patterns.
-scattering events as billiard balls colliding, coherently scattered are those that remain in step, and incoherently scattered electrons have random phase relationship.
-Assuming single scattering events in TEM,
-
-angle in radians, solid angle in steradians, cross section $\sigma$ in \si{m^2}, which when divided by area of atom, represents a probability that scattering event will occur.
-differential cross section for an isolated atom is $\frac{d\sigma}{d\Omega} = \frac{1}{2\pi \sin\theta} \frac{d\sigma}{d\theta}$.
-The total cross section is just $\sigma$ times atom number in unit volume.
-The mean free path is the inverse of $\sigma_{total}$, that is $\lambda_{MFP} = 1/\sigma_{total}$.
-penetrate electron cloud, spherical wavelets, the cross section for electrons elastically scattered into angles larger than $\theta$ is $\sigma_{nucleus}= 1.62\times10^{-24} (\frac{Z}{E_0})^2\cot^2\frac{\theta}{2}$; scattering factor $f(\theta)$ for low angle ($< \sim 3^{\circ}$).
-The positions of diffracted e-beams determined by size and shape of unit cell, and intensities governed by distribution, number, and types of atoms in the specimen.
+including controlling the interactions of electron with magnetic fields and with specimen.
 
@@
 
-\begin{itemize}
-\item X-ray: characteristic X-ray for elemental analysis, Bremsstrahlung X-ray also useful for biological sample; $K_\alpha$ line from L to K transition, and $K_\beta$ from M to K transition, $L_\alpha$ line from M to L transition, Inelastic cross section, Bethe expression, X-ray energies are not identical to the ionized energy because after first emission, the atom is not in ground state until a free electron fill the last hole in the outermost shell.
-A cascade of transitions, Coster-Kroning transition, X-ray line shift slightly due to the chemical bonding to another atom.
-XEDS is not good at analyzing light elements due to the low fluorescence yield, which is strongly dependent on Z.
-Bremsstrahlung X-ray emission is strongly forward,
-\item SE: ejected from the conduction or valence bands, weak so only escaping if near the surface, STEM, complex cross section mechanism, 
-\item Auger: Auger electron has specific energy similar to X-Ray, but is much more strongly absorbed than X-ray. Stated another way, Auger electron is hard to escape, so it is a surface sensitive. 
-\item CL: spatial resolution around 100 nm, 
-\item collective interaction, plasmon and phonon, plasmon excitation cross section in Lorenztian form $\frac{d\sigma_\theta}{d\Omega} = \frac{1}{2\pi a_0} \frac{\theta_E}{\theta^2 + \theta_E^2}$, where $\theta_E = E_p/2E_0$,
-\end{itemize}
+penetrate electron cloud, spherical wavelets, the cross section for electrons elastically scattered into angles larger than $\theta$ is $\sigma_{nucleus}= 1.62\times10^{-24} (\frac{Z}{E_0})^2\cot^2\frac{\theta}{2}$; scattering factor $f(\theta)$ for low angle ($< \sim 3^{\circ}$).
+
+Point-group and space-group determination from convergent-beam patterns.
+crystal symmetry analysis.
+e-beam wavelength in metal.
+The high-resolution comes at the cost of poor sampling.
+Human eyes and brain understand reflected light image, and not well-trained for the transmission images.
+
+One must be just as aware of the instrument's limitations as one is of its advantages.
+TEM is initially developed to overcome the image resolution imposed by light microscopes.
+constitute, draw analogies, resolving power, E-beam is one type of ionizing radiation, which is capable of removing the tightly bound, inner-shell electrons from attractive field of nucleus (visible light, is non-ionizing radiation to some extent).
+a wide range of secondary signal can be produced, the spectra exhibits characteristic peaks, which identify the elements present in the specimen.
+In analog to laser as a highly coherent source, .
+
+Both wave and particle approach, non-scattering is invisible, backscattered in large angle and secondary electrons are of interest in SEM, where they provide Z contrast and surface-sensitive, topographical images.
+forward scattered is of interest in TEM.
+scattering events as billiard balls colliding, coherently scattered are those that remain in step, and incoherently scattered electrons have random phase relationship.
+Assuming single scattering events in TEM,
+
+The cost of TEM adds up to \$10 per eV. seize the public's imaginations.
 
@@
 
-detrimental, available means, safety as a primary concern, radiation-leak test, used in isolation, telepresence, increasingly attractive feature, give rise to, worth illustrating, remain unaffected, stated another way, line of thought, reduced and lowered, electron crystallography, interplanar spacing, intrinsic to the specimen,
-
+\fi
 \section{Raman and UV-Vis Spectroscopy}
 
-\url{http://www.kayelaby.npl.co.uk/chemistry/3_8/3_8_5.html}
-
-Raman spectroscopy, a common vibrational spectroscopy, is based on the inelastic scattering of a monochromatic excitation source in energy range of 100 to 4000 \si{cm^{-1}}.
-Being nondestructive and requiring minimal preparation,
-it is an excellent tools to assess lattice dynamics and fingerprint species.\cite{McCreery2000}
+Raman spectroscopy, a common vibrational spectroscopy, is based on the inelastic scattering of a monochromatic excitation source with photon energy variation range of 100 to 4000 \si{cm^{-1}}.
+This energy difference between incident photon and inelastically scattered photon is closely related to a series of vibrational modes.
+Being nondestructive and requiring minimal preparation, it is an excellent tools to assess lattice dynamics and fingerprint species.\cite{McCreery2000} For instances, characteristic Raman shift can be used to determine material compositions; changes in Raman peak (FWHM, frequency shift) are often related to strain; polarization Raman spectra can be used to derive crystal orientation and symmetry.
 
@@
 
+\iffalse
 A Raman pattern database can be found at \url{http://wwwobs.univ-bpclermont.fr/sfmc/ramandb2/index.html}.
+
+In analytical practice, frequency is expressed in reciprocal wavelength (as cm−1), called wavenumbers;
+
+\fi
 
@@
 
+\iffalse
+
+hemispherical reflectance, 
+diffusive reflectance is a mathematical artifice without direct physical meaning.
+
+p332- 338
+
+\fi
 \section{Substrates and Pre-growth Treatments}\label{ch2sub}
@@
 
-Image J.\cite{Schneider2012} TEM lattice measurement.
+The SEM images are cropped using Adobe Photoshop for highlighting the features and fitting into text width.
+To obtain the dimension of specimen, scale bar was measured and compared to the size of interest using ImageJ\cite{Schneider2012} for SEM, TEM images and SAED pattern.
+It is worth noting that ImageJ could directly read the dm3 format generated in Gatan imaging software, which is more productive than the scale bar method.
 
-Fityk. \cite{Wojdyr2010}
+Various spectra, be it from XRD, EDX, Raman, or UV-Vis, were redraw using Origin Pro 8.0.
+The peak fitting was performed using Fityk, a nonlinear curve fitting program specialized in data processing from powder diffraction, chromatography, photoluminescence and photoelectron spectroscopy, infrared and Raman spectroscopy, \emph{etc}.\cite{Wojdyr2010}
 
-XRD pattern, Spectra(EDX, Raman, UV-Vis) redraw using Origin Pro 8.0.
+\iffalse
+incoherent illumination $s = \frac{1.22 \lambda_{vac}}{2n\sin i}$, 
+coherent illumination in microscope $s = \frac{\lambda_{vac}}{n\sin i}$,, 
+phase contrast: transforming phase change in object plane into amplitude variation in image plane. 
+much better than needed, human eye resolving power 0.3 mrad,
+
+The illumination can be considered as incoherent (adding intensity) if the object is self-luminous, or if illminated from all direction.
+
+The opposite occurs in TEM probably, where the specimen is irradiated with complete transverse coherence across its area. back 
+focal plane displays the Fourier transform of complex amplitude in object plane.
+The optical system is a spatial low-pass filter: it builds up images from only the low Fourier components present at the object, having higher values cutoff.
+
+with the aid of Fig.
+
+\fi

### 2014-09-06 BackMatter/app3.tex
ch2 and appendix update

@@
-\chapter{Processes developed during Ph.D. study}
+%\chapter{Processes developed during Ph.D. study}
+\chapter{Growth Recipes}
 
-\section{Growth recipes}
+A schematic diagram of the home-built CVD system is shown in Fig.~\ref{fig:ch2cvd}.
+
+\begin{figure}[htb]
+\centering
+\includegraphics[width=0.9\textwidth]{CVD_model.jpg}
+\caption{Sketch of CVD system for oxide growth, where A1: quartz tube; B1: bubbler; C1-2: gas cylinders; E1: mechanical pump; H1-2: ceramic heater; MFC: flow controller; P1: pressure gauge; V1-4: valves; V5-7: butterfly valves.
+Note: the thermal sensor attached on H-1 is not shown.
+}
+\label{fig:ch2cvd}
+\end{figure}
+
+The following text will refer to this diagram using \fbox{symbol in box} when a specific component is mentioned.
+Please note that the actual CVD system is subject to changes, \emph{e.g.}, in the sulfurization system, a cold trap is used and oxygen tank is absent; whereas in the ZnTe system, a pressure controller is added and hydrogen instead of oxygen is used.
+
+\section{Basic Operation}
+Before performing growth, check the CVD system to confirm its normal state, where the vacuum in idle status is manifested as:
+\begin{itemize}
+\item 5-7 mTorr reading for the pressure gauge (\fbox{P-1})of ZnTe CVD;
+\item 20-22 mTorr reading for the pressure gauge (\fbox{P-1})of oxide CVD;
+\item 45-50 mTorr reading for the pressure gauge (\fbox{P-1}) of sulfur CVD. 
+\end{itemize} 
+and the mass flow controller reading (\fbox{MFC}) should be either negative or zero. If large deviation occurs, check the vacuum sealing and report to lab manager.
+
+\subsection{Venting the chamber}
+To load/unload sample into/out of the chamber, one first needs to bring the pressure up to 1 atm.
+This is done by purging the chamber using Ar gas using steps as following (\textbf{FOLLOW THE EXACT ORDER}):
+\begin{enumerate}
+\item close \fbox{V-5}, one should observe \fbox{P-1} reading increases;
+\item toggle Ar gas switch from OFF to ON, wait for 10 s;
+\item toggle Ar gas purge switch, watching \fbox{P-1} closely; When the chamber is purged with Ar, the indications of actual pressure reaching 1 atm inside are shown as: 
+\begin{itemize}
+\item 760 Torr reading for the ZnTe CVD;
+\item 32-33 Torr reading for the oxide CVD;
+\item 24 Torr reading for the sulfur CVD. 
+\end{itemize} \textbf{Avoid} using higher venting pressure. 
+\item Turn off Ar purge switch rapidly when 1 atm is reached; 
+\item Slowly open \fbox{V-4} to test the ``water'' level in \fbox{B-1}. Close \fbox{V-4} if the level goes up; fully open \fbox{V-4} if otherwise. 
+\end{enumerate}
+%Using the same procedure when harvesting the samples.
+
+\subsection{Pumping down the chamber}
+Most of synthesis experiments in this group are performed in low pressure conditions, so after loading the substrate and source, one needs to pump down the system using the following steps (\textbf{FOLLOW THE EXACT ORDER}):
+\begin{enumerate}
+\item seal the chamber and keep the Ar flow on, one should observe continuous bubbling in \fbox{B-1}. If not check the vacuum sealing;
+\item turn off ANY gas flow first, then close \fbox{V-4};
+\item open \fbox{V-5} slowly, check \fbox{P-1} reading, which should drop rapidly to similar value as in idle status. If not, STOP and check the vacuum sealing.  
+\end{enumerate}
+
+\subsection{Starting heating} 
+The heating is controlled by a close-loop PID method, with the control panel shown in Fig.~\ref{fig:omega}. 
+\begin{figure}[htb]
+\centering
+\includegraphics[width=0.4\textwidth]{omega_temp}
+\caption{Front panel of temperature controller, and the four keys are denoted as $\Omega$, $\nabla$, $\Delta$, and $\Xi$ here. SV means setting value; PV means present value.}
+\label{fig:omega}
+\end{figure}
+
+Change to heating mode by the following steps:
+\begin{enumerate}
+\item turn on the voltage transformer; 
+\item hold $\Xi$ key for 3 second;
+\item use $\nabla$ or $\Delta$ key to circle until ``r.s'' emerges;
+\item hold $\Xi$ key for 1 second to confirm.
+\end{enumerate}
+
+\textcolor{red}{Check the CVD system status periodically, and update the default status. \textbf{DO NOT} proceed if in question. Consult the lab manager or supervisor.}
+
+\section{Emergence Procedures}
+
+When the temperature controller is recovered from a power outrage event, it will try to resume the previous heating procedure or start the stored procedure.
+This can be a problem depending on the previous CVD system status.
+Therefore, it is required that the temperature controller is put to standby mode manually by the frequent user.
+
+Change to standby mode by the following steps:
+\begin{enumerate}
+\item turn off the voltage transformer; 
+\item hold $\Xi$ key for 3 second;
+\item use $\nabla$ or $\Delta$ key to circle until ``stby'' emerges;
+\item hold $\Xi$ key for 1 second to confirm.
+\end{enumerate}
+
+\newpage
+%\section{Growth Recipes}
+
+\section{Substrates and Precursors}
+
+The precursors are summarized in Table.~\ref{tb:pre} and Table.~\ref{tb:mosource}, and substrates in Table.~\ref{tb:subs}.
+
+\begin{table}[htb]
+\centering
+\caption{List of reactants:\ce{WO3},\ce{WS2}}\label{tb:pre}
+\begin{tabular}{lcccr}
+\toprule
+Materials & Name & Purity & Average size & Vendor LOT\\
+\midrule
+Tungsten & 3N   &  99.9\% & 17 $\mu$m & Alfa Aesar \#39749\\
+         & 3N5  &  99.95\% & 32 $\mu$m  & Alfa Aesar \#42477\\
+         & 4N5  &  99.995\% & 3.3 $\mu$m  & Materion T-2049 \\
+         & 5N   &  99.999\% & 1.5 $\mu$m & Alfa Aesar \#12973\\
+Sulfur   & S    &   99.5\%  &  NA  & Alfa Aesar \#10785\\
+\bottomrule
+\end{tabular}
+\end{table}
+
+\begin{table}[htb]
+\centering
+\caption{List of reactants: \ce{MoO3}}\label{tb:mosource}
+\begin{tabular}{lcccr}
+\toprule
+Material & Stock No & LOT &Purity & Vendor\\
+\midrule
+\ce{NaOH}        & S318-500 & 070241 & 99.8\% & Fisher Scientific \\
+\ce{NaI}        & 11665 & K11W054 & 99.9\% &  Alfa Aesar \\
+\ce{KI}        & 42857 & H06Z051 & 99.9\% &  Alfa Aesar \\
+\ce{Na2CO3}        & 33377 & 114X012 & 99.95\% &  Alfa Aesar \\
+\ce{Molybdenum}        & 00932 & I07S024 & 99.9\% &  Alfa Aesar\\
+\bottomrule
+\end{tabular}
+\end{table}
+
+\begin{table}[htb]
+\centering
+\caption{List of substrates}\label{tb:subs}
+\begin{tabular}{lcp{3in}}
+\toprule
+Name & Resistivity (\si{\ohm cm}) &  Remark\\
+\midrule
+\ce{SiO2}-Si  & 0.06 - 0.12  & p type, Born, (100), 1 $\mu$m thermally grown \ce{SiO2} \\
+\ce{SiO2}-Si  & 1 - 10       & p type, Born, (100), 300 nm thermally grown \ce{SiO2} \\
+\ce{Si}       & 3 - 7        & n type, Phosporus (100) \\
+Glass         & NA           &  microscope slide\\
+ITO glass     &               & \ce{SiO2} passivated, 1.1 mm thick float glass \\
+Mica          & NA            & \ce{K(Al2)(Si3Al)O10(OH)2} \\
+\bottomrule
+\end{tabular}
+\end{table}
+
+\section{Tungsten Oxides Growth}
+\subsection{Seeded Growth}
+
+\begin{figure}[htb]
+\centering
+\includegraphics[width=0.7\textwidth]{wo3_seed}
+\caption{Seed \ce{WO3} growth setup, the symbols meaning are explained in Table.~\ref{tb:pre}}
+\label{fig:seed}
+\end{figure}
+
+The substrate treatment in the seeded growth only includes usual cleaning using organic solvents. The growth steps are as following:
+
+\begin{enumerate}
+\item Load $\sim$1 g high purity W powder into the handler end of the long boat, spread the power evenly into 1 in long;  
+\item Load a thin layer of 3N W powder on the clean substrate, spread them uniformly by putting the polished side of another clean Si substrate against the power and sliding the top substrate gently; 
+\item Position the substrate with W powder into the same long boat in a way that when the whole boat in loaded into the chamber, the separation between substrate and power source is the same as indicated in Fig.~\ref{fig:seed};
+\item Vent the chamber to 1 atm, load the long boat with the substrate and source as shown in Fig.~\ref{fig:seed};
+\item Seal the chamber, check the valve status, pump down and record the pressure gauge reading when it becomes stabilized; 
+\item Admit gases (10 sccm Ar and 0.3 sccm \ce{O2}) into the chamber, record the corresponding pressure reading;
+\item Close the furnace, begin the heating procedure as required in Fig.~\ref{fig:seed}; 
+\item Close the butterfly valve to pressure gauge (V-6 in Fig.~\ref{fig:ch2cvd});
+\item Put up the warning sign beside the furnace;
+\end{enumerate}
+
+\subsection{NaOH-Si Growth}
+
+The substrate treatment in this growth includes \begin{enumerate*}[label=\itshape\alph*\upshape)]
+\item usual cleaning using organic solvents;
+\item plasma cleaning (2 Torr oxygen, 3 min); and
+\item drop casting of NaOH solution (50 $\mu$L, 0.01 mol/L).
+\end{enumerate*} The growth steps are as following:
+
+\begin{figure}[htb]
+\centering
+\includegraphics[width=0.7\textwidth]{wo3_naoh}
+\caption{NaOH \ce{WO3} growth, the symbols meaning are explained in Table.~\ref{tb:pre}}
+\label{fig:naw}
+\end{figure}
+
+\begin{enumerate}
+\item Load $\sim$1 g high purity W powder into the handler end of the long boat, spread the power evenly into 1 in long;
+\item Position the NaOH--treated substrate into the same long boat in a way that when the whole boat in loaded into the chamber, the separation between substrate and power source is the same as indicated in Fig.~\ref{fig:naw};
+\item Vent the chamber to 1 atm, load the long boat with the substrate and source as shown in Fig.~\ref{fig:naw};
+\item Seal the chamber, check the valve status, pump down and record the pressure gauge reading when it becomes stabilized; 
+\item Admit gases (10 sccm Ar and 0.4 sccm \ce{O2}) into the chamber, record the corresponding pressure reading;
+\item Close the furnace, begin the heating procedure as required in Fig.~\ref{fig:naw}; 
+\item Close the butterfly valve to pressure gauge (V-6 in Fig.~\ref{fig:ch2cvd});
+\item Put up the warning sign beside the furnace;
+\end{enumerate}
+
+\section{Sulfurization}
+
+The as-synthesized \ce{WO3} samples are further sulfurized to fabricate the core-shell heterostructure.
+
+\begin{figure}[htb]
+\centering
+\includegraphics[width=0.7\textwidth]{ws2_coreshell}
+\caption{\ce{WO3} sulfurization growth}
+\label{fig:suf}
+\end{figure}
+
+\begin{enumerate}
+\item Prepare 200 -- 300 g Sulfur in a small boat;
+\item Vent the chamber to 1 atm, and position the as-grown \ce{WO3} sample and small boat with S into chamber as indicated in Fig.~\ref{fig:suf};
+\item Seal the chamber, check the valve status, pump down and record the pressure gauge reading when it becomes stabilized; 
+\item Add liquid nitrogen into cold trap; 
+\item Admit gases (30 sccm Ar) into the chamber, record the corresponding pressure reading;
+\item Close the furnace, begin the heating procedure as required in Fig.~\ref{fig:suf}; 
+\item Close the butterfly valve to pressure gauge (V-6 in Fig.~\ref{fig:ch2cvd});
+\item Put up the warning sign beside the furnace;
+\end{enumerate}
+
+\section{Moly Oxide Growth}
+
+The substrate treatment in this growth includes \begin{enumerate*}[label=\itshape\alph*\upshape)]
+\item usual cleaning using organic solvents;
+\item plasma cleaning (2 Torr oxygen, 3 min); and
+\item drop casting of NaOH solution (50 $\mu$L, 0.01 mol/L).
+\end{enumerate*} The growth steps are as following:
+
+\begin{figure}[htb]
+\centering
+\includegraphics[width=0.7\textwidth]{moo3_naoh}
+\caption{NaOH \ce{MoO3} growth}
+\label{fig:namo}
+\end{figure}
+
+\begin{enumerate}
+\item Load $\sim$1 g Mo powder into the handler end of the long boat, spread the power evenly into 1 in long;
+\item Position the NaOH--treated substrate into the same long boat in a way that when the whole boat in loaded into the chamber, the separation between substrate and power source is the same as indicated in Fig.~\ref{fig:namo};
+\item Vent the chamber to 1 atm (32-33 Torr reading on gauge), load the long boat with the substrate and source as shown in Fig.~\ref{fig:namo};
+\item Seal the chamber, check the valve status, pump down and record the pressure gauge reading when it becomes stabilized; 
+\item Admit gases (10 sccm Ar and 10 sccm \ce{O2}) into the chamber, record the corresponding pressure reading;
+\item Close the furnace, begin the heating procedure as required in Fig.~\ref{fig:namo}; 
+\item Close the butterfly valve to pressure gauge (V-6 in Fig.~\ref{fig:ch2cvd});
+\item Put up the warning sign beside the furnace;
+\end{enumerate}
+
+\iffalse
+
+\begin{figure}[htb]
+\centering
+\includegraphics[width=0.4\textwidth]{omega_temp}
+\caption{Front panel of temperature controller, and the four keys are denoted as $\Omega$, $\nabla$, $\Delta$, and $\Xi$ here. SV means setting value; PV means present value.}
+\label{fig:omega}
+\end{figure}
+
+Change heating procedure ( heating time and temperature) by the following steps:
+\begin{enumerate}
+\item hold $\Omega$ key for 3 second; a new display should show up, 
+\item use $Xi$ key to circle until ``r.s'' emerges;
+\item hold $\Xi$ key for 1 second to confirm.
+\end{enumerate}
+
+\subsection{sulfurization}
 
@@
 \textbf{3D pdf}
+
+\fi

### 2014-09-06 BackMatter/paper.tex
ch2 and appendix update

@@
 
+why graphene on copper: a review article.
+\cite{Mattevi2011} research thrust, post CMOS fab tech.
+Exposure of hydrocarbon or evaporated carbon onto transition metal, the formation of graphite was surmised as a consequence of diffusion and segregation of carbon impurities from bulk to surface.
+carbon solubility in the metal and.
+
+The lack of control over layer No on Ni is partially attributed to the face that the segregation of carbon from the metal carbide upon cooling occurs rapidly within the Ni grains and heterogeneously at the grain boundaries.
+phase diagram of Ni and C reveals that the solubility of carbon in nickel at high T > 800 C form a solid solution.
+metastable phase \ce{Ni3C} promote the precipitation of C out of Ni.
+Carbon preferentially precipitates out at the grain boundaries of polycrystalline Ni subs so the thickness at graphite is higher than within grains.
+On Fe, due to the high affinity between Fe and C (\ce{Fe3C} is a stable carbide), the formation of $sp^2$ crystalline carbon film is suppressed.
+
+on copper (decomposition of methane gas at 1100 C), independent of heating or cooling rate.
+For copper, the 3d shell is filled, leading to less reactive configuration and weaker affinity towards Carbon.
+Cu can only form soft bonds with C via the charge transfer from the $\pi$ electron in  sp2 hybridized C to the empty 4s states of copper, as supported by the fact that copper does not form any carbide phase, and low C solubility.
+This low affinity and weak bond makes copper a true catalyst fro graphitic carbon formation.
+pre-treatment of copper foil, \ce{CuO}, \ce{Cu2O} removal by reducing annealing at 1000 C.
+
+epitaxial and lattice mismatch is present,
+
+\textbf{four-point probe}
+
+sheet resistivity. a current source in an infinite sheet gives rise to the logarithmic potential
+\[
+\phi - \phi_0 = - \frac{I\rho}{2\pi}\log r,
+\]
+the potential for a dipole becomes
+\[
+\phi - \phi_0 = \frac{I\rho}{2\pi}\log r_1/r_2,
+\]
+
+When equal spacing probes are used, then potential difference between two inner points is 
+\[
+\delta\phi = V = \frac{I \rho}{\pi}\log2,
+\]
+so sheet resistivity $\rho$ is obtained as
+\[
+\rho = 4.5324V/I.
+\]
+
 \section{The physics of semiconductor}
@@
 quasi-fermi level $\phi_n$ or $\phi_p$.
+
+\section{Gary semiconductor fabrication}
+
+photolithography a patter transferring process from mask to photoresist.
+clean room needed to remove dust particles, which could cause dislocation on an epitaxial film, low breakdown voltage in gate oxide, or short circuit.
+
+resolution, registration for effectiveness, throughput for efficiency, shadow printing where mask and wafer in direct contact: cons, dust could case permanent damage to mask, a small gap $d$ (10-50 $\mu$m ) used usually, and the minimium linewideth CD is roughly $\sqrt{\lambda d}$; and projection printing , resolution $l_m = \frac{k_1 \lambda}{NA}$, and depth of focus $\frac{k_2 \lambda}{NA^2}$.
+193-nm using ArF excimer laser, and 157 nm using \ce{F2} excimer laser.
+
+365 nm probably used for \ce{LiNbO3} waveguide.
+
+resolution enhancement using phase shifting mask,  using the electric field of EM wave to chemically activate the photoresist.
+A $\pi$ phase change is obtained by using a transparent layer of $d = \lambda/2(n - 1)$ thickness.
+near-field diffraction,
+
+EUV 10 - 14 nm, C inner shell electron transition,
+
+\section{non-imaging optics}
+
+black body radiation power density $S$ is about 1 \si{kW\per m^2}, the balanced temperature $T = \sqrt[4]{S/\sigma} = 364$ K, where $\sigma$ is Stefan-Boltzmann constant.
+
+ray tracing in vector form as $n^{\prime} r^{\prime} \times n = n r \times n$, invariant $na\theta$,

### 2014-09-06 ch-intro/ch-instr.tex
ch2 and appendix update

@@
 Diffuse reflection spectroscopy (DRS) serves as another tool to estimate the sample band gap using Kubelka-Munk theory (KM).\cite{Tandon1970} The original KM theory was proposed in 1931,\cite{Kubelka1931} and has been popular in the color-related industry, such as painting, pigments, and paper.
+This method is useful for the analysis of samples of difficultly soluble substances and for samples that will react with the solvents upon being dissolved.
+It is also particularly applicable when single crystals of the material could not be obtained.
 Some key points were recapitulated in this thesis.
@@
 p332- 338
+
+the reflecting power associated with a specular-type process is often termed reflectivity, while reflectance is the analogous term for diffusely reflected radiation.
+This two types of reflection are present simultaneously.
+
+Cauchy formula, empirical equation which has subsequently been placed on a firm theoretical basis.
+
+intensity for a complex quantities is obtained by multiplying the complex conjugate.
+
+For strongly absorbing materials, the reflected light is complementary to the color of light transmitted by it, such as gold transmission is green;
+
+For the weakly absorbing substances of rough surface, it will appear the same color by transmission or reflection.
+
+penetration depth is wavelength dependent $d = \frac{In2 \lambda}{2\pi \sqrt{\sin^2\theta_i - n^2}}$, longer wavelength penetrated further than did shorter wavelength. attenuated total reflectance,
+
+thin film, amorphous, mean free path of electron is diminished, and porous in structure. The maxwell-garnett theory provides a satisfactory explanation, where free electron density is reduced.
+
+diffuse reflection: $I = I_0 \exp(-\epsilon d)$, Lambert cosine law formulated. multiple scattering by individual particles. 
+$R_tot = \alpha R_sp + (1- \alpha) R_diff $,
+
+multiple scattering of diffuse radiation in a medium composed of closely packed particles.
+
+\[
+\log{f(r_\infty) = \log{k} - \log{s}}
+\]
+
+It is concluded that the KM function can be used to obtain the characteristic color curve of a given sample only in the limit of small total absorption.
+
+by mixing the sample with an abundance of the reflectance standard, the regular reflection is extensively eliminated.
+
+The color of an object depends on the spectral composition of the source.
+The color of many light sources can be specified in terms of the temperature to which a blackbody radiator must be heated in order to achieve a color match for the source, which is known as color temperature.
+
+integrating sphere: the intensity at any part of the sphere, due to the reflected light is a measure of the total flux from a particular source, independent of the spatial distribution or location of the source on the sphere.
+
+substitution method, comparison method,
 
@@
 
+The information about an object is on display in the objective lens's back focal plane in a Fourier-transform form.
+dark field, removing zero order; Schlieren technique, removing half of diffraction from one side of back focal plane; applications: apodizing in telescope, satellite transmitting aerial structure,
+
 with the aid of Fig. 
+conjugate plane,
+
+electron lens can be made of electrostatic field, and magnetic field, and the B field can be generated from ferromagnetic materials (soft iron, 2 T) or superconducting (100 T).
+
+$C_s$ has dimensions of length, and is approximately equal to the focal length of objective lens (1-3 mm in TEM).
+
+$r_{min} \approx 0.91(C_s \lambda^3)^{1/4}$ is about 0.3 nm typically; with $C_s$ correction, $r_{min}$ can be further reduced to 0.07 nm.
+And human eye can resolve a distance of 0.2 mm, therefore the maximum useful magnification is about $0.2 \times 10^{-3}/0.3 \times 10^{-9} \sim 670 K$.
+
+And after interacting with specimen, the energy spread of transmitted E-beam becomes about 20eV, which will limit the resolution more than does the spherical aberration.
+
+\textbf{coherence of E-beam}
+
+faint points, large disk, the feature of interest is what make the materials imperfect,
+
+20 keV E-beam in TV.
+
+In XRD, both diffraction peak position and intensity are used; whereas in TEM, most time only the positions of spots are of concern.
+
+physical process of diffraction where the atomic planes appear to behave as mirrors for incident E-beam;
 

### 2014-09-11 BackMatter/app_training.tex
training instruction added

--- 2014-09-06 BackMatter/app3.tex
@@
 
-A schematic diagram of the home-built CVD system is shown in Fig.~\ref{fig:ch2cvd}.
+\date{\today}
+Prepared by Tao Sheng
 
+\begin{landscape}
 \begin{figure}[htb]
 \centering
-\includegraphics[width=0.9\textwidth]{CVD_model.jpg}
+\includegraphics[width=8in]{CVD_model.jpg}
 \caption{Sketch of CVD system for oxide growth, where A1: quartz tube; B1: bubbler; C1-2: gas cylinders; E1: mechanical pump; H1-2: ceramic heater; MFC: flow controller; P1: pressure gauge; V1-4: valves; V5-7: butterfly valves.
@@
 \end{figure}
+\end{landscape}
 
+A schematic diagram of the home-built CVD system is shown in Fig.~\ref{fig:ch2cvd}. 
 The following text will refer to this diagram using \fbox{symbol in box} when a specific component is mentioned.
-Please note that the actual CVD system is subject to changes, \emph{e.g.}, in the sulfurization system, a cold trap is used and oxygen tank is absent; whereas in the ZnTe system, a pressure controller is added and hydrogen instead of oxygen is used.
+Please note that the actual CVD system is subject to changes, \emph{e.g.}, in the sulfurization CVD, a cold trap is used and oxygen tank is absent; whereas in the ZnTe CVD, a pressure controller is added and hydrogen instead of oxygen is used.
 
-\section{Basic Operation}
+In this instruction, a few ``unusual'' units will be used frequently, i.e., Torr for pressure and sccm for flow rate.
+Note 1 atm $\equiv$ 760 Torr, and 1 sccm means 1 cubic centimeter per minute at standard condition (RT, 1 atm).
+
+To visualize the important components in the CVD system, a photograph gallery is presented in Fig.~\ref{fig:gallery}.
+Check to make sure you can recognize it in both the schematic drawing (Fig.~\ref{fig:ch2cvd}) and the actual system.
+
+\begin{figure}[htb]
+\centering
+\subfloat[\fbox{P-1}]{\label{fig:gauge}\includegraphics[width=0.4\textwidth]{pressure_gauge}}\hspace{0.04\textwidth}
+\subfloat[]{\label{fig:switch}\includegraphics[width=0.4\textwidth]{toggle_switch}}
+
+\caption{Photograph of pressure gauge reading panel}
+\label{fig:gallery}
+\end{figure}
+
 Before performing growth, check the CVD system to confirm its normal state, where the vacuum in idle status is manifested as:
@@
 \item 5-7 mTorr reading for the pressure gauge (\fbox{P-1})of ZnTe CVD;
-\item 20-22 mTorr reading for the pressure gauge (\fbox{P-1})of oxide CVD;
+\item 20-22 mTorr reading for the pressure gauge (\fbox{P-1})of oxide CVD, as shown in Fig.~\ref{fig:gauge};
 \item 45-50 mTorr reading for the pressure gauge (\fbox{P-1}) of sulfur CVD. 
 \end{itemize} 
-and the mass flow controller reading (\fbox{MFC}) should be either negative or zero. If large deviation occurs, check the vacuum sealing and report to lab manager.
+and the mass flow controller reading (\fbox{MFC}) should be either negative or zero.
 
+\textcolor{red}{If large deviation occurs, check the vacuum sealing and report to lab manager.}
+
+When the chamber is purged with Ar, the indications of actual inner pressure reaching 1 atm inside are shown as: 
+\begin{itemize}
+\item 760 Torr reading for the pressure gauge (\fbox{P-1}) of ZnTe CVD;
+\item 32-33 Torr reading for the pressure gauge (\fbox{P-1})of oxide CVD;
+\item 24 Torr reading for the pressure gauge (\fbox{P-1}) of sulfur CVD.  
+\end{itemize}
+
+\textcolor{red}{\textbf{Avoid} using higher venting pressure, otherwise it might damage the chamber.}
+
+\section{Basic Operation}
+Some common operations used in all CVD system are listed. 
 \subsection{Venting the chamber}
+The Ar gas switch panel is shown in Fig.~\ref{fig:switch}. 
+\begin{figure}[htb]
+\centering
+\includegraphics[width=0.4\textwidth]{toggle_switch.jpg}
+\caption{Photograph of toggle switch panel}
+\label{fig:switch}
+\end{figure}
 To load/unload sample into/out of the chamber, one first needs to bring the pressure up to 1 atm.
@@
 \begin{enumerate}
-\item close \fbox{V-5}, one should observe \fbox{P-1} reading increases;
-\item toggle Ar gas switch from OFF to ON, wait for 10 s;
-\item toggle Ar gas purge switch, watching \fbox{P-1} closely; When the chamber is purged with Ar, the indications of actual pressure reaching 1 atm inside are shown as: 
-\begin{itemize}
-\item 760 Torr reading for the ZnTe CVD;
-\item 32-33 Torr reading for the oxide CVD;
-\item 24 Torr reading for the sulfur CVD. 
-\end{itemize} \textbf{Avoid} using higher venting pressure. 
-\item Turn off Ar purge switch rapidly when 1 atm is reached; 
+\item close \fbox{V-5}, you should observe \fbox{P-1} reading increases;
+\item toggle Ar gas switch from OFF to ON, wait for 10 s to see the corresponding \fbox{MFC} display setting flow rate;
+\item toggle Ar gas purge switch, watching pressure gauge \fbox{P-1} closely; 
+\item Turn off Ar purge switch rapidly when ``1 atm'' is reached; 
 \item Slowly open \fbox{V-4} to test the ``water'' level in \fbox{B-1}. Close \fbox{V-4} if the level goes up; fully open \fbox{V-4} if otherwise. 
@@
 
-\subsection{Starting heating} 
+\subsection{Using Mass Flow Controller}
+
+\subsection{Starting and Stop Heating} 
 The heating is controlled by a close-loop PID method, with the control panel shown in Fig.~\ref{fig:omega}. 
@@
 \centering
-\includegraphics[width=0.4\textwidth]{omega_temp}
+\includegraphics[width=0.3\textwidth]{transformer}
+\includegraphics[width=0.3\textwidth]{omega_temp}
+
+\includegraphics[width=0.3\textwidth]{temp_cont2}
+\includegraphics[width=0.3\textwidth]{temp_cont3}
 \caption{Front panel of temperature controller, and the four keys are denoted as $\Omega$, $\nabla$, $\Delta$, and $\Xi$ here. SV means setting value; PV means present value.}
@@
 
-Change to heating mode by the following steps:
+Change CVD from standby to heating mode by the following steps:
 \begin{enumerate}
@@
 
-\section{Emergence Procedures}
+\section{Advanced Operations and Emergence Procedures}
 
@@
 
+\section{Substrate Preparation}
+
 \section{Tungsten Oxides Growth}
@@
 
-The substrate treatment in the seeded growth only includes usual cleaning using organic solvents. The growth steps are as following:
+The substrate used here can be either Si or 1$\mu$m \ce{SiO2}-Si. The treatment method in the seeded growth only includes usual cleaning using organic solvents. The growth steps are as following:
 
@@
 \item Close the furnace, begin the heating procedure as required in Fig.~\ref{fig:seed}; 
-\item Close the butterfly valve to pressure gauge (V-6 in Fig.~\ref{fig:ch2cvd});
+\item Close the butterfly valve to pressure gauge (\fbox{V-6} in Fig.~\ref{fig:ch2cvd});
 \item Put up the warning sign beside the furnace;
@@
 
-The substrate treatment in this growth includes \begin{enumerate*}[label=\itshape\alph*\upshape)]
+The substrate used here can be either Si or 1$\mu$m \ce{SiO2}-Si. The treatment in this growth includes \begin{enumerate*}[label=\itshape\alph*\upshape)]
 \item usual cleaning using organic solvents;
@@
 \item Close the furnace, begin the heating procedure as required in Fig.~\ref{fig:naw}; 
-\item Close the butterfly valve to pressure gauge (V-6 in Fig.~\ref{fig:ch2cvd});
+\item Close the butterfly valve to pressure gauge (\fbox{V-6} in Fig.~\ref{fig:ch2cvd});
 \item Put up the warning sign beside the furnace;
@@
 \begin{enumerate}
-\item Prepare 200 -- 300 g Sulfur in a small boat;
+\item Prepare 200 -- 300 mg Sulfur in a small boat;
 \item Vent the chamber to 1 atm, and position the as-grown \ce{WO3} sample and small boat with S into chamber as indicated in Fig.~\ref{fig:suf};
@@
 \item Close the furnace, begin the heating procedure as required in Fig.~\ref{fig:suf}; 
-\item Close the butterfly valve to pressure gauge (V-6 in Fig.~\ref{fig:ch2cvd});
+\item Close the butterfly valve to pressure gauge (\fbox{V-6} in Fig.~\ref{fig:ch2cvd});
 \item Put up the warning sign beside the furnace;
@@
 
-The substrate treatment in this growth includes \begin{enumerate*}[label=\itshape\alph*\upshape)]
+The substrate used here can be either Si or 1$\mu$m \ce{SiO2}-Si. The substrate treatment in this growth includes \begin{enumerate*}[label=\itshape\alph*\upshape)]
 \item usual cleaning using organic solvents;
@@
 \item drop casting of NaOH solution (50 $\mu$L, 0.01 mol/L).
-\end{enumerate*} The growth steps are as following:
+\end{enumerate*} When other alkaline ions containing substrates are used, such as glass, ITO glass and mica, the NaOH treatment is skipped. The growth steps are as following:
 
@@
 \item Close the furnace, begin the heating procedure as required in Fig.~\ref{fig:namo}; 
-\item Close the butterfly valve to pressure gauge (V-6 in Fig.~\ref{fig:ch2cvd});
+\item Close the butterfly valve to pressure gauge (\fbox{V-6} in Fig.~\ref{fig:ch2cvd});
 \item Put up the warning sign beside the furnace;
@@
 
-Change heating procedure ( heating time and temperature) by the following steps:
-\begin{enumerate}
-\item hold $\Omega$ key for 3 second; a new display should show up, 
-\item use $Xi$ key to circle until ``r.s'' emerges;
-\item hold $\Xi$ key for 1 second to confirm.
-\end{enumerate}
-
-\subsection{sulfurization}
-
 \section{Characterization and data processing}
@@
 
-\subsection{TEM-Raman integrated measurements}
-
-\subsection{data processing}
-
-\textbf{Multipeaks fitting}
-
-\textbf{3D pdf}
-
 \fi

### 2014-09-21 ch-tms/tmspart.tex
initial review version 0.1

@@
 The enhancement of the total Raman cross section at excitonic resonance in which excitons serve as the intermediate state is stronger compared to that of interband resonance.
-The strong enhancement at excitonic resonance is attributed to the characteristics of excitons in layered materials such as large binding energy, enhanced oscillator strength, and small damping constant.\cite{Zhao2013} \citeauthor{Chung1998} grew \ce{WS2} film using \ce{W(CO)6} and \ce{H2S} precursor.\cite{Chung1998} Raman spectra ($\lambda=632nm$) on films with non-parallel orientation revealed the presence of shoulder mode under $A_{1g}$, which is assigned to LA and TA phonon coupling.
+The strong enhancement at excitonic resonance is attributed to the characteristics of excitons in layered materials such as large binding energy, enhanced oscillator strength, and small damping constant.\cite{Zhao2013} \citeauthor{Chung1998} grew \ce{WS2} film using \ce{W(CO)6} and \ce{H2S} precursor.\cite{Chung1998} Raman spectra ($\lambda=632 nm$) on films with non-parallel orientation revealed the presence of shoulder mode under $A_{1g}$, which is assigned to LA and TA phonon coupling.
 This coupling process stems from disorder-activated zone boundary phonons.
@@
 Yet there is different opinion on these assignments.
-\citeauthor{Molina-Sanchez2011} label the 350 $cm^{-1}$ band as \ce{E_{1u}} instead of 2LA.\cite{Molina-Sanchez2011} And recent theoretical investigations suggest 416 $cm^{-1}$ peak is inactive$B_{1u}$ mode\cite{Molina-Sanchez2011,Ataca2012}, which is the Davydov doublet with $A_{1g}$ mode.
+\citeauthor{Molina-Sanchez2011} label the 350 \si{cm^{-1}} band as \ce{E_{1u}} instead of 2LA.\cite{Molina-Sanchez2011} And recent theoretical investigations suggest 416 \si{cm^{-1}} peak is inactive $B_{1u}$ mode\cite{Molina-Sanchez2011,Ataca2012}, which is the Davydov doublet with $A_{1g}$ mode.
 \citeauthor{Staiger2012} adopted these assignments in studying the resonance Raman profile of \ce{WS2} NTs.\cite{Staiger2012} It was found that
@@
 
-\citeauthor{Krause2009} also measured the resonant Raman on \ce{WS2} nanotubes and found a split within 420 cm$^{-1}$ region, which is labelled as $D-A_{1g}$ mode in analog with the similar defect mode of graphene.\cite{Krause2009} This  $D-A_{1g}$ mode was found enhanced as diameter of \ce{WS2} NTs decrease.
-This thesis work will use $B_{1u}({\Gamma})$ mode to interpret this emerging line at about 416 $cm^{-1}$ of \ce{WS2} NTs, and adopt the 350 $cm^{-1}$ as 2LA(M).
+\citeauthor{Krause2009} also measured the resonant Raman on \ce{WS2} nanotubes and found a split within 420 \si{cm^{-1}} region, which is labelled as $D-A_{1g}$ mode in analog with the similar defect mode of graphene.\cite{Krause2009} This  $D-A_{1g}$ mode was found enhanced as diameter of \ce{WS2} NTs decrease.
+This thesis work will use $B_{1u}({\Gamma})$ mode to interpret this emerging line at about 416 \si{cm^{-1}} of \ce{WS2} NTs, and adopt the 350 \si{cm^{-1}} as 2LA(M).
 \citeauthor{Krause2009a} confirmed $B_{1u}$ mode arise from the inherent structure of \ce{WS2} nanomaterials instead of surface layer effect.

### 2014-09-21 ch-wox/part1.tex
initial review version 0.1

@@
 On basis of this property, \gls{ecd} of tremendous energy saving potential is conceptualized and some products have already been commercialized (i.e.
-smart window\footnote{``We did a case study in five cities, and the average savings in commercial buildings are about 25 percent of the heating, ventilation, and air-conditioning energy use annually," says CEO of View, Inc.}).
+smart window\footnote{"We did a case study in five cities, and the average savings in commercial buildings are about 25 percent of the heating, ventilation, and air-conditioning energy use annually," says CEO of View, Inc.}).
 

### 2014-09-24 FrontMatter/Abstract.tex
inital review revised 1

@@
 
-Transition metal oxides and dichacolgenides.
+Transition metal oxides (TMOs) exhibit rich structures and useful properties, and could been used in solar energy harvesting (\emph{e.g.}, photoelectrochemistry, photocatalysis, and photovoltaics) and energy saving (\emph{e.g.}, electrochromism and photochromism) applications.
+Nano-engineering of these TMOs could produce a variety of nanostructures, modify the electronic and optical properties, potentially enhance the performances and extend their applications into new regimes.
+To fully harvest the advantages of these materials, a scalable growth method and a comprehensive understanding towards the growth-structure-property relation must be established.
+This Ph.D.
+study focused on one-dimensional (1D) tungsten trioxide (\ce{WO3}) and molybdenum trioxide (\ce{MoO3}) nanostructures.
+This dissertation synthesized 1D \ce{WO3} and \ce{MoO3} nanostructures using chemical vapor deposition (CVD) approach, characterized the morphologies and structures, and measured the electrical and optical properties of the as-prepared nanostructures.
+This study aims at accomplishing controlled and scalable growth of \ce{WO3} and \ce{MoO3} using CVD method, establishing the structure-property relations to rationalize nanostructure synthesis for energy applications, and presenting preliminary results on the devices assembled using the \ce{WO3} and \ce{MoO3} nanostructures.
 
+thesis outline?
 \end{abstract}

### 2014-09-24 ch-intro/ch-instr.tex
inital review revised 1

@@
 For other mature techniques, the contents will be limited to the extent where experienced material researchers could repeat the experiments performed here.
-Particular attentions will also be mentioned to properly characterize the nanostrucutres synthesized in this work .
+Particular attentions will also be mentioned for properly characterizing the nanostrucutres synthesized in this work.
 This chapter is concluded with data processing discussion.
@@
 \section{Home-built CVD System}
-
 The synthesis was accomplished in a home-made hot-wall CVD system, as visualized in Fig.~\ref{fig:ch2cvd}.
-The furnace is made by two semi-cylindrical ceramic fiber heaters (WATLOW inc.) with power density from 0.8 to 4.6 \si{W cm^{-2}}.
-Quartz tube (Quartz Sci inc.) of 1 in diameter was primarily used as reaction chamber.
+The furnace is made by two semi-cylindrical ceramic fiber heaters (WATLOW, Inc.) with power density from 0.8 to 4.6 \si{W cm^{-2}}.
+Quartz tube (Quartz Sci, Inc.) of 1 in diameter was primarily used as reaction chamber.
 A mechanical pump was connected to maintain the low pressure environment inside the chamber.
 The length of uniform heating zone is 6 in, with cooling zone extending outward.
-Carriers gas argon (Ar) and reactant gas oxygen (\ce{O2}) was regulated by two mass flow controllers.
+Carriers gas argon (Ar) and reactant gas oxygen (\ce{O2}) was regulated by mass flow controllers.
 
@@
 The controllable parameters of this CVD system include central heating temperature, absolute gas flow and relative ratio of (Ar/\ce{O2}), amount of source material and location of the substrates.
-The operation capability is summarized in Table.~\ref{tab:cvd}.
+The operation capability is summarized in Table~\ref{tab:cvd}.
 
@@
 \centering
-\caption{CVD parameters map}\label{tab:cvd}
+\caption{home-built CVD parameters}\label{tab:cvd}
     \begin{tabular}{lcccr}
@@
 The heating temperature $T$ profile measured at different settings in ambient environment was shown in Fig.~\ref{fig:ch2temp}.
-There exists a uniform heating zone in the center area, spanning over about 2 in.
-Then $T$ descends gradually within the 6 in heating zone, and decrease rapidly at the rest part.
+There exists a uniform heating zone in the center area, spanning over about 2 in; then $T$ descends gradually within the 6 in heating zone, and decrease rapidly at the rest part.
 In this study, a zero position is defined at the upstream edge of reaction chamber covered by the furnace.
@@
 SE is generated from the emission of valence band electrons.
-And due to the limited energy ($<50$ eV), the emission from deep region is mostly absorbed again; only those SE that are at the vicinity of specimen surface can escape.
+And due to the limited energy ($<50$ eV), the emission from deep region is mostly absorbed again; only those electrons that are at the vicinity of specimen surface can escape.
 Hence the SE image is topographical sensitive.
@@
 The X-ray emission stems from inner shell transition of the constitutive atoms, and cathodoluminescence from bandgap transition.
-Other E-beam generated signals, such as Auger electrons, are not useful unless with ultra-high vacuum and clean surface.
+Other E-beam generated signals, such as Auger electrons, are usually not useful in SEM unless with ultra-high vacuum and clean surface.
 
@@
 \includegraphics[width=0.5\textwidth]{xrd_2theta.png}
-
 \caption[XRD configuration]{Bragg-Brentano geometry used in powder diffractometer}
@@
 
-The nanostructures usually grew with preferred orientation; therefore, they cannot be treated as powders.
+The 1D nanostructures in this study usually grew with preferred orientation; therefore, they cannot be treated as powders.
 The interpretation of XRD patterns could become difficult somehow.
-Two possible approaches could be followed to resolve this problem: one is using grazing angle XRD which could reveal in-plane domain size and orientation;\cite{Tersigni2011,Goorsky2002} the other is combining XRD with alternative techniques, such as Raman, TEM.
+Two possible approaches could be followed to bypass this difficulty: one is using grazing angle XRD which could reveal in-plane domain size and orientation;\cite{Tersigni2011,Goorsky2002} the other is combining XRD with alternative techniques, such as Raman, TEM.
 The latter approach was pursued in this work.
@@
 
-TEM qualifies as a very powerful and versatile tool for material characterization.
+TEM qualifies as a powerful and versatile tool for material characterization.
 Akin to the electron-materials interaction introduced in Sec.~\ref{sec:sem}, various signals are generated when the thin specimen was radiated by electron beam.
@@
 
-JEOL JEM-2100 TEM with a \ce{LaB6} filament operated at 200 kV was used in current thesis.
+JEOL JEM-2100 TEM with a \ce{LaB6} filament operated at 200 kV was used in this work.
 A numerical comparison between the scattering events in XRD and TEM is provided to visualize the difference.
 In both processes, the constructive interference is described by $2d\sin\theta = \lambda$, where $d$ is crystal plane distance, $\lambda$ is incident wavelength (photon or electron), and $\theta$, again, is half of the scattering angle.
-Table.~\ref{tab:ch2tem} demonstrates the origin of difference in these two techniques.
+Table~\ref{tab:ch2tem} demonstrates the origin of difference in these two techniques.
 
@@
 However, it is generally more difficult to manipulate electron with magnetic field than do photon with dielectric lens.
-The current resolving power in TEM is on the order of 1.0 \AA without correction of spherical aberration.
+The current resolving power in TEM is on the order of 1.0 \si{\angstrom} without correction of spherical aberration.
 The nominal resolution of JEM-2100 is 2.3 \AA.
@@
 A JEOL double tilt holder was used to rotate the crystal orientation.
-TEM images and SEADs were acquired using a charge coupled device (CCD) from Gatan, inc.
-EDX spectroscopy was captured by similar Oxford Instrument INCA attachment.
+TEM images and SEADs were acquired using a charge coupled device (CCD) from Gatan, Inc.
+EDX spectroscopy was captured by similar Oxford Instrument INCA attachment introduced in Sec.~\ref{sec:sem}.
 
@@
 \fi
+
 \section{Raman and UV-Vis Spectroscopy}
@@
 In this study, Raman measurement was performed using a confocal micro-Raman system (Horiba Scentific, Labram HR800) with excitation wavelengths of 441, 532 and 632 nm.
-For nanowire samples, the laser powers were kept between 0.2 and 0.3 mW, and the acquisition time was 100 s to avoid possible thermal damage.
+For nanowire samples, the laser powers were kept between 0.2 and 0.3 mW, and typical acquisition time was 100 s to avoid possible thermal damage.
 The spectral resolution is about 1 \si{cm^{-1}} and the depth resolution about 2 $\mu$m.
@@
 A Raman pattern database can be found at \url{http://wwwobs.univ-bpclermont.fr/sfmc/ramandb2/index.html}. 
-
 In analytical practice, frequency is expressed in reciprocal wavelength (as cm−1), called wavenumbers;
-
 \fi
@@
 The absorption of materials can be described by Lambert-Beer law: $I = I_0 \exp(-A)=I_0\exp(-\alpha(\lambda) x)$, where $\alpha$ is the absorption coefficient in unit of \si{cm^{-1}}, and $x$ is the optical path in cm.
-When the sample is in liquid form, it is more convenient to use $A =\epsilon_\lambda C x$, where $C$ is the molar concentration (M = \si{\mole dm^{-3}}), and $\epsilon_\lambda$ is the extinction coefficient/molar absorptivity (\si{M^{-1} cm^{-1}}).
+When the sample is in liquid form, it is more convenient to use $A =\epsilon_\lambda C x$, where $C$ is the molar concentration (M = \si{\mole \per L}), and $\epsilon_\lambda$ is the extinction coefficient/molar absorptivity (\si{M^{-1} cm^{-1}}).
 For example, $\epsilon$ for methylene blue (MB) is $10^5 M^{-1}cm^{-1}$ at 660 nm.\cite{Mills1999} So by measuring the maximum absorbance of known sample, its concentration can be estimated accordingly.
@@
 
-In this thesis, UV-Vis and diffuse reflectance spectra were recorded using Schimadzu, UV2600Plus.
+\begin{figure}[htb]
+\centering
+\includegraphics[width=0.5\textwidth]{UV-Vis_drs}
+\caption[UV-Vis and DRS measurement]{schematic drawing of (a) UV-Vis and (b) DRS measurement setup adopted from UV2600Plus manual.}
+\label{fig:ch2uvvis}
+\end{figure}
+
+In this thesis, UV-Vis and diffuse reflectance spectra were recorded using Schimadzu, UV2600Plus, with schematic measurement setup shown in Fig.~\ref{fig:ch2uvvis}.
 For UV-Vis measurement in transmission mode, the as-synthesized sample was removed from substrates by light sonication(Branson 1510R-MTH, 70W) in ethanol or DI water for 15 seconds.
@@
 \fi
+
 \section{Substrates and Pre-growth Treatments}\label{ch2sub}
 
-Silicon and silicon dioxides on Si wafer ($p$-Si(100),Unversity Wafer inc.) were primarily used, and other substrates (i.e.
-Mica\footnote{ \ce{K(Al2)(Si3Al)O10(OH)2}}, glass (Fisher Scientific, microscope slide, 12-549),\footnote{Typical composition is 72.6\% \ce{SiO2}, 0.8\% \ce{B2O3}, 1.7\% \ce{Al2O3}, 4.6\% \ce{CaO}, 3.6\% \ce{MgO} and 15.2\% \ce{Na2O}} stainless steel) were occasionally adapted.
+Silicon and silicon dioxides on Si wafer ($p$-Si(100), Unversity Wafer Inc.) were primarily used, and other substrates (i.e.
+Mica\footnote{ \ce{K(Al2)(Si3Al)O10(OH)2}}, glass (Fisher Scientific, microscope slide, 12-549),\footnote{Typical composition is 72.6\% \ce{SiO2}, 0.8\% \ce{B2O3}, 1.7\% \ce{Al2O3}, 4.6\% \ce{CaO}, 3.6\% \ce{MgO} and 15.2\% \ce{Na2O}} stainless steel) were occasionally used.
 Substrates were first cut into rectangular pieces of certain size and then ultrasonically cleaned (Branson 1510R-MTH) with acetone and alcohol for about 15 minutes each followed by blow-drying with nitrogen gas.
 After solution cleaning, the Si surface is hydrophobic.
-Depending on the specific experimental requirement, sometimes a hydrophilic surface is desired.
-A plasma cleaning was used (Kurt J Lesker: Plasma-Preen 862) to render a hydrophilic Si surface.
-The treatment was done at 2 Torr \ce{O2} for 3 minutes.
+Depending on the specific experimental requirement, a hydrophilic surface may be desired.
+A plasma cleaning was used (Kurt J Lesker: Plasma-Preen 862) to render a hydrophilic Si surface, where reaction among $e$, \ce{O^+}, \ce{O2^+}, \ce{O^-},\ce{O2} occurs, and \ce{OH}-terminated surface followed.\cite{Habib2010} The treatment was done at 2 Torr \ce{O2} for 3 minutes.
 In addition, substrates can be coated with a thin layer of metal before growth.
 This process will be covered  in Sec.~\ref{sec:mag}.
-
-oxygen plasma treatment on HF-etched Si (001). reaction among $e$, \ce{O^+}, \ce{O2^+}, \ce{O^-},\ce{O2}. \ce{OH}-terminated surface obtained.\cite{Habib2010}
 
@@
 
-\section{data processing tools}
+\section{Data Processing}
 
@@
 Various spectra, be it from XRD, EDX, Raman, or UV-Vis, were redraw using Origin Pro 8.0.
-The peak fitting was performed using Fityk, a nonlinear curve fitting program specialized in data processing from powder diffraction, chromatography, photoluminescence and photoelectron spectroscopy, infrared and Raman spectroscopy, \emph{etc}.\cite{Wojdyr2010}
+The peak fitting was performed using \emph{Fityk}, a nonlinear curve fitting program specialized in data processing from powder diffraction, chromatography, photoluminescence and photoelectron spectroscopy, infrared and Raman spectroscopy, \emph{etc}.\cite{Wojdyr2010}
 

### 2014-09-24 ch-intro/ch-intro.tex
inital review revised 1

@@
 \section{Background and Motivation: Nanomaterials for Energy Applications}
+\today
 
 TMO as electrochromic device and TMDC as newly 2D semiconductor, and some VLS.
+Transition metal oxides (TMOs) exhibit rich structures and useful properties, and could been used in solar energy harvesting (\emph{e.g.}, photoelectrochemistry, photocatalysis, and photovoltaics) and energy saving (\emph{e.g.}, electrochromism and photochromism) applications.
 
+\iffalse
 Materials that human can make define the age they live in.
@@
 
+\fi
 Energy saving and harvesting.
@@
 
+how to show the crystalline TMO is better than amorphous thin film counterparts.
+
+Commercial buildings in U.S.
+consumed approximately 35\% of the electricity use.\footnote{U.S.
+Department of Energy, "Energy Efficiency Trends in Residential and Commercial Buildings", 2008.} And traditional windows in the buildings account for up to 40\% of the total heating, cooling and lighting consumption.
+The smart windows is an energy efficient solution by allowing for separate control of the visible and NIR illumination/transmission.
+
 \subsection{Electrochromism for Energy Saving}
@@
 coloration efficiency, the doping amount,
+
+Electrochromic materials are a group of functional materials whose coloration status  can be reversibly switched using a finite durance of low DC voltage (\textless 5 V).
+Another important advantage of smart windows based on EC materials is the failure mode being clear instead of opaque compared to other techniques, e.g, liquid crystal, suspended particles.
 
@@
 
+In comparison to oxides thin films, 1D TMO nanostructures (e.g., nanowires) have following advantages to improve the response speed and enhance the coloration efficiency: (1) With reduced diameters down to nanometer scale, the distance for ion diffusing into and out of the nanowires is significantly shortened.
+(2) The gap between nanowires always provides channels for fast ion diffusion outside the nanowires.
+(3) The large surface area to bulk volume ratio of nanowires is desired to improve the overall usage of material, which results in enhanced the contrast between colored and bleached states.
+Furthermore, doped with certain metals (such as Ti and Ag), the crystalline structure of the TMO nanowires can be modified with enhanced electrochromic properties.\cite{Xiong2008}
+
 \section{Dissertation Outline}
+% what content should be presented
 
@@
 
-This dissertation work primarily focuses on growth and characterization, and will only present some preliminary tests on device and applications.
+This dissertation primarily focuses on growth and characterization, and will only present some preliminary tests on device and applications.
 Experimental tools for growth and characterization will be introduced in Chapter 2.
@@
 The dissertation is then concluded with a summary and future work.
+
+\iffalse
 
@@
 
+\fi
+
 %\input{../end.tex} %  comment out when assembling

### 2014-09-24 ch-moox/moox.tex
inital review revised 1

@@
 
-This remaining sections are organized as following: a brief review on previous studies of \ce{MoO3} is given first, followed is the synthesis method in this dissertation.
+The remaining sections are organized as following: a brief review on previous studies of \ce{MoO3} is given first, followed is the synthesis method in this dissertation.
 Emphasis will be placed on morphological and crystal structure characterization of 1D \ce{MoO3} nanostructures, and the verification of proposed VSS mechanism.
@@
 
-Molybdenum oxide (\ce{MoO3}) crystallizes in three phases, orthorhombic $\alpha$-\ce{MoO3}, monoclinic $\beta$-\ce{MoO3} and the metastable hexagonal h-\ce{MoO3}.\citep{Deb1968,Fibers2007} $\alpha$-\ce{MoO3} phase (hereafter \ce{MoO3}) exhibits anisotropic structure with strong bonding along [001] and [100] direction while van der Waals interaction along [010] direction.\cite{He2003} Due to this unique structure, \ce{MoO3} was found to have several important properties and a wide range of technological applications, such as electrochromism and photochromism,\cite{Yao1992} lubricants,\cite{Sheehan1996} photocatalysts,\cite{Chen2010} and gas sensor, including \ce{CO},\cite{Comini2005} \ce{NO2},\cite{Taurino2006} \ce{H2}\cite{Sha2009} and ethanol.\cite{Choopun} Moreover, other features arise when nanoscale \ce{MoO3} is specifically prepared, for instance, field emission.\citep{Li2002d,Zhou2003b}  As a layered hosting material, \ce{MoO3} can be further modified by intercalating with alkaline ions\citep{Spahr1995,Li2006b,Hu2011} and even divalent ion.\cite{Sian2005} This structural richness have enabled improved performance in Li-ion\cite{Mai2007} and sodium-ion battery.\cite{Hariharan2013} In combination with \ce{TiO2} forming a core-shell structure, these nanoparitcles are reported to lower the photon absorption energy of \ce{TiO2}.\cite{Elder2000} When combined with Ag as layered structure, transparent conducting behavior was observed.\cite{Nguyen2012} In addition, \ce{MoO3} is a good precursor for preparing other useful materials, such as \ce{MoS2} fullerene\cite{Li2003c} and few layer \ce{MoS2}.\cite{Lin2012} It will also be an important member of the van der Waals heterostructures.\cite{Geim2013}
+Molybdenum oxide (\ce{MoO3}) crystallizes in three phases, orthorhombic $\alpha$-\ce{MoO3}, monoclinic $\beta$-\ce{MoO3} and the metastable hexagonal h-\ce{MoO3}.\citep{Deb1968,Fibers2007} $\alpha$-\ce{MoO3} phase (hereafter \ce{MoO3}) exhibits anisotropic structure with strong bonding along [001] and [100] direction while van der Waals interaction along [010] direction.\cite{He2003} Due to this unique structure, \ce{MoO3} was found to have several important properties and a wide range of technological applications, such as electrochromism and photochromism,\cite{Yao1992} lubricants,\cite{Sheehan1996} photocatalysts,\cite{Chen2010} and gas sensor, including \ce{CO},\cite{Comini2005} \ce{NO2},\cite{Taurino2006} \ce{H2}\cite{Sha2009} and ethanol.\cite{Choopun} Moreover, other features arise when nanoscale \ce{MoO3} is specifically prepared, e.g., field emission.\citep{Li2002d,Zhou2003b}  As a layered hosting material, \ce{MoO3} can be further modified by intercalating with alkaline ions\citep{Spahr1995,Li2006b,Hu2011} and even divalent ion.\cite{Sian2005} This structural richness have enabled improved performance in Li-ion\cite{Mai2007} and sodium-ion battery.\cite{Hariharan2013} In combination with \ce{TiO2} forming a core-shell structure, these nanoparitcles are reported to lower the photon absorption energy of \ce{TiO2}.\cite{Elder2000} When combined with Ag as layered structure, transparent conducting behavior was observed.\cite{Nguyen2012} In addition, \ce{MoO3} is a good precursor for preparing other useful materials, such as \ce{MoS2} fullerene\cite{Li2003c} and few layer \ce{MoS2}.\cite{Lin2012} It will also be an important member of the van der Waals heterostructures.\cite{Geim2013}
 
-\subsection{Growth of molybdenum oxide}
-
+\subsection{Growth of Molybdenum Oxide}
 Researchers have been exploring a variety of methods to synthesized different \ce{MoO3} nanostructures.
@@
 Both methods have its own merits.
-Hydrothermal process usually need lower temperature(\textless 300 \si{\degreeCelsius}), but the duration is usually long and requires several post-growth processing steps; while vapor deposition demands relatively high temperature (\textgreater 500 \si{\degreeCelsius}) yet with a shorter time.
+Hydrothermal process usually need lower temperature(\textless 300 \si{\degreeCelsius}), but the duration is usually long and requires several post-growth processing steps; whereas vapor deposition demands relatively high temperature (\textgreater 500 \si{\degreeCelsius}) yet with a shorter time.
 Both methods are scalable for industrial applications.
-However the hydrothermal treatment seems to allow more  nanostructures control than do the vapor deposition method.
+However the hydrothermal treatment seems to allow more  nanostructures control than does the vapor deposition method.
 Nanobelts,\cite{Li2002b} helical nanosheets, nanoflowers, prims-like rods\cite{Li2006a} and nanoribbons\cite{Camacho-Bragado2006} were obtained by the former one while nanoflakes,\cite{Chen2009} nanobelts\cite{Hu2009} and nanowires\citep{Zhou2003b,Chen2011b} dominated the product morphology for the latter one.
@@
 
-\subsection{Lattice structures of molybdenum oxide and molybdates}
+\subsection{Lattice Structures of Molybdenum Oxide and Molybdates}
 
 The coordination number of Mo in \ce{MoO3} is six, so usually \ce{MoO6} octahedra are considered as the building blocks.
-As shown in Fig, the layered structure consisting of zig-zag rows of edge-sharing \ce{MoO6} octahedra, while the rows are mutually connected by corners.
+As shown in Fig.~\ref{fig:mo3model}, the layered structure consisting of zig-zag rows of edge-sharing \ce{MoO6} octahedra, while the rows are mutually connected by corners.
+
+\begin{figure}[htb]
+\centering
+\includegraphics[width=0.7\textwidth]{MoO3_model}
+\caption[\ce{MoO3} crystal model]{\ce{MoO3} crystal model.}
+\label{fig:mo3model}
+\end{figure}
 
@@
 Two half-layers, which are stapled along $b$ axis, build up one \ce{MoO3} layer.\cite{Itoh2001a} This view stresses that the \ce{MoO6} octahedra are rather distorted.
-A brief summary of crystallography, band structure and dielectric function is listed in Appendix.
+%A brief summary of crystallography, band structure and dielectric function is listed in Appendix.
 
-It is known that a series of molybdate compound forms when alkali metal ions are incorporated into the \ce{MoO3} lattice, and the structures are summarized in Table.~\ref{tab:naxmow}.
-Due to the weak cation-oxygen bonding, alkali metal cations only introduce small perturbations into the energies of \ce{Mo-O} ensembles in comparison to cations of other elements.
+It is known that a series of molybdate compound forms when alkali metal ions are incorporated into the \ce{MoO3} lattice, and the structures are summarized in Table~\ref{tab:naxmow}.
+Due to the weak cation-oxygen bonding, alkali metal cations only introduce small perturbations into the energies of \ce{Mo-O} matrix in comparison to cations of other elements.
 And no mixing of vibrations of the cationic sublattices with that of \ce{Mo-O} lattices is anticipated.
@@
 For \ce{A2M_nO_{3n+1}}, exact assignment is not available yet due to the complicated \ce{MO6} octahedra.
-
-Molybdenum bronze also exhibits intriguing features, for instance, charge-density-wave states\footnote{In CDW states, conductivity is non-Ohmic above a threshold electric field.} was found in blue bronze \ce{K_{0.3}MoO3}, which can be prepared by electrolytic reduction of \ce{K2MoO4} and \ce{MoO3} melt.\cite{Dumas1983} \ce{K_{0.3}MoO3} stay as monoclinic phase at room temperature, with lattice parameter $a=18.249$ \AA, $b=7.561$ \AA, $c=9.856$ \AA, and $\beta=117.54$, and exhibits a semiconductor-to-metal transition at 180 K.
+Molybdenum bronze also exhibits intriguing features, for instance, \gls{cdw} states\footnote{In \gls{cdw} states, conductivity is non-Ohmic above a threshold electric field.} was found in blue bronze \ce{K_{0.3}MoO3}, which can be prepared by electrolytic reduction of \ce{K2MoO4} and \ce{MoO3} melt.\cite{Dumas1983} \ce{K_{0.3}MoO3} stay as monoclinic phase at room temperature, with lattice parameter $a=18.249$ \AA, $b=7.561$ \AA, $c=9.856$ \AA, and $\beta=117.54^{\circ}$, and exhibits a semiconductor-to-metal transition at 180 K.
 Electrical transport measurements yield an highly anisotropic ratio of DC conductivities of 1:10:1000.
@@
 
-\subsection{Synthesis methods in this thesis}\label{sec:grow}
+\subsection{Synthesis Methods in This Thesis}\label{sec:grow}
 
-The reactants used in this study were listed in Table.~\ref{tb:mosource}. All reactants were used as received without further processing.
+The reactants used in this study were listed in Table~\ref{tb:mosource}. All reactants were used as received without further processing.
 
@@
 Silicon substrates was first cleaned according to the procedure in Sec.~\ref{ch2sub} on page~\pageref{ch2sub}.
-To apply the catalysts, 54 $\mu$L 10 mM \ce{NaOH} (or \ce{KI}, \ce{Na2CO3}) was drop-cast and then naturally left dry in a convection hood.
+To apply the catalysts, 54 $\mu$L 10 mM \ce{NaOH} (or \ce{KI}, \ce{Na2CO3}) was drop-cast onto clean substrates and then naturally left dry in a convection hood.
 Other alkaline ions-containing substrates, such as glass (Fisher Scientific, microscope slide, 12-549) and indium tin oxide (ITO) coated glass (Delta Technologies, 25\si{\ohm}), were cleaned by the same routine except the absence of plasma cleaning and subsequent aqueous solution dipping.
@@
 
-In a typical synthesis (Fig.~\ref{fig:mooxgrowth}), molybdenum powders were loaded into the uniform heating zone and the sealed chamber was first pumped down to 10 mTorr.
+In a typical synthesis run (Fig.~\ref{fig:mooxgrowth}), about 2 g molybdenum powders were loaded into the uniform heating zone and the sealed chamber was first pumped down to 10 mTorr.
 Then oxygen flow varying between 0.1 sccm to 10 sccm (standard cubic centimeter per minute) was admitted from upstream inlet.
@@
 The substrate was placed in downstream location where the temperature was about 350 to 650 \si{\degreeCelsius} according to open air temperature profile.
-To observe the formation of droplets, clean silicon substrate was coated with 9 nm molybdenum film using magnetron sputtering, followed by \ce{NaOH} dipping as described before.
-Then the substrate was placed into chamber for growth, where all the parameters remained unchanged except the absence of Mo powder source.
-Non-catalytic growth shares the same procedure except the Si substrate treatment.
+Non-catalytic growth shares the same procedure except the NaOH treatment.
 
@@
 
-In this section, the growth of \ce{MoO3} on Si was presented first, followed by catalytic growth, both of which were characterized by SEM, XRD, TEM and EDX.
+In this section, the growth of \ce{MoO3} on bare Si substrates was presented first, followed by catalytic growth, both of which were characterized by SEM, XRD, TEM and EDX.
 Then the catalytic growth mechanism was investigated using \ce{NaOH} treated Si substrate.
-\subsection{Growth on Si substrates}\label{sec:nonsi}
+\subsection{Growth on Si Substrate}\label{sec:nonsi}
 
 The oxidization of Mo starts at 500 \si{\degreeCelsius}, and \ce{MoO3} vapor pressure begins to increase rapidly above 700 \si{\degreeCelsius}.\cite{Margrave1967} The melting point of \ce{MoO3} is reported as 795 \si{\degreeCelsius}.
-Based on these data, the growth was designed with parameters listed in Table.~\ref{tab:mooxsi}.
+Based on these data, the growth was designed with parameters listed in Table~\ref{tab:mooxsi}.
 It is worth mentioning that these parameters are selected and optimized from a wide range of combinations.
-And when the influence of one parameter is studied, the others are fixed.
+When the influence of one parameter is studied, the others are fixed, following the standard practice in controlled experiments.
 %growth parameter
@@
 The usual length of Si substrate is 1 in.
-When positioned at 7 in, it is then located in a temperature range of $650 \sim 350$ \si{\degreeCelsius}.
+When positioned at 7 in, it is then located in a temperature zone of $650 \sim 350$ \si{\degreeCelsius}.
 % cvd layout
@@
 
-From previous works in our group,\cite{predeep2011} the author found that with $T_h = 600$ \si{\degreeCelsius} and substrate placed at 6.5 in, microflakes grew at the high temperature edge of Si, suggesting the nucleation already started.\footnote{020510 batch} When flow of oxygen was gradually reduced, diminished size of micro-flake was observed at the same location of substrates.
-This results indicated the rate-determining step is diffusion when oxygen flow was in the range of 2 sccm to 0.5 sccm.\footnote{(31210-31510 batches)} The author also found the deposition amount on a particular location of the substrate is not linearly proportional to the growth time, \emph{i.e.}, the growth at upper stream edge first increase then decrease.
-This is not surprising when considering the temperature field requires some time to become synchronized as depicted in Fig.~\ref{fig:mooxgrowth}.
-Using conditions in Table.~\ref{tab:mooxsi} and 2 h growth, the author observed the typical micro-flakes morphologies as shown in Fig.~\ref{fig:mosisem}.
-Most flakes exhibit rectangular shape, with average thickness of one micron, standard deviation $\sigma_D=0.34$  $\mu m$.
+From previous works in our group,\cite{predeep2011} the author found that with $T_h = 600$ \si{\degreeCelsius} and substrate placed at 6.5 in, microflakes grew at the high temperature edge of Si, suggesting the nucleation already started.\footnote{in 020510 batch} When flow of oxygen was gradually reduced, diminished size of micro-flake was observed at the same location of substrates.
+This results indicated the rate-determining step is diffusion when oxygen flow was in the range of 2 sccm to 0.5 sccm.\footnote{in (31210-31510) batches} It was also found the deposition amount on a particular location of the substrate is not linearly proportional to the growth time, \emph{i.e.}, the growth at upper stream edge first increase then decrease.
+This is not surprising when considering the 3D temperature field in chamber requires some time to become synchronized as depicted in Fig.~\ref{fig:mooxgrowth}.
+Using conditions in Table~\ref{tab:mooxsi} and 2 h growth, this study observed the typical micro-flakes morphologies as shown in Fig.~\ref{fig:mosisem}.
+Most flakes exhibit rectangular shape, with average thickness of one micron, standard deviation $\sigma_D=0.34 \mu$m.
 % sem
@@
 
-As shown in Fig.~\ref{fig:mooxch}, the crystal structure and phase of as-synthesized samples were examined by XRD and Raman.
+As shown in Fig.~\ref{fig:mooxch}, the crystal structure and phase of the as-synthesized specimen were examined by XRD and Raman.
 The XRD pattern (Fig.~\ref{fig:moxrd}) is readily indexed to the orthorhombic phase of \ce{MoO3} (ICDD PDF 05-0508, \emph{a}=3.9628 \AA, \emph{b}=13.855 \AA, \emph{c}=3.6964 \AA).
@@
 \end{figure}
-
-The Raman spectrum of as-synthesized specimens also closely matches \ce{MoO3} features in previous studies.\cite{Dixit1986,Silveira2012} During m-Raman measurement, the laser spot was carefully focused onto the plates and several inspections on different positions were observed to ensure the reproductivity of spectra data.
+The Raman spectrum of the as-synthesized specimen also closely matches \ce{MoO3} features in previous studies.\cite{Dixit1986,Silveira2012} During m-Raman measurement, the laser spot was carefully focused onto the plates and several inspections on different positions were observed to ensure the reproductivity of spectra data.
 As shown in Fig.~\ref{fig:moram}, 14 distinct bands were well resolved.
@@
 The 819 \si{cm^{-1}} peak is from doubly coordinated oxygen stretching mode arising from corner-shared oxygen between two octahedral.
-The 996 \si{cm^{-1}} peak comes from unshared oxygen stretching mode.\cite{Siciliano2009} The assignment is summarized in Table.~\ref{tab:moram}.
+The 996 \si{cm^{-1}} peak comes from unshared oxygen stretching mode.\cite{Siciliano2009} The assignment is summarized in Table~\ref{tab:moram}.
 % raman assign
@@
 
-\subsection{Growth on NaOH-Si substrate}\label{sec:naohsi}
+\subsection{Growth on NaOH-Si Substrate}\label{sec:naohsi}
 
-All samples in Sec.~\ref{sec:naohsi} were grown for 2 h, too.
+All growth time of samples prepared in Sec.~\ref{sec:naohsi} were 2 h, the same as in Sec.~\ref{sec:nonsi}.
 The only difference in growth conditions from Sec.~\ref{sec:nonsi} is the Si substrate treatment.
-When NaOH is applied onto Si, the morphologies change significantly.
+When NaOH is applied onto Si, the deposition morphologies change significantly.
 Fig.~\ref{fig:ch4sem2by3} shows a comparison of the morphology difference between the non-catalyst growth (Fig.~\ref{fig:ch4sem2by3}a) and the catalyst-assisted growth (Fig.~\ref{fig:ch4sem2by3}b-f) revealed by SEM.
 The non-catalyst growth morphology has been discussed from Fig.~\ref{fig:mosisem} on page~\pageref{fig:mosisem}.
-Several different structures emerge when catalyst is applied, such as nanobelts in Fig.~\ref{fig:ch4sem2by3}d with length up to hundreds of microns, and microtowers in Fig.~\ref{fig:ch4sem2by3}f with diameter around 10 $\mu m$.
+Several different structures emerge when catalyst is applied, such as nanobelts in Fig.~\ref{fig:ch4sem2by3}d with length up to hundreds of microns, and microtowers in Fig.~\ref{fig:ch4sem2by3}f with diameter around 10 $\mu$m.
 
@@
 The crystal structures of the as-synthesized specimens were characterized with X-ray diffraction (XRD) for the non-catalyst growth (Fig.~\ref{fig:ch4tem3by3}a) and catalyst-assisted growth (Fig.~\ref{fig:ch4tem3by3}b).
-The calculated lattice parameters and standard database value(ICDD PDF 05-0508), as listed in Table.~\ref{tab:ch4xrd}, matches favorably.
+The calculated lattice parameters and standard database value (ICDD PDF 05-0508) matches favorably, as listed in Table~\ref{tab:ch4xrd}.
 No other phases were found from XRD spectra for both specimens.
@@
 Fig.~\ref{fig:ch4tem3by3}c shows low magnification TEM image of a rectangular nanoplate grown without catalysts and the SAED pattern.
-The nanoplate was exfoliated by ultra-sonication in acetone solution to obtain high-resolution TEM (HRTEM) image, hence the nanoplate was broken into a smaller piece.
-The SAED pattern in [010] axis and the HRTEM image (Fig.~\ref{fig:ch4tem3by3}d) show the nanoplate has a (010) top surface and two orthogonal edges along [100] and [001] respectively.
+The nanoplate was exfoliated by ultra-sonication in acetone solution to obtain high-resolution TEM (HRTEM) image, hence the nanoplate was broken into fragments.
+The SAED pattern in [010] axis and the HRTEM image (Fig.~\ref{fig:ch4tem3by3}d) show the nanoplate has a (010) top surface and two orthogonal edges along [100] and [001], respectively.
 For the catalyst-assisted growth, Fig.~\ref{fig:ch4tem3by3}e and Fig.~\ref{fig:ch4tem3by3}f-g confirm both the forked nanoplate and the nanobelt have a (010) top surface and a growth direction of [001], while Fig.~\ref{fig:ch4tem3by3}h reveals the microtower grow with (010) layers stacking along a [010] direction.
@@
 These values are slightly smaller than the standard data for $\alpha$-\ce{MoO3} and the results from XRD measurements.
-This deviation in lattice parameters may arise from the small error in TEM measurements and the lattice distortion from the electron beam irradiation.
-These results indicate that all the as-synthesized 1D structures have a layered structure.
-Raman scattering measurement on the catalytic growth sample revealed similar \ce{MoO3} bands, as already displayed in Fig.~\ref{fig:mooxch} on page~\pageref{fig:mooxch}.
+This deviation in lattice parameters may arise from the error in TEM measurements and the lattice distortion from the electron beam irradiation.\cite{Wang2004b} These results indicate that all the as-synthesized 1D structures have a layered structure.
+Raman measurement on the catalytic growth sample revealed similar \ce{MoO3} bands, as already displayed in Fig.~\ref{fig:mooxch} on page~\pageref{fig:mooxch}.
 
-\subsection{Growth mechanism study}\label{sec:nasi}
+\subsection{Growth Mechanism Study}\label{sec:nasi}
 
-To provide a proper context, Vapor-Liquid-Solid (VLS) process is brief introduced.
-VLS is first proposed by Wagner,\cite{Wagner1964} and further developed by \citeauthor{Givargizov1975}.\cite{Givargizov1975} This method has become an important strategy for synthesizing 1D nanostructures.\cite{Lieber1998} Conventionally, a liquid eutectic droplet is formed by catalyst itself or by alloying with the growth material, acting as a trap of growth species.
+To provide a proper context, \gls{vls} process is brief introduced.
+\gls{vls} is first proposed by Wagner,\cite{Wagner1964} and further developed by \citeauthor{Givargizov1975}.\cite{Givargizov1975} This method has become an important strategy for synthesizing 1D nanostructures.\cite{Lieber1998} Conventionally, a liquid eutectic droplet is formed by catalyst itself or by alloying with the growth material, acting as a trap of growth species.
 The growth is initialized by supersaturation of the liquid alloy and subsequent precipitation at the solid-liquid interface.
@@
 
-Previous study in our group has found that \ce{MoO3} deposition on ITO glass exhibits new morphologies that are not observed on Si substrates, yet the mechanism is not well investigated.\cite{predeep2011} Based on the VLS process, it is known that a eutectic state is the key to promote preferred growth direction.
-A list of composition difference between glass and Si substrate shows the extra elements of Na, K, Ca, etc.
+Previous study in our group has found that \ce{MoO3} deposition on ITO glass exhibits new morphologies that are not observed on Si substrates, yet the mechanism is not well investigated.\cite{predeep2011} Based on the \gls{vls} process, it is known that a eutectic state is the key to promote preferred growth direction.
+A list of composition difference between glass and Si substrate shows the extra elements of Na, K, Ca, \emph{etc}.
 Since the concentration of Na is highest among these extra elements, it is most likely to induce the new morphology growth.
-A literature search indeed results a Na-Mo-O phase diagram as shown in Fig.~\ref{fig:ch4pd}.\cite{Hoermann1929} Notice the phases of the Na-Mo-O system can be written as \ce{Na2O.nMoO3}, where n = 1, 2, 3, and 4.
+A literature search indeed shows that there exists a Na-Mo-O phase diagram as shown in Fig.~\ref{fig:ch4pd}.\cite{Hoermann1929} Notice the phases of the Na-Mo-O system can be written as \ce{Na2O.nMoO3}, where n = 1, 2, 3, and 4.
 
@@
 \centering
-\includegraphics[width=0.4\textwidth]{Na2MoO4_Phase}
-\caption[Phase diagram of Na-Mo-O system]{Phase diagram of \ce{Na2MoO4} and \ce{MoO3} reproduced from ref.~\cite{Hoermann1929}}
+\includegraphics[width=0.6\textwidth]{moo3_pdsmall}
+\caption[Phase diagram of Na-Mo-O system]{Phase diagram of \ce{Na2MoO4} and \ce{MoO3} reproduced from Ref.~\cite{Hoermann1929}}
 \label{fig:ch4pd}
@@
 First, Mo powder is oxidized and \ce{MoO3} vapor is produced and transported to downstream by Ar carrier gas.
-Then NaOH reacts with incoming \ce{MoO3} according to formula~\ref{eq:pd}.
-
-\begin{align}\label{eq:pd}
-\cee{NaOH(l) + MoO3(g) -> Na2MoO4(l) + H2O(g)}\\
-\cee{Na2MoO4 + nMoO3   -> Na2O.(n + 1)MoO3}
+Then NaOH reacts with incoming \ce{MoO3} according to Formula~\ref{eq:pd}.
+\begin{subequations}\label{eq:pd}
+\begin{align}
+\cee{NaOH(l) + MoO3(g) &\rightarrow Na2MoO4(l) + H2O(g)\\
+Na2MoO4 + nMoO3   &\rightarrow Na2O.(n + 1)MoO3}
 \end{align}
-
+\end{subequations}
 The melting point of \ce{Na2MoO4} is 687 \si{\degreeCelsius}.
-Based on the open air temperature profile (Fig.~\ref{fig:mooxgrowth}), the substrate is locate in temperature zone between 650 and 350 \si{\degreeCelsius}.
-The temperature distribution is different from ambient measurement due to the pressure change and thermal conduction along the Si substrate.
-It is difficult to acquire the accurate values along the substrate.
-However by considering the flow rate, the actual temperature will be higher than predicted by open air measurement.\cite{Subannajui2010} The melting of \ce{Na2MoO4} is highly possible when taking into account of its size as well.\cite{Bruggemann1997} The continuous supply of \ce{MoO3} growth species will push the phase evolution towards high \ce{MoO3} molar ratio end, with $n$ in \ce{Na2O.nMoO3} increasing from 1 to 4.
+Based on the open air temperature profile (Fig.~\ref{fig:mooxgrowth}), the substrate is located in temperature zone between 650 and 350 \si{\degreeCelsius}.
+The actual temperature distribution during growth is different from ambient measurement due to the pressure change and thermal conduction along the Si substrate.
+It is difficult to acquire the accurate values along the substrate; however, by considering the flow rate, the actual temperature will be higher than predicted by open air measurement.\cite{Subannajui2010} The melting of \ce{Na2MoO4} is highly possible when taking into account of its size as well.\cite{Bruggemann1997} The continuous supply of \ce{MoO3} growth species will push the phase evolution towards high \ce{MoO3} molar ratio end, with $n$ in \ce{Na2O.nMoO3} increasing from 1 to 4.
 Each site of \ce{Na2MoO4} will continue absorb incoming \ce{MoO3}, forming a swelling droplet.
 \ce{MoO3} will precipitate from these seeds when a critical supersaturation concentration is reached, which is about 75\% according to Fig.~\ref{fig:ch4pd}.\footnote{This ratio considerably exceeds that of the usual metal catalyst scenario.
-This high solubility accounts for several observations in current experiments: the dimensions of individual deposit is much larger than that of initial droplet, the concentration of sodium in final products is extremely low.}
-
-Based on this aforementioned analysis, the author propose a hypothesis:
+This high solubility accounts for several observations in current experiments: the dimensions of individual deposit is much larger than that of initial droplet, the concentration of sodium in final products is extremely low.}    Based on this aforementioned analysis, the author propose a hypothesis:
 %theorem environment
@@
 In a typical 2 h growth, the \ce{MoO3} weight increase is about 20 mg, which is about $1.4\times 10^{-4}$ mol.
-This amount far exceeds the mole of applied NaOH $5\times 10^{-7}$.\footnote{Sec.~\ref{sec:grow} on page.~\pageref{sec:grow}} To capture the early stage growth, the supply of \ce{MoO3} must be reduced in a controlled way.
+This amount far exceeds the applied NaOH of $5\times 10^{-7}$ mol.\footnote{Sec.~\ref{sec:grow} on page.~\pageref{sec:grow}} To capture the early stage growth, the supply of \ce{MoO3} must be reduced in a controlled way.
 This can be accomplished by tuning two factors: oxygen flow rate and growth time.
@@
 The oxygen regulated growths were characterized using SEM, EDX and Raman, as shown in Fig.~\ref{fig:ch4oxy}.
-When \ce{O2} flow $\leq 1$ sccm, the deposition show micron size plate growth(Fig.~\ref{fig:ch4oxy}a and d).
+When \ce{O2} flow $\leq 1$ sccm, the deposition show micron size plate growth (Fig.~\ref{fig:ch4oxy}a and d).
 As oxygen flow becomes higher, the deposition amount increases dramatically, with a morphology of 1D forked plate decorated by triangular shape particles.
@@
 \ce{MoO3} phase shows two peaks in this region with the strongest one at about 820 \si{cm^{-1}}; \ce{Na2Mo2O7} phase exhibits four peaks in this region with the strongest one moving to 937 \si{cm^{-1}}, whereas \ce{Na2Mo4O13} phase shows even more peaks in high-frequency region, with a doublet at 962 and 970 \si{cm^{-1}}, respectively.\cite{Schofield2005,Saraiva2011} As predicted by the phase diagram (Fig.~\ref{fig:ch4pd}), Raman spectra identified \ce{Na2Mo2O7} phase in the 0.1 sccm growth (Fig.~\ref{fig:ch4oxy}b), and \ce{Na2Mo4O13} phase on the particles in the rest three growths (Fig.~\ref{fig:ch4oxy}e, h, and k).
-This observation supports the previous hypothesis about the reaction sequence on NaOH-Si substrate.
+This observation supports the previous hypothesis about the reaction sequence on NaOH-Si substrate (Formula~\ref{eq:pd}).
 Element analysis performed on the Raman sites also confirm the presence of Na, Mo and O in particles growth, and only Mo and O in the plate growth (Fig.~\ref{fig:ch4oxy}c, f, i, and l).
@@
 With the increase of the growth time, these nanoplates keep growing and become larger, longer, and denser.
-Ultra-long 1D \ce{MoO3} structures start to grow on top of the nanoplate arrays.
-For 60 min growth, ultra-long nanobelts appear on top of the nanoplates.
+Long 1D \ce{MoO3} structures start to grow on top of the nanoplate arrays.
+For 60 min growth, long nanobelts appear on top of the nanoplates.
 For the growth time of 90 min, the nanobelts grow longer, and some grow into microbelts.
@@
 
-To reveal the growth mechanisms for the ultra-long 1D structures in the second stage, specimens were carefully examined to locate the catalyst particles.
-Small catalyst particles ranging from several hundred nanometers to several microns were found at different locations of these ultra-long 1D structures.
+To reveal the growth mechanisms for the long 1D structures in the second stage, specimens were carefully examined to locate the catalyst particles.
+Small catalyst particles ranging from several hundred nanometers to several microns were found at different locations of these long 1D structures.
 As shown in Fig.~\ref{fig:ch4edx1} and Fig.~\ref{fig:ch4edx2}, EDX element analysis confirmed the presence of Na, Mo, and O in these particles, indicating the particles are sodium molybdate catalysts.
@@
 \end{figure}
-
 It could be of difficulty to observe the sodium molybdate particles on the as-synthesized belts and towers due to the following two factors, one is the consumption of catalysts, such as evaporation; the other is the unpredictable location of the catalyst.
-Unlike the conventional VLS growth where the catalysts were predominantly found at the tip of 1D nanostructures, the catalyst in current study were mostly found at the side wall of long nanobelts, and the location could be on the tip, or several microns away from tip.
+Unlike the conventional \gls{vls} growth where the catalysts were predominantly found at the tip of 1D nanostructures, the catalyst in current study were mostly found at the side wall of long nanobelts, and the location could be on the tip, or several microns away from tip.
 As for the microtowers, it is even rare to observe Na element.\footnote{try m-Raman at different depths}
@@
 Also some belt-like growth is visible on reaction chamber walls, suggesting the evaporation and transport of \ce{Na_xMoO3} vapor phase;
-\item 30 min growth: belts growth begin (500 microns long, grow rate is estimated to be 0.5 $\mu m/s$), tower structures show up as well, but much less than belt.
+\item 30 min growth: belts growth begin (500 microns long, grow rate is estimated to be 0.5 $\mu$ m/s), tower structures show up as well, but much less than belt.
 Two kinds of belts found, tapering and non-tapering.
@@
 \item 2 h growth: there are crossed tapering belts at downstream boundary, with more than one droplet located along the interface of two perpendicular belts, EDX confirmed high Na content.
-\item Using NaOH treated hydrophobic substrates, dense tower array growth was found along the edge areas or molten periphery of droplets, where 5 mins growth already show the initial stage of tower with diameter about 1 $\mu m$, which increase to 10 $\mu m$ in prolonged growth.
+\item Using NaOH treated hydrophobic substrates, dense tower array growth was found along the edge areas or molten periphery of droplets, where 5 min growth already show the initial stage of tower with diameter about 1 $\mu$ m, which increase to 10 $\mu$ m in prolonged growth.
 \end{enumerate}
@@
 \ce{MoO3} could precipitate at catalyst-deposition interface, or propagate along catalyst-environment boundary and spread on the already formed \ce{MoO3} surface.
-Meanwhile, the VS process is not suppressed and \ce{MoO3} adatoms could directly condense on \ce{MoO3} surface.
+Meanwhile, the \gls{vs} process is not suppressed and \ce{MoO3} adatoms could directly condense on \ce{MoO3} surface.
 
@@
 Hereby the transverse growth mode is attributed to the strong spreading capability of \ce{MoO3}.
-The final morphology of observed nanoplate and nanobelt is a combined result of VS and VLS growth.
+The final morphology of observed nanoplate and nanobelt is a combined result of \gls{vs} and \gls{vls} growth.
 
@@
 It is worth mentioning that catalyst particles were not observed on all the 1D structures.
-This fact can be explained by following reasons.
-(1) Catalyst particles can nucleate at any locations along the 1D structures.
-Some particles may be invisible hiding on the backside of the 1D structures.
-(2) Because of the evaporation, the catalyst particles may become too small to be detected.
+This fact can be explained by following reasons:
+\begin{enumerate*}[label=\itshape\alph*\upshape)]
+\item Catalyst particles can nucleate at any locations along the 1D structures. Some particles may be invisible hiding on the backside of the 1D structures;
+\item Because of the evaporation, the catalyst particles may become too small to be detected.
 Some particles could even disappear terminating the catalyzed growth, which may explain the growth of the microtowers with a flat top.
-The evaporation and nucleation of catalyst not only promote the growth of the 1D structures in the second stage growth, they also shape the morphologies of these 1D structures.
-Many 1D structures in the second stage were found to have a tapered shape, such as triangular nanobelts (Figure 2b and 2d) and microbelts (Figure 6k), microtowers with tapered tips (Figure 2f and Figure 7f) and cone-shaped microtowers (Figure 7h).
+\end{enumerate*} The evaporation and nucleation of catalyst not only promote the growth of the 1D structures in the second stage growth, they also shape the morphologies of these 1D structures.
+Many 1D structures in the second stage were found to have a tapered shape, such as triangular nanobelts (Fig.~\ref{fig:ch4sem2by3}b and d), microtowers with tapered tips (Fig.~\ref{fig:ch4sem2by3}f).
 Several factors can contribute to the tapering of the 1D structures.
-First, the reduction in catalyst size may induce the tapering.[38] Due to the evaporation, the size of the catalyst particles can shrink during the growth resulting in the tapered growth.
-The VS growth on the side surfaces is another possible mechanism, which promotes the radial growth of the 1D structures forming the tapered shape.
+First, the reduction in catalyst size may induce the tapering.
+Due to the evaporation, the size of the catalyst particles can shrink during the growth resulting in the tapered growth.
+The \gls{vs} growth on the side surfaces is another possible mechanism, which promotes the radial growth of the 1D structures forming the tapered shape.
 Another important factor is the gradually reduced growth during the cooling process.
@@
 
-\section{Extension of alkaline metal catalyzed growth}
-
-\subsection{Growth on alkaline metal containing substrate}
-
+\section{Extension of Alkaline Metal Catalyzed Growth}
+\subsection{Growth on Alkaline Metal Containing Substrate}
 In analog with the \ce{Na2MoO4}-\ce{MoO3} binary phase diagram, other alkaline metals, such as Li and K, could also form A-Mo-O alloy at elevated temperature.
-This fact enable the usage of a variety of alkaline metal based material as catalyst to promote VLS or VSS growth of \ce{MoO3}.
+This fact allows for the usage of a variety of alkaline metal based material as catalyst to promote \gls{vls} or \gls{vss} growth of \ce{MoO3}.
 Some experiments have been performed in this study, including growth using KI and \ce{Na2CO3} treated Si substrate, glass and mica.
 Fig.~\ref{fig:ch4al1}a-b show the long belt growth on KI treated Si substrate and towers on ITO glass, respectively.
-Compared to NaOH-Si growth, the belt on KI appears with rough edge, whereas the towers on ITO glass exhibit obvious stacking features.
+Compared to NaOH-Si growth, the belt on KI appears with rough edge, whereas the towers on ITO glass exhibit stacking features.
 
@@
 No long belt or tower was observed on the sample with \ce{Na2CO3}.
-Long belts found on mica(\ce{K(Al2)(Si3Al)O10(OH)2}) probably arise from potassium-catalyzed VLS mechanism.\cite{Hu2011} More detailed results on glass will be presented in Sec.~\ref{sec:glass}.
+Long belts found on mica (\ce{K(Al2)(Si3Al)O10(OH)2}) probably arise from potassium-catalyzed \gls{vls} mechanism.\cite{Hu2011} More detailed results on glass will be presented in Sec.~\ref{sec:glass}.
 
@@
 
-The various growth morphologies found using alkaline metal based materials as catalysts demonstrate the proposed VLS mechanism and transverse mode is a general phenomenon, and broad engineering space could be explored to control the dimension of \ce{MoO3}.
+The various growth morphologies found using alkaline metal based materials as catalysts demonstrate the proposed \gls{vss} mechanism and transverse mode is a general phenomenon, and broad engineering space could be explored to control the dimension of \ce{MoO3}.
 
-\subsection{Growth on glass}\label{sec:glass}
-
+\subsection{Growth on Glass}\label{sec:glass}
 The mass transport of sodium ions in silica glass is first estimated to evaluate the amount of catalyst available during the growth of \ce{MoO3}.
@@
 And the dynamics is governed by diffusion equation
-
 \begin{align}
@@
 \end{align}
-
 where $C$ is concentration in unit of \si{mol\per cm^3}, and $D$ is diffusion coefficient in unit of \si{cm^2\per\second}.
-Diffusion coefficient highly depends on the overall environments in which the ions resides.
-Typical values of D for Na ions are listed in Table.~\ref{tab:mona}
+Diffusion coefficient highly depends on the overall environment in which the ions reside.
+Typical values of $D$ for Na ions are listed in Table~\ref{tab:mona}
 
@@
 \centering
-\caption{Na diffusion coefficient (\si{cm^2\per\second}), R is molar gas constant (8.315 \si{\joule\per mol\per K}), and T is temperature in K}\label{tab:mona}
+\caption[Na diffusion coefficient]{Na diffusion coefficient (\si{cm^2\per\second}), R is molar gas constant (8.315 \si{\joule\per mol\per K}), and T is temperature in K}\label{tab:mona}
 \begin{tabular}{lcr}
@@
 \item Na concentration: 0.01 \si{mol\per cm^3}
-\item D: $1.1\times10^{-7}$ \si{cm^2\per\second}
+\item $D$: $1.1\times10^{-7}$ \si{cm^2\per\second}
 \end{itemize}
-
 Then the net flux $J$ is estimated as
 \begin{align}
-J = -D \frac{\Delta C}{\Delta x} = 2.0\times 10^{-8} \si{mol\per cm^2\per\second}
+J = -D \frac{\Delta C}{\Delta x} = 2.0\times 10^{-8} \si{mol\per cm^2\per\second}.
 \end{align}
 
-In a typical 2 h growth, the net amount of Na diffusing out of substrate is then $1.44\times10^{-4}$mol, about 10\% of total Na ions.
-The diffusion length $\sqrt{Dt}$ is 190 $\mu m$.
-Notice this result overestimate since the flux will reduce gradually.
+In typical growth of 2 h, the net amount of Na diffusing out of substrate is then $1.44\times10^{-4}$mol, about 10\% of total Na ions in the glass substrates.
+The diffusion length $\sqrt{Dt}$ is 190 $\mu$ m.
+Notice this result overestimates since the flux will reduce gradually.
 Meanwhile the molar amount of \ce{NaOH} applied on Si substrate is about $5\times10^{-7}$mol.
@@
 However, few report could be found in literature.
-Only one was reported by \citeauthor{Kazenas2010}.\cite{Kazenas2010} The partial pressure of \ce{Na2MoO4} is calculated to be 0.2 mTorr at 800 \si{\degreeCelsius} and $3.5\times 10^{-3}$ mTorr at 670 \si{\degreeCelsius}.\footnote{$logP(atm)= -13794/T + 6.19$}
+Only one was reported by \citeauthor{Kazenas2010}.\cite{Kazenas2010} The partial pressure of \ce{Na2MoO4} is calculated to be 0.2 mTorr at 800 \si{\degreeCelsius} and $3.5\times 10^{-3}$ mTorr at 670 \si{\degreeCelsius}.\footnote{$\log P(atm)= -13794/T + 6.19$}
 
@@
 
-\subsection{Liquid exfoliation of molybdenum oxide}
+The 800-1-15 combination produces the most interesting \ce{MoO3} morphology, as illustrated in Fig.
 
-Few layer (FL) materials attracts intensive research efforts recently.
-The author also made some efforts using liquid exfoliation method to prepare FL \ce{MoO3}.
+%
+
+\subsection{Liquid Exfoliation of Molybdenum Oxide}
+
+\gls{fl} materials attracts intensive research efforts recently.
+This study also made some efforts using liquid exfoliation method to prepare \gls{fl} \ce{MoO3}.
 The exfoliated \ce{MoO3} was characterized using UV-Vis and TEM.
-The optical contrast of FL \ce{MoO3} on \ce{SiO2}-Si is also calculated, which could serve as a guideline to identify FL \ce{MoO3} using optical microscope.
+The optical contrast of \gls{fl} \ce{MoO3} on \ce{SiO2}-Si is also calculated, which could serve as a guideline to identify \gls{fl} \ce{MoO3} using optical microscope.
 
@@
 There are two scattering mechanisms: Rayleigh scattering and Tyndall scattering.
-Rayleigh scattering, which occurs when particles are comparable to wavelength, is inversely proportional to the fourth power of wavelength; While Tyndall scattering, which occurs when the particles are larger, is inversely proportional to the square of the wavelength.
+Rayleigh scattering, which occurs when particles are comparable to wavelength, is inversely proportional to the fourth power of wavelength; while Tyndall scattering, which occurs when the particles are larger, is inversely proportional to the square of the wavelength.
 To fully evaluate the true absorbance of the sample itself, one needs to decouple the scattering part from apparent absorbance.
-Generally  one part of spectrum is selected and assumed it is only caused by scattering.
+Generally, one part of spectrum is selected and assumed it is only caused by scattering.
 Then a empirical dependence shown in Eq.~\ref{eq:sca2} is used as polynomial fitting model.
@@
 
-According to the corrected absorbance spectrum, optical band gap can be deduced, which is known as Tauc Plot.\cite{Tauc1972} The procedure is recapitulated here briefly.
+According to the corrected absorbance spectrum, optical bandgap can be deduced, which is known as Tauc Plot.\cite{Tauc1972} The procedure is recapitulated here briefly.
 Eq.~\ref{eq:tauc} is given to empirically relate optical band gap to absorption.
@@
 \end{equation}
-where B is a proportional coefficient, $\alpha$ is absorption\footnote{The absorbance $A = 0.4343\alpha*l$, where l is the optical path} and $E_g^{opt}$ is defined as optical band gap.
+where B is a proportional coefficient, $\alpha$ is absorption coefficient\footnote{The absorbance $A = 0.4343\alpha*l$, where l is the optical path} and $E_g^{opt}$ is defined as optical bandgap.
 The value n is correlated to the nature of optical transition.
@@
 Depending on the synthesis methods and \ce{MoO3} morphologies, the transition phenomena might vary.
-On the \ce{MoO3} films, \citeauthor{Bouzidi2003} assumed a direct gap (n = 1/2)\cite{Bouzidi2003} while \citeauthor{Szekeres2002} not.\cite{Szekeres2002} The author use n = 2 in this work, plot $\sqrt{(h\nu \alpha)}$ versus photon energy, and extrapolate the linear part onto $h\nu$ axis.
+On the \ce{MoO3} films, \citeauthor{Bouzidi2003} assumed a direct gap (n = 1/2)\cite{Bouzidi2003} while \citeauthor{Szekeres2002} used an indirect gap.\cite{Szekeres2002} The author use n = 2 in this work, plot $\sqrt{(h\nu \alpha)}$ versus photon energy, and extrapolate the linear part onto $h\nu$ axis.
 The intercept is used as $E_g^{opt}$ then.
@@
 
-An alternative apporach is a) define $Y = \alpha E=\alpha h\nu$, and obtain $Y' = \frac{\partial Y}{\partial E}$, then b) plot $Y'/Y$ versus $h\nu$.
+An alternative approach is a) define $Y = \alpha E=\alpha h\nu$, and obtain $Y' = \frac{\partial Y}{\partial E}$, then b) plot $Y'/Y$ versus $h\nu$.
 The band gap value can be obtained from the intercept of extrapolated line on photo energy axis.\cite{Choopun} This approach is not difficult to comprehend as long as we notice from Eq.~\ref{eq:tauc}, $Y = B (h\nu - E_g^{opt})^n$ and $Y' = B n(h\nu - E_g^{opt})^{n-1}$.
@@
 
-The dielectric constants\footnote{Not a constant at all, instead, it has complicated dependence on photon energy} ($\epsilon = \epsilon_1 + i*\epsilon_2$) of \ce{MoO3} have been studied in several reports.\cite{Deb1968,Sabhapathi1995,Miyata1996,Abdellaoui1997,Mondragon1999} The author extracted $\epsilon_1$ from Ref\cite{Itoh2001a} due to the wide photon energy range utilized there.
+The dielectric constants\footnote{Not a constant at all, instead, it has complicated dependence on photon energy} ($\epsilon = \epsilon_1 + i*\epsilon_2$) of \ce{MoO3} have been studied in several reports.\cite{Deb1968,Sabhapathi1995,Miyata1996,Abdellaoui1997,Mondragon1999} The author extracted $\epsilon_1$ from Ref.~\cite{Itoh2001a} due to the wide photon energy range utilized there.
 Notice that $\epsilon_2$ is approximately zero when $h\nu$ is less than 4 eV.
-Since this study is primarily concerned with the optical contrast of FL \ce{MoO3} in visible wavelength region($h\nu < 3$ eV), the refractive indices $n$ is calculated from $n = \sqrt{\epsilon_1}$.
+Since this study is primarily concerned with the optical contrast of few-layered \ce{MoO3} in visible wavelength region ($h\nu < 3$ eV), the refractive indices $n$ is calculated from $n = \sqrt{\epsilon_1}$.
 Due to the orthorhombic phase, \ce{MoO3} exhibit birefringence, that is there are two refractive indices, $n_c$ and $n_a$, as shown in Fig.~\ref{fig:moind}.
 The refractive index is between $ 2.2\sim 2.4$ along $a$ axis, and $ 2.5\sim 2.8$ along $c$ axis.
-Comparison to the low frequency dielectric constant ($18.0\pm1$) implies a primarily ionic bonding in \ce{MoO3}.\cite{He2003}
 
@@
 The positive extreme occur at around 80 nm and 240 nm \ce{SiO2} layer, slightly less than the optimum for observing graphene.
-The refractive indices of Si and \ce{SiO2} within visible wavelengths and MATLAB source code for optical contrast calculation is included in Appendix, with which one can readily evaluate the few layers \ce{MoO3} scenarios and the circumstance when incident light is polarized along $a$ axis.
+The refractive indices of Si and \ce{SiO2} within visible wavelengths and MATLAB source code for optical contrast calculation is included in Appendix~\ref{app:matlab}, with which one can readily evaluate the few layers \ce{MoO3} scenarios and the circumstance when incident light is polarized along $a$ axis.
 
@@
 The clearly resolved lattices indicate high crystal quality of these exfoliated \ce{MoO3}.
-
 \begin{figure}[htb]
@@
 \end{figure}
+Nevertheless, identifying these few layer \ce{MoO3} under optical microscope is still difficult due to both the small flake size and low contrast.\footnote{Human eye threshold contrast (contrast sensitivity)$^{-1}$ is about 10\%.} One need to improve the liquid exfoliation process to obtain larger dimension and high yield.
+This is, however, beyond the scope of current study.
 
-Nevertheless, identifying these few layer \ce{MoO3} under optical microscope is still difficult due to both the small flake size and low contrast.\footnote{Human eye threshold contrast (contrast sensitivity)$^{-1}$ is about 10\%.} One need to improve the liquid exfoliation process to obtain larger dimension and high yield.
-This is however beyond the scope of current study.
+\section{Summary}
 
-\section{summary}
+In this chapter,

### 2014-09-24 ch-tms/tms.tex
inital review revised 1

@@
 In this chapter, a TEM-Raman integrated study on \ce{WO3}-\ce{WS2} core-shell nanostructures is presented.
-We leverage a home-built micromanipulator apparatus to transfer the nanostructures between TEM grids and other desired substrates.
+This study leverages a home-built micromanipulator apparatus to transfer the nanostructures between TEM grids and other desired substrates.
 This technique has enabled us to correlate TEM and micro-Raman measurement on individual nanowires, thereby enhancing the understanding of structure-property relations which would otherwise be blurred in conventional ensemble averaged methods.
@@
 
-The remaining section is arranged in following order: a review on the growth of \ce{MS2} (M = Mo, W) nanotubes (NTs) and 2D few layer (FL) structures will be introduced first, followed by Raman spectroscopy summary on NTs and FL.
-The thesis will then focus on synthesis of \ce{WO3}-\ce{WS2} heterostructure and various characterizations, including both ensemble averaged and on individual nanowires.
+The remaining section is arranged in following order: a review on the growth of \ce{MS2} (M = Mo, W) nanotubes (NTs) and 2D \gls{fl} structures will be introduced first, followed by Raman spectroscopy summary on \ce{WS2} NTs and FL.
+The thesis will then focus on synthesis of \ce{WO3}-\ce{WS2} heterostructure and various characterizations on both ensemble and individual nanowires.
 This chapter is concluded with a brief summary and future work.
@@
 
-\subsection{synthesis method in this work}
+\subsection{synthesis Method in This Work}
 
@@
 All reactants were employed as received without further processing.
-Substrates cleaning precudures have been introduced in Sec.~\ref{ch2sub}.
+Substrates cleaning procedures have been introduced in Sec.~\ref{ch2sub}.
 
@@
 \centering
-\caption{List of reactants}\label{tab:ch5pre}
+\caption{List of reactants for \ce{WO3}-\ce{WS2}}\label{tab:ch5pre}
 \begin{tabular}{lccr}
@@
 \ce{WO3}-\ce{WS2} core-shell NWs were synthesized using direct sulfurization of \ce{WO3} NWs.
-As depicted in Fig.~\ref{fig:ch5grow}c, the as-grown \ce{WO3} NWs were loaded into the center of heating furnace, and $\sim200$mg sulfur (Alfa Aesar 10785, 99.5\%) was positioned just outside the upstream edge of furnace, where the maximum temperature was about 240 \si{\degreeCelsius}.
+As depicted in Fig.~\ref{fig:ch5grow}c, the as-grown \ce{WO3} NWs were loaded into the center of heating furnace, and $\sim200$ mg sulfur (Alfa Aesar 10785, 99.5\%) was positioned just outside the upstream edge of furnace, where the maximum temperature was about 240 \si{\degreeCelsius}.
 After pumping down, the reaction chamber was flushed two times to expel residual air.
@@
 
-\subsubsection{Optimization of W powder oxidization}\label{sec:woxd}
+\subsubsection{Optimization of W powder Oxidization}\label{sec:woxd}
 
@@
 
-\subsubsection{Seeded growth of tungsten oxide NWs}
+\subsubsection{Seeded Growth of Tungsten Oxide NWs}
 With the oxidation experiments study in Sec.~\ref{sec:woxd}, favorable conditions for local growth of NWs were extracted to perform seeded growth.
@@
 Instead, any material that could produce appropriate growth vapor could be employed, indicating the versatility of this approach.
-\subsubsection{Ensemble measurements on core-shell NWs}
+\subsubsection{Ensemble Measurements on Core-Shell NWs}
 
@@
 
-After examining dozens of core-shell NWs, the author found the \ce{WS2} layer number at NW tip was usually the largest, reaching more than ten, and the layer number could decrease to one along the NW body, but there exist some layer number fluctuation and shape modification.
+After examining dozens of core-shell NWs, this thesis found the \ce{WS2} layer number at NW tip was usually the largest, reaching more than ten, and the layer number could decrease to one along the NW body, but there exist some layer number fluctuation and shape modification.
 Fig.~\ref{fig:ch5ws2tem3} shows a smooth transition of \ce{WS2} layer number on the tip region of one NW.
@@
 A systematic study on the sulfurization must be performed to understand the growth dynamics.
-The growth mechanism of \ce{WS2} nanotubes from oxides were thoroughly studied,\cite{Feldman1998} and it is generally agreed that the sulfurization of \ce{WO3} is a diffusion limited reaction.\cite{Feldman1996} It was also suggested that the core \ce{WO3} NWs will become non-stoichiometric phases upon sulfurization.\cite{Feldman1996,ZAK2009} In this study, the author recognize this possibility but also consider two factors different from previous studies: one is the usage of sulfur as precursor instead of \ce{H2} and/or \ce{H2S} as in previous reports, which will accelerate the reduction of \ce{WO3} significantly due to the formation of \ce{H2O}; the other is the short reaction time and light degree of sulfurization, which probably will not distort the \ce{WO3} lattice significantly, as evidenced by the XRD and HRTEM analysis in this section.
+The growth mechanism of \ce{WS2} nanotubes from oxides were thoroughly studied,\cite{Feldman1998} and it is generally agreed that the sulfurization of \ce{WO3} is a diffusion limited reaction.\cite{Feldman1996} It was also suggested that the core \ce{WO3} NWs will become non-stoichiometric phases upon sulfurization.\cite{Feldman1996,ZAK2009} This study recognizes this possibility but also consider two factors different from previous studies: one is the usage of sulfur as precursor instead of \ce{H2} and/or \ce{H2S} as in previous reports, which will accelerate the reduction of \ce{WO3} significantly due to the formation of \ce{H2O}; the other is the short reaction time and light degree of sulfurization, which probably will not distort the \ce{WO3} lattice significantly, as evidenced by the XRD and HRTEM analysis in this section.
 The sulfurization dynamic is then proposed as following in this thesis: the tips of \ce{WO3} NWs exhibit greater crystalline disorder, and \ce{WS2} layers on tips are folded at least along two axes, resulting a higher density of defects and thus a higher sulfurization rate; while the folding along NW body is quasi-one dimensional, subsequently the sulfurization rate could be lower.
@@
 
-Among most of the core-shell NWs examined under TEM, the author observed no discernible consumed core region.
+No obviously consumed core region was observed among most of the core-shell NWs examined under TEM.
 An exception is shown in Fig.~\ref{fig:ch5ws2tem2}.
@@
 
-\subsection{TEM-Raman integrated study}
+\subsection{TEM-Raman Integrated Study}\label{tms:raman}
 
@@
 \includegraphics[width=0.5\textwidth]{ws2trans}
-\caption[Manipulating core-shell NWs]{Core-shell nanowires transfer steps. }
+\caption[Manipulating core-shell NWs]{Core-shell nanowires transfer steps.
+(a) tungsten tip under X100 objective, (b) NWs dispersed onto PDMS, (c) one NW picked up using tungsten tip and (d) tranferred NW on TEM grid}
 \label{fig:ch5ws2trans}
@@
 \includegraphics[width=0.6\textwidth]{ws2map}
-\caption[Mapping core-shell NWs]{Core-shell nanowires mapping. }
+\caption[Mapping core-shell NWs]{Core-shell nanowires mapping.
+Optical image of one NW on TEM under (a) x100 magnification and (b) digital zoom-in view; (b) Low magnification and (d) high magnification TEM images on the same NW.}
 \label{fig:ch5ws2map}
@@
 The resonant nature\cite{Stacy1985} of Raman shift is recognized by the broad band at about 350 \si{cm^{-1}}.
-Recent theoretical\cite{Molina-Sanchez2011} and experimental\cite{Staiger2012} studies on 2D and tubular \ce{WS2} agree this band consist of first order mode $E_{2g}^1$ and second order mode $2LA(M)$, although there is still discrepancy on the exact symmetry assignment, \emph{i.e.}, the presence of $E_{2g}^1(M)$ mode.\cite{Berkdemir2013,Peimyoo2013}.
+Recent theoretical\cite{Molina-Sanchez2011} and experimental\cite{Staiger2012} studies on 2D and tubular \ce{WS2} agree this band consist of first order mode $E_{2g}^1$ and second order mode $2LA(M)$, although there is still discrepancy on the exact symmetry assignment, i.e., the presence of $E_{2g}^1(M)$ mode.\cite{Berkdemir2013,Peimyoo2013}.
 The other peak at about 420 \si{cm^{-1}} is assigned to $A_{1g}$ mode in both bulk\cite{Sekine1980} and few layer \ce{WS2}.
@@
 \centering
-\includegraphics[width=0.7\textwidth]{ws2_tem_ram}
+\includegraphics[width=0.9\textwidth]{ws2_tem_ram}
 \caption[TEM-Raman integrated characterization on core-shell NWs]{(a)-(d) HRTEM images on several NWs showing the \ce{WS2} wall number variation from one to about ten.
@@
 
-\section{summary}
+\section{Summary}
 
-\section{literature to read}
+\iffalse
+
+%\section{literature to read}
 
@@
 
-\section{literature read}
+%\section{literature read}
 
@@
 Nanotube growth is relatively independent of substrates and FL layer is closely related to substrate. Film growth could provide some insight into the latter scenario.
+
+\fi

### 2014-09-24 ch-tms/tmspart.tex
inital review revised 1

@@
 \subsection{Growth of TMDC}
-Shortly after the discovery of carbon nanotube (CNT) in 1991,\cite{Iijima1991} its transition metal dichalcogenides (TMDC) counterparts, \emph{i.e.} \ce{WS2}, was synthesized in 1992.\cite{Tenne1992} In the following decades, other TMDC and several metal oxides nanotubes were demonstrated as well.
-\citeauthor{Rao2003} did an excellent work to review these inorganic nanotubes.\cite{Rao2003} Here the author just recapitulate the main categories of synthesis methods.
+Shortly after the discovery of carbon nanotube (CNT) in 1991,\cite{Iijima1991} its transition metal dichalcogenides (TMDC) counterparts, i.e., \ce{WS2}, was synthesized in 1992.\cite{Tenne1992} In the following decades, other TMDC and several metal oxides nanotubes were demonstrated as well.
+\citeauthor{Rao2003} did an excellent work to review these inorganic nanotubes.\cite{Rao2003} Hence this study just recapitulates the main categories of synthesis methods:
 \begin{enumerate}
-\item Reducing \ce{MO3} in \ce{H2} and \ce{H2S} atmosphere\footnote{M = Mo, W in this work}
-\item Direct decomposition of \ce{MS3}
-\item Decomposition of the ammonium salt \ce{(NH4)2MS4}
-\item Using CNT as templates, arc discharge, or laser ablation
+\item Reducing \ce{MO3} in \ce{H2} and \ce{H2S} atmosphere;\footnote{M = Mo, W in this work}
+\item Direct decomposition of \ce{MS3};
+\item Decomposition of the ammonium salt \ce{(NH4)2MS4};
+\item Using CNT as templates, arc discharge, or laser ablation.
 \end{enumerate}
-
 Except the aforementioned methods, another important reaction in CVD domain is
@@
 \end{equation}
-This reaction has been explored by several authors,\cite{Stoffels1999} and could be used under atmospheric pressure.\cite{Li2004a}
+This reaction has been explored by several authors\cite{Stoffels1999} and could be used under atmospheric pressure.\cite{Li2004a}
 
-All these methods can be applied to the growth of TMDC few layer structures, either directly or with some modifications.
+All these methods can be applied to the growth of TMDC few layer structures, directly or with some modifications.
 Among all the members of TMDC nanotubes, \ce{WS2} and \ce{MoS2} NTs are probably the most well investigated.\cite{Homyonfer1997,Tenne1998,Frey1998,Frey1999,Rothschild2000,Zak2000} The reaction mechanism of \ce{WO3} with \ce{H2}/\ce{H2S} has been thoroughly studied \cite{Feldman1998} and high yield synthesis approach has been established.\cite{Margolin2004} For \ce{WO3} nanoparticles precursor, it was found that the simultaneous reduction and sulfurization is essential for encapsulation of fullerene like \ce{WS2} structures from the oxide nanoparticles.
@@
 \citeauthor{Sloan1999} investigated tungsten oxides structures incorporated in \ce{WS2}.\cite{Sloan1999} The encapsulated \ce{WO_x} cores often exhibit \ce{W3O8} and \ce{W5O_{14}} phases, both of which belong to the \ce{W_nO_{3n-1}} homogenous series, arising as a result of \gls{cs} planes.\cite{Miyano} Some \ce{WO_x} cores show oxygen vacancy instead of CS planes, leading to prominent streaking in SAED patterns.
-Although high yield growth method of \ce{WS2} has been available, the extent to which one can control the NT configuration is still limited, \emph{i.e.}, single-walled NT has not been routinely synthesized and the electronic properties can only be predicted theoretically.
+Although high yield growth method of \ce{WS2} has been available, the extent to which one can control the NT configuration is still limited, i.e., single-walled NT has not been routinely synthesized and the electronic properties can only be predicted theoretically.
 \citeauthor{Seifert2000} investigated the electronic structures of \ce{WS2} nanotube using DFT calculation.\cite{Seifert2000} It was found zigzag (n,0) NTs exhibts a direct gap at $\Gamma$ point, whose size increase monotonically with tube diameter, while armchair (n,n) NTs, unlike its metallic counterpart of (n,n) CNT, show indirect band gap increasing with tube diameter.
@@
 So this work focuses on reviewing the CVD based methods.
-The author will review literatures to date on both \ce{WS2} films and few layer structures, and highlight several typical investigations using different synthesis methods, as summarized in Table~\ref{tab:tmsgrowth}.
+This study will review literatures to date on both \ce{WS2} films and few layer structures, and highlight several typical investigations using different synthesis methods, as summarized in Table~\ref{tab:tmsgrowth}.
 It is important to note that the synthesis of NTs is relevantly independent of substrates, which is in sharp contrast to the scenario of few layer growth.
 The \ce{WS2} nucleation and interaction with substrates play dominant roles in the growth of 2D FL structures.
-This lead us to focus on the \ce{WS2} films growth, which presumably could provide valuable insight into the nucleation process on various substrates.
+Hence it is reasonable to focus on the \ce{WS2} films growth, which presumably could provide valuable insight into the nucleation process on various substrates.
 
-\textbf{\ce{MS2} films} \citeauthor{Lee1994} studied the CVD of \ce{MoS2} by \ce{MoCl5} or \ce{MoF6} and \ce{H2S} in great details.
+\citeauthor{Lee1994} studied the CVD of \ce{MoS2} by \ce{MoCl5} or \ce{MoF6} and \ce{H2S} in great details.
 Phase diagrams for \ce{Mo-S-Cl-H} and \ce{Mo-S-F-H} system at 1 kPa were simulated.\cite{Lee1994} \citeauthor{Endler1999} also investigated the solid-phase diagram for \ce{Mo-S-Cl-H-Ar} system.\cite{Endler1999} It was found pure \ce{MoS2} was main product when molar ratio of \ce{H2S}-\ce{MoCl5} exceeds 2.
@@
 \citeauthor{Regula1997} studied the Ni-W-S phase diagram and the role of Ni layer in promoting \ce{WS2} film growth from amorphous \ce{WS3}.\cite{Regula1997} \emph{In-situ} TEM analysis confirmed the formation of \ce{NiS_x} droplets and lateral growth of \ce{WS2} from these droplets.\cite{Regula1998} Recently, it has been shown that direct sulfurization of W coating (20nm) at 750 \si{\degreeCelsius} on \ce{SiO2}-Si can also produce \ce{WS2} film.\cite{Shanmugam2012a} However, the film is of bulk in nature.
-This could be explained by the study of \citeauthor{Genut1992} towards \ce{WS2} growth on various substrates,\cite{Genut1992} as summarized in Table~\ref{tab:ws2subs}.
-It was found that the \ce{WS2} nucleate from an amorphous \ce{WS3} phase and the substrate has a critical role in determining both the reaction onset temperature and the texture.
+Previous study of \ce{WS2} growth on various substrates by \citeauthor{Genut1992} was summarized in Table~\ref{tab:ws2subs}.\cite{Genut1992} It was found that the \ce{WS2} nucleate from an amorphous \ce{WS3} phase and the substrate has a critical role in determining both the reaction onset temperature and the texture.
 The adhesion of tungsten to quartz was found to be much stronger than to glass.
@@
 
-\textbf{\ce{MS2} FL} For \ce{MoS2}, the reaction mechanism of \ce{MoO3} to \ce{MoS2} was studied by \citeauthor{Weber1996}.\cite{Weber1996} This study provided guidelines for the recent syntheses of \ce{MoS2} by sulfurization of \ce{MoO3}.\cite{Lin2012,Lee2012b,Liu2012a,Najmaei2013} Similar studies on sulfurization of \ce{WO3.H2O} to \ce{WS2} and decomposition of \ce{(NH4)2WO2S2} were also reported.\cite{VanderVlies2002,VanderVlies2002a} In combination with the knowledge from \ce{WS2}, the author compare those insight from several recent reports on \ce{WS2} FL.
+For \ce{MoS2}, the reaction mechanism of \ce{MoO3} to \ce{MoS2} was studied by \citeauthor{Weber1996}.\cite{Weber1996} This study presumably provided guidelines for the recent syntheses of \ce{MoS2} by sulfurization of \ce{MoO3}.\cite{Lin2012,Lee2012b,Liu2012a,Najmaei2013} Similar studies on sulfurization of \ce{WO3.H2O} to \ce{WS2} and decomposition of \ce{(NH4)2WO2S2} were also reported.\cite{VanderVlies2002,VanderVlies2002a} In combination with the knowledge from \ce{WS2}, this thesis compares those insight from several recent reports on \ce{WS2} FL.
 \citeauthor{Cong2013} prepared monolayer \ce{WS2} on 300 nm \ce{SiO2}-Si by sulfurization of \ce{WO3} powders in a one-end sealed tube.\cite{Cong2013} It was suggested that pre-cleaning the inner tube by IPA and DI water could effectively increase the pressure of vapor source.
@@
 
-\citeauthor{Peimyoo2013} prepared \ce{WS2} on \ce{SiO2}-Si using \ce{WO3} powder and sulfur at 800 \si{\degreeCelsius}, aiming at the light emission studies to clarify several contradictory reports.\cite{Peimyoo2013} Uniform PL intensity was found on the triangular \ce{WS2} flakes, in contrast to previous edge enhanced PL.\cite{Berkdemir2013} Raman spectra (532nm) fit includes $E_{2g}^1(M)$ mode at 343 cm$^{-1}$, according to the phonon dispersion calculation \cite{Molina-Sanchez2011} and experimental observation\cite{Zeng2013a,Zhao2013,Lee2013}.
+\citeauthor{Peimyoo2013} prepared \ce{WS2} on \ce{SiO2}-Si using \ce{WO3} powder and sulfur at 800 \si{\degreeCelsius}, aiming at the light emission studies to clarify several contradictory reports.\cite{Peimyoo2013} Uniform PL intensity was found on the triangular \ce{WS2} flakes, in contrast to previous edge enhanced PL.\cite{Berkdemir2013} Raman spectra (532 nm) fit includes $E_{2g}^1(M)$ mode at 343 cm$^{-1}$, according to the phonon dispersion calculation \cite{Molina-Sanchez2011} and experimental observation\cite{Zeng2013a,Zhao2013,Lee2013}.
 However, none of these experimental reports specifically mentioned $E_{2g}^1(M)$ mode.
@@
 As to the growth setup, similar tube furnace as in Ref \cite{VanderZande2013} and \cite{Najmaei2013} was used.
-To gain additional wisdom on \ce{MoS2} growth, the author thus summarize the growth strategies in Ref \cite{VanderZande2013} and \cite{Najmaei2013} as following.
-\citeauthor{VanderZande2013} prepared \ce{MoS2} on 285nm \ce{SiO2}-Si using \ce{MoO3} and S as precursors.\cite{VanderZande2013} In contrast to the seeding method adopted in ref\cite{Lee2013,Lee2012b}, \citeauthor{VanderZande2013} stressed the importance of carefully cleaned substrates\footnote{acetone, 2hrs in \ce{H2SO4} and \ce{H2O2} (3:1) and 5 mins oxygen plasma} and minimum exposure of precursor to air.\footnote{APCVD, 105 \si{\degreeCelsius} for 4hrs, 700 \si{\degreeCelsius} hold for 5mins, and 10 sccm \ce{N2} within 2 inch tube.
+To gain additional wisdom on \ce{MoS2} growth, this thesis thus summarizes the growth strategies in Ref \cite{VanderZande2013} and \cite{Najmaei2013} as following.
+\citeauthor{VanderZande2013} prepared \ce{MoS2} on 285 nm \ce{SiO2}-Si using \ce{MoO3} and S as precursors.\cite{VanderZande2013} In contrast to the seeding method adopted in ref\cite{Lee2013,Lee2012b}, \citeauthor{VanderZande2013} stressed the importance of carefully cleaned substrates\footnote{acetone, 2 h in \ce{H2SO4} and \ce{H2O2} (3:1) and 5 min oxygen plasma} and minimum exposure of precursor to air.\footnote{APCVD, 105 \si{\degreeCelsius} for 4 h, 700 \si{\degreeCelsius} hold for 5 min, and 10 sccm \ce{N2} within 2 in tube.
 rapid cooling from 570 \si{\degreeCelsius}} Dirty substrates or old precursors will lead to hexagonal, 3-point star or irregular polycrystalline structures.
-The growth setup is similar to those in Ref\cite{Lee2012b}.
+The growth setup is similar to those in Ref.\cite{Lee2012b}.
 The substrate and \ce{MoO3} source distance is critical in determining the growth density.
@@
 It was also noted that the \ce{MoS2} flakes morphology seems more uniform in Ref\cite{VanderZande2013} than that in Ref\cite{Lee2012b}.
-On the other hand, \citeauthor{Najmaei2013} also demostrated \ce{MoS2} FL growth by sulfurization of \ce{MoO3} nanoribbons.\cite{Najmaei2013} The ribbons is applied by dispersion and meant to control the source amount.
+On the other hand, \citeauthor{Najmaei2013} also demonstrated \ce{MoS2} FL growth by sulfurization of \ce{MoO3} nanoribbons,\cite{Najmaei2013} which was applied by dispersion and meant to control the source amount.
 It was found the diffusion of vapor \ce{MoO_{3-x}} is rate-limiting step in \ce{MoS2} growth.
 This means the amount of source is critical in successful synthesis.
-The nucleation event is more frequently observed at subs edges, scratches or rough surface.
+The nucleation event is more frequently observed at substrate edges, scratches or rough surface.
 Step edges is then intentionally created to facilitate the nucleation.
-As to the growth dynamics, it was postulated the oxisulfides(\ce{MoOS2} Raman spectra found), as intermediate phase, diffuse across the bare substrates and form triangular domains upon further sulfurization.
-The optimal growth conditions are 800--850 \si{\degreeCelsius}, 700 Torr, and sufficient sulfur.
-This theis then conjectures that the substrate cleaning in ref\cite{Peimyoo2013} should be similar to that in ref\cite{VanderZande2013}, yet the source-to-substrate layout and growth pressure are still needed to be optimized with respect to our current apparatus.
+As to the growth dynamics, it was postulated the oxysulfides (\ce{MoOS2} Raman spectra found), as intermediate phase, diffuse across the bare substrates and form triangular domains upon further sulfurization.
+The optimal growth conditions are 800-850 \si{\degreeCelsius}, 700 Torr, and sufficient sulfur.
+This thesis then conjectures that the substrate cleaning in Ref.\cite{Peimyoo2013} should be similar to that in ref\cite{VanderZande2013}, yet the source-to-substrate layout and growth pressure are still needed to be optimized with respect to the home-built CVD apparatus.
 
@@
 It was found the source substrate distance plays an important role in determining the morphology of the as-grown flakes.\footnote{There is a lattice mismatch between \ce{Al2O3} (4.785 \AA) and \ce{WS2} (3.153 \AA)} The edge termination is not well studied.
-Raman spectra indicate a universal down-shift of $A_{1g}$ peak (1L from 418 on \ce{SiO2}-Si to 416.4 on sapphire).
-PL signal on \ce{SiO2}-Si is stronger than on sapphire.
+Raman spectra indicate a universal down-shift of $A_{1g}$ peak (1L from 418 \si{cm^{-1}} on \ce{SiO2}-Si to 416.4 \si{cm^{-1}} on sapphire).
+PL signal of \ce{WS2} on \ce{SiO2}-Si is stronger than that on sapphire.
 The visibility of \ce{WS2} on \ce{Al2O3} is poor.
@@
 FET on/off ratio is about 100, indicating low mobility.
-The other conditions includes 880 \si{\degreeCelsius}, 90 mm source-to-substrate distance, 1 in quartz tube, and LBM furnace.
-The growth conditions are probably adopted from ref\cite{Huanga2013}.
+The other conditions includes 880 \si{\degreeCelsius}, 90 mm source-to-substrate distance, 1 in quartz tube.
+The growth conditions are probably adopted from Ref.\cite{Huanga2013}.
 
 It is worth noting the flake sizes on sapphire\cite{Zhang2013h} seems larger than that on \ce{SiO2}/Si\cite{Peimyoo2013}, either due to the nucleation barrier difference or the amount of growth vapor and growth time.
-The flake sizes in ref \cite{Cong2013} is not quite uniform, though it could be even larger than that on sapphire \cite{Zhang2013h}.
+The flake sizes in Ref.\cite{Cong2013} is not quite uniform, though it could be even larger than that on sapphire from Ref.\cite{Zhang2013h}.
 One common feature of aforementioned investigations is growth occurs on bare substrates and no catalyst or seeding promoter is employed.
-While there is another synthesis approach \cite{Lee2013,Ling2014} exclusively focusing on using seeding promoter.
+While there is another synthesis approach\cite{Lee2013,Ling2014} exclusively focusing on using seeding promoter.
 \citeauthor{Lee2013} obtained \ce{MoS2} and \ce{WS2} FL on PTAS-treated substrates (\ce{C24H12K4O8}), where tiny ($\sim 200$ nm) seeds were found under AFM.
-More recently, \citeauthor{Ling2014} systemically investigated the role of seeding promoter in facilitating the nucleation of \ce{MoS2} monolayers.\cite{Ling2014} It was found various aromatic molecules are effective yet inorganic nanoparticles are not.
+More recently, \citeauthor{Ling2014} systemically investigated the role of seeding promoter in facilitating the nucleation of \ce{MoS2} monolayer.\cite{Ling2014} It was found various aromatic molecules are effective yet inorganic nanoparticles are not.
 The mechanism of thin film growth depends on the surface energy and chemical potentials of the deposited layers and their substrates.
@@
 Seeding promoter probably lowered the surface energy by wetting, thus provided heterogenous nucleation sites.
-Continuous \ce{MoS2} monolayer is obtained by evaporating \ce{F16CuPc} of 2 \AA on desired receiving substrates.
+Continuous \ce{MoS2} ML is obtained by evaporating \ce{F16CuPc} of 2 \si{\angstrom} on desired receiving substrates.
 In each growth, about $10^{-10}$ mol PTAS was applied onto \ce{SiO2}-Si, which was rendered hydrophilic and gentle gas blow to distribute the solution evenly.
@@
 \begin{itemize}
-\item \ce{WO3} powder size distribution and absolute amount (0.69 g \ce{WO3} in 10 mL acetone or IPA, inspired by the \ce{MoO3} nanoribbons usage)
-\item Sulfur amount and heating method to ensure a constant sulfur-rich environment
-\item \ce{WO3} powder source to substrate distance, which is coupled to pressure and carrier gas flow in determining the transport (atmospheric, 3-5 mm)
-\item temperature ramping and growth time (750-800 \si{\degreeCelsius}, 3-10 min)
-\item 300 nm-\ce{SiO2}-Si substrate to make OM flakes identification easier
+\item \ce{WO3} powder size distribution and absolute amount (0.69 g \ce{WO3} in 10 mL acetone or IPA, inspired by the \ce{MoO3} nanoribbons usage);
+\item Sulfur amount and heating method to ensure a constant sulfur-rich environment;
+\item \ce{WO3} powder source to substrate distance, which is coupled to pressure and carrier gas flow in determining the transport (atmospheric, 3-5 mm);
+\item temperature ramping and growth time (750-800 \si{\degreeCelsius}, 3-10 min);
+\item 300 nm \ce{SiO2}-Si substrate to make OM flakes identification easier.
 \end{itemize}
@@
 
-\subsection{Raman on bulk and FL TMDC}
+\subsection{Raman on Bulk and FL TMDC}
 
@@
 The previous Raman efforts on \ce{MS2} film, especially the one using resonant conditions, provided critical insight into the electronic structure and lattice dynamics of these TMDC layered materials.
-Next a comparison of Raman knowledge between TMDC nanotubes and FL structures is given.
+A comparison of Raman between TMDC nanotubes and FL structures is given.
 For \ce{WS2} NTs, focus is on the asymmetry of $A_{1g}$ mode and its origin.
 And for \ce{WS2} FL structures, layer number dependent fingerprint is summarized, and some attempts on analysis the resonant Raman profiles of \ce{WS2} are made.
-
 It is worth noting that Raman technique proves to be extreme useful in characterizing CNT and graphene, i.e., tube diameter by assigning the RBMs (radial breathing modes) and G peaks position.\cite{Bonaccorso2013} And Raman spectroscopy also qualifies as an excellent tool to monitor tensile features of TMDC in both 2D and tubular forms.\cite{Tang2013}
@@
 Raman spectra arise from the inelastic light scattering of optical phonons.
-In back scattering geometry, the phonon wave-vector stands as $q = 4\pi\frac{n}{\lambda}$.
-The refractive index $\tilde{n}$ of \ce{WS2} at 532 nm is about $4.726 - 0.737i$.
-Compared to the size of Brillouin zone ($\pi/a = 10^{10}m^{-1}$), resonant Raman could or could not probe phonon at $M$ point.
+In back scattering geometry, the photon wave-vector stands as $q = 4\pi\frac{n}{\lambda}$.
+The refractive index $\tilde{n}$ of \ce{WS2} at 532 nm is about $4.726 - 0.737i$, corresponding to a wave-vector about $1\times10^8$ \si{m^{-1}}.
+Compared to the size of Brillouin zone ($\pi/a = 10^{10}$\si{m^{-1}}), off-resonant Raman could only probe phonon at $\Gamma$ point, where the phonon momentum ($\hbar k$) is close to zero.
 
-Before discussing the Raman spectra features, the author briefly recapitulate some symmetry notations and vibration modes.
+Before discussing the Raman spectra features, this thesis briefly recapitulates some symmetry notations and vibration modes.
 \ce{MoS2} is used as an example, and those definitions apply to \ce{WS2} as well.
@@
 \centering
-\caption{Lattices vibration of \ce{MS2}, adopted from ref\cite{Molina-Sanchez2011}}\label{tab:tmslattice}
+\caption[Lattices vibration of \ce{MS2}]{Lattices vibration of \ce{MS2}, adopted from Ref.\cite{Molina-Sanchez2011}}\label{tab:tmslattice}
 \begin{tabular}{lcccc}
@@
 \end{table}
-
 The $E$ type phonon branches correspond to in-plane normal modes, while the $A$ type phonons result from out-of-plane vibrations.
@@
 The $E_{2g}^2$ mode is a shear mode corresponding to the vibration of two rigid layers against
-each other and appears at very low frequencies ($<50 cm^{-1}$ \cite{Zhang2013e}).
+each other and appears at very low frequencies ($<50$ \si{cm^{-1}} \cite{Zhang2013e}).
 The $E_{1g}$ mode, which is an in-plane vibration of only the S atoms, is forbidden in the backscattering Raman configuration.
@@
     \cmidrule(l){3-5}
-    Symmetry                & Atoms & \ce{WS2} ML\cite{Cong2013}  & \ce{WS2} NT \cite{JMR7990865}  & \ce{WS2} bulk \cite{Sourisseau1991} \\
+    Symmetry                &  & \ce{WS2} ML\cite{Cong2013}  & \ce{WS2} NT \cite{JMR7990865}  & \ce{WS2} bulk \cite{Sourisseau1991} \\
     \midrule
@@
 Raman technique has also provided much insight into the few layer \ce{MS2}.
-\ce{MS2} layer numbers are readily identified by the wavenumber distance between $A_{1g}$ and $E_{2g}^1$ mode for \ce{MoS2}\cite{Buscema2013} and \ce{WS2}\cite{Berkdemir2013}.
+\ce{MS2} layer numbers are readily identified by the Raman shift distance between $A_{1g}$ and $E_{2g}^1$ mode for \ce{MoS2}\cite{Buscema2013} and \ce{WS2}\cite{Berkdemir2013}.
 Yet due to the relative small shift of $A_{1g}$ mode and little shift of $E_{2g}^1$ mode in \ce{WS2} FL, the frequencies distance might not qualify as an unambiguous way to distinguish layer numbers.
 Yet the resonant Raman profile on \ce{WS2} exhibit unique features between the intensity of 2LA and $A_{1g}$ mode,\cite{Berkdemir2013,Zhao2013} which provide another routine to assure the monolayer presence.
-However, the author notice some discrepancy in de-convolution of \ce{WS2} resonant profile between 300 and 400 cm$^{-1}$, i.e., the presence of $E_{2g}^1(M)$ mode at about 344 cm$^{-1}$.\cite{Peimyoo2013,Cong2013,Berkdemir2013} Rigid assignments of this mode still requires further theoretical\cite{Ataca2012} and experimental efforts.
-In addition, \citeauthor{M2013} reported temperature dependent of 1L \ce{WS2}.\cite{M2013} When the temperature increase from 77 K to 623 K, A1g shift from 420 to 416.5 cm$^{-1}$.
+However, this thesis notices some discrepancy in de-convolution of \ce{WS2} resonant profile between 300 and 400 cm$^{-1}$, i.e., the presence of $E_{2g}^1(M)$ mode at about 344 cm$^{-1}$.\cite{Peimyoo2013,Cong2013,Berkdemir2013} Rigid assignments of this mode still requires further theoretical\cite{Ataca2012} and experimental efforts.
+In addition, \citeauthor{M2013} reported temperature dependent of 1L \ce{WS2}.\cite{M2013} When the temperature increase from 77 K to 623 K, $A_{1g}$ shift from 420 to 416.5 cm$^{-1}$.
 Interestingly in this report 2LA/$A_{1g}$ ratio (514 nm excitation) seems less than unit.
@@
 This is caused by the different cross-section enhancement for a specific excitation condition.
-The A and B excitonic absorption in \ce{WS2} mainly arise from the $d_{xy}$ and $d_{x^2 - y^2}$ states to $d_{z^2}$ states of tungsten atoms.
+The A and B excitonic absorption in \ce{WS2} mainly arises from the $d_{xy}$ and $d_{x^2 - y^2}$ states to $d_{z^2}$ states of tungsten atoms.
 Thus, electrons excited by 633 nm laser have a character of tungsten $d_{z^2}$ orbitals aligned along the $c$ axis perpendicular to \ce{WS2} basal plane.
@@
 \begin{enumerate}
-\item $B_{1u}$ mode arise from curvature and structural disorder
-\item $B_{1u}/A_{1g}$ intensity ratio strongly depends on excitation, and exceeds unity when excitation energy less than 1.9 eV.
+\item $B_{1u}$ mode arise from curvature and structural disorder;
+\item $B_{1u}/A_{1g}$ intensity ratio strongly depends on excitation, and exceeds unity when excitation energy less than 1.9 eV; and
 \item  An excitonic transition energy of NT is found have a local minimum at about 50 nm, (layer number probably \textgreater 10), and increase either way. Yet all below the bulk value.
@@
 \citeauthor{Krause2009a} confirmed $B_{1u}$ mode arise from the inherent structure of \ce{WS2} nanomaterials instead of surface layer effect.
-It is also worth noting that $A_{1g}$ is stronger than 2LA under 632 nm yet weaker under 532 nm excitation, similar to previous discussion of FL scenarios.\cite{Krause2009a} This is in consistent with our observation of Raman spectra on the \ce{WS2}-\ce{WO3} structures, as discussed later.
+It is also worth noting that $A_{1g}$ is stronger than 2LA under 632 nm yet weaker under 532 nm excitation, similar to previous discussion of FL scenarios.\cite{Krause2009a} Similar observation of Raman spectra on the \ce{WS2}-\ce{WO3} structures was found in this study, as discussed in Sec.~\ref{tms:raman}.
 \citeauthor{Rafailov2005} estimated the orientation dependence of resonant raman on one MWNT \ce{WS2} attached to the cantilever tip of AFM.\cite{Rafailov2005} Antenna effect lead to optical transition occurring only for polarization parallel to nanotube axis.
@@
 
-As a useful reference, the lattices dimensions are summarized in Table~\ref{tab:ms2lattice},
+As a reference, the lattice dimensions are summarized in Table~\ref{tab:ms2lattice}.
 %lattice

### 2014-09-24 ch-wox/ch-wox.tex
inital review revised 1

@@
 
-\section{growth method and results discussion}
+\section{Growth Methods and Results Discussion}
 
@@
 % Tungsten powders size and purity
-\begin{table}
+\begin{table}[htb]
 \centering
@@
 
-In a typical OT experiment (Fig.~\ref{fig:wogrow}), about 2 g tungsten powder was positioned in the upstream end of a quartz boat and downstream about 2.5 in the substrate was stationed.
-The substrates were p-type, boron-doped and [100]-orientated silicon with about 1 $\mu m$ thermally-grown silicon oxide layer on the polished side.
+In a typical OT experiment (Fig.~\ref{fig:wogrow}), about 2 g tungsten powder was positioned in the upstream end of a quartz boat and downstream about 2.5 inch the substrate was stationed.
+The substrates were p-type, boron-doped and [100]-orientated silicon with about 1 $\mu$m thermally-grown silicon oxide layer on the polished side.
 The cleaning procedures have been elucidated on page.~\pageref{ch2sub}.
@@
 
-\subsection{Tungsten Oxides by OT Growth}\label{sec:nawox}
+\subsection{Tungsten Oxides: Residual Effect}\label{sec:nawox}
 
@@
 This difference mainly arises from the average size, which will dictate the degree of oxidation.
+Another possible reason is the presence of foreign elements in each W powders.
+As indicated by the certificate of analysis from corresponding vendors (attached in Appendix), carbon, nickel, iron and sodium can amount up to tens of ppm in low purity W sources.
 
@@
 The nanostructures were \glspl{nw} with lengths up to several hundred microns and diameters about 40 to 500 nm.
-The deposition of nanowires was generally located on the substrates with a growth temperature range from 660 to 420 \si{\degreeCelsius}.
-Close-up view at higher magnification revealed some nanowires were cylinder-shaped and some were belt-shaped.
-At lower temperature end of substrate, microplate structures with a rectangular shape grew among the nanowires as displayed in Fig.~\ref{fig:nawoxsemedx}b and inset.
-The chemical compositions of the deposition were analyzed using EDX.
-A representative EDX spectrum in Fig.~\ref{fig:nawoxsemedx}c shows the existence of W, Na, O, and Si signals in the specimen, where the Si signal is from the substrate.
+The deposition of nanowires was generally located on the substrates with the growth temperature ranging from 660 to 420 \si{\degreeCelsius}.
+Enlarged view at higher magnification revealed some nanowires were cylindrical and some were bundled belt.
+Rectangular microplate structures grew at lower temperature end of substrate, as displayed in Fig.~\ref{fig:nawoxsemedx}b and inset.
+The chemical compositions of the deposition were analyzed using \gls{edx}.
+A representative \gls{edx} spectrum in Fig.~\ref{fig:nawoxsemedx}c shows the existence of W, Na, O, and Si signals in the specimen, where the Si signal is from the substrate.
 The crystal structures of the as-synthesized specimens were examined using XRD.
 The diffraction peaks were carefully indexed and the deposition was identified as two phases of sodium tungsten oxides and one phase of tungsten oxide as indicated on Fig.~\ref{fig:nawoxsemedx}d.
-The two sodium tungsten oxide phases are the triclinic \ce{Na5W_{14}O_{44}} phase (ICDD PDF 04-012-4449, \emph{a}=7.2740 \AA, \emph{b}=7.2911 \AA, \emph{c}=18.5510 \AA, $\alpha$=96.37$^\circ$, $\beta$=90.89$^\circ$, $\gamma$=119.65$^\circ$) and the triclinic \ce{Na2W4O_{13}} phase.\footnote{ICDD PDF 04-012-7108, \emph{a}=11.1630 \AA, \emph{b}=3.8940 \AA, \emph{c}=8.2550 \AA, $\alpha$=90.60$^\circ$, $\beta$=131.36$^\circ$, $\gamma$=79.70$^\circ$} The tungsten oxide is the monoclinic \ce{WO3} phase.\footnote{ICDD PDF 01-083-0950, \emph{a}=7.30084 \AA, \emph{b}=7.53889 \AA, \emph{c}=7.6896 \AA, $\beta$=90.89$^\circ$}
+The two sodium tungsten oxide phases are the triclinic \ce{Na5W_{14}O_{44}} phase (ICDD PDF 04-012-4449, \emph{a}=7.2740 \AA, \emph{b}=7.2911 \AA, \emph{c}=18.5510 \AA, $\alpha$=96.37$^\circ$, $\beta$=90.89$^\circ$, $\gamma$=119.65$^\circ$) and the triclinic \ce{Na2W4O_{13}} phase (ICDD PDF 04-012-7108, \emph{a}=11.1630 \AA, \emph{b}=3.8940 \AA, \emph{c}=8.2550 \AA, $\alpha$=90.60$^\circ$, $\beta$=131.36$^\circ$, $\gamma$=79.70$^\circ$).
+The tungsten oxide is the monoclinic \ce{WO3} phase (ICDD PDF 01-083-0950, \emph{a}=7.30084 \AA, \emph{b}=7.53889 \AA, \emph{c}=7.6896 \AA, $\beta$=90.89$^\circ$).
 
@@
 XRD measurements revealed the overall structure of the specimen.
-To obtain detailed information on the crystallinity, composition, and growth direction of the nanostructures, TEM analyses with imaging, electron diffraction, and EDX were performed on more than 20 nanowires.
+To obtain detailed information on the crystallinity, composition, and growth direction of the nanostructures, TEM analyses with imaging, electron diffraction, and \gls{edx} were performed on more than 20 nanowires.
 The majority of the nanowires were identified as the \ce{Na5W_{14}O_{44}} phase (Fig.~\ref{fig:nawoxtem}a-c).
@@
 EDX measurement (Fig.~\ref{fig:nawoxtem}c) shows the nanowire consisted of W, Na, and O.
-No other elements were detected.\footnote{The Cu and C signals come from the supporting Cu grid with lacey carbon and the Cr signal from the tip of JEOL double tilt holder.} Small fraction of nanowires were found to be the monoclinic \ce{WO3} phase.
-(Fig.~\ref{fig:nawoxtem}d-f) The SAED shown in the inset of Fig.~\ref{fig:nawoxtem}e was recorded in [100] zone.
+No other elements were detected.\footnote{The Cu and C signals come from the supporting Cu grid with lacey carbon and the Cr signal from the tip of JEOL double tilt holder.} Small fraction of nanowires were found to be the monoclinic \ce{WO3} phase (Fig.~\ref{fig:nawoxtem}d-f).
+The SAED shown in the inset of Fig.~\ref{fig:nawoxtem}e was recorded in [100] zone.
 The growth direction of the \ce{WO3} nanowire was determined to be perpendicular to the (002) plane with a d-spacing of 0.38 nm.
@@
 Normalized to the highest W peak, the Na peak intensity in Fig.~\ref{fig:nawoxtem}i is higher than the one in Fig.~\ref{fig:nawoxtem}c.
-This result indicates a higher Na:W ratio for the \ce{Na2W4O_{13}} plate structure than that of \ce{Na5W_{14}O_{44}} nanowires, in consistent with the compositions of the two phases.
+This result indicates a higher Na:W ratio for the \ce{Na2W4O_{13}} plate structure than that of \ce{Na5W_{14}O_{44}} nanowires, in consistent with the compositions of these two phases.
 % tem
@@
 Major peaks at 107, 695, 765, 913, 943, and 965 \si{cm^{-1}} cannot be assigned to reference in literatures.
-According to the TEM results, the nanowires are mainly \ce{Na5W_{14}O_{44}}, therefore these peaks should belong to the \ce{Na5W_{14}O_{44}} phase.
+According to XRD and TEM analyses, the nanowires are mainly \ce{Na5W_{14}O_{44}}; therefore these peaks should belong to the \ce{Na5W_{14}O_{44}} phase.
 So far no Raman spectrum has been reported for this phase, hence this is probably the first observed Raman pattern for \ce{Na5W_{14}O_{44}}.
-
+% nawox raman
 \begin{figure}[htb]
@@
 \end{figure}
-
-Based on the correlation of Raman spectra and crystallographic data of a variety of tungsten bronze, an empirical formula to relate the Raman peaks and \ce{W-O} bonding lengthshas been found as 
+Based on the correlation of Raman spectra and crystallographic data of a variety of tungsten bronze, an empirical formula to relate the Raman peaks and \ce{W-O} bonding lengths has been found as
 \begin{equation}\label{eq:wobond}
@@
 Multi-peak Lorentzian fitting is preformed to precisely determine the central maximum.
-Good fitting is obtained, as shown in Fig.~\ref{fig:naworamfit}.
-The calculated \ce{W-O} bond distances using Eq.~\ref{eq:wobond} are listed in Table~\ref{tab:nawobond}.
-The predicted \ce{W-O} bond lengths comply very well with the crystallographic value of \ce{Na5W_{14}O_{44}} phase.\cite{Triantafyllou1999a} The 107 \si{cm^{-1}} peak probably is caused by \ce{Na-O} bond.
+Good fitting is obtained as shown in Fig.~\ref{fig:naworamfit}.
+The calculated \ce{W-O} bond distances using Eq.~\ref{eq:wobond} are then listed in Table~\ref{tab:nawobond}.
+The predicted \ce{W-O} bond lengths agree very well with the crystallographic value of \ce{Na5W_{14}O_{44}} phase.\cite{Triantafyllou1999a} The 107 \si{cm^{-1}} peak probably is caused by \ce{Na-O} bond.
 % Na5 raman fitting
@@
 \toprule
-peak center (\si{cm^{-1}}) & length (\AA) & peak center (\si{cm^{-1}}) & length (\AA) \\
+Fitted center (\si{cm^{-1}}) & length (\AA) & Fitted center (\si{cm^{-1}}) & length (\AA) \\
 \midrule
@@
 Heated at elevated temperatures, the W precursor, quartz tube, and quartz boat were three possible sources for Na.
-The sodium concentration in 3N source was 20ppm as provided by vendor.\footnote{Due to the non-uniform distribution of foreign elements, detection of sodium by EDX is possible although the concentration is below the limit of typical EDX capacity.} The Na concentrations in quartz tube and quartz boat (GE 214 quartz, Wilmad Labglass) were 1 ppm and 0.7 ppm,  respectively.
+The sodium concentration in 3N source was 20 ppm as provided by vendor.\footnote{Due to the non-uniform distribution of foreign elements, detection of sodium by EDX is possible although the concentration is below the limit of typical EDX capacity.} The Na concentrations in quartz tube and quartz boat (GE 214 quartz, Wilmad Labglass) were 1 ppm and 0.7 ppm, respectively.
 To confirm the major source of Na content coming from 3N powder, control experiments were employed by using W source with higher purities (4N5 or 5N).
@@
 These results verified the Na content was mainly from the 3N W powders.
-In the experiments, the W source was first slowly oxidized at 1000 \si{\degreeCelsius} with 1 sccm \ce{O2} and the oxidized source was then evaporated producing \ce{WO3} and other substoichiometric tungsten oxide vapors.
-The tungsten oxide vapors produced this way were limited by the slow oxidation, as indicated by (i) only small amount of the tungsten source was consumed during the growth and (ii) only the top layer of the tungsten source was oxidized showing a dark blue color after growth.
-Due to its low concentration, the exact composition of the Na content in the tungsten source is not clear.
+In the OT growth experiments, the W source was first slowly oxidized at 1000 \si{\degreeCelsius} with 1 sccm \ce{O2} and the oxidized source was then evaporated producing \ce{WO3} and other substoichiometric tungsten oxide vapors.
+The tungsten oxide vapors produced this way were limited by the slow oxidation, as indicated by
+\begin{enumerate*}[label=\itshape\alph*\upshape)]
+\item only small amount of the tungsten source was consumed during the growth; and
+\item only the top layer of the tungsten source was oxidized showing a dark blue color after growth.
+\end{enumerate*} Due to its low concentration, the exact composition of the Na content in the tungsten source is difficult to probe.
 However, the evaporation rate of the Na content is expected to be high when heated at 1000 \si{\degreeCelsius}.
@@
 Detailed morphological changes are depicted in Fig.~\ref{fig:nawoxsemall}.
-
 \begin{figure}[htb]
@@
 \end{figure}
-
 For the first growth (Fig.~\ref{fig:nawoxsemall}a-c) in a new clean reaction chamber, there were only a little nanowires scattered in Zone I (Fig.~\ref{fig:nawoxsemall}a), ultra-long nanowires were mostly found in Zone II with higher density and coverage (Fig.~\ref{fig:nawoxsemall}b), and in Zone III the coverage, density, and length of nanowires gradually reduced as the growth location moved downstream (Fig.~\ref{fig:nawoxsemall}c).
@@
 
-The \ce{Na5W14O44} phase was further confirmed by a XRD scanning from 4 to 10 degree in $2\theta/\Omega$.
+The \ce{Na5W14O44} phase was further confirmed by a XRD scanning from 4 to 10 degree in $2\theta/\Omega$ configuration.
 As shown in Fig.~\ref{fig:naxrdlow}, two peaks at 4.84$^{\circ}$ and 9.65$^{\circ}$ were well resolved, corresponding a lattice spacing of 18.25 and 9.16 \AA, respectively.
-This compares favorably with both HRTEM analysis (Fig.~\ref{fig:nawoxtem}e) and ICDD database results.
+This compares favorably with both HRTEM analysis (Fig.~\ref{fig:nawoxtem}e) and ICDD PDF 04-012-4449 database reference.
 
@@
 
-\subsection{Tungsten Oxides by }\label{sec:sgfg}
+\subsection{Tungsten Oxides: Seeded Growth }\label{sec:sgfg}
 
-As mentioned in Section.~\ref{sec:nawox}, growth using higher purity tungsten powders primarily produce dense layer deposition, and growth using 3N powder is plagued with the impurity effect.
+As mentioned in Sec.~\ref{sec:nawox}, growth using higher purity tungsten powders primarily produce dense layer deposition, and growth using 3N powder is plagued with the impurity effect.
 New growth method is required to obtain \ce{WO3} NWs.
@@
 
-\section{summary}
+\section{Summary}
 

### 2014-09-24 ch-wox/part1.tex
inital review revised 1

@@
 Then the growth methods in this study are presented, followed by corresponding characterization and discussion.
-This chanpter is concluded with a brief summary.
+This chapter is concluded with a brief summary.
 
@@
 On basis of this property, \gls{ecd} of tremendous energy saving potential is conceptualized and some products have already been commercialized (i.e.
-smart window\footnote{"We did a case study in five cities, and the average savings in commercial buildings are about 25 percent of the heating, ventilation, and air-conditioning energy use annually," says CEO of View, Inc.}).
+smart window\footnote{"We did a case study in five cities, and the average savings in commercial buildings are about 25 percent of the heating, ventilation, and air-conditioning energy use annually," says CEO of View, Inc.}), although the materials used is not clear.
 
@@
 Among all the developed models, polaronic absorption is the most widely accepted mechanism for coloration.
-In polaron model,\footnote{When a free electron travels through a polar solid, it creates a local lattice displacement (longitudinal optical phonon clouds) due to the coulombic interaction with neighboring ions.
+The concept of polaron was first proposed by Landau in 1933.
+In ionic or highly polar crystals, such as II-VI semiconductors, alkali halides and transition metal oxides, the Coulomb interaction between a conduction electron and the lattice ions results in a strong electron-phonon coupling.
+A new quasi-particle, virtual phonon, can be defined corresponding to the effect of electron pulling nearby positive ions towards it and pushing nearby negative ions away.
+The electron and its virtual phonons, taken together, can be treated as a new composite particle, called an electron polaron; the hole polaron is defined analogously.\cite{Devreese1996} In polaron model,\footnote{When a free electron travels through a polar solid, it creates a local lattice displacement (longitudinal optical phonon clouds) due to the coulombic interaction with neighboring ions.
 This local distortion and the electron together is equivalent to a new elementary exciton of the crystal, and is named as polaron} the intercalation of \ce{M^+} (M = H, \ce{Li}, or Na) ions into \ce{WO3} films is accompanied with the formation of small polarons ($r_p$ comparable to unit cell size) and formal reduction of some \ce{W^{6+}} sites to \ce{W^{5+}}, as depicted in Eq.~\ref{eq:ec}.
-During the intercalation process, the \ce{M^+} ions enter into these vacant sites.\cite{Hepel2008} Coloration occurs when the polaron band .
+During the intercalation process, the \ce{M^+} ions enter into these vacant sites.\cite{Hepel2008} Coloration occurs when electron transition occurs from the hole polaron band to the electron polaron band.
 
 \begin{align}\label{eq:ec}
-x\ce{M+} + x\ce{e-} +  \ce{$\alpha \hyphen$WO$_{3-y}$}-> \ce{$\alpha \hyphen$M$_x$WO$_{3-y}$},
+x\ce{M+} + x\ce{e-} +  \ce{$\alpha \hyphen$WO$_{3-y}$} \rightarrow \ce{$\alpha \hyphen$M$_x$WO$_{3-y}$},
 \end{align}
-
 And the polaron binding energy ($E_p$) is given by
@@
 \end{align}
-
 where $\epsilon_\infty$ and $\epsilon_{st}$ are optical and static dielectric constants respectively, and polaron radius $r_p$, which specifies how far the lattice distortion extends, is related to polaron density $N_p$ by $r_p = \frac{1}{2}\sqrt[3]{\pi/6N_p}$.
 However, the polaron model has difficulty in estimating $r_p$.
-The asymmetric optical absorption spectrum are often characteristic of large polarons, and dielectric constants ($\epsilon_\infty = 6.52,\epsilon_{st} > 50$,\cite{Deb2008}) suggests the formation of bipolaron.
+The asymmetric optical absorption spectrum are often characteristic of large polarons, and dielectric constants ($\epsilon_\infty = 6.52,\epsilon_{st} > 50$,\cite{Deb2008}) suggests the formation of bipolaron in \ce{WO3}.
 Moreover, polaron model does not take oxygen vacancy into account, which plays a vital role in the nonstoichiometric tungsten oxides.
@@
 The positively charged vacancy exerts coulombic repulsion to the nearest W-ions, which results in a displacement of the neighboring W-ions and an upward shift of the defect level into the bandgap, thereby creating a color center.
-The optical transition from $V_O^+$ to $V_O^{2+}$ (a state within the conduction band)
-contributes to coloration.\cite{Deb2008}
+The optical transition from $V_O^+$ to $V_O^{2+}$ (a state within the conduction band) contributes to coloration.\cite{Deb2008}
 
@@
 Coloration mechanism is represented by Eq.~\ref{eq:cl_bl1} and \ref{eq:cl_bl2}, which described the polaron hopping from one site to another.\cite{Chatten2005}
-
 \begin{align}
@@
 \end{align}
-
 Similar scenarios occurs in the gasochromic effect.
@@
 But there is a disagreement on the final states.
-Double injection supports the formation of tungsten bronze \ce{H_xWO3} while color center insists on the inward diffusion of oxygen vacancy and outward diffusion of water molecules.
+Double injection supports the formation of tungsten bronze \ce{H_xWO3} while color center model insists on the inward diffusion of oxygen vacancy and outward diffusion of water molecules.
 Both have been substantiated experimentally.
@@
 
-Photocatalytic activity occurs when a semiconductor in aqueous solution is illuminated by photons of energy larger than the band gap, then electron-hole pairs generate free radicals, (i.e.
-\ce{OH.}) which enable further reactions.
-For water splitting using solar energy, the band gap should be within $2.0 \sim 3.0 $ eV, and CB edge should be more negative than reduction potential of \ce{H^+/H2}, whereas the VB top should be more positive than the oxidation potential of \ce{H2O}/\ce{O2}.\cite{Wang2012} The valence band holes (\ce{h^+}) oxidize water to oxygen and conduction band electrons propel hydrogen generation, as depicted in Eq.~\ref{eq:hervb} and \ref{eq:hercb}.
-
+Photocatalytic activity occurs when a semiconductor in aqueous solution is illuminated by photons of energy larger than the bandgap, then electron-hole pairs generate free radicals, i.e., \ce{OH.}, which enable further reactions.
+For water splitting using solar energy, the band gap should be within $2.0 \sim 3.0 $ eV, and CB edge should be more negative than reduction potential of \ce{H^+/H2}, whereas the VB top should be more positive than the oxidation potential of \ce{H2O}/\ce{O2}.\cite{Wang2012} The valence band holes (\ce{h^+}) oxidize water to oxygen and conduction band electrons propel hydrogen generation, as depicted in Eq.~\ref{eq:h2o}.
+\begin{subequations}\label{eq:h2o}
 \begin{align}
@@
 \end{align}
-
-As shown in Fig.~\ref{fig:woxnhe}, \ce{WO3} has \gls{cb} edge positioned slightly more positive than reduction potential of \ce{H^+/H2}(versus \gls{nhe}), and \gls{vb} edge much more positive than the oxidation potential of \ce{H2O/O2}.
+\end{subequations}
+As shown in Fig.~\ref{fig:woxnhe}, \ce{WO3} has \gls{cb} edge positioned slightly more positive than reduction potential of \ce{H^+/H2}(versus \gls{nhe}), and \gls{vb} edge much more positive than the oxidation potential of \ce{H2O}/\ce{O2}.
 So the photo-cleavage of water cannot be accomplished by \ce{WO3} alone.
 Nevertheless, a tandem cell approach by \ce{WO3} film and dye-sensitized \ce{TiO2} has been demonstrated with an efficiency of 4.5\%.\cite{Michael1999} It is worth noting that green plants also have two photosynthetic systems connected in series, one for oxidation of water into oxygen and the other for fixation of carbon dioxide.
-
 % wo3 vs NHE
@@
 \includegraphics[width=0.7\textwidth]{woxnhe.jpg}
-\caption[Bands positions of \ce{WO3} versus NHE]{Bands positions of \ce{WO3} in contact with aqueous electolyte at pH 1. adapted from Ref\cite{Gratzel2001}}
+\caption[Bands positions of \ce{WO3} versus NHE]{Bands positions of \ce{WO3} in contact with aqueous electolyte at pH 1, adapted from Ref.\cite{Gratzel2001}}
 \label{fig:woxnhe}
 \end{figure}
-
 Moreover, favorable oxygen evolution of \ce{WO3} brings good performance in degradation of organic compounds\cite{Hepel2001,Luo2001,Watcharenwong2008}.
@@
 The temperature-dependent phase transition and corresponding lattice constants in bulk form is summarized in Table.~\ref{tab:wo3phase}.\cite{Zheng2011} And a firm assignation of space group to monoclinic phases are still in debate.\cite{Chatten2005} It is noticed that the lattice parameters obtained via \emph{ab initio} calculation closely match the experimental values.\cite{Migas2010a} The phase transition scenarios in nanostructured \ce{WO3} are supposed to be more sophisticated.
-Within Gibbs-Thomson frame work, one can generally expect lower transition temperature than their bulk counterparts due to enhanced surface energy.
+Within Gibbs-Thomson framework, one can generally expect lower transition temperature than their bulk counterparts due to enhanced surface energy.
 Temperature-dependent Raman spectroscopy provided support for this deduction.\cite{Boulova2002}
@@
 
-% band gap table
-\begin{table}[htb]
-\centering
-\caption{Tungsten oxides band gap }\label{tab:wo3eg}
-\begin{tabular}{lccr}
-\toprule
-Phase & Experimental (eV) & Theory (eV) &  \\
-\midrule
-amorphous \ce{WO3} & 3.2  & NA &    \\
-monoclinic bulk \ce{WO3} &  2.6   & 1.73\cite{Migas2010a}  &    \\
-tetragonal bulk \ce{WO3} &     & 0.66 \cite{Migas2010a}&    \\
-\bottomrule
-\end{tabular}
-\end{table}
-
 \subsection{Synthesis strategies}\label{sec:woxgrowth}
 
-As the chemical formula suggested, the most straightforward way is heating metallic tungsten in various forms (i.e.
-powders,\cite{Zhou2005a,Cao2009,Hsieh2010} foils and wires).
+As the chemical formula \ce{WO3} suggested, the most straightforward way is heating metallic tungsten in various forms,\cite{Zhou2005a,Cao2009,Hsieh2010} i.e., powders, foils and wires.
 Actually \ce{WO_x} \glspl{nw}\footnote{$x$ is between 2 and 3} were observed when directly heating W wires.\cite{Gu2002a} Due to the extreme high melting point of W, it requires very high temperature (say, above 1100 \si{\degreeCelsius}) to produce large amount of growth species.
-Therefore scalable growth seems difficult.
+Therefore scalable growth seems difficult at low temperature range unless other activation mechanisms are used.
 The DC current heating proved to be a route with potential large yield.
-Tungsten wire or filament is connected to a voltage source, and substrate is positioned in proximity to the heated W wire.\cite{Lingfei2006,Thangala2007,Chang2007}
+Tungsten wire or filament is connected to a current source, and substrate is positioned in proximity to the heated W wire.\cite{Lingfei2006,Thangala2007,Chang2007} Tungsten oxides powder can also been used as precursor to prepare \ce{WO_{x}} \glspl{nw}.\cite{Huang2008a,Wang2009} Hydrogen-containing agents (i.e.
+water, \ce{H2}, or methane\cite{Klinke2005}) were often involved into the reaction.\cite{Baek2007,Karuppanan2007} The potential benefit is \ce{WO3} has a much lower melting point ($\approx 1470$ \si{\degreeCelsius}) than that of metallic tungsten.
 
-Tungsten oxides powder can also been used as precursor to prepare \ce{WO_{x}} \glspl{nw}.\cite{Huang2008a,Wang2009} Hydrogen-containing agents (i.e.
-water, \ce{H2}, or methane\cite{Klinke2005}) were often involved into the reaction.\cite{Baek2007,Karuppanan2007} The potential benefit is \ce{WO3} has a much lower melting point ($\approx 1470$ \si{\degreeCelsius}) than that of W.
-
-Direct oxidation and \ce{WO3} conversion could be grouped as addition approach.
-In contrast, decomposition method is also feasible.
+In contrast, organometallic decomposition is another feasible method.
 \citeauthor{Pol2005} obtained \ce{W18O49} nanorods by thermal dissociation of \ce{WO(OMe)4} at 700 \si{\degreeCelsius}, and \ce{WO3} by further annealing at 500 \si{\degreeCelsius} in air atmosphere.\cite{Pol2005}
@@
 Finally the product is separated from the solution and dried, layered \ce{WO3.nH2O} flakes are usual products.
+A brief summary representative synthesis methods is shown in Table~\ref{tab:wox}.
 
@@
 \toprule
-composition  &  methods & highlights &  reference  \\
+Phase  &  Methods & Highlights &  Reference  \\
 \midrule
@@
 \addlinespace[0.5em]
-& W powder heating Ar/\ce{O2} flow  & triclinic phase, CL at 370,415nm, UV-Vis, 3eV & \cite{Hsieh2010} \\
+& W powder heating, Ar/\ce{O2} flow  & triclinic phase, CL at 370,415nm, UV-Vis, 3eV & \cite{Hsieh2010} \\
 \cmidrule(l){2-4}
@@
 \midrule
-\ce{W18O49} & \ce{KOH} etching of W tips followed by heating in Ar flow  & oxygen from leakage, VS process& \textcite{Gu2002a} \\
+\ce{W18O49} & \ce{KOH} etching of W tips followed by heating in Ar flow  & oxygen from leakage, VS process& \cite{Gu2002a} \\
 \addlinespace[0.5em]
-& \ce{NW(CO)6}, \ce{Me3NO.2H2O} and oleylamine by hydrothermal  &  RT PL at 350nm and 440nm & \cite{Lee2003}  \\
+& \ce{W(CO)6}, \ce{Me3NO.2H2O} and oleylamine by hydrothermal  &  RT PL at 350nm and 440nm & \cite{Lee2003}  \\
 \bottomrule

### 2014-09-24 misc/draft.tex
inital review revised 1

@@
 \subsection{used}
+
+\citeauthor{Chatten2005} also studied the oxygen vacancy in different phases of \ce{WO3}.\cite{Chatten2005}
 
@@
 
+% band gap table
+\begin{table}[htb]
+\centering
+\caption{Tungsten oxides band gap }\label{tab:wo3eg}
+\begin{tabular}{lccr}
+\toprule
+Phase & Experimental (eV) & Theory (eV) &  \\
+\midrule
+amorphous \ce{WO3} & 3.2  & NA &    \\
+monoclinic bulk \ce{WO3} &  2.6   & 1.73\cite{Migas2010a}  &    \\
+tetragonal bulk \ce{WO3} &     & 0.66 \cite{Migas2010a}&    \\
+\bottomrule
+\end{tabular}
+\end{table}
+
 W plasma oxidation.\cite{Romanyuk2005} 200nm W coating on Si (100) sub, temperature at RT, 390, and 490 C, oxygen pressure 0.5 Pa, oxidation time for 10 to 3600 s.
@@
 \subsection{to be used}
+
+The refractive index is between $ 2.2\sim 2.4$ along $a$ axis, and $ 2.5\sim 2.8$ along $c$ axis.
+Comparison to the low frequency dielectric constant ($18.0\pm1$) implies a primarily ionic bonding in \ce{MoO3}.\cite{He2003}
 

### 2014-09-26 ch-moox/moox.tex
wox and moox proofreading

@@
 
-The author studied the effect of temperature, oxygen partial pressure and growth time towards \ce{MoO3} deposition on glass substrates.
-Each factor is divided into two levels, with T at 700 and 800 \si{\degreeCelsius}, \ce{O2} at 1 and 10 sccm, and growth time of 15 and 60 min.
-And the morphological variation is summarized in Table~\ref{tab:mo3glass}.
+This thesis studied the effect of temperature, oxygen partial pressure and growth time towards \ce{MoO3} deposition on glass substrates.
+Each factor was divided into two levels, with $T$ at 700 and 800 \si{\degreeCelsius}, \ce{O2} flow at 1 and 10 sccm, and growth time of 15 and 60 min.
+And the morphological variations revealed by SEM imaging were summarized in Table~\ref{tab:mo3glass}.
 % glass growth matrix
@@
 
-The 800-1-15 combination produces the most interesting \ce{MoO3} morphology, as illustrated in Fig.
-
+The 800-1-15 combination produced dense \ce{MoO3} nanoplate with length about 10 $\mu$m, width $300\sim500$ nm and thickness less than 100 nm, as illustrated in Fig.~\ref{fig:ch4glass}. 
 %
+\begin{figure}[htb]
+\centering
+\includegraphics[width=0.7\textwidth]{moo3_glass}
+\caption[\ce{MoO3} nanoplates on glass]{Optimized \ce{MoO3} nanoplates growth on glass.}
+\label{fig:ch4glass}
+\end{figure}
+These \ce{MoO3} nanoplates are of high crystalline quality, and could potentially show enhanced photoelectrochemical and electrochromic activities.
 
@@
 
-The exfoliation solution is 30\% isopropanol (IPA) in DI water, which has been proved to work well on other layered compounds.\cite{Halim2013} After 20 minutes sonication, the dispersion is milky.
-The transmission spectra of this dispersion immediately upon sonication and after 40 h for gravity sedimentation was measured, as illustrated in Fig.~\ref{fig:moabs}.
-The t0 line mainly arises from the scattering of flakes in the dispersion.
+The exfoliation solution is 30\% isopropanol (IPA) in DI water, which has been proved to work well on other layered compounds.\cite{Halim2013} After 20 min sonication, the dispersion appears milky.
+The transmission spectra of this dispersion immediately upon sonication and after 40 h of gravity sedimentation were measured and compared in Fig.~\ref{fig:moabs}.
+The t0 line mainly arise from the scattering of flakes in the dispersion.
 There are two scattering mechanisms: Rayleigh scattering and Tyndall scattering.
@@
 To fully evaluate the true absorbance of the sample itself, one needs to decouple the scattering part from apparent absorbance.
-Generally, one part of spectrum is selected and assumed it is only caused by scattering.
-Then a empirical dependence shown in Eq.~\ref{eq:sca2} is used as polynomial fitting model.
+Generally, one part of spectrum away from absorption edge is selected and assumed it is only caused by scattering.
+Then an empirical dependence shown in Eq.~\ref{eq:sca2} is used in the polynomial fitting model.
 

### 2014-09-26 ch-wox/ch-wox.tex
wox and moox proofreading

@@
 \end{figure}
-Tungsten metals crystallize in body center cubic (BCC) phase.
+Tungsten metal crystallizes in body center cubic (BCC) phase.
 Overall, the facets were still discernible.
@@
 
-% 061212 sample
+%061212 sample
 \begin{figure}[htb]
@@
 \end{figure}
+
+The optical transmission and reflection properties of the as-grown \ce{Na5W14O44} NWs were evaluated using UV-Vis spectroscopy, as shown in Fig.~\ref{fig:ch3naxuvvis}.
+The sample was prepared on a quartz substrate, which is transparent from 300 to 1300 nm.
+SEM images (not shown) found dense NWs array growth similar to those on \ce{SiO2}-Si substrates, indicating the residue effect is not sensitive to the substrate.
+%051412 sample
+\begin{figure}[htb]
+\centering
+\subfloat[]{\label{fig:nauv}\includegraphics[width=0.45\textwidth]{uvvis_naxwo3}}\hspace{0.04\textwidth}
+\subfloat[]{\label{fig:nadrs}\includegraphics[width=0.45\textwidth]{uvvis_naxwo2}}
+\caption[UV-Vis and DRS of \ce{Na5W14O44} NWs on quartz]{(a) Optical transmission and (b) diffuse reflection spectra of \ce{Na5W14O44} NWs on quartz.}
+\label{fig:ch3naxuvvis}
+\end{figure}
+The transmission (Fig.~\ref{fig:nauv}) was about 70\% above 400nm, and began to drop significantly for shorter wavelength.
+This variation was also identified in the diffuse reflection spectrum (DRS) in Fig.~\ref{fig:nadrs}, where the reflection reached to a maximum of 16\% at 390 nm.
+One difference is the DRS increased from 1300 nm to 400nm, presumably due to the inverse scattering intensity with NW dimension of 300 nm.
+The calculated absorption was shown in Fig.~\ref{fig:nauv}, suggesting a bandgap edge at about 380 nm.
+This is consistent with the observed white sample color; however, the \ce{Na5W14O44} should be metallic in theory.
+More investigation is needed to vigorously determined the electronic transport properties of \ce{Na5W14O44} NW.
 

### 2014-09-27 misc/draft.tex
list of abbreviation temperatory solution found

@@
 The ratio between absorption and scattering, not the absolute value of each quality, determines the reflection features.
+\section{iffalse}
+
+\iffalse
+An eucentric specimen stage is used, thus observation area remain fixed when tilting the specimen.
+The pressure in SEM chamber is on the order of $10^{-3} \sim 10^{-4}$ Pa, which is usually maintained by a diffusion pump, or turbo molecular pump when oil-free operation is needed.
+For a field emission electron source, a sputter ion pump becomes necessary due to the high vacuum requirement.
+
+The SEM instrument used in this study is JEOL JSM-6480 and EDX attachment from Oxford Instrument INCA. Typical observation conditions are listed as following:
+
+\begin{enumerate}
+\item SEM
+\begin{itemize}
+
+\item Acceleration voltage: 10 kV
+\item Working distance: 10 mm
+\item Scanning time: 80 s
+\end{itemize}
+\item EDX
+\begin{itemize}
+
+\item Acceleration voltage: 20 kV
+\item Working distance: 10 mm
+\item Dead time: $20\sim30$\%
+\end{itemize}
+\end{enumerate}
+
+\begin{quotation}
+Since the intensity of characteristic X-rays is proportional to the concentration of the corresponding element, quantitative analysis
+can be performed. In actual experiment, a standard specimen containing elements with known concentrations is used. The
+concentration of a certain element in an unknown specimen can be obtained by comparing the X-ray intensities of the certain element
+between the standard specimen and unknown specimen. However, X-rays generated in the specimen may be absorbed in
+this specimen or excite the X-rays from other elements before they are emitted in vacuum. Thus, quantitative correction is needed.
+In the present EDS and WDS, correction calculation is easily made; however, a prerequisite is required for this correction. That is,
+elemental distribution in an X-ray generation area is uniform, the specimen surface is flat, and the electron probe enters perpendicular to the specimen.
+Actually, many specimens observed with the SEM do not satisfy this prerequisite; therefore, it should be noted that a quantitative analysis result might have appreciable errors.
+\end{quotation}
+
+\fi
+
+\iffalse
+Similar to the photon-lattice interaction in XRD, the process of TEM could be understood as electron scattering events by the same crystal plane.
+
+\begin{itemize}
+\item X-ray: characteristic X-ray for elemental analysis, Bremsstrahlung X-ray also useful for biological sample; $K_\alpha$ line from L to K transition, and $K_\beta$ from M to K transition, $L_\alpha$ line from M to L transition, Inelastic cross section, Bethe expression, X-ray energies are not identical to the ionized energy because after first emission, the atom is not in ground state until a free electron fill the last hole in the outermost shell.
+A cascade of transitions, Coster-Kroning transition, X-ray line shift slightly due to the chemical bonding to another atom.
+XEDS is not good at analyzing light elements due to the low fluorescence yield, which is strongly dependent on Z.
+Bremsstrahlung X-ray emission is strongly forward,
+\item SE: ejected from the conduction or valence bands, weak so only escaping if near the surface, STEM, complex cross section mechanism, 
+\item Auger: Auger electron has specific energy similar to X-Ray, but is much more strongly absorbed than X-ray. Stated another way, Auger electron is hard to escape, so it is surface sensitive. 
+\item CL: spatial resolution around 100 nm, 
+\item collective interaction, plasmon and phonon, plasmon excitation cross section in Lorenztian form $\frac{d\sigma_\theta}{d\Omega} = \frac{1}{2\pi a_0} \frac{\theta_E}{\theta^2 + \theta_E^2}$, where $\theta_E = E_p/2E_0$,
+\end{itemize}
+
+The diameter of E-beam in TEM is less than 5 nm in general, and can be $< 0.1$ nm at best.
+
+correction of spherical aberration ($C_s$) and chromatic aberration ($C_c$), $C_s$ is done by , $C_c$ by energy-filtering, which is more useful for thicker specimens.
+$C_s$ correction permits the generation of smaller electron probes with higher currents, which significantly improves both analytical spatial resolution and sensitivity.
+$C_c$ correction offer the possibility to form band-gap imaging and chemical-bond imaging.
+The limiting apertures increase the depth of field for specimen, and the depth of focus for the image.\cite{Williams2009}
+
+including controlling the interactions of electron with magnetic fields and with specimen.
+
+XRD: X-ray scattered by electrons, electron scattered by both electrons and nuclei.
+Fresnel vs.
+Fraunhofer, high-angle scattered electron are incoherent; therefore, it can be used to form high-resolution Z-contrast image of a crystalline specimen, regardless of the orientation.
+Auger electron spectroscopy.
+EELS and XEDS constitute analytical electron microscopy (AEM).
+close approach the single-atom level.
+well suited to, energy-loss electrons cause Kikuchi lines to arise in DPs.
+Ionized atom enters excited state,
+
+penetrate electron cloud, spherical wavelets, the cross section for electrons elastically scattered into angles larger than $\theta$ is $\sigma_{nucleus}= 1.62\times10^{-24} (\frac{Z}{E_0})^2\cot^2\frac{\theta}{2}$; scattering factor $f(\theta)$ for low angle ($< \sim 3^{\circ}$).
+
+Point-group and space-group determination from convergent-beam patterns.
+crystal symmetry analysis.
+e-beam wavelength in metal.
+The high-resolution comes at the cost of poor sampling.
+Human eyes and brain understand reflected light image, and not well-trained for the transmission images.
+
+One must be just as aware of the instrument's limitations as one is of its advantages.
+TEM is initially developed to overcome the image resolution imposed by light microscopes.
+constitute, draw analogies, resolving power, E-beam is one type of ionizing radiation, which is capable of removing the tightly bound, inner-shell electrons from attractive field of nucleus (visible light, is non-ionizing radiation to some extent).
+a wide range of secondary signal can be produced, the spectra exhibits characteristic peaks, which identify the elements present in the specimen.
+In analog to laser as a highly coherent source, .
+
+Both wave and particle approach, non-scattering is invisible, backscattered in large angle and secondary electrons are of interest in SEM, where they provide Z contrast and surface-sensitive, topographical images.
+forward scattered is of interest in TEM.
+scattering events as billiard balls colliding, coherently scattered are those that remain in step, and incoherently scattered electrons have random phase relationship.
+Assuming single scattering events in TEM,
+
+The cost of TEM adds up to \$10 per eV. seize the public's imaginations.
+
+The cross section of tungsten, moly is
+
+Focused ion beam (FIB) to prepare thin foils of individual gates from one of the many millions of such on a wafer.
+The events of electron passing through one crystal plane, The coherent length of e-beam, collection angle,
+
+\fi
+
+\iffalse
+incoherent illumination $s = \frac{1.22 \lambda_{vac}}{2n\sin i}$, 
+coherent illumination in microscope $s = \frac{\lambda_{vac}}{n\sin i}$,, 
+phase contrast: transforming phase change in object plane into amplitude variation in image plane. 
+much better than needed, human eye resolving power 0.3 mrad,
+
+The illumination can be considered as incoherent (adding intensity) if the object is self-luminous, or if illminated from all direction.
+
+The opposite occurs in TEM probably, where the specimen is irradiated with complete transverse coherence across its area. back 
+focal plane displays the Fourier transform of complex amplitude in object plane.
+The optical system is a spatial low-pass filter: it builds up images from only the low Fourier components present at the object, having higher values cutoff.
+
+The information about an object is on display in the objective lens's back focal plane in a Fourier-transform form.
+dark field, removing zero order; Schlieren technique, removing half of diffraction from one side of back focal plane; applications: apodizing in telescope, satellite transmitting aerial structure,
+
+with the aid of Fig. 
+conjugate plane,
+
+electron lens can be made of electrostatic field, and magnetic field, and the B field can be generated from ferromagnetic materials (soft iron, 2 T) or superconducting (100 T).
+
+$C_s$ has dimensions of length, and is approximately equal to the focal length of objective lens (1-3 mm in TEM).
+
+$r_{min} \approx 0.91(C_s \lambda^3)^{1/4}$ is about 0.3 nm typically; with $C_s$ correction, $r_{min}$ can be further reduced to 0.07 nm.
+And human eye can resolve a distance of 0.2 mm, therefore the maximum useful magnification is about $0.2 \times 10^{-3}/0.3 \times 10^{-9} \sim 670 K$.
+
+And after interacting with specimen, the energy spread of transmitted E-beam becomes about 20eV, which will limit the resolution more than does the spherical aberration.
+
+\textbf{coherence of E-beam}
+
+faint points, large disk, the feature of interest is what make the materials imperfect,
+
+20 keV E-beam in TV.
+
+In XRD, both diffraction peak position and intensity are used; whereas in TEM, most time only the positions of spots are of concern.
+
+physical process of diffraction where the atomic planes appear to behave as mirrors for incident E-beam;
+
+\fi
+
+\iffalse
+A Raman pattern database can be found at \url{http://wwwobs.univ-bpclermont.fr/sfmc/ramandb2/index.html}. 
+In analytical practice, frequency is expressed in reciprocal wavelength (as cm−1), called wavenumbers;
+\fi
+
+\iffalse
+
+hemispherical reflectance, 
+diffusive reflectance is a mathematical artifice without direct physical meaning.
+
+p332- 338
+
+the reflecting power associated with a specular-type process is often termed reflectivity, while reflectance is the analogous term for diffusely reflected radiation.
+This two types of reflection are present simultaneously.
+
+Cauchy formula, empirical equation which has subsequently been placed on a firm theoretical basis.
+
+intensity for a complex quantities is obtained by multiplying the complex conjugate.
+
+For strongly absorbing materials, the reflected light is complementary to the color of light transmitted by it, such as gold transmission is green;
+
+For the weakly absorbing substances of rough surface, it will appear the same color by transmission or reflection.
+
+penetration depth is wavelength dependent $d = \frac{In2 \lambda}{2\pi \sqrt{\sin^2\theta_i - n^2}}$, longer wavelength penetrated further than did shorter wavelength. attenuated total reflectance,
+
+thin film, amorphous, mean free path of electron is diminished, and porous in structure. The maxwell-garnett theory provides a satisfactory explanation, where free electron density is reduced.
+
+diffuse reflection: $I = I_0 \exp(-\epsilon d)$, Lambert cosine law formulated. multiple scattering by individual particles. 
+$R_tot = \alpha R_sp + (1- \alpha) R_diff $,
+
+multiple scattering of diffuse radiation in a medium composed of closely packed particles.
+
+\[
+\log{f(r_\infty) = \log{k} - \log{s}}
+\]
+
+It is concluded that the KM function can be used to obtain the characteristic color curve of a given sample only in the limit of small total absorption.
+
+by mixing the sample with an abundance of the reflectance standard, the regular reflection is extensively eliminated.
+
+The color of an object depends on the spectral composition of the source.
+The color of many light sources can be specified in terms of the temperature to which a blackbody radiator must be heated in order to achieve a color match for the source, which is known as color temperature.
+
+integrating sphere: the intensity at any part of the sphere, due to the reflected light is a measure of the total flux from a particular source, independent of the spatial distribution or location of the source on the sphere.
+
+substitution method, comparison method,
+
+\fi
+
+\section{Data Processing}
+
+The SEM images are cropped using Adobe Photoshop for highlighting the features and fitting into text width.
+To obtain the dimension of specimen, scale bar was measured and compared to the size of interest using ImageJ\cite{Schneider2012} for SEM, TEM images and SAED pattern.
+It is worth noting that ImageJ could directly read the dm3 format generated in Gatan imaging software, which is more productive than the scale bar method.
+
+Various spectra, be it from XRD, EDX, Raman, or UV-Vis, were redraw using Origin Pro 8.0.
+The peak fitting was performed using \emph{Fityk}, a nonlinear curve fitting program specialized in data processing from powder diffraction, chromatography, photoluminescence and photoelectron spectroscopy, infrared and Raman spectroscopy, \emph{etc}.\cite{Wojdyr2010}
 
@@
 \subsection{not used}
-Both tungsten (W) and molybdenum (Mo) belong to Group VIB transition metal, with outer shell electrons configuration as $4d^55s^1$ and $5d^46s^2$, respectively.
+
+\iffalse
+Materials that human can make define the age they live in.
+From Stone Age to Bronze Age and Iron Age, people evolve as mastering more and more sophisticated techniques of manipulating metals, such as alloying and annealing.
+Obtaining extreme high purity of silicon brings us into Information Age.
+Future is difficult to predict.
+But nanotechnology is one direction that we can not ignore.
+According to \gls{nni}, \gls{nanotechnology}.
+This definition alludes that dimension comes before compositions.
+It is often related to the quantum confinement or surface area in nanomaterials, which we will later revisit with specific scenario.
+
+There are three states of matter under usual conditions: solid,liquid and gas.
+Solids materials could be further categorized into five groups: metals, ceramics, polymers, semiconductors, and composites.\cite{William2009} This classification is based on both composition and mechanical, electrical, and thermal properties as well as the associated functionality(i.e., \gls{ceramics} are typically hard yet brittle, insulating to electricity and resistant to heating).
+
+\fi
+
+\iffalse
+
+We have synthesized \gls{tmo} and \gls{tmdc} at nanoscale, measured their crystalline structures and optical properties and demonstrated some devices assembled using as-synthesized nanomaterials.
+We aim to illustrate that by nanoengineering these \gls{tmo} and \gls{tmdc}, enhanced performances over their bulk states could be expected and new properties will arise.
+In the remaining sections of this chapter, we will discuss some general perspectives of nanomaterials, the growth apparatus and characterization methods that apply to all experiments done in this work.
+Then chapter 2 will focus on growth of \ce{WO3} and its derivative.
+We employed thermal \gls{cvd} to synthesize \ce{WO3} \gls{nw}, and we investigated the role of impurity in tungsten metallic powders, during which we observed a new state of sodium tungsten oxides: \ce{Na5W14O44} nanowires.
+We also found a method to potentially obtain large yield of \ce{WO3} \gls{nw}.
+Chapter 3 will concentrate on \ce{MoO3}.
+We explored two different growth mechanism of \ce{MoO3}:\gls{vs} and \gls{vls}.
+We discovered that alkaline oxides can be used as catalyst to grow two distinct \ce{MoO3} morphologies: nanobelts and towers.
+We further demonstrated the application of as-synthesized \ce{MoO3} nanomaterials in electrochromic devices.
+In chapter 4 we discuss  We synthesized  and inspected the growth of \gls{fl} \ce{WS2}.
+Chapter 5 will conclude with an overall summary.
+
+\fi
+
 Therefore we refer their oxides and chalcogenides as \gls{tmo} and \gls{tmdc}.\footnote{Obviously transition metals include many other elements, all of which have partially filled $d$-electron shell.
@@
 
+\section{literature to read}
+
+The geometrical symmetry groups of WS2 NT.\cite{Milosevic2000} 
+The basis/lattice vectors $a_1$ and $a_2$ are defined in transition metal plane with equal length $a_0 \approx 3$ \AA.
+This monolayered sheet can be rolled up to form a tubular structure when the chiral/translation vector $c = n_1a_1 + n_2a_2$ becomes the circumference of the tube.
+The diameter of a nanotube is given by
+\begin{equation}
+d = \frac{\mid c \mid}{\pi} = \frac{a_0}{\pi}\sqrt{n_1^2 + n_1n_2 + n_2^2}
+\end{equation}
+Notice $a_1 \cdot a_2 = a_1a_2 \cos\pi/3$, where the cosine times 2 is unit. 
+In analog with carbon nanotube, chiral angle $\theta$ is given by
+\begin{equation}
+\theta = \tan^{-1}\frac{\sqrt{3}n_2}{2n_1 + n_2}
+\end{equation}
+
+Chiral angles from the interval $[0,pi/6]$ is sufficient for all possible tubes.
+Tubes $(n,0)$ with zero chiral angle are named zigzag, tubes $(n,n)$ with $\pi/6$ chiral angle are armchair, whereas all others are referred as chiral ones with $\theta \in (0,pi/6)$.
+
+hydrogen evolution catalysts. \cite{Merki2011}
+
+Raman substrate dependence \cite{Buscema2013}
+
+stability of TMS NTs \cite{Seifert2002}
+
+2H and 1T in \ce{MoS2} \cite{Eda2012}
+
+\ce{MoS2} FET statistical study. \cite{Liu2013i}
+
+water splitting review. \cite{B800489G}
+
+\ce{WS2} theory and experimental combined study. \cite{Klein2001}
+
+2D review on oxides \cite{Osada2012}
+
+Pb catalyzed \ce{MoS2} nanotube \cite{Brontvein2012}
+
+\ce{WS2} Raman.\cite{Zhao2013} \cite{Sekine1980}
+
+phonon dispersion $E_{2g}^1(M)$? \cite{Ataca2012}
+
+MoS2 optical properties.\cite{Search1979}
+
+FL heterostructure. \cite{Yu2013a}
+
+\cite{Kang2013} TMDC alloy DFT.
+
+thermoelectric TMDC \cite{Wickramaratne2014}
+
+\ce{CH4N2S} thiourea + \ce{WOx} to \ce{WS2} \cite{Leonard-Deepak2011}
+
+\ce{WS2} by \ce{WCl_n} and \ce{H2S}, raman (632nm) show bulk features\cite{Tenne2008}.
+
+direct gap of ML at corner of BZ, point K.
+
+\begin{align}
+\cee{WCl6 + S &\rightarrow WS2 + Cl2S2}\\
+\cee{MoCl5 + S &\rightarrow MoS2 + S2Cl2} \\
+\cee{S2Cl2 + NaOH &\rightarrow NaCl + S + Na2SO3 + H2O}
+\end{align}
+
+\section{literature read}
+
+CNT chirality by TEM \cite{Zhang1993} TEM chirality of \ce{MoS2} NTs
+
+first demonstration of \ce{WS2} NT n-type FET. \cite{Levi2013}
+the importance of contact, and avoiding moisture.
+
+The calculated carrier concentration is about $10^{19}cm^{-3}$, a highly doped semiconductor, possibibly arising from sulfur vacancy.
+
+\ce{WS2} NT transport \cite{Zhang2012c}
+less grain boundary more mobility,
+
+\citeauthor{Ramasubramaniam2011} investigated the band gap tuning in bilayer TMDC materials by applying external $E$ field.
+Similar research has been done for graphene and bilayer boron nitride.
+Semiconductor-metal transition was suggested for \ce{MoS2} and \ce{WS2}, with difference on the CBM and VBM evolution.
+In \ce{MoS2}, the valence-band-splitting cause the A and B excitons in optical absorption measurement.
+Calculation shows that CB and VB are translated toward the Fermi level with increasing E field.
+The external field localized charge along $c$ axis, but delocalized that within the plane normal towards $c$, thereby driving the semi-metal transition.
+It was mentioned that this transition is not anticipated in monolayer \ce{MoS2}.
+It was emphasized that precise band gaps might be different from the author’s results, yet the gap-tuning should be universal.\cite{Ramasubramaniam2011}
+
+\cite{Song2013} \ce{WO3} by ALD, and sulfurized in Ar and \ce{H2S} (10:1) at 1000 C.
+\ce{WS2} layer No and peak intensities ratio under 633nm excitation is correlated.
+It was found the 2LA/A1g is less than 1 for 1L.
+In supporting info 532 nm Raman spectra, the 2LA/A1g is presumably larger than 1 for 1L.
+\ce{WS2} NT on Si NWs is also demonstrated.
+
+\cite{Tenne2010} chemical modification of NTs.
+Functional ligand consists of an anchor group that attaches to the NTs surface and a tail which render them soluble in various solvents.
+PTAS functionalized BN nanotube lead to the formation of stable suspensions in aqueous solutions.
+The strong attachment is formed through $\pi-\pi$ interactions.
+
+inorganic nanotubes review \cite{Tenne2004} , unsaturated bonds number increases as the size of MS2 sheet decreases.
+
+Water splitting materials should process a band gap larger than 1.4eV, considering both the NHE potential distance and practical application.
+The monolayer \ce{WS2} exhibits direct gap of 1.98 eV.
+Quantum confinement could push the gap separation farther away.
+\cite{wilcoxon1997} \citeauthor{Notley2013} use liquid exfoliation to prepare \ce{WS2} NPs.\cite{Notley2013} Non-ionic surfactant concentration is about 0.1\%w/w.
+Continuously adding surfactant during sonication improves the yield.
+Optimum surface tension is found at about 40 mJ/m$^2$.
+
+G/\ce{WS2}/G stacked solar cell. For lubricant, and surface protection. Absorption $\sim 10^7 m^{-1}$. \cite{Britnell2013}
+
+In Ref\cite{Zeng2013}, single crystal \ce{WS2} growth using \ce{I2} transport was described in supporting info.
+\ce{C24H12K4O8}\footnote{http://www.chemspider.com/Chemical-Structure.24771386.html}
+
+416 peak was prevously assumed to be a combination of LA and TA phonons at K points.
+
+Raman conditions: 0.3 mW, 532 nm, 200 sec acquisition time. photon flux = $0.3E-3\times6.242E+18/1.2398/0.532=2.84E15$
+
+416 cm raman on WS2. B1u is pressure sensitive. \cite{Staiger2012} also studied pressure dependence.
+
+A1g mode using resonance Raman excitation shows upshift, which is presumably caused by folding induced strains.
+And TEM SAED reveal 3R symmetry.
+We did not observed this upshift of A1g probably due to the large diameter and few layer involved.
+
+Nanotube growth is relatively independent of substrates and FL layer is closely related to substrate. Film growth could provide some insight into the latter scenario.
+
+\fi
+
+\subsubsection{Seeded Growth of Tungsten Oxide NWs}
+With the oxidation experiments study in Sec.~\ref{sec:woxd}, favorable conditions for local growth of NWs were extracted to perform seeded growth.
+
+\begin{figure}[htb]
+\centering
+\subfloat[]{\label{fig:sga}\includegraphics[width=0.4\textwidth]{wox_sg_a.jpg}}\hspace{0.04\textwidth}
+\subfloat[]{\label{fig:sgb}\includegraphics[width=0.4\textwidth]{wox_sg_b.jpg}}
+\caption[Characterization of seeded growth \ce{WO3}: SEM]{Characterizations of seeded growth.
+(a) SEM graphs of \ce{WO3} NWs on \ce{SiO2/Si} substrate.
+(b) A high magnification view showing uniform NW growth and close-up view of one NW.
+}
+\label{fig:woseedsem}
+\end{figure}
+
+As shown in Fig.~\ref{fig:sgb}, dense NWs array was obtained on tungsten powder seeds with individual wires of length up to 5 $\mu$m and diameter about 50 to 200 nm, according to the estimation made in the close-up view.
+Each tungsten powder stood as independent growth site (Fig.~\ref{fig:sga}) with island-layer growth on the substrates, a common feature without using tungsten powder as seed under current experimental conditions.
+It was occasionally observed that NWs growth was initiated adjacent some tungsten powders.
+This phenomenon was correlated to the local trap of vapor flow since it was more often found among the enclosed area by tungsten powders.
+It is also found that the diameter of NWs decrease as the distance between powders and upstream edge increases.
+This is a combination effect of lower temperature and reduced \ce{WOx} growth species supply.
+Similar phenomena were observed in other studies.
+\citeauthor{Thangala2007} reported that a decrease in NW density with increasing substrate temperature, and an increase of NW density with increasing partial pressure of oxygen.\cite{Thangala2007}
+
+% seeded edx 
+\begin{figure}[htb]
+\centering
+\includegraphics[width=0.5\textwidth]{wo3_seed_edx}
+\caption[Composition analysis on seeded growth \ce{WO3} NWs]{EDX spectroscopy on seeded growth \ce{WO3} NWs.}
+\label{fig:woedx}
+\end{figure}
+Energy-dispersive X-ray spectroscopy (EDX) analysis on the seeded growth \ce{WO3} NWs is shown in Fig.~\ref{fig:woedx}.
+Only W and O elements were detected on the NW array.
+The background level from 3 to 8 keV was a manifestation of the continuous components of W X-ray spectrum.
+
+% sg raman xrd
+\begin{figure}[htb]
+\centering
+\subfloat[]{\label{fig:sgxrd}\includegraphics[width=0.45\textwidth]{xrd_cs_before}}\hspace{0.04\textwidth}
+\subfloat[]{\label{fig:sgram}\includegraphics[width=0.45\textwidth]{wox_raman_1}}
+\caption[Characterization of seeded growth \ce{WO3}: XRD and Raman]{ (a) XRD pattern of as-prepared sample indicating the \ce{WO3} phase and the presence of metallic core.
+(b) Raman spectrum on NWs region showing the feature of \ce{WO3}.}
+\label{fig:woseedxrd}
+\end{figure}
+
+Fig.~\ref{fig:sgxrd} is the XRD spectrum of one typical sample.
+The peaks under circular symbol were identified to be the monoclinic \ce{WO3} phase (ICDD PDF 01-083-0950, \emph{a}=7.30084 \AA, \emph{b}=7.53889 \AA, \emph{c}=7.6896 \AA, $\beta$=90.89$^\circ$), while the peak under the triangular symbol was indexed to cubic tungsten phase (ICDD PDF 04-16-3405, \emph{a}=3.157 \AA), in agreement with the EDX analysis (Fig.~\ref{fig:woedx}).
+This means that during the \ce{WO3} seeded growth of 4 h heating at 1000 \si{\degreeCelsius}, the tungsten powder in downstream low temperature region (600 -- 700 \si{\degreeCelsius}) is not entirely oxidized.
+Micro-Raman scattering spectroscopy was performed on the as-synthesized sample as well.
+During Raman examination, the laser spot was carefully focused onto the NWs on powders and several inspections on different positions were observed to ensure the reproductivity of spectra data.
+As shown in Fig.~\ref{fig:sgram}, five distinct bands were well resolved, with peaks located at 131, 265, 327, 711 and 803 \si{cm^{-1}}, respectively.
+This pattern was typical features of \ce{WO3}, consistent with previous study.\cite{Salje1975a,Dixit1986} The high background level probably arises from the metallic core.
+
+% sg tem
+\begin{figure}[htb]
+\centering
+\includegraphics[width=0.9\textwidth]{JAP-2column_Fig5major.jpg}
+\caption[Characterization of \ce{WO3}: TEM]{TEM graphs of as-prepared NWs.
+(a) TEM image of one nanowire with diameter about 40 nm.
+(b) HRTEM images showing the spacing is 0.38 nm, corresponding to (002) plane distance.}
+\label{fig:woseedtem1}
+\end{figure}
+
+TEM specimen was prepared by using carbon grid to slightly scratch the as-grown sample.
+Fig.~\ref{fig:woseedtem1} shows the feature of majority NWs.
+The growth direction is determined to be perpendicular to (002) plane.
+The streaking in SEAD pattern presumably arises from stacking defaults.
+The author also find some NWs exhibit high crystalline quality, as revealed by the TEM analysis in Fig.~\ref{fig:woseedtem2}.
+The NW grew normal to (002) plane with a measured lattice spacing of 3.79 \AA, which is favorably compared to the XRD peak at $23.07^\circ$ (7.7103 \AA).
+The sharp SEAD pattern and clear phase contrast in HRTEM demonstrated are both strong evidence of good crystallinity.
+This formation indicated current growth parameters have promising potential to obtain highly crystalline \ce{WO3} NWs in large scale.
+
+% sg tem
+\begin{figure}[htb]
+\centering
+\includegraphics[width=0.9\textwidth]{JAP-2column_Fig5minor.jpg}
+\caption[Characterization of \ce{WO3}: TEM cont]{TEM graphs of as-prepared NWs.
+(a) TEM image of one nanowire, the diameter is about 70 nm.
+(b) HRTEM images showing the spacing is 0.379 nm, corresponding to (002) plane distance.}
+\label{fig:woseedtem2}
+\end{figure}
+
+In regarding to the formation of NWs on tungsten powder itself, this study assumes the driving force is related to interfacial strain between W and \ce{WOx}.
+Oxidation of tungsten proceed slowly at room temperature and an oxide layer of 100 \AA was found on the surface of tungsten foils.\cite{Warren1996} The tungsten powder used in current study would be covered by a thin oxide layer as well.
+During oxidation, different oxidation rates exist for different crystallographic orientations on the tungsten powder.
+Oxidation occurring at boundaries and defects are preferred thermodynamically.\cite{You2010} Compressive strain will gradually accumulate at the tungsten oxide/tungsten interface, which might limit the diffusion rate of oxygen at temperature lower than 500 \si{\degreeCelsius}.\cite{tungsten1999} At elevated temperature, cracks will primarily occur, as observed in Fig.~\ref{fig:pdtemp}.
+When heated up, tungsten and the oxide shell will probably relax the strain by converting into substoichiometric NWs, a similar process as suggested by \citeauthor{Klinke2005} in the chemically induced strain growth of tungsten oxide NWs.\cite{Klinke2005} It is worth noting that tungsten oxide nanowires could also formed when \ce{WO3} is reduced.\cite{Sarin1975} The elongation of \ce{WOx} is thermodynamically favorable during the conversion from metallic tungsten to tungsten oxide as well.
+Local evaporation-condensation process might also contribute to the formation of NWs on tungsten powder.
+
+The enhanced yield of NWs obtained via seeded growth could be explained by a vapor-solid (VS) mechanism.
+External supply of growth species will condense onto the powders and substrate simultaneously, promoting the elongation of NWs on power as well as resulting island-layer growth on substrate.
+The local NW density in oxidation experiment was much higher than that of seeded growth.
+It is reasonable to presume that during seeded growth, several NWs in a small region on powder will coalescence, as evidenced by the bundled structures.
+At last, the author would like to point out that when low purity tungsten powder (3N) was used as source, sodium tungsten oxide nanowires were found to be dominant in the final product.
+The details have been published.\cite{Sheng2014} It seems surprising that when 3N powder was used as seeds, only \ce{WO3} nanowires were obtained.
+This result was attributed to the lower temperature and significantly reduced amount of 3N powder used in the seeded growth, compared with the conditions used in Ref.\cite{Sheng2014}.
+The source material in seeded growth is not limited to high purity tungsten powder.
+Instead, any material that could produce appropriate growth vapor could be employed, indicating the versatility of this approach.
+
+\subsubsection{Optimization of W powder Oxidization}\label{sec:woxd}
+
+Understanding the oxidation of tungsten powder is the key to obtain high yield in seeded growth.
+Oxidation of tungsten have been investigated under diverse conditions, such as at elevated temperature (\textgreater 1100 \si{\degreeCelsius} ) and oxygen pressure on the order of Torr,\cite{Base1965} and at temperatures ranging from 20 to 500 \si{\degreeCelsius} under atmosphere pressure.\cite{Warren1996} \ce{WO_x} NWs were readily found when tungsten (foil, wire, or powder) is oxidized under various conditions.\cite{Zhu1999,Karuppanan2007,Hsieh2010} However the study on tungsten powder oxidation behavior between intermediate temperature range and under low pressure is still rare.
+This work studied the oxidation of tungsten powders with diverse size within temperature range from 500 to 1000 \si{\degreeCelsius} and under several mTorr oxygen partial pressure.
+Using tungsten powder as seed, the author further illustrate an economic approach to obtain large yield of \ce{WO3} nanowires at relatively lower temperature than previous efforts.
+It is demonstrated that there is an optimal tungsten powder size under our experimental conditions for seeded growth.
+This will provide some insight on the role of tungsten powder as source material in CVD growth of \ce{WO_x}.
+
+Commercial available tungsten powders with different size are usually associated with purity variation as well, as already listed in Table.~\ref{tab:ch5pre}.
+The dimensions of tungsten powder were obtained by measuring the average size in SEM graphs.
+A systematic investigation was performed on the oxidation behavior of tungsten powder to evaluate the temperature effect, size-dependence and influence of oxygen partial pressure.
+% seed optimal
+\begin{figure}[htb]
+\centering
+\includegraphics[width=0.6\textwidth]{JAP-2column_Fig1.jpg}
+\caption[W powder oxidation: temperature effect]{SEM graphs of 99.9\% (3N) tungsten powder oxidization at different temperatures of a) 500 \si{\degreeCelsius}, b) 600 \si{\degreeCelsius}, c) 650 \si{\degreeCelsius}, d) 750 \si{\degreeCelsius}, showing the optimal temperature for local formation of nanowires is between 600--650 \si{\degreeCelsius}.
+Oxygen flow rate is 1 sccm.}
+\label{fig:pdtemp}
+\end{figure}
+
+Fig.~\ref{fig:pdtemp} illustrated the effect of temperature on the morphological change and surface nanowires formation of 3N powder.
+At 500 \si{\degreeCelsius}, most tungsten powder retained its original shape and a layer of tiny dense NWs begun to grow.
+When temperature was increased to 600 \si{\degreeCelsius}, 3N powder started to crack with longer NWs on the isolated surface.
+Further increase of temperature lead to irregular shapes of tungsten power and aggregation of NWs, giving rise to the nanorods and bunched or bundled structures.
+It could be determined from the morphology variation that the optimal seeded growth temperature for 3N powder was in the range of 600 to 650 \si{\degreeCelsius}.
+% seed optimal
+\begin{figure}[htb]
+\centering
+\includegraphics[width=0.6\textwidth]{JAP-2column_Fig3.jpg}
+\caption[W powder oxidation: size effect]{SEM graphs illustrating the oxidization of four different size of tungsten powders at 600~\si{\degreeCelsius} and 1 sccm oxygen flow.
+a) 17 $\mu m$, b) 32 $\mu m$, c) 3.3 $\mu m$, d) 1.5 $\mu m$.}
+\label{fig:pdsize}
+\end{figure}
+
+Fig.~\ref{fig:pdsize} depicted the oxidation of different sizes of tungsten powder under the same experimental conditions.
+In contrast to the morphology of 3N powder shown in Fig.~\ref{fig:pdtemp}, 3N5 powder surface is primarily covered with sub-micro particles as well as some short tiny NWs, whereas 4N5 and 5N powder were thoroughly oxidized, showing branched flowers feature.
+This dramatic difference could be explained in terms of surface energy and oxygen diffusion.
+With smaller dimension, the increased surface-to-volume ratio and short diffusion path both lower the energy barrier of oxidation.\cite{tungsten1999} It was logical to deduce that higher temperature or increased oxygen level might favor the NWs formation on 3N5 powder.
+When it comes to seeded growth, however, the powder size distribution was an important factor to give uniform NWs deposition.
+Since the size distribution of 3N powder is more uniform than that of 3N5 powder, the author employed the former as seeds.
+% seed optimal
+\begin{figure}[htb]
+\centering
+\includegraphics[width=0.6\textwidth]{JAP-2column_Fig2.jpg}
+\caption[W powder oxidation: oxygen pressure]{SEM graphs of 3N tungsten powder oxidization at 600 \si{\degreeCelsius} under different rates of oxygen flow: a) 1 sccm, b) 2 sccm, c) 3 sccm, d) 10 sccm.
+The oxygen partial pressures were 13 mTorr, 23 mTorr, 32 mTorr, and 82 mTorr, respectively with background pressure subtracted.}
+\label{fig:pdoxy}
+\end{figure}
+
+Fig.~\ref{fig:pdoxy} depicted the morphology change of 3N powder with respect to varied oxygen partial pressure.
+When the oxygen flow is lower than 3 sccm, 3N powder almost stayed as the same, with cracks separating the dense layer of NWs.
+When oxygen flow is increased to 10 sccm, the 3N powder exemplified an enlarged version of that for 4N5 or 5N powder under 1 sccm oxygen flow.
+This observation again supported the surface energy explanation.
+
 \subsection{used}
@@
 seriously pursued. 
+\section{docend}
+
+%\section{Crystal Structures and Electronic Properties}
+
+Solid and orderliness.
+
+Two theories arise to describe the outer shell electrons and to correlate the structure and physical properties: \gls{cft} and band theory.\cite{Goodenough1971} \gls{cft} assumes weak interaction between neighboring atoms and localization of electron towards parent atom, whereas band theory assumes that electron is shared equally by all nuclei and therefore a many-electron problems follows.
+Description of a single electron in periodic potential fail to treat the electron correlations adequately, as the interaction between atoms becomes weaker.For transition metals, $s$ and $p$ electrons are well described by a collective-electron model, while the 4f or 5f electrons are tightly bound to nuclei and screened from the neighboring atoms by 5s, 5p or 6s, 6p core electrons, hence it matches well with a localized-electron model.
+d electrons show intermediate character.
+
+In vapor synthesis process, two growth mechanism exists: VS and VLS.
+VS process is widely accepted for the growth of \ce{MoO3}.
+Yet we caution that synthesis conditions should be scrutinized to determine the exact mechanism.
+\citeauthor{Li2002c} suggested a VS mechanism at 700 \si{\degreeCelsius} and VLS at 750 \si{\degreeCelsius} and higher.\cite{Li2002c} \citeauthor{Fibers2007} proposed a modified VS mechanism probably because the deposition occurs on \ce{Al2SiO5} with possible \ce{Al_{0.95}SiNa_{0.06}O_x} involved.
+Therefore temperature and possible impurity could potentially alter the growth mechanism.
+We divide the growth results into two categories: on Si substrate and on non-Si substrate, and describe them respectively.
+We also briefly mention using liquid exfoliation to prepare few layer \ce{MoO3}.
+
+This rectangular shape implies the boundary plane along growth direction (long axis) is (001), in consistency with previous experimental reports\cite{Zeng1998,Li2002b} and theoretical studies.\cite{Firment1983,Cora1997} We also observed different shapes, i.e., elongated hexagonal using similar growth conditions.
+This is not an indication of different growth mode.
+It is a normal thermodynamic fluctuation.
+The growth rates along different crystalline direction of \ce{MoO3} are determined by the free surface energy.
+In fact, (201), (101) and (102) planes have all been observed as terminating planes.\cite{Zeng1998} The stacking rate of \ce{MoO6} octahedra along $a$ and $c$ axis could develop some other ratio.
+And the coexistence of different planes in one growth suggests the similarity of free surface energies between these surfaces.
+In other words, the migration barrier of adatoms on (010) plane is presumably much lower than that on other low index planes due to the Van der Waals interaction nature along [010] direction.
+
+\citeauthor{Wang2013c} changed the NW growth direction by changing the shape of droplets; \citeauthor{Biswas2013} reported enhanced aspect ratio of Ge NWs from bimetallic alloy.
+
+We first repeated the previous growth on ITO/glass, and then found similar deposition phenomena on glass and mica substrates.
+We suspected that the morphology difference on the substrates employed in this study arises from the compositions difference.
+Both mica and glass contains alkaline elements which are absent in Si and \ce{SiO2}/Si substrates.
+We primarily verify this hypothesis by utilizing \ce{NaOH} treated Si substrates and found that the overall morphology almost reproduces that on ITO and mica substrates.
+We then propose a new growth mechanism based on the VLS process to explain the deposition of \ce{MoO3} on alkaline-ions-containing substrates.
+
+ITO versus NaOH images.
+
+According to the phase diagram shown in Fig.~\ref{fig:pd}, \ce{Na2MoO4} - \ce{MoO3} phase above 800 \si{\degreeCelsius} are \ce{Na2MoO4}(l) + \ce{MoO3}(l), More discussion should follow $\ldots$.
+
+%\subsubsection{Phase evolution probing by Raman}
+
+\citeauthor{Hardcastle1990} summarized an empirical formula to relate the Raman peaks and \ce{Mo-O} bonding lengths.\cite{Hardcastle1990} This correlation assumes general form as
+\begin{equation}\label{eq:mobond}
+\nu = A \exp{B\cdot R},
+\end{equation}
+where $A=32895$ and $B=-2.073$ are fitting parameters, R is bond distance in unit of \AA.
+Given a stretching frequency, the resolution for calculated bond distance is $\pm0.016$ \AA.
+Another empirical expression connect the bond valence $s$ and bond distance R: $s(M-O) \approx (R/X)^{-6} $, where X=1.882 when M is Mo, and 1.904 when M is W.
+The valence sum rule could be then used to check the state of Mo cation.
+It should be noticed that not all observed Raman lines could be correlated to a \ce{Mo-O} bond distance by extrapolation of Eq.~\ref{eq:mobond}.
+It is then regarded as a symmetry related vibrational mode, i.e.
+820 \si{cm^{-1} in \ce{MoO3}.
+From the correlation of various Mo compounds, a general conclusion is the lower the stretching frequency for the shortest metal-oxygen bond, the more regular is the structure.
+
+% droplet position statistics
+\begin{figure}[htb]
+\centering
+\includegraphics[width=0.6\textwidth]{droplets_sta}
+\caption[Droplet position statistics]{Droplet position statistics. On-tip and not-on-tip counts variation with respect to growth time. }
+\label{fig:mo3dropsta}
+\end{figure}
+
+Nanotower is a less common morphology in the structures of nanomaterials.\cite{Kharissova2010} We have not found report on  \ce{MoO3} nanotower structures, although there are several studies on \ce{In2O3},\cite{Jean2010,Yan2007}, GaN\cite{Xiao2012} and ZnO\cite{Zhang2013c}.
+\citeauthor{Jean2010} investigated the growth mechanism of \ce{In2O3} nanotowers and attributed it to the periodical axial and continuous lateral growth interaction, where the former was first guided by Au-In alloy liquid, and subsequent by self-catalytic In droplets (MP 156C) while the latter due to VS process.
+In contrast, \citeauthor{Yan2007} observed similar \ce{In2O3} nanotower growth and proposed that the axial growth is controlled by Au-catalytic VLS process.
+\citeauthor{Xiao2012} reported the GaN nanotower grown on Ni-coated Si(111) substrates and explained the growth as asymmetric self-copy process based on VLS mechanism.
+\citeauthor{Zhang2013c} studied the growth of ZnO nanotower and provided a competitive model between axial and lateral growth controlled by Zn vapor to explain the as-synthesized structures.
+(When ZnO and carbon mixture was used as source instead of ZnO alone, nanorods array results, presumably due to the stable supply of Zn vapor owing to the gentle carbothermal reduction.) Therefore the fluctuation of reagents is probably responsible for tapering and periodical modification, which is absent in the coin roll style growth of \ce{MoO3} tower on Si.
+The occasionally observed tapering or enlarging on \ce{MoO3} tower can be attributed to the cooling down growth.
+
+We divide the growth into two stages according to the emerging time of long belts and towers.
+In first stage the growth is dominated by lateral growth, as illustrated in .
+In the second stage, \ce{NaxMoO3} is evaporated and recondensed in the low temperature region, and some droplet will form, and when at proper locations, introduce secondary VLS growth.
+
+In first stage, the Na-Mo-O liquid is formed and have much more higher absorption rate than that of bare substrate.
+The absorbed species will diffuse along the surface and inside the liquid.
+It was difficult to estimate which diffusion path one is faster.
+
+\textbf{open questions}
+\begin{itemize}
+\item Is the liquid consumed? if so, how? : evaporation
+\item How the size of liquid is related to the morphology evolution?
+\item Possible doping level of alkaline ions
+\item other lateral growth mode such as Ni-W-S system
+\item VLS-VS interaction, or possible solution-liquid-solid, VSS,
+\item the interpretation of phase diagram
+\item the overall molar amount of NaOH and MoO3 deposition
+\item Young's parameters, contact angle informations, Gibbs free energy calculation
+\item catalyst composition variation during growth
+\item \ce{Na2Mo4O_{13}} phases, solid solubility of \ce{Na2MoO4} in solid \ce{MoO3} is high.
+\item vapor pressure of \ce{Na2Mo4O_{13}} and \ce{MoO3}.
+\end{itemize}
+
+As shown in Fig, we found several solid clusters with diameter about 1 $\mu m$ on the top part of long belts.
+According to the \ce{Na2MoO4}-\ce{MoO3} binary compounds phase diagram, we expect the terminating solid clusters have a Na:Mo ratio close to 0.6.
+The experimental results match well with this predictions.
+EDX analysis reveal the presence of Na on the solid cluster but not at about 1$\mu m$ away from previous location.\footnote{the sensitivity of our instrument is estimated to be 1\% atomic level} Quantitative atomic ratio derived from the solid cluster is not close to the one predicted by phase diagram probably due to the high Mo content in adjacent area.
+However, XRD examinations on a short time growth sample revealed a possible \ce{Na2Mo4O13} phase(PDF 028-1112), providing an indirection evidence of the droplet composition.
+We also suspect that the growth will become different below 500 \si{\degreeCelsius} since no liquid would remain.
+Substrate placed at low temp end show.
+We can also deduce that other sodium compounds can be employed as substrate treatment agent. This argument is confirmed by \ce{Na2CO3} and \ce{KI} assisted growth.

### 2014-09-27 FrontMatter/Abstract.tex
outline adjusted 30%

@@
 study focused on one-dimensional (1D) tungsten trioxide (\ce{WO3}) and molybdenum trioxide (\ce{MoO3}) nanostructures.
-This dissertation synthesized 1D \ce{WO3} and \ce{MoO3} nanostructures using chemical vapor deposition (CVD) approach, characterized the morphologies and structures, and measured the electrical and optical properties of the as-prepared nanostructures.
+This dissertation synthesized 1D \ce{WO3} and \ce{MoO3} nanostructures using chemical vapor deposition (CVD) approach, characterized the morphologies and structures, and measured the optical properties of the as-prepared nanostructures.
 This study aims at accomplishing controlled and scalable growth of \ce{WO3} and \ce{MoO3} using CVD method, establishing the structure-property relations to rationalize nanostructure synthesis for energy applications, and presenting preliminary results on the devices assembled using the \ce{WO3} and \ce{MoO3} nanostructures.
 
-thesis outline?
 \end{abstract}

### 2014-09-27 FrontMatter/FrontMatter.tex
initial review version 0.1
inital review revised 1
outline adjusted 30%

@@
-  \title{Research plan: Controlled Growth and Property Measurement of One-dimensional Oxide Nanostructures for Energy Applications}
+  \title{Controlled Growth and Property Measurement of One-dimensional Oxide Nanostructures for Energy Applications}
   \author{Tao Sheng}
@@
 \begin{dedication}
-This mis my appear in the named sectional unit, otherwise each glossary will
-appear in a chapter, if chapters exist, otherwise in a section. Unnumbered
-sectional units will be used by default.
+TBD.
 \end{dedication}
@@
 \begin{ackn}
-This work is supported by National Science Foundation (DMR-1006547) and the start-up fund from the Department of Mechanical Engineering and Engineering Science(MEES) and Charlotte Research Institute at the University of North Carolina at Charlotte (UNC Charlotte).
-We appreciate the Department of MEES and the Center for Optoelectronics and Optical Communications at UNC Charlotte for the support of multiuser facilities.
+TBD.
 \end{ackn}
+
 %\pagebreak{}
@@
 % for more, see http://tex.stackexchange.com/questions/82993/how-to-change-the-name-of-document-elements-like-figure-contents-bibliogr?lq=1
-\setcounter{tocdepth}{1}
+\setcounter{tocdepth}{2}
 % ----- end of work around--------
@@
 \printglossary[type=\acronymtype]
+\addcontentsline{toc}{chapter}{\acronymname}
 \clearpage

### 2014-09-27 ch-intro/ch-instr.tex
outline adjusted 30%

@@
 
-\section{Home-built CVD System}
-The synthesis was accomplished in a home-made hot-wall CVD system, as visualized in Fig.~\ref{fig:ch2cvd}.
+\section{Synthesis Equipments}
+\subsection{Home-built CVD System}
+The syntheses were accomplished in a home-made hot-wall CVD system.
+The reaction chamber part and a schematic drawing of whole system can be visualized in Fig.~\ref{fig:ch2cvd}.
+The reaction chamber consists of fused silica tube and a thermal furnace.
 The furnace is made by two semi-cylindrical ceramic fiber heaters (WATLOW, Inc.) with power density from 0.8 to 4.6 \si{W cm^{-2}}.
-Quartz tube (Quartz Sci, Inc.) of 1 in diameter was primarily used as reaction chamber.
+Quartz tube (Quartz Sci, Inc.) of 1 in diameter was inserted into the furnace serving as reaction chamber.
 A mechanical pump was connected to maintain the low pressure environment inside the chamber.
@@
 There exists a uniform heating zone in the center area, spanning over about 2 in; then $T$ descends gradually within the 6 in heating zone, and decrease rapidly at the rest part.
-In this study, a zero position is defined at the upstream edge of reaction chamber covered by the furnace.
+In this study, a zero position referred as 0 inch is defined at the upstream edge of reaction chamber covered by the furnace.
 
@@
 \includegraphics[width=0.8\textwidth]{temp_profile.pdf}
-\caption[CVD temperature profile]{Temperature profile of home-built low-pressure chemical vapor system.}
+\caption[CVD temperature profile in ambient environment]{Temperature profile of home-built low-pressure chemical vapor system measured in ambient environment.}
 \label{fig:ch2temp}
@@
 On the hot substrate, adatoms diffuse and do not settle down until finding an appropriate location where equilibrium is favored.
-Detailed growth conditions are introduced in corresponding chapters.
+Detailed growth conditions will be introduced in the corresponding chapters.
+Basic operations and several growth recipes using the home-built CVD system are included in Appendix.
 
-\section{Scanning Electron Microscopy (SEM) and Energy Dispersive X-ray Spectroscopy (EDX)}\label{sec:sem}
+\subsection{Substrates Treatments}\label{ch2sub}
+
+Silicon and silicon dioxides on Si wafer ($p$-Si(100), University Wafer Inc.) were primarily used, and other substrates, i.e., Mica\footnote{\ce{K(Al2)(Si3Al)O10(OH)2}}, glass (Fisher Scientific, microscope slide, 12-549),\footnote{Typical composition is 72.6\% \ce{SiO2}, 0.8\% \ce{B2O3}, 1.7\% \ce{Al2O3}, 4.6\% \ce{CaO}, 3.6\% \ce{MgO} and 15.2\% \ce{Na2O}} stainless steel, were also employed.
+Si and \ce{SiO2}-Si substrates were first cut into rectangular pieces of certain size and then ultrasonically cleaned (Branson 1510R-MTH) with acetone and alcohol for about 15 min, each followed by blow-drying with nitrogen gas.
+After solution cleaning, the substrate surface is usually hydrophobic.
+Depending on the specific experimental requirement, a hydrophilic surface may be required.
+A plasma cleaner (Kurt J Lesker, Plasma-Preen 862) was used to render a hydrophilic Si surface, where reaction among $e$, \ce{O^+}, \ce{O2^+}, \ce{O^-},\ce{O2} occurs, and \ce{OH}-terminated surface followed.\cite{Habib2010} The treatment was done at 2 Torr \ce{O2} for 3 min.
+Glass substrates cleaning is the same as that of Si.
+Mica is cleaved right before the growth withoud extra cleaning steps.
+In addition, substrates can be coated with a thin layer of metal before growth.
+This process will be covered in Sec.~\ref{sec:mag}.
+
+\subsection{Magnetron Sputtering}\label{sec:mag}
+Sputtering, a process in which atoms are ejected from a solid target material by bombarding it with energetic particles, is a well established physical vapor deposition (PVD) process with a high degree of controllability.
+The high energy and controllable parameters of sputtering can result in the growth of well-structured and crystalline films.
+Further, sputtering can be easily implemented as a roll-to-roll process for large-scale manufacturing.
+It is widely utilized for deposition of \ce{WO_x} in industry.
+
+In this work, magnetron sputtering (Denton Vacuum Desk IV) was used to coat thin layers of metals onto cleaned substrates, such as W, Mo, Au, Ag, Pd, and Pt.
+As shown in Fig.~\ref{fig:ch2magsp}, a high potential created between the target (cathode) and substrate ionizes the argon molecules.
+These ions are accelerated to bombard the target foils, knocking out active atoms which subsequently deposit onto the substrates.
+A magnetic field is applied to confine electrons to the vicinity of the foils.
+These electrons in turn increase the ionization yield.
+\begin{figure}[htb]
+\centering
+\includegraphics[width=0.8\textwidth]{magsp.jpg}
+\caption[magnetron sputtering system]{Schematic drawing of sputtering adopted from ref\cite{Song2008}}
+\label{fig:ch2magsp}
+\end{figure}
+
+Sputtering is a better PVD technique than e-beam deposition since it alleviates the adverse effects in the latter.
+\ce{Ar+} ions are accelerated to target foils.
+The pressure of \ce{Ar+} has two functions: to sputter off the target ions, and to influence the mean free path (MFP).
+These collisions between target ions and \ce{Ar+} leads to almost all arrival angle, thus uniform coverage.
+The sputter yield is number of target ions released per ions hitting on target.
+If \ce{Ar+} ion energy is less than 100 eV, the yield is zero; If larger than 10 keV, implantation of \ce{Ar+} into target foils occurs.
+Usually yield between 1 and 2 is desired.
+The MFP in sputtering is on order of 3 cm (assuming pressure 30 mTorr), with source-to-substrate distance as 5 cm, average number of collisions is about 5/3$\sim$2.
+
+\section{Characterization Tools}
+\subsection{Scanning Electron Microscopy (SEM)}\label{sec:sem}
 
@@
 
-In this study, SE images were mainly used to reveal the morphology of the samples.
-Energy dispersive X-ray spectroscopy provides compositional information attaining to the studied sample because of the characteristic X-ray lines from each element.
-The X-ray detector (INCA, 7573-M, 10 \si{mm^2} Si cooled by liquid nitrogen) is equipped with a super thin window enabling light element detection such as boron.
+In this study, secondary electron images were mainly used to reveal the morphology of the samples.
+Unless otherwise noticed, the SEM images in this work were all acquired using 10 kV acceleration voltage, 10 mm working distance and 30 spot size.
+
+Charge effect could arise on the samples grown in this study, leading to anomalous contrast on the images.
+Several measures could be taken to alleviate this adverse influence, including adjusting the acceleration voltage, tilting the specimen, and coating a thin layer of metal.
+Sometimes when an area is scanned for a long time at high magnification, the surrounding region could appear brighter after switching to a lower magnification.
+This is a sample contamination, due to the E-beam induced polymerization and deposition of hydrocarbon molecules in the vicinity of that smaller area.
+
+\subsection{Energy Dispersive X-ray Spectroscopy (EDX)}\label{sec:edx}
+
+Energy dispersive X-ray spectroscopy provides compositional information attaining to the studied sample because of the characteristic X-ray emission from each constitutive element.
+EDX unit is usually attached to another electron microscopy, SEM or TEM.
+In this study, the SEM-attached EDX was primarily used.
+The X-ray detector (INCA 7573-M, 10 \si{mm^2} Si cooled by liquid nitrogen) is equipped with a super thin window enabling light element detection such as boron.
+Typical working parameters of EDX detection in this study include 20 kV acceleration voltage, 10 mm working distance and 60 s analysis time.
+
 To obtain quantitative results on EDX spectra, special attentions should be paid to the following aspects:
@@
 \end{itemize}
-
 Even for qualitative analysis, ambiguity exists when the $K$ lines of lighter elements overlap with $L$ lines of heavier elements.
@@
 
-Charge effect could arise on the samples grown in this study, leading to anomalous contrast on the images.
-Several measures could be taken to alleviate this adverse influence, including adjusting the acceleration voltage, tilting the specimen, and coating a thin layer of metal.
-Sometimes when an area is scanned for a long time at high magnification, the surrounding region could appear brighter after switching to a lower magnification.
-This is a sample contamination, due to the E-beam induced polymerization and deposition of hydrocarbon molecules in the vicinity of that smaller area.
-
-\iffalse
-An eucentric specimen stage is used, thus observation area remain fixed when tilting the specimen.
-The pressure in SEM chamber is on the order of $10^{-3} \sim 10^{-4}$ Pa, which is usually maintained by a diffusion pump, or turbo molecular pump when oil-free operation is needed.
-For a field emission electron source, a sputter ion pump becomes necessary due to the high vacuum requirement.
-
-The SEM instrument used in this study is JEOL JSM-6480 and EDX attachment from Oxford Instrument INCA. Typical observation conditions are listed as following:
-
-\begin{enumerate}
-\item SEM
-\begin{itemize}
-
-\item Acceleration voltage: 10 kV
-\item Working distance: 10 mm
-\item Scanning time: 80 s
-\end{itemize}
-\item EDX
-\begin{itemize}
-
-\item Acceleration voltage: 20 kV
-\item Working distance: 10 mm
-\item Dead time: $20\sim30$\%
-\end{itemize}
-\end{enumerate}
-
-\begin{quotation}
-Since the intensity of characteristic X-rays is proportional to the concentration of the corresponding element, quantitative analysis
-can be performed. In actual experiment, a standard specimen containing elements with known concentrations is used. The
-concentration of a certain element in an unknown specimen can be obtained by comparing the X-ray intensities of the certain element
-between the standard specimen and unknown specimen. However, X-rays generated in the specimen may be absorbed in
-this specimen or excite the X-rays from other elements before they are emitted in vacuum. Thus, quantitative correction is needed.
-In the present EDS and WDS, correction calculation is easily made; however, a prerequisite is required for this correction. That is,
-elemental distribution in an X-ray generation area is uniform, the specimen surface is flat, and the electron probe enters perpendicular to the specimen.
-Actually, many specimens observed with the SEM do not satisfy this prerequisite; therefore, it should be noted that a quantitative analysis result might have appreciable errors.
-\end{quotation}
-
-\fi
-
-\section{X-ray Diffraction (XRD)}
-
+\subsection{X-ray Diffraction (XRD)}
 Crystal structures of the as-synthesized specimens in this study were characterized using PANXpert Pro MRD with Cu $K\alpha_{avg}$ radiation at $\lambda$=1.5418 \AA.
@@
 
-\section{Transmission Electron Microscopy (TEM)}
+\subsection{Transmission Electron Microscopy (TEM)}
 
@@
 Table~\ref{tab:ch2tem} demonstrates the origin of difference in these two techniques.
-
 \begin{table}[htb]
@@
 3.135 \AA & Cu $K\alpha$ & 1.541 \AA & 28.45$^\circ$  \\
-3.135 \AA & 200 kV & 0.0251 \AA \textsuperscript{\emph{a}}& 0.45$^\circ$  \\
+3.135 \AA & 200 kV & 0.0251 \si{\angstrom}\textsuperscript{\emph{a}}& 0.45$^\circ$  \\
 \bottomrule
@@
 \end{table}
-
 This small deviation angle determines the way of secondary signal usage in TEM.
-In analog to the diffraction-limited resolution in conventional lens optics, the ultimate resolved point distance in TEM should be on the order of electron wavelength used, which is 0.025 \AA at 200 kV.
+In analog to the diffraction-limited resolution in conventional lens optics, the ultimate resolved point distance in TEM should be on the order of electron wavelength used, which is 0.025 \si{\angstrom} at 200 kV.
 However, it is generally more difficult to manipulate electron with magnetic field than do photon with dielectric lens.
 The current resolving power in TEM is on the order of 1.0 \si{\angstrom} without correction of spherical aberration.
-The nominal resolution of JEM-2100 is 2.3 \AA.
+The nominal resolution of JEM-2100 is 2.3 \si{\angstrom}.
 On the other hand, it is much easier to fine tune the power (focal length) of lens in TEM than in conventional optics.
@@
 TEM images and SEADs were acquired using a charge coupled device (CCD) from Gatan, Inc.
-EDX spectroscopy was captured by similar Oxford Instrument INCA attachment introduced in Sec.~\ref{sec:sem}.
-
+EDX spectroscopy was captured by similar Oxford Instrument INCA attachment introduced in Sec.~\ref{sec:edx}.
 To make the best out of TEM analysis, one also needs to be aware of the limitations of TEM.
@@
 
-\iffalse
-Similar to the photon-lattice interaction in XRD, the process of TEM could be understood as electron scattering events by the same crystal plane.
-
-\begin{itemize}
-\item X-ray: characteristic X-ray for elemental analysis, Bremsstrahlung X-ray also useful for biological sample; $K_\alpha$ line from L to K transition, and $K_\beta$ from M to K transition, $L_\alpha$ line from M to L transition, Inelastic cross section, Bethe expression, X-ray energies are not identical to the ionized energy because after first emission, the atom is not in ground state until a free electron fill the last hole in the outermost shell.
-A cascade of transitions, Coster-Kroning transition, X-ray line shift slightly due to the chemical bonding to another atom.
-XEDS is not good at analyzing light elements due to the low fluorescence yield, which is strongly dependent on Z.
-Bremsstrahlung X-ray emission is strongly forward,
-\item SE: ejected from the conduction or valence bands, weak so only escaping if near the surface, STEM, complex cross section mechanism, 
-\item Auger: Auger electron has specific energy similar to X-Ray, but is much more strongly absorbed than X-ray. Stated another way, Auger electron is hard to escape, so it is surface sensitive. 
-\item CL: spatial resolution around 100 nm, 
-\item collective interaction, plasmon and phonon, plasmon excitation cross section in Lorenztian form $\frac{d\sigma_\theta}{d\Omega} = \frac{1}{2\pi a_0} \frac{\theta_E}{\theta^2 + \theta_E^2}$, where $\theta_E = E_p/2E_0$,
-\end{itemize}
-
-The diameter of E-beam in TEM is less than 5 nm in general, and can be $< 0.1$ nm at best.
-
-correction of spherical aberration ($C_s$) and chromatic aberration ($C_c$), $C_s$ is done by , $C_c$ by energy-filtering, which is more useful for thicker specimens.
-$C_s$ correction permits the generation of smaller electron probes with higher currents, which significantly improves both analytical spatial resolution and sensitivity.
-$C_c$ correction offer the possibility to form band-gap imaging and chemical-bond imaging.
-The limiting apertures increase the depth of field for specimen, and the depth of focus for the image.\cite{Williams2009}
-
-including controlling the interactions of electron with magnetic fields and with specimen.
-
-XRD: X-ray scattered by electrons, electron scattered by both electrons and nuclei.
-Fresnel vs.
-Fraunhofer, high-angle scattered electron are incoherent; therefore, it can be used to form high-resolution Z-contrast image of a crystalline specimen, regardless of the orientation.
-Auger electron spectroscopy.
-EELS and XEDS constitute analytical electron microscopy (AEM).
-close approach the single-atom level.
-well suited to, energy-loss electrons cause Kikuchi lines to arise in DPs.
-Ionized atom enters excited state,
-
-penetrate electron cloud, spherical wavelets, the cross section for electrons elastically scattered into angles larger than $\theta$ is $\sigma_{nucleus}= 1.62\times10^{-24} (\frac{Z}{E_0})^2\cot^2\frac{\theta}{2}$; scattering factor $f(\theta)$ for low angle ($< \sim 3^{\circ}$).
-
-Point-group and space-group determination from convergent-beam patterns.
-crystal symmetry analysis.
-e-beam wavelength in metal.
-The high-resolution comes at the cost of poor sampling.
-Human eyes and brain understand reflected light image, and not well-trained for the transmission images.
-
-One must be just as aware of the instrument's limitations as one is of its advantages.
-TEM is initially developed to overcome the image resolution imposed by light microscopes.
-constitute, draw analogies, resolving power, E-beam is one type of ionizing radiation, which is capable of removing the tightly bound, inner-shell electrons from attractive field of nucleus (visible light, is non-ionizing radiation to some extent).
-a wide range of secondary signal can be produced, the spectra exhibits characteristic peaks, which identify the elements present in the specimen.
-In analog to laser as a highly coherent source, .
-
-Both wave and particle approach, non-scattering is invisible, backscattered in large angle and secondary electrons are of interest in SEM, where they provide Z contrast and surface-sensitive, topographical images.
-forward scattered is of interest in TEM.
-scattering events as billiard balls colliding, coherently scattered are those that remain in step, and incoherently scattered electrons have random phase relationship.
-Assuming single scattering events in TEM,
-
-The cost of TEM adds up to \$10 per eV. seize the public's imaginations.
-
-The cross section of tungsten, moly is
-
-Focused ion beam (FIB) to prepare thin foils of individual gates from one of the many millions of such on a wafer.
-The events of electron passing through one crystal plane, The coherent length of e-beam, collection angle,
-
-\fi
-
-\section{Raman and UV-Vis Spectroscopy}
+\section{Optical Measurements}
+\subsection{Raman Spectroscopy}
 
@@
 
-In this study, Raman measurement was performed using a confocal micro-Raman system (Horiba Scentific, Labram HR800) with excitation wavelengths of 441, 532 and 632 nm.
+In this study, Raman measurement was performed using a confocal micro-Raman system (Horiba Scentific, Labram HR800) with excitation wavelengths at 441, 532 and 632 nm, where the corresponding photon energy is 2.81 eV, 2.33 eV and 1.96 eV, respectively.
 For nanowire samples, the laser powers were kept between 0.2 and 0.3 mW, and typical acquisition time was 100 s to avoid possible thermal damage.
@@
 
-\iffalse
-A Raman pattern database can be found at \url{http://wwwobs.univ-bpclermont.fr/sfmc/ramandb2/index.html}. 
-In analytical practice, frequency is expressed in reciprocal wavelength (as cm−1), called wavenumbers;
-\fi
-
-UV-Vis-NIR spectrophotometer is a useful tool to obtain absorption and reflectance from various samples.
+\subsection{UV-Vis Spectroscopy}
+UV-Vis-NIR spectrophotometer is a useful tool to obtain optical properties from various samples.
 Generally speaking, the UV spectrum ranges from 100 nm to 400 nm, and visible spectrum spans from 400 nm to 750 nm.
@@
 The cost of fabricating a spectrometer covering the whole NIR region can be quite high.
-The instrument used in this thesis (Schimadzu, UV2600Plus) can measure from 220 nm to 1350 nm (5.6 eV to 0.92 eV) with an integrating sphere.
+The instrument used in this dissertation (Schimadzu, UV2600Plus) can measure from 220 nm to 1350 nm (5.6 eV to 0.92 eV) with an integrating sphere.
 
@@
 When the sample is in liquid form, it is more convenient to use $A =\epsilon_\lambda C x$, where $C$ is the molar concentration (M = \si{\mole \per L}), and $\epsilon_\lambda$ is the extinction coefficient/molar absorptivity (\si{M^{-1} cm^{-1}}).
-For example, $\epsilon$ for methylene blue (MB) is $10^5 M^{-1}cm^{-1}$ at 660 nm.\cite{Mills1999} So by measuring the maximum absorbance of known sample, its concentration can be estimated accordingly.
+For example, $\epsilon$ for methylene blue (MB) is $10^5$ \si{M^{-1}cm^{-1}} at 660 nm.\cite{Mills1999} So by measuring the maximum absorbance of sample with known composition, its concentration can be estimated accordingly.
 
@@
 Then the dispersion was transferred into one 10 mm quartz cuvette (Thorlabs, W005654) for absorption measurement with another paired cuvette containing pairing liquid only.
-To carry out diffuse reflectance measurement, integrating sphere (ISR2600Plus) was used with an incident angle of 0 deg.
+To carry out diffuse reflectance measurement, integrating sphere (ISR2600Plus) was used with an incident angle of 0 degree.
 The baseline reflectance was first recorded with the standard white plate (barium sulfate powder, \ce{BaSO4}) placed at the exit window on the sample path side, then the target sample was set in for relative reflectance measurement.
@@
 Chemical wrapping paper can be inserted between the glass rod and \ce{BaSO4} powder to prevent the powder sticking.
-Nanostructured sample could be mounted directly with the growth substrate, or ground and spread evenly onto \ce{BaSO4} surface.
-
-\iffalse
-
-hemispherical reflectance, 
-diffusive reflectance is a mathematical artifice without direct physical meaning.
-
-p332- 338
-
-the reflecting power associated with a specular-type process is often termed reflectivity, while reflectance is the analogous term for diffusely reflected radiation.
-This two types of reflection are present simultaneously.
-
-Cauchy formula, empirical equation which has subsequently been placed on a firm theoretical basis.
-
-intensity for a complex quantities is obtained by multiplying the complex conjugate.
-
-For strongly absorbing materials, the reflected light is complementary to the color of light transmitted by it, such as gold transmission is green;
-
-For the weakly absorbing substances of rough surface, it will appear the same color by transmission or reflection.
-
-penetration depth is wavelength dependent $d = \frac{In2 \lambda}{2\pi \sqrt{\sin^2\theta_i - n^2}}$, longer wavelength penetrated further than did shorter wavelength. attenuated total reflectance,
-
-thin film, amorphous, mean free path of electron is diminished, and porous in structure. The maxwell-garnett theory provides a satisfactory explanation, where free electron density is reduced.
-
-diffuse reflection: $I = I_0 \exp(-\epsilon d)$, Lambert cosine law formulated. multiple scattering by individual particles. 
-$R_tot = \alpha R_sp + (1- \alpha) R_diff $,
-
-multiple scattering of diffuse radiation in a medium composed of closely packed particles.
-
-\[
-\log{f(r_\infty) = \log{k} - \log{s}}
-\]
-
-It is concluded that the KM function can be used to obtain the characteristic color curve of a given sample only in the limit of small total absorption.
-
-by mixing the sample with an abundance of the reflectance standard, the regular reflection is extensively eliminated.
-
-The color of an object depends on the spectral composition of the source.
-The color of many light sources can be specified in terms of the temperature to which a blackbody radiator must be heated in order to achieve a color match for the source, which is known as color temperature.
-
-integrating sphere: the intensity at any part of the sphere, due to the reflected light is a measure of the total flux from a particular source, independent of the spatial distribution or location of the source on the sphere.
-
-substitution method, comparison method,
-
-\fi
-
-\section{Substrates and Pre-growth Treatments}\label{ch2sub}
-
-Silicon and silicon dioxides on Si wafer ($p$-Si(100), Unversity Wafer Inc.) were primarily used, and other substrates (i.e.
-Mica\footnote{ \ce{K(Al2)(Si3Al)O10(OH)2}}, glass (Fisher Scientific, microscope slide, 12-549),\footnote{Typical composition is 72.6\% \ce{SiO2}, 0.8\% \ce{B2O3}, 1.7\% \ce{Al2O3}, 4.6\% \ce{CaO}, 3.6\% \ce{MgO} and 15.2\% \ce{Na2O}} stainless steel) were occasionally used.
-Substrates were first cut into rectangular pieces of certain size and then ultrasonically cleaned (Branson 1510R-MTH) with acetone and alcohol for about 15 minutes each followed by blow-drying with nitrogen gas.
-After solution cleaning, the Si surface is hydrophobic.
-Depending on the specific experimental requirement, a hydrophilic surface may be desired.
-A plasma cleaning was used (Kurt J Lesker: Plasma-Preen 862) to render a hydrophilic Si surface, where reaction among $e$, \ce{O^+}, \ce{O2^+}, \ce{O^-},\ce{O2} occurs, and \ce{OH}-terminated surface followed.\cite{Habib2010} The treatment was done at 2 Torr \ce{O2} for 3 minutes.
-In addition, substrates can be coated with a thin layer of metal before growth.
-This process will be covered  in Sec.~\ref{sec:mag}.
-
-\subsection{Magnetron Sputtering}\label{sec:mag}
-
-Sputtering, a process in which atoms are ejected from a solid target material by bombarding it with energetic particles, is a well established physical vapor deposition (PVD) process with a high degree of controllability.
-The high energy and controllable parameters of sputtering can result in the growth of well-structured and crystalline films.
-Further, sputtering can be easily implemented as a roll-to-roll process for large-scale manufacturing.
-It is widely utilized for deposition of \ce{WO_x} in industry.
-
-In this work, magnetron sputtering (Denton Vacuum Desk IV) was used to coat thin layers of metals onto cleaned substrates, such as W, Mo, Au, Ag, Pd, and Pt.
-As shown in Fig.~\ref{fig:ch2magsp}, a high potential created between the target (cathode) and substrate ionizes the argon molecules.
-These ions are accelerated to bombard the target foils, knocking out active atoms which subsequently deposit onto the substrates.
-A magnetic field is applied to confine electrons to the vicinity of the foils.
-These electrons in turn increase the ionization yield.
-
-\begin{figure}[htb]
-\centering
-\includegraphics[width=0.8\textwidth]{magsp.jpg}
-\caption[magnetron sputtering system]{Schematic drawing of sputtering adopted from ref\cite{Song2008}}
-\label{fig:ch2magsp}
-\end{figure}
-
-Sputtering is a better PVD technique than e-beam deposition since it alleviates the adverse effects in the latter.
-\ce{Ar+} ions are accelerated to target foils.
-The pressure of \ce{Ar+} has two functions: to sputter off the target ions, and to influence the mean free path (MFP).
-These collisions between target ions and \ce{Ar+} leads to almost all arrival angle, thus uniform coverage.
-The sputter yield is number of target ions released per ions hitting on target.
-If \ce{Ar+} ion energy is less than 100 eV, the yield is zero; If larger than 10 keV, implantation of \ce{Ar+} into target foils occurs.
-Usually yield between 1 and 2 is desired.
-The MFP in sputtering is on order of 3 cm (assuming pressure 30 mTorr), with source-to-substrate distance as 5 cm, average number of collisions is about 5/3$\sim$2.
-
-\section{Data Processing}
-
-The SEM images are cropped using Adobe Photoshop for highlighting the features and fitting into text width.
-To obtain the dimension of specimen, scale bar was measured and compared to the size of interest using ImageJ\cite{Schneider2012} for SEM, TEM images and SAED pattern.
-It is worth noting that ImageJ could directly read the dm3 format generated in Gatan imaging software, which is more productive than the scale bar method.
-
-Various spectra, be it from XRD, EDX, Raman, or UV-Vis, were redraw using Origin Pro 8.0.
-The peak fitting was performed using \emph{Fityk}, a nonlinear curve fitting program specialized in data processing from powder diffraction, chromatography, photoluminescence and photoelectron spectroscopy, infrared and Raman spectroscopy, \emph{etc}.\cite{Wojdyr2010}
-
-\iffalse
-incoherent illumination $s = \frac{1.22 \lambda_{vac}}{2n\sin i}$, 
-coherent illumination in microscope $s = \frac{\lambda_{vac}}{n\sin i}$,, 
-phase contrast: transforming phase change in object plane into amplitude variation in image plane. 
-much better than needed, human eye resolving power 0.3 mrad,
-
-The illumination can be considered as incoherent (adding intensity) if the object is self-luminous, or if illminated from all direction.
-
-The opposite occurs in TEM probably, where the specimen is irradiated with complete transverse coherence across its area. back 
-focal plane displays the Fourier transform of complex amplitude in object plane.
-The optical system is a spatial low-pass filter: it builds up images from only the low Fourier components present at the object, having higher values cutoff.
-
-The information about an object is on display in the objective lens's back focal plane in a Fourier-transform form.
-dark field, removing zero order; Schlieren technique, removing half of diffraction from one side of back focal plane; applications: apodizing in telescope, satellite transmitting aerial structure,
-
-with the aid of Fig. 
-conjugate plane,
-
-electron lens can be made of electrostatic field, and magnetic field, and the B field can be generated from ferromagnetic materials (soft iron, 2 T) or superconducting (100 T).
-
-$C_s$ has dimensions of length, and is approximately equal to the focal length of objective lens (1-3 mm in TEM).
-
-$r_{min} \approx 0.91(C_s \lambda^3)^{1/4}$ is about 0.3 nm typically; with $C_s$ correction, $r_{min}$ can be further reduced to 0.07 nm.
-And human eye can resolve a distance of 0.2 mm, therefore the maximum useful magnification is about $0.2 \times 10^{-3}/0.3 \times 10^{-9} \sim 670 K$.
-
-And after interacting with specimen, the energy spread of transmitted E-beam becomes about 20eV, which will limit the resolution more than does the spherical aberration.
-
-\textbf{coherence of E-beam}
-
-faint points, large disk, the feature of interest is what make the materials imperfect,
-
-20 keV E-beam in TV.
-
-In XRD, both diffraction peak position and intensity are used; whereas in TEM, most time only the positions of spots are of concern.
-
-physical process of diffraction where the atomic planes appear to behave as mirrors for incident E-beam;
-
-\fi
+Nanostructured sample on transparent substrates, i.e., quartz, could be mounted directly with the growth substrate, or ground and spread evenly onto \ce{BaSO4} surface.

### 2014-09-27 ch-intro/ch-intro.tex
outline adjusted 30%

@@
 \section{Background and Motivation: Nanomaterials for Energy Applications}
-\today
 
-TMO as electrochromic device and TMDC as newly 2D semiconductor, and some VLS.
-Transition metal oxides (TMOs) exhibit rich structures and useful properties, and could been used in solar energy harvesting (\emph{e.g.}, photoelectrochemistry, photocatalysis, and photovoltaics) and energy saving (\emph{e.g.}, electrochromism and photochromism) applications.
+Transition metal generally refers to any elements in the d-block of periodic table, and transition metal oxides (TMOs) mean the chemical compounds that consist of at least one transition metal element and oxygen.
+Similarly, transition metal dichalcogenides (TMDCs) are compounds that combine at least one transition metal with chalcogen elements from group VIA (S, Se, Te, Po).
+Oxygen also belongs to group VIA, but is often treated separately.
+This study focused on the following three materials: molybdenum oxide, tungsten oxide and tungsten disulfide.
+Both tungsten (W) and molybdenum (Mo) belong to Group VIB transition metal, with outer shell electrons configuration as $4d^55s^1$ and $5d^46s^2$, respectively.
 
-\iffalse
-Materials that human can make define the age they live in.
-From Stone Age to Bronze Age and Iron Age, people evolve as mastering more and more sophisticated techniques of manipulating metals, such as alloying and annealing.
-Obtaining extreme high purity of silicon brings us into Information Age.
-Future is difficult to predict.
-But nanotechnology is one direction that we can not ignore.
-According to \gls{nni}, \gls{nanotechnology}.
-This definition alludes that dimension comes before compositions.
-It is often related to the quantum confinement or surface area in nanomaterials, which we will later revisit with specific scenario.
+The two metal oxides, \ce{MoO3} and \ce{WO3}, have been studied for decades for energy related applications, e.g., photoelectrochemistry,\cite{Su2010} photocatalysis,\cite{Watcharenwong2008, Macphee2010} photovoltaics\cite{Coridan2013} and electrochromism.\cite{Yoshimura1985, Mortimer2011} \ce{WS2} has also been investigated in various forms, i.e., thin film, nanotube, and 2D atomic layer recently.
+\ce{WS2} exhibits some potentials in solar cell, water cleavage, and field effect transistor.
 
-There are three states of matter under usual conditions: solid,liquid and gas.
-Solids materials could be further categorized into five groups: metals, ceramics, polymers, semiconductors, and composites.\cite{William2009} This classification is based on both composition and mechanical, electrical, and thermal properties as well as the associated functionality(i.e., \gls{ceramics} are typically hard yet brittle, insulating to electricity and resistant to heating).
+\subsection{Electrochromism for Energy Saving}
 
-\fi
-Energy saving and harvesting.
+Commercial buildings in U.S.
+consumed approximately 35\% of the electricity use.\footnote{U.S.
+Department of Energy, "Energy Efficiency Trends in Residential and Commercial Buildings", 2008.} And traditional windows in the buildings account for up to 40\% of the total heating, cooling and lighting consumption.
+The smart windows is an energy efficient solution by allowing for separate control of the visible and NIR illumination/transmission.
+
+Electrochromic materials are a group of functional materials whose coloration status can be reversibly switched using a finite durance of low DC voltage (\textless 5 V).
+Another important advantage of smart windows based on EC materials is the failure mode being clear instead of opaque compared to other techniques, e.g, liquid crystal, suspended particles.
+
+coloration efficiency, the doping amount,
+
+\subsection{Photocatalysis for Energy Harvesting}
+
+Photocatalytic activity occurs when a semiconductor in aqueous solution is illuminated by photons of energy larger than the bandgap, then electron-hole pairs generate free radicals, i.e., \ce{OH.}, which enable further reactions.
+For water splitting using solar energy, the band gap should be within $2.0 \sim 3.0 $ eV, and CB edge should be more negative than reduction potential of \ce{H^+/H2}, whereas the VB top should be more positive than the oxidation potential of \ce{H2O}/\ce{O2}.\cite{Wang2012} The valence band holes (\ce{h^+}) oxidize water to oxygen and conduction band electrons propel hydrogen generation, as depicted in Eq.~\ref{eq:h2o}.
+\begin{subequations}\label{eq:h2o}
+\begin{align}
+4\ce{h^+} +  \ce{H2O} &\rightarrow \ce{O2} + 4\ce{H^+} \label{eq:hervb}\\
+4\ce{H^+} +  4e^- &\rightarrow 2\ce{H2} \label{eq:hercb}
+\end{align}
+\end{subequations}
+As shown in Fig.~\ref{fig:woxnhe}, \ce{WO3} has \gls{cb} edge positioned slightly more positive than reduction potential of \ce{H^+/H2}(versus \gls{nhe}), and \gls{vb} edge much more positive than the oxidation potential of \ce{H2O}/\ce{O2}.
+So the photo-cleavage of water cannot be accomplished by \ce{WO3} alone.
+Nevertheless, a tandem cell approach by \ce{WO3} film and dye-sensitized \ce{TiO2} has been demonstrated with an efficiency of 4.5\%.\cite{Michael1999} It is worth noting that green plants also have two photosynthetic systems connected in series, one for oxidation of water into oxygen and the other for fixation of carbon dioxide.
+% wo3 vs NHE
+\begin{figure}[htb]
+\centering
+\includegraphics[width=0.7\textwidth]{woxnhe.jpg}
+\caption[Bands positions of \ce{WO3} versus NHE]{Bands positions of \ce{WO3} in contact with aqueous electolyte at pH 1, adapted from Ref.\cite{Gratzel2001}}
+\label{fig:woxnhe}
+\end{figure}
+Moreover, favorable oxygen evolution of \ce{WO3} brings good performance in degradation of organic compounds\cite{Hepel2001,Luo2001,Watcharenwong2008}.
+The formation of long-lived holes is recognized as a key requirement.\cite{Pesci2011} Besides, \ce{WO3} is remarkably stable in acid, making it a significant candidate for treating water pollutant caused by organic acids.\cite{Monllor-Satoca2006}
+
+\subsection{Advantages of Nano-Engineering}
 
@@
 
-Commercial buildings in U.S.
-consumed approximately 35\% of the electricity use.\footnote{U.S.
-Department of Energy, "Energy Efficiency Trends in Residential and Commercial Buildings", 2008.} And traditional windows in the buildings account for up to 40\% of the total heating, cooling and lighting consumption.
-The smart windows is an energy efficient solution by allowing for separate control of the visible and NIR illumination/transmission.
-
-\subsection{Electrochromism for Energy Saving}
-
-coloration efficiency, the doping amount,
-
-Electrochromic materials are a group of functional materials whose coloration status  can be reversibly switched using a finite durance of low DC voltage (\textless 5 V).
-Another important advantage of smart windows based on EC materials is the failure mode being clear instead of opaque compared to other techniques, e.g, liquid crystal, suspended particles.
-
-\subsection{Photocatalysis for Energy Harvesting}
-
-\subsection{Advantage of Nano-engineering}
-
 In comparison to oxides thin films, 1D TMO nanostructures (e.g., nanowires) have following advantages to improve the response speed and enhance the coloration efficiency: (1) With reduced diameters down to nanometer scale, the distance for ion diffusing into and out of the nanowires is significantly shortened.
@@
 
+\section{Objective and Scope}
+To fully harvest the advantages of these TMO and TMDC one-dimensional nanomaterials, a scalable growth method and a comprehensive understanding towards the growth-structure-property relation must first be established.
+Therefore, this dissertation primarily focuses on synthesis, growth mechanism study and characterization, and will only present preliminary results on device and applications.
+
 \section{Dissertation Outline}
-% what content should be presented
-
-The materials studied in this work/dissertation are tungsten oxides (\ce{WO3}), molybdenum oxides (\ce{MoO3}),and their chalcogenide counterparts (\ce{WS2} and \ce{MoS2}).
-
-This dissertation primarily focuses on growth and characterization, and will only present some preliminary tests on device and applications.
-Experimental tools for growth and characterization will be introduced in Chapter 2.
-Chapter 3 will be devoted to tungsten oxides (\ce{WO3}) and sodium tungsten oxides (\ce{Na5W14O44}) nanowires, where the role of sodium compounds in metallic tungsten precursors are thoroughly investigated.
-Chapter 4 will turn to molybdenum oxides (\ce{MoO3}) growth using alkaline metal compounds as catalysts.
-In Chapter 5, the growth of \gls{tmdc} and heterostructures will be discussed.
+The materials studied in this dissertation are tungsten oxides (\ce{WO3}), molybdenum oxides (\ce{MoO3}),and tungsten disulfide (\ce{WS2}).
+Experimental tools will be introduced in Chapter 2, including CVD apparatus and substrate treatments for growth, electron microscopes and optical spectrometers for characterization.
+Chapter 3 is devoted to tungsten oxides (\ce{WO3}) and sodium tungsten oxides (\ce{Na5W14O44}) nanowires, where the role of sodium in metallic tungsten precursors are thoroughly investigated; a potentially scalable growth method is also developed.
+Chapter 4 will turn to molybdenum oxide (\ce{MoO3}) growth using alkaline metal compounds as catalysts.
+In Chapter 5, a heterostructure based on \ce{WO3} \glspl{nw} is studied.
 Emphasis will be placed on the characterization of individual \ce{WO3}-\ce{WS2} core-shell \gls{nw}.
 The dissertation is then concluded with a summary and future work.
-
-\iffalse
-
-We have synthesized \gls{tmo} and \gls{tmdc} at nanoscale, measured their crystalline structures and optical properties and demonstrated some devices assembled using as-synthesized nanomaterials.
-We aim to illustrate that by nanoengineering these \gls{tmo} and \gls{tmdc}, enhanced performances over their bulk states could be expected and new properties will arise.
-In the remaining sections of this chapter, we will discuss some general perspectives of nanomaterials, the growth apparatus and characterization methods that apply to all experiments done in this work.
-Then chapter 2 will focus on growth of \ce{WO3} and its derivative.
-We employed thermal \gls{cvd} to synthesize \ce{WO3} \gls{nw}, and we investigated the role of impurity in tungsten metallic powders, during which we observed a new state of sodium tungsten oxides: \ce{Na5W14O44} nanowires.
-We also found a method to potentially obtain large yield of \ce{WO3} \gls{nw}.
-Chapter 3 will concentrate on \ce{MoO3}.
-We explored two different growth mechanism of \ce{MoO3}:\gls{vs} and \gls{vls}.
-We discovered that alkaline oxides can be used as catalyst to grow two distinct \ce{MoO3} morphologies: nanobelts and towers.
-We further demonstrated the application of as-synthesized \ce{MoO3} nanomaterials in electrochromic devices.
-In chapter 4 we discuss  We synthesized  and inspected the growth of \gls{fl} \ce{WS2}.
-Chapter 5 will conclude with an overall summary.
-
-\fi
-
-%\input{../end.tex} %  comment out when assembling

### 2014-09-27 ch-moox/moox.tex
outline adjusted 30%

@@
 % git version control added 012614
-\chapter{Molybdenum Oxides}
+\chapter{New Vapor-Solid-Solid Growth Modes of Molybdenum Oxide}
 
@@
 
-\section{Synthesis and Properties of Molybdenum Oxide}
+\subsection{Properties and Applications of Molybdenum Oxide}
 
 Molybdenum oxide (\ce{MoO3}) crystallizes in three phases, orthorhombic $\alpha$-\ce{MoO3}, monoclinic $\beta$-\ce{MoO3} and the metastable hexagonal h-\ce{MoO3}.\citep{Deb1968,Fibers2007} $\alpha$-\ce{MoO3} phase (hereafter \ce{MoO3}) exhibits anisotropic structure with strong bonding along [001] and [100] direction while van der Waals interaction along [010] direction.\cite{He2003} Due to this unique structure, \ce{MoO3} was found to have several important properties and a wide range of technological applications, such as electrochromism and photochromism,\cite{Yao1992} lubricants,\cite{Sheehan1996} photocatalysts,\cite{Chen2010} and gas sensor, including \ce{CO},\cite{Comini2005} \ce{NO2},\cite{Taurino2006} \ce{H2}\cite{Sha2009} and ethanol.\cite{Choopun} Moreover, other features arise when nanoscale \ce{MoO3} is specifically prepared, e.g., field emission.\citep{Li2002d,Zhou2003b}  As a layered hosting material, \ce{MoO3} can be further modified by intercalating with alkaline ions\citep{Spahr1995,Li2006b,Hu2011} and even divalent ion.\cite{Sian2005} This structural richness have enabled improved performance in Li-ion\cite{Mai2007} and sodium-ion battery.\cite{Hariharan2013} In combination with \ce{TiO2} forming a core-shell structure, these nanoparitcles are reported to lower the photon absorption energy of \ce{TiO2}.\cite{Elder2000} When combined with Ag as layered structure, transparent conducting behavior was observed.\cite{Nguyen2012} In addition, \ce{MoO3} is a good precursor for preparing other useful materials, such as \ce{MoS2} fullerene\cite{Li2003c} and few layer \ce{MoS2}.\cite{Lin2012} It will also be an important member of the van der Waals heterostructures.\cite{Geim2013}
-
-\subsection{Growth of Molybdenum Oxide}
-Researchers have been exploring a variety of methods to synthesized different \ce{MoO3} nanostructures.
-Only a brief introduction will be given here, since these efforts has been well documented in several review articles.\cite{He2003} Most of these methods can be categorized into two groups: solution-based hydrothermal procedures \citep{Li2002b,Xia2006,Li2006a,Camacho-Bragado2006} and chemical vapor transport and deposition approaches.\citep{Zeng1998,Li2002c,Li2002d,Zhou2003b,Fibers2007,Yan2009}.
-Both methods have its own merits.
-Hydrothermal process usually need lower temperature(\textless 300 \si{\degreeCelsius}), but the duration is usually long and requires several post-growth processing steps; whereas vapor deposition demands relatively high temperature (\textgreater 500 \si{\degreeCelsius}) yet with a shorter time.
-Both methods are scalable for industrial applications.
-However the hydrothermal treatment seems to allow more  nanostructures control than does the vapor deposition method.
-Nanobelts,\cite{Li2002b} helical nanosheets, nanoflowers, prims-like rods\cite{Li2006a} and nanoribbons\cite{Camacho-Bragado2006} were obtained by the former one while nanoflakes,\cite{Chen2009} nanobelts\cite{Hu2009} and nanowires\citep{Zhou2003b,Chen2011b} dominated the product morphology for the latter one.
-The assistance of Au catalyst in vapor deposition only altered the orientation\cite{Yan2009} or served as preferred nucleation sites\cite{Cai2011} without producing new \ce{MoO3} structures.
-\citeauthor{Chithambararaj2013} prepared hexagonal \ce{MoO3} nanocrystal via hydrothermal method and demonstrated the photodegradation of methylene blue (MB) under visible light.\cite{Chithambararaj2013} The efficiency dependence on catalysis/dye ratio, light intensity and temperature was studied.
-h-\ce{MoO3} was mostly synthesized using solution methods, where \ce{NH4+} and \ce{OH-} were possible structure directing and stable agents.
-The band gap of h-\ce{MoO3} estimated from diffusion reflection spectrum is $2.8\sim3.0$ eV.
-Hexagonal phase of \ce{MoO3} is readily identified by the XRD pattern (strong peak at $2\theta=20^{\circ}$).
-It is worth noting that in spite of these numerous growth of \ce{MoO3}, reports on catalytic growth are still scarce.
-
-\subsection{Lattice Structures of Molybdenum Oxide and Molybdates}
 
@@
 
-\subsection{Synthesis Methods in This Thesis}\label{sec:grow}
+\subsection{Synthesis Review of Molybdenum Oxide}
+Researchers have been exploring a variety of methods to synthesized different \ce{MoO3} nanostructures.
+Only a brief introduction will be given here, since these efforts has been well documented in several review articles.\cite{He2003} Most of these methods can be categorized into two groups: solution-based hydrothermal procedures \citep{Li2002b,Xia2006,Li2006a,Camacho-Bragado2006} and chemical vapor transport and deposition approaches.\citep{Zeng1998,Li2002c,Li2002d,Zhou2003b,Fibers2007,Yan2009}.
+Both methods have its own merits.
+Hydrothermal process usually need lower temperature(\textless 300 \si{\degreeCelsius}), but the duration is usually long and requires several post-growth processing steps; whereas vapor deposition demands relatively high temperature (\textgreater 500 \si{\degreeCelsius}) yet with a shorter time.
+Both methods are scalable for industrial applications.
+However the hydrothermal treatment seems to allow more  nanostructures control than does the vapor deposition method.
+Nanobelts,\cite{Li2002b} helical nanosheets, nanoflowers, prims-like rods\cite{Li2006a} and nanoribbons\cite{Camacho-Bragado2006} were obtained by the former one while nanoflakes,\cite{Chen2009} nanobelts\cite{Hu2009} and nanowires\citep{Zhou2003b,Chen2011b} dominated the product morphology for the latter one.
+The assistance of Au catalyst in vapor deposition only altered the orientation\cite{Yan2009} or served as preferred nucleation sites\cite{Cai2011} without producing new \ce{MoO3} structures.
+\citeauthor{Chithambararaj2013} prepared hexagonal \ce{MoO3} nanocrystal via hydrothermal method and demonstrated the photodegradation of methylene blue (MB) under visible light.\cite{Chithambararaj2013} The efficiency dependence on catalysis/dye ratio, light intensity and temperature was studied.
+h-\ce{MoO3} was mostly synthesized using solution methods, where \ce{NH4+} and \ce{OH-} were possible structure directing and stable agents.
+The band gap of h-\ce{MoO3} estimated from diffusion reflection spectrum is $2.8\sim3.0$ eV.
+Hexagonal phase of \ce{MoO3} is readily identified by the XRD pattern (strong peak at $2\theta=20^{\circ}$).
+It is worth noting that in spite of these numerous growth of \ce{MoO3}, reports on catalytic growth are still scarce.
+
+\section{Experimental}\label{sec:grow}
 
@@
 Then the catalytic growth mechanism was investigated using \ce{NaOH} treated Si substrate.
-\subsection{Growth on Si Substrate}\label{sec:nonsi}
+\subsection{Non-catalyst Growth}\label{sec:nonsi}
 
@@
 
-\subsection{Growth on NaOH-Si Substrate}\label{sec:naohsi}
+\subsection{Catalyst-assisted Growth}\label{sec:naohsi}
 
@@
 
-\subsection{Verification of Growth Model}
-
 The transport of molybdates in proposed growth model is verified by a side-by-side experiment, as schematically depicted in Fig.~\ref{fig:ch4sbs}a.
@@
 
-\section{Extension of Alkaline Metal Catalyzed Growth}
 \subsection{Growth on Alkaline Metal Containing Substrate}
@@
 
-\subsection{Liquid Exfoliation of Molybdenum Oxide}
+\subsection{Optical Properties of Molybdenum Oxide}
 

### 2014-09-27 ch-tms/tms.tex
outline adjusted 30%

@@
-\chapter{Transition metal dichalcogenides}
+\chapter{Tungsten Oxide-Tungsten Disulfide Heterostructure}
 
@@
 
-\section{Results and Discussion}
-
-\subsection{synthesis Method in This Work}
+\section{Experimental}
 
@@
 
-\subsection{Characterizations}
-
-\subsubsection{Optimization of W powder Oxidization}\label{sec:woxd}
-
-Understanding the oxidation of tungsten powder is the key to obtain high yield in seeded growth.
-Oxidation of tungsten have been investigated under diverse conditions, such as at elevated temperature (\textgreater 1100 \si{\degreeCelsius} ) and oxygen pressure on the order of Torr,\cite{Base1965} and at temperatures ranging from 20 to 500 \si{\degreeCelsius} under atmosphere pressure.\cite{Warren1996} \ce{WO_x} NWs were readily found when tungsten (foil, wire, or powder) is oxidized under various conditions.\cite{Zhu1999,Karuppanan2007,Hsieh2010} However the study on tungsten powder oxidation behavior between intermediate temperature range and under low pressure is still rare.
-This work studied the oxidation of tungsten powders with diverse size within temperature range from 500 to 1000 \si{\degreeCelsius} and under several mTorr oxygen partial pressure.
-Using tungsten powder as seed, the author further illustrate an economic approach to obtain large yield of \ce{WO3} nanowires at relatively lower temperature than previous efforts.
-It is demonstrated that there is an optimal tungsten powder size under our experimental conditions for seeded growth.
-This will provide some insight on the role of tungsten powder as source material in CVD growth of \ce{WO_x}.
-
-Commercial available tungsten powders with different size are usually associated with purity variation as well, as already listed in Table.~\ref{tab:ch5pre}.
-The dimensions of tungsten powder were obtained by measuring the average size in SEM graphs.
-A systematic investigation was performed on the oxidation behavior of tungsten powder to evaluate the temperature effect, size-dependence and influence of oxygen partial pressure.
-% seed optimal
-\begin{figure}[htb]
-\centering
-\includegraphics[width=0.6\textwidth]{JAP-2column_Fig1.jpg}
-\caption[W powder oxidation: temperature effect]{SEM graphs of 99.9\% (3N) tungsten powder oxidization at different temperatures of a) 500 \si{\degreeCelsius}, b) 600 \si{\degreeCelsius}, c) 650 \si{\degreeCelsius}, d) 750 \si{\degreeCelsius}, showing the optimal temperature for local formation of nanowires is between 600--650 \si{\degreeCelsius}.
-Oxygen flow rate is 1 sccm.}
-\label{fig:pdtemp}
-\end{figure}
-
-Fig.~\ref{fig:pdtemp} illustrated the effect of temperature on the morphological change and surface nanowires formation of 3N powder.
-At 500 \si{\degreeCelsius}, most tungsten powder retained its original shape and a layer of tiny dense NWs begun to grow.
-When temperature was increased to 600 \si{\degreeCelsius}, 3N powder started to crack with longer NWs on the isolated surface.
-Further increase of temperature lead to irregular shapes of tungsten power and aggregation of NWs, giving rise to the nanorods and bunched or bundled structures.
-It could be determined from the morphology variation that the optimal seeded growth temperature for 3N powder was in the range of 600 to 650 \si{\degreeCelsius}.
-% seed optimal
-\begin{figure}[htb]
-\centering
-\includegraphics[width=0.6\textwidth]{JAP-2column_Fig3.jpg}
-\caption[W powder oxidation: size effect]{SEM graphs illustrating the oxidization of four different size of tungsten powders at 600~\si{\degreeCelsius} and 1 sccm oxygen flow.
-a) 17 $\mu m$, b) 32 $\mu m$, c) 3.3 $\mu m$, d) 1.5 $\mu m$.}
-\label{fig:pdsize}
-\end{figure}
-
-Fig.~\ref{fig:pdsize} depicted the oxidation of different sizes of tungsten powder under the same experimental conditions.
-In contrast to the morphology of 3N powder shown in Fig.~\ref{fig:pdtemp}, 3N5 powder surface is primarily covered with sub-micro particles as well as some short tiny NWs, whereas 4N5 and 5N powder were thoroughly oxidized, showing branched flowers feature.
-This dramatic difference could be explained in terms of surface energy and oxygen diffusion.
-With smaller dimension, the increased surface-to-volume ratio and short diffusion path both lower the energy barrier of oxidation.\cite{tungsten1999} It was logical to deduce that higher temperature or increased oxygen level might favor the NWs formation on 3N5 powder.
-When it comes to seeded growth, however, the powder size distribution was an important factor to give uniform NWs deposition.
-Since the size distribution of 3N powder is more uniform than that of 3N5 powder, the author employed the former as seeds.
-% seed optimal
-\begin{figure}[htb]
-\centering
-\includegraphics[width=0.6\textwidth]{JAP-2column_Fig2.jpg}
-\caption[W powder oxidation: oxygen pressure]{SEM graphs of 3N tungsten powder oxidization at 600 \si{\degreeCelsius} under different rates of oxygen flow: a) 1 sccm, b) 2 sccm, c) 3 sccm, d) 10 sccm.
-The oxygen partial pressures were 13 mTorr, 23 mTorr, 32 mTorr, and 82 mTorr, respectively with background pressure subtracted.}
-\label{fig:pdoxy}
-\end{figure}
-
-Fig.~\ref{fig:pdoxy} depicted the morphology change of 3N powder with respect to varied oxygen partial pressure.
-When the oxygen flow is lower than 3 sccm, 3N powder almost stayed as the same, with cracks separating the dense layer of NWs.
-When oxygen flow is increased to 10 sccm, the 3N powder exemplified an enlarged version of that for 4N5 or 5N powder under 1 sccm oxygen flow.
-This observation again supported the surface energy explanation.
-
-\subsubsection{Seeded Growth of Tungsten Oxide NWs}
-With the oxidation experiments study in Sec.~\ref{sec:woxd}, favorable conditions for local growth of NWs were extracted to perform seeded growth.
-
-\begin{figure}[htb]
-\centering
-\subfloat[]{\label{fig:sga}\includegraphics[width=0.4\textwidth]{wox_sg_a.jpg}}\hspace{0.04\textwidth}
-\subfloat[]{\label{fig:sgb}\includegraphics[width=0.4\textwidth]{wox_sg_b.jpg}}
-\caption[Characterization of seeded growth \ce{WO3}: SEM]{Characterizations of seeded growth.
-(a) SEM graphs of \ce{WO3} NWs on \ce{SiO2/Si} substrate.
-(b) A high magnification view showing uniform NW growth and close-up view of one NW.
-}
-\label{fig:woseedsem}
-\end{figure}
-
-As shown in Fig.~\ref{fig:sgb}, dense NWs array was obtained on tungsten powder seeds with individual wires of length up to 5 $\mu$m and diameter about 50 to 200 nm, according to the estimation made in the close-up view.
-Each tungsten powder stood as independent growth site (Fig.~\ref{fig:sga}) with island-layer growth on the substrates, a common feature without using tungsten powder as seed under current experimental conditions.
-It was occasionally observed that NWs growth was initiated adjacent some tungsten powders.
-This phenomenon was correlated to the local trap of vapor flow since it was more often found among the enclosed area by tungsten powders.
-It is also found that the diameter of NWs decrease as the distance between powders and upstream edge increases.
-This is a combination effect of lower temperature and reduced \ce{WOx} growth species supply.
-Similar phenomena were observed in other studies.
-\citeauthor{Thangala2007} reported that a decrease in NW density with increasing substrate temperature, and an increase of NW density with increasing partial pressure of oxygen.\cite{Thangala2007}
-
-% seeded edx 
-\begin{figure}[htb]
-\centering
-\includegraphics[width=0.5\textwidth]{wo3_seed_edx}
-\caption[Composition analysis on seeded growth \ce{WO3} NWs]{EDX spectroscopy on seeded growth \ce{WO3} NWs.}
-\label{fig:woedx}
-\end{figure}
-Energy-dispersive X-ray spectroscopy (EDX) analysis on the seeded growth \ce{WO3} NWs is shown in Fig.~\ref{fig:woedx}.
-Only W and O elements were detected on the NW array.
-The background level from 3 to 8 keV was a manifestation of the continuous components of W X-ray spectrum.
-
-% sg raman xrd
-\begin{figure}[htb]
-\centering
-\subfloat[]{\label{fig:sgxrd}\includegraphics[width=0.45\textwidth]{xrd_cs_before}}\hspace{0.04\textwidth}
-\subfloat[]{\label{fig:sgram}\includegraphics[width=0.45\textwidth]{wox_raman_1}}
-\caption[Characterization of seeded growth \ce{WO3}: XRD and Raman]{ (a) XRD pattern of as-prepared sample indicating the \ce{WO3} phase and the presence of metallic core.
-(b) Raman spectrum on NWs region showing the feature of \ce{WO3}.}
-\label{fig:woseedxrd}
-\end{figure}
-
-Fig.~\ref{fig:sgxrd} is the XRD spectrum of one typical sample.
-The peaks under circular symbol were identified to be the monoclinic \ce{WO3} phase (ICDD PDF 01-083-0950, \emph{a}=7.30084 \AA, \emph{b}=7.53889 \AA, \emph{c}=7.6896 \AA, $\beta$=90.89$^\circ$), while the peak under the triangular symbol was indexed to cubic tungsten phase (ICDD PDF 04-16-3405, \emph{a}=3.157 \AA), in agreement with the EDX analysis (Fig.~\ref{fig:woedx}).
-This means that during the \ce{WO3} seeded growth of 4 h heating at 1000 \si{\degreeCelsius}, the tungsten powder in downstream low temperature region (600 -- 700 \si{\degreeCelsius}) is not entirely oxidized.
-Micro-Raman scattering spectroscopy was performed on the as-synthesized sample as well.
-During Raman examination, the laser spot was carefully focused onto the NWs on powders and several inspections on different positions were observed to ensure the reproductivity of spectra data.
-As shown in Fig.~\ref{fig:sgram}, five distinct bands were well resolved, with peaks located at 131, 265, 327, 711 and 803 \si{cm^{-1}}, respectively.
-This pattern was typical features of \ce{WO3}, consistent with previous study.\cite{Salje1975a,Dixit1986} The high background level probably arises from the metallic core.
-
-% sg tem
-\begin{figure}[htb]
-\centering
-\includegraphics[width=0.9\textwidth]{JAP-2column_Fig5major.jpg}
-\caption[Characterization of \ce{WO3}: TEM]{TEM graphs of as-prepared NWs.
-(a) TEM image of one nanowire with diameter about 40 nm.
-(b) HRTEM images showing the spacing is 0.38 nm, corresponding to (002) plane distance.}
-\label{fig:woseedtem1}
-\end{figure}
-
-TEM specimen was prepared by using carbon grid to slightly scratch the as-grown sample.
-Fig.~\ref{fig:woseedtem1} shows the feature of majority NWs.
-The growth direction is determined to be perpendicular to (002) plane.
-The streaking in SEAD pattern presumably arises from stacking defaults.
-The author also find some NWs exhibit high crystalline quality, as revealed by the TEM analysis in Fig.~\ref{fig:woseedtem2}.
-The NW grew normal to (002) plane with a measured lattice spacing of 3.79 \AA, which is favorably compared to the XRD peak at $23.07^\circ$ (7.7103 \AA).
-The sharp SEAD pattern and clear phase contrast in HRTEM demonstrated are both strong evidence of good crystallinity.
-This formation indicated current growth parameters have promising potential to obtain highly crystalline \ce{WO3} NWs in large scale.
-
-% sg tem
-\begin{figure}[htb]
-\centering
-\includegraphics[width=0.9\textwidth]{JAP-2column_Fig5minor.jpg}
-\caption[Characterization of \ce{WO3}: TEM cont]{TEM graphs of as-prepared NWs.
-(a) TEM image of one nanowire, the diameter is about 70 nm.
-(b) HRTEM images showing the spacing is 0.379 nm, corresponding to (002) plane distance.}
-\label{fig:woseedtem2}
-\end{figure}
-
-In regarding to the formation of NWs on tungsten powder itself, this study assumes the driving force is related to interfacial strain between W and \ce{WOx}.
-Oxidation of tungsten proceed slowly at room temperature and an oxide layer of 100 \AA was found on the surface of tungsten foils.\cite{Warren1996} The tungsten powder used in current study would be covered by a thin oxide layer as well.
-During oxidation, different oxidation rates exist for different crystallographic orientations on the tungsten powder.
-Oxidation occurring at boundaries and defects are preferred thermodynamically.\cite{You2010} Compressive strain will gradually accumulate at the tungsten oxide/tungsten interface, which might limit the diffusion rate of oxygen at temperature lower than 500 \si{\degreeCelsius}.\cite{tungsten1999} At elevated temperature, cracks will primarily occur, as observed in Fig.~\ref{fig:pdtemp}.
-When heated up, tungsten and the oxide shell will probably relax the strain by converting into substoichiometric NWs, a similar process as suggested by \citeauthor{Klinke2005} in the chemically induced strain growth of tungsten oxide NWs.\cite{Klinke2005} It is worth noting that tungsten oxide nanowires could also formed when \ce{WO3} is reduced.\cite{Sarin1975} The elongation of \ce{WOx} is thermodynamically favorable during the conversion from metallic tungsten to tungsten oxide as well.
-Local evaporation-condensation process might also contribute to the formation of NWs on tungsten powder.
-
-The enhanced yield of NWs obtained via seeded growth could be explained by a vapor-solid (VS) mechanism.
-External supply of growth species will condense onto the powders and substrate simultaneously, promoting the elongation of NWs on power as well as resulting island-layer growth on substrate.
-The local NW density in oxidation experiment was much higher than that of seeded growth.
-It is reasonable to presume that during seeded growth, several NWs in a small region on powder will coalescence, as evidenced by the bundled structures.
-At last, the author would like to point out that when low purity tungsten powder (3N) was used as source, sodium tungsten oxide nanowires were found to be dominant in the final product.
-The details have been published.\cite{Sheng2014} It seems surprising that when 3N powder was used as seeds, only \ce{WO3} nanowires were obtained.
-This result was attributed to the lower temperature and significantly reduced amount of 3N powder used in the seeded growth, compared with the conditions used in Ref.\cite{Sheng2014}.
-The source material in seeded growth is not limited to high purity tungsten powder.
-Instead, any material that could produce appropriate growth vapor could be employed, indicating the versatility of this approach.
-\subsubsection{Ensemble Measurements on Core-Shell NWs}
+\section{Results and Discussion}
+\subsection{Ensemble Measurements on Core-Shell NWs Array}
 
@@
 
-\subsection{TEM-Raman Integrated Study}\label{tms:raman}
+\subsection{TEM-Raman Integrated Study on Individual NW}\label{tms:raman}
 
@@
 \section{Summary}
-
-\iffalse
-
-%\section{literature to read}
-
-The geometrical symmetry groups of WS2 NT.\cite{Milosevic2000} 
-The basis/lattice vectors $a_1$ and $a_2$ are defined in transition metal plane with equal length $a_0 \approx 3$ \AA.
-This monolayered sheet can be rolled up to form a tubular structure when the chiral/translation vector $c = n_1a_1 + n_2a_2$ becomes the circumference of the tube.
-The diameter of a nanotube is given by
-\begin{equation}
-d = \frac{\mid c \mid}{\pi} = \frac{a_0}{\pi}\sqrt{n_1^2 + n_1n_2 + n_2^2}
-\end{equation}
-Notice $a_1 \cdot a_2 = a_1a_2 \cos\pi/3$, where the cosine times 2 is unit. 
-In analog with carbon nanotube, chiral angle $\theta$ is given by
-\begin{equation}
-\theta = \tan^{-1}\frac{\sqrt{3}n_2}{2n_1 + n_2}
-\end{equation}
-
-Chiral angles from the interval $[0,pi/6]$ is sufficient for all possible tubes.
-Tubes $(n,0)$ with zero chiral angle are named zigzag, tubes $(n,n)$ with $\pi/6$ chiral angle are armchair, whereas all others are referred as chiral ones with $\theta \in (0,pi/6)$.
-
-hydrogen evolution catalysts. \cite{Merki2011}
-
-Raman substrate dependence \cite{Buscema2013}
-
-stability of TMS NTs \cite{Seifert2002}
-
-2H and 1T in \ce{MoS2} \cite{Eda2012}
-
-\ce{MoS2} FET statistical study. \cite{Liu2013i}
-
-water splitting review. \cite{B800489G}
-
-\ce{WS2} theory and experimental combined study. \cite{Klein2001}
-
-2D review on oxides \cite{Osada2012}
-
-Pb catalyzed \ce{MoS2} nanotube \cite{Brontvein2012}
-
-\ce{WS2} Raman.\cite{Zhao2013} \cite{Sekine1980}
-
-phonon dispersion $E_{2g}^1(M)$? \cite{Ataca2012}
-
-MoS2 optical properties.\cite{Search1979}
-
-FL heterostructure. \cite{Yu2013a}
-
-\cite{Kang2013} TMDC alloy DFT.
-
-thermoelectric TMDC \cite{Wickramaratne2014}
-
-\ce{CH4N2S} thiourea + \ce{WOx} to \ce{WS2} \cite{Leonard-Deepak2011}
-
-\ce{WS2} by \ce{WCl_n} and \ce{H2S}, raman (632nm) show bulk features\cite{Tenne2008}.
-
-direct gap of ML at corner of BZ, point K.
-
-\begin{align}
-\cee{WCl6 + S &\rightarrow WS2 + Cl2S2}\\
-\cee{MoCl5 + S &\rightarrow MoS2 + S2Cl2} \\
-\cee{S2Cl2 + NaOH &\rightarrow NaCl + S + Na2SO3 + H2O}
-\end{align}
-
-%\section{literature read}
-
-CNT chirality by TEM \cite{Zhang1993} TEM chirality of \ce{MoS2} NTs
-
-first demonstration of \ce{WS2} NT n-type FET. \cite{Levi2013}
-the importance of contact, and avoiding moisture.
-
-The calculated carrier concentration is about $10^{19}cm^{-3}$, a highly doped semiconductor, possibibly arising from sulfur vacancy.
-
-\ce{WS2} NT transport \cite{Zhang2012c}
-less grain boundary more mobility,
-
-\citeauthor{Ramasubramaniam2011} investigated the band gap tuning in bilayer TMDC materials by applying external $E$ field.
-Similar research has been done for graphene and bilayer boron nitride.
-Semiconductor-metal transition was suggested for \ce{MoS2} and \ce{WS2}, with difference on the CBM and VBM evolution.
-In \ce{MoS2}, the valence-band-splitting cause the A and B excitons in optical absorption measurement.
-Calculation shows that CB and VB are translated toward the Fermi level with increasing E field.
-The external field localized charge along $c$ axis, but delocalized that within the plane normal towards $c$, thereby driving the semi-metal transition.
-It was mentioned that this transition is not anticipated in monolayer \ce{MoS2}.
-It was emphasized that precise band gaps might be different from the author’s results, yet the gap-tuning should be universal.\cite{Ramasubramaniam2011}
-
-\cite{Song2013} \ce{WO3} by ALD, and sulfurized in Ar and \ce{H2S} (10:1) at 1000 C.
-\ce{WS2} layer No and peak intensities ratio under 633nm excitation is correlated.
-It was found the 2LA/A1g is less than 1 for 1L.
-In supporting info 532 nm Raman spectra, the 2LA/A1g is presumably larger than 1 for 1L.
-\ce{WS2} NT on Si NWs is also demonstrated.
-
-\cite{Tenne2010} chemical modification of NTs.
-Functional ligand consists of an anchor group that attaches to the NTs surface and a tail which render them soluble in various solvents.
-PTAS functionalized BN nanotube lead to the formation of stable suspensions in aqueous solutions.
-The strong attachment is formed through $\pi-\pi$ interactions.
-
-inorganic nanotubes review \cite{Tenne2004} , unsaturated bonds number increases as the size of MS2 sheet decreases.
-
-Water splitting materials should process a band gap larger than 1.4eV, considering both the NHE potential distance and practical application.
-The monolayer \ce{WS2} exhibits direct gap of 1.98 eV.
-Quantum confinement could push the gap separation farther away.
-\cite{wilcoxon1997} \citeauthor{Notley2013} use liquid exfoliation to prepare \ce{WS2} NPs.\cite{Notley2013} Non-ionic surfactant concentration is about 0.1\%w/w.
-Continuously adding surfactant during sonication improves the yield.
-Optimum surface tension is found at about 40 mJ/m$^2$.
-
-G/\ce{WS2}/G stacked solar cell. For lubricant, and surface protection. Absorption $\sim 10^7 m^{-1}$. \cite{Britnell2013}
-
-In Ref\cite{Zeng2013}, single crystal \ce{WS2} growth using \ce{I2} transport was described in supporting info.
-\ce{C24H12K4O8}\footnote{http://www.chemspider.com/Chemical-Structure.24771386.html}
-
-416 peak was prevously assumed to be a combination of LA and TA phonons at K points.
-
-Raman conditions: 0.3 mW, 532 nm, 200 sec acquisition time. photon flux = $0.3E-3\times6.242E+18/1.2398/0.532=2.84E15$
-
-416 cm raman on WS2. B1u is pressure sensitive. \cite{Staiger2012} also studied pressure dependence.
-
-A1g mode using resonance Raman excitation shows upshift, which is presumably caused by folding induced strains.
-And TEM SAED reveal 3R symmetry.
-We did not observed this upshift of A1g probably due to the large diameter and few layer involved.
-
-Nanotube growth is relatively independent of substrates and FL layer is closely related to substrate. Film growth could provide some insight into the latter scenario.
-
-\fi

### 2014-09-27 ch-tms/tmspart.tex
outline adjusted 30%

@@
 \section{Introduction}
-% \subsection{crystal structure of tmdc}
-\subsection{Growth of TMDC}
+\subsection{Synthesis Review of TMDCs}
 Shortly after the discovery of carbon nanotube (CNT) in 1991,\cite{Iijima1991} its transition metal dichalcogenides (TMDC) counterparts, i.e., \ce{WS2}, was synthesized in 1992.\cite{Tenne1992} In the following decades, other TMDC and several metal oxides nanotubes were demonstrated as well.
@@
 
-\subsection{Raman on Bulk and FL TMDC}
+\subsection{Raman on Bulk and FL TMDCs}
 

### 2014-09-27 ch-wox/part1.tex
outline adjusted 30%

@@
 Besides smart window based on EC effect, \ce{WO_x} is also well investigated for several other significant applications: photoelectrochemical cell for solar energy conversion and storage, photocatalysis for hydrogen evolution reaction, chemical and biological sensing based on gasochromic effect.
-In addition, a few young fields are not thoroughly explored: field emission, optical storage, thermoelectrcity, ferroelectricity, and superconductivity.
+In addition, a few young fields are not thoroughly explored: field emission, optical storage, thermo-electricity, ferro-electricity, and superconductivity.
 
@@
 
-\subsection{Rich and useful technological appeals}
+\subsection{Applications of Tungsten Oxides and Sodium Tungsten Oxides}
 
@@
 
-Photocatalytic activity occurs when a semiconductor in aqueous solution is illuminated by photons of energy larger than the bandgap, then electron-hole pairs generate free radicals, i.e., \ce{OH.}, which enable further reactions.
-For water splitting using solar energy, the band gap should be within $2.0 \sim 3.0 $ eV, and CB edge should be more negative than reduction potential of \ce{H^+/H2}, whereas the VB top should be more positive than the oxidation potential of \ce{H2O}/\ce{O2}.\cite{Wang2012} The valence band holes (\ce{h^+}) oxidize water to oxygen and conduction band electrons propel hydrogen generation, as depicted in Eq.~\ref{eq:h2o}.
-\begin{subequations}\label{eq:h2o}
-\begin{align}
-4\ce{h^+} +  \ce{H2O} &\rightarrow \ce{O2} + 4\ce{H^+} \label{eq:hervb}\\
-4\ce{H^+} +  4e^- &\rightarrow 2\ce{H2} \label{eq:hercb}
-\end{align}
-\end{subequations}
-As shown in Fig.~\ref{fig:woxnhe}, \ce{WO3} has \gls{cb} edge positioned slightly more positive than reduction potential of \ce{H^+/H2}(versus \gls{nhe}), and \gls{vb} edge much more positive than the oxidation potential of \ce{H2O}/\ce{O2}.
-So the photo-cleavage of water cannot be accomplished by \ce{WO3} alone.
-Nevertheless, a tandem cell approach by \ce{WO3} film and dye-sensitized \ce{TiO2} has been demonstrated with an efficiency of 4.5\%.\cite{Michael1999} It is worth noting that green plants also have two photosynthetic systems connected in series, one for oxidation of water into oxygen and the other for fixation of carbon dioxide.
-% wo3 vs NHE
-\begin{figure}[htb]
-\centering
-\includegraphics[width=0.7\textwidth]{woxnhe.jpg}
-\caption[Bands positions of \ce{WO3} versus NHE]{Bands positions of \ce{WO3} in contact with aqueous electolyte at pH 1, adapted from Ref.\cite{Gratzel2001}}
-\label{fig:woxnhe}
-\end{figure}
-Moreover, favorable oxygen evolution of \ce{WO3} brings good performance in degradation of organic compounds\cite{Hepel2001,Luo2001,Watcharenwong2008}.
-The formation of long-lived holes is recognized as a key requirement.\cite{Pesci2011} Besides, \ce{WO3} is remarkably stable in acid, making it a significant candidate for treating water pollutant caused by organic acids.\cite{Monllor-Satoca2006}
-
-\subsection{Crystal structures and properties of tungsten oxides and sodium tungsten oxides}\label{sec:wonawo}
+\subsection{Properties of Tungsten Oxides and Sodium Tungsten Oxides}\label{sec:wonawo}
 
@@
 
-\subsection{Synthesis strategies}\label{sec:woxgrowth}
+\subsection{Review of Synthesis Methods}\label{sec:woxgrowth}
 

### 2014-09-27 main.tex
ch2 enhanced
ch2 and appendix update
training instruction added
wox and moox proofreading
outline adjusted 30%

--- 2014-08-01 main.tex
@@
 \documentclass[12pt,oneside]{book}
- %
    \usepackage{uncc-thesis} % uncc format specification seems this style should be loaded before other packages
-
    \input{package_iff.tex} % additonal packages and tweaking
    \input{./FrontMatter/abbre}
-
    \makeglossaries
-
 \begin{document}
-
-%       \input{./FrontMatter/FrontMatter}
-
-% \include{./ch-intro/ch-intro}
- \include{./ch-intro/ch-instr}
+    \input{./FrontMatter/FrontMatter}
+    \include{./ch-intro/ch-intro}
+    %\include{./ch-intro/ch-instr}
    % \include{./ch-wox/ch-wox}
-  \include{./ch-moox/moox} % no tex needed, otherwise there is error
+   % \include{./ch-moox/moox} % no tex needed, otherwise there is error
    % \include{./ch-tms/tms}
 \appendix
-   %\glsaddallunused
-%    \include{./BackMatter/app1}
-%     \include{./BackMatter/app2}
+  % \glsaddallunused
+    \include{./BackMatter/app1}
+   %\include{./BackMatter/app2}
+   %\include{./BackMatter/app_training}
+   % \include{./BackMatter/app-tms}
 %   \include{./BackMatter/paper}
@@
 \end{document}
-
-Both tungsten (W) and molybdenum (Mo) belong to Group VIB transition metal, with outer shell electrons configuration as $4d^55s^1$ and $5d^46s^2$, respectively.
-Therefore we refer their oxides and chalcogenides as \gls{tmo} and \gls{tmdc}.\footnote{Obviously transition metals include many other elements, all of which have partially filled $d$-electron shell.
-But here we use TM to denote W and Mo exclusively.}
-
-Nucleation is a process of generating a new phase from a metastable old phase, where the Gibbs energy per molecule of the bulk of the emerging new phase is less than that of the old phase.
-
-General CVD knowledge, substrate preparation, and\cite{MichealK.Zuraw2003}
-
-\section{Crystal Structures and Electronic Properties}
-
-Solid and orderliness.
-
-Two theories arise to describe the outer shell electrons and to correlate the structure and physical properties: \gls{cft} and band theory.\cite{Goodenough1971} \gls{cft} assumes weak interaction between neighboring atoms and localization of electron towards parent atom, whereas band theory assumes that electron is shared equally by all nuclei and therefore a many-electron problems follows.
-Description of a single electron in periodic potential fail to treat the electron correlations adequately, as the interaction between atoms becomes weaker.For transition metals, $s$ and $p$ electrons are well described by a collective-electron model, while the 4f or 5f electrons are tightly bound to nuclei and screened from the neighboring atoms by 5s, 5p or 6s, 6p core electrons, hence it matches well with a localized-electron model.
-d electrons show intermediate character.
-
-In vapor synthesis process, two growth mechanism exists: VS and VLS.
-VS process is widely accepted for the growth of \ce{MoO3}.
-Yet we caution that synthesis conditions should be scrutinized to determine the exact mechanism.
-\citeauthor{Li2002c} suggested a VS mechanism at 700 \si{\degreeCelsius} and VLS at 750 \si{\degreeCelsius} and higher.\cite{Li2002c} \citeauthor{Fibers2007} proposed a modified VS mechanism probably because the deposition occurs on \ce{Al2SiO5} with possible \ce{Al_{0.95}SiNa_{0.06}O_x} involved.
-Therefore temperature and possible impurity could potentially alter the growth mechanism.
-We divide the growth results into two categories: on Si substrate and on non-Si substrate, and describe them respectively.
-We also briefly mention using liquid exfoliation to prepare few layer \ce{MoO3}.
-
-This rectangular shape implies the boundary plane along growth direction (long axis) is (001), in consistency with previous experimental reports\cite{Zeng1998,Li2002b} and theoretical studies.\cite{Firment1983,Cora1997} We also observed different shapes, i.e., elongated hexagonal using similar growth conditions.
-This is not an indication of different growth mode.
-It is a normal thermodynamic fluctuation.
-The growth rates along different crystalline direction of \ce{MoO3} are determined by the free surface energy.
-In fact, (201), (101) and (102) planes have all been observed as terminating planes.\cite{Zeng1998} The stacking rate of \ce{MoO6} octahedra along $a$ and $c$ axis could develop some other ratio.
-And the coexistence of different planes in one growth suggests the similarity of free surface energies between these surfaces.
-In other words, the migration barrier of adatoms on (010) plane is presumably much lower than that on other low index planes due to the Van der Waals interaction nature along [010] direction.
-
-\citeauthor{Wang2013c} changed the NW growth direction by changing the shape of droplets; \citeauthor{Biswas2013} reported enhanced aspect ratio of Ge NWs from bimetallic alloy.
-
-We first repeated the previous growth on ITO/glass, and then found similar deposition phenomena on glass and mica substrates.
-We suspected that the morphology difference on the substrates employed in this study arises from the compositions difference.
-Both mica and glass contains alkaline elements which are absent in Si and \ce{SiO2}/Si substrates.
-We primarily verify this hypothesis by utilizing \ce{NaOH} treated Si substrates and found that the overall morphology almost reproduces that on ITO and mica substrates.
-We then propose a new growth mechanism based on the VLS process to explain the deposition of \ce{MoO3} on alkaline-ions-containing substrates.
-
-ITO versus NaOH images.
-
-According to the phase diagram shown in Fig.~\ref{fig:pd}, \ce{Na2MoO4} - \ce{MoO3} phase above 800 \si{\degreeCelsius} are \ce{Na2MoO4}(l) + \ce{MoO3}(l), More discussion should follow $\ldots$.
-
-\subsubsection{Phase evolution probing by Raman}
-
-\citeauthor{Hardcastle1990} summarized an empirical formula to relate the Raman peaks and \ce{Mo-O} bonding lengths.\cite{Hardcastle1990} This correlation assumes general form as
-\begin{equation}\label{eq:mobond}
-\nu = A \exp{B\cdot R},
-\end{equation}
-where $A=32895$ and $B=-2.073$ are fitting parameters, R is bond distance in unit of \AA.
-Given a stretching frequency, the resolution for calculated bond distance is $\pm0.016$ \AA.
-Another empirical expression connect the bond valence $s$ and bond distance R: $s(M-O) \approx (R/X)^{-6} $, where X=1.882 when M is Mo, and 1.904 when M is W.
-The valence sum rule could be then used to check the state of Mo cation.
-It should be noticed that not all observed Raman lines could be correlated to a \ce{Mo-O} bond distance by extrapolation of Eq.~\ref{eq:mobond}.
-It is then regarded as a symmetry related vibrational mode, i.e.
-820 \si{cm^{-1} in \ce{MoO3}.
-From the correlation of various Mo compounds, a general conclusion is the lower the stretching frequency for the shortest metal-oxygen bond, the more regular is the structure.
-
-% droplet position statistics
-\begin{figure}[htb]
-\centering
-\includegraphics[width=0.6\textwidth]{droplets_sta}
-\caption[Droplet position statistics]{Droplet position statistics. On-tip and not-on-tip counts variation with respect to growth time. }
-\label{fig:mo3dropsta}
-\end{figure}

### 2014-09-28 BackMatter/app2.tex
initial review version 0.1
outline adjusted 50%

@@
 Knudsen equation is 
-\[
-J = ($\alpha$)3.51\times10^{22}\frac{P_{torr}}{\sqrt{MT}},
-\]
+$$
+J = \alpha3.51\times10^{22}\frac{P_{torr}}{\sqrt{MT}},
+$$
 Condensation rate $J(\text{atoms}/\text{cm}^2 \text{sec})$, M in grams/mol. 
@@
 Mean free path of gas in vacuum:
-\[
+$$
 \lambda_p = \frac{5\times10^{-3}}{P} \approx 0.05,
-\]
+$$
 where $\lambda_p$ is in centimeter, and P is pressure in Torr. Gas impingement flux $\Phi$, is a measure of the frequency with which gas molecules impinge on or collide with a surface.
-\[
+$$
 \Phi = 3.513\times10^{22}\frac{P}{\sqrt{M T}},
-\]
+$$
+
 Gas flow could be divided into three regimes: molecular flow, intermediate flow and viscous flow.
 Knudsen number is
-\[
+$$
 K_n = D/\lambda_p \approx 50,
-\]
+$$
 where D is characteristic dimension of the CVD system.

### 2014-09-28 ch-intro/ch-instr.tex
outline adjusted 50%

@@
 
-In this study, the nanostructures were grown in a home-built chemical vapor deposition system and characterized using both electron microscopy and optical spectroscopy methods, including SEM, XRD, EDX, TEM, Raman and UV-Vis.
+In this study, the nanostructures were grown in a home-built chemical vapor deposition system and characterized using both electron microscopy and optical spectroscopy methods, including \gls{sem}, \gls{xrd}, \gls{edx}, \gls{tem}, Raman and UV-Vis.
 Other sample and substrate preparation methods are also briefly introduced.
-A detailed introduction will be given to the CVD system.
+A detailed introduction will be given to the \gls{cvd} system.
 For other mature techniques, the contents will be limited to the extent where experienced material researchers could repeat the experiments performed here.
@@
 \subsection{Home-built CVD System}
-The syntheses were accomplished in a home-made hot-wall CVD system.
+The syntheses were accomplished in a home-made hot-wall \gls{cvd} system.
 The reaction chamber part and a schematic drawing of whole system can be visualized in Fig.~\ref{fig:ch2cvd}.
@@
 
-The controllable parameters of this CVD system include central heating temperature, absolute gas flow and relative ratio of (Ar/\ce{O2}), amount of source material and location of the substrates.
+The controllable parameters of this \gls{cvd} system include central heating temperature, absolute gas flow and relative ratio of (Ar/\ce{O2}), amount of source material and location of the substrates.
 The operation capability is summarized in Table~\ref{tab:cvd}.
@@
 Detailed growth conditions will be introduced in the corresponding chapters.
-Basic operations and several growth recipes using the home-built CVD system are included in Appendix.
+Basic operations and several growth recipes using the home-built \gls{cvd} system are included in Appendix.
 
@@
 Depending on the specific experimental requirement, a hydrophilic surface may be required.
-A plasma cleaner (Kurt J Lesker, Plasma-Preen 862) was used to render a hydrophilic Si surface, where reaction among $e$, \ce{O^+}, \ce{O2^+}, \ce{O^-},\ce{O2} occurs, and \ce{OH}-terminated surface followed.\cite{Habib2010} The treatment was done at 2 Torr \ce{O2} for 3 min.
+A plasma cleaner (Kurt J Lesker, Plasma-Preen 862) was used to render a hydrophilic Si surface, where reaction among $e$, \ce{O+}, \ce{O2+}, \ce{O-},\ce{O2} occurs, and \ce{OH}-terminated surface followed.\cite{Habib2010} The treatment proceeds at 2 Torr \ce{O2} for 3 min.
 Glass substrates cleaning is the same as that of Si.
-Mica is cleaved right before the growth withoud extra cleaning steps.
+Mica is cleaved right before the growth without extra cleaning steps.
 In addition, substrates can be coated with a thin layer of metal before growth.
@@
 \subsection{Magnetron Sputtering}\label{sec:mag}
-Sputtering, a process in which atoms are ejected from a solid target material by bombarding it with energetic particles, is a well established physical vapor deposition (PVD) process with a high degree of controllability.
+Sputtering, a process in which atoms are ejected from a solid target material by bombarding it with energetic particles, is a well established \gls{pvd} process with a high degree of controllability.
 The high energy and controllable parameters of sputtering can result in the growth of well-structured and crystalline films.
@@
 \ce{Ar+} ions are accelerated to target foils.
-The pressure of \ce{Ar+} has two functions: to sputter off the target ions, and to influence the mean free path (MFP).
+The pressure of \ce{Ar+} has two functions: to sputter off the target ions, and to influence the \gls{mfp}.
 These collisions between target ions and \ce{Ar+} leads to almost all arrival angle, thus uniform coverage.
@@
 Usually yield between 1 and 2 is desired.
-The MFP in sputtering is on order of 3 cm (assuming pressure 30 mTorr), with source-to-substrate distance as 5 cm, average number of collisions is about 5/3$\sim$2.
+The \gls{mfp} in sputtering is on order of 3 cm (assuming pressure 30 mTorr), with source-to-substrate distance as 5 cm, average number of collisions is about 5/3$\sim$2.
 
@@
 The SEM instrument used in this study is JEOL JSM-6480.
-The electron beam (E-beam) source is a tungsten filament heated at about 2800 K.
+The \gls{ebeam} source is a tungsten filament heated at about 2800 K.
 The acceleration voltage can be up to 30 kV.
 After acceleration, electron beam strikes the sample mounted on specimen stage, producing rich signals as illustrated in Fig.~\ref{fig:ch2sem}.
-Depending on the energy and scattering angle, the out-coming electrons from specimen can be grouped into backscattering electron (BSE) and secondary electron (SE), respectively.
-SE is generated from the emission of valence band electrons.
+Depending on the energy and scattering angle, the out-coming electrons from specimen can be grouped into \gls{bse} and \gls{se}, respectively.
+\gls{se} is generated from the emission of valence band electrons.
 And due to the limited energy ($<50$ eV), the emission from deep region is mostly absorbed again; only those electrons that are at the vicinity of specimen surface can escape.
-Hence the SE image is topographical sensitive.
-The emission efficiency is strongly affected by the geometry (tilting angle of specimen surface) and voltage potential (charging effect), so does the contrast in SE image.
-On the other hand, backscattered electron could have large energy close to that of incident E-beam.
-The scattering cross section strongly depends on atomic number (Z), thus allowing for the compositional analysis.
+Hence the \gls{se} image is topographical sensitive.
+The emission efficiency is strongly affected by the geometry (tilting angle of specimen surface) and voltage potential (charging effect), so does the contrast in \gls{se} image.
+On the other hand, backscattered electron could have large energy close to that of incident \gls{ebeam}.
+The scattering cross section strongly depends on atomic number Z, thus allowing for the compositional analysis.
 The X-ray emission stems from inner shell transition of the constitutive atoms, and cathodoluminescence from bandgap transition.
-Other E-beam generated signals, such as Auger electrons, are usually not useful in SEM unless with ultra-high vacuum and clean surface.
+Other \gls{ebeam} generated signals, such as Auger electrons, are usually not useful in SEM unless with ultra-high vacuum and clean surface.
 
@@
 Sometimes when an area is scanned for a long time at high magnification, the surrounding region could appear brighter after switching to a lower magnification.
-This is a sample contamination, due to the E-beam induced polymerization and deposition of hydrocarbon molecules in the vicinity of that smaller area.
+This is a sample contamination, due to the \gls{ebeam} induced polymerization and deposition of hydrocarbon molecules in the vicinity of that smaller area.
 
@@
 \subsection{X-ray Diffraction (XRD)}
-Crystal structures of the as-synthesized specimens in this study were characterized using PANXpert Pro MRD with Cu $K\alpha_{avg}$ radiation at $\lambda$=1.5418 \AA.
+Crystal structures of the as-synthesized specimens in this study were characterized using PANXpert Pro MRD with Cu $K\alpha_{avg}$ radiation at $\lambda$=1.5418 \si{\angstrom}.
 The high energy photon ($E = 1239.8/0.15148= 8184.5$ eV) was generated using accelerated electron beam from tungsten filament to bombard Cu target.
@@
 Akin to the electron-materials interaction introduced in Sec.~\ref{sec:sem}, various signals are generated when the thin specimen was radiated by electron beam.
-Besides the SAED pattern and HRTEM imaging, other TEM based techniques include CBED, EDX, EELS and CL, etc.
+Besides the \gls{saed} pattern and \gls{hrtem} imaging, other TEM based techniques include \gls{cbed}, EDX, \gls{eels} and \gls{cl}, etc.
 Therefore, TEM is essentially a signal-generating and detecting tool.
@@
 On the other hand, it is much easier to fine tune the power (focal length) of lens in TEM than in conventional optics.
-This capacity enables other observation approaches that would be rather difficult, if not impossible, to be realized in lens optics, such as selected area electron diffraction pattern (SAED).
+This capacity enables other observation approaches that would be rather difficult, if not impossible, to be realized in lens optics, such as \gls{saed}.
 
@@
 A JEOL double tilt holder was used to rotate the crystal orientation.
-TEM images and SEADs were acquired using a charge coupled device (CCD) from Gatan, Inc.
+TEM images and SEADs were acquired using a \gls{ccd} from Gatan, Inc.
 EDX spectroscopy was captured by similar Oxford Instrument INCA attachment introduced in Sec.~\ref{sec:edx}.
@@
 The former one is inherent and can only be partially overcome by combining TEM with other ensemble characterization tools.
-As to the latter one, it should be noted that the specimen is usually in focus from top to bottom surface; therefore the images, DPs and spectra are all averaged through the thickness of specimen.
+As to the latter one, it should be noted that the specimen is usually in focus from top to bottom surface; therefore the images, \glspl{dp} and spectra are all averaged through the thickness of specimen.
 In other words, single TEM image has no depth sensitivity.\cite{Williams2009}
@@
 This energy difference between incident photon and inelastically scattered photon is closely related to a series of vibrational modes.
-Being nondestructive and requiring minimal preparation, it is an excellent tools to assess lattice dynamics and fingerprint species.\cite{McCreery2000} For instances, characteristic Raman shift can be used to determine material compositions; changes in Raman peak (FWHM, frequency shift) are often related to strain; polarization Raman spectra can be used to derive crystal orientation and symmetry.
+Being nondestructive and requiring minimal preparation, it is an excellent tools to assess lattice dynamics and fingerprint species.\cite{McCreery2000} For instances, characteristic Raman shift can be used to determine material compositions; changes in Raman peak (\gls{fwhm}, frequency shift) are often related to strain; polarization Raman spectra can be used to derive crystal orientation and symmetry.
 
@@
 
-Diffuse reflection spectroscopy (DRS) serves as another tool to estimate the sample band gap using Kubelka-Munk theory (KM).\cite{Tandon1970} The original KM theory was proposed in 1931,\cite{Kubelka1931} and has been popular in the color-related industry, such as painting, pigments, and paper.
+\Gls{drs} serves as another tool to estimate the sample band gap using \gls{kmt}.\cite{Tandon1970} The original KM theory was proposed in 1931,\cite{Kubelka1931} and has been popular in the color-related industry, such as painting, pigments, and paper.
 This method is useful for the analysis of samples of difficultly soluble substances and for samples that will react with the solvents upon being dissolved.

### 2014-09-28 ch-intro/ch-intro.tex
outline adjusted 50%

@@
 
-Transition metal generally refers to any elements in the d-block of periodic table, and transition metal oxides (TMOs) mean the chemical compounds that consist of at least one transition metal element and oxygen.
-Similarly, transition metal dichalcogenides (TMDCs) are compounds that combine at least one transition metal with chalcogen elements from group VIA (S, Se, Te, Po).
+Transition metal generally refers to any element in the d-block of periodic table, and \glspl{tmo} mean the chemical compounds that consist of at least one transition metal element and oxygen.
+Similarly, \glspl{tmdc} are compounds that combine at least one transition metal with chalcogen elements from group VIA (S, Se, Te, Po).
 Oxygen also belongs to group VIA, but is often treated separately.
@@
 
+some calculation on doping, uv-vis results on the thin film.
+
 \subsection{Photocatalysis for Energy Harvesting}
@@
 \end{subequations}
-As shown in Fig.~\ref{fig:woxnhe}, \ce{WO3} has \gls{cb} edge positioned slightly more positive than reduction potential of \ce{H^+/H2}(versus \gls{nhe}), and \gls{vb} edge much more positive than the oxidation potential of \ce{H2O}/\ce{O2}.
+As shown in Fig.~\ref{fig:woxnhe}, \ce{WO3} has \gls{cb} edge positioned slightly more positive than reduction potential of \ce{H^+/H2} versus \gls{nhe}, and \gls{vb} edge much more positive than the oxidation potential of \ce{H2O}/\ce{O2}.
 So the photo-cleavage of water cannot be accomplished by \ce{WO3} alone.
@@
 
-In comparison to oxides thin films, 1D TMO nanostructures (e.g., nanowires) have following advantages to improve the response speed and enhance the coloration efficiency: (1) With reduced diameters down to nanometer scale, the distance for ion diffusing into and out of the nanowires is significantly shortened.
+In comparison to oxides thin films, 1D \gls{tmo} nanostructures (e.g., nanowires) have following advantages to improve the response speed and enhance the coloration efficiency: (1) With reduced diameters down to nanometer scale, the distance for ion diffusing into and out of the nanowires is significantly shortened.
 (2) The gap between nanowires always provides channels for fast ion diffusion outside the nanowires.
@@
 \section{Objective and Scope}
-To fully harvest the advantages of these TMO and TMDC one-dimensional nanomaterials, a scalable growth method and a comprehensive understanding towards the growth-structure-property relation must first be established.
-Therefore, this dissertation primarily focuses on synthesis, growth mechanism study and characterization, and will only present preliminary results on device and applications.
+To fully harvest the advantages of these \gls{tmo} and \gls{tmdc} one-dimensional nanomaterials, a scalable growth method and a comprehensive understanding towards the growth-structure-property relation must first be established.
+Considering the nature of this Ph.D.\ study, this dissertation primarily focuses on synthesis, growth mechanism study and characterization, and will only present preliminary results on device and applications.
 

### 2014-09-28 ch-moox/moox.tex
outline adjusted 50%

@@
 % git version control added 012614
-\chapter{New Vapor-Solid-Solid Growth Modes of Molybdenum Oxide}
+\chapter{New Vapor-Solid-Solid Growth Modes of MoO$_3$}
 
@@
 In the transverse mode, the 1D structures grow perpendicularly to the catalyst-deposition interface with catalyst particles on the side surfaces; whereas in the axial mode, the crystal grows along the catalyst-deposition axis.
-The growth modes were explained by a modified vapor-solid-solid (VSS) mechanism, and factors that affect the growth were explored in details.
+The growth modes were explained by a modified \gls{vss} mechanism, and factors that affect the growth were explored in details.
 
@@
 With 10 sccm UHP Ar as carrier gas, the overall pressure reached about 200 mTorr.
-The heating temperature was ramped up to 800 \si{\degreeCelsius} in 30 minutes and lasted for 15 to 120 minutes.
+The heating temperature was ramped up to 800 \si{\degreeCelsius} in 30 min and lasted for 15 to 120 min.
 Then the heating power was turned off and the chamber was allowed to naturally cool down to room temperature.
@@
 \section{Results and Discussion on Molybdenum Oxide}\label{sec:result}
-
 In this section, the growth of \ce{MoO3} on bare Si substrates was presented first, followed by catalytic growth, both of which were characterized by SEM, XRD, TEM and EDX.
 Then the catalytic growth mechanism was investigated using \ce{NaOH} treated Si substrate.
+The growth mechanism was probed using two series of control experiments.
+Then a growth model was proposed and verified.
+In the end, this growth model was applied onto other substrates with alkaline metal ions, and various \ce{MoO3} nanostructures were produced.
+
 \subsection{Non-catalyst Growth}\label{sec:nonsi}
@@
 Notice that on the horizontal axis of temperature, zero inch is defined at the upstream edge of furnace.
-To facilitate discussion and provide a tight context, the author define the position of substrate as the coordinate of its upper-stream edge along this temperature axis (i.e.
-the substrate location is 7 in in Fig.~\ref{fig:mooxgrowth}).
+To facilitate discussion and provide a tight context, the author define the position of substrate as the coordinate of its upper-stream edge along this temperature axis, i.e., the substrate location is 7 in in Fig.~\ref{fig:mooxgrowth}.
 The usual length of Si substrate is 1 in.
@@
 
-From previous works in our group,\cite{predeep2011} the author found that with $T_h = 600$ \si{\degreeCelsius} and substrate placed at 6.5 in, microflakes grew at the high temperature edge of Si, suggesting the nucleation already started.\footnote{in 020510 batch} When flow of oxygen was gradually reduced, diminished size of micro-flake was observed at the same location of substrates.
+From previous works in our group,\cite{predeep2011} it was found that with $T_h = 600$ \si{\degreeCelsius} and substrate placed at 6.5 in, microflakes grew at the high temperature edge of Si, suggesting the nucleation already started.\footnote{in 020510 batch} When flow of oxygen was gradually reduced, diminished size of micro-flake was observed at the same location of substrates.
 This results indicated the rate-determining step is diffusion when oxygen flow was in the range of 2 sccm to 0.5 sccm.\footnote{in (31210-31510) batches} It was also found the deposition amount on a particular location of the substrate is not linearly proportional to the growth time, \emph{i.e.}, the growth at upper stream edge first increase then decrease.
@@
 
-Understanding the interaction between liquid droplet and the solid interface allows for a rich engineering space to fine tune the geometry and structures of as-grown nanostructures.
+Understanding the interaction between liquid droplet and the solid interface allows for a rich engineering space to fine tune the geometry and structures of the as-grown nanostructures.
 For instances, the diameter of Si nanowires (NWs) can be controlled by laser ablated catalyst\cite{Morales1998} or well-defined Au nanoparticles.\cite{Cui2001b} Under proper conditions, axial modulation can produce nanowire superlattices from group IV and III-V materials.\citep{Gudiksen2002,Bjork2002}  Radial composition modulation have also been demonstrated by selectively suppressing VLS process, providing a robust routine for homogeneous or heterogeneous core-shell structures.\cite{Lauhon2002a}
@@
 \centering
-\includegraphics[width=0.8\textwidth]{MoO3_EDX_Raman}
+\includegraphics[width=0.9\textwidth]{MoO3_EDX_Raman}
 \caption[Growth evolution of \ce{MoO3}: first stage]{Evolution of the early stage for catalyst-assisted \ce{MoO3} growth: SEM images, micro-Raman spectra, and EDX spectra of the specimens grown for 15 min with different \ce{O2} flows of (a-c) 0.1 sccm, (d-f) 1 sccm, (g-i) 3 sccm, and (j-l) 10 sccm.
@@
 \centering
-\includegraphics[width=0.8\textwidth]{mooe_sem_ev}
+\includegraphics[width=0.9\textwidth]{mooe_sem_ev}
 \caption[Growth evolution of \ce{MoO3}: second stage]{Growth evolution of the second stage of catalyst-assisted growth of \ce{MoO3} 1D structures: SEM images of the deposition at different growth temperatures with growth time of row 1: 15 min, row 2: 30 min, row 3: 60 min, and row 4: 90 min.
@@
 \centering
-\includegraphics[width=0.6\textwidth]{vls_mode2}
+\includegraphics[width=0.7\textwidth]{vls_mode2}
 \caption[Growth model of \ce{MoO3}]{Schematic drawing on the growth steps of the proposed growth model in hypothesis~\ref{hypo2}.}
@@
 
-\subsection{Growth on Alkaline Metal Containing Substrate}
+\subsection{Growth on Alkaline Metal Containing Substrates}
 In analog with the \ce{Na2MoO4}-\ce{MoO3} binary phase diagram, other alkaline metals, such as Li and K, could also form A-Mo-O alloy at elevated temperature.
@@
 \subsection{Growth on Glass}\label{sec:glass}
-The mass transport of sodium ions in silica glass is first estimated to evaluate the amount of catalyst available during the growth of \ce{MoO3}.
+Achieving morphology controlled growth of \ce{MoO3} on transparent substrates, e.g., glass, is an important progress towards process integration and device fabrication in photo-energy related applications.
+Because the alkaline ions in glass can diffuse out at elevated temperature, the proposed \gls{vss} mechanism will modify the \ce{MoO3} deposition.
+Therefore, the mass transport of sodium ions in silica glass is first estimated to evaluate the amount of catalyst available during the growth of \ce{MoO3}.
 The driving force could be external field or concentration gradient.
 And the dynamics is governed by diffusion equation
-\begin{align}
+\begin{align}\label{eq:nadiff}
 \frac{\partial C}{\partial t} = D \frac{\partial^2 C}{\partial x^2},
@@
 \end{table}
-
-It is worth mentioning that the gradient of Gibbs free enthalpy overruled the concentration of a particular species, and higher \ce{OH^-} contents tend to reduce Na diffusivity.\cite{Materials2012}  The substrates used in this work are glass and ITO/glass.
-Related parameters is as following:
+It is worth mentioning that the gradient of Gibbs free enthalpy overruled the concentration of a particular species, and higher \ce{OH-} contents tend to reduce Na diffusivity.\cite{Materials2012} The substrates used in this work are glass and ITO/glass; the relevant parameters are as following:
 \begin{itemize}
@@
 \end{itemize}
-Then the net flux $J$ is estimated as
+Substituting these values into Eq.~\ref{eq:nadiff}, the net flux $J$ is estimated as
 \begin{align}
@@
 \end{align}
-
-In typical growth of 2 h, the net amount of Na diffusing out of substrate is then $1.44\times10^{-4}$mol, about 10\% of total Na ions in the glass substrates.
-The diffusion length $\sqrt{Dt}$ is 190 $\mu$ m.
+In typical growth of 2 h, the net amount of Na diffusing out of substrate is then $1.44\times10^{-4}$ mol, which is about 10\% of total Na ions in the glass substrates.
+The diffusion length $\sqrt{Dt}$ is 190 $\mu$m.
 Notice this result overestimates since the flux will reduce gradually.
-Meanwhile the molar amount of \ce{NaOH} applied on Si substrate is about $5\times10^{-7}$mol.
+Meanwhile the molar amount of \ce{NaOH} applied on Si substrate is about $5\times10^{-7}$ mol.
 Considering the adjusted ratio, Na contents should be much more when using glass substrate than when using NaOH-Si substrate.
@@
 \cmidrule(l){1-3}
- Temperature & \ce{O2} & Time & Morphology  \\
+$T$ (\si{\degreeCelsius}) & \ce{O2} (sccm) & Time (min) & Morphology  \\
 \midrule
-700    &  10   & 15  &   about 50 $\mu m$ belts, some towers \\
+700    &  10   & 15  &   about 50 $\mu$m belts, some towers \\
 700   &  1   & 60  &   irregular shape, not too much growth\\
 700    &  10   & 60  &   droplet almost all on tip of belts, many towers \\
-800    &  1   & 15  &   tens $\mu m$ belt with sharp edge(100 nm thick, and 1micro wide) dominates\\
-800   &  1   & 60  &   exhibit ITO features, droplets on tips of belt, many tower like structures\\
+800    &  1   & 15  &   tens $\mu$m belt with sharp edge(100 nm thick, and 1micro wide) dominates\\
+800   &  1   & 60  &   exhibiting ITO features, droplets on tips of belt, many tower like structures\\
 800    &  10   & 15  &   rounded edge flakes dominate, modest density tapering belt, and some possible tower\\
@@
 \end{table}
-
 The 800-1-15 combination produced dense \ce{MoO3} nanoplate with length about 10 $\mu$m, width $300\sim500$ nm and thickness less than 100 nm, as illustrated in Fig.~\ref{fig:ch4glass}.
-%
+These \ce{MoO3} nanoplates are of high crystalline quality, and could potentially show enhanced photoelectrochemical and electrochromic activities.
 \begin{figure}[htb]
@@
 \end{figure}
-These \ce{MoO3} nanoplates are of high crystalline quality, and could potentially show enhanced photoelectrochemical and electrochromic activities.
 

### 2014-09-28 ch-tms/tms.tex
outline adjusted 50%

@@
-\chapter{Tungsten Oxide-Tungsten Disulfide Heterostructure}
+\chapter{WO$_3$-WS$_2$ Heterostructure}
 
@@
 The shoulder mode at tip2 spectrum is a manifestation of $B_{1u}$ mode from curved \ce{WS2} layer.
-According to previous analysis, the apparent ratio between in-plane and out-of-plane vibration indicates site tip2 has multi-wall \ce{WS2}, and the other two possibly have few-wall \ce{WS2}.
+According to previous analysis, the apparent ratio between in-plane and out-of-plane vibration indicates site tip2 has multi-wall \ce{WS2}, and the other two possibly have few-walled \ce{WS2}.
 

### 2014-09-28 ch-tms/tmspart.tex
outline adjusted 50%

@@
 \section{Introduction}
+\subsection{Properties of TMDCs}
+Tungsten disulfide (\ce{WS2}) is a group VI dichalcogenide semiconductor compound.
+The molecular weight is 249.97 \si{g\per \mole}.
+Almost all natural \ce{WS2} belongs to P63/mmc space group (2H-\ce{WS2}), where $a$ is 3.153 \si{\angstrom}, $c$ is 12.323 \si{\angstrom} (PDF 04-003-4478).
+Two other crystal structures were found in man-made \ce{WS2}, i.e., 1T and 3R, where 3R can be prepared by bromine (Br) chemical vapor transport (CVT) method \cite{Schutte1987} and 1T was generally found in alkaline intercalated \ce{WS2}.\cite{Yang1996a, Enyashin2011}
+
+As a reference, the lattice dimensions are summarized in Table~\ref{tab:ms2lattice}.
+%lattice
+\begin{table}[htb]
+\centering
+\caption{Lattices dimension of \ce{MS2}}\label{tab:ms2lattice}
+\begin{tabular}{lccr}
+\toprule
+         &  & 2H-\ce{MoS2}\cite{Coehoorn1987,Ataca2012} & 2H-\ce{WS2}\cite{Albe2002,Schutte1987} \\
+\midrule
+Lattice constant & a(\AA) & 3.1604 & 3.171 \\
+                 & c(\AA) & 12.295 & 12.359 \\
+Within \ce{MS2} layer & M-3S (\AA)& 2.37  & 2.405   \\
+                      & S-1S (\AA)& 3.11  & 3.14   \\
+Between \ce{MS2} layer& S-3S (\AA)&   & 3.53   \\
+\bottomrule
+\end{tabular}
+\end{table}
+
 \subsection{Synthesis Review of TMDCs}
-Shortly after the discovery of carbon nanotube (CNT) in 1991,\cite{Iijima1991} its transition metal dichalcogenides (TMDC) counterparts, i.e., \ce{WS2}, was synthesized in 1992.\cite{Tenne1992} In the following decades, other TMDC and several metal oxides nanotubes were demonstrated as well.
+Shortly after the discovery of \gls{cnt} in 1991,\cite{Iijima1991} its transition metal dichalcogenides (TMDC) counterparts, i.e., \ce{WS2}, was synthesized in 1992.\cite{Tenne1992} In the following decades, other TMDC and several metal oxides nanotubes were demonstrated as well.
 \citeauthor{Rao2003} did an excellent work to review these inorganic nanotubes.\cite{Rao2003} Hence this study just recapitulates the main categories of synthesis methods:
@@
 \ce{Ni3S2} phase was found and surfactant-mediated epitaxy is proposed.
-\citeauthor{Regula1997} studied the Ni-W-S phase diagram and the role of Ni layer in promoting \ce{WS2} film growth from amorphous \ce{WS3}.\cite{Regula1997} \emph{In-situ} TEM analysis confirmed the formation of \ce{NiS_x} droplets and lateral growth of \ce{WS2} from these droplets.\cite{Regula1998} Recently, it has been shown that direct sulfurization of W coating (20nm) at 750 \si{\degreeCelsius} on \ce{SiO2}-Si can also produce \ce{WS2} film.\cite{Shanmugam2012a} However, the film is of bulk in nature.
+\citeauthor{Regula1997} studied the Ni-W-S phase diagram and the role of Ni layer in promoting \ce{WS2} film growth from amorphous \ce{WS3}.\cite{Regula1997} \emph{In-situ} TEM analysis confirmed the formation of \ce{NiS_x} droplets and lateral growth of \ce{WS2} from these droplets.\cite{Regula1998} Recently, it has been shown that direct sulfurization of W coating (20 nm) at 750 \si{\degreeCelsius} on \ce{SiO2}-Si can also produce \ce{WS2} film.\cite{Shanmugam2012a} However, the film is of bulk in nature.
 Previous study of \ce{WS2} growth on various substrates by \citeauthor{Genut1992} was summarized in Table~\ref{tab:ws2subs}.\cite{Genut1992} It was found that the \ce{WS2} nucleate from an amorphous \ce{WS3} phase and the substrate has a critical role in determining both the reaction onset temperature and the texture.
@@
 
-\subsection{Raman on Bulk and FL TMDCs}
+\subsection{Raman on WS$_2$: Bulk, FL and NTs}\label{sec:ntram}
 
@@
 The refractive index $\tilde{n}$ of \ce{WS2} at 532 nm is about $4.726 - 0.737i$, corresponding to a wave-vector about $1\times10^8$ \si{m^{-1}}.
-Compared to the size of Brillouin zone ($\pi/a = 10^{10}$\si{m^{-1}}), off-resonant Raman could only probe phonon at $\Gamma$ point, where the phonon momentum ($\hbar k$) is close to zero.
+Compared to the size of Brillouin zone ($\pi/a = 10^{10}$ \si{m^{-1}}), off-resonant Raman could only probe phonon at $\Gamma$ point, where the phonon momentum ($\hbar k$) is close to zero.
 
@@
 
-\subsection{Raman on TMDC NTs}\label{sec:ntram}
-
-\citeauthor{Dobardzic2005} calculated \ce{MoS2} SWNT phonon dispersion.
+\citeauthor{Dobardzic2005} calculated \ce{MoS2} \gls{swnt} phonon dispersion.
 The dependence of wavenumbers and their displacement on chirality and diameter were discussed.
@@
 Symmetry assignment is zigzag when $(n,0)$, armchair when $(n,n)$ and chiral when $(n_1, n_2), n_1>n_2$.
-\citeauthor{Dobardzic2006} theoretically presented Raman scattering of any polarization on SWNT of \ce{WS2} and their dependence on diameter (1-20 nm) and chiral angle.
+\citeauthor{Dobardzic2006} theoretically presented Raman scattering of any polarization on \gls{swnt} of \ce{WS2} and their dependence on diameter (1-20 nm) and chiral angle.
 The author assigned 351 cm$^{-1}$ as $E_u$ for \ce{WS2} NT.\cite{Dobardzic2006} \citeauthor{Ghorbani-Asl2013} discuss the electronic and vibrational properties for large diameter \ce{WS2} NTs\cite{Ghorbani-Asl2013}.
@@
 \citeauthor{Virsek2007} investigated the Raman scattering ($\lambda=632$ nm) of \ce{WS2} NTs.\cite{Virsek2007} The silicon peak at 520 cm$^{-1}$ is used for calibration.
-Up-shift of $A_{1g}$ and $E_{2g}$ modes (i.e.
-420 to 423 cm$^{-1}$ at $A_{1g}$ mode) were observed, which is attributed to the strain in 3R stacking layers.
-
-As a reference, the lattice dimensions are summarized in Table~\ref{tab:ms2lattice}.
-%lattice
-\begin{table}[htb]
-\centering
-\caption{Lattices dimension of \ce{MS2}}\label{tab:ms2lattice}
-\begin{tabular}{lccr}
-\toprule
-         &  & 2H-\ce{MoS2}\cite{Coehoorn1987,Ataca2012} & 2H-\ce{WS2}\cite{Albe2002,Schutte1987} \\
-\midrule
-Lattice constant & a(\AA) & 3.1604 & 3.171 \\
-                 & c(\AA) & 12.295 & 12.359 \\
-Within \ce{MS2} layer & M-3S (\AA)& 2.37  & 2.405   \\
-                      & S-1S (\AA)& 3.11  & 3.14   \\
-Between \ce{MS2} layer& S-3S (\AA)&   & 3.53   \\
-\bottomrule
-\end{tabular}
-\end{table}
+Up-shift of $A_{1g}$ and $E_{2g}$ modes (i.e., 420 to 423 cm$^{-1}$ at $A_{1g}$ mode) were observed, which is attributed to the strain in 3R stacking layers.

### 2014-09-28 ch-wox/ch-wox.tex
outline adjusted 30%
outline adjusted 50%

@@
 
-\chapter{tungsten oxides}
+\chapter{Impurity Effects on WO$_3$ Nanowires}
 
@@
 
-\section{Growth Methods and Results Discussion}
+\section{Experimental}
 
-Tungsten powders were utilized as source materials in this work.
+Metallic tungsten powders were utilized as source materials in this work.
 Four kinds of W powder were used in total, as summarized in Table.~\ref{tab:powder}.
-Two growth configurations were explored, namely ordinary transport (OT) and seeded growth (SG).
+Two growth configurations were explored, namely ordinary transport and seeded growth.
 % Tungsten powders size and purity
@@
 
-In a typical OT experiment (Fig.~\ref{fig:wogrow}), about 2 g tungsten powder was positioned in the upstream end of a quartz boat and downstream about 2.5 inch the substrate was stationed.
+In a typical ordinary transport experiment (Fig.~\ref{fig:wogrow}), about 2 g tungsten powder was positioned in the upstream end of a quartz boat and downstream about 2.5 inch the substrate was stationed.
 The substrates were p-type, boron-doped and [100]-orientated silicon with about 1 $\mu$m thermally-grown silicon oxide layer on the polished side.
@@
 
-\subsection{Tungsten Oxides: Residual Effect}\label{sec:nawox}
+\section{Results ans Discussion}
+\subsection{Tungsten Oxides: Impurities and Residual Effects}\label{sec:nawox}
 
-The growth dynamics of each source were investigated in OT configuration.
+The growth dynamics of each source were investigated in ordinary transport configuration.
 In each experiment, the temperature, flow rate and source and substrate locations were controlled.
@@
 
-\textbf{OT growth of 3N}
-
-The sodium contents in 3N powders fundamentally change the deposition in OT growth.
+The sodium contents in 3N powders fundamentally change the deposition in ordinary transport growth.
 Typical morphologies of the as-synthesized nanostructures grown on a \ce{SiO2}-Si substrate were shown in Fig.~\ref{fig:nawoxsemedx}a.
@@
 \end{equation}
-where $R$ is tungsten-oxygen bond length in \AA, and $\nu$ is Raman stretching wavenumber in \si{cm^{-1}}.\cite{Hardcastle1995} The standard deviation of estimating \ce{W-O} bond distance from Raman stretching wavenumber is $\pm0.034$ \AA.
+where $R$ is tungsten-oxygen bond length in \si{\angstrom}, and $\nu$ is Raman stretching wavenumber in \si{cm^{-1}}.\cite{Hardcastle1995} The standard deviation of estimating \ce{W-O} bond distance from Raman stretching wavenumber is $\pm0.034$ \si{\angstrom}.
 The observed Raman peaks of \ce{Na5W_{14}O_{44}} phase lies at 965, 943, 913, 808, 786, 778, 765, 695 and 107 \si{cm^{-1}}.
@@
 The sodium concentration in 3N source was 20 ppm as provided by vendor.\footnote{Due to the non-uniform distribution of foreign elements, detection of sodium by EDX is possible although the concentration is below the limit of typical EDX capacity.} The Na concentrations in quartz tube and quartz boat (GE 214 quartz, Wilmad Labglass) were 1 ppm and 0.7 ppm, respectively.
-To confirm the major source of Na content coming from 3N powder, control experiments were employed by using W source with higher purities (4N5 or 5N).
+To verify the major source of Na content coming from 3N powder, control experiments were employed by using W source with higher purities (4N5 or 5N).
 These ultra-high purity W sources produced pure tungsten oxide deposition and no Na content was detected by EDX.
@@
 The transmission (Fig.~\ref{fig:nauv}) was about 70\% above 400nm, and began to drop significantly for shorter wavelength.
-This variation was also identified in the diffuse reflection spectrum (DRS) in Fig.~\ref{fig:nadrs}, where the reflection reached to a maximum of 16\% at 390 nm.
+This variation was also identified in the diffuse reflection spectrum in Fig.~\ref{fig:nadrs}, where the reflection reached to a maximum of 16\% at 390 nm.
 One difference is the DRS increased from 1300 nm to 400nm, presumably due to the inverse scattering intensity with NW dimension of 300 nm.
@@
 More investigation is needed to vigorously determined the electronic transport properties of \ce{Na5W14O44} NW.
-
-\textbf{OT growth of 3N5, 4N5 and 5N}
-
-Typical morphologies of OT growth using other powders are shown in Fig.~\ref{fig:wox3n5} and Fig.~\ref{fig:wox4n5}, respectively.
-The common feature of these samples is the dominance of islands growth in upstream end and layers growth in downstream end.
-The exact dimension still shows some minor difference, particularly in low temperature region.
-The deposition with 4N5 and 5N have much smaller grain size than that with 3N5 powder.
 % 3N5 powder growth
@@
 \end{figure}
-It is worth pointing out that there are some NWs growth in low temperature end associated with 4N5 (Fig.~\ref{fig:wox4n5}c), although not in large scale.
+Typical morphologies of ordinary transport growth using other powders are shown in Fig.~\ref{fig:wox3n5} and Fig.~\ref{fig:wox4n5}, respectively.
+The common feature of these samples is the dominance of islands growth in upstream end and layers growth in downstream end.
+The exact dimension still shows some minor difference, particularly in low temperature region.
+The deposition with 4N5 and 5N have much smaller grain size than that with 3N5 powder.
 % 4N5 powder growth
@@
 \end{figure}
+It is worth pointing out that there are some NWs growth in low temperature end associated with 4N5 (Fig.~\ref{fig:wox4n5}c), although not in large scale.
 
@@
 
-As mentioned in Sec.~\ref{sec:nawox}, growth using higher purity tungsten powders primarily produce dense layer deposition, and growth using 3N powder is plagued with the impurity effect.
-New growth method is required to obtain \ce{WO3} NWs.
-Here we figured out two alternatives to address this issue: seeded growth (SG) and flow growth (FG).
-In seeded growth, additional tungsten powders on the substrate serves as local seed.
-This approach is essentially the same as previous studies where tungsten foils was used as substrate.
-The advantage of our method is W powder cost much less than a whole piece of foil, and provide more surface area than W foil in the same volume.
-The FG method utilizes the flow dynamics of our CVD apparatus.
-We will discuss both of them in details.
+As mentioned in Sec.~\ref{sec:nawox}, growth using higher purity tungsten powders primarily produces thin film deposition, and growth using 3N powder is plagued with the impurity effect producing sodium tungsten oxide NW instead of tungsten oxide NW.
+New growth method is thus explored to obtain \ce{WO3} NWs.
+In this study, a seeded growth approach was developed and proved to be a successful alternative way.
+In the seeded growth, additional tungsten powders was used on the substrate serving as local seed, on which dense \ce{WO3} NW array grew.
 
@@
 Oxidation of tungsten have been investigated under diverse conditions, such as at elevated temperature (\textgreater 1100 \si{\degreeCelsius} ) and oxygen pressure on the order of Torr,\cite{Base1965} and at temperatures ranging from 20 to 500 \si{\degreeCelsius} under atmosphere pressure.\cite{Warren1996} \ce{WO_x} NWs were readily found when tungsten (foil, wire, or powder) is oxidized under various conditions.\cite{Zhu1999,Karuppanan2007,Hsieh2010} However the study on tungsten powder oxidation behavior between intermediate temperature range and under low pressure is still rare.
-In this work, we studied the oxidation of tungsten powders with diverse size within temperature range from 500 to 1000 \si{\degreeCelsius} and under several mTorr oxygen partial pressure.
-Using tungsten powder as seed, we further illustrate an economic approach to obtain large yield of \ce{WO3} nanowires at relatively lower temperature than previous efforts.
-We also demonstrate that there is an optimal tungsten powder size under our experimental conditions for seeded growth.
-This will provide some insight on the role of tungsten powder as source material in CVD growth of \ce{WO_x}.
+This thesis studied the oxidation of tungsten powders with diverse size within temperature range from 500 to 1000 \si{\degreeCelsius} and under several mTorr oxygen partial pressure.
+It was illustrated that using tungsten powder as seed is an economic approach to obtain high yield of \ce{WO3} nanowires at relatively lower temperature.
+It was also demonstrated that there was an optimal tungsten powder size under current experimental conditions for seeded growth.
+This observation will provide some insight on the role of tungsten powder as source material in CVD growth of \ce{WO_x}.
 
 Commercial available tungsten powders with different size are usually associated with purity variation as well.
-We investigated four kinds of tungsten powder as already summarized in Table~\ref{tab:powder}.
+Four kinds of tungsten powders were used as precursor to prepare \ce{WO3} NWs, as already summarized in Table~\ref{tab:powder}.
 The dimensions of tungsten powder were obtained by measuring the average size in SEM graphs.
-We performed a systematic investigation on the oxidation behavior of tungsten powder.
-In a typical oxidation experiment, tungsten powders were loaded into the uniform heating zone and the sealed chamber was first pumped down to 5--8 mTorr.
+A systematic investigation was performed on the oxidation behavior of tungsten powder to evaluate the temperature effect, size-dependence and influence of oxygen partial pressure.
+
+In a typical oxidation experiment, tungsten powders were loaded into the uniform heating zone and the sealed chamber was pumped down to an ultimate pressure of $5\sim8$ mTorr.
 Then oxygen flow varying between 1 sccm to 10 sccm was admitted from upstream inlet.
-With 10 sccm Ar as carrier gas, the overall pressure was about 100 mTorr.
-The heating temperature was in the range of 500 to 750 \si{\degreeCelsius}.
-We present the temperature effect, size-dependence and influence of oxygen partial pressure as following.
+With 10 sccm UHP Ar (99.999\%) as carrier gas, the overall pressure reached to about 100 mTorr.
+The heating temperature (500 to 750 \si{\degreeCelsius}) was ramped up in 30 min and lasted for 30 min.
+Then the heating power was turned off and the chamber was allowed to naturally cool down to room temperature.
+
 % seed optimal
@@
 \includegraphics[width=0.7\textwidth]{JAP-2column_Fig1.jpg}
-\caption[W powder oxidation: temperature effect]{SEM graphs of 99.9\% (3N) tungsten powder oxidization at different temperatures of a) 500\si{\degreeCelsius}, b) 600\si{\degreeCelsius}, c) 650\si{\degreeCelsius}, d) 750\si{\degreeCelsius}, showing the optimal temperature for local formation of nanowires is between 600--650\si{\degreeCelsius}.
+\caption[W powder oxidation: temperature effect]{SEM graphs of 99.9\% (3N) tungsten powder oxidization at different temperatures of a) 500 \si{\degreeCelsius}, b) 600 \si{\degreeCelsius}, c) 650 \si{\degreeCelsius}, d) 750 \si{\degreeCelsius}, showing the optimal temperature for local formation of nanowires is between 600-650 \si{\degreeCelsius}.
 Oxygen flow rate is 1 sccm.}
@@
 \caption[W powder oxidation: size effect]{SEM graphs illustrating the oxidization of four different size of tungsten powders at 600~\si{\degreeCelsius} and 1 sccm oxygen flow.
-a) $17\mu m$, b) $32\mu m$, c) $3.3\mu m$, d) $1.5\mu m$.}
+a) 17 $\mu$m, b) 32 $\mu$m, c) 3.3 $\mu$m, d) 1.5 $\mu$m.}
 \label{fig:pdsize}
@@
 Fig.~\ref{fig:pdsize} depicted the oxidation of different sizes of tungsten powder under the same experimental conditions.
-In contrast to the morphology of 3N powder shown in Fig.~\ref{fig:pdtemp}, 3N5 powder surface is primarily covered with sub-micro particles as well as some short tiny NWs, whereas 4N5 and 5N powder were thoroughly oxidized, showing branched flowers feature.
+In contrast to the morphology of 3N powder shown in Fig.~\ref{fig:pdtemp}, 3N5 powder surface is primarily covered with sub-micron particles as well as some short tiny NWs; whereas 4N5 and 5N powder were thoroughly oxidized, showing branched flowers feature.
 This dramatic difference could be explained in terms of surface energy and oxygen diffusion.
@@
 When it comes to seeded growth, however, the powder size distribution was an important factor to give uniform NWs deposition.
-Since the size distribution of 3N powder is more uniform than that of 3N5 powder, we only employed the former as seeds.
+Since the size distribution of 3N powder is more uniform than that of 3N5 powder, this study used the former as seeds.
 % seed optimal
@@
 The seeded growth was performed by placing high purity tungsten powders (4N5 or 5N) in heating zone and receiving substrate with 3N tungsten powders in downstream location where the temperature was about 600 \si{\degreeCelsius}.
-The temperature profile and source and substrate locations remain essentially the same as in Fig.~\ref{fig:wogrow} except the presence of 3N powder on receiving substrate.
-In all experiments, tungsten powders were uniformly distributed by sliding two pieces of substrates and the growth time was kept at 4 hours.
+The temperature profile and source and substrate locations remain essentially the same as in Fig.~\ref{fig:wogrow} except the presence of 3N powder on substrate.
+In all experiments, tungsten powders were uniformly distributed by sliding two pieces of substrates and the growth time was kept at 4 h.
 % sg sem
@@
 \caption[Characterization of seeded growth \ce{WO3}: SEM]{Characterizations of seeded growth.
-(a) SEM graphs of \ce{WO3} NWs on \ce{SiO2/Si} substrate.
+(a) SEM graphs of \ce{WO3} NWs on \ce{SiO2}/Si substrate.
 (b) A high magnification view showing uniform NW growth and close-up view of one NW.
@@
 \end{figure}
-
-As shown in Fig.~\ref{fig:sgb}, dense NWs array was obtained on tungsten powder seeds with individual wires of length up to 5 $\mu$m and diameter about 50 to 200 nm, according to the estimation made in the close-up view.
+As shown in Fig.~\ref{fig:sgb}, dense NWs array was obtained on tungsten powder seeds with individual wires of length up to 10 $\mu$m and diameter about 50 to 200 nm, according to the measurements made in the close-up view.
 Each tungsten powder stood as independent growth site (Fig.~\ref{fig:sga}) with island-layer growth on the substrates, a common feature without using tungsten powder as seed under current experimental conditions.
 It was occasionally observed that NWs growth was initiated adjacent some tungsten powders.
-We suspect that this phenomenon was correlated to the local trap of vapor flow since it was more often found among the enclosed area by tungsten powders.
-We also found that the diameter of NWs decrease as the distance between powders and upstream edge increases.
+This phenomenon was correlated to the local trap of vapor flow since it was more often found among the enclosed area by tungsten powders.
+It is also found that the diameter of NWs decrease as the distance between powders and upstream edge increases.
 This is a combination effect of lower temperature and reduced \ce{WOx} growth species supply.
@@
 \citeauthor{Thangala2007} reported that a decrease in NW density with increasing substrate temperature, and an increase of NW density with increasing partial pressure of oxygen.\cite{Thangala2007}
+
+% seeded edx 
+\begin{figure}[htb]
+\centering
+\includegraphics[width=0.5\textwidth]{wo3_seed_edx}
+\caption[Composition analysis on seeded growth \ce{WO3} NWs]{EDX spectroscopy on seeded growth \ce{WO3} NWs.}
+\label{fig:woedx}
+\end{figure}
+\gls{edx} analysis on the seeded growth \ce{WO3} NWs is shown in Fig.~\ref{fig:woedx}.
+Only W and O elements were detected on the NW array.
+The background level from 3 to 8 keV was a manifestation of the continuous components of W X-ray spectrum.
+
 % sg raman xrd
@@
 \centering
-\subfloat[]{\label{fig:sgxrd}\includegraphics[width=0.45\textwidth]{wox_xrd_1}}\hspace{0.04\textwidth}
+\subfloat[]{\label{fig:sgxrd}\includegraphics[width=0.45\textwidth]{xrd_cs_before}}\hspace{0.04\textwidth}
 \subfloat[]{\label{fig:sgram}\includegraphics[width=0.45\textwidth]{wox_raman_1}}
@@
 Fig.~\ref{fig:sgxrd} is the XRD spectrum of one typical sample.
-The peaks under circular symbol were identified to be the monoclinic \ce{WO3} phase (ICDD PDF 01-083-0950,\emph{a}=7.30084\AA, \emph{b}=7.53889\AA, \emph{c}=7.6896\AA, $\beta$=90.8920$^\circ$), while the peak under the triangular symbol was indexed to cubic tungsten phase (ICDD PDF 04-16-3405, \emph{a}=3.157\AA).
-This metallic core was anticipated considering the oxygen flow levels in previous oxidation experiment and the seeded growth (Fig.~\ref{fig:pdoxy}).
-Micro-Raman scattering spectroscopy was performed on as-synthesized sample as well.
+The peaks under circular symbol were identified to be the monoclinic \ce{WO3} phase (ICDD PDF 01-083-0950, \emph{a}=7.30084 \AA, \emph{b}=7.53889 \AA, \emph{c}=7.6896 \AA, $\beta$=90.89$^\circ$), while the peak under the triangular symbol was indexed to cubic tungsten phase (ICDD PDF 04-16-3405, \emph{a}=3.157 \AA), in agreement with the EDX analysis (Fig.~\ref{fig:woedx}).
+This means that during the \ce{WO3} seeded growth of 4 h heating at 1000 \si{\degreeCelsius}, the tungsten powder in downstream low temperature region (600-700 \si{\degreeCelsius}) is not entirely oxidized.
+Micro-Raman scattering spectroscopy was performed on the as-synthesized sample as well.
 During Raman examination, the laser spot was carefully focused onto the NWs on powders and several inspections on different positions were observed to ensure the reproductivity of spectra data.
-As shown in Fig.~\ref{fig:sgram}, five distinct bands were well resolved, with its peaks located at 131, 265, 327, 711 and 803 \si{cm^{-1}}, respectively.
-This pattern was typical features of \ce{WO3}, consistent with previous study.\cite{Salje1975a,Dixit1986} The high background level probably arise from the metallic core.
+As shown in Fig.~\ref{fig:sgram}, five distinct bands were well resolved, with peaks located at 131, 265, 327, 711 and 803 \si{cm^{-1}}, respectively.
+This pattern was typical features of \ce{WO3}, consistent with previous study.\cite{Salje1975a,Dixit1986} The high background level probably arises from the metallic core.
 % sg tem
@@
 \caption[Characterization of \ce{WO3}: TEM]{TEM graphs of as-prepared NWs.
-(a) TEM image of one nanowire, the diameter is about 40 nm.
+(a) TEM image of one nanowire with diameter about 40 nm.
 (b) HRTEM images showing the spacing is 0.38 nm, corresponding to (002) plane distance.}
@@
 
-We also examine the as-synthesized NWs using TEM.
 TEM specimen was prepared by using carbon grid to slightly scratch the as-grown sample.
-One can also disperse the NWs into acetone and then drop cast onto TEM grids.
 Fig.~\ref{fig:woseedtem1} shows the feature of majority NWs.
-The growth direction is determined to be perpendicular to (002) plane, similar to previous reports.
-The streakings in SEAD pattern presumably arise from stacking defaults.
-We also find some NWs exhibit high crystalline quality, as revealed by the TEM analysis in Fig.~\ref{fig:woseedtem2}.
+The growth direction is determined to be perpendicular to (002) plane.
+The streaking in SEAD pattern presumably arises from stacking defaults during \ce{WO3} NW growth.
+This study also found some NWs exhibit high crystalline quality, as revealed by the TEM analysis in Fig.~\ref{fig:woseedtem2}.
+The NW grew normal to (002) plane with a measured lattice spacing of 3.79 \AA, which is favorably compared to the XRD peak at $23.07^\circ$ (7.7103 \AA).
 The sharp SEAD pattern and clear phase contrast in HRTEM demonstrated are both strong evidence of good crystallinity.
-This formation indicated our growth parameters have promising potential to obtain highly crystalline \ce{WO3} NWs.
+This formation indicated current growth parameters have promising potential to obtain highly crystalline \ce{WO3} NWs in large scale.
 
@@
 
-We would like to discuss a little more on the dispersion of \ce{WO3} NWs, since the stability of \ce{WO3} dispersion is important for its applications.
-\citeauthor{Kozan2008} studied the stability of \ce{WO3} in various polar solvents such as acetone, isopropanol(IPA), ethanol, 1-methoxy-2-propanol (1M-2P) and N-dimethylformamide(DMF).\cite{Kozan2008} High power ultra-sonication was applied for about 2 minutes followed by a low power ultrasonic bath for 15 minutes.
-The the solvent was left to sedimentation.
-Samples was drawn out with pipette and transferred to clean substrate for observation.
-It is suggested that bundled NWs aggregates in 1M-2P seem to breakup at the outer branches to a small extent and turn into slightly more compact aggregate, providing well-dispersed stable suspension.
-Subsequently, this suggests we could harvest the as-grown nanowires by a solution ultra-sonication method.
-Generally there will be metallic tungsten in the core region of powder particles.
-The separation of NWs could be done via the route reported by \citeauthor{Kumar2008}, where separation by sonication in 1-methoxy 2-propanol followed by gravity sedimentation.\cite{Kozan2008}
-
-%\textbf{Growth mechanism}
-
-In regarding to the formation of NWs on tungsten powder itself, we assume the driving force is related to interfacial strain between W and \ce{WOx}.
-Oxidation of tungsten proceed slowly at room temperature and an oxide layer of $100 \AA$  was found.\cite{Warren1996} The tungsten powder used in current study would be covered by a thin oxide layer as well.
+In regarding to the formation of NWs on tungsten powder itself, this study assumes the driving force is related to interfacial strain between W and \ce{WOx}.
+Oxidation of tungsten proceed slowly at room temperature and an oxide layer of 100 \si{\angstrom} was found on the surface of tungsten foils.\cite{Warren1996} The tungsten powder used in current study would be covered by a thin oxide layer as well.
 During oxidation, different oxidation rates exist for different crystallographic orientations on the tungsten powder.
-Oxidation occurring at boundaries and defects are preferred.\cite{You2010} Compressive strain will gradually accumulate at the tungsten oxide/tungsten interface, which might limit the diffusion rate of oxygen at temperature lower than 500 \si{\degreeCelsius}.\cite{tungsten1999} At elevated temperature, cracks will primarily occur, as observed in Fig.~\ref{fig:pdtemp}.
-When heated up, tungsten and the oxide shell will probably relax the strain by converting into substoichiometric NWs, a similar process as suggested by \citeauthor{Klinke2005} in the chemically induced strain growth of tungsten oxide NWs.\cite{Klinke2005} It is worth noting that tungsten oxide nanowires could also formed when \ce{WO3} is reduced.\cite{Sarin1975} We speculate that the elongation of \ce{WOx} is thermodynamically favorable during the conversion from metallic tungsten to tungsten oxide as well.
-Another possible formation  mechanism of NWs on tungsten powder is a local evaporation-condensation process.
+Oxidation occurring at boundaries and defects are preferred thermodynamically.\cite{You2010} Compressive strain will gradually accumulate at the tungsten oxide/tungsten interface, which might limit the diffusion rate of oxygen at temperature lower than 500 \si{\degreeCelsius}.\cite{tungsten1999} At elevated temperature, cracks will primarily occur, as observed in Fig.~\ref{fig:pdtemp}.
+When heated up, tungsten and the oxide shell will probably relax the strain by converting into sub-stoichiometric NWs, a similar process as suggested by \citeauthor{Klinke2005} in the chemically induced strain growth of tungsten oxide NWs.\cite{Klinke2005} It is worth noting that tungsten oxide nanowires could also formed when \ce{WO3} is reduced.\cite{Sarin1975} The elongation of \ce{WOx} is thermodynamically favorable during the conversion from metallic tungsten to tungsten oxide as well.
+Local evaporation-condensation process might also contribute to the formation of NWs on tungsten powder.
 
@@
 External supply of growth species will condense onto the powders and substrate simultaneously, promoting the elongation of NWs on power as well as resulting island-layer growth on substrate.
-We found that the local NW density in oxidation experiment was much higher than that of seeded growth.
+The local NW density in oxidation experiment was much higher than that of seeded growth.
 It is reasonable to presume that during seeded growth, several NWs in a small region on powder will coalescence, as evidenced by the bundled structures.
-At last, we point out that when low purity tungsten powder (3N) in our stock was used as source, sodium tungsten oxide nanowires were found to be dominant in the final product.
-The details have been discussed in Section.~\ref{sec:nawox}.
-It seems surprising that when 3N powder was used as seeds, only \ce{WO3} nanowires was obtained.
-We attribute this result to the lower temperature and significantly reduced amount of 3N powder used in the seeded growth, compared with the conditions in another study.
+At last, the author would like to point out that when low purity tungsten powder (3N) was used as source, sodium tungsten oxide nanowires were found to be dominant in the final product.
+The details have been published.\cite{Sheng2014} It seems surprising that when 3N powder was used as seeds, only \ce{WO3} nanowires were obtained.
+This result was attributed to the lower temperature and significantly reduced amount of 3N powder used in the seeded growth, compared with the conditions used in Ref.\cite{Sheng2014}.
 The source material in seeded growth is not limited to high purity tungsten powder.
-Instead, any material that could produce appropriate growth vapor could be employed, indicating the versatility of our approach.
+Instead, any material that could produce appropriate growth vapor could be employed, indicating the versatility of this approach.
 
-%FG
-As shown in Fig.~\ref{fig:wogrowsf}b, we use two substrates in flow growth, each of which is approximate 12 mm long.
-Substrate 1 (Sub1) is located at 6.75 to 7 inch (See Fig.~\ref{fig:wogrow} horizontal axis), and substrate 2 (sub2) is placed in close vicinity of downstream end of sub1.
-Source (4N5 and 5N powder) is located at 5 inch, and 0.3 sccm \ce{O2} is used to reduce the \ce{WO_x} vapor pressure.
-Deposition on sub1 is characterized by dense layer, similar to those shown in Fig.~\ref{fig:wox4n5}b.
-However, deposition on sub2 (Fig.~\ref{fig:sg1}) is in sharp contrast to that shown in Fig.~\ref{fig:wox4n5}c, although they are both located in the low temperature region of reaction chamber.
-The NW density is dramatically increased in flow growth layout.
+\subsection{Tungsten Oxides: Misc}
+
+Two interesting approaches for \ce{WO3} NW growth were found during this study, both of which can produce \ce{WO3} NWs with its own merit.
+The first one is related to the vapor flow dynamic in the deposition region.
+As shown in Sec.~\ref{sec:nawox}, ordinary transport growth using high purity W power mostly leads to thin film growth on one substrate of 1 in long.
+However, it was found that when two shorter substrates were closely placed together, the \ce{WO3} NW yield was significantly enhanced in the second substrate located in lower temperature region.
+For instance, substrate 1 (Sub1) is located at 6.75 to 7 inch (Fig.~\ref{fig:wogrow} horizontal axis on page~\pageref{fig:wogrow}), and substrate 2 (sub2) is placed in close vicinity of downstream end of sub1.
+W source moves to 5 inch, and 0.3 sccm \ce{O2} is used to reduce the \ce{WO_x} vapor pressure.
+Deposition on sub1 is characterized by thin film, similar to those shown in Fig.~\ref{fig:wox4n5}b.
+However, deposition on sub2 (Fig.~\ref{fig:fg1}) is in sharp contrast to that shown in Fig.~\ref{fig:wox4n5}c, although they are both located in the low temperature region of reaction chamber.
+The NW density is dramatically increased.
 The NWs have length about 1 to 2 $\mu m$ and diameter about 200 nm.
-Close-up view (inset of Fig.~\ref{fig:sg2}) show the NWs have clear facets, implying its high crystalline quality.
+Close-up view (inset of Fig.~\ref{fig:fg2}) shows the NWs have clear facets, implying its high crystalline quality.
 % fg sem
@@
 \centering
-\subfloat[]{\label{fig:sg1}\includegraphics[width=0.45\textwidth]{wox_flow1}}\hspace{0.04\textwidth}
-\subfloat[]{\label{fig:sg2}\includegraphics[width=0.45\textwidth]{wox_flow2}}
+\subfloat[]{\label{fig:fg1}\includegraphics[width=0.45\textwidth]{wox_flow1}}\hspace{0.04\textwidth}
+\subfloat[]{\label{fig:fg2}\includegraphics[width=0.45\textwidth]{wox_flow2}}
 \caption[Characterization of flow growth \ce{WO3}: SEM]{ (a) Low magnification SEM image showing dense array of NWs (b) High magnification SEM image of NWs grew out of layer and close-up view on individual wire.}
-\label{fig:fgsem}
+\label{fig:wogrowsf}
 \end{figure}
+The growth mechanism here can be explained by aforementioned VS process as well.
+Both local flow and temperature play an vital role in the formation of dense NW array.
+Splitting one substrate into two presumably introduces some fluctuation in the vapor flow.
+It is well known that in lamellar flow region, there is a velocity boundary above the side wall.
+In spite of the high crystalline quality, the \ce{WO3} is not long enough and yield is limited by the evaporation of source materials; therefore this approach is not seriously pursued in this study.
+
 %TEM to be done on D8.
@@
 
-The growth mechanism stay the same as aforementioned VS process.
-Both local flow and temperature play an vital role in the formation of dense NW array.
-Splitting one substrate into two presumably introduces some fluctuation in the vapor flow.
-It is well known that in lamellar flow region, there is a velocity boundary above the side wall.
-
 \section{Summary}
@@
 to be added, NaOH WO3 results. 
-
-%\printbibliography  %  comment out when assembling
-%\input{../end.tex} %  comment out when assembling
+A systematical investigation of \ce{WO3} NW growth using W powders as precursor in CVD method was performed.

### 2014-09-28 ch-wox/part1.tex
outline adjusted 50%

@@
 Therefore the exact mechanism in \ce{WO_x} still requires further investigation.
+
+\iffalse
 The author believe the resolution to a large extent depends on the phase transitions, as discussed in Section.~\ref{sec:wonawo}.
+\fi
 
@@
 \ce{WO3} is wide gap n-type semiconductor with valence band top featuring $2p$ states of oxygen and conduction band bottom arising primarily from $5d$ states of tungsten with some mixing of oxygen $2p$ states.\cite{Gillet2004} \citeauthor{Migas2010a} maintained there is essentially identical band dispersion near the gap region in case of $\epsilon$-\ce{WO3}, $\delta$-\ce{WO3}, $\gamma$-\ce{WO3} and $\beta$-\ce{WO3}.\cite{Migas2010a} When there is oxygen vacancy, the Fermi level moves into the conduction band and the gap shrinks by about 0.5 eV.
-\citeauthor{Migas2010a} also pointed out the flat bands at VBM and CBM could lead to poor transport of holes and electrons, thus may compromising the function in photoelectrochemical cells.
+\citeauthor{Migas2010a} also pointed out the flat bands at \gls{vbm} and \gls{cbm} could lead to poor transport of holes and electrons, thus may compromising the function in photoelectrochemical cells.
 

### 2014-09-28 misc/draft.tex
outline adjusted 50%

@@
 \subsection{not used}
+
+This approach is essentially the same as previous studies where tungsten foils was used as substrate.The advantage of this method is W powder cost much less than a whole piece of foil, and provide more surface area than W foil in the same volume.
+
+ The FG method utilizes the flow dynamics of our CVD apparatus. We will discuss both of them in details.
+We would like to discuss a little more on the dispersion of \ce{WO3} NWs, since the stability of \ce{WO3} dispersion is important for its applications.
+\citeauthor{Kozan2008} studied the stability of \ce{WO3} in various polar solvents such as acetone, isopropanol(IPA), ethanol, 1-methoxy-2-propanol (1M-2P) and N-dimethylformamide(DMF).\cite{Kozan2008} High power ultra-sonication was applied for about 2 minutes followed by a low power ultrasonic bath for 15 minutes.
+The the solvent was left to sedimentation.
+Samples was drawn out with pipette and transferred to clean substrate for observation.
+It is suggested that bundled NWs aggregates in 1M-2P seem to breakup at the outer branches to a small extent and turn into slightly more compact aggregate, providing well-dispersed stable suspension.
+Subsequently, this suggests we could harvest the as-grown nanowires by a solution ultra-sonication method.
+Generally there will be metallic tungsten in the core region of powder particles.
+The separation of NWs could be done via the route reported by \citeauthor{Kumar2008}, where separation by sonication in 1-methoxy 2-propanol followed by gravity sedimentation.\cite{Kozan2008}
 
@@
 
-\subsection{used}
+\subsection{not used}
 
@@
 The peaks under circular symbol were identified to be the monoclinic \ce{WO3} phase (ICDD PDF 01-083-0950, \emph{a}=7.30084 \AA, \emph{b}=7.53889 \AA, \emph{c}=7.6896 \AA, $\beta$=90.89$^\circ$), while the peak under the triangular symbol was indexed to cubic tungsten phase (ICDD PDF 04-16-3405, \emph{a}=3.157 \AA), in agreement with the EDX analysis (Fig.~\ref{fig:woedx}).
-This means that during the \ce{WO3} seeded growth of 4 h heating at 1000 \si{\degreeCelsius}, the tungsten powder in downstream low temperature region (600 -- 700 \si{\degreeCelsius}) is not entirely oxidized.
+This means that during the \ce{WO3} seeded growth of 4 h heating at 1000 \si{\degreeCelsius}, the tungsten powder in downstream low temperature region (600-700 \si{\degreeCelsius}) is not entirely oxidized.
 Micro-Raman scattering spectroscopy was performed on the as-synthesized sample as well.

### 2014-09-28 misc/SI_thesis.tex
paper draft and supporting info tidy up

--- 2014-09-27 misc/draft.tex
@@
-\chapter{paper draft}
+\chapter{intro}
+
+Concentration of charge carrier $n$ is related to gate voltage $V_g$ by:
+\[
+n = \frac{\epsilon_0 \epsilon V_g}{ed}
+\]
+where $\epsilon_r = \epsilon_0 \epsilon$ is dielectric constant of gate materials.
+
+intrinsic silicon equilibrium charge carrier concentration at RT is $n_i = p_i = 1.5 \times 10^{10} cm^{-3}$, much smaller than silicon atoms density as $5\times 10 ^{22} cm^{-3}$.
+
+The average distance between dopant atoms is cubed root of concentration, $d = (10^{18} cm^{-3})^{-1/3} = 10nm$.
+
+The electron mobility $\mu_n = 1500 cm^2/V\cdot sec $ at RT for Si, and hole mobility $\mu_p = 450 cm^2/V\cdot sec$ at RT.
+
+for p-type silicon, when the conductivity $\sigma = 1 (ohm cm )^{-1}$, the doping level is
+$N_A = \frac{\sigma}{q \mu_p}= 1 / (1.6E-19 \times 450) = 1.4E16 cm^{-3}$.
+
+Built-in voltage $V_0 = \frac{kT}{q}ln(N_A N_D/n_i^2)$, depletion region width $W = \sqrt{\frac{2 \epsilon_{Si} V_0}{q}(1/N_A + 1/N_D)}$, where $\epsilon_{Si} = 11.7 \epsilon_0$.
+When applying external field, depletion width $W = \sqrt{\frac{2 \epsilon_{Si} (V_0 - V) }{q}(1/N_A + 1/N_D)}$
+
+The capacitance of p-n junction is $C = A \sqrt{\frac{q \epsilon_{Si}}{2(V_0 -V)}(N_D N_A/(N_A + N_D))}$.
+
+\iffalse
+Materials that human can make define the age they live in.
+From Stone Age to Bronze Age and Iron Age, people evolve as mastering more and more sophisticated techniques of manipulating metals, such as alloying and annealing.
+Obtaining extreme high purity of silicon brings us into Information Age.
+Future is difficult to predict.
+But nanotechnology is one direction that we can not ignore.
+According to \gls{nni}, \gls{nanotechnology}.
+This definition alludes that dimension comes before compositions.
+It is often related to the quantum confinement or surface area in nanomaterials, which we will later revisit with specific scenario.
+
+There are three states of matter under usual conditions: solid,liquid and gas.
+Solids materials could be further categorized into five groups: metals, ceramics, polymers, semiconductors, and composites.\cite{William2009} This classification is based on both composition and mechanical, electrical, and thermal properties as well as the associated functionality(i.e., \gls{ceramics} are typically hard yet brittle, insulating to electricity and resistant to heating).
+
+\fi
+
+\iffalse
+
+We have synthesized \gls{tmo} and \gls{tmdc} at nanoscale, measured their crystalline structures and optical properties and demonstrated some devices assembled using as-synthesized nanomaterials.
+We aim to illustrate that by nanoengineering these \gls{tmo} and \gls{tmdc}, enhanced performances over their bulk states could be expected and new properties will arise.
+In the remaining sections of this chapter, we will discuss some general perspectives of nanomaterials, the growth apparatus and characterization methods that apply to all experiments done in this work.
+Then chapter 2 will focus on growth of \ce{WO3} and its derivative.
+We employed thermal \gls{cvd} to synthesize \ce{WO3} \gls{nw}, and we investigated the role of impurity in tungsten metallic powders, during which we observed a new state of sodium tungsten oxides: \ce{Na5W14O44} nanowires.
+We also found a method to potentially obtain large yield of \ce{WO3} \gls{nw}.
+Chapter 3 will concentrate on \ce{MoO3}.
+We explored two different growth mechanism of \ce{MoO3}:\gls{vs} and \gls{vls}.
+We discovered that alkaline oxides can be used as catalyst to grow two distinct \ce{MoO3} morphologies: nanobelts and towers.
+We further demonstrated the application of as-synthesized \ce{MoO3} nanomaterials in electrochromic devices.
+In chapter 4 we discuss  We synthesized  and inspected the growth of \gls{fl} \ce{WS2}.
+Chapter 5 will conclude with an overall summary.
+
+\fi
+\section{crystal growth}
+
+Nucleation is a process of generating a new phase from a metastable old phase, where the Gibbs energy per molecule of the bulk of the emerging new phase is less than that of the old phase.
+
+General CVD knowledge, substrate preparation, and\cite{MichealK.Zuraw2003}
+
+\section{band and bond}
+
+Solid and orderliness.
+
+Two theories arise to describe the outer shell electrons and to correlate the structure and physical properties: \gls{cft} and band theory.\cite{Goodenough1971} \gls{cft} assumes weak interaction between neighboring atoms and localization of electron towards parent atom, whereas band theory assumes that electron is shared equally by all nuclei and therefore a many-electron problems follows.
+Description of a single electron in periodic potential fail to treat the electron correlations adequately, as the interaction between atoms becomes weaker.For transition metals, $s$ and $p$ electrons are well described by a collective-electron model, while the 4f or 5f electrons are tightly bound to nuclei and screened from the neighboring atoms by 5s, 5p or 6s, 6p core electrons, hence it matches well with a localized-electron model.
+d electrons show intermediate character.
+
+\chapter{experimental}
+
+\section{diffuse reflection}
 
@@
 
-\citeauthor{Morandi2005} studied the absorbance and diffuse reflectin of \ce{MoO3} and \ce{WO3} thin films using FT-IT and UV-Vis spectroscopy.
+\citeauthor{Morandi2005} studied the absorbance and diffuse reflection of \ce{MoO3} and \ce{WO3} thin films using FT-IR and UV-Vis spectroscopy.
 The observed absorption in visible and middle IR region were attributed to oxygen defects induced donor levels.\cite{Morandi2005}
@@
 The ratio between absorption and scattering, not the absolute value of each quality, determines the reflection features.
-\section{iffalse}
+
+\iffalse
+
+hemispherical reflectance, 
+diffusive reflectance is a mathematical artifice without direct physical meaning.
+
+p332-338
+
+the reflecting power associated with a specular-type process is often termed reflectivity, while reflectance is the analogous term for diffusely reflected radiation.
+This two types of reflection are present simultaneously.
+
+Cauchy formula, empirical equation which has subsequently been placed on a firm theoretical basis.
+
+intensity for a complex quantities is obtained by multiplying the complex conjugate.
+
+For strongly absorbing materials, the reflected light is complementary to the color of light transmitted by it, such as gold transmission is green;
+
+For the weakly absorbing substances of rough surface, it will appear the same color by transmission or reflection.
+
+penetration depth is wavelength dependent $d = \frac{In2 \lambda}{2\pi \sqrt{\sin^2\theta_i - n^2}}$, longer wavelength penetrated further than did shorter wavelength. attenuated total reflectance,
+
+thin film, amorphous, mean free path of electron is diminished, and porous in structure. The maxwell-garnett theory provides a satisfactory explanation, where free electron density is reduced.
+
+diffuse reflection: $I = I_0 \exp(-\epsilon d)$, Lambert cosine law formulated. multiple scattering by individual particles. 
+$R_tot = \alpha R_sp + (1- \alpha) R_diff $,
+
+multiple scattering of diffuse radiation in a medium composed of closely packed particles.
+
+\[
+\log{f(r_\infty) = \log{k} - \log{s}}
+\]
+
+It is concluded that the KM function can be used to obtain the characteristic color curve of a given sample only in the limit of small total absorption.
+
+by mixing the sample with an abundance of the reflectance standard, the regular reflection is extensively eliminated.
+
+The color of an object depends on the spectral composition of the source.
+The color of many light sources can be specified in terms of the temperature to which a blackbody radiator must be heated in order to achieve a color match for the source, which is known as color temperature.
+
+integrating sphere: the intensity at any part of the sphere, due to the reflected light is a measure of the total flux from a particular source, independent of the spatial distribution or location of the source on the sphere.
+
+substitution method, comparison method,
+
+\fi
+\section{tem text}
 
@@
 close approach the single-atom level.
-well suited to, energy-loss electrons cause Kikuchi lines to arise in DPs.
+energy-loss electrons cause Kikuchi lines to arise in DPs.
 Ionized atom enters excited state,
@@
 
-The illumination can be considered as incoherent (adding intensity) if the object is self-luminous, or if illminated from all direction.
+The illumination can be considered as incoherent (adding intensity) if the object is self-luminous, or if illuminated from all direction.
 
@@
 
-And after interacting with specimen, the energy spread of transmitted E-beam becomes about 20eV, which will limit the resolution more than does the spherical aberration.
+And after interacting with specimen, the energy spread of transmitted E-beam becomes about 20 eV, which will limit the resolution more than does the spherical aberration.
 
@@
 
+\section{raman}
+
 \iffalse
@@
 
-\iffalse
+\chapter{wo3}
+metal oxide contact on work function and band structure.\cite{Greiner2013}
 
-hemispherical reflectance, 
-diffusive reflectance is a mathematical artifice without direct physical meaning.
+\citeauthor{Wang2009a} mentioned that amorphous \ce{WO3} can only be used in lithium-based electrolytes due to its in-compact structure and high dissolution rate in acidic electrolyte solutions.
+Electrochromic materials that can endure acidic electrolytes without degradation should be developed.
+Crystalline \ce{WO3} nanostructures with their much denser structures and small particle sizes are promising to be used as suitable electrochromic material in acidic electrolytes.
 
-p332- 338
+\subsection{polarons}
 
-the reflecting power associated with a specular-type process is often termed reflectivity, while reflectance is the analogous term for diffusely reflected radiation.
-This two types of reflection are present simultaneously.
+The concept of polaron was first proposed by Landau in 1933.
+In ionic or highly polar crystals, such as II-VI semiconductors, alkali halides and transition metal oxides, the Coulomb interaction between a conduction electron and the lattice ions results in a strong electron-phonon coupling.
+A new quasi-particle, virtual phonon, can be defined corresponding to the effect of electron pulling nearby positive ions towards it and pushing nearby negative ions away.
+The electron and its virtual phonons, taken together, can be treated as a new composite particle, called an electron polaron; the hole polaron is defined analogously.
+\cite{Devreese1996}
 
-Cauchy formula, empirical equation which has subsequently been placed on a firm theoretical basis.
+the electrical conductivity is given by $\sigma = n e \mu$, where $n$ is the density of free carriers, $\mu$ is their mobility and $e$ is electronic charge.
+The mobility is given by $\mu = e\tau/m^*$ with $\tau$ is carrier resistivity relaxation time and $m^*$ is the carrier effective mass.
 
-intensity for a complex quantities is obtained by multiplying the complex conjugate.
+\section{ECD}
 
-For strongly absorbing materials, the reflected light is complementary to the color of light transmitted by it, such as gold transmission is green;
+Characterization of ECD (work like a thin-film batteries) includes transmission measurement and associated EC calculation, charge-discharge time, current-time curve and the fitting of obtained data.
 
-For the weakly absorbing substances of rough surface, it will appear the same color by transmission or reflection.
+The coloration efficiency (CE) represents the change in the optical density (OD) per unit charge density ($Q/A$, in units of \si{\cm^2\per\coulomb}) during switching and can be calculated according to the formula:
+\begin{equation}
+CE = \frac{\Delta~OD}{(Q/A)} [cm^2/C],
+\end{equation}
+where OD = $log(T_{bleach}/T_{color})$. The EC and optical density depend on the wavelength and are usually higher in the near IR than in the visible region.
+Using Ohm's law($U_s = IR = RQ/t_s$) with switch voltage $U_s$, resistance R and surface area A, switching time $t_s$ could be estimated as
+\begin{equation}
+t_s = \Delta~OD\cdot A \cdot R /(CE\cdot U_s).
+\end{equation}
 
-penetration depth is wavelength dependent $d = \frac{In2 \lambda}{2\pi \sqrt{\sin^2\theta_i - n^2}}$, longer wavelength penetrated further than did shorter wavelength. attenuated total reflectance,
+The degree of \ce{H^+} intercalation, $x$, is determined by integrating cathodic current, and given by
+\begin{equation}
+x = \frac{Q}{F}\frac{M_\ce{WO3}}{m_f}
+\end{equation}
+where $m_f$ is the mass of film, $M_\ce{WO3}$ is the molar mass of \ce{WO3*1/3H2O}, and F is Faraday's constant.
+The color center density, $c$, is then obtained using formula
+\begin{equation}
+c= \frac{x M_\ce{WO3}N_A}{\rho}
+\end{equation}
+where $N_A$ is Avogadro number, $\rho$ is density of film.
 
-thin film, amorphous, mean free path of electron is diminished, and porous in structure. The maxwell-garnett theory provides a satisfactory explanation, where free electron density is reduced.
+battery and ECD.\cite{Granqvist2012} electrolyte: PVB (poly vinyl buteral).
+alternative materials and design: organic, Prussian Blue as EC materials, metal hydrides, suspended particle device, liquid crystal, electroplating,
+challenges: large area nanoporosity, transparent conducting contact, electrolyte with good ionic conductivity and poor electronic conductivity, stable under UV; assembly and large scale manufacturing;
+cathodic coloration:
+anodic coloration:
+The coloration mechanism: \ce{MO6} octahedrons lead to $e_g$ and $t_{2g}$ level and ion channelling.
+ref54,60,65,66,200,209,
 
-diffuse reflection: $I = I_0 \exp(-\epsilon d)$, Lambert cosine law formulated. multiple scattering by individual particles. 
-$R_tot = \alpha R_sp + (1- \alpha) R_diff $,
+\ce{WO3} as cathodic and either polyaniline(PANI) or Prussian white (PW) as anodic electrochromic half cells. \cite{Heckner2002}
 
-multiple scattering of diffuse radiation in a medium composed of closely packed particles.
-
-\[
-\log{f(r_\infty) = \log{k} - \log{s}}
-\]
-
-It is concluded that the KM function can be used to obtain the characteristic color curve of a given sample only in the limit of small total absorption.
-
-by mixing the sample with an abundance of the reflectance standard, the regular reflection is extensively eliminated.
-
-The color of an object depends on the spectral composition of the source.
-The color of many light sources can be specified in terms of the temperature to which a blackbody radiator must be heated in order to achieve a color match for the source, which is known as color temperature.
-
-integrating sphere: the intensity at any part of the sphere, due to the reflected light is a measure of the total flux from a particular source, independent of the spatial distribution or location of the source on the sphere.
-
-substitution method, comparison method,
-
-\fi
-
-\section{Data Processing}
-
-The SEM images are cropped using Adobe Photoshop for highlighting the features and fitting into text width.
-To obtain the dimension of specimen, scale bar was measured and compared to the size of interest using ImageJ\cite{Schneider2012} for SEM, TEM images and SAED pattern.
-It is worth noting that ImageJ could directly read the dm3 format generated in Gatan imaging software, which is more productive than the scale bar method.
-
-Various spectra, be it from XRD, EDX, Raman, or UV-Vis, were redraw using Origin Pro 8.0.
-The peak fitting was performed using \emph{Fityk}, a nonlinear curve fitting program specialized in data processing from powder diffraction, chromatography, photoluminescence and photoelectron spectroscopy, infrared and Raman spectroscopy, \emph{etc}.\cite{Wojdyr2010}
-
-\section{wo3}
-
-\subsection{used}
-
-\citeauthor{Chatten2005} also studied the oxygen vacancy in different phases of \ce{WO3}.\cite{Chatten2005}
-
-SG and FG experiments remain essentially the same as that of OT growth, except that in SG additional tungsten powders were distributed onto the receiving substrate, and in FG more than one piece of substrate was employed.
-The modification is schematically illustrated in Fig.~\ref{fig:wogrowsf}.
-More details will be provided when it comes to the discussion.
-% sg fg
-\begin{figure}[htb]
-\centering
-\includegraphics[width=0.5\textwidth]{sg_and_fg.jpg}
-\caption[\ce{WO3} NW growth: SG and FG]{\ce{WO3} NW growth: SG and FG. (a) Seeded growth with additional powders on substrate (b) Flow growth with multiple substrates}
-\label{fig:wogrowsf}
-\end{figure}
-
-With four kinds of W powders and three layouts, we designed the experimental matrix as illustrated in Table.~\ref{tab:matrix}.
-The symbol $\times$ means this combination is covered in this work, and NA means otherwise.
-% Tungsten powders growth design
 \begin{table}[htb]
-\centering
-\caption{Tungsten powders growth design}\label{tab:matrix}
-\begin{tabular}{lccr}
+\caption{Combinations of ECD configuration}\label{tb:ecd}
+\begin{tabular}{lcccr}
 \toprule
- & Ordinary Transport & Seeded growth & Flow growth \\
+TC(both side) & electrochromic & ion conductor & counter electrode  & reference\\
 \midrule
-3N   &  $\times$ & NA &  NA   \\
-3N5  &  $\times$ & NA &  NA   \\
-4N5  &  $\times$ & $\times$ & $\times$ \\
-5N   &  $\times$ & $\times$ &  $\times$ \\
+ITO &  \ce{WO3} & \ce{H^+\hyphen} polymer & PANI &\citeauthor{Heckner2002}\\
+FTO &  \ce{WO3} & \ce{K^+\hyphen} polymer & PW &\cite{Heckner2002}\\
+ITO & \ce{WO3} NWs & \ce{LiClO4\hyphen}PC & none & author design \\
+\ce{Na_xWO3} NWs &\ce{WO3} NWs & \ce{LiClO4\hyphen}PC & none & author design\\
 \bottomrule
@@
 
-We will first present the OT growth results in section~\ref{sec:nawox}, and discuss the other two in section~\ref{sec:sgfg}.
-
-We found the growth using 3N source show distinctive features in comparison to the rest.
-This mainly arise from the higher sodium concentration in 3N source than that in others.
-Therefore we focus on 3N source first, and move on to other latter.
-
-% Na5 raman fitting
-\begin{figure}[htb]
-\centering
-\includegraphics[width=0.6\textwidth]{naxwo_ramfit}
-\caption[\ce{Na5W_{14}O_{44}} Raman fitting]{Multi-peaks Lorentzian fitting on two major peaks region of \ce{Na5W_{14}O_{44}}.
-The peaks sum height difference is caused by different baseline value adopted in each fitting.}
-\label{fig:naworamfit}
-\end{figure}
-
-% W-O bond length
 \begin{table}[htb]
 \centering
-\caption{\ce{W-O} bond length predication}\label{tab:nawobond}
-\begin{tabular}{lccr}
+\caption{Comparison of MoOx ECD}\label{tab:moxecd}
+\begin{tabular}{lcccr}
 \toprule
-peak center & length (\AA) & peak center & length (\AA) \\
+$\lambda$ & $\Delta T$ & $t_c$ & $t_b$ & $CE$  \\
+         (nm) & (\%)    & (s) & (s) & ($cm^2/C$)  \\
 \midrule
-694.6 & 1.900 &  808.6 &  1.821 \\
-745.4 & 1.863 &  911.5 &  1.758 \\
-764.4 & 1.850 &  933.0 &  1.745 \\
-778.7 & 1.840 &   943.5 & 1.740 \\
-788.4 & 1.834 &   965.4 & 1.728 \\
+  \\
 \bottomrule
@@
 
-An empirical formula to relate the Raman peaks and \ce{W-O} bonding lengths \cite{Hardcastle1995} is
-\begin{equation}\label{eq:wobond}
-\nu = 25823 \exp{-1.902\cdot R}.
-\end{equation}
-And the standard deviation of estimating \ce{W-O} bond distance from Raman stretching wavenumber is $\pm0.034$\AA.
-The observed Raman peaks of \ce{Na5W_{14}O_{44}} phase lies at 965, 943, 913, 808, 786, 778, 765, 695 and 107 cm.
-Multi-peaks Lorentzian fitting is preformed to precisely determine the central maximum.
-Good fitting is obtained, as shown in Fig.~\ref{fig:naworamfit}.
-We then calculated \ce{W-O} bond distance using Eq.~\ref{eq:wobond}, as illustrated in Table~\ref{tab:nawobond}.
-The predicted \ce{W-O} bond length comply very well with the crystallographic value of \ce{Na5W_{14}O_{44}} phase.\cite{Triantafyllou1999a} The 107 peak probably is caused by \ce{Na-O} bond.
-
-\subsection{not used}
-
-\iffalse
-Materials that human can make define the age they live in.
-From Stone Age to Bronze Age and Iron Age, people evolve as mastering more and more sophisticated techniques of manipulating metals, such as alloying and annealing.
-Obtaining extreme high purity of silicon brings us into Information Age.
-Future is difficult to predict.
-But nanotechnology is one direction that we can not ignore.
-According to \gls{nni}, \gls{nanotechnology}.
-This definition alludes that dimension comes before compositions.
-It is often related to the quantum confinement or surface area in nanomaterials, which we will later revisit with specific scenario.
-
-There are three states of matter under usual conditions: solid,liquid and gas.
-Solids materials could be further categorized into five groups: metals, ceramics, polymers, semiconductors, and composites.\cite{William2009} This classification is based on both composition and mechanical, electrical, and thermal properties as well as the associated functionality(i.e., \gls{ceramics} are typically hard yet brittle, insulating to electricity and resistant to heating).
-
-\fi
-
-\iffalse
-
-We have synthesized \gls{tmo} and \gls{tmdc} at nanoscale, measured their crystalline structures and optical properties and demonstrated some devices assembled using as-synthesized nanomaterials.
-We aim to illustrate that by nanoengineering these \gls{tmo} and \gls{tmdc}, enhanced performances over their bulk states could be expected and new properties will arise.
-In the remaining sections of this chapter, we will discuss some general perspectives of nanomaterials, the growth apparatus and characterization methods that apply to all experiments done in this work.
-Then chapter 2 will focus on growth of \ce{WO3} and its derivative.
-We employed thermal \gls{cvd} to synthesize \ce{WO3} \gls{nw}, and we investigated the role of impurity in tungsten metallic powders, during which we observed a new state of sodium tungsten oxides: \ce{Na5W14O44} nanowires.
-We also found a method to potentially obtain large yield of \ce{WO3} \gls{nw}.
-Chapter 3 will concentrate on \ce{MoO3}.
-We explored two different growth mechanism of \ce{MoO3}:\gls{vs} and \gls{vls}.
-We discovered that alkaline oxides can be used as catalyst to grow two distinct \ce{MoO3} morphologies: nanobelts and towers.
-We further demonstrated the application of as-synthesized \ce{MoO3} nanomaterials in electrochromic devices.
-In chapter 4 we discuss  We synthesized  and inspected the growth of \gls{fl} \ce{WS2}.
-Chapter 5 will conclude with an overall summary.
-
-\fi
-
-Therefore we refer their oxides and chalcogenides as \gls{tmo} and \gls{tmdc}.\footnote{Obviously transition metals include many other elements, all of which have partially filled $d$-electron shell.
-But here we use TM to denote W and Mo exclusively.}
-
-Nucleation is a process of generating a new phase from a metastable old phase, where the Gibbs energy per molecule of the bulk of the emerging new phase is less than that of the old phase.
-
-General CVD knowledge, substrate preparation, and\cite{MichealK.Zuraw2003}
-
-The energetic sources are ion bombardment, electron beam, laser ablation, and combustion flame\cite{Rao2011}.
-
-The sol–gel process is a well-known, intensively studied wetchemical technique that is widely used in materials synthesis.
-This method generally starts with a precursor solution (the ``sol") to form discrete particles or a networked gel structure.
-During the course of gelation (aging process), various forms of hydrolysis and polycondensation take place.
-In addition, doped \ce{WO3} was also demonstrated
-The composition and phase of final product highly depend on the synthesis conditions.
-
-We do not discuss tungsten oxide hydrates (\ce{WO3.nH2O}) in this work since the product of thermal CVD approach is not plagued with this complexity.
-It's necessary, however, to deal with hydrated \ce{WO3} in the liquid synthesis routes, as indicated in Section.~\ref{sec:woxgrowth}.
-
-Nonstoichiometric tungsten oxides \ce{WO_x} (i.e. \ce{WO_{2.92}}, \ce{WO_{2.87}}) are known as Magn$\acute{e}$li phases.
-
-Theoretical computation of electronic band structures for \ce{WO_x} proves difficult due to the aforementioned phase transition.
-oxygen deficiency, structure change, electronic properties vary according.
-
-the ubiquity of \ce{WO6} octahedra is essential for not only the optical properties but the ability to insert and extract ions in the EC oxides, due to the tunnels in three dimensions serving as path for transport of small ions.
-The intercalation of hydrogen or alkali ions into \ce{WO3} created electron donor level.
-By absorbing the red part of incident spectrum, electrons at donor level make transition to the conduction band, causing the blue coloration in \ce{H_xWO3}.
-
-its one dimensional (1D) nanostructure has attained intensive research efforts in recent years due to the potential applications in advanced nano-electric and nano-optoelectronic devices.
-
 \begin{quote}
-a viable electrochromic smart window must exhibit a cycling life time \textgreater $10^5$ cycles, corresponding to an operation life at 10 - 20 years.
+a viable electrochromic smart window must exhibit a cycling life time \textgreater $10^5$ cycles, corresponding to an operation life at 10 -- 20 years.
 \end{quote}
 
-\subsection{to be used}
+\citeauthor{Sella1998} studied the optical and structural properties of RF sputtered thin film of \ce{WO3} and \ce{VO2} for electrochromic devices.
+Ionic conductor was built using transparent polymer electrolyte, which was prepared from a solution of 1 M \ce{LiClO4} in propylene carbonate which was mixed with methylmetharcylate (MMA).
+The main characteristics of polymer electrolyte were: viscosity at 25 \si{\degreeCelsius} $\approx$ 12920 Pa.s, conductivity $\approx 10^{-2}-10^{-4}$ \si{\per\ohm\per cm},non-hygroscopic if PMMA concentration \textgreater 30\%.
+A specific counter-electrode layer was not used since the encapsulated polymer electrolyte processes a very high ion storage capacity.\cite{Sella1998}
 
-% band gap table
-\begin{table}[htb]
+The device proposed was reproduced as shown in Fig.~\ref{fig:Sella1998ECD}
+\begin{figure}[htb]
     \centering
-\caption{Tungsten oxides band gap }\label{tab:wo3eg}
-\begin{tabular}{lccr}
-\toprule
-Phase & Experimental (eV) & Theory (eV) &  \\
-\midrule
-amorphous \ce{WO3} & 3.2  & NA &    \\
-monoclinic bulk \ce{WO3} &  2.6   & 1.73\cite{Migas2010a}  &    \\
-tetragonal bulk \ce{WO3} &     & 0.66 \cite{Migas2010a}&    \\
-\bottomrule
-\end{tabular}
-\end{table}
+    \includegraphics[angle=270,width=0.8\textwidth]{Sella1998ECD}
+    \caption{citation, see original captions} \label{fig:Sella1998ECD}
+\end{figure}
 
-W plasma oxidation.\cite{Romanyuk2005} 200nm W coating on Si (100) sub, temperature at RT, 390, and 490 C, oxygen pressure 0.5 Pa, oxidation time for 10 to 3600 s.
-The resultant thickness of \ce{WO3} at RT  and time of 10 s and 3600 s is found to be 0.2 nm and 11 nm respectively.
-
-\[
- d = d_0 exp(kt)
-\]
-
-after fitting, $d_0 = 0.19777$ nm, $k = 0.00112 $ s$^{-1}$, so to oxidize 1nm W coating completely, oxygen plasma time is 1450 s at 0.5 Pa partially pressure; 2 nm for 2000 s.
-
-\ce{WOx} and optical electric field enhancement.
-The enhancement arise from the structure composed of a conductive layer and an insulating layer that are laminated therein.\footnote{US patent 8601610B2} In \ce{WOx} nanorods, the oxygen deficient planes are conductive, each having atomic thickness and separated by several nm \ce{WO3}.
-Localized surface plasmons could possibly exist on these conductive planes.
-Therefore SERS applies and single molecule Raman scattering using a tungsten oxide nanorod has been demonstrated.
-The \ce{W_nO_{3n-1}} ($n \geq 2$) exhibit $\{ 001 \}$ CS structure.
-Chemical formulae corresponding to n=2, 3, 4, 5 and 6 are \ce{W2O5=WO_{2.5}}, \ce{W3O8=W_{2.67}}, \ce{W4O_{11}=WO_{2.75}}, \ce{W5O_{14}=WO_{2.8}}, and \ce{W6O_{17}=WO_{2.83}}, which indicates the existence of a oxygen deficient plane at every n row.
-Actually the value x in \ce{WOx} could almost continuously vary within a range of 2.5 to 3.
-\ce{W_{18}O_{49}=\ce{WO_{2.72}}} is an exception without $\{ 001 \}$ CS structure.
-Moreover, the oxygen deficient planes could extend along directions other than $\{ 001 \}$.
-For instance, the $\{ 102 \}$ CS planes appears in \ce{WOx} where x is within 2.93 to 2.98, and  the $\{ 103 \}$ CS planes for x within 2.87 to 2.93.\cite{Sloan1999}  \citeauthor{Shingaya2013} also synthesized \ce{WS2}-\ce{WO_x} structures and found similar Raman scattering enhancement.
-The x value is estimated by the Raman spectra peaks.\cite{Shingaya2013}(Data not shown in patent)
-
-For photochemical water reduction to occur, the flat-band potential of the semiconductor (for highly doped semiconductors, this equals the bottom of the conductance band) must exceed the proton reduction potential of 0.0 V vs NHE at pH =0.
-\cite{Osterloh2008} flat-band potentials strongly depend on ion absorption (protonation of surface hydroxyl groups), crystallographic orientation of the exposed surface, surface defects, and surface oxidation processes.
-
-\ce{W_{18}O_{49}} Raman, IR shielding.\cite{Guo2012} \cite{Guo2011}
-broad peak between 750-780 cm-1.
-
-\ce{WnO_{3n-1}} NPs. \cite{Frey2001}
-
-WO3-x raman info, the encapsulated WOx core has been investigated in depth.
-several stable phase could occur, including \{001\} CS phases, \{103\} CS phases.
-no evidence of $\gamma$-\ce{W_{18}O_{49}} phase is found.
-The cross-section ($\sigma$) for Raman scattering and the absorption coefficient of the WS2 layers are much larger than those of the suboxide phase encapsulated inside.
-
-WO2:168(w),189(w), 286(vs), 345(w), 423(w), 479(m), 512(m), 599(m),
-617(m) cm-1, and a mode at 781(s) cm-1 which tails to higher energies (w-weak; m-medium; s-strong; vs-very strong).
-
-W5O14: 215, 264, 325, 349, 418, 425,707, and 800 cm-1, 900 maybe
-
-WO3: 808, 719, 275;
-
-W3O8: 870;
-
-no 950 peak indicates no hydrated phases.
-
-\ce{WO_{3-x}} Raman peak at 778. \cite{Deb2007}
-
-% wo3-x phases
-\begin{table}[htb]
-\centering
-\caption{List of \ce{WO_{3-x}} phases}\label{tab:wo3xphase}
-\begin{tabular}{lccccc}
-\toprule
-&&&\multicolumn{3}{c}{Lattice constants \AA} \\
-\cmidrule(l){4-6}
- Symbol    & PDF  & Phase & a & b & c   \\
-\midrule
-\ce{W18O49}  & 00-036-0101 & monoclinic & 18.324 & 3.784 & 14.035  \\
-$\delta$-\ce{WO3}   & $-50 \sim 17$  & triclinic & 7.309 & 7.522 & 7.686  \\
-$\gamma$-\ce{WO3}   & $17 \sim 330$  & monoclinic I & 7.306 & 7.540 & 7.692  \\
-$\beta$-\ce{WO3}    & $330 \sim 740$  & orthorhombic & 7.384 & 7.512 & 3.846  \\
-$\alpha$-\ce{WO3}   & $> 740$  & tetragonal & 5.25 & NA & 3.91  \\
-$h$-\ce{WO3}        &  $<400$  & hexagonal & 7.298 & NA & 3.899  \\
-\bottomrule
-\end{tabular}
-\end{table}
-
-\section{moo3}
-
-\subsection{used}
-
+\chapter{moo3}
 \ce{MoO3}, an alternative interpretation in terms of tetrahedral coordination of Mo atoms is also proposed.
-This is caused by the fact that four of the six surrounding O atom are at distances from 1.67\AA to 1.95\AA, while the remaining two are as far as 2.25 and 2.33\AA.
+This is caused by the fact that four of the six surrounding O atom are at distances from 1.67 \si{\angstrom} to 1.95 \si{\angstrom}, while the remaining two are as far as 2.25 and 2.33 \si{\angstrom}.
 This also stress that the \ce{MOO6} octahedra are rather distorted.
-
-\subsection{to be used}
-
-The refractive index is between $ 2.2\sim 2.4$ along $a$ axis, and $ 2.5\sim 2.8$ along $c$ axis.
-Comparison to the low frequency dielectric constant ($18.0\pm1$) implies a primarily ionic bonding in \ce{MoO3}.\cite{He2003}
-
-\cite{Matar2011} Using electronegativity $\chi$ and chemical hardness $\eta$ to assess electron affinity $E_a$, work function $W_f$, Fermi energy $E_f$ and band gap $E_g$.
-\begin{align}
-\chi &= 0.5(W_f + E_a)\\
-\eta & = 0.5(W_f - E_a)
-\end{align}
-where I is ionization potential and $E_a$ is electron affinity.
-
-Correlation between optical band gap and formation enthalpy; reaction occurs in order to form compounds with a larger gap.
-$E_g = A \exp(0.34E_{\Delta H^0})$, and A adopts different values depending on the metal elements:
-\begin{itemize}
-\item A=0.8 for s and f block elements,
-\item A = 1 for d block elements,
-\item A = 1.35 for p block elements.
-\end{itemize}
-
-\citeauthor{Sreedhara2013} studied the kinetics of photodegradation of methylene blue\footnote{\ce{C16H18N3SCl},319.8 g/mol, MP: 100C accompanied with decomposition \url{http://en.wikipedia.org/wiki/Methylene_blue}} dye by few layer \ce{MoO3}.
-For the photodegradation method, it was stated that `` the samples were collected after the photoreaction had been centrifuged for 5 min to remove the photocatalyst before UV-Vis measurement.''
 
@@
 
-\section{ws2}
+In second state, the one with smaller droplet probably would exhibit faster growth rate in $\langle001\rangle$ direction due to its shortest lattice constant, while the other one endures more growth along$\langle010\rangle$ direction.
+We suspect that the liquid size that induce the tower growth is much larger than that of belts.
+From the final morphology of as-synthesized sample, we find that the above proposed two growth approaches could change into each other, that is belt growth could be initiated on the top of tower growth and vice visa.
+We assume this phenomena arise from the interaction between vapor supply, temperature and the shape of liquid catalyst.
+Or it may just come from the vapor transport of \ce{NaxMoO3}.
+It had been shown by actively engineering the shape of catalysis, the growth direction of  InP NW could be switched between [111] and [100].\cite{Wang2013c} The same mechanism might exist in our case as well.
+For instance, when a belt is sufficient long and it could extend into the low temperature part, where the supply of MoOx vapor is reduced due to the consumption, and the shape of liquid might vary as well.
+Both will result in different absorption and subsequent diffusion rate along and inside the liquid catalyst.
+We also observed that belt growth could initiate from tower growth in reduced time growth.
+Actually this may be one possible mechanism of belts formation.
+
+(The presence of \ce{Na6MoO33} phase is an indirect evidence for the formation of eutectic \ce{Na2MoO4}- \ce{MoO3} binary compounds at growth temperature.
+The bulk phase diagram may not accurately represent the phase transition occurring in catalyst droplet and solid interface.
+And it will usually lead to a significant temperature decrease of eutectic point from the bulk value.
+Nanoparticles do not completely melt and instead act as an active site for reactant absorption and diffusion, leading to a vapor-solid-solid growth mechanism.
+
+In vapor synthesis process, two growth mechanism exists: VS and VLS.
+VS process is widely accepted for the growth of \ce{MoO3}.
+Yet we caution that synthesis conditions should be scrutinized to determine the exact mechanism.
+\citeauthor{Li2002c} suggested a VS mechanism at 700 \si{\degreeCelsius} and VLS at 750 \si{\degreeCelsius} and higher.\cite{Li2002c} \citeauthor{Fibers2007} proposed a modified VS mechanism probably because the deposition occurs on \ce{Al2SiO5} with possible \ce{Al_{0.95}SiNa_{0.06}O_x} involved.
+Therefore temperature and possible impurity could potentially alter the growth mechanism.
+We divide the growth results into two categories: on Si substrate and on non-Si substrate, and describe them respectively.
+We also briefly mention using liquid exfoliation to prepare few layer \ce{MoO3}.
+
+This rectangular shape implies the boundary plane along growth direction (long axis) is (001), in consistency with previous experimental reports\cite{Zeng1998,Li2002b} and theoretical studies.\cite{Firment1983,Cora1997} We also observed different shapes, i.e., elongated hexagonal using similar growth conditions.
+This is not an indication of different growth mode.
+It is a normal thermodynamic fluctuation.
+The growth rates along different crystalline direction of \ce{MoO3} are determined by the free surface energy.
+In fact, (201), (101) and (102) planes have all been observed as terminating planes.\cite{Zeng1998} The stacking rate of \ce{MoO6} octahedra along $a$ and $c$ axis could develop some other ratio.
+And the coexistence of different planes in one growth suggests the similarity of free surface energies between these surfaces.
+In other words, the migration barrier of adatoms on (010) plane is presumably much lower than that on other low index planes due to the Van der Waals interaction nature along [010] direction.
+
+\citeauthor{Hardcastle1990} summarized an empirical formula to relate the Raman peaks and \ce{Mo-O} bonding lengths.\cite{Hardcastle1990} This correlation assumes general form as
+\begin{equation}\label{eq:mobond}
+\nu = A \exp{B\cdot R},
+\end{equation}
+where $A=32895$ and $B=-2.073$ are fitting parameters, R is bond distance in unit of \AA.
+Given a stretching frequency, the resolution for calculated bond distance is $\pm0.016$ \AA.
+Another empirical expression connect the bond valence $s$ and bond distance R: $s(M-O) \approx (R/X)^{-6} $, where X=1.882 when M is Mo, and 1.904 when M is W.
+The valence sum rule could be then used to check the state of Mo cation.
+It should be noticed that not all observed Raman lines could be correlated to a \ce{Mo-O} bond distance by extrapolation of Eq.~\ref{eq:mobond}.
+It is then regarded as a symmetry related vibrational mode, i.e., 820 \si{cm^{-1}} in \ce{MoO3}.
+From the correlation of various Mo compounds, a general conclusion is the lower the stretching frequency for the shortest metal-oxygen bond, the more regular is the structure.
+
+\chapter{tmdc}
+
+CNT chirality by TEM \cite{Zhang1993} TEM chirality of \ce{MoS2} NTs
+
+\ce{WS2} NT transport \cite{Zhang2012c}
+less grain boundary more mobility,
+
+\citeauthor{Ramasubramaniam2011} investigated the band gap tuning in bilayer TMDC materials by applying external $E$ field.
+Similar research has been done for graphene and bilayer boron nitride.
+Semiconductor-metal transition was suggested for \ce{MoS2} and \ce{WS2}, with difference on the CBM and VBM evolution.
+In \ce{MoS2}, the valence-band-splitting cause the A and B excitons in optical absorption measurement.
+Calculation shows that CB and VB are translated toward the Fermi level with increasing E field.
+The external field localized charge along $c$ axis, but delocalized that within the plane normal towards $c$, thereby driving the semi-metal transition.
+It was mentioned that this transition is not anticipated in monolayer \ce{MoS2}.
+It was emphasized that precise band gaps might be different from the author’s results, yet the gap-tuning should be universal.\cite{Ramasubramaniam2011}
+
+\cite{Song2013} \ce{WO3} by ALD, and sulfurized in Ar and \ce{H2S} (10:1) at 1000 C.
+\ce{WS2} layer No and peak intensities ratio under 633nm excitation is correlated.
+It was found the 2LA/A1g is less than 1 for 1L.
+In supporting info 532 nm Raman spectra, the 2LA/A1g is presumably larger than 1 for 1L.
+\ce{WS2} NT on Si NWs is also demonstrated.
+
+\cite{Tenne2010} chemical modification of NTs.
+Functional ligand consists of an anchor group that attaches to the NTs surface and a tail which render them soluble in various solvents.
+PTAS functionalized BN nanotube lead to the formation of stable suspensions in aqueous solutions.
+The strong attachment is formed through $\pi-\pi$ interactions.
+
+inorganic nanotubes review \cite{Tenne2004} , unsaturated bonds number increases as the size of MS2 sheet decreases.
+
+Water splitting materials should process a band gap larger than 1.4 eV, considering both the NHE potential distance and practical application.
+The monolayer \ce{WS2} exhibits direct gap of 1.98 eV.
+Quantum confinement could push the gap separation farther away.
+\cite{wilcoxon1997} \citeauthor{Notley2013} use liquid exfoliation to prepare \ce{WS2} NPs.\cite{Notley2013} Non-ionic surfactant concentration is about 0.1\%w/w.
+Continuously adding surfactant during sonication improves the yield.
+Optimum surface tension is found at about 40 mJ/m$^2$.
+
+G/\ce{WS2}/G stacked solar cell. For lubricant, and surface protection. Absorption $\sim 10^7 m^{-1}$. \cite{Britnell2013}
+
+In Ref\cite{Zeng2013}, single crystal \ce{WS2} growth using \ce{I2} transport was described in supporting info.
+\ce{C24H12K4O8}\footnote{http://www.chemspider.com/Chemical-Structure.24771386.html}
+
+416 peak was prevously assumed to be a combination of LA and TA phonons at K points.
+416 cm raman on WS2. B1u is pressure sensitive. \cite{Staiger2012} also studied pressure dependence.
+
+A1g mode using resonance Raman excitation shows upshift, which is presumably caused by folding induced strains.
+And TEM SAED reveal 3R symmetry.
+We did not observed this upshift of A1g probably due to the large diameter and few layer involved.
+
+Nanotube growth is relatively independent of substrates and FL layer is closely related to substrate. Film growth could provide some insight into the latter scenario.
+
+\section{calculation}
+
+Raman conditions: 0.3 mW, 532 nm, 200 sec acquisition time. photon flux = $0.3E-3\times6.242E+18/1.2398/0.532=2.84E15$
+
+first demonstration of \ce{WS2} NT n-type FET. \cite{Levi2013}
+the importance of contact, and avoiding moisture.
+
+The calculated carrier concentration is about $10^{19}cm^{-3}$, a highly doped semiconductor, possibibly arising from sulfur vacancy.
+
+\ce{WS2} absorption coefficient $10^{-7}m^{-1}$, mean free path of photo-excited charge carriers 1 $\mu m$.
+the wave vector of photon is considerably small than size of BZ, therefore The wave vector of phonon in Raman scattering usually close to zero.
+
+Multiple phonon scattering, For two identical phonons, the corresponding Raman peak in the spectrum is called an overtone of the peak from the corresponding one-phonon process.
+And the wave vector conservation rule is automatically filled, therefore the phonon involved is not limited to BZ center anymore.
+\[
+I(G) \approx \sum_k \frac{\langle f|H_M|b\rangle \langle b|H_{ep}|a\rangle \langle a|H_M|i\rangle}{(E_p - E_k^{\pi *}- E_k^{\pi}-i\gamma)(E_p - E_k^{\pi *}- E_k^{\pi}-i\gamma- \hbar\Omega_{G})}
+\]
+
+\subsection{strain}
+
+$E_{2g}$ mode is strain sensitive.
+
+\citeauthor{Ghorbani-Asl2013} studied the strain in tubular TMDC and found a linear dependence of Raman scattering on strain (3 \si{cm^{-1}} per percentage for $E_{2g}$mode).\cite{Ghorbani-Asl2013}
+
+For 2D materials, strain may be induced by elongation of an appropriate substrate, e.g.
+by uniform mechanical strain, or by using a material with high thermal expansion coefficient and varying the temperature.
+For TMD MWNT, tensile tests have been reported by various groups.
+However, to date, it is not perfectly clear whether inner and outer walls are stretched simultaneously, or rather the outer walls slide on the inner ones.
+The latter hypothesis would result in a broadening of the Raman signals, while the first one would leave the signal widths rather unaffected.
+In any case, there would be a shift of the Raman signals that can serve as precise scale for determining the strain.\cite{Ghorbani-Asl2013}
+
+\citeauthor{Virsek2007} performed a Raman-TEM integrated study on multiwalled \ce{WS2} NT with diameter \textgreater 200 nm.
+The tubes were synthesized using chemical transport method.
+Up-shift of Raman is explained by strain in the walls.
+This shift is not observed in the specimen by sulfurization process of oxides.
+Applied hydrostatic pressure is isotropic,\cite{Staiger2012} while the strain is expected to anisotropic.
+Strain can also be relaxed by chirality.\cite{Virsek2007}
+
+strain effect by first-principles calculations. direct gap is only maintain in a narrow strain range (-1.3 -- 0.3 \%), \cite{Yun2012}.
+
+Semiconducting to metallic transition in \ce{MoS2} at compressive strain of 15\% or tensile strain of 8\%; direct-to-indirect gap transition for 1L \ce{MoS2} at about 2\%. \cite{Scalise2012}
+
+\chapter{to be used}
+
+\cite{Matar2011} Using electronegativity $\chi$ and chemical hardness $\eta$ to assess electron affinity $E_a$, work function $W_f$, Fermi energy $E_f$ and band gap $E_g$.
+\begin{align}
+\chi &= 0.5(W_f + E_a)\\
+\eta & = 0.5(W_f - E_a)
+\end{align}
+where I is ionization potential and $E_a$ is electron affinity.
+
+Correlation between optical band gap and formation enthalpy; reaction occurs in order to form compounds with a larger gap.
+$E_g = A \exp(0.34E_{\Delta H^0})$, and A adopts different values depending on the metal elements:
+\begin{itemize}
+\item A=0.8 for s and f block elements,
+\item A = 1 for d block elements,
+\item A = 1.35 for p block elements.
+\end{itemize}
+
+\section{MB}
+
+MB is a heterocyclic aromatic dye which is blue colored in oxidizing environment.
+Upon reduction, MB is turned into colorless leuco MB.
+This can be used as an oxygen indicator in food industry.
+Photo-bleaching of MB can be also due to its leuco formation rather than total decomposition.
+Photocatalytic decomposition can be minimized by keeping the solution at acidic condition (pH = 4), which will limit the formation of oxidative hydroxyl radicals (E = 2.8 eV vs normal hydrogen electrode).
+Oxygen dissolved in the solution play a key role in conversion of LMB to MB under visible light.
+Purging with \ce{N2} for 20 min
 
@@
 
+\citeauthor{Sreedhara2013} studied the kinetics of photodegradation of methylene blue\footnote{\ce{C16H18N3SCl},319.8 g/mol, MP: 100C accompanied with decomposition \url{http://en.wikipedia.org/wiki/Methylene_blue}} dye by few layer \ce{MoO3}.
+For the photodegradation method, it was stated that `` the samples were collected after the photoreaction had been centrifuged for 5 min to remove the photocatalyst before UV-Vis measurement.''
+
+Raman \cite{Xiao2007}.
+Silver has the strongest SERS enhancement due to the larger imaginary part of the dielectric constant and higher thermal conductivity.
+Milli-Q grade water ((Milli-pore)\textgreater 18.2Mohm).
+
+MB Raman peaks: 445, 1618, ref20. some peak splitting and shift observed on SERS, attributed to chemical adsorption. definition of Raman enhancement factor.
+
+SERR MB on Ag. \cite{Nicolai2003}
+MB: the absorption spectrum in VIS is used to infer about different adsorbed forms of MB. the formation of large aggregates.
+
+ can remove dissolved oxygen. \cite{Wang2014a}
+
+solar energy harvesting representative study.\cite{Yoneyama1972} MB to LMB (\ce{C16H19N3S}) in aqueous solution upon illumination of \ce{TiO2}.
+The colorimetric analysis was performed in a glove box under nitrogen atmosphere.
+The absence of oxygen is important to prevent the oxidation of LMB to blue MB.
+\[
+\cee{MB^+ H2O + H^+ \rightarrow MBH3^{2+} + 1/2O2}
+\]
+where MB represents the uncharged center of MB molecule.
+
+common wisdom expect that a dye incapable of injecting an electron at the excited state to CdS.
+MB, which process N-methyl groups in its molecular structure and does not sensitize CdS is an exemplary candidate.
+quantum efficiency is defined as probability of MB converted to azure B per incident photon.
+QE of CdS to MB decomposition is reduced in nitrogen bubbling treated solutions, indicating the necessity of oxygen.
+Two possible mechanisms: a) adsorbed oxygen acts as a trap for the conduction electron and prevent the accumulation of negative charge within space charge region of CdS, supported by the formation of \ce{O2^-} in excitation of CdS in aqueous suspension.\cite{Takizawa1978}
+
+ref 16, MB aqueous solution stability. Liquid chromatogram, azure B (trimethylthionine), and thionine. Electrochemical measurement,
+
+MB adsorption.
+photocatalytic oxidation of MB by \ce{TiO2} film.
+photo-oxidation reaction occurs at the surface of photocatalyst.
+Mb molar extinction coefficient was found to be 66700 1/cm 1/M.
+Langmuir adsorption isotherm.\cite{Matthews1989}
+
+\[
+[MB]_{ads} = \frac{k_1 k_2 [MB]}{1 + k_1[MB]}
+\]
+and integrated form of Langmuir adsorption isotherm
+\[
+t = \frac{1}{k_1K} In\frac{[S]^0}{[S]} + \frac{1}{K}([S]^0 - [S])
+\]
+where $K = k_2 \phi N T_r$, with $\phi$ as quantum yield, N as total absorbed photons, and $T_r$ as rate of transport.
+\[
+\cee{C16H18N3SCl + 25.5O2 \rightarrow 16CO2 + 6H2O + 3HNO3 + H2SO4 +HCl}
+\]
+which indicates the total oxidation of $10 \mu M$ MB would exhaust the ambient oxygen concentration of initially air-equilibrated solutions (about $250 \mu M$ ).
+ref 28 Thus the transport of both oxygen and MB to the photocatalyst surface are anticipated to be key factors.
+
+photoelectrochromism at \ce{TiO2}/MB interface and its control.
+Efficient capture of photogenerated holes by a reducing agent is crucial to the reversibility of bleach-recoloration transition.
+This transition is kinetically dictated by electron transfer.
+Holes transfer is not desired.\cite{DeTacconi1997}
+
+256 nm band is associated to the presence of LMB.
+LMB formation is not favored at alkaline pH values in aqueous solution.
+The OH radicals are generated either with the surface hydroxyl groups on \ce{TiO2} or with water, and its high oxidizing power cause photocatalytic decomposition of the dye.
+
+An elementary step in decomposition of MB is N-dealkylation, which is preceded by radical cation formation.\cite{Takizawa1978} This radical cation can be spectroscopically monitored by the presence of 520nm band for MB.
+In MB absorption spectrum, 664 and 614 nm band ratio is related to monomer and dimer relaxation.
+\begin{align}
+\cee{TiO2 &\rightarrow e_{CB}^- + h_{VB}^+ \\
+h_{VB}^+ + red &\rightarrow ox\\
+MB^+ + 2e_{CB}^ + H^+ &\rightarrow LMB}
+\end{align}
+
+Measure the ratio between 614 and 663 nm before and after adding WS2 can indicate the adsorption of monomer and dimer MB.
+
+MB can act as sacrificial electron acceptor in the reduction to leuco form.
+The decomposition is favored under oxygen-rich environment.
+MB feature peaks at 663, 614 and 292 nm, and $\epsilon_{660}=10^5 M^{-1}cm^{-1}$.
+The doubly reduced form of MB, LMB has feature peak at 256 nm.
+The singly reduced form of MB, \ce{MB.^-} is pale yellow, with peak at 420nm.\cite{Mills1999}
+\[
+\cee{MB + e_{CB}^- ->[pH<7] MB.^-}
+\cee{2MB.^- \rightarrow MB + LMB}
+\cee{O2 + e_{CB}^- \rightarrow O2.^-}
+\]
+
+The oxidized form of MB, \ce{MB.^+} has peak at 520nm, which is stable in acidic solution, but decomposes irreversibly in slight alkaline solution(pH = 9).
+thionine peaks at 600nm.
+MB forms dimers in aqueous solution,
+\ce{
+2MB <=>[K_D] (MB)_2
+}
+A typical value of $K_D$ is 3970 1/M. A quadratic equation can be solved to obtain the monomer concentration:
+\[
+2K_D [MB]^2 + [MB] - [MB]_{total} = 0
+\]
+MB adsorption on metal oxides. Monomer size is less than 1.5nm.
+Logarithmic acid dissociation constant $pK_a= -\log_10 \frac{[A^-][H^+]}{[HA]}$. The oxidation potential for \ce{H2O}-\ce{O2} couple is 1.23V and 0.817V versus NHE at pH 0 and pH 7, respectively.
+
+%\begin{align}
+%\cee{MB + SED &->[TiO2][h\nu \leq 3.2eV] LMB + SED^{2+}\\
+%2LMB + O2 &\rightarrow 2MB + 2H2O}
+%\end{align}
+
+S.L. Murov, I. Carmichael, G.L. Hug, Handbook of Photochemistry, 2nd revised ed. Marcel Dekker, New York, 1993.
+
+aerobic or anaerobic, dimerise, photominerlization, gas to liquid transfer.
+
+Mb to LMB transition as visual time monitor. commercial colorimetric oxygen indicators. radical-bearing carbon with unpaired electrons. MB = \ce{MB^+Cl^-}.\cite{Galagan2008}
+
+monomer MB and dimer MB kinetics.\cite{Spencer1979}
+
+MB. \cite{Lee2003a}
+\begin{align}
+\cee{ 2LMB &->[\text{UV}] LMB^*\\
+2LMB^* + O2 &\rightarrow 2MB^+ + 2OH^-}
+\end{align}
+
+\[
+\cee{2LMB ->[\alpha] LMB^*}
+\cee{2LMB ->[\text{above}] LMB^*}
+\]
+
 \section{literature to read}
 
-The geometrical symmetry groups of WS2 NT.\cite{Milosevic2000} 
-The basis/lattice vectors $a_1$ and $a_2$ are defined in transition metal plane with equal length $a_0 \approx 3$ \AA.
-This monolayered sheet can be rolled up to form a tubular structure when the chiral/translation vector $c = n_1a_1 + n_2a_2$ becomes the circumference of the tube.
-The diameter of a nanotube is given by
-\begin{equation}
-d = \frac{\mid c \mid}{\pi} = \frac{a_0}{\pi}\sqrt{n_1^2 + n_1n_2 + n_2^2}
-\end{equation}
-Notice $a_1 \cdot a_2 = a_1a_2 \cos\pi/3$, where the cosine times 2 is unit. 
-In analog with carbon nanotube, chiral angle $\theta$ is given by
-\begin{equation}
-\theta = \tan^{-1}\frac{\sqrt{3}n_2}{2n_1 + n_2}
-\end{equation}
+\ce{WS2} 1L doping calculation. \cite{Ma2011}
 
-Chiral angles from the interval $[0,pi/6]$ is sufficient for all possible tubes.
-Tubes $(n,0)$ with zero chiral angle are named zigzag, tubes $(n,n)$ with $\pi/6$ chiral angle are armchair, whereas all others are referred as chiral ones with $\theta \in (0,pi/6)$.
+electrochromic films. \cite{Yoshimura1985}
+ECD \cite{Jiao2012} recent review \cite{Mortimer2011}
+PEC, photoelectrode, WO3 and Si tandem structures.\cite{Coridan2013}
+WO3 photoactivity MB. \cite{Watcharenwong2008}
+
+2D wo3.\cite{Kalantar-zadeh2010a} 
+WO3 plasmon \cite{Manthiram2012}
+
+\ce{WO3} indirect gap 2.6eV, direct gap 3.4eV. \cite{Koffyberg1979}
+
+Raman fingerprint of m-\ce{WO3}, h-\ce{WO3} and \ce{WO3.nH2O} were summarized in ref\cite{Daniel1987}.
+
+\ce{WO3} on FTO by flame synthesis.\cite{Rao2014} \cite{Xu2006}
+
+Seeded \ce{W_{18}O_{49}} NWs growth on W foil.\cite{Hong2006a}
+
+\ce{Na2W4O_{13}} growth and optical properties. \cite{Oishi2001} \cite{Itoh2001}
+
+\ce{Na2W4O_{13}} crystal phase \cite{Viswanathan1974}
+
+\citeauthor{Salje1984} studied the transport in \ce{WO_{3-x}} ($0\leq x \leq 0.28$).\cite{Salje1984} It was found \ce{WO_{3-x}} show metallic conductivity when $x > 0.1$.
+
+\ce{WO_{3-x}} \cite{Migas2010}
+
+\ce{WO3} high temperature phase. \cite{Vogt1999}
+tungsten bronzes \cite{Wiseman1976}
+
+Phase transformation of \ce{Na2MoO4} and \ce{Na2WO4} by Raman scattering. \cite{Lima2011}
+
+\ce{WO2} NWs synthesis and raman \cite{Ma2005}.
+
+\ce{WO_{3-x}} CS planes and conductivity.\cite{Sahle1983}
+
+\ce{W-O} equilibrium diagram \cite{Wriedt1989}
+
+\ce{W_{18}O_{49}} electrochromic devices.\cite{Liu2013d} should compare with this one \cite{Wang2008}
+
+nucleation catalysis \cite{Turnbull1952}
+
+\ce{WO3} NWs aggregates. \cite{Kozan2008a}
+
+optical properties of \ce{WO3} gaps\cite{Saygin-Hinczewski2008}
+
+\ce{WO3} atomic layer by exfoliation and annealing \ce{WO3.H2O}. \cite{Kalantar-zadeh2010a}
+
+sodium tungstates raman \cite{Redkin2010}
+
+charge density wave in K-doped \ce{WO3} \cite{Raj2008}
+
+\ce{W_{18}O_{49}} Raman, IR shielding.\cite{Guo2012} \cite{Guo2011}
+broad peak between 750-780 cm-1.
+
+\ce{WnO_{3n-1}} NPs. \cite{Frey2001}
+
+\ce{WO3} growth hydrothermal.\cite{Moshofsky2012}
+
+\ce{W_{18}O_{49}} on tungsten foil by thermal growth\cite{VanHieu2012}
+
+Cathodoluminescence \cite{Parish2007}
+
+optical characterization of WOx film.\cite{Valyukh2010a}
+
+E-beam penetration \cite{Kanaya2002}
+
+optics in electron microscopy. \cite{GarciadeAbajo2010a}
+
+Ge NW growth using Ga as catalyst. \cite{Chandrasekaran2006}
+
+\ce{MoO3} photocatalytic \cite{Chithambararaj2013}
+photocatalytic experimental setup.\cite{Hupka2006}
+\ce{MoO3} pseudocapacitor  \cite{Brezesinski2010}
+
+\ce{MoOx} few layer as hole selective contact in solar cell.\cite{Battaglia2014}
+\ce{MoO_x} on n-type Si acts as a high work function metal (6.6eV), enabling a dopant-free contact and thus junction-less devices.
+piranha clean of FTO. 50ms switch.\cite{Scherer2012}
+
+hydrogen absorption in \ce{MoO3}.\cite{Sha2009}
+
+\ce{Na6Mo_{11}O_{36}} phase. \cite{Bramnik2004}
+
+\ce{Na6Mo_{10}O_{33}} phase, \cite{Gatehouse1983}
+
+\ce{MoO3} thin film. \cite{Carcia1987}
+
+\ce{H_xMoO3} raman.\cite{Hirata1996}
+
+MoO3 spreading \cite{Leyrer1990}
+
+Na2Mo2O7, Na2Mo4O13 phase transition \cite{SinghMudher2005}\cite{Tangri1992}
+
+visibility of FL \cite{Benameur2011}
+
+exfoliation IPA \cite{Halim2013}  \cite{Zhou2011a}
+
+\ce{MoO3} good style. \cite{Siciliano2009} \cite{Abdellaoui1997}
+
+\ce{MoO3}  DFT study \cite{B511044K} \cite{Cora1997} \cite{Sayede2005}
+
+\ce{MoO3} raman \cite{Lee2002}
 
@@
 
-\ce{WS2} by \ce{WCl_n} and \ce{H2S}, raman (632nm) show bulk features\cite{Tenne2008}.
+\ce{WS2} by \ce{WCl_n} and \ce{H2S}, raman (632 nm) show bulk features\cite{Tenne2008}.
 
@@
 
-\begin{align}
-\cee{WCl6 + S &\rightarrow WS2 + Cl2S2}\\
-\cee{MoCl5 + S &\rightarrow MoS2 + S2Cl2} \\
-\cee{S2Cl2 + NaOH &\rightarrow NaCl + S + Na2SO3 + H2O}
-\end{align}
+TMO review.\cite{Goodenough2013}
+
+h-\ce{MoO3} \cite{Lunk2010} \cite{Zheng2009}
+
+\ce{MoO3} (010) surface defect. \cite{Chen2001}
+
+mass spectrometry data to extract vapor pressure of \ce{NaxMoO3}.
+strain and Raman theoretical analysis.\cite{Chang2013a}
+
+magnetic properties of ws2.\cite{Zhang2013j}
 
@@
 
-CNT chirality by TEM \cite{Zhang1993} TEM chirality of \ce{MoS2} NTs
+To develop large-size single-crystal graphene on dielectric substrates.
+small carbon flow near-equilibrium CVD process.
+Grain size about 10 microns, precursor \ce{CH4} and \ce{H2} (ratio 2.3:50) at 1180 C.
+\ce{SiO2}-Si surface roughness.
+Although the growth substrates (quartz,\ce{SiO2}-Si and \ce{Si3N4}-\ce{SiO2}-Si ) have a complicated stereo network similar to diamond, regular hexagonal G growth is obtained, which indicates the deposition is determined by equilibrium kinetics, and this should be applicable to other 2D materials as well.
+I2D/IG exceeds two on \ce{SiO2}-Si subs (514.5nm), indicating monolayer G.
+armchair (AC) G edge grows faster than zigzag (ZZ) edge.\cite{Chen2013j}
 
-first demonstration of \ce{WS2} NT n-type FET. \cite{Levi2013}
-the importance of contact, and avoiding moisture.
+catalytic graphitization of solid carbon sources.
+catalytic transformation, the source is in solid state, low temperature (less than 600C), 2nm  \ce{Al2O3} by ALD as carbon diffusion barrier.
+amorphous silicon (a-Si), Ni lower the activation barrier ,  tetrahedral amorphous carbon (ta-C).\cite{Weatherup2013}
 
-The calculated carrier concentration is about $10^{19}cm^{-3}$, a highly doped semiconductor, possibibly arising from sulfur vacancy.
+low energy (50eV) ion implantation doping in G.
+Ions penetrate pristine G at energy larger than 100eV.
+Individual substitutional incorporation of B into G lattice is demonstrated.
+1\% doping level was obtained.
+\cite{Bangert2013}
 
-\ce{WS2} NT transport \cite{Zhang2012c}
-less grain boundary more mobility,
+\ce{CaF2} a material suitable for scattering efficiency S comparison measurement due to its large band gap ($S\times \omega_L^4$ is constant below 5eV).
 
-\citeauthor{Ramasubramaniam2011} investigated the band gap tuning in bilayer TMDC materials by applying external $E$ field.
-Similar research has been done for graphene and bilayer boron nitride.
-Semiconductor-metal transition was suggested for \ce{MoS2} and \ce{WS2}, with difference on the CBM and VBM evolution.
-In \ce{MoS2}, the valence-band-splitting cause the A and B excitons in optical absorption measurement.
-Calculation shows that CB and VB are translated toward the Fermi level with increasing E field.
-The external field localized charge along $c$ axis, but delocalized that within the plane normal towards $c$, thereby driving the semi-metal transition.
-It was mentioned that this transition is not anticipated in monolayer \ce{MoS2}.
-It was emphasized that precise band gaps might be different from the author’s results, yet the gap-tuning should be universal.\cite{Ramasubramaniam2011}
+heterojunction is employed to transferred photo-generated carriers.
+Schottky barrier conduction band electron trapping and consequent longer electron-hole pair lifetimes.
+Numerous studies have suggested that fine particles of transition metals or their oxides, when dispersed on the surface of a photocatalyst matrix, can act as electron traps on n-type semiconductors.\cite{Zhou2010}
 
-\cite{Song2013} \ce{WO3} by ALD, and sulfurized in Ar and \ce{H2S} (10:1) at 1000 C.
-\ce{WS2} layer No and peak intensities ratio under 633nm excitation is correlated.
-It was found the 2LA/A1g is less than 1 for 1L.
-In supporting info 532 nm Raman spectra, the 2LA/A1g is presumably larger than 1 for 1L.
-\ce{WS2} NT on Si NWs is also demonstrated.
+\citeauthor{Cao2014} studied the layer-dependence \ce{MoS2} electrocatalysis and propose the vertical hopping efficiency of electrons instead of the edge site numbers is a key factor for catalytic reaction.\cite{Cao2014} ref19,20
 
-\cite{Tenne2010} chemical modification of NTs.
-Functional ligand consists of an anchor group that attaches to the NTs surface and a tail which render them soluble in various solvents.
-PTAS functionalized BN nanotube lead to the formation of stable suspensions in aqueous solutions.
-The strong attachment is formed through $\pi-\pi$ interactions.
+It was found that the critical step in this process is the fast conversion of the oxide nanoparticle surface into a closed monolayer of \ce{WS2}.
+\ce{W18O49} as an intermediate phase is observed.
+XRD peaks shift to monitor strain.(002) peak of nanotube shifted to lower angles, the interlayer spacing increase by about 2\% as compared to the bulk powder, likely due to the build-in strain.\cite{ZAK2009}
+$\epsilon = (a - a_0)/a_0$ =(6.4-6.16)/6.16 = 3.8\%. tensile strain ($\epsilon > 0$)
 
-inorganic nanotubes review \cite{Tenne2004} , unsaturated bonds number increases as the size of MS2 sheet decreases.
+DFT doped \ce{WO3} for photocatalytic reaction.\cite{Wang2012} CBM arises from W $5d$ states and splits into $t_{2g}$ and $e_g$ states under crystal field.
+VBM comes from O $2p$ states, including $2p_\sigma$ (along \ce{W-O} bonds) and $2p_\pi$ (normal to \ce{W-O} bonds).
 
-Water splitting materials should process a band gap larger than 1.4eV, considering both the NHE potential distance and practical application.
-The monolayer \ce{WS2} exhibits direct gap of 1.98 eV.
-Quantum confinement could push the gap separation farther away.
-\cite{wilcoxon1997} \citeauthor{Notley2013} use liquid exfoliation to prepare \ce{WS2} NPs.\cite{Notley2013} Non-ionic surfactant concentration is about 0.1\%w/w.
-Continuously adding surfactant during sonication improves the yield.
-Optimum surface tension is found at about 40 mJ/m$^2$.
+oxygen vacancies in \ce{WO_{3-x}}.\cite{Wang2011b}  Coloration and electron conductivity changes.
+\citeauthor{Wang2011b} found strong dependence of WO3-x electronic properties on $V_O$ concentration and the the crystallographic direction on which O is removed.
+DFT band gap calculation is close to experimental value.
+Vacancy levels are found at 2.1eV.
 
-G/\ce{WS2}/G stacked solar cell. For lubricant, and surface protection. Absorption $\sim 10^7 m^{-1}$. \cite{Britnell2013}
+The Raman spectra of \ce{WO_x} is rare because of the difficulty of preparing pure suboxides phase and the strong shielding of \ce{WS2}.
+Yet it does exhibit distinct Raman spectra.
+\cite{Tenne2005} The 870 line is attributed to \ce{W3O8}.\cite{Hardcastle1995}
 
-In Ref\cite{Zeng2013}, single crystal \ce{WS2} growth using \ce{I2} transport was described in supporting info.
-\ce{C24H12K4O8}\footnote{http://www.chemspider.com/Chemical-Structure.24771386.html}
+\citeauthor{Huang2006} studied the \ce{W3On} cluster with n from 7 to 10.\cite{Huang2006} It was found \ce{W3O9} clusters possess a HOMO-LUMO gap about 3.4eV.
+This closeness to bulk value suggests \ce{W3O9} could be viewed as the smallest molecular unit for bulk \ce{WO3}.
 
-416 peak was prevously assumed to be a combination of LA and TA phonons at K points.
+plasmon dispersion in 2D materials, plasmon resonances in visible regions by doping induced free carrier density.
+2D plasmonics, depolarization factors, partial reduction of Mo to a lower valence state.
+\cite{Alsaif2014a}
 
-Raman conditions: 0.3 mW, 532 nm, 200 sec acquisition time. photon flux = $0.3E-3\times6.242E+18/1.2398/0.532=2.84E15$
+WS2 photoluminescence spectra of few layer and nanotube:
+NT electrical structures depend on chirality, diameter and layer No as well as strain.
+Theoretical calculation indicates the SWNT with diameter larger than 4nm should approach the single layer limit.\cite{Ghorbani-Asl2013}
 
-416 cm raman on WS2. B1u is pressure sensitive. \cite{Staiger2012} also studied pressure dependence.
+Other chalcogenide has also been synthesized using this one-end sealed layout.\cite{Mukherjee2013}
 
-A1g mode using resonance Raman excitation shows upshift, which is presumably caused by folding induced strains.
-And TEM SAED reveal 3R symmetry.
-We did not observed this upshift of A1g probably due to the large diameter and few layer involved.
+\citeauthor{Zou2007} prepared W/\ce{WS2} core-shell NPs by reaction of tungsten and sulfur under hydrogen atmosphere.\cite{Zou2007}
 
-Nanotube growth is relatively independent of substrates and FL layer is closely related to substrate. Film growth could provide some insight into the latter scenario.
+CVD 1L WS2 PL.\cite{Peimyoo2013} (of NTU Yu group) PL peak at 635nm, width 40 meV,
 
-\fi
+CVD 1L WS2.\cite{Cong2013} (of NTU Yu group) 457 nm excitation, PL at 525nm and 630nm,
 
-\subsubsection{Seeded Growth of Tungsten Oxide NWs}
-With the oxidation experiments study in Sec.~\ref{sec:woxd}, favorable conditions for local growth of NWs were extracted to perform seeded growth.
+\ce{MoS2} sing-walled nanotube.\cite{Xiao2014}
 
-\begin{figure}[htb]
-\centering
-\subfloat[]{\label{fig:sga}\includegraphics[width=0.4\textwidth]{wox_sg_a.jpg}}\hspace{0.04\textwidth}
-\subfloat[]{\label{fig:sgb}\includegraphics[width=0.4\textwidth]{wox_sg_b.jpg}}
-\caption[Characterization of seeded growth \ce{WO3}: SEM]{Characterizations of seeded growth.
-(a) SEM graphs of \ce{WO3} NWs on \ce{SiO2/Si} substrate.
-(b) A high magnification view showing uniform NW growth and close-up view of one NW.
-}
-\label{fig:woseedsem}
-\end{figure}
+1T MoS2: metallic phase a negative temperature coefficient for conductivity, XRD pattern identified. \cite{Wypych1992}
 
-As shown in Fig.~\ref{fig:sgb}, dense NWs array was obtained on tungsten powder seeds with individual wires of length up to 5 $\mu$m and diameter about 50 to 200 nm, according to the estimation made in the close-up view.
-Each tungsten powder stood as independent growth site (Fig.~\ref{fig:sga}) with island-layer growth on the substrates, a common feature without using tungsten powder as seed under current experimental conditions.
-It was occasionally observed that NWs growth was initiated adjacent some tungsten powders.
-This phenomenon was correlated to the local trap of vapor flow since it was more often found among the enclosed area by tungsten powders.
-It is also found that the diameter of NWs decrease as the distance between powders and upstream edge increases.
-This is a combination effect of lower temperature and reduced \ce{WOx} growth species supply.
-Similar phenomena were observed in other studies.
-\citeauthor{Thangala2007} reported that a decrease in NW density with increasing substrate temperature, and an increase of NW density with increasing partial pressure of oxygen.\cite{Thangala2007}
+stable 1T WS2 multiwalled NT by Re doping.\cite{Enyashin2011}.
+2H to 1T transition formerly known only for WS2 and MoS2 intercalated by alkali metals.
+3R transition to 2H upon heating since 2H is the most stable one.
 
-% seeded edx 
-\begin{figure}[htb]
-\centering
-\includegraphics[width=0.5\textwidth]{wo3_seed_edx}
-\caption[Composition analysis on seeded growth \ce{WO3} NWs]{EDX spectroscopy on seeded growth \ce{WO3} NWs.}
-\label{fig:woedx}
-\end{figure}
-Energy-dispersive X-ray spectroscopy (EDX) analysis on the seeded growth \ce{WO3} NWs is shown in Fig.~\ref{fig:woedx}.
-Only W and O elements were detected on the NW array.
-The background level from 3 to 8 keV was a manifestation of the continuous components of W X-ray spectrum.
+1T \ce{MoS2} Raman.\cite{Yang1991} strong peaks at 156, 226, and 330 cm-1.
+M point frequencies measured by neutron scattering.
+M point is folded into BZ zone center due to the formation of superlattice.
 
-% sg raman xrd
-\begin{figure}[htb]
-\centering
-\subfloat[]{\label{fig:sgxrd}\includegraphics[width=0.45\textwidth]{xrd_cs_before}}\hspace{0.04\textwidth}
-\subfloat[]{\label{fig:sgram}\includegraphics[width=0.45\textwidth]{wox_raman_1}}
-\caption[Characterization of seeded growth \ce{WO3}: XRD and Raman]{ (a) XRD pattern of as-prepared sample indicating the \ce{WO3} phase and the presence of metallic core.
-(b) Raman spectrum on NWs region showing the feature of \ce{WO3}.}
-\label{fig:woseedxrd}
-\end{figure}
+Electrons and Phonons in Layered Crystal Structures, edited by T. J. Wieting (Reidel, Dordrecht, Holland, 1979).
 
-Fig.~\ref{fig:sgxrd} is the XRD spectrum of one typical sample.
-The peaks under circular symbol were identified to be the monoclinic \ce{WO3} phase (ICDD PDF 01-083-0950, \emph{a}=7.30084 \AA, \emph{b}=7.53889 \AA, \emph{c}=7.6896 \AA, $\beta$=90.89$^\circ$), while the peak under the triangular symbol was indexed to cubic tungsten phase (ICDD PDF 04-16-3405, \emph{a}=3.157 \AA), in agreement with the EDX analysis (Fig.~\ref{fig:woedx}).
-This means that during the \ce{WO3} seeded growth of 4 h heating at 1000 \si{\degreeCelsius}, the tungsten powder in downstream low temperature region (600 -- 700 \si{\degreeCelsius}) is not entirely oxidized.
-Micro-Raman scattering spectroscopy was performed on the as-synthesized sample as well.
-During Raman examination, the laser spot was carefully focused onto the NWs on powders and several inspections on different positions were observed to ensure the reproductivity of spectra data.
-As shown in Fig.~\ref{fig:sgram}, five distinct bands were well resolved, with peaks located at 131, 265, 327, 711 and 803 \si{cm^{-1}}, respectively.
-This pattern was typical features of \ce{WO3}, consistent with previous study.\cite{Salje1975a,Dixit1986} The high background level probably arises from the metallic core.
+\ce{WS2} p-type or n-type.
+Fermi level at the surface of semiconductor is pinned to a fixed position relative to the CBM and VBM by a sufficient density of surface states situated between CBM and VBM.
+\cite{Baglio1983}
 
-% sg tem
-\begin{figure}[htb]
-\centering
-\includegraphics[width=0.9\textwidth]{JAP-2column_Fig5major.jpg}
-\caption[Characterization of \ce{WO3}: TEM]{TEM graphs of as-prepared NWs.
-(a) TEM image of one nanowire with diameter about 40 nm.
-(b) HRTEM images showing the spacing is 0.38 nm, corresponding to (002) plane distance.}
-\label{fig:woseedtem1}
-\end{figure}
+Electronic structure of \ce{MoS2}.\cite{Eknapakul2014} K intercalating into bulk to create quasi-standing 1L.
+Large effective mass 0.6 $m_e$ found, implying low mobility.
+Direct gap 1.88eV is measured.
 
-TEM specimen was prepared by using carbon grid to slightly scratch the as-grown sample.
-Fig.~\ref{fig:woseedtem1} shows the feature of majority NWs.
-The growth direction is determined to be perpendicular to (002) plane.
-The streaking in SEAD pattern presumably arises from stacking defaults.
-The author also find some NWs exhibit high crystalline quality, as revealed by the TEM analysis in Fig.~\ref{fig:woseedtem2}.
-The NW grew normal to (002) plane with a measured lattice spacing of 3.79 \AA, which is favorably compared to the XRD peak at $23.07^\circ$ (7.7103 \AA).
-The sharp SEAD pattern and clear phase contrast in HRTEM demonstrated are both strong evidence of good crystallinity.
-This formation indicated current growth parameters have promising potential to obtain highly crystalline \ce{WO3} NWs in large scale.
+Self-assembled monolayer (SAM) on \ce{SiO2} and its effect on \ce{MoS2} 1L.\cite{Najmaei2014}
 
-% sg tem
-\begin{figure}[htb]
-\centering
-\includegraphics[width=0.9\textwidth]{JAP-2column_Fig5minor.jpg}
-\caption[Characterization of \ce{WO3}: TEM cont]{TEM graphs of as-prepared NWs.
-(a) TEM image of one nanowire, the diameter is about 70 nm.
-(b) HRTEM images showing the spacing is 0.379 nm, corresponding to (002) plane distance.}
-\label{fig:woseedtem2}
-\end{figure}
+\citeauthor{Shi2013} studied the strained monolayer \ce{MoS2} and \ce{WS2}.
+The results show that exciton binding energy is insensitive to the strain, while optical band gap becomes smaller as strain increases.
+Monolayer \ce{WS2} PL maximum located at about 1.95 eV.
+Calculation shows the electron effective mass of \ce{WS2} is the smallest, rendering higher mobility in device.\cite{Shi2013}
 
-In regarding to the formation of NWs on tungsten powder itself, this study assumes the driving force is related to interfacial strain between W and \ce{WOx}.
-Oxidation of tungsten proceed slowly at room temperature and an oxide layer of 100 \AA was found on the surface of tungsten foils.\cite{Warren1996} The tungsten powder used in current study would be covered by a thin oxide layer as well.
-During oxidation, different oxidation rates exist for different crystallographic orientations on the tungsten powder.
-Oxidation occurring at boundaries and defects are preferred thermodynamically.\cite{You2010} Compressive strain will gradually accumulate at the tungsten oxide/tungsten interface, which might limit the diffusion rate of oxygen at temperature lower than 500 \si{\degreeCelsius}.\cite{tungsten1999} At elevated temperature, cracks will primarily occur, as observed in Fig.~\ref{fig:pdtemp}.
-When heated up, tungsten and the oxide shell will probably relax the strain by converting into substoichiometric NWs, a similar process as suggested by \citeauthor{Klinke2005} in the chemically induced strain growth of tungsten oxide NWs.\cite{Klinke2005} It is worth noting that tungsten oxide nanowires could also formed when \ce{WO3} is reduced.\cite{Sarin1975} The elongation of \ce{WOx} is thermodynamically favorable during the conversion from metallic tungsten to tungsten oxide as well.
-Local evaporation-condensation process might also contribute to the formation of NWs on tungsten powder.
+\citeauthor{Kosmider2013} studied the heterojunction between two monolayers of \ce{MoS2} and \ce{WS2}.
+Top of VB in W layer and bottom of CB in Mo layer, forming type II structure.
+bilayer gap 1.2 eV.\cite{Kosmider2013}
 
-The enhanced yield of NWs obtained via seeded growth could be explained by a vapor-solid (VS) mechanism.
-External supply of growth species will condense onto the powders and substrate simultaneously, promoting the elongation of NWs on power as well as resulting island-layer growth on substrate.
-The local NW density in oxidation experiment was much higher than that of seeded growth.
-It is reasonable to presume that during seeded growth, several NWs in a small region on powder will coalescence, as evidenced by the bundled structures.
-At last, the author would like to point out that when low purity tungsten powder (3N) was used as source, sodium tungsten oxide nanowires were found to be dominant in the final product.
-The details have been published.\cite{Sheng2014} It seems surprising that when 3N powder was used as seeds, only \ce{WO3} nanowires were obtained.
-This result was attributed to the lower temperature and significantly reduced amount of 3N powder used in the seeded growth, compared with the conditions used in Ref.\cite{Sheng2014}.
-The source material in seeded growth is not limited to high purity tungsten powder.
-Instead, any material that could produce appropriate growth vapor could be employed, indicating the versatility of this approach.
+Band structure  of \ce{MoS2} in bulk form was calculated by \citeauthor{Mattheiss1973}.The calculation result is 1.2eV (indirect gap).\cite{Mattheiss1973}
 
-\subsubsection{Optimization of W powder Oxidization}\label{sec:woxd}
+Alkali metal intercalated \ce{WS2} film was prepared.\cite{Homyonfer1997} Stage 6 superlattice formation was suggested according to X-ray diffraction, and photoresponse spectra and electron tunneling measurement were done.
 
-Understanding the oxidation of tungsten powder is the key to obtain high yield in seeded growth.
-Oxidation of tungsten have been investigated under diverse conditions, such as at elevated temperature (\textgreater 1100 \si{\degreeCelsius} ) and oxygen pressure on the order of Torr,\cite{Base1965} and at temperatures ranging from 20 to 500 \si{\degreeCelsius} under atmosphere pressure.\cite{Warren1996} \ce{WO_x} NWs were readily found when tungsten (foil, wire, or powder) is oxidized under various conditions.\cite{Zhu1999,Karuppanan2007,Hsieh2010} However the study on tungsten powder oxidation behavior between intermediate temperature range and under low pressure is still rare.
-This work studied the oxidation of tungsten powders with diverse size within temperature range from 500 to 1000 \si{\degreeCelsius} and under several mTorr oxygen partial pressure.
-Using tungsten powder as seed, the author further illustrate an economic approach to obtain large yield of \ce{WO3} nanowires at relatively lower temperature than previous efforts.
-It is demonstrated that there is an optimal tungsten powder size under our experimental conditions for seeded growth.
-This will provide some insight on the role of tungsten powder as source material in CVD growth of \ce{WO_x}.
+decrease in dielectric screening and thereby enhanced excitonic effect.
+DFT is not good at describing photoemission, GW approximation overcome this deficiency but still not enough for photoabsorption process in which ehps are created.
+BSE equation is used to compensate this discrepancy, WX2 exhibits larger spin-orbit splitting as compared to MX2 family.\cite{Ramasubramaniam2012}
 
-Commercial available tungsten powders with different size are usually associated with purity variation as well, as already listed in Table.~\ref{tab:ch5pre}.
-The dimensions of tungsten powder were obtained by measuring the average size in SEM graphs.
-A systematic investigation was performed on the oxidation behavior of tungsten powder to evaluate the temperature effect, size-dependence and influence of oxygen partial pressure.
-% seed optimal
-\begin{figure}[htb]
-\centering
-\includegraphics[width=0.6\textwidth]{JAP-2column_Fig1.jpg}
-\caption[W powder oxidation: temperature effect]{SEM graphs of 99.9\% (3N) tungsten powder oxidization at different temperatures of a) 500 \si{\degreeCelsius}, b) 600 \si{\degreeCelsius}, c) 650 \si{\degreeCelsius}, d) 750 \si{\degreeCelsius}, showing the optimal temperature for local formation of nanowires is between 600--650 \si{\degreeCelsius}.
-Oxygen flow rate is 1 sccm.}
-\label{fig:pdtemp}
-\end{figure}
-
-Fig.~\ref{fig:pdtemp} illustrated the effect of temperature on the morphological change and surface nanowires formation of 3N powder.
-At 500 \si{\degreeCelsius}, most tungsten powder retained its original shape and a layer of tiny dense NWs begun to grow.
-When temperature was increased to 600 \si{\degreeCelsius}, 3N powder started to crack with longer NWs on the isolated surface.
-Further increase of temperature lead to irregular shapes of tungsten power and aggregation of NWs, giving rise to the nanorods and bunched or bundled structures.
-It could be determined from the morphology variation that the optimal seeded growth temperature for 3N powder was in the range of 600 to 650 \si{\degreeCelsius}.
-% seed optimal
-\begin{figure}[htb]
-\centering
-\includegraphics[width=0.6\textwidth]{JAP-2column_Fig3.jpg}
-\caption[W powder oxidation: size effect]{SEM graphs illustrating the oxidization of four different size of tungsten powders at 600~\si{\degreeCelsius} and 1 sccm oxygen flow.
-a) 17 $\mu m$, b) 32 $\mu m$, c) 3.3 $\mu m$, d) 1.5 $\mu m$.}
-\label{fig:pdsize}
-\end{figure}
-
-Fig.~\ref{fig:pdsize} depicted the oxidation of different sizes of tungsten powder under the same experimental conditions.
-In contrast to the morphology of 3N powder shown in Fig.~\ref{fig:pdtemp}, 3N5 powder surface is primarily covered with sub-micro particles as well as some short tiny NWs, whereas 4N5 and 5N powder were thoroughly oxidized, showing branched flowers feature.
-This dramatic difference could be explained in terms of surface energy and oxygen diffusion.
-With smaller dimension, the increased surface-to-volume ratio and short diffusion path both lower the energy barrier of oxidation.\cite{tungsten1999} It was logical to deduce that higher temperature or increased oxygen level might favor the NWs formation on 3N5 powder.
-When it comes to seeded growth, however, the powder size distribution was an important factor to give uniform NWs deposition.
-Since the size distribution of 3N powder is more uniform than that of 3N5 powder, the author employed the former as seeds.
-% seed optimal
-\begin{figure}[htb]
-\centering
-\includegraphics[width=0.6\textwidth]{JAP-2column_Fig2.jpg}
-\caption[W powder oxidation: oxygen pressure]{SEM graphs of 3N tungsten powder oxidization at 600 \si{\degreeCelsius} under different rates of oxygen flow: a) 1 sccm, b) 2 sccm, c) 3 sccm, d) 10 sccm.
-The oxygen partial pressures were 13 mTorr, 23 mTorr, 32 mTorr, and 82 mTorr, respectively with background pressure subtracted.}
-\label{fig:pdoxy}
-\end{figure}
-
-Fig.~\ref{fig:pdoxy} depicted the morphology change of 3N powder with respect to varied oxygen partial pressure.
-When the oxygen flow is lower than 3 sccm, 3N powder almost stayed as the same, with cracks separating the dense layer of NWs.
-When oxygen flow is increased to 10 sccm, the 3N powder exemplified an enlarged version of that for 4N5 or 5N powder under 1 sccm oxygen flow.
-This observation again supported the surface energy explanation.
-
-\subsection{used}
-
-As the experimental setup for direct tensile tests of nanotubes is state-of-the-art,\cite{Tang2013} the application of tensile stress on 2D TMD systems is rather difficult due to the excellent lubricating properties of these materials.
-
-\citeauthor{Zhang2013e} investigated the shear (C) and layer breathing mode (LBM) in the low frequency region of \ce{MoS2}.\cite{Zhang2013e} Even layer \ce{MS2} belong to point group D$_{6h}$ with inversion symmetry, while odd layer \ce{MS2} correspond to D$_{3h}$ without inversion symmetry.
-The excitation wavelength is 532nm from a diode-pumped solid-state laser.
-A power$\sim$0.23mW is used to avoid sample heating.
-
-reaction mechanism of \ce{MoO3} to \ce{Mo2S}.\cite{Weber1996}
-
-\citeauthor{Ling2014} studied the role of seeding promoters in CVD growth of FL \ce{MoS2}.\cite{Ling2014} PTAS treated substrates provided nucleation site and thus enable uniform deposition of \ce{MS2}.
-This enhancement perhaps arise from the \ce{K+} ions.
-
-\citeauthor{Splendiani2010} reported the PL in monolayer \ce{MoS2}.
-Calculation indicated the indirect gap become larger when thinning, while the previous direct one almost stays as the same, the value is about 1.85eV (direct gap).\cite{Splendiani2010}
-
-thermal decomposition of (NH4)2MoO2S2 and intermediate product MoOS2 was studied. application: hyfrodesulfurization in refinery \cite{Weber1996}
-
-\cee{MoCl5 + 1/4S8 + 5/2H2 \rightarrow MoS2 + 5HCl} \cite{Stoffels1999}
-
-A direct gap of $\sim 2eV$ at the corners of BZ is formed in 1L \ce{WS2}, Growth on bottom piece show the multiple domain flakes occurs at initial stage of the growth, starting from \ce{WO3} particles.
-%\cite{Cong2013}
-\subsection{to be used}
-
-Exfoliated WS2 few layer PL.\cite{Zhao2012} excitonic absorption peaks A and B arising from direction transition at K point are found around 625nm (1.98eV) and 550nm, respectively, which are in agreement with results from bulk layers.
-The A, B excitons difference was a result of strong spin-orbital coupling.
-Relative PL quantum yield of WS2 between 1L and 2L is on the order of 2.
-The FWHM of WS2 peak is about 75 meV.
-wider than thermal energy at room temperature,
-
-Electro microscopy on stacking sequences of WS2 NT.\cite{Houben2012} The probability of parallel stacking is about 30\%.
-a metal-semi superstructures.
-In NT, the layers are slightly shifted with respect to each other due to the constraints, thus the stacking is not exactly as pure phases of 2H(prismatic antiparallel), 3R(prismatic parallel) or 1T (octahedral parallel) with their perfect translational symmetry.
-
-chevron pattern, contradictory, contradicting, Debye scattering model for XRD.
-
-\begin{quote}
-hexagonal polytype 2Hb with two molecular layers (spacegroup P63/mmc) and a rhombohedral polytype 3R with three molecular layers per unit cell (space group R3m), a high pressure polytype that is stable in plane geometry at pressures above 4 GPa.
-The two prismatic phases are semiconducting, and the octahedral one is metallic-like.
-
-1T phase may be the result of a transformation from the 3R to the 2H phase by an intermediate 1T phase that is trapped by fast quenching
-
-\end{quote}
-
-aberration corrected TEM is used.
-
-HRTEM on WS2 NT.\cite{Sadan2008} negative spherical-aberration imaging (NCSI).
-NCSI condiction were achieved at a negative spherical aberration of -20um balanced by an overfocus of +17 nm.
-Focal series reconstruction to retrieve the phase of electron exit plan wavefunction.
-Zigzag, armchair revealed.
-
-In centrosymmetric crystals, the vibrational modes must either have even (Raman-active) or odd (IR-active) parity under inversion, which is known as rule of mutual exclusion.
-When this symmetry is broken, some modes may be simultaneously IR and Raman active.
-
-inelastic neutron scattering to study the non-zone center LA mode.
-Zone-edge scattering can occur due to zone-folding process.
-The formation of superlattice could activate formerly inactive zone-edge phonons.
-The folding of BZ along $\Gamma-M$ would cause the M point to coincide with $\Gamma$ point, so LA(M) phonons would become Raman active in a first-order process.
-
-\ce{SiO_x}-Si, \ce{WS2} absorption coefficient $10^{-7}m^{-1}$, mean free path of photo-excited charge carriers 1 $\mu m$.
-the wave vector of photon is considerably small than size of BZ, therefore The wave vector of phonon in Raman scattering usually close to zero.
-
-Multiple phonon scattering, For two identical phonons, the corresponding Raman peak in the spectrum is called an overtone of the peak from the corresponding one-phonon process.
-And the wave vector conservation rule is automatically filled, therefore the phonon involved is not limited to BZ center anymore.
-\[
-I(G) \approx \sum_k \frac{\langle f|H_M|b\rangle \langle b|H_{ep}|a\rangle \langle a|H_M|i\rangle}{(E_p - E_k^{\pi *}- E_k^{\pi}-i\gamma)(E_p - E_k^{\pi *}- E_k^{\pi}-i\gamma- \hbar\Omega_{G})}
-\]
-
-the average distance traveled by an excited electron-hole pair before combination $l=\nu_F/\omega_D=4nm$.
-
-Confocal Raman spectrometer:to obtain Raman spectrum in a specific depth of sample. Edge filter to cut off Rayleigh emission.
-
-resolution $d= 1.22 \lambda/NA$,
-
-Light Scattering in Solids II,. Springer, Berlin, 1982
-
-influence of core WOx, Raman scattering by plasma-LO coupling to determine carrier concentration. measure resonant cross sections in absolute units.
-
-disorder-induced light scattering, Van Hove critical points,
-In resonant second-order scattering:
-overtone: the same phonon,
-combination: two different phonons;
-
-\[
-\frac{\ud\sigma}{\ud\Omega}= \omega_s^4 cm^6 Sr^{-1}
-\]
-
-scattering volume V in number of unit cells can be considered as one big molecule.
-
-a single nanowire tends to minimize its surface. 2D isoperimetric quotient or circularity $C= \frac{4\pi A}{P^2}$, where A is area and P is perimeter of the cross-section.
-
-\section{ECD}
-
-Characterization of ECD (work like a thin-film batteries) includes transmission measurement and associated EC calculation, charge-discharge time, current-time curve and the fitting of obtained data.
-
-The coloration efficiency (CE) represents the change in the optical density (OD) per unit charge density ($Q/A$, in units of \si{\cm^2\per\coulomb}) during switching and can be calculated according to the formula:
-\begin{equation}
-CE = \frac{\Delta~OD}{(Q/A)} [cm^2/C],
-\end{equation}
-where OD = $log(T_{bleach}/T_{color})$. The EC and optical density depend on the wavelength and are usually higher in the near IR than in the visible region.
-Using Ohm's law($U_s = IR = RQ/t_s$) with switch voltage $U_s$, resistance R and surface area A, switching time $t_s$ could be estimated as
-\begin{equation}
-t_s = \Delta~OD\cdot A \cdot R /(CE\cdot U_s).
-\end{equation}
-
-battery and ECD.\cite{Granqvist2012} electrolyte: PVB (poly vinyl buteral).
-alternative materials and design: organic, Prussian Blue as EC materials, metal hydrides, suspended particle device, liquid crystal, electroplating,
-challenges: large area nanoporosity, transparent conducting contact, electrolyte with good ionic conductivity and poor electronic conductivity, stable under UV; assembly and large scale manufacturing;
-cathodic coloration:
-anodic coloration:
-The coloration mechanism: \ce{MO6} octahedrons lead to $e_g$ and $t_{2g}$ level and ion channelling.
-ref54,60,65,66,200,209,
-
-\ce{WO3} as cathodic and either polyaniline(PANI) or Prussian white (PW) as anodic electrochromic half cells. \cite{Heckner2002}
-
-Characterization of ECD includes transmission measurement and associated EC calculation, charge-discharge time, current-time curve and the fitting of obtained data.
-
-\begin{quote}
-a viable electrochromic smart window must exhibit a cycling life time \textgreater $10^5$ cycles, corresponding to an operation life at 10 -- 20 years.
-\end{quote}
-
-\citeauthor{Sella1998} studied the optical and structural properties of RF sputtered thin film of \ce{WO3} and \ce{VO2} for electrochromic devices.
-Ionic conductor was built using transparent polymer electrolyte, which was prepared from a solution of 1M \ce{LiClO4} in propylene carbonate which was mixed with methylmetharcylate (MMA).
-The main characteristics of polymer electrolyte were: viscosity at 25 \si{\degreeCelsius} $\approx$ 12920 Pa.s, conductivity $\approx 10^{-2}-10^{-4}$ \si{\per\ohm\per cm},non-hygroscopic if PMMA concentration \textgreater 30\%.
-A specific counter-electrode layer was not used since the encapsulated polymer electrolyte processes a very high ion storage capacity.\cite{Sella1998}
-
-The device proposed was reproduced as shown in Fig.~\ref{fig:Sella1998ECD}
-\begin{figure}[htb]
-    \centering
-    \includegraphics[angle=270,width=0.8\textwidth]{Sella1998ECD}
-    \caption{citation, see original captions} \label{fig:Sella1998ECD}
-\end{figure}
-
-\subsection{polarons}
-
-The concept of polaron was first proposed by Landau in 1933.
-In ionic or highly polar crystals, such as II-VI semiconductors, alkali halides and transition metal oxides, the Coulomb interaction between a conduction electron and the lattice ions results in a strong electron-phonon coupling.
-A new quasi-particle, virtual phonon, can be defined corresponding to the effect of electron pulling nearby positive ions towards it and pushing nearby negative ions away.
-The electron and its virtual phonons, taken together, can be treated as a new composite particle, called an electron polaron; the hole polaron is defined analogously.
-\cite{Devreese1996}
-
-\subsection{NW waveguide}
-
-seriously pursued. 
-\section{docend}
-
-%\section{Crystal Structures and Electronic Properties}
-
-Solid and orderliness.
-
-Two theories arise to describe the outer shell electrons and to correlate the structure and physical properties: \gls{cft} and band theory.\cite{Goodenough1971} \gls{cft} assumes weak interaction between neighboring atoms and localization of electron towards parent atom, whereas band theory assumes that electron is shared equally by all nuclei and therefore a many-electron problems follows.
-Description of a single electron in periodic potential fail to treat the electron correlations adequately, as the interaction between atoms becomes weaker.For transition metals, $s$ and $p$ electrons are well described by a collective-electron model, while the 4f or 5f electrons are tightly bound to nuclei and screened from the neighboring atoms by 5s, 5p or 6s, 6p core electrons, hence it matches well with a localized-electron model.
-d electrons show intermediate character.
-
-In vapor synthesis process, two growth mechanism exists: VS and VLS.
-VS process is widely accepted for the growth of \ce{MoO3}.
-Yet we caution that synthesis conditions should be scrutinized to determine the exact mechanism.
-\citeauthor{Li2002c} suggested a VS mechanism at 700 \si{\degreeCelsius} and VLS at 750 \si{\degreeCelsius} and higher.\cite{Li2002c} \citeauthor{Fibers2007} proposed a modified VS mechanism probably because the deposition occurs on \ce{Al2SiO5} with possible \ce{Al_{0.95}SiNa_{0.06}O_x} involved.
-Therefore temperature and possible impurity could potentially alter the growth mechanism.
-We divide the growth results into two categories: on Si substrate and on non-Si substrate, and describe them respectively.
-We also briefly mention using liquid exfoliation to prepare few layer \ce{MoO3}.
-
-This rectangular shape implies the boundary plane along growth direction (long axis) is (001), in consistency with previous experimental reports\cite{Zeng1998,Li2002b} and theoretical studies.\cite{Firment1983,Cora1997} We also observed different shapes, i.e., elongated hexagonal using similar growth conditions.
-This is not an indication of different growth mode.
-It is a normal thermodynamic fluctuation.
-The growth rates along different crystalline direction of \ce{MoO3} are determined by the free surface energy.
-In fact, (201), (101) and (102) planes have all been observed as terminating planes.\cite{Zeng1998} The stacking rate of \ce{MoO6} octahedra along $a$ and $c$ axis could develop some other ratio.
-And the coexistence of different planes in one growth suggests the similarity of free surface energies between these surfaces.
-In other words, the migration barrier of adatoms on (010) plane is presumably much lower than that on other low index planes due to the Van der Waals interaction nature along [010] direction.
-
-\citeauthor{Wang2013c} changed the NW growth direction by changing the shape of droplets; \citeauthor{Biswas2013} reported enhanced aspect ratio of Ge NWs from bimetallic alloy.
-
-We first repeated the previous growth on ITO/glass, and then found similar deposition phenomena on glass and mica substrates.
-We suspected that the morphology difference on the substrates employed in this study arises from the compositions difference.
-Both mica and glass contains alkaline elements which are absent in Si and \ce{SiO2}/Si substrates.
-We primarily verify this hypothesis by utilizing \ce{NaOH} treated Si substrates and found that the overall morphology almost reproduces that on ITO and mica substrates.
-We then propose a new growth mechanism based on the VLS process to explain the deposition of \ce{MoO3} on alkaline-ions-containing substrates.
-
-ITO versus NaOH images.
-
-According to the phase diagram shown in Fig.~\ref{fig:pd}, \ce{Na2MoO4} - \ce{MoO3} phase above 800 \si{\degreeCelsius} are \ce{Na2MoO4}(l) + \ce{MoO3}(l), More discussion should follow $\ldots$.
-
-%\subsubsection{Phase evolution probing by Raman}
-
-\citeauthor{Hardcastle1990} summarized an empirical formula to relate the Raman peaks and \ce{Mo-O} bonding lengths.\cite{Hardcastle1990} This correlation assumes general form as
-\begin{equation}\label{eq:mobond}
-\nu = A \exp{B\cdot R},
-\end{equation}
-where $A=32895$ and $B=-2.073$ are fitting parameters, R is bond distance in unit of \AA.
-Given a stretching frequency, the resolution for calculated bond distance is $\pm0.016$ \AA.
-Another empirical expression connect the bond valence $s$ and bond distance R: $s(M-O) \approx (R/X)^{-6} $, where X=1.882 when M is Mo, and 1.904 when M is W.
-The valence sum rule could be then used to check the state of Mo cation.
-It should be noticed that not all observed Raman lines could be correlated to a \ce{Mo-O} bond distance by extrapolation of Eq.~\ref{eq:mobond}.
-It is then regarded as a symmetry related vibrational mode, i.e.
-820 \si{cm^{-1} in \ce{MoO3}.
-From the correlation of various Mo compounds, a general conclusion is the lower the stretching frequency for the shortest metal-oxygen bond, the more regular is the structure.
-
-% droplet position statistics
-\begin{figure}[htb]
-\centering
-\includegraphics[width=0.6\textwidth]{droplets_sta}
-\caption[Droplet position statistics]{Droplet position statistics. On-tip and not-on-tip counts variation with respect to growth time. }
-\label{fig:mo3dropsta}
-\end{figure}
-
-Nanotower is a less common morphology in the structures of nanomaterials.\cite{Kharissova2010} We have not found report on  \ce{MoO3} nanotower structures, although there are several studies on \ce{In2O3},\cite{Jean2010,Yan2007}, GaN\cite{Xiao2012} and ZnO\cite{Zhang2013c}.
-\citeauthor{Jean2010} investigated the growth mechanism of \ce{In2O3} nanotowers and attributed it to the periodical axial and continuous lateral growth interaction, where the former was first guided by Au-In alloy liquid, and subsequent by self-catalytic In droplets (MP 156C) while the latter due to VS process.
-In contrast, \citeauthor{Yan2007} observed similar \ce{In2O3} nanotower growth and proposed that the axial growth is controlled by Au-catalytic VLS process.
-\citeauthor{Xiao2012} reported the GaN nanotower grown on Ni-coated Si(111) substrates and explained the growth as asymmetric self-copy process based on VLS mechanism.
-\citeauthor{Zhang2013c} studied the growth of ZnO nanotower and provided a competitive model between axial and lateral growth controlled by Zn vapor to explain the as-synthesized structures.
-(When ZnO and carbon mixture was used as source instead of ZnO alone, nanorods array results, presumably due to the stable supply of Zn vapor owing to the gentle carbothermal reduction.) Therefore the fluctuation of reagents is probably responsible for tapering and periodical modification, which is absent in the coin roll style growth of \ce{MoO3} tower on Si.
-The occasionally observed tapering or enlarging on \ce{MoO3} tower can be attributed to the cooling down growth.
-
-We divide the growth into two stages according to the emerging time of long belts and towers.
-In first stage the growth is dominated by lateral growth, as illustrated in .
-In the second stage, \ce{NaxMoO3} is evaporated and recondensed in the low temperature region, and some droplet will form, and when at proper locations, introduce secondary VLS growth.
-
-In first stage, the Na-Mo-O liquid is formed and have much more higher absorption rate than that of bare substrate.
-The absorbed species will diffuse along the surface and inside the liquid.
-It was difficult to estimate which diffusion path one is faster.
-
-\textbf{open questions}
-\begin{itemize}
-\item Is the liquid consumed? if so, how? : evaporation
-\item How the size of liquid is related to the morphology evolution?
-\item Possible doping level of alkaline ions
-\item other lateral growth mode such as Ni-W-S system
-\item VLS-VS interaction, or possible solution-liquid-solid, VSS,
-\item the interpretation of phase diagram
-\item the overall molar amount of NaOH and MoO3 deposition
-\item Young's parameters, contact angle informations, Gibbs free energy calculation
-\item catalyst composition variation during growth
-\item \ce{Na2Mo4O_{13}} phases, solid solubility of \ce{Na2MoO4} in solid \ce{MoO3} is high.
-\item vapor pressure of \ce{Na2Mo4O_{13}} and \ce{MoO3}.
-\end{itemize}
-
-As shown in Fig, we found several solid clusters with diameter about 1 $\mu m$ on the top part of long belts.
-According to the \ce{Na2MoO4}-\ce{MoO3} binary compounds phase diagram, we expect the terminating solid clusters have a Na:Mo ratio close to 0.6.
-The experimental results match well with this predictions.
-EDX analysis reveal the presence of Na on the solid cluster but not at about 1$\mu m$ away from previous location.\footnote{the sensitivity of our instrument is estimated to be 1\% atomic level} Quantitative atomic ratio derived from the solid cluster is not close to the one predicted by phase diagram probably due to the high Mo content in adjacent area.
-However, XRD examinations on a short time growth sample revealed a possible \ce{Na2Mo4O13} phase(PDF 028-1112), providing an indirection evidence of the droplet composition.
-We also suspect that the growth will become different below 500 \si{\degreeCelsius} since no liquid would remain.
-Substrate placed at low temp end show.
-We can also deduce that other sodium compounds can be employed as substrate treatment agent. This argument is confirmed by \ce{Na2CO3} and \ce{KI} assisted growth.
+oxygen plasma treatment on HF-etched Si (001). reaction among $e$, \ce{O^+}, \ce{O2^+}, \ce{O^-},\ce{O2}. \ce{OH}-terminated surface obtained.\cite{Habib2010}

### 2014-09-28 misc/draft.tex
paper draft and supporting info tidy up

--- 2014-09-24 misc/draft.tex
@@
 \chapter{paper draft}
+\section{Data Processing}
 
-The KM two-flux model has been extensively used to describe the optical properties of inhomogeneous materials that consist of scattering and absorbing particles in a matrix.\cite{Vargas1997} There are some limitation in the assumptions made in original KM model, e.g., the distribution of scattering on the optical path.
-And revised KM models have been proposed to eliminate these limitations.\cite{Yang2004}
+The SEM images are cropped using Adobe Photoshop for highlighting the features and fitting into text width.
+To obtain the dimension of specimen, scale bar was measured and compared to the size of interest using ImageJ\cite{Schneider2012} for SEM, TEM images and SAED pattern.
+It is worth noting that ImageJ could directly read the dm3 format generated in Gatan imaging software, which is more productive than the scale bar method.
 
-\citeauthor{Morandi2005} studied the absorbance and diffuse reflectin of \ce{MoO3} and \ce{WO3} thin films using FT-IT and UV-Vis spectroscopy.
-The observed absorption in visible and middle IR region were attributed to oxygen defects induced donor levels.\cite{Morandi2005}
-
-The ratio between absorption and scattering, not the absolute value of each quality, determines the reflection features.
+Various spectra, be it from XRD, EDX, Raman, or UV-Vis, were redraw using Origin Pro 8.0.
+The peak fitting was performed using \emph{Fityk}, a nonlinear curve fitting program specialized in data processing from powder diffraction, chromatography, photoluminescence and photoelectron spectroscopy, infrared and Raman spectroscopy, \emph{etc}.\cite{Wojdyr2010}
 
 \section{wo3}
+Tungsten bronzes was coined by Wohler in 1837.\cite{Deb2008} \ce{Na_{x}WO3}
+
+\ce{WO3} catalyst.\cite{Miyauchi2013}  potential of CB e more negative than redox potential of \ce{O2}-\ce{O2-} (-0.046 V vs NHE at pH 0).
+Z-scheme two photo absorption.
+photogenerated electron in CB of \ce{WO3} can reduce itself by formation of color centers.
+photocatalytic applications in solar hydrogen generation and organic pollutant degradation.
+A low recombination rate is preferred for high photocatalytic efficiency. The simultaneous migration of electrons and holes.
+
+WO3: effective mass of bipolaron = 1.9me. for electron, for hole:
+unzip nanotube. passivate BN ribbons with O and S; another player terrones psu.
+applications: electrically controlled optical shutters for heat and light modulation, smart windows associated with solar cell to provide dynamical control of incoming illumination.
+
+nanoscale Kirkendall effect: the outward diffusion of metal cations are balanced by an influx of vacancies. For example, diffusion coefficient of Ni in NiO is higher than that of oxygen.
 
@@
 \subsection{not used}
-Both tungsten (W) and molybdenum (Mo) belong to Group VIB transition metal, with outer shell electrons configuration as $4d^55s^1$ and $5d^46s^2$, respectively.
-Therefore we refer their oxides and chalcogenides as \gls{tmo} and \gls{tmdc}.\footnote{Obviously transition metals include many other elements, all of which have partially filled $d$-electron shell.
-But here we use TM to denote W and Mo exclusively.}
 
-Nucleation is a process of generating a new phase from a metastable old phase, where the Gibbs energy per molecule of the bulk of the emerging new phase is less than that of the old phase.
+This approach is essentially the same as previous studies where tungsten foils was used as substrate.The advantage of this method is W powder cost much less than a whole piece of foil, and provide more surface area than W foil in the same volume.
 
-General CVD knowledge, substrate preparation, and\cite{MichealK.Zuraw2003}
+The FG method utilizes the flow dynamics of our CVD apparatus. We will discuss both of them in details.
+We would like to discuss a little more on the dispersion of \ce{WO3} NWs, since the stability of \ce{WO3} dispersion is important for its applications.
+\citeauthor{Kozan2008} studied the stability of \ce{WO3} in various polar solvents such as acetone, isopropanol(IPA), ethanol, 1-methoxy-2-propanol (1M-2P) and N-dimethylformamide(DMF).\cite{Kozan2008} High power ultra-sonication was applied for about 2 minutes followed by a low power ultrasonic bath for 15 minutes.
+The the solvent was left to sedimentation.
+Samples was drawn out with pipette and transferred to clean substrate for observation.
+It is suggested that bundled NWs aggregates in 1M-2P seem to breakup at the outer branches to a small extent and turn into slightly more compact aggregate, providing well-dispersed stable suspension.
+Subsequently, this suggests we could harvest the as-grown nanowires by a solution ultra-sonication method.
+Generally there will be metallic tungsten in the core region of powder particles.
+The separation of NWs could be done via the route reported by \citeauthor{Kumar2008}, where separation by sonication in 1-methoxy 2-propanol followed by gravity sedimentation.\cite{Kozan2008}
 
@@
 
-The sol–gel process is a well-known, intensively studied wetchemical technique that is widely used in materials synthesis.
+The sol–gel process is a well-known, intensively studied wet-chemical technique that is widely used in materials synthesis.
 This method generally starts with a precursor solution (the ``sol") to form discrete particles or a networked gel structure.
 During the course of gelation (aging process), various forms of hydrolysis and polycondensation take place.
+
 In addition, doped \ce{WO3} was also demonstrated
-The composition and phase of final product highly depend on the synthesis conditions.
 
@@
 
-Nonstoichiometric tungsten oxides \ce{WO_x} (i.e. \ce{WO_{2.92}}, \ce{WO_{2.87}}) are known as Magn$\acute{e}$li phases.
+Nonstoichiometric tungsten oxides \ce{WO_x} (i.e., \ce{WO_{2.92}}, \ce{WO_{2.87}}) are known as Magn$\acute{e}$li phases.
 
@@
 \begin{quote}
-a viable electrochromic smart window must exhibit a cycling life time \textgreater $10^5$ cycles, corresponding to an operation life at 10 - 20 years.
+a viable electrochromic smart window must exhibit a cycling life time \textgreater $10^5$ cycles, corresponding to an operation life at 10 - 20 year.
 \end{quote}
@@
 
-% band gap table
+%wo3 band gap table
 \begin{table}[htb]
@@
 
-after fitting, $d_0 = 0.19777$ nm, $k = 0.00112 $ s$^{-1}$, so to oxidize 1nm W coating completely, oxygen plasma time is 1450 s at 0.5 Pa partially pressure; 2 nm for 2000 s.
-
-\ce{WOx} and optical electric field enhancement.
-The enhancement arise from the structure composed of a conductive layer and an insulating layer that are laminated therein.\footnote{US patent 8601610B2} In \ce{WOx} nanorods, the oxygen deficient planes are conductive, each having atomic thickness and separated by several nm \ce{WO3}.
-Localized surface plasmons could possibly exist on these conductive planes.
-Therefore SERS applies and single molecule Raman scattering using a tungsten oxide nanorod has been demonstrated.
-The \ce{W_nO_{3n-1}} ($n \geq 2$) exhibit $\{ 001 \}$ CS structure.
-Chemical formulae corresponding to n=2, 3, 4, 5 and 6 are \ce{W2O5=WO_{2.5}}, \ce{W3O8=W_{2.67}}, \ce{W4O_{11}=WO_{2.75}}, \ce{W5O_{14}=WO_{2.8}}, and \ce{W6O_{17}=WO_{2.83}}, which indicates the existence of a oxygen deficient plane at every n row.
-Actually the value x in \ce{WOx} could almost continuously vary within a range of 2.5 to 3.
-\ce{W_{18}O_{49}=\ce{WO_{2.72}}} is an exception without $\{ 001 \}$ CS structure.
-Moreover, the oxygen deficient planes could extend along directions other than $\{ 001 \}$.
-For instance, the $\{ 102 \}$ CS planes appears in \ce{WOx} where x is within 2.93 to 2.98, and  the $\{ 103 \}$ CS planes for x within 2.87 to 2.93.\cite{Sloan1999}  \citeauthor{Shingaya2013} also synthesized \ce{WS2}-\ce{WO_x} structures and found similar Raman scattering enhancement.
-The x value is estimated by the Raman spectra peaks.\cite{Shingaya2013}(Data not shown in patent)
-
-For photochemical water reduction to occur, the flat-band potential of the semiconductor (for highly doped semiconductors, this equals the bottom of the conductance band) must exceed the proton reduction potential of 0.0 V vs NHE at pH =0.
-\cite{Osterloh2008} flat-band potentials strongly depend on ion absorption (protonation of surface hydroxyl groups), crystallographic orientation of the exposed surface, surface defects, and surface oxidation processes.
+after fitting, $d_0 = 0.19777$ nm, $k = 0.00112 $ s$^{-1}$, so to oxidize 1 nm W coating completely, oxygen plasma time is 1450 s at 0.5 Pa partially pressure; 2 nm for 2000 s.
 
@@
 \section{moo3}
-
-\subsection{used}
-
-\ce{MoO3}, an alternative interpretation in terms of tetrahedral coordination of Mo atoms is also proposed.
-This is caused by the fact that four of the six surrounding O atom are at distances from 1.67\AA to 1.95\AA, while the remaining two are as far as 2.25 and 2.33\AA.
-This also stress that the \ce{MOO6} octahedra are rather distorted.
+\subsection{not used}
 
@@
 
+10nm MoOx as hole extraction layer (HEL).
+Without HEL, Holes accumulates at QD/anode interface, causing increased recombination rate.
+With HEL, hole diffuse into this layer, reducing the recombination.
+
+The molecular unit in crystal exhibits different vibrational frequencies from that in solution or gas phases.
+
+\ce{Na2Mo4O_{13}} phases monoclinic at RT, solid solubility of \ce{Na2MoO4} in solid \ce{MoO3} is high. vapor pressure of \ce{Na2Mo4O_{13}} over \ce{MoO3}.
+
+melting point of \ce{Na2Mo4O_{13}}
+Mp: \ce{Na2Mo2O7} 960K
+
+\ce{MoO3} vapor pressure:
+
+The real phase diagram is the one between \ce{Na2Mo4O_{13}} and \ce{MoO3}.
+the growth temperature could be much lower than the eutectic point.
+
+KI MP:  681
+NaI MP: 661
+
+NaOH Raman peaks lie at 3633 cm. \cite{walrafen2006} Raman scattering of \ce{Na2SiO3} exhibit major peak at 966 and 589 cm.\cite{Richet1996}
+
+visibility of mica thin layer on \ce{SiO2}-Si.
+\cite{Castellanos-gomez2011} 1.5\% contrast is almost at the threshold of human eye sensitivity.
+When the thickness is below 60nm, Raman could not detect mica.
+
+\ce{MoO3} SWNT by hydrothermal method.\cite{Hu2008a} Raman spectra is off compared to single crystal \ce{MoO3}.  Van der Waals interaction and layered structure make NT possible.
+
 The refractive index is between $ 2.2\sim 2.4$ along $a$ axis, and $ 2.5\sim 2.8$ along $c$ axis.
 Comparison to the low frequency dielectric constant ($18.0\pm1$) implies a primarily ionic bonding in \ce{MoO3}.\cite{He2003}
+\citeauthor{Wang2013c} changed the NW growth direction by changing the shape of droplets; \citeauthor{Biswas2013} reported enhanced aspect ratio of Ge NWs from bimetallic alloy.
 
-\cite{Matar2011} Using electronegativity $\chi$ and chemical hardness $\eta$ to assess electron affinity $E_a$, work function $W_f$, Fermi energy $E_f$ and band gap $E_g$.
-\begin{align}
-\chi &= 0.5(W_f + E_a)\\
-\eta & = 0.5(W_f - E_a)
-\end{align}
-where I is ionization potential and $E_a$ is electron affinity.
+We first repeated the previous growth on ITO/glass, and then found similar deposition phenomena on glass and mica substrates.
+We suspected that the morphology difference on the substrates employed in this study arises from the compositions difference.
+Both mica and glass contains alkaline elements which are absent in Si and \ce{SiO2}/Si substrates.
+We primarily verify this hypothesis by utilizing \ce{NaOH} treated Si substrates and found that the overall morphology almost reproduces that on ITO and mica substrates.
+We then propose a new growth mechanism based on the VLS process to explain the deposition of \ce{MoO3} on alkaline-ions-containing substrates.
 
-Correlation between optical band gap and formation enthalpy; reaction occurs in order to form compounds with a larger gap.
-$E_g = A \exp(0.34E_{\Delta H^0})$, and A adopts different values depending on the metal elements:
+ITO versus NaOH images.
+
+According to the phase diagram shown in Fig.~\ref{fig:pd}, \ce{Na2MoO4} - \ce{MoO3} phase above 800 \si{\degreeCelsius} are \ce{Na2MoO4}(l) + \ce{MoO3}(l), More discussion should follow $\ldots$.
+
+% droplet position statistics
+\begin{figure}[htb]
+\centering
+\includegraphics[width=0.6\textwidth]{droplets_sta}
+\caption[Droplet position statistics]{Droplet position statistics. On-tip and not-on-tip counts variation with respect to growth time. }
+\label{fig:mo3dropsta}
+\end{figure}
+
+Nanotower is a less common morphology in the structures of nanomaterials.\cite{Kharissova2010} We have not found report on  \ce{MoO3} nanotower structures, although there are several studies on \ce{In2O3},\cite{Jean2010,Yan2007}, GaN\cite{Xiao2012} and ZnO\cite{Zhang2013c}.
+\citeauthor{Jean2010} investigated the growth mechanism of \ce{In2O3} nanotowers and attributed it to the periodical axial and continuous lateral growth interaction, where the former was first guided by Au-In alloy liquid, and subsequent by self-catalytic In droplets (MP 156C) while the latter due to VS process.
+In contrast, \citeauthor{Yan2007} observed similar \ce{In2O3} nanotower growth and proposed that the axial growth is controlled by Au-catalytic VLS process.
+\citeauthor{Xiao2012} reported the GaN nanotower grown on Ni-coated Si(111) substrates and explained the growth as asymmetric self-copy process based on VLS mechanism.
+\citeauthor{Zhang2013c} studied the growth of ZnO nanotower and provided a competitive model between axial and lateral growth controlled by Zn vapor to explain the as-synthesized structures.
+(When ZnO and carbon mixture was used as source instead of ZnO alone, nanorods array results, presumably due to the stable supply of Zn vapor owing to the gentle carbothermal reduction.) Therefore the fluctuation of reagents is probably responsible for tapering and periodical modification, which is absent in the coin roll style growth of \ce{MoO3} tower on Si.
+The occasionally observed tapering or enlarging on \ce{MoO3} tower can be attributed to the cooling down growth.
+
+We divide the growth into two stages according to the emerging time of long belts and towers.
+In first stage the growth is dominated by lateral growth, as illustrated in .
+In the second stage, \ce{NaxMoO3} is evaporated and recondensed in the low temperature region, and some droplet will form, and when at proper locations, introduce secondary VLS growth.
+
+In first stage, the Na-Mo-O liquid is formed and have much more higher absorption rate than that of bare substrate.
+The absorbed species will diffuse along the surface and inside the liquid.
+It was difficult to estimate which diffusion path one is faster.
+
+\textbf{open questions}
 \begin{itemize}
-\item A=0.8 for s and f block elements,
-\item A = 1 for d block elements,
-\item A = 1.35 for p block elements.
+\item Is the liquid consumed? if so, how? : evaporation
+\item How the size of liquid is related to the morphology evolution?
+\item Possible doping level of alkaline ions
+\item other lateral growth mode such as Ni-W-S system
+\item VLS-VS interaction, or possible solution-liquid-solid, VSS,
+\item the interpretation of phase diagram
+\item the overall molar amount of NaOH and MoO3 deposition
+\item Young's parameters, contact angle informations, Gibbs free energy calculation
+\item catalyst composition variation during growth
+\item \ce{Na2Mo4O_{13}} phases, solid solubility of \ce{Na2MoO4} in solid \ce{MoO3} is high.
+\item vapor pressure of \ce{Na2Mo4O_{13}} and \ce{MoO3}.
 \end{itemize}
 
-\citeauthor{Sreedhara2013} studied the kinetics of photodegradation of methylene blue\footnote{\ce{C16H18N3SCl},319.8 g/mol, MP: 100C accompanied with decomposition \url{http://en.wikipedia.org/wiki/Methylene_blue}} dye by few layer \ce{MoO3}.
-For the photodegradation method, it was stated that `` the samples were collected after the photoreaction had been centrifuged for 5 min to remove the photocatalyst before UV-Vis measurement.''
-
-% Melting points 
-\begin{table}[htb]
-\centering
-\renewcommand*{\thetable}{S\arabic{table}}
-\caption{physical constants of reactants }\label{tb:thermo}
-\begin{tabular}{lccr}
-\toprule
-Material & MP(\si{\degreeCelsius}) & BP(\si{\degreeCelsius}) & reference\\
-\midrule
-\ce{NaOH}        & 318 & 1388 & handbook  \\
-\ce{NaI}        & 651 & 1300 & MSDS    \\
-\ce{KI}        & 681 & 1330 & MSDS   \\
-\ce{Na2CO3}        & 851 & Not determined & MSDS    \\
-\ce{Na2MoO4}        & 687 & Not available & handbook   \\
-\ce{MoO3}    & 795 & 1155 & MSDS   \\
-\ce{MoO2}    & 1100(decomp) & Not available & MSDS   \\
-\bottomrule
-\end{tabular}
-\end{table}
+As shown in Fig, we found several solid clusters with diameter about 1 $\mu m$ on the top part of long belts.
+According to the \ce{Na2MoO4}-\ce{MoO3} binary compounds phase diagram, we expect the terminating solid clusters have a Na:Mo ratio close to 0.6.
+The experimental results match well with this predictions.
+EDX analysis reveal the presence of Na on the solid cluster but not at about 1$\mu m$ away from previous location.\footnote{the sensitivity of our instrument is estimated to be 1\% atomic level} Quantitative atomic ratio derived from the solid cluster is not close to the one predicted by phase diagram probably due to the high Mo content in adjacent area.
+However, XRD examinations on a short time growth sample revealed a possible \ce{Na2Mo4O13} phase(PDF 028-1112), providing an indirection evidence of the droplet composition.
+We also suspect that the growth will become different below 500 \si{\degreeCelsius} since no liquid would remain.
+Substrate placed at low temp end show.
+We can also deduce that other sodium compounds can be employed as substrate treatment agent. This argument is confirmed by \ce{Na2CO3} and \ce{KI} assisted growth.
 
 \section{ws2}
+\subsection{Seeded Growth of Tungsten Oxide NWs}
+With the oxidation experiments study in Sec.~\ref{sec:woxd}, favorable conditions for local growth of NWs were extracted to perform seeded growth.
 
-\textbf{\ce{WS2}-\ce{WO3}}: 1 kW light source(Hg, or Xe lamp), photon flux, phenol (\ce{C6H5OH}, 94.1g/mol, MP 40C)concentration is 20 mg/L, hydroxyl group.
-The quantitative analysis of phenol was performed via a standard colorimetric method.\footnote{\url{http://omlc.ogi.edu/spectra/PhotochemCAD/html/072.html}}
-\citeauthor{DiPaola1999} prepared \ce{WS2}-\ce{WO3} mixture in two methods, sulfurization of \ce{WO3} and oxidation of \ce{WS2},with the latter are more active.
-\citeauthor{DiPaola1999} also concluded that the actual efficiency of mixed \ce{WS2}-\ce{WO3} catalysts depends on the ratio of each composition present of the surface of the particles, and the maximum of photoactivity is obtained with 40-50\% surface molar ratio of \ce{WS2}.
+\begin{figure}[htb]
+\centering
+\subfloat[]{\label{fig:sga}\includegraphics[width=0.4\textwidth]{wox_sg_a.jpg}}\hspace{0.04\textwidth}
+\subfloat[]{\label{fig:sgb}\includegraphics[width=0.4\textwidth]{wox_sg_b.jpg}}
+\caption[Characterization of seeded growth \ce{WO3}: SEM]{Characterizations of seeded growth.
+(a) SEM graphs of \ce{WO3} NWs on \ce{SiO2/Si} substrate.
+(b) A high magnification view showing uniform NW growth and close-up view of one NW.
+}
+\label{fig:woseedsem}
+\end{figure}
 
-ref 25, 28 and 41.
+As shown in Fig.~\ref{fig:sgb}, dense NWs array was obtained on tungsten powder seeds with individual wires of length up to 5 $\mu$m and diameter about 50 to 200 nm, according to the estimation made in the close-up view.
+Each tungsten powder stood as independent growth site (Fig.~\ref{fig:sga}) with island-layer growth on the substrates, a common feature without using tungsten powder as seed under current experimental conditions.
+It was occasionally observed that NWs growth was initiated adjacent some tungsten powders.
+This phenomenon was correlated to the local trap of vapor flow since it was more often found among the enclosed area by tungsten powders.
+It is also found that the diameter of NWs decrease as the distance between powders and upstream edge increases.
+This is a combination effect of lower temperature and reduced \ce{WOx} growth species supply.
+Similar phenomena were observed in other studies.
+\citeauthor{Thangala2007} reported that a decrease in NW density with increasing substrate temperature, and an increase of NW density with increasing partial pressure of oxygen.\cite{Thangala2007}
+
+% seeded edx 
+\begin{figure}[htb]
+\centering
+\includegraphics[width=0.5\textwidth]{wo3_seed_edx}
+\caption[Composition analysis on seeded growth \ce{WO3} NWs]{EDX spectroscopy on seeded growth \ce{WO3} NWs.}
+\label{fig:woedx}
+\end{figure}
+Energy-dispersive X-ray spectroscopy (EDX) analysis on the seeded growth \ce{WO3} NWs is shown in Fig.~\ref{fig:woedx}.
+Only W and O elements were detected on the NW array.
+The background level from 3 to 8 keV was a manifestation of the continuous components of W X-ray spectrum.
+
+% sg raman xrd
+\begin{figure}[htb]
+\centering
+\subfloat[]{\label{fig:sgxrd}\includegraphics[width=0.45\textwidth]{xrd_cs_before}}\hspace{0.04\textwidth}
+\subfloat[]{\label{fig:sgram}\includegraphics[width=0.45\textwidth]{wox_raman_1}}
+\caption[Characterization of seeded growth \ce{WO3}: XRD and Raman]{ (a) XRD pattern of as-prepared sample indicating the \ce{WO3} phase and the presence of metallic core.
+(b) Raman spectrum on NWs region showing the feature of \ce{WO3}.}
+\label{fig:woseedxrd}
+\end{figure}
+
+Fig.~\ref{fig:sgxrd} is the XRD spectrum of one typical sample.
+The peaks under circular symbol were identified to be the monoclinic \ce{WO3} phase (ICDD PDF 01-083-0950, \emph{a}=7.30084 \AA, \emph{b}=7.53889 \AA, \emph{c}=7.6896 \AA, $\beta$=90.89$^\circ$), while the peak under the triangular symbol was indexed to cubic tungsten phase (ICDD PDF 04-16-3405, \emph{a}=3.157 \AA), in agreement with the EDX analysis (Fig.~\ref{fig:woedx}).
+This means that during the \ce{WO3} seeded growth of 4 h heating at 1000 \si{\degreeCelsius}, the tungsten powder in downstream low temperature region (600-700 \si{\degreeCelsius}) is not entirely oxidized.
+Micro-Raman scattering spectroscopy was performed on the as-synthesized sample as well.
+During Raman examination, the laser spot was carefully focused onto the NWs on powders and several inspections on different positions were observed to ensure the reproductivity of spectra data.
+As shown in Fig.~\ref{fig:sgram}, five distinct bands were well resolved, with peaks located at 131, 265, 327, 711 and 803 \si{cm^{-1}}, respectively.
+This pattern was typical features of \ce{WO3}, consistent with previous study.\cite{Salje1975a,Dixit1986} The high background level probably arises from the metallic core.
+
+% sg tem
+\begin{figure}[htb]
+\centering
+\includegraphics[width=0.9\textwidth]{JAP-2column_Fig5major.jpg}
+\caption[Characterization of \ce{WO3}: TEM]{TEM graphs of as-prepared NWs.
+(a) TEM image of one nanowire with diameter about 40 nm.
+(b) HRTEM images showing the spacing is 0.38 nm, corresponding to (002) plane distance.}
+\label{fig:woseedtem1}
+\end{figure}
+
+TEM specimen was prepared by using carbon grid to slightly scratch the as-grown sample.
+Fig.~\ref{fig:woseedtem1} shows the feature of majority NWs.
+The growth direction is determined to be perpendicular to (002) plane.
+The streaking in SEAD pattern presumably arises from stacking defaults.
+The author also find some NWs exhibit high crystalline quality, as revealed by the TEM analysis in Fig.~\ref{fig:woseedtem2}.
+The NW grew normal to (002) plane with a measured lattice spacing of 3.79 \AA, which is favorably compared to the XRD peak at $23.07^\circ$ (7.7103 \AA).
+The sharp SEAD pattern and clear phase contrast in HRTEM demonstrated are both strong evidence of good crystallinity.
+This formation indicated current growth parameters have promising potential to obtain highly crystalline \ce{WO3} NWs in large scale.
+
+% sg tem
+\begin{figure}[htb]
+\centering
+\includegraphics[width=0.9\textwidth]{JAP-2column_Fig5minor.jpg}
+\caption[Characterization of \ce{WO3}: TEM cont]{TEM graphs of as-prepared NWs.
+(a) TEM image of one nanowire, the diameter is about 70 nm.
+(b) HRTEM images showing the spacing is 0.379 nm, corresponding to (002) plane distance.}
+\label{fig:woseedtem2}
+\end{figure}
+
+In regarding to the formation of NWs on tungsten powder itself, this study assumes the driving force is related to interfacial strain between W and \ce{WOx}.
+Oxidation of tungsten proceed slowly at room temperature and an oxide layer of 100 \AA was found on the surface of tungsten foils.\cite{Warren1996} The tungsten powder used in current study would be covered by a thin oxide layer as well.
+During oxidation, different oxidation rates exist for different crystallographic orientations on the tungsten powder.
+Oxidation occurring at boundaries and defects are preferred thermodynamically.\cite{You2010} Compressive strain will gradually accumulate at the tungsten oxide/tungsten interface, which might limit the diffusion rate of oxygen at temperature lower than 500 \si{\degreeCelsius}.\cite{tungsten1999} At elevated temperature, cracks will primarily occur, as observed in Fig.~\ref{fig:pdtemp}.
+When heated up, tungsten and the oxide shell will probably relax the strain by converting into substoichiometric NWs, a similar process as suggested by \citeauthor{Klinke2005} in the chemically induced strain growth of tungsten oxide NWs.\cite{Klinke2005} It is worth noting that tungsten oxide nanowires could also formed when \ce{WO3} is reduced.\cite{Sarin1975} The elongation of \ce{WOx} is thermodynamically favorable during the conversion from metallic tungsten to tungsten oxide as well.
+Local evaporation-condensation process might also contribute to the formation of NWs on tungsten powder.
+
+The enhanced yield of NWs obtained via seeded growth could be explained by a vapor-solid (VS) mechanism.
+External supply of growth species will condense onto the powders and substrate simultaneously, promoting the elongation of NWs on power as well as resulting island-layer growth on substrate.
+The local NW density in oxidation experiment was much higher than that of seeded growth.
+It is reasonable to presume that during seeded growth, several NWs in a small region on powder will coalescence, as evidenced by the bundled structures.
+At last, the author would like to point out that when low purity tungsten powder (3N) was used as source, sodium tungsten oxide nanowires were found to be dominant in the final product.
+The details have been published.\cite{Sheng2014} It seems surprising that when 3N powder was used as seeds, only \ce{WO3} nanowires were obtained.
+This result was attributed to the lower temperature and significantly reduced amount of 3N powder used in the seeded growth, compared with the conditions used in Ref.\cite{Sheng2014}.
+The source material in seeded growth is not limited to high purity tungsten powder.
+Instead, any material that could produce appropriate growth vapor could be employed, indicating the versatility of this approach.
+
+\subsection{Optimization of W powder Oxidization}\label{sec:woxd}
+
+Understanding the oxidation of tungsten powder is the key to obtain high yield in seeded growth.
+Oxidation of tungsten have been investigated under diverse conditions, such as at elevated temperature (\textgreater 1100 \si{\degreeCelsius} ) and oxygen pressure on the order of Torr,\cite{Base1965} and at temperatures ranging from 20 to 500 \si{\degreeCelsius} under atmosphere pressure.\cite{Warren1996} \ce{WO_x} NWs were readily found when tungsten (foil, wire, or powder) is oxidized under various conditions.\cite{Zhu1999,Karuppanan2007,Hsieh2010} However the study on tungsten powder oxidation behavior between intermediate temperature range and under low pressure is still rare.
+This work studied the oxidation of tungsten powders with diverse size within temperature range from 500 to 1000 \si{\degreeCelsius} and under several mTorr oxygen partial pressure.
+Using tungsten powder as seed, the author further illustrate an economic approach to obtain large yield of \ce{WO3} nanowires at relatively lower temperature than previous efforts.
+It is demonstrated that there is an optimal tungsten powder size under our experimental conditions for seeded growth.
+This will provide some insight on the role of tungsten powder as source material in CVD growth of \ce{WO_x}.
+
+Commercial available tungsten powders with different size are usually associated with purity variation as well, as already listed in Table.~\ref{tab:ch5pre}.
+The dimensions of tungsten powder were obtained by measuring the average size in SEM graphs.
+A systematic investigation was performed on the oxidation behavior of tungsten powder to evaluate the temperature effect, size-dependence and influence of oxygen partial pressure.
+% seed optimal
+\begin{figure}[htb]
+\centering
+\includegraphics[width=0.6\textwidth]{JAP-2column_Fig1.jpg}
+\caption[W powder oxidation: temperature effect]{SEM graphs of 99.9\% (3N) tungsten powder oxidization at different temperatures of a) 500 \si{\degreeCelsius}, b) 600 \si{\degreeCelsius}, c) 650 \si{\degreeCelsius}, d) 750 \si{\degreeCelsius}, showing the optimal temperature for local formation of nanowires is between 600--650 \si{\degreeCelsius}.
+Oxygen flow rate is 1 sccm.}
+\label{fig:pdtemp}
+\end{figure}
+
+Fig.~\ref{fig:pdtemp} illustrated the effect of temperature on the morphological change and surface nanowires formation of 3N powder.
+At 500 \si{\degreeCelsius}, most tungsten powder retained its original shape and a layer of tiny dense NWs begun to grow.
+When temperature was increased to 600 \si{\degreeCelsius}, 3N powder started to crack with longer NWs on the isolated surface.
+Further increase of temperature lead to irregular shapes of tungsten power and aggregation of NWs, giving rise to the nanorods and bunched or bundled structures.
+It could be determined from the morphology variation that the optimal seeded growth temperature for 3N powder was in the range of 600 to 650 \si{\degreeCelsius}.
+% seed optimal
+\begin{figure}[htb]
+\centering
+\includegraphics[width=0.6\textwidth]{JAP-2column_Fig3.jpg}
+\caption[W powder oxidation: size effect]{SEM graphs illustrating the oxidization of four different size of tungsten powders at 600~\si{\degreeCelsius} and 1 sccm oxygen flow.
+a) 17 $\mu m$, b) 32 $\mu m$, c) 3.3 $\mu m$, d) 1.5 $\mu m$.}
+\label{fig:pdsize}
+\end{figure}
+
+Fig.~\ref{fig:pdsize} depicted the oxidation of different sizes of tungsten powder under the same experimental conditions.
+In contrast to the morphology of 3N powder shown in Fig.~\ref{fig:pdtemp}, 3N5 powder surface is primarily covered with sub-micro particles as well as some short tiny NWs, whereas 4N5 and 5N powder were thoroughly oxidized, showing branched flowers feature.
+This dramatic difference could be explained in terms of surface energy and oxygen diffusion.
+With smaller dimension, the increased surface-to-volume ratio and short diffusion path both lower the energy barrier of oxidation.\cite{tungsten1999} It was logical to deduce that higher temperature or increased oxygen level might favor the NWs formation on 3N5 powder.
+When it comes to seeded growth, however, the powder size distribution was an important factor to give uniform NWs deposition.
+Since the size distribution of 3N powder is more uniform than that of 3N5 powder, the author employed the former as seeds.
+% seed optimal
+\begin{figure}[htb]
+\centering
+\includegraphics[width=0.6\textwidth]{JAP-2column_Fig2.jpg}
+\caption[W powder oxidation: oxygen pressure]{SEM graphs of 3N tungsten powder oxidization at 600 \si{\degreeCelsius} under different rates of oxygen flow: a) 1 sccm, b) 2 sccm, c) 3 sccm, d) 10 sccm.
+The oxygen partial pressures were 13 mTorr, 23 mTorr, 32 mTorr, and 82 mTorr, respectively with background pressure subtracted.}
+\label{fig:pdoxy}
+\end{figure}
+
+Fig.~\ref{fig:pdoxy} depicted the morphology change of 3N powder with respect to varied oxygen partial pressure.
+When the oxygen flow is lower than 3 sccm, 3N powder almost stayed as the same, with cracks separating the dense layer of NWs.
+When oxygen flow is increased to 10 sccm, the 3N powder exemplified an enlarged version of that for 4N5 or 5N powder under 1 sccm oxygen flow.
+This observation again supported the surface energy explanation.
 
@@
 
-A direct gap of $\sim 2eV$ at the corners of BZ is formed in 1L \ce{WS2}, Growth on bottom piece show the multiple domain flakes occurs at initial stage of the growth, starting from \ce{WO3} particles.
-%\cite{Cong2013}
+A direct gap of $\sim 2eV$ at the corners of BZ is formed in 1L \ce{WS2}, Growth on bottom piece show the multiple domain flakes occurs at initial stage of the growth, starting from \ce{WO3} particles.\cite{Cong2013}
+
 \subsection{to be used}
@@
 The two prismatic phases are semiconducting, and the octahedral one is metallic-like.
-
 1T phase may be the result of a transformation from the 3R to the 2H phase by an intermediate 1T phase that is trapped by fast quenching
-
 \end{quote}
@@
 The folding of BZ along $\Gamma-M$ would cause the M point to coincide with $\Gamma$ point, so LA(M) phonons would become Raman active in a first-order process.
-
-\ce{SiO_x}-Si, \ce{WS2} absorption coefficient $10^{-7}m^{-1}$, mean free path of photo-excited charge carriers 1 $\mu m$.
-the wave vector of photon is considerably small than size of BZ, therefore The wave vector of phonon in Raman scattering usually close to zero.
-
-Multiple phonon scattering, For two identical phonons, the corresponding Raman peak in the spectrum is called an overtone of the peak from the corresponding one-phonon process.
-And the wave vector conservation rule is automatically filled, therefore the phonon involved is not limited to BZ center anymore.
-\[
-I(G) \approx \sum_k \frac{\langle f|H_M|b\rangle \langle b|H_{ep}|a\rangle \langle a|H_M|i\rangle}{(E_p - E_k^{\pi *}- E_k^{\pi}-i\gamma)(E_p - E_k^{\pi *}- E_k^{\pi}-i\gamma- \hbar\Omega_{G})}
-\]
 
@@
 a single nanowire tends to minimize its surface. 2D isoperimetric quotient or circularity $C= \frac{4\pi A}{P^2}$, where A is area and P is perimeter of the cross-section.
-
-\section{ECD}
-
-Characterization of ECD (work like a thin-film batteries) includes transmission measurement and associated EC calculation, charge-discharge time, current-time curve and the fitting of obtained data.
-
-The coloration efficiency (CE) represents the change in the optical density (OD) per unit charge density ($Q/A$, in units of \si{\cm^2\per\coulomb}) during switching and can be calculated according to the formula:
-\begin{equation}
-CE = \frac{\Delta~OD}{(Q/A)} [cm^2/C],
-\end{equation}
-where OD = $log(T_{bleach}/T_{color})$. The EC and optical density depend on the wavelength and are usually higher in the near IR than in the visible region.
-Using Ohm's law($U_s = IR = RQ/t_s$) with switch voltage $U_s$, resistance R and surface area A, switching time $t_s$ could be estimated as
-\begin{equation}
-t_s = \Delta~OD\cdot A \cdot R /(CE\cdot U_s).
-\end{equation}
-
-battery and ECD.\cite{Granqvist2012} electrolyte: PVB (poly vinyl buteral).
-alternative materials and design: organic, Prussian Blue as EC materials, metal hydrides, suspended particle device, liquid crystal, electroplating,
-challenges: large area nanoporosity, transparent conducting contact, electrolyte with good ionic conductivity and poor electronic conductivity, stable under UV; assembly and large scale manufacturing;
-cathodic coloration:
-anodic coloration:
-The coloration mechanism: \ce{MO6} octahedrons lead to $e_g$ and $t_{2g}$ level and ion channelling.
-ref54,60,65,66,200,209,
-
-\ce{WO3} as cathodic and either polyaniline(PANI) or Prussian white (PW) as anodic electrochromic half cells. \cite{Heckner2002}
-
-Characterization of ECD includes transmission measurement and associated EC calculation, charge-discharge time, current-time curve and the fitting of obtained data.
-
-\begin{quote}
-a viable electrochromic smart window must exhibit a cycling life time \textgreater $10^5$ cycles, corresponding to an operation life at 10 -- 20 years.
-\end{quote}
-
-\citeauthor{Sella1998} studied the optical and structural properties of RF sputtered thin film of \ce{WO3} and \ce{VO2} for electrochromic devices.
-Ionic conductor was built using transparent polymer electrolyte, which was prepared from a solution of 1M \ce{LiClO4} in propylene carbonate which was mixed with methylmetharcylate (MMA).
-The main characteristics of polymer electrolyte were: viscosity at 25 \si{\degreeCelsius} $\approx$ 12920 Pa.s, conductivity $\approx 10^{-2}-10^{-4}$ \si{\per\ohm\per cm},non-hygroscopic if PMMA concentration \textgreater 30\%.
-A specific counter-electrode layer was not used since the encapsulated polymer electrolyte processes a very high ion storage capacity.\cite{Sella1998}
-
-The device proposed was reproduced as shown in Fig.~\ref{fig:Sella1998ECD}
-\begin{figure}[htb]
-    \centering
-    \includegraphics[angle=270,width=0.8\textwidth]{Sella1998ECD}
-    \caption{citation, see original captions} \label{fig:Sella1998ECD}
-\end{figure}
-
-\subsection{polarons}
-
-The concept of polaron was first proposed by Landau in 1933.
-In ionic or highly polar crystals, such as II-VI semiconductors, alkali halides and transition metal oxides, the Coulomb interaction between a conduction electron and the lattice ions results in a strong electron-phonon coupling.
-A new quasi-particle, virtual phonon, can be defined corresponding to the effect of electron pulling nearby positive ions towards it and pushing nearby negative ions away.
-The electron and its virtual phonons, taken together, can be treated as a new composite particle, called an electron polaron; the hole polaron is defined analogously.
-\cite{Devreese1996}
-
-\subsection{NW waveguide}
-
-seriously pursued.

### 2014-09-28 misc/mwe.tex
moo3 draft 50%
ch2 enhanced
inital review revised 1
list of abbreviation temperatory solution found
paper draft and supporting info tidy up

--- 2014-01-26 misc/mwe.tex
@@
    \newacronym{cft}{CFT}{crystal-field theory}
-
    \makeglossaries
@@
     \renewcommand{\glossarypreamble}{\thispagestyle{myheadings}} % after, this works.
+    %\renewcommand{\acronymname}{LIST OF ABBREVIATIONS}
     \printglossary[type=\acronymtype]
+    \addcontentsline{toc}{chapter}{\acronymname}
     \clearpage
@@
 
- %   \include{./ch-intro/ch-intro}
-
-After 20 minutes sonication, the dispersion is milky.
-We measured the transmission spectra of this dispersion immediately upon sonication and after 40 hrs for gravity sedimentation, as illustrated in Fig.~\ref{fig:moabs}.
-The t0 line mainly arises from the scattering of flakes in the dispersion.
-There are two scattering mechanisms: Rayleigh scattering and Tyndall scattering.
-Rayleigh scattering, which occurs when particles are comparable to wavelength, is inversely proportional to the fourth power of wavelength; While Tyndall scattering, which occurs when the particles are larger, is inversely proportional to the square of the wavelength.
-To fully evaluate the true absorbance of the sample itself, one needs to decouple the scattering part from apparent absorbance.
-Generally we select one part of spectrum and assume it is only caused by scattering.
-Then a empirical dependence shown in Eq.~\ref{eq:sca2} is used as polynomial fitting model.
-
-\begin{align}
-Abs_{sca}  & = a\times \lambda^{n}  \label{eq:sca1}\\
-\log{Abs_{sca}} & = \log{a} + n*\log{\lambda} \label{eq:sca2}
-\end{align}
-
-After least-squares fitting, the coefficients $a$ and $n$ can be used to estimated the scattering in other wavelengths.
-The fitting of n usually falls between -2 and -4.
-We examined the t40h line in Fig.~\ref{fig:moabs} and found the scattering part is almost zero.
-Therefore we did not perform aforementioned fitting.
-This is not always the case.
-In chapter on the \ce{WS2} section, we do need to do so.
-
-\begin{itemize}
-\item s inversely proportional to the fourth
-\item  inversely proportional to the fourth
-\item s inversely proportional to the fourth
-\end{itemize}
-
-\begin{figure}[htb]
-\centering
-\subcaptionbox{\label{fig:moind}}{\includegraphics[width=0.35\linewidth]{n_MoO3}}%
-\subcaptionbox{\label{fig:mocon}}{\includegraphics[width=0.55\linewidth]{Graph20}}
-\caption[Refractive indices of \ce{MoO3}]{(a) Refractive indices of \ce{MoO3} Dashed line is n along $a$ axis while solid line is along $c$ axis.
-(b) optical contrast mapping of 1L \ce{MoO3} on \ce{SiO2}-Si.
-The x axis is \ce{SiO2} thickness, y axis is wavelength.It is assumed that the incident light is polarized along c axis of \ce{MoO3}.}
-\label{fig:mofl}
-\end{figure}
-%[width=0.45\textwidth]
-
-Rayleigh scattering and Tyndall scattering.
-Rayleigh scattering, which occurs when particles are comparable to wavelength, is inversely proportional to the fourth power of wavelength; While Tyndall scattering, which occurs when the particles are larger, is inversely proportional to the square of the wavelength.
-To fully evaluate the true absorbance of the sample itself, one needs to decouple the scattering part from apparent absorbance.
-Generally we select one part of spectrum and assume it is only caused by scattering.
-Then a empirical dependence shown in Eq.~\ref{eq:sca2} is used as polynomial fitting model.
+ %  \include{./test}
+     \include{./SI_thesis}
+     \include{./draft}
+     \include{./paper}
 

### 2014-09-28 misc/paper.tex
paper draft and supporting info tidy up

--- 2014-09-06 BackMatter/paper.tex
@@
 \chapter{paper reading}
-
-\section{WO3}
-
-Tungsten bronzes was coined by Wohler in 1837.\cite{Deb2008} \ce{Na_{x}WO3}
-
-\subsection{applications}
-
-\citeauthor{Wang2009a} mentioned that amorphous \ce{WO3} can only be used in lithium-based electrolytes due to its in-compact structure and high dissolution rate in acidic electrolyte solutions.
-Electrochromic materials that can endure acidic electrolytes without degradation should be developed.
-Crystalline \ce{WO3} nanostructures with their much denser structures and small particle sizes are promising to be used as suitable electrochromic material in acidic electrolytes.
-
-photocatalytic applications in solar hydrogen generation and organic pollutant degradation.
-
-photocatalyst\cite{Macphee2010},
-photoelectrochemical energy application \cite{Su2010}
-
-Raman \cite{Xiao2007}.
-Silver has the strongest SERS enhancement due to the larger imaginary part of the dielectric constant and higher thermal conductivity.
-Milli-Q grade water ((Milli-pore)\textgreater 18.2Mohm).
-
-MB Raman peaks: 445, 1618, ref20. some peak splitting and shift observed on SERS, attributed to chemical adsorption. definition of Raman enhancement factor (9,26).
-
-SERR MB on Ag. \cite{Nicolai2003}
-MB: the absorption spectrum in VIS is used to infer about different adsorbed forms of MB. the formation of large aggregates. I call attention to the fact that.
-
-WO3: effective mass of bipolaron = 1.9me. for electron, for hole:
-unzip nanotube. passivate BN ribbons with O and S; another player terrones psu.
-
-\ce{WO3} catalyst.\cite{Miyauchi2013}  potential of CB e more negative than redox potential of \ce{O2}-\ce{O2^-} (-0.046 V vs NHE at pH 0).
-Z-scheme two photo absorption.
-photogenerated ele in CB of WO3 can reduce itself by formation of color centers.
-
-electrochromic films. \cite{Yoshimura1985}
-
-ECD \cite{Jiao2012} recent review \cite{Mortimer2011}
-
-PEC, photoelectrode, WO3 and Si tandem structures.\cite{Coridan2013}
-
-WO3 photoactivity MB. \cite{Watcharenwong2008}
-A low recombination rate is preferred for high photocatalytic efficiency. The simultaneous migration of electrons and holes.
-
-\subsection{properties}
-
-\citeauthor{Chatten2005} also studied the oxygen vacancy in different phases of \ce{WO3}.\cite{Chatten2005}
-
-2D wo3.\cite{Kalantar-zadeh2010a} 
-WO3 plasmon \cite{Manthiram2012}
-
-DFT doped \ce{WO3} for photocatalytic reaction.\cite{Wang2012} CBM arises from W $5d$ states and splits into $t_{2g}$ and $e_g$ states under crystal field.
-VBM comes from O $2p$ states, including $2p_\sigma$ (along \ce{W-O} bonds) and $2p_\pi$ (normal to \ce{W-O} bonds).
-
-oxygen vacancies in \ce{WO_{3-x}}.\cite{Wang2011b}  Coloration and electron conductivity changes.
-\citeauthor{Wang2011b} found strong dependence of WO3-x electronic properties on $V_O$ concentration and the the crystallographic direction on which O is removed.
-DFT band gap calculation is close to experimental value.
-Vacancy levels are found at 2.1eV.
-
-The Raman spectra of \ce{WO_x} is rare because of the difficulty of preparing pure suboxides phase and the strong shielding of \ce{WS2}.
-Yet it does exhibit distinct Raman spectra.
-\cite{Tenne2005} The 870 line is attributed to \ce{W3O8}.\cite{Hardcastle1995}
-
-\citeauthor{Huang2006} studied the \ce{W3On} cluster with n from 7 to 10.\cite{Huang2006} It was found \ce{W3O9} clusters possess a HOMO-LUMO gap about 3.4eV.
-This closeness to bulk value suggests \ce{W3O9} could be viewed as the smallest molecular unit for bulk \ce{WO3}.
-
-\ce{WO3} indirect gap 2.6eV, direct gap 3.4eV. \cite{Koffyberg1979}
-
-Raman fingerprint of m-\ce{WO3}, h-\ce{WO3} and \ce{WO3.nH2O} were summarized in ref\cite{Daniel1987}.
-
-\ce{WO3} on FTO by flame synthesis.\cite{Rao2014} \cite{Xu2006}
-
-Seeded \ce{W_{18}O_{49}} NWs growth on W foil.\cite{Hong2006a}
-
-\ce{Na2W4O_{13}} growth and optical properties. \cite{Oishi2001} \cite{Itoh2001}
-
-\ce{Na2W4O_{13}} crystal phase \cite{Viswanathan1974}
-
-\citeauthor{Salje1984} studied the transport in \ce{WO_{3-x}} ($0\leq x \leq 0.28$).\cite{Salje1984} It was found \ce{WO_{3-x}} show metallic conductivity when $x > 0.1$.
-
-\ce{WO_{3-x}} \cite{Migas2010}
-
-\ce{WO3} high temperature phase. \cite{Vogt1999}
-tungsten bronzes \cite{Wiseman1976}
-
-Phase transformation of \ce{Na2MoO4} and \ce{Na2WO4} by Raman scattering. \cite{Lima2011}
-
-\ce{WO2} NWs synthesis and raman \cite{Ma2005}.
-
-\ce{WO_{3-x}} CS planes and conductivity.\cite{Sahle1983}
-
-\ce{W-O} equilibrium diagram \cite{Wriedt1989}
-
-\ce{W_{18}O_{49}} electrochromic devices.\cite{Liu2013d} should compare with this one \cite{Wang2008}
-
-nucleation catalysis \cite{Turnbull1952}
-
-\ce{WO3} NWs aggregates. \cite{Kozan2008a}
-
-optical properties of \ce{WO3} gaps\cite{Saygin-Hinczewski2008}
-
-\ce{WO3} atomic layer by exfoliation and annealing \ce{WO3.H2O}. \cite{Kalantar-zadeh2010a}
-
-sodium tungstates raman \cite{Redkin2010}
-
-charge density wave in K-doped \ce{WO3} \cite{Raj2008}
-
-\ce{W_{18}O_{49}} Raman, IR shielding.\cite{Guo2012} \cite{Guo2011}
-broad peak between 750-780 cm-1.
-
-\ce{WnO_{3n-1}} NPs. \cite{Frey2001}
-
-\ce{WO3} growth hydrothermal.\cite{Moshofsky2012}
-
-\ce{W_{18}O_{49}} on tungsten foil by thermal growth\cite{VanHieu2012}
-
-Cathodoluminescence \cite{Parish2007}
-
-optical characterization of WOx film.\cite{Valyukh2010a}
-
-E-beam penetration \cite{Kanaya2002}
-
-optics in electron microscopy. \cite{GarciadeAbajo2010a}
-
-\section{MoO3}
-
-VLS:
-Ge NW growth using Ga as catalyst. \cite{Chandrasekaran2006}
-
-plasmon dispersion in 2D materials, plasmon resonances in visible regions by doping induced free carrier density.
-2D plasmonics, depolarization factors, partial reduction of Mo to a lower valence state.
-\cite{Alsaif2014a}
-
-\subsection{app}
-applications: electrically controlled optical shutters for heat and light modulation, smart windows associated with solar cell to provide dynamical control of incoming illumination.
-
-piranha clean of FTO. 50ms switch.\cite{Scherer2012} 
-nanoscale Kirkendall effect: the outward diffusion of metal cations are balanced by an influx of vacancies. For example, diffusion coefficient of Ni in NiO is higher than that of oxygen.
-
-\ce{MoO3} photocatalytic \cite{Chithambararaj2013}
-photocatalytic experimental setup.\cite{Hupka2006}
-\ce{MoO3} pseudocapacitor  \cite{Brezesinski2010}
-
-\ce{MoOx} few layer as hole selective contact in solar cell.\cite{Battaglia2014}
-\ce{MoO_x} on n-type Si acts as a high work function metal (6.6eV), enabling a dopant-free contact and thus junction-less devices.
-
-\subsection{properties}
-
-\begin{table}[htb]
-\caption{Combinations of ECD configuration}\label{tb:ecd}
-\begin{tabular}{lcccr}
-\toprule
-TC(both side) & electrochromic & ion conductor & counter electrode  & reference\\
-\midrule
-ITO &  \ce{WO3} & \ce{H^+\hyphen} polymer & PANI &\citeauthor{Heckner2002}\\
-FTO &  \ce{WO3} & \ce{K^+\hyphen} polymer & PW &\cite{Heckner2002}\\
-ITO & \ce{WO3} NWs & \ce{LiClO4\hyphen}PC & none & author design \\
-\ce{Na_xWO3} NWs &\ce{WO3} NWs & \ce{LiClO4\hyphen}PC & none & author design\\
-\bottomrule
-\end{tabular}
-\end{table}
-
-\begin{table}[htb]
-\centering
-\caption{Comparison of MoOx ECD}\label{tab:moxecd}
-\begin{tabular}{lcccr}
-\toprule
-$\lambda$ & $\Delta T$ & $t_c$ & $t_b$ & $CE$  \\
-         (nm) & (\%)    & (s) & (s) & ($cm^2/C$)  \\
-\midrule
-Range      & RT-1100    & 10mTorr-1atm & 0 - 100 & 0-30  \\
-\bottomrule
-\end{tabular}
-\end{table}
-
-10nm MoOx as hole extraction layer (HEL).
-Without HEL, Holes accumulates at QD/anode interface, causing increased recombination rate.
-With HEL, hole diffuse into this layer, reducing the recombination.
-
-The molecular unit in crystal exhibits different vibrational frequencies from that in solution or gas phases.
-
-\ce{Na2Mo4O_{13}} phases monoclinic at RT, solid solubility of \ce{Na2MoO4} in solid \ce{MoO3} is high. vapor pressure of \ce{Na2Mo4O_{13}} over \ce{MoO3}.
-
-melting point of \ce{Na2Mo4O_{13}}
-Mp: \ce{Na2Mo2O7} 960K
-
-\ce{MoO3} vapor pressure:
-
-The real phase diagram is the one between \ce{Na2Mo4O_{13}} and \ce{MoO3}.
-the growth temperature could be much lower than the eutectic point.
-
-KI MP:  681
-NaI MP: 661
-
-NaOH Raman peaks lie at 3633 cm. \cite{walrafen2006} Raman scattering of \ce{Na2SiO3} exhibit major peak at 966 and 589 cm.\cite{Richet1996}
-
-hydrogen absorption in \ce{MoO3}.\cite{Sha2009}
-
-\ce{Na6Mo_{11}O_{36}} phase. \cite{Bramnik2004}
-
-\ce{Na6Mo_{10}O_{33}} phase, \cite{Gatehouse1983}
-
-\ce{MoO3} thin film. \cite{Carcia1987}
-
-\ce{H_xMoO3} raman.\cite{Hirata1996}
-
-MoO3 spreading \cite{Leyrer1990}
-
-Na2Mo2O7, Na2Mo4O13 phase transition \cite{SinghMudher2005}\cite{Tangri1992}
-
-visibility of FL \cite{Benameur2011}
-
-exfoliation IPA \cite{Halim2013}  \cite{Zhou2011a}
-
-\ce{MoO3} good style. \cite{Siciliano2009} \cite{Abdellaoui1997}
-
-\ce{MoO3}  DFT study \cite{B511044K} \cite{Cora1997} \cite{Sayede2005}
-
-\ce{MoO3} raman \cite{Lee2002}
-
-visibility of mica thin layer on \ce{SiO2}-Si.
-\cite{Castellanos-gomez2011} 1.5\% contrast is almost at the threshold of human eye sensitivity.
-When the thickness is below 60nm, Raman could not detect mica.
-
-\ce{MoO3} (010) surface defect. \cite{Chen2001}
-
-mass spectrometry data to extract vapor pressure of \ce{NaxMoO3}.
-
-\ce{MoO3} SWNT by hydrothermal method.\cite{Hu2008a} Raman spectra is off compared to single crystal \ce{MoO3}.  Van der Waals interaction and layered structure make NT possible.
-
-TMO review.\cite{Goodenough2013}
-
-h-\ce{MoO3} \cite{Lunk2010} \cite{Zheng2009}
 
@@
 petroleum oil catalytic refinement, solid lubricants in aerospace industry.
-
-heterojunction is employed to transferred photo-generated carriers.
-Schottky barrier conduction band electron trapping and consequent longer electron-hole pair lifetimes.
-Numerous studies have suggested that fine particles of transition metals or their oxides, when dispersed on the surface of a photocatalyst matrix, can act as electron traps on n-type semiconductors.\cite{Zhou2010}
-
-\citeauthor{Cao2014} studied the layer-dependence \ce{MoS2} electrocatalysis and propose the vertical hopping efficiency of electrons instead of the edge site numbers is a key factor for catalytic reaction.\cite{Cao2014} ref19,20
-
-\subsection{strain}
-
-$E_{2g}$ mode is strain sensitive.
-
-\citeauthor{Ghorbani-Asl2013} studied the strain in tubular TMDC and found a linear dependence of Raman scattering on strain (3 \si{cm^{-1}} per percentage for $E_{2g}$mode).\cite{Ghorbani-Asl2013}
-
-For 2D materials, strain may be induced by elongation of an appropriate substrate, e.g.
-by uniform mechanical strain, or by using a material with high thermal expansion coefficient and varying the temperature.
-For TMD MWNT, tensile tests have been reported by various groups.
-However, to date, it is not perfectly clear whether inner and outer walls are stretched simultaneously, or rather the outer walls slide on the inner ones.
-The latter hypothesis would result in a broadening of the Raman signals, while the first one would leave the signal widths rather unaffected.
-In any case, there would be a shift of the Raman signals that can serve as precise scale for determining the strain.\cite{Ghorbani-Asl2013}
-
-\citeauthor{Virsek2007} performed a Raman-TEM integrated study on multiwalled \ce{WS2} NT with diameter \textgreater 200 nm.
-The tubes were synthesized using chemical transport method.
-Up-shift of Raman is explained by strain in the walls.
-This shift is not observed in the specimen by sulfurization process of oxides.
-Applied hydrostatic pressure is isotropic,\cite{Staiger2012} while the strain is expected to anisotropic.
-Strain can also be relaxed by chirality.\cite{Virsek2007}
-
-strain effect by first-principles calculations. direct gap is only maintain in a narrow strain range (-1.3 -- 0.3 \%), \cite{Yun2012}.
-
-Semiconducting to metallic transition in \ce{MoS2} at compressive strain of 15\% or tensile strain of 8\%; direct-to-indirect gap transition for 1L \ce{MoS2} at about 2\%. \cite{Scalise2012}
-
-strain and Raman theoretical analysis.\cite{Chang2013a}
-
-magnetic properties of ws2.\cite{Zhang2013j}
-
-growth mechanism of WS2 NT:
-
-It was found that the critical step in this process is the fast conversion of the oxide nanoparticle surface into a closed monolayer of WS2.
-W18O49 as an intermediate phase is observed.
-XRD peaks shift to monitor strain.(002) peak of nanotube shifted to lower angles, the interlayer spacing increase by about 2\% as compared to the bulk powder, likely due to the build-in strain.\cite{ZAK2009}
-$\epsilon = (a - a_0)/a_0$ =(6.4-6.16)/6.16 = 3.8\%. tensile strain ($\epsilon > 0$)
 
@@
 
-\subsection{growth and properties}
-
-WS2 photoluminescence spectra of few layer and nanotube:
-NT electrical structures depend on chirality, diameter and layer No as well as strain.
-Theoretical calculation indicates the SWNT with diameter larger than 4nm should approach the single layer limit.\cite{Ghorbani-Asl2013}
-
-Other chalcogenide has also been synthesized using this one-end sealed layout.\cite{Mukherjee2013}
-
-\citeauthor{Zou2007} prepared W/\ce{WS2} core-shell NPs by reaction of tungsten and sulfur under hydrogen atmosphere.\cite{Zou2007}
-
-CVD 1L WS2 PL.\cite{Peimyoo2013} (of NTU Yu group) PL peak at 635nm, width 40 meV,
-
-CVD 1L WS2.\cite{Cong2013} (of NTU Yu group) 457 nm excitation, PL at 525nm and 630nm,
-
-\ce{MoS2} sing-walled nanotube.\cite{Xiao2014}
-
-1T MoS2: metallic phase a negative temperature coefficient for conductivity, XRD pattern identified. \cite{Wypych1992}
-
-stable 1T WS2 multiwalled NT by Re doping.\cite{Enyashin2011}.
-2H to 1T transition formerly known only for WS2 and MoS2 intercalated by alkali metals.
-3R transition to 2H upon heating since 2H is the most stable one.
-
-1T \ce{MoS2} Raman.
-\cite{Yang1991} strong peaks at 156, 226, and 330 cm-1.
-M point frequencies measured by neutron scattering.
-M point is folded into BZ zone center due to the formation of superlattice.
-
-Electrons and Phonons in Layered Crystal Structures, edited by T. J. Wieting (Reidel, Dordrecht, Holland, 1979).
-
-\ce{WS2} p-type or n-type.
-Fermi level at the surface of semiconductor is pinned to a fixed position relative to the CBM and VBM by a sufficient density of surface states situated between CBM and VBM.
-\cite{Baglio1983}
-
-Electronic structure of \ce{MoS2}.\cite{Eknapakul2014} K intercalating into bulk to create quasi-standing 1L.
-Large effective mass 0.6 $m_e$ found, implying low mobility.
-Direct gap 1.88eV is measured.
-
-Self-assembled monolayer (SAM) on \ce{SiO2} and its effect on \ce{MoS2} 1L.\cite{Najmaei2014}
-
-\ce{WS2} 1L doping calculation. \cite{Ma2011}
-
-multipeak Lorentzian fitting. 270 to 410 cm
-
-\citeauthor{Shi2013} studied the strained monolayer \ce{MoS2} and WS2.
-The results show that exciton binding energy is insensitive to the strain, while optical band gap becomes smaller as strain increases.
-Monolayer WS2 PL maximum located at about 1.95 eV.
-Calculation shows the electron effective mass of WS2 is the smallest, rendering higher mobility in device.\cite{Shi2013}
-
-\citeauthor{Kosmider2013} studied the heterojunction between two monolayers of \ce{MoS2} and WS2.
-Top of VB in W layer and bottom of CB in Mo layer, forming type II structure.
-bilayer gap 1.2 eV.\cite{Kosmider2013}
-
-Band structure  of \ce{MoS2} in bulk form was calculated by \citeauthor{Mattheiss1973}.The calculation result is 1.2eV (indirect gap).\cite{Mattheiss1973}
-
-Alkali metal intercalated \ce{WS2} film was prepared.\cite{Homyonfer1997} Stage 6 superlattice formation was suggested according to X-ray diffraction, and photoresponse spectra and electron tunneling measurement were done.
-
-quantitative Raman of MoS2 on insulating subs. intensity difference between supported and suspended was highlighted, detailed model in support info.Li2013
-
-WO3-x (1nm) on SiO2/Si sulfurization at 750-950 degree,\cite{Elias2013}
-
-decrease in dielectric screening and thereby enhanced excitonic effect.
-DFT is not good at describing photoemission, GW approximation overcome this deficiency but still not enough for photoabsorption process in which ehps are created.
-BSE equation is used to compensate this discrepancy, WX2 exhibits larger spin-orbit splitting as compared to MX2 family.\cite{Ramasubramaniam2012}
-
-arise as a result of, dispersal of Na by electron probe.
-
 \section{CNT}
@@
 BN nanotube capping, zigzag is more stable than armchair. \cite{Menon1999}
-
-To develop large-size single-crystal graphene on dielectric substrates.
-small carbon flow near-equilibrium CVD process.
-Grain size about 10 microns, precursor \ce{CH4} and \ce{H2} (ratio 2.3:50) at 1180 C.
-\ce{SiO2}-Si surface roughness.
-Although the growth substrates (quartz,\ce{SiO2}-Si and \ce{Si3N4}-\ce{SiO2}-Si ) have a complicated stereo network similar to diamond, regular hexagonal G growth is obtained, which indicates the deposition is determined by equilibrium kinetics, and this should be applicable to other 2D materials as well.
-I2D/IG exceeds two on \ce{SiO2}-Si subs (514.5nm), indicating monolayer G.
-armchair (AC) G edge grows faster than zigzag (ZZ) edge.\cite{Chen2013j}
-
-catalytic graphitization of solid carbon sources.
-catalytic transformation, the source is in solid state, low temperature (less than 600C), 2nm  \ce{Al2O3} by ALD as carbon diffusion barrier.
-amorphous silicon (a-Si), Ni lower the activation barrier ,  tetrahedral amorphous carbon (ta-C).\cite{Weatherup2013}
-
-low energy (50eV) ion implantation doping in G.
-Ions penetrate pristine G at energy larger than 100eV.
-Individual substitutional incorporation of B into G lattice is demonstrated.
-1\% doping level was obtained.
-\cite{Bangert2013}
-
 CVD G on copper. Size of single crystal domain and nucleation site density.\cite{Wu2013b}
@@
 massless relativistic chiral particles, Klein paradox, 100\% tunneling and extreme high mobility.
-
-\ce{CaF2} a material suitable for scattering efficiency S comparison measurement due to its large band gap ($S\times \omega_L^4$ is constant below 5eV).
 
@@
 
-intrinsic silicon equilibrium charge carrier concentration at RT is $n_i = p_i = 1.5 \times 10^{10} cm^{-3}$, much smaller than silicon atoms density as $5\times 10 ^{22} cm^{-3}$.
-
-The average distance between dopant atoms is cubed root of concentration, $d = (10^{18} cm^{-3})^{-1/3} = 10nm$.
-
-The electron mobility $\mu_n = 1500 cm^2/V\cdot sec $ at RT for Si, and hole mobility $\mu_p = 450 cm^2/V\cdot sec$ at RT.
-
-for p-type silicon, when the conductivity $\sigma = 1 (ohm cm )^{-1}$, the doping level is
-$N_A = \frac{\sigma}{q \mu_p}= 1 / (1.6E-19 \times 450) = 1.4E16 cm^{-3}$.
-
-Built-in voltage $V_0 = \frac{kT}{q}ln(N_A N_D/n_i^2)$, depletion region width $W = \sqrt{\frac{2 \epsilon_{Si} V_0}{q}(1/N_A + 1/N_D)}$, where $\epsilon_{Si} = 11.7 \epsilon_0$.
-When applying external field, depletion width $W = \sqrt{\frac{2 \epsilon_{Si} (V_0 - V) }{q}(1/N_A + 1/N_D)}$
-
-The capacitance of p-n junction is $C = A \sqrt{\frac{q \epsilon_{Si}}{2(V_0 -V)}(N_D N_A/(N_A + N_D))}$.
-
-oxygen plasma treatment on HF-etched Si (001). reaction among $e$, \ce{O^+}, \ce{O2^+}, \ce{O^-},\ce{O2}. \ce{OH}-terminated surface obtained.\cite{Habib2010}
-
-\subsection{MB}
-MB is a heterocyclic aromatic dye which is blue colored in oxidizing environment.
-Upon reduction, MB is turned into colorless leuco MB.
-This can be used as an oxygen indicator in food industry.
-Photo-bleaching of MB can be also due to its leuco formation rather than total decomposition.
-Photocatalytic decomposition can be minimized by keeping the solution at acidic condition (PH = 4), which will limit the formation of oxidative hydroxyl radicals (E = 2.8eV vs normal hydrogen electrode).
-Oxygen dissolved in the solution play a key role in conversion of LMB to MB under visible light.
-Purging with \ce{N2} for 20mins can remove dissolved oxygen.
-\cite{Wang2014a}
-
-solar energy harvesting representative study.\cite{Yoneyama1972} MB to LMB (\ce{C16H19N3S}) in aqueous solution upon illumination of \ce{TiO2}.
-The colorimetric analysis was performed in a glove box under nitrogen atmosphere.
-The absence of oxygen is important to prevent the oxidation of LMB to blue MB.
-\[
-\cee{MB^+ H2O + H^+ \rightarrow MBH3^{2+} + 1/2O2}
-\]
-where MB represents the uncharged center of MB molecule.
-
-common wisdom expect that a dye incapable of injecting an electron at the excited state to CdS.
-MB, which process N-methyl groups in its molecular structure and does not sensitize CdS is an exemplary candidate.
-quantum efficiency is defined as probability of MB converted to azure B per incident photon.
-QE of CdS to MB decomposition is reduced in nitrogen bubbling treated solutions, indicating the necessity of oxygen.
-Two possible mechanisms: a) adsorbed oxygen acts as a trap for the conduction electron and prevent the accumulation of negative charge within space charge region of CdS, supported by the formation of \ce{O2^-} in excitation of CdS in aqueous suspension.\cite{Takizawa1978}
-
-ref 16, MB aqueous solution stability. Liquid chromatogram, azure B (trimethylthionine), and thionine. Electrochemical measurement,
-
-MB adsorption.
-photocatalytic oxidation of MB by \ce{TiO2} film.
-photo-oxidation reaction occurs at the surface of photocatalyst.
-Mb molar extinction coefficient was found to be 66700 1/cm 1/M.
-Langmuir adsorption isotherm.\cite{Matthews1989}
-
-\[
-[MB]_{ads} = \frac{k_1 k_2 [MB]}{1 + k_1[MB]}
-\]
-and integrated form of Langmuir adsorption isotherm
-\[
-t = \frac{1}{k_1K} In\frac{[S]^0}{[S]} + \frac{1}{K}([S]^0 - [S])
-\]
-where $K = k_2 \phi N T_r$, with $\phi$ as quantum yield, N as total absorbed photons, and $T_r$ as rate of transport.
-\[
-\cee{C16H18N3SCl + 25.5O2 \rightarrow 16CO2 + 6H2O + 3HNO3 + H2SO4 +HCl}
-\]
-which indicates the total oxidation of $10 \mu M$ MB would exhaust the ambient oxygen concentration of initially air-equilibrated solutions (about $250 \mu M$ ).
-ref 28 Thus the transport of both oxygen and MB to the photocatalyst surface are anticipated to be key factors.
-
-photoelectrochromism at \ce{TiO2}/MB interface and its control.
-Efficient capture of photogenerated holes by a reducing agent is crucial to the reversibility of bleach-recoloration transition.
-This transition is kinetically dictated by electron transfer.
-Holes transfer is not desired.\cite{DeTacconi1997}
-
-256 nm band is associated to the presence of LMB.
-LMB formation is not favored at alkaline pH values in aqueous solution.
-The OH radicals are generated either with the surface hydroxyl groups on \ce{TiO2} or with water, and its high oxidizing power cause photocatalytic decomposition of the dye.
-
-An elementary step in decomposition of MB is N-dealkylation, which is preceded by radical cation formation.\cite{Takizawa1978} This radical cation can be spectroscopically monitored by the presence of 520nm band for MB.
-In MB absorption spectrum, 664 and 614 nm band ratio is related to monomer and dimer relaxation.
-\begin{align}
-\cee{TiO2 &\rightarrow e_{CB}^- + h_{VB}^+ \\
-h_{VB}^+ + red &\rightarrow ox\\
-MB^+ + 2e_{CB}^ + H^+ &\rightarrow LMB}
-\end{align}
-
-Measure the ratio between 614 and 663 nm before and after adding WS2 can indicate the adsorption of monomer and dimer MB.
-
-MB can act as sacrificial electron acceptor in the reduction to leuco form.
-The decomposition is favored under oxygen-rich environment.
-MB feature peaks at 663, 614 and 292 nm, and $\epsilon_{660}=10^5 M^{-1}cm^{-1}$.
-The doubly reduced form of MB, LMB has feature peak at 256 nm.
-The singly reduced form of MB, \ce{MB.^-} is pale yellow, with peak at 420nm.\cite{Mills1999}
-\[
-\cee{MB + e_{CB}^- ->[pH<7] MB.^-}
-\cee{2MB.^- \rightarrow MB + LMB}
-\cee{O2 + e_{CB}^- \rightarrow O2.^-}
-\]
-
-The oxidized form of MB, \ce{MB.^+} has peak at 520nm, which is stable in acidic solution, but decomposes irreversibly in slight alkaline solution(pH = 9).
-thionine peaks at 600nm.
-MB forms dimers in aqueous solution,
-\ce{
-2MB <=>[K_D] (MB)_2
-}
-A typical value of $K_D$ is 3970 1/M. A quadratic equation can be solved to obtain the monomer concentration:
-\[
-2K_D [MB]^2 + [MB] - [MB]_{total} = 0
-\]
-MB adsorption on metal oxides. Monomer size is less than 1.5nm.
-Logarithmic acid dissociation constant $pK_a= -\log_10 \frac{[A^-][H^+]}{[HA]}$. The oxidation potential for \ce{H2O}-\ce{O2} couple is 1.23V and 0.817V versus NHE at pH 0 and pH 7, respectively.
-
-%\begin{align}
-%\cee{MB + SED &->[TiO2][h\nu \leq 3.2eV] LMB + SED^{2+}\\
-%2LMB + O2 &\rightarrow 2MB + 2H2O}
-%\end{align}
-
-S.L. Murov, I. Carmichael, G.L. Hug, Handbook of Photochemistry, 2nd revised ed. Marcel Dekker, New York, 1993.
-
-aerobic or anaerobic, dimerise, photominerlization, gas to liquid transfer.
-
-Mb to LMB transition as visual time monitor. commercial colorimetric oxygen indicators. radical-bearing carbon with unpaired electrons. MB = \ce{MB^+Cl^-}.\cite{Galagan2008}
-
-monomer MB and dimer MB kinetics.\cite{Spencer1979}
-
-MB. \cite{Lee2003a}
-\begin{align}
-\cee{ 2LMB &->[\text{UV}] LMB^*\\
-2LMB^* + O2 &\rightarrow 2MB^+ + 2OH^-}
-\end{align}
-
-\[
-\cee{2LMB ->[\alpha] LMB^*}
-\cee{2LMB ->[\text{above}] LMB^*}
-\]
-
 \section{solar cell}
 
-\ce{TiO2} NPs for high loading of sensitizing dye. Hole conducting electrolyte with \ce{I^-} and \ce{I3^-} concentration close to $10^19 cm^3$. chemical anchoring groups.
+\ce{TiO2} NPs for high loading of sensitizing dye. Hole conducting electrolyte with \ce{I^-} and \ce{I3^-} concentration close to $E+19$ \si{cm^3}. chemical anchoring groups.
 
@@
 
-\section{vocabulary}
-$\delta\omega/\epsilon$
-
-\subsection{pronunciation}
-
-chamber, vias, valve, figure, energetic, managerial, inert, volatile, chromic,
-laminar, palladium, platinum, photovoltaic, acronym, chirality, stoichiometric, cyclic voltammetry, quasi, pseudo,
-
 \section{job related paper}
@@
 
-why graphene on copper: a review article.
+\textbf{why graphene on copper: a review article}.
 \cite{Mattevi2011} research thrust, post CMOS fab tech.
@@
 The lack of control over layer No on Ni is partially attributed to the face that the segregation of carbon from the metal carbide upon cooling occurs rapidly within the Ni grains and heterogeneously at the grain boundaries.
-phase diagram of Ni and C reveals that the solubility of carbon in nickel at high T > 800 C form a solid solution.
+phase diagram of Ni and C reveals that the solubility of carbon in nickel at high T \textgreater 800 C form a solid solution.
 metastable phase \ce{Ni3C} promote the precipitation of C out of Ni.

### 2014-09-28 misc/test.tex
paper draft and supporting info tidy up

\chapter{test}
abc \si{\angstrom} abs

\section{level one}
Inline lists, which are sequential in nature, just like enumerated lists, but are
\begin{enumerate*}[label=\itshape\alph*\upshape)]
\item formatted within their paragraph;
\item usually labelled with letters; and
\item usually have the final item prefixed with `and' or `or',
\end{enumerate*} like this example.

\begin{hypothesis}
After 20 minutes sonication, the dispersion is milky. We measured the transmission spectra of this dispersion immediately upon sonication and after 40 hrs for gravity sedimentation.
\end{hypothesis}
\subsection{level two }
\Gls{cft}, \gls{cvd}
\subsubsection{level three}
After 20 minutes sonication, the dispersion is milky. We measured the transmission spectra of this dispersion immediately upon sonication and after 40 hrs for gravity sedimentation. The t0 line mainly arises from the scattering of flakes in the dispersion. There are two scattering mechanisms: Rayleigh scattering and Tyndall scattering. Rayleigh scattering, which occurs when particles are comparable to wavelength, is inversely proportional to the fourth power of wavelength; While Tyndall scattering, which occurs when the particles are larger, is inversely proportional to the square of the wavelength. To fully evaluate the true absorbance of the sample itself, one needs to decouple the scattering part from apparent absorbance. Generally we select one part of spectrum and assume it is only caused by scattering. Then a empirical dependence shown in Eq.~\ref{eq:sca2} is used as polynomial fitting model. test.

\begin{align}
Abs_{sca}  & = a\times \lambda^{n}  \label{eq:sca1}\\
\log{Abs_{sca}} & = \log{a} + n*\log{\lambda} \label{eq:sca2}
\end{align}

After least-squares fitting, the coefficients $a$ and $n$ can be used to estimated the scattering in other wavelengths. The fitting of n usually falls between -2 and -4. We examined the t40h line and found the scattering part is almost zero. Therefore we did not perform aforementioned fitting. This is not always the case. In chapter on the \ce{WS2} section, we do need to do so.

\begin{itemize}
\item s inversely proportional to the fourth
\item  inversely proportional to the fourth
\item s inversely proportional to the fourth
\end{itemize}

\begin{figure}[htb]
\centering
\subcaptionbox{\label{fig:moind}}{\includegraphics[width=0.45\linewidth]{n_MoO3}}%
\subcaptionbox{\label{fig:mocon}}{\includegraphics[width=0.45\linewidth]{MoO3_1L}}
\caption[Refractive indices of \ce{MoO3}]{(a) Refractive indices of \ce{MoO3} Dashed line is n along $a$ axis while solid line is along $c$ axis. (b) optical contrast mapping of 1L \ce{MoO3} on \ce{SiO2}-Si. The x axis is \ce{SiO2} thickness, y axis is wavelength.It is assumed that the incident light is polarized along c axis of \ce{MoO3}.}
\label{fig:mofl}
\end{figure}
%[width=0.45\textwidth]

Rayleigh scattering and Tyndall scattering. Rayleigh scattering, which occurs when particles are comparable to wavelength, is inversely proportional to the fourth power of wavelength; While Tyndall scattering, which occurs when the particles are larger, is inversely proportional to the square of the wavelength. To fully evaluate the true absorbance of the sample itself, one needs to decouple the scattering part from apparent absorbance. Generally we select one part of spectrum and assume it is only caused by scattering. Then a empirical dependence shown in Eq.~\ref{eq:sca2} is used as polynomial fitting model.
\begin{figure}[htb]
\centering
\subcaptionbox{\label{fig:moxrd}}{\includegraphics[width=0.45\linewidth]{xrd_moo3}}%
\subcaptionbox{\label{fig:moram}}{\includegraphics[width=0.45\linewidth]{xrd_moo3}}
\caption[Crystalline phase characterization of \ce{MoO3} on Si]{(a) XRD pattern and (b) Raman spectrum of typical \ce{MoO3} on Si, $\lambda_{ex} = 532nm$.}
\label{fig:mooxch}
\end{figure}

piranha clean of FTO. 50ms switch.\cite{Scherer2012} nanoscale Kirkendall effect: the outward diffusion of metal cations are balanced by an influx of vacancies. For example, diffusion coefficient of Ni in NiO is higher than that of oxygen.
\subsection{EC windows and thin film batteries}

battery and ECD.\cite{Granqvist2012} electrolyte: PVB (poly vinyl buteral).
alternative materials and design: organic, Prussian Blue as EC materials, metal hydrides, suspended particle device, liquid crystal, electroplating,
challenges: large area nanoporosity, transparent conducting contact, electrolyte with good ionic conductivity and poor electronic conductivity, stable under UV; assembly and large scale manufacturing;
cathodic coloration:
anodic coloration:
The coloration mechanism: \ce{MO6} octahedrons lead to $e_g$ and $t_{2g}$ level and ion channelling.
ref54,60,65,66,200,209,

\ce{WO3} as cathodic and either polyaniline(PANI) or Prussian white (PW) as anodic electrochromic half cells. \cite{Heckner2002}

Characterization of ECD includes transmission measurement and associated EC calculation, charge-discharge time, current-time curve and the fitting of obtained data.

\begin{quote}
a viable electrochromic smart window must exhibit a cycling life time \textgreater $10^5$ cycles, corresponding to an operation life at 10 - 20 years.
\end{quote}

\citeauthor{Sella1998} studied the optical and structural properties of RF sputtered thin film of \ce{WO3} and \ce{VO2} for electrochromic devices. Ionic conductor was built using transparent polymer electrolyte, which was prepared from a solution of 1M \ce{LiClO4} in propylene carbonate which was mixed with methylmetharcylate (MMA). The main characteristics of polymer electrolyte were: viscosity at 25 \si{\degreeCelsius} $\approx$ 12920 Pa.s, conductivity $\approx 10^{-2}-10^{-4}$\si{\per\ohm\per cm},non-hygroscopic if PMMA concentration \textgreater 30\%. A specific counter-electrode layer was not used since the encapsulated polymer electrolyte processes a very high ion storage capacity.\cite{Sella1998}

### 2014-09-28 ch-intro/ch-intro.tex
SI info inserted into main text

@@
 Photocatalytic activity occurs when a semiconductor in aqueous solution is illuminated by photons of energy larger than the bandgap, then electron-hole pairs generate free radicals, i.e., \ce{OH.}, which enable further reactions.
-For water splitting using solar energy, the band gap should be within $2.0 \sim 3.0 $ eV, and CB edge should be more negative than reduction potential of \ce{H^+/H2}, whereas the VB top should be more positive than the oxidation potential of \ce{H2O}/\ce{O2}.\cite{Wang2012} The valence band holes (\ce{h^+}) oxidize water to oxygen and conduction band electrons propel hydrogen generation, as depicted in Eq.~\ref{eq:h2o}.
+For water splitting using solar energy, the band gap should be within $2.0 \sim 3.0 $ eV, and CB edge should be more negative than reduction potential of \ce{H^+/H2}, whereas the VB top should be more positive than the oxidation potential of \ce{H2O}/\ce{O2}.\cite{Osterloh2008,Wang2012} The valence band holes (\ce{h^+}) oxidize water to oxygen and conduction band electrons propel hydrogen generation, as depicted in Eq.~\ref{eq:h2o}.
 \begin{subequations}\label{eq:h2o}
@@
 The formation of long-lived holes is recognized as a key requirement.\cite{Pesci2011} Besides, \ce{WO3} is remarkably stable in acid, making it a significant candidate for treating water pollutant caused by organic acids.\cite{Monllor-Satoca2006}
+
+For photochemical water reduction to occur, the flat-band potential of the semiconductor (for highly doped semiconductors, this equals to the bottom of the conductance band) must exceed the proton reduction potential of 0.0 V vs NHE at pH=0.\cite{Osterloh2008} Flat-band potentials strongly depend on ion absorption (protonation of surface hydroxyl groups), crystallographic orientation of the exposed surface, surface defects, and surface oxidation processes.
 

### 2014-09-28 ch-tms/tmspart.tex
SI info inserted into main text

@@
 
+The geometrical symmetry groups of WS2 NT.\cite{Milosevic2000} 
+The basis/lattice vectors $a_1$ and $a_2$ are defined in transition metal plane with equal length $a_0 \approx 3$ \AA.
+This monolayered sheet can be rolled up to form a tubular structure when the chiral/translation vector $c = n_1a_1 + n_2a_2$ becomes the circumference of the tube.
+The diameter of a nanotube is given by
+\begin{equation}
+d = \frac{\mid c \mid}{\pi} = \frac{a_0}{\pi}\sqrt{n_1^2 + n_1n_2 + n_2^2}
+\end{equation}
+Notice $a_1 \cdot a_2 = a_1a_2 \cos\pi/3$, where the cosine times 2 is unit. 
+In analog with carbon nanotube, chiral angle $\theta$ is given by
+\begin{equation}
+\theta = \tan^{-1}\frac{\sqrt{3}n_2}{2n_1 + n_2}
+\end{equation}
+
+Chiral angles from the interval $[0,pi/6]$ is sufficient for all possible tubes.
+Tubes $(n,0)$ with zero chiral angle are named zigzag, tubes $(n,n)$ with $\pi/6$ chiral angle are armchair, whereas all others are referred as chiral ones with $\theta \in (0,pi/6)$.
+\begin{figure}[htb]
+\centering
+\includegraphics[width=0.8\textwidth]{ws2_tube1}
+\caption[\ce{WS2} nanotube rolling]{\ce{WS2} nanotube rolling}
+\label{fig:ch5ntroll}
+\end{figure}
+
 \subsection{Synthesis Review of TMDCs}
@@
 \end{equation}
+\begin{align}
+\cee{WCl6 + S &\rightarrow WS2 + Cl2S2}\\
+\cee{MoCl5 + S &\rightarrow MoS2 + S2Cl2} \\
+\cee{S2Cl2 + NaOH &\rightarrow NaCl + S + Na2SO3 + H2O}
+\end{align}
 This reaction has been explored by several authors\cite{Stoffels1999} and could be used under atmospheric pressure.\cite{Li2004a}

### 2014-09-28 ch-wox/part1.tex
SI info inserted into main text

@@
 
-In the past decades, tons of works have been devoted to understanding the chromogenic phenomena in \ce{WO3}. Several key results were highlighted as reviewed in Ref.\cite{Deb2008},
+In the past decades, tons of works have been devoted to understanding the chromogenic phenomena in \ce{WO3}. Several key results were highlighted as reviewed in Ref.\cite{Deb2008}:
 \begin{itemize}
-    \item coloration and bleaching can also be stimulated by other routes, such as by UV irradiation, thermal treating, heating in vacuum, reducing atmosphere, \emph{etc}
-    \item no electrical coloration occurs in vacuum, but other routes still work
-    \item coloration is associated with a proportional increase in conductivity
-    \item coloration spectrum is essentially similar in all cases except small variation in peak position
-    \item coloration is structural sensitive and most efficient in amorphous films
+    \item coloration and bleaching can also be stimulated by other routes, such as by UV irradiation, thermal treating, heating in vacuum, reducing atmosphere, \emph{etc};
+    \item no electrical coloration occurs in vacuum, but other routes still work;
+    \item coloration is associated with a proportional increase in conductivity;
+    \item coloration spectrum is essentially similar in all cases except small variation in peak position;
+    \item coloration is structural sensitive and most efficient in amorphous films.
 \end{itemize}
@@
 
+\ce{WO3} and optical electric field enhancement.
+The \ce{W_nO_{3n-1}} ($n \geq 2$) exhibit $\{ 001 \}$ CS structure.
+Chemical formula corresponding to n=2, 3, 4, 5 and 6 are \ce{W2O5=WO_{2.5}}, \ce{W3O8=W_{2.67}}, \ce{W4O_{11}=WO_{2.75}}, \ce{W5O_{14}=WO_{2.8}}, and \ce{W6O_{17}=WO_{2.83}}, which indicates the existence of a oxygen deficient plane at every n row.
+Actually the value x in \ce{WO_x} could almost continuously vary within a range of 2.5 to 3.
+\ce{W_{18}O_{49}=\ce{WO_{2.72}}} is an exception without $\{ 001 \}$ CS structure.
+Moreover, the oxygen deficient planes could extend along directions other than $\{ 001 \}$.
+For instance, the $\{ 102 \}$ CS planes appears in \ce{WO_x} where x is within 2.93 to 2.98, and  the $\{ 103 \}$ CS planes for x within 2.87 to 2.93.\cite{Sloan1999} The enhancement arises from the structure composed of a conductive layer and an insulating layer that are laminated therein.\cite{Shingaya2013} In \ce{WO_x} nanorods, the oxygen deficient planes are conductive, each having atomic thickness and separated by several nm \ce{WO3}.
+Localized surface plasmons could possibly exist on these conductive planes.
+Therefore \gls{sers} applies and single molecule Raman scattering using individual tungsten oxide nanorod has been demonstrated.
+\citeauthor{Shingaya2013} also synthesized \ce{WS2}-\ce{WO_x} core-shell structures and found similar Raman scattering enhancement.
+The x value is estimated by the Raman spectra peaks.\cite{Shingaya2013}(Data not shown in patent)
+
 \subsection{Review of Synthesis Methods}\label{sec:woxgrowth}

### 2014-09-28 figure_table.tex
ch2 enhanced
wox and moox proofreading
SI info inserted into main text

@@
+\subsection{misc}
+
 \si{\degreeCelsius}
+
+\si{\angstrom}
+
+Inline lists, which are sequential in nature, just like enumerated lists, but are
+\begin{enumerate*}[label=\itshape\alph*\upshape)]
+\item formatted within their paragraph;
+\item usually labelled with letters; and
+\item usually have the final item prefixed with `and' or `or',
+\end{enumerate*} like this example.
 
@@
 
+%float package
 \begin{figure}[htb]
@@
 
-\subsection{chromic}
+\section{vocabulary}
+well suited to,
+seriously pursued. 
+One must be just as aware of the instrument's limitations as one is of its advantages
+I call attention to the fact that.
+arise as a result of, dispersal of Na by electron probe.
+$\delta\omega/\epsilon$
 
-the electrical conductivity is given by $\sigma = n e \mu$, where $n$ is the density of free carriers, $\mu$ is their mobility and $e$ is electronic charge.
-The mobility is given by $\mu = e\tau/m^*$ with $\tau$ is carrier resistivity relaxation time and $m^*$ is the carrier effective mass.
+\subsection{pronunciation}
 
-The degree of \ce{H^+} intercalation, $x$, is determined by integrating cathodic current, and given by
-\begin{equation}
-x = \frac{Q}{F}\frac{M_\ce{WO3}}{m_f}
-\end{equation}
-where $m_f$ is the mass of film, $M_\ce{WO3}$ is the molar mass of \ce{WO3*1/3H2O}, and F is Faraday's constant.
-The color center density, $c$, is then obtained using formula
-\begin{equation}
-c= \frac{x M_\ce{WO3}N_A}{\rho}
-\end{equation}
-where $N_A$ is Avogadro number, $\rho$ is density of film.
-
-In second state, the one with smaller droplet probably would exhibit faster growth rate in $\langle001\rangle$ direction due to its shortest lattice constant, while the other one endures more growth along$\langle010\rangle$ direction.
-We suspect that the liquid size that induce the tower growth is much larger than that of belts.
-From the final morphology of as-synthesized sample, we find that the above proposed two growth approaches could change into each other, that is belt growth could be initiated on the top of tower growth and vice visa.
-We assume this phenomena arise from the interaction between vapor supply, temperature and the shape of liquid catalyst.
-Or it may just come from the vapor transport of \ce{NaxMoO3}.
-It had been shown by actively engineering the shape of catalysis, the growth direction of  InP NW could be switched between [111] and [100].\cite{Wang2013c} The same mechanism might exist in our case as well.
-For instance, when a belt is sufficient long and it could extend into the low temperature part, where the supply of MoOx vapor is reduced due to the consumption, and the shape of liquid might vary as well.
-Both will result in different absorption and subsequent diffusion rate along and inside the liquid catalyst.
-We also observed that belt growth could initiate from tower growth in reduced time growth.
-Actually this may be one possible mechanism of belts formation.
-
-(The presence of \ce{Na6MoO33} phase is an indirect evidence for the formation of eutectic \ce{Na2MoO4}- \ce{MoO3} binary compounds at growth temperature.
-The bulk phase diagram may not accurately represent the phase transition occurring in catalyst droplet and solid interface.
-And it will usually lead to a significant temperature decrease of eutectic point from the bulk value.
-Nanoparticles do not completely melt and instead act as an active site for reactant absorption and diffusion, leading to a vapor-solid-solid growth mechanism.
-)
+chamber, vias, valve, figure, energetic, managerial, inert, volatile, chromic,
+laminar, palladium, platinum, photovoltaic, acronym, chirality, stoichiometric, cyclic voltammetry, quasi, pseudo,

### 2014-10-02 misc/SI_thesis.tex
temperatory fix for multiline chapter name display in ToC
sty file modified after format reivew mwe tested

@@
-\chapter{intro}
+\chapter{INTRO ON THE CONTROLLED GROWTH AND PROPERTIES MEASUREMENTS OF 1D NWS}
+\chaptermark{header version}
+
+\section{A LONG SECTION TITLE FOR TOC CONTENT LINE WRAPPING TEST TEST TEST A LONG SECTION TITLE FOR TOC CONTENT LINE WRAPPING TEST TEST TEST}
 
@@
 
+Raman assignment of \ce{WO3}
+
+XRD assignment of \ce{WO3}
+
+raman assign
+\begin{table}[htb]
+\centering
+\caption{Symmetry assignment of \ce{WO3}}\label{tab:woram}
+\begin{tabular}{cccc}
+\toprule
+Raman shift (\si{cm^{-1}}) & Symmetry &  Ref.   & Remarks   \\
+\midrule
+131(m)   & $B_{2g}$    &           & $T_c$    \ce{WO3} \\
+265(m)   & $B_{3g}$    &           & $T_c$    \\
+327(m)   & $A_g/B_{1g}$&           & $T_b$   \\
+711(s)     & $B_{2g}$    & $\tau$    &          \\
+803(vs)     & $A_g$       &           & $R_c$    \\
+\midrule
+230(m)   & $B_{3g}$     & $\delta$ & \ce{O=Mo=O}  \ce{WO3.H2O} \\
+380(w)   & $B_{1g}$     & $\delta$ & \ce{O-Mo-O}  & scissor  \\
+428(w)   & $A_g$        & $\nu_{as}$ & \ce{O-Mo-O}  & stretch,bend  \\
+650(s)  & $B_{2g},B_{3g}$ & $\nu_{as}$  & \ce{O-Mo-O}  & stretch  \\
+816(vs)   & $A_g$        & $\nu_{as}$  & \ce{O=Mo}  & stretch  \\
+946(vw)      & $A_g$         & $\nu_{as}$  & \ce{O=Mo}  & stretch  \\
+\bottomrule
+\end{tabular}
+
+vw-very weak; w-weak; m-medium; s-strong; vs-very strong
+\end{table}
+
+\ce{Na2W2O7} Raman. \cite{Knee1979}
+
+\ce{WO3}, \ce{WP3.H2O}\cite{Daniel1987}
+
+xrd assignment
+\begin{table}
+\centering
+\caption{XRD assignments}\label{tbl:xrd}
+\begin{tabular}{llllll}
+\toprule
+\ce{WO3} &          &\ce{Na5W14O44} &      & \ce{Na2W4O13} & \\
+2$\theta$   & hkl   & 2$\theta$   & hkl    & 2$\theta$   & hkl   \\
+\midrule
+ 23.05   & 0 0 2 & 9.65    & 0 0 2  & 10.85   & 1 0 0 \\
+ 23.59   & 0 2 0 & 14.49   & 0 0 3  & 21.8    & 2 0 0 \\
+ 24.31   & 2 0 0 & 19.37   & 0 0 4  & 32.97   & 3 0 0 \\
+ 26.6    & 1 2 0 & 24.27   & 0 0 5  & 56.45   & 5 0 0 \\
+ 34.1    & 2 0 2 & 29.22   & 0 0 6  &         &       \\
+         & 2 2 0 &         &        &         &        \\
+ 47.11   & 0 0 4 & 39.36   & 0 0 8  &         &        \\
+ 48.29   & 0 4 0 & 44.46   & 0 0 9  &         &        \\
+ 49.79   & 4 0 0 & 49.71   & 0 0 10 &         &        \\
+         & 1 4 0 &         &        &         &        \\
+         &       & 55.23   & 0 0 11 &         &        \\
+         &       & 60.77   & 0 0 12 &         &        \\
+\bottomrule
+\end{tabular}
+\end{table}
+
 \subsection{polarons}
@@
 \]
+
+In short summary, this thesis stresses that there are several key factors in successfully synthesizing \ce{WS2} FL:
+\begin{itemize}
+\item \ce{WO3} powder size distribution and absolute amount (0.69 g \ce{WO3} in 10 mL acetone or IPA, inspired by the \ce{MoO3} nanoribbons usage);
+\item Sulfur amount and heating method to ensure a constant sulfur-rich environment;
+\item \ce{WO3} powder source to substrate distance, which is coupled to pressure and carrier gas flow in determining the transport (atmospheric, 3-5 mm);
+\item temperature ramping and growth time (750-800 \si{\degreeCelsius}, 3-10 min);
+\item 300 nm \ce{SiO2}-Si substrate to make OM flakes identification easier.
+\end{itemize}
+
+Four kinds of tungsten powders were used as precursor to prepare \ce{WO3} NWs, and sulfur powder was used to fabricate \ce{WO3}-\ce{WS2} core-shell NWs, as summarized in Table.~\ref{tab:ch5pre}.
+All reactants were employed as received without further processing.
+Substrates cleaning procedures have been introduced in Sec.~\ref{ch2sub}.
+
+% Tungsten powders size and purity
+\begin{table}[htb]
+\centering
+\caption{List of reactants for \ce{WO3}-\ce{WS2}}\label{tab:ch5pre}
+\begin{tabular}{lccr}
+\toprule
+Name & purity & average size & vendor info\\
+\midrule
+3N   &  99.9\% & 17 $\mu$m & Alfa Aesar \#39749\\
+3N5   &  99.95\% & 32 $\mu$m  & Alfa Aesar \#42477\\
+4N5   &  99.995\% & 3.3 $\mu$m  & Materion T-2049 \\
+5N   &  99.999\% & 1.5 $\mu$m & Alfa Aesar \#12973\\
+S    &   99.5\%  &  NA  & Alfa Aesar \#10785\\
+\bottomrule
+\end{tabular}
+\end{table}
+
+\ce{WO3} NWs were obtained by a seeded growth with tungsten powders applied onto the Si substrate. To find out the optimal conditions, tungsten powder oxidation experimental were carried out.
 
@@
 Ions penetrate pristine G at energy larger than 100eV.
-Individual substitutional incorporation of B into G lattice is demonstrated.
+Individual substitution incorporation of B into G lattice is demonstrated.
 1\% doping level was obtained.

### 2014-10-02 misc/mwe.tex
temperatory fix for multiline chapter name display in ToC
sty file modified after format reivew mwe tested

@@
 
-  \title{\LaTeX is great}
-  \author{me}
+\title{Controlled growth and property measurement of one-dimensional oxide nanostructures for energy applications}
+  \author{Tao Sheng}
+  \university{The University of North Carolina at Charlotte}
+  \location{Charlotte}
+  \thesisyear{\the\year}
+  \degree{Doctor of Philosophy}
+  \department{Physics and Optical Science}
+
+  \committeemember{Dr. Haitao Zhang} % First sets the \advisor default.
+  \committeemember{Dr. Tsinghua Her}
+  \committeemember{Dr. Michael Fiddy}
+  \committeemember{Dr. Stuart Smith}
+  \committeemember{Dr. Yu Wang} % Maximum of 10 can be specified.
+
+%  \advisor{Dr. Haitao Zhang}
+
 \maketitle
+% no space line between abstract and main text
+\begin{abstract}
+Transition metal oxides (TMOs) exhibit rich structures and useful properties, and could been used in solar energy harvesting (\emph{e.g.}, photoelectrochemistry, photocatalysis, and photovoltaics) and energy saving (\emph{e.g.}, electrochromism and photochromism) applications.
+Nano-engineering of these TMOs could produce a variety of nanostructures, modify the electronic and optical properties, potentially enhance the performances and extend their applications into new regimes.
+To fully harvest the advantages of these materials, a scalable growth method and a comprehensive understanding towards the growth-structure-property relation must be established.
+This Ph.D.
+study focused on one-dimensional (1D) tungsten trioxide (\ce{WO3}) and molybdenum trioxide (\ce{MoO3}) nanostructures.
+This dissertation synthesized 1D \ce{WO3} and \ce{MoO3} nanostructures using chemical vapor deposition (CVD) approach, characterized the morphologies and structures, and measured the optical properties of the as-prepared nanostructures.
+This study aims at accomplishing controlled and scalable growth of \ce{WO3} and \ce{MoO3} using CVD method, establishing the structure-property relations to rationalize nanostructure synthesis for energy applications, and presenting preliminary results on the devices assembled using the \ce{WO3} and \ce{MoO3} nanostructures.
+
+\end{abstract}
+
+\begin{dedication}
+morphologies and structures, and measured the optical properties of the as-prepared nanostructures.
+This study aims at accomplishing controlled and scalable growth of \ce{WO3} and \ce{MoO3} using CVD method, establishing the structure-property relations to rationalize nanostructure synthesis for energy applications, and presenting preliminary results on the devices assembled using the \ce{WO3} and \ce{MoO3} nanostructures.
+
+\end{dedication}
+
+%\pagebreak{}
+
+\begin{ackn}
+morphologies and structures, and measured the optical properties of the as-prepared nanostructures.
+This study aims at accomplishing controlled and scalable growth of \ce{WO3} and \ce{MoO3} using CVD method, establishing the structure-property relations to rationalize nanostructure synthesis for energy applications, and presenting preliminary results on the devices assembled using the \ce{WO3} and \ce{MoO3} nanostructures.
+
+\end{ackn}
+
+%\pagebreak{}
+%% --- Work around some bugs due to babel package---
+% for more, see http://tex.stackexchange.com/questions/82993/how-to-change-the-name-of-document-elements-like-figure-contents-bibliogr?lq=1
+\setcounter{tocdepth}{2}
+% ----- end of work around--------
 
@@
 
-    \begin{singlespace}
-    %\thispagestyle{myheadings} % before, this does not work
-    \renewcommand{\glossarypreamble}{\thispagestyle{myheadings}} % after, this works.
-    %\renewcommand{\acronymname}{LIST OF ABBREVIATIONS}
+%\thispagestyle{myheadings}
+\renewcommand{\glossarypreamble}{\thispagestyle{myheadings}}
+\renewcommand{\acronymname}{LIST OF ABBREVIATIONS}
+\glossarystyle{long}
 \printglossary[type=\acronymtype]
@@
 \clearpage
-    \end{singlespace}
 
- %  \include{./test}
-     \include{./SI_thesis}
-     \include{./draft}
+    \include{./test}
+     %\include{./SI_thesis}
+    % \include{./draft}
      \include{./paper}
@@
     \renewcommand{\bibname}{REFERENCES}
-    \begin{singlespace}
     \printbibliography
-    \end{singlespace}
 
 \end{document}
+
+* remove all bold font, including figure captions, hypothesis env
+* abstract; after skip line number is 2, title capital the first letter only
+* section after skip none
+* no external link in electronic version, turn off doi
+*

### 2014-10-02 misc/test.tex
sty file modified after format reivew mwe tested

@@
 \centering
-\subcaptionbox{\label{fig:moind}}{\includegraphics[width=0.45\linewidth]{n_MoO3}}%
-\subcaptionbox{\label{fig:mocon}}{\includegraphics[width=0.45\linewidth]{MoO3_1L}}
-\caption[Refractive indices of \ce{MoO3}]{(a) Refractive indices of \ce{MoO3} Dashed line is n along $a$ axis while solid line is along $c$ axis.
-(b) optical contrast mapping of 1L \ce{MoO3} on \ce{SiO2}-Si.
-The x axis is \ce{SiO2} thickness, y axis is wavelength.It is assumed that the incident light is polarized along c axis of \ce{MoO3}.}
-\label{fig:mofl}
+\subfloat[]{\label{fig:mosem1}\includegraphics[width=0.45\textwidth]{mosemsi_a}}\hspace{0.04\textwidth}
+\subfloat[]{\label{fig:mosem2}\includegraphics[width=0.45\textwidth]{mosemsi_b}}
+\caption[Representative morphologies of \ce{MoO3} on Si]{(a) Low magnification and (b) high magnification SEM images of representative depositions of \ce{MoO3} on Si for non-catalytic growth.}
+\label{fig:mosisem}
 \end{figure}
@@
 Then a empirical dependence shown in Eq.~\ref{eq:sca2} is used as polynomial fitting model.
-\begin{figure}[htb]
-\centering
-\subcaptionbox{\label{fig:moxrd}}{\includegraphics[width=0.45\linewidth]{xrd_moo3}}%
-\subcaptionbox{\label{fig:moram}}{\includegraphics[width=0.45\linewidth]{xrd_moo3}}
-\caption[Crystalline phase characterization of \ce{MoO3} on Si]{(a) XRD pattern and (b) Raman spectrum of typical \ce{MoO3} on Si, $\lambda_{ex} = 532nm$.}
-\label{fig:mooxch}
-\end{figure}
 

### 2014-10-02 FrontMatter/Abstract.tex
after format review, bold font in figure caption removed, frontmatter spacing fixed

@@
 \begin{abstract}
-
 Transition metal oxides (TMOs) exhibit rich structures and useful properties, and could been used in solar energy harvesting (\emph{e.g.}, photoelectrochemistry, photocatalysis, and photovoltaics) and energy saving (\emph{e.g.}, electrochromism and photochromism) applications.

### 2014-10-02 ch-moox/moox.tex
after format review, bold font in figure caption removed, frontmatter spacing fixed

@@
 
-In this chapter,
+In this chapter, a new growth model of \ce{MoO3} using alkaline metal ions as catalysts was discovered and investigated in depth.
+The growth kinetics was closely inspected using a series of controlled experiments.
+A modified vapor-solid-solid mechanism was proposed and favorably verified.
+Two growth modes, i.e., transverse growth and axial growth, were highlighted, which not only improved the yield, but also allowed for versatile morphology control of 1D \ce{MoO3} nanostructures.
+This methodology was further extended onto glass and ITO glass substrates, paving the way to a more integrated process of using \ce{MoO3} nanostructures onto various solar energy saving and harvesting applications.

### 2014-10-02 ch-tms/tms.tex
after format review, bold font in figure caption removed, frontmatter spacing fixed

@@
-\chapter{WO$_3$-WS$_2$ Heterostructure}
+\chapter{TEM-RAMAN STUDY ON INDIVIDUAL TUNGSTEN OXIDE-TUNGSTEN DISULFIDE CORE-SHELL NANOWIRE}
 
@@
 
-Four kinds of tungsten powders were used as precursor to prepare \ce{WO3} NWs, and sulfur powder was used to fabricate \ce{WO3}-\ce{WS2} core-shell NWs, as summarized in Table.~\ref{tab:ch5pre}.
-All reactants were employed as received without further processing.
-Substrates cleaning procedures have been introduced in Sec.~\ref{ch2sub}.
-
-% Tungsten powders size and purity
-\begin{table}[htb]
-\centering
-\caption{List of reactants for \ce{WO3}-\ce{WS2}}\label{tab:ch5pre}
-\begin{tabular}{lccr}
-\toprule
-Name & purity & average size & vendor info\\
-\midrule
-3N   &  99.9\% & 17 $\mu$m & Alfa Aesar \#39749\\
-3N5   &  99.95\% & 32 $\mu$m  & Alfa Aesar \#42477\\
-4N5   &  99.995\% & 3.3 $\mu$m  & Materion T-2049 \\
-5N   &  99.999\% & 1.5 $\mu$m & Alfa Aesar \#12973\\
-S    &   99.5\%  &  NA  & Alfa Aesar \#10785\\
-\bottomrule
-\end{tabular}
-\end{table}
-
-\ce{WO3} NWs were obtained by a seeded growth with tungsten powders applied onto the Si substrate.
-To find out the optimal conditions, tungsten powder oxidation experimental were carried out.
-Schematic layout of each growth were illustated in Fig.~\ref{fig:ch5grow} including the sulfurization process.
+The \ce{WO3}-\ce{WS2} core-shell nanowires were fabricated using a sulfurization process based on the \ce{WO3} NWs prepared by the seeded growth method in Chapter~3, Sec.~\ref{sec:sgfg}.
+For the sake of completeness, schematic layout of overall growth were illustrated in Fig.~\ref{fig:ch5grow} including the oxidation of W powder, the seeded growth and the sulfurization process.
 
@@
 The surface of the NWs were rather smooth without other attachments.
-The NWs array grow slightly larger than the W seed ( $\sim 12 \mu$m), mostly due to the elongation of NW.
+The NWs array grow slightly larger than the W seeds ($\sim$12 $\mu$m), mostly due to the elongation of NW.
 
@@
 \end{figure}
-
 This observation can also be used to account for the extreme small peak at 13.87$^{\circ}$ in the post-sulfurization spectrum.
-Compared the reference 2H-\ce{WS2} (002) peak (14.37$^{\circ}$, ICDD PDF 04-003-4478), this redshift indicates an increase of lattice spacing along $c$ axis (from 6.16 \AA to 6.38 \AA).
+Compared the reference 2H-\ce{WS2} (002) peak (14.37$^{\circ}$, ICDD PDF 04-003-4478), the redshift of sample peak indicates an increase of lattice spacing along $c$ axis (from 6.16 \si{\angstrom} to 6.38 \si{\angstrom}).
 The FWHM of this (002) peak is about 1.1$^{\circ}$, giving an estimation on the crystalline size of 7.5 nm according to Scherrer equation.
@@
 Fig.~\ref{fig:ch5ws2tem1} shows HRTEM imaging on typical tip and body region of the core-shell NW, respectively.
-A comparison with the pre-sulfurization specimen (Fig.~\ref{fig:woseedtem2}) readily reveals the formation of core-shell morphology after sulfurization.
+A comparison with the pre-sulfurization specimen (Fig.~\ref{fig:woseedtem2} on page~\pageref{fig:woseedtem2}) readily reveals the formation of core-shell morphology after sulfurization.
 The measured layer spacing is 6.4 \AA, slight larger than bulk 2H-\ce{WS2} of 6.16 \AA, but in good agreement with XRD results in Fig.~\ref{fig:ch5ws2xrd}.
@@
 \end{figure}
-
-After examining dozens of core-shell NWs, this thesis found the \ce{WS2} layer number at NW tip was usually the largest, reaching more than ten, and the layer number could decrease to one along the NW body, but there exist some layer number fluctuation and shape modification.
+After examining dozens of core-shell NWs, it was found the \ce{WS2} layer number at NW tip was usually the largest, reaching more than ten, and the layer number could decrease to one along the NW body, but there exist some layer number fluctuation and shape modification.
 Fig.~\ref{fig:ch5ws2tem3} shows a smooth transition of \ce{WS2} layer number on the tip region of one NW.
@@
 \section{Summary}
+
+A comprehensive understanding of the structure-property relation, which is essential to successful application of nanomaterials, is often hindered by the ensemble averaged characterizations in conventional methods.
+The present work in this chapter, to some extent, circumvents this limitation by leveraging a home-built micromanipulator apparatus to transfer the nanostructures between TEM grids and other desired substrates.
+And considerable insight on the \ce{WO3}-\ce{WS2} core-shell nanostructures was obtained: few-layer, even single-layer \ce{WS2} nanotube was observed with \ce{WO3} core; layer dependent Raman spectra were studied at on-resonance and off-resonance conditions; the fingerprint of few-layer \ce{WS2} was revealed; photoluminescence from core-shell NWs was identified.
+These results hold great values to the application of \ce{WO3}-\ce{WS2} heterostrucutres in photocatalysis and photoelectrochemical applications.
+More important, this technique of TEM-Raman integrated study could be readily applied to a variety of other nanomaterials, therefore opening a broad spectrum for the understanding of the structure-property relation, propelling the potential nano-engineering applications.
+
+\chapter{SUMMARY AND FUTURE WORK}

### 2014-10-02 ch-tms/tmspart.tex
after format review, bold font in figure caption removed, frontmatter spacing fixed

@@
 In each growth, about $10^{-10}$ mol PTAS was applied onto \ce{SiO2}-Si, which was rendered hydrophilic and gentle gas blow to distribute the solution evenly.
-
-In short summary, this thesis stresses that there are several key factors in successfully synthesizing \ce{WS2} FL:
-\begin{itemize}
-\item \ce{WO3} powder size distribution and absolute amount (0.69 g \ce{WO3} in 10 mL acetone or IPA, inspired by the \ce{MoO3} nanoribbons usage);
-\item Sulfur amount and heating method to ensure a constant sulfur-rich environment;
-\item \ce{WO3} powder source to substrate distance, which is coupled to pressure and carrier gas flow in determining the transport (atmospheric, 3-5 mm);
-\item temperature ramping and growth time (750-800 \si{\degreeCelsius}, 3-10 min);
-\item 300 nm \ce{SiO2}-Si substrate to make OM flakes identification easier.
-\end{itemize}
 

### 2014-10-02 ch-wox/ch-wox.tex
temperatory fix for multiline chapter name display in ToC
after format review, bold font in figure caption removed, frontmatter spacing fixed

@@
 
-\chapter{Impurity Effects on WO$_3$ Nanowires}
+\chapter{IMPURITY EFFECTS ON THE GROWTH OF TUNGSTEN OXIDE NANOWIRES}
 
@@
 These results are consistent with the SEM observation (Fig.~\ref{fig:nawoxsemall}) and the composition change from the EDX measurements (Fig.~\ref{fig:nawoxser}b).
+Details XRD indices assignment is summarized in Table~\ref{tbl:xrd}.
+
+\begin{table}
+\centering
+\caption{XRD assignments}\label{tbl:xrd}
+\begin{tabular}{llllll}
+\toprule
+\ce{WO3} &          &\ce{Na5W14O44} &      & \ce{Na2W4O13} & \\
+2$\theta$   & hkl   & 2$\theta$   & hkl    & 2$\theta$   & hkl   \\
+\midrule
+ 23.05   & 0 0 2 & 9.65    & 0 0 2  & 10.85   & 1 0 0 \\
+ 23.59   & 0 2 0 & 14.49   & 0 0 3  & 21.8    & 2 0 0 \\
+ 24.31   & 2 0 0 & 19.37   & 0 0 4  & 32.97   & 3 0 0 \\
+ 26.60   & 1 2 0 & 24.27   & 0 0 5  & 56.45   & 5 0 0 \\
+ 34.10   & 2 0 2 & 29.22   & 0 0 6  &         &       \\
+ 47.11   & 0 0 4 & 39.36   & 0 0 8  &         &        \\
+ 48.29   & 0 4 0 & 44.46   & 0 0 9  &         &        \\
+ 49.79   & 4 0 0 & 49.71   & 0 0 10 &         &        \\
+         &       & 55.23   & 0 0 11 &         &        \\
+         &       & 60.77   & 0 0 12 &         &        \\
+\bottomrule
+\end{tabular}
+\end{table}
 
@@
 More investigation is needed to vigorously determined the electronic transport properties of \ce{Na5W14O44} NW.
+\textbf{Ordinary transport growth using other W powders}
 % 3N5 powder growth
@@
 \end{figure}
+
 Typical morphologies of ordinary transport growth using other powders are shown in Fig.~\ref{fig:wox3n5} and Fig.~\ref{fig:wox4n5}, respectively.
@@
 \end{figure}
-It is worth pointing out that there are some NWs growth in low temperature end associated with 4N5 (Fig.~\ref{fig:wox4n5}c), although not in large scale.
+It is worth pointing out that there are some NWs growth in low temperature end associated with 4N5 growth(Fig.~\ref{fig:wox4n5}c), although not in large scale.
 
@@
 Understanding the oxidation of tungsten powder is the key to obtain high yield in seeded growth.
-Oxidation of tungsten have been investigated under diverse conditions, such as at elevated temperature (\textgreater 1100 \si{\degreeCelsius} ) and oxygen pressure on the order of Torr,\cite{Base1965} and at temperatures ranging from 20 to 500 \si{\degreeCelsius} under atmosphere pressure.\cite{Warren1996} \ce{WO_x} NWs were readily found when tungsten (foil, wire, or powder) is oxidized under various conditions.\cite{Zhu1999,Karuppanan2007,Hsieh2010} However the study on tungsten powder oxidation behavior between intermediate temperature range and under low pressure is still rare.
+Oxidation of tungsten have been investigated under diverse conditions, such as at elevated temperature (\textgreater 1100 \si{\degreeCelsius}) and oxygen pressure on the order of Torr,\cite{Base1965} and at temperatures ranging from 20 to 500 \si{\degreeCelsius} under atmosphere pressure.\cite{Warren1996} \ce{WO_x} NWs were readily found when tungsten (foil, wire, or powder) is oxidized under various conditions.\cite{Zhu1999,Karuppanan2007,Hsieh2010} However the study on tungsten powder oxidation behavior between intermediate temperature range and under low pressure is still rare.
 This thesis studied the oxidation of tungsten powders with diverse size within temperature range from 500 to 1000 \si{\degreeCelsius} and under several mTorr oxygen partial pressure.
@@
 The NW density is dramatically increased.
-The NWs have length about 1 to 2 $\mu m$ and diameter about 200 nm.
+The NWs have length about 1 to 2 $\mu$m and diameter about 200 nm.
 Close-up view (inset of Fig.~\ref{fig:fg2}) shows the NWs have clear facets, implying its high crystalline quality.
@@
 %\end{figure}
+to be added, NaOH WO3 results.
 
@@
 
-to be added, NaOH WO3 results. 
-A systematical investigation of \ce{WO3} NW growth using W powders as precursor in CVD method was performed.
+A systematical investigation of \ce{WO3} nanowire growth using CVD method with tungsten powders as precursor was performed.
+Four kinds of tungsten powder sources were used, and the sodium impurity effect was throughly studied.
+\ce{Na5W14O44} NW was first reported from this study; the crystal structure was investigated in details, and HRTEM images were obtained.
+Besides, the Raman vibrational spectroscopy of \ce{Na5W14O44} was also revealed.
+The presence of sodium tungsten oxide phase indicates that the CVD growth of \ce{WO3} is extremely sensitive to Na contents.
+The insight of \ce{WO3} growth kinetics we have gained from this study could help establish a systematic connection between the interaction of transition metal oxide and alkaline metal ions, thereby turning this deleterious effect into a beneficial approach of controlled growth.
+In fact, favorable results have been observed on both \ce{WO3} and \ce{MoO3} 1D nanostructures syntheses using NaOH treated Si substrates.
+Details will be presented in Chapter 4 and 6.
+Moreover, two alternative approaches of \ce{WO3} NWs were also attempted, and the seeded growth method proved effective for large scale growth.

### 2014-10-02 misc/mwe.tex
after format review, bold font in figure caption removed, frontmatter spacing fixed

@@
 * no external link in electronic version, turn off doi
-*
+* adjusting space between list of fig tbl, in tocloft afterskip command
+
+`a ref <https://staff.washington.edu/fox/tex/uwthesis.shtml>`_

### 2014-10-09 misc/SI_thesis.tex
supporting info reading

@@
 
-\section{A LONG SECTION TITLE FOR TOC CONTENT LINE WRAPPING TEST TEST TEST A LONG SECTION TITLE FOR TOC CONTENT LINE WRAPPING TEST TEST TEST}
+\section{KK, optics modeling, doping}
+
+optical properties of \ce{WO3} gaps\cite{Saygin-Hinczewski2008}
 
@@
 
-The average distance between dopant atoms is cubed root of concentration, $d = (10^{18} cm^{-3})^{-1/3} = 10nm$.
+The average distance between dopant atoms is cubed root of concentration, $d = (10^{18})^{-1/3}$ \si{cm^{-3}}$^{-1/3}$ = 10 nm.
 
@@
 for p-type silicon, when the conductivity $\sigma = 1 (ohm cm )^{-1}$, the doping level is
-$N_A = \frac{\sigma}{q \mu_p}= 1 / (1.6E-19 \times 450) = 1.4E16 cm^{-3}$.
+$N_A = \frac{\sigma}{q \mu_p}= 1 / (1.6E-19 \times 450)$ = 1.4E16 \si{cm^{-3}}.
 
@@
 Two theories arise to describe the outer shell electrons and to correlate the structure and physical properties: \gls{cft} and band theory.\cite{Goodenough1971} \gls{cft} assumes weak interaction between neighboring atoms and localization of electron towards parent atom, whereas band theory assumes that electron is shared equally by all nuclei and therefore a many-electron problems follows.
-Description of a single electron in periodic potential fail to treat the electron correlations adequately, as the interaction between atoms becomes weaker.For transition metals, $s$ and $p$ electrons are well described by a collective-electron model, while the 4f or 5f electrons are tightly bound to nuclei and screened from the neighboring atoms by 5s, 5p or 6s, 6p core electrons, hence it matches well with a localized-electron model.
+Description of a single electron in periodic potential fail to treat the electron correlations adequately, as the interaction between atoms becomes weaker.
+For transition metals, $s$ and $p$ electrons are well described by a collective-electron model, while the 4f or 5f electrons are tightly bound to nuclei and screened from the neighboring atoms by 5s, 5p or 6s, 6p core electrons, hence it matches well with a localized-electron model.
 d electrons show intermediate character.
@@
 
+sodium tungsten bronzes, DRS from 335 nm to 1250 nm show \ce{Na_{0.3}WO3} exhibits absorption peak at about 650 nm.\cite{Brown1954}
+
+oxygen deficiency, electron carrier con about $5\times10^{18}$ \si{cm^3}, absorption edge at 2.7 eV attributed allowed transition.
+absorption in infrared region observed but not rigorously resolved: donor level in the forbidden gap near VB, or thermally excited electrons in CB.
+Absorption increase when oxygen vacancy is created.
+Resistivity increase as heated up.
+\cite{Berak1970}
+
+A systematic study of optical and electrical properties of \ce{WO3} thin film.\cite{Deb1973} Film density 6.5 \si{g\per cm^3}, substantial porosity.
+\ce{WO3} become substoichiometric at 1300-1500 K, and evaporate at a composition near \ce{WO_{2.96}}.
+$K \propor (h\nu - E_g)^2/h\nu$, indicating an allowed band to band transition, and 3.25 eV energy gap determined thereby.
+Refractive index $\epsilon_{st}$ of thin film \ce{WO3} found at 2.2, lower than that of single crystal value of 2.5; $n$ increases to 4.0 at absorption edge region, with $\alpha$ as high as $10^5$ \si{cm^{-1}}.
+So the color center can form in a thin layer of 100 nm; its density estimated by the Smakula's Equation:
+\[
+Nf = 0.89\times10^17\frac{n}{(n^2+2)^2} \alpha d
+\]
+where $f$ osc strength, n ref index, $\alpha$ in \si{cm^{-1}}, and d is the half width of absorption band. Assuming $f$ = 1, N to be $5\times10^{19}$ \si{cm^3}. 
+Narrow conduction band proposed to explain the high energy peak at 4.39 eV and 5.25 eV. Impurity band when the ele wavefuntion overlap, the color center spacing comparable to lattice constant.
+
 \citeauthor{Wang2009a} mentioned that amorphous \ce{WO3} can only be used in lithium-based electrolytes due to its in-compact structure and high dissolution rate in acidic electrolyte solutions.
@@
 Raman assignment of \ce{WO3}
-
 XRD assignment of \ce{WO3}
@@
 
-\ce{Na2W2O7} Raman. \cite{Knee1979}
-
-\ce{WO3}, \ce{WP3.H2O}\cite{Daniel1987}
+\begin{table}[htb]
+\centering
+\caption{Raman fingerprints of tungsten oxides and sodium tungsten compounds}\label{tab:woram2}
+\begin{tabular}{lp{3in}r}
+\toprule
+Name & Raman Shift (\si{cm^{-1}}) &  Ref   \\
+\midrule
+\ce{WO2}  & 287(s), 334(w), 514(m), 600(w), 621(w), 785(vs) & \cite{Ma2005} \\
+\ce{W18O49}  & broad bands from 750 to 780 & \cite{Guo2012} \\
+             &  267(s), 778(s), 969(m) & \cite{Liu2013d} \\
+m-\ce{WO3}  & 131(m), 265(m), 327(m), 715(s), 807(vs) &  \cite{Salje1975a,Daniel1987} \\
+h-\ce{WO3}  & 162(m), 253(m), 320(m), 645, 690(s), 817(vs) &  \cite{Daniel1987}\\
+\ce{WO3.H2O}  & 230(m), 377(w), 428(w), 650(s), 816(vs), 946(vs) &  \cite{Daniel1987} \\
+\ce{WO3.2H2O}  & 235, 268(m), 380(w), 662(s), 685(vs), 960(vs) & \cite{Daniel1987} \\
+\ce{Na2WO4}  & 94(w), 314(vw), 377(m), 813(m), 930(vs) &  \cite{Lima2011} \\
+\ce{Na2W2O7}  & 381(w), 422(w), 763(w), 835(s), 886(m), 948(m), 957(vs) &  \cite{Knee1979} \\
+\ce{Na4W4O13} & &\\
+\ce{Na5W14O44} & & this work
+\bottomrule
+\end{tabular}
+Materials in solid state, 
+vw-very weak; w-weak; m-medium; s-strong; vs-very strong
+\end{table}
+
+Nanoscale \ce{WO3} Raman.\cite{Boulova2002}
+
+\ce{WO3} and sub-wo3 conductivity vs temp. \cite{Sahle1983}
+
+oxygen vacancies in \ce{WO_{3-x}}.\cite{Wang2011b}  Coloration and electron conductivity changes.
+\citeauthor{Wang2011b} found strong dependence of WO3-x electronic properties on $V_O$ concentration and the the crystallographic direction on which O is removed.
+DFT band gap calculation is close to experimental value.
+Vacancy levels are found at 2.1eV.
+
+The Raman spectra of \ce{WO_x} is rare because of the difficulty of preparing pure suboxides phase and the strong shielding of \ce{WS2}.
+Yet it does exhibit distinct Raman spectra.
+\cite{Tenne2005} The 870 line is attributed to \ce{W3O8}.\cite{Hardcastle1995}
+
+Delichere1988coloured states
+
+\ce{W18O49} reflectivity, carrier density $1.87\times10^{22}$ \si{cm^{-3}}, quasi-free carrier reflection of Drude type, \cite{Brandt1981}
 
@@
 
+carrier density estimation, the stoichiometry of tungsten bronze was calculation from the inserted charge by Faraday's Law.
+Na diffuses slower than H+, accumulating at the surface of wo3 film and preventing further intercalation.\cite{Dini1996}
+
+\[
+m = \frac{Q}{F} \frac{M}{z},
+\]
+where $m$ is the mass of substance at an electrode in gram, $Q$ is the total charge transferred; F is Faraday constant; $M$ is molar mass; $z$ is the valency number of ions.
+
+The degree of \ce{H^+} intercalation, $x$, is determined by integrating cathodic current, and given by
+\begin{equation}
+x = \frac{Q}{F}\frac{M_\ce{WO3}}{m_f}
+\end{equation}
+where $m_f$ is the mass of film, $M_\ce{WO3}$ is the molar mass of \ce{WO3*1/3H2O}, and F is Faraday's constant. 
+The color center density, $c$, is then obtained using formula
+\begin{equation}
+c= \frac{x \rho N_A}{M_\ce{WO3}}
+\end{equation}
+where $N_A$ is Avogadro number, $\rho$ is density of film.
+
+During the test of ECD, constant current source is often used. The total charge $Q$ is then $It$. Charge density, the diffusion of \ce{Na+},
+
 Characterization of ECD (work like a thin-film batteries) includes transmission measurement and associated EC calculation, charge-discharge time, current-time curve and the fitting of obtained data.
 
-The coloration efficiency (CE) represents the change in the optical density (OD) per unit charge density ($Q/A$, in units of \si{\cm^2\per\coulomb}) during switching and can be calculated according to the formula:
+The coloration efficiency (CE) represents the change in the optical density (OD) per unit charge density ($Q/A$ in unit of \si{\coulomb}\per\cm^2) during switching and can be calculated according to the formula:
 \begin{equation}
@@
 
-The degree of \ce{H^+} intercalation, $x$, is determined by integrating cathodic current, and given by
-\begin{equation}
-x = \frac{Q}{F}\frac{M_\ce{WO3}}{m_f}
-\end{equation}
-where $m_f$ is the mass of film, $M_\ce{WO3}$ is the molar mass of \ce{WO3*1/3H2O}, and F is Faraday's constant.
-The color center density, $c$, is then obtained using formula
-\begin{equation}
-c= \frac{x M_\ce{WO3}N_A}{\rho}
-\end{equation}
-where $N_A$ is Avogadro number, $\rho$ is density of film.
-
 battery and ECD.\cite{Granqvist2012} electrolyte: PVB (poly vinyl buteral).
@@
 anodic coloration:
-The coloration mechanism: \ce{MO6} octahedrons lead to $e_g$ and $t_{2g}$ level and ion channelling.
+The coloration mechanism: \ce{MO6} octahedrons lead to $e_g$ and $t_{2g}$ level and ion channeling.
 ref54,60,65,66,200,209,
@@
 first demonstration of \ce{WS2} NT n-type FET. \cite{Levi2013}
-the importance of contact, and avoiding moisture.
-
-The calculated carrier concentration is about $10^{19}cm^{-3}$, a highly doped semiconductor, possibibly arising from sulfur vacancy.
+the importance of contact, and avoiding moisture. The calculated carrier concentration is about $10^{19}cm^{-3}$, a highly doped semiconductor, possibly arising from sulfur vacancy.
 
@@
 MB adsorption on metal oxides. Monomer size is less than 1.5nm.
-Logarithmic acid dissociation constant $pK_a= -\log_10 \frac{[A^-][H^+]}{[HA]}$. The oxidation potential for \ce{H2O}-\ce{O2} couple is 1.23V and 0.817V versus NHE at pH 0 and pH 7, respectively.
+Logarithmic acid dissociation constant $pK_a= -\log_10 \frac{[A^-][H^+]}{[HA]}$. The oxidation potential for \ce{H2O}-\ce{O2} couple is 1.23 V and 0.817 V versus NHE at pH 0 and pH 7, respectively.
 
@@
 
-Raman fingerprint of m-\ce{WO3}, h-\ce{WO3} and \ce{WO3.nH2O} were summarized in ref\cite{Daniel1987}.
-
 \ce{WO3} on FTO by flame synthesis.\cite{Rao2014} \cite{Xu2006}
@@
 \ce{WO3} high temperature phase. \cite{Vogt1999}
-tungsten bronzes \cite{Wiseman1976}
-
-Phase transformation of \ce{Na2MoO4} and \ce{Na2WO4} by Raman scattering. \cite{Lima2011}
-
-\ce{WO2} NWs synthesis and raman \cite{Ma2005}.
 
@@
 
-optical properties of \ce{WO3} gaps\cite{Saygin-Hinczewski2008}
-
 \ce{WO3} atomic layer by exfoliation and annealing \ce{WO3.H2O}. \cite{Kalantar-zadeh2010a}
 
-sodium tungstates raman \cite{Redkin2010}
-
 charge density wave in K-doped \ce{WO3} \cite{Raj2008}
 
-\ce{W_{18}O_{49}} Raman, IR shielding.\cite{Guo2012} \cite{Guo2011}
-broad peak between 750-780 cm-1.
-
 \ce{WnO_{3n-1}} NPs. \cite{Frey2001}
@@
 optical characterization of WOx film.\cite{Valyukh2010a}
-
+homogeneous optical properties of \ce{WO3} film,\cite{Valyukh2010a}
+
+Tungsten bronze: \ce{AxWO3}, or \ce{AxW_{1-x}^{6+}W_x^{5+}O3}, 
+Tungstates: \ce{(A2O)x.(WO3)n}, full oxidized, no free electron, transparent in visible and NIR.
+
+============================
 E-beam penetration \cite{Kanaya2002}
@@
 \section{literature read}
+
+\ce{W_{18}O_{49}} Raman, IR shielding.\cite{Guo2012} \cite{Guo2011}
+broad peak between 750-780 cm-1.
+\ce{Na2W2O7} Raman. \cite{Knee1979}
+Raman fingerprint of m-\ce{WO3}, h-\ce{WO3} and \ce{WO3.nH2O} were summarized in ref\cite{Daniel1987}.
+Phase transformation of \ce{Na2MoO4} and \ce{Na2WO4} by Raman scattering. \cite{Lima2011}
+sodium tungstates solution compounds Raman \cite{Redkin2010}
+\ce{WO2} NWs synthesis and raman \cite{Ma2005}
+tungsten bronzes \cite{Wiseman1976}
 
@@
 
-oxygen vacancies in \ce{WO_{3-x}}.\cite{Wang2011b}  Coloration and electron conductivity changes.
-\citeauthor{Wang2011b} found strong dependence of WO3-x electronic properties on $V_O$ concentration and the the crystallographic direction on which O is removed.
-DFT band gap calculation is close to experimental value.
-Vacancy levels are found at 2.1eV.
-
-The Raman spectra of \ce{WO_x} is rare because of the difficulty of preparing pure suboxides phase and the strong shielding of \ce{WS2}.
-Yet it does exhibit distinct Raman spectra.
-\cite{Tenne2005} The 870 line is attributed to \ce{W3O8}.\cite{Hardcastle1995}
-
 \citeauthor{Huang2006} studied the \ce{W3On} cluster with n from 7 to 10.\cite{Huang2006} It was found \ce{W3O9} clusters possess a HOMO-LUMO gap about 3.4eV.

### 2014-10-09 ch-intro/ch-intro.tex
intro writing after format review

@@
 Transition metal generally refers to any element in the d-block of periodic table, and \glspl{tmo} mean the chemical compounds that consist of at least one transition metal element and oxygen.
-Similarly, \glspl{tmdc} are compounds that combine at least one transition metal with chalcogen elements from group VIA (S, Se, Te, Po).
-Oxygen also belongs to group VIA, but is often treated separately.
-This study focused on the following three materials: molybdenum oxide, tungsten oxide and tungsten disulfide.
-Both tungsten (W) and molybdenum (Mo) belong to Group VIB transition metal, with outer shell electrons configuration as $4d^55s^1$ and $5d^46s^2$, respectively.
+Similarly, \glspl{tmdc} are compounds that combine at least one transition metal with chalcogen elements from group VIA (S, Se, Te, Po).\footnote{Oxygen also belongs to group VIA, but is often treated separately.} This study focused on the following three materials: molybdenum oxide, tungsten oxide and tungsten disulfide.
+Both tungsten (W) and molybdenum (Mo) belong to Group VIB transition metal with outer shell electrons configuration as $4d^55s^1$ and $5d^46s^2$, respectively.
 
 The two metal oxides, \ce{MoO3} and \ce{WO3}, have been studied for decades for energy related applications, e.g., photoelectrochemistry,\cite{Su2010} photocatalysis,\cite{Watcharenwong2008, Macphee2010} photovoltaics\cite{Coridan2013} and electrochromism.\cite{Yoshimura1985, Mortimer2011} \ce{WS2} has also been investigated in various forms, i.e., thin film, nanotube, and 2D atomic layer recently.
-\ce{WS2} exhibits some potentials in solar cell, water cleavage, and field effect transistor.
+\ce{WS2} exhibits potentials in solar cell, water cleavage, and field effect transistor.
+Heterostructures formed between \gls{tmo} and \gls{tmdc} provide another degree of freedom to fine tune the band structures, which could potentially enhance the photon energy harvesting applications.
 
@@
 
-Commercial buildings in U.S.
-consumed approximately 35\% of the electricity use.\footnote{U.S.
-Department of Energy, "Energy Efficiency Trends in Residential and Commercial Buildings", 2008.} And traditional windows in the buildings account for up to 40\% of the total heating, cooling and lighting consumption.
-The smart windows is an energy efficient solution by allowing for separate control of the visible and NIR illumination/transmission.
+Commercial buildings in U.S.\ consumed approximately 35\% of the electricity use.\footnote{U.S.
+Department of Energy, "Energy Efficiency Trends in Residential and Commercial Buildings", 2008.} And traditional windows in the buildings account for up to 40\% of the total heating, cooling and lighting consumption, which is of low energy efficiency.
+The smart window is an energy efficient answer by allowing for separate control of the visible and NIR illumination/transmission.
+Several solutions have been proposed in both academia and industry to develop smart window, including liquid crystal, suspended particles and electrochromic materials.
+Previous efforts show the electrochromic materials is the most promising component in smart window design in comparison to other options, in that it requires little power to switch between bleaching and coloration status (changing the optical transmission) and the failure mode is being clear instead of opaque, which is of great importance in commercial application.
 
-Electrochromic materials are a group of functional materials whose coloration status can be reversibly switched using a finite durance of low DC voltage (\textless 5 V).
-Another important advantage of smart windows based on EC materials is the failure mode being clear instead of opaque compared to other techniques, e.g, liquid crystal, suspended particles.
+Electrochromism, where the optical property is changed upon applying low DC voltage (\textless 5 V), have been found in numerous inorganic and organic substances, e.g., \ce{V2O5}, \ce{WO3}, and \ce{NiO} for former group, and prussian blue, polyaniline for the latter one.
+This study covers two inorganic metal oxides, i.e., \ce{WO3} and \ce{MoO3}.
+Detailed electrochromic mechanism will be discussed in Chapter 1; a brief review of electrochromism study on \ce{WO3} is presented here.
 
+Typical transmission spectra of prototype \gls{ecd} based on \ce{WO3} thin film are shown in Fig.~\ref{}, where T in bleaching and coloration states 
+A thin film example on the valency number, color center density. some calculation on doping, uv-vis results on the thin film. 
+how the transmission, absorption, and reflection is modulated.
+
+The problems of amorphous wo3.
+
+\gls{tmo} are a group of functional materials whose bleaching-coloration status can be reversibly switched using a finite durance of low DC voltage (\textless 5 V).
+Another important advantage of smart windows based on EC materials is the failure mode being clear instead of opaque compared to other techniques.
+
+exhibits electrochromic functionality. reversible, recoverable, electrochromism, 
 coloration efficiency, the doping amount, 
+ion mobility is the bottleneck, 
+The optical properties modification in EC materials is related to the electron density difference.
 
-some calculation on doping, uv-vis results on the thin film.
+\subsection{Photocatalysis for Solar Energy Harvesting}
 
-\subsection{Photocatalysis for Energy Harvesting}
-
-Photocatalytic activity occurs when a semiconductor in aqueous solution is illuminated by photons of energy larger than the bandgap, then electron-hole pairs generate free radicals, i.e., \ce{OH.}, which enable further reactions.
-For water splitting using solar energy, the band gap should be within $2.0 \sim 3.0 $ eV, and CB edge should be more negative than reduction potential of \ce{H^+/H2}, whereas the VB top should be more positive than the oxidation potential of \ce{H2O}/\ce{O2}.\cite{Osterloh2008,Wang2012} The valence band holes (\ce{h^+}) oxidize water to oxygen and conduction band electrons propel hydrogen generation, as depicted in Eq.~\ref{eq:h2o}.
+Photocatalytic activity occurs when a semiconductor in aqueous solution is illuminated by photons of energy larger than the bandgap, then the carriers (electron and hole) drift and generate free radicals, i.e., \ce{OH.}, which enable further reactions.
+For water splitting using solar energy, the bandgap should be within $2.0 \sim 3.0 $ eV, and CB edge should be more negative than reduction potential of \ce{H^+/H2}, whereas the VB top should be more positive than the oxidation potential of \ce{H2O}/\ce{O2}.\cite{Osterloh2008,Wang2012} The valence band holes (\ce{h^+}) oxidize water to oxygen and conduction band electrons propel hydrogen generation, as depicted in Eq.~\ref{eq:h2o}.
 \begin{subequations}\label{eq:h2o}
@@
 \includegraphics[width=0.7\textwidth]{woxnhe.jpg}
-\caption[Bands positions of \ce{WO3} versus NHE]{Bands positions of \ce{WO3} in contact with aqueous electolyte at pH 1, adapted from Ref.\cite{Gratzel2001}}
+\caption[Band positions of \ce{WO3} versus NHE]{Band positions of \ce{WO3} in contact with aqueous electrolyte at pH 1, adapted from Ref.\cite{Gratzel2001}}
 \label{fig:woxnhe}

### 2014-10-09 figure_table.tex
after format review, bold font in figure caption removed, frontmatter spacing fixed
intro writing after format review

@@
 \end{enumerate*} like this example.
+
+http://tex.stackexchange.com/questions/19675/siunitx-threeparttables-and-table-footnotes
 
@@
 \label{fig:mosisem}
+\end{figure}
+
+\begin{figure}[htb]
+\centering
+\subcaptionbox{\label{fig:moxrd}}{\includegraphics[width=0.45\linewidth]{xrd_moo3}}%
+\subcaptionbox{\label{fig:moram}}{\includegraphics[width=0.45\linewidth]{xrd_moo3}}
+\caption[Crystalline phase characterization of \ce{MoO3} on Si]{(a) XRD pattern and (b) Raman spectrum of typical \ce{MoO3} on Si, $\lambda_{ex} = 532nm$.}
+\label{fig:mooxch}
+\end{figure}
+
+\begin{figure}[htb]
+\centering
+\subcaptionbox{\label{fig:moind}}{\includegraphics[width=0.45\linewidth]{n_MoO3}}%
+\subcaptionbox{\label{fig:mocon}}{\includegraphics[width=0.45\linewidth]{MoO3_1L}}
+\caption[Refractive indices of \ce{MoO3}]{(a) Refractive indices of \ce{MoO3} Dashed line is n along $a$ axis while solid line is along $c$ axis.
+(b) optical contrast mapping of 1L \ce{MoO3} on \ce{SiO2}-Si.
+The x axis is \ce{SiO2} thickness, y axis is wavelength.It is assumed that the incident light is polarized along c axis of \ce{MoO3}.}
+\label{fig:mofl}
 \end{figure}
@@
 
+antidazzle window, electrochemical intercalation, coloration-bleaching kinetics, present as a minor phase, 
+(i.e. )
+(cf. )
+up-scaling capability, band edge smeared; major bands situated at
+
 \subsection{pronunciation}

### 2014-10-24 misc/SI_thesis.tex
misc works of paper reading, wo3 raman table etc

@@
 
+how to show the crystalline TMO is better than amorphous thin film counterparts.
+
+In comparison to oxides thin films, 1D \gls{tmo} nanostructures (e.g., nanowires) have following advantages to improve the response speed and enhance the coloration efficiency: (1) With reduced diameters down to nanometer scale, the distance for ion diffusing into and out of the nanowires is significantly shortened.
+(2) The gap between nanowires always provides channels for fast ion diffusion outside the nanowires.
+(3) The large surface area to bulk volume ratio of nanowires is desired to improve the overall usage of material, which results in enhanced the contrast between colored and bleached states.
+Furthermore, doped with certain metals (such as Ti and Ag), the crystalline structure of the TMO nanowires can be modified with enhanced electrochromic properties.\cite{Xiong2008}
+
 optical properties of \ce{WO3} gaps\cite{Saygin-Hinczewski2008}
+
+soda lime glass. thermal radiative transfer through windows, \cite{Rubin1985} \ce{FeO} absorb infrared, and \ce{Fe2O3} in ultraviolet,
+
+The phase of amplitude reflection coeffs
+\[
+\phi(\omega) = \frac{1}{2\pi} \int_0^\infty \frac{d\log r}{d\omega'}\log(abs(\frac{\omega' + \omega}{\omega' - \omega}))d\omega'
+\]
+
+two python projects available, KKcalc\cite{Watts2014} and hyperSpy. 
+http://www1.univap.br/gaa/nkabs-database/data.htm
+
+KK relations in optical materials research. 
+\begin{align}
+N(\omega) &= [N(-\omega)]^* \\
+N(\omega) - 1 &\approx -\frac{\omega_p^2}{2\omega^2}\\
+r(\omega) = \frac{N(\omega)-1}{N(\omega)+1} &= \frac{n-1+ik}{n+1+ik}\\
+r(\omega) &= |r(\omega)| \exp[i\theta(\omega)]\\
+\log r(\omega) &= \log|r(\omega)| + i\theta(\omega)
+\end{align}
+
+phase retrieval, 
+Principal value:
+\[
+P\cdot\int_0^\infty f(x)dx = \lim_{\delta\rightarrow 0} (\int_0^{a-\delta} f(x)dx + \int_{a+\delta}^\infty f(x)dx)
+\]
+
+Maclaurin methodology, \cite{Rocha2014}. The singularity,
+
+\[
+\nu_1, \nu_2, \nu_3, \ldots, \nu_m;\\
+k_1,k_2,
+\]
+
+\[
+n(\nu) = n_0 + 2/\pi \int_{\nu_1}^{\nu_2} \frac{\nu' k(\nu')}{\nu'^2 - \nu^2} d\nu'
+\]
+discretized as
+
+\[
+I_i = n_0 + 2/\pi \times 2h \times \sum_j f_j,
+\]
+where
+\[
+f_j = 0.5*k_j (\frac{1}{\nu_j - \nu_i} + \frac{1}{\nu_j + \nu_i})
+\]
+
+dispersive and dissipative mode, sum rules given. \cite{King1979}
+\[
+F(\omega) = \frac{\log r(\omega)}{\omega + i\omega'}
+\]
 
@@
 A systematic study of optical and electrical properties of \ce{WO3} thin film.\cite{Deb1973} Film density 6.5 \si{g\per cm^3}, substantial porosity.
-\ce{WO3} become substoichiometric at 1300-1500 K, and evaporate at a composition near \ce{WO_{2.96}}.
-$K \propor (h\nu - E_g)^2/h\nu$, indicating an allowed band to band transition, and 3.25 eV energy gap determined thereby.
+\ce{WO3} becomes substoichiometric at 1300-1500 K, and evaporate at a composition near \ce{WO_{2.96}}.
+$K \propto (h\nu - E_g)^2/h\nu$, indicating an allowed band to band transition, and 3.25 eV energy gap determined thereby.
 Refractive index $\epsilon_{st}$ of thin film \ce{WO3} found at 2.2, lower than that of single crystal value of 2.5; $n$ increases to 4.0 at absorption edge region, with $\alpha$ as high as $10^5$ \si{cm^{-1}}.
@@
 Narrow conduction band proposed to explain the high energy peak at 4.39 eV and 5.25 eV. Impurity band when the ele wavefuntion overlap, the color center spacing comparable to lattice constant.
+
+polycrystalline \ce{WO3} film reflectivity in NIR.\cite{Goldner1983} tentatively,  $E_p$ 4.07 eV was obtained by $R$ fitting using Drude model.
+
+T and R data on ECD. \cite{OBrien1999}
+
+ECD wo3 NW for fast response time. \cite{Liao2006a}
+
+exhibits electrochromic functionality. reversible, recoverable, electrochromism, 
+coloration efficiency, the doping amount, 
+ion mobility is the bottleneck, 
+The optical properties modification in EC materials is related to the electron density difference.
 
@@
 raman assign
-\begin{table}[htb]
-\centering
-\caption{Symmetry assignment of \ce{WO3}}\label{tab:woram}
-\begin{tabular}{cccc}
-\toprule
-Raman shift (\si{cm^{-1}}) & Symmetry &  Ref.   & Remarks   \\
-\midrule
-131(m)   & $B_{2g}$    &           & $T_c$    \ce{WO3} \\
-265(m)   & $B_{3g}$    &           & $T_c$    \\
-327(m)   & $A_g/B_{1g}$&           & $T_b$   \\
-711(s)     & $B_{2g}$    & $\tau$    &          \\
-803(vs)     & $A_g$       &           & $R_c$    \\
-\midrule
-230(m)   & $B_{3g}$     & $\delta$ & \ce{O=Mo=O}  \ce{WO3.H2O} \\
-380(w)   & $B_{1g}$     & $\delta$ & \ce{O-Mo-O}  & scissor  \\
-428(w)   & $A_g$        & $\nu_{as}$ & \ce{O-Mo-O}  & stretch,bend  \\
-650(s)  & $B_{2g},B_{3g}$ & $\nu_{as}$  & \ce{O-Mo-O}  & stretch  \\
-816(vs)   & $A_g$        & $\nu_{as}$  & \ce{O=Mo}  & stretch  \\
-946(vw)      & $A_g$         & $\nu_{as}$  & \ce{O=Mo}  & stretch  \\
-\bottomrule
-\end{tabular}
-
-vw-very weak; w-weak; m-medium; s-strong; vs-very strong
-\end{table}
 
@@
 \ce{Na2W2O7}  & 381(w), 422(w), 763(w), 835(s), 886(m), 948(m), 957(vs) &  \cite{Knee1979} \\
-\ce{Na4W4O13} & &\\
-\ce{Na5W14O44} & & this work
+\ce{Na2W4O13} & &\\
+\ce{Na5W14O44} & & this work\\
 \bottomrule
@@
 
-Delichere1988coloured states
+Delichere1988 coloured states
 
@@
 
-The coloration efficiency (CE) represents the change in the optical density (OD) per unit charge density ($Q/A$ in unit of \si{\coulomb}\per\cm^2) during switching and can be calculated according to the formula:
+The coloration efficiency (CE) represents the change in the optical density (OD) per unit charge density ($Q/A$ in unit of \si{\coulomb \per cm^2} during switching and can be calculated according to the formula:
 \begin{equation}

### 2014-10-24 misc/draft.tex
supporting info reading
misc works of paper reading, wo3 raman table etc

@@
 nanoscale Kirkendall effect: the outward diffusion of metal cations are balanced by an influx of vacancies. For example, diffusion coefficient of Ni in NiO is higher than that of oxygen.
+
+\gls{tmo} are a group of functional materials whose bleaching-coloration status can be reversibly switched using a finite durance of low DC voltage (\textless 5 V).
+Another important advantage of smart windows based on EC materials is the failure mode being clear instead of opaque compared to other techniques.
 
@@
 
+\begin{equation}\label{eq:mclns}
+\cee{MoCl5(WCl6) + S \rightarrow MoS2(WS2) + S2Cl2}.
+\end{equation}
+
 Exfoliated WS2 few layer PL.\cite{Zhao2012} excitonic absorption peaks A and B arising from direction transition at K point are found around 625nm (1.98eV) and 550nm, respectively, which are in agreement with results from bulk layers.

### 2014-10-24 ch-intro/ch-instr.tex
after format review, bold font in figure caption removed, frontmatter spacing fixed
figure caption fixed, proof reading and introduction chapter done

@@
 \subfloat[]{\includegraphics[width=0.9\textwidth]{CVD_model.jpg}}
-\caption[CVD system]{Home-built low-pressure chemical vapor system.
+\caption[Home-built low-pressure chemical vapor deposition system]{Home-built low-pressure chemical vapor deposition system.
 (a) Photograph of reaction chamber.
@@
 \centering
-\caption{home-built CVD parameters}\label{tab:cvd}
+\caption{Home-built CVD parameters}\label{tab:cvd}
     \begin{tabular}{lcccr}
@@
 \includegraphics[width=0.8\textwidth]{temp_profile.pdf}
-\caption[CVD temperature profile in ambient environment]{Temperature profile of home-built low-pressure chemical vapor system measured in ambient environment.}
+\caption{Temperature profile of home-built CVD in ambient environment.}
 \label{fig:ch2temp}
@@
 Depending on the specific experimental requirement, a hydrophilic surface may be required.
-A plasma cleaner (Kurt J Lesker, Plasma-Preen 862) was used to render a hydrophilic Si surface, where reaction among $e$, \ce{O+}, \ce{O2+}, \ce{O-},\ce{O2} occurs, and \ce{OH}-terminated surface followed.\cite{Habib2010} The treatment proceeds at 2 Torr \ce{O2} for 3 min.
+A plasma cleaner (Kurt J Lesker, Plasma-Preen 862) was used to render a hydrophilic Si surface, where reaction among $e$, \ce{O+}, \ce{O2+}, \ce{O^-},\ce{O2} occurs, and \ce{OH}-terminated surface followed.\cite{Habib2010} The treatment proceeds at 2 Torr \ce{O2} for 3 min.
 Glass substrates cleaning is the same as that of Si.
@@
 \centering
-\includegraphics[width=0.8\textwidth]{magsp.jpg}
-\caption[magnetron sputtering system]{Schematic drawing of sputtering adopted from ref\cite{Song2008}}
+\includegraphics[width=0.7\textwidth]{magsp.jpg}
+\caption[Schematic drawing of magnetron sputtering system]{Schematic drawing of magnetron sputtering system. Reproduced from Ref.\cite{Song2008}}
 \label{fig:ch2magsp}
@@
 \includegraphics[width=0.5\textwidth]{sem_sch.png}
-\caption[SEM excitation volume]{schematic drawing of electron materials interaction in SEM. Some process is not shown, such as Auger emission.}
+\caption[Schematic drawing of electron materials interaction in SEM]{Schematic drawing of electron materials interaction in SEM. Some process is not shown, such as Auger emission.}
 \label{fig:ch2sem}
@@
 \includegraphics[width=0.5\textwidth]{xrd_2theta.png}
-\caption[XRD configuration]{Bragg-Brentano geometry used in powder diffractometer}
+\caption{Bragg-Brentano geometry used in XRD configuration}
 \label{fig:ch2theta}
@@
 \centering
-\caption{XRD settings}\label{tab:ch2xrd}
+\caption{XRD settings used in this study}\label{tab:ch2xrd}
 \begin{tabular}{lp{1.5in}lp{1.5in}}
@@
 \centering
-\caption{Scattering angle difference of Si(111)}\label{tab:ch2tem}
+\caption{Scattering angle difference of Si(111) in XRD and TEM}\label{tab:ch2tem}
 \begin{tabular}{lccr}
@@
 3.135 \AA & Cu $K\alpha$ & 1.541 \AA & 28.45$^\circ$  \\
-3.135 \AA & 200 kV & 0.0251 \si{\angstrom}\textsuperscript{\emph{a}}& 0.45$^\circ$  \\
+3.135 \AA & 200 kV & 0.0251 \si{\angstrom} & 0.45$^\circ$  \\
 \bottomrule
 \end{tabular}
-
-\textsuperscript{\emph{a}} with relativistic correction;
 \end{table}
@@
 \includegraphics[width=0.5\textwidth]{UV-Vis_drs}
-\caption[UV-Vis and DRS measurement]{schematic drawing of (a) UV-Vis and (b) DRS measurement setup adopted from UV2600Plus manual.}
+\caption[Schematic drawing of UV-Vis and DRS measurement]{Schematic drawing of (a) UV-Vis and (b) DRS measurement setup adopted from UV2600Plus manual.}
 \label{fig:ch2uvvis}

### 2014-10-24 ch-intro/ch-intro.tex
figure caption fixed, proof reading and introduction chapter done

@@
 The two metal oxides, \ce{MoO3} and \ce{WO3}, have been studied for decades for energy related applications, e.g., photoelectrochemistry,\cite{Su2010} photocatalysis,\cite{Watcharenwong2008, Macphee2010} photovoltaics\cite{Coridan2013} and electrochromism.\cite{Yoshimura1985, Mortimer2011} \ce{WS2} has also been investigated in various forms, i.e., thin film, nanotube, and 2D atomic layer recently.
-\ce{WS2} exhibits potentials in solar cell, water cleavage, and field effect transistor.
-Heterostructures formed between \gls{tmo} and \gls{tmdc} provide another degree of freedom to fine tune the band structures, which could potentially enhance the photon energy harvesting applications.
+\ce{WS2} exhibits potentials in solar cell,\cite{Britnell2013} water cleavage,\cite{Ballif1999} and field effect transistor.\cite{Perkins2013} Heterostructures formed between \gls{tmo} and \gls{tmdc} provide another degree of freedom to fine tune the band structures, which could enhance the photon energy harvesting performances.
 
@@
 The smart window is an energy efficient answer by allowing for separate control of the visible and NIR illumination/transmission.
-Several solutions have been proposed in both academia and industry to develop smart window, including liquid crystal, suspended particles and electrochromic materials.
-Previous efforts show the electrochromic materials is the most promising component in smart window design in comparison to other options, in that it requires little power to switch between bleaching and coloration status (changing the optical transmission) and the failure mode is being clear instead of opaque, which is of great importance in commercial application.
+Several solutions have been proposed in both academia and industry to develop smart window, including liquid crystal, suspended particles and electrochromic materials.\cite{Lampert1998} Previous efforts\cite{Deb2008} show the electrochromic materials is the most promising component in smart window design in comparison to other options, in that it requires little power to switch between bleaching and coloration status (changing the optical transmission) and the failure mode is being clear instead of opaque, which is of great importance in commercial applications.
 
-Electrochromism, where the optical property is changed upon applying low DC voltage (\textless 5 V), have been found in numerous inorganic and organic substances, e.g., \ce{V2O5}, \ce{WO3}, and \ce{NiO} for former group, and prussian blue, polyaniline for the latter one.
-This study covers two inorganic metal oxides, i.e., \ce{WO3} and \ce{MoO3}.
+Electrochromism, where the optical property of the materials is changed upon applying low DC voltage (\textless 5 V), have been found in numerous inorganic and organic substances, e.g., \ce{V2O5}, \ce{WO3}, and \ce{NiO} for the former group, and prussian blue, polyaniline for the latter one.
+This study covers two inorganic metal oxides, \ce{WO3} and \ce{MoO3}.
 Detailed electrochromic mechanism will be discussed in Chapter 1; a brief review of electrochromism study on \ce{WO3} is presented here.
+\begin{figure}[htb]
+\centering
+\subfloat[]{\label{fig:introecd}\includegraphics[width=0.45\textwidth]{ecd_bw}}\hspace{0.04\textwidth}
+\subfloat[]{\label{fig:introtran}\includegraphics[width=0.45\textwidth]{ECD_trans}}
+\caption[ECD prototype and its transmission properties]{ECD prototype and its transmission properties.
+(a) Schematic diagram of \gls{ecd}, and (b) optical transmission in color and bleached states, reproduced from \cite{Lampert1998}}
+\label{fig:introec}
+\end{figure}
 
-Typical transmission spectra of prototype \gls{ecd} based on \ce{WO3} thin film are shown in Fig.~\ref{}, where T in bleaching and coloration states 
-A thin film example on the valency number, color center density. some calculation on doping, uv-vis results on the thin film. 
-how the transmission, absorption, and reflection is modulated.
+Prototype \gls{ecd} usually consists of a stacked configuration as shown in Fig.~\ref{fig:introecd}.
+Typical transmission spectra of prototype \gls{ecd} based on \ce{WO3} thin film are shown in Fig.~\ref{fig:introtran}\cite{Lampert1998}, where $T$ in bleaching and coloration states exhibit dynamic changes.
+The reflectance spectra of \ce{WO3} \gls{ecd} strongly depends on the device design.\cite{OBrien1999} As to the absorption, it was deduced that the infrared part was absorbed to a large extent, which was radiated again.
+Assuming the emission property of \gls{ecd} being that of blackbody, Fig.~\ref{fig:introbb} displays the wavelength distribution of spectral radiance, where the spectra span from 3 $\mu$m up to 30 $\mu$m, with peaks around $8\sim10$ $\mu$m.
+Further thermal engineering is needed to better regulate the infrared radiation.
 
-The problems of amorphous wo3.
+\begin{figure}[htb]
+\centering
+\includegraphics[width=0.6\textwidth]{blackbody1}
+\caption{Spectral radiance of blackbody at 0, 50 and 100 \si{\degreeCelsius}.}
+\label{fig:introbb}
+\end{figure}
 
-\gls{tmo} are a group of functional materials whose bleaching-coloration status can be reversibly switched using a finite durance of low DC voltage (\textless 5 V).
-Another important advantage of smart windows based on EC materials is the failure mode being clear instead of opaque compared to other techniques.
-
-exhibits electrochromic functionality. reversible, recoverable, electrochromism, 
-coloration efficiency, the doping amount, 
-ion mobility is the bottleneck, 
-The optical properties modification in EC materials is related to the electron density difference.
+The successful deployment of \gls{ecd} based on \ce{WO3} relies on several factors:\cite{Granqvist2000}
+\begin{itemize}
+\item low cost transparent conductive materials with low resistivity;
+\item low cost ion electrolyte of poor electron mobility;
+\item high yield growth method of \ce{WO3} and integration with other manufacturing process;
+\item and life cycle $> 10^5$ for long time outdoor usage.
+\end{itemize}
+The deficiency of \gls{ecd} based on amorphous or polycrystalline \ce{WO3} film is the accumulation of ions at the film surface preventing further intercalation,\cite{Dini1996} which led to low coloration efficiency and short life time.
+In contrast, nano-structured single crystalline \ce{WO3} could bypass this limitation, as detailed in Sec.~\ref{sec:nanoadv}.
 
@@
 Photocatalytic activity occurs when a semiconductor in aqueous solution is illuminated by photons of energy larger than the bandgap, then the carriers (electron and hole) drift and generate free radicals, i.e., \ce{OH.}, which enable further reactions.
-For water splitting using solar energy, the bandgap should be within $2.0 \sim 3.0 $ eV, and CB edge should be more negative than reduction potential of \ce{H^+/H2}, whereas the VB top should be more positive than the oxidation potential of \ce{H2O}/\ce{O2}.\cite{Osterloh2008,Wang2012} The valence band holes (\ce{h^+}) oxidize water to oxygen and conduction band electrons propel hydrogen generation, as depicted in Eq.~\ref{eq:h2o}.
+For water splitting using solar energy, the bandgap should be within $2.0 \sim 3.0 $ eV, and \gls{cb} edge should be more negative than reduction potential of \ce{H^+/H2}, whereas the \gls{vb} top should be more positive than the oxidation potential of \ce{H2O}/\ce{O2}.\cite{Osterloh2008,Wang2012} The valence band holes (\ce{h^+}) oxidize water to oxygen and conduction band electrons propel hydrogen generation, as depicted in Eq.~\ref{eq:h2o}.
 \begin{subequations}\label{eq:h2o}
@@
 \includegraphics[width=0.7\textwidth]{woxnhe.jpg}
-\caption[Band positions of \ce{WO3} versus NHE]{Band positions of \ce{WO3} in contact with aqueous electrolyte at pH 1, adapted from Ref.\cite{Gratzel2001}}
+\caption[Band position of \ce{WO3} versus NHE]{Band position of \ce{WO3} in contact with aqueous electrolyte at pH 1. Reproduced from Ref.\cite{Gratzel2001}}
 \label{fig:woxnhe}
@@
 
-For photochemical water reduction to occur, the flat-band potential of the semiconductor (for highly doped semiconductors, this equals to the bottom of the conductance band) must exceed the proton reduction potential of 0.0 V vs NHE at pH=0.\cite{Osterloh2008} Flat-band potentials strongly depend on ion absorption (protonation of surface hydroxyl groups), crystallographic orientation of the exposed surface, surface defects, and surface oxidation processes.
+For photochemical water reduction to occur, the flat-band potential of the semiconductor (for highly doped semiconductors, this equals to the bottom of the conductance band) must exceed the proton reduction potential of 0.0 V vs NHE at pH0.
+Flat-band potentials strongly depend on ion absorption (protonation of surface hydroxyl groups), crystallographic orientation of the exposed surface, surface defects, and surface oxidation processes.\cite{Osterloh2008}
 
-\subsection{Advantages of Nano-Engineering}
+\subsection{Advantages of Nano-Engineering}\label{sec:nanoadv}
 
-why nano?
-surface-to-volume ratio, more surface area for catalytic reaction; surface energy state: tuned by dimension; quantum confinement effects: exciton size vs physical dimension.
-easy for dopant diffusion, thereby band structure modification; charge-separation and transport mechanism may also differ from bulk.
+Several differences are noted in regarding to bulk materials and nanostructured materials.
+Nanostructured materials possesses gigantic surface area in comparison to its bulk counterpart of the same volume; for instance, given 1 gram \ce{SiO2} nanoparticles in diameter of 10 nm and assuming the density being 1.2 \si{g\per cm^3}, the estimated surface area will be $1\times10^6$ \si{cm^2}.
+This huge surface-to-volume ratio is generally a favorable feature for catalytic reactions, which predominately occur on the surface.\cite{Sha2009} Other features due to nanostructure include
+\begin{enumerate*}[label=\itshape\alph*\upshape)]
+\item surface energy state, thereby band structure modification;
+\item quantum confinement effect when exciton size is smaller then physical dimension; and
+\item different charge-separation and transport mechanism.
+\end{enumerate*} Overall, these features usually promise enhanced performance.
 
-how to show the crystalline TMO is better than amorphous thin film counterparts.
+Specifically/in regarding to the contents of this study, electrochromic applications based on \gls{tmo} nanowires will benefit from the reduced diffusion depth by eliminating the deficiency of ions accumulation accounted in amorphous oxide thin film devices, which, in turn, leads to shorter response time and higher coloration efficiency.\cite{Huang2008a,Scherer2012} And photocatalytic applications using \gls{tmo} nanostructures could harvest the huge surface area on which unsaturated bond reside, thereby enabling a much higher efficiency.\cite{Mills1993,Merki2011,Chen2011b}
 
-In comparison to oxides thin films, 1D \gls{tmo} nanostructures (e.g., nanowires) have following advantages to improve the response speed and enhance the coloration efficiency: (1) With reduced diameters down to nanometer scale, the distance for ion diffusing into and out of the nanowires is significantly shortened.
-(2) The gap between nanowires always provides channels for fast ion diffusion outside the nanowires.
-(3) The large surface area to bulk volume ratio of nanowires is desired to improve the overall usage of material, which results in enhanced the contrast between colored and bleached states.
-Furthermore, doped with certain metals (such as Ti and Ag), the crystalline structure of the TMO nanowires can be modified with enhanced electrochromic properties.\cite{Xiong2008}
+To make fully use of the nano-engineering, one must just be as aware of the limitations as one is of its advantages.
+For example, an obvious disadvantage is the difficulty of device fabrication using nanomaterials due to the size and requirements of new integration process.
+There also exist some uncertainty as to the energy band modification present in nanostructures, which could be either useful or not depending on the application scenario.\cite{Wang2012} With this explained, the dissertation moves on to the objective and scope section.
 
-\section{Objective and Scope}
-To fully harvest the advantages of these \gls{tmo} and \gls{tmdc} one-dimensional nanomaterials, a scalable growth method and a comprehensive understanding towards the growth-structure-property relation must first be established.
-Considering the nature of this Ph.D.\ study, this dissertation primarily focuses on synthesis, growth mechanism study and characterization, and will only present preliminary results on device and applications.
+\section{Scope and Dissertation Outline}
+To fully harvest the advantages of these \gls{tmo} and \gls{tmdc} one-dimensional nanomaterials, a scalable growth method and a comprehensive understanding towards the growth-structure-property relation must be established in the first place.
+This Ph.D.\ study primarily focuses on \ce{WO3} and \ce{MoO3} nanostructure synthesis, the growth mechanism study, crystal structure characterization, and optical properties measurement.
 
-\section{Dissertation Outline}
 The materials studied in this dissertation are tungsten oxides (\ce{WO3}), molybdenum oxides (\ce{MoO3}),and tungsten disulfide (\ce{WS2}).

### 2014-10-24 ch-moox/moox.tex
figure caption fixed, proof reading and introduction chapter done

@@
 % git version control added 012614
-\chapter{New Vapor-Solid-Solid Growth Modes of MoO$_3$}
+\chapter{Vapor-Solid-Solid Growth of MoO$_3$}
 
@@
 As shown in Fig.~\ref{fig:mo3model}, the layered structure consisting of zig-zag rows of edge-sharing \ce{MoO6} octahedra, while the rows are mutually connected by corners.
-
 \begin{figure}[htb]
 \centering
-\includegraphics[width=0.7\textwidth]{MoO3_model}
+\includegraphics[width=0.5\textwidth]{MoO3_model}
 \caption[\ce{MoO3} crystal model]{\ce{MoO3} crystal model.}
@@
 \end{figure}
-
 While considering the fact that four of the six surrounding O atom are at distances from 1.67 to 1.95 \AA, while the remaining two are as far as 2.25 and 2.33 \AA, \ce{MoO3} could also be considered as built up of chains of \ce{MoO4} tetrahedra connected by the sharing of two oxygen corners with two neighbouring tetrahedra in $c$ axis.
@@
 \subsection{Synthesis Review of Molybdenum Oxide}
+
 Researchers have been exploring a variety of methods to synthesized different \ce{MoO3} nanostructures.
@@
 \centering
-\caption{Reactants list}\label{tb:mosource}
+\caption{Reactants list of \ce{MoO3} growth}\label{tb:mosource}
 \begin{tabular}{lcccr}
@@
 \ce{Na2CO3}    & 33377 & 114X012 & 99.95\% &  Alfa Aesar \\
-\ce{Molybdenum}        & 00932 & I07S024 & 99.9\% &  Alfa Aesar\\
+\ce{Molybdenum}& 00932 & I07S024 & 99.9\% &  Alfa Aesar\\
 \bottomrule
@@
 \includegraphics[width=0.7\textwidth]{CVD_and_temp_MoO3.jpg}
-\caption[Growth setup of \ce{MoO3}]{Chemical vapor system and its temperature profile.
+\caption[CVD growth setup of \ce{MoO3}]{CVD growth setup of \ce{MoO3}.
 The triangular labels $\blacktriangledown$ were measured points at ambient environment.
@@
 From previous works in our group,\cite{predeep2011} it was found that with $T_h = 600$ \si{\degreeCelsius} and substrate placed at 6.5 in, microflakes grew at the high temperature edge of Si, suggesting the nucleation already started.\footnote{in 020510 batch} When flow of oxygen was gradually reduced, diminished size of micro-flake was observed at the same location of substrates.
-This results indicated the rate-determining step is diffusion when oxygen flow was in the range of 2 sccm to 0.5 sccm.\footnote{in (31210-31510) batches} It was also found the deposition amount on a particular location of the substrate is not linearly proportional to the growth time, \emph{i.e.}, the growth at upper stream edge first increase then decrease.
+This results indicated the rate-determining step is diffusion when oxygen flow was in the range of 2 sccm to 0.5 sccm.
+It was also found the deposition amount on a particular location of the substrate is not linearly proportional to the growth time, \emph{i.e.}, the growth at upper stream edge first increase then decrease.
 This is not surprising when considering the 3D temperature field in chamber requires some time to become synchronized as depicted in Fig.~\ref{fig:mooxgrowth}.
@@
 Most flakes exhibit rectangular shape, with average thickness of one micron, standard deviation $\sigma_D=0.34 \mu$m.
-% sem
+% sem in (31210-31510) batches
 \begin{figure}[htb]
 \centering
-\subfloat[]{\label{fig:mosem1}\includegraphics[width=0.45\textwidth]{mosemsi_a}}\hspace{0.04\textwidth}
-\subfloat[]{\label{fig:mosem2}\includegraphics[width=0.45\textwidth]{mosemsi_b}}
-\caption[Representative morphologies of \ce{MoO3} on Si]{(a) Low magnification and (b) high magnification SEM images of representative depositions of \ce{MoO3} on Si for non-catalytic growth.}
+\subfloat[]{\label{fig:mosem1}\includegraphics[width=0.4\textwidth]{mosemsi_a}}\hspace{0.04\textwidth}
+\subfloat[]{\label{fig:mosem2}\includegraphics[width=0.4\textwidth]{mosemsi_b}}
+\caption[Representative morphologies of \ce{MoO3} on Si]{Representative morphologies of \ce{MoO3} on Si: (a) low magnification and (b) high magnification SEM images of representative depositions of \ce{MoO3} on Si for non-catalytic growth.}
 \label{fig:mosisem}
@@
 \subfloat[]{\label{fig:moram}\includegraphics[width=0.45\textwidth]{raman_moo3}}
-\caption[Crystalline phase characterization of \ce{MoO3} on Si]{(a) XRD pattern and (b) Raman spectrum of typical \ce{MoO3} on Si, $\lambda_{ex} = 532$ nm.}
+\caption[Crystalline phase characterization of \ce{MoO3} on Si]{Crystalline phase characterization of \ce{MoO3} on Si: (a) XRD pattern and (b) Raman spectrum of typical \ce{MoO3} on Si, $\lambda_{ex} = 532$ nm.}
 \label{fig:mooxch}
@@
 \centering
-\includegraphics[width=0.8\textwidth]{MoO3_SEM_a.jpg}
-\caption[SEM imaging on \ce{MoO3} catalytic growth]{Effect of alkaline metal-based catalysts on the morphology of \ce{MoO3} depositions.
-(a) SEM image of rectangular nanoplates grown without catalysts.
+\includegraphics[width=0.9\textwidth]{MoO3_SEM_a.jpg}
+\caption[SEM imaging on \ce{MoO3} catalytic growth]{SEM imaging on \ce{MoO3} catalytic growth.
+Effect of alkaline metal-based catalysts on the morphology of \ce{MoO3} depositions: (a) SEM image of rectangular nanoplates grown without catalysts.
 (b-f) SEM images of different morphologies grown with NaOH catalysts: (b) nanobelts grown on top of dense array of nanoplates,(c) close-up view of the forked nanoplates from an area indicated by the square in Fig.~\ref{fig:ch4sem2by3}, (d) long nanobelts, (e) side-view of ultra-long microbelts, and (f) side-view of microtowers.
@@
 \centering
-\caption{Lattice information of \ce{MoO3}}\label{tab:ch4xrd}
+\caption{Lattice parameters of \ce{MoO3} derived from XRD}\label{tab:ch4xrd}
 \begin{tabular}{lccc}
@@
 \includegraphics[width=0.8\textwidth]{MoO3_TEM_XRD.jpg}
-\caption[XRD and TEM on \ce{MoO3} catalytic growth]{XRD spectra of (a) a specimen grown without catalysts and (b) a specimen grown with NaOH catalysts.
+\caption[XRD and TEM on \ce{MoO3} catalytic growth]{XRD and TEM on \ce{MoO3} catalytic growth.
+XRD spectra of (a) a specimen grown without catalysts and (b) a specimen grown with NaOH catalysts.
 (c) Low-magnification TEM image and (d) HRTEM image of nanoplate grown without catalyst.
@@
 \centering
-\includegraphics[width=0.6\textwidth]{moo3_pdsmall}
-\caption[Phase diagram of Na-Mo-O system]{Phase diagram of \ce{Na2MoO4} and \ce{MoO3} reproduced from Ref.~\cite{Hoermann1929}}
+\includegraphics[width=0.5\textwidth]{moo3_pdsmall}
+\caption[Phase diagram of \ce{Na2MoO4} and \ce{MoO3}]{Phase diagram of \ce{Na2MoO4} and \ce{MoO3} reproduced from Ref.~\cite{Hoermann1929}}
 \label{fig:ch4pd}
@@
 %theorem environment
-\begin{hypothesis}\label{hypo1}
+
 The reaction on NaOH-Si substrate follow the phase diagram, and \ce{Na2Mo4O13} serves as the catalyst promoting various 1D \ce{MoO3} growth.
-\end{hypothesis}
 
@@
 \includegraphics[width=0.9\textwidth]{MoO3_EDX_Raman}
-\caption[Growth evolution of \ce{MoO3}: first stage]{Evolution of the early stage for catalyst-assisted \ce{MoO3} growth: SEM images, micro-Raman spectra, and EDX spectra of the specimens grown for 15 min with different \ce{O2} flows of (a-c) 0.1 sccm, (d-f) 1 sccm, (g-i) 3 sccm, and (j-l) 10 sccm.
+\caption[Evolution of the early stage for catalyst-assisted \ce{MoO3} growth]{Evolution of the early stage for catalyst-assisted \ce{MoO3} growth: SEM images, micro-Raman spectra, and EDX spectra of the specimens grown for 15 min with different \ce{O2} flows of (a-c) 0.1 sccm, (d-f) 1 sccm, (g-i) 3 sccm, and (j-l) 10 sccm.
 }
@@
 \includegraphics[width=0.9\textwidth]{mooe_sem_ev}
-\caption[Growth evolution of \ce{MoO3}: second stage]{Growth evolution of the second stage of catalyst-assisted growth of \ce{MoO3} 1D structures: SEM images of the deposition at different growth temperatures with growth time of row 1: 15 min, row 2: 30 min, row 3: 60 min, and row 4: 90 min.
-The estimated temperature for each column from left to right is 525 \si{\degreeCelsius}, 445 \si{\degreeCelsius}, 390 \si{\degreeCelsius} and 340 \si{\degreeCelsius}, respectively.
-}
+\caption[Growth evolution of the second stage of catalyst-assisted growth of \ce{MoO3} 1D structures]{Growth evolution of the second stage of catalyst-assisted growth of \ce{MoO3} 1D structures: SEM images of the deposition at different growth temperatures with growth time of row 1: 15 min, row 2: 30 min, row 3: 60 min, and row 4: 90 min.}
 \label{fig:ch4ev}
@@
 \includegraphics[width=0.5\textwidth]{MoO3_SFig_EDX}
-\caption[Growth evolution of \ce{MoO3}: second stage]{SEM images and EDS spectra identifying the location, morphology, and composition of the catalyst particles on the nanobelt structures: (a-b) a catalyst particle (I) in the middle of a nanobelt (II), (c-d) two catalyst particles (I and II) leading the growth of two perpendicular nanobelts.
+\caption[SEM images and EDS spectra identifying the location, morphology, and composition of the catalyst particles on the nanobelt structures]{SEM images and EDS spectra identifying the location, morphology, and composition of the catalyst particles on the nanobelt structures: (a-b) a catalyst particle (I) in the middle of a nanobelt (II), (c-d) two catalyst particles (I and II) leading the growth of two perpendicular nanobelts.
 }
@@
 \includegraphics[width=0.5\textwidth]{MoO3_SFig_EDX_tower}
-\caption[Growth evolution of \ce{MoO3}: second stage]{SEM images and EDS spectra for identifying the location, morphology, and composition of the catalysts on the microtower structures: (a-b) a tiny catalyst particle (I) on top of a small cone shaped microtower (II), and (c-d) a catalyst particle (III) on a large and short microtower (IV).}
+\caption[SEM images and EDS spectra for identifying the location, morphology, and composition of the catalysts on the microtower structures]{SEM images and EDS spectra for identifying the location, morphology, and composition of the catalysts on the microtower structures: (a-b) a tiny catalyst particle (I) on top of a small cone shaped microtower (II), and (c-d) a catalyst particle (III) on a large and short microtower (IV).}
 \label{fig:ch4edx2}
@@
 Unlike the conventional \gls{vls} growth where the catalysts were predominantly found at the tip of 1D nanostructures, the catalyst in current study were mostly found at the side wall of long nanobelts, and the location could be on the tip, or several microns away from tip.
-As for the microtowers, it is even rare to observe Na element.\footnote{try m-Raman at different depths}
+As for the microtowers, it is even rare to observe Na element.
 
@@
 A growth model is proposed to account for the observed morphologies of \ce{MoO3} long nanobelt and tower-like structures.
-\begin{hypothesis}\label{hypo2}
+
+\fbox{%
+\parbox{0.8\textwidth}{%
 A transverse growth mode exists with growth direction perpendicular to the catalyst-deposition interface, promoting \ce{MoO3} nanoplate and nanobelt growth.
 A axial growth mode akin to conventional VLS process exists, and is responsible for \ce{MoO3} tower-like growth.
-\end{hypothesis}
+}%
+}
 
@@
 \includegraphics[width=0.7\textwidth]{vls_mode2}
-\caption[Growth model of \ce{MoO3}]{Schematic drawing on the growth steps of the proposed growth model in hypothesis~\ref{hypo2}.}
+\caption{Schematic drawing on the growth steps of the proposed growth mode.}
 \label{fig:ch4vls}
@@
 \includegraphics[width=0.8\textwidth]{MoO3_SFig_sidebyside}
-\caption[side by side growth of \ce{MoO3}]{(a) Schematic drawing of the side-by-side growth with one NaOH catalyst treated substrate and one bare substrate.
+\caption[Side-by-side growth of \ce{MoO3}]{Side-by-side growth of \ce{MoO3}.
+(a) Schematic drawing of the side-by-side growth with one NaOH catalyst treated substrate and one bare substrate.
 SEM images of the growth on the untreated substrates at different growth times: (b-e) 30 min and (f-i) 120 min.
@@
 \includegraphics[width=0.6\textwidth]{Fig7_MoO3_Small}
-\caption[Alternative catalysts for \ce{MoO3} growth 1]{SEM images of \ce{MoO3} 1D structures. (a) nanobelts grown with KI and (b) microtowers grown on ITO glass}
+\caption[Alternative catalysts for \ce{MoO3} growth]{Alternative catalysts for \ce{MoO3} growth.
+SEM images of \ce{MoO3} 1D structures.
+(a) nanobelts grown with KI and (b) microtowers grown on ITO glass}
 \label{fig:ch4al1}
@@
 \includegraphics[width=0.8\textwidth]{SFig5_MoO3_Small}
-\caption[Alternative catalysts for \ce{MoO3} growth 2]{SEM images of MoO3 1D structures: (a) forked nanoplates grown with \ce{Na2CO3}, (b) triangular microbelts grown on glass, and (c) nanobelts and microbelts grown on mica.}
+\caption[Alternative catalysts for \ce{MoO3} growth cont]{Alternative catalysts for \ce{MoO3} growth.
+SEM images of MoO3 1D structures: (a) forked nanoplates grown with \ce{Na2CO3}, (b) triangular microbelts grown on glass, and (c) nanobelts and microbelts grown on mica.}
 \label{fig:ch4al2}
@@
 \includegraphics[width=0.7\textwidth]{moo3_glass}
-\caption[\ce{MoO3} nanoplates on glass]{Optimized \ce{MoO3} nanoplates growth on glass.}
+\caption{Optimized \ce{MoO3} nanoplates growth on glass.}
 \label{fig:ch4glass}
@@
 \subfloat[]{\label{fig:mobg}\includegraphics[width=0.45\textwidth]{MoO3-bg}}
-\caption[UV-Vis spectra of exfoliated \ce{MoO3}]{(a) UV-Vis absorbance spectra of exfoliated \ce{MoO3}.
+\caption[UV-Vis spectra of exfoliated \ce{MoO3}]{UV-Vis spectra of exfoliated \ce{MoO3}.
+(a) UV-Vis absorbance spectra of exfoliated \ce{MoO3}.
 Dashed line (t0) represents measurement immediately after sonication, and solid line (t40h) is obtained after sitting for 40 h.
@@
 \subfloat[]{\label{fig:mocon}\includegraphics[width=0.45\textwidth]{MoO3_1L}}
-\caption[Refractive indices of \ce{MoO3}]{(a) Refractive indices of \ce{MoO3} Dashed line is n along $a$ axis while solid line is along $c$ axis.
+\caption[Refractive indices of \ce{MoO3}]{Refractive indices of \ce{MoO3}.
+(a) Refractive indices of \ce{MoO3} Dashed line is n along $a$ axis while solid line is along $c$ axis.
 (b) optical contrast mapping of 1L \ce{MoO3} on \ce{SiO2}-Si.
-The x axis is \ce{SiO2} thickness, y axis is wavelength.It is assumed that the incident light is polarized along c axis of \ce{MoO3}.}
+The $x$ axis is \ce{SiO2} thickness, $y$ axis is wavelength.
+It is assumed that the incident light is polarized along $c$ axis of \ce{MoO3}.}
 \label{fig:mofl}
@@
 \includegraphics[width=0.8\textwidth]{exf_moo3.jpg}
-\caption[TEM images of exfoliated \ce{MoO3}]{(a) TEM image and (b) HRTEM image of FL \ce{MoO3} obtained by liquid sonication method.}
+\caption[TEM images of exfoliated \ce{MoO3}]{TEM images of exfoliated \ce{MoO3}. (a) TEM image and (b) HRTEM image of FL \ce{MoO3} obtained by liquid sonication method.}
 \label{fig:motem}

### 2014-10-24 ch-tms/tms.tex
figure caption fixed, proof reading and introduction chapter done

@@
 \includegraphics[width=0.7\textwidth]{cs_sfig1_all}
-\caption[\ce{WO3} NW growth: OT]{Schematic diagrams of (a) tungsten power oxidization, (b) seeded growth of \ce{WO3} NW, and (c) sulfurization process.
+\caption[Schematic diagrams of tungsten power oxidization, seeded growth of \ce{WO3} NW, and sulfurization process.]{Schematic diagrams of (a) tungsten power oxidization, (b) seeded growth of \ce{WO3} NW, and (c) sulfurization process.
 (d) Chemical vapor deposition system temperature profile measured at ambient condition.
@@
 The NWs array grow slightly larger than the W seeds ($\sim$12 $\mu$m), mostly due to the elongation of NW.
-
 \begin{figure}[htb]
@@
 \includegraphics[width=0.7\textwidth]{ws2_sem_edx}
-\caption[Morphology and composition analysis on \ce{WO3}-\ce{WS2} NWs]{Morphology and composition analysis on the as-synthesized core-shell structures.
+\caption[Morphology and composition analysis on the as-synthesized \ce{WO3}-\ce{WS2} core-shell structures]{Morphology and composition analysis on the as-synthesized \ce{WO3}-\ce{WS2} core-shell structures.
 (a) SEM images showing the NWs almost retain their original shapes after sulfurization, and (b) EDX spectroscopy revealing the presence of sulfur element after sulfurization.}
@@
 \end{figure}
-
 The EDX spectrum in Fig.~\ref{fig:ch5ws2sem} revealed the presence of sulfur element, indicating the effectiveness of sulfurization.
@@
 This result as well as the SEM imaging indicates \ce{WO3} NWs could preserve some long range order after the sulfurization for 15 min at 750 \si{\degreeCelsius}.
-
 %fig xrd ws2 
@@
 \includegraphics[width=0.7\textwidth]{ws2_cs_xrd}
-\caption[XRD on core-shell NWs]{X-ray diffraction spectra before and after sulfurization. The reference spectra for $c$-W, 2H-\ce{WS2} and $m$-\ce{WO3} are included with some major peaks labeled.}
+\caption[X-ray diffraction spectra before and after sulfurization]{X-ray diffraction spectra before and after sulfurization.
+The reference spectra for $c$-W, 2H-\ce{WS2} and $m$-\ce{WO3} are included with some major peaks labeled.}
 \label{fig:ch5ws2xrd}
@@
 A comparison with the pre-sulfurization specimen (Fig.~\ref{fig:woseedtem2} on page~\pageref{fig:woseedtem2}) readily reveals the formation of core-shell morphology after sulfurization.
-The measured layer spacing is 6.4 \AA, slight larger than bulk 2H-\ce{WS2} of 6.16 \AA, but in good agreement with XRD results in Fig.~\ref{fig:ch5ws2xrd}.
+The measured layer spacing is 6.4 \si{\angstrom}, slight larger than bulk 2H-\ce{WS2} of 6.16 \si{\angstrom}, but in good agreement with XRD results in Fig.~\ref{fig:ch5ws2xrd}.
 The clear contrast in core region also prove the lattice structure of \ce{WO3} is not seriously distorted.
-
 % tem core shell layer
@@
 \includegraphics[width=0.9\textwidth]{ws2_coreshell_tem}
-\caption[TEM imaging on core-shell NWs: 1]{HRTEM imaging on one core-shell nanowire showing layer number changes.}
+\caption{HRTEM imaging on one core-shell nanowire showing layer number changes.}
 \label{fig:ch5ws2tem1}
@@
 \includegraphics[width=0.8\textwidth]{ws2_growth3}
-\caption[TEM imaging on core-shell NWs: 2]{HRTEM imaging on the tip area of one core-shell nanowire.}
+\caption{HRTEM imaging on the tip area of one core-shell nanowire.}
 \label{fig:ch5ws2tem3}
 \end{figure}
-
 As illustrated in Fig.~\ref{fig:ch5ws2tem4}, complicated \ce{WS2} encapsulation was observed on one tapered core-shell NW.
@@
 On some turning region, the \ce{WS2} seems penetrating into the body of primary \ce{WO3} NW.
-
 % coreshell tem
@@
 \includegraphics[width=0.8\textwidth]{ws2_growth4}
-\caption[TEM imaging on core-shell NWs: 3]{HRTEM imaging on one tapered core-shell nanowire showing fluctuation of layer numbers}
+\caption{HRTEM imaging on one tapered core-shell nanowire showing fluctuation of layer numbers}
 \label{fig:ch5ws2tem4}
@@
 It is worth mentioning that some interesting growth behavior around the void region, where a new \ce{WS2} layer pushing through the already formed \ce{WS2} ones, deviating from the diffusion growth model.
-
 % coreshell tem
@@
 \includegraphics[width=0.8\textwidth]{ws2_growth1}
-\caption[TEM imaging on core-shell NWs: 4]{HRTEM imaging on one core-shell nanowire showing consumed core.}
+\caption{HRTEM imaging on one core-shell nanowire showing consumed core.}
 \label{fig:ch5ws2tem2}
@@
 To perform TEM-Raman integrated study, the core-shell specimen was first dispersed into ethanol solution and then dipped onto polydimethylsiloxane (PDMS) support.
-A home-built micromanipulator with proble tip (tungsten, 100nm point radius, Micromaipulator) was used to pick up the core-shell NWs and transfer them onto TEM grids (Lacey C, 300 mesh, Cu, 01895-F Ted Pella, Inc) under 100x objective.
+A home-built micromanipulator with probe tip (tungsten, 100nm point radius, Micromaipulator) was used to pick up the core-shell NWs and transfer them onto TEM grids (Lacey C, 300 mesh, Cu, 01895-F Ted Pella, Inc) under 100X objective.
 The steps are visualized in Fig.~\ref{fig:ch5ws2trans}.
@@
 \includegraphics[width=0.5\textwidth]{ws2trans}
-\caption[Manipulating core-shell NWs]{Core-shell nanowires transfer steps.
+\caption[Core-shell nanowires transfer steps]{Core-shell nanowires transfer steps.
 (a) tungsten tip under X100 objective, (b) NWs dispersed onto PDMS, (c) one NW picked up using tungsten tip and (d) tranferred NW on TEM grid}
@@
 \end{figure}
-
 The transferred NWs were first examined using TEM to identify the \ce{WS2} layers configuration and the associated geometrical orientation.
@@
 \includegraphics[width=0.6\textwidth]{ws2map}
-\caption[Mapping core-shell NWs]{Core-shell nanowires mapping.
+\caption[Core-shell nanowires mapping]{Core-shell nanowires mapping.
 Optical image of one NW on TEM under (a) x100 magnification and (b) digital zoom-in view; (b) Low magnification and (d) high magnification TEM images on the same NW.}
@@
 \end{figure}
-
 Fig.~\ref{fig:ch5ws2ram}a-d depict typical \ce{WO3}-\ce{WS2} NWs used in TEM-Raman integrated study.
@@
 Theoretical investigation suggests assigning this mode as $B_{1u}$, the Davydov doublet of $A_{1g}$ mode.\cite{Ataca2012} And experimental study confirmed this $B_{1u}$ mode arise from structural disorder of \ce{WS2} layers, and the intensity ratio between $B_{1u}$ and $A_{1g}$ strongly depended on excitation wavelength.\cite{Staiger2012} This study observed $B_{1u}$ mode under 532 nm is much less prominent than that of 632 nm, in consistent with previous reports.\cite{Krause2009,Krause2009a}
-
 % fig Raman TEM
@@
 \includegraphics[width=0.9\textwidth]{ws2_tem_ram}
-\caption[TEM-Raman integrated characterization on core-shell NWs]{(a)-(d) HRTEM images on several NWs showing the \ce{WS2} wall number variation from one to about ten.
+\caption[TEM-Raman integrated characterization on core-shell NWs]{TEM-Raman integrated characterization on core-shell NWs.
+(a)-(d) HRTEM images on several NWs showing the \ce{WS2} wall number variation from one to about ten.
 (e) Raman spectra acquired from core-shell NWs supported on TEM grids, indicating a sharp contrast between the in-plane and out-of-plane vibrations.
@@
 \end{figure}
-
 Multi-peak Lorentzian fitting was also attempted on spectra shown in Fig.~\ref{fig:ch5ws2ram}e.
@@
 Multiple Raman spectra for each layer were averaged, as shown in Fig.~\ref{fig:ch5ws2ram}f.
-
 % fig Raman TEM
@@
 \includegraphics[width=0.4\textwidth]{ws2_peak_ratio}
-\caption[Multi-peak Lorentzian fitting on core-shell NWs]{Comparison of apparent peak ratio and de-convolution value.}
+\caption[Multi-peak Lorentzian fitting on core-shell NWs]{Multi-peak Lorentzian fitting on core-shell NWs. Comparison of apparent peak ratio and de-convolution value.}
 \label{fig:ch5ws2pr}
 \end{figure}
-
 The intensity ratio $I_{E/A}$ decreases monotonically with the increase of \ce{WS2} wall number, a similar trend as observed on 2D few layer \ce{WS2}.
@@
 
-PL was examined with core-shell NWs on insulating \ce{SiO2}-Si substrates.
+\Gls{pl} was examined with core-shell NWs on insulating \ce{SiO2}-Si substrates.
 A typical Raman spectrum from 160 to 6000 \si{cm^{-1}} is presented in Fig.~\ref{fig:ws2ramall}.
@@
 A broad PL peak was also observed with center at 628 nm and FWHM of 23 nm, corresponding to a photon energy of 1.974 eV with width of 72 meV.
-
 % ws2/wo3 on sio2,1 
@@
 \centering
-\includegraphics[width=0.75\textwidth]{ws2_sio2_all}
-\caption[Raman spectrum of \ce{WO3}-\ce{WS2} on \ce{SiO2}-Si 1]{Raman spectrum acquired on the middle spot of core-shell NW (inset) using 532 nm. The $x$ axis is in logarithmic scale.}
+\includegraphics[width=0.6\textwidth]{ws2_sio2_all}
+\caption{Raman spectrum acquired on the middle spot of core-shell NW (inset) using 532 nm. The $x$ axis is in logarithmic scale.}
 \label{fig:ws2ramall}
 \end{figure}
-
 Another feature is the presence of three peaks centering at 1860, 3695, and 5500 \si{cm^{-1}}, respectively, where the latter two is probably the secondary and third overtone of the first peak.
@@
 This comparison suggested there might be some enhancement mechanism from \ce{WS2} resonant Raman vibrations.
-
 \begin{figure}[htb]
@@
 \includegraphics[width=0.5\textwidth]{ws2_sio2_all_blue}
-\caption[Raman spectrum of \ce{WO3}-\ce{WS2} on \ce{SiO2}-Si 2]{Raman spectrum acquired on the middle spot of core-shell NW shown in the inset of Fig.~\ref{fig:ws2ramall}.}
+\caption{Raman spectrum acquired on the middle spot of core-shell NW shown in the inset of Fig.~\ref{fig:ws2ramall}.}
 \label{fig:ws2ramblue}
 \end{figure}
-
 Three Raman sites were chosen to probe possible layer variation using both 532 and 441 nm, with the naming displayed in the inset of Fig.~\ref{fig:ws2ramall}.
@@
 According to previous analysis, the apparent ratio between in-plane and out-of-plane vibration indicates site tip2 has multi-wall \ce{WS2}, and the other two possibly have few-walled \ce{WS2}.
-
 \begin{figure}[htb]
@@
 \subfloat[]{\label{fig:blue}\includegraphics[width=0.45\textwidth]{ws2_sio2_raman_blue}}
-\caption[Raman spectrum of \ce{WO3}-\ce{WS2} on \ce{SiO2}-Si 3]{Raman scattering from (a) 532 nm and (b) 441 nm excitation scanned along the core-shell NW.}
+\caption{Raman scattering from (a) 532 nm and (b) 441 nm excitation scanned along the core-shell NW.}
 \label{fig:ws2ram3site}
 \end{figure}
-
 This predication is confirmed by the associated PL measurement as displayed in Fig.~\ref{fig:ws2plgreen}.
 Strong luminescent peaks were found at site mid and tip1, and an extremely weak from site tip2.
-The PL peaks centered at 1958 and 1934 meV for mid and tip1, respectively.
+The PL peaks centered at 1.958 and 1.934 eV for mid and tip1, respectively.
 The second and third order peaks also show up on all three Raman sites.
-
 \begin{figure}[htb]

### 2014-10-24 ch-tms/tmspart.tex
figure caption fixed, proof reading and introduction chapter done

@@
 
-The geometrical symmetry groups of WS2 NT.\cite{Milosevic2000} 
-The basis/lattice vectors $a_1$ and $a_2$ are defined in transition metal plane with equal length $a_0 \approx 3$ \AA.
+The geometrical symmetry groups of WS2 NT.\cite{Milosevic2000} The basis/lattice vectors $a_1$ and $a_2$ are defined in transition metal plane with equal length $a_0 \approx 3$ \si{\angstrom}.
 This monolayered sheet can be rolled up to form a tubular structure when the chiral/translation vector $c = n_1a_1 + n_2a_2$ becomes the circumference of the tube.
@@
 \begin{equation}
-d = \frac{\mid c \mid}{\pi} = \frac{a_0}{\pi}\sqrt{n_1^2 + n_1n_2 + n_2^2}
+d = \frac{\mid c \mid}{\pi} = \frac{a_0}{\pi}\sqrt{n_1^2 + n_1n_2 + n_2^2}.
 \end{equation}
-Notice $a_1 \cdot a_2 = a_1a_2 \cos\pi/3$, where the cosine times 2 is unit. 
-In analog with carbon nanotube, chiral angle $\theta$ is given by
+Notice $a_1 \cdot a_2 = a_1a_2 \cos\pi/3$, where the cosine times 2 is unit. In analog with carbon nanotube, chiral angle $\theta$ is given by
 \begin{equation}
-\theta = \tan^{-1}\frac{\sqrt{3}n_2}{2n_1 + n_2}
+\theta = \tan^{-1}\frac{\sqrt{3}n_2}{2n_1 + n_2}.
 \end{equation}
-
-Chiral angles from the interval $[0,pi/6]$ is sufficient for all possible tubes.
-Tubes $(n,0)$ with zero chiral angle are named zigzag, tubes $(n,n)$ with $\pi/6$ chiral angle are armchair, whereas all others are referred as chiral ones with $\theta \in (0,pi/6)$.
+Chiral angles from the interval $[0,\pi/6]$ is sufficient for all possible tubes.
+Tubes $(n,0)$ with zero chiral angle are named zigzag, tubes $(n,n)$ with $\pi/6$ chiral angle are armchair, whereas all others are referred as chiral ones with $\theta \in (0,\pi/6)$.
 \begin{figure}[htb]
 \centering
-\includegraphics[width=0.8\textwidth]{ws2_tube1}
+\includegraphics[width=0.7\textwidth]{ws2_tube1}
 \caption[\ce{WS2} nanotube rolling]{\ce{WS2} nanotube rolling}
@@
 Except the aforementioned methods, another important reaction in CVD domain is
-\begin{equation}\label{eq:mclns}
-\cee{MoCl5(WCl6) + S \rightarrow MoS2(WS2) + S2Cl2}.
-\end{equation}
 \begin{align}
@@
 \citeauthor{Zhang2013h} synthesized \ce{WS2} on sapphire (0001) using \ce{WO3} powder and sulfur as precursor under 900 \si{\degreeCelsius}.\cite{Zhang2013h} Ar slightly mixed with \ce{H2} is used to tailor the shape of \ce{WS2} flakes.
-It was found the source substrate distance plays an important role in determining the morphology of the as-grown flakes.\footnote{There is a lattice mismatch between \ce{Al2O3} (4.785 \AA) and \ce{WS2} (3.153 \AA)} The edge termination is not well studied.
+It was found the source substrate distance plays an important role in determining the morphology of the as-grown flakes.\footnote{There is a lattice mismatch between \ce{Al2O3} (4.785 \si{\angstrom}) and \ce{WS2} (3.153 \si{\angstrom})} The edge termination is not well studied.
 Raman spectra indicate a universal down-shift of $A_{1g}$ peak (1L from 418 \si{cm^{-1}} on \ce{SiO2}-Si to 416.4 \si{cm^{-1}} on sapphire).
@@
 \centering
-\caption{TMDC FL methods summary}\label{tab:tmsgrowth}
+\caption{TMDC few layer growth methods summary}\label{tab:tmsgrowth}
 {\footnotesize
@@
 \centering
-\caption[Lattices vibration of \ce{MS2}]{Lattices vibration of \ce{MS2}, adopted from Ref.\cite{Molina-Sanchez2011}}\label{tab:tmslattice}
+\caption[Lattices vibration of \ce{MS2}]{Lattices vibration of \ce{MS2}, reproduced from Ref.\cite{Molina-Sanchez2011}}\label{tab:tmslattice}
 \begin{tabular}{lcccc}
@@
 \includegraphics[width=0.7\textwidth]{ws2_ramsch}
-\caption[\ce{MS2} vibration symmetry]{\ce{MS2} vibration symmetry in bulk and monalyer, adopted from REF\cite{Ghorbani-asl}}
+\caption[\ce{MS2} vibration symmetry]{\ce{MS2} vibration symmetry in bulk and monolayer, adopted from Ref.\cite{Ghorbani-asl}}
 \label{fig:ws2ramsch}
@@
   \centering
-  \caption{\ce{WS2} symmetry assignment}  \label{tbl:ws2raman}
+  \caption{\ce{WS2} Raman symmetry assignment}  \label{tbl:ws2raman}
   \begin{tabular}{ccccc}

### 2014-10-24 ch-wox/ch-wox.tex
figure caption fixed, proof reading and introduction chapter done

@@
 Metallic tungsten powders were utilized as source materials in this work.
-Four kinds of W powder were used in total, as summarized in Table.~\ref{tab:powder}.
+Four kinds of W powder were used in total, as summarized in Table~\ref{tab:powder}.
 Two growth configurations were explored, namely ordinary transport and seeded growth.
@@
 The cleaning procedures have been elucidated on page.~\pageref{ch2sub}.
-The boat was then loaded into reaction chamber in a way that the powder source was placed in the center of heating zone, and the substrate upstream end was aligned at 6.5 in.\footnote{As defined in Fig.~\ref{fig:wogrow}} After pumping down, 1 sccm \ce{O2} and 10 sccm Ar were admitted into the chamber, respectively, after which the overall pressure read approximately 110 mTorr.
+The boat was then loaded into reaction chamber in a way that the powder source was placed in the center of heating zone, and the substrate upstream end was aligned at 6.5 inch.\footnote{As defined in Fig.~\ref{fig:wogrow}} After pumping down, 1 \gls{sccm} \ce{O2} and 10 sccm Ar were admitted into the chamber, respectively, after which the overall pressure read approximately 110 mTorr.
 The temperature ramped up to 1000 \si{\degreeCelsius} in 30 min and lasted for 4 h, and subsequently the apparatus was allowed to naturally cool down to room temperature.
@@
 \includegraphics[width=0.7\textwidth]{CVD_and_temp.jpg}
-\caption[\ce{WO3} NW growth: OT]{Chemical vapor system and its temperature profile.
+\caption[\ce{WO3} NW CVD growth]{\ce{WO3} NW CVD growth and the temperature profile.
 The nominal NWs growth temperature were estimated according to the interpolation data.
-The zero inch location is defined at the upstream edge of furnace.}
+Zero inch location is defined at the upstream edge of furnace.}
 \label{fig:wogrow}
@@
 Another possible reason is the presence of foreign elements in each W powders.
-As indicated by the certificate of analysis from corresponding vendors (attached in Appendix), carbon, nickel, iron and sodium can amount up to tens of ppm in low purity W sources.
+As indicated by the certificate of analysis from corresponding vendors, carbon, nickel, iron and sodium can amount up to tens of ppm in low purity W sources.
 
@@
 The diffraction peaks were carefully indexed and the deposition was identified as two phases of sodium tungsten oxides and one phase of tungsten oxide as indicated on Fig.~\ref{fig:nawoxsemedx}d.
-The two sodium tungsten oxide phases are the triclinic \ce{Na5W_{14}O_{44}} phase (ICDD PDF 04-012-4449, \emph{a}=7.2740 \AA, \emph{b}=7.2911 \AA, \emph{c}=18.5510 \AA, $\alpha$=96.37$^\circ$, $\beta$=90.89$^\circ$, $\gamma$=119.65$^\circ$) and the triclinic \ce{Na2W4O_{13}} phase (ICDD PDF 04-012-7108, \emph{a}=11.1630 \AA, \emph{b}=3.8940 \AA, \emph{c}=8.2550 \AA, $\alpha$=90.60$^\circ$, $\beta$=131.36$^\circ$, $\gamma$=79.70$^\circ$).
-The tungsten oxide is the monoclinic \ce{WO3} phase (ICDD PDF 01-083-0950, \emph{a}=7.30084 \AA, \emph{b}=7.53889 \AA, \emph{c}=7.6896 \AA, $\beta$=90.89$^\circ$).
+The two sodium tungsten oxide phases are the triclinic \ce{Na5W_{14}O_{44}} phase (ICDD PDF 04-012-4449, \emph{a}=7.2740 \si{\angstrom}, \emph{b}=7.2911 \si{\angstrom}, \emph{c}=18.5510 \si{\angstrom}, $\alpha$=96.37$^\circ$, $\beta$=90.89$^\circ$, $\gamma$=119.65$^\circ$) and the triclinic \ce{Na2W4O_{13}} phase (ICDD PDF 04-012-7108, \emph{a}=11.1630 \si{\angstrom}, \emph{b}=3.8940 \si{\angstrom}, \emph{c}=8.2550 \si{\angstrom}, $\alpha$=90.60$^\circ$, $\beta$=131.36$^\circ$, $\gamma$=79.70$^\circ$).
+The tungsten oxide is the monoclinic \ce{WO3} phase (ICDD PDF 01-083-0950, \emph{a}=7.30084 \si{\angstrom}, \emph{b}=7.53889 \si{\angstrom}, \emph{c}=7.6896 \si{\angstrom}, $\beta$=90.89$^\circ$).
 
@@
 \includegraphics[width=0.7\textwidth]{nawox_semedx.jpg}
-\caption[SEM and EDX on \ce{Na_xWO3}]{SEM images of (a) dense array of as-synthesized ultra-long nanowires on SiO2-Si substrate and (b) rectangular microplates grow among the nanowires.
+\caption[SEM and EDX on \ce{Na_xWO3}]{SEM images of (a) dense array of as-synthesized ultra-long nanowires on \ce{SiO2}-Si substrate and (b) rectangular microplates grow among the nanowires.
 (c) EDS and (d) XRD spectra showing the chemical compositions and phases of the deposition.}
@@
 The long edge of the plate was identified as parallel to the (010) plane and the short edge parallel to the ($\bar{1}01$) plane.
-From XRD spectra, the long edge of \ce{Na2W4O_{13}} plate can be figured out as the $\vec{c}$ axis ([001]) and the short edge is along the $\vec{b}$ axis ([010]).
+From XRD spectra, the long edge of \ce{Na2W4O_{13}} plate can be figured out as the $\vec{c}$ axis and the short edge is along the $\vec{b}$ axis.
 Fig.~\ref{fig:nawoxtem}i shows the plate structure also consisted of W, Na, and O and no other impurities were detected.
@@
 \includegraphics[width=0.8\textwidth]{nawox_tem.jpg}
-\caption[SEM images of morphology evolution]{TEM images at low-magnification, HRTEM images, and EDS spectra of a \ce{Na5W_{14}O_{44}} NW (a, b, c), a \ce{WO3} NW (d, e, f), and a \ce{Na2W4O_{13}} microplate (g, h, i).
-}
+\caption[TEM analyses on sodium tungsten oxide sample]{TEM images at low-magnification, HRTEM images, and EDS spectra of a \ce{Na5W_{14}O_{44}} NW (a, b, c), a \ce{WO3} NW (d, e, f), and a \ce{Na2W4O_{13}} microplate (g, h, i).}
 \label{fig:nawoxtem}
@@
 \includegraphics[width=0.7\textwidth]{nawox_raman_series}
-\caption[Raman spectra on \ce{Na_xWO3}]{Micro-Raman spectra of (a) microplates matching the reported peak positions of the \ce{Na2W4O_{13}} phase, and (b) nanowires with comparisons to the reported major peak positions of \ce{WO3} (shown by black line) and \ce{Na2W4O_{13}} (shown by red line) phases.}
+\caption[Raman spectra on \ce{Na_xWO3}]{Raman spectra of (a) microplates matching the reported peak positions of the \ce{Na2W4O_{13}} phase, and (b) nanowires with comparisons to the reported major peak positions of \ce{WO3} (shown by black line) and \ce{Na2W4O_{13}} (shown by red line) phases.}
 \label{fig:nawoxram}
@@
 \end{equation}
-where $R$ is tungsten-oxygen bond length in \si{\angstrom}, and $\nu$ is Raman stretching wavenumber in \si{cm^{-1}}.\cite{Hardcastle1995} The standard deviation of estimating \ce{W-O} bond distance from Raman stretching wavenumber is $\pm0.034$ \si{\angstrom}.
+where $R$ is tungsten-oxygen bond length in \si{\angstrom}, and $\nu$ is Raman stretching wavenumber in \si{cm^{-1}}.\cite{Hardcastle1995} The standard deviation of estimating \ce{W-O} bond distance from Raman stretching wavenumber is $\pm 0.034$ \si{\angstrom}.
 The observed Raman peaks of \ce{Na5W_{14}O_{44}} phase lies at 965, 943, 913, 808, 786, 778, 765, 695 and 107 \si{cm^{-1}}.
@@
 \includegraphics[width=0.6\textwidth]{naxwo_ramfit}
-\caption[\ce{Na5W_{14}O_{44}} Raman fitting]{Multi-peak Lorentzian fitting on two major peaks region of \ce{Na5W_{14}O_{44}}.
+\caption[Multi-peak Lorentzian fitting on \ce{Na5W_{14}O_{44}}]{Multi-peak Lorentzian fitting on two major peaks region of \ce{Na5W_{14}O_{44}}.
 The peaks sum height difference is caused by different baseline value adopted in each fitting.}
@@
 These results verified the Na content was mainly from the 3N W powders.
-In the OT growth experiments, the W source was first slowly oxidized at 1000 \si{\degreeCelsius} with 1 sccm \ce{O2} and the oxidized source was then evaporated producing \ce{WO3} and other substoichiometric tungsten oxide vapors.
+In the OT growth experiments, the W source was first slowly oxidized at 1000 \si{\degreeCelsius} with 1 sccm \ce{O2} and the oxidized source was then evaporated producing \ce{WO3} and other sub-stoichiometric tungsten oxide vapors.
 The tungsten oxide vapors produced this way were limited by the slow oxidation, as indicated by
@@
 \includegraphics[width=0.8\textwidth]{nawox_edx_series.jpg}
-\caption[Photograph of a series of 3N growth]{(a) Photograph of a series of specimens grown in the same reaction chamber with the increase of growth number showing different growth zones and corresponding morphology changes.
+\caption[Photograph of a series of specimens grown]{(a) Photograph of a series of specimens grown in the same reaction chamber with the increase of growth number showing different growth zones and corresponding morphology changes.
 (b) Change of Na/W ratios with the increase of growth number at different growth zones.}
@@
 \includegraphics[width=0.8\textwidth]{nawox_sem_series.jpg}
-\caption[SEM images of morphology evolution]{Low magnification SEM images of the NWs at different growth zones showing morphology changes with the increase of growth number.
+\caption[SEM images of morphology evolution]{SEM images of morphology evolution of the NWs at different growth zones showing morphology changes with the increase of growth number.
 The insets show detailed structures of the NWs.}
@@
 Therefore, the vapors from both the source materials and the local residue deposition will result in an enhanced growth of nanowires (Fig.~\ref{fig:nawoxsch}b).
-To prove this hypothesis, control experiments were performed utilizing a quartz tube used multiple times previously (e.g., a growth number of 9).
+To prove this hypothesis, control experiments were performed utilizing a quartz tube used multiple times previously (e.g.
+a growth number of 9).
 The experiments were carried out without any source materials while other growth parameters remain the same.
@@
 \includegraphics[width=0.8\textwidth]{wox_xrd_series}
-\caption[XRD spectra evolution of \ce{Na_xWO3} growth]{XRD spectra of the as-synthesized specimen with the increase of growth number from 1 to 5.}
+\caption{XRD spectra of the as-synthesized specimen with the increase of growth number from 1 to 5.}
 \label{fig:nawoxxrd}
@@
 These results are consistent with the SEM observation (Fig.~\ref{fig:nawoxsemall}) and the composition change from the EDX measurements (Fig.~\ref{fig:nawoxser}b).
-Details XRD indices assignment is summarized in Table~\ref{tbl:xrd}.
+Details XRD indices assignment is summarized in Table~\ref{tbl:wo3xrd}.
 
@@
 \centering
-\caption{XRD assignments}\label{tbl:xrd}
+\caption{XRD assignments of specimens in \ce{Na_xWO3} growth}\label{tbl:wo3xrd}
 \begin{tabular}{llllll}
@@
 The \ce{Na5W14O44} phase was further confirmed by a XRD scanning from 4 to 10 degree in $2\theta/\Omega$ configuration.
-As shown in Fig.~\ref{fig:naxrdlow}, two peaks at 4.84$^{\circ}$ and 9.65$^{\circ}$ were well resolved, corresponding a lattice spacing of 18.25 and 9.16 \AA, respectively.
+As shown in Fig.~\ref{fig:naxrdlow}, two peaks at 4.84$^{\circ}$ and 9.65$^{\circ}$ were well resolved, corresponding a lattice spacing of 18.25 and 9.16 \si{\angstrom}, respectively.
 This compares favorably with both HRTEM analysis (Fig.~\ref{fig:nawoxtem}e) and ICDD PDF 04-012-4449 database reference.
@@
 \includegraphics[width=0.5\textwidth]{naxwo_xrd_low}
-\caption[low angle scan of XRD pattern]{Low angle scan of XRD pattern on the as-grown sodium tungsten oxide sample}
+\caption{Low angle scan of XRD pattern on the as-grown sodium tungsten oxide sample}
 \label{fig:naxrdlow}
@@
 \subfloat[]{\label{fig:nadrs}\includegraphics[width=0.45\textwidth]{uvvis_naxwo2}}
-\caption[UV-Vis and DRS of \ce{Na5W14O44} NWs on quartz]{(a) Optical transmission and (b) diffuse reflection spectra of \ce{Na5W14O44} NWs on quartz.}
+\caption[UV-Vis and \gls{drs} of \ce{Na5W14O44} NWs on quartz]{UV-Vis and DRS of \ce{Na5W14O44} NWs on quartz: (a) Optical transmission and (b) diffuse reflection spectra.}
 \label{fig:ch3naxuvvis}
@@
 One difference is the DRS increased from 1300 nm to 400nm, presumably due to the inverse scattering intensity with NW dimension of 300 nm.
-The calculated absorption was shown in Fig.~\ref{fig:nauv}, suggesting a bandgap edge at about 380 nm.
-This is consistent with the observed white sample color; however, the \ce{Na5W14O44} should be metallic in theory.
+The calculated absorption was shown in Fig.~\ref{fig:nauv}, suggesting an energy gap edge at about 380 nm.
+This is consistent with the observed white sample color; however, the conductivity of \ce{Na5W14O44} has not been investigated experimentally.
+Based on the electron sum rule, the sodium tungsten oxide can be cast into \ce{Na5W_1^{5+}W_{13}^{6+}O44}, which indicates the W atom state is quite close to that in \ce{WO3}.
 More investigation is needed to vigorously determined the electronic transport properties of \ce{Na5W14O44} NW.
-\textbf{Ordinary transport growth using other W powders}
+
+\subsubsection{Ordinary transport growth using other W powders}
 % 3N5 powder growth
@@
 
-\subsection{Tungsten Oxides: Seeded Growth }\label{sec:sgfg}
+\subsection{Tungsten Oxides: Seeded Growth}\label{sec:sgfg}
 
@@
 \includegraphics[width=0.7\textwidth]{JAP-2column_Fig1.jpg}
-\caption[W powder oxidation: temperature effect]{SEM graphs of 99.9\% (3N) tungsten powder oxidization at different temperatures of a) 500 \si{\degreeCelsius}, b) 600 \si{\degreeCelsius}, c) 650 \si{\degreeCelsius}, d) 750 \si{\degreeCelsius}, showing the optimal temperature for local formation of nanowires is between 600-650 \si{\degreeCelsius}.
+\caption[W powder oxidation: temperature effect]{W powder oxidation: temperature effect.
+SEM graphs of 99.9\% (3N) tungsten powder oxidization at different temperatures of a) 500 \si{\degreeCelsius}, b) 600 \si{\degreeCelsius}, c) 650 \si{\degreeCelsius}, d) 750 \si{\degreeCelsius}, showing the optimal temperature for local formation of nanowires is between 600-650 \si{\degreeCelsius}.
 Oxygen flow rate is 1 sccm.}
@@
 \includegraphics[width=0.7\textwidth]{JAP-2column_Fig3.jpg}
-\caption[W powder oxidation: size effect]{SEM graphs illustrating the oxidization of four different size of tungsten powders at 600~\si{\degreeCelsius} and 1 sccm oxygen flow.
+\caption[W powder oxidation: size effect]{W powder oxidation: size effect.
+SEM graphs illustrating the oxidization of four different size of tungsten powders at 600~\si{\degreeCelsius} and 1 sccm oxygen flow.
 a) 17 $\mu$m, b) 32 $\mu$m, c) 3.3 $\mu$m, d) 1.5 $\mu$m.}
@@
 \includegraphics[width=0.7\textwidth]{JAP-2column_Fig2.jpg}
-\caption[W powder oxidation: oxygen pressure]{SEM graphs of 3N tungsten powder oxidization at 600 \si{\degreeCelsius} under different rates of oxygen flow: a) 1 sccm, b) 2 sccm, c) 3 sccm, d) 10 sccm.
+\caption[W powder oxidation: oxygen pressure]{W powder oxidation: oxygen pressure.
+SEM graphs of 3N tungsten powder oxidization at 600 \si{\degreeCelsius} under different rates of oxygen flow: a) 1 sccm, b) 2 sccm, c) 3 sccm, d) 10 sccm.
 The oxygen partial pressures were 13 mTorr, 23 mTorr, 32 mTorr, and 82 mTorr, respectively with background pressure subtracted.}
@@
 \subfloat[]{\label{fig:sgb}\includegraphics[width=0.4\textwidth]{wox_sg_b.jpg}}
-\caption[Characterization of seeded growth \ce{WO3}: SEM]{Characterizations of seeded growth.
+\caption[SEM characterization of \ce{WO3}seeded growth]{SEM characterization of \ce{WO3}seeded growth.
 (a) SEM graphs of \ce{WO3} NWs on \ce{SiO2}/Si substrate.
-(b) A high magnification view showing uniform NW growth and close-up view of one NW.
-}
+(b) A high magnification view showing uniform NW growth and close-up view of one NW.}
 \label{fig:woseedsem}
@@
 \includegraphics[width=0.5\textwidth]{wo3_seed_edx}
-\caption[Composition analysis on seeded growth \ce{WO3} NWs]{EDX spectroscopy on seeded growth \ce{WO3} NWs.}
+\caption[Composition analysis on seeded growth \ce{WO3} NWs]{Composition analysis on seeded growth \ce{WO3} NWs. EDX spectroscopy on seeded growth \ce{WO3} NWs.}
 \label{fig:woedx}
@@
 \subfloat[]{\label{fig:sgram}\includegraphics[width=0.45\textwidth]{wox_raman_1}}
-\caption[Characterization of seeded growth \ce{WO3}: XRD and Raman]{ (a) XRD pattern of as-prepared sample indicating the \ce{WO3} phase and the presence of metallic core.
+\caption[Characterization of seeded growth \ce{WO3}: XRD and Raman]{Characterization of seeded growth \ce{WO3}: XRD and Raman.
+(a) XRD pattern of as-prepared sample indicating the \ce{WO3} phase and the presence of metallic core.
 (b) Raman spectrum on NWs region showing the feature of \ce{WO3}.}
@@
 \includegraphics[width=0.9\textwidth]{JAP-2column_Fig5major.jpg}
-\caption[Characterization of \ce{WO3}: TEM]{TEM graphs of as-prepared NWs.
-(a) TEM image of one nanowire with diameter about 40 nm.
-(b) HRTEM images showing the spacing is 0.38 nm, corresponding to (002) plane distance.}
+\caption[Characterization of \ce{WO3}: TEM]{TEM Characterization of \ce{WO3}: (a) TEM image of one nanowire with diameter about 40 nm, and (b) HRTEM images showing the spacing is 0.38 nm, corresponding to (002) plane distance.}
 \label{fig:woseedtem1}
@@
 \includegraphics[width=0.9\textwidth]{JAP-2column_Fig5minor.jpg}
-\caption[Characterization of \ce{WO3}: TEM cont]{TEM graphs of as-prepared NWs.
-(a) TEM image of one nanowire, the diameter is about 70 nm.
-(b) HRTEM images showing the spacing is 0.379 nm, corresponding to (002) plane distance.}
+\caption[Characterization of \ce{WO3}: TEM cont]{TEM Characterization of \ce{WO3}: (a) TEM image of one nanowire, the diameter is about 70 nm, and (b) HRTEM images showing the spacing is 0.379 nm, corresponding to (002) plane distance.}
 \label{fig:woseedtem2}
@@
 Oxidation occurring at boundaries and defects are preferred thermodynamically.\cite{You2010} Compressive strain will gradually accumulate at the tungsten oxide/tungsten interface, which might limit the diffusion rate of oxygen at temperature lower than 500 \si{\degreeCelsius}.\cite{tungsten1999} At elevated temperature, cracks will primarily occur, as observed in Fig.~\ref{fig:pdtemp}.
-When heated up, tungsten and the oxide shell will probably relax the strain by converting into sub-stoichiometric NWs, a similar process as suggested by \citeauthor{Klinke2005} in the chemically induced strain growth of tungsten oxide NWs.\cite{Klinke2005} It is worth noting that tungsten oxide nanowires could also formed when \ce{WO3} is reduced.\cite{Sarin1975} The elongation of \ce{WOx} is thermodynamically favorable during the conversion from metallic tungsten to tungsten oxide as well.
+When heated up, tungsten and the oxide shell will probably relax the strain by converting into sub-stoichiometric NWs, a similar process as suggested by \citeauthor{Klinke2005} in the chemically induced strain growth of tungsten oxide NWs.\cite{Klinke2005} It is worth noting that tungsten oxide nanowires could also formed when \ce{WO3} is reduced.\cite{Sarin1975} The elongation of \ce{WO_x} is thermodynamically favorable during the conversion from metallic tungsten to tungsten oxide as well.
 Local evaporation-condensation process might also contribute to the formation of NWs on tungsten powder.
@@
 \subfloat[]{\label{fig:fg2}\includegraphics[width=0.45\textwidth]{wox_flow2}}
-\caption[Characterization of flow growth \ce{WO3}: SEM]{ (a) Low magnification SEM image showing dense array of NWs (b) High magnification SEM image of NWs grew out of layer and close-up view on individual wire.}
+\caption[Characterization of flow growth \ce{WO3}: SEM]{Characterization of flow growth \ce{WO3}: SEM.
+(a) Low magnification SEM image showing dense array of NWs (b) High magnification SEM image of NWs grew out of layer and close-up view on individual wire.}
 \label{fig:wogrowsf}
@@
 
-%TEM to be done on D8.
-% fg tem
-%\begin{figure}[htb]
-%\centering
-%\includegraphics[width=0.8\textwidth]{wo3_tem.jpg}
-%\caption[Flow growth of \ce{wo3}:TEM]{TEM characterization of FG \ce{WO3} NWs. }
-%\label{fig:fgtem}
-%\end{figure}
-to be added, NaOH WO3 results.
+%to be added, NaOH WO3 results.
 

### 2014-10-24 ch-wox/part1.tex
figure caption fixed, proof reading and introduction chapter done

@@
 Intense research interest was rekindled by the discovery of \gls{ec} effect in \citeyear{Granqvist1993}.\cite{Granqvist1993}  Nano-engineering \ce{WO_x} bring more possibility and flexibility to its already rich characteristics, therefore resulting in research efforts spanning multiple fields of scientific community.
-Besides smart window based on EC effect, \ce{WO_x} is also well investigated for several other significant applications: photoelectrochemical cell for solar energy conversion and storage, photocatalysis for hydrogen evolution reaction, chemical and biological sensing based on gasochromic effect.
+Besides smart window based on \gls{ec} effect, \ce{WO_x} is also well investigated for several other significant applications: photoelectrochemical cell for solar energy conversion and storage, photocatalysis for hydrogen evolution reaction, chemical and biological sensing based on gasochromic effect.
 In addition, a few young fields are not thoroughly explored: field emission, optical storage, thermo-electricity, ferro-electricity, and superconductivity.
 
-In this chapter, a literature review on \ce{WO_x} and \ce{Na_xWO3} will be given first, with focus on technological application, crystal structure and electronic properties and synthesis approaches.
+In this chapter, a literature review on \ce{WO_x} and \ce{Na_xWO3} will be given first, with focus on technological application, crystal structure, and synthesis approaches.
 Then the growth methods in this study are presented, followed by corresponding characterization and discussion.
@@
 \end{align}
-Similar scenarios occurs in the gasochromic effect.
+Similar scenario occurs in the gasochromic effect.
 Two models, double injection and color center, arise to account for the coloration upon exposure to certain gases.
@@
 The author believe the resolution to a large extent depends on the phase transitions, as discussed in Section.~\ref{sec:wonawo}.
+
+A thin film example on the valency number, color center density. some calculation on doping, uv-vis results on the thin film.
+
 \fi
@@
 Tungsten trioxide (\ce{WO3}) crystallizes in multiple phases.
-The basic building block is \ce{WO6} octahedra.\footnote{Tungsten, with its electronic configuration as \ce{(Xe)4f^{14}5d^{4}6s^{2}}, has empty 5d and 6s orbitals in its +6 oxidation state.} \ce{WO3} crystal structure consists of \ce{WO6} octahedra joined at their corners, which may be considered as a perovskite structure of \ce{CaTiO3} with all \ce{Ca^{2+}} sites vacant.
+The basic building block is \ce{WO6} octahedra.\footnote{Tungsten, with its electronic configuration as \ce{(Xe)4f^{14}5d^{4}6s^{2}}, has empty 5d and 6s orbitals in its $+6$ oxidation state.} \ce{WO3} crystal structure consists of \ce{WO6} octahedra joined at their corners, which may be considered as a perovskite structure of \ce{CaTiO3} with all \ce{Ca^{2+}} sites vacant.
 A representative lattice structure is illustrated in Fig.~\ref{fig:wo3oct}.
 These distorted \ce{WO6} octahedra adapt different tilting angles in different phases and edge-sharing octahedra also arise.
-The temperature-dependent phase transition and corresponding lattice constants in bulk form is summarized in Table.~\ref{tab:wo3phase}.\cite{Zheng2011} And a firm assignation of space group to monoclinic phases are still in debate.\cite{Chatten2005} It is noticed that the lattice parameters obtained via \emph{ab initio} calculation closely match the experimental values.\cite{Migas2010a} The phase transition scenarios in nanostructured \ce{WO3} are supposed to be more sophisticated.
-Within Gibbs-Thomson framework, one can generally expect lower transition temperature than their bulk counterparts due to enhanced surface energy.
-Temperature-dependent Raman spectroscopy provided support for this deduction.\cite{Boulova2002}
-
 % wo3 phases
@@
 \end{table}
+The temperature-dependent phase transition and corresponding lattice constants in bulk form is summarized in Table~\ref{tab:wo3phase}.\cite{Zheng2011} And a firm assignation of space group to monoclinic phases are still in debate.\cite{Chatten2005} It is noticed that the lattice parameters obtained via \emph{ab initio} calculation closely match the experimental values.\cite{Migas2010a} The phase transition scenarios in nanostructured \ce{WO3} are supposed to be more sophisticated.
+Within Gibbs-Thomson framework, one can generally expect lower transition temperature than their bulk counterparts due to enhanced surface energy.
+Temperature-dependent Raman spectroscopy provided support for this deduction.\cite{Boulova2002}
 
@@
 
-\ce{WO3} and optical electric field enhancement.
+Besides \ce{WO3}, tungsten oxide exists in a series of sub-stoichiometric states.
 The \ce{W_nO_{3n-1}} ($n \geq 2$) exhibit $\{ 001 \}$ CS structure.
-Chemical formula corresponding to n=2, 3, 4, 5 and 6 are \ce{W2O5=WO_{2.5}}, \ce{W3O8=W_{2.67}}, \ce{W4O_{11}=WO_{2.75}}, \ce{W5O_{14}=WO_{2.8}}, and \ce{W6O_{17}=WO_{2.83}}, which indicates the existence of a oxygen deficient plane at every n row.
-Actually the value x in \ce{WO_x} could almost continuously vary within a range of 2.5 to 3.
+Chemical formula corresponding to n=2, 3, 4, 5 and 6 are \ce{W2O5=WO_{2.5}}, \ce{W3O8=W_{2.67}}, \ce{W4O_{11}=WO_{2.75}}, \ce{W5O_{14}=WO_{2.8}}, and \ce{W6O_{17}=WO_{2.83}}, which indicates the existence of a oxygen deficient plane at every $n$ row.
+Actually the value $x$ in \ce{WO_x} could almost continuously vary within a range of 2.5 to 3.
 \ce{W_{18}O_{49}=\ce{WO_{2.72}}} is an exception without $\{ 001 \}$ CS structure.
 Moreover, the oxygen deficient planes could extend along directions other than $\{ 001 \}$.
-For instance, the $\{ 102 \}$ CS planes appears in \ce{WO_x} where x is within 2.93 to 2.98, and  the $\{ 103 \}$ CS planes for x within 2.87 to 2.93.\cite{Sloan1999} The enhancement arises from the structure composed of a conductive layer and an insulating layer that are laminated therein.\cite{Shingaya2013} In \ce{WO_x} nanorods, the oxygen deficient planes are conductive, each having atomic thickness and separated by several nm \ce{WO3}.
+For instance, the $\{ 102 \}$ CS planes appears in \ce{WO_x} where $x$ is within 2.93 to 2.98, and  the $\{ 103 \}$ CS planes for $x$ within 2.87 to 2.93.\cite{Sloan1999} The enhancement arises from the structure composed of a conductive layer and an insulating layer that are laminated therein.\cite{Shingaya2013} In \ce{WO_x} nanorods, the oxygen deficient planes are conductive, each having atomic thickness and separated by several nm of \ce{WO3} layers.
 Localized surface plasmons could possibly exist on these conductive planes.
-Therefore \gls{sers} applies and single molecule Raman scattering using individual tungsten oxide nanorod has been demonstrated.
-\citeauthor{Shingaya2013} also synthesized \ce{WS2}-\ce{WO_x} core-shell structures and found similar Raman scattering enhancement.
-The x value is estimated by the Raman spectra peaks.\cite{Shingaya2013}(Data not shown in patent)
+Therefore \gls{sers} applies and single molecule Raman scattering using individual tungsten oxide nanorod has been demonstrated.\cite{Shingaya2013}
 
@@
 In contrast, organometallic decomposition is another feasible method.
-\citeauthor{Pol2005} obtained \ce{W18O49} nanorods by thermal dissociation of \ce{WO(OMe)4} at 700 \si{\degreeCelsius}, and \ce{WO3} by further annealing at 500 \si{\degreeCelsius} in air atmosphere.\cite{Pol2005}
-
-Spray pyrolysis is a typical aerosol-assisted \gls{cvd} technique.
+\citeauthor{Pol2005} obtained \ce{W18O49} nanorods by thermal dissociation of \ce{WO(OMe)4} at 700 \si{\degreeCelsius}, and \ce{WO3} by further annealing at 500 \si{\degreeCelsius} in air atmosphere.\cite{Pol2005} Spray pyrolysis is a typical aerosol-assisted \gls{cvd} technique.
 Typical process flow is: the precursor solution is pumped to an atomizer, and then sprayed through the carrier gas as a fine mist of very small droplets onto heated substrates.
@@
 \centering
-\caption{Tungsten Oxides Growth and Application}\label{tab:wox}
+\caption{Summary of tungsten oxides growth methods}\label{tab:wox}
 {\footnotesize

### 2014-10-24 figure_table.tex
figure caption fixed, proof reading and introduction chapter done

@@
 \label{fig:mosisem}
+\end{figure}
+
+\begin{figure}[htb]
+\centering
+\includegraphics[width=0.8\textwidth]{CVD_and_temp_MoO3.jpg}
+\caption[CVD system]{Chemical vapor system and its temperature profile.The length of heating zone is 6 inches.
+On the horizontal axis of temperature, zero inch is defined at the upstream edge of furnace.The triangular labels $\blacktriangledown$ were measured points at ambient pressure.The nominal substrates temperature were estimated from interpolation data.}
+\label{fig:s1}
 \end{figure}
@@
 
-\begin{figure}[htb]
-\centering
-\includegraphics[width=0.8\textwidth]{CVD_and_temp_MoO3.jpg}
-\caption[CVD system]{Chemical vapor system and its temperature profile.The length of heating zone is 6 inches.
-On the horizontal axis of temperature, zero inch is defined at the upstream edge of furnace.The triangular labels $\blacktriangledown$ were measured points at ambient pressure.The nominal substrates temperature were estimated from interpolation data.}
-\label{fig:s1}
-\end{figure}
-
 \begin{table}[htb]
@@
 
+\begin{table}[htb]
+\centering
+\caption{Symmetry assignment of \ce{WO3}}\label{tab:woram}
+\begin{tabular}{cccc}
+\toprule
+Raman shift (\si{cm^{-1}}) & Symmetry &  Ref.   & Remarks   \\
+\midrule
+131(m)   & $B_{2g}$    &           & $T_c$    \ce{WO3} 
+\bottomrule
+\end{tabular}
+vw-very weak; w-weak; m-medium; s-strong; vs-very strong
+\end{table}
+
 %\newgeometry{margin=1in}
@@
 (cf. )
-up-scaling capability, band edge smeared; major bands situated at
+up-scaling capability, band edge smeared; major bands situated at, 
+bypassing a limitation, held back by a restriction, discern,  nanoscopy, run in parallel tracks, line of thought take shape, delve into, devise, commotion, fruition, foundation was laid, one variant, ponder, passivated, halt, lack of progress, p-dope FaN in a controlled manner, transcend, theoretical description, and experimental implementation,
 

### 2014-10-28 ch-intro/ch-intro.tex
camera ready

@@
 \centering
-\includegraphics[width=0.6\textwidth]{blackbody1}
+\includegraphics[width=0.5\textwidth]{blackbody1}
 \caption{Spectral radiance of blackbody at 0, 50 and 100 \si{\degreeCelsius}.}
@@
 \item low cost ion electrolyte of poor electron mobility;
-\item high yield growth method of \ce{WO3} and integration with other manufacturing process;
-\item and life cycle $> 10^5$ for long time outdoor usage.
+\item high yield growth method of \ce{WO3} and integration with other manufacturing process; and 
+\item life cycle $> 10^5$ for long time outdoor usage.
 \end{itemize}
@@
 \centering
-\includegraphics[width=0.7\textwidth]{woxnhe.jpg}
+\includegraphics[width=0.6\textwidth]{woxnhe.jpg}
 \caption[Band position of \ce{WO3} versus NHE]{Band position of \ce{WO3} in contact with aqueous electrolyte at pH 1. Reproduced from Ref.\cite{Gratzel2001}}
@@
 
-Specifically/in regarding to the contents of this study, electrochromic applications based on \gls{tmo} nanowires will benefit from the reduced diffusion depth by eliminating the deficiency of ions accumulation accounted in amorphous oxide thin film devices, which, in turn, leads to shorter response time and higher coloration efficiency.\cite{Huang2008a,Scherer2012} And photocatalytic applications using \gls{tmo} nanostructures could harvest the huge surface area on which unsaturated bond reside, thereby enabling a much higher efficiency.\cite{Mills1993,Merki2011,Chen2011b}
+In regarding to the contents of this study, electrochromic applications based on \gls{tmo} nanowires will benefit from the reduced diffusion depth by eliminating the deficiency of ions accumulation accounted in amorphous oxide thin film devices, which, in turn, leads to shorter response time and higher coloration efficiency.\cite{Huang2008a,Scherer2012} And photocatalytic applications using \gls{tmo} nanostructures could harvest the huge surface area on which unsaturated bond reside, thereby enabling a much higher efficiency.\cite{Mills1993,Merki2011,Chen2011b}
 

### 2014-10-28 ch-moox/mooptics.tex
camera ready

--- 2014-10-24 ch-moox/moox.tex
@@
-% git version control added 012614
-\chapter{Vapor-Solid-Solid Growth of MoO$_3$}
-
-\section{Introduction}
-
-In this work, a new growth mechanism of molybdenum oxide (\ce{MoO3}) 1D structures was discovered, highlighted by \ce{MoO3} long nanobelts and micro-scale towers.
-The samples were synthesized using a group of alkaline metal based catalysts, including \ce{NaOH}, \ce{KI}, and \ce{Na2CO3}.
-In contrast to the sole axial growth found in the conventional catalyst-assisted growth, two different growth modes were observed for the \ce{MoO3} 1D growth here: transverse growth and axial growth.
-In the transverse mode, the 1D structures grow perpendicularly to the catalyst-deposition interface with catalyst particles on the side surfaces; whereas in the axial mode, the crystal grows along the catalyst-deposition axis.
-The growth modes were explained by a modified \gls{vss} mechanism, and factors that affect the growth were explored in details.
-
-The remaining sections are organized as following: a brief review on previous studies of \ce{MoO3} is given first, followed is the synthesis method in this dissertation.
-Emphasis will be placed on morphological and crystal structure characterization of 1D \ce{MoO3} nanostructures, and the verification of proposed VSS mechanism.
-This chapter is concluded with a summary of VSS growth and some preliminary results of morphology controlled \ce{MoO3} nanostructures.
-
-\subsection{Properties and Applications of Molybdenum Oxide}
-
-Molybdenum oxide (\ce{MoO3}) crystallizes in three phases, orthorhombic $\alpha$-\ce{MoO3}, monoclinic $\beta$-\ce{MoO3} and the metastable hexagonal h-\ce{MoO3}.\citep{Deb1968,Fibers2007} $\alpha$-\ce{MoO3} phase (hereafter \ce{MoO3}) exhibits anisotropic structure with strong bonding along [001] and [100] direction while van der Waals interaction along [010] direction.\cite{He2003} Due to this unique structure, \ce{MoO3} was found to have several important properties and a wide range of technological applications, such as electrochromism and photochromism,\cite{Yao1992} lubricants,\cite{Sheehan1996} photocatalysts,\cite{Chen2010} and gas sensor, including \ce{CO},\cite{Comini2005} \ce{NO2},\cite{Taurino2006} \ce{H2}\cite{Sha2009} and ethanol.\cite{Choopun} Moreover, other features arise when nanoscale \ce{MoO3} is specifically prepared, e.g., field emission.\citep{Li2002d,Zhou2003b}  As a layered hosting material, \ce{MoO3} can be further modified by intercalating with alkaline ions\citep{Spahr1995,Li2006b,Hu2011} and even divalent ion.\cite{Sian2005} This structural richness have enabled improved performance in Li-ion\cite{Mai2007} and sodium-ion battery.\cite{Hariharan2013} In combination with \ce{TiO2} forming a core-shell structure, these nanoparitcles are reported to lower the photon absorption energy of \ce{TiO2}.\cite{Elder2000} When combined with Ag as layered structure, transparent conducting behavior was observed.\cite{Nguyen2012} In addition, \ce{MoO3} is a good precursor for preparing other useful materials, such as \ce{MoS2} fullerene\cite{Li2003c} and few layer \ce{MoS2}.\cite{Lin2012} It will also be an important member of the van der Waals heterostructures.\cite{Geim2013}
-
-The coordination number of Mo in \ce{MoO3} is six, so usually \ce{MoO6} octahedra are considered as the building blocks.
-As shown in Fig.~\ref{fig:mo3model}, the layered structure consisting of zig-zag rows of edge-sharing \ce{MoO6} octahedra, while the rows are mutually connected by corners.
-\begin{figure}[htb]
-\centering
-\includegraphics[width=0.5\textwidth]{MoO3_model}
-\caption[\ce{MoO3} crystal model]{\ce{MoO3} crystal model.}
-\label{fig:mo3model}
-\end{figure}
-While considering the fact that four of the six surrounding O atom are at distances from 1.67 to 1.95 \AA, while the remaining two are as far as 2.25 and 2.33 \AA, \ce{MoO3} could also be considered as built up of chains of \ce{MoO4} tetrahedra connected by the sharing of two oxygen corners with two neighbouring tetrahedra in $c$ axis.
-The infinite chains of \ce{MoO4} tetrahedra from half-layers in the $ac$ plane.
-Two half-layers, which are stapled along $b$ axis, build up one \ce{MoO3} layer.\cite{Itoh2001a} This view stresses that the \ce{MoO6} octahedra are rather distorted.
-%A brief summary of crystallography, band structure and dielectric function is listed in Appendix.
-
-It is known that a series of molybdate compound forms when alkali metal ions are incorporated into the \ce{MoO3} lattice, and the structures are summarized in Table~\ref{tab:naxmow}.
-Due to the weak cation-oxygen bonding, alkali metal cations only introduce small perturbations into the energies of \ce{Mo-O} matrix in comparison to cations of other elements.
-And no mixing of vibrations of the cationic sublattices with that of \ce{Mo-O} lattices is anticipated.
-So the structural features of \ce{Mo-O} polyhedra are dominating factors affecting the vibration frequencies and thermodynamic values of the molybdates.\cite{Fomichev1992}
-
-\begin{table}[htb]
-\centering
-\caption{Crystal structures of alkali metal molybdates and tungstates}\label{tab:naxmow}
-\begin{tabular}{llr}
-\toprule
-formula & structure  &  \\
-\midrule
-\ce{A2O}:\ce{MO3}\textsuperscript{\emph{a}} & isolated tetrahedral \ce{MO4} anions& \\
-\ce{A2O}:\ce{2MO3} & chain-type anions of \ce{MO4} and \ce{MO6} & \\
-\ce{A2O}:\ce{3MO3} & chain-type anions of \ce{MO5} and \ce{MO6} & \\
-\ce{A2O}:\ce{4MO3} & chain-type anions of \ce{MO6} & \\
-\bottomrule
-
-\textsuperscript{\emph{a}} A = Li, Na, K, Rb, Cs; M = Mo, W;
-\end{tabular}
-\end{table}
-
-Raman band assignment for \ce{A2MO4} is well grounded.
-Alkali metal cations with octahedral coordination occur below 230 cm$^{-1}$.
-For \ce{A2M_nO_{3n+1}}, exact assignment is not available yet due to the complicated \ce{MO6} octahedra.
-Molybdenum bronze also exhibits intriguing features, for instance, \gls{cdw} states\footnote{In \gls{cdw} states, conductivity is non-Ohmic above a threshold electric field.} was found in blue bronze \ce{K_{0.3}MoO3}, which can be prepared by electrolytic reduction of \ce{K2MoO4} and \ce{MoO3} melt.\cite{Dumas1983} \ce{K_{0.3}MoO3} stay as monoclinic phase at room temperature, with lattice parameter $a=18.249$ \AA, $b=7.561$ \AA, $c=9.856$ \AA, and $\beta=117.54^{\circ}$, and exhibits a semiconductor-to-metal transition at 180 K.
-Electrical transport measurements yield an highly anisotropic ratio of DC conductivities of 1:10:1000.
-Along this high conducting axis, metallic reflection behavior is confirmed by optical measurements.
-Therefore, this blue bronze $\ce{K_{0.3}MoO3}$ is known as quasi-1D metal.\cite{Sing1999}
-
-\subsection{Synthesis Review of Molybdenum Oxide}
-
-Researchers have been exploring a variety of methods to synthesized different \ce{MoO3} nanostructures.
-Only a brief introduction will be given here, since these efforts has been well documented in several review articles.\cite{He2003} Most of these methods can be categorized into two groups: solution-based hydrothermal procedures \citep{Li2002b,Xia2006,Li2006a,Camacho-Bragado2006} and chemical vapor transport and deposition approaches.\citep{Zeng1998,Li2002c,Li2002d,Zhou2003b,Fibers2007,Yan2009}.
-Both methods have its own merits.
-Hydrothermal process usually need lower temperature(\textless 300 \si{\degreeCelsius}), but the duration is usually long and requires several post-growth processing steps; whereas vapor deposition demands relatively high temperature (\textgreater 500 \si{\degreeCelsius}) yet with a shorter time.
-Both methods are scalable for industrial applications.
-However the hydrothermal treatment seems to allow more  nanostructures control than does the vapor deposition method.
-Nanobelts,\cite{Li2002b} helical nanosheets, nanoflowers, prims-like rods\cite{Li2006a} and nanoribbons\cite{Camacho-Bragado2006} were obtained by the former one while nanoflakes,\cite{Chen2009} nanobelts\cite{Hu2009} and nanowires\citep{Zhou2003b,Chen2011b} dominated the product morphology for the latter one.
-The assistance of Au catalyst in vapor deposition only altered the orientation\cite{Yan2009} or served as preferred nucleation sites\cite{Cai2011} without producing new \ce{MoO3} structures.
-\citeauthor{Chithambararaj2013} prepared hexagonal \ce{MoO3} nanocrystal via hydrothermal method and demonstrated the photodegradation of methylene blue (MB) under visible light.\cite{Chithambararaj2013} The efficiency dependence on catalysis/dye ratio, light intensity and temperature was studied.
-h-\ce{MoO3} was mostly synthesized using solution methods, where \ce{NH4+} and \ce{OH-} were possible structure directing and stable agents.
-The band gap of h-\ce{MoO3} estimated from diffusion reflection spectrum is $2.8\sim3.0$ eV.
-Hexagonal phase of \ce{MoO3} is readily identified by the XRD pattern (strong peak at $2\theta=20^{\circ}$).
-It is worth noting that in spite of these numerous growth of \ce{MoO3}, reports on catalytic growth are still scarce.
-
-\section{Experimental}\label{sec:grow}
-
-The reactants used in this study were listed in Table~\ref{tb:mosource}. All reactants were used as received without further processing.
-
-\begin{table}[htb]
-\centering
-\caption{Reactants list of \ce{MoO3} growth}\label{tb:mosource}
-\begin{tabular}{lcccr}
-\toprule
-Material & Stock No & LOT &Purity & Vendor\\
-\midrule
-\ce{NaOH}     & S318-500 & 070241 & 99.8\% & Fisher Scientific \\
-\ce{NaI}      & 11665 & K11W054 & 99.9\% &  Alfa Aesar \\
-\ce{KI}        & 42857 & H06Z051 & 99.9\% &  Alfa Aesar \\
-\ce{Na2CO3}    & 33377 & 114X012 & 99.95\% &  Alfa Aesar \\
-\ce{Molybdenum}& 00932 & I07S024 & 99.9\% &  Alfa Aesar\\
-\bottomrule
-\end{tabular}
-\end{table}
-
-Silicon substrates was first cleaned according to the procedure in Sec.~\ref{ch2sub} on page~\pageref{ch2sub}.
-To apply the catalysts, 54 $\mu$L 10 mM \ce{NaOH} (or \ce{KI}, \ce{Na2CO3}) was drop-cast onto clean substrates and then naturally left dry in a convection hood.
-Other alkaline ions-containing substrates, such as glass (Fisher Scientific, microscope slide, 12-549) and indium tin oxide (ITO) coated glass (Delta Technologies, 25\si{\ohm}), were cleaned by the same routine except the absence of plasma cleaning and subsequent aqueous solution dipping.
-Mica was cleaved right before growth without other treatment.
-
-In a typical synthesis run (Fig.~\ref{fig:mooxgrowth}), about 2 g molybdenum powders were loaded into the uniform heating zone and the sealed chamber was first pumped down to 10 mTorr.
-Then oxygen flow varying between 0.1 sccm to 10 sccm (standard cubic centimeter per minute) was admitted from upstream inlet.
-With 10 sccm UHP Ar as carrier gas, the overall pressure reached about 200 mTorr.
-The heating temperature was ramped up to 800 \si{\degreeCelsius} in 30 min and lasted for 15 to 120 min.
-Then the heating power was turned off and the chamber was allowed to naturally cool down to room temperature.
-The substrate was placed in downstream location where the temperature was about 350 to 650 \si{\degreeCelsius} according to open air temperature profile.
-Non-catalytic growth shares the same procedure except the NaOH treatment.
-
-\section{Results and Discussion on Molybdenum Oxide}\label{sec:result}
-In this section, the growth of \ce{MoO3} on bare Si substrates was presented first, followed by catalytic growth, both of which were characterized by SEM, XRD, TEM and EDX.
-Then the catalytic growth mechanism was investigated using \ce{NaOH} treated Si substrate.
-The growth mechanism was probed using two series of control experiments.
-Then a growth model was proposed and verified.
-In the end, this growth model was applied onto other substrates with alkaline metal ions, and various \ce{MoO3} nanostructures were produced.
-
-\subsection{Non-catalyst Growth}\label{sec:nonsi}
-
-The oxidization of Mo starts at 500 \si{\degreeCelsius}, and \ce{MoO3} vapor pressure begins to increase rapidly above 700 \si{\degreeCelsius}.\cite{Margrave1967} The melting point of \ce{MoO3} is reported as 795 \si{\degreeCelsius}.
-Based on these data, the growth was designed with parameters listed in Table~\ref{tab:mooxsi}.
-It is worth mentioning that these parameters are selected and optimized from a wide range of combinations.
-When the influence of one parameter is studied, the others are fixed, following the standard practice in controlled experiments.
-%growth parameter
-\begin{table}[htb]
-\centering
-\caption{Growth conditions of \ce{MoO3} on Si}\label{tab:mooxsi}
-\begin{tabular}{lcccr}
-\toprule
-&&&\multicolumn{2}{c}{Flow (sccm)} \\
-\cmidrule(l){4-5}
- & Temperature $T_h$ (\si{\degreeCelsius}) & Pressure (mTorr) & Ar & \ce{O2}  \\
-\midrule
-Typical values  & 800    & 200 & 10 & 10  \\
-\bottomrule
-\end{tabular}
-\end{table}
-
-The growth layout is schematically shown in Fig.~\ref{fig:mooxgrowth}.
-Notice that on the horizontal axis of temperature, zero inch is defined at the upstream edge of furnace.
-To facilitate discussion and provide a tight context, the author define the position of substrate as the coordinate of its upper-stream edge along this temperature axis, i.e., the substrate location is 7 in in Fig.~\ref{fig:mooxgrowth}.
-The usual length of Si substrate is 1 in.
-When positioned at 7 in, it is then located in a temperature zone of $650 \sim 350$ \si{\degreeCelsius}.
-% cvd layout
-\begin{figure}[htb]
-\centering
-\includegraphics[width=0.7\textwidth]{CVD_and_temp_MoO3.jpg}
-\caption[CVD growth setup of \ce{MoO3}]{CVD growth setup of \ce{MoO3}.
-The triangular labels $\blacktriangledown$ were measured points at ambient environment.
-The nominal substrates temperature were estimated from interpolation data.}
-\label{fig:mooxgrowth}
-\end{figure}
-
-From previous works in our group,\cite{predeep2011} it was found that with $T_h = 600$ \si{\degreeCelsius} and substrate placed at 6.5 in, microflakes grew at the high temperature edge of Si, suggesting the nucleation already started.\footnote{in 020510 batch} When flow of oxygen was gradually reduced, diminished size of micro-flake was observed at the same location of substrates.
-This results indicated the rate-determining step is diffusion when oxygen flow was in the range of 2 sccm to 0.5 sccm.
-It was also found the deposition amount on a particular location of the substrate is not linearly proportional to the growth time, \emph{i.e.}, the growth at upper stream edge first increase then decrease.
-This is not surprising when considering the 3D temperature field in chamber requires some time to become synchronized as depicted in Fig.~\ref{fig:mooxgrowth}.
-Using conditions in Table~\ref{tab:mooxsi} and 2 h growth, this study observed the typical micro-flakes morphologies as shown in Fig.~\ref{fig:mosisem}.
-Most flakes exhibit rectangular shape, with average thickness of one micron, standard deviation $\sigma_D=0.34 \mu$m.
-% sem in (31210-31510) batches
-\begin{figure}[htb]
-\centering
-\subfloat[]{\label{fig:mosem1}\includegraphics[width=0.4\textwidth]{mosemsi_a}}\hspace{0.04\textwidth}
-\subfloat[]{\label{fig:mosem2}\includegraphics[width=0.4\textwidth]{mosemsi_b}}
-\caption[Representative morphologies of \ce{MoO3} on Si]{Representative morphologies of \ce{MoO3} on Si: (a) low magnification and (b) high magnification SEM images of representative depositions of \ce{MoO3} on Si for non-catalytic growth.}
-\label{fig:mosisem}
-\end{figure}
-
-As shown in Fig.~\ref{fig:mooxch}, the crystal structure and phase of the as-synthesized specimen were examined by XRD and Raman.
-The XRD pattern (Fig.~\ref{fig:moxrd}) is readily indexed to the orthorhombic phase of \ce{MoO3} (ICDD PDF 05-0508, \emph{a}=3.9628 \AA, \emph{b}=13.855 \AA, \emph{c}=3.6964 \AA).
-The space group is $D_{2h}^{16}(Pbnm)$.
-This crystal structure is indeed a unique example among transition metal oxides, representing a transitional stage between tetrahedra and octahedral coordination.\cite{Itoh2001a} The strongest peak index is (110), suggesting the orientation of \ce{MoO3} is not parallel to the substrate, which is consistent with the morphology displayed in Fig.~\ref{fig:mosem1}.
-In contrast, a different XRD peak pattern is observed in Sec.~\ref{sec:nasi}, where the catalytic growth occurs.
-% xrd raman
-\begin{figure}[htb]
-\centering
-\subfloat[]{\label{fig:moxrd}\includegraphics[width=0.45\textwidth]{xrd_moo3}}\hspace{0.04\textwidth}
-\subfloat[]{\label{fig:moram}\includegraphics[width=0.45\textwidth]{raman_moo3}}
-\caption[Crystalline phase characterization of \ce{MoO3} on Si]{Crystalline phase characterization of \ce{MoO3} on Si: (a) XRD pattern and (b) Raman spectrum of typical \ce{MoO3} on Si, $\lambda_{ex} = 532$ nm.}
-\label{fig:mooxch}
-\end{figure}
-The Raman spectrum of the as-synthesized specimen also closely matches \ce{MoO3} features in previous studies.\cite{Dixit1986,Silveira2012} During m-Raman measurement, the laser spot was carefully focused onto the plates and several inspections on different positions were observed to ensure the reproductivity of spectra data.
-As shown in Fig.~\ref{fig:moram}, 14 distinct bands were well resolved.
-The 284 \si{cm^{-1}} peak represents the wagging mode for double bond \ce{O=Mo=O}.
-The 337 and 380  \si{cm^{-1}} peaks are assigned to \ce{O-Mo-O} bending and scissoring modes.
-The 199 \si{cm^{-1}} peak and two other weaker peaks at 218 and 247 \si{cm^{-1}} represent \ce{O=Mo=O} $B_{2g}$ twist, $A_g$ chain mode and \ce{O=Mo=O} $B_{3g}$ twist mode, respectively.
-The 667 \si{cm^{-1}} peak is assigned to triply coordinated oxygen stretching model resulting from edge-shared oxygen in common to three octahedral.
-The 819 \si{cm^{-1}} peak is from doubly coordinated oxygen stretching mode arising from corner-shared oxygen between two octahedral.
-The 996 \si{cm^{-1}} peak comes from unshared oxygen stretching mode.\cite{Siciliano2009} The assignment is summarized in Table~\ref{tab:moram}.
-% raman assign
-\begin{table}[htb]
-\centering
-\caption{Experimental Raman peaks assignment of \ce{MoO3} on Si.\cite{Eda1992,Siciliano2009}}\label{tab:moram}
-\begin{tabular}{llcll}
-\toprule
-this work(\si{cm^{-1}}) & Sym.  &    & Assignment &   \\
-\midrule
-117      & $B_{2g}$    &           & $T_c$  & RCM  \\
-129      & $B_{3g}$    &           & $T_c$  & RCM  \\
-158      & $A_g/B_{1g}$&           & $T_b$  & RCM  \\
-199      & $B_{2g}$    & $\tau$    & \ce{O=Mo=O}  & twist  \\
-218      & $A_g$       &           & $R_c$     & RCM  \\
-247      & $B_{3g}$    & $\tau$    & \ce{O=Mo=O}  & twist  \\
-284      & $B_{2g}$    &           & \ce{O=Mo=O}  & wag  \\
-292      & $B_{3g}$     & $\delta$ & \ce{O=Mo=O}  & wag  \\
-337      & $A_g,B_{1g}$ & $\delta$ & \ce{O-Mo-O} & bend  \\
-380      & $B_{1g}$     & $\delta$ & \ce{O-Mo-O}  & scissor  \\
-474      & $A_g$        & $\nu_{as}$ & \ce{O-Mo-O}  & stretch,bend  \\
-667      & $B_{2g},B_{3g}$ & $\nu_{as}$  & \ce{O-Mo-O}  & stretch  \\
-819      & $A_g$        & $\nu_{as}$  & \ce{O=Mo}  & stretch  \\
-996      & $A_g$         & $\nu_{as}$  & \ce{O=Mo}  & stretch  \\
-\bottomrule
-\end{tabular}
-\end{table}
-
-\subsection{Catalyst-assisted Growth}\label{sec:naohsi}
-
-All growth time of samples prepared in Sec.~\ref{sec:naohsi} were 2 h, the same as in Sec.~\ref{sec:nonsi}.
-The only difference in growth conditions from Sec.~\ref{sec:nonsi} is the Si substrate treatment.
-When NaOH is applied onto Si, the deposition morphologies change significantly.
-Fig.~\ref{fig:ch4sem2by3} shows a comparison of the morphology difference between the non-catalyst growth (Fig.~\ref{fig:ch4sem2by3}a) and the catalyst-assisted growth (Fig.~\ref{fig:ch4sem2by3}b-f) revealed by SEM.
-The non-catalyst growth morphology has been discussed from Fig.~\ref{fig:mosisem} on page~\pageref{fig:mosisem}.
-Several different structures emerge when catalyst is applied, such as nanobelts in Fig.~\ref{fig:ch4sem2by3}d with length up to hundreds of microns, and microtowers in Fig.~\ref{fig:ch4sem2by3}f with diameter around 10 $\mu$m.
-
-% sem
-\begin{figure}[htb]
-\centering
-\includegraphics[width=0.9\textwidth]{MoO3_SEM_a.jpg}
-\caption[SEM imaging on \ce{MoO3} catalytic growth]{SEM imaging on \ce{MoO3} catalytic growth.
-Effect of alkaline metal-based catalysts on the morphology of \ce{MoO3} depositions: (a) SEM image of rectangular nanoplates grown without catalysts.
-(b-f) SEM images of different morphologies grown with NaOH catalysts: (b) nanobelts grown on top of dense array of nanoplates,(c) close-up view of the forked nanoplates from an area indicated by the square in Fig.~\ref{fig:ch4sem2by3}, (d) long nanobelts, (e) side-view of ultra-long microbelts, and (f) side-view of microtowers.
-Insets show detailed features of different \ce{MoO3} structures.}
-\label{fig:ch4sem2by3}
-\end{figure}
-
-The crystal structures of the as-synthesized specimens were characterized with X-ray diffraction (XRD) for the non-catalyst growth (Fig.~\ref{fig:ch4tem3by3}a) and catalyst-assisted growth (Fig.~\ref{fig:ch4tem3by3}b).
-The calculated lattice parameters and standard database value (ICDD PDF 05-0508) matches favorably, as listed in Table~\ref{tab:ch4xrd}.
-No other phases were found from XRD spectra for both specimens.
-This result indicates that if there were any catalyst phases present in the catalyst-assisted specimen, they must be of extremely low amount as compared to that of the \ce{MoO3} phase, presumably below the detection limit.
-% xrd 
-\begin{table}[htb]
-\centering
-\caption{Lattice parameters of \ce{MoO3} derived from XRD}\label{tab:ch4xrd}
-\begin{tabular}{lccc}
-\toprule
-           & $a$ (\AA) & $b$ (\AA) & $c$ (\AA)   \\
-\midrule
-Non-catalytic growth  & 3.963    & 13.882 & 3.701  \\
-Catalytic growth  & 3.967    & 13.865 & 3.701  \\
-PDF 05-0508       & 3.9628    & 13.855 & 3.6964  \\
-\bottomrule
-\end{tabular}
-\end{table}
-
-The XRD pattern of catalyst-assisted growth shown in Fig.~\ref{fig:ch4tem3by3}b is dominated by the (0$k$0) family peaks, showing a different preferred orientation from the non-catalytic growth.
-The reason will be discussed in Sec.~\ref{sec:nasi}.
-
-% tem
-\begin{figure}[htb]
-\centering
-\includegraphics[width=0.8\textwidth]{MoO3_TEM_XRD.jpg}
-\caption[XRD and TEM on \ce{MoO3} catalytic growth]{XRD and TEM on \ce{MoO3} catalytic growth.
-XRD spectra of (a) a specimen grown without catalysts and (b) a specimen grown with NaOH catalysts.
-(c) Low-magnification TEM image and (d) HRTEM image of nanoplate grown without catalyst.
-Low-magnification TEM images of (e) forked nanoplate, (f) nanobelt, and (h) microtower, and (g) HRTEM image of nanobelt.
-Insets show SAED patterns of different \ce{MoO3} 1D structures}
-\label{fig:ch4tem3by3}
-\end{figure}
-
-Fig.~\ref{fig:ch4tem3by3}c shows low magnification TEM image of a rectangular nanoplate grown without catalysts and the SAED pattern.
-The nanoplate was exfoliated by ultra-sonication in acetone solution to obtain high-resolution TEM (HRTEM) image, hence the nanoplate was broken into fragments.
-The SAED pattern in [010] axis and the HRTEM image (Fig.~\ref{fig:ch4tem3by3}d) show the nanoplate has a (010) top surface and two orthogonal edges along [100] and [001], respectively.
-For the catalyst-assisted growth, Fig.~\ref{fig:ch4tem3by3}e and Fig.~\ref{fig:ch4tem3by3}f-g confirm both the forked nanoplate and the nanobelt have a (010) top surface and a growth direction of [001], while Fig.~\ref{fig:ch4tem3by3}h reveals the microtower grow with (010) layers stacking along a [010] direction.
-Lattice measurements in Fig.~\ref{fig:ch4tem3by3}d and g indicate a planar distance of 0.38 nm for (100) planes and 0.36 nm for (001) planes.
-These values are slightly smaller than the standard data for $\alpha$-\ce{MoO3} and the results from XRD measurements.
-This deviation in lattice parameters may arise from the error in TEM measurements and the lattice distortion from the electron beam irradiation.\cite{Wang2004b} These results indicate that all the as-synthesized 1D structures have a layered structure.
-Raman measurement on the catalytic growth sample revealed similar \ce{MoO3} bands, as already displayed in Fig.~\ref{fig:mooxch} on page~\pageref{fig:mooxch}.
-
-\subsection{Growth Mechanism Study}\label{sec:nasi}
-
-To provide a proper context, \gls{vls} process is brief introduced.
-\gls{vls} is first proposed by Wagner,\cite{Wagner1964} and further developed by \citeauthor{Givargizov1975}.\cite{Givargizov1975} This method has become an important strategy for synthesizing 1D nanostructures.\cite{Lieber1998} Conventionally, a liquid eutectic droplet is formed by catalyst itself or by alloying with the growth material, acting as a trap of growth species.
-The growth is initialized by supersaturation of the liquid alloy and subsequent precipitation at the solid-liquid interface.
-The choice of catalyst usually is among the several noble metals since they are physically active but chemically stable or inert in most growth scenarios.
-The growth materials span a wide range including group IV,\cite{Hochbaum2005} group III-V,\citep{Dalacu2013, Xiao2012, Dubrovskii2011} group II-VI,\cite{Hao2006} and some metal oxides, such as \ce{ZnO},\citep{Huang2001a,Ramgir2010} \ce{MgO},\citep{HEUER1967, Nagashima2007} \ce{SiO2},\cite{Pan2002} and \ce{TiO2},\cite{Zhuge2012} to name a few.
-The catalysts can be Au, Pd, Pt, Ni,\cite{Xiao2012} Ti, Ga,\cite{Pan2002} and even KI.
-
-Understanding the interaction between liquid droplet and the solid interface allows for a rich engineering space to fine tune the geometry and structures of the as-grown nanostructures.
-For instances, the diameter of Si nanowires (NWs) can be controlled by laser ablated catalyst\cite{Morales1998} or well-defined Au nanoparticles.\cite{Cui2001b} Under proper conditions, axial modulation can produce nanowire superlattices from group IV and III-V materials.\citep{Gudiksen2002,Bjork2002}  Radial composition modulation have also been demonstrated by selectively suppressing VLS process, providing a robust routine for homogeneous or heterogeneous core-shell structures.\cite{Lauhon2002a}
-
-Previous study in our group has found that \ce{MoO3} deposition on ITO glass exhibits new morphologies that are not observed on Si substrates, yet the mechanism is not well investigated.\cite{predeep2011} Based on the \gls{vls} process, it is known that a eutectic state is the key to promote preferred growth direction.
-A list of composition difference between glass and Si substrate shows the extra elements of Na, K, Ca, \emph{etc}.
-Since the concentration of Na is highest among these extra elements, it is most likely to induce the new morphology growth.
-A literature search indeed shows that there exists a Na-Mo-O phase diagram as shown in Fig.~\ref{fig:ch4pd}.\cite{Hoermann1929} Notice the phases of the Na-Mo-O system can be written as \ce{Na2O.nMoO3}, where n = 1, 2, 3, and 4.
-
-%phase diagram
-\begin{figure}[htb]
-\centering
-\includegraphics[width=0.5\textwidth]{moo3_pdsmall}
-\caption[Phase diagram of \ce{Na2MoO4} and \ce{MoO3}]{Phase diagram of \ce{Na2MoO4} and \ce{MoO3} reproduced from Ref.~\cite{Hoermann1929}}
-\label{fig:ch4pd}
-\end{figure}
-
-Based on this phase diagram and the growth conditions adopted in this study, it is predicted that the overall reactions occur in the following sequences.
-First, Mo powder is oxidized and \ce{MoO3} vapor is produced and transported to downstream by Ar carrier gas.
-Then NaOH reacts with incoming \ce{MoO3} according to Formula~\ref{eq:pd}.
-\begin{subequations}\label{eq:pd}
-\begin{align}
-\cee{NaOH(l) + MoO3(g) &\rightarrow Na2MoO4(l) + H2O(g)\\
-Na2MoO4 + nMoO3   &\rightarrow Na2O.(n + 1)MoO3}
-\end{align}
-\end{subequations}
-The melting point of \ce{Na2MoO4} is 687 \si{\degreeCelsius}.
-Based on the open air temperature profile (Fig.~\ref{fig:mooxgrowth}), the substrate is located in temperature zone between 650 and 350 \si{\degreeCelsius}.
-The actual temperature distribution during growth is different from ambient measurement due to the pressure change and thermal conduction along the Si substrate.
-It is difficult to acquire the accurate values along the substrate; however, by considering the flow rate, the actual temperature will be higher than predicted by open air measurement.\cite{Subannajui2010} The melting of \ce{Na2MoO4} is highly possible when taking into account of its size as well.\cite{Bruggemann1997} The continuous supply of \ce{MoO3} growth species will push the phase evolution towards high \ce{MoO3} molar ratio end, with $n$ in \ce{Na2O.nMoO3} increasing from 1 to 4.
-Each site of \ce{Na2MoO4} will continue absorb incoming \ce{MoO3}, forming a swelling droplet.
-\ce{MoO3} will precipitate from these seeds when a critical supersaturation concentration is reached, which is about 75\% according to Fig.~\ref{fig:ch4pd}.\footnote{This ratio considerably exceeds that of the usual metal catalyst scenario.
-This high solubility accounts for several observations in current experiments: the dimensions of individual deposit is much larger than that of initial droplet, the concentration of sodium in final products is extremely low.}    Based on this aforementioned analysis, the author propose a hypothesis:
-%theorem environment
-
-The reaction on NaOH-Si substrate follow the phase diagram, and \ce{Na2Mo4O13} serves as the catalyst promoting various 1D \ce{MoO3} growth.
-
-In a typical 2 h growth, the \ce{MoO3} weight increase is about 20 mg, which is about $1.4\times 10^{-4}$ mol.
-This amount far exceeds the applied NaOH of $5\times 10^{-7}$ mol.\footnote{Sec.~\ref{sec:grow} on page.~\pageref{sec:grow}} To capture the early stage growth, the supply of \ce{MoO3} must be reduced in a controlled way.
-This can be accomplished by tuning two factors: oxygen flow rate and growth time.
-In this thesis, two series of controlled growth were used to probe the evolution of \ce{MoO3} deposition on NaOH-Si substrate.
-The first series regulated \ce{O2} flow at 0.1, 1, 3 and 10 sccm with fixed growth time of 15 min.
-The second series controls growth time at 15, 30, 60, and 90 min with fixed \ce{O2} flow of 10 sccm.
-Two series share one common growth of 10 sccm \ce{O2} for 15 min.
-
-The oxygen regulated growths were characterized using SEM, EDX and Raman, as shown in Fig.~\ref{fig:ch4oxy}.
-When \ce{O2} flow $\leq 1$ sccm, the deposition show micron size plate growth (Fig.~\ref{fig:ch4oxy}a and d).
-As oxygen flow becomes higher, the deposition amount increases dramatically, with a morphology of 1D forked plate decorated by triangular shape particles.
-% sem
-\begin{figure}[htb]
-\centering
-\includegraphics[width=0.9\textwidth]{MoO3_EDX_Raman}
-\caption[Evolution of the early stage for catalyst-assisted \ce{MoO3} growth]{Evolution of the early stage for catalyst-assisted \ce{MoO3} growth: SEM images, micro-Raman spectra, and EDX spectra of the specimens grown for 15 min with different \ce{O2} flows of (a-c) 0.1 sccm, (d-f) 1 sccm, (g-i) 3 sccm, and (j-l) 10 sccm.
-}
-\label{fig:ch4oxy}
-\end{figure}
-
-Micro-Raman scattering was used to probe the phase change during the oxygen regulated growth.
-The Raman spectra of sodium molybdates is featured with multiple strong peaks located between 800 and 1000 \si{cm^{-1}}, which we refer as high-frequency region hereafter.
-\ce{MoO3} phase shows two peaks in this region with the strongest one at about 820 \si{cm^{-1}}; \ce{Na2Mo2O7} phase exhibits four peaks in this region with the strongest one moving to 937 \si{cm^{-1}}, whereas \ce{Na2Mo4O13} phase shows even more peaks in high-frequency region, with a doublet at 962 and 970 \si{cm^{-1}}, respectively.\cite{Schofield2005,Saraiva2011} As predicted by the phase diagram (Fig.~\ref{fig:ch4pd}), Raman spectra identified \ce{Na2Mo2O7} phase in the 0.1 sccm growth (Fig.~\ref{fig:ch4oxy}b), and \ce{Na2Mo4O13} phase on the particles in the rest three growths (Fig.~\ref{fig:ch4oxy}e, h, and k).
-This observation supports the previous hypothesis about the reaction sequence on NaOH-Si substrate (Formula~\ref{eq:pd}).
-Element analysis performed on the Raman sites also confirm the presence of Na, Mo and O in particles growth, and only Mo and O in the plate growth (Fig.~\ref{fig:ch4oxy}c, f, i, and l).
-It is worth noting that the absence of Na signal in the forked \ce{MoO3} plate indicates the doping level would be lower than the detection limit of 0.01 wt.\% if the Na doping ever occurs.
-It should be pointed out the existence of \ce{Na2Mo3O10} phase is in doubt so far, and no Raman fingerprint is reported.\cite{Fomichev1992}
-
-The morphologies of second series experiment at constant \ce{O2} flow and varied growth time were shown in Fig.~\ref{fig:ch4ev}.
-The 15 min and 30 min growth show that dense arrays of \ce{MoO3} forked nanoplates with a length of hundreds of microns covering the substrate areas at different temperatures.
-With the increase of the growth time, these nanoplates keep growing and become larger, longer, and denser.
-Long 1D \ce{MoO3} structures start to grow on top of the nanoplate arrays.
-For 60 min growth, long nanobelts appear on top of the nanoplates.
-For the growth time of 90 min, the nanobelts grow longer, and some grow into microbelts.
-Microtowers start to grow as well.
-
-\begin{figure}[htb]
-\centering
-\includegraphics[width=0.9\textwidth]{mooe_sem_ev}
-\caption[Growth evolution of the second stage of catalyst-assisted growth of \ce{MoO3} 1D structures]{Growth evolution of the second stage of catalyst-assisted growth of \ce{MoO3} 1D structures: SEM images of the deposition at different growth temperatures with growth time of row 1: 15 min, row 2: 30 min, row 3: 60 min, and row 4: 90 min.}
-\label{fig:ch4ev}
-\end{figure}
-
-To reveal the growth mechanisms for the long 1D structures in the second stage, specimens were carefully examined to locate the catalyst particles.
-Small catalyst particles ranging from several hundred nanometers to several microns were found at different locations of these long 1D structures.
-As shown in Fig.~\ref{fig:ch4edx1} and Fig.~\ref{fig:ch4edx2}, EDX element analysis confirmed the presence of Na, Mo, and O in these particles, indicating the particles are sodium molybdate catalysts.
-
-\begin{figure}[htb]
-\centering
-\includegraphics[width=0.5\textwidth]{MoO3_SFig_EDX}
-\caption[SEM images and EDS spectra identifying the location, morphology, and composition of the catalyst particles on the nanobelt structures]{SEM images and EDS spectra identifying the location, morphology, and composition of the catalyst particles on the nanobelt structures: (a-b) a catalyst particle (I) in the middle of a nanobelt (II), (c-d) two catalyst particles (I and II) leading the growth of two perpendicular nanobelts.
-}
-\label{fig:ch4edx1}
-\end{figure}
-
-\begin{figure}[htb]
-\centering
-\includegraphics[width=0.5\textwidth]{MoO3_SFig_EDX_tower}
-\caption[SEM images and EDS spectra for identifying the location, morphology, and composition of the catalysts on the microtower structures]{SEM images and EDS spectra for identifying the location, morphology, and composition of the catalysts on the microtower structures: (a-b) a tiny catalyst particle (I) on top of a small cone shaped microtower (II), and (c-d) a catalyst particle (III) on a large and short microtower (IV).}
-\label{fig:ch4edx2}
-\end{figure}
-It could be of difficulty to observe the sodium molybdate particles on the as-synthesized belts and towers due to the following two factors, one is the consumption of catalysts, such as evaporation; the other is the unpredictable location of the catalyst.
-Unlike the conventional \gls{vls} growth where the catalysts were predominantly found at the tip of 1D nanostructures, the catalyst in current study were mostly found at the side wall of long nanobelts, and the location could be on the tip, or several microns away from tip.
-As for the microtowers, it is even rare to observe Na element.
-
-Some observations under similar controlled growth conditions is also listed as following to support the proposed growth model:
-
-\begin{enumerate}
-\item When no Mo powder is used, NaOH still holds onto substrate with some locations exhibiting etching.
-\item When no Mo powder is used while growth is performed in an old tube or oxygen flow is limited to a extreme small value, circular droplet-like solid were found and Mo, Na and O were detected, suggesting the existence of VLS mechanism.
-Using Mo coated substrate and subsequent NaOH treatment, similar droplets formation was repeated.
-No discernible XRD pattern emerged, illustrating the amorphous nature of liquid catalyst.
-\item 1 min growth shows plates in high temperature end and irregular shapes in low temperature end.
-\item 15 min growth shows \ce{MoO3} plates parallel to substrate, with some belts emerging and growing out of the substrate plane.
-This is presumably due to the growth direction mismatch between different plates.
-Morphology will also depend on local NaOH concentration.
-NaOH trace mark turns into connected plates at the original locations, showing the high concentration mediated the morphology evolution.
-The possible catalyst solid was sitting on the top of plate layer.
-Also some belt-like growth is visible on reaction chamber walls, suggesting the evaporation and transport of \ce{Na_xMoO3} vapor phase;
-\item 30 min growth: belts growth begin (500 microns long, grow rate is estimated to be 0.5 $\mu$ m/s), tower structures show up as well, but much less than belt.
-Two kinds of belts found, tapering and non-tapering.
-The former one seems to have droplets mostly associated with sidewalls of the top part.
-\item In reduced time or less oxygen supply growth, Na-containing site was found located onto the sidewall of belts instead of the usual expected tip.
-XRD pattern indicated the existence of \ce{Na_xMoO3} phase.
-And \ce{MoO3} XRD pattern is dominated by (0k0) peaks, indicating a 2D layer-by-layer growth with lateral rate exceeding that of axial direction.
-\item 2 h growth: there are crossed tapering belts at downstream boundary, with more than one droplet located along the interface of two perpendicular belts, EDX confirmed high Na content.
-\item Using NaOH treated hydrophobic substrates, dense tower array growth was found along the edge areas or molten periphery of droplets, where 5 min growth already show the initial stage of tower with diameter about 1 $\mu$ m, which increase to 10 $\mu$ m in prolonged growth.
-\end{enumerate}
-
-The growth of \ce{MoO3} on NaOH-Si can be divided into two stages delimited by the emerging of long nanobelts and microtowers.
-A growth model is proposed to account for the observed morphologies of \ce{MoO3} long nanobelt and tower-like structures.
-
-\fbox{%
-\parbox{0.8\textwidth}{%
-A transverse growth mode exists with growth direction perpendicular to the catalyst-deposition interface, promoting \ce{MoO3} nanoplate and nanobelt growth.
-A axial growth mode akin to conventional VLS process exists, and is responsible for \ce{MoO3} tower-like growth.
-}%
-}
-
-The first stage is dominated by transverse growth.
-The atomic steps in proposed growth model are depicted in the upper panel of Fig.~\ref{fig:ch4vls}.
-It has been verified that \ce{Na2Mo4O13} forms during the early stage of growth, and can act as catalysts.
-Although the exact phase (liquid or solid) of \ce{Na2Mo4O13} is not known yet in current study, it can be deduced that the \ce{Na2Mo4O13} exists as an active site for the adsorption of incoming \ce{MoO3} growth species.
-When the catalyst is smaller than some critical size, there is no preferred growth direction.
-This changed when the precipitated solid exceeds certain critical dimension, and the morphology evolution is then determined by the relative size of already formed solid and the associated catalyst.
-Several pathways could occur after the accommodation of \ce{MoO3} vapor and supersaturation.
-\ce{MoO3} could precipitate at catalyst-deposition interface, or propagate along catalyst-environment boundary and spread on the already formed \ce{MoO3} surface.
-Meanwhile, the \gls{vs} process is not suppressed and \ce{MoO3} adatoms could directly condense on \ce{MoO3} surface.
-
-\begin{figure}[htb]
-\centering
-\includegraphics[width=0.7\textwidth]{vls_mode2}
-\caption{Schematic drawing on the growth steps of the proposed growth mode.}
-\label{fig:ch4vls}
-\end{figure}
-
-Some unique features of \ce{MoO3} must be taken into consideration to properly evaluate the dominate pathway(s).
-It has been reported that \ce{MoO3} can spontaneously spread over the surface of supports (\emph{e.g.}, \ce{Al2O3}, \ce{SiO2}, and Au) to form a monolayer or submonolayer at a temperature (257 \si{\degreeCelsius}) well below the melting point.\cite{Leyrer1990} This strong spreading behavior can be explained by the solid-solid wetting process, in which the driving force is the decrease in total surface free energy.\cite{Leyrer1988} Although the detailed transport mechanisms of the spreading are still in debate, it is suggested that the high mobility of the Mo oxide species on substrates and \ce{MoO3} islands can promote the spreading and the ambient gases could further enhance the spreading.\cite{Gunther2000, Song2003} Based on above analysis and the final morphology of \ce{MoO3}, the dominance of accommodation and spreading pathway in higher temperature part of the growth sample is most possible in this study.
-Hereby the transverse growth mode is attributed to the strong spreading capability of \ce{MoO3}.
-The final morphology of observed nanoplate and nanobelt is a combined result of \gls{vs} and \gls{vls} growth.
-
-On the other hand, the tower-like structures in the second stage follow the axial growth mode in conventional VLS process.
-The molybdates can be evaporated from the higher temperature end and re-condense onto the lower temperature region.
-As illustrated in the lower panel of Fig.~\ref{fig:ch4vls}, this could initiate either belt growth or tower growth depending on the locations.
-The microtowers in this study primarily grow at the low temperature end of the substrate, where the spreading capability of the Mo oxide species is possibly limited.
-Thus the transverse growth pathway is probably suppressed and axial growth becomes dominant.
-
-The transport of molybdates in proposed growth model is verified by a side-by-side experiment, as schematically depicted in Fig.~\ref{fig:ch4sbs}a.
-Two substrates, one with NaOH catalyst and one bare substrate, were loaded side-by-side at the same location for the growth.
-To avoid any possible catalyst transports through surface diffusion, the two substrates were separated with several millimeters gap in between.
-
-\begin{figure}[htb]
-\centering
-\includegraphics[width=0.8\textwidth]{MoO3_SFig_sidebyside}
-\caption[Side-by-side growth of \ce{MoO3}]{Side-by-side growth of \ce{MoO3}.
-(a) Schematic drawing of the side-by-side growth with one NaOH catalyst treated substrate and one bare substrate.
-SEM images of the growth on the untreated substrates at different growth times: (b-e) 30 min and (f-i) 120 min.
-For 30 min growth: (b) low magnification SEM image showing labeled growth areas with different morphologies, (c) rectangular nanoplates grown without catalyst, (d) nanobelts grown with catalyst, and (e) forked nanoplates grown with catalyst.
-For 120 min growth: (f) rectangular nanoplates without catalyst, (g) forked nanoplates with catalyst, (h) microbelts with catalyst, and (i) microtowers with catalyst.}
-\label{fig:ch4sbs}
-\end{figure}
-
-After the growth, besides the non-catalyst rectangular plates, catalyst induced 1D structures were also found on the bare substrate (Fig.~\ref{fig:ch4sbs}b-i).
-This result clearly confirms that the catalyst can be evaporated and transferred from the NaOH treated substrate to the untreated one.
-The catalyst vapors can nucleate and form catalyst particles on the \ce{MoO3} deposition promoting the VLS growth of different 1D structures.
-It is worth mentioning that catalyst particles were not observed on all the 1D structures.
-This fact can be explained by following reasons:
-\begin{enumerate*}[label=\itshape\alph*\upshape)]
-\item Catalyst particles can nucleate at any locations along the 1D structures. Some particles may be invisible hiding on the backside of the 1D structures;
-\item Because of the evaporation, the catalyst particles may become too small to be detected.
-Some particles could even disappear terminating the catalyzed growth, which may explain the growth of the microtowers with a flat top.
-\end{enumerate*} The evaporation and nucleation of catalyst not only promote the growth of the 1D structures in the second stage growth, they also shape the morphologies of these 1D structures.
-Many 1D structures in the second stage were found to have a tapered shape, such as triangular nanobelts (Fig.~\ref{fig:ch4sem2by3}b and d), microtowers with tapered tips (Fig.~\ref{fig:ch4sem2by3}f).
-Several factors can contribute to the tapering of the 1D structures.
-First, the reduction in catalyst size may induce the tapering.
-Due to the evaporation, the size of the catalyst particles can shrink during the growth resulting in the tapered growth.
-The \gls{vs} growth on the side surfaces is another possible mechanism, which promotes the radial growth of the 1D structures forming the tapered shape.
-Another important factor is the gradually reduced growth during the cooling process.
-During the cooling, the \ce{MoO3} vapor supply reduced and the growth temperature gradually decrease.
-Hence the growth rate slows down producing the tapered tips on the top of some 1D structures.
-
-\subsection{Growth on Alkaline Metal Containing Substrates}
-In analog with the \ce{Na2MoO4}-\ce{MoO3} binary phase diagram, other alkaline metals, such as Li and K, could also form A-Mo-O alloy at elevated temperature.
-This fact allows for the usage of a variety of alkaline metal based material as catalyst to promote \gls{vls} or \gls{vss} growth of \ce{MoO3}.
-Some experiments have been performed in this study, including growth using KI and \ce{Na2CO3} treated Si substrate, glass and mica.
-Fig.~\ref{fig:ch4al1}a-b show the long belt growth on KI treated Si substrate and towers on ITO glass, respectively.
-Compared to NaOH-Si growth, the belt on KI appears with rough edge, whereas the towers on ITO glass exhibit stacking features.
-
-\begin{figure}[htb]
-\centering
-\includegraphics[width=0.6\textwidth]{Fig7_MoO3_Small}
-\caption[Alternative catalysts for \ce{MoO3} growth]{Alternative catalysts for \ce{MoO3} growth.
-SEM images of \ce{MoO3} 1D structures.
-(a) nanobelts grown with KI and (b) microtowers grown on ITO glass}
-\label{fig:ch4al1}
-\end{figure}
-
-Fig.~\ref{fig:ch4al2}a-c illustrate the forked plate growth on \ce{Na2CO3} treated Si, sword-shape belts on glass, and nanoblets growth on mica, respectively.
-No long belt or tower was observed on the sample with \ce{Na2CO3}.
-Long belts found on mica (\ce{K(Al2)(Si3Al)O10(OH)2}) probably arise from potassium-catalyzed \gls{vls} mechanism.\cite{Hu2011} More detailed results on glass will be presented in Sec.~\ref{sec:glass}.
-
-\begin{figure}[htb]
-\centering
-\includegraphics[width=0.8\textwidth]{SFig5_MoO3_Small}
-\caption[Alternative catalysts for \ce{MoO3} growth cont]{Alternative catalysts for \ce{MoO3} growth.
-SEM images of MoO3 1D structures: (a) forked nanoplates grown with \ce{Na2CO3}, (b) triangular microbelts grown on glass, and (c) nanobelts and microbelts grown on mica.}
-\label{fig:ch4al2}
-\end{figure}
-
-The various growth morphologies found using alkaline metal based materials as catalysts demonstrate the proposed \gls{vss} mechanism and transverse mode is a general phenomenon, and broad engineering space could be explored to control the dimension of \ce{MoO3}.
-
-\subsection{Growth on Glass}\label{sec:glass}
-Achieving morphology controlled growth of \ce{MoO3} on transparent substrates, e.g., glass, is an important progress towards process integration and device fabrication in photo-energy related applications.
-Because the alkaline ions in glass can diffuse out at elevated temperature, the proposed \gls{vss} mechanism will modify the \ce{MoO3} deposition.
-Therefore, the mass transport of sodium ions in silica glass is first estimated to evaluate the amount of catalyst available during the growth of \ce{MoO3}.
-The driving force could be external field or concentration gradient.
-And the dynamics is governed by diffusion equation
-\begin{align}\label{eq:nadiff}
-\frac{\partial C}{\partial t} = D \frac{\partial^2 C}{\partial x^2},
-\end{align}
-where $C$ is concentration in unit of \si{mol\per cm^3}, and $D$ is diffusion coefficient in unit of \si{cm^2\per\second}.
-Diffusion coefficient highly depends on the overall environment in which the ions reside.
-Typical values of $D$ for Na ions are listed in Table~\ref{tab:mona}
-
-\begin{table}[htb]
-\centering
-\caption[Na diffusion coefficient]{Na diffusion coefficient (\si{cm^2\per\second}), R is molar gas constant (8.315 \si{\joule\per mol\per K}), and T is temperature in K}\label{tab:mona}
-\begin{tabular}{lcr}
-\toprule
- Composition & Value  & Reference  \\
-\midrule
-Quartz      & $3.8\times10^{-2}\exp(\frac{-24500}{RT})$  & \cite{Rybach1967a}  \\
- \addlinespace[0.5em]
-Sodalite      & $6.6\exp(\frac{-42500}{RT})$  & \cite{Sippel1963}  \\
- \addlinespace[0.5em]
-Obsidian     & $4.4\times10^{-2}\exp(\frac{-22900}{RT})$  & \cite{Sippel1963}  \\
- \addlinespace[0.5em]
-silicate glass & $3.1\times10^{-8}$ at 420\si{\degreeCelsius} & \cite{Jbara1995} \\
- \addlinespace[0.5em]
-\ce{SiO2} glass & $1.1\times10^{-7}$ at 670\si{\degreeCelsius} &  \cite{FRISCHAT1968}\\
-\bottomrule
-\end{tabular}
-\end{table}
-It is worth mentioning that the gradient of Gibbs free enthalpy overruled the concentration of a particular species, and higher \ce{OH-} contents tend to reduce Na diffusivity.\cite{Materials2012} The substrates used in this work are glass and ITO/glass; the relevant parameters are as following:
-\begin{itemize}
-\item dimension: $25\times10\times1$ mm
-\item density: 2.567 \si{g\per cm^3}
-\item Na concentration: 0.01 \si{mol\per cm^3}
-\item $D$: $1.1\times10^{-7}$ \si{cm^2\per\second}
-\end{itemize}
-Substituting these values into Eq.~\ref{eq:nadiff}, the net flux $J$ is estimated as
-\begin{align}
-J = -D \frac{\Delta C}{\Delta x} = 2.0\times 10^{-8} \si{mol\per cm^2\per\second}.
-\end{align}
-In typical growth of 2 h, the net amount of Na diffusing out of substrate is then $1.44\times10^{-4}$ mol, which is about 10\% of total Na ions in the glass substrates.
-The diffusion length $\sqrt{Dt}$ is 190 $\mu$m.
-Notice this result overestimates since the flux will reduce gradually.
-Meanwhile the molar amount of \ce{NaOH} applied on Si substrate is about $5\times10^{-7}$ mol.
-Considering the adjusted ratio, Na contents should be much more when using glass substrate than when using NaOH-Si substrate.
-Another important factor is the evaporation of sodium molybdates.
-However, few report could be found in literature.
-Only one was reported by \citeauthor{Kazenas2010}.\cite{Kazenas2010} The partial pressure of \ce{Na2MoO4} is calculated to be 0.2 mTorr at 800 \si{\degreeCelsius} and $3.5\times 10^{-3}$ mTorr at 670 \si{\degreeCelsius}.\footnote{$\log P(atm)= -13794/T + 6.19$}
-
-This thesis studied the effect of temperature, oxygen partial pressure and growth time towards \ce{MoO3} deposition on glass substrates.
-Each factor was divided into two levels, with $T$ at 700 and 800 \si{\degreeCelsius}, \ce{O2} flow at 1 and 10 sccm, and growth time of 15 and 60 min.
-And the morphological variations revealed by SEM imaging were summarized in Table~\ref{tab:mo3glass}.
-% glass growth matrix
-\begin{table}[htb]
-\centering
-\caption{\ce{MoO3} growth on glass}\label{tab:mo3glass}
-\begin{tabular}{lccp{3in}}
-\toprule
-\multicolumn{3}{c}{Growth Conditions} \\
-\cmidrule(l){1-3}
-$T$ (\si{\degreeCelsius}) & \ce{O2} (sccm) & Time (min) & Morphology  \\
-\midrule
-700    &  10   & 15  &   about 50 $\mu$m belts, some towers \\
-700   &  1   & 60  &   irregular shape, not too much growth\\
-700    &  10   & 60  &   droplet almost all on tip of belts, many towers \\
-800    &  1   & 15  &   tens $\mu$m belt with sharp edge(100 nm thick, and 1micro wide) dominates\\
-800   &  1   & 60  &   exhibiting ITO features, droplets on tips of belt, many tower like structures\\
-800    &  10   & 15  &   rounded edge flakes dominate, modest density tapering belt, and some possible tower\\
-800    &  10   & 60  &   ITO/glass features, aggregated belts, some towers\\
-\bottomrule
-\end{tabular}
-\end{table}
-The 800-1-15 combination produced dense \ce{MoO3} nanoplate with length about 10 $\mu$m, width $300\sim500$ nm and thickness less than 100 nm, as illustrated in Fig.~\ref{fig:ch4glass}.
-These \ce{MoO3} nanoplates are of high crystalline quality, and could potentially show enhanced photoelectrochemical and electrochromic activities.
-\begin{figure}[htb]
-\centering
-\includegraphics[width=0.7\textwidth]{moo3_glass}
-\caption{Optimized \ce{MoO3} nanoplates growth on glass.}
-\label{fig:ch4glass}
-\end{figure}
-
-\subsection{Optical Properties of Molybdenum Oxide}
-
 \gls{fl} materials attracts intensive research efforts recently.
@@
 This is, however, beyond the scope of current study.
-
-\section{Summary}
-
-In this chapter, a new growth model of \ce{MoO3} using alkaline metal ions as catalysts was discovered and investigated in depth.
-The growth kinetics was closely inspected using a series of controlled experiments.
-A modified vapor-solid-solid mechanism was proposed and favorably verified.
-Two growth modes, i.e., transverse growth and axial growth, were highlighted, which not only improved the yield, but also allowed for versatile morphology control of 1D \ce{MoO3} nanostructures.
-This methodology was further extended onto glass and ITO glass substrates, paving the way to a more integrated process of using \ce{MoO3} nanostructures onto various solar energy saving and harvesting applications.

### 2014-10-28 ch-moox/moox.tex
camera ready

@@
 % git version control added 012614
-\chapter{Vapor-Solid-Solid Growth of MoO$_3$}
+\chapter{Vapor-Solid-Solid Growth of MOLYBDENUM OXIDE}
 
@@
 As shown in Fig.~\ref{fig:mo3model}, the layered structure consisting of zig-zag rows of edge-sharing \ce{MoO6} octahedra, while the rows are mutually connected by corners.
-\begin{figure}[htb]
+\begin{figure}[ht]
 \centering
@@
 \centering
-\includegraphics[width=0.7\textwidth]{CVD_and_temp_MoO3.jpg}
+\includegraphics[width=0.6\textwidth]{CVD_and_temp_MoO3.jpg}
 \caption[CVD growth setup of \ce{MoO3}]{CVD growth setup of \ce{MoO3}.
@@
 
-\fbox{%
-\parbox{0.8\textwidth}{%
+\emph{
 A transverse growth mode exists with growth direction perpendicular to the catalyst-deposition interface, promoting \ce{MoO3} nanoplate and nanobelt growth.
 A axial growth mode akin to conventional VLS process exists, and is responsible for \ce{MoO3} tower-like growth.
-}%
 }
@@
 
-\gls{fl} materials attracts intensive research efforts recently.
-This study also made some efforts using liquid exfoliation method to prepare \gls{fl} \ce{MoO3}.
-The exfoliated \ce{MoO3} was characterized using UV-Vis and TEM.
-The optical contrast of \gls{fl} \ce{MoO3} on \ce{SiO2}-Si is also calculated, which could serve as a guideline to identify \gls{fl} \ce{MoO3} using optical microscope.
-
-The exfoliation solution is 30\% isopropanol (IPA) in DI water, which has been proved to work well on other layered compounds.\cite{Halim2013} After 20 min sonication, the dispersion appears milky.
-The transmission spectra of this dispersion immediately upon sonication and after 40 h of gravity sedimentation were measured and compared in Fig.~\ref{fig:moabs}.
-The t0 line mainly arise from the scattering of flakes in the dispersion.
-There are two scattering mechanisms: Rayleigh scattering and Tyndall scattering.
-Rayleigh scattering, which occurs when particles are comparable to wavelength, is inversely proportional to the fourth power of wavelength; while Tyndall scattering, which occurs when the particles are larger, is inversely proportional to the square of the wavelength.
-To fully evaluate the true absorbance of the sample itself, one needs to decouple the scattering part from apparent absorbance.
-Generally, one part of spectrum away from absorption edge is selected and assumed it is only caused by scattering.
-Then an empirical dependence shown in Eq.~\ref{eq:sca2} is used in the polynomial fitting model.
-
-\begin{align}
-Abs_{sca}  & = a\times \lambda^{n}  \label{eq:sca1}\\
-\log{Abs_{sca}} & = \log{a} + n*\log{\lambda} \label{eq:sca2}
-\end{align}
-
-After least-squares fitting, the coefficients $a$ and $n$ can be used to estimated the scattering in other wavelengths.
-The fitting of $n$ usually falls between -2 and -4.
-The author examined the t40h line in Fig.~\ref{fig:moabs} and found the scattering part is almost zero.
-Therefore no scattering fitting was performed.
-
+%\input{./ch-moox/mooptics}
+The optical properties of the as-grown specimen was evaluated using \gls{drs} method.
+Fig.~\ref{fig:modrs} show the hemisphere diffuse reflection spectrum from 800 nm to 250 nm, where the diffuse reflection kept increasing from 27\% to 33\% when incident wavelength scanned from 800nm to about 400 nm, then drop sharply to 15\% between 400 nm and 300 nm.
+The KMT function fitting was used to estimated the energy gap, as displayed in Fig.~\ref{fig:mokmt}.
+Extrapolation indicated a gap of 3.2 eV, corresponding to absorption edge at 387 nm.
+This matches well with the DRS data.
 \begin{figure}[htb]
 \centering
-\subfloat[]{\label{fig:moabs}\includegraphics[width=0.45\textwidth]{MoO3-abs}}\hspace{0.04\textwidth}
-\subfloat[]{\label{fig:mobg}\includegraphics[width=0.45\textwidth]{MoO3-bg}}
-\caption[UV-Vis spectra of exfoliated \ce{MoO3}]{UV-Vis spectra of exfoliated \ce{MoO3}.
-(a) UV-Vis absorbance spectra of exfoliated \ce{MoO3}.
-Dashed line (t0) represents measurement immediately after sonication, and solid line (t40h) is obtained after sitting for 40 h.
-The dot dashed line is reference spectrum of the 30\% IPA.
-(b) Band gap estimation}
-\label{fig:mouv}
+\subfloat[]{\label{fig:modrs}\includegraphics[width=0.45\textwidth]{moo3_DRS}}\hspace{0.04\textwidth}
+\subfloat[]{\label{fig:mokmt}\includegraphics[width=0.45\textwidth]{moo3_kmt}}
+\caption[DRS spectrum of \ce{MoO3} nanostructures]{DRS spectrum of \ce{MoO3} nanostructures: (a) diffuse reflection spectrum, and (b) the associated KMT function.}
+\label{fig:moo3drs}
 \end{figure}
-
-According to the corrected absorbance spectrum, optical bandgap can be deduced, which is known as Tauc Plot.\cite{Tauc1972} The procedure is recapitulated here briefly.
-Eq.~\ref{eq:tauc} is given to empirically relate optical band gap to absorption.
-
-\begin{equation}\label{eq:tauc}
- (h\nu \alpha)^{\frac{1}{n}} = B(h\nu - E_g^{opt}),
-\end{equation}
-where B is a proportional coefficient, $\alpha$ is absorption coefficient\footnote{The absorbance $A = 0.4343\alpha*l$, where l is the optical path} and $E_g^{opt}$ is defined as optical bandgap.
-The value n is correlated to the nature of optical transition.
-\begin{itemize}
-\item For direct allowed transition, n = 1/2;
-\item For direct forbidden transition, n = 3/2;
-\item For indirect allowed transition, n = 2;
-\item And for indirect forbidden transition, n = 3.
-\end{itemize}
-
-When the transition nature of sample is not well known, one should apply each to check which one provide the best fit.
-Depending on the synthesis methods and \ce{MoO3} morphologies, the transition phenomena might vary.
-On the \ce{MoO3} films, \citeauthor{Bouzidi2003} assumed a direct gap (n = 1/2)\cite{Bouzidi2003} while \citeauthor{Szekeres2002} used an indirect gap.\cite{Szekeres2002} The author use n = 2 in this work, plot $\sqrt{(h\nu \alpha)}$ versus photon energy, and extrapolate the linear part onto $h\nu$ axis.
-The intercept is used as $E_g^{opt}$ then.
-The estimated energy gap and some results from previous studies is summarized in Table.~\ref{tab:mobg}.
-
+Another reflection peak was found at 260 nm, illustrating there is more complex electronic band structures above 4 eV.
+As a comparison, the estimated energy gap and results from previous studies is summarized in Table~\ref{tab:mobg}.
 \begin{table}[htb]
@@
 \cite{Julien1995} & 2.8$\sim$ 3.2 & NA & films\\
- this work  & 3.1  & NA & nanoflakes\\
+ this work  & 3.2  & NA & nanoflakes\\
 \bottomrule
@@
 \end{table}
-
-An alternative approach is a) define $Y = \alpha E=\alpha h\nu$, and obtain $Y' = \frac{\partial Y}{\partial E}$, then b) plot $Y'/Y$ versus $h\nu$.
-The band gap value can be obtained from the intercept of extrapolated line on photo energy axis.\cite{Choopun} This approach is not difficult to comprehend as long as we notice from Eq.~\ref{eq:tauc}, $Y = B (h\nu - E_g^{opt})^n$ and $Y' = B n(h\nu - E_g^{opt})^{n-1}$.
-The advantage is one can also estimate n without using assumption.
-
-The dielectric constants\footnote{Not a constant at all, instead, it has complicated dependence on photon energy} ($\epsilon = \epsilon_1 + i*\epsilon_2$) of \ce{MoO3} have been studied in several reports.\cite{Deb1968,Sabhapathi1995,Miyata1996,Abdellaoui1997,Mondragon1999} The author extracted $\epsilon_1$ from Ref.~\cite{Itoh2001a} due to the wide photon energy range utilized there.
-Notice that $\epsilon_2$ is approximately zero when $h\nu$ is less than 4 eV.
-Since this study is primarily concerned with the optical contrast of few-layered \ce{MoO3} in visible wavelength region ($h\nu < 3$ eV), the refractive indices $n$ is calculated from $n = \sqrt{\epsilon_1}$.
-Due to the orthorhombic phase, \ce{MoO3} exhibit birefringence, that is there are two refractive indices, $n_c$ and $n_a$, as shown in Fig.~\ref{fig:moind}.
-The refractive index is between $ 2.2\sim 2.4$ along $a$ axis, and $ 2.5\sim 2.8$ along $c$ axis.
-
-\begin{figure}[htb]
-\centering
-\subfloat[]{\label{fig:moind}\includegraphics[width=0.45\textwidth]{n_MoO3}}\hspace{0.04\textwidth}
-\subfloat[]{\label{fig:mocon}\includegraphics[width=0.45\textwidth]{MoO3_1L}}
-\caption[Refractive indices of \ce{MoO3}]{Refractive indices of \ce{MoO3}.
-(a) Refractive indices of \ce{MoO3} Dashed line is n along $a$ axis while solid line is along $c$ axis.
-(b) optical contrast mapping of 1L \ce{MoO3} on \ce{SiO2}-Si.
-The $x$ axis is \ce{SiO2} thickness, $y$ axis is wavelength.
-It is assumed that the incident light is polarized along $c$ axis of \ce{MoO3}.}
-\label{fig:mofl}
-\end{figure}
-
-Fig.~\ref{fig:mocon} illustrates the optical contrast mapping of 1L \ce{MoO3} on \ce{SiO2}-Si when the incident light is polarized along $c$ axis of \ce{MoO3}.
-One can see that there is a pseudo-periodical trend with either wavelength or \ce{SiO2} thickness fixed.
-The positive extreme occur at around 80 nm and 240 nm \ce{SiO2} layer, slightly less than the optimum for observing graphene.
-The refractive indices of Si and \ce{SiO2} within visible wavelengths and MATLAB source code for optical contrast calculation is included in Appendix~\ref{app:matlab}, with which one can readily evaluate the few layers \ce{MoO3} scenarios and the circumstance when incident light is polarized along $a$ axis.
-
-The dimension and phase of exfoliated \ce{MoO3} is examined using TEM.
-Fig.~\ref{fig:motem} shows the size of exfoliated \ce{MoO3} is about 500 nm.
-High-resolution TEM (HRTEM) image was taken to assess the \ce{MoO3} crystallinity.
-The clearly resolved lattices indicate high crystal quality of these exfoliated \ce{MoO3}.
-\begin{figure}[htb]
-\centering
-\includegraphics[width=0.8\textwidth]{exf_moo3.jpg}
-\caption[TEM images of exfoliated \ce{MoO3}]{TEM images of exfoliated \ce{MoO3}. (a) TEM image and (b) HRTEM image of FL \ce{MoO3} obtained by liquid sonication method.}
-\label{fig:motem}
-\end{figure}
-Nevertheless, identifying these few layer \ce{MoO3} under optical microscope is still difficult due to both the small flake size and low contrast.\footnote{Human eye threshold contrast (contrast sensitivity)$^{-1}$ is about 10\%.} One need to improve the liquid exfoliation process to obtain larger dimension and high yield.
-This is, however, beyond the scope of current study.
 

### 2014-10-28 ch-tms/tms.tex
camera ready

@@
-\chapter{TEM-RAMAN STUDY ON INDIVIDUAL TUNGSTEN OXIDE-TUNGSTEN DISULFIDE CORE-SHELL NANOWIRE}
+\chapter{TUNGSTEN OXIDE-TUNGSTEN DISULFIDE NANOWIRES}
 
@@
 The present work in this chapter, to some extent, circumvents this limitation by leveraging a home-built micromanipulator apparatus to transfer the nanostructures between TEM grids and other desired substrates.
-And considerable insight on the \ce{WO3}-\ce{WS2} core-shell nanostructures was obtained: few-layer, even single-layer \ce{WS2} nanotube was observed with \ce{WO3} core; layer dependent Raman spectra were studied at on-resonance and off-resonance conditions; the fingerprint of few-layer \ce{WS2} was revealed; photoluminescence from core-shell NWs was identified.
+Considerable insight on the \ce{WO3}-\ce{WS2} core-shell nanostructures was obtained: few-layer, even single-layer tubular \ce{WS2} nanostructure was observed with \ce{WO3} core; layer dependent Raman spectra were studied at on-resonance and off-resonance conditions; the fingerprint of few-layer \ce{WS2} was revealed; photoluminescence from core-shell NWs was identified.
 These results hold great values to the application of \ce{WO3}-\ce{WS2} heterostrucutres in photocatalysis and photoelectrochemical applications.
@@
 \chapter{SUMMARY AND FUTURE WORK}
+
+In summary, synthesis of \ce{WO3} and \ce{MoO3} nanostructures based on CVD method were thoroughly investigated in this study.
+Sodium impurity effect was revealed and \ce{Na5W14O44} nanowire was first reported.
+Partially enlightened by this discovery, a new VSS growth mechanism of \ce{MoO3} was found and the growth dynamics was systematically probed.
+Comprehensive electron microscopy characterizations were performed on both \ce{WO3} and \ce{MoO3}.
+And the insight of growth kinetics can be used to establish a systematic connection between the interaction of transition metal oxide and alkaline metal ions.
+Besides, seeded growth of \ce{WO3} was demonstrated to be an effective and scalable approach for obtaining single crystalline 1D \ce{WO3} nanostructure.
+Based on these \ce{WO3} nanowires, \ce{WO3}-\ce{WS2} heterostructure was synthesized using a simple sulfurization process and single-walled \ce{WS2} tubular core-shell nanowire was observed.
+More important, a TEM-Raman integrated approach was tested aiming at providing a location-resolved map between crystal structure and optical properties.
+As a result, layer number dependence of Raman spectra on \ce{WS2} tubular nanostructure was fingerprinted, and direct bandgap \gls{pl} from \ce{WS2} was observed.
+This result indicates a broad space for band structure tuning of \ce{WO3}-\ce{WS2}.
+Moreover, the integration of TEM-Raman serves as an excellent tool to correlation the structure-property relationship for nanomaterials.
+
+For future work, the author suggested several following perspectives:
+\begin{enumerate}
+\item further investigation of \ce{WO3} growth using alkaline metal ions as catalysts;
+\item probing the VSS growth method of \ce{MoO3} using HRTEM and analyzing the droplet state; and
+\item applying TEM-Raman integrated study onto other nanostructures.
+\end{enumerate}

### 2014-10-28 ch-wox/ch-wox.tex
camera ready

@@
 
-\chapter{IMPURITY EFFECTS ON THE GROWTH OF TUNGSTEN OXIDE NANOWIRES}
+\chapter{IMPURITY EFFECTS ON TUNGSTEN OXIDE NANOWIRES}
 
@@
 The substrates were p-type, boron-doped and [100]-orientated silicon with about 1 $\mu$m thermally-grown silicon oxide layer on the polished side.
-The cleaning procedures have been elucidated on page.~\pageref{ch2sub}.
+The cleaning procedures have been elucidated on page~\pageref{ch2sub}.
 The boat was then loaded into reaction chamber in a way that the powder source was placed in the center of heating zone, and the substrate upstream end was aligned at 6.5 inch.\footnote{As defined in Fig.~\ref{fig:wogrow}} After pumping down, 1 \gls{sccm} \ce{O2} and 10 sccm Ar were admitted into the chamber, respectively, after which the overall pressure read approximately 110 mTorr.
@@
 \centering
-\includegraphics[width=0.7\textwidth]{CVD_and_temp.jpg}
+\includegraphics[width=0.6\textwidth]{CVD_and_temp.jpg}
 \caption[\ce{WO3} NW CVD growth]{\ce{WO3} NW CVD growth and the temperature profile.
@@
 \end{tabular}
+\end{table}
+For a comprehensive comparison purpose, the Raman fingerprints of various tungsten oxides and tungstate is shown in Table.~\ref{tab:woram2}. 
+\begin{table}[htb]
+\centering
+\caption{Raman fingerprints of tungsten oxides and sodium tungsten compounds}\label{tab:woram2}
+\begin{tabular}{lp{3in}r}
+\toprule
+Phase & Raman Shift (\si{cm^{-1}}) &  Reference   \\
+\midrule
+\ce{WO2}  & 287(s), 334(w), 514(m), 600(w), 621(w), 785(vs) & \cite{Ma2005} \\
+\ce{W18O49}  & broad bands from 750 to 780 & \cite{Guo2012} \\
+             &  267(s), 778(s), 969(m) & \cite{Liu2013d} \\
+m-\ce{WO3}  & 131(m), 265(m), 327(m), 715(s), 807(vs) &  \cite{Salje1975a,Daniel1987} \\
+h-\ce{WO3}  & 162(m), 253(m), 320(m), 645, 690(s), 817(vs) &  \cite{Daniel1987}\\
+\ce{WO3.H2O}  & 230(m), 377(w), 428(w), 650(s), 816(vs), 946(vs) &  \cite{Daniel1987} \\
+\ce{WO3.2H2O}  & 235, 268(m), 380(w), 662(s), 685(vs), 960(vs) & \cite{Daniel1987} \\
+\ce{Na2WO4}  & 94(w), 314(vw), 377(m), 813(m), 930(vs) &  \cite{Lima2011} \\
+\ce{Na2W2O7}  & 381(w), 422(w), 763(w), 835(s), 886(m), 948(m), 957(vs) &  \cite{Knee1979} \\
+\ce{Na2W4O13} & 263(w), 272(w), 311(w), 366(w), 777(vs), 794(s), 949(m) &\cite{Fomichev1992}\\
+\ce{Na5W14O44} & 107(s),695(m), 765(vs), 913(w), 943(m), 965(m)& this work\\
+\bottomrule
+\end{tabular}
+
+Materials in solid state, 
+vw-very weak; w-weak; m-medium; s-strong; vs-very strong
 \end{table}

### 2014-11-21 figure_table.tex
SI papers reading

--- 2014-10-09 figure_table.tex
@@
 (cf. )
-up-scaling capability, band edge smeared; major bands situated at
+
+put under the spotlight, barely satisfactory, decrement of,  more numerous than elsewhere, draw attention to it. not as restrictive an assumption as it may seem.
+
+up-scaling capability, band edge smeared; major bands situated at, 
+bypassing a limitation, held back by a restriction, discern,  nanoscopy, run in parallel tracks, line of thought take shape, delve into, devise, commotion, fruition, foundation was laid, one variant, ponder, passivated, halt, lack of progress, p-dope FaN in a controlled manner, transcend, theoretical description, and experimental implementation,
+
+stochastic, doctrine, ample evidence, suits - diamonds, clubs, hearts, and spades
+
+settling towards minimum energy, a free electron of momentum $p$ cab be represented by a wave of wavelength $\lambda = h/p$.
+to the extent to which theoretical results correspond with reality.
+apparent agreement of theory and experiment carries no guarantee that .
+another school of thought,
+
+bottom-up paradigm.
+curiosity was drawn toward.
+exemplify.
+unambiguous interpretation.
+pronounced, Nevertheless, highlight the necessity , As a consequence, proved beneficial.
+insight we have gained from our investigations.
+solve this conflict.
+critical ingredients.
+regime.
+dominate and reveal itself.
+
+closer inspection, consecutive, a characteristic feature of aggregation process.
+on the basis of present results, some conclusion could be drawn concerning the ..
+The observation that ....
+indicated ....
+,discerned, discrepancy, deviating, deviation, accompanied,
+
+progressively consumed and converted into sulfide. ensuing purification, a matter of controversy,
+
+entail, prerequisite, kinetically hindered, rate-determining step, confirmed experimentally. closed cap. various synthetic methodologies.
+grouping into two categories, phenomenological arguments, primarily, establish a systematic connection. 
+in this letter, reason reside in, sizing histogram, vessel, implementation of , predominantly, stacking sequence.
+naturally abundant, fundamentally intriguing and technologically attractive, thermodynamically preferred. 
+pronounced effect, strategy for extending methodology, modify, change, alter.
+
+exothermic, endothermic. occurrence, impediment, batches. prevail in accordance with
+
+measured properties compare favorably with theoretical analysis. 
+elimination of dangling bonds. conformal coating. Equation is visualized in Fig.
+fluidic dynamics, entangled web, dimensional heterostructure, kinetically hindered. preceding text, more specifically, hold great potential. 
+residence time, crucial aspects. temperature gradient. diverse function, distinct experiment.
+
+trigonal prismatic coordination, bridging coordination types. intercalation mechanism been elucidated 
+hydration.
+not always deleterious, branched nanocrystal, orientation dictated by substrates, moscovite mica, concurrently, as described herein.
+applicable, suggestive, anion-terminated facets.
+phase segregation.
+
+Inorganic fullerenes, transitional metal dichalcogenides. postulate
+
+vast, disorder, orderliness, irregularly, solidifies, 
+a constant competition between the attractive force which hole the atoms together and the irregular motions which tend to knock them apart. 
+Liquid and gas are alike in their ability to flow but unlike in the volumes they occupy, while liquid and solid are alike in the volumes they occupy but unlike in their ability to flow.
+
+the departure of molecules from most solids at ordinary temperature is so infrequent that the evaporation is imperceptible. 
+one kind of disorder and limitless orderliness.
+endless variety, diversity, ingredient, grows into being.
+They adopt positions on the surface that are forced on them by the kind of orderliness confronting them.
+Settling into those positions, they extend the orderliness outward, and thus the crystal grows.
+
+manifest their presence in various ways.
+impartially, small proportion, interstitial vacancy, point, line, plane disorder.
+the few layers of atoms near the surface will be slightly more compressed  inward than the bulk of the crystal.
+entangle, agitate, the increasing viscosity of liquids as their temperature goes down is a measure of the increasing difficulty with which the molecules move past one another.
+
+more distant past, rock, mineral, percolate, steam boiler, 
+Snow flakes grow directly from moist air-in other words, from a gas. Carbon dioxide fizzes out of soft drinks when you release the pressure. dissolved or mixed, 
+Gases are usually less soluble in a liquid when it is hot than when it is cold, but the reverse is usually true of solids.
+The opposite effects arise from the same cause: increasing temperature tend to increase their disorder.
+
+True solution: they are dispersed through one another molecularly, not in little chunks. 
+The solubility of the substituent is limited, much as is the solubility of salt in water. retain the crystalline arrangement.
+
+Zinc and copper, silver and gold. 
+When molecules of solute are moving about in a liquid, they cannot go as far in as short a time as they can when they are moving about in a gas: the diffusion rate is much slower. Perfume in air,
+
+Soldering depends on dissolving a little of the solid metal in the molten solder to form an alloy at the boundary;
+
+Factors that influence whether a substance will dissolve in something else: the random motion of the molecules, tending to separate and disorder them, wage a constant war with the attractive forces.
+
+The associations between the molecules of solute and of solvent keep forming and breaking and forming again.
+
+water reduces the electric forces more than almost any other liquid does, a reason why water is an effective solvent for materials whose molecular constituents bear electric charges.
+A bare ion attracts a few water molecules, behaving like a new charged compound.
+It is this charged molecule, not the bare ion, which moves around through the solution.
+(hydration of an ion)
+
+Attached water, watery clothing.
 

### 2014-11-21 misc/SI_thesis.tex
camera ready
SI papers reading

@@
 \chapter{wo3}
+
+\ce{WO3} crystalline film ECD, electrochemical anodized, \cite{Ou2012}
+
 metal oxide contact on work function and band structure.\cite{Greiner2013}
@@
 \toprule
-Name & Raman Shift (\si{cm^{-1}}) &  Ref   \\
+Phase & Raman Shift (\si{cm^{-1}}) &  Reference   \\
 \midrule
@@
 \ce{Na2W2O7}  & 381(w), 422(w), 763(w), 835(s), 886(m), 948(m), 957(vs) &  \cite{Knee1979} \\
-\ce{Na2W4O13} & &\\
-\ce{Na5W14O44} & & this work\\
+\ce{Na2W4O13} & 949(m), 794(s), 777(vs), 366(w), 311(w), 272(w), 263(w) &\cite{Fomichev1992}\\
+\ce{Na5W14O44} & 965(m), 943(m), 913(w), 765(vs), 695(m), 107(s) & this work\\
 \bottomrule
@@
 
+\section{heterojunction}
+
+arix1410.8201: contact resistance at TMDC/metal interface due to Schottky barrier.
+\ce{MoS2} transistor is a Schottky barrier transistor with effective barrier height controlled by gate and drain biases.
+The carrier path for n-type \ce{MoS2} defined from source to drain.
+Thermal-assisted tunneling from source metal Fermi level to the channel.
+To reduce the contact resistance in \ce{MoS2} FET,
+\begin{itemize}
+\item low $\phi$ contact metal
+\item heterojunction with graphene 
+\item heavily doping the source/drain region
+\item substitute doping of \ce{Cl-} for \ce{S2-}, $\sigma = $
+\end{itemize}
+
+Fermi-level pinning at semi interface due to sulfur vacancies.\cite{Liu2013c}
+
+\ce{MoO_{3-x}} as high workfunctio material aligned deeply into the VB of \ce{MoS2} as a p-contact,\cite{Battaglia2014} \cite{Chuang2014a} \ce{MoO_{3-x}} forms defect states within the band gap,
+
+PEI as n-type surface dopant,
+
+electron density in \ce{WS2} to be 6E11 \si{cm^{-2}} ref95,\cite{SikHwang2012}
+
+scanning tunneling spectroscopy.
+\ce{WSe2} with Fermi level at 1.15 eV below conduction band.
+\cite{McDonnell2014} The use of binding energy shift in the core level as a measure of band bending at interfaces.
+\ce{MoS2} exhibit both p-type and n-type behavior due to local variation in stoichiometry.
+0.3\% areal density was found to be able to dominate the electron Schottky barrier height.
+
+\ce{MoS2}, photoionization energy $5.47\pm0.15$ eV, \cite{Schlaf1999}, and  bandgap of 1.17 eV, deriving the electron affinity as $\chi_A= 4.3\pm0.15$ eV.
+
+interface dipole \cite{Lin2013a}
+MX2 electrolyte photocurrent measurement, \ce{MoS2} gap 1.17 eV, \cite{Kautek1980}
+
+The electron affinity rule, band offset of \ce{SnS2} on \ce{MoS2}, linear models, comparison of model with experimental results difficult due to the uncertainties or superposition of physical effects.\cite{Schlaf1999} interdiffusion, chemical reaction across the interface.
+X-ray photoemission spectroscopy and ultraviolet photoelectron spectroscopy, valence band offset from XPS and UPS measurements; conduction bands are not accessible since photoelectron spectroscopy (PES) only allows the measurement of occupied DOS.
+and $\Delta C$ is calculated using $\Delta V$ and $E_g$.
+
+Some conventions used as following:
+\begin{enumerate} 
+\item Fermi level is zero energy;
+\item binding energies are positive;
+\end{enumerate}
+
+\begin{table}[htb]
+\centering
+\caption{WS2 and  \ce{WO3}}\label{tab:woram}
+\begin{tabular}{lccccr}
+\toprule
+Name & Nc & Nv &  $E_g$ (eV)   & $\chi$ & $\epsilon_{st}$  \\
+\midrule
+\ce{WO3} &    &     &  2.7    &      & 50\\    
+\ce{WS2} &    &     &  1.9~1.5   &      & \\    
+\bottomrule
+\end{tabular}
+\end{table}
+
+\subsection{method}
+angle-resolved photo-emission/photo-electron spectroscopy. (ARPES)
+\[
+E_binding = \hbar\omega - E_k - \phi
+\]
+where $E_k$ is kinetic energy of outgoing electron, which can be measured.
+$\phi$ is electron work function towards vacuum.
+$\hbar\omega$ is incident photon energy, and is varied.
+The UV-PS spectra represent the DOS integrated over all wave vectors.
+Normal emission UPS,
+
+hall effect,
+
+photoelectrolysis quantum efficiency,
+
+\subsection{parameters for wo3 and ws2}
+
+Lithium tunsten bronze, e mobility decrease with T; the decreasing mobility with higher T could be taken to indicate the principal mechanism for scattering the conduction carriers is by thermal motion of atoms in host lattice.
+\ce{MxWO3} derived from a host of \ce{WO3} lattice doped with alkali metal M.
+\cite{Sienko1961}
+
+\ce{WO3} valence band about 4 eV wide. \cite{Bringans1981}, \cite{DeAngelis1977}
+
+semiconductor-electrolyte interface, parallel capacitance C, flat band potential, Schottky-Mott plot,\cite{DiQuarto1981} 
+\[
+\frac{1}{C_p^2} = \frac{2}{\epsilon_0\epsilon e N_d} (U_E - U_{FB} - \frac{kT}{e})
+\]
+DOS $Neff$ as 1E20 \si{cm^{-3}eV^{-1}} and using 
+\[
+-qU_{FB} = E_F = E_{CB} + kT\log N_d/Neff
+\]
+
+quantum efficiency measurement of water photoelectrolysis.
+n-type oxide as anode, biased and forming a depleting region on the surface.
+$\alpha$ is proportional to $\eta$, and Tauc method was used to extrapolate band gap.
+\cite{Koffyberg1979}
+
+12\% usage of solar spectrum, conductivity $\sigma = 6\times10^{-1}$ \si{\per\ohm\per\cm}, taking electron mobility as $\mu=10$ \si{cm^2\per Vs},\cite{Berak1970} the carrier density is 4E15 \si{cm^{-3}}.\cite{Butler1976} \ce{WO3} and SCE reference electrode in one cell, and Pt in the other.
+Pt cell was bubbled with Ar to remove dissolved \ce{O2}.
+pH changes shift the Fermi level of electrolyte; run a cell without applied potential is desirable, and \ce{WO3} is inferior to \ce{TiO2} in this respect.
+The bands are essentially flat, and depletion layer necessary for charge separation does not exist.
+
+low energy photons sample mainly the valence electron structure of oxygen, and high-energy photons see the tungsten contribution more strongly.\cite{Bullett2000}
+
+\begin{table}[htb]
+\centering
+\caption{band gaps of \ce{WO3}}\label{tab:wobg}
+\begin{tabular}{cccc}
+\toprule
+Material state & energy gap (eV) & probing technique   & Reference   \\
+\midrule
+amorphous film & 2.62(i), 3.52(d)   &    photoelectrolysis  & $\rho=0.75$ \si{\ohm cm}\cite{Koffyberg1979}\\ 
+10 $\mu$m powder layer & 2.6   &   PL at liquid nitrogen & \cite{Paracchini1982b}\\ 
+amorphous film & 3.1 & photo-current &\cite{DiQuarto1981} \\
+amorphous film & 2.7 & photo-current &\cite{Butler1976} \\
+(001) surface of \ce{WO3} crystal &  & UV photoemission spectroscopy &\cite{Bringans1981} \\
+\bottomrule
+\end{tabular}
+\end{table}
+
+\subsection{calculation results}
+
 \chapter{to be used}
@@
 \section{literature read}
+
+Under O poor condition, formation energy of Vo is -0.02 eV, almost spontaneous.
+\ce{WO3} hole diffusion length 150 nm; etching hydrothermal grown wo3 flakes in weak acidic condition; Mott-Schottly plot, positive slope as expected for n type, carrier density as 5.92E20 \si{cm^{-3}} \cite{Li2014g},
+
+a comprehensive process of \ce{WO3} NP for ECD. \cite{Wojcik2014}
+
+2D \ce{WO3} flakes, electron Hall mobility 12 \si{cm^2V^{-1}s^{-1}}, high charge transport due to high relative permittivity suppressing the Coulomb charge effects.
+\cite{Zhuiykov2014} After \ce{H+} intercalation the band gap reduced to 2.5 eV.
+carrier mobility 275 \si{cm^2V^{-1}s^{-1}} for exfoliated Q2D \ce{WO3-x}, commercial Si-basded device about 500 \si{cm^2V^{-1}s^{-1}}.
+Ohmic contact between Q2D wo3-x and Au electrode,
+
+\cite{Hutter2014}
 

### 2014-11-21 misc/paper.tex
misc works of paper reading, wo3 raman table etc
SI papers reading

@@
 
-\section{misc}
+\section{misc: vls, crystal,}
 
@@
 nucleation and film growth \cite{Hanbucken1984}
+
+lateral growth, \cite{Zhang2014c}
 
@@
 \section{job related paper}
+
+arixv: 1411.3774: current transport across metal-semi interface treated as thermionic emission:
+\[
+J(V_D) = J_S(\exp\frac{qV_D}{nkT}-1)
+\]
+where 
+\[
+J_S = \frac{4\pi q m^* k^2T^2}{h^3}\exp(-\frac{q\Phi_B}{kT})
+\]
+
+arix: 1411.2815: graphene on Cu.
+
+The invention of efficient blue LEDs has led to white light sources for illumination.
+When exciting a phosphor material with a blue LED, light is emitted in the green and red spectral ranges, which, combined with the blue light, appears as white.
 
@@
 
+by Kevin
+
 quantum well devices exploit spatial quantization effects to increase the efficiency as well as alter the lasing threshold, and novel semiconductor is made to emit light at wavelengths different from those possible when only bulk material is used.
@@
 \textbf{junctions}
-p-n homojunctions, p-n or n-n heterojunctions, metal-semi junctions, most important types: Schottky barriers, or ohmic contact.
+\begin{itemize}
+\item p-n homojunctions,
+\item p-n or n-n heterojunctions,
+\item metal-semi junctions, 
+\item metal-insulator-semi 
+\end{itemize}
+
+most important types: Schottky barriers, or ohmic contact.
 
@@
 n electron carrier, p holes carrier.
+concentration gradient,
 
@@
 
+The built-in potential for a homojunction is equal to the full amount of band bending in equilibrium.
+
+Gaussian surface and space charge neutral,
+
 ch11.5 nonequilibrium conditions
 quasi-fermi level $\phi_n$ or $\phi_p$.
+
+A simple python script for this task can be found at \url{http://pythonhosted.org/eq_band_diagram/}.
+
+\section{Semiconductor Statistics}
+
+Band theory: broadening of the discrete quantized energy levels or the collective electron point of view. 
+Drude's model:
+\[
+\kappa/\sigma = 3 (\frac{k}{e})^2T
+\]
+
+infinitesimal range $dp$, the absence of a ground state in orthohelium; for a system of indistinguishable particles which occupy quantum states in accordance with the Pauli principle, the thermal equilibrium probability of occupancy for a state of energy E is
+\[
+f(E) = (1+\exp(\frac{E-\phi}{kT}))^(-1).
+\]
+
+Only for energies within a few $kT$ of $\phi$ is the probability of occupancy appreciably different from zero or unity.
+$\phi$ is determined by the condition that the number of occupied states at all energies must be equal to the total number of electrons present:
+\[
+n_0 = \int_{-\infty}^{\infty} f(E)g(E)dE
+\]
+
+At 0 K, Fermi level is given by 
+\[
+\phi_0 = \frac{h^2}{2m}(\frac{3n_0}{8\pi})^{2/3},
+\]
+whic is about 5 eV for monovalent metal.
+200 times of $kT$ for RT.
+Only electrons near Fermi level contribute significantly to conductivities.
+separation of the concepts of free electron and conduction electron, where in the energy range $\partial f/\partial E$ is finite can be regarded as conduction electrons.
+
+band theory based on a single electron approximation. crystal potential into Schrodinger Equation:
+\[
+\psi = U_k(r)\cdot\exp(ikr),
+\]
+
+In perfect crystal, $\psi$ with imaginary $k$ is discard, like the evanescent wave with decay, and the corresponding energy range is forbidden energy bands.
+For E with real $k$, plane wave solution exists forming permitted electron bands.
+The permitted wave function $\psi$ are the same in every unit cell of a periodic lattice, and the electron wave is not attenuated, i.e., an infinite mean free path emerging naturally in a perfect crystal.
+Scattering occurs due to defects, grain boundaries, imperfections developing localized energy states within the forbidden gaps, lattice vacancies, and the modulation of interatomic spacing be thermal vibration.
+
+Brillouin zone drawing.
+Each BZ occupies the same volume of k-space, accommodating 2N electron states, where N is the total number of atoms in the crystal.
+Inner shell electrons are closely associated with a single nucleus; whereas the outermost electrons belong to the crystal as a whole.
+
+electron can interchange states, with no observable result. electron and hole as real particles,
+
+donor center moves or not?
+
+multi-electron theories validate all the qualitative feature of simple band theory.
+How much does an electron deform the lattice in its vicinity?
+This is the question of the distinction between a free electron and a polaron.
+
+One-electron band theory ignores multiplet structure: exciton, and orbital overlapping.
+
+electrical properties of some metal and semiconductors are virtually unchanged in melting, suggesting a band structure is preserved even though there is no long range order.
+The dividision of permitted electron states into groups is dicated by the nature of short-range order, which hold in highly ordered crystal, in an amorphous phase or liquid phase of the same solid.
+
+group velocities of an electron wave-packet in space is 
+\[
+v = \frac{\hbar}{\Delta_k E}
+\]
+, electron energy E(k) can be plotted as a multi-value function within the first BZ.
+
+effective mass tensor has positive principal values at the lowest energy in a band, and negative ones at the top of a band.
+In both tight binding method and nearly free electron method, the E dispersion on wave-vector k can be written as
+\[
+E = E_c + \frac{\hbar^2(k-k_c)^2}{2m_c}
+\]
+just above the bottom of a band; and 
+\[
+E = E_v - \frac{\hbar^2(k-k_v)^2}{2m_v}
+\]
+near the top of a band.
+
+General expression of DOS is 
+\[
+g(E) =  \int \frac{dS}{4\pi^3\Delta_kE}
+\]
+and using effective mass renormalization, the wave-functions can be solved by
+\[
+\frac{\hbar^2}{2m^*} \Delta^2\psi + E\psi = 0
+\]
+
+Si conduction band minimum along [100] direction, about 25\% near the edge. Flaw encompasses foreign atoms, vacancies, interstitials.
+
+When $n_0$ is large and $T$ is small, electron distribution is degenerate, all states are occupied up to an energy one or two kT short of the Fermi level; when $n_0$ is small and $T$ is not too low, occupied state lie within three or four kT above Ec, and Fermi level below Ec.
+
+tabulation of Fermi-Dirac integral,
+
+\[
+n_0 = N_c F_{1/2}(\eta) = 2(2\pi mkT/h^2)^{3/2}F_{1/2}(\frac{\phi - E_c}{kT})
+\]
+
+For classical or non-degenerate semiconductor, the total number of electrons in CB is given by
+\[
+n_0 = N_c\exp(\frac{\phi - E_c}{kT})
+\]
+and $N_c$ acts as effective density of states. In analog, hole density can be written as
+
+\[
+p_0 = N_v\exp(\frac{-\phi - E_v}{kT})
+\]
+
+To evaluate the Fermi level dependency on $T$ at non-degenerate conditions, 
+\[
+\frac{d\phi}{d(kT)} \approx - (3/2 + \log(N_c/n_0))
+\]
+
+For intrinsic semiconductor, $n_0= p_0 = n_i$ set the position of Fermi level, which is the root of equation
+\[
+ N_c F_{1/2}(\eta) =  N_v F_{1/2}(-E_i - \eta)
+\]
+In non-degenerate limiting form, 
+\[
+\phi_i = E_c - 1/2E_i + 3/4kT\log(N_v/N_c)
+\]
+based on thermal equilibrium, where the same electrochemical potential should be experienced by all states.
+
+degeneracy occurs when $E_c - \phi$ became negative.
+
+For extrinsic situation, 
+\[
+\frac{n_0p_0}{n_i^2} \leq 1
+\]
+
+Define $N_r = n_0 - p_0$ as the difference between densities of impurity states, then in terms of $n_i$ and $N_r$, at low temperature when intrinsic excitation is feeble, 
+\begin{align}
+n_0 &\approx N_r + n_i^2/N_r\\
+p_0 &\approx n_i^2/N_r
+\end{align}
+
+minimum energy and maximum entropy, electrical neutrality, iterative technique,
+
+$N_d$ donor impurity atoms per unit volume, $N_di$ density of ionized donor atoms, wave function of s character,
+
+Electron trapped in ground state and excited states, anisotropic elastic strain, attacked piecemeal,
+
+extrinsic semiconductor is always partially compensated; $N_a$ total density of electron for acceptors. elementary manipulation leads to; rearranged to read as
+
+a donor impurity is electrically neutral whether it has an electron bound in the ground state at Ec - Ed or in an excited state closer to the conduction band.
+
+semilogarithmic plot, donor states impacted by excited states, split ground states, anisotropic strain,
+
+amphoteric impurities, either donor or acceptor depending on F level, such as Au in germanium.
 
@@
 ray tracing in vector form as $n^{\prime} r^{\prime} \times n = n r \times n$, invariant $na\theta$,
+
+\section{Transparent conductive oxides}
+
+set the scene, ingredient, synthetic chemical routes, be of value, TCO, creep into, . \cite{Edwards2004}
+
+$\sigma = ne\mu$, with $n$ as \si{cm^{-3}}, $e$ as C, and $\mu$ in \si{cm^2\per V\per s}. Then $\sigma$ in unit of \si{A\per V \per cm}.
+
+A materials sorting map based on $n-\mu$.
+ITO with $\mu\sim10^4$ \si{\per\ohm cm^{-1}}.
+If the conductivity is sufficiently high, the thermal emittance is accordingly low.
+High $\sigma$ in ITO is related to the presence of shallow donor or impurity states ($\sim kT$) located close to the \ce{In2O3} CB, produced via \ce{Sn4+} doping for \ce{In3+} or oxygen vacancy.
+Thermal ionization promote the excess or donor electron into CB, giving rise to far-infrared absorption.
+At the same time, the host band gap is left intact.
+
+nonmetal-to-metal transition, itinerant-electron scattering,
+
+\ce{SnO2} into \ce{In2O3} as substitutional dopant, Sn with outer-shell electron configuration as $5s^25p^2$, and In as $5s^25p^1$.
+The Schrodinger wave solutions gives Bohr radius, $a_H \sim 13$ \si{\angstrom} for isolated ions, a large orbit extending many crystal cells, but localized at donor center?
+
+\[
+n^{1/3}\cdot a_H = \text{const.}
+\]
+or 
+\[
+k_Fl_e \approx 1
+\]
+where Fermi wavenumber $k_F = (3\pi^2n)^{1/3}$, $le$ is the mean free path.
+
+The conductivity when $T\rightarrow 0K$ is used to discern metal from nonmetal, where the former always display finite conductivity, and the latter presumably extrapolated to zero.
+
+optical window for ITO is set at short wavelength by direct band gap and at longer wavelength by its plasma edge, determined by the $n$.
+
+In essence, the role of host matrix in (Metal-to-Nonmetal)MNM transition is important primarily in that it determines the form of the radial distribution of localized impurity state.\cite{Edwards1978}
+
+\[
+n_c^{1/3}\cdot a_H = K
+\]
+
+Isotropic Bohr radius is calculated from experimental ionization energy of localized state via $e^2/2\epsilon_{st} E_{expt}$.
+The critical density $n_c$ for \ce{WO3:Na} is estimated to be $4\times 10^{22}$ \si{cm^{-3}}, with experimental value $a_H^* = 1.3$ \si{\angstrom}.
+
+W as the unperturbed bandwidth of an array of one-electron state, and U as the intradonor Coulomb repulsion energy, which is the primary driving force in transition from metallic to insulating states.
+
+\begin{align}
+\psi(r) &= \sum_j \alpha_j F_j(r)\phi_j(r)\\
+F(r) &= (\pi a_H^{*3})^{-1/2} \exp(-r/a_H^*)
+\end{align}
+
+An overlap-correlation problem,
+
+delicate interpretation of experimental findings, strong dependency of RM m-\ce{WO_{3-x}} electronic properties on $V_O$ concentration and crystallographic direction along which $V_O$ is created.\cite{Wang2011b}
+
+Coloration and electron conductivity changes.
+\citeauthor{Wang2011b} found strong dependence of WO3-x electronic properties on $V_O$ concentration and the the crystallographic direction on which O is removed.
+DFT band gap calculation is close to experimental value.
+Vacancy levels are found at 2.1 eV.
+When $V_O$ is in x axis, the associated electronic state is about 1 eV below CBM,
+
+\section{ZnTe}
+
+Zn rich suppress NW growth, Zeiss U55 SEM, XF3050 silicon drift detector, Quantax software from Bruker.EDX mapping show uniform Zn and Te distribution along NW, no atomic ratio is inferred.
+\cite{Rueda-Fonseca2014}
+
+ZnTe, p type, band gap 2.25 eV. I_LO intensity ratio: area or height?
+
+PL 1.88 eV, O impurity substituted isoelectronically. second order scattering, energy of scattered photons differs from the incident ones by two vibrational quanta.  \cite{Irwin1970}
+
+photon occupation number, $n_j = (\exp(h\nu/kT) - 1)^{-1}$,
+
+The coupling strength of the electron-phonon interaction can be evaluated by comparing the relative intensities of the overtones to the fundamental Raman band.
+DUring the steady-state Raman measurement, the trapped charge would build up producing a local electric field, which polarize the exciton.
+\cite{Zhang2012}
+
+integrated intensities.

### 2015-01-10 ch-intro/ch-instr.tex
camera ready
After first review in 2014

@@
 
-\section{Synthesis Equipments}
-\subsection{Home-built CVD System}
+\section{Synthesis Equipments and Processes}
+\subsection{Home-built Chemical Vapor Deposition System}
 The syntheses were accomplished in a home-made hot-wall \gls{cvd} system.
@@
 (a) Photograph of reaction chamber.
-(b) Sketch of CVD system, where A1: quartz tube; B1: bubbler; C1-2: gas cylinders; E1: mechanical pump; H1-2: ceramic heater; MFC: flow controller; P1: pressure gauge; V1-4: valves; V5-7: butterfly valves.}
+(b) Sketch of CVD system, where A1: quartz tube; B1: bubbler; C1-2: gas cylinders; E1: mechanical pump; H1-2: ceramic heater; MFC: flow controller; P1: pressure gauge; V1-4: needle valves; V5-7: butterfly valves.}
 \label{fig:ch2cvd}
@@
 \centering
-\includegraphics[width=0.8\textwidth]{temp_profile.pdf}
-\caption{Temperature profile of home-built CVD in ambient environment.}
+\includegraphics[width=0.7\textwidth]{temp_profile.pdf}
+\caption[Temperature profile of home-built CVD in ambient environment]{Temperature profile of home-built CVD in ambient environment.}
 \label{fig:ch2temp}
@@
 
-Silicon and silicon dioxides on Si wafer ($p$-Si(100), University Wafer Inc.) were primarily used, and other substrates, i.e., Mica\footnote{\ce{K(Al2)(Si3Al)O10(OH)2}}, glass (Fisher Scientific, microscope slide, 12-549),\footnote{Typical composition is 72.6\% \ce{SiO2}, 0.8\% \ce{B2O3}, 1.7\% \ce{Al2O3}, 4.6\% \ce{CaO}, 3.6\% \ce{MgO} and 15.2\% \ce{Na2O}} stainless steel, were also employed.
+Silicon (Si) and 1 $\mu$m silicon dioxides on Si wafer (\ce{SiO2}-Si) (University Wafer Inc.) were primarily used, and other substrates, i.e., Mica\footnote{\ce{K(Al2)(Si3Al)O10(OH)2}}, glass (Fisher Scientific, microscope slide, 12-549),\footnote{Typical composition is 72.6\% \ce{SiO2}, 0.8\% \ce{B2O3}, 1.7\% \ce{Al2O3}, 4.6\% \ce{CaO}, 3.6\% \ce{MgO} and 15.2\% \ce{Na2O}} stainless steel, were also employed.
 Si and \ce{SiO2}-Si substrates were first cut into rectangular pieces of certain size and then ultrasonically cleaned (Branson 1510R-MTH) with acetone and alcohol for about 15 min, each followed by blow-drying with nitrogen gas.
@@
 A plasma cleaner (Kurt J Lesker, Plasma-Preen 862) was used to render a hydrophilic Si surface, where reaction among $e$, \ce{O+}, \ce{O2+}, \ce{O^-},\ce{O2} occurs, and \ce{OH}-terminated surface followed.\cite{Habib2010} The treatment proceeds at 2 Torr \ce{O2} for 3 min.
-Glass substrates cleaning is the same as that of Si.
-Mica is cleaved right before the growth without extra cleaning steps.
+Glass substrate cleaning procedure is the same as that of Si.
+Mica substrates are cleaved right before the growth without extra cleaning steps.
 In addition, substrates can be coated with a thin layer of metal before growth.
@@
 
-In this work, magnetron sputtering (Denton Vacuum Desk IV) was used to coat thin layers of metals onto cleaned substrates, such as W, Mo, Au, Ag, Pd, and Pt.
+In this work, magnetron sputtering (Denton Vacuum Desk IV) was used to coat thin layers of metals onto cleaned substrates.
 As shown in Fig.~\ref{fig:ch2magsp}, a high potential created between the target (cathode) and substrate ionizes the argon molecules.
@@
 
-Sputtering is a better PVD technique than e-beam deposition since it alleviates the adverse effects in the latter.
+Sputtering is a better PVD technique than \gls{ebeam} deposition since it alleviates the adverse effects in the latter.
 \ce{Ar+} ions are accelerated to target foils.
@@
 These collisions between target ions and \ce{Ar+} leads to almost all arrival angle, thus uniform coverage.
-The sputter yield is number of target ions released per ions hitting on target.
+The sputtering yield is number of target ions released per ions hitting on target.
 If \ce{Ar+} ion energy is less than 100 eV, the yield is zero; If larger than 10 keV, implantation of \ce{Ar+} into target foils occurs.
@@
 \includegraphics[width=0.5\textwidth]{sem_sch.png}
-\caption[Schematic drawing of electron materials interaction in SEM]{Schematic drawing of electron materials interaction in SEM. Some process is not shown, such as Auger emission.}
+\caption[Schematic drawing of electron-matter interactions in SEM]{Schematic drawing of electron-matter interactions in SEM.\cite{Good2000} Some processes are not shown, such as Auger emission.}
 \label{fig:ch2sem}
@@
 In this study, secondary electron images were mainly used to reveal the morphology of the samples.
-Unless otherwise noticed, the SEM images in this work were all acquired using 10 kV acceleration voltage, 10 mm working distance and 30 spot size.
+Unless otherwise noticed, the SEM images in this work were acquired using 10 kV acceleration voltage, 10 mm working distance and 30 spot size.
 
@@
 \includegraphics[width=0.5\textwidth]{xrd_2theta.png}
-\caption{Bragg-Brentano geometry used in XRD configuration}
+\caption[Bragg-Brentano geometry used in XRD configuration]{Bragg-Brentano geometry used in XRD configuration.\cite{Good2000}}
 \label{fig:ch2theta}
@@
 Besides the \gls{saed} pattern and \gls{hrtem} imaging, other TEM based techniques include \gls{cbed}, EDX, \gls{eels} and \gls{cl}, etc.
-Therefore, TEM is essentially a signal-generating and detecting tool.
-Fundamental physics of electron is needed to obtain a comprehensive understanding of these TEM related techniques.
+Therefore, TEM is essentially a signal-generating and detecting tool.\cite{Williams2009} Fundamental physics of electron is needed to obtain a comprehensive understanding of these TEM related techniques.
 Only a brief summary is given here.
@@
 \] 
-where $\theta$ is scattering angle in radians, $\Omega$ is solid angle in steradians (sr), and $\theta$ is half of the scattering angle.
+where $2\theta$ is scattering angle in radians, $\Omega$ is solid angle in steradians (sr), and $\theta$ is half of the scattering angle.
 The total cross section is just $\sigma$ times atom numbers in unit volume.
@@
 
-\Gls{drs} serves as another tool to estimate the sample band gap using \gls{kmt}.\cite{Tandon1970} The original KM theory was proposed in 1931,\cite{Kubelka1931} and has been popular in the color-related industry, such as painting, pigments, and paper.
+Diffuse reflectance spectroscopy (DRS) serves as another tool to estimate the sample band gap using \gls{kmt}.\cite{Tandon1970} The original KM theory was proposed in 1931,\cite{Kubelka1931} and has been popular in the color-related industry, such as painting, pigments, and paper.
 This method is useful for the analysis of samples of difficultly soluble substances and for samples that will react with the solvents upon being dissolved.
@@
 The sample is under isotropic diffuse illumination.
-And the upward flux $J$ and downward flux $I$ are characterized by the K-M scattering and absorption coefficients denoted as $S$ and $K$, respectively; that is
+And the upward flux $J$ and downward flux $I$ are characterized by the KM scattering and absorption coefficients denoted as $S$ and $K$, respectively; that is
 \begin{align}
@@
 
-In this thesis, UV-Vis and diffuse reflectance spectra were recorded using Schimadzu, UV2600Plus, with schematic measurement setup shown in Fig.~\ref{fig:ch2uvvis}.
-For UV-Vis measurement in transmission mode, the as-synthesized sample was removed from substrates by light sonication(Branson 1510R-MTH, 70W) in ethanol or DI water for 15 seconds.
+In this thesis, UV-Vis and \gls{drs} were recorded using Schimadzu, UV2600Plus, with schematic measurement setup shown in Fig.~\ref{fig:ch2uvvis}.
+For UV-Vis measurement in transmission mode, the as-synthesized sample was removed from substrates by light sonication (Branson 1510R-MTH, 70W) in ethanol or DI water for 15 seconds.
 The dispersion was left for 12 h to enable the possible sedimentation.
 Then the dispersion was transferred into one 10 mm quartz cuvette (Thorlabs, W005654) for absorption measurement with another paired cuvette containing pairing liquid only.
-To carry out diffuse reflectance measurement, integrating sphere (ISR2600Plus) was used with an incident angle of 0 degree.
+To carry out diffuse reflectance measurement, an integrating sphere (ISR2600Plus) was used with an incident angle of 0 degree.
 The baseline reflectance was first recorded with the standard white plate (barium sulfate powder, \ce{BaSO4}) placed at the exit window on the sample path side, then the target sample was set in for relative reflectance measurement.

### 2015-01-10 ch-intro/ch-intro.tex
After first review in 2014

@@
 
-Transition metal generally refers to any element in the d-block of periodic table, and \glspl{tmo} mean the chemical compounds that consist of at least one transition metal element and oxygen.
-Similarly, \glspl{tmdc} are compounds that combine at least one transition metal with chalcogen elements from group VIA (S, Se, Te, Po).\footnote{Oxygen also belongs to group VIA, but is often treated separately.} This study focused on the following three materials: molybdenum oxide, tungsten oxide and tungsten disulfide.
+Transition metals generally refer to any element in the d-block of periodic table, and \glspl{tmo} mean the chemical compounds that consist of at least one transition metal element and oxygen.
+Similarly, \glspl{tmdc} are compounds that combine at least one transition metal with chalcogen elements from group VIA (S, Se, Te, Po).\footnote{Oxygen also belongs to group VIA, but is often treated separately.} This study focused on the following three materials: molybdenum oxide, tungsten oxide, and tungsten disulfide.
 Both tungsten (W) and molybdenum (Mo) belong to Group VIB transition metal with outer shell electrons configuration as $4d^55s^1$ and $5d^46s^2$, respectively.
 
-The two metal oxides, \ce{MoO3} and \ce{WO3}, have been studied for decades for energy related applications, e.g., photoelectrochemistry,\cite{Su2010} photocatalysis,\cite{Watcharenwong2008, Macphee2010} photovoltaics\cite{Coridan2013} and electrochromism.\cite{Yoshimura1985, Mortimer2011} \ce{WS2} has also been investigated in various forms, i.e., thin film, nanotube, and 2D atomic layer recently.
-\ce{WS2} exhibits potentials in solar cell,\cite{Britnell2013} water cleavage,\cite{Ballif1999} and field effect transistor.\cite{Perkins2013} Heterostructures formed between \gls{tmo} and \gls{tmdc} provide another degree of freedom to fine tune the band structures, which could enhance the photon energy harvesting performances.
+The two metal oxides, \ce{MoO3} and \ce{WO3}, have been studied for decades for energy related applications, e.g., photoelectrochemistry,\cite{Su2010} photocatalysis,\cite{Watcharenwong2008, Macphee2010} photovoltaics\cite{Coridan2013} and electrochromism.\cite{Yoshimura1985, Mortimer2011} \ce{WS2} has also been investigated in various forms, i.e., thin films, nanotubes, and 2D atomic layers recently.
+\ce{WS2} exhibits potentials in solar cells,\cite{Britnell2013} water cleavage,\cite{Ballif1999} and field effect transistors.\cite{Perkins2013} Heterostructures formed between \gls{tmo} and \gls{tmdc} provide another degree of freedom to fine tune the band structures, which could enhance the photon energy harvesting performances.
 
@@
 
-Commercial buildings in U.S.\ consumed approximately 35\% of the electricity use.\footnote{U.S.
-Department of Energy, "Energy Efficiency Trends in Residential and Commercial Buildings", 2008.} And traditional windows in the buildings account for up to 40\% of the total heating, cooling and lighting consumption, which is of low energy efficiency.
-The smart window is an energy efficient answer by allowing for separate control of the visible and NIR illumination/transmission.
-Several solutions have been proposed in both academia and industry to develop smart window, including liquid crystal, suspended particles and electrochromic materials.\cite{Lampert1998} Previous efforts\cite{Deb2008} show the electrochromic materials is the most promising component in smart window design in comparison to other options, in that it requires little power to switch between bleaching and coloration status (changing the optical transmission) and the failure mode is being clear instead of opaque, which is of great importance in commercial applications.
+Commercial buildings in U.S.\ consumed approximately 35\% of the electricity usage.\cite{us2008} And traditional windows in the buildings account for up to 40\% of the total heating, cooling, and lighting consumption, which is of low energy efficiency.
+Smart window is an energy efficient answer by allowing for separate control of the visible and NIR illumination/transmission.
+Several solutions have been proposed in both academia and industry to develop smart windows, including liquid crystal, suspended particles, and electrochromic materials.\cite{Lampert1998} Previous efforts\cite{Deb2008} show the electrochromic materials is the most promising component in smart window design in comparison to other options, in that it requires little power to switch between bleaching and coloration status (changing the optical transmission) and the failure mode is being clear instead of opaque, which is of great importance in commercial applications.
 
-Electrochromism, where the optical property of the materials is changed upon applying low DC voltage (\textless 5 V), have been found in numerous inorganic and organic substances, e.g., \ce{V2O5}, \ce{WO3}, and \ce{NiO} for the former group, and prussian blue, polyaniline for the latter one.
+Electrochromism, where the optical property of the materials is changed upon applying low DC voltage (\textless 5 V), has been found in numerous inorganic and organic substances, e.g., \ce{V2O5}, \ce{WO3}, and \ce{NiO} for the former group, and prussian blue and polyaniline for the latter one.
 This study covers two inorganic metal oxides, \ce{WO3} and \ce{MoO3}.
@@
 Prototype \gls{ecd} usually consists of a stacked configuration as shown in Fig.~\ref{fig:introecd}.
-Typical transmission spectra of prototype \gls{ecd} based on \ce{WO3} thin film are shown in Fig.~\ref{fig:introtran}\cite{Lampert1998}, where $T$ in bleaching and coloration states exhibit dynamic changes.
+Typical transmission spectra of the prototype \gls{ecd} based on \ce{WO3} thin film are shown in Fig.~\ref{fig:introtran},\cite{Lampert1998} where optical transimission $T$ in bleaching and coloration states exhibit dynamic changes.
 The reflectance spectra of \ce{WO3} \gls{ecd} strongly depends on the device design.\cite{OBrien1999} As to the absorption, it was deduced that the infrared part was absorbed to a large extent, which was radiated again.
@@
 \includegraphics[width=0.5\textwidth]{blackbody1}
-\caption{Spectral radiance of blackbody at 0, 50 and 100 \si{\degreeCelsius}.}
+\caption[Spectral radiance of blackbody at 0, 50 and 100 \si{\degreeCelsius} predicated by Planck's Law]{Spectral radiance of blackbody at 0, 50 and 100 \si{\degreeCelsius} predicated by Planck's Law.}
 \label{fig:introbb}
@@
 \item low cost ion electrolyte of poor electron mobility;
-\item high yield growth method of \ce{WO3} and integration with other manufacturing process; and 
+\item high yield growth method of \ce{WO3} and integration with other manufacturing process; 
 \item life cycle $> 10^5$ for long time outdoor usage.
@@
 \end{figure}
-Moreover, favorable oxygen evolution of \ce{WO3} brings good performance in degradation of organic compounds\cite{Hepel2001,Luo2001,Watcharenwong2008}.
-The formation of long-lived holes is recognized as a key requirement.\cite{Pesci2011} Besides, \ce{WO3} is remarkably stable in acid, making it a significant candidate for treating water pollutant caused by organic acids.\cite{Monllor-Satoca2006}
+Moreover, favorable oxygen evolution of \ce{WO3} brings good performance in degradation of organic compounds.\cite{Hepel2001,Luo2001,Watcharenwong2008} The formation of long-lived holes is recognized as a key requirement.\cite{Pesci2011} Besides, \ce{WO3} is remarkably stable in acid, making it a significant candidate for treating water pollutant caused by organic acids.\cite{Monllor-Satoca2006}
 
-For photochemical water reduction to occur, the flat-band potential of the semiconductor (for highly doped semiconductors, this equals to the bottom of the conductance band) must exceed the proton reduction potential of 0.0 V vs NHE at pH0.
+For photochemical water reduction to occur, the flat-band potential of the semiconductor (for highly doped semiconductors, this equals to the bottom of the conductance band) must exceed the proton reduction potential of 0.0 V vs NHE at pH 0.
 Flat-band potentials strongly depend on ion absorption (protonation of surface hydroxyl groups), crystallographic orientation of the exposed surface, surface defects, and surface oxidation processes.\cite{Osterloh2008}

### 2015-01-10 ch-moox/moox.tex
After first review in 2014

@@
 
-The oxidization of Mo starts at 500 \si{\degreeCelsius}, and \ce{MoO3} vapor pressure begins to increase rapidly above 700 \si{\degreeCelsius}.\cite{Margrave1967} The melting point of \ce{MoO3} is reported as 795 \si{\degreeCelsius}.
-Based on these data, the growth was designed with parameters listed in Table~\ref{tab:mooxsi}.
+The oxidization of Mo starts at 500 \si{\degreeCelsius}, and \ce{MoO3} vapor pressure begins to increase rapidly above 700 \si{\degreeCelsius}.\cite{Margrave1967} The melting point of \ce{MoO3} is reported as 795 \si{\degreeCelsius}.\cite{Levin1959} Based on these data, the growth was designed with parameters listed in Table~\ref{tab:mooxsi}.
 It is worth mentioning that these parameters are selected and optimized from a wide range of combinations.
@@
 Notice that on the horizontal axis of temperature, zero inch is defined at the upstream edge of furnace.
-To facilitate discussion and provide a tight context, the author define the position of substrate as the coordinate of its upper-stream edge along this temperature axis, i.e., the substrate location is 7 in in Fig.~\ref{fig:mooxgrowth}.
-The usual length of Si substrate is 1 in.
-When positioned at 7 in, it is then located in a temperature zone of $650 \sim 350$ \si{\degreeCelsius}.
+To facilitate discussion and provide a tight context, the author define the position of substrate as the coordinate of its upper-stream edge along this temperature axis, i.e., the substrate location is 7 inch in Fig.~\ref{fig:mooxgrowth}.
+The usual length of Si substrate is 1 inch.
+When positioned at 7 inch, it is then located in a temperature zone of $650 \sim 350$ \si{\degreeCelsius}.
 % cvd layout
@@
 \centering
-\caption{Experimental Raman peaks assignment of \ce{MoO3} on Si.\cite{Eda1992,Siciliano2009}}\label{tab:moram}
+\caption[Experimental Raman peaks assignment of \ce{MoO3} on Si]{Experimental Raman peaks assignment of \ce{MoO3} on Si.\cite{Eda1992,Siciliano2009}}\label{tab:moram}
 \begin{tabular}{llcll}
@@
 \midrule
-117      & $B_{2g}$    &           & $T_c$  & RCM  \\
+117      & $B_{2g}$    &           & $T_c$  & RCM\textsuperscript{\emph{a}}  \\
 129      & $B_{3g}$    &           & $T_c$  & RCM  \\
@@
 \end{tabular}
+
+  \textsuperscript{\emph{a}} R chain mode;
+
 \end{table}
@@
 \includegraphics[width=0.9\textwidth]{MoO3_SEM_a.jpg}
-\caption[SEM imaging on \ce{MoO3} catalytic growth]{SEM imaging on \ce{MoO3} catalytic growth.
-Effect of alkaline metal-based catalysts on the morphology of \ce{MoO3} depositions: (a) SEM image of rectangular nanoplates grown without catalysts.
+\caption[Effect of alkali metal based catalysts on the morphology of \ce{MoO3} depositions]{Effect of alkali metal based catalysts on the morphology of \ce{MoO3} depositions: (a) SEM image of rectangular nanoplates grown without catalysts.
 (b-f) SEM images of different morphologies grown with NaOH catalysts: (b) nanobelts grown on top of dense array of nanoplates,(c) close-up view of the forked nanoplates from an area indicated by the square in Fig.~\ref{fig:ch4sem2by3}, (d) long nanobelts, (e) side-view of ultra-long microbelts, and (f) side-view of microtowers.
@@
 \includegraphics[width=0.8\textwidth]{MoO3_TEM_XRD.jpg}
-\caption[XRD and TEM on \ce{MoO3} catalytic growth]{XRD and TEM on \ce{MoO3} catalytic growth.
+\caption[XRD and TEM on \ce{MoO3} growths with and without catalyst]{XRD and TEM on \ce{MoO3} growths with and without catalyst.
 XRD spectra of (a) a specimen grown without catalysts and (b) a specimen grown with NaOH catalysts.
@@
 Since the concentration of Na is highest among these extra elements, it is most likely to induce the new morphology growth.
-A literature search indeed shows that there exists a Na-Mo-O phase diagram as shown in Fig.~\ref{fig:ch4pd}.\cite{Hoermann1929} Notice the phases of the Na-Mo-O system can be written as \ce{Na2O.nMoO3}, where n = 1, 2, 3, and 4.
+A literature search indeed shows that there exists a Na-Mo-O phase diagram as shown in Fig.~\ref{fig:ch4pd}.\cite{Hoermann1929} Notice that\footnote{http://forum.wordreference.com/showthread.php?t=244497} the phases of the Na-Mo-O system can be written as \ce{Na2O.nMoO3}, where n = 1, 2, 3, and 4.
 
@@
 \includegraphics[width=0.5\textwidth]{moo3_pdsmall}
-\caption[Phase diagram of \ce{Na2MoO4} and \ce{MoO3}]{Phase diagram of \ce{Na2MoO4} and \ce{MoO3} reproduced from Ref.~\cite{Hoermann1929}}
+\caption[Phase diagram of \ce{Na2MoO4} and \ce{MoO3}]{Phase diagram of \ce{Na2MoO4}-\ce{MoO3} reproduced from Ref.~\cite{Hoermann1929}}
 \label{fig:ch4pd}
@@
 Each site of \ce{Na2MoO4} will continue absorb incoming \ce{MoO3}, forming a swelling droplet.
-\ce{MoO3} will precipitate from these seeds when a critical supersaturation concentration is reached, which is about 75\% according to Fig.~\ref{fig:ch4pd}.\footnote{This ratio considerably exceeds that of the usual metal catalyst scenario.
+\ce{MoO3} will precipitate from these seeds when a critical supersaturation concentration is reached, which is about 75\% in unit of mole according to Fig.~\ref{fig:ch4pd}.\footnote{This ratio considerably exceeds that of the usual metal catalyst scenario.
 This high solubility accounts for several observations in current experiments: the dimensions of individual deposit is much larger than that of initial droplet, the concentration of sodium in final products is extremely low.}    Based on this aforementioned analysis, the author propose a hypothesis:
@@
 \includegraphics[width=0.7\textwidth]{vls_mode2}
-\caption{Schematic drawing on the growth steps of the proposed growth mode.}
+\caption[Schematic drawing on the growth steps of the proposed growth mode]{Schematic drawing on the growth steps of the proposed growth mode.}
 \label{fig:ch4vls}
@@
 
-\subsection{Growth on Alkaline Metal Containing Substrates}
+\subsection{Growth on Alkali Metal Containing Substrates}
 In analog with the \ce{Na2MoO4}-\ce{MoO3} binary phase diagram, other alkaline metals, such as Li and K, could also form A-Mo-O alloy at elevated temperature.
@@
 \includegraphics[width=0.7\textwidth]{moo3_glass}
-\caption{Optimized \ce{MoO3} nanoplates growth on glass.}
+\caption[Optimized \ce{MoO3} nanoplates growth on glass]{Optimized \ce{MoO3} nanoplates growth on glass.}
 \label{fig:ch4glass}

### 2015-01-10 ch-tms/tms.tex
After first review in 2014

@@
 \includegraphics[width=0.7\textwidth]{cs_sfig1_all}
-\caption[Schematic diagrams of tungsten power oxidization, seeded growth of \ce{WO3} NW, and sulfurization process.]{Schematic diagrams of (a) tungsten power oxidization, (b) seeded growth of \ce{WO3} NW, and (c) sulfurization process.
+\caption[Schematic diagrams of tungsten power oxidization, seeded growth of \ce{WO3} NW, and sulfurization process]{Schematic diagrams of (a) tungsten power oxidization, (b) seeded growth of \ce{WO3} NW, and (c) sulfurization process.
 (d) Chemical vapor deposition system temperature profile measured at ambient condition.
@@
 \includegraphics[width=0.9\textwidth]{ws2_coreshell_tem}
-\caption{HRTEM imaging on one core-shell nanowire showing layer number changes.}
+\caption[HRTEM imaging on one core-shell nanowire showing layer number variation]{HRTEM imaging on one core-shell nanowire showing layer number variation.}
 \label{fig:ch5ws2tem1}
@@
 \includegraphics[width=0.8\textwidth]{ws2_growth3}
-\caption{HRTEM imaging on the tip area of one core-shell nanowire.}
+\caption[HRTEM imaging on the tip area of one core-shell nanowire]{HRTEM imaging on the tip area of one core-shell nanowire.}
 \label{fig:ch5ws2tem3}
@@
 \includegraphics[width=0.8\textwidth]{ws2_growth4}
-\caption{HRTEM imaging on one tapered core-shell nanowire showing fluctuation of layer numbers}
+\caption[HRTEM imaging on one tapered core-shell nanowire showing fluctuation of layer numbers]{HRTEM imaging on one tapered core-shell nanowire showing fluctuation of layer numbers.}
 \label{fig:ch5ws2tem4}
@@
 \includegraphics[width=0.8\textwidth]{ws2_growth1}
-\caption{HRTEM imaging on one core-shell nanowire showing consumed core.}
+\caption[HRTEM imaging on one core-shell nanowire showing consumed core]{HRTEM imaging on one core-shell nanowire showing consumed core.}
 \label{fig:ch5ws2tem2}
@@
 \includegraphics[width=0.6\textwidth]{ws2_sio2_all}
-\caption{Raman spectrum acquired on the middle spot of core-shell NW (inset) using 532 nm. The $x$ axis is in logarithmic scale.}
+\caption[Raman spectrum acquired on the middle spot of core-shell NW (inset) using 532 nm.
+The $x$ axis is in logarithmic scale]{Raman spectrum acquired on the middle spot of core-shell NW (inset) using 532 nm.
+The $x$ axis is in logarithmic scale.}
 \label{fig:ws2ramall}
@@
 \includegraphics[width=0.5\textwidth]{ws2_sio2_all_blue}
-\caption{Raman spectrum acquired on the middle spot of core-shell NW shown in the inset of Fig.~\ref{fig:ws2ramall}.}
+\caption[Raman spectrum acquired on the middle spot of core-shell NW shown in the inset of Fig.~\ref{fig:ws2ramall}]{Raman spectrum acquired on the middle spot of core-shell NW shown in the inset of Fig.~\ref{fig:ws2ramall}.}
 \label{fig:ws2ramblue}
@@
 \subfloat[]{\label{fig:blue}\includegraphics[width=0.45\textwidth]{ws2_sio2_raman_blue}}
-\caption{Raman scattering from (a) 532 nm and (b) 441 nm excitation scanned along the core-shell NW.}
+\caption[Raman scattering from (a) 532 nm and (b) 441 nm excitation scanned along the core-shell NW]{Raman scattering from (a) 532 nm and (b) 441 nm excitation scanned along the core-shell NW.}
 \label{fig:ws2ram3site}

### 2015-01-10 ch-tms/tmspart.tex
camera ready
After first review in 2014

@@
 \end{equation}
-Notice $a_1 \cdot a_2 = a_1a_2 \cos\pi/3$, where the cosine times 2 is unit. In analog with carbon nanotube, chiral angle $\theta$ is given by
+Notice $a_1 \cdot a_2 = a_1a_2 \cos\pi/3$, where the $\cos\pi/3 \times 2 = 1$. In analog with carbon nanotube, chiral angle $\theta$ is given by
 \begin{equation}
@@
 \centering
-\includegraphics[width=0.7\textwidth]{ws2_tube1}
+\includegraphics[width=0.6\textwidth]{ws2_tube1}
 \caption[\ce{WS2} nanotube rolling]{\ce{WS2} nanotube rolling}
@@
 \centering
-\caption{TMDC few layer growth methods summary}\label{tab:tmsgrowth}
+\caption{Summary of TMDC few layer growth methods}\label{tab:tmsgrowth}
 {\footnotesize
@@
 \centering
-\caption[Lattices vibration of \ce{MS2}]{Lattices vibration of \ce{MS2}, reproduced from Ref.\cite{Molina-Sanchez2011}}\label{tab:tmslattice}
+\caption[Lattices vibration modes of \ce{MS2}]{Lattices vibration of \ce{MS2}, reproduced from Ref.\cite{Molina-Sanchez2011}}\label{tab:tmslattice}
 \begin{tabular}{lcccc}

### 2015-01-10 ch-wox/ch-wox.tex
After first review in 2014

@@
 \centering
-\caption{Tungsten powders size and purity}\label{tab:powder}
+\caption{Tungsten powder sizes and purities}\label{tab:powder}
 \begin{tabular}{lccr}
@@
 
-\section{Results ans Discussion}
+\section{Results and Discussion on 1D Nanowire Growth}
 \subsection{Tungsten Oxides: Impurities and Residual Effects}\label{sec:nawox}
@@
 \includegraphics[width=0.7\textwidth]{nawox_semedx.jpg}
-\caption[SEM and EDX on \ce{Na_xWO3}]{SEM images of (a) dense array of as-synthesized ultra-long nanowires on \ce{SiO2}-Si substrate and (b) rectangular microplates grow among the nanowires.
+\caption[SEM and EDX on \ce{Na_xWO3}]{SEM images of (a) dense array of the as-synthesized ultra-long nanowires on \ce{SiO2}-Si substrate and (b) rectangular microplates grow among the nanowires.
 (c) EDS and (d) XRD spectra showing the chemical compositions and phases of the deposition.}
@@
 \centering
-\caption{Raman fingerprints of tungsten oxides and sodium tungsten compounds}\label{tab:woram2}
+\caption{Raman fingerprints of tungsten oxides and sodium tungsten oxides}\label{tab:woram2}
 \begin{tabular}{lp{3in}r}
@@
 This result confirmed the nanowire growth could be enhanced by the presence of the residue deposition and explained the morphology changes of the nanowires with the increase of growth number.
-% xrd na5
+%xrd na5
 \begin{figure}[htb]
@@
 \includegraphics[width=0.8\textwidth]{wox_xrd_series}
-\caption{XRD spectra of the as-synthesized specimen with the increase of growth number from 1 to 5.}
+\caption[XRD spectra of the as-synthesized specimen with the increase of growth number from 1 to 5]{XRD spectra of the as-synthesized specimen with the increase of growth number from 1 to 5.}
 \label{fig:nawoxxrd}
 \end{figure}
-
 The general trend of Na/W ratios with the growth number can also be explained by the aforementioned effect of residue deposition.
@@
 \centering
-\caption{XRD assignments of specimens in \ce{Na_xWO3} growth}\label{tbl:wo3xrd}
+\caption{Assignment of XRD peak indices to different phases}\label{tbl:wo3xrd}
 \begin{tabular}{llllll}
@@
 Based on the electron sum rule, the sodium tungsten oxide can be cast into \ce{Na5W_1^{5+}W_{13}^{6+}O44}, which indicates the W atom state is quite close to that in \ce{WO3}.
-More investigation is needed to vigorously determined the electronic transport properties of \ce{Na5W14O44} NW.
+More investigation is needed to vigorously determined the electronic transport properties of \ce{Na5W14O44} NWs.
 
@@
 \includegraphics[width=0.9\textwidth]{wox3n5.jpg}
-\caption[SEM images of \ce{WO3} growth using 3N5 powder]{SEM images of \ce{WO3} growth using 3N5 powder showing the morphology variation from (a) high temperature and (b) intermediate temperature, to (c) low temperature.}
+\caption[SEM images of \ce{WO3} growth using 3N5 powder]{SEM images of \ce{WO3} growth using 3N5 powder showing the morphology variation from (a) high temperature, (b) intermediate temperature, to (c) low temperature.}
 \label{fig:wox3n5}
@@
 As mentioned in Sec.~\ref{sec:nawox}, growth using higher purity tungsten powders primarily produces thin film deposition, and growth using 3N powder is plagued with the impurity effect producing sodium tungsten oxide NW instead of tungsten oxide NW.
-New growth method is thus explored to obtain \ce{WO3} NWs.
+New growth method was thus explored to obtain \ce{WO3} NWs.
 In this study, a seeded growth approach was developed and proved to be a successful alternative way.
@@
 \subfloat[]{\label{fig:sgb}\includegraphics[width=0.4\textwidth]{wox_sg_b.jpg}}
-\caption[SEM characterization of \ce{WO3}seeded growth]{SEM characterization of \ce{WO3}seeded growth.
+\caption[SEM characterization of \ce{WO3} seeded growth]{SEM characterization of \ce{WO3} seeded growth.
 (a) SEM graphs of \ce{WO3} NWs on \ce{SiO2}/Si substrate.
@@
 
-\subsection{Tungsten Oxides: Misc}
+\subsection{Tungsten Oxides: Other Methods}
 

### 2015-01-12 ch-moox/moox.tex
MoO3 chapter alkaline replaced

@@
 In this work, a new growth mechanism of molybdenum oxide (\ce{MoO3}) 1D structures was discovered, highlighted by \ce{MoO3} long nanobelts and micro-scale towers.
-The samples were synthesized using a group of alkaline metal based catalysts, including \ce{NaOH}, \ce{KI}, and \ce{Na2CO3}.
+The samples were synthesized using a group of alkali metal based catalysts, including \ce{NaOH}, \ce{KI}, and \ce{Na2CO3}.
 In contrast to the sole axial growth found in the conventional catalyst-assisted growth, two different growth modes were observed for the \ce{MoO3} 1D growth here: transverse growth and axial growth.
@@
 
-Molybdenum oxide (\ce{MoO3}) crystallizes in three phases, orthorhombic $\alpha$-\ce{MoO3}, monoclinic $\beta$-\ce{MoO3} and the metastable hexagonal h-\ce{MoO3}.\citep{Deb1968,Fibers2007} $\alpha$-\ce{MoO3} phase (hereafter \ce{MoO3}) exhibits anisotropic structure with strong bonding along [001] and [100] direction while van der Waals interaction along [010] direction.\cite{He2003} Due to this unique structure, \ce{MoO3} was found to have several important properties and a wide range of technological applications, such as electrochromism and photochromism,\cite{Yao1992} lubricants,\cite{Sheehan1996} photocatalysts,\cite{Chen2010} and gas sensor, including \ce{CO},\cite{Comini2005} \ce{NO2},\cite{Taurino2006} \ce{H2}\cite{Sha2009} and ethanol.\cite{Choopun} Moreover, other features arise when nanoscale \ce{MoO3} is specifically prepared, e.g., field emission.\citep{Li2002d,Zhou2003b}  As a layered hosting material, \ce{MoO3} can be further modified by intercalating with alkaline ions\citep{Spahr1995,Li2006b,Hu2011} and even divalent ion.\cite{Sian2005} This structural richness have enabled improved performance in Li-ion\cite{Mai2007} and sodium-ion battery.\cite{Hariharan2013} In combination with \ce{TiO2} forming a core-shell structure, these nanoparitcles are reported to lower the photon absorption energy of \ce{TiO2}.\cite{Elder2000} When combined with Ag as layered structure, transparent conducting behavior was observed.\cite{Nguyen2012} In addition, \ce{MoO3} is a good precursor for preparing other useful materials, such as \ce{MoS2} fullerene\cite{Li2003c} and few layer \ce{MoS2}.\cite{Lin2012} It will also be an important member of the van der Waals heterostructures.\cite{Geim2013}
+Molybdenum oxide (\ce{MoO3}) crystallizes in three phases, orthorhombic $\alpha$-\ce{MoO3}, monoclinic $\beta$-\ce{MoO3} and the metastable hexagonal h-\ce{MoO3}.\citep{Deb1968,Fibers2007} $\alpha$-\ce{MoO3} phase (hereafter \ce{MoO3}) exhibits anisotropic structure with strong bonding along [001] and [100] direction while van der Waals interaction along [010] direction.\cite{He2003} Due to this unique structure, \ce{MoO3} was found to have several important properties and a wide range of technological applications, such as electrochromism and photochromism,\cite{Yao1992} lubricants,\cite{Sheehan1996} photocatalysts,\cite{Chen2010} and gas sensor, including \ce{CO},\cite{Comini2005} \ce{NO2},\cite{Taurino2006} \ce{H2}\cite{Sha2009} and ethanol.\cite{Choopun} Moreover, other features arise when nanoscale \ce{MoO3} is specifically prepared, e.g., field emission.\citep{Li2002d,Zhou2003b}  As a layered hosting material, \ce{MoO3} can be further modified by intercalating with alkali ions\citep{Spahr1995,Li2006b,Hu2011} and even divalent ion.\cite{Sian2005} This structural richness have enabled improved performance in Li-ion\cite{Mai2007} and sodium-ion battery.\cite{Hariharan2013} In combination with \ce{TiO2} forming a core-shell structure, these nanoparitcles are reported to lower the photon absorption energy of \ce{TiO2}.\cite{Elder2000} When combined with Ag as layered structure, transparent conducting behavior was observed.\cite{Nguyen2012} In addition, \ce{MoO3} is a good precursor for preparing other useful materials, such as \ce{MoS2} fullerene\cite{Li2003c} and few layer \ce{MoS2}.\cite{Lin2012} It will also be an important member of the van der Waals heterostructures.\cite{Geim2013}
 
@@
 To apply the catalysts, 54 $\mu$L 10 mM \ce{NaOH} (or \ce{KI}, \ce{Na2CO3}) was drop-cast onto clean substrates and then naturally left dry in a convection hood.
-Other alkaline ions-containing substrates, such as glass (Fisher Scientific, microscope slide, 12-549) and indium tin oxide (ITO) coated glass (Delta Technologies, 25\si{\ohm}), were cleaned by the same routine except the absence of plasma cleaning and subsequent aqueous solution dipping.
+Other alkali ions-containing substrates, such as glass (Fisher Scientific, microscope slide, 12-549) and indium tin oxide (ITO) coated glass (Delta Technologies, 25\si{\ohm}), were cleaned by the same routine except the absence of plasma cleaning and subsequent aqueous solution dipping.
 Mica was cleaved right before growth without other treatment.
@@
 Then a growth model was proposed and verified.
-In the end, this growth model was applied onto other substrates with alkaline metal ions, and various \ce{MoO3} nanostructures were produced.
+In the end, this growth model was applied onto other substrates with alkali metal ions, and various \ce{MoO3} nanostructures were produced.
 
@@
 \subsection{Growth on Alkali Metal Containing Substrates}
-In analog with the \ce{Na2MoO4}-\ce{MoO3} binary phase diagram, other alkaline metals, such as Li and K, could also form A-Mo-O alloy at elevated temperature.
-This fact allows for the usage of a variety of alkaline metal based material as catalyst to promote \gls{vls} or \gls{vss} growth of \ce{MoO3}.
+In analog with the \ce{Na2MoO4}-\ce{MoO3} binary phase diagram, other alkali metals, such as Li and K, could also form A-Mo-O alloy at elevated temperature.
+This fact allows for the usage of a variety of alkali metal based material as catalyst to promote \gls{vls} or \gls{vss} growth of \ce{MoO3}.
 Some experiments have been performed in this study, including growth using KI and \ce{Na2CO3} treated Si substrate, glass and mica.
@@
 
-The various growth morphologies found using alkaline metal based materials as catalysts demonstrate the proposed \gls{vss} mechanism and transverse mode is a general phenomenon, and broad engineering space could be explored to control the dimension of \ce{MoO3}.
+The various growth morphologies found using alkali metal based materials as catalysts demonstrate the proposed \gls{vss} mechanism and transverse mode is a general phenomenon, and broad engineering space could be explored to control the dimension of \ce{MoO3}.
 
@@
 Achieving morphology controlled growth of \ce{MoO3} on transparent substrates, e.g., glass, is an important progress towards process integration and device fabrication in photo-energy related applications.
-Because the alkaline ions in glass can diffuse out at elevated temperature, the proposed \gls{vss} mechanism will modify the \ce{MoO3} deposition.
+Because the alkali ions in glass can diffuse out at elevated temperature, the proposed \gls{vss} mechanism will modify the \ce{MoO3} deposition.
 Therefore, the mass transport of sodium ions in silica glass is first estimated to evaluate the amount of catalyst available during the growth of \ce{MoO3}.
@@
 
-In this chapter, a new growth model of \ce{MoO3} using alkaline metal ions as catalysts was discovered and investigated in depth.
+In this chapter, a new growth model of \ce{MoO3} using alkali metal ions as catalysts was discovered and investigated in depth.
 The growth kinetics was closely inspected using a series of controlled experiments.

### 2015-01-12 misc/SI_thesis.tex
vls vss paper reading

@@
 \chapter{moo3}
+
+molybdena, mobility of the hexavalent \ce{Mo6+} ions in MoO3 modified by Na+, \cite{El-Shobaky1998} Solid-solid reaction between \ce{Na2O} and \ce{MoO3}: 
+\[
+\cee{Na2O + 2MoO3 \rightarrow[500 C] Na2Mo2O7}
+\]
+The solubility of sodium oxide in \ce{MoO3} lattices is controlled by the chemical affinity towards the formation of \ce{Na2Mo2O7}.
+Other phases, such as \ce{Na2Mo3O8}, \ce{Na2Mo3O4} were detected by XRD.
+
+MoO3 spreading on \ce{Al2O3}: solid-solid wetting process, favored by the decrease of total surface energy. 800 K heating, gas phase transport ruled out.\cite{Leyrer1990} 
+\[
+\Delta F = \gamma_M - \gamma_S + \gamma_{MS}
+\]
+where the subscript M, S denote material and substrate, respectively.
+solid state reaction between MoO3 and Al2O3 can occur, resulting \ce{Al2(MoO4)3}, while reaction between MoO3 and \ce{SiO2} is not reported.
+
+MoO3 on Au (111).\cite{Song2003} spreading phase as molten MoO3. surface free energy of \ce{Al2O3} as , \ce{MoO3} as .
+
+crystal anisotropy affect the morphology and growth direction. \cite{Schwarz2009} \cite{Schwarz2010}
+
+\cite{Dubrovskii2011}
+
+\cite{Cao2012a}
+
+\cite{Shin2012}
+
+\cite{Rathi2013}
+
+Si NW growth using Au and SiH4, the growth species incorporation rate into liquid appears larger than that into solid because of the catalytic reaction on the metal, not of the rough surface of liquid phase.
+The catalytic particles can lower the barrier that is present on the particle-solid interface as compared to that on the vapor-solid interface.
+As to the catalytic particle being liquid \cite{Harmand2005, Park2006} or solid \cite{Dick2005,Persson2004}, results from the growth of III-V NWs using different catalysts indicate it barely matter.
+\cite{Kolasinski2006} And the phase from which the growth material is taken is of little consequence.
+The essential role of catalyst appears to be in lowering the activation energy of nucleation at the growth interface.
+
+Cu-Si NW, VSS mechanism, in-situ TEM, \cite{Wen2009} Si growth direction show multiple ones instead of the major 111 direction in VLS method.
+solid catalyst be advantageous in fabricating heterostructure due to the low solubility of growth species in solid.
+
+ZnO NW by AuZn alloy, VSS occurs via a solid diffusion mechanism.\cite{Campos2008} the low-temperature growth of ZnO nanowires from solid Au–Zn catalysts as being an intermediate between the VLS and VS processes.
+The presence of a low-energy epitaxial interface between solid catalyst and the NW will favor NW growth.
+
+Size effect evaluated by cohesive energy theory.\cite{Qi2005} $T = T_b (1 - N/2n)$, where N surface atoms and n total atoms.
+
+\begin{table}[htb]
+\centering
+\caption{melting of nanosolids}\label{tab:nano}
+\begin{tabular}{ccp{2in}}
+\toprule
+Morphology & N/n &  Remarks   \\
+\midrule
+sphere     &  4d/D  & d atom diameter, D sphere diameter   \\ 
+disk-like     &  4d(1/3h+ 2/3l)  & d atom diameter, l disk diameter, h disk height \\ 
+nanowire     &  8d/3l & d atom diameter, l wire diameter   \\ 
+\bottomrule
+\end{tabular}
+Note: atomic diameter calculated by atomic volume per mole.
+\end{table}
+
+For example, the atomic weight of Pb is 207 g/mol, and density is 11.34 g/cm3; then the molar volume is 207/11.34 = 18.2539.
+Assuming sphere as building unit, then $\frac{\pi}{6}D^3$ = 18.2539/N_A.
+Solving D as 0.3868 nm.
+
+for \ce{MoO3}, d as 0.46 nm.
+
+catalyst acts as a sink for Zn, generating concentration gradient.
+growth rate and diffusion coefficient estimation, MoO3 diffusing in liquid should be faster than in solid, this can explain the longer dimension in the length of belts than the height of towers.
+open issue,
+Na2MoO4-MoO3 phase diagram indicates that for T less than 500 C, the Na-Mo-O alloy will remain solid for all MoO3 concentration.
+
 \ce{MoO3}, an alternative interpretation in terms of tetrahedral coordination of Mo atoms is also proposed.
 This is caused by the fact that four of the six surrounding O atom are at distances from 1.67 \si{\angstrom} to 1.95 \si{\angstrom}, while the remaining two are as far as 2.25 and 2.33 \si{\angstrom}.
-This also stress that the \ce{MOO6} octahedra are rather distorted.
+This also stress that the \ce{MoO6} octahedra are rather distorted.
 

### 2015-01-13 ch-wox/ch-wox.tex
wox chapter patched

@@
 In a typical ordinary transport experiment (Fig.~\ref{fig:wogrow}), about 2 g tungsten powder was positioned in the upstream end of a quartz boat and downstream about 2.5 inch the substrate was stationed.
-The substrates were p-type, boron-doped and [100]-orientated silicon with about 1 $\mu$m thermally-grown silicon oxide layer on the polished side.
-The cleaning procedures have been elucidated on page~\pageref{ch2sub}.
-The boat was then loaded into reaction chamber in a way that the powder source was placed in the center of heating zone, and the substrate upstream end was aligned at 6.5 inch.\footnote{As defined in Fig.~\ref{fig:wogrow}} After pumping down, 1 \gls{sccm} \ce{O2} and 10 sccm Ar were admitted into the chamber, respectively, after which the overall pressure read approximately 110 mTorr.
-The temperature ramped up to 1000 \si{\degreeCelsius} in 30 min and lasted for 4 h, and subsequently the apparatus was allowed to naturally cool down to room temperature.
 % cvd NW growth
@@
 \end{figure}
+The substrates were p-type, boron-doped and [100]-orientated silicon with about 1 $\mu$m thermally-grown silicon oxide layer on the polished side.
+The cleaning procedures have been elucidated on page~\pageref{ch2sub}.
+The boat was then loaded into reaction chamber in a way that the powder source was placed in the center of heating zone, and the substrate upstream end was aligned at 6.5 inch.\footnote{As defined in Fig.~\ref{fig:wogrow}} After pumping down, 1 \gls{sccm} \ce{O2} and 10 sccm Ar were admitted into the chamber, respectively, after which the overall pressure read approximately 110 mTorr.
+The temperature ramped up to 1000 \si{\degreeCelsius} in 30 min and lasted for 4 h, and subsequently the apparatus was allowed to naturally cool down to room temperature.
 
@@
 \midrule
-3N      & Morphology from high to low temperature: islands, dense layer and a few NWs & Dense wires become more and more, \ce{NaxWO3} phase dominates & 20  \\
+3N      & Morphology from high to low temperature: islands, dense layer and a few NWs & Dense wires become more and more, sodium tungsten oxides phases dominate & 20  \\
 3N5     & islands in high temperature end and layers in low temperature end & NA &      NA\\
@@
 This compares favorably with both HRTEM analysis (Fig.~\ref{fig:nawoxtem}e) and ICDD PDF 04-012-4449 database reference.
-
 %061212 sample
@@
 
-\subsubsection{Ordinary transport growth using other W powders}
+Typical morphologies of ordinary transport growth using other powders are shown in Fig.~\ref{fig:wox3n5} and Fig.~\ref{fig:wox4n5}, respectively.
+The common feature of these samples is the dominance of islands growth in upstream end and layers growth in downstream end.
+The exact dimension still shows some minor difference, particularly in low temperature region.
+The deposition with 4N5 and 5N have much smaller grain size than that with 3N5 powder.
 % 3N5 powder growth
@@
 
-Typical morphologies of ordinary transport growth using other powders are shown in Fig.~\ref{fig:wox3n5} and Fig.~\ref{fig:wox4n5}, respectively.
-The common feature of these samples is the dominance of islands growth in upstream end and layers growth in downstream end.
-The exact dimension still shows some minor difference, particularly in low temperature region.
-The deposition with 4N5 and 5N have much smaller grain size than that with 3N5 powder.
 % 4N5 powder growth
@@
 
-Two interesting approaches for \ce{WO3} NW growth were found during this study, both of which can produce \ce{WO3} NWs with its own merit.
-The first one is related to the vapor flow dynamic in the deposition region.
+Another interesting approach for \ce{WO3} NW growth were also found in this study, producing \ce{WO3} NWs of high crystalline quality.
+The method was supposed to be related to the vapor flow dynamic in the deposition region.
 As shown in Sec.~\ref{sec:nawox}, ordinary transport growth using high purity W power mostly leads to thin film growth on one substrate of 1 in long.
@@
 The presence of sodium tungsten oxide phase indicates that the CVD growth of \ce{WO3} is extremely sensitive to Na contents.
-The insight of \ce{WO3} growth kinetics we have gained from this study could help establish a systematic connection between the interaction of transition metal oxide and alkaline metal ions, thereby turning this deleterious effect into a beneficial approach of controlled growth.
+The insight of \ce{WO3} growth kinetics we have gained from this study could help establish a systematic connection between the interaction of transition metal oxide and alkali metal ions, thereby turning this deleterious effect into a beneficial approach of controlled growth.
 In fact, favorable results have been observed on both \ce{WO3} and \ce{MoO3} 1D nanostructures syntheses using NaOH treated Si substrates.

### 2015-01-13 ch-wox/part1.tex
After first review in 2014
wox chapter patched

@@
 \section{Introduction}
-
-Tungsten oxide (\ce{WO_x}) is an important functional materials with distinctive properties and technology applications.
-Intense research interest was rekindled by the discovery of \gls{ec} effect in \citeyear{Granqvist1993}.\cite{Granqvist1993}  Nano-engineering \ce{WO_x} bring more possibility and flexibility to its already rich characteristics, therefore resulting in research efforts spanning multiple fields of scientific community.
-Besides smart window based on \gls{ec} effect, \ce{WO_x} is also well investigated for several other significant applications: photoelectrochemical cell for solar energy conversion and storage, photocatalysis for hydrogen evolution reaction, chemical and biological sensing based on gasochromic effect.
+Tungsten oxides (\ce{WO_x}) is a group of important functional materials with distinctive properties and technology applications.
+Intense research interest was rekindled by the discovery of \gls{ec} effect in \citeyear{Granqvist1993}.\cite{Granqvist1993}  Nano-engineering \ce{WO_x} bring more possibility and flexibility to its already rich characteristics, therefore resulting in research efforts spanning multiple fields in the scientific community.
+Besides smart window based on \gls{ec} effect, tungsten oxides are also well investigated for several other significant applications: photoelectrochemical cell for solar energy conversion and storage, photocatalysis for hydrogen evolution reaction, chemical and biological sensing based on gasochromic effect.
 In addition, a few young fields are not thoroughly explored: field emission, optical storage, thermo-electricity, ferro-electricity, and superconductivity.
 
-In this chapter, a literature review on \ce{WO_x} and \ce{Na_xWO3} will be given first, with focus on technological application, crystal structure, and synthesis approaches.
-Then the growth methods in this study are presented, followed by corresponding characterization and discussion.
-This chapter is concluded with a brief summary.
+In this chapter, a literature review on tungsten oxides and sodium tungsten oxides will be given first, with focus on technological applications, crystal structures, and synthesis approaches.
+Several growth methods were explored in this study to investigate the crystallographic dynamics of tungsten oxides and sodium tungsten oxides nanostructures.
+The characterization results were presented, followed by in-depth discussion.
+This chapter is concluded with a brief summary: the impurities effect on the formation of sodium tungsten oxides nanostructures and the seeded growth method for tungsten trioxide \glspl{nw} of high crystalline quality.
 
-\subsection{Applications of Tungsten Oxides and Sodium Tungsten Oxides}
+\subsection{Properties and Applications of Tungsten Oxides and Sodium Tungsten Oxides}\label{sec:wonawo}
+Tungsten trioxide (\ce{WO3}) crystallizes in multiple phases.
+The basic building block is \ce{WO6} octahedra.\footnote{Tungsten, with its electronic configuration as \ce{(Xe)4f^{14}5d^{4}6s^{2}}, has empty 5d and 6s orbitals in its $+6$ oxidation state.} \ce{WO3} crystal structure consists of \ce{WO6} octahedra joined at their corners, which may be considered as a perovskite structure of \ce{CaTiO3} with all \ce{Ca^{2+}} sites vacant.
+A representative lattice structure is illustrated in Fig.~\ref{fig:wo3oct}.
+These distorted \ce{WO6} octahedra adapt different tilting angles in different phases and edge-sharing octahedra also arise.
+% wo3 phases
+\begin{table}[htb]
+\centering
+\caption{List of \ce{WO3} phases}\label{tab:wo3phase}
+\begin{tabular}{lccccc}
+\toprule
+&&&\multicolumn{3}{c}{Lattice constants \AA} \\
+\cmidrule(l){4-6}
+ Symbol    & Temperature (\si{\degreeCelsius}) & Phase & a & b & c   \\
+\midrule
+$\epsilon$-\ce{WO3} & $ -140 \sim -50$  & monoclinic II & 7.378 & 7.378 & 7.664  \\
+$\delta$-\ce{WO3} & $-50 \sim 17$  & triclinic & 7.309 & 7.522 & 7.686  \\
+$\gamma$-\ce{WO3} & $17 \sim 330$  & monoclinic I & 7.306 & 7.540 & 7.692  \\
+$\beta$-\ce{WO3} & $330 \sim 740$  & orthorhombic & 7.384 & 7.512 & 3.846  \\
+$\alpha$-\ce{WO3} & $> 740$  & tetragonal & 5.25 & NA & 3.91  \\
+$h$-\ce{WO3} &  $<400$  & hexagonal & 7.298 & NA & 3.899  \\
+\bottomrule
+\end{tabular}
+\end{table}
+The temperature-dependent phase transition and corresponding lattice constants in bulk form is summarized in Table~\ref{tab:wo3phase}.\cite{Zheng2011} And a firm assignation of space group to monoclinic phases are still in debate.\cite{Chatten2005} It is noticed that the lattice parameters obtained via \emph{ab initio} calculation closely match the experimental values.\cite{Migas2010a} The phase transition scenarios in nanostructured \ce{WO3} are supposed to be more sophisticated.
+Within Gibbs-Thomson framework, one can generally expect lower transition temperature than their bulk counterparts due to enhanced surface energy.
+Temperature-dependent Raman spectroscopy provided support for this deduction.\cite{Boulova2002}
+\begin{figure}[htb]
+\centering
+\includegraphics[width=0.4\textwidth]{octwo3.jpg}
+\caption[Octahedra model of \ce{WO3}]{Octahedra model of \ce{WO3}}
+\label{fig:wo3oct}
+\end{figure}
 
-Electrochromic effect of tungsten oxide means the coloration (deep blue) and bleaching (transparent) states of \ce{WO3} are reversibly switched upon forward and backward voltage, and the coloration or bleached states remain after disconnecting the voltage.
+\ce{WO3} is a wide gap n-type semiconductor with valence band top featuring $2p$ states of oxygen and conduction band bottom arising primarily from $5d$ states of tungsten with some mixing of oxygen $2p$ states.\cite{Gillet2004} \citeauthor{Migas2010a} maintained there is essentially identical band dispersion near the gap region in case of $\epsilon$-\ce{WO3}, $\delta$-\ce{WO3}, $\gamma$-\ce{WO3} and $\beta$-\ce{WO3}.\cite{Migas2010a} When there is oxygen vacancy, the Fermi level moves into the conduction band and the gap shrinks by about 0.5 eV.
+\citeauthor{Migas2010a} also pointed out the flat bands at \gls{vbm} and \gls{cbm} could lead to poor transport of holes and electrons, thus may compromising the function in photoelectrochemical cells.
+
+Besides \ce{WO3}, tungsten oxide exists in a series of sub-stoichiometric states.
+The \ce{W_nO_{3n-1}} ($n \geq 2$) exhibit $\{ 001 \}$ CS structure.
+Chemical formula corresponding to n=2, 3, 4, 5 and 6 are \ce{W2O5=WO_{2.5}}, \ce{W3O8=W_{2.67}}, \ce{W4O_{11}=WO_{2.75}}, \ce{W5O_{14}=WO_{2.8}}, and \ce{W6O_{17}=WO_{2.83}}, which indicates the existence of a oxygen deficient plane at every $n$ row.
+Actually the value $x$ in \ce{WO_x} could almost continuously vary within a range of 2.5 to 3.
+\ce{W_{18}O_{49}=\ce{WO_{2.72}}} is an exception without $\{ 001 \}$ CS structure.
+Moreover, the oxygen deficient planes could extend along directions other than $\{ 001 \}$.
+For instance, the $\{ 102 \}$ CS planes appears in \ce{WO_x} where $x$ is within 2.93 to 2.98, and  the $\{ 103 \}$ CS planes for $x$ within 2.87 to 2.93.\cite{Sloan1999} The enhancement arises from the structure composed of a conductive layer and an insulating layer that are laminated therein.\cite{Shingaya2013} In \ce{WO_x} nanorods, the oxygen deficient planes are conductive, each having atomic thickness and separated by several nm of \ce{WO3} layers.
+Localized surface plasmons could possibly exist on these conductive planes.
+Therefore \gls{sers} applies and single molecule Raman scattering using individual tungsten oxide nanorod has been demonstrated.\cite{Shingaya2013}
+
+Tungsten oxides were probably best known for the electrochromic effect, meaning the coloration (deep blue) and bleaching (transparent) states of \ce{WO3} are reversibly switched upon forward and backward voltage, and the coloration or bleached states remain after disconnecting the voltage.
 On basis of this property, \gls{ecd} of tremendous energy saving potential is conceptualized and some products have already been commercialized (i.e.
@@
 During the intercalation process, the \ce{M^+} ions enter into these vacant sites.\cite{Hepel2008} Coloration occurs when electron transition occurs from the hole polaron band to the electron polaron band.
-
 \begin{align}\label{eq:ec}
-x\ce{M+} + x\ce{e-} +  \ce{$\alpha \hyphen$WO$_{3-y}$} \rightarrow \ce{$\alpha \hyphen$M$_x$WO$_{3-y}$},
+x\ce{M+} + x\ce{e-} +  \ce{$\alpha \hyphen$WO$_{3-y}$} \rightarrow \ce{$\alpha \hyphen$M$_x$WO$_{3-y}$}
 \end{align}
@@
 \begin{align}
-E_p = - \frac{e^2}{2r_p} (\epsilon_\infty^{-1} - \epsilon_{st}^{-1}),
+E_p = - \frac{e^2}{2r_p} (\epsilon_\infty^{-1} - \epsilon_{st}^{-1})
 \end{align}
@@
 
-\iffalse
-The author believe the resolution to a large extent depends on the phase transitions, as discussed in Section.~\ref{sec:wonawo}.
-
-A thin film example on the valency number, color center density. some calculation on doping, uv-vis results on the thin film.
-
-\fi
-
-\subsection{Properties of Tungsten Oxides and Sodium Tungsten Oxides}\label{sec:wonawo}
-
-Tungsten trioxide (\ce{WO3}) crystallizes in multiple phases.
-The basic building block is \ce{WO6} octahedra.\footnote{Tungsten, with its electronic configuration as \ce{(Xe)4f^{14}5d^{4}6s^{2}}, has empty 5d and 6s orbitals in its $+6$ oxidation state.} \ce{WO3} crystal structure consists of \ce{WO6} octahedra joined at their corners, which may be considered as a perovskite structure of \ce{CaTiO3} with all \ce{Ca^{2+}} sites vacant.
-A representative lattice structure is illustrated in Fig.~\ref{fig:wo3oct}.
-These distorted \ce{WO6} octahedra adapt different tilting angles in different phases and edge-sharing octahedra also arise.
-% wo3 phases
-\begin{table}[htb]
-\centering
-\caption{List of \ce{WO3} phases}\label{tab:wo3phase}
-\begin{tabular}{lccccc}
-\toprule
-&&&\multicolumn{3}{c}{Lattice constants \AA} \\
-\cmidrule(l){4-6}
- Symbol    & Temperature (\si{\degreeCelsius}) & Phase & a & b & c   \\
-\midrule
-$\epsilon$-\ce{WO3} & $ -140 \sim -50$  & monoclinic II & 7.378 & 7.378 & 7.664  \\
-$\delta$-\ce{WO3} & $-50 \sim 17$  & triclinic & 7.309 & 7.522 & 7.686  \\
-$\gamma$-\ce{WO3} & $17 \sim 330$  & monoclinic I & 7.306 & 7.540 & 7.692  \\
-$\beta$-\ce{WO3} & $330 \sim 740$  & orthorhombic & 7.384 & 7.512 & 3.846  \\
-$\alpha$-\ce{WO3} & $> 740$  & tetragonal & 5.25 & NA & 3.91  \\
-$h$-\ce{WO3} &  $<400$  & hexagonal & 7.298 & NA & 3.899  \\
-\bottomrule
-\end{tabular}
-\end{table}
-The temperature-dependent phase transition and corresponding lattice constants in bulk form is summarized in Table~\ref{tab:wo3phase}.\cite{Zheng2011} And a firm assignation of space group to monoclinic phases are still in debate.\cite{Chatten2005} It is noticed that the lattice parameters obtained via \emph{ab initio} calculation closely match the experimental values.\cite{Migas2010a} The phase transition scenarios in nanostructured \ce{WO3} are supposed to be more sophisticated.
-Within Gibbs-Thomson framework, one can generally expect lower transition temperature than their bulk counterparts due to enhanced surface energy.
-Temperature-dependent Raman spectroscopy provided support for this deduction.\cite{Boulova2002}
-
-\begin{figure}[htb]
-\centering
-\includegraphics[width=0.4\textwidth]{octwo3.jpg}
-\caption[Octahedra model of \ce{WO3}]{Octahedra model of \ce{WO3}}
-\label{fig:wo3oct}
-\end{figure}
-
-\ce{WO3} is wide gap n-type semiconductor with valence band top featuring $2p$ states of oxygen and conduction band bottom arising primarily from $5d$ states of tungsten with some mixing of oxygen $2p$ states.\cite{Gillet2004} \citeauthor{Migas2010a} maintained there is essentially identical band dispersion near the gap region in case of $\epsilon$-\ce{WO3}, $\delta$-\ce{WO3}, $\gamma$-\ce{WO3} and $\beta$-\ce{WO3}.\cite{Migas2010a} When there is oxygen vacancy, the Fermi level moves into the conduction band and the gap shrinks by about 0.5 eV.
-\citeauthor{Migas2010a} also pointed out the flat bands at \gls{vbm} and \gls{cbm} could lead to poor transport of holes and electrons, thus may compromising the function in photoelectrochemical cells.
-
-Besides \ce{WO3}, tungsten oxide exists in a series of sub-stoichiometric states.
-The \ce{W_nO_{3n-1}} ($n \geq 2$) exhibit $\{ 001 \}$ CS structure.
-Chemical formula corresponding to n=2, 3, 4, 5 and 6 are \ce{W2O5=WO_{2.5}}, \ce{W3O8=W_{2.67}}, \ce{W4O_{11}=WO_{2.75}}, \ce{W5O_{14}=WO_{2.8}}, and \ce{W6O_{17}=WO_{2.83}}, which indicates the existence of a oxygen deficient plane at every $n$ row.
-Actually the value $x$ in \ce{WO_x} could almost continuously vary within a range of 2.5 to 3.
-\ce{W_{18}O_{49}=\ce{WO_{2.72}}} is an exception without $\{ 001 \}$ CS structure.
-Moreover, the oxygen deficient planes could extend along directions other than $\{ 001 \}$.
-For instance, the $\{ 102 \}$ CS planes appears in \ce{WO_x} where $x$ is within 2.93 to 2.98, and  the $\{ 103 \}$ CS planes for $x$ within 2.87 to 2.93.\cite{Sloan1999} The enhancement arises from the structure composed of a conductive layer and an insulating layer that are laminated therein.\cite{Shingaya2013} In \ce{WO_x} nanorods, the oxygen deficient planes are conductive, each having atomic thickness and separated by several nm of \ce{WO3} layers.
-Localized surface plasmons could possibly exist on these conductive planes.
-Therefore \gls{sers} applies and single molecule Raman scattering using individual tungsten oxide nanorod has been demonstrated.\cite{Shingaya2013}
-
 \subsection{Review of Synthesis Methods}\label{sec:woxgrowth}
@@
 Finally the product is separated from the solution and dried, layered \ce{WO3.nH2O} flakes are usual products.
-A brief summary representative synthesis methods is shown in Table~\ref{tab:wox}.
+A brief summary of representative synthesis methods is shown in Table~\ref{tab:wox}.
 
@@
 \centering
-\caption{Summary of tungsten oxides growth methods}\label{tab:wox}
+\caption{Summary of tungsten oxide growth methods}\label{tab:wox}
 {\footnotesize

### 2015-01-13 ch-moox/moox.tex
moox chapter patched

@@
 
-It is known that a series of molybdate compound forms when alkali metal ions are incorporated into the \ce{MoO3} lattice, and the structures are summarized in Table~\ref{tab:naxmow}.
+It is known that a series of molybdate compounds form when alkali metal ions are incorporated into the \ce{MoO3} lattice, and the structures are summarized in Table~\ref{tab:naxmow}.
 Due to the weak cation-oxygen bonding, alkali metal cations only introduce small perturbations into the energies of \ce{Mo-O} matrix in comparison to cations of other elements.
@@
 
-\subsection{Growth on Alkali Metal Containing Substrates}
+\subsection{Growth on Alkali Metal Containing Substrates}\label{sec:glass}
 In analog with the \ce{Na2MoO4}-\ce{MoO3} binary phase diagram, other alkali metals, such as Li and K, could also form A-Mo-O alloy at elevated temperature.
@@
 The various growth morphologies found using alkali metal based materials as catalysts demonstrate the proposed \gls{vss} mechanism and transverse mode is a general phenomenon, and broad engineering space could be explored to control the dimension of \ce{MoO3}.
-
-\subsection{Growth on Glass}\label{sec:glass}
-Achieving morphology controlled growth of \ce{MoO3} on transparent substrates, e.g., glass, is an important progress towards process integration and device fabrication in photo-energy related applications.
+As an example, this study further illustrated the tunable growth of \ce{MoO3} nanoribbons on glass substrate.
+Achieving morphology controlled growth of \ce{MoO3} on transparent substrates, e.g., glass, is an important progress towards process integration and device fabrication in photon-energy related applications.
 Because the alkali ions in glass can diffuse out at elevated temperature, the proposed \gls{vss} mechanism will modify the \ce{MoO3} deposition.

### 2015-01-14 ch-tms/tms.tex
coreshell chapter revised

@@
 
-The remaining section is arranged in following order: a review on the growth of \ce{MS2} (M = Mo, W) nanotubes (NTs) and 2D \gls{fl} structures will be introduced first, followed by Raman spectroscopy summary on \ce{WS2} NTs and FL.
+The remaining sections are arranged in following order: a review on the growth of \ce{MS2} (M = Mo, W) \glspl{nt} and 2D \gls{fl} structures will be introduced first, followed by Raman spectroscopy summary on \ce{WS2} NTs and FL.
 The thesis will then focus on synthesis of \ce{WO3}-\ce{WS2} heterostructure and various characterizations on both ensemble and individual nanowires.
@@
 For the sake of completeness, schematic layout of overall growth were illustrated in Fig.~\ref{fig:ch5grow} including the oxidation of W powder, the seeded growth and the sulfurization process.
-
 % cvd NW growth
@@
 \end{figure}
-
 In a typical oxidation experiment shown in Fig.~\ref{fig:ch5grow}a, tungsten powders were loaded into the uniform heating zone and the sealed chamber was pumped down to an ultimate pressure of $5\sim8$ mTorr.
@@
 
-In a representative seeded growth (Fig.~\ref{fig:ch5grow}b), 4N5 or 5N tungsten source powder (Table.~\ref{tab:ch5pre}) was positioned in the upstream end of a quartz boat and downstream about 2.5 in the substrate was stationed.
+In a representative seeded growth (Fig.~\ref{fig:ch5grow}b), 4N5 or 5N tungsten source powder (Table.~\ref{tab:powder}) was positioned in the upstream end of a quartz boat and downstream about 2.5 inch the substrate was stationed.
 Additional tungsten seed powders (3N) were distributed evenly onto the substrate.
@@
 \centering
-\includegraphics[width=0.7\textwidth]{ws2_sem_edx}
+\includegraphics[width=0.7\textwidth]{ws2_sem_edx_labeled}
 \caption[Morphology and composition analysis on the as-synthesized \ce{WO3}-\ce{WS2} core-shell structures]{Morphology and composition analysis on the as-synthesized \ce{WO3}-\ce{WS2} core-shell structures.
-(a) SEM images showing the NWs almost retain their original shapes after sulfurization, and (b) EDX spectroscopy revealing the presence of sulfur element after sulfurization.}
+(a) Low magnification and (b) high magnification SEM images showing the NWs almost retain their original shapes after sulfurization.
+(c) EDX spectroscopy revealing the presence of sulfur element after sulfurization.}
 \label{fig:ch5ws2sem}
@@
 \caption[X-ray diffraction spectra before and after sulfurization]{X-ray diffraction spectra before and after sulfurization.
-The reference spectra for $c$-W, 2H-\ce{WS2} and $m$-\ce{WO3} are included with some major peaks labeled.}
+The reference spectra for $c$-W, 2H-\ce{WS2} and $m$-\ce{WO3} are included with major peaks labeled.}
 \label{fig:ch5ws2xrd}
@@
 Due to this small spacing, TEM is primarily utilized to observe the detailed morphology of \ce{WO3}-\ce{WS2} core-shell NWs.
-Fig.~\ref{fig:ch5ws2tem1} shows HRTEM imaging on typical tip and body region of the core-shell NW, respectively.
+Fig.~\ref{fig:ch5ws2tem1}c and d show HRTEM imaging on typical tip and body region of the core-shell NW, respectively.
 A comparison with the pre-sulfurization specimen (Fig.~\ref{fig:woseedtem2} on page~\pageref{fig:woseedtem2}) readily reveals the formation of core-shell morphology after sulfurization.
-The measured layer spacing is 6.4 \si{\angstrom}, slight larger than bulk 2H-\ce{WS2} of 6.16 \si{\angstrom}, but in good agreement with XRD results in Fig.~\ref{fig:ch5ws2xrd}.
+The measured layer spacing is 6.5 \si{\angstrom}, slightly larger than bulk 2H-\ce{WS2} of 6.16 \si{\angstrom}, but in good agreement with XRD result in Fig.~\ref{fig:ch5ws2xrd}.
 The clear contrast in core region also prove the lattice structure of \ce{WO3} is not seriously distorted.
@@
 \centering
-\includegraphics[width=0.9\textwidth]{ws2_coreshell_tem}
-\caption[HRTEM imaging on one core-shell nanowire showing layer number variation]{HRTEM imaging on one core-shell nanowire showing layer number variation.}
+\includegraphics[width=0.8\textwidth]{ws2_tem_labeled}
+\caption[HRTEM imaging before and after sulfurization]{HRTEM imaging before and after sulfurization illustrating the presence of core-shell structure.
+(a) Low magnification and (b) HRTEM images on \ce{WO3} NW specimen from seeded growth;  HRTEM images on the core-shell nanowire of (c) tip region and (d) body region showing layer number variation.
+The contrast between (b) and (d) readily identify the formation of core-shell structure.
+}
 \label{fig:ch5ws2tem1}
@@
 \centering
-\includegraphics[width=0.8\textwidth]{ws2_growth3}
+\includegraphics[width=0.7\textwidth]{ws2_growth3}
 \caption[HRTEM imaging on the tip area of one core-shell nanowire]{HRTEM imaging on the tip area of one core-shell nanowire.}
@@
 \centering
-\includegraphics[width=0.8\textwidth]{ws2_growth4}
+\includegraphics[width=0.7\textwidth]{ws2_growth4}
 \caption[HRTEM imaging on one tapered core-shell nanowire showing fluctuation of layer numbers]{HRTEM imaging on one tapered core-shell nanowire showing fluctuation of layer numbers.}
@@
 \centering
-\includegraphics[width=0.8\textwidth]{ws2_growth1}
+\includegraphics[width=0.7\textwidth]{ws2_growth1}
 \caption[HRTEM imaging on one core-shell nanowire showing consumed core]{HRTEM imaging on one core-shell nanowire showing consumed core.}
@@
 \end{figure}
+
 Fig.~\ref{fig:ch5ws2ram}a-d depict typical \ce{WO3}-\ce{WS2} NWs used in TEM-Raman integrated study.
@@
 The resonant nature\cite{Stacy1985} of Raman shift is recognized by the broad band at about 350 \si{cm^{-1}}.
-Recent theoretical\cite{Molina-Sanchez2011} and experimental\cite{Staiger2012} studies on 2D and tubular \ce{WS2} agree this band consist of first order mode $E_{2g}^1$ and second order mode $2LA(M)$, although there is still discrepancy on the exact symmetry assignment, i.e., the presence of $E_{2g}^1(M)$ mode.\cite{Berkdemir2013,Peimyoo2013}.
+Recent theoretical\cite{Molina-Sanchez2011} and experimental\cite{Staiger2012} studies on 2D and tubular \ce{WS2} agree this band consists of first order mode $E_{2g}^1$ and second order mode $2LA(M)$, although there is still discrepancy on the exact symmetry assignment, i.e., the presence of $E_{2g}^1(M)$ mode.\cite{Berkdemir2013,Peimyoo2013}.
 The other peak at about 420 \si{cm^{-1}} is assigned to $A_{1g}$ mode in both bulk\cite{Sekine1980} and few layer \ce{WS2}.
@@
 \centering
-\includegraphics[width=0.9\textwidth]{ws2_tem_ram}
+\includegraphics[width=0.8\textwidth]{ws2_temram_labeled}
 \caption[TEM-Raman integrated characterization on core-shell NWs]{TEM-Raman integrated characterization on core-shell NWs.
-(a)-(d) HRTEM images on several NWs showing the \ce{WS2} wall number variation from one to about ten.
-(e) Raman spectra acquired from core-shell NWs supported on TEM grids, indicating a sharp contrast between the in-plane and out-of-plane vibrations.
-Notice that the Raman spectra primarily arise from the outer \ce{WS2} shell, and only weak Raman shift at about 800 \si{cm^{-1}} were observed at some bare core region (not shown here).
-(f) Layer number dependence on averaged intensity ratio between the in-plane and out-of-plane Raman bands.
-}
+(a)-(d) HRTEM images on four NWs showing the \ce{WS2} wall number variation from one to about ten.
+(e) Raman spectra acquired from the same core-shell NWs supported on TEM grids, indicating a sharp contrast between the in-plane and out-of-plane vibrations.
+Notice that the Raman spectra primarily arise from the outer \ce{WS2} shell, and only weak Raman shift at about 800 \si{cm^{-1}} were observed at some bare core region (not shown here).}
 \label{fig:ch5ws2ram}
 \end{figure}
-Multi-peak Lorentzian fitting was also attempted on spectra shown in Fig.~\ref{fig:ch5ws2ram}e.
-Similar trend was found between the apparent peak ratio and the de-convolution value, as shown in Fig.~\ref{fig:ch5ws2pr}.
-For a qualitative purpose, the overall intensity ratio $I_{E/A}$ between in-plane E band ($E_{2g}^1+2LA$) and out-of-plane A band ($A_{1g}+B_{1u}$) is sufficient.
-This value is then extracted to correlate with layer number variation.
-Multiple Raman spectra for each layer were averaged, as shown in Fig.~\ref{fig:ch5ws2ram}f.
+
+Rigid analysis of the Raman spectra must be performed to reach solid conclusion.
+Hence, multi-peak Lorentzian fitting was attempted on the spectra in Fig.~\ref{fig:ch5ws2ram}e, and the result for 1 layer \ce{WS2} core-shell NW was displayed in Fig.~\ref{fig:ch5ws2ml}.
+The de-convolution peaks compared favorably with original Raman spectrum, and similar operation were used for other three spectra.
+Fig.~\ref{fig:ch5ws2pr} show the layer number dependence on three group of intensity ratios extracted from apparent value, deconvoluted height and integrated intensity, respectively.
+Similar trend was found among all three set of data, though the integrated intensity appears more sensitive towards layer No variation.
+For a qualitative purpose, the apparent intensity ratio $I_{E/A}$ between in-plane E band ($E_{2g}^1+2LA$) and out-of-plane A band ($A_{1g}+B_{1u}$) was used as a quick gauge to distinguish \ce{WS2} few layer.
 % fig Raman TEM
@@
 \centering
-\includegraphics[width=0.4\textwidth]{ws2_peak_ratio}
-\caption[Multi-peak Lorentzian fitting on core-shell NWs]{Multi-peak Lorentzian fitting on core-shell NWs. Comparison of apparent peak ratio and de-convolution value.}
-\label{fig:ch5ws2pr}
+\subfloat[]{\label{fig:ch5ws2ml}\includegraphics[width=0.45\textwidth]{ws2_1L_fitting}}\hspace{0.04\textwidth}
+\subfloat[]{\label{fig:ch5ws2pr}\includegraphics[width=0.45\textwidth]{ws2_peak_ratio}}
+\caption[Multi-peak Lorentzian fitting on core-shell NWs]{(a) Multi-peak Lorentzian fitting on core-shell NWs, and (b) Layer number dependence on averaged intensity ratio between the in-plane and out-of-plane Raman bands.}
+\label{fig:ch5ws2prl}
 \end{figure}
-The intensity ratio $I_{E/A}$ decreases monotonically with the increase of \ce{WS2} wall number, a similar trend as observed on 2D few layer \ce{WS2}.
-The exact value of $I_{E/A}$ shows modest difference with 2D sheet, which is attributed to the suspended configuration of current core-shell NWs specimen and the presence of \ce{WO3} core.
-It has been demonstrated that the optical interference from dielectric environment significantly modified the Raman scattering of layered MoS2, regardless lattice vibration modes.\cite{Li2012} The author calculated the reflectivity of three different stacking scenarios to estimate the influence of \ce{WO3} and insulating substrate, as shown in.
-It can be concluded that under 532 nm excitation, the \ce{WO3} core shows little influence on the Raman intensity when \ce{WS2} tube is suspended in air, whereas the \ce{SiO2}/Si substrates will dramatically enhance the Raman scattering of the core-shell NWs.
-It could be further predicted that current Raman spectra on core-shell NWs can be used to estimate the \ce{WS2} nanotube wall numbers.
+$I_{E/A}$ is then extracted to correlate with layer number variation on tens of core-shell NWs.
+As shown in Fig.~\ref{fig:ch5ws2ramap}, the mapping of \ce{WS2} layer dependent $I_{E/A}$ almost follows the same trend in Fig.~\ref{fig:ch5ws2pr} with some variation attributed to the core-shell NW diameter difference.
+\begin{figure}[htb]
+\centering
+\includegraphics[width=0.6\textwidth]{ws2_ratio_map}
+\caption[Mapping on the \ce{WS2} layer dependent intensity ratio]{Mapping on the \ce{WS2} layer dependent intensity ratio.
+The Raman spectra were acquired on individual NW suspended on 300 mesh lacey C TEM grid.}
+\label{fig:ch5ws2ramap}
+\end{figure}
+The intensity ratio $I_{E/A}$ decreases monotonically with the increase of \ce{WS2} wall number, a similar trend as observed on 2D few layer \ce{WS2},\cite{Berkdemir2013} and the exact value of $I_{E/A}$ shows modest difference with 2D sheet, which could be attributed to the suspended configuration of current core-shell NWs specimen and the presence of \ce{WO3} core.
+Furthermore, our results indicate that $I_{E/A} > 2$ for single-walled \ce{WS2} core-shell NW, and when the \ce{WS2} wall number is about 3, $I_{E/A}=1$.
+These two values act as a quick determination of \ce{WS2} wall number when the NW is suspended.
+
+Before using this observation in more general scenarios, one should evaluate the influence of \ce{WO3} and other dielectric substrates.
+It has been demonstrated that the optical interference from dielectric environment significantly modified the intensity of Raman scattering from layered \ce{MoS2}, regardless lattice vibration modes.\cite{Li2012} In this work, the author calculated the reflectivity of three different stacking scenarios to estimate the influence of \ce{WO3} and insulating substrate, as shown in Fig.~\ref{fig:ch5ws2stk}.
+It can be concluded that under 532 nm excitation, the \ce{WO3} core shows little influence on the Raman intensity when \ce{WS2} nanotube is suspended in air; whereas the \ce{SiO2}/Si substrates will dramatically enhance the Raman scattering of the core-shell NWs.
+It could be further predicted that current Raman spectra on the core-shell NWs can be used to estimate \ce{WS2} nanotube wall numbers.
+\begin{figure}[htb]
+\centering
+\includegraphics[width=0.7\textwidth]{ws2_stack}
+\caption[Optical reflectance simulation on three different \ce{WS2} layer stacking configurations]{Optical reflectance simulation on three different \ce{WS2} layer stacking configurations.}
+\label{fig:ch5ws2stk}
+\end{figure}
 
@@
 \centering
-\includegraphics[width=0.6\textwidth]{ws2_sio2_all}
+\includegraphics[width=0.7\textwidth]{ws2_sio2_all}
 \caption[Raman spectrum acquired on the middle spot of core-shell NW (inset) using 532 nm.
@@
 Another feature is the presence of three peaks centering at 1860, 3695, and 5500 \si{cm^{-1}}, respectively, where the latter two is probably the secondary and third overtone of the first peak.
-The origin of this peak family is still under research.
-A possible candidate points at the hydrocarbon contamination attached onto the core-shell NWs, as already been observed using TEM imaging.
-Interesting the intensity of this three-peak family attenuated significantly when using 441 nm excitation, as shown in Fig.~\ref{fig:ws2ramblue}.
+It was confirmed that this three peaks belong to Raman shift instead of PL, since similar peaks were observed using different excitation wavelength of 441 nm and 532 nm.
+The origin of this peak family is still under research, and one possible candidate is the \ce{C=O} bonding, which presumably come from the carbon impurity in tungsten powders as seeds.
+It was also possible that the \ce{C=O} bonding arise from the hydrocarbon contamination attached onto the core-shell NWs.
+Interestingly, the intensity of this three-peak family attenuated significantly when using 441 nm excitation, as shown in Fig.~\ref{fig:ws2ramblue}.
 This comparison suggested there might be some enhancement mechanism from \ce{WS2} resonant Raman vibrations.
@@
 \end{figure}
-This predication is confirmed by the associated PL measurement as displayed in Fig.~\ref{fig:ws2plgreen}.
+This predication is confirmed by the associated PL measurement displayed in Fig.~\ref{fig:ws2plgreen}.
 Strong luminescent peaks were found at site mid and tip1, and an extremely weak from site tip2.

### 2015-01-14 ch-tms/tmspart.tex
coreshell chapter revised

@@
 \section{Introduction}
-\subsection{Properties of TMDCs}
+\subsection{Properties and Applications of WS$_2$}
 Tungsten disulfide (\ce{WS2}) is a group VI dichalcogenide semiconductor compound.
@@
 Almost all natural \ce{WS2} belongs to P63/mmc space group (2H-\ce{WS2}), where $a$ is 3.153 \si{\angstrom}, $c$ is 12.323 \si{\angstrom} (PDF 04-003-4478).
-Two other crystal structures were found in man-made \ce{WS2}, i.e., 1T and 3R, where 3R can be prepared by bromine (Br) chemical vapor transport (CVT) method \cite{Schutte1987} and 1T was generally found in alkaline intercalated \ce{WS2}.\cite{Yang1996a, Enyashin2011}
-
-As a reference, the lattice dimensions are summarized in Table~\ref{tab:ms2lattice}.
+Two other crystal structures were found in man-made \ce{WS2}, i.e., 1T and 3R, where 3R can be prepared by bromine (Br) chemical vapor transport (CVT) method \cite{Schutte1987} and 1T was generally found in alkaline intercalated \ce{WS2}.\cite{Yang1996a, Enyashin2011} As a reference, the lattice dimensions are summarized in Table~\ref{tab:ms2lattice}.
 %lattice
@@
 
-The geometrical symmetry groups of WS2 NT.\cite{Milosevic2000} The basis/lattice vectors $a_1$ and $a_2$ are defined in transition metal plane with equal length $a_0 \approx 3$ \si{\angstrom}.
+\ce{WS2} can also form tubular structures in analog with those of carbon nanotubes.
+The geometrical symmetry group of \ce{WS2} NT has been reported.\cite{Milosevic2000} The basis/lattice vectors $a_1$ and $a_2$ are defined in transition metal plane with equal length $a_0 \approx 3$ \si{\angstrom}.
 This monolayered sheet can be rolled up to form a tubular structure when the chiral/translation vector $c = n_1a_1 + n_2a_2$ becomes the circumference of the tube.
@@
 \centering
-\includegraphics[width=0.6\textwidth]{ws2_tube1}
+\includegraphics[width=0.8\textwidth]{ws2_tube1}
 \caption[\ce{WS2} nanotube rolling]{\ce{WS2} nanotube rolling}
@@
 
-\subsection{Synthesis Review of TMDCs}
+\subsection{Synthesis Review on WS$_2$}
 Shortly after the discovery of \gls{cnt} in 1991,\cite{Iijima1991} its transition metal dichalcogenides (TMDC) counterparts, i.e., \ce{WS2}, was synthesized in 1992.\cite{Tenne1992} In the following decades, other TMDC and several metal oxides nanotubes were demonstrated as well.
@@
 
-\subsection{Raman on WS$_2$: Bulk, FL and NTs}\label{sec:ntram}
+\subsection{Raman on WS$_2$: Bulk, Few Layer and Nanotube}\label{sec:ntram}
 

### 2015-01-15 FrontMatter/Abstract.tex
all chapter fine tuned

--- 2014-09-27 FrontMatter/Abstract.tex
@@
 \begin{abstract}
-
-Transition metal oxides (TMOs) exhibit rich structures and useful properties, and could been used in solar energy harvesting (\emph{e.g.}, photoelectrochemistry, photocatalysis, and photovoltaics) and energy saving (\emph{e.g.}, electrochromism and photochromism) applications.
-Nano-engineering of these TMOs could produce a variety of nanostructures, modify the electronic and optical properties, potentially enhance the performances and extend their applications into new regimes.
+Transition metal oxides (TMOs) exhibit rich structures and useful properties, and could be used in applications of solar energy harvesting (\emph{e.g.}, photoelectrochemistry, photocatalysis, and photovoltaics) and energy saving (\emph{e.g.}, electrochromism and photochromism).
+Nano-engineering of these TMOs could produce a variety of nanostructures, modify the electronic and optical properties, and potentially enhance the performances and extend their applications into new regimes.
 To fully harvest the advantages of these materials, a scalable growth method and a comprehensive understanding towards the growth-structure-property relation must be established.
 This Ph.D.
-study focused on one-dimensional (1D) tungsten trioxide (\ce{WO3}) and molybdenum trioxide (\ce{MoO3}) nanostructures.
+study focused on one-dimensional (1D) nanostructures of tungsten trioxide (\ce{WO3}) and molybdenum trioxide (\ce{MoO3}).
 This dissertation synthesized 1D \ce{WO3} and \ce{MoO3} nanostructures using chemical vapor deposition (CVD) approach, characterized the morphologies and structures, and measured the optical properties of the as-prepared nanostructures.
-This study aims at accomplishing controlled and scalable growth of \ce{WO3} and \ce{MoO3} using CVD method, establishing the structure-property relations to rationalize nanostructure synthesis for energy applications, and presenting preliminary results on the devices assembled using the \ce{WO3} and \ce{MoO3} nanostructures.
 
+This dissertation work consists of three main parts, each centering on \ce{WO3}, \ce{MoO3}, and \ce{WS2}-\ce{WO3}, respectively.
+Systematical investigation of \ce{WO3} nanostructure using CVD method with tungsten powders as precursor led to the following accomplishments:
+\begin{enumerate*}[label=\itshape\alph*\upshape)]
+\item the discovery of \ce{Na5W14O44} nanowires;
+\item knowledge of the delicate role of sodium in tungsten source powders; and
+\item a seeded growth method to produce high quality \ce{WO3} nanowires.
+\end{enumerate*} Enlightened by the intricate interactions between sodium content and tungsten oxide, this dissertation extended vapor-liquid-solid strategy into \ce{MoO3} 1D nanostructure growth, and discovered two morphologies of \ce{MoO3}: ultra-longbelts and microtowers.
+Careful observation in extensive experiments identified the catalytic role of sodium hydroxide applied on the growth substrate, and readily proved the catalytic behavior exists with other alkali based metal contents.
+The third part of this work moved the investigation center from growth to property characterization.
+A novel TEM-Raman integrated study was performed on \ce{WS2}-\ce{WO3} core-shell NWs, allowing for the observation of high resolution TEM imaging, Raman and Photoluminescence spectroscopy on individual nanowires.
+The single-walled \ce{WS2} tubular nanostructure was first identified.
+The combined results further illustrated the existence of \ce{WS2} wall number dependent Raman fingerprint on resonant Raman spectra.
+
+In summary, this study explored methods for controlled and scalable growth of 1D \ce{WO3} and \ce{MoO3} nanostructures based on both vapor-solid and vapor-solid-solid approaches, characterized the structure-property relations to rationalize nanostructure synthesis for energy applications, and presented preliminary results for the devices fabrications using the \ce{WO3} and \ce{MoO3} nanostructures.
 \end{abstract}

### 2015-01-15 FrontMatter/FrontMatter.tex
after format review, bold font in figure caption removed, frontmatter spacing fixed
intro writing after format review
After first review in 2014
all chapter fine tuned

@@
-  \title{Controlled Growth and Property Measurement of One-dimensional Oxide Nanostructures for Energy Applications}
+  %\title{Controlled Growth and Property Measurement of One-dimensional Oxide Nanostructures for Energy Applications}
+  \title{Controlled growth and property measurement of one-dimensional oxide nanostructures for energy applications}
   \author{Tao Sheng}
@@
   \degree{Doctor of Philosophy}
-  \department{Physics and Optical Science}
+  \department{Optical Science and Engineering}
 
@@
 
-\begin{dedication}
-TBD.
-\end{dedication}
+\begin{ackn}
+\begin{singlespace}
+Studying in UNC Charlotte has been an unique and rewarding experience for myself, which I shall recall frequently for a long time to come.
+So I am grateful to all the people here I have spent time with.
+Dr.
+Haitao Zhang has been an excellent advisor to me.
+I enjoyed the time learning a new set of skills, discussing research questions, and obtaining important life lessons from him.
+I thank Dr.
+Davies for the help she gave when I joined the Optical Science and Engineering program; I thank Dr.
+Terry Xu for allowing me to work in her lab since 2012, within which I finished most of the crystal growth work.
+I also thank Dr.
+Yong Zhang for the access to Raman instrument in his group, without which my research would be seriously diminished.
+I appreciate the financial supports of GASP in UNC Charlotte, the research assistantship from National Science Foundation (DMR-1006547), and the teaching assistantship from Physics and Optical Science department.
+I also appreciate the Center for Optoelectronics and Optical Communications at UNC Charlotte for the support in multiuser facilities.
+I would also like to thank all my friends and/or research partners I have met in Charlotte: Dr.
+Bob Cao, Dr.
+Jianwei Wang, Liqin Su, Henan Liu, Jinghua Ge, Siang Yee Chang, Zhe Guan, and Youfei Jiang.
 
-%\pagebreak{}
+Most important, I am grateful to my parents who support my decisions as always.
 
-\begin{ackn}
-TBD.
+\begin{minipage}[b]{0.95\textwidth}
+
+\begin{flushright}
+
+\emph{Sheng, Tao}
+
+\emph{January 2015}
+
+\emph{Charlotte, NC}
+
+\end{flushright}
+\end{minipage}
+\end{singlespace}
 \end{ackn}
@@
 \listoffigures
-\begin{singlespace}
-%\thispagestyle{myheadings}
+
 \renewcommand{\glossarypreamble}{\thispagestyle{myheadings}}
 \renewcommand{\acronymname}{LIST OF ABBREVIATIONS}
-\glossarystyle{long}
-\printglossary[type=\acronymtype]
-\addcontentsline{toc}{chapter}{\acronymname}
-\clearpage
-\end{singlespace}
-%\listofabbre
+%\glsaddall
+\setlength{\glsdescwidth}{0.5\textwidth}
+\glossarystyle{mysuper3col}
+\printglossary[type=\acronymtype, toctitle=\acronymname]
+
+%\addcontentsline{toc}{chapter}{\acronymname} this method has wrong page numbering for list of abb
+% more than one page; instead, use toc option when loading glossaries package, and specify % toctitle when printing it.
 

### 2015-01-15 ch-intro/ch-instr.tex
all chapter fine tuned

@@
 The SEM instrument used in this study is JEOL JSM-6480.
-The \gls{ebeam} source is a tungsten filament heated at about 2800 K.
-The acceleration voltage can be up to 30 kV.
+The \gls{ebeam} source is a tungsten filament heated at about 2800 K.\cite{jeolsem} The acceleration voltage can be up to 30 kV.
 After acceleration, electron beam strikes the sample mounted on specimen stage, producing rich signals as illustrated in Fig.~\ref{fig:ch2sem}.
@@
 Chemical wrapping paper can be inserted between the glass rod and \ce{BaSO4} powder to prevent the powder sticking.
-Nanostructured sample on transparent substrates, i.e., quartz, could be mounted directly with the growth substrate, or ground and spread evenly onto \ce{BaSO4} surface.
+Nanostructured sample on transparent substrates, i.e., quartz, could be mounted directly with the growth substrate, or ground and spread evenly onto \ce{BaSO4} surface.\cite{isr2011}

### 2015-01-15 ch-intro/ch-intro.tex
all chapter fine tuned

@@
 Photocatalytic activity occurs when a semiconductor in aqueous solution is illuminated by photons of energy larger than the bandgap, then the carriers (electron and hole) drift and generate free radicals, i.e., \ce{OH.}, which enable further reactions.
-For water splitting using solar energy, the bandgap should be within $2.0 \sim 3.0 $ eV, and \gls{cb} edge should be more negative than reduction potential of \ce{H^+/H2}, whereas the \gls{vb} top should be more positive than the oxidation potential of \ce{H2O}/\ce{O2}.\cite{Osterloh2008,Wang2012} The valence band holes (\ce{h^+}) oxidize water to oxygen and conduction band electrons propel hydrogen generation, as depicted in Eq.~\ref{eq:h2o}.
+For photochemical water reduction to occur, the flat-band potential of the semiconductor (for highly doped semiconductors, this equals to the bottom of the conductance band) must exceed the proton reduction potential of 0.0 V vs NHE at pH 0.
+Flat-band potentials strongly depend on ion absorption (protonation of surface hydroxyl groups), crystallographic orientation of the exposed surface, surface defects, and surface oxidation processes.\cite{Osterloh2008} For water splitting using solar energy, the bandgap should be within $2.0 \sim 3.0 $ eV, and \gls{cb} edge should be more negative than reduction potential of \ce{H^+/H2}, whereas the \gls{vb} top should be more positive than the oxidation potential of \ce{H2O}/\ce{O2}.\cite{Osterloh2008,Wang2012} The valence band holes (\ce{h^+}) oxidize water to oxygen and conduction band electrons propel hydrogen generation, as depicted in Eq.~\ref{eq:h2o}.
 \begin{subequations}\label{eq:h2o}
@@
 Moreover, favorable oxygen evolution of \ce{WO3} brings good performance in degradation of organic compounds.\cite{Hepel2001,Luo2001,Watcharenwong2008} The formation of long-lived holes is recognized as a key requirement.\cite{Pesci2011} Besides, \ce{WO3} is remarkably stable in acid, making it a significant candidate for treating water pollutant caused by organic acids.\cite{Monllor-Satoca2006}
-
-For photochemical water reduction to occur, the flat-band potential of the semiconductor (for highly doped semiconductors, this equals to the bottom of the conductance band) must exceed the proton reduction potential of 0.0 V vs NHE at pH 0.
-Flat-band potentials strongly depend on ion absorption (protonation of surface hydroxyl groups), crystallographic orientation of the exposed surface, surface defects, and surface oxidation processes.\cite{Osterloh2008}
 
@@
 Chapter 3 is devoted to tungsten oxides (\ce{WO3}) and sodium tungsten oxides (\ce{Na5W14O44}) nanowires, where the role of sodium in metallic tungsten precursors are thoroughly investigated; a potentially scalable growth method is also developed.
-Chapter 4 will turn to molybdenum oxide (\ce{MoO3}) growth using alkaline metal compounds as catalysts.
+Chapter 4 will turn to molybdenum oxide (\ce{MoO3}) growth using alkali metal compounds as catalysts.
 In Chapter 5, a heterostructure based on \ce{WO3} \glspl{nw} is studied.
 Emphasis will be placed on the characterization of individual \ce{WO3}-\ce{WS2} core-shell \gls{nw}.
-The dissertation is then concluded with a summary and future work.
+The dissertation is then concluded with summary and future work.

### 2015-01-15 ch-moox/moox.tex
all chapter fine tuned

@@
 Researchers have been exploring a variety of methods to synthesized different \ce{MoO3} nanostructures.
-Only a brief introduction will be given here, since these efforts has been well documented in several review articles.\cite{He2003} Most of these methods can be categorized into two groups: solution-based hydrothermal procedures \citep{Li2002b,Xia2006,Li2006a,Camacho-Bragado2006} and chemical vapor transport and deposition approaches.\citep{Zeng1998,Li2002c,Li2002d,Zhou2003b,Fibers2007,Yan2009}.
-Both methods have its own merits.
+Only a brief introduction will be given here, since these efforts has been well documented in several review articles.\cite{He2003} Most of these methods can be categorized into two groups: solution-based hydrothermal procedures \citep{Li2002b,Xia2006,Li2006a,Camacho-Bragado2006} and chemical vapor transport and deposition approaches.\citep{Zeng1998,Li2002c,Li2002d,Zhou2003b,Fibers2007,Yan2009} Both methods have its own merits.
 Hydrothermal process usually need lower temperature(\textless 300 \si{\degreeCelsius}), but the duration is usually long and requires several post-growth processing steps; whereas vapor deposition demands relatively high temperature (\textgreater 500 \si{\degreeCelsius}) yet with a shorter time.
@@
 Mica was cleaved right before growth without other treatment.
-
+\begin{table}[htb]
+\centering
+\caption{Physical constants of reactants }\label{tb:mothermo}
+\begin{tabular}{lccr}
+\toprule
+Material & MP(\si{\degreeCelsius}) & BP(\si{\degreeCelsius}) & Reference\\
+\midrule
+\ce{NaOH}        & 318 & 1388 & \cite{crc1977}  \\
+\ce{NaI}        & 651 & 1300 & \cite{crc1977}    \\
+\ce{KI}        & 681 & 1330 & \cite{crc1977}   \\
+\ce{Na2CO3}        & 851 & Not determined & \cite{crc1977}    \\
+\ce{Na2MoO4}        & 687 & Not available & \cite{crc1977}   \\
+\ce{MoO3}    & 795 & 1155 & \cite{crc1977}   \\
+\ce{MoO2}    & 1100(decomp) & Not available & MSDS   \\
+\bottomrule
+\end{tabular}
+\end{table}
 In a typical synthesis run (Fig.~\ref{fig:mooxgrowth}), about 2 g molybdenum powders were loaded into the uniform heating zone and the sealed chamber was first pumped down to 10 mTorr.
@@
 
-Based on this phase diagram and the growth conditions adopted in this study, it is predicted that the overall reactions occur in the following sequences.
+Based on this phase diagram, the physical constants of reactants in Table~\ref{tb:mothermo}, and the growth conditions adopted in this study, it is predicted that the overall reactions occur in the following sequences.
 First, Mo powder is oxidized and \ce{MoO3} vapor is produced and transported to downstream by Ar carrier gas.
@@
 \begin{align}
-\cee{NaOH(l) + MoO3(g) &\rightarrow Na2MoO4(l) + H2O(g)\\
+\cee{NaOH(l) + MoO3(g) &\rightarrow Na2MoO4 + H2O(g)\\
 Na2MoO4 + nMoO3   &\rightarrow Na2O.(n + 1)MoO3}
@@
 No long belt or tower was observed on the sample with \ce{Na2CO3}.
-Long belts found on mica (\ce{K(Al2)(Si3Al)O10(OH)2}) probably arise from potassium-catalyzed \gls{vls} mechanism.\cite{Hu2011} More detailed results on glass will be presented in Sec.~\ref{sec:glass}.
+Long belts found on mica (\ce{K(Al2)(Si3Al)O10(OH)2}) probably arise from potassium-catalyzed \gls{vls} mechanism.\cite{Hu2011}
 
@@
 \centering
-\includegraphics[width=0.7\textwidth]{moo3_glass}
+\includegraphics[width=0.7\textwidth]{moo3_glass_lbd}
 \caption[Optimized \ce{MoO3} nanoplates growth on glass]{Optimized \ce{MoO3} nanoplates growth on glass.}

### 2015-01-15 ch-tms/tmspart.tex
all chapter fine tuned

@@
 Flat caps often dominates.
-\citeauthor{Zhu2000} maintained that this oxide-to-sulfides mechanism might apply to closed caps only, not to those open ended tubes.\cite{Zhu2000} TEM diffraction analysis could distinguish the chirality of NTs, as demonstrated by CNT \cite{Zhang1993} and \ce{MoS2}\cite{MARGULIS1996}.
-\ce{WS2} NT chirality revealed by TEM SAED shows armchair NTs dominates.
+\citeauthor{Zhu2000} maintained that this oxide-to-sulfides mechanism might apply to closed caps only, not to those open ended tubes.\cite{Zhu2000} TEM diffraction analysis could distinguish the chirality of NTs, as demonstrated by CNT \cite{Zhang1993} and \ce{MoS2}.\cite{MARGULIS1996} \ce{WS2} NT chirality revealed by TEM SAED shows armchair NTs dominates.
 \citeauthor{Sloan1999} investigated tungsten oxides structures incorporated in \ce{WS2}.\cite{Sloan1999} The encapsulated \ce{WO_x} cores often exhibit \ce{W3O8} and \ce{W5O_{14}} phases, both of which belong to the \ce{W_nO_{3n-1}} homogenous series, arising as a result of \gls{cs} planes.\cite{Miyano} Some \ce{WO_x} cores show oxygen vacancy instead of CS planes, leading to prominent streaking in SAED patterns.
@@
 
-\citeauthor{Peimyoo2013} prepared \ce{WS2} on \ce{SiO2}-Si using \ce{WO3} powder and sulfur at 800 \si{\degreeCelsius}, aiming at the light emission studies to clarify several contradictory reports.\cite{Peimyoo2013} Uniform PL intensity was found on the triangular \ce{WS2} flakes, in contrast to previous edge enhanced PL.\cite{Berkdemir2013} Raman spectra (532 nm) fit includes $E_{2g}^1(M)$ mode at 343 cm$^{-1}$, according to the phonon dispersion calculation \cite{Molina-Sanchez2011} and experimental observation\cite{Zeng2013a,Zhao2013,Lee2013}.
-However, none of these experimental reports specifically mentioned $E_{2g}^1(M)$ mode.
-Tentative assignments of multi-phonon bands are summarized in supporting information of Ref\cite{Zhao2013}.
+\citeauthor{Peimyoo2013} prepared \ce{WS2} on \ce{SiO2}-Si using \ce{WO3} powder and sulfur at 800 \si{\degreeCelsius}, aiming at the light emission studies to clarify several contradictory reports.\cite{Peimyoo2013} Uniform PL intensity was found on the triangular \ce{WS2} flakes, in contrast to previous edge enhanced PL\cite{Berkdemir2013}.
+Raman spectra (532 nm) fit includes $E_{2g}^1(M)$ mode at 343 cm$^{-1}$, according to the phonon dispersion calculation \cite{Molina-Sanchez2011} and experimental observation.\cite{Zeng2013a,Zhao2013,Lee2013} However, none of these experimental reports specifically mentioned $E_{2g}^1(M)$ mode.
+Tentative assignments of multi-phonon bands are summarized in supporting information of Ref.\cite{Zhao2013}.
 As to the growth setup, similar tube furnace as in Ref \cite{VanderZande2013} and \cite{Najmaei2013} was used.
 To gain additional wisdom on \ce{MoS2} growth, this thesis thus summarizes the growth strategies in Ref \cite{VanderZande2013} and \cite{Najmaei2013} as following.
-\citeauthor{VanderZande2013} prepared \ce{MoS2} on 285 nm \ce{SiO2}-Si using \ce{MoO3} and S as precursors.\cite{VanderZande2013} In contrast to the seeding method adopted in ref\cite{Lee2013,Lee2012b}, \citeauthor{VanderZande2013} stressed the importance of carefully cleaned substrates\footnote{acetone, 2 h in \ce{H2SO4} and \ce{H2O2} (3:1) and 5 min oxygen plasma} and minimum exposure of precursor to air.\footnote{APCVD, 105 \si{\degreeCelsius} for 4 h, 700 \si{\degreeCelsius} hold for 5 min, and 10 sccm \ce{N2} within 2 in tube.
+\citeauthor{VanderZande2013} prepared \ce{MoS2} on 285 nm \ce{SiO2}-Si using \ce{MoO3} and S as precursors.\cite{VanderZande2013} In contrast to the seeding method adopted in Refs.\cite{Lee2013,Lee2012b}, \citeauthor{VanderZande2013} stressed the importance of carefully cleaned substrates\footnote{acetone, 2 h in \ce{H2SO4} and \ce{H2O2} (3:1) and 5 min oxygen plasma} and minimum exposure of precursor to air.\footnote{APCVD, 105 \si{\degreeCelsius} for 4 h, 700 \si{\degreeCelsius} hold for 5 min, and 10 sccm \ce{N2} within 2 in tube.
 rapid cooling from 570 \si{\degreeCelsius}} Dirty substrates or old precursors will lead to hexagonal, 3-point star or irregular polycrystalline structures.
@@
 The substrate and \ce{MoO3} source distance is critical in determining the growth density.
-The synthesis strategy in Ref\cite{Lee2013,Lee2012b} is briefly mentioned as well, where PTAS treated substrate is found to promote the deposition, while KCl treated substrates did not, and small carrier gas flow is preferred (1 sccm \ce{N2}).
+The synthesis strategy in Refs.\cite{Lee2013,Lee2012b} is briefly mentioned as well, where PTAS treated substrate is found to promote the deposition, while KCl treated substrates did not, and small carrier gas flow is preferred (1 sccm \ce{N2}).
 It was also noted that the \ce{MoS2} flakes morphology seems more uniform in Ref\cite{VanderZande2013} than that in Ref\cite{Lee2012b}.
@@
 The optimal growth conditions are 800-850 \si{\degreeCelsius}, 700 Torr, and sufficient sulfur.
-This thesis then conjectures that the substrate cleaning in Ref.\cite{Peimyoo2013} should be similar to that in ref\cite{VanderZande2013}, yet the source-to-substrate layout and growth pressure are still needed to be optimized with respect to the home-built CVD apparatus.
+This thesis then conjectures that the substrate cleaning in Ref.\cite{Peimyoo2013} should be similar to that in Ref.\cite{VanderZande2013}, yet the source-to-substrate layout and growth pressure are still needed to be optimized with respect to the home-built CVD apparatus.
 
@@
 
-It is worth noting the flake sizes on sapphire\cite{Zhang2013h} seems larger than that on \ce{SiO2}/Si\cite{Peimyoo2013}, either due to the nucleation barrier difference or the amount of growth vapor and growth time.
+It is worth noting the flake sizes on sapphire\cite{Zhang2013h} seems larger than that on \ce{SiO2}/Si,\cite{Peimyoo2013} either due to the nucleation barrier difference or the amount of growth vapor and growth time.
 The flake sizes in Ref.\cite{Cong2013} is not quite uniform, though it could be even larger than that on sapphire from Ref.\cite{Zhang2013h}.
@@
 In back scattering geometry, the photon wave-vector stands as $q = 4\pi\frac{n}{\lambda}$.
-The refractive index $\tilde{n}$ of \ce{WS2} at 532 nm is about $4.726 - 0.737i$, corresponding to a wave-vector about $1\times10^8$ \si{m^{-1}}.
+The refractive index $\tilde{n}$ of \ce{WS2} at 532 nm is about $4.726 - 0.737i$,\cite{Beal1976, Peimyoo2013} corresponding to a wave-vector about $1\times10^8$ \si{m^{-1}}.
 Compared to the size of Brillouin zone ($\pi/a = 10^{10}$ \si{m^{-1}}), off-resonant Raman could only probe phonon at $\Gamma$ point, where the phonon momentum ($\hbar k$) is close to zero.
@@
 Raman technique has also provided much insight into the few layer \ce{MS2}.
-\ce{MS2} layer numbers are readily identified by the Raman shift distance between $A_{1g}$ and $E_{2g}^1$ mode for \ce{MoS2}\cite{Buscema2013} and \ce{WS2}\cite{Berkdemir2013}.
-Yet due to the relative small shift of $A_{1g}$ mode and little shift of $E_{2g}^1$ mode in \ce{WS2} FL, the frequencies distance might not qualify as an unambiguous way to distinguish layer numbers.
+\ce{MS2} layer numbers are readily identified by the Raman shift distance between $A_{1g}$ and $E_{2g}^1$ mode for \ce{MoS2}\cite{Buscema2013} and \ce{WS2}.\cite{Berkdemir2013} Yet due to the relative small shift of $A_{1g}$ mode and little shift of $E_{2g}^1$ mode in \ce{WS2} FL, the frequencies distance might not qualify as an unambiguous way to distinguish layer numbers.
 Yet the resonant Raman profile on \ce{WS2} exhibit unique features between the intensity of 2LA and $A_{1g}$ mode,\cite{Berkdemir2013,Zhao2013} which provide another routine to assure the monolayer presence.
@@
 \citeauthor{Dobardzic2006} theoretically presented Raman scattering of any polarization on \gls{swnt} of \ce{WS2} and their dependence on diameter (1-20 nm) and chiral angle.
-The author assigned 351 cm$^{-1}$ as $E_u$ for \ce{WS2} NT.\cite{Dobardzic2006} \citeauthor{Ghorbani-Asl2013} discuss the electronic and vibrational properties for large diameter \ce{WS2} NTs\cite{Ghorbani-Asl2013}.
-Single-walled NT is approximated by 1H monolayer and others by 2H bulk structure.
+The author assigned 351 cm$^{-1}$ as $E_u$ for \ce{WS2} NT.\cite{Dobardzic2006} \citeauthor{Ghorbani-Asl2013} discuss the electronic and vibrational properties for large diameter \ce{WS2} NTs.\cite{Ghorbani-Asl2013} Single-walled NT is approximated by 1H monolayer and others by 2H bulk structure.
 It was found that large-diameter nanotubes can be approximated with layered systems as their properties should be nearly the same at the scale.
@@
 Yet there is different opinion on these assignments.
-\citeauthor{Molina-Sanchez2011} label the 350 \si{cm^{-1}} band as \ce{E_{1u}} instead of 2LA.\cite{Molina-Sanchez2011} And recent theoretical investigations suggest 416 \si{cm^{-1}} peak is inactive $B_{1u}$ mode\cite{Molina-Sanchez2011,Ataca2012}, which is the Davydov doublet with $A_{1g}$ mode.
+\citeauthor{Molina-Sanchez2011} label the 350 \si{cm^{-1}} band as \ce{E_{1u}} instead of 2LA.\cite{Molina-Sanchez2011} And recent theoretical investigations suggest 416 \si{cm^{-1}} peak is inactive $B_{1u}$ mode,\cite{Molina-Sanchez2011,Ataca2012} which is the Davydov doublet with $A_{1g}$ mode.
 \citeauthor{Staiger2012} adopted these assignments in studying the resonance Raman profile of \ce{WS2} NTs.\cite{Staiger2012} It was found that

### 2015-01-15 ch-wox/ch-wox.tex
all chapter fine tuned

@@
 The method was supposed to be related to the vapor flow dynamic in the deposition region.
-As shown in Sec.~\ref{sec:nawox}, ordinary transport growth using high purity W power mostly leads to thin film growth on one substrate of 1 in long.
-However, it was found that when two shorter substrates were closely placed together, the \ce{WO3} NW yield was significantly enhanced in the second substrate located in lower temperature region.
-For instance, substrate 1 (Sub1) is located at 6.75 to 7 inch (Fig.~\ref{fig:wogrow} horizontal axis on page~\pageref{fig:wogrow}), and substrate 2 (sub2) is placed in close vicinity of downstream end of sub1.
-W source moves to 5 inch, and 0.3 sccm \ce{O2} is used to reduce the \ce{WO_x} vapor pressure.
-Deposition on sub1 is characterized by thin film, similar to those shown in Fig.~\ref{fig:wox4n5}b.
-However, deposition on sub2 (Fig.~\ref{fig:fg1}) is in sharp contrast to that shown in Fig.~\ref{fig:wox4n5}c, although they are both located in the low temperature region of reaction chamber.
-The NW density is dramatically increased.
-The NWs have length about 1 to 2 $\mu$m and diameter about 200 nm.
-Close-up view (inset of Fig.~\ref{fig:fg2}) shows the NWs have clear facets, implying its high crystalline quality.
 % fg sem
@@
 \end{figure}
+As shown in Sec.~\ref{sec:nawox}, ordinary transport growth using high purity W power mostly leads to thin film growth on one substrate of 1 inch long.
+However, it was found that when two shorter substrates were closely placed together, the \ce{WO3} NW yield was significantly enhanced in the second substrate located in lower temperature region.
+For instance, substrate 1 (Sub1) is located at 6.75 to 7 inch (Fig.~\ref{fig:wogrow} horizontal axis on page~\pageref{fig:wogrow}), and substrate 2 (sub2) is placed in close vicinity of downstream end of sub1.
+W source moves to 5 inch, and 0.3 sccm \ce{O2} is used to reduce the \ce{WO_x} vapor pressure.
+Deposition on sub1 is characterized by thin film, similar to those shown in Fig.~\ref{fig:wox4n5}b.
+However, deposition on sub2 (Fig.~\ref{fig:fg1}) is in sharp contrast to that shown in Fig.~\ref{fig:wox4n5}c, although they are both located in the low temperature region of reaction chamber.
+The NW density is dramatically increased.
+The NWs have length about 1 to 2 $\mu$m and diameter about 200 nm.
+Close-up view (inset of Fig.~\ref{fig:fg2}) shows the NWs have clear facets, implying its high crystalline quality.
+
 The growth mechanism here can be explained by aforementioned VS process as well.

### 2015-01-15 ch-wox/part1.tex
all chapter fine tuned

@@
 
-\subsection{Properties and Applications of Tungsten Oxides and Sodium Tungsten Oxides}\label{sec:wonawo}
+\subsection{Properties and Applications of Tungsten Oxides}\label{sec:wonawo}
 Tungsten trioxide (\ce{WO3}) crystallizes in multiple phases.

### 2015-01-19 ch-intro/ch-instr.tex
walked in to exchange opinions with Advr, and walking out with his on wox and moox

@@
 In this work, magnetron sputtering (Denton Vacuum Desk IV) was used to coat thin layers of metals onto cleaned substrates.
-As shown in Fig.~\ref{fig:ch2magsp}, a high potential created between the target (cathode) and substrate ionizes the argon molecules.
-These ions are accelerated to bombard the target foils, knocking out active atoms which subsequently deposit onto the substrates.
-A magnetic field is applied to confine electrons to the vicinity of the foils.
-These electrons in turn increase the ionization yield.
+As shown in Fig.~\ref{fig:ch2magsp}, the metal target is the cathode and the specimen is anode.
+A dc voltage is applied to ionizes the argon gas, and a permanent magnet behind the target focuses the gas plasma onto the target and also deflect electrons from the sample.
+These ions are then accelerated to bombard the target foils, knocking out active atoms which subsequently deposit onto the substrates.
 \begin{figure}[htb]
 \centering
-\includegraphics[width=0.7\textwidth]{magsp.jpg}
-\caption[Schematic drawing of magnetron sputtering system]{Schematic drawing of magnetron sputtering system. Reproduced from Ref.\cite{Song2008}}
+\includegraphics[width=0.7\textwidth]{sputter.jpg}
+\caption[Schematic drawing of magnetron sputtering system]{Schematic drawing of magnetron sputtering system. Reproduced from Ref.\cite{Goldstein2007}}
 \label{fig:ch2magsp}
 \end{figure}
-
-Sputtering is a better PVD technique than \gls{ebeam} deposition since it alleviates the adverse effects in the latter.
 \ce{Ar+} ions are accelerated to target foils.
 The pressure of \ce{Ar+} has two functions: to sputter off the target ions, and to influence the \gls{mfp}.
-These collisions between target ions and \ce{Ar+} leads to almost all arrival angle, thus uniform coverage.
+These collisions between target ions and \ce{Ar+} lead to almost all arrival angles, thus uniform coverage.
 The sputtering yield is number of target ions released per ions hitting on target.
@@
 Usually yield between 1 and 2 is desired.
-The \gls{mfp} in sputtering is on order of 3 cm (assuming pressure 30 mTorr), with source-to-substrate distance as 5 cm, average number of collisions is about 5/3$\sim$2.
+The \gls{mfp} in sputtering is on order of 3 cm (assuming pressure of 30 mTorr), with source-to-substrate distance as 5 cm, average number of collisions is about 5/3$\sim$2.
+
+A common purpose of sputter coating is to facilitate SEM observation.
+Pure gold target can be used for low-magnification studies; a platinum target will deliver satisfactory result for medium-to-high resolution studies.
+For high-magnification studies, a target of gold-palladium alloy is a good choice because the epitaxial growth is limited.\cite{Goldstein2007}
 
@@
 The X-ray emission stems from inner shell transition of the constitutive atoms, and cathodoluminescence from bandgap transition.
-Other \gls{ebeam} generated signals, such as Auger electrons, are usually not useful in SEM unless with ultra-high vacuum and clean surface.
 
@@
 \centering
-\includegraphics[width=0.5\textwidth]{UV-Vis_drs}
+\includegraphics[width=0.7\textwidth]{UV-Vis_drs}
 \caption[Schematic drawing of UV-Vis and DRS measurement]{Schematic drawing of (a) UV-Vis and (b) DRS measurement setup adopted from UV2600Plus manual.}

### 2015-01-19 ch-moox/moox.tex
walked in to exchange opinions with Advr, and walking out with his on wox and moox

@@
 
-\subsection{Synthesis Review of Molybdenum Oxide}
+\subsection{Review of Synthesis Methods of Molybdenum Oxide}
 
@@
 The reactants used in this study were listed in Table~\ref{tb:mosource}. All reactants were used as received without further processing.
-
 \begin{table}[htb]
@@
 Silicon substrates was first cleaned according to the procedure in Sec.~\ref{ch2sub} on page~\pageref{ch2sub}.
-To apply the catalysts, 54 $\mu$L 10 mM \ce{NaOH} (or \ce{KI}, \ce{Na2CO3}) was drop-cast onto clean substrates and then naturally left dry in a convection hood.
+To apply the catalysts, 54 $\mu$L 10 mM \ce{NaOH} (or \ce{KI}, \ce{Na2CO3}) was drop-cast onto clean substrates and then air dried in a chemical fume hood.
 Other alkali ions-containing substrates, such as glass (Fisher Scientific, microscope slide, 12-549) and indium tin oxide (ITO) coated glass (Delta Technologies, 25\si{\ohm}), were cleaned by the same routine except the absence of plasma cleaning and subsequent aqueous solution dipping.
@@
 In a typical synthesis run (Fig.~\ref{fig:mooxgrowth}), about 2 g molybdenum powders were loaded into the uniform heating zone and the sealed chamber was first pumped down to 10 mTorr. 
-Then oxygen flow varying between 0.1 sccm to 10 sccm (standard cubic centimeter per minute) was admitted from upstream inlet.
-With 10 sccm UHP Ar as carrier gas, the overall pressure reached about 200 mTorr.
-The heating temperature was ramped up to 800 \si{\degreeCelsius} in 30 min and lasted for 15 to 120 min.
-Then the heating power was turned off and the chamber was allowed to naturally cool down to room temperature.
-The substrate was placed in downstream location where the temperature was about 350 to 650 \si{\degreeCelsius} according to open air temperature profile.
-Non-catalytic growth shares the same procedure except the NaOH treatment.
-
-\section{Results and Discussion on Molybdenum Oxide}\label{sec:result}
-In this section, the growth of \ce{MoO3} on bare Si substrates was presented first, followed by catalytic growth, both of which were characterized by SEM, XRD, TEM and EDX.
-Then the catalytic growth mechanism was investigated using \ce{NaOH} treated Si substrate.
-The growth mechanism was probed using two series of control experiments.
-Then a growth model was proposed and verified.
-In the end, this growth model was applied onto other substrates with alkali metal ions, and various \ce{MoO3} nanostructures were produced.
-
-\subsection{Non-catalyst Growth}\label{sec:nonsi}
-
-The oxidization of Mo starts at 500 \si{\degreeCelsius}, and \ce{MoO3} vapor pressure begins to increase rapidly above 700 \si{\degreeCelsius}.\cite{Margrave1967} The melting point of \ce{MoO3} is reported as 795 \si{\degreeCelsius}.\cite{Levin1959} Based on these data, the growth was designed with parameters listed in Table~\ref{tab:mooxsi}.
-It is worth mentioning that these parameters are selected and optimized from a wide range of combinations.
-When the influence of one parameter is studied, the others are fixed, following the standard practice in controlled experiments.
-%growth parameter
-\begin{table}[htb]
-\centering
-\caption{Growth conditions of \ce{MoO3} on Si}\label{tab:mooxsi}
-\begin{tabular}{lcccr}
-\toprule
-&&&\multicolumn{2}{c}{Flow (sccm)} \\
-\cmidrule(l){4-5}
- & Temperature $T_h$ (\si{\degreeCelsius}) & Pressure (mTorr) & Ar & \ce{O2}  \\
-\midrule
-Typical values  & 800    & 200 & 10 & 10  \\
-\bottomrule
-\end{tabular}
-\end{table}
-
-The growth layout is schematically shown in Fig.~\ref{fig:mooxgrowth}.
-Notice that on the horizontal axis of temperature, zero inch is defined at the upstream edge of furnace.
-To facilitate discussion and provide a tight context, the author define the position of substrate as the coordinate of its upper-stream edge along this temperature axis, i.e., the substrate location is 7 inch in Fig.~\ref{fig:mooxgrowth}.
-The usual length of Si substrate is 1 inch.
-When positioned at 7 inch, it is then located in a temperature zone of $650 \sim 350$ \si{\degreeCelsius}.
 % cvd layout
@@
 \end{figure}
+Then oxygen flow varying between 0.1 sccm to 10 sccm (standard cubic centimeter per minute) was admitted from upstream inlet.
+With 10 sccm UHP Ar as carrier gas, the overall pressure reached about 200 mTorr.
+The heating temperature was ramped up to 800 \si{\degreeCelsius} in 30 min and lasted for 15 to 120 min.
+Then the heating power was turned off and the chamber was allowed to naturally cool down to room temperature.
+The substrate was placed in downstream location where the temperature was about 350 to 650 \si{\degreeCelsius} according to open air temperature profile.
+Non-catalytic growth shares the same procedure except the NaOH treatment on Si substrates.
 
-From previous works in our group,\cite{predeep2011} it was found that with $T_h = 600$ \si{\degreeCelsius} and substrate placed at 6.5 in, microflakes grew at the high temperature edge of Si, suggesting the nucleation already started.\footnote{in 020510 batch} When flow of oxygen was gradually reduced, diminished size of micro-flake was observed at the same location of substrates.
-This results indicated the rate-determining step is diffusion when oxygen flow was in the range of 2 sccm to 0.5 sccm.
-It was also found the deposition amount on a particular location of the substrate is not linearly proportional to the growth time, \emph{i.e.}, the growth at upper stream edge first increase then decrease.
-This is not surprising when considering the 3D temperature field in chamber requires some time to become synchronized as depicted in Fig.~\ref{fig:mooxgrowth}.
-Using conditions in Table~\ref{tab:mooxsi} and 2 h growth, this study observed the typical micro-flakes morphologies as shown in Fig.~\ref{fig:mosisem}.
+\section{Results and Discussion on Molybdenum Oxide}\label{sec:result}
+In this section, the growth of \ce{MoO3} on bare Si substrates was presented first, followed by catalytic growth, both of which were characterized by SEM, XRD, TEM and EDX.
+Then the catalytic growth mechanism was investigated using \ce{NaOH} treated Si substrate.
+The growth mechanism was probed using two series of control experiments.
+Then a growth model was proposed and verified.
+In the end, this growth model was applied onto other substrates with alkali metal ions, and various \ce{MoO3} nanostructures were produced.
+
+\subsection{Non-catalytic Growth}\label{sec:nonsi}
+
+For \ce{MoO3} non-catalytic growth, this study observed the typical micro-flakes morphologies as shown in Fig.~\ref{fig:mosisem}.
 Most flakes exhibit rectangular shape, with average thickness of one micron, standard deviation $\sigma_D=0.34 \mu$m.
@@
 \textsuperscript{\emph{a}} R chain mode;
-
 \end{table}
@@
 Since the concentration of Na is highest among these extra elements, it is most likely to induce the new morphology growth.
-A literature search indeed shows that there exists a Na-Mo-O phase diagram as shown in Fig.~\ref{fig:ch4pd}.\cite{Hoermann1929} Notice that\footnote{http://forum.wordreference.com/showthread.php?t=244497} the phases of the Na-Mo-O system can be written as \ce{Na2O.nMoO3}, where n = 1, 2, 3, and 4.
+A literature search indeed shows that there exists \ce{Na2MoO4}-\ce{MoO3} phase diagram as shown in Fig.~\ref{fig:ch4pd}.\cite{Hoermann1929} Notice that the phases of the Na-Mo-O system can be written as \ce{Na2O.nMoO3}, where n = 1, 2, 3, and 4.
 
@@
 It is difficult to acquire the accurate values along the substrate; however, by considering the flow rate, the actual temperature will be higher than predicted by open air measurement.\cite{Subannajui2010} The melting of \ce{Na2MoO4} is highly possible when taking into account of its size as well.\cite{Bruggemann1997} The continuous supply of \ce{MoO3} growth species will push the phase evolution towards high \ce{MoO3} molar ratio end, with $n$ in \ce{Na2O.nMoO3} increasing from 1 to 4.
-Each site of \ce{Na2MoO4} will continue absorb incoming \ce{MoO3}, forming a swelling droplet.
-\ce{MoO3} will precipitate from these seeds when a critical supersaturation concentration is reached, which is about 75\% in unit of mole according to Fig.~\ref{fig:ch4pd}.\footnote{This ratio considerably exceeds that of the usual metal catalyst scenario.
-This high solubility accounts for several observations in current experiments: the dimensions of individual deposit is much larger than that of initial droplet, the concentration of sodium in final products is extremely low.}    Based on this aforementioned analysis, the author propose a hypothesis:
+Each site of \ce{Na2MoO4} will continue absorb incoming \ce{MoO3}, forming a swelling particle.
+\ce{MoO3} will precipitate from these seeds when a critical supersaturation concentration is reached, which is about 75\% in unit of mole according to Fig.~\ref{fig:ch4pd}.
+This ratio considerably exceeds that of the usual metal catalyst scenario.
+This high solubility accounts for several observations in current experiments: the dimensions of individual deposit is much larger than that of initial particle, the concentration of sodium in final products is extremely low.
+Based on this aforementioned analysis, the author proposed following hypothesis:
 %theorem environment
 
-The reaction on NaOH-Si substrate follow the phase diagram, and \ce{Na2Mo4O13} serves as the catalyst promoting various 1D \ce{MoO3} growth.
+\emph{The reaction on NaOH-Si substrate follow the phase diagram, and \ce{Na2Mo4O13} serves as the catalyst promoting various 1D \ce{MoO3} growth.}
 
 In a typical 2 h growth, the \ce{MoO3} weight increase is about 20 mg, which is about $1.4\times 10^{-4}$ mol.
-This amount far exceeds the applied NaOH of $5\times 10^{-7}$ mol.\footnote{Sec.~\ref{sec:grow} on page.~\pageref{sec:grow}} To capture the early stage growth, the supply of \ce{MoO3} must be reduced in a controlled way.
+This amount far exceeds the applied NaOH of $5\times 10^{-7}$ mol used in the procedure of Sec.~\ref{sec:grow} on page~\pageref{sec:grow}.
+To capture the early stage growth, the supply of \ce{MoO3} must be reduced in a controlled way.
 This can be accomplished by tuning two factors: oxygen flow rate and growth time.
 In this thesis, two series of controlled growth were used to probe the evolution of \ce{MoO3} deposition on NaOH-Si substrate.
-The first series regulated \ce{O2} flow at 0.1, 1, 3 and 10 sccm with fixed growth time of 15 min.
+The first series regulated \ce{O2} flow at 0.1, 1, 3, and 10 sccm with fixed growth time of 15 min.
 The second series controls growth time at 15, 30, 60, and 90 min with fixed \ce{O2} flow of 10 sccm.
@@
 The oxygen regulated growths were characterized using SEM, EDX and Raman, as shown in Fig.~\ref{fig:ch4oxy}.
-When \ce{O2} flow $\leq 1$ sccm, the deposition show micron size plate growth (Fig.~\ref{fig:ch4oxy}a and d).
-As oxygen flow becomes higher, the deposition amount increases dramatically, with a morphology of 1D forked plate decorated by triangular shape particles.
+When \ce{O2} flow was $\leq 1$ sccm, the deposition show micron size plate growth (Fig.~\ref{fig:ch4oxy}a and d).
+As oxygen flow becomes higher, the deposition amount increased dramatically, with a morphology of 1D forked plate decorated by triangular shape particles.
 % sem
@@
 It is worth noting that the absence of Na signal in the forked \ce{MoO3} plate indicates the doping level would be lower than the detection limit of 0.01 wt.\% if the Na doping ever occurs.
-It should be pointed out the existence of \ce{Na2Mo3O10} phase is in doubt so far, and no Raman fingerprint is reported.\cite{Fomichev1992}
-
+It should be pointed out the existence of \ce{Na2Mo3O10} phase is in doubt so far, and no Raman fingerprint is reported.\cite{Fomichev1992} Table~\ref{tb:moo3ram} compared the Raman spectra of sodium molybdates and \ce{MoO3} between present work and literature reports.
+% moo3ram
+\begin{landscape}
+\begin{table}[htb]
+\centering
+\caption{Comparison of Raman shift (\si{cm^{-1}}) of sodium molybdates and molybdenum oxide}\label{tb:moo3ram}
+\begin{tabular}{lllllllll}
+\toprule
+        & \ce{Na2Mo2O7}    &    &    & \ce{Na2Mo2O7}    &       &       & \ce{MoO3}   &    \\
+\midrule
+\cite{Saraiva2011} & \cite{Fomichev1992} & this work& \cite{Fomichev1992} & \cite{Schofield2005} & this work   & \cite{Eda1992} & \cite{Siciliano2009}   &  this work   \\
+\midrule
+ 939    & 939/935 & 937         &        & 995    & 995         & 995    & 996       & 996   \\
+ 921    & 920/918 & 919         & 970    & 971    & 970         & 819    & 819       & 820   \\
+ 873    & 875/869 & 873         & 960    & 963    & 962         & 666    & 666       & 667   \\
+ 833    & 836/828 & 833         & 940    &        &             & 471    & 473       &       \\
+ 821    & 818/815 &             & 925    &        & 926         & 378    & 378       & 380   \\
+ 768    & 774/765 &             & 910    & 918    & 915         & 366    & 365       & 364   \\
+ 741    & 741/739 &             & 895    & 899    & 898         & 338    & 337       & 338   \\
+ 524    & 526/525 &             & 870    &        &             & 291    & 291       & 291   \\
+ 467    & 464/460 &             & 835    & 841    & 841         & 283    & 283       & 284   \\
+ 413    & 411/411 &             &        & 820    & 819         & 246    & 244       & 245   \\
+ 369    & 369/368 & 366         & 745    &        &             & 217    & 218       & 216   \\
+ 339    & 340/336 & 340         & 650    & 666    &             & 197    & 197       & 199   \\
+ 295    & 296/294 &             &        & 620    & 619         & 159    & 158       & 156   \\
+ 249    & 245/245 &             & 438    &        &             & 129    & 129       &       \\
+ 226    & 228/227 & 226         &        &        & 417         & 117    & 117       &       \\
+        & 215/215 &             & 405    &        &             & 100    & 98        &       \\
+ 200    & 199/199 & 198         &        & 396    & 393         & 84     & 84        &       \\
+ 176    &         &             & 382    & 381    &             &        &           &       \\
+ 137    & 140/138 &             &        & 368    &             &        &           &       \\
+ 120    & 120/120 &             & 348    &        &             &        &           &       \\
+ 84     & 84/84   &             & 335    & 339    & 336         &        &           &       \\
+        & 45/44   &             & 320    & 320    & 318         &        &           &       \\
+ 36     &         &             & 295    & 293    &             &        &           &       \\
+        &         &             & 272    &        & 267         &        &           &       \\
+        &         &             & 255    &        &             &        &           &       \\
+        &         &             &        & 246    &             &        &           &       \\
+        &         &             & 220    & 225    & 224         &        &           &       \\
+        &         &             &        & 202    &             &        &           &       \\
+        &         &             &        & 159    & 155         &        &           &       \\
+\bottomrule
+\end{tabular}
+\end{table}
+\end{landscape}
 The morphologies of second series experiment at constant \ce{O2} flow and varied growth time were shown in Fig.~\ref{fig:ch4ev}.
@@
 \includegraphics[width=0.5\textwidth]{MoO3_SFig_EDX}
-\caption[SEM images and EDS spectra identifying the location, morphology, and composition of the catalyst particles on the nanobelt structures]{SEM images and EDS spectra identifying the location, morphology, and composition of the catalyst particles on the nanobelt structures: (a-b) a catalyst particle (I) in the middle of a nanobelt (II), (c-d) two catalyst particles (I and II) leading the growth of two perpendicular nanobelts.
-}
+\caption[SEM images and EDS spectra identifying the location, morphology, and composition of the catalyst particles on the nanobelt structures]{SEM images and EDS spectra identifying the location, morphology, and composition of the catalyst particles on the nanobelt structures: (a-b) a catalyst particle (I) in the middle of a nanobelt (II), (c-d) two catalyst particles (I and II) leading the growth of two perpendicular nanobelts.}
 \label{fig:ch4edx1}
@@
 \item When no Mo powder is used, NaOH still holds onto substrate with some locations exhibiting etching.
-\item When no Mo powder is used while growth is performed in an old tube or oxygen flow is limited to a extreme small value, circular droplet-like solid were found and Mo, Na and O were detected, suggesting the existence of VLS mechanism.
-Using Mo coated substrate and subsequent NaOH treatment, similar droplets formation was repeated.
+\item When no Mo powder is used while growth is performed in an old tube or oxygen flow is limited to a extreme small value, circular particle-like solid were found and Mo, Na and O were detected, suggesting the existence of VLS mechanism.
+Using Mo coated substrate and subsequent NaOH treatment, similar particles formation was repeated.
 No discernible XRD pattern emerged, illustrating the amorphous nature of liquid catalyst.
@@
 Two kinds of belts found, tapering and non-tapering.
-The former one seems to have droplets mostly associated with sidewalls of the top part.
+The former one seems to have particles mostly associated with sidewalls of the top part.
 \item In reduced time or less oxygen supply growth, Na-containing site was found located onto the sidewall of belts instead of the usual expected tip.
@@
 And \ce{MoO3} XRD pattern is dominated by (0k0) peaks, indicating a 2D layer-by-layer growth with lateral rate exceeding that of axial direction.
-\item 2 h growth: there are crossed tapering belts at downstream boundary, with more than one droplet located along the interface of two perpendicular belts, EDX confirmed high Na content.
-\item Using NaOH treated hydrophobic substrates, dense tower array growth was found along the edge areas or molten periphery of droplets, where 5 min growth already show the initial stage of tower with diameter about 1 $\mu$ m, which increase to 10 $\mu$ m in prolonged growth.
+\item 2 h growth: there are crossed tapering belts at downstream boundary, with more than one particle located along the interface of two perpendicular belts, EDX confirmed high Na content.
+\item Using NaOH treated hydrophobic substrates, dense tower array growth was found along the edge areas or molten periphery of particles, where 5 min growth already show the initial stage of tower with diameter about 1 $\mu$ m, which increase to 10 $\mu$ m in prolonged growth.
 \end{enumerate}
@@
 The final morphology of observed nanoplate and nanobelt is a combined result of \gls{vs} and \gls{vls} growth.
-
 On the other hand, the tower-like structures in the second stage follow the axial growth mode in conventional VLS process.
@@
 Thus the transverse growth pathway is probably suppressed and axial growth becomes dominant.
+The above analysis was substantiated by the multiple observation revealed by SEM imaging, as shown in Fig.~\ref{fig:ch4msch}.
+\begin{figure}[htb]
+\centering
+\includegraphics[width=0.6\textwidth]{moo3_sche}
+\caption[SEM images for catalytic \ce{MoO3} growth]{SEM images for catalytic \ce{MoO3} growth: SEM images showing catalyst particles at different locations: (a) tip of a forked nanplate, (b) middle of a nanobelt, and (c) tip of another thin nanobelt; SEM images of microtowers with different morphologies: (d) cylindrical shape with tapered tip, (e) flat top, and (f) cone shape.
+}
+\label{fig:ch4msch}
+\end{figure}
 
@@
 To avoid any possible catalyst transports through surface diffusion, the two substrates were separated with several millimeters gap in between.
-
 \begin{figure}[htb]
@@
 \end{figure}
-
 After the growth, besides the non-catalyst rectangular plates, catalyst induced 1D structures were also found on the bare substrate (Fig.~\ref{fig:ch4sbs}b-i).
@@
 This fact allows for the usage of a variety of alkali metal based material as catalyst to promote \gls{vls} or \gls{vss} growth of \ce{MoO3}.
-Some experiments have been performed in this study, including growth using KI and \ce{Na2CO3} treated Si substrate, glass and mica.
-Fig.~\ref{fig:ch4al1}a-b show the long belt growth on KI treated Si substrate and towers on ITO glass, respectively.
-Compared to NaOH-Si growth, the belt on KI appears with rough edge, whereas the towers on ITO glass exhibit stacking features.
+Two group of experiments have been performed in this study; the first one used \ce{KI} and \ce{Na2CO3} treated Si substrate, the second one used alkali metal ions containing substrate, including ITO/glass, glass, and mica.
+Fig.~\ref{fig:ch4al1}a-b show the long belt growth on KI treated Si substrate and the forked plate growth on \ce{Na2CO3} treated Si, respectively.
+Compared to NaOH-Si growth, the belt on KI appears with rough edge, whereas No long belt or tower was observed on the sample with \ce{Na2CO3}.
 
@@
 \centering
-\includegraphics[width=0.6\textwidth]{Fig7_MoO3_Small}
+\includegraphics[width=0.6\textwidth]{moo3_alt2}
 \caption[Alternative catalysts for \ce{MoO3} growth]{Alternative catalysts for \ce{MoO3} growth.
-SEM images of \ce{MoO3} 1D structures.
-(a) nanobelts grown with KI and (b) microtowers grown on ITO glass}
+SEM images of \ce{MoO3} 1D structures: (a) nanobelts grown with KI on Si and (b) the forked plate growth with \ce{Na2CO3} on Si.}
 \label{fig:ch4al1}
@@
 
-Fig.~\ref{fig:ch4al2}a-c illustrate the forked plate growth on \ce{Na2CO3} treated Si, sword-shape belts on glass, and nanoblets growth on mica, respectively.
-No long belt or tower was observed on the sample with \ce{Na2CO3}.
-Long belts found on mica (\ce{K(Al2)(Si3Al)O10(OH)2}) probably arise from potassium-catalyzed \gls{vls} mechanism.\cite{Hu2011}
+Fig.~\ref{fig:ch4al2}a-c illustrate microtowers grown on ITO glass, sword-shape belts on glass, and nanoblets growth on mica, respectively.
+The towers on ITO glass exhibited stacking features.
+The sword-shape belts on glass arise from a combination of VSS and VS mechanism.
+The long belts found on mica (\ce{K(Al2)(Si3Al)O10(OH)2}) probably arise from potassium-catalyzed \gls{vls} mechanism.\cite{Hu2011}
 
@@
 \centering
-\includegraphics[width=0.8\textwidth]{SFig5_MoO3_Small}
+\includegraphics[width=0.8\textwidth]{moo3_alt1}
 \caption[Alternative catalysts for \ce{MoO3} growth cont]{Alternative catalysts for \ce{MoO3} growth.
-SEM images of MoO3 1D structures: (a) forked nanoplates grown with \ce{Na2CO3}, (b) triangular microbelts grown on glass, and (c) nanobelts and microbelts grown on mica.}
+SEM images of MoO3 1D structures: (a) microtowers grown on ITO glass, (b) triangular microbelts grown on glass, and (c) nanobelts and microbelts grown on mica.}
 \label{fig:ch4al2}
 \end{figure}
-
-The various growth morphologies found using alkali metal based materials as catalysts demonstrate the proposed \gls{vss} mechanism and transverse mode is a general phenomenon, and broad engineering space could be explored to control the dimension of \ce{MoO3}.
-As an example, this study further illustrated the tunable growth of \ce{MoO3} nanoribbons on glass substrate.
-Achieving morphology controlled growth of \ce{MoO3} on transparent substrates, e.g., glass, is an important progress towards process integration and device fabrication in photon-energy related applications.
+A rudimentary analysis on the \ce{Na+} diffusion in glass was performed to understand the growth dynamics of \ce{MoO3} using those alkali ions containing substrates.
 Because the alkali ions in glass can diffuse out at elevated temperature, the proposed \gls{vss} mechanism will modify the \ce{MoO3} deposition.
@@
 \centering
-\caption[Na diffusion coefficient]{Na diffusion coefficient (\si{cm^2\per\second}), R is molar gas constant (8.315 \si{\joule\per mol\per K}), and T is temperature in K}\label{tab:mona}
+\caption[Mass transport of sodium ions in silica glass]{Mass transport of sodium ions in silica glass, with diffusion coefficient in unit of \si{cm^2\per\second}}\label{tab:mona}
 \begin{tabular}{lcr}
 \toprule
- Composition & Value  & Reference  \\
+ Composition & Na diffusion coefficient  & Reference  \\
 \midrule
@@
 \end{tabular}
+
+R is molar gas constant (8.315 \si{\joule\per mol\per K}), and T is temperature in K.
 \end{table}
@@
 Only one was reported by \citeauthor{Kazenas2010}.\cite{Kazenas2010} The partial pressure of \ce{Na2MoO4} is calculated to be 0.2 mTorr at 800 \si{\degreeCelsius} and $3.5\times 10^{-3}$ mTorr at 670 \si{\degreeCelsius}.\footnote{$\log P(atm)= -13794/T + 6.19$}
-
-This thesis studied the effect of temperature, oxygen partial pressure and growth time towards \ce{MoO3} deposition on glass substrates.
-Each factor was divided into two levels, with $T$ at 700 and 800 \si{\degreeCelsius}, \ce{O2} flow at 1 and 10 sccm, and growth time of 15 and 60 min.
-And the morphological variations revealed by SEM imaging were summarized in Table~\ref{tab:mo3glass}.
-% glass growth matrix
-\begin{table}[htb]
-\centering
-\caption{\ce{MoO3} growth on glass}\label{tab:mo3glass}
-\begin{tabular}{lccp{3in}}
-\toprule
-\multicolumn{3}{c}{Growth Conditions} \\
-\cmidrule(l){1-3}
-$T$ (\si{\degreeCelsius}) & \ce{O2} (sccm) & Time (min) & Morphology  \\
-\midrule
-700    &  10   & 15  &   about 50 $\mu$m belts, some towers \\
-700   &  1   & 60  &   irregular shape, not too much growth\\
-700    &  10   & 60  &   droplet almost all on tip of belts, many towers \\
-800    &  1   & 15  &   tens $\mu$m belt with sharp edge(100 nm thick, and 1micro wide) dominates\\
-800   &  1   & 60  &   exhibiting ITO features, droplets on tips of belt, many tower like structures\\
-800    &  10   & 15  &   rounded edge flakes dominate, modest density tapering belt, and some possible tower\\
-800    &  10   & 60  &   ITO/glass features, aggregated belts, some towers\\
-\bottomrule
-\end{tabular}
-\end{table}
-The 800-1-15 combination produced dense \ce{MoO3} nanoplate with length about 10 $\mu$m, width $300\sim500$ nm and thickness less than 100 nm, as illustrated in Fig.~\ref{fig:ch4glass}.
-These \ce{MoO3} nanoplates are of high crystalline quality, and could potentially show enhanced photoelectrochemical and electrochromic activities.
-\begin{figure}[htb]
-\centering
-\includegraphics[width=0.7\textwidth]{moo3_glass_lbd}
-\caption[Optimized \ce{MoO3} nanoplates growth on glass]{Optimized \ce{MoO3} nanoplates growth on glass.}
-\label{fig:ch4glass}
-\end{figure}
 

### 2015-01-19 ch-wox/ch-wox.tex
walked in to exchange opinions with Advr, and walking out with his on wox and moox

@@
 \section{Experimental}
-
 Metallic tungsten powders were utilized as source materials in this work.
 Four kinds of W powder were used in total, as summarized in Table~\ref{tab:powder}.
-Two growth configurations were explored, namely ordinary transport and seeded growth.
+Two growth configurations were explored, namely non-seeded growth and seeded growth.
 % Tungsten powders size and purity
@@
 
-In a typical ordinary transport experiment (Fig.~\ref{fig:wogrow}), about 2 g tungsten powder was positioned in the upstream end of a quartz boat and downstream about 2.5 inch the substrate was stationed.
+\subsection{Non-seeded growth}
+
+In a typical non-seeded experiment (Fig.~\ref{fig:wogrow}), about 2 g tungsten powder was positioned in the upstream end of a quartz boat and downstream about 2.5 inch the substrate was stationed. 
 % cvd NW growth
@@
 The substrates were p-type, boron-doped and [100]-orientated silicon with about 1 $\mu$m thermally-grown silicon oxide layer on the polished side.
-The cleaning procedures have been elucidated on page~\pageref{ch2sub}.
-The boat was then loaded into reaction chamber in a way that the powder source was placed in the center of heating zone, and the substrate upstream end was aligned at 6.5 inch.\footnote{As defined in Fig.~\ref{fig:wogrow}} After pumping down, 1 \gls{sccm} \ce{O2} and 10 sccm Ar were admitted into the chamber, respectively, after which the overall pressure read approximately 110 mTorr.
+The substrate cleaning procedures have been elucidated on page~\pageref{ch2sub}.
+The boat was then loaded into reaction chamber in a way that the powder source was placed in the center of heating zone, and the substrate upstream end was aligned at 6.5 inch as defined in Fig.~\ref{fig:wogrow}.
+After pumping down, 1 \gls{sccm} \ce{O2} and 10 sccm Ar were admitted into the chamber, respectively, after which the overall pressure read approximately 110 mTorr.
 The temperature ramped up to 1000 \si{\degreeCelsius} in 30 min and lasted for 4 h, and subsequently the apparatus was allowed to naturally cool down to room temperature.
+
+\subsection{Seeded growth}
+In the seeded growth, additional tungsten powders was used on the substrate serving as local seed, on which dense \ce{WO3} NW array grew.
+For the tungsten seed particles, 3N powders were used in typical NW growth, and other tungsten powders with different sizes were employed in control experiments including 3N5, 4N5, and 5N.
+All reactants were employed as received without further processing.
+
+In a typical growth, high purity tungsten source was positioned at the upstream end of a quartz boat, with the substrate located ca.
+65 mm downstream.
+The quartz boat was then transferred into the reaction chamber in a way that the tungsten source was located at the center of the reaction chamber.
+During the growth, the tungsten source was heated at 1000 \si{\degreeCelsius}, while the substrate temperature ranged from 800 \si{\degreeCelsius} to 400 \si{\degreeCelsius}.
+After the reaction chamber was pumped down to an ultimate pressure of $\sim8$ mTorr, 1 sccm oxygen (\ce{O2}) and 10 sccm argon (Ar) were introduced into the chamber, respectively.
+The heating temperature was ramped to 1000 \si{\degreeCelsius} in 30 min and lasted for 240 min.
+Subsequently, the apparatus was allowed to naturally cool down to room temperature.
+
+To study the growth mechanism, controlled experiments were performed on the oxidation of the tungsten seed particles dispersed on the substrate.
+In a typical oxidation experiment, tungsten powders were loaded into the uniform heating zone and the sealed chamber was pumped down to an ultimate pressure of $\sim8$ mTorr.
+Then oxygen flow varying between 1 sccm to 10 sccm was admitted from upstream inlet.
+With 10 sccm UHP Ar (99.999\%) as carrier gas, the overall pressure reached to about 100 mTorr.
+The heating temperature (500 to 750 \si{\degreeCelsius}) was ramped up in 30 min and lasted for 30 min.
+Then the heating power was turned off and the chamber was allowed to naturally cool down to room temperature.
 
@@
 \includegraphics[width=0.7\textwidth]{nawox_semedx.jpg}
-\caption[SEM and EDX on \ce{Na_xWO3}]{SEM images of (a) dense array of the as-synthesized ultra-long nanowires on \ce{SiO2}-Si substrate and (b) rectangular microplates grow among the nanowires.
+\caption[SEM, EDX and XRD on sodium tungsten oxides sample]{SEM images of (a) dense array of the as-synthesized ultra-long nanowires on \ce{SiO2}-Si substrate and (b) rectangular microplates grow among the nanowires.
 (c) EDS and (d) XRD spectra showing the chemical compositions and phases of the deposition.}
@@
 \includegraphics[width=0.8\textwidth]{nawox_tem.jpg}
-\caption[TEM analyses on sodium tungsten oxide sample]{TEM images at low-magnification, HRTEM images, and EDS spectra of a \ce{Na5W_{14}O_{44}} NW (a, b, c), a \ce{WO3} NW (d, e, f), and a \ce{Na2W4O_{13}} microplate (g, h, i).}
+\caption[TEM analyses on sodium tungsten oxides sample]{TEM images at low-magnification, HRTEM images, and EDS spectra of a \ce{Na5W_{14}O_{44}} NW (a, b, c), a \ce{WO3} NW (d, e, f), and a \ce{Na2W4O_{13}} microplate (g, h, i).}
 \label{fig:nawoxtem}
@@
 \includegraphics[width=0.7\textwidth]{nawox_raman_series}
-\caption[Raman spectra on \ce{Na_xWO3}]{Raman spectra of (a) microplates matching the reported peak positions of the \ce{Na2W4O_{13}} phase, and (b) nanowires with comparisons to the reported major peak positions of \ce{WO3} (shown by black line) and \ce{Na2W4O_{13}} (shown by red line) phases.}
+\caption[Raman spectra on sodium tungsten oxides sample]{Raman spectra of (a) microplates matching the reported peak positions of the \ce{Na2W4O_{13}} phase, and (b) nanowires with comparisons to the reported major peak positions of \ce{WO3} (shown by black line) and \ce{Na2W4O_{13}} (shown by red line) phases.}
 \label{fig:nawoxram}
@@
 \includegraphics[width=0.9\textwidth]{nawox_sch.jpg}
-\caption[Schematic drawings of residual \ce{Na_xWO3} growth]{Schematic drawings showing (a) growth with tungsten source in a new tube, (b) enhanced growth with both residue deposition and tungsten source, and (c) growth with residue deposition only.}
+\caption[Schematic drawings of residual sodium tungsten oxides growth]{Schematic drawings showing (a) growth with tungsten source in a new tube, (b) enhanced growth with both residue deposition and tungsten source, and (c) growth with residue deposition only.}
 \label{fig:nawoxsch}
@@
 In this study, a seeded growth approach was developed and proved to be a successful alternative way.
-In the seeded growth, additional tungsten powders was used on the substrate serving as local seed, on which dense \ce{WO3} NW array grew.
 
@@
 A systematic investigation was performed on the oxidation behavior of tungsten powder to evaluate the temperature effect, size-dependence and influence of oxygen partial pressure.
-
-In a typical oxidation experiment, tungsten powders were loaded into the uniform heating zone and the sealed chamber was pumped down to an ultimate pressure of $5\sim8$ mTorr.
-Then oxygen flow varying between 1 sccm to 10 sccm was admitted from upstream inlet.
-With 10 sccm UHP Ar (99.999\%) as carrier gas, the overall pressure reached to about 100 mTorr.
-The heating temperature (500 to 750 \si{\degreeCelsius}) was ramped up in 30 min and lasted for 30 min.
-Then the heating power was turned off and the chamber was allowed to naturally cool down to room temperature.
 
@@
 
-In regarding to the formation of NWs on tungsten powder itself, this study assumes the driving force is related to interfacial strain between W and \ce{WOx}.
+In regarding to the formation of NWs on tungsten powder itself, this study assumes the driving force is related to interfacial strain between W and \ce{WO_x}.
 Oxidation of tungsten proceed slowly at room temperature and an oxide layer of 100 \si{\angstrom} was found on the surface of tungsten foils.\cite{Warren1996} The tungsten powder used in current study would be covered by a thin oxide layer as well.
@@
 
-\subsection{Tungsten Oxides: Other Methods}
+\subsection{Tungsten Oxides: Other Method}
 

### 2015-01-19 misc/SI_thesis.tex
all chapter fine tuned
mini working exmp updated

@@
 
+Functional oxides lie in the doping characteristics: cations with mixed valence states, and anions with vacancies.
+Vapor-phase growth, powder source is vaporized at an elevated T and .\cite{Dai2003} Dislocation growth mechanism, VS driven by dislocation, kinetics during growth controlled by T and supersaturation ratio.
+Probability of nucleation and desorption; cation-anion molecules float, the rough structure of the tip; self-catalyzed, where a thin metal layer is present, \cite{Sears1955,Blakely1962}
+
+Thermal evaporation process sensitive to the concentration of oxygen in growth system, influencing not only the volatility of source materials but also the stoichiometry of vapor phase.\cite{Dai2002}
+
 \section{band and bond}
@@
 \chapter{experimental}
+In this work, magnetron sputtering (Denton Vacuum Desk IV) was used to coat thin layers of metals onto cleaned substrates.
+As shown in Fig.~\ref{fig:ch2magsp}, a high potential created between the target (cathode) and substrate ionizes the argon molecules.
+These ions are accelerated to bombard the target foils, knocking out active atoms which subsequently deposit onto the substrates.
+A magnetic field is applied to confine electrons to the vicinity of the foils.
+These electrons in turn increase the ionization yield.
+Sputtering is a better PVD technique than \gls{ebeam} deposition since it alleviates the adverse effects in the latter. 
+Other \gls{ebeam} generated signals, such as Auger electrons, are usually not useful in SEM unless with ultra-high vacuum and clean surface.
 
@@
 \chapter{wo3}
+
+\iffalse
+The author believe the resolution to a large extent depends on the phase transitions, as discussed in Section.~\ref{sec:wonawo}.
+
+A thin film example on the valency number, color center density. some calculation on doping, uv-vis results on the thin film.
+
+\fi
 
@@
 For example, the atomic weight of Pb is 207 g/mol, and density is 11.34 g/cm3; then the molar volume is 207/11.34 = 18.2539.
-Assuming sphere as building unit, then $\frac{\pi}{6}D^3$ = 18.2539/N_A.
+Assuming sphere as building unit, then $\frac{\pi}{6}D^3 = 18.2539/N_A$.
 Solving D as 0.3868 nm.
@@
 \toprule
-Material & MP(\si{\degreeCelsius}) & BP(\si{\degreeCelsius}) & reference\\
+Material & MP(\si{\degreeCelsius}) & BP(\si{\degreeCelsius}) & Reference\\
 \midrule
-\ce{NaOH}        & 318 & 1388 & handbook  \\
-\ce{NaI}        & 651 & 1300 & MSDS    \\
-\ce{KI}        & 681 & 1330 & MSDS   \\
-\ce{Na2CO3}        & 851 & Not determined & MSDS    \\
-\ce{Na2MoO4}        & 687 & Not available & handbook   \\
-\ce{MoO3}    & 795 & 1155 & MSDS   \\
+\ce{NaOH}        & 318 & 1388 & \cite{crc1977}  \\
+\ce{NaI}        & 651 & 1300 & \cite{crc1977}    \\
+\ce{KI}        & 681 & 1330 & \cite{crc1977}   \\
+\ce{Na2CO3}        & 851 & Not determined & \cite{crc1977}    \\
+\ce{Na2MoO4}        & 687 & Not available & \cite{crc1977}   \\
+\ce{MoO3}    & 795 & 1155 & \cite{crc1977}   \\
 \ce{MoO2}    & 1100(decomp) & Not available & MSDS   \\
+\bottomrule
+\end{tabular}
+\end{table}
+
+\begin{table}[htb]
+\centering
+\caption{Comparison of Raman shift (\si{cm^{-1}}) of sodium molybdates and molybdenum oxide}\label{tb:moo3ram}
+\begin{tabular}{lllllllll}
+\toprule
+        & \ce{Na2Mo2O7}    &    &    & \ce{Na2Mo2O7}    &       &       & \ce{MoO3}   &    \\
+\midrule
+\cite{Saraiva2011} & \cite{Fomichev1992} & this work& \cite{Fomichev1992} & \cite{Schofield2005} & this work   & \cite{Eda1992} & \cite{Siciliano2009}   &  this work   \\
+\midrule
+ 939    & 939/935 & 937         &        & 995    & 995         & 995    & 996       & 996   \\
+ 921    & 920/918 & 919         & 970    & 971    & 970         & 819    & 819       & 820   \\
+ 873    & 875/869 & 873         & 960    & 963    & 962         & 666    & 666       & 667   \\
+ 833    & 836/828 & 833         & 940    &        &             & 471    & 473       &       \\
+ 821    & 818/815 &             & 925    &        & 926         & 378    & 378       & 380   \\
+ 768    & 774/765 &             & 910    & 918    & 915         & 366    & 365       & 364   \\
+ 741    & 741/739 &             & 895    & 899    & 898         & 338    & 337       & 338   \\
+ 524    & 526/525 &             & 870    &        &             & 291    & 291       & 291   \\
+ 467    & 464/460 &             & 835    & 841    & 841         & 283    & 283       & 284   \\
+ 413    & 411/411 &             &        & 820    & 819         & 246    & 244       & 245   \\
+ 369    & 369/368 & 366         & 745    &        &             & 217    & 218       & 216   \\
+ 339    & 340/336 & 340         & 650    & 666    &             & 197    & 197       & 199   \\
+ 295    & 296/294 &             &        & 620    & 619         & 159    & 158       & 156   \\
+ 249    & 245/245 &             & 438    &        &             & 129    & 129       &       \\
+ 226    & 228/227 & 226         &        &        & 417         & 117    & 117       &       \\
+        & 215/215 &             & 405    &        &             & 100    & 98        &       \\
+ 200    & 199/199 & 198         &        & 396    & 393         & 84     & 84        &       \\
+ 176    &         &             & 382    & 381    &             &        &           &       \\
+ 137    & 140/138 &             &        & 368    &             &        &           &       \\
+ 120    & 120/120 &             & 348    &        &             &        &           &       \\
+ 84     & 84/84   &             & 335    & 339    & 336         &        &           &       \\
+        & 45/44   &             & 320    & 320    & 318         &        &           &       \\
+ 36     &         &             & 295    & 293    &             &        &           &       \\
+        &         &             & 272    &        & 267         &        &           &       \\
+        &         &             & 255    &        &             &        &           &       \\
+        &         &             &        & 246    &             &        &           &       \\
+        &         &             & 220    & 225    & 224         &        &           &       \\
+        &         &             &        & 202    &             &        &           &       \\
+        &         &             &        & 159    & 155         &        &           &       \\
+        &         &             &        & 131    &             &        &           &       \\
+        &         &             &        & 119    &             &        &           &       \\
 \bottomrule
@@
 
-Tungsten bronze: \ce{AxWO3}, or \ce{AxW_{1-x}^{6+}W_x^{5+}O3}, 
+Tungsten bronze: \ce{A_xWO3}, or \ce{A_xW_{1-x}^{6+}W_x^{5+}O3}, 
 Tungstates: \ce{(A2O)x.(WO3)n}, full oxidized, no free electron, transparent in visible and NIR.

### 2015-01-19 misc/draft.tex
After first review in 2014
mini working exmp updated

@@
 \chapter{paper draft}
+
+\footnote{U.S. Department of Energy, "Energy Efficiency Trends in Residential and Commercial Buildings", 2008.}
+
 \section{Data Processing}
@@
 \subsection{not used}
+
+The oxidization of Mo starts at 500 \si{\degreeCelsius}, and \ce{MoO3} vapor pressure begins to increase rapidly above 700 \si{\degreeCelsius}.\cite{Margrave1967} The melting point of \ce{MoO3} is reported as 795 \si{\degreeCelsius}.\cite{Levin1959} Based on these data, the growth was designed with parameters listed in Table~\ref{tab:mooxsi}.
+It is worth mentioning that these parameters are selected and optimized from a wide range of combinations.
+When the influence of one parameter is studied, the others are fixed, following the standard practice in controlled experiments.
+%growth parameter
+\begin{table}[htb]
+\centering
+\caption{Growth conditions of \ce{MoO3} on Si}\label{tab:mooxsi}
+\begin{tabular}{lcccr}
+\toprule
+&&&\multicolumn{2}{c}{Flow (sccm)} \\
+\cmidrule(l){4-5}
+ & Temperature $T_h$ (\si{\degreeCelsius}) & Pressure (mTorr) & Ar & \ce{O2}  \\
+\midrule
+Typical values  & 800    & 200 & 10 & 10  \\
+\bottomrule
+\end{tabular}
+\end{table}
+
+The growth layout is schematically shown in Fig.~\ref{fig:mooxgrowth}.
+Notice that on the horizontal axis of temperature, zero inch is defined at the upstream edge of furnace.
+To facilitate discussion and provide a tight context, the author define the position of substrate as the coordinate of its upper-stream edge along this temperature axis, i.e., the substrate location is 7 inch in Fig.~\ref{fig:mooxgrowth}.
+The usual length of Si substrate is 1 inch.
+When positioned at 7 inch, it is then located in a temperature zone of $650 \sim 350$ \si{\degreeCelsius}.
+
+From previous works in our group,\cite{predeep2011} it was found that with $T_h = 600$ \si{\degreeCelsius} and substrate placed at 6.5 in, microflakes grew at the high temperature edge of Si, suggesting the nucleation already started.\footnote{in 020510 batch} When flow of oxygen was gradually reduced, diminished size of micro-flake was observed at the same location of substrates.
+This results indicated the rate-determining step is diffusion when oxygen flow was in the range of 2 sccm to 0.5 sccm.
+It was also found the deposition amount on a particular location of the substrate is not linearly proportional to the growth time, \emph{i.e.}, the growth at upper stream edge first increase then decrease.
+This is not surprising when considering the 3D temperature field in chamber requires some time to become synchronized as depicted in Fig.~\ref{fig:mooxgrowth}.
+Using conditions in Table~\ref{tab:mooxsi} and 2 h growth,
+
+\footnote{http://forum.wordreference.com/showthread.php?t=244497}
 

### 2015-01-24 ch-tms/tms.tex
core shell chapter revised

@@
 The \ce{WO3}-\ce{WS2} core-shell nanowires were fabricated using a sulfurization process based on the \ce{WO3} NWs prepared by the seeded growth method in Chapter~3, Sec.~\ref{sec:sgfg}.
-For the sake of completeness, schematic layout of overall growth were illustrated in Fig.~\ref{fig:ch5grow} including the oxidation of W powder, the seeded growth and the sulfurization process.
+For the sake of completeness, schematic layout of the two-step growth were illustrated in Fig.~\ref{fig:ch5grow} including the seeded growth and subsequent sulfurization process.
 % cvd NW growth
@@
 \centering
-\includegraphics[width=0.7\textwidth]{cs_sfig1_all}
-\caption[Schematic diagrams of tungsten power oxidization, seeded growth of \ce{WO3} NW, and sulfurization process]{Schematic diagrams of (a) tungsten power oxidization, (b) seeded growth of \ce{WO3} NW, and (c) sulfurization process.
-(d) Chemical vapor deposition system temperature profile measured at ambient condition.
-The zero inch location is defined at the upstream edge of furnace.}
+\includegraphics[width=0.6\textwidth]{cs_growth_lbd}
+\caption[Schematic diagrams of seeded growth of \ce{WO3} NW and sulfurization process]{Schematic diagrams of (a) seeded growth of \ce{WO3} NW and (b) sulfurization process. }
 \label{fig:ch5grow}
 \end{figure}
-In a typical oxidation experiment shown in Fig.~\ref{fig:ch5grow}a, tungsten powders were loaded into the uniform heating zone and the sealed chamber was pumped down to an ultimate pressure of $5\sim8$ mTorr.
-Then oxygen flow varying between 1 sccm to 10 sccm (standard cubic centimeter per minute) was admitted from upstream inlet.
-With 10 sccm UHP Ar (99.999\%) as carrier gas, the overall pressure reached to about 100 mTorr.
-The heating temperature (500 to 750 \si{\degreeCelsius}) was ramped up in 30 min and lasted for 30 min.
-Then the heating power was turned off and the chamber was allowed to naturally cool down to room temperature.
-
-In a representative seeded growth (Fig.~\ref{fig:ch5grow}b), 4N5 or 5N tungsten source powder (Table.~\ref{tab:powder}) was positioned in the upstream end of a quartz boat and downstream about 2.5 inch the substrate was stationed.
+In a representative seeded growth (Fig.~\ref{fig:ch5grow}a), 4N5 or 5N tungsten source powder as defined in Table~\ref{tab:powder} was positioned in the upstream end of a quartz boat and downstream about 2.5 inch the substrate was stationed.
 Additional tungsten seed powders (3N) were distributed evenly onto the substrate.
@@
 \ce{WO3}-\ce{WS2} core-shell NWs were synthesized using direct sulfurization of \ce{WO3} NWs.
-As depicted in Fig.~\ref{fig:ch5grow}c, the as-grown \ce{WO3} NWs were loaded into the center of heating furnace, and $\sim200$ mg sulfur (Alfa Aesar 10785, 99.5\%) was positioned just outside the upstream edge of furnace, where the maximum temperature was about 240 \si{\degreeCelsius}.
+As depicted in Fig.~\ref{fig:ch5grow}b, the as-grown \ce{WO3} NWs were loaded into the center of heating furnace, and $\sim200$ mg sulfur (Alfa Aesar 10785, 99.5\%) was positioned just outside the upstream edge of furnace, where the maximum temperature was about 240 \si{\degreeCelsius}.
 After pumping down, the reaction chamber was flushed two times to expel residual air.
@@
 The surface of the NWs were rather smooth without other attachments.
-The NWs array grow slightly larger than the W seeds ($\sim$12 $\mu$m), mostly due to the elongation of NW.
+The NWs array grew slightly larger than the W seeds ($\sim$12 $\mu$m), mostly due to the elongation of NW.
 \begin{figure}[htb]
@@
 \caption[Morphology and composition analysis on the as-synthesized \ce{WO3}-\ce{WS2} core-shell structures]{Morphology and composition analysis on the as-synthesized \ce{WO3}-\ce{WS2} core-shell structures.
-(a) Low magnification and (b) high magnification SEM images showing the NWs almost retain their original shapes after sulfurization.
+(a) Low magnification and (b) high magnification SEM images showing the NWs morphologies after sulfurization.
 (c) EDX spectroscopy revealing the presence of sulfur element after sulfurization.}
@@
 \end{figure}
+
 After examining dozens of core-shell NWs, it was found the \ce{WS2} layer number at NW tip was usually the largest, reaching more than ten, and the layer number could decrease to one along the NW body, but there exist some layer number fluctuation and shape modification.
@@
 \centering
-\includegraphics[width=0.7\textwidth]{ws2_growth3}
+\includegraphics[width=0.7\textwidth]{cs_tem_g1}
 \caption[HRTEM imaging on the tip area of one core-shell nanowire]{HRTEM imaging on the tip area of one core-shell nanowire.}
@@
 \centering
-\includegraphics[width=0.7\textwidth]{ws2_growth4}
+\includegraphics[width=0.7\textwidth]{cs_tem_g3_lbd}
 \caption[HRTEM imaging on one tapered core-shell nanowire showing fluctuation of layer numbers]{HRTEM imaging on one tapered core-shell nanowire showing fluctuation of layer numbers.}
@@
 
-No obviously consumed core region was observed among most of the core-shell NWs examined under TEM.
-An exception is shown in Fig.~\ref{fig:ch5ws2tem2}.
-It is worth mentioning that some interesting growth behavior around the void region, where a new \ce{WS2} layer pushing through the already formed \ce{WS2} ones, deviating from the diffusion growth model.
 % coreshell tem
@@
 \centering
-\includegraphics[width=0.7\textwidth]{ws2_growth1}
+\includegraphics[width=0.7\textwidth]{core-shell_void_growth}
 \caption[HRTEM imaging on one core-shell nanowire showing consumed core]{HRTEM imaging on one core-shell nanowire showing consumed core.}
@@
 \end{figure}
+No obviously consumed core region was observed among most of the core-shell NWs examined under TEM.
+An exception is shown in Fig.~\ref{fig:ch5ws2tem2}.
+Note the rectangular area show abrupt termination of one \ce{WS2} layer, which was tentatively attributed to stacking fault in this study.
 
@@
 \centering
-\includegraphics[width=0.5\textwidth]{ws2trans}
+\includegraphics[width=0.5\textwidth]{cs_NW_transfer}
 \caption[Core-shell nanowires transfer steps]{Core-shell nanowires transfer steps.
-(a) tungsten tip under X100 objective, (b) NWs dispersed onto PDMS, (c) one NW picked up using tungsten tip and (d) tranferred NW on TEM grid}
+(a) tungsten tip under X100 objective, (b) NWs dispersed onto PDMS, (c) one NW picked up using tungsten tip and (d) tranferred NW on TEM grid with two tips indicated by the arrows.}
 \label{fig:ch5ws2trans}
@@
 \centering
-\includegraphics[width=0.6\textwidth]{ws2map}
+\includegraphics[width=0.6\textwidth]{cs_nw_map}
 \caption[Core-shell nanowires mapping]{Core-shell nanowires mapping.
-Optical image of one NW on TEM under (a) x100 magnification and (b) digital zoom-in view; (b) Low magnification and (d) high magnification TEM images on the same NW.}
+Optical image of one NW on the lacey  carbon TEM grid under (a) x100 magnification and (c) digital zoom-in view with two end indicated by the arrows, TEM images of (b) low magnification and (d) high magnification acquired on the same NW specimen.}
 \label{fig:ch5ws2map}
@@
 
-Fig.~\ref{fig:ch5ws2ram}a-d depict typical \ce{WO3}-\ce{WS2} NWs used in TEM-Raman integrated study.
+Fig.~\ref{fig:ch5ws2ram}a-d depict typical \ce{WO3}-\ce{WS2} NWs in the TEM-Raman integrated study.
 The diameter of these core-shell NWs is around 100 nm and the length around 10 $\mu$m, allowing for up to five distinctive Raman scattering sites.
-Fig.~\ref{fig:ch5ws2ram}e shows the associated Raman spectra acquired on core-shell NWs using 532 nm excitation.
+Fig.~\ref{fig:ch5ws2ram}e shows the associated Raman spectra acquired on core-shell NWs using 532 nm excitation wavelength.
 Two strong peaks were observed between 300 and 450 \si{cm^{-1}}.
@@
 The other peak at about 420 \si{cm^{-1}} is assigned to $A_{1g}$ mode in both bulk\cite{Sekine1980} and few layer \ce{WS2}.
-Tubular \ce{WS2} structure can be viewed as rolling up the planar \ce{WS2} sheet, and new Raman features arise subsequently, \emph{e.g.}, a shoulder mode emerges on the low frequency side of $A_{1g}$ mode.
+Tubular \ce{WS2} structure can be viewed as rolling up the planar \ce{WS2} sheet, and new Raman features arise subsequently, e.g., a shoulder mode emerges on the low frequency side of $A_{1g}$ mode.
 Theoretical investigation suggests assigning this mode as $B_{1u}$, the Davydov doublet of $A_{1g}$ mode.\cite{Ataca2012} And experimental study confirmed this $B_{1u}$ mode arise from structural disorder of \ce{WS2} layers, and the intensity ratio between $B_{1u}$ and $A_{1g}$ strongly depended on excitation wavelength.\cite{Staiger2012} This study observed $B_{1u}$ mode under 532 nm is much less prominent than that of 632 nm, in consistent with previous reports.\cite{Krause2009,Krause2009a}
@@
 \centering
-\includegraphics[width=0.8\textwidth]{ws2_temram_labeled}
+\includegraphics[width=0.8\textwidth]{cs_temram}
 \caption[TEM-Raman integrated characterization on core-shell NWs]{TEM-Raman integrated characterization on core-shell NWs.
@@
 Rigid analysis of the Raman spectra must be performed to reach solid conclusion.
-Hence, multi-peak Lorentzian fitting was attempted on the spectra in Fig.~\ref{fig:ch5ws2ram}e, and the result for 1 layer \ce{WS2} core-shell NW was displayed in Fig.~\ref{fig:ch5ws2ml}.
+Hence, multi-peak Lorentzian fitting was emplpyed on the spectra in Fig.~\ref{fig:ch5ws2ram}e, and the result for 1 layer \ce{WS2} core-shell NW was displayed in Fig.~\ref{fig:ch5ws2ml}.
 The de-convolution peaks compared favorably with original Raman spectrum, and similar operation were used for other three spectra.
-Fig.~\ref{fig:ch5ws2pr} show the layer number dependence on three group of intensity ratios extracted from apparent value, deconvoluted height and integrated intensity, respectively.
+Fig.~\ref{fig:ch5ws2pr} show the layer number dependence on three group of intensity ratios extracted from apparent value, de-convoluted height and integrated intensity, respectively.
 Similar trend was found among all three set of data, though the integrated intensity appears more sensitive towards layer No variation.
-For a qualitative purpose, the apparent intensity ratio $I_{E/A}$ between in-plane E band ($E_{2g}^1+2LA$) and out-of-plane A band ($A_{1g}+B_{1u}$) was used as a quick gauge to distinguish \ce{WS2} few layer.
+For a qualitative purpose, the apparent intensity ratio $I_{E/A}$ between in-plane E band ($E_{2g}^1+2LA$) and out-of-plane A band ($A_{1g}+B_{1u}$) was used as a quick criterion to distinguish \ce{WS2} few layer.
 % fig Raman TEM
@@
 \end{figure}
+
 $I_{E/A}$ is then extracted to correlate with layer number variation on tens of core-shell NWs.
@@
 The intensity ratio $I_{E/A}$ decreases monotonically with the increase of \ce{WS2} wall number, a similar trend as observed on 2D few layer \ce{WS2},\cite{Berkdemir2013} and the exact value of $I_{E/A}$ shows modest difference with 2D sheet, which could be attributed to the suspended configuration of current core-shell NWs specimen and the presence of \ce{WO3} core.
-Furthermore, our results indicate that $I_{E/A} > 2$ for single-walled \ce{WS2} core-shell NW, and when the \ce{WS2} wall number is about 3, $I_{E/A}=1$.
-These two values act as a quick determination of \ce{WS2} wall number when the NW is suspended.
+Furthermore, these results indicated that $I_{E/A} > 2$ for single-walled \ce{WS2} core-shell NW, and when the \ce{WS2} wall number is about 3, $I_{E/A}=1$.
+These two values served as a quick determination of \ce{WS2} wall number when the NW is suspended.
 
@@
 In summary, synthesis of \ce{WO3} and \ce{MoO3} nanostructures based on CVD method were thoroughly investigated in this study.
-Sodium impurity effect was revealed and \ce{Na5W14O44} nanowire was first reported.
+Sodium impurity effect in tungsten powder source was revealed and the formation of \ce{Na5W14O44} nanowire was first reported.
 Partially enlightened by this discovery, a new VSS growth mechanism of \ce{MoO3} was found and the growth dynamics was systematically probed.
 Comprehensive electron microscopy characterizations were performed on both \ce{WO3} and \ce{MoO3}.
-And the insight of growth kinetics can be used to establish a systematic connection between the interaction of transition metal oxide and alkaline metal ions.
-Besides, seeded growth of \ce{WO3} was demonstrated to be an effective and scalable approach for obtaining single crystalline 1D \ce{WO3} nanostructure.
+And the insight of growth kinetics can be used to establish a systematic connection between the interaction of transition metal oxide and alkali metal ions.
+As an example, preliminary results of \ce{WO3} NWs growth using \ce{NaOH} treated Si substrate and controlled \ce{MoO3} 1D nanostructures growth on glass were presented in Sec.~\ref{sec:nawo} and Sec.~\ref{sec:mogls}, respectively.
+
+Besides, seeded growth of \ce{WO3} was demonstrated to be an effective and scalable approach for obtaining single crystalline 1D \ce{WO3} NWs.
 Based on these \ce{WO3} nanowires, \ce{WO3}-\ce{WS2} heterostructure was synthesized using a simple sulfurization process and single-walled \ce{WS2} tubular core-shell nanowire was observed.
 More important, a TEM-Raman integrated approach was tested aiming at providing a location-resolved map between crystal structure and optical properties.
-As a result, layer number dependence of Raman spectra on \ce{WS2} tubular nanostructure was fingerprinted, and direct bandgap \gls{pl} from \ce{WS2} was observed.
+As a result, layer number dependence of Raman spectra on \ce{WS2} tubular nanostructure was fingerprinted, and direct bandgap \gls{pl} from \ce{WS2} tubular structure was observed.
 This result indicates a broad space for band structure tuning of \ce{WO3}-\ce{WS2}.
-Moreover, the integration of TEM-Raman serves as an excellent tool to correlation the structure-property relationship for nanomaterials.
+Moreover, the integration of TEM-Raman serves as an excellent tool to correlate the structure-property relationship for other 1D nanomaterials.
 
+\section{Preliminary results of NaOH WO$_3$ growth}\label{sec:nawo}
+The growth conditions almost remain the same as that of non-seeded \ce{WO3} growth except that the substrate were located at 7.5 inch (refer to page~\pageref{sec:woxnonseed} for details).
+As shown in Fig.~\ref{fig:naohwsem}, dense NWs were observed on \ce{NaOH} treated substrate as revealed by SEM imaging, where the length ranged from 3 to 10 $\mu$m and diameter from 50 to 200 nm.
+Compared with the \ce{WO3} NWs in seeded growth, the deposition here also exhibited some plausible plate morphology.
+\begin{figure}[htb]
+\centering
+\includegraphics[width=0.7\textwidth]{naohwo3_sem.jpg}
+\caption[SEM characterization of \ce{NaOH} \ce{WO3} growth]{SEM characterization of \ce{NaOH} \ce{WO3} growth.
+(a) Low-magnification SEM graphs showing dense \ce{WO3} NWs.
+(b) A high magnification view showing thin NW growth.}
+\label{fig:naohwsem}
+\end{figure}
+
+\begin{figure}[htb]
+\centering
+\includegraphics[width=0.5\textwidth]{naoh-wo3_edx}
+\caption[Composition analysis on \ce{NaOH} \ce{WO3} growth NWs identifying small fraction Na content]{Composition analysis on \ce{NaOH} \ce{WO3} growth NWs identifying small fraction Na content.}
+\label{fig:naohwedx}
+\end{figure}
+\gls{edx} analysis on the \ce{NaOH} \ce{WO3} sample is shown in Fig.~\ref{fig:naohwedx}.
+Tungsten, oxygen, and sodium elements were detected on the plate growth region, with Na/W atomic ratio of 0.05/1.
+%082713 sample
+\begin{figure}[htb]
+\centering
+\subfloat[]{\label{fig:nawxrd}\includegraphics[width=0.45\textwidth]{naoh-wo3_xrd}}\hspace{0.04\textwidth}
+\subfloat[]{\label{fig:nawram}\includegraphics[width=0.45\textwidth]{naoh-wo3_raman}}
+\caption[Characterization of \ce{NaOH} \ce{WO3} NWs: XRD and Raman]{Characterization of \ce{NaOH} \ce{WO3} NWs: XRD and Raman.
+(a) XRD pattern of the as-prepared sample, and (b) Raman spectrum on NWs region.}
+\label{fig:naohwxrd}
+\end{figure}
+
+Fig.~\ref{fig:nawxrd} displays the XRD pattern on one representative sample.
+The phase identification turned out to be ambiguous.
+One candidate was orthorhombic \ce{WO3} phase (ICDD PDF 00-020-1324, \emph{a}=7.384 \si{\angstrom}, \emph{b}=7.512 \si{\angstrom}, \emph{c}=3.846 \si{\angstrom}); another one was monoclinic \ce{W10O29} phase (ICDD PDF 04-007-0501, \emph{a}=12.1 \si{\angstrom}, \emph{b}=3.78 \si{\angstrom}, \emph{c}=23.4 \si{\angstrom}, $\beta$=90.5$^\circ$).
+Micro-Raman scattering spectroscopy was performed on the as-synthesized sample as well.
+As shown in Fig.~\ref{fig:nawram}, five distinct bands were well resolved, with peaks located at 230, 380, 428, 650 and 816 \si{cm^{-1}}, respectively.
+Another small hump was also observed at 946 \si{cm^{-1}}.
+This Raman spectrum deviated from typical features of \ce{WO3},\cite{Salje1975a,Dixit1986} but matched well with \ce{WO3.H2O} in one previous study.\cite{Daniel1987} However, the XRD pattern did not reveal tungsten oxide hydrates feature.\footnote{(ICDD PDF 04-011-1708, \emph{a}=7.35 \si{\angstrom}, \emph{b}=12.5 \si{\angstrom}, \emph{c}=7.70 \si{\angstrom}} Further analysis is therefore required to confirm the exact phase of \ce{NaOH} \ce{WO3} NWs.\cite{Azimirad2009a}
+
+\begin{figure}[htb]
+\centering
+\includegraphics[width=0.7\textwidth]{naoh_wo3_tem.jpg}
+\caption[Characterization of \ce{NaOH} \ce{WO3}: TEM]{TEM Characterization of \ce{NaOH} \ce{WO3}: (a) TEM image of one nanowire with diameter ca.
+20 nm, and (b) HRTEM images on the tip region showing absence of catalytic particle.}
+\label{fig:naohwtem}
+\end{figure}
+
+TEM specimen was prepared by using carbon grid to slightly scratch the as-grown sample.
+Fig.~\ref{fig:naohwtem} shows the feature of majority NWs.
+The growth direction is difficult to determined due to the presence of streaking in SAED pattern (not shown here), which presumably arises from stacking defaults during the NW growth.
+HRTEM revealed dominant plane spacings of 3.90 and 3.80 \si{\angstrom}, in favorable comparison to the XRD peak at $22.92^\circ$ and $23.66^\circ$.
+It is worth noting that catalyst particles were absent on the tip of NWs during the TEM observation.
+\begin{figure}[htb]
+\centering
+\includegraphics[width=0.5\textwidth]{Na2WO4_phase}
+\caption[Phase diagram of \ce{Na2WO4}-\ce{WO3}]{Phase diagram of \ce{Na2WO4}-\ce{WO3} reproduced from Ref.~\cite{Hoermann1929}}
+\label{fig:nawopd}
+\end{figure}
+Based on the above characterizations, it can be concluded that the majority of NW belonged to tungsten oxide, although Na doping cannot be ruled out completely.
+According to the \ce{Na2WO4}-\ce{WO3} phase diagram in Fig.~\ref{fig:nawopd}, the eutectic temperature is ca.
+720 \si{\degreeCelsius}.\cite{Mann2007} Further investigations are required to better understanding the growth mechanism.
+The author suggested using other alkali metal compound as catalyst to probe the \ce{WO3} growth.
+
+\section{Preliminary results of MoO$_3$ growth on glass}\label{sec:mogls}
+
+The various growth morphologies found using alkali metal based materials as catalysts demonstrate the proposed \gls{vss} mechanism and transverse mode is a general phenomenon, and broad engineering space could be explored to control the dimension of \ce{MoO3}.
+As an example, this study further illustrated the tunable growth of \ce{MoO3} nanoribbons on glass substrate.
+Achieving morphology controlled growth of \ce{MoO3} on transparent substrates, e.g., glass, is an important progress towards process integration and device fabrication in photon-energy related applications.
+
+This thesis studied the effect of temperature, oxygen partial pressure and growth time towards \ce{MoO3} deposition on glass substrates.
+Each factor was divided into two levels, with $T$ at 700 and 800 \si{\degreeCelsius}, \ce{O2} flow at 1 and 10 sccm, and growth time of 15 and 60 min.
+And the morphological variations revealed by SEM imaging were summarized in Table~\ref{tab:mo3glass}.
+% glass growth matrix
+\begin{table}[htb]
+\centering
+\caption{\ce{MoO3} growth on glass}\label{tab:mo3glass}
+\begin{tabular}{lccp{3in}}
+\toprule
+\multicolumn{3}{c}{Growth Conditions} \\
+\cmidrule(l){1-3}
+$T$ (\si{\degreeCelsius}) & \ce{O2} (sccm) & Time (min) & Morphology  \\
+\midrule
+700    &  10   & 15  &   about 50 $\mu$m belts, some towers \\
+700    &  1    & 60  &   irregular shape, not too much growth\\
+700    &  10   & 60  &   particle almost all on tip of belts, many towers \\
+800    &  1    & 15  &   tens $\mu$m belt with sharp edge(100 nm thick, and 1micro wide) dominates\\
+800    &  1    & 60  &   exhibiting ITO features, particles on tips of belt, many tower like structures\\
+800    &  10   & 15  &   rounded edge flakes dominate, modest density tapering belt, and some possible tower\\
+800    &  10   & 60  &   ITO/glass features, aggregated belts, some towers\\
+\bottomrule
+\end{tabular}
+\end{table}
+The 800-1-15 combination produced dense \ce{MoO3} nanoplate with length about 10 $\mu$m, width $300\sim500$ nm and thickness less than 100 nm, as illustrated in Fig.~\ref{fig:ch4glass}.
+These \ce{MoO3} nanoplates are of high crystalline quality, and could potentially show enhanced photoelectrochemical and electrochromic activities.
+%010714r1 sample
+\begin{figure}[htb]
+\centering
+\includegraphics[width=0.7\textwidth]{moo3_glass_lbd}
+\caption[Optimized \ce{MoO3} nanoplates growth on glass]{Optimized \ce{MoO3} nanoplates growth on glass.}
+\label{fig:ch4glass}
+\end{figure}
+%raman data on moo3 glass available
 For future work, the author suggested several following perspectives:
 \begin{enumerate}
-\item further investigation of \ce{WO3} growth using alkaline metal ions as catalysts;
-\item probing the VSS growth method of \ce{MoO3} using HRTEM and analyzing the droplet state; and
+\item further investigation of \ce{WO3} growth using alkali metal ions as catalysts;
+\item probing the VSS growth method of \ce{MoO3} using HRTEM and analyzing the catalyst state; and
 \item applying TEM-Raman integrated study onto other nanostructures.

### 2015-01-24 ch-tms/tmspart.tex
core shell chapter revised

@@
 The apex of triangles could be active site of nucleation, \ce{WS_{2+x}} formation is confirmed by secondary ion mass spectrometry.
-Possible thick \ce{WS_{2+x}} flakes decompose subsequently, leading to ML \ce{WS2}.
+Possible thick \ce{WS_{2+x}} flakes decompose subsequently, leading to \gls{ml} \ce{WS2}.
 The substrates are thoroughly cleaned.
@@
 Seeding promoter probably lowered the surface energy by wetting, thus provided heterogenous nucleation sites.
-Continuous \ce{MoS2} ML is obtained by evaporating \ce{F16CuPc} of 2 \si{\angstrom} on desired receiving substrates.
+Continuous \ce{MoS2} \gls{ml} is obtained by evaporating \ce{F16CuPc} of 2 \si{\angstrom} on desired receiving substrates.
 In each growth, about $10^{-10}$ mol PTAS was applied onto \ce{SiO2}-Si, which was rendered hydrophilic and gentle gas blow to distribute the solution evenly.
@@
 \citeauthor{Sourisseau1991} investigated the resonant Raman profiles in 2H-\ce{WS2} using ten different excitation wavelengths.\cite{Sourisseau1991} Dramatic intensity variation at 352 \si{cm^{-1}} was observed, which is assume to be of two-phonon signal nature, and corresponds to an overtone or combination band of phonons with non-zero momenta contributing to indirect gap absorption edge.
-\citeauthor{Sourisseau1991} assigned this phonon with non-zero momenta as $LA(K_5)$ type.
+\citeauthor{Sourisseau1991} assigned this phonon with non-zero momenta as $LA(K_5)$ type (\gls{la}).
 The enhancement of the total Raman cross section at excitonic resonance in which excitons serve as the intermediate state is stronger compared to that of interband resonance.
-The strong enhancement at excitonic resonance is attributed to the characteristics of excitons in layered materials such as large binding energy, enhanced oscillator strength, and small damping constant.\cite{Zhao2013} \citeauthor{Chung1998} grew \ce{WS2} film using \ce{W(CO)6} and \ce{H2S} precursor.\cite{Chung1998} Raman spectra ($\lambda=632 nm$) on films with non-parallel orientation revealed the presence of shoulder mode under $A_{1g}$, which is assigned to LA and TA phonon coupling.
+The strong enhancement at excitonic resonance is attributed to the characteristics of excitons in layered materials such as large binding energy, enhanced oscillator strength, and small damping constant.\cite{Zhao2013} \citeauthor{Chung1998} grew \ce{WS2} film using \ce{W(CO)6} and \ce{H2S} precursor.\cite{Chung1998} Raman spectra ($\lambda=632 nm$) on films with non-parallel orientation revealed the presence of shoulder mode under $A_{1g}$, which is assigned to \gls{la} and \gls{ta} phonon coupling.
 This coupling process stems from disorder-activated zone boundary phonons.

### 2015-01-28 FrontMatter/FrontMatter.tex
images replaced, fine tune

@@
 \begin{ackn}
-\begin{singlespace}
 Studying in UNC Charlotte has been an unique and rewarding experience for myself, which I shall recall frequently for a long time to come.
@@
 \end{minipage}
-\end{singlespace}
 \end{ackn}

### 2015-01-28 ch-tms/tms.tex
images replaced, fine tune

@@
 It could be further predicted that current Raman spectra on the core-shell NWs can be used to estimate \ce{WS2} nanotube wall numbers.
+
 \begin{figure}[htb]
 \centering
-\includegraphics[width=0.7\textwidth]{ws2_stack}
+\subfloat[]{\label{fig:stk1}\includegraphics[width=0.30\textwidth]{stacking1}}\hspace{0.03\textwidth}
+\subfloat[]{\label{fig:stk2}\includegraphics[width=0.30\textwidth]{stacking2}}\hspace{0.03\textwidth}
+\subfloat[]{\label{fig:stk3}\includegraphics[width=0.30\textwidth]{stacking3}}
 \caption[Optical reflectance simulation on three different \ce{WS2} layer stacking configurations]{Optical reflectance simulation on three different \ce{WS2} layer stacking configurations.}
@@
 Another small hump was also observed at 946 \si{cm^{-1}}.
-This Raman spectrum deviated from typical features of \ce{WO3},\cite{Salje1975a,Dixit1986} but matched well with \ce{WO3.H2O} in one previous study.\cite{Daniel1987} However, the XRD pattern did not reveal tungsten oxide hydrates feature.\footnote{(ICDD PDF 04-011-1708, \emph{a}=7.35 \si{\angstrom}, \emph{b}=12.5 \si{\angstrom}, \emph{c}=7.70 \si{\angstrom}} Further analysis is therefore required to confirm the exact phase of \ce{NaOH} \ce{WO3} NWs.\cite{Azimirad2009a}
+This Raman spectrum deviated from typical features of \ce{WO3},\cite{Salje1975a,Dixit1986} but matched well with \ce{WO3.H2O} in one previous study.\cite{Daniel1987} However, the XRD pattern did not reveal tungsten oxide hydrates feature.\footnote{ICDD PDF 04-011-1708, \emph{a}=7.35 \si{\angstrom}, \emph{b}=12.5 \si{\angstrom}, \emph{c}=7.70 \si{\angstrom}} Further analysis is therefore required to confirm the exact phase of \ce{NaOH} \ce{WO3} NWs.\cite{Azimirad2009a}
 

### 2015-01-28 ch-tms/tmspart.tex
images replaced, fine tune

@@
 
-\subsection{Synthesis Review on WS$_2$}
+\subsection{Review of Synthesis Methods of WS$_2$}
 Shortly after the discovery of \gls{cnt} in 1991,\cite{Iijima1991} its transition metal dichalcogenides (TMDC) counterparts, i.e., \ce{WS2}, was synthesized in 1992.\cite{Tenne1992} In the following decades, other TMDC and several metal oxides nanotubes were demonstrated as well.

### 2015-02-05 ch-intro/ch-intro.tex
main text fine tuned

@@
 \centering
-\includegraphics[width=0.5\textwidth]{blackbody1}
+\includegraphics[width=0.5\textwidth]{blackbody1.pdf}
 \caption[Spectral radiance of blackbody at 0, 50 and 100 \si{\degreeCelsius} predicated by Planck's Law]{Spectral radiance of blackbody at 0, 50 and 100 \si{\degreeCelsius} predicated by Planck's Law.}
@@
 
-Photocatalytic activity occurs when a semiconductor in aqueous solution is illuminated by photons of energy larger than the bandgap, then the carriers (electron and hole) drift and generate free radicals, i.e., \ce{OH.}, which enable further reactions.
-For photochemical water reduction to occur, the flat-band potential of the semiconductor (for highly doped semiconductors, this equals to the bottom of the conductance band) must exceed the proton reduction potential of 0.0 V vs NHE at pH 0.
-Flat-band potentials strongly depend on ion absorption (protonation of surface hydroxyl groups), crystallographic orientation of the exposed surface, surface defects, and surface oxidation processes.\cite{Osterloh2008} For water splitting using solar energy, the bandgap should be within $2.0 \sim 3.0 $ eV, and \gls{cb} edge should be more negative than reduction potential of \ce{H^+/H2}, whereas the \gls{vb} top should be more positive than the oxidation potential of \ce{H2O}/\ce{O2}.\cite{Osterloh2008,Wang2012} The valence band holes (\ce{h^+}) oxidize water to oxygen and conduction band electrons propel hydrogen generation, as depicted in Eq.~\ref{eq:h2o}.
+Photocatalytic activity occurs at the semiconductor-electrolyte interface where charge carriers (electrons or holes) are produced in a semiconductor illuminated by photons of energy exceeding that of the band gap, then drift and generate free radicals, i.e.
+\ce{OH.}, enabling further reactions.
+A much desired goal is water splitting using photocatalytic activity from solar energy.
+Semiconductor is in the center of photoelectrochemical cell design for water splitting, e.g.
+the band gap should be within $2.0 \sim 3.0 $ eV, and \gls{cb} edge should be more negative than reduction potential of \ce{H^+/H2}, whereas the \gls{vb} top should be more positive than the oxidation potential of \ce{H2O}/\ce{O2}.\cite{Osterloh2008,Wang2012} The valence band holes (\ce{h^+}) oxidize water to oxygen and conduction band electrons propel hydrogen generation, as depicted in Eq.~\ref{eq:h2o}.
 \begin{subequations}\label{eq:h2o}
@@
 \end{subequations}
-As shown in Fig.~\ref{fig:woxnhe}, \ce{WO3} has \gls{cb} edge positioned slightly more positive than reduction potential of \ce{H^+/H2} versus \gls{nhe}, and \gls{vb} edge much more positive than the oxidation potential of \ce{H2O}/\ce{O2}.
-So the photo-cleavage of water cannot be accomplished by \ce{WO3} alone.
-Nevertheless, a tandem cell approach by \ce{WO3} film and dye-sensitized \ce{TiO2} has been demonstrated with an efficiency of 4.5\%.\cite{Michael1999} It is worth noting that green plants also have two photosynthetic systems connected in series, one for oxidation of water into oxygen and the other for fixation of carbon dioxide.
+
 % wo3 vs NHE
@@
 \end{figure}
-Moreover, favorable oxygen evolution of \ce{WO3} brings good performance in degradation of organic compounds.\cite{Hepel2001,Luo2001,Watcharenwong2008} The formation of long-lived holes is recognized as a key requirement.\cite{Pesci2011} Besides, \ce{WO3} is remarkably stable in acid, making it a significant candidate for treating water pollutant caused by organic acids.\cite{Monllor-Satoca2006}
+As shown in Fig.~\ref{fig:woxnhe}, \ce{WO3} has \gls{cb} edge positioned slightly more positive than reduction potential of \ce{H^+/H2} versus \gls{nhe}, and \gls{vb} edge much more positive than the oxidation potential of \ce{H2O}/\ce{O2}.
+So the photo-cleavage of water cannot be accomplished by \ce{WO3} alone.
+Nevertheless, a tandem cell approach by \ce{WO3} film and dye-sensitized \ce{TiO2} has been demonstrated with an efficiency of 4.5\%.\cite{Michael1999} It is worth noting that green plants also have two photosynthetic systems connected in series, one for oxidation of water into oxygen and the other for fixation of carbon dioxide.
+Moreover, favorable oxygen evolution of \ce{WO3} brings good performance in degradation of organic compounds.\cite{Hepel2001,Luo2001,Watcharenwong2008} The formation of long-lived holes is recognized as a key requirement.\cite{Pesci2011} Besides, \ce{WO3} is remarkably stable in acid (pH $<5$), making it a significant candidate for treating water pollutant caused by organic acids.\cite{Monllor-Satoca2006}
 

### 2015-02-05 ch-moox/moox.tex
images replaced, fine tune
main text fine tuned

@@
 % xrd raman
+% 081113 sample
 \begin{figure}[htb]
@@
 \end{table}
-It is worth mentioning that the gradient of Gibbs free enthalpy overruled the concentration of a particular species, and higher \ce{OH-} contents tend to reduce Na diffusivity.\cite{Materials2012} The substrates used in this work are glass and ITO/glass; the relevant parameters are as following:
+
+The substrates used in this work are glass and ITO/glass; the relevant parameters are as following:
 \begin{itemize}
@@
 \begin{align}
-J = -D \frac{\Delta C}{\Delta x} = 2.0\times 10^{-8} \si{mol\per cm^2\per\second}.
+J = -D \frac{\Delta C}{\Delta x} = 2.0\times 10^{-8} \si{mol cm^{-2}s^{-1}}.
 \end{align}

### 2015-02-05 ch-tms/tmspart.tex
main text fine tuned

@@
                       & S-1S (\AA)& 3.11  & 3.14   \\
-Between \ce{MS2} layer& S-3S (\AA)&   & 3.53   \\
+Between \ce{MS2} layer& S-3S (\AA)& NA  & 3.53   \\
 \bottomrule
@@
  \addlinespace[0.5em]
-\ce{MoS2} FL \cite{Mann2013,Najmaei2013,Ji2013} Rice & \ce{MoO3} powders or ribbons, Sulfur & Ar flow, 530-850 \si{\degreeCelsius}, total pressure 0.2-2 Torr, 5-30 min, mica or \ce{SiO2}-Si\\
+\ce{MoS2} FL \cite{Mann2013,Najmaei2013,Ji2013} & \ce{MoO3} powders or ribbons, Sulfur & Ar flow, 530-850 \si{\degreeCelsius}, total pressure 0.2-2 Torr, 5-30 min, mica or \ce{SiO2}-Si\\
  \addlinespace[0.5em]
@@
 \includegraphics[width=0.7\textwidth]{ws2_ramsch}
-\caption[\ce{MS2} vibration symmetry]{\ce{MS2} vibration symmetry in bulk and monolayer, adopted from Ref.\cite{Ghorbani-asl}}
+\caption[\ce{MS2} vibration symmetry]{\ce{MS2} vibration symmetry in bulk and monolayer, reproduced from Ref.\cite{Ghorbani-Asl2013}}
 \label{fig:ws2ramsch}

### 2015-02-05 ch-wox/ch-wox.tex
core shell chapter revised
images replaced, fine tune
main text fine tuned

@@
 
-\subsection{Non-seeded growth}
+\subsection{Non-seeded growth}\label{sec:woxnonseed}
 
@@
 
-\section{Results and Discussion on 1D Nanowire Growth}
+\section{Results and Discussion on 1D WO$_3$ Nanowire}
 \subsection{Tungsten Oxides: Impurities and Residual Effects}\label{sec:nawox}
@@
 The \ce{Na5W14O44} phase was further confirmed by a XRD scanning from 4 to 10 degree in $2\theta/\Omega$ configuration.
-As shown in Fig.~\ref{fig:naxrdlow}, two peaks at 4.84$^{\circ}$ and 9.65$^{\circ}$ were well resolved, corresponding a lattice spacing of 18.25 and 9.16 \si{\angstrom}, respectively.
+As shown in Fig.~\ref{fig:naxrdlow}, two peaks at 4.84$^{\circ}$ and 9.65$^{\circ}$ were well resolved, corresponding a lattice spacing of 18.25 \si{\angstrom} and 9.16 \si{\angstrom}, respectively.
 This compares favorably with both HRTEM analysis (Fig.~\ref{fig:nawoxtem}e) and ICDD PDF 04-012-4449 database reference.
@@
 Understanding the oxidation of tungsten powder is the key to obtain high yield in seeded growth.
-Oxidation of tungsten have been investigated under diverse conditions, such as at elevated temperature (\textgreater 1100 \si{\degreeCelsius}) and oxygen pressure on the order of Torr,\cite{Base1965} and at temperatures ranging from 20 to 500 \si{\degreeCelsius} under atmosphere pressure.\cite{Warren1996} \ce{WO_x} NWs were readily found when tungsten (foil, wire, or powder) is oxidized under various conditions.\cite{Zhu1999,Karuppanan2007,Hsieh2010} However the study on tungsten powder oxidation behavior between intermediate temperature range and under low pressure is still rare.
+Oxidation of tungsten have been investigated under diverse conditions, such as at elevated temperature (\textgreater 1100 \si{\degreeCelsius}) and oxygen pressure on the order of Torr,\cite{Gulbransen1960} and at temperatures ranging from 20 to 500 \si{\degreeCelsius} under atmosphere pressure.\cite{Warren1996} \ce{WO_x} NWs were readily found when tungsten (foil, wire, or powder) is oxidized under various conditions.\cite{Zhu1999,Karuppanan2007,Hsieh2010} However the study on tungsten powder oxidation behavior between intermediate temperature range and under low pressure is still rare.
 This thesis studied the oxidation of tungsten powders with diverse size within temperature range from 500 to 1000 \si{\degreeCelsius} and under several mTorr oxygen partial pressure.

### 2015-02-08 misc/SI_thesis.tex
misc paper reading, citation style

@@
 
+\ce{WO3} \cite{Zhang2015}
+VBM at 3V versus NHE, strongly oxidative to drive oxygen evolution.
+
+\ce{WO3} NW on FTO.\cite{Kalanur2013} hole diffusion length of 150 nm, without in-depth discussion.
+improve IPCE (incident photon-to-electron conversion efficiency) by exploiting nanostructured \ce{WO3}, 1D good for the light absorption and charge separation.
+not grow on ITO, Si, and glass, only on FTO.
+ref24
+
+PEC by \ce{WO3} film, 6.7 $\mu$m diffusion length, n-type semi (n-SC), semi-electrolyte interface, photo-excited charge carriers were separated by the electric field in the depletion region of SC.\cite{Wang2000} UV-Vis in ref 13, and photoelectrochemistry in ref 15.
+Look for the excited-state lifetime.
+
+\[
+\cee{4h\nu + n-SC + 2H2O \rightarrow O2 + 2H2 + n-SC}
+\]
+below the onset potential, all photogenerated charge carriers recombine or lost in the interfacial reactions.
+At equilibrium in the dark, the Fermi level of SC is the same as the electrode potential of the solution.
+When overpotential is less than 1500 mV (why 1500, what to do with 700 mV for Si), VB of \ce{WO3} is not reached.
+With band gap illumination, excited electron and hole generated.
+At open circuit condition, Fermi level of SC shift up, or to a more negative potential.
+This potential shift is the driving force of electrons in two-electrode system, such as solar cell, and can be described by
+\[
+\frac{n}{n_0} = \exp(-\frac{E_F - E_{F,0}}{kT})
+\]
+In the three-electrode system, the quasi-Fermi level is controlled by a potentiostat. Current is described by a diffusion-controlled process. penetration depth is wavelength correlated.
+
+band shift 59 mv/pH,
+
+electron transport, \ce{Fe2O3} with suitable band gap of 2.1 eV, but low charge carrier mobility and short diffusion length (20nm), unpaired spin are highly localized due to the radius of 3d orbitals for the first-row transitiona metals.\cite{Yourey2011} Tungsten oxide is diamagnetic, hole mobility of 10 \si{cm^2V^{-1}s^{-1}}, \cite{Butler1977}.
+\ce{WO3} only stable under acidic conditions; at pH $>5$, it dissolves.
+Spectra were recorded in reflectance mode.
+Impedance data show the valance band edge of \ce{CuWO4} is raised by 0.5 V compared to that in \ce{WO3}, and the flat band potential of \ce{CuWO4} matches that of \ce{WO3}, being +0.4 V vs NHE.
+
+\ce{WO3} charge carrier dynamics by transient absorption spectroscopy, 95\% recombination within 10 $\mu$s, the requirement of photoholes with a lifetime on ms to seconds time scale for water oxidation on \ce{WO3}.
+\cite{Pesci2011}
+
+\ce{NaxWO3} electronic structure by UPS. \cite{Hochst1982}
+
+\ce{WO3} ECD and pseudocapacitance due to redox reaction between \ce{W6+} and \ce{W5+}.\cite{Yang2014} galvanostatic,
+
+Schottky barrier mode for \ce{WO3} electrolyte interface.\cite{Butler1977} Field-induced shift of band gap observed, on the order of 300 meV; The CE is made large enough (so no \ce{H2} evolution overpotential exists) not to limit the kinetics of oxygen evolution at WE; It was found that the hole diffusion length is about one tenth of the depletion layer width; and optical absorption depth is comparable to the depletion layer thickness.
+
+The flat band potential is a measure of the potential which must be applied to the SC, relative to some reference electrode, such that the bands remain flat as one approaches to interface.
+$U_{fb}$ is a measure of the electron affinity of the SC, and is related to it by
+\[
+\chi = \text{SCE} + U_{fb}
+\]
+where SCE is the position versus vacuum level (ca. 4.5 eV). It was mentioned that the capacitance measurement from Mott-Schottky plot strongly depends on the sample history and electrolyte.
+
+\ce{WS2} NIR photocatalysis.\cite{Sang2014}
+
+\ce{WS2} hydrogen evolution,\cite{Voiry2013a}
+
+NIR photocatalysis.\cite{Li2014j}
+
+NIR photocatalysis.\cite{Pak2012}
+
+\ce{WS2} for cancer cell thermo-therapy. \cite{Cheng2014}
+
+\ce{Na_{0.33}WO3} by W coating on glass and annealing.\cite{Azimirad2009a} the amount of Na ions matter in regarding to the final composition.\cite{Mann2007}
+
+wo3 thin film optical modeling. \cite{Saygin-Hinczewski2008}
+
 \ce{WS2} 1L doping calculation. \cite{Ma2011}
@@
 
-\ce{Na2W4O_{13}} growth and optical properties. \cite{Oishi2001} \cite{Itoh2001}
+planar defect driven \ce{WOx} growth.\cite{Smith2014} only low supersaturation controlled by temp gradient permits NW growth, with low growth rate.
+leak rate in unit of sccm air; growth rate of 42 $\mu$g per h.
+an accompanying SAED pattern, unequally spaced lattice plane lead to streaking of diffraction spots.
+planar defects along (102), (103) direction, perpendicular to the (010) growth direction.
+defect-mediated morphology control.
+W film as reducing reactant to form sub-stoichiometric WOx species.
+composition and morphology are connected,
+
+\[
+\cee{WO3 + W \rightarrow WOx}
+\]
 
@@
 Tungstates: \ce{(A2O)x.(WO3)n}, full oxidized, no free electron, transparent in visible and NIR. 
+\ce{Na2W4O_{13}} growth and optical properties. \cite{Oishi2001} \cite{Itoh2001}
 
@@
 photocatalytic experimental setup.\cite{Hupka2006}
-\ce{MoO3} pseudocapacitor  \cite{Brezesinski2010}
+\ce{MoO3} pseudo-capacitor  \cite{Brezesinski2010}
 

### 2015-02-08 misc/mwe.tex
supporting info reading
misc works of paper reading, wo3 raman table etc
misc paper reading, citation style

@@
    \input{package.tex} % additonal packages and tweaking
-
-   \newacronym{cvd}{CVD}{chemical vapor deposition}
-   \newacronym{cft}{CFT}{crystal-field theory}
+  \input{acronym.tex}
    \makeglossaries
@@
     \include{./test}
-     %\include{./SI_thesis}
-    % \include{./draft}
+    \include{./SI_thesis}
+    \include{./draft}
     \include{./paper}
@@
 `a ref <https://staff.washington.edu/fox/tex/uwthesis.shtml>`_
+* the toc figure caption and others
+*
+
+\usepackage[style=numeric-comp,
+		    sorting=none,
+		    date=year,
+            hyperref=true,
+            url=false,
+            isbn=true,
+            doi=false,
+            backref=true,
+            maxcitenames=2,
+            maxbibnames=4,
+            block=none,
+            backend=biber,
+            natbib=true]{biblatex}
+% \usepackage[bibencoding=latin1]{biblatex}
+\DeclareSourcemap{
+    \maps[datatype=bibtex]{
+        \map{
+            \step[fieldset=abstract,null]
+        }
+    }
+}
+\AtEveryBibitem{\ifentrytype{article}{\clearfield{issn}}{}}
+\AtEveryBibitem{\clearfield{month}}
+\AtEveryCitekey{\clearfield{month}}
+
+\DefineBibliographyStrings{english}{%
+    backrefpage  = {see p.}, % for single page number
+    backrefpages = {see pp.} % for multiple page numbers
+}
+% suppress 'in:'
+\renewbibmacro{in:}{%
+  \ifentrytype{article}{}{\printtext{\bibstring{in}\intitlepunct}}}
+% document preamble
+% removes period at the very end of bibliographic record
+\renewcommand{\finentrypunct}{}
+% removes pagination (p./pp.) before page numbers
+\DeclareFieldFormat{pages}{#1}

### 2015-02-08 misc/paper.tex
mini working exmp updated
misc paper reading, citation style

@@
 \section{job related paper}
+
+electrowetting (EW), eleectrofluidic (EFD), Laplace pressure, electromechnical pressure, hydrophobic surface, \cite{Yang2010a}
 
@@
 
-ZnTe, p type, band gap 2.25 eV. I_LO intensity ratio: area or height?
+ZnTe, p type, band gap 2.25 eV. $I_LO$ intensity ratio: area or height?
 
@@
 integrated intensities.
+
+\section{electrochemistry}
+
+potentiostat is an electronic instrument controlling the potential difference between WE and RE, and measuring the current between WE and CE.
+working electrode, counter electrode, and reference electrode.
+Two-electrode setups for energy devices, batteries, fuel cells, and super caps; three-electrode setups, the RE is positioned close to WE.
+four-electrode setup, for impedance measurement, solution resistance; another specialized one is zero resistance ammeter, where WE and CE are shorted.
+
+the Fermi level is that same as the electrochemical potential of the solid. potential is measured versus a RE; positive voltage is oxidative, and negative voltage is reductive.
+
+DSSC is photoelectrochemical cell.
+
+The electrochemical bandgap is slightly larger than the corresponding optical bandgap due to the interfacial barrier for charge injection
+
+potential measured between WE and RE, current between WE and CE.\cite{Anon2003}
+
+Cyclic voltammetry, triangle waveform potential applied to WE, and WE current is recorded.
+CE also known as substrate, back contact, auxiliary electrode.
+The total surface area of CE (sink of electrons) must be higher than that of WE, so that it will not become a limiting factor in the kinetics of electrochemical process.
+
+the reaction on an electrode surface, standard reduction reaction all relative to the \ce{H2}/\ce{H+} reaction at 298 K and pH 0.
+
+voltammetric, voltammegram, 2.303 RT/F = 59 mV.
+
+KMT for thin film. \cite{Murphy2007}
+
+flat band potential (FBP) vs open circuit potential (OCP)
+
+FBP defined as difference between Fermi level and redox level, 
+flat-band condition represents the extrapolated voltage at which the space-charge would be infinitely thin (infinite capacitance).
+
+\url{http://ecee.colorado.edu/~bart/book/flatband.htm}
+
+OCP of an electrode is a thermodynamic parameter which tells about the thermodynamic tendency of that electrode to participate in the electrochemical corrosion reactions with the surrounding medium.
+it is the potential of the electrode at which the cathodic and anodic reaction rates are equal under the absence of applied potential.
+in a given corrosive environment, an electrode with nobler OCP is more thermodynamically stable than an electrode with less noble OCP.
+That means an electrode with an OCP of 150 mV is more thermodynamically stable (shows less tendency to participate in the corrosion reactions) than an electrode with 110mV OCP in a given environment.
+
+flat band potential is the characteristic of the space charge region of a semiconducting electrode.
+it is the potential at which the Fermi energy level of the semiconducting electrode (a metal electrode with an overlying semiconducting film) and the fermi energy level (redox potential) of the electrolyte/ aqueous corrosion medium are equal.
+At flat band potential, there is no band bending.
+
+Thus OCP is the characteristic of a metal electrode whereas the flat band potential is the characteristic of a semiconducting electrode.
+
+In SC, the workfunction is not directly accessible; photoelectric method measured the ionization energy, from VBM to vacuum.
+
+surface state on covalently bonded SC; a positive space charge is formed below the surface of an n-type SC, b/c electrons are transferred to the surface states.
+A positive space charge means lower ele density, accordingly the energy distance between Fermi level and the conduction band is increased at the surface, leading to upwards band bending.
+
+the efficiency of a majority (ele in n-SC) carrier transfer.
+
+how to relate the external applied voltage U on a pn junction to the quasi Fermi level difference.
+
+SC-liquid junctions, 
+electrolyte: ions as charge carriers
+\[
+\sigma = F(z_1\mu_+ + z_2\mu_-)c/1000
+\]
+
+Diffusion constant related to the mobility by the Einstein relation $D = \frac{kT}{e} \mu$.
+
+solvation, dissociation energy compensated by the hydration energy.
+
+electrochemical potential vs chemical potential, 
+\[
+\bar{\mu} = \mu + nF\phi
+\]
+and the reference point is those two equal to each other.
+
+electrode potential vs NHE $U_E$.
+
+NHE related to vacuum level by $E_{ref} = -4.5$ eV.
+
+adsorption due to electrostatic attraction or bond formation; \ce{TiO2} form bonds with \ce{H+}, \ce{WS2} tends to be hydrophobic, only at the steps, a free valency of metal may cause bonding to hydroxyl group of water.
+hydroxylated surface; Helmholtz layers forms due to these two kinds of interactions.
+\cite{Memming2000}
+
+For metal electrode, the counter charge just below the surface; for SC, the counter charge distribute a considerable distance; 
+the potential across a single solid-liquid interface cannot be measured. These Helmholtz layers modeled as parallel-plate capacitor.
+
+The equivalent capacity of diffuse layer can be neglected given a high concentration ions ($\leq 10^{-2}$M). In SC, the space charge region, $C_{sc}$ differential capacity, and Mott-Schottky relation
+\[
+\frac{1}{C_{sc}^2} = (\frac{2L}{\epsilon\epsilon_0})^2(\frac{e\delta\phi_{sc}}{kT} - 1)
+\]
+
+SC electrode interface potential
+\[
+U_E = \delta\phi_{sc} + \delta\phi_H + \text{const.}
+\]
+
+Variation of electrode potential occurs across the space layer region, and the potential of the H double layer remains constant.
+This is a very important result, meaning that the external applied voltage only occurs on the space charge layer.
+
+From the capacity potential curve, the minimum value corresponds to a potential, defined as flat band potential $U_{fb} (\delta\phi_{sc} = 0)$, meaning there is no band bending when $U_{fb}$ is applied onto where?
+$U_{fb}$ for many SC electrode depends on pH, indicating SC surface exhibit reaction with \ce{H2O}.
+The TMDC basal plane should much less activity, no pH dependence has been found on \ce{WSe2}.
+It is possible that the \ce{WS2}-\ce{WO3} core shell structure can also benefit from this fact, shielding the \ce{WO3} from external solvent.
+Further study of flat band potential dependence on pH is needed to verify this hypothesis.
+
+Comparison of Mott-Schottky curves and $U_{fb}$ as obtained with n and p type electrodes with the same SC is of interest. 
+\[
+\delta\phi_{n} + \delta\phi_{p} \sim E_g
+\]
+can be anticipated.
+
+Upon illumination, $U_{fb}$ shifts. The origin is manifold, one being surface states, where the accumulation of charger carriers changes the band structures on space layer region.
+
+electron transfer reaction is an activated and not a spontaneous process.
+
+surface radical (dangling bond),
+
+argument in favor of
+
+The impact of SC on electrochemistry.\cite{Gerischer1990} charge be adsorpted, losing part of the solvation shell, interface between metal and electrolyte as a capacitor; depletion layer or accumulation layer in term of electron.
+differential capacitance measurement tells the variation of charge distribution, DOS in unit of \si{cm^{-3}eV^{-1}}; to be cont.
+
+In energy band structure of $E-k$, the zero energy is chosen at the top of VB, so the $E$ here should be chemical potential, \cite{Sze2006} 
+When defining the Fermi level, the follow integral is used
+\[
+n = \int_{E_C}^\infty N(E)f(E)dE
+\]
+So the Fermi level is again compared to the VBM.
+
+The ionization energy of acceptor is measured against valence band edge;
+zero electron or hole current requires $\frac{dE_F}{dx} = 0$.
+
+Deviation of SC-Metal barrier due to 1) interface layer, 2) surface state, and 3) image force.
+
+\url{http://physics.stackexchange.com/questions/70341/fermi-level-alignment-and-electrochemical-potential-between-two-metals?rq=1}
+
+\begin{table}
+  \centering
+  \caption{A table with notes}  \label{tbl:notes}
+  \begin{tabular}{lp{4in}}
+    \toprule
+    Term      & Definition \\
+    \midrule
+    electrochemical potential      & the total free energy of the system per electron \\
+    electric potential             &  \\
+    galvani potential              & the integral of electric (E) field\\
+    electrostatic potential        &  \\
+    (inner) chemical potential     & partial molar free energy, \\
+    redox potential                & for electrolyte $E_{redox}$, a counterpart of Fermi level for solid SC\\
+    band bending                   & \\
+    overpotential                & \\
+    \bottomrule
+  \end{tabular}
+\end{table}
+
+\[
+\bar{\mu} = \mu + zF\phi
+\]
+where $\mu$ is chemical potential, $\phi$ is electrostatic potential;
+
+Flat-band potentials strongly depend on ion absorption (protonation of surface hydroxyl groups), crystallographic orientation of the exposed surface, surface defects, and surface oxidation processes.\cite{Osterloh2008} For photoelectrochemical water reduction to occur, the flat-band potential of the semiconductor (for highly doped semiconductors, this equals to the bottom of the conductance band) must exceed the proton reduction potential of 0.0 V vs \gls{nhe}.
+
+To do Mott-Schottky measurement, SC is subjected to reverse bias--a voltage to increase the potential step across the junction--and the differential capacity is determined as a function of applied potential V.
+The equation
+\[
+1/(C_{sc})^2 = 2(\delta\phi RT/F)/(\epsilon\epsilon_0 N_d)
+\]
+Where $C_{sc}$ is the spece charge capacity in unit of , $\delta\phi = V - U_{fb}$.
+
+The width of band gap is a measure of the chemical bond strength.\cite{Gratzel2001} Nano-engineering SC exhibits following benefits: 
+depletion or accumulation layer cannot formed in nanostructure, then the voltage remain small under reverse bias.
+As a result, there is no local electric field to assis in the separation of photogenerated charge carriers.
+The photoresponse of the nano-SC electrode is then determined by the rate of reactions of these charge carriers with the electrolyte.
+It is confirmed that the same nanocrystalline film could show n-type or p-type behaviors depending on the nature of the hole or electron scavenger present in electrolyte phase.\cite{Hodes1992}
+
+On the concept of chemical potential, a tendency to change of location, of chemical composition or state of aggregation.\cite{Job2006} The perishing of chemicals in sealed bottles.
+in unit of Joule per mole.
+Gravito-chemical potential
+\[
+\bar{\mu} = \mu + M\cdot\psi
+\]
+Similar to the electric potential acts along with chemical potential. 
+The net drive force $\Delta\bar{\mu} = 0$ when electro-chemical equilibrium is reached.
+
+$\mu$ in the grand canonical density operator is the uniquely correct definition of chemical potential (c.p.) valid for all finite systems.\cite{Kaplan2006} $\phi$ is not encouraged.
+
+PV cells depend on creation of ephs and the separation.\cite{Hodes1992} LJ, liquid junction; charge separation did not occur by a space-charge field.
+
+Graphene electrode, BN as barrier, and TMDC as SC.\cite{Withers2015}
+
+The coexistence of discrete and continuum states on NWs is a centural feature of the electronic structure.
+and DOS from pseudopotential calculation found deviation from conventional model (Effective mass approximation).
+Angular momentum states,  \cite{Wang2014n}
+
+Basic operations and several growth recipes using the home-built \gls{cvd} system are included in Appendix.
+
+the TEM specimen was prepared either by directly scratching the as-synthesized sample using TEM grid (Cu, lacy carbon, 300 mesh), or dispersed into aqueous or organic solutions, then drop-cast onto TEM grid.
+
+The enhancement arises from the structure composed of a conductive layer and an insulating layer that are laminated therein.\cite{Shingaya2013}
+
+It is well known that in lamellar flow region, there is a velocity boundary above the side wall.
+
+Raman band assignment for \ce{A2MO4} is well grounded.
+Alkali metal cations with octahedral coordination occur below 230 cm$^{-1}$.
+For \ce{A2M_nO_{3n+1}}, exact assignment is not available yet due to the complicated \ce{MO6} octahedra.
+
+Based on the \gls{vls} process, it is known that a eutectic state is the key to promote preferred growth direction
+The melting of \ce{Na2MoO4} was highly possible when taking into account of its size as well.\cite{Bruggemann1997}
+
+\item When no Mo powder was used while growth was performed in an old tube or oxygen flow is limited to a extreme small value, circular particle-like solid were found and Mo, Na and O were detected, suggesting the existence of VLS mechanism.
+Using Mo coated substrate and subsequent NaOH treatment, similar particles formation was repeated.
+No discernible XRD pattern emerged, illustrating the amorphous nature of liquid catalyst.
+\item 30 min growth: belts growth begin (500 microns long, grow rate is estimated to be 0.5 $\mu$ m/s), tower structures show up as well, but much less than belt.
+Two kinds of belts found, tapering and non-tapering.
+The former one seems to have particles mostly associated with sidewalls of the top part.
+\item In reduced time or less oxygen supply growth, Na-containing site was found located onto the sidewall of belts instead of the usual expected tip.
+XRD pattern indicated the existence of \ce{Na_xMoO3} phase.
+And \ce{MoO3} XRD pattern is dominated by (0k0) peaks, indicating a 2D layer-by-layer growth with lateral rate exceeding that of axial direction.
+\item 2 h growth: there are crossed tapering belts at downstream boundary, with more than one particle located along the interface of two perpendicular belts, EDX confirmed high Na content.
+
+people used chamber pot when there was no running water system. 
+This difference presumably vanished when nanotube diameter exceeded 100 nm.
+considering the integration into current microelectronic process, which was found higher for film prepared without an intermediate Ni coating
+
+This thesis then conjectured that the substrate cleaning in Ref.\cite{Peimyoo2013} should be similar to that in Ref.\cite{VanderZande2013}, yet the source-to-substrate layout and growth pressure were still needed to be optimized with respect to the home-built CVD apparatus.
+No 1L vs nL statistic is available.
+
+15 optical modes e allowed assuming 6 atoms in primitive cell.

### 2015-02-08 FrontMatter/Abstract.tex
grammar overhaul, tense, clause, ISBN

--- 2014-09-27 FrontMatter/Abstract.tex
@@
 \begin{abstract}
+Transition metal oxides (TMOs) exhibit rich structures and useful properties and could be used in applications of solar energy harvesting (\emph{e.g.}, photoelectrochemistry, photocatalysis, and photovoltaics) and energy saving (\emph{e.g.}, electrochromism and photochromism).
+Nano-engineering of these TMOs could produce a variety of nanostructures, modify the electronic and optical properties, and potentially enhance the performances and extend their applications into new regimes.
+To fully harvest the advantages of these materials, a scalable growth method and a comprehensive understanding towards the growth-structure-property relation must be established.
+This doctoral study focused on one-dimensional (1D) nanostructures of tungsten trioxide (\ce{WO3}) and molybdenum trioxide (\ce{MoO3}).
+This dissertation synthesized 1D \ce{WO3} and \ce{MoO3} nanostructures using the chemical vapor deposition (CVD) approach, characterized the morphologies and structures, and measured the optical properties of the as-prepared nanostructures.
 
-Transition metal oxides (TMOs) exhibit rich structures and useful properties, and could been used in solar energy harvesting (\emph{e.g.}, photoelectrochemistry, photocatalysis, and photovoltaics) and energy saving (\emph{e.g.}, electrochromism and photochromism) applications.
-Nano-engineering of these TMOs could produce a variety of nanostructures, modify the electronic and optical properties, potentially enhance the performances and extend their applications into new regimes.
-To fully harvest the advantages of these materials, a scalable growth method and a comprehensive understanding towards the growth-structure-property relation must be established.
-This Ph.D.
-study focused on one-dimensional (1D) tungsten trioxide (\ce{WO3}) and molybdenum trioxide (\ce{MoO3}) nanostructures.
-This dissertation synthesized 1D \ce{WO3} and \ce{MoO3} nanostructures using chemical vapor deposition (CVD) approach, characterized the morphologies and structures, and measured the optical properties of the as-prepared nanostructures.
-This study aims at accomplishing controlled and scalable growth of \ce{WO3} and \ce{MoO3} using CVD method, establishing the structure-property relations to rationalize nanostructure synthesis for energy applications, and presenting preliminary results on the devices assembled using the \ce{WO3} and \ce{MoO3} nanostructures.
+This dissertation consists of three main parts, each centering on \ce{WO3}, \ce{MoO3}, and \ce{WS2}-\ce{WO3}, respectively.
+Systematical investigation of the \ce{WO3} nanostructure prepared by the CVD method with tungsten powders as precursor led to the following accomplishments:
+\begin{enumerate*}[label=\itshape\alph*\upshape)]
+\item the discovery of \ce{Na5W14O44} nanowires;
+\item a knowledge of the delicate role of sodium in tungsten source powders; and
+\item a seeded growth method to produce high quality \ce{WO3} nanowires.
+\end{enumerate*} Enlightened by the intricate interactions between sodium content and tungsten oxide, this dissertation extended the vapor-liquid-solid strategy into \ce{MoO3} 1D nanostructure growth and discovered two morphologies of \ce{MoO3}: ultra-longbelts and microtowers.
+Careful observation in extensive experiments identified the catalytic role of sodium hydroxide during the growth of \ce{MoO3} and readily proved that the catalytic behavior also exists with other alkali-based metal contents.
+The third part of this work moved the investigation center from growth to property characterization.
+A novel TEM-Raman integrated study was performed on \ce{WS2}-\ce{WO3} core-shell NWs, allowing for the observation of high resolution TEM imaging, Raman spectroscopy, and photoluminescence spectroscopy on individual nanowires.
+The single-walled \ce{WS2} tubular nanostructure was first identified.
+The combined results further illustrated the existence of \ce{WS2} wall number dependent Raman fingerprints on resonant Raman spectra.
 
+In summary, this study explored methods for controlled and scalable growth of 1D \ce{WO3} and \ce{MoO3} nanostructures based on both vapor-solid and vapor-solid-solid approaches, characterized the structure-property relations to rationalize nanostructure synthesis for energy applications, and presented preliminary results for the device fabrications using the \ce{WO3} and \ce{MoO3} nanostructures.
 \end{abstract}

### 2015-02-08 ch-intro/ch-instr.tex
main text fine tuned
grammar overhaul, tense, clause, ISBN

@@
 
-In this study, the nanostructures were grown in a home-built chemical vapor deposition system and characterized using both electron microscopy and optical spectroscopy methods, including \gls{sem}, \gls{xrd}, \gls{edx}, \gls{tem}, Raman and UV-Vis.
+In this study, the nanostructures were grown in a home-built \gls{cvd} system and characterized using both electron microscopy and optical spectroscopy methods, including \gls{sem}, \gls{xrd}, \gls{edx}, \gls{tem}, Raman and UV-Vis spectroscopy.
+A detailed description is given to the \gls{cvd} system.
 Other sample and substrate preparation methods are also briefly introduced.
-A detailed introduction will be given to the \gls{cvd} system.
-For other mature techniques, the contents will be limited to the extent where experienced material researchers could repeat the experiments performed here.
-Particular attentions will also be mentioned for properly characterizing the nanostrucutres synthesized in this work.
-This chapter is concluded with data processing discussion.
+For mature processes and techniques, the contents are limited to the extent where experienced material researchers could repeat the experiments performed here.
+Some details are mentioned in particular to perform the nanostrucutres characterization in a proper way.
 
@@
 The syntheses were accomplished in a home-made hot-wall \gls{cvd} system.
-The reaction chamber part and a schematic drawing of whole system can be visualized in Fig.~\ref{fig:ch2cvd}.
+The reaction chamber and a schematic drawing of whole system can be visualized in Fig.~\ref{fig:ch2cvd}.
 The reaction chamber consists of fused silica tube and a thermal furnace.
 The furnace is made by two semi-cylindrical ceramic fiber heaters (WATLOW, Inc.) with power density from 0.8 to 4.6 \si{W cm^{-2}}.
-Quartz tube (Quartz Sci, Inc.) of 1 in diameter was inserted into the furnace serving as reaction chamber.
-A mechanical pump was connected to maintain the low pressure environment inside the chamber.
-The length of uniform heating zone is 6 in, with cooling zone extending outward.
-Carriers gas argon (Ar) and reactant gas oxygen (\ce{O2}) was regulated by mass flow controllers.
+Quartz tube (Quartz Sci, Inc.) of 1 inch diameter is inserted into the furnace serving as the reaction chamber.
+A mechanical pump is connected to maintain the low pressure environment inside the chamber.
+The length of heating zone is 6 inch, with 1 inch cooling zone extending outward on each side.
+Carriers gas argon (Ar) and reactant gas oxygen (\ce{O2}) are regulated by mass flow controllers.
 
@@
 
-The controllable parameters of this \gls{cvd} system include central heating temperature, absolute gas flow and relative ratio of (Ar/\ce{O2}), amount of source material and location of the substrates.
+The controllable parameters of this \gls{cvd} system include the central heating temperature, the absolute gas flow, amount of source materials, and the location of substrates.
 The operation capability is summarized in Table~\ref{tab:cvd}.
-
 \begin{table}[htb]
@@
     \midrule
-    Range      & RT-1100    & 10 mTorr-1 atm & 0 - 100 & 0-30  \\
+    Range      & RT - 1100    & 10 mTorr -1 atm & 0 - 100 & 0 - 30  \\
     Resolution & $\pm1$  & correlated to flow & 1   & 0.1  \\
@@
 \end{table}
-
-The heating temperature $T$ profile measured at different settings in ambient environment was shown in Fig.~\ref{fig:ch2temp}.
-There exists a uniform heating zone in the center area, spanning over about 2 in; then $T$ descends gradually within the 6 in heating zone, and decrease rapidly at the rest part.
+The heating temperature $T$ profile measured at different settings in ambient environment is shown in Fig.~\ref{fig:ch2temp}.
+There exists a uniform heating zone in the center area, spanning over about 2 inch; then $T$ descends gradually within the 6 inch heating zone and decreases rapidly at the rest part.
 In this study, a zero position referred as 0 inch is defined at the upstream edge of reaction chamber covered by the furnace.
-
 \begin{figure}[htb]
@@
 \end{figure}
-
-The substrates were mostly positioned just outside the downstream heating zone since within this region, the vapor undergoes a rapid temperature gradient and precipitation occurs.
-The source material placed in the furnace center is oxidized and evaporated.
+In typical growth, the substrates are positioned just outside the downstream heating zone, since within this region the vapor of growth species undergoes a rapid temperature gradient, and precipitation occurs.
+After the chamber is heated to target temperatures, the source material (tungsten and molybdenum powders) placed in the furnace center is oxidized and evaporated.
 The growth species, transported by carrier gas, bombard both substrate and chamber wall.
-Some will be adsorbed by the substrate and become adatoms while some may remain as gas molecules, waiting for another event.
+Some will be adsorbed by the substrate and become adatoms, while some may remain as gas molecules, waiting for another event.
 On the hot substrate, adatoms diffuse and do not settle down until finding an appropriate location where equilibrium is favored.
 Detailed growth conditions will be introduced in the corresponding chapters.
-Basic operations and several growth recipes using the home-built \gls{cvd} system are included in Appendix.
-
 \subsection{Substrates Treatments}\label{ch2sub}
 
-Silicon (Si) and 1 $\mu$m silicon dioxides on Si wafer (\ce{SiO2}-Si) (University Wafer Inc.) were primarily used, and other substrates, i.e., Mica\footnote{\ce{K(Al2)(Si3Al)O10(OH)2}}, glass (Fisher Scientific, microscope slide, 12-549),\footnote{Typical composition is 72.6\% \ce{SiO2}, 0.8\% \ce{B2O3}, 1.7\% \ce{Al2O3}, 4.6\% \ce{CaO}, 3.6\% \ce{MgO} and 15.2\% \ce{Na2O}} stainless steel, were also employed.
+Silicon (Si) and 1 $\mu$m silicon dioxides on Si wafer (\ce{SiO2}-Si) (University Wafer Inc.) were primarily used, and other substrates were also employed, i.e.
+Mica\footnote{\ce{K(Al2)(Si3Al)O10(OH)2}}, glass (Fisher Scientific, microscope slide, 12-549),\footnote{Typical composition is 72.6\% \ce{SiO2}, 0.8\% \ce{B2O3}, 1.7\% \ce{Al2O3}, 4.6\% \ce{CaO}, 3.6\% \ce{MgO} and 15.2\% \ce{Na2O}} and stainless steel.
 Si and \ce{SiO2}-Si substrates were first cut into rectangular pieces of certain size and then ultrasonically cleaned (Branson 1510R-MTH) with acetone and alcohol for about 15 min, each followed by blow-drying with nitrogen gas.
@@
 A plasma cleaner (Kurt J Lesker, Plasma-Preen 862) was used to render a hydrophilic Si surface, where reaction among $e$, \ce{O+}, \ce{O2+}, \ce{O^-},\ce{O2} occurs, and \ce{OH}-terminated surface followed.\cite{Habib2010} The treatment proceeds at 2 Torr \ce{O2} for 3 min.
-Glass substrate cleaning procedure is the same as that of Si.
-Mica substrates are cleaved right before the growth without extra cleaning steps.
+Glass substrate cleaning procedure was the same as that of Si.
+Mica substrates were cleaved right before the growth without extra cleaning steps.
 In addition, substrates can be coated with a thin layer of metal before growth.
@@
 
-In this work, magnetron sputtering (Denton Vacuum Desk IV) was used to coat thin layers of metals onto cleaned substrates.
-As shown in Fig.~\ref{fig:ch2magsp}, the metal target is the cathode and the specimen is anode.
+In this work, magnetron sputtering (Denton Vacuum Desk IV) was used to coat thin layer of metals onto cleaned substrates.
+As shown in Fig.~\ref{fig:ch2magsp}, the metal target is the cathode, and the specimen is anode.
 A dc voltage is applied to ionizes the argon gas, and a permanent magnet behind the target focuses the gas plasma onto the target and also deflect electrons from the sample.
@@
 \centering
-\includegraphics[width=0.7\textwidth]{sputter.jpg}
+\includegraphics[width=0.6\textwidth]{sputter.jpg}
 \caption[Schematic drawing of magnetron sputtering system]{Schematic drawing of magnetron sputtering system. Reproduced from Ref.\cite{Goldstein2007}}
@@
 \ce{Ar+} ions are accelerated to target foils.
-The pressure of \ce{Ar+} has two functions: to sputter off the target ions, and to influence the \gls{mfp}.
+The pressure of \ce{Ar+} has two functions: to sputter off the target ions and to influence the \gls{mfp}.
 These collisions between target ions and \ce{Ar+} lead to almost all arrival angles, thus uniform coverage.
 The sputtering yield is number of target ions released per ions hitting on target.
-If \ce{Ar+} ion energy is less than 100 eV, the yield is zero; If larger than 10 keV, implantation of \ce{Ar+} into target foils occurs.
-Usually yield between 1 and 2 is desired.
-The \gls{mfp} in sputtering is on order of 3 cm (assuming pressure of 30 mTorr), with source-to-substrate distance as 5 cm, average number of collisions is about 5/3$\sim$2.
+If \ce{Ar+} ion energy is less than 100 eV, the yield is zero; if larger than 10 keV, implantation of \ce{Ar+} into target foils occurs.
+Usually, yield between 1 and 2 is desired.
+The \gls{mfp} in sputtering is on order of 3 cm (assuming pressure of 30 mTorr).
+With source-to-substrate distance as 5 cm, average number of collisions is about 5/3$\sim$2.
 
@@
 The \gls{ebeam} source is a tungsten filament heated at about 2800 K.\cite{jeolsem} The acceleration voltage can be up to 30 kV.
-After acceleration, electron beam strikes the sample mounted on specimen stage, producing rich signals as illustrated in Fig.~\ref{fig:ch2sem}.
-Depending on the energy and scattering angle, the out-coming electrons from specimen can be grouped into \gls{bse} and \gls{se}, respectively.
-\gls{se} is generated from the emission of valence band electrons.
-And due to the limited energy ($<50$ eV), the emission from deep region is mostly absorbed again; only those electrons that are at the vicinity of specimen surface can escape.
-Hence the \gls{se} image is topographical sensitive.
-The emission efficiency is strongly affected by the geometry (tilting angle of specimen surface) and voltage potential (charging effect), so does the contrast in \gls{se} image.
-On the other hand, backscattered electron could have large energy close to that of incident \gls{ebeam}.
-The scattering cross section strongly depends on atomic number Z, thus allowing for the compositional analysis.
-The X-ray emission stems from inner shell transition of the constitutive atoms, and cathodoluminescence from bandgap transition.
-
+After acceleration, electron beam strikes the sample mounted on specimen stage producing rich signals, as illustrated in Fig.~\ref{fig:ch2sem}.
 \begin{figure}[htb]
@@
 \end{figure}
+Depending on the energy and scattering angle, the out-coming electrons from specimen can be grouped into \gls{bse} and \gls{se}, respectively.
+\gls{se} is generated from the emission of valence band electrons.
+And due to the limited energy ($<50$ eV), the emission from deep region is mostly absorbed again; only those electrons that are at the vicinity of specimen surface can escape.
+Hence, the \gls{se} image is topographical sensitive.
+The emission efficiency is strongly affected by the geometry (tilting angle of specimen surface) and voltage potential (charging effect), so does the contrast in \gls{se} image.
+On the other hand, backscattered electron could have large energy close to that of incident \gls{ebeam}.
+The scattering cross section strongly depends on atomic number Z, thus allowing for the compositional analysis.
+The X-ray emission stems from inner shell transition of the constitutive atoms, and cathodoluminescence arises from band gap transition.
 
 In this study, secondary electron images were mainly used to reveal the morphology of the samples.
-Unless otherwise noticed, the SEM images in this work were acquired using 10 kV acceleration voltage, 10 mm working distance and 30 spot size.
+Unless otherwise noticed, the SEM images were acquired using 10 kV acceleration voltage, 10 mm working distance, and 30 spot size.
 
@@
 In this study, the SEM-attached EDX was primarily used.
-The X-ray detector (INCA 7573-M, 10 \si{mm^2} Si cooled by liquid nitrogen) is equipped with a super thin window enabling light element detection such as boron.
-Typical working parameters of EDX detection in this study include 20 kV acceleration voltage, 10 mm working distance and 60 s analysis time.
+The X-ray detector (INCA 7573-M, 10 \si{mm^2} Si cooled by liquid nitrogen) is equipped with a super thin window enabling light element detection, such as boron.
+Typical working parameters of EDX detection in this study include 20 kV acceleration voltage, 10 mm working distance, and 60 s analysis time.
 
 To obtain quantitative results on EDX spectra, special attentions should be paid to the following aspects:
-\begin{itemize}
-\item elemental distribution in an X-ray generation area is uniform,
-\item the specimen surface is flat,
-\item the electron beam enters perpendicular to the specimen. 
+\begin{enumerate*}[label=\itshape\alph*\upshape)]
+\item elemental distribution in an X-ray generation area is uniform;
+\item the specimen surface is flat;
+\item the electron beam enters perpendicular to the specimen; and
 \item a reference sample consisting of identical elements and known ratio is used. 
-\end{itemize}
-Even for qualitative analysis, ambiguity exists when the $K$ lines of lighter elements overlap with $L$ lines of heavier elements.
-For instance, Na-$K_\alpha$ (1.041 keV) interferes with $L_\alpha$ lines of Zn (1.009 keV) and Cu (0.928 keV).
+\end{enumerate*} Even for qualitative analysis, ambiguity exists when the $K$ lines of lighter elements overlap with $L$ lines of heavier elements; for instance, Na-$K_\alpha$ (1.041 keV) interferes with $L_\alpha$ lines of Zn (1.009 keV) and Cu (0.928 keV).
 Overall spectra and growth conditions should be weighted against possible wrong assignment.
@@
 \subsection{X-ray Diffraction (XRD)}
-Crystal structures of the as-synthesized specimens in this study were characterized using PANXpert Pro MRD with Cu $K\alpha_{avg}$ radiation at $\lambda$=1.5418 \si{\angstrom}.
-The high energy photon ($E = 1239.8/0.15148= 8184.5$ eV) was generated using accelerated electron beam from tungsten filament to bombard Cu target.
+Crystal structures of the as-synthesized specimens in this study were characterized using PANXpert Pro MRD with Cu K$\alpha_{avg}$ radiation at $\lambda$=1.5418 \si{\angstrom}.
+The high energy photon flux ($E = 1239.8/0.15148= 8184.5$ eV) was generated by using accelerated electron beam from tungsten filament to bombard Cu target.
 The $\theta-2\theta$ configuration was primarily used, as shown in Fig.~\ref{fig:ch2theta}.
@@
 Only at specific angles constructive interference occurs, and a diffraction peak registers when the detector is scanned across that angle.
-
 The as-synthesized specimens were mounted onto diffractometer in a way that the X-ray will illuminate interested region during the whole scanning.
-Typical settings used was summarized in Table.~\ref{tab:ch2xrd}.
-
+Typical settings used were summarized in Table~\ref{tab:ch2xrd}.
 \begin{table}[htb]
@@
 \end{table}
-
 The 1D nanostructures in this study usually grew with preferred orientation; therefore, they cannot be treated as powders.
 The interpretation of XRD patterns could become difficult somehow.
-Two possible approaches could be followed to bypass this difficulty: one is using grazing angle XRD which could reveal in-plane domain size and orientation;\cite{Tersigni2011,Goorsky2002} the other is combining XRD with alternative techniques, such as Raman, TEM.
+Two possible approaches were suggested to bypass this difficulty: one is using grazing angle XRD which could reveal in-plane domain sizes and orientations;\cite{Tersigni2011,Goorsky2002} the other is combining XRD with alternative techniques, such as Raman and TEM.
 The latter approach was pursued in this work.
@@
 TEM qualifies as a powerful and versatile tool for material characterization.
-Akin to the electron-materials interaction introduced in Sec.~\ref{sec:sem}, various signals are generated when the thin specimen was radiated by electron beam.
-Besides the \gls{saed} pattern and \gls{hrtem} imaging, other TEM based techniques include \gls{cbed}, EDX, \gls{eels} and \gls{cl}, etc.
-Therefore, TEM is essentially a signal-generating and detecting tool.\cite{Williams2009} Fundamental physics of electron is needed to obtain a comprehensive understanding of these TEM related techniques.
-Only a brief summary is given here.
+Akin to the electron-materials interaction introduced in Sec.~\ref{sec:sem}, various signals are generated when the thin specimen is radiated by electron beam.
+Besides the \gls{saed} pattern and \gls{hrtem} imaging, other TEM based techniques include \gls{cbed}, EDX, \gls{eels} and \gls{cl}, etc; therefore, TEM is essentially a signal-generating and detecting tool.\cite{Williams2009} Fundamental physics of electron is needed to obtain a comprehensive understanding of these TEM related techniques, and only a brief summary is given here.
 
-Electron scattering was dictated by Coulomb interaction, and can be characterized by the following four aspects: the cross section (scattering probability), differential cross section (scattering angle), mean free path, and inelastic or elastic scattering.
+Electron scattering is dictated by Coulomb interaction, and can be characterized by the following four aspects: the cross section (scattering probability), differential cross section (scattering angle), mean free path, and inelastic or elastic scattering.
 The cross section $\sigma$ in \si{m^2}, which when divided by area of targeting atom, represents a probability that scattering event will occur.
@@
 \[
-\frac{d\sigma}{d\Omega} = \frac{1}{2\pi \sin\theta} \frac{d\sigma}{d\theta},
+\frac{d\sigma}{d\Omega} = \frac{1}{2\pi \sin\theta} \frac{d\sigma}{d\theta}
 \] 
@@
 The spatial distribution of scattering is observed as contrast in images, and angular distribution is viewed in form of diffraction patterns.
-The positions of diffracted E-beams are determined by size and shape of unit cell, and intensities governed by distribution, number, and types of atoms in the specimen.
+The positions of diffracted E-beams are determined by size and shape of unit cell, and intensities are governed by distribution, number, and types of atoms in the specimen.
 
 JEOL JEM-2100 TEM with a \ce{LaB6} filament operated at 200 kV was used in this work.
-A numerical comparison between the scattering events in XRD and TEM is provided to visualize the difference.
+A numerical comparison between the scattering events in XRD and TEM is provided to visualize the difference in these two techniques.
 In both processes, the constructive interference is described by $2d\sin\theta = \lambda$, where $d$ is crystal plane distance, $\lambda$ is incident wavelength (photon or electron), and $\theta$, again, is half of the scattering angle.
@@
 \midrule
-3.135 \AA & Cu $K\alpha$ & 1.541 \AA & 28.45$^\circ$  \\
+3.135 \AA & Cu K$\alpha$ & 1.541 \AA & 28.45$^\circ$  \\
 3.135 \AA & 200 kV & 0.0251 \si{\angstrom} & 0.45$^\circ$  \\
@@
 However, it is generally more difficult to manipulate electron with magnetic field than do photon with dielectric lens.
-The current resolving power in TEM is on the order of 1.0 \si{\angstrom} without correction of spherical aberration.
+The current resolving power in TEM is on the order of 1.0 \si{\angstrom} without correction of the spherical aberration.
 The nominal resolution of JEM-2100 is 2.3 \si{\angstrom}.
 On the other hand, it is much easier to fine tune the power (focal length) of lens in TEM than in conventional optics.
-This capacity enables other observation approaches that would be rather difficult, if not impossible, to be realized in lens optics, such as \gls{saed}.
+This capacity enables other observation approaches that would be rather difficult, if not impossible, to be realized in lens optics, such as \gls{saed} pattern.
 
-In this study, the TEM specimen was prepared either by directly scratching the as-synthesized sample using TEM grid (Cu, lacy carbon, 300 mesh), or dispersed into aqueous or organic solutions, then drop-cast onto TEM grid.
-A JEOL double tilt holder was used to rotate the crystal orientation.
-TEM images and SEADs were acquired using a \gls{ccd} from Gatan, Inc.
+In this study, a JEOL double tilt holder was used to rotate the crystal orientation.
+TEM images and \gls{saed} patterns were acquired using a \gls{ccd} (Gatan, Inc.).
 EDX spectroscopy was captured by similar Oxford Instrument INCA attachment introduced in Sec.~\ref{sec:edx}.
 To make the best out of TEM analysis, one also needs to be aware of the limitations of TEM.
-Two aspects were pointed out here, including small sampling and interpreting of the image.
+Two aspects were pointed out here, namely the small sampling volume and the image interpreting.
 The former one is inherent and can only be partially overcome by combining TEM with other ensemble characterization tools.
@@
 Raman spectroscopy, a common vibrational spectroscopy, is based on the inelastic scattering of a monochromatic excitation source with photon energy variation range of 100 to 4000 \si{cm^{-1}}.
-This energy difference between incident photon and inelastically scattered photon is closely related to a series of vibrational modes.
-Being nondestructive and requiring minimal preparation, it is an excellent tools to assess lattice dynamics and fingerprint species.\cite{McCreery2000} For instances, characteristic Raman shift can be used to determine material compositions; changes in Raman peak (\gls{fwhm}, frequency shift) are often related to strain; polarization Raman spectra can be used to derive crystal orientation and symmetry.
+This energy difference between incident photon and inelastically scattered photon is closely related to a series of vibrational modes of the sample under observation.
+Being nondestructive and requiring minimal preparation, Raman spectroscopy is an excellent tools to assess lattice dynamics and to fingerprint species.\cite{McCreery2000} For instances, characteristic Raman shift can be used to determine material compositions; changes in Raman peak (\gls{fwhm}, frequency shift) are often related to strain; polarization Raman spectra can be used to derive crystal orientation and symmetry.
 
@@
 
-In this study, Raman measurement was performed using a confocal micro-Raman system (Horiba Scentific, Labram HR800) with excitation wavelengths at 441, 532 and 632 nm, where the corresponding photon energy is 2.81 eV, 2.33 eV and 1.96 eV, respectively.
+In this study, Raman measurement was performed using a confocal micro-Raman system (Horiba Scentific, Labram HR800) with excitation wavelengths at 441, 532, and 632 nm, where the corresponding photon energy is 2.81 eV, 2.33 eV, and 1.96 eV, respectively.
 For nanowire samples, the laser powers were kept between 0.2 and 0.3 mW, and typical acquisition time was 100 s to avoid possible thermal damage.
-The spectral resolution is about 1 \si{cm^{-1}} and the depth resolution about 2 $\mu$m.
+The spectral resolution is about 1 \si{cm^{-1}}, and the depth resolution about 2 $\mu$m.
 
@@
 UV-Vis-NIR spectrophotometer is a useful tool to obtain optical properties from various samples.
-Generally speaking, the UV spectrum ranges from 100 nm to 400 nm, and visible spectrum spans from 400 nm to 750 nm.
-Absorption from atmospheric \ce{CO2} becomes significant below 200 nm; therefore 100 to 200 nm region is usually not measured unless some vacuum technique is applied.
-Near-IR ranges from 0.75 to 3 $\mu$m.
-The cost of fabricating a spectrometer covering the whole NIR region can be quite high.
+Generally speaking, the UV spectrum ranges from 100 nm to 400 nm; visible spectrum spans from 400 nm to 750 nm; and near-IR ranges from 0.75 to 3 $\mu$m.
+Absorption from atmospheric \ce{CO2} becomes significant below 200 nm; therefore 100 to 200 nm region is usually not measured unless some vacuum technique is applied.The cost of fabricating a spectrometer covering the whole NIR region can be quite high.
 The instrument used in this dissertation (Schimadzu, UV2600Plus) can measure from 220 nm to 1350 nm (5.6 eV to 0.92 eV) with an integrating sphere.
@@
 By auto-correlation analysis, the decay rate of scattering intensity correlation can be related to the diffusion coefficient of small particles in the solvent.\cite{Maret1987} This approach, however, will not be pursued in this work.
-Instead, the scattering effect is partially circumvented by using diffuse reflection technique.
+Instead, the scattering effect of the nanostructured samples is partially circumvented by using diffuse reflection technique.
 
-Diffuse reflectance spectroscopy (DRS) serves as another tool to estimate the sample band gap using \gls{kmt}.\cite{Tandon1970} The original KM theory was proposed in 1931,\cite{Kubelka1931} and has been popular in the color-related industry, such as painting, pigments, and paper.
+Diffuse reflectance spectroscopy (DRS) serves as another tool to estimate the sample band gap using \gls{kmt}.\cite{Tandon1970} The original KM theory was proposed in 1931\cite{Kubelka1931} and has been popular in the color-related industry, such as painting, pigments, and paper.
 This method is useful for the analysis of samples of difficultly soluble substances and for samples that will react with the solvents upon being dissolved.
 It is also particularly applicable when single crystals of the material could not be obtained.
-Some key points were recapitulated in this thesis.
+Some key points of \gls{drs} were recapitulated in this thesis.
 
@@
 In this thesis, UV-Vis and \gls{drs} were recorded using Schimadzu, UV2600Plus, with schematic measurement setup shown in Fig.~\ref{fig:ch2uvvis}.
-For UV-Vis measurement in transmission mode, the as-synthesized sample was removed from substrates by light sonication (Branson 1510R-MTH, 70W) in ethanol or DI water for 15 seconds.
+For UV-Vis measurement in transmission mode, the as-synthesized sample was removed from substrates by light sonication (Branson 1510R-MTH, 70W) in ethanol or DI water for 15 second.
 The dispersion was left for 12 h to enable the possible sedimentation.
-Then the dispersion was transferred into one 10 mm quartz cuvette (Thorlabs, W005654) for absorption measurement with another paired cuvette containing pairing liquid only.
+Then, the dispersion was transferred into one 10 mm quartz cuvette (Thorlabs, W005654) for absorption measurement with another paired cuvette containing pairing liquid only.
 To carry out diffuse reflectance measurement, an integrating sphere (ISR2600Plus) was used with an incident angle of 0 degree.
@@
 Chemical wrapping paper can be inserted between the glass rod and \ce{BaSO4} powder to prevent the powder sticking.
-Nanostructured sample on transparent substrates, i.e., quartz, could be mounted directly with the growth substrate, or ground and spread evenly onto \ce{BaSO4} surface.\cite{isr2011}
+Nanostructured sample on transparent substrates, i.e.
+quartz, could be mounted directly with the growth substrate, or ground and spread evenly onto \ce{BaSO4} surface.\cite{isr2011}

### 2015-02-08 ch-intro/ch-intro.tex
grammar overhaul, tense, clause, ISBN

@@
 Transition metals generally refer to any element in the d-block of periodic table, and \glspl{tmo} mean the chemical compounds that consist of at least one transition metal element and oxygen.
-Similarly, \glspl{tmdc} are compounds that combine at least one transition metal with chalcogen elements from group VIA (S, Se, Te, Po).\footnote{Oxygen also belongs to group VIA, but is often treated separately.} This study focused on the following three materials: molybdenum oxide, tungsten oxide, and tungsten disulfide.
-Both tungsten (W) and molybdenum (Mo) belong to Group VIB transition metal with outer shell electrons configuration as $4d^55s^1$ and $5d^46s^2$, respectively.
+Similarly, \glspl{tmdc} are compounds that combine at least one transition metal with chalcogen elements from group VIA (S, Se, Te, Po).\footnote{Oxygen also belongs to group VIA, but is often treated separately.} Both tungsten (W) and molybdenum (Mo) belong to Group VIB transition metal with outer shell electrons configuration as $4d^55s^1$ and $5d^46s^2$, respectively.
+This study focused on the following three materials: molybdenum oxide (\ce{MoO3}), tungsten oxide (\ce{WO3}), and tungsten disulfide (\ce{WS2}).
 
-The two metal oxides, \ce{MoO3} and \ce{WO3}, have been studied for decades for energy related applications, e.g., photoelectrochemistry,\cite{Su2010} photocatalysis,\cite{Watcharenwong2008, Macphee2010} photovoltaics\cite{Coridan2013} and electrochromism.\cite{Yoshimura1985, Mortimer2011} \ce{WS2} has also been investigated in various forms, i.e., thin films, nanotubes, and 2D atomic layers recently.
-\ce{WS2} exhibits potentials in solar cells,\cite{Britnell2013} water cleavage,\cite{Ballif1999} and field effect transistors.\cite{Perkins2013} Heterostructures formed between \gls{tmo} and \gls{tmdc} provide another degree of freedom to fine tune the band structures, which could enhance the photon energy harvesting performances.
+The two metal oxides, \ce{MoO3} and \ce{WO3}, have been studied for decades for energy related applications, e.g., photoelectrochemistry,\cite{Su2010} photocatalysis,\cite{Watcharenwong2008, Macphee2010} photovoltaics,\cite{Coridan2013} and electrochromism.\cite{Yoshimura1985, Mortimer2011} \ce{WS2} has also been investigated in various morphologies, i.e., thin films, nanotubes, and 2D atomic layers recently.
+\ce{WS2} exhibits potentials in solar cells,\cite{Britnell2013} water cleavage,\cite{Ballif1999} and field effect transistors.\cite{Perkins2013} Heterostructures formed between \gls{tmo} and \gls{tmdc} provide another degree of freedom to fine tune the band structures, which could enhance the solar energy harvesting performances.\cite{Chen2011b}
 
@@
 Smart window is an energy efficient answer by allowing for separate control of the visible and NIR illumination/transmission.
-Several solutions have been proposed in both academia and industry to develop smart windows, including liquid crystal, suspended particles, and electrochromic materials.\cite{Lampert1998} Previous efforts\cite{Deb2008} show the electrochromic materials is the most promising component in smart window design in comparison to other options, in that it requires little power to switch between bleaching and coloration status (changing the optical transmission) and the failure mode is being clear instead of opaque, which is of great importance in commercial applications.
+Several solutions have been proposed in both academia and industry to develop smart windows, including liquid crystal, suspended particles, and electrochromic materials.\cite{Lampert1998} Previous efforts show the electrochromic materials is the most promising component in smart window design in comparison to other options,\cite{Deb2008} in that it requires little power to switch between bleaching and coloration status (changing the optical transmission) and the failure mode is being clear instead of opaque, which is of great importance in commercial applications.
 
@@
 
-Prototype \gls{ecd} usually consists of a stacked configuration as shown in Fig.~\ref{fig:introecd}.
+Prototype \gls{ecd} usually consists of a stacked configuration, as shown in Fig.~\ref{fig:introecd}.
 Typical transmission spectra of the prototype \gls{ecd} based on \ce{WO3} thin film are shown in Fig.~\ref{fig:introtran},\cite{Lampert1998} where optical transimission $T$ in bleaching and coloration states exhibit dynamic changes.
 The reflectance spectra of \ce{WO3} \gls{ecd} strongly depends on the device design.\cite{OBrien1999} As to the absorption, it was deduced that the infrared part was absorbed to a large extent, which was radiated again.
-Assuming the emission property of \gls{ecd} being that of blackbody, Fig.~\ref{fig:introbb} displays the wavelength distribution of spectral radiance, where the spectra span from 3 $\mu$m up to 30 $\mu$m, with peaks around $8\sim10$ $\mu$m.
-Further thermal engineering is needed to better regulate the infrared radiation.
+Assuming the emission property of \gls{ecd} being that of the blackbody, Fig.~\ref{fig:introbb} displays the wavelength distribution of spectral radiance, where the spectra span from 3 $\mu$m up to 30 $\mu$m, with peaks around $8\sim10$ $\mu$m.
+Further thermal engineering is needed to better regulate this infrared radiation.
 
@@
 \end{itemize}
-The deficiency of \gls{ecd} based on amorphous or polycrystalline \ce{WO3} film is the accumulation of ions at the film surface preventing further intercalation,\cite{Dini1996} which led to low coloration efficiency and short life time.
+The deficiency of \gls{ecd} based on amorphous or polycrystalline \ce{WO3} film was the accumulation of ions at the film surface preventing further intercalation,\cite{Dini1996} which led to low coloration efficiency and short life time.
 In contrast, nano-structured single crystalline \ce{WO3} could bypass this limitation, as detailed in Sec.~\ref{sec:nanoadv}.
@@
 Semiconductor is in the center of photoelectrochemical cell design for water splitting, e.g.
-the band gap should be within $2.0 \sim 3.0 $ eV, and \gls{cb} edge should be more negative than reduction potential of \ce{H^+/H2}, whereas the \gls{vb} top should be more positive than the oxidation potential of \ce{H2O}/\ce{O2}.\cite{Osterloh2008,Wang2012} The valence band holes (\ce{h^+}) oxidize water to oxygen and conduction band electrons propel hydrogen generation, as depicted in Eq.~\ref{eq:h2o}.
+the band gap should be within $2.0 \sim 3.0 $ eV, and \gls{cb} edge should be more negative than reduction potential of \ce{H^+/H2}, whereas the \gls{vb} top should be more positive than the oxidation potential of \ce{H2O}/\ce{O2}.\cite{Osterloh2008,Wang2012} The valence band holes (\ce{h^+}) oxidize water to oxygen, and conduction band electrons propel hydrogen generation, as depicted in Eq.~\ref{eq:h2o}.
 \begin{subequations}\label{eq:h2o}
@@
 \end{figure}
-As shown in Fig.~\ref{fig:woxnhe}, \ce{WO3} has \gls{cb} edge positioned slightly more positive than reduction potential of \ce{H^+/H2} versus \gls{nhe}, and \gls{vb} edge much more positive than the oxidation potential of \ce{H2O}/\ce{O2}.
-So the photo-cleavage of water cannot be accomplished by \ce{WO3} alone.
+As shown in Fig.~\ref{fig:woxnhe}, \ce{WO3} has \gls{cb} edge positioned slightly more positive than the reduction potential of \ce{H^+/H2} versus \gls{nhe} and \gls{vb} edge much more positive than the oxidation potential of \ce{H2O}/\ce{O2}; therefore, photo-cleavage of water cannot be accomplished by \ce{WO3} alone.
 Nevertheless, a tandem cell approach by \ce{WO3} film and dye-sensitized \ce{TiO2} has been demonstrated with an efficiency of 4.5\%.\cite{Michael1999} It is worth noting that green plants also have two photosynthetic systems connected in series, one for oxidation of water into oxygen and the other for fixation of carbon dioxide.
-Moreover, favorable oxygen evolution of \ce{WO3} brings good performance in degradation of organic compounds.\cite{Hepel2001,Luo2001,Watcharenwong2008} The formation of long-lived holes is recognized as a key requirement.\cite{Pesci2011} Besides, \ce{WO3} is remarkably stable in acid (pH $<5$), making it a significant candidate for treating water pollutant caused by organic acids.\cite{Monllor-Satoca2006}
+Moreover, favorable oxygen evolution of \ce{WO3} has brought good performance in degradation of organic compounds.\cite{Hepel2001,Luo2001,Watcharenwong2008} The formation of long-lived holes is recognized as a key requirement.\cite{Pesci2011} Besides, \ce{WO3} is remarkably stable in acid (pH $<5$), making it a significant candidate for treating water pollutants caused by organic acids.\cite{Monllor-Satoca2006}
 
@@
 
-Several differences are noted in regarding to bulk materials and nanostructured materials.
+Several differences are noted between bulk materials and nanostructured materials.
 Nanostructured materials possesses gigantic surface area in comparison to its bulk counterpart of the same volume; for instance, given 1 gram \ce{SiO2} nanoparticles in diameter of 10 nm and assuming the density being 1.2 \si{g\per cm^3}, the estimated surface area will be $1\times10^6$ \si{cm^2}.
@@
 
-In regarding to the contents of this study, electrochromic applications based on \gls{tmo} nanowires will benefit from the reduced diffusion depth by eliminating the deficiency of ions accumulation accounted in amorphous oxide thin film devices, which, in turn, leads to shorter response time and higher coloration efficiency.\cite{Huang2008a,Scherer2012} And photocatalytic applications using \gls{tmo} nanostructures could harvest the huge surface area on which unsaturated bond reside, thereby enabling a much higher efficiency.\cite{Mills1993,Merki2011,Chen2011b}
+In regarding to the contents of this study, electrochromic applications based on \gls{tmo} nanowires will benefit from the reduced diffusion depth by eliminating the deficiency of ions accumulation in amorphous oxide thin film devices, which in turn leads to shorter response time and higher coloration efficiency.\cite{Huang2008a,Scherer2012} And photocatalytic applications using \gls{tmo} nanostructures could harvest the huge surface area on which unsaturated bond reside, thereby enabling a much higher efficiency.\cite{Mills1993,Merki2011,Chen2011b}
 
-To make fully use of the nano-engineering, one must just be as aware of the limitations as one is of its advantages.
-For example, an obvious disadvantage is the difficulty of device fabrication using nanomaterials due to the size and requirements of new integration process.
+To make fully use of the nano-engineering, one must just be as aware of the limitations as one is of its advantages; for example, an obvious disadvantage is the difficulty of device fabrication using nanomaterials due to the size and requirements of new integration process.
 There also exist some uncertainty as to the energy band modification present in nanostructures, which could be either useful or not depending on the application scenario.\cite{Wang2012} With this explained, the dissertation moves on to the objective and scope section.
@@
 To fully harvest the advantages of these \gls{tmo} and \gls{tmdc} one-dimensional nanomaterials, a scalable growth method and a comprehensive understanding towards the growth-structure-property relation must be established in the first place.
-This Ph.D.\ study primarily focuses on \ce{WO3} and \ce{MoO3} nanostructure synthesis, the growth mechanism study, crystal structure characterization, and optical properties measurement.
+This study primarily focuses on the \ce{WO3} and \ce{MoO3} nanostructure synthesis, the growth mechanism study, crystal structures characterization, and optical properties measurement.
 
 The materials studied in this dissertation are tungsten oxides (\ce{WO3}), molybdenum oxides (\ce{MoO3}),and tungsten disulfide (\ce{WS2}).
-Experimental tools will be introduced in Chapter 2, including CVD apparatus and substrate treatments for growth, electron microscopes and optical spectrometers for characterization.
+Experimental tools will be introduced in Chapter 2, including the CVD apparatus and substrate treatments for growth and electron microscopes and optical spectrometers for characterization.
 Chapter 3 is devoted to tungsten oxides (\ce{WO3}) and sodium tungsten oxides (\ce{Na5W14O44}) nanowires, where the role of sodium in metallic tungsten precursors are thoroughly investigated; a potentially scalable growth method is also developed.
-Chapter 4 will turn to molybdenum oxide (\ce{MoO3}) growth using alkali metal compounds as catalysts.
+Chapter 4 turns to molybdenum oxide (\ce{MoO3}) growth using alkali metal compounds as catalysts.
 In Chapter 5, a heterostructure based on \ce{WO3} \glspl{nw} is studied.
 Emphasis will be placed on the characterization of individual \ce{WO3}-\ce{WS2} core-shell \gls{nw}.
-The dissertation is then concluded with summary and future work.
+At last, this dissertation is closed with summary and future work.

### 2015-02-08 ch-moox/moox.tex
grammar overhaul, tense, clause, ISBN

@@
 In contrast to the sole axial growth found in the conventional catalyst-assisted growth, two different growth modes were observed for the \ce{MoO3} 1D growth here: transverse growth and axial growth.
-In the transverse mode, the 1D structures grow perpendicularly to the catalyst-deposition interface with catalyst particles on the side surfaces; whereas in the axial mode, the crystal grows along the catalyst-deposition axis.
-The growth modes were explained by a modified \gls{vss} mechanism, and factors that affect the growth were explored in details.
+In the transverse mode, the 1D structures grew perpendicularly to the catalyst-deposition interface with catalyst particles on the side surfaces; whereas in the axial mode, the crystal grew along the catalyst-deposition axis.
+The growth modes were explained by a modified \gls{vss} mechanism, and the growth kinetics were explored in details.
 
-The remaining sections are organized as following: a brief review on previous studies of \ce{MoO3} is given first, followed is the synthesis method in this dissertation.
-Emphasis will be placed on morphological and crystal structure characterization of 1D \ce{MoO3} nanostructures, and the verification of proposed VSS mechanism.
-This chapter is concluded with a summary of VSS growth and some preliminary results of morphology controlled \ce{MoO3} nanostructures.
+The remaining sections are organized as following: a brief review on previous studies of \ce{MoO3} is given first, followed by the synthesis method in this dissertation.
+Emphasis will be placed on morphological and crystal structure characterization of 1D \ce{MoO3} nanostructures and the verification of proposed VSS mechanism.
+This chapter is concluded with a summary of VSS growth and preliminary results on morphology controlled \ce{MoO3} nanostructures.
 
@@
 
-Molybdenum oxide (\ce{MoO3}) crystallizes in three phases, orthorhombic $\alpha$-\ce{MoO3}, monoclinic $\beta$-\ce{MoO3} and the metastable hexagonal h-\ce{MoO3}.\citep{Deb1968,Fibers2007} $\alpha$-\ce{MoO3} phase (hereafter \ce{MoO3}) exhibits anisotropic structure with strong bonding along [001] and [100] direction while van der Waals interaction along [010] direction.\cite{He2003} Due to this unique structure, \ce{MoO3} was found to have several important properties and a wide range of technological applications, such as electrochromism and photochromism,\cite{Yao1992} lubricants,\cite{Sheehan1996} photocatalysts,\cite{Chen2010} and gas sensor, including \ce{CO},\cite{Comini2005} \ce{NO2},\cite{Taurino2006} \ce{H2}\cite{Sha2009} and ethanol.\cite{Choopun} Moreover, other features arise when nanoscale \ce{MoO3} is specifically prepared, e.g., field emission.\citep{Li2002d,Zhou2003b}  As a layered hosting material, \ce{MoO3} can be further modified by intercalating with alkali ions\citep{Spahr1995,Li2006b,Hu2011} and even divalent ion.\cite{Sian2005} This structural richness have enabled improved performance in Li-ion\cite{Mai2007} and sodium-ion battery.\cite{Hariharan2013} In combination with \ce{TiO2} forming a core-shell structure, these nanoparitcles are reported to lower the photon absorption energy of \ce{TiO2}.\cite{Elder2000} When combined with Ag as layered structure, transparent conducting behavior was observed.\cite{Nguyen2012} In addition, \ce{MoO3} is a good precursor for preparing other useful materials, such as \ce{MoS2} fullerene\cite{Li2003c} and few layer \ce{MoS2}.\cite{Lin2012} It will also be an important member of the van der Waals heterostructures.\cite{Geim2013}
+Molybdenum oxide (\ce{MoO3}) crystallizes in three phases: orthorhombic $\alpha$-\ce{MoO3}, monoclinic $\beta$-\ce{MoO3}, and the metastable hexagonal h-\ce{MoO3}.\citep{Deb1968,Fibers2007} $\alpha$-\ce{MoO3} phase (hereafter \ce{MoO3}) exhibits anisotropic structure with strong bonding along [001] and [100] direction while van der Waals interaction along [010] direction.\cite{He2003} Due to this unique structure, \ce{MoO3} has been found to have several important properties and a wide range of technological applications, such as electrochromism and photochromism,\cite{Yao1992} lubricants,\cite{Sheehan1996} photocatalysts,\cite{Chen2010} and gas sensor, including \ce{CO},\cite{Comini2005} \ce{NO2},\cite{Taurino2006} \ce{H2},\cite{Sha2009} and ethanol.\cite{Choopun} Moreover, other features arise when nanoscale \ce{MoO3} is specifically prepared, e.g.
+field emission.\citep{Li2002d,Zhou2003b}  As a layered hosting material, \ce{MoO3} can be further modified by intercalating with alkali ions\citep{Spahr1995,Li2006b,Hu2011} and even divalent ion.\cite{Sian2005} This structural richness has enabled improved performance in Li-ion\cite{Mai2007} and sodium-ion battery.\cite{Hariharan2013} In combination with \ce{TiO2} forming a core-shell structure, these nanoparitcles were reported to lower the photon absorption energy of \ce{TiO2}.\cite{Elder2000} When \ce{MoO3} was combined with Ag as layered structure, transparent conducting behavior was observed.\cite{Nguyen2012} In addition, \ce{MoO3} has been a good precursor for preparing other useful materials, such as \ce{MoS2} fullerene\cite{Li2003c} and few layer \ce{MoS2}.\cite{Lin2012} Recently, 2D atomic layers attracts intensive research efforts, and \ce{MoO3} can be an important member in fabricating the van der Waals heterostructures.\cite{Geim2013}
 
-The coordination number of Mo in \ce{MoO3} is six, so usually \ce{MoO6} octahedra are considered as the building blocks.
-As shown in Fig.~\ref{fig:mo3model}, the layered structure consisting of zig-zag rows of edge-sharing \ce{MoO6} octahedra, while the rows are mutually connected by corners.
-\begin{figure}[ht]
+The coordination number of Mo in \ce{MoO3} is six; thus \ce{MoO6} octahedra are often considered as the building block.
+As shown in Fig.~\ref{fig:mo3model}, the layered structure consists of zig-zag rows of edge-sharing \ce{MoO6} octahedra, and the rows are mutually connected by corners.
+\begin{figure}[htb]
 \centering
@@
 \end{figure}
-While considering the fact that four of the six surrounding O atom are at distances from 1.67 to 1.95 \AA, while the remaining two are as far as 2.25 and 2.33 \AA, \ce{MoO3} could also be considered as built up of chains of \ce{MoO4} tetrahedra connected by the sharing of two oxygen corners with two neighbouring tetrahedra in $c$ axis.
-The infinite chains of \ce{MoO4} tetrahedra from half-layers in the $ac$ plane.
+Another point of view emerges when one considers the fact that four of the six surrounding O atoms are at distances from 1.67 to 1.95 \AA, while the remaining two are as far as 2.25 and 2.33 \AA, \ce{MoO3} could also be considered as chains of \ce{MoO4} tetrahedra connected by the sharing of two oxygen corners with two neighbouring tetrahedra in $c$ axis.
+The infinite chains of \ce{MoO4} tetrahedra form half-layers in the $ac$ plane.
 Two half-layers, which are stapled along $b$ axis, build up one \ce{MoO3} layer.\cite{Itoh2001a} This view stresses that the \ce{MoO6} octahedra are rather distorted.
@@
 
-It is known that a series of molybdate compounds form when alkali metal ions are incorporated into the \ce{MoO3} lattice, and the structures are summarized in Table~\ref{tab:naxmow}.
+It is known that a series of molybdates form when alkali metal ions are incorporated into the \ce{MoO3} lattice, and the structures are summarized in Table~\ref{tab:naxmow}.
 Due to the weak cation-oxygen bonding, alkali metal cations only introduce small perturbations into the energies of \ce{Mo-O} matrix in comparison to cations of other elements.
@@
 
-Raman band assignment for \ce{A2MO4} is well grounded.
-Alkali metal cations with octahedral coordination occur below 230 cm$^{-1}$.
-For \ce{A2M_nO_{3n+1}}, exact assignment is not available yet due to the complicated \ce{MO6} octahedra.
-Molybdenum bronze also exhibits intriguing features, for instance, \gls{cdw} states\footnote{In \gls{cdw} states, conductivity is non-Ohmic above a threshold electric field.} was found in blue bronze \ce{K_{0.3}MoO3}, which can be prepared by electrolytic reduction of \ce{K2MoO4} and \ce{MoO3} melt.\cite{Dumas1983} \ce{K_{0.3}MoO3} stay as monoclinic phase at room temperature, with lattice parameter $a=18.249$ \AA, $b=7.561$ \AA, $c=9.856$ \AA, and $\beta=117.54^{\circ}$, and exhibits a semiconductor-to-metal transition at 180 K.
+Molybdenum bronze also exhibits intriguing features; for instance, \gls{cdw} states\footnote{In \gls{cdw} states, conductivity is non-Ohmic above a threshold electric field.} was found in blue bronze \ce{K_{0.3}MoO3}, which can be prepared by electrolytic reduction of \ce{K2MoO4} and \ce{MoO3} melt.\cite{Dumas1983} \ce{K_{0.3}MoO3} stays as monoclinic phase at room temperature with lattice parameter $a=18.249$ \AA, $b=7.561$ \AA, $c=9.856$ \AA, and $\beta=117.54^{\circ}$ and exhibits a semiconductor-to-metal transition at 180 K.
 Electrical transport measurements yield an highly anisotropic ratio of DC conductivities of 1:10:1000.
 Along this high conducting axis, metallic reflection behavior is confirmed by optical measurements.
-Therefore, this blue bronze $\ce{K_{0.3}MoO3}$ is known as quasi-1D metal.\cite{Sing1999}
+Therefore, this blue bronze $\ce{K_{0.3}MoO3}$ is also known as quasi-1D metal.\cite{Sing1999}
 
@@
 
-Researchers have been exploring a variety of methods to synthesized different \ce{MoO3} nanostructures.
-Only a brief introduction will be given here, since these efforts has been well documented in several review articles.\cite{He2003} Most of these methods can be categorized into two groups: solution-based hydrothermal procedures \citep{Li2002b,Xia2006,Li2006a,Camacho-Bragado2006} and chemical vapor transport and deposition approaches.\citep{Zeng1998,Li2002c,Li2002d,Zhou2003b,Fibers2007,Yan2009} Both methods have its own merits.
-Hydrothermal process usually need lower temperature(\textless 300 \si{\degreeCelsius}), but the duration is usually long and requires several post-growth processing steps; whereas vapor deposition demands relatively high temperature (\textgreater 500 \si{\degreeCelsius}) yet with a shorter time.
+Researchers have been exploring a variety of methods to synthesize different \ce{MoO3} nanostructures.
+Only a brief introduction will be given here, since these efforts has been well documented in several review articles.\cite{He2003} Most of these methods can be categorized into two groups: solution-based hydrothermal procedures \citep{Li2002b,Xia2006,Li2006a,Camacho-Bragado2006} and chemical vapor deposition approaches.\citep{Zeng1998,Li2002c,Li2002d,Zhou2003b,Fibers2007,Yan2009} Both methods have its own merits.
+Hydrothermal process usually needs lower temperature(\textless 300 \si{\degreeCelsius}), but the duration is usually long, and the sample requires several post-growth processing steps; whereas vapor deposition demands relatively high temperature (\textgreater 500 \si{\degreeCelsius}) yet a shorter time.
 Both methods are scalable for industrial applications.
-However the hydrothermal treatment seems to allow more  nanostructures control than does the vapor deposition method.
-Nanobelts,\cite{Li2002b} helical nanosheets, nanoflowers, prims-like rods\cite{Li2006a} and nanoribbons\cite{Camacho-Bragado2006} were obtained by the former one while nanoflakes,\cite{Chen2009} nanobelts\cite{Hu2009} and nanowires\citep{Zhou2003b,Chen2011b} dominated the product morphology for the latter one.
+However, the hydrothermal treatment seems to allow more  nanostructures control than does the vapor deposition method.
+Nanobelts,\cite{Li2002b} helical nanosheets, nanoflowers, prims-like rods,\cite{Li2006a} and nanoribbons\cite{Camacho-Bragado2006} were obtained by the former one while nanoflakes,\cite{Chen2009} nanobelts,\cite{Hu2009} and nanowires\citep{Zhou2003b,Chen2011b} dominated the product morphology for the latter one.
 The assistance of Au catalyst in vapor deposition only altered the orientation\cite{Yan2009} or served as preferred nucleation sites\cite{Cai2011} without producing new \ce{MoO3} structures.
-\citeauthor{Chithambararaj2013} prepared hexagonal \ce{MoO3} nanocrystal via hydrothermal method and demonstrated the photodegradation of methylene blue (MB) under visible light.\cite{Chithambararaj2013} The efficiency dependence on catalysis/dye ratio, light intensity and temperature was studied.
+\citeauthor{Chithambararaj2013} prepared hexagonal \ce{MoO3} nanocrystal via hydrothermal method and demonstrated the photodegradation of methylene blue (MB) under visible light.\cite{Chithambararaj2013} The efficiency dependence on catalysis/dye ratio, light intensity, and temperature was studied.
 h-\ce{MoO3} was mostly synthesized using solution methods, where \ce{NH4+} and \ce{OH-} were possible structure directing and stable agents.
@@
 
-Silicon substrates was first cleaned according to the procedure in Sec.~\ref{ch2sub} on page~\pageref{ch2sub}.
-To apply the catalysts, 54 $\mu$L 10 mM \ce{NaOH} (or \ce{KI}, \ce{Na2CO3}) was drop-cast onto clean substrates and then air dried in a chemical fume hood.
+Silicon substrates was first cleaned according to the procedures stated in Sec.~\ref{ch2sub} on page~\pageref{ch2sub} and directly used in non-catalyst-assisted experiment.
+In catalyst-assisted growth, hydrophilic Si substrates were first drop-cast with \ce{NaOH} (or \ce{KI}, \ce{Na2CO3}) solution (54 $\mu$L 10 mM) and then air dried in a chemical fume hood before experiment.
 Other alkali ions-containing substrates, such as glass (Fisher Scientific, microscope slide, 12-549) and indium tin oxide (ITO) coated glass (Delta Technologies, 25\si{\ohm}), were cleaned by the same routine except the absence of plasma cleaning and subsequent aqueous solution dipping.
@@
 \end{table}
-In a typical synthesis run (Fig.~\ref{fig:mooxgrowth}), about 2 g molybdenum powders were loaded into the uniform heating zone and the sealed chamber was first pumped down to 10 mTorr. 
+In a typical catalytic synthesis (Fig.~\ref{fig:mooxgrowth}), about 2 g molybdenum powders were loaded into the uniform heating zone, and the sealed chamber was first pumped down to 10 mTorr. 
 % cvd layout
@@
 \includegraphics[width=0.6\textwidth]{CVD_and_temp_MoO3.jpg}
-\caption[CVD growth setup of \ce{MoO3}]{CVD growth setup of \ce{MoO3}.
-The triangular labels $\blacktriangledown$ were measured points at ambient environment.
-The nominal substrates temperature were estimated from interpolation data.}
+\caption[CVD growth setup of \ce{MoO3}]{CVD growth setup of \ce{MoO3}. The triangular labels $\blacktriangledown$ were measured points at ambient environment.}
 \label{fig:mooxgrowth}
 \end{figure}
-Then oxygen flow varying between 0.1 sccm to 10 sccm (standard cubic centimeter per minute) was admitted from upstream inlet.
+Oxygen flow, varying between 0.1 sccm to 10 sccm, was then admitted from the upstream inlet.
 With 10 sccm UHP Ar as carrier gas, the overall pressure reached about 200 mTorr.
 The heating temperature was ramped up to 800 \si{\degreeCelsius} in 30 min and lasted for 15 to 120 min.
-Then the heating power was turned off and the chamber was allowed to naturally cool down to room temperature.
+At last, the heating power was turned off, and the chamber was allowed to naturally cool to room temperature.
 The substrate was placed in downstream location where the temperature was about 350 to 650 \si{\degreeCelsius} according to open air temperature profile.
-Non-catalytic growth shares the same procedure except the NaOH treatment on Si substrates.
+Non-catalytic growth shared the same procedure except the NaOH treatment on Si substrates.
 
@@
 The growth mechanism was probed using two series of control experiments.
-Then a growth model was proposed and verified.
+Then, a VSS growth model was proposed and verified.
 In the end, this growth model was applied onto other substrates with alkali metal ions, and various \ce{MoO3} nanostructures were produced.
@@
 
-For \ce{MoO3} non-catalytic growth, this study observed the typical micro-flakes morphologies as shown in Fig.~\ref{fig:mosisem}.
-Most flakes exhibit rectangular shape, with average thickness of one micron, standard deviation $\sigma_D=0.34 \mu$m.
+For \ce{MoO3} non-catalytic growth, this study observed micro-flakes morphology, as shown in Fig.~\ref{fig:mosisem}.
+Most flakes exhibited rectangular shape with average thickness of one micron and standard deviation $\sigma_D$ of $0.34 \mu$m.
 % sem in (31210-31510) batches
@@
 As shown in Fig.~\ref{fig:mooxch}, the crystal structure and phase of the as-synthesized specimen were examined by XRD and Raman.
-The XRD pattern (Fig.~\ref{fig:moxrd}) is readily indexed to the orthorhombic phase of \ce{MoO3} (ICDD PDF 05-0508, \emph{a}=3.9628 \AA, \emph{b}=13.855 \AA, \emph{c}=3.6964 \AA).
+The XRD pattern (Fig.~\ref{fig:moxrd}) was readily indexed to the orthorhombic phase of \ce{MoO3} (ICDD PDF 05-0508, \emph{a}=3.9628 \AA, \emph{b}=13.855 \AA, and \emph{c}=3.6964 \AA).
 The space group is $D_{2h}^{16}(Pbnm)$.
-This crystal structure is indeed a unique example among transition metal oxides, representing a transitional stage between tetrahedra and octahedral coordination.\cite{Itoh2001a} The strongest peak index is (110), suggesting the orientation of \ce{MoO3} is not parallel to the substrate, which is consistent with the morphology displayed in Fig.~\ref{fig:mosem1}.
-In contrast, a different XRD peak pattern is observed in Sec.~\ref{sec:nasi}, where the catalytic growth occurs.
+This crystal structure is indeed a unique example among transition metal oxides, representing a transitional stage between tetrahedra and octahedral coordination.\cite{Itoh2001a} The strongest peak index was (110), suggesting the orientation of \ce{MoO3} was not parallel to the substrate, in consistent with the morphology displayed in Fig.~\ref{fig:mosem1}.
+In contrast, different dominating orientation was observed in the XRD pattern from catalytic growth (Sec.~\ref{sec:nasi}).
 % xrd raman
@@
 \end{figure}
-The Raman spectrum of the as-synthesized specimen also closely matches \ce{MoO3} features in previous studies.\cite{Dixit1986,Silveira2012} During m-Raman measurement, the laser spot was carefully focused onto the plates and several inspections on different positions were observed to ensure the reproductivity of spectra data.
+The Raman spectrum of the as-synthesized specimen also closely matched \ce{MoO3} features in previous studies.\cite{Dixit1986,Silveira2012} During m-Raman measurement, the laser spot was carefully focused onto the \ce{MoO3} flakes, and several inspections on different positions were observed to ensure the reproductivity of spectra data.
 As shown in Fig.~\ref{fig:moram}, 14 distinct bands were well resolved.
-The 284 \si{cm^{-1}} peak represents the wagging mode for double bond \ce{O=Mo=O}.
-The 337 and 380  \si{cm^{-1}} peaks are assigned to \ce{O-Mo-O} bending and scissoring modes.
-The 199 \si{cm^{-1}} peak and two other weaker peaks at 218 and 247 \si{cm^{-1}} represent \ce{O=Mo=O} $B_{2g}$ twist, $A_g$ chain mode and \ce{O=Mo=O} $B_{3g}$ twist mode, respectively.
-The 667 \si{cm^{-1}} peak is assigned to triply coordinated oxygen stretching model resulting from edge-shared oxygen in common to three octahedral.
-The 819 \si{cm^{-1}} peak is from doubly coordinated oxygen stretching mode arising from corner-shared oxygen between two octahedral.
-The 996 \si{cm^{-1}} peak comes from unshared oxygen stretching mode.\cite{Siciliano2009} The assignment is summarized in Table~\ref{tab:moram}.
+The 284 \si{cm^{-1}} peak represented the wagging mode for double bond \ce{O=Mo=O}.
+The 337 and 380  \si{cm^{-1}} peaks were assigned to \ce{O-Mo-O} bending and scissoring modes, respectively.
+The 199 \si{cm^{-1}} peak and two other weaker peaks at 218 and 247 \si{cm^{-1}} represented \ce{O=Mo=O} $B_{2g}$ twist, $A_g$ chain mode, and \ce{O=Mo=O} $B_{3g}$ twist mode, respectively.
+The 667 \si{cm^{-1}} peak was assigned to triply coordinated oxygen stretching model resulting from edge-shared oxygen in common to three octahedral.
+The 819 \si{cm^{-1}} peak arose from doubly coordinated oxygen stretching mode between two octahedral.
+The 996 \si{cm^{-1}} peak was from unshared oxygen stretching mode.\cite{Siciliano2009} The Rama symmetry assignment was summarized in Table~\ref{tab:moram}.
 % raman assign
@@
 
-All growth time of samples prepared in Sec.~\ref{sec:naohsi} were 2 h, the same as in Sec.~\ref{sec:nonsi}.
-The only difference in growth conditions from Sec.~\ref{sec:nonsi} is the Si substrate treatment.
-When NaOH is applied onto Si, the deposition morphologies change significantly.
-Fig.~\ref{fig:ch4sem2by3} shows a comparison of the morphology difference between the non-catalyst growth (Fig.~\ref{fig:ch4sem2by3}a) and the catalyst-assisted growth (Fig.~\ref{fig:ch4sem2by3}b-f) revealed by SEM.
+All growth time of samples prepared in Sec.~\ref{sec:naohsi} was 2 h, the same as that in Sec.~\ref{sec:nonsi}.
+The only difference in growth conditions from Sec.~\ref{sec:nonsi} was the Si substrate treatment.
+When NaOH was applied onto Si, the deposition morphologies were changed significantly.
+Fig.~\ref{fig:ch4sem2by3} show a comparison of the morphology difference between the non-catalyst growth (Fig.~\ref{fig:ch4sem2by3}a) and the catalyst-assisted growth (Fig.~\ref{fig:ch4sem2by3}b-f) revealed by SEM imaging.
 The non-catalyst growth morphology has been discussed from Fig.~\ref{fig:mosisem} on page~\pageref{fig:mosisem}.
-Several different structures emerge when catalyst is applied, such as nanobelts in Fig.~\ref{fig:ch4sem2by3}d with length up to hundreds of microns, and microtowers in Fig.~\ref{fig:ch4sem2by3}f with diameter around 10 $\mu$m.
+Several different structures emerged when catalyst was applied, such as nanobelts in Fig.~\ref{fig:ch4sem2by3}d with length up to hundreds of microns and microtowers in Fig.~\ref{fig:ch4sem2by3}f with diameter around 10 $\mu$m.
+A detailed description of these \ce{MoO3} nanostructures has been published and can be found in Ref.\cite{Sheng2015}.
 
@@
 
-The crystal structures of the as-synthesized specimens were characterized with X-ray diffraction (XRD) for the non-catalyst growth (Fig.~\ref{fig:ch4tem3by3}a) and catalyst-assisted growth (Fig.~\ref{fig:ch4tem3by3}b).
-The calculated lattice parameters and standard database value (ICDD PDF 05-0508) matches favorably, as listed in Table~\ref{tab:ch4xrd}.
+The crystal structures of the as-synthesized specimens were characterized with \gls{xrd} for the non-catalyst growth (Fig.~\ref{fig:ch4tem3by3}a) and catalyst-assisted growth (Fig.~\ref{fig:ch4tem3by3}b).
+The calculated lattice parameters and standard database value (ICDD PDF 05-0508) matched favorably, as listed in Table~\ref{tab:ch4xrd}.
 No other phases were found from XRD spectra for both specimens.
-This result indicates that if there were any catalyst phases present in the catalyst-assisted specimen, they must be of extremely low amount as compared to that of the \ce{MoO3} phase, presumably below the detection limit.
+This result indicated that if there were any catalyst phases present in the catalyst-assisted specimen, they must be of extremely low amount as compared to that of the \ce{MoO3} phase, presumably below the detection limit.
 % xrd 
@@
 \end{table}
-
-The XRD pattern of catalyst-assisted growth shown in Fig.~\ref{fig:ch4tem3by3}b is dominated by the (0$k$0) family peaks, showing a different preferred orientation from the non-catalytic growth.
+The XRD pattern of catalyst-assisted growth shown in Fig.~\ref{fig:ch4tem3by3}b was dominated by the (0$k$0) family peaks, showing a different preferred orientation from the non-catalytic growth.
 The reason will be discussed in Sec.~\ref{sec:nasi}.
-
 % tem
@@
 \end{figure}
-
-Fig.~\ref{fig:ch4tem3by3}c shows low magnification TEM image of a rectangular nanoplate grown without catalysts and the SAED pattern.
-The nanoplate was exfoliated by ultra-sonication in acetone solution to obtain high-resolution TEM (HRTEM) image, hence the nanoplate was broken into fragments.
-The SAED pattern in [010] axis and the HRTEM image (Fig.~\ref{fig:ch4tem3by3}d) show the nanoplate has a (010) top surface and two orthogonal edges along [100] and [001], respectively.
-For the catalyst-assisted growth, Fig.~\ref{fig:ch4tem3by3}e and Fig.~\ref{fig:ch4tem3by3}f-g confirm both the forked nanoplate and the nanobelt have a (010) top surface and a growth direction of [001], while Fig.~\ref{fig:ch4tem3by3}h reveals the microtower grow with (010) layers stacking along a [010] direction.
-Lattice measurements in Fig.~\ref{fig:ch4tem3by3}d and g indicate a planar distance of 0.38 nm for (100) planes and 0.36 nm for (001) planes.
-These values are slightly smaller than the standard data for $\alpha$-\ce{MoO3} and the results from XRD measurements.
-This deviation in lattice parameters may arise from the error in TEM measurements and the lattice distortion from the electron beam irradiation.\cite{Wang2004b} These results indicate that all the as-synthesized 1D structures have a layered structure.
+Fig.~\ref{fig:ch4tem3by3}c show low magnification TEM image of a rectangular nanoplate grown without catalysts and the SAED pattern.
+The nanoplate was exfoliated by ultra-sonication in acetone solution to obtain high-resolution TEM (HRTEM) image; hence, the nanoplate was broken into fragments.
+The SAED pattern in [010] axis and the HRTEM image (Fig.~\ref{fig:ch4tem3by3}d) show the nanoplate had a (010) top surface and two orthogonal edges along [100] and [001], respectively.
+For the catalyst-assisted growth, Fig.~\ref{fig:ch4tem3by3}e and Fig.~\ref{fig:ch4tem3by3}f-g confirmed both the forked nanoplate and the nanobelt had a (010) top surface and a growth direction of [001]; while Fig.~\ref{fig:ch4tem3by3}h revealed the microtower grew with (010) layers stacking along a [010] direction.
+Lattice measurements in Fig.~\ref{fig:ch4tem3by3}d and g indicated a planar distance of 0.38 nm for (100) planes and 0.36 nm for (001) planes.
+These values were slightly smaller than the standard data for $\alpha$-\ce{MoO3} and the results from XRD measurements.
+This deviation in lattice parameters may arise from the error in TEM measurements and/or the lattice distortion of \ce{MoO3} during the electron beam irradiation.\cite{Wang2004b} These results indicated that all the as-synthesized 1D structures had a layered structure.
 Raman measurement on the catalytic growth sample revealed similar \ce{MoO3} bands, as already displayed in Fig.~\ref{fig:mooxch} on page~\pageref{fig:mooxch}.
@@
 
-To provide a proper context, \gls{vls} process is brief introduced.
-\gls{vls} is first proposed by Wagner,\cite{Wagner1964} and further developed by \citeauthor{Givargizov1975}.\cite{Givargizov1975} This method has become an important strategy for synthesizing 1D nanostructures.\cite{Lieber1998} Conventionally, a liquid eutectic droplet is formed by catalyst itself or by alloying with the growth material, acting as a trap of growth species.
-The growth is initialized by supersaturation of the liquid alloy and subsequent precipitation at the solid-liquid interface.
-The choice of catalyst usually is among the several noble metals since they are physically active but chemically stable or inert in most growth scenarios.
-The growth materials span a wide range including group IV,\cite{Hochbaum2005} group III-V,\citep{Dalacu2013, Xiao2012, Dubrovskii2011} group II-VI,\cite{Hao2006} and some metal oxides, such as \ce{ZnO},\citep{Huang2001a,Ramgir2010} \ce{MgO},\citep{HEUER1967, Nagashima2007} \ce{SiO2},\cite{Pan2002} and \ce{TiO2},\cite{Zhuge2012} to name a few.
+The growth process of the 1D \ce{MoO3} nanoflakes in non-catalytic experiment can be explained by the \gls{vs} mechanism, as proposed in other vapor phase depositions of \ce{MoO3} nanostructures.\cite{Brezesinski2010, Kalantar-zadeh2010} It has been shown that \ce{MoO3} growth on the NaOH treated Si substrates exhibited dramatic differences.
+Previous study in our group had found that \ce{MoO3} deposition on ITO glass exhibited new morphologies that were not observed on Si substrates under the same growth conditions, yet the mechanism was not well investigated.\cite{predeep2011} A list of composition difference between glass and Si substrate show the additional elements of Na, K, and Ca, \emph{etc} in glass.
+Since the concentration of Na is highest among these extra elements, it is most likely to induce the new morphology growth.
+Therefore, a \gls{vls} mechanism may exist for the \ce{MoO3} growth when alkali metal ions are involved.
+To provide a proper context, \gls{vls} process is briefly introduced here.
+
+\gls{vls} was first proposed by Wagner\cite{Wagner1964} and further developed by \citeauthor{Givargizov1975}.\cite{Givargizov1975} This method has become an important strategy for synthesizing 1D nanostructures.\cite{Lieber1998} Conventionally, a liquid eutectic droplet is formed by catalyst itself or by alloying with the growth material, acting as a trap of growth species.
+The growth is initialized by supersaturation of the liquid alloy, and subsequently precipitation occurs at the solid-liquid interface.
+The choice of catalyst usually is among the several noble metals, since they are physically active but chemically stable or inert in most growth scenarios.
+The growth materials span a wide range, including group IV,\cite{Hochbaum2005} group III-V,\citep{Dalacu2013, Xiao2012, Dubrovskii2011} group II-VI,\cite{Hao2006} and some metal oxides, such as \ce{ZnO},\citep{Huang2001a,Ramgir2010} \ce{MgO},\citep{HEUER1967, Nagashima2007} \ce{SiO2},\cite{Pan2002} and \ce{TiO2},\cite{Zhuge2012} to name a few.
 The catalysts can be Au, Pd, Pt, Ni,\cite{Xiao2012} Ti, Ga,\cite{Pan2002} and even KI.
+Understanding the interaction between liquid droplet and the solid interface allows for a rich engineering space to fine tune the geometry and structures of the as-grown nanostructures.
+For instances, the diameter of Si nanowires can be controlled by laser ablated catalyst\cite{Morales1998} or well-defined Au nanoparticles.\cite{Cui2001b} Under proper conditions, axial modulation can produce nanowire superlattices from group IV and III-V materials.\citep{Gudiksen2002,Bjork2002} Radial composition modulation has also been demonstrated by selectively suppressing VLS process, providing a robust routine for homogeneous or heterogeneous core-shell structures.\cite{Lauhon2002a}
 
-Understanding the interaction between liquid droplet and the solid interface allows for a rich engineering space to fine tune the geometry and structures of the as-grown nanostructures.
-For instances, the diameter of Si nanowires (NWs) can be controlled by laser ablated catalyst\cite{Morales1998} or well-defined Au nanoparticles.\cite{Cui2001b} Under proper conditions, axial modulation can produce nanowire superlattices from group IV and III-V materials.\citep{Gudiksen2002,Bjork2002}  Radial composition modulation have also been demonstrated by selectively suppressing VLS process, providing a robust routine for homogeneous or heterogeneous core-shell structures.\cite{Lauhon2002a}
-
-Previous study in our group has found that \ce{MoO3} deposition on ITO glass exhibits new morphologies that are not observed on Si substrates, yet the mechanism is not well investigated.\cite{predeep2011} Based on the \gls{vls} process, it is known that a eutectic state is the key to promote preferred growth direction.
-A list of composition difference between glass and Si substrate shows the extra elements of Na, K, Ca, \emph{etc}.
-Since the concentration of Na is highest among these extra elements, it is most likely to induce the new morphology growth.
-A literature search indeed shows that there exists \ce{Na2MoO4}-\ce{MoO3} phase diagram as shown in Fig.~\ref{fig:ch4pd}.\cite{Hoermann1929} Notice that the phases of the Na-Mo-O system can be written as \ce{Na2O.nMoO3}, where n = 1, 2, 3, and 4.
-
+Back to the \ce{MoO3} and alkali metal ions, a literature search found that there exists a \ce{Na2MoO4}-\ce{MoO3} phase diagram, as shown in Fig.~\ref{fig:ch4pd}.\cite{Hoermann1929} Note that the phases of the Na-Mo-O system can be written as \ce{Na2O.nMoO3}, where n = 1, 2, 3, and 4.
 %phase diagram
@@
 \end{figure}
-
-Based on this phase diagram, the physical constants of reactants in Table~\ref{tb:mothermo}, and the growth conditions adopted in this study, it is predicted that the overall reactions occur in the following sequences.
-First, Mo powder is oxidized and \ce{MoO3} vapor is produced and transported to downstream by Ar carrier gas.
-Then NaOH reacts with incoming \ce{MoO3} according to Formula~\ref{eq:pd}.
+Based on this phase diagram, the physical constants of reactants in Table~\ref{tb:mothermo}, and the growth conditions adopted in this study, it was predicted that the overall reactions occurred in the following sequences.
+First, Mo powder was oxidized, and \ce{MoO3} vapor was produced and transported to downstream by Ar carrier gas.
+Then, NaOH reacted with the incoming \ce{MoO3} vapor according to Formula~\ref{eq:pd}.
 \begin{subequations}\label{eq:pd}
@@
 The melting point of \ce{Na2MoO4} is 687 \si{\degreeCelsius}.
-Based on the open air temperature profile (Fig.~\ref{fig:mooxgrowth}), the substrate is located in temperature zone between 650 and 350 \si{\degreeCelsius}.
-The actual temperature distribution during growth is different from ambient measurement due to the pressure change and thermal conduction along the Si substrate.
-It is difficult to acquire the accurate values along the substrate; however, by considering the flow rate, the actual temperature will be higher than predicted by open air measurement.\cite{Subannajui2010} The melting of \ce{Na2MoO4} is highly possible when taking into account of its size as well.\cite{Bruggemann1997} The continuous supply of \ce{MoO3} growth species will push the phase evolution towards high \ce{MoO3} molar ratio end, with $n$ in \ce{Na2O.nMoO3} increasing from 1 to 4.
-Each site of \ce{Na2MoO4} will continue absorb incoming \ce{MoO3}, forming a swelling particle.
-\ce{MoO3} will precipitate from these seeds when a critical supersaturation concentration is reached, which is about 75\% in unit of mole according to Fig.~\ref{fig:ch4pd}.
-This ratio considerably exceeds that of the usual metal catalyst scenario.
-This high solubility accounts for several observations in current experiments: the dimensions of individual deposit is much larger than that of initial particle, the concentration of sodium in final products is extremely low.
+Based on the open air temperature profile (Fig.~\ref{fig:mooxgrowth}), the substrate was located in temperature zone between 650 and 350 \si{\degreeCelsius}.
+The actual temperature distribution during growth was different from ambient measurement due to the pressure change and thermal conduction along the Si substrate.
+It was difficult to acquire the accurate temperatures along the substrate; however, by considering the flow rate, the actual temperature should be higher than that predicted by open air measurement.\cite{Subannajui2010} The continuous supply of \ce{MoO3} growth species pushed the phase evolution towards high \ce{MoO3} molar ratio end, with $n$ in \ce{Na2O.nMoO3} increasing from 1 to 4.
+Each site of \ce{Na2MoO4} continued absorb incoming \ce{MoO3}, forming a swelling particle.
+\ce{MoO3} precipitated from these seeds when a critical supersaturation concentration was reached, which was about 75\% in unit of mole according to Fig.~\ref{fig:ch4pd}.
+This ratio considerably exceeded that of the usual metal catalyst scenario, such as the Au-Si system.
+This high solubility accounted for several observations in current experiments: the dimensions of individual deposit was much larger than that of initial particle and the concentration of sodium in final products was extremely low.
 Based on this aforementioned analysis, the author proposed following hypothesis:
-%theorem environment
 
-\emph{The reaction on NaOH-Si substrate follow the phase diagram, and \ce{Na2Mo4O13} serves as the catalyst promoting various 1D \ce{MoO3} growth.}
+\emph{The reaction on NaOH-Si substrate follows the phase diagram, and \ce{Na2Mo4O13} serves as the catalyst promoting various 1D \ce{MoO3} growth.}
 
-In a typical 2 h growth, the \ce{MoO3} weight increase is about 20 mg, which is about $1.4\times 10^{-4}$ mol.
-This amount far exceeds the applied NaOH of $5\times 10^{-7}$ mol used in the procedure of Sec.~\ref{sec:grow} on page~\pageref{sec:grow}.
+In a typical 2 h growth, the \ce{MoO3} weight increase was about 20 mg, which was $1.4\times 10^{-4}$ mol.
+This amount far exceeded the applied NaOH of $5\times 10^{-7}$ mol used in the procedure of Sec.~\ref{sec:grow} on page~\pageref{sec:grow}.
 To capture the early stage growth, the supply of \ce{MoO3} must be reduced in a controlled way.
@@
 The first series regulated \ce{O2} flow at 0.1, 1, 3, and 10 sccm with fixed growth time of 15 min.
-The second series controls growth time at 15, 30, 60, and 90 min with fixed \ce{O2} flow of 10 sccm.
-Two series share one common growth of 10 sccm \ce{O2} for 15 min.
+The second series controlled the growth time at 15, 30, 60, and 90 min with fixed \ce{O2} flow of 10 sccm.
+Two series shared one common growth of 10 sccm \ce{O2} for 15 min.
 
-The oxygen regulated growths were characterized using SEM, EDX and Raman, as shown in Fig.~\ref{fig:ch4oxy}.
+The oxygen regulated growths were characterized using SEM, EDX, and Raman, as shown in Fig.~\ref{fig:ch4oxy}.
 When \ce{O2} flow was $\leq 1$ sccm, the deposition show micron size plate growth (Fig.~\ref{fig:ch4oxy}a and d).
-As oxygen flow becomes higher, the deposition amount increased dramatically, with a morphology of 1D forked plate decorated by triangular shape particles.
+As oxygen flow became higher, the deposition amount increased dramatically, with a morphology of 1D forked plate decorated by triangular shape particles.
 % sem
@@
 \end{figure}
-
 Micro-Raman scattering was used to probe the phase change during the oxygen regulated growth.
-The Raman spectra of sodium molybdates is featured with multiple strong peaks located between 800 and 1000 \si{cm^{-1}}, which we refer as high-frequency region hereafter.
-\ce{MoO3} phase shows two peaks in this region with the strongest one at about 820 \si{cm^{-1}}; \ce{Na2Mo2O7} phase exhibits four peaks in this region with the strongest one moving to 937 \si{cm^{-1}}, whereas \ce{Na2Mo4O13} phase shows even more peaks in high-frequency region, with a doublet at 962 and 970 \si{cm^{-1}}, respectively.\cite{Schofield2005,Saraiva2011} As predicted by the phase diagram (Fig.~\ref{fig:ch4pd}), Raman spectra identified \ce{Na2Mo2O7} phase in the 0.1 sccm growth (Fig.~\ref{fig:ch4oxy}b), and \ce{Na2Mo4O13} phase on the particles in the rest three growths (Fig.~\ref{fig:ch4oxy}e, h, and k).
-This observation supports the previous hypothesis about the reaction sequence on NaOH-Si substrate (Formula~\ref{eq:pd}).
-Element analysis performed on the Raman sites also confirm the presence of Na, Mo and O in particles growth, and only Mo and O in the plate growth (Fig.~\ref{fig:ch4oxy}c, f, i, and l).
-It is worth noting that the absence of Na signal in the forked \ce{MoO3} plate indicates the doping level would be lower than the detection limit of 0.01 wt.\% if the Na doping ever occurs.
-It should be pointed out the existence of \ce{Na2Mo3O10} phase is in doubt so far, and no Raman fingerprint is reported.\cite{Fomichev1992} Table~\ref{tb:moo3ram} compared the Raman spectra of sodium molybdates and \ce{MoO3} between present work and literature reports.
+The Raman spectra of sodium molybdates was featured with multiple strong peaks located between 800 and 1000 \si{cm^{-1}}, which was referred as high-frequency region hereafter.
+\ce{MoO3} phase show two peaks in this region with the strongest one at about 820 \si{cm^{-1}}; \ce{Na2Mo2O7} phase exhibited four peaks in this region with the strongest one moving to 937 \si{cm^{-1}}, whereas \ce{Na2Mo4O13} phase show even more peaks in the high-frequency region with a doublet at 962 and 970 \si{cm^{-1}}, respectively.\cite{Schofield2005,Saraiva2011} As predicted by the phase diagram (Fig.~\ref{fig:ch4pd}), Raman spectra identified \ce{Na2Mo2O7} phase in the 0.1 sccm growth (Fig.~\ref{fig:ch4oxy}b), and \ce{Na2Mo4O13} phase on the particles in the rest three growths (Fig.~\ref{fig:ch4oxy}e, h, and k).
+This observation supported the previous hypothesis about the reaction sequences on NaOH-Si substrate (Formula~\ref{eq:pd}).
+Element analysis performed on the Raman sites also confirmed the presence of Na, Mo, and O in particles growth and only Mo and O in the plate growth (Fig.~\ref{fig:ch4oxy}c, f, i, and l).
+It is worth noting that the absence of Na signal in the forked \ce{MoO3} plate indicated the doping level would be lower than the detection limit of 0.01 wt.\% if the Na doping ever occurred.
+It should also be pointed out the existence of \ce{Na2Mo3O10} phase is in doubt so far, and no Raman fingerprint is reported.\cite{Fomichev1992} Table~\ref{tb:moo3ram} compared the Raman spectra of sodium molybdates and \ce{MoO3} between present work and literature reports.
 % moo3ram
@@
 The 15 min and 30 min growth show that dense arrays of \ce{MoO3} forked nanoplates with a length of hundreds of microns covering the substrate areas at different temperatures.
-With the increase of the growth time, these nanoplates keep growing and become larger, longer, and denser.
-Long 1D \ce{MoO3} structures start to grow on top of the nanoplate arrays.
-For 60 min growth, long nanobelts appear on top of the nanoplates.
-For the growth time of 90 min, the nanobelts grow longer, and some grow into microbelts.
-Microtowers start to grow as well.
+With the increase of the growth time, these nanoplates kept growing and became larger, longer, and denser.
+Long 1D \ce{MoO3} structures started to grow on top of the nanoplate arrays.
+For 60 min growth, long nanobelts appeared on top of the nanoplates.
+For the growth time of 90 min, the nanobelts grew longer, and some grew into microbelts.
+Microtowers started to grow as well.
 
@@
 \end{figure}
-
 To reveal the growth mechanisms for the long 1D structures in the second stage, specimens were carefully examined to locate the catalyst particles.
 Small catalyst particles ranging from several hundred nanometers to several microns were found at different locations of these long 1D structures.
-As shown in Fig.~\ref{fig:ch4edx1} and Fig.~\ref{fig:ch4edx2}, EDX element analysis confirmed the presence of Na, Mo, and O in these particles, indicating the particles are sodium molybdate catalysts.
+As shown in Fig.~\ref{fig:ch4edx1} and Fig.~\ref{fig:ch4edx2}, EDX element analysis confirmed the presence of Na, Mo, and O in these particles, indicating the particles were sodium molybdate catalysts.
 
@@
 It could be of difficulty to observe the sodium molybdate particles on the as-synthesized belts and towers due to the following two factors, one is the consumption of catalysts, such as evaporation; the other is the unpredictable location of the catalyst.
-Unlike the conventional \gls{vls} growth where the catalysts were predominantly found at the tip of 1D nanostructures, the catalyst in current study were mostly found at the side wall of long nanobelts, and the location could be on the tip, or several microns away from tip.
-As for the microtowers, it is even rare to observe Na element.
-
-Some observations under similar controlled growth conditions is also listed as following to support the proposed growth model:
-
+Unlike the conventional \gls{vls} growth where the catalysts were predominantly found at the tip of 1D nanostructures, the catalyst in current study were mostly found at the side wall of long nanobelts, and the location could be on the tip or several microns away from the tip.
+As for the microtowers, it was even rare to observe Na element.
+Some observations under similar controlled growth conditions was also listed as following to support the proposed growth model:
 \begin{enumerate}
-\item When no Mo powder is used, NaOH still holds onto substrate with some locations exhibiting etching.
-\item When no Mo powder is used while growth is performed in an old tube or oxygen flow is limited to a extreme small value, circular particle-like solid were found and Mo, Na and O were detected, suggesting the existence of VLS mechanism.
-Using Mo coated substrate and subsequent NaOH treatment, similar particles formation was repeated.
-No discernible XRD pattern emerged, illustrating the amorphous nature of liquid catalyst.
-\item 1 min growth shows plates in high temperature end and irregular shapes in low temperature end.
-\item 15 min growth shows \ce{MoO3} plates parallel to substrate, with some belts emerging and growing out of the substrate plane.
-This is presumably due to the growth direction mismatch between different plates.
+\item When no Mo powder was used, NaOH still held onto substrate with some locations exhibiting etching.
+\item 1 min growth show plates in high temperature end and irregular shapes in low temperature end.
+\item 15 min growth show \ce{MoO3} plates parallel to substrate, with some belts emerging and growing out of the substrate plane.
+This was presumably due to the growth direction mismatch between different plates.
 Morphology will also depend on local NaOH concentration.
-NaOH trace mark turns into connected plates at the original locations, showing the high concentration mediated the morphology evolution.
+NaOH trace mark turned into connected plates at the original locations, showing the high concentration mediated the morphology evolution.
 The possible catalyst solid was sitting on the top of plate layer.
-Also some belt-like growth is visible on reaction chamber walls, suggesting the evaporation and transport of \ce{Na_xMoO3} vapor phase;
-\item 30 min growth: belts growth begin (500 microns long, grow rate is estimated to be 0.5 $\mu$ m/s), tower structures show up as well, but much less than belt.
-Two kinds of belts found, tapering and non-tapering.
-The former one seems to have particles mostly associated with sidewalls of the top part.
-\item In reduced time or less oxygen supply growth, Na-containing site was found located onto the sidewall of belts instead of the usual expected tip.
-XRD pattern indicated the existence of \ce{Na_xMoO3} phase.
-And \ce{MoO3} XRD pattern is dominated by (0k0) peaks, indicating a 2D layer-by-layer growth with lateral rate exceeding that of axial direction.
-\item 2 h growth: there are crossed tapering belts at downstream boundary, with more than one particle located along the interface of two perpendicular belts, EDX confirmed high Na content.
-\item Using NaOH treated hydrophobic substrates, dense tower array growth was found along the edge areas or molten periphery of particles, where 5 min growth already show the initial stage of tower with diameter about 1 $\mu$ m, which increase to 10 $\mu$ m in prolonged growth.
+Some belt-like growth was visible on reaction chamber walls, suggesting the evaporation and transport of \ce{Na_xMoO3} vapor phase;
+\item Using NaOH treated hydrophobic substrates, dense tower array growth was found along the edge areas or molten periphery of particles, where 5 min growth already show the initial stage of tower with diameter about 1 $\mu$ m, which increased to 10 $\mu$ m in prolonged growth.
 \end{enumerate}
@@
 The growth of \ce{MoO3} on NaOH-Si can be divided into two stages delimited by the emerging of long nanobelts and microtowers.
-A growth model is proposed to account for the observed morphologies of \ce{MoO3} long nanobelt and tower-like structures.
+A growth model was proposed to account for the observed morphologies of \ce{MoO3} long nanobelt and tower-like structures.
 
@@
 
-The first stage is dominated by transverse growth.
-The atomic steps in proposed growth model are depicted in the upper panel of Fig.~\ref{fig:ch4vls}.
-It has been verified that \ce{Na2Mo4O13} forms during the early stage of growth, and can act as catalysts.
-Although the exact phase (liquid or solid) of \ce{Na2Mo4O13} is not known yet in current study, it can be deduced that the \ce{Na2Mo4O13} exists as an active site for the adsorption of incoming \ce{MoO3} growth species.
-When the catalyst is smaller than some critical size, there is no preferred growth direction.
-This changed when the precipitated solid exceeds certain critical dimension, and the morphology evolution is then determined by the relative size of already formed solid and the associated catalyst.
+The first stage was dominated by transverse growth.
+The atomic steps in proposed growth model were depicted in the upper panel of Fig.~\ref{fig:ch4vls}.
+It has been verified that \ce{Na2Mo4O13} formed during the early stage of growth and acted as catalysts.
+Although the exact phase (liquid or solid) of \ce{Na2Mo4O13} was not known yet in current study, it can be deduced that the \ce{Na2Mo4O13} existed as an active site for the adsorption of incoming \ce{MoO3} growth species.
+When the catalyst was smaller than some critical size, there is no preferred growth direction.
+This changed when the precipitated solid exceeded certain critical dimension, and the morphology evolution was then determined by the relative size of already formed solid and the associated catalyst.
 Several pathways could occur after the accommodation of \ce{MoO3} vapor and supersaturation.
@@
 Some unique features of \ce{MoO3} must be taken into consideration to properly evaluate the dominate pathway(s).
-It has been reported that \ce{MoO3} can spontaneously spread over the surface of supports (\emph{e.g.}, \ce{Al2O3}, \ce{SiO2}, and Au) to form a monolayer or submonolayer at a temperature (257 \si{\degreeCelsius}) well below the melting point.\cite{Leyrer1990} This strong spreading behavior can be explained by the solid-solid wetting process, in which the driving force is the decrease in total surface free energy.\cite{Leyrer1988} Although the detailed transport mechanisms of the spreading are still in debate, it is suggested that the high mobility of the Mo oxide species on substrates and \ce{MoO3} islands can promote the spreading and the ambient gases could further enhance the spreading.\cite{Gunther2000, Song2003} Based on above analysis and the final morphology of \ce{MoO3}, the dominance of accommodation and spreading pathway in higher temperature part of the growth sample is most possible in this study.
-Hereby the transverse growth mode is attributed to the strong spreading capability of \ce{MoO3}.
-The final morphology of observed nanoplate and nanobelt is a combined result of \gls{vs} and \gls{vls} growth.
-On the other hand, the tower-like structures in the second stage follow the axial growth mode in conventional VLS process.
+It has been reported that \ce{MoO3} can spontaneously spread over the surface of supports (\emph{e.g.} \ce{Al2O3}, \ce{SiO2}, and Au) to form a monolayer or submonolayer at a temperature (257 \si{\degreeCelsius}) well below the melting point.\cite{Leyrer1990} This strong spreading behavior can be explained by the solid-solid wetting process, in which the driving force was the decrease in total surface free energy.\cite{Leyrer1988} Although the detailed transport mechanisms of the spreading are still in debate, it is suggested that the high mobility of the Mo oxide species on substrates and \ce{MoO3} islands can promote the spreading and the ambient gases could further enhance the spreading.\cite{Gunther2000, Song2003} Based on above analysis and the final morphology of \ce{MoO3}, the dominance of accommodation and spreading pathway in higher temperature part of the growth sample was most possible in this study.
+Hereby the transverse growth mode was attributed to the strong spreading capability of \ce{MoO3}.
+The final morphology of observed nanoplate and nanobelt was a combined result of \gls{vs} and \gls{vls} growth.
+On the other hand, the tower-like structures in the second stage followed the axial growth mode in conventional VLS process.
 The molybdates can be evaporated from the higher temperature end and re-condense onto the lower temperature region.
 As illustrated in the lower panel of Fig.~\ref{fig:ch4vls}, this could initiate either belt growth or tower growth depending on the locations.
-The microtowers in this study primarily grow at the low temperature end of the substrate, where the spreading capability of the Mo oxide species is possibly limited.
-Thus the transverse growth pathway is probably suppressed and axial growth becomes dominant.
+The microtowers in this study primarily grew at the low temperature end of the substrate, where the spreading capability of the Mo oxide species was possibly limited.
+Thus the transverse growth pathway was probably suppressed and axial growth became dominant.
 The above analysis was substantiated by the multiple observation revealed by SEM imaging, as shown in Fig.~\ref{fig:ch4msch}.
@@
 
-The transport of molybdates in proposed growth model is verified by a side-by-side experiment, as schematically depicted in Fig.~\ref{fig:ch4sbs}a.
+The transport of molybdates in proposed growth model was verified by a side-by-side experiment, as schematically depicted in Fig.~\ref{fig:ch4sbs}a.
 Two substrates, one with NaOH catalyst and one bare substrate, were loaded side-by-side at the same location for the growth.
@@
 \end{figure}
-After the growth, besides the non-catalyst rectangular plates, catalyst induced 1D structures were also found on the bare substrate (Fig.~\ref{fig:ch4sbs}b-i).
-This result clearly confirms that the catalyst can be evaporated and transferred from the NaOH treated substrate to the untreated one.
-The catalyst vapors can nucleate and form catalyst particles on the \ce{MoO3} deposition promoting the VLS growth of different 1D structures.
+After the growth, besides the non-catalyst rectangular plates, catalyst induced 1D \ce{MoO3} structures were also found on the bare substrate (Fig.~\ref{fig:ch4sbs}b-i).
+This result clearly confirmed that the catalyst can be evaporated and transferred from the NaOH-treated substrate onto the bare one.
+The catalyst vapors can nucleate and form catalyst particles on the \ce{MoO3} deposition promoting the VSS growth of different 1D structures.
 It is worth mentioning that catalyst particles were not observed on all the 1D structures.
@@
 \item Because of the evaporation, the catalyst particles may become too small to be detected.
-Some particles could even disappear terminating the catalyzed growth, which may explain the growth of the microtowers with a flat top.
-\end{enumerate*} The evaporation and nucleation of catalyst not only promote the growth of the 1D structures in the second stage growth, they also shape the morphologies of these 1D structures.
+Some particles could even disappeared terminating the catalyzed growth, which may explain the growth of the microtowers with a flat top.
+\end{enumerate*} The evaporation and nucleation of catalyst not only promoted the growth of the 1D structures in the second stage growth, they also shaped the morphologies of these 1D structures.
 Many 1D structures in the second stage were found to have a tapered shape, such as triangular nanobelts (Fig.~\ref{fig:ch4sem2by3}b and d), microtowers with tapered tips (Fig.~\ref{fig:ch4sem2by3}f).
@@
 Due to the evaporation, the size of the catalyst particles can shrink during the growth resulting in the tapered growth.
-The \gls{vs} growth on the side surfaces is another possible mechanism, which promotes the radial growth of the 1D structures forming the tapered shape.
-Another important factor is the gradually reduced growth during the cooling process.
-During the cooling, the \ce{MoO3} vapor supply reduced and the growth temperature gradually decrease.
-Hence the growth rate slows down producing the tapered tips on the top of some 1D structures.
+The \gls{vs} growth on the side surfaces was another possible mechanism, which promoted the radial growth of the 1D structures forming the tapered shape.
+Another important factor was the gradually reduced growth during the cooling process.
+During the cooling, the \ce{MoO3} vapor supply reduced, and the growth temperature gradually decreased.
+Hence, the growth rate slowed down producing the tapered tips on the top of some 1D structures.
 
 \subsection{Growth on Alkali Metal Containing Substrates}\label{sec:glass}
-In analog with the \ce{Na2MoO4}-\ce{MoO3} binary phase diagram, other alkali metals, such as Li and K, could also form A-Mo-O alloy at elevated temperature.
+In analogy to the \ce{Na2MoO4}-\ce{MoO3} binary phase diagram, other alkali metals, such as Li and K, could also form A-Mo-O alloy at elevated temperature.
 This fact allows for the usage of a variety of alkali metal based material as catalyst to promote \gls{vls} or \gls{vss} growth of \ce{MoO3}.
-Two group of experiments have been performed in this study; the first one used \ce{KI} and \ce{Na2CO3} treated Si substrate, the second one used alkali metal ions containing substrate, including ITO/glass, glass, and mica.
+Two group of experiments have been performed in this study; the first one used \ce{KI} and \ce{Na2CO3} treated Si substrate and the second one used alkali metal ions containing substrate, including ITO/glass, glass, and mica.
 Fig.~\ref{fig:ch4al1}a-b show the long belt growth on KI treated Si substrate and the forked plate growth on \ce{Na2CO3} treated Si, respectively.
-Compared to NaOH-Si growth, the belt on KI appears with rough edge, whereas No long belt or tower was observed on the sample with \ce{Na2CO3}.
+Compared to NaOH-Si growth, the belt on KI appeared with rough edge; whereas no long belt or tower was observed on the sample with \ce{Na2CO3}.
 
@@
 
-Fig.~\ref{fig:ch4al2}a-c illustrate microtowers grown on ITO glass, sword-shape belts on glass, and nanoblets growth on mica, respectively.
+Fig.~\ref{fig:ch4al2}a-c illustrated microtowers grown on ITO glass, sword-shape belts on glass, and nanoblets growth on mica, respectively.
 The towers on ITO glass exhibited stacking features.
-The sword-shape belts on glass arise from a combination of VSS and VS mechanism.
-The long belts found on mica (\ce{K(Al2)(Si3Al)O10(OH)2}) probably arise from potassium-catalyzed \gls{vls} mechanism.\cite{Hu2011}
+The sword-shape belts on glass arose from a combination of VSS and VS mechanism.
+The long belts found on mica (\ce{K(Al2)(Si3Al)O10(OH)2}) probably stemmed from potassium-catalyzed \gls{vls} mechanism.\cite{Hu2011}
 
@@
 \end{figure}
-A rudimentary analysis on the \ce{Na+} diffusion in glass was performed to understand the growth dynamics of \ce{MoO3} using those alkali ions containing substrates.
+A rudimentary analysis on the \ce{Na+} diffusion in glass was performed to understand the growth dynamics of \ce{MoO3} on the alkali ions containing substrates.
 Because the alkali ions in glass can diffuse out at elevated temperature, the proposed \gls{vss} mechanism will modify the \ce{MoO3} deposition.
-Therefore, the mass transport of sodium ions in silica glass is first estimated to evaluate the amount of catalyst available during the growth of \ce{MoO3}.
-The driving force could be external field or concentration gradient.
-And the dynamics is governed by diffusion equation
+Therefore, the mass transport of sodium ions in silica glass was first estimated to evaluate the amount of catalyst available during the growth of \ce{MoO3}.
+The driving force could be external field or concentration gradient, and the dynamics was governed by diffusion equation
 \begin{align}\label{eq:nadiff}
@@
 Diffusion coefficient highly depends on the overall environment in which the ions reside.
-Typical values of $D$ for Na ions are listed in Table~\ref{tab:mona}
+Typical values of $D$ for Na ions were listed in Table~\ref{tab:mona}
 
@@
 
-The substrates used in this work are glass and ITO/glass; the relevant parameters are as following:
+The substrates used in this work were glass and ITO/glass; the relevant parameters were as following:
 \begin{itemize}
@@
 \end{itemize}
-Substituting these values into Eq.~\ref{eq:nadiff}, the net flux $J$ is estimated as
+Substituting these values into Eq.~\ref{eq:nadiff}, the net flux $J$ was estimated to be
 \begin{align}
@@
 \end{align}
-In typical growth of 2 h, the net amount of Na diffusing out of substrate is then $1.44\times10^{-4}$ mol, which is about 10\% of total Na ions in the glass substrates.
-The diffusion length $\sqrt{Dt}$ is 190 $\mu$m.
-Notice this result overestimates since the flux will reduce gradually.
-Meanwhile the molar amount of \ce{NaOH} applied on Si substrate is about $5\times10^{-7}$ mol.
-Considering the adjusted ratio, Na contents should be much more when using glass substrate than when using NaOH-Si substrate.
-Another important factor is the evaporation of sodium molybdates.
-However, few report could be found in literature.
-Only one was reported by \citeauthor{Kazenas2010}.\cite{Kazenas2010} The partial pressure of \ce{Na2MoO4} is calculated to be 0.2 mTorr at 800 \si{\degreeCelsius} and $3.5\times 10^{-3}$ mTorr at 670 \si{\degreeCelsius}.\footnote{$\log P(atm)= -13794/T + 6.19$}
+In typical growth of 2 h, the net amount of Na diffusing out of substrate was then $1.44\times10^{-4}$ mol, about 10\% of total Na ions in the glass substrates.
+The diffusion length $\sqrt{Dt}$ was 190 $\mu$m.
+Note this result overestimated since the flux will reduce gradually.
+Meanwhile the molar amount of \ce{NaOH} applied on Si substrate was about $5\times10^{-7}$ mol.
+Considering the adjusted ratio, Na contents should be much more when using glass substrate than using NaOH-Si substrate.
+Another important factor was the evaporation of sodium molybdates.
+However, few relevant report could be found in literature.
+Only one was reported by \citeauthor{Kazenas2010}.\cite{Kazenas2010} The partial pressure of \ce{Na2MoO4} was calculated to be 0.2 mTorr at 800 \si{\degreeCelsius} and $3.5\times 10^{-3}$ mTorr at 670 \si{\degreeCelsius}.\footnote{$\log P(atm)= -13794/T + 6.19$}
 
@@
 %\input{./ch-moox/mooptics}
-The optical properties of the as-grown specimen was evaluated using \gls{drs} method.
-Fig.~\ref{fig:modrs} show the hemisphere diffuse reflection spectrum from 800 nm to 250 nm, where the diffuse reflection kept increasing from 27\% to 33\% when incident wavelength scanned from 800nm to about 400 nm, then drop sharply to 15\% between 400 nm and 300 nm.
+The optical properties of the as-grown specimen were evaluated using \gls{drs} method.
+Fig.~\ref{fig:modrs} show the hemisphere diffuse reflection spectrum from 800 nm to 250 nm, where the diffuse reflection $R_{dff}$ kept increasing from 27\% to 33\% when incident wavelength scanned from 800nm to about 400 nm; then, $R_{dff}$ dropped sharply to 15\% between 400 nm and 300 nm.
 The KMT function fitting was used to estimated the energy gap, as displayed in Fig.~\ref{fig:mokmt}.
 Extrapolation indicated a gap of 3.2 eV, corresponding to absorption edge at 387 nm.
-This matches well with the DRS data.
+This matched well with the DRS data.
 \begin{figure}[htb]
@@
 \end{figure}
-Another reflection peak was found at 260 nm, illustrating there is more complex electronic band structures above 4 eV.
-As a comparison, the estimated energy gap and results from previous studies is summarized in Table~\ref{tab:mobg}.
+Another reflection peak was found at 260 nm, illustrating there is more complex electronic band structures for \ce{MoO3} above 4 eV.
+As a comparison, the estimated energy gap and results from previous studies was summarized in Table~\ref{tab:mobg}.
 \begin{table}[htb]
@@
 A modified vapor-solid-solid mechanism was proposed and favorably verified.
-Two growth modes, i.e., transverse growth and axial growth, were highlighted, which not only improved the yield, but also allowed for versatile morphology control of 1D \ce{MoO3} nanostructures.
+Two growth modes, i.e., transverse growth and axial growth, were highlighted, which not only improved the yield but also allowed for versatile morphology control of 1D \ce{MoO3} nanostructures.
 This methodology was further extended onto glass and ITO glass substrates, paving the way to a more integrated process of using \ce{MoO3} nanostructures onto various solar energy saving and harvesting applications.

### 2015-02-08 ch-tms/tms.tex
grammar overhaul, tense, clause, ISBN

@@
 In this chapter, a TEM-Raman integrated study on \ce{WO3}-\ce{WS2} core-shell nanostructures is presented.
-This study leverages a home-built micromanipulator apparatus to transfer the nanostructures between TEM grids and other desired substrates.
-This technique has enabled us to correlate TEM and micro-Raman measurement on individual nanowires, thereby enhancing the understanding of structure-property relations which would otherwise be blurred in conventional ensemble averaged methods.
-\ce{WO3}-\ce{WS2} heterostructure is chosen due to the potential applications in photocatalysis and hydrogen evolution.
+This study leverages a home-built micromanipulator apparatus to transfer the nanostructures from growth substrates to TEM grids.
+This transferring technique has allowed for correlating TEM and micro-Raman measurement on individual \ce{WO3}-\ce{WS2} core-shell nanowire and enhancing the understanding of structure-property relations, which would otherwise be blurred in conventional ensemble averaged methods.
+\ce{WO3}-\ce{WS2} heterostructure was chosen due to its potential applications in photocatalysis and hydrogen evolution.\cite{DiPaola1999,Chen2011b}
 
-The remaining sections are arranged in following order: a review on the growth of \ce{MS2} (M = Mo, W) \glspl{nt} and 2D \gls{fl} structures will be introduced first, followed by Raman spectroscopy summary on \ce{WS2} NTs and FL.
+The remaining sections are arranged in the following order: a review on the growth of \ce{MS2} (M = Mo, W) \glspl{nt} and 2D \gls{fl} structures will be introduced first, followed by Raman spectroscopy summary on \ce{WS2} NTs and FL.
 The thesis will then focus on synthesis of \ce{WO3}-\ce{WS2} heterostructure and various characterizations on both ensemble and individual nanowires.
@@
 
-The \ce{WO3}-\ce{WS2} core-shell nanowires were fabricated using a sulfurization process based on the \ce{WO3} NWs prepared by the seeded growth method in Chapter~3, Sec.~\ref{sec:sgfg}.
-For the sake of completeness, schematic layout of the two-step growth were illustrated in Fig.~\ref{fig:ch5grow} including the seeded growth and subsequent sulfurization process.
+The \ce{WO3}-\ce{WS2} core-shell nanowires were fabricated using a sulfurization process based on the \ce{WO3} NWs prepared from the seeded growth method in Chapter~3, Sec.~\ref{sec:sgfg}.
+For the sake of completeness, schematic layout of the two-step growth were illustrated in Fig.~\ref{fig:ch5grow}, including the seeded growth and subsequent sulfurization process.
 % cvd NW growth
@@
 \centering
-\includegraphics[width=0.6\textwidth]{cs_growth_lbd}
+\includegraphics[width=0.5\textwidth]{cs_growth_lbd}
 \caption[Schematic diagrams of seeded growth of \ce{WO3} NW and sulfurization process]{Schematic diagrams of (a) seeded growth of \ce{WO3} NW and (b) sulfurization process. }
@@
 \end{figure}
-In a representative seeded growth (Fig.~\ref{fig:ch5grow}a), 4N5 or 5N tungsten source powder as defined in Table~\ref{tab:powder} was positioned in the upstream end of a quartz boat and downstream about 2.5 inch the substrate was stationed.
+In a representative seeded growth (Fig.~\ref{fig:ch5grow}a), 4N5 or 5N tungsten source powders as defined in Table~\ref{tab:powder} were positioned in the upstream end of a quartz boat, and downstream about 2.5 inch the substrate was stationed.
 Additional tungsten seed powders (3N) were distributed evenly onto the substrate.
@@
 A cold trap filled with liquid nitrogen in downstream was used to collect possible sulfur precipitation.
-Then the furnace was heated to 750 \si{\degreeCelsius} in 30 min, held for 15 min, and allowed to naturally cool down to room temperature.
-During entire growth process, 30 sccm Ar was used as carrier flow.
+Then, the furnace was heated to 750 \si{\degreeCelsius} in 30 min, held for 15 min, and allowed to naturally cool down to room temperature.
+During entire growth process, 30 sccm Ar was used as carrier gas.
 
@@
 
-The morphology of \ce{WO3} NWs in micron scale almost stay the same after sulfurization, as shown in the inset SEM imaging of Fig.~\ref{fig:ch5ws2sem}.
-The length of individual nanowire can be up to 15 $\mu$m and the diameter varies from about 40 to 300 nm.
+The morphology of \ce{WO3} NWs in micron scale almost stayed the same after sulfurization, as shown in the inset SEM imaging of Fig.~\ref{fig:ch5ws2sem}.
+The length of individual nanowire were up to 15 $\mu$m, and the diameter varied from about 40 to 200 nm.
 The surface of the NWs were rather smooth without other attachments.
@@
 The EDX spectrum in Fig.~\ref{fig:ch5ws2sem} revealed the presence of sulfur element, indicating the effectiveness of sulfurization.
-Compared to the XRD pattern on seeded growth \ce{WO3} sample, post-sulfurization pattern (Fig.~\ref{fig:ch5ws2xrd}) shows a much reduced \ce{WO3} intensity with W phase becoming relatively prominent.
-Still the peaks at 23.44$^{\circ}$ and 24.36$^{\circ}$ can be indexed to \ce{WO3} (020) and (200) reflection, respectively.
-This result as well as the SEM imaging indicates \ce{WO3} NWs could preserve some long range order after the sulfurization for 15 min at 750 \si{\degreeCelsius}.
+Compared to the XRD pattern on seeded growth \ce{WO3} sample, post-sulfurization pattern (Fig.~\ref{fig:ch5ws2xrd}) show a much reduced \ce{WO3} intensity with W phase becoming relatively prominent.
+The peaks at 23.44$^{\circ}$ and 24.36$^{\circ}$ were indexed to \ce{WO3} (020) and (200) reflection, respectively.
+This result as well as the SEM imaging indicated \ce{WO3} NWs preserved some long range order after the sulfurization process of 15 min at 750 \si{\degreeCelsius}.
 %fig xrd ws2 
@@
 This observation can also be used to account for the extreme small peak at 13.87$^{\circ}$ in the post-sulfurization spectrum.
-Compared the reference 2H-\ce{WS2} (002) peak (14.37$^{\circ}$, ICDD PDF 04-003-4478), the redshift of sample peak indicates an increase of lattice spacing along $c$ axis (from 6.16 \si{\angstrom} to 6.38 \si{\angstrom}).
-The FWHM of this (002) peak is about 1.1$^{\circ}$, giving an estimation on the crystalline size of 7.5 nm according to Scherrer equation.
+In comparison to the reference 2H-\ce{WS2} (002) peak (14.37$^{\circ}$, ICDD PDF 04-003-4478), the redshift of specimen peak here indicated an increase of lattice spacing along $c$ axis (from 6.16 \si{\angstrom} to 6.38 \si{\angstrom}).
+The FWHM of this (002) peak was about 1.1$^{\circ}$, giving an estimation on the crystalline size of 7.5 nm according to Scherrer equation.
 
-Due to this small spacing, TEM is primarily utilized to observe the detailed morphology of \ce{WO3}-\ce{WS2} core-shell NWs.
+Due to this small spacing, TEM was primarily utilized to observe the detailed morphology of \ce{WO3}-\ce{WS2} core-shell NWs.
 Fig.~\ref{fig:ch5ws2tem1}c and d show HRTEM imaging on typical tip and body region of the core-shell NW, respectively.
-A comparison with the pre-sulfurization specimen (Fig.~\ref{fig:woseedtem2} on page~\pageref{fig:woseedtem2}) readily reveals the formation of core-shell morphology after sulfurization.
-The measured layer spacing is 6.5 \si{\angstrom}, slightly larger than bulk 2H-\ce{WS2} of 6.16 \si{\angstrom}, but in good agreement with XRD result in Fig.~\ref{fig:ch5ws2xrd}.
-The clear contrast in core region also prove the lattice structure of \ce{WO3} is not seriously distorted.
+A comparison with the pre-sulfurization specimen (Fig.~\ref{fig:woseedtem2} on page~\pageref{fig:woseedtem2}) readily revealed the formation of core-shell morphology after sulfurization.
+The measured layer spacing of 6.5 \si{\angstrom} appeared slightly larger than bulk 2H-\ce{WS2} value of 6.16 \si{\angstrom}, but matched well with the XRD result in Fig.~\ref{fig:ch5ws2xrd}.
+The sharp contrast in core region also proved the lattice structure of \ce{WO3} was not seriously distorted upon sulfurization.
 % tem core shell layer
@@
 
-After examining dozens of core-shell NWs, it was found the \ce{WS2} layer number at NW tip was usually the largest, reaching more than ten, and the layer number could decrease to one along the NW body, but there exist some layer number fluctuation and shape modification.
-Fig.~\ref{fig:ch5ws2tem3} shows a smooth transition of \ce{WS2} layer number on the tip region of one NW.
-The layer number is about 7 on the tip corner, gradually decreases from 4 to 3 along the NW body, and stops at 2.
-Closer observation indicates the layer spacing is not quite uniform in the tip area, probably due to the complex curvature and bending.
+After examining dozens of core-shell NWs, this study found the \ce{WS2} layer number at NW tip was usually the largest, reaching more than ten, and the layer number decreased to one along the NW body; but there also existed some layer number fluctuation and shape modification.
+Fig.~\ref{fig:ch5ws2tem3} show a smooth transition of \ce{WS2} layer number on the tip region of one NW.
+The layer number was about 7 on the tip corner, gradually decreased from 4 to 3 along the NW body, and stopped at 2 layers.
+Closer observation indicated the layer spacing was not quite uniform in the tip area, probably due to the complex curvature and bending.
 \ce{WS2} fullerene also show similar structures.
-Since the closing of the tip region could be of great complexity and the induced strain could modify Raman signal considerably, the TEM-Raman integrated measurement in this study will focus on the body region only, with those having smooth transition of layer number.
+Since the closing of the tip region could be of great complexity and the induced strain could modify Raman signal considerably, the TEM-Raman integrated measurement in this study focused on the body region of the core-shell NWs with smooth transition layer number.
 % coreshell tem
@@
 As illustrated in Fig.~\ref{fig:ch5ws2tem4}, complicated \ce{WS2} encapsulation was observed on one tapered core-shell NW.
-This tapering probably arose from the sulfurization process, but could be also due to the parent \ce{WO3} NW.
+This tapering probably arose from the sulfurization process but could be also due to the parent \ce{WO3} NW.
 The diameter varied from about 200 nm to 15 nm, and the \ce{WS2} layer number also changed in a nonlinear manner.
-On some turning region, the \ce{WS2} seems penetrating into the body of primary \ce{WO3} NW.
+On some turning region, the \ce{WS2} seemed penetrating into the body of primary \ce{WO3} NW.
 % coreshell tem
@@
 A systematic study on the sulfurization must be performed to understand the growth dynamics.
-The growth mechanism of \ce{WS2} nanotubes from oxides were thoroughly studied,\cite{Feldman1998} and it is generally agreed that the sulfurization of \ce{WO3} is a diffusion limited reaction.\cite{Feldman1996} It was also suggested that the core \ce{WO3} NWs will become non-stoichiometric phases upon sulfurization.\cite{Feldman1996,ZAK2009} This study recognizes this possibility but also consider two factors different from previous studies: one is the usage of sulfur as precursor instead of \ce{H2} and/or \ce{H2S} as in previous reports, which will accelerate the reduction of \ce{WO3} significantly due to the formation of \ce{H2O}; the other is the short reaction time and light degree of sulfurization, which probably will not distort the \ce{WO3} lattice significantly, as evidenced by the XRD and HRTEM analysis in this section.
-The sulfurization dynamic is then proposed as following in this thesis: the tips of \ce{WO3} NWs exhibit greater crystalline disorder, and \ce{WS2} layers on tips are folded at least along two axes, resulting a higher density of defects and thus a higher sulfurization rate; while the folding along NW body is quasi-one dimensional, subsequently the sulfurization rate could be lower.
-Besides, sulfurization could also initiated from the NW body, presumably due to the presence of surface defects.
+The growth mechanism of \ce{WS2} nanotubes from oxides has been thoroughly studied,\cite{Feldman1998} and it was generally agreed that the sulfurization of \ce{WO3} was a diffusion limited reaction.\cite{Feldman1996} It was also suggested that the core \ce{WO3} NWs became non-stoichiometric phases upon sulfurization.\cite{Feldman1996,ZAK2009} This study recognized this possibility but also considered two factors different from previous studies: one was the usage of sulfur as precursor instead of \ce{H2} and/or \ce{H2S} as in previous reports, which accelerated the reduction of \ce{WO3} significantly due to the formation of \ce{H2O}; the other was the short reaction time and light degree of sulfurization, which probably would not distort the \ce{WO3} lattice significantly, as evidenced by the XRD and HRTEM analysis in this section.
+The sulfurization dynamic was then proposed as following in this thesis: the tips of \ce{WO3} NWs exhibited greater crystalline disorder, and \ce{WS2} layers on tips were folded at least along two axes, resulting a higher density of defects and thus a higher sulfurization rate; while the folding along NW body was quasi-one dimensional, subsequently the sulfurization rate could be lower.
+Besides, sulfurization could also be initiated from the NW body, presumably due to the presence of surface defects.
 As a result, this led to the uneven \ce{WS2} layer number distribution along the core-shell NWs.
@@
 No obviously consumed core region was observed among most of the core-shell NWs examined under TEM.
-An exception is shown in Fig.~\ref{fig:ch5ws2tem2}.
+An exception was shown in Fig.~\ref{fig:ch5ws2tem2}.
 Note the rectangular area show abrupt termination of one \ce{WS2} layer, which was tentatively attributed to stacking fault in this study.
@@
 
-To perform TEM-Raman integrated study, the core-shell specimen was first dispersed into ethanol solution and then dipped onto polydimethylsiloxane (PDMS) support.
+To perform TEM-Raman integrated study, the core-shell specimen was first dispersed into ethanol solution; and then the solution was dipped onto polydimethylsiloxane (PDMS) support.
 A home-built micromanipulator with probe tip (tungsten, 100nm point radius, Micromaipulator) was used to pick up the core-shell NWs and transfer them onto TEM grids (Lacey C, 300 mesh, Cu, 01895-F Ted Pella, Inc) under 100X objective.
-The steps are visualized in Fig.~\ref{fig:ch5ws2trans}.
+The steps were visualized in Fig.~\ref{fig:ch5ws2trans}.
 % ws2 transfer
@@
 The transferred NWs were first examined using TEM to identify the \ce{WS2} layers configuration and the associated geometrical orientation.
-Then the core-shell NWs on TEM grids were probed under Raman in a location-resolved manner.
-Only those core-shell NWs exhibiting relative smooth \ce{WS2} wall number transition was used in subsequent Raman measurement (wall number and layer number were used interchangeably in this work, but 1 wall is not equal to 1 layer due to the tubular structure).
-To perform TEM and Raman analysis on individual NWs, only one NW was placed in each cell on the TEM grid (65 $\times$ 65 $\mu$m).
+Then, the core-shell NWs on TEM grids were probed under Raman in a location-resolved manner.
+Only those core-shell NWs exhibiting relative smooth \ce{WS2} wall number transition were used in subsequent Raman measurement (wall number and layer number were used interchangeably in this work, but note that 1 wall is not equal to 1 layer due to the tubular structure).
+To perform TEM and Raman analysis on individual NWs, this study placed one NW only in each cell of the TEM grid (65 $\times$ 65 $\mu$m).
 And the low magnification TEM images and optical images were compared to map the NW location and orientation.
 The carbon film patterns served as a unique background to resolve possible ambiguity.
-An example is given in Fig.~\ref{fig:ch5ws2map}.
+An example was given in Fig.~\ref{fig:ch5ws2map}.
 % ws2 map
@@
 
-Fig.~\ref{fig:ch5ws2ram}a-d depict typical \ce{WO3}-\ce{WS2} NWs in the TEM-Raman integrated study.
-The diameter of these core-shell NWs is around 100 nm and the length around 10 $\mu$m, allowing for up to five distinctive Raman scattering sites.
-Fig.~\ref{fig:ch5ws2ram}e shows the associated Raman spectra acquired on core-shell NWs using 532 nm excitation wavelength.
+Fig.~\ref{fig:ch5ws2ram}a-d depicted typical morphologies of the \ce{WO3}-\ce{WS2} NWs in the TEM-Raman integrated study.
+The diameter of these core-shell NWs was about 100 nm, and the length about 10 $\mu$m, allowing for up to five distinctive Raman scattering sites.
+Fig.~\ref{fig:ch5ws2ram}e show the associated Raman spectra acquired on the core-shell NWs using 532 nm excitation wavelength.
 Two strong peaks were observed between 300 and 450 \si{cm^{-1}}.
-The resonant nature\cite{Stacy1985} of Raman shift is recognized by the broad band at about 350 \si{cm^{-1}}.
-Recent theoretical\cite{Molina-Sanchez2011} and experimental\cite{Staiger2012} studies on 2D and tubular \ce{WS2} agree this band consists of first order mode $E_{2g}^1$ and second order mode $2LA(M)$, although there is still discrepancy on the exact symmetry assignment, i.e., the presence of $E_{2g}^1(M)$ mode.\cite{Berkdemir2013,Peimyoo2013}.
-The other peak at about 420 \si{cm^{-1}} is assigned to $A_{1g}$ mode in both bulk\cite{Sekine1980} and few layer \ce{WS2}.
-Tubular \ce{WS2} structure can be viewed as rolling up the planar \ce{WS2} sheet, and new Raman features arise subsequently, e.g., a shoulder mode emerges on the low frequency side of $A_{1g}$ mode.
-Theoretical investigation suggests assigning this mode as $B_{1u}$, the Davydov doublet of $A_{1g}$ mode.\cite{Ataca2012} And experimental study confirmed this $B_{1u}$ mode arise from structural disorder of \ce{WS2} layers, and the intensity ratio between $B_{1u}$ and $A_{1g}$ strongly depended on excitation wavelength.\cite{Staiger2012} This study observed $B_{1u}$ mode under 532 nm is much less prominent than that of 632 nm, in consistent with previous reports.\cite{Krause2009,Krause2009a}
+The resonant nature\cite{Stacy1985} of Raman shift was recognized by the broad band at about 350 \si{cm^{-1}}.
+Recent theoretical\cite{Molina-Sanchez2011} and experimental\cite{Staiger2012} studies on 2D and tubular \ce{WS2} agreed that this band consisted of first order mode $E_{2g}^1$ and second order mode $2LA(M)$, although there was still discrepancy on the exact symmetry assignment, i.e., the presence of $E_{2g}^1(M)$ mode.\cite{Berkdemir2013,Peimyoo2013}.
+The other peak at about 420 \si{cm^{-1}} was assigned to $A_{1g}$ mode in both bulk\cite{Sekine1980} and few layer \ce{WS2}.
+Tubular \ce{WS2} structure can be viewed as rolling up the planar \ce{WS2} sheet, and new Raman features arose subsequently, e.g., a shoulder mode emerged on the low frequency side of $A_{1g}$ mode.
+Theoretical investigation suggested assigning this mode as $B_{1u}$, the Davydov doublet of $A_{1g}$ mode.\cite{Ataca2012} And experimental study confirmed this $B_{1u}$ mode arose from structural disorder of \ce{WS2} layers, and the intensity ratio between $B_{1u}$ and $A_{1g}$ strongly depended on excitation wavelength.\cite{Staiger2012} This study observed $B_{1u}$ mode under 532 nm was much less prominent than that of 632 nm, in consistent with previous reports.\cite{Krause2009,Krause2009a}
 % fig Raman TEM
@@
 Rigid analysis of the Raman spectra must be performed to reach solid conclusion.
-Hence, multi-peak Lorentzian fitting was emplpyed on the spectra in Fig.~\ref{fig:ch5ws2ram}e, and the result for 1 layer \ce{WS2} core-shell NW was displayed in Fig.~\ref{fig:ch5ws2ml}.
+Hence, multi-peak Lorentzian fitting was employed on the spectra in Fig.~\ref{fig:ch5ws2ram}e, and the result for 1 layer \ce{WS2} core-shell NW was displayed in Fig.~\ref{fig:ch5ws2ml}.
 The de-convolution peaks compared favorably with original Raman spectrum, and similar operation were used for other three spectra.
-Fig.~\ref{fig:ch5ws2pr} show the layer number dependence on three group of intensity ratios extracted from apparent value, de-convoluted height and integrated intensity, respectively.
-Similar trend was found among all three set of data, though the integrated intensity appears more sensitive towards layer No variation.
-For a qualitative purpose, the apparent intensity ratio $I_{E/A}$ between in-plane E band ($E_{2g}^1+2LA$) and out-of-plane A band ($A_{1g}+B_{1u}$) was used as a quick criterion to distinguish \ce{WS2} few layer.
+Fig.~\ref{fig:ch5ws2pr} show the layer number dependence on three group of intensity ratios extracted from apparent value, de-convoluted height, and integrated intensity, respectively.
+Similar trend was found among all three set of data, though the integrated intensity appeared more sensitive towards layer No variation.
+For a qualitative purpose, the apparent intensity ratio $I_{E/A}$ between in-plane E band ($E_{2g}^1+2LA$) and out-of-plane A band ($A_{1g}+B_{1u}$) was used as a quick criterion to distinguish \ce{WS2} few layer in this study.
 % fig Raman TEM
@@
 \end{figure}
-
-$I_{E/A}$ is then extracted to correlate with layer number variation on tens of core-shell NWs.
-As shown in Fig.~\ref{fig:ch5ws2ramap}, the mapping of \ce{WS2} layer dependent $I_{E/A}$ almost follows the same trend in Fig.~\ref{fig:ch5ws2pr} with some variation attributed to the core-shell NW diameter difference.
+$I_{E/A}$ was then extracted to correlate with layer number variation on tens of core-shell NWs.
+As shown in Fig.~\ref{fig:ch5ws2ramap}, the mapping of \ce{WS2} layer dependent $I_{E/A}$ almost followed the same trend in Fig.~\ref{fig:ch5ws2pr} with some variation attributed to the core-shell NW diameter difference.
 \begin{figure}[htb]
@@
 \end{figure}
-The intensity ratio $I_{E/A}$ decreases monotonically with the increase of \ce{WS2} wall number, a similar trend as observed on 2D few layer \ce{WS2},\cite{Berkdemir2013} and the exact value of $I_{E/A}$ shows modest difference with 2D sheet, which could be attributed to the suspended configuration of current core-shell NWs specimen and the presence of \ce{WO3} core.
-Furthermore, these results indicated that $I_{E/A} > 2$ for single-walled \ce{WS2} core-shell NW, and when the \ce{WS2} wall number is about 3, $I_{E/A}=1$.
-These two values served as a quick determination of \ce{WS2} wall number when the NW is suspended.
+The intensity ratio $I_{E/A}$ decreased monotonically with the increase of \ce{WS2} wall number, a similar trend as observed on 2D few layer \ce{WS2},\cite{Berkdemir2013} and the exact value of $I_{E/A}$ show modest difference with 2D sheet, which could be attributed to the suspended configuration of current core-shell NWs specimen and the presence of \ce{WO3} core.
+Furthermore, these results indicated that $I_{E/A} > 2$ for single-walled \ce{WS2} core-shell NW, and when the \ce{WS2} wall number was about 3, $I_{E/A}=1$.
+These two values served as a quick determination of \ce{WS2} wall number when the NW was suspended.
 
@@
 It has been demonstrated that the optical interference from dielectric environment significantly modified the intensity of Raman scattering from layered \ce{MoS2}, regardless lattice vibration modes.\cite{Li2012} In this work, the author calculated the reflectivity of three different stacking scenarios to estimate the influence of \ce{WO3} and insulating substrate, as shown in Fig.~\ref{fig:ch5ws2stk}.
-It can be concluded that under 532 nm excitation, the \ce{WO3} core shows little influence on the Raman intensity when \ce{WS2} nanotube is suspended in air; whereas the \ce{SiO2}/Si substrates will dramatically enhance the Raman scattering of the core-shell NWs.
-It could be further predicted that current Raman spectra on the core-shell NWs can be used to estimate \ce{WS2} nanotube wall numbers.
+It was concluded that under 532 nm excitation, the \ce{WO3} core show little influence on the Raman intensity when \ce{WS2} nanotube was suspended in air; whereas the \ce{SiO2}/Si substrates dramatically enhanced the Raman scattering of the core-shell NWs.
+It was further predicted that current Raman spectra on the core-shell NWs can be used to estimate \ce{WS2} nanotube wall numbers.
 
@@
 \Gls{pl} was examined with core-shell NWs on insulating \ce{SiO2}-Si substrates.
-A typical Raman spectrum from 160 to 6000 \si{cm^{-1}} is presented in Fig.~\ref{fig:ws2ramall}.
+A typical Raman spectrum from 160 to 6000 \si{cm^{-1}} was presented in Fig.~\ref{fig:ws2ramall}.
 This pattern was acquired on the middle spot of the core-shell NW shown as inset.
@@
 \end{figure}
-Another feature is the presence of three peaks centering at 1860, 3695, and 5500 \si{cm^{-1}}, respectively, where the latter two is probably the secondary and third overtone of the first peak.
-It was confirmed that this three peaks belong to Raman shift instead of PL, since similar peaks were observed using different excitation wavelength of 441 nm and 532 nm.
-The origin of this peak family is still under research, and one possible candidate is the \ce{C=O} bonding, which presumably come from the carbon impurity in tungsten powders as seeds.
-It was also possible that the \ce{C=O} bonding arise from the hydrocarbon contamination attached onto the core-shell NWs.
+Another feature was the presence of three peaks centering at 1860, 3695, and 5500 \si{cm^{-1}}, respectively, where the latter two were probably the secondary and third overtone of the first peak.
+It was confirmed that this three peaks belonged to Raman shift instead of PL, since similar peaks were observed using different excitation wavelength of 441 nm and 532 nm.
+The origin of this peak family was still under research, and one possible candidate was the \ce{C=O} bonding, which presumably came from the carbon impurity in tungsten powders as seeds.
+It was also possible that the \ce{C=O} bonding arose from the hydrocarbon contamination attached onto the core-shell NWs.
 Interestingly, the intensity of this three-peak family attenuated significantly when using 441 nm excitation, as shown in Fig.~\ref{fig:ws2ramblue}.
@@
 \end{figure}
-Three Raman sites were chosen to probe possible layer variation using both 532 and 441 nm, with the naming displayed in the inset of Fig.~\ref{fig:ws2ramall}.
-The Raman patterns are shown in Fig.~\ref{fig:ws2ram3site}a-b.
-The off-resonance profile in Fig.~\ref{fig:ws2ram3site}b shows only two modes, with $E_{2g}^1$ mode at about 357 \si{cm^{-1}} and $A_{1g}$ mode at $418\sim419$ \si{cm^{-1}}.
-In contrast, the on-resonance profile in Fig.~\ref{fig:ws2ram3site}a exhibits much richer spectra.
-The shoulder mode at tip2 spectrum is a manifestation of $B_{1u}$ mode from curved \ce{WS2} layer.
-According to previous analysis, the apparent ratio between in-plane and out-of-plane vibration indicates site tip2 has multi-wall \ce{WS2}, and the other two possibly have few-walled \ce{WS2}.
+Three Raman sites were chosen to probe possible layer variation using both 532 and 441 nm excitation with the naming displayed in the inset of Fig.~\ref{fig:ws2ramall}.
+The Raman patterns were shown in Fig.~\ref{fig:ws2ram3site}a-b.
+The off-resonance profile in Fig.~\ref{fig:ws2ram3site}b show only two modes: $E_{2g}^1$ mode at about 357 \si{cm^{-1}} and $A_{1g}$ mode at $418\sim419$ \si{cm^{-1}}.
+In contrast, the on-resonance profile in Fig.~\ref{fig:ws2ram3site}a exhibited much richer spectra.
+The shoulder mode at tip2 spectrum was a manifestation of $B_{1u}$ mode from curved \ce{WS2} layer.
+According to previous analysis, the apparent ratio between in-plane and out-of-plane vibration indicated site tip2 had multi-wall \ce{WS2}, and the other two possibly had few-walled \ce{WS2}.
 \begin{figure}[htb]
@@
 \end{figure}
-This predication is confirmed by the associated PL measurement displayed in Fig.~\ref{fig:ws2plgreen}.
-Strong luminescent peaks were found at site mid and tip1, and an extremely weak from site tip2.
+This predication was confirmed by the associated PL measurement displayed in Fig.~\ref{fig:ws2plgreen}.
+Strong luminescent peaks were found at site mid and tip1, and an extremely weak peak were found from site tip2.
 The PL peaks centered at 1.958 and 1.934 eV for mid and tip1, respectively.
@@
 A comprehensive understanding of the structure-property relation, which is essential to successful application of nanomaterials, is often hindered by the ensemble averaged characterizations in conventional methods.
-The present work in this chapter, to some extent, circumvents this limitation by leveraging a home-built micromanipulator apparatus to transfer the nanostructures between TEM grids and other desired substrates.
-Considerable insight on the \ce{WO3}-\ce{WS2} core-shell nanostructures was obtained: few-layer, even single-layer tubular \ce{WS2} nanostructure was observed with \ce{WO3} core; layer dependent Raman spectra were studied at on-resonance and off-resonance conditions; the fingerprint of few-layer \ce{WS2} was revealed; photoluminescence from core-shell NWs was identified.
-These results hold great values to the application of \ce{WO3}-\ce{WS2} heterostrucutres in photocatalysis and photoelectrochemical applications.
+The present work in this chapter, to some extent, circumvented this limitation by leveraging a home-built micromanipulator apparatus to transfer the nanostructures between TEM grids and other desired substrates.
+Considerable insight on the \ce{WO3}-\ce{WS2} core-shell nanostructures was obtained: few-layer, even single-layer tubular \ce{WS2} nanostructure was observed with \ce{WO3} core; layer dependent Raman spectra were studied at on-resonance and off-resonance conditions; the fingerprint of few-layer \ce{WS2} was revealed; and photoluminescence from core-shell NWs was identified.
+These results held great values to the application of \ce{WO3}-\ce{WS2} heterostrucutres in photocatalysis and photoelectrochemical applications.
 More important, this technique of TEM-Raman integrated study could be readily applied to a variety of other nanomaterials, therefore opening a broad spectrum for the understanding of the structure-property relation, propelling the potential nano-engineering applications.
@@
 In summary, synthesis of \ce{WO3} and \ce{MoO3} nanostructures based on CVD method were thoroughly investigated in this study.
-Sodium impurity effect in tungsten powder source was revealed and the formation of \ce{Na5W14O44} nanowire was first reported.
-Partially enlightened by this discovery, a new VSS growth mechanism of \ce{MoO3} was found and the growth dynamics was systematically probed.
+Sodium impurity effect in tungsten powder source was revealed, and the formation of \ce{Na5W14O44} nanowire was first reported.
+Partially enlightened by this discovery, a new VSS growth mechanism of \ce{MoO3} was found, and the growth dynamics was systematically probed.
 Comprehensive electron microscopy characterizations were performed on both \ce{WO3} and \ce{MoO3}.
@@
 Besides, seeded growth of \ce{WO3} was demonstrated to be an effective and scalable approach for obtaining single crystalline 1D \ce{WO3} NWs.
-Based on these \ce{WO3} nanowires, \ce{WO3}-\ce{WS2} heterostructure was synthesized using a simple sulfurization process and single-walled \ce{WS2} tubular core-shell nanowire was observed.
+Based on these \ce{WO3} nanowires, \ce{WO3}-\ce{WS2} heterostructure was synthesized using a simple sulfurization process, and single-walled \ce{WS2} tubular core-shell nanowire was observed.
 More important, a TEM-Raman integrated approach was tested aiming at providing a location-resolved map between crystal structure and optical properties.
-As a result, layer number dependence of Raman spectra on \ce{WS2} tubular nanostructure was fingerprinted, and direct bandgap \gls{pl} from \ce{WS2} tubular structure was observed.
-This result indicates a broad space for band structure tuning of \ce{WO3}-\ce{WS2}.
-Moreover, the integration of TEM-Raman serves as an excellent tool to correlate the structure-property relationship for other 1D nanomaterials.
+As a result, layer number dependence of Raman spectra on \ce{WS2} tubular nanostructure was fingerprinted, and direct band gap \gls{pl} from \ce{WS2} tubular structure was observed.
+These results indicated a broad space for band structure tuning of \ce{WO3}-\ce{WS2}.
+Moreover, the integration of TEM-Raman served as an excellent tool to correlate the structure-property relationship for other 1D nanomaterials.
 
 \section{Preliminary results of NaOH WO$_3$ growth}\label{sec:nawo}
-The growth conditions almost remain the same as that of non-seeded \ce{WO3} growth except that the substrate were located at 7.5 inch (refer to page~\pageref{sec:woxnonseed} for details).
-As shown in Fig.~\ref{fig:naohwsem}, dense NWs were observed on \ce{NaOH} treated substrate as revealed by SEM imaging, where the length ranged from 3 to 10 $\mu$m and diameter from 50 to 200 nm.
+The growth conditions almost remained the same as that of the non-seeded \ce{WO3} growth except that the substrate were located at 7.5 inch (refer to page~\pageref{sec:woxnonseed} for details).
+As shown in Fig.~\ref{fig:naohwsem}, dense NWs were observed on \ce{NaOH} treated substrate by SEM imaging, where the length ranged from 3 to 10 $\mu$m and diameter from 50 to 200 nm.
 Compared with the \ce{WO3} NWs in seeded growth, the deposition here also exhibited some plausible plate morphology.
@@
 \end{figure}
-\gls{edx} analysis on the \ce{NaOH} \ce{WO3} sample is shown in Fig.~\ref{fig:naohwedx}.
-Tungsten, oxygen, and sodium elements were detected on the plate growth region, with Na/W atomic ratio of 0.05/1.
+\gls{edx} analysis on the \ce{NaOH} \ce{WO3} sample was shown in Fig.~\ref{fig:naohwedx}.
+Tungsten, oxygen, and sodium elements were detected on the plate growth region with Na/W atomic ratio close to 0.05/1.
 %082713 sample
@@
 \end{figure}
-
-Fig.~\ref{fig:nawxrd} displays the XRD pattern on one representative sample.
+Fig.~\ref{fig:nawxrd} displayed the XRD pattern on one representative sample.
 The phase identification turned out to be ambiguous.
@@
 Micro-Raman scattering spectroscopy was performed on the as-synthesized sample as well.
-As shown in Fig.~\ref{fig:nawram}, five distinct bands were well resolved, with peaks located at 230, 380, 428, 650 and 816 \si{cm^{-1}}, respectively.
+As shown in Fig.~\ref{fig:nawram}, five distinct bands were well resolved with peaks located at 230, 380, 428, 650 and 816 \si{cm^{-1}}, respectively.
 Another small hump was also observed at 946 \si{cm^{-1}}.
-This Raman spectrum deviated from typical features of \ce{WO3},\cite{Salje1975a,Dixit1986} but matched well with \ce{WO3.H2O} in one previous study.\cite{Daniel1987} However, the XRD pattern did not reveal tungsten oxide hydrates feature.\footnote{ICDD PDF 04-011-1708, \emph{a}=7.35 \si{\angstrom}, \emph{b}=12.5 \si{\angstrom}, \emph{c}=7.70 \si{\angstrom}} Further analysis is therefore required to confirm the exact phase of \ce{NaOH} \ce{WO3} NWs.\cite{Azimirad2009a}
+This Raman spectrum deviated from typical features of \ce{WO3},\cite{Salje1975a,Dixit1986} but matched well with \ce{WO3.H2O} in one previous study;\cite{Daniel1987} however, the XRD pattern did not reveal tungsten oxide hydrates feature.\footnote{ICDD PDF 04-011-1708, \emph{a}=7.35 \si{\angstrom}, \emph{b}=12.5 \si{\angstrom}, \emph{c}=7.70 \si{\angstrom}} Further analysis was therefore required to confirm the exact phase of \ce{NaOH} \ce{WO3} NWs.\cite{Azimirad2009a}
 
@@
 TEM specimen was prepared by using carbon grid to slightly scratch the as-grown sample.
-Fig.~\ref{fig:naohwtem} shows the feature of majority NWs.
-The growth direction is difficult to determined due to the presence of streaking in SAED pattern (not shown here), which presumably arises from stacking defaults during the NW growth.
+Fig.~\ref{fig:naohwtem} show the feature of majority NWs.
+The growth direction was difficult to determined due to the presence of streaking in SAED pattern (not shown here), which presumably arose from stacking defaults during the NW growth.
 HRTEM revealed dominant plane spacings of 3.90 and 3.80 \si{\angstrom}, in favorable comparison to the XRD peak at $22.92^\circ$ and $23.66^\circ$.
-It is worth noting that catalyst particles were absent on the tip of NWs during the TEM observation.
+It was worth noting that catalyst particles were absent on the tip of NWs during the TEM observation.
 \begin{figure}[htb]
@@
 \end{figure}
-Based on the above characterizations, it can be concluded that the majority of NW belonged to tungsten oxide, although Na doping cannot be ruled out completely.
+Based on the above characterizations, this thesis concluded that the majority of NW belonged to tungsten oxide, although Na doping cannot be ruled out completely.
 According to the \ce{Na2WO4}-\ce{WO3} phase diagram in Fig.~\ref{fig:nawopd}, the eutectic temperature is ca.
@@
 
-The various growth morphologies found using alkali metal based materials as catalysts demonstrate the proposed \gls{vss} mechanism and transverse mode is a general phenomenon, and broad engineering space could be explored to control the dimension of \ce{MoO3}.
+The various growth morphologies found using alkali metal based materials as catalysts demonstrated the proposed \gls{vss} mechanism and transverse mode was a general phenomenon, and broad engineering space could be explored to control the dimension of \ce{MoO3}.
 As an example, this study further illustrated the tunable growth of \ce{MoO3} nanoribbons on glass substrate.
-Achieving morphology controlled growth of \ce{MoO3} on transparent substrates, e.g., glass, is an important progress towards process integration and device fabrication in photon-energy related applications.
+Achieving morphology controlled growth of \ce{MoO3} on transparent substrates, e.g.
+glass, is an important progress towards process integration and device fabrication in photon-energy related applications.
 
-This thesis studied the effect of temperature, oxygen partial pressure and growth time towards \ce{MoO3} deposition on glass substrates.
-Each factor was divided into two levels, with $T$ at 700 and 800 \si{\degreeCelsius}, \ce{O2} flow at 1 and 10 sccm, and growth time of 15 and 60 min.
+This thesis studied the effect of temperature, oxygen partial pressure, and growth time towards \ce{MoO3} deposition on glass substrates.
+Each factor was divided into two levels with $T$ at 700 and 800 \si{\degreeCelsius}, \ce{O2} flow at 1 and 10 sccm, and growth time of 15 and 60 min, respectively.
 And the morphological variations revealed by SEM imaging were summarized in Table~\ref{tab:mo3glass}.
@@
 The 800-1-15 combination produced dense \ce{MoO3} nanoplate with length about 10 $\mu$m, width $300\sim500$ nm and thickness less than 100 nm, as illustrated in Fig.~\ref{fig:ch4glass}.
-These \ce{MoO3} nanoplates are of high crystalline quality, and could potentially show enhanced photoelectrochemical and electrochromic activities.
+These \ce{MoO3} nanoplates were of high crystalline quality and could potentially show enhanced photoelectrochemical and electrochromic activities.
 %010714r1 sample

### 2015-02-08 ch-tms/tmspart.tex
grammar overhaul, tense, clause, ISBN

@@
 The molecular weight is 249.97 \si{g\per \mole}.
-Almost all natural \ce{WS2} belongs to P63/mmc space group (2H-\ce{WS2}), where $a$ is 3.153 \si{\angstrom}, $c$ is 12.323 \si{\angstrom} (PDF 04-003-4478).
-Two other crystal structures were found in man-made \ce{WS2}, i.e., 1T and 3R, where 3R can be prepared by bromine (Br) chemical vapor transport (CVT) method \cite{Schutte1987} and 1T was generally found in alkaline intercalated \ce{WS2}.\cite{Yang1996a, Enyashin2011} As a reference, the lattice dimensions are summarized in Table~\ref{tab:ms2lattice}.
+Almost all natural \ce{WS2} belongs to P63/mmc space group (2H-\ce{WS2}), where $a$ is 3.153 \si{\angstrom} and $c$ is 12.323 \si{\angstrom} (PDF 04-003-4478).
+Two other crystal structures were found in man-made \ce{WS2}, i.e.
+1T and 3R, where 3R can be prepared by bromine (Br) chemical vapor transport (CVT) method \cite{Schutte1987} and 1T was generally found in alkaline intercalated \ce{WS2}.\cite{Yang1996a, Enyashin2011} As a reference, the lattice dimensions of \ce{MoS2} and \ce{WS2} were summarized in Table~\ref{tab:ms2lattice}.
 %lattice
@@
 \end{table}
-
-\ce{WS2} can also form tubular structures in analog with those of carbon nanotubes.
-The geometrical symmetry group of \ce{WS2} NT has been reported.\cite{Milosevic2000} The basis/lattice vectors $a_1$ and $a_2$ are defined in transition metal plane with equal length $a_0 \approx 3$ \si{\angstrom}.
+\ce{WS2} can also form tubular nanostructures in a similar way as do carbon nanotubes.
+The geometrical symmetry group of \ce{WS2} NTs has been reported.\cite{Milosevic2000} The basis/lattice vectors $a_1$ and $a_2$ are defined in transition metal plane with equal length $a_0 \approx 3$ \si{\angstrom}.
 This monolayered sheet can be rolled up to form a tubular structure when the chiral/translation vector $c = n_1a_1 + n_2a_2$ becomes the circumference of the tube.
@@
 \begin{equation}
-d = \frac{\mid c \mid}{\pi} = \frac{a_0}{\pi}\sqrt{n_1^2 + n_1n_2 + n_2^2}.
+d = \frac{\mid c \mid}{\pi} = \frac{a_0}{\pi}\sqrt{n_1^2 + n_1n_2 + n_2^2}
 \end{equation}
-Notice $a_1 \cdot a_2 = a_1a_2 \cos\pi/3$, where the $\cos\pi/3 \times 2 = 1$. In analog with carbon nanotube, chiral angle $\theta$ is given by
+Note that $a_1 \cdot a_2 = a_1a_2 \cos\pi/3$, where $\cos\pi/3 \times 2 = 1$. In analogy with carbon nanotube, chiral angle $\theta$ is
 \begin{equation}
-\theta = \tan^{-1}\frac{\sqrt{3}n_2}{2n_1 + n_2}.
+\theta = \tan^{-1}\frac{\sqrt{3}n_2}{2n_1 + n_2}
 \end{equation}
-Chiral angles from the interval $[0,\pi/6]$ is sufficient for all possible tubes.
-Tubes $(n,0)$ with zero chiral angle are named zigzag, tubes $(n,n)$ with $\pi/6$ chiral angle are armchair, whereas all others are referred as chiral ones with $\theta \in (0,\pi/6)$.
+Chiral angles from the interval $[0,\pi/6]$ is sufficient for all possible tube structures.
+Tubes $(n,0)$ with zero chiral angle are named as zigzag; tubes $(n,n)$ with $\pi/6$ chiral angle are armchair; consequently, all others are referred as chiral ones with $\theta \in (0,\pi/6)$.
+Fig.~\ref{fig:ch5ntroll} illustrated basis vectors in the atomic plane of unfolded \ce{WS2} and several nanotube indices.
 \begin{figure}[htb]
@@
 \subsection{Review of Synthesis Methods of WS$_2$}
-Shortly after the discovery of \gls{cnt} in 1991,\cite{Iijima1991} its transition metal dichalcogenides (TMDC) counterparts, i.e., \ce{WS2}, was synthesized in 1992.\cite{Tenne1992} In the following decades, other TMDC and several metal oxides nanotubes were demonstrated as well.
-\citeauthor{Rao2003} did an excellent work to review these inorganic nanotubes.\cite{Rao2003} Hence this study just recapitulates the main categories of synthesis methods:
+Shortly after the discovery of \gls{cnt} in 1991,\cite{Iijima1991} its transition metal dichalcogenides (TMDC) counterparts, i.e.
+\ce{WS2}, was synthesized in 1992.\cite{Tenne1992} In the following decades, other TMDC and several metal oxides nanotubes were demonstrated as well.
+\citeauthor{Rao2003} did an excellent work to review these inorganic nanotubes.\cite{Rao2003} Hence, this study recapitulated the main categories of synthesis methods:
 \begin{enumerate}
@@
 \end{enumerate}
-Except the aforementioned methods, another important reaction in CVD domain is
+Except the aforementioned methods, another important reaction in CVD domain was
 \begin{align}
@@
 All these methods can be applied to the growth of TMDC few layer structures, directly or with some modifications.
-Among all the members of TMDC nanotubes, \ce{WS2} and \ce{MoS2} NTs are probably the most well investigated.\cite{Homyonfer1997,Tenne1998,Frey1998,Frey1999,Rothschild2000,Zak2000} The reaction mechanism of \ce{WO3} with \ce{H2}/\ce{H2S} has been thoroughly studied \cite{Feldman1998} and high yield synthesis approach has been established.\cite{Margolin2004} For \ce{WO3} nanoparticles precursor, it was found that the simultaneous reduction and sulfurization is essential for encapsulation of fullerene like \ce{WS2} structures from the oxide nanoparticles.
-During the surfurization process, remaining oxide core is gradually reduced and transformed into an ordered superlattice of $\{ 001 \}$ \gls{cs} planes.
-Further reaction will consume up the \ce{WO_x} core, leaving multi-walled \ce{WS2} NTs only.
-For precursor of \ce{WO3} nanowires, \citeauthor{Feldman1996} proposed that TMDC nanotubes growth began with the reduced \ce{WO3} phases, in particular \ce{W_{18}O_{49}}.\cite{Feldman1996} It is worth noting that \ce{MS2} can be prepared by direct sulfurization from its oxides phase, but reaction \cee{MO3 + Se \rightarrow MSe2} will not proceed unless introducing other reducing agents, such as \ce{H2}.\cite{Tsirlina1998} This fact highlights that sulfur is rather radical at elevated temperature.
+Among all the members of TMDC nanotubes, \ce{WS2} and \ce{MoS2} NTs were probably the most well investigated.\cite{Homyonfer1997,Tenne1998,Frey1998,Frey1999,Rothschild2000,Zak2000} The reaction mechanism of \ce{WO3} with \ce{H2}/\ce{H2S} was thoroughly studied,\cite{Feldman1998} and high yield synthesis approach has been established.\cite{Margolin2004} For \ce{WO3} nanoparticles precursor, it was found that the simultaneous reduction and sulfurization was essential for encapsulation of fullerene like \ce{WS2} structures from the oxide nanoparticles.
+During the sulfurization process, remaining oxide core was gradually reduced and transformed into an ordered superlattice of $\{ 001 \}$ \gls{cs} planes.
+Further reaction consumed the \ce{WO_x} core, leading to multi-walled \ce{WS2} NTs.
+For precursor of \ce{WO3} nanowires, \citeauthor{Feldman1996} proposed that TMDC nanotubes growth began with the reduced \ce{WO3} phases, in particular \ce{W_{18}O_{49}}.\cite{Feldman1996} It is worth noting that \ce{MS2} can be prepared by direct sulfurization from its oxides phase, but reaction \cee{MO3 + Se \rightarrow MSe2} will not proceed unless other reducing agents, e.g.
+\ce{H2}, are used simultaneously.\cite{Tsirlina1998} This fact highlights that sulfur is rather radical at elevated temperature.
 
 \citeauthor{Zhu2000} performed a detailed morphological and structural analysis on \ce{WS2} NTs synthesized using \ce{WO_{3-x}} NWs and \ce{H2S}.\cite{Zhu2000} Sulfur vacancy was found on the outer wall of NT.
-The tips exhibits various structures.
-Open-ended can be observed, more frequently than that in carbon nanotubes (CNTs), which is often sealed.
+The tips exhibited various structures.
+Open-ended \ce{WS2} was observed more frequently than did in carbon nanotubes (CNTs), which was often sealed.
 \citeauthor{Zhu2000} suggested this open-ended tubes resulted from continuous growth on other nanotubes.
-And the closure configuration is rather complicated.
-Flat caps often dominates.
-\citeauthor{Zhu2000} maintained that this oxide-to-sulfides mechanism might apply to closed caps only, not to those open ended tubes.\cite{Zhu2000} TEM diffraction analysis could distinguish the chirality of NTs, as demonstrated by CNT \cite{Zhang1993} and \ce{MoS2}.\cite{MARGULIS1996} \ce{WS2} NT chirality revealed by TEM SAED shows armchair NTs dominates.
-\citeauthor{Sloan1999} investigated tungsten oxides structures incorporated in \ce{WS2}.\cite{Sloan1999} The encapsulated \ce{WO_x} cores often exhibit \ce{W3O8} and \ce{W5O_{14}} phases, both of which belong to the \ce{W_nO_{3n-1}} homogenous series, arising as a result of \gls{cs} planes.\cite{Miyano} Some \ce{WO_x} cores show oxygen vacancy instead of CS planes, leading to prominent streaking in SAED patterns.
-Although high yield growth method of \ce{WS2} has been available, the extent to which one can control the NT configuration is still limited, i.e., single-walled NT has not been routinely synthesized and the electronic properties can only be predicted theoretically.
-\citeauthor{Seifert2000} investigated the electronic structures of \ce{WS2} nanotube using DFT calculation.\cite{Seifert2000} It was found zigzag (n,0) NTs exhibts a direct gap at $\Gamma$ point, whose size increase monotonically with tube diameter, while armchair (n,n) NTs, unlike its metallic counterpart of (n,n) CNT, show indirect band gap increasing with tube diameter.
-\citeauthor{Zibouche2012} reached the same conclusion on \ce{WS2} SWNT.\cite{Zibouche2012} It was also found band gaps of armchair and zigzag NTs increase with diameter, going from values close to bulk and approaching that of  monolayer, and for a given tube diameter, $E_g$ of zigzag NTs are larger than those of armchair NTs.
-This difference presumably vanishes when nanotube diameter exceeds 100 nm.
+And the closure configuration was rather complicated; flat caps often dominated.
+\citeauthor{Zhu2000} maintained that this oxide-to-sulfides mechanism might apply to closed caps only, not to those open ended tubes.\cite{Zhu2000} TEM diffraction analysis could distinguish the chirality of NTs, as demonstrated on CNT\cite{Zhang1993} and \ce{MoS2}.\cite{MARGULIS1996} \ce{WS2} NT chirality revealed by TEM SAED show armchair NTs often dominated.
+\citeauthor{Sloan1999} investigated tungsten oxides structures incorporated in \ce{WS2}.\cite{Sloan1999} The encapsulated \ce{WO_x} cores often exhibited \ce{W3O8} and \ce{W5O_{14}} phases,  a feature of the \ce{W_nO_{3n-1}} homogenous series, arising as a result of \gls{cs} planes.\cite{Miyano} Some \ce{WO_x} cores show oxygen vacancy instead of CS planes, leading to prominent streaking in SAED patterns.
+Although high yield growth method of \ce{WS2} has been available, the extent to which one can control the NT configuration was still limited: single-walled \ce{WS2} NT has not been routinely synthesized, and the electronic properties can only be predicted theoretically.
+\citeauthor{Seifert2000} investigated the electronic structures of \ce{WS2} nanotube using DFT calculation.\cite{Seifert2000} It was found that zigzag (n,0) NTs exhibted a direct gap at $\Gamma$ point, whose size increased monotonically with tube diameter; whereas armchair (n,n) NTs, unlike its metallic counterpart of (n,n) CNT, show indirect band gap increasing with tube diameter.
+\citeauthor{Zibouche2012} reached the same conclusion on \ce{WS2} SWNT.\cite{Zibouche2012} It was also found band gaps of armchair and zigzag NTs increased with diameter, going from values close to bulk and approaching that of monolayer; and for a given tube diameter, $E_g$ of zigzag NTs were larger than those of armchair NTs.
 
-Parallel with the scenario of CNT and graphene, TMDC few layer structures attract intensive research efforts recently.
-These unfolded TMDC nanotubes exhibit many appealing features, i.e., indirect-to-direct band gap transition,\cite{Splendiani2010} valley electronics, and become a promising candidate in energy harvesting, optoelectronics and photocatalytic activity.
-For scientific research purpose, exfoliation by liquid \cite{Smith2011} or mechanical methods \cite{Lee2010a} can provide sufficient materials.
-Yet considering the integration into current microelectronic process, CVD synthesis of thickness controllable 2D TMDC is highly desired, which stills hold the greatest potential for high yield production of \ce{MS2}.
-So this work focuses on reviewing the CVD based methods.
-This study will review literatures to date on both \ce{WS2} films and few layer structures, and highlight several typical investigations using different synthesis methods, as summarized in Table~\ref{tab:tmsgrowth}.
+Parallel with the scenario of CNT and graphene, TMDC few layer structures have attracted intensive research efforts recently.
+These atomic TMDC layers exhibited many appealing features, i.e., indirect-to-direct band gap transition,\cite{Splendiani2010} and became a promising candidate in energy harvesting, optoelectronics, and photocatalytic applications.
+For scientific research purpose, exfoliation by liquid\cite{Smith2011} or mechanical methods\cite{Lee2010a} can provide sufficient materials, yet CVD synthesis of thickness controllable 2D TMDC is stills highly desired, which holds the greatest potential for high yield production of \ce{MS2}.
+So this work focused on reviewing the CVD based methods.
+This study will review literatures to date on both \ce{WS2} films and few layer structures and highlight several typical investigations using different synthesis methods, as summarized in Table~\ref{tab:tmsgrowth}.
 It is important to note that the synthesis of NTs is relevantly independent of substrates, which is in sharp contrast to the scenario of few layer growth.
 The \ce{WS2} nucleation and interaction with substrates play dominant roles in the growth of 2D FL structures.
-Hence it is reasonable to focus on the \ce{WS2} films growth, which presumably could provide valuable insight into the nucleation process on various substrates.
+Hence, it is reasonable to focus on the \ce{WS2} films growth, which presumably could provide valuable insight into the nucleation process on various substrates.
 
 \citeauthor{Lee1994} studied the CVD of \ce{MoS2} by \ce{MoCl5} or \ce{MoF6} and \ce{H2S} in great details.
-Phase diagrams for \ce{Mo-S-Cl-H} and \ce{Mo-S-F-H} system at 1 kPa were simulated.\cite{Lee1994} \citeauthor{Endler1999} also investigated the solid-phase diagram for \ce{Mo-S-Cl-H-Ar} system.\cite{Endler1999} It was found pure \ce{MoS2} was main product when molar ratio of \ce{H2S}-\ce{MoCl5} exceeds 2.
+Phase diagrams for \ce{Mo-S-Cl-H} and \ce{Mo-S-F-H} system at 1 kPa were simulated.\cite{Lee1994} \citeauthor{Endler1999} also investigated the solid-phase diagram for \ce{Mo-S-Cl-H-Ar} system.\cite{Endler1999} It was found pure \ce{MoS2} was main product when molar ratio of \ce{H2S}-\ce{MoCl5} exceeded 2.
 More important, \ce{MoS2} basal plane orientation can be parallel to substrate when the thickness was smaller than 50 nm.
-\citeauthor{Ennaoui1995a} grew tungsten disulfide film using sulfurization of \ce{WO3} under \ce{N2}/\ce{H2} gas flow.\cite{Ennaoui1995a} The composition was found to be \ce{WS_{2.13}}, and the excess of sulfur lead to p-type conductivity.
-XRD peaks ratio is used as a measure of film orientation, which was found higher for film prepared without an intermediate Ni coating.
-\ce{Ni3S2} phase was found and surfactant-mediated epitaxy is proposed.
-\citeauthor{Regula1997} studied the Ni-W-S phase diagram and the role of Ni layer in promoting \ce{WS2} film growth from amorphous \ce{WS3}.\cite{Regula1997} \emph{In-situ} TEM analysis confirmed the formation of \ce{NiS_x} droplets and lateral growth of \ce{WS2} from these droplets.\cite{Regula1998} Recently, it has been shown that direct sulfurization of W coating (20 nm) at 750 \si{\degreeCelsius} on \ce{SiO2}-Si can also produce \ce{WS2} film.\cite{Shanmugam2012a} However, the film is of bulk in nature.
-Previous study of \ce{WS2} growth on various substrates by \citeauthor{Genut1992} was summarized in Table~\ref{tab:ws2subs}.\cite{Genut1992} It was found that the \ce{WS2} nucleate from an amorphous \ce{WS3} phase and the substrate has a critical role in determining both the reaction onset temperature and the texture.
+\citeauthor{Ennaoui1995a} grew tungsten disulfide film using sulfurization of \ce{WO3} under \ce{N2}/\ce{H2} gas flow.\cite{Ennaoui1995a} The composition was found to be \ce{WS_{2.13}}, and the excess of sulfur led to p-type conductivity.
+XRD peaks ratio was used as a measure of film orientation.
+\ce{Ni3S2} phase was found, and surfactant-mediated epitaxy was proposed.
+\citeauthor{Regula1997} studied the Ni-W-S phase diagram and the role of Ni layer in promoting \ce{WS2} film growth from amorphous \ce{WS3}.\cite{Regula1997} \emph{In-situ} TEM analysis confirmed the formation of \ce{NiS_x} droplets and lateral growth of \ce{WS2} from these droplets.\cite{Regula1998} Recently, it has been shown that direct sulfurization of W coating (20 nm) at 750 \si{\degreeCelsius} on \ce{SiO2}-Si can also produce \ce{WS2} film.\cite{Shanmugam2012a} However, the film was of bulk in nature.
+Previous study of \ce{WS2} growth on various substrates by \citeauthor{Genut1992} was summarized in Table~\ref{tab:ws2subs}.\cite{Genut1992} It was found that the \ce{WS2} nucleated from an amorphous \ce{WS3} phase and the substrate had a critical role in determining both the reaction onset temperature and the texture.
 The adhesion of tungsten to quartz was found to be much stronger than to glass.
-And oxygen-containing species such as \ce{H2O} or OH tend to cause \ce{WS2} basal plane perpendicular to substrate.
+And oxygen-containing species, such as \ce{H2O} or OH, tended to cause \ce{WS2} basal plane perpendicular to substrate.
 % WS2 films
@@
 
-For \ce{MoS2}, the reaction mechanism of \ce{MoO3} to \ce{MoS2} was studied by \citeauthor{Weber1996}.\cite{Weber1996} This study presumably provided guidelines for the recent syntheses of \ce{MoS2} by sulfurization of \ce{MoO3}.\cite{Lin2012,Lee2012b,Liu2012a,Najmaei2013} Similar studies on sulfurization of \ce{WO3.H2O} to \ce{WS2} and decomposition of \ce{(NH4)2WO2S2} were also reported.\cite{VanderVlies2002,VanderVlies2002a} In combination with the knowledge from \ce{WS2}, this thesis compares those insight from several recent reports on \ce{WS2} FL.
-\citeauthor{Cong2013} prepared monolayer \ce{WS2} on 300 nm \ce{SiO2}-Si by sulfurization of \ce{WO3} powders in a one-end sealed tube.\cite{Cong2013} It was suggested that pre-cleaning the inner tube by IPA and DI water could effectively increase the pressure of vapor source.
-This observation probably arise from the reduction of \ce{WO3} assisted by IPA and water residuals, or due to the possible presence of \ce{H2S}.
-Intermediate phase \ce{WO_yS_{2-y}} and \ce{WS_{2+x}} is proposed in the growth mechanism.
-The apex of triangles could be active site of nucleation, \ce{WS_{2+x}} formation is confirmed by secondary ion mass spectrometry.
-Possible thick \ce{WS_{2+x}} flakes decompose subsequently, leading to \gls{ml} \ce{WS2}.
-The substrates are thoroughly cleaned.
+For \ce{MoS2}, the reaction mechanism of \ce{MoO3} to \ce{MoS2} was studied by \citeauthor{Weber1996}.\cite{Weber1996} This study presumably provided guidelines for the recent syntheses of \ce{MoS2} by sulfurization of \ce{MoO3}.\cite{Lin2012,Lee2012b,Liu2012a,Najmaei2013} Similar studies on sulfurization of \ce{WO3.H2O} to \ce{WS2} and decomposition of \ce{(NH4)2WO2S2} were also reported.\cite{VanderVlies2002,VanderVlies2002a} In combination with the knowledge from \ce{WS2}, this thesis compared those insight from several recent reports on \ce{WS2} FL.
+\citeauthor{Cong2013} prepared monolayer \ce{WS2} on 300 nm \ce{SiO2}-Si by sulfurization of \ce{WO3} powders in a one-end sealed tube.\cite{Cong2013} It was suggested that pre-cleaning the inner tube by \gls{ipa} and DI water could effectively increase the pressure of vapor source.
+This observation probably arose from the reduction of \ce{WO3} assisted by IPA and water residuals, or due to the possible presence of \ce{H2S}.
+Intermediate phase \ce{WO_yS_{2-y}} and \ce{WS_{2+x}} was proposed in the growth mechanism.
+The apex of triangles could be active site of nucleation, and \ce{WS_{2+x}} formation was confirmed by secondary ion mass spectrometry.
+Possible thick \ce{WS_{2+x}} flakes decomposed subsequently, leading to \gls{ml} \ce{WS2}.
+The substrates were thoroughly cleaned.
 It was mentioned that separate sulfur heating improved the PL uniformity.
-Sulfurization mechanism study of \ce{WO3} suggested \ce{W^{6+}} cannot be directly reduce to \ce{W^{4+}} in \ce{WS2}.\cite{VanderVlies2002,VanderVlies2002a} Tungsten oxysulfides was necessary as the intermediate phase.
+Sulfurization mechanism study of \ce{WO3} suggested \ce{W^{6+}} cannot be directly reduce to \ce{W^{4+}} in \ce{WS2}.\cite{VanderVlies2002,VanderVlies2002a} Tungsten oxysulfides was necessary as an intermediate phase.
 
 \citeauthor{Peimyoo2013} prepared \ce{WS2} on \ce{SiO2}-Si using \ce{WO3} powder and sulfur at 800 \si{\degreeCelsius}, aiming at the light emission studies to clarify several contradictory reports.\cite{Peimyoo2013} Uniform PL intensity was found on the triangular \ce{WS2} flakes, in contrast to previous edge enhanced PL\cite{Berkdemir2013}.
-Raman spectra (532 nm) fit includes $E_{2g}^1(M)$ mode at 343 cm$^{-1}$, according to the phonon dispersion calculation \cite{Molina-Sanchez2011} and experimental observation.\cite{Zeng2013a,Zhao2013,Lee2013} However, none of these experimental reports specifically mentioned $E_{2g}^1(M)$ mode.
-Tentative assignments of multi-phonon bands are summarized in supporting information of Ref.\cite{Zhao2013}.
+Raman spectra (532 nm) fit included $E_{2g}^1(M)$ mode at 343 cm$^{-1}$, according to the phonon dispersion calculation \cite{Molina-Sanchez2011} and experimental observation.\cite{Zeng2013a,Zhao2013,Lee2013} However, none of these experimental reports specifically mentioned $E_{2g}^1(M)$ mode.
+Tentative assignments of multi-phonon bands were summarized in supporting information of Ref.\cite{Zhao2013}.
 As to the growth setup, similar tube furnace as in Ref \cite{VanderZande2013} and \cite{Najmaei2013} was used.
-To gain additional wisdom on \ce{MoS2} growth, this thesis thus summarizes the growth strategies in Ref \cite{VanderZande2013} and \cite{Najmaei2013} as following.
-\citeauthor{VanderZande2013} prepared \ce{MoS2} on 285 nm \ce{SiO2}-Si using \ce{MoO3} and S as precursors.\cite{VanderZande2013} In contrast to the seeding method adopted in Refs.\cite{Lee2013,Lee2012b}, \citeauthor{VanderZande2013} stressed the importance of carefully cleaned substrates\footnote{acetone, 2 h in \ce{H2SO4} and \ce{H2O2} (3:1) and 5 min oxygen plasma} and minimum exposure of precursor to air.\footnote{APCVD, 105 \si{\degreeCelsius} for 4 h, 700 \si{\degreeCelsius} hold for 5 min, and 10 sccm \ce{N2} within 2 in tube.
-rapid cooling from 570 \si{\degreeCelsius}} Dirty substrates or old precursors will lead to hexagonal, 3-point star or irregular polycrystalline structures.
-The growth setup is similar to those in Ref.\cite{Lee2012b}.
-The substrate and \ce{MoO3} source distance is critical in determining the growth density.
-The synthesis strategy in Refs.\cite{Lee2013,Lee2012b} is briefly mentioned as well, where PTAS treated substrate is found to promote the deposition, while KCl treated substrates did not, and small carrier gas flow is preferred (1 sccm \ce{N2}).
-It was also noted that the \ce{MoS2} flakes morphology seems more uniform in Ref\cite{VanderZande2013} than that in Ref\cite{Lee2012b}.
+To gain additional wisdom on \ce{MoS2} growth, this thesis thus summarized the growth strategies in Ref \cite{VanderZande2013} and \cite{Najmaei2013} as following.
+\citeauthor{VanderZande2013} prepared \ce{MoS2} on 285 nm \ce{SiO2}-Si using \ce{MoO3} and S as precursors.\cite{VanderZande2013} In contrast to the seeding method adopted in Refs.\cite{Lee2013,Lee2012b}, \citeauthor{VanderZande2013} stressed the importance of carefully cleaned substrates\footnote{acetone, 2 h in \ce{H2SO4} and \ce{H2O2} (3:1) and 5 min oxygen plasma} and minimum exposure of precursor to air.\footnote{APCVD, 105 \si{\degreeCelsius} for 4 h, 700 \si{\degreeCelsius} hold for 5 min, and 10 sccm \ce{N2} within 2 inch tube.
+rapid cooling from 570 \si{\degreeCelsius}} Dirty substrates or old precursors led to hexagonal, 3-point star or irregular polycrystalline structures.
+The growth setup was similar to those in Ref.\cite{Lee2012b}.
+The substrate and \ce{MoO3} source distance was critical in determining the growth density.
+The synthesis strategy in Refs.\cite{Lee2013,Lee2012b} was briefly mentioned as well, where \gls{ptas} treated substrate was found to promote the deposition, while KCl treated substrates did not; small carrier gas flow was preferred (1 sccm \ce{N2}).
+It was also noted that the \ce{MoS2} flakes morphology seemed more uniform in Ref\cite{VanderZande2013} than that in Ref\cite{Lee2012b}.
 On the other hand, \citeauthor{Najmaei2013} also demonstrated \ce{MoS2} FL growth by sulfurization of \ce{MoO3} nanoribbons,\cite{Najmaei2013} which was applied by dispersion and meant to control the source amount.
-It was found the diffusion of vapor \ce{MoO_{3-x}} is rate-limiting step in \ce{MoS2} growth.
-This means the amount of source is critical in successful synthesis.
-The nucleation event is more frequently observed at substrate edges, scratches or rough surface.
-Step edges is then intentionally created to facilitate the nucleation.
-As to the growth dynamics, it was postulated the oxysulfides (\ce{MoOS2} Raman spectra found), as intermediate phase, diffuse across the bare substrates and form triangular domains upon further sulfurization.
-The optimal growth conditions are 800-850 \si{\degreeCelsius}, 700 Torr, and sufficient sulfur.
-This thesis then conjectures that the substrate cleaning in Ref.\cite{Peimyoo2013} should be similar to that in Ref.\cite{VanderZande2013}, yet the source-to-substrate layout and growth pressure are still needed to be optimized with respect to the home-built CVD apparatus.
+It was found the diffusion of vapor \ce{MoO_{3-x}} was the rate-limiting step in \ce{MoS2} growth.
+This indicated the amount of source was critical in successful synthesis.
+The nucleation event was more frequently observed at substrate edges, scratches, or rough surface.
+Step edges was then intentionally created to facilitate the nucleation.
+As to the growth dynamics, it was postulated the oxysulfides (\ce{MoOS2} Raman spectra found), as intermediate phase, diffused across the bare substrates and formed triangular domains upon further sulfurization.
+The optimal growth conditions were 800-850 \si{\degreeCelsius}, 700 Torr, and sufficient sulfur.
 
-\citeauthor{Zhang2013h} synthesized \ce{WS2} on sapphire (0001) using \ce{WO3} powder and sulfur as precursor under 900 \si{\degreeCelsius}.\cite{Zhang2013h} Ar slightly mixed with \ce{H2} is used to tailor the shape of \ce{WS2} flakes.
-It was found the source substrate distance plays an important role in determining the morphology of the as-grown flakes.\footnote{There is a lattice mismatch between \ce{Al2O3} (4.785 \si{\angstrom}) and \ce{WS2} (3.153 \si{\angstrom})} The edge termination is not well studied.
-Raman spectra indicate a universal down-shift of $A_{1g}$ peak (1L from 418 \si{cm^{-1}} on \ce{SiO2}-Si to 416.4 \si{cm^{-1}} on sapphire).
-PL signal of \ce{WS2} on \ce{SiO2}-Si is stronger than that on sapphire.
-The visibility of \ce{WS2} on \ce{Al2O3} is poor.
-No 1L vs nL statistic is available.
-FET on/off ratio is about 100, indicating low mobility.
-The other conditions includes 880 \si{\degreeCelsius}, 90 mm source-to-substrate distance, 1 in quartz tube.
-The growth conditions are probably adopted from Ref.\cite{Huanga2013}.
+\citeauthor{Zhang2013h} synthesized \ce{WS2} on sapphire (0001) using \ce{WO3} powder and sulfur as precursor under 900 \si{\degreeCelsius}.\cite{Zhang2013h} Ar slightly mixed with \ce{H2} was used to tailor the shape of \ce{WS2} flakes.
+It was found the source substrate distance played an important role in determining the morphology of the as-grown flakes.\footnote{There is a lattice mismatch between \ce{Al2O3} (4.785 \si{\angstrom}) and \ce{WS2} (3.153 \si{\angstrom})} The edge termination was not well studied.
+Raman spectra indicated a universal down-shift of $A_{1g}$ peak (1L from 418 \si{cm^{-1}} on \ce{SiO2}-Si to 416.4 \si{cm^{-1}} on sapphire).
+PL signal of \ce{WS2} on \ce{SiO2}-Si was stronger than that on sapphire.
+The visibility of \ce{WS2} on \ce{Al2O3} was poor.
+FET on/off ratio was about 100, indicating low carrier mobility.
+The other conditions included 880 \si{\degreeCelsius}, 90 mm source-to-substrate distance, and 1 inch quartz tube.
+The growth conditions were probably adopted from Ref.\cite{Huanga2013}.
 
-It is worth noting the flake sizes on sapphire\cite{Zhang2013h} seems larger than that on \ce{SiO2}/Si,\cite{Peimyoo2013} either due to the nucleation barrier difference or the amount of growth vapor and growth time.
-The flake sizes in Ref.\cite{Cong2013} is not quite uniform, though it could be even larger than that on sapphire from Ref.\cite{Zhang2013h}.
-One common feature of aforementioned investigations is growth occurs on bare substrates and no catalyst or seeding promoter is employed.
-While there is another synthesis approach\cite{Lee2013,Ling2014} exclusively focusing on using seeding promoter.
+It is worth noting the flake sizes on sapphire\cite{Zhang2013h} seemed larger than that on \ce{SiO2}/Si,\cite{Peimyoo2013} either due to the nucleation barrier difference or the amount of growth vapor and growth time.
+The flake sizes in Ref.\cite{Cong2013} was not quite uniform, though it could be even larger than that on sapphire from Ref.\cite{Zhang2013h}.
+One common feature of aforementioned investigations was growth occurred on bare substrates and no catalyst or seeding promoter was employed.
+While there is another synthesis approach\cite{Lee2013,Ling2014} exclusively focused on using seeding promoter.
 \citeauthor{Lee2013} obtained \ce{MoS2} and \ce{WS2} FL on PTAS-treated substrates (\ce{C24H12K4O8}), where tiny ($\sim 200$ nm) seeds were found under AFM.
-More recently, \citeauthor{Ling2014} systemically investigated the role of seeding promoter in facilitating the nucleation of \ce{MoS2} monolayer.\cite{Ling2014} It was found various aromatic molecules are effective yet inorganic nanoparticles are not.
-The mechanism of thin film growth depends on the surface energy and chemical potentials of the deposited layers and their substrates.
-Layer growth is preferred when surface adhesive force is stronger than adatoms cohesive force.
+More recently, \citeauthor{Ling2014} systemically investigated the role of seeding promoter in facilitating the nucleation of \ce{MoS2} monolayer.\cite{Ling2014} It was found various aromatic molecules were effective yet inorganic nanoparticles were not.
+The mechanism of thin film growth depended on the surface energy, chemical potentials of the deposited layers, and their substrates.
+Layer growth was preferred when surface adhesive force was stronger than adatoms cohesive force.
 Seeding promoter probably lowered the surface energy by wetting, thus provided heterogenous nucleation sites.
-Continuous \ce{MoS2} \gls{ml} is obtained by evaporating \ce{F16CuPc} of 2 \si{\angstrom} on desired receiving substrates.
+Continuous \ce{MoS2} \gls{ml} was obtained by evaporating \ce{F16CuPc} of 2 \si{\angstrom} on desired receiving substrates.
 In each growth, about $10^{-10}$ mol PTAS was applied onto \ce{SiO2}-Si, which was rendered hydrophilic and gentle gas blow to distribute the solution evenly.
@@
 The previous Raman efforts on \ce{MS2} film, especially the one using resonant conditions, provided critical insight into the electronic structure and lattice dynamics of these TMDC layered materials.
-A comparison of Raman between TMDC nanotubes and FL structures is given.
-For \ce{WS2} NTs, focus is on the asymmetry of $A_{1g}$ mode and its origin.
-And for \ce{WS2} FL structures, layer number dependent fingerprint is summarized, and some attempts on analysis the resonant Raman profiles of \ce{WS2} are made.
+A comparison of Raman between TMDC nanotubes and FL structures was given.
+For \ce{WS2} NTs, the focus was on the asymmetry of $A_{1g}$ mode and its origin.
+And for \ce{WS2} FL structures, layer number dependent fingerprint was summarized, and some attempts on analysis the resonant Raman profiles of \ce{WS2} were made.
 It is worth noting that Raman technique proves to be extreme useful in characterizing CNT and graphene, i.e., tube diameter by assigning the RBMs (radial breathing modes) and G peaks position.\cite{Bonaccorso2013} And Raman spectroscopy also qualifies as an excellent tool to monitor tensile features of TMDC in both 2D and tubular forms.\cite{Tang2013}
@@
 Before discussing the Raman spectra features, this thesis briefly recapitulates some symmetry notations and vibration modes.
-\ce{MoS2} is used as an example, and those definitions apply to \ce{WS2} as well.
+\ce{MoS2} was used as an example, and those definitions applied to \ce{WS2} as well.
 Hexagonal \ce{MoS2} belongs to space group $D_{6h}^4$, and the repeat unit in $c$ axis contains two layers, where sulfur atoms in one layer are directly above the molybdenum atoms in adjacent layers, which is often referred as 2H-\ce{MoS2}.
 Group theory predicts two infrared- and four Raman-active modes for 2H-\ce{MoS2}, which are mutually exclusive when the center of inversion is present.
-First it should be emphasized that in few layer structures, \ce{MoS2} with odd layers belong to different space group from that of even layers.
+First it should be emphasized that in few layer structures, \ce{MoS2} with odd layers belongs to different space group from that of even layers.
 Bulk MoS$_2$ and 2L-MoS$_2$ belong to the space group P6$_3$/$_{mmc}$ (point group D$_{6h}$).
@@
 The atoms site groups are a subgroup of the crystal factor group.
-The correlation of the Mo site group D$_{3h}$, S site group C$_{3v}$, and factor group D$_{6h}$ allows one to derive the following irreducible representations for the 18 normal vibration modes at $\vec{\Gamma}$: $\vec{\Gamma}$= $A_{1g}+2A_{2u}+2B_{2g}+B_{1u}+E_{1g}+2E_{1u}+2E_{2g}+E_{2u}$, where $A_{2u}$ and $E_{1u}$ are translational acoustic modes, $A_{1g}$, $E_{1g}$ and $E_{2g}$ are Raman active, $A_{2u}$ and $E_{1u}$ are infrared (IR) active.
+The correlation of the Mo site group D$_{3h}$, S site group C$_{3v}$, and factor group D$_{6h}$ allows one to derive the following irreducible representations for the 18 normal vibration modes at $\vec{\Gamma}$: $\vec{\Gamma}$= $A_{1g}+2A_{2u}+2B_{2g}+B_{1u}+E_{1g}+2E_{1u}+2E_{2g}+E_{2u}$, where $A_{2u}$ and $E_{1u}$ are translational acoustic modes, $A_{1g}$, $E_{1g}$ and $E_{2g}$ are Raman active, and $A_{2u}$ and $E_{1u}$ are infrared (IR) active.
 As a contrast, 1L-MoS$_2$ has $D_{3h}$ symmetry with three atoms per unit cell.
 The irreducible representation of $D_{3h}$ gives: $\vec{\Gamma}$= $2A_2^{''}$+$A_1^{'}$+$2E^{'}$+$E^{''}$, with $A_2^{''}$ and $E^{'}$ acoustic modes, $A_2^{''}$ IR active, $A_1^{'}$ and $E^{''}$ Raman active, and the other $E^{'}$ both Raman and IR active (See Fig.~\ref{fig:ws2ramsch}).
-NL-MoS$_2$ has 9N-3 optical modes: 3N-1 are vibrations along the c axis, and 3N-1 are doubly degenerate in-plane vibrations.
-For rigid-layer vibrations, there are N-1 layer breathing modes (LBMs) along the c axis, and N-1 doubly degenerate shear modes perpendicular to it.
+NL-MoS$_2$ has $9N-3$ optical modes: $3N-1$ are vibrations along the $c$ axis, and $3N-1$ are doubly degenerate in-plane vibrations.
+For rigid-layer vibrations, there are $N-1$ layer \glspl{lbm} along the $c$ axis, and $N-1$ doubly degenerate shear modes perpendicular to it.
 When N is even, there are 0 Raman active LBMs and $\frac{N}{2}$ doubly degenerate shear modes.
-When N is odd, there are $\frac{N-1}{2}$ LBMs and N-1 doubly degenerate shear modes.\cite{Wieting1971,Zhang2013e} This discussion can be visualized in Table~\ref{tab:tmslattice}.
+When N is odd, there are $\frac{N-1}{2}$ LBMs and $N-1$ doubly degenerate shear modes.\cite{Wieting1971,Zhang2013e} This discussion can be visualized in Table~\ref{tab:tmslattice}.
 
@@
 \end{table}
-The $E$ type phonon branches correspond to in-plane normal modes, while the $A$ type phonons result from out-of-plane vibrations.
-$A_{1g}$ mode is an out-of-plane vibration involving only the S atoms while the $E_{2g}^1$ mode involves in-plane displacement of transition metal and S atoms.
+The $E$ type phonon branches correspond to in-plane normal modes; and the $A$ type phonons result from out-of-plane vibrations.
+$A_{1g}$ mode is an out-of-plane vibration involving only the S atoms, while the $E_{2g}^1$ mode involves in-plane displacement of transition metal and S atoms.
 The $E_{2g}^2$ mode is a shear mode corresponding to the vibration of two rigid layers against
@@
 The $E_{1g}$ mode, which is an in-plane vibration of only the S atoms, is forbidden in the backscattering Raman configuration.
-In 2H-type TMDC, the $A_{1g}$ mode is more sensitive to electrostatic doping, while $E_{2g}^1$ mode is more sensitive to strain, in which the FWHM of the peaks are indicator of external force quantity.\cite{Zhao2013}
+In 2H-type TMDC, the $A_{1g}$ mode is more sensitive to electrostatic doping; whereas $E_{2g}^1$ mode is more sensitive to strain, in which the FWHM of the peaks are indicator of external force quantity.\cite{Zhao2013}
 
@@
 
-Lattice vibration of natural \ce{MoS2} crystal was studied by \citeauthor{Wieting1971} using infrared and Raman spectroscopy.\cite{Wieting1971} It was found the $E_{1u}$ IR mode and one $E_{2g}$ Raman mode are nearly degenerate in energy.
-15 optical modes are allowed assuming 6 atoms in primitive cell.
-Refractive indices from reflectivity measurement were $n_0$= 3.9, $n_e$ = 2.5.
-\citeauthor{Stacy1985} studied \ce{MoS2} and \ce{WS2} Raman spectra using lasing energy close to the absorption edges.\cite{Stacy1985} Second order scattering from phonon with nonzero momentum is used to explain the rich Raman spectra.
-\citeauthor{Sourisseau1991} investigated the resonant Raman profiles in 2H-\ce{WS2} using ten different excitation wavelengths.\cite{Sourisseau1991} Dramatic intensity variation at 352 \si{cm^{-1}} was observed, which is assume to be of two-phonon signal nature, and corresponds to an overtone or combination band of phonons with non-zero momenta contributing to indirect gap absorption edge.
+Lattice vibration of natural \ce{MoS2} crystal was studied by \citeauthor{Wieting1971} using infrared and Raman spectroscopy.\cite{Wieting1971} It was found the $E_{1u}$ IR mode and one $E_{2g}$ Raman mode were nearly degenerate in energy.
+Refractive indices from reflectivity measurement were $n_0$= 3.9 and $n_e$ = 2.5.
+\citeauthor{Stacy1985} studied \ce{MoS2} and \ce{WS2} Raman spectra using lasing energy close to the absorption edges.\cite{Stacy1985} Second order scattering from phonon with nonzero momentum was used to explain the rich Raman spectra.
+\citeauthor{Sourisseau1991} investigated the resonant Raman profiles in 2H-\ce{WS2} using ten different excitation wavelengths.\cite{Sourisseau1991} Dramatic intensity variation at 352 \si{cm^{-1}} was observed, which was assumed to be of two-phonon signal nature and corresponded to an overtone or combination band of phonons with non-zero momenta contributing to indirect gap absorption edge.
 \citeauthor{Sourisseau1991} assigned this phonon with non-zero momenta as $LA(K_5)$ type (\gls{la}).
-The enhancement of the total Raman cross section at excitonic resonance in which excitons serve as the intermediate state is stronger compared to that of interband resonance.
-The strong enhancement at excitonic resonance is attributed to the characteristics of excitons in layered materials such as large binding energy, enhanced oscillator strength, and small damping constant.\cite{Zhao2013} \citeauthor{Chung1998} grew \ce{WS2} film using \ce{W(CO)6} and \ce{H2S} precursor.\cite{Chung1998} Raman spectra ($\lambda=632 nm$) on films with non-parallel orientation revealed the presence of shoulder mode under $A_{1g}$, which is assigned to \gls{la} and \gls{ta} phonon coupling.
-This coupling process stems from disorder-activated zone boundary phonons.
+The enhancement of the total Raman cross section at excitonic resonance in which excitons served as the intermediate state was stronger compared to that of interband resonance.
+The strong enhancement at excitonic resonance was attributed to the characteristics of excitons in layered materials such as large binding energy, enhanced oscillator strength, and small damping constant.\cite{Zhao2013} \citeauthor{Chung1998} grew \ce{WS2} film using \ce{W(CO)6} and \ce{H2S} precursor.\cite{Chung1998} Raman spectra ($\lambda=632 nm$) on films with non-parallel orientation revealed the presence of shoulder mode under $A_{1g}$, which was assigned to \gls{la} and \gls{ta} phonon coupling.
+This coupling process stemmed from disorder-activated zone boundary phonons.
 A further discussion on this non-symmetric feature of $A_{1g}$ mode will be continued in section~\ref{sec:ntram}.
@@
 
-Raman technique has also provided much insight into the few layer \ce{MS2}.
-\ce{MS2} layer numbers are readily identified by the Raman shift distance between $A_{1g}$ and $E_{2g}^1$ mode for \ce{MoS2}\cite{Buscema2013} and \ce{WS2}.\cite{Berkdemir2013} Yet due to the relative small shift of $A_{1g}$ mode and little shift of $E_{2g}^1$ mode in \ce{WS2} FL, the frequencies distance might not qualify as an unambiguous way to distinguish layer numbers.
-Yet the resonant Raman profile on \ce{WS2} exhibit unique features between the intensity of 2LA and $A_{1g}$ mode,\cite{Berkdemir2013,Zhao2013} which provide another routine to assure the monolayer presence.
+Raman technique has provided much insight into the few layer \ce{MS2}.
+\ce{MS2} layer numbers were readily identified by the Raman shift distance between $A_{1g}$ and $E_{2g}^1$ mode for \ce{MoS2}\cite{Buscema2013} and \ce{WS2}.\cite{Berkdemir2013} Yet due to the relative small shift of $A_{1g}$ mode and little shift of $E_{2g}^1$ mode in \ce{WS2} FL, the frequencies distance might not qualify as an unambiguous way to distinguish layer numbers.
+The resonant Raman profile on \ce{WS2} exhibited unique features between the intensity of 2LA and $A_{1g}$ mode,\cite{Berkdemir2013,Zhao2013} which provided another routine to assure the monolayer presence.
 However, this thesis notices some discrepancy in de-convolution of \ce{WS2} resonant profile between 300 and 400 cm$^{-1}$, i.e., the presence of $E_{2g}^1(M)$ mode at about 344 cm$^{-1}$.\cite{Peimyoo2013,Cong2013,Berkdemir2013} Rigid assignments of this mode still requires further theoretical\cite{Ataca2012} and experimental efforts.
 In addition, \citeauthor{M2013} reported temperature dependent of 1L \ce{WS2}.\cite{M2013} When the temperature increase from 77 K to 623 K, $A_{1g}$ shift from 420 to 416.5 cm$^{-1}$.
-Interestingly in this report 2LA/$A_{1g}$ ratio (514 nm excitation) seems less than unit.
-The spectra were obtain from mechanically exfoliated \ce{WS2} lying on 300 nm \ce{SiO2}-Si substrate.
-Moreover, The $A_{1g}$ and $E_{2g}^1$ intensities ratio exhibit reverse behaviors under 532 and 632 nm excitation.
-This is caused by the different cross-section enhancement for a specific excitation condition.
-The A and B excitonic absorption in \ce{WS2} mainly arises from the $d_{xy}$ and $d_{x^2 - y^2}$ states to $d_{z^2}$ states of tungsten atoms.
-Thus, electrons excited by 633 nm laser have a character of tungsten $d_{z^2}$ orbitals aligned along the $c$ axis perpendicular to \ce{WS2} basal plane.
+Interestingly, 2LA/$A_{1g}$ ratio (514 nm excitation) seemed less than unit in this report.
+The spectra were obtained from mechanically exfoliated \ce{WS2} lying on 300 nm \ce{SiO2}-Si substrate.
+Moreover, The $A_{1g}$ and $E_{2g}^1$ intensities ratio exhibited reverse behaviors under 532 and 632 nm excitation.
+This was caused by the different cross-section enhancement for a specific excitation condition.
+The A and B excitonic absorption in \ce{WS2} mainly arose from the $d_{xy}$ and $d_{x^2 - y^2}$ states to $d_{z^2}$ states of tungsten atoms.
+Thus, electrons excited by 633 nm laser had a character of tungsten $d_{z^2}$ orbitals aligned along the $c$ axis perpendicular to \ce{WS2} basal plane.
 Since $A_{1g}$ mode involves out of plane displacement along $c$ axis, $A_{1g}$ phonons could couple more strongly with $d_{z^2}$ states than that of $E_{2g}^1$ phonons.
-As a result, $A_{1g}$ mode is stronger than $E_{2g}^1$ mode at 633 nm resonance.\cite{Zhao2013} However, the reverse effect for 532 nm excitation could not be well explained using the above argument.
+As a result, $A_{1g}$ mode was stronger than $E_{2g}^1$ mode at 633 nm resonance.\cite{Zhao2013} However, the reverse effect for 532 nm excitation could not be well explained using the above argument.
 This may be caused by electron-phonon coupling with other inter-band transition electrons.
@@
 The dependence of wavenumbers and their displacement on chirality and diameter were discussed.
-The calculation method enables studying lattice dynamics with NT diameter up to 50 nm.
+The calculation method enabled studying lattice dynamics with NT diameter up to 50 nm.
 The chiral vector $(n_1, n_2)$ is defined within the molybdenum plane.
@@
 \citeauthor{Dobardzic2006} theoretically presented Raman scattering of any polarization on \gls{swnt} of \ce{WS2} and their dependence on diameter (1-20 nm) and chiral angle.
-The author assigned 351 cm$^{-1}$ as $E_u$ for \ce{WS2} NT.\cite{Dobardzic2006} \citeauthor{Ghorbani-Asl2013} discuss the electronic and vibrational properties for large diameter \ce{WS2} NTs.\cite{Ghorbani-Asl2013} Single-walled NT is approximated by 1H monolayer and others by 2H bulk structure.
+The author assigned 351 cm$^{-1}$ as $E_u$ for \ce{WS2} NT.\cite{Dobardzic2006} \citeauthor{Ghorbani-Asl2013} discussed the electronic and vibrational properties for large diameter \ce{WS2} NTs.\cite{Ghorbani-Asl2013} Single-walled NT was approximated by 1H monolayer and others by 2H bulk structure.
 It was found that large-diameter nanotubes can be approximated with layered systems as their properties should be nearly the same at the scale.
-Only hypothetical SWNTs, and possibly MWNTs with alternating layer compositions, may show direct band gaps.
+Only hypothetical SWNTs and possibly MWNTs with alternating layer compositions, may show direct band gaps.
 Slight mechanical deformation of the SWNTs would result in a change of the direct band gap back to the indirect one, located between $\Gamma$ and $K$ high-symmetry points, similarly to the monolayers.
 As for 2D materials, quantum confinement to single-walled tubes would result in direct band-gap semiconductors with $\Delta$ occurring at the $K$ point.
-Single-walled tubes exhibit slightly softer out-of-plane $A'$ and stronger in-plane $E'$ modes.
-Those results indicate that the weak interlayer interactions in MS$_2$ materials cannot be associated with the van der Waals interactions only, but most probably with Coulomb electrostatic interactions as well.
+Single-walled tubes exhibited slightly softer out-of-plane $A'$ and stronger in-plane $E'$ modes.
+Those results indicated that the weak interlayer interactions in MS$_2$ materials cannot be associated with the van der Waals interactions only, but most probably with Coulomb electrostatic interactions as well.
 
 Raman signatures of \ce{WS2} nanotubes show distinct features to the spectra of their bulk counterpart.
-\citeauthor{JMR7990865} observed a new line at 152 cm$^{-1}$ in \ce{WS2} NT, which is absent in 2H-\ce{WS2}.\cite{JMR7990865} Another feature is a emerging shoulder on the low energy side of $A_{1g}$ mode at about 416 cm$^{-1}$.
-This has been attributed to a combination mode of LA + TA phonons from the $K$ point of Brillouin zone.\cite{Sourisseau1991} The shoulder mode associated with $A_{1g}$ is attributed to LA + TA.
-As pressure increase from 0 GPa to 18 GPa, these two bands, both shifting to higher wavenumbers, first separate and then recombine.
-It was assumed the compression mainly occurs in $c$ axis, so the stiffening of $A_{1g}$ is anticipated.
-A more prominent feature is the resonance profile broadening the shape of $E_{2g}^1$ mode, which is often assigned to 2LA mode.
+\citeauthor{JMR7990865} observed a new line at 152 cm$^{-1}$ in \ce{WS2} NT, which was absent in 2H-\ce{WS2}.\cite{JMR7990865} Another feature was an emerging shoulder on the low energy side of $A_{1g}$ mode at about 416 cm$^{-1}$.
+This has been attributed to a combination mode of LA + TA phonons from the $K$ point of Brillouin zone.\cite{Sourisseau1991} The shoulder mode associated with $A_{1g}$ was attributed to LA + TA.
+As pressure increased from 0 GPa to 18 GPa, these two bands, both shifting to higher wavenumbers, first separated and then recombined.
+It was assumed the compression mainly occurs in $c$ axis, so the stiffening of $A_{1g}$ was anticipated.
+A more prominent feature was the resonance profile broadening the shape of $E_{2g}^1$ mode, which was often assigned to 2LA mode.
 Yet there is different opinion on these assignments.
-\citeauthor{Molina-Sanchez2011} label the 350 \si{cm^{-1}} band as \ce{E_{1u}} instead of 2LA.\cite{Molina-Sanchez2011} And recent theoretical investigations suggest 416 \si{cm^{-1}} peak is inactive $B_{1u}$ mode,\cite{Molina-Sanchez2011,Ataca2012} which is the Davydov doublet with $A_{1g}$ mode.
+\citeauthor{Molina-Sanchez2011} labeled the 350 \si{cm^{-1}} band as \ce{E_{1u}} instead of 2LA.\cite{Molina-Sanchez2011} And recent theoretical investigations suggested 416 \si{cm^{-1}} peak is inactive $B_{1u}$ mode,\cite{Molina-Sanchez2011,Ataca2012} which is the Davydov doublet with $A_{1g}$ mode.
 \citeauthor{Staiger2012} adopted these assignments in studying the resonance Raman profile of \ce{WS2} NTs.\cite{Staiger2012} It was found that
-\begin{enumerate}
-\item $B_{1u}$ mode arise from curvature and structural disorder;
-\item $B_{1u}/A_{1g}$ intensity ratio strongly depends on excitation, and exceeds unity when excitation energy less than 1.9 eV; and
-\item  An excitonic transition energy of NT is found have a local minimum at about 50 nm, (layer number probably \textgreater 10), and increase either way. Yet all below the bulk value.
-\end{enumerate}
+\begin{enumerate*}[label=\itshape\alph*\upshape)]
+\item $B_{1u}$ mode arose from curvature and structural disorder;
+\item $B_{1u}/A_{1g}$ intensity ratio strongly depended on excitation and exceeded unity when excitation energy less than 1.9 eV; and
+\item  An excitonic transition energy of NT was found at a local minimum of about 50 nm (layer number probably \textgreater 10) and increased either way, yet all energies stayed below the bulk value.
+\end{enumerate*}
 
-\citeauthor{Krause2009} also measured the resonant Raman on \ce{WS2} nanotubes and found a split within 420 \si{cm^{-1}} region, which is labelled as $D-A_{1g}$ mode in analog with the similar defect mode of graphene.\cite{Krause2009} This $D-A_{1g}$ mode was found enhanced as diameter of \ce{WS2} NTs decrease.
-This thesis work will use $B_{1u}({\Gamma})$ mode to interpret this emerging line at about 416 \si{cm^{-1}} of \ce{WS2} NTs, and adopt the 350 \si{cm^{-1}} as 2LA(M).
-\citeauthor{Krause2009a} confirmed $B_{1u}$ mode arise from the inherent structure of \ce{WS2} nanomaterials instead of surface layer effect.
-It is also worth noting that $A_{1g}$ is stronger than 2LA under 632 nm yet weaker under 532 nm excitation, similar to previous discussion of FL scenarios.\cite{Krause2009a} Similar observation of Raman spectra on the \ce{WS2}-\ce{WO3} structures was found in this study, as discussed in Sec.~\ref{tms:raman}.
-\citeauthor{Rafailov2005} estimated the orientation dependence of resonant raman on one MWNT \ce{WS2} attached to the cantilever tip of AFM.\cite{Rafailov2005} Antenna effect lead to optical transition occurring only for polarization parallel to nanotube axis.
-And therefore resonance Raman intensity of SWNT varies as nanotube orientation.
+\citeauthor{Krause2009} also measured the resonant Raman on \ce{WS2} nanotubes and found a split within 420 \si{cm^{-1}} region, which was labeled as $D-A_{1g}$ mode in analogy with the similar defect mode of graphene.\cite{Krause2009} This $D-A_{1g}$ mode was found enhanced as diameter of \ce{WS2} NTs decreased.
+This thesis work will use $B_{1u}({\Gamma})$ mode to interpret this emerging line at about 416 \si{cm^{-1}} of \ce{WS2} NTs and adopt the 350 \si{cm^{-1}} as 2LA(M).
+\citeauthor{Krause2009a} confirmed $B_{1u}$ mode arose from the inherent structure of \ce{WS2} nanomaterials instead of surface layer effect.
+It is also worth noting that $A_{1g}$ appeared stronger than 2LA under 632 nm yet weaker under 532 nm excitation, similar to previous discussion of FL scenarios.\cite{Krause2009a} Similar observation of Raman spectra on the \ce{WS2}-\ce{WO3} structures was found in this study, as discussed in Sec.~\ref{tms:raman}.
+\citeauthor{Rafailov2005} estimated the orientation dependence of resonant Raman on one MWNT \ce{WS2} attached to the cantilever tip of AFM.\cite{Rafailov2005} Antenna effect led to optical transition occurring only for polarization parallel to nanotube axis; therefore, resonance Raman intensity of SWNT varied as nanotube orientation.
 This dependence may provide a routine to distinguish different chiral NTs.
-Polarized Raman spectra (632 nm excitation) is obtained, showing $A_{1g}$ and $E_{2g}$ sharing the same polarization behavior.
-\citeauthor{Virsek2007} investigated the Raman scattering ($\lambda=632$ nm) of \ce{WS2} NTs.\cite{Virsek2007} The silicon peak at 520 cm$^{-1}$ is used for calibration.
-Up-shift of $A_{1g}$ and $E_{2g}$ modes (i.e., 420 to 423 cm$^{-1}$ at $A_{1g}$ mode) were observed, which is attributed to the strain in 3R stacking layers.
+Polarized Raman spectra (632 nm excitation) was obtained showing $A_{1g}$ and $E_{2g}$ sharing the same polarization behavior.
+\citeauthor{Virsek2007} investigated the Raman scattering ($\lambda=632$ nm) of \ce{WS2} NTs.\cite{Virsek2007} The silicon peak at 520 cm$^{-1}$ was used for calibration.
+Up-shift of $A_{1g}$ and $E_{2g}$ modes (i.e., 420 to 423 cm$^{-1}$ at $A_{1g}$ mode) were observed, which was attributed to the strain in 3R stacking layers.

### 2015-02-08 ch-wox/ch-wox.tex
grammar overhaul, tense, clause, ISBN

@@
 \section{Experimental}
-Metallic tungsten powders were utilized as source materials in this work.
+Metallic tungsten powders (W) were utilized as source materials in this work.
 Four kinds of W powder were used in total, as summarized in Table~\ref{tab:powder}.
@@
 
-In a typical non-seeded experiment (Fig.~\ref{fig:wogrow}), about 2 g tungsten powder was positioned in the upstream end of a quartz boat and downstream about 2.5 inch the substrate was stationed. 
+In a typical non-seeded experiment (Fig.~\ref{fig:wogrow}), about 2 g tungsten powder was positioned in the upstream end of a quartz boat, and downstream about 2.5 inch the substrate was stationed. 
 % cvd NW growth
@@
 The substrate cleaning procedures have been elucidated on page~\pageref{ch2sub}.
-The boat was then loaded into reaction chamber in a way that the powder source was placed in the center of heating zone, and the substrate upstream end was aligned at 6.5 inch as defined in Fig.~\ref{fig:wogrow}.
+The boat was then loaded into the reaction chamber in a way that the powder source was placed in the center of the heating zone, and the substrate upstream end was aligned at 6.5 inch, as defined in Fig.~\ref{fig:wogrow}.
 After pumping down, 1 \gls{sccm} \ce{O2} and 10 sccm Ar were admitted into the chamber, respectively, after which the overall pressure read approximately 110 mTorr.
-The temperature ramped up to 1000 \si{\degreeCelsius} in 30 min and lasted for 4 h, and subsequently the apparatus was allowed to naturally cool down to room temperature.
+The temperature ramped up to 1000 \si{\degreeCelsius} in 30 min and lasted for 4 h, and subsequently the apparatus was allowed to naturally cool to room temperature.
 
 \subsection{Seeded growth}
-In the seeded growth, additional tungsten powders was used on the substrate serving as local seed, on which dense \ce{WO3} NW array grew.
-For the tungsten seed particles, 3N powders were used in typical NW growth, and other tungsten powders with different sizes were employed in control experiments including 3N5, 4N5, and 5N.
+In the seeded growth, additional tungsten powders were used on the substrate serving as local seed, on which a dense \ce{WO3} NW array grew.
+For the tungsten seed particles, 3N powders were used in typical NW growth, and other tungsten powders with different sizes were employed in control experiments, including 3N5, 4N5, and 5N.
 All reactants were employed as received without further processing.
 
-In a typical growth, high purity tungsten source was positioned at the upstream end of a quartz boat, with the substrate located ca.
+In a typical growth, high purity tungsten powders were positioned at the upstream end of a quartz boat, with the substrate located ca.
 65 mm downstream.
@@
 The heating temperature was ramped to 1000 \si{\degreeCelsius} in 30 min and lasted for 240 min.
-Subsequently, the apparatus was allowed to naturally cool down to room temperature.
+Subsequently, the apparatus was allowed to naturally cool to room temperature.
 
 To study the growth mechanism, controlled experiments were performed on the oxidation of the tungsten seed particles dispersed on the substrate.
-In a typical oxidation experiment, tungsten powders were loaded into the uniform heating zone and the sealed chamber was pumped down to an ultimate pressure of $\sim8$ mTorr.
-Then oxygen flow varying between 1 sccm to 10 sccm was admitted from upstream inlet.
+In a typical oxidation experiment, tungsten powders were loaded into the uniform heating zone, and the sealed chamber was pumped down to an ultimate pressure of $\sim8$ mTorr.
+Then oxygen flow, varying between 1 sccm to 10 sccm, was admitted from the upstream inlet.
 With 10 sccm UHP Ar (99.999\%) as carrier gas, the overall pressure reached to about 100 mTorr.
-The heating temperature (500 to 750 \si{\degreeCelsius}) was ramped up in 30 min and lasted for 30 min.
-Then the heating power was turned off and the chamber was allowed to naturally cool down to room temperature.
+The heating temperature (500 to 750 \si{\degreeCelsius}) was ramped up in 30 min and lasted for 30 min; then, the heating power was turned off, and the chamber was allowed to naturally cool to room temperature.
 
@@
 
-The growth dynamics of each source were investigated in ordinary transport configuration.
-In each experiment, the temperature, flow rate and source and substrate locations were controlled.
+The growth dynamics of each source were investigated in the non-seeded growth.
+In each experiment, the temperature, flow rate, source, and substrate locations were controlled.
 Another parameter the author found important is the growth number\footnote{Defined as the order of growth performed in the same reaction chamber} in the same reaction chamber.
-Usually one will conduct several runs in the same chamber, and different results may arise with respect to the growth number.
+Usually, one will conduct several runs in the same chamber, and different results may arise with respect to the growth number.
 With this degree of freedom included, the primary features of the deposition and the associated parameters were summarized in Table~\ref{tab:wot}.
@@
 
-The change of metallic W source after growth carries important information on the growth.
-So before examining the deposition on substrates, the SEM images of all powders before and after growth are presented in Fig.~\ref{fig:pdbefore} and Fig.~\ref{fig:pdafter}, respectively.
+The change of metallic W source after growth carries important information about the growth.
+So before examining the deposition on substrates, the SEM images of all powders before and after growth were presented in Fig.~\ref{fig:pdbefore} and Fig.~\ref{fig:pdafter}, respectively.
 % powder before growth
@@
 Overall, the facets were still discernible.
-The 4N5 and 5N powders share similar appearance and size distribution (Fig.~\ref{fig:pdbefore}c-d).
-In contrast, 3N powders are almost half the size of 3N5 ones, and have more uniform size distribution as well.
-Absolute size and its distribution play a key role in its usage as seed, as discussed in Section~\ref{sec:sgfg}.
+The 4N5 and 5N powders shared similar appearance and size distribution (Fig.~\ref{fig:pdbefore}c-d).
+In contrast, 3N powders were almost half the size of 3N5 ones and had more uniform size distribution as well.
+Absolute size and its distribution played a key role in its usage as seed, as discussed in Section~\ref{sec:sgfg}.
 % powder after growth
@@
 \end{figure}
-After growth, 4N5 and 5N powder (Fig.~\ref{fig:pdafter}c-d) both develop the round edges, while 3N and 3N5 powders (Fig.~\ref{fig:pdafter}a-b) become bundled rods.
-This difference mainly arises from the average size, which will dictate the degree of oxidation.
-Another possible reason is the presence of foreign elements in each W powders.
-As indicated by the certificate of analysis from corresponding vendors, carbon, nickel, iron and sodium can amount up to tens of ppm in low purity W sources.
+After growth, 4N5 and 5N powder (Fig.~\ref{fig:pdafter}c-d) both developed the round edges, while 3N and 3N5 powders (Fig.~\ref{fig:pdafter}a-b) became bundled rods.
+This difference mainly arose from the average size, which dictated the degree of oxidation.
+Another possible reason was the presence of foreign elements in each W powders.
+As indicated by the certificate of analysis from corresponding vendors, carbon, nickel, iron, and sodium amounts up to tens of ppm in low purity W source.
 
-The sodium contents in 3N powders fundamentally change the deposition in ordinary transport growth.
+The sodium contents in 3N powders fundamentally changed the deposition in ordinary transport growth.
 Typical morphologies of the as-synthesized nanostructures grown on a \ce{SiO2}-Si substrate were shown in Fig.~\ref{fig:nawoxsemedx}a.
@@
 The chemical compositions of the deposition were analyzed using \gls{edx}.
-A representative \gls{edx} spectrum in Fig.~\ref{fig:nawoxsemedx}c shows the existence of W, Na, O, and Si signals in the specimen, where the Si signal is from the substrate.
+A representative \gls{edx} spectrum in Fig.~\ref{fig:nawoxsemedx}c show the existence of W, Na, O, and Si signals in the specimen, where the Si signal was from the substrate.
 The crystal structures of the as-synthesized specimens were examined using XRD.
-The diffraction peaks were carefully indexed and the deposition was identified as two phases of sodium tungsten oxides and one phase of tungsten oxide as indicated on Fig.~\ref{fig:nawoxsemedx}d.
-The two sodium tungsten oxide phases are the triclinic \ce{Na5W_{14}O_{44}} phase (ICDD PDF 04-012-4449, \emph{a}=7.2740 \si{\angstrom}, \emph{b}=7.2911 \si{\angstrom}, \emph{c}=18.5510 \si{\angstrom}, $\alpha$=96.37$^\circ$, $\beta$=90.89$^\circ$, $\gamma$=119.65$^\circ$) and the triclinic \ce{Na2W4O_{13}} phase (ICDD PDF 04-012-7108, \emph{a}=11.1630 \si{\angstrom}, \emph{b}=3.8940 \si{\angstrom}, \emph{c}=8.2550 \si{\angstrom}, $\alpha$=90.60$^\circ$, $\beta$=131.36$^\circ$, $\gamma$=79.70$^\circ$).
-The tungsten oxide is the monoclinic \ce{WO3} phase (ICDD PDF 01-083-0950, \emph{a}=7.30084 \si{\angstrom}, \emph{b}=7.53889 \si{\angstrom}, \emph{c}=7.6896 \si{\angstrom}, $\beta$=90.89$^\circ$).
+The diffraction peaks were carefully indexed and the deposition was identified as two phases of sodium tungsten oxides and one phase of tungsten oxide, as indicated on Fig.~\ref{fig:nawoxsemedx}d.
+The two sodium tungsten oxide phases were the triclinic \ce{Na5W_{14}O_{44}} phase (ICDD PDF 04-012-4449, \emph{a}=7.2740 \si{\angstrom}, \emph{b}=7.2911 \si{\angstrom}, \emph{c}=18.5510 \si{\angstrom}, $\alpha$=96.37$^\circ$, $\beta$=90.89$^\circ$, $\gamma$=119.65$^\circ$) and the triclinic \ce{Na2W4O_{13}} phase (ICDD PDF 04-012-7108, \emph{a}=11.1630 \si{\angstrom}, \emph{b}=3.8940 \si{\angstrom}, \emph{c}=8.2550 \si{\angstrom}, $\alpha$=90.60$^\circ$, $\beta$=131.36$^\circ$, $\gamma$=79.70$^\circ$).
+The tungsten oxide was the monoclinic \ce{WO3} phase (ICDD PDF 01-083-0950, \emph{a}=7.30084 \si{\angstrom}, \emph{b}=7.53889 \si{\angstrom}, \emph{c}=7.6896 \si{\angstrom}, $\beta$=90.89$^\circ$).
 
@@
 The majority of the nanowires were identified as the \ce{Na5W_{14}O_{44}} phase (Fig.~\ref{fig:nawoxtem}a-c).
-The HRTEM image in Fig.~\ref{fig:nawoxtem}b reveals that the nanowire exhibits a single-crystalline structure.
+The HRTEM image in Fig.~\ref{fig:nawoxtem}b revealed that the nanowire exhibited a single-crystalline structure.
 The corresponding diffraction pattern in the inset of Fig.~\ref{fig:nawoxtem}b was recorded in $[\bar{1}10]$ axis.
@@
 The growth direction of \ce{Na5W_{14}O_{44}} NWs was determined to be parallel to the (001) plane.
-EDX measurement (Fig.~\ref{fig:nawoxtem}c) shows the nanowire consisted of W, Na, and O.
+EDX measurement (Fig.~\ref{fig:nawoxtem}c) show the nanowire consisted of W, Na, and O.
 No other elements were detected.\footnote{The Cu and C signals come from the supporting Cu grid with lacey carbon and the Cr signal from the tip of JEOL double tilt holder.} Small fraction of nanowires were found to be the monoclinic \ce{WO3} phase (Fig.~\ref{fig:nawoxtem}d-f).
@@
 The growth direction of the \ce{WO3} nanowire was determined to be perpendicular to the (002) plane with a d-spacing of 0.38 nm.
-EDX spectrum in Fig.~\ref{fig:nawoxtem}f shows the nanowire consisted of W and O without Na or other impurities.
+EDX spectrum in Fig.~\ref{fig:nawoxtem}f indicated the nanowire consisted of W and O without Na or other impurities.
 The rectangular microplate structures shown in Fig.~\ref{fig:nawoxsemedx}b were also collected for TEM examination.
@@
 From XRD spectra, the long edge of \ce{Na2W4O_{13}} plate can be figured out as the $\vec{c}$ axis and the short edge is along the $\vec{b}$ axis.
-Fig.~\ref{fig:nawoxtem}i shows the plate structure also consisted of W, Na, and O and no other impurities were detected.
-Normalized to the highest W peak, the Na peak intensity in Fig.~\ref{fig:nawoxtem}i is higher than the one in Fig.~\ref{fig:nawoxtem}c.
-This result indicates a higher Na:W ratio for the \ce{Na2W4O_{13}} plate structure than that of \ce{Na5W_{14}O_{44}} nanowires, in consistent with the compositions of these two phases.
+Fig.~\ref{fig:nawoxtem}i show the plate structure also consisted of W, Na, and O and no other impurities were detected.
+Normalized to the highest W peak, the Na peak intensity in Fig.~\ref{fig:nawoxtem}i was higher than the one in Fig.~\ref{fig:nawoxtem}c.
+This result indicated a higher Na:W ratio for the \ce{Na2W4O_{13}} plate structure than that of \ce{Na5W_{14}O_{44}} nanowires, in consistent with the compositions of these two phases.
 % tem
@@
 Micro-Raman spectroscopy was also carried out at room temperature in ambient atmosphere to confirm the phases of the microplates and ultra-long nanowires.
-Fig.~\ref{fig:nawoxram}a shows the m-Raman spectrum of the microplates.
-The Raman lines at 949, 794-777, 366-263 \si{cm^{-1}} closely matches the reported \ce{Na2W4O_{13}} Raman shift frequencies.\cite{Fomichev1992} The Raman spectrum from the ultra-long nanowires is shown in Fig.~\ref{fig:nawoxram}b.
-The spectrum shows major peaks in 100-150 \si{cm^{-1}}, 650-900 \si{cm^{-1}}, and 900-100 \si{cm^{-1}} regions.
-As compared to the reported peak positions (shown by reference lines in Fig.~\ref{fig:nawoxram}b), the nanowires consist of only little or no amount of \ce{WO3} and \ce{Na2W4O_{13}} phases.
+Fig.~\ref{fig:nawoxram}a show the m-Raman spectrum of the microplates.
+The Raman lines at 949, 794-777, 366-263 \si{cm^{-1}} closely matched the reported \ce{Na2W4O_{13}} Raman shift.\cite{Fomichev1992} The Raman spectrum from the ultra-long nanowires was shown in Fig.~\ref{fig:nawoxram}b.
+The spectrum show major peaks in 100-150 \si{cm^{-1}}, 650-900 \si{cm^{-1}}, and 900-100 \si{cm^{-1}} regions.
+As compared to the reported peak positions (shown by reference lines in Fig.~\ref{fig:nawoxram}b), the nanowires consisted of only little amount of \ce{WO3} or \ce{Na2W4O_{13}} phase.
 Major peaks at 107, 695, 765, 913, 943, and 965 \si{cm^{-1}} cannot be assigned to reference in literatures.
-According to XRD and TEM analyses, the nanowires are mainly \ce{Na5W_{14}O_{44}}; therefore these peaks should belong to the \ce{Na5W_{14}O_{44}} phase.
+According to XRD and TEM analyses, the nanowires were mainly \ce{Na5W_{14}O_{44}}; therefore these peaks should belong to the \ce{Na5W_{14}O_{44}} phase.
 So far no Raman spectrum has been reported for this phase, hence this is probably the first observed Raman pattern for \ce{Na5W_{14}O_{44}}.
@@
 \end{figure}
+
 Based on the correlation of Raman spectra and crystallographic data of a variety of tungsten bronze, an empirical formula to relate the Raman peaks and \ce{W-O} bonding lengths has been found as
@@
 \end{equation}
-where $R$ is tungsten-oxygen bond length in \si{\angstrom}, and $\nu$ is Raman stretching wavenumber in \si{cm^{-1}}.\cite{Hardcastle1995} The standard deviation of estimating \ce{W-O} bond distance from Raman stretching wavenumber is $\pm 0.034$ \si{\angstrom}.
-The observed Raman peaks of \ce{Na5W_{14}O_{44}} phase lies at 965, 943, 913, 808, 786, 778, 765, 695 and 107 \si{cm^{-1}}.
-Multi-peak Lorentzian fitting is preformed to precisely determine the central maximum.
-Good fitting is obtained as shown in Fig.~\ref{fig:naworamfit}.
-The calculated \ce{W-O} bond distances using Eq.~\ref{eq:wobond} are then listed in Table~\ref{tab:nawobond}.
-The predicted \ce{W-O} bond lengths agree very well with the crystallographic value of \ce{Na5W_{14}O_{44}} phase.\cite{Triantafyllou1999a} The 107 \si{cm^{-1}} peak probably is caused by \ce{Na-O} bond.
+where $R$ is tungsten-oxygen bond length in \si{\angstrom}, and $\nu$ is Raman stretching wavenumber in \si{cm^{-1}}.\cite{Hardcastle1995} The standard deviation of estimating \ce{W-O} bond distance from Raman stretching wavenumber was $\pm 0.034$ \si{\angstrom}.
+The observed Raman peaks of \ce{Na5W_{14}O_{44}} phase were located at 965, 943, 913, 808, 786, 778, 765, 695, and 107 \si{cm^{-1}}.
+Multi-peak Lorentzian fitting was preformed to precisely determine the central maximum.
+Good fitting was obtained in this study, as shown in Fig.~\ref{fig:naworamfit}.
+The calculated \ce{W-O} bond distances using Eq.~\ref{eq:wobond} were then listed in Table~\ref{tab:nawobond}.
+The predicted \ce{W-O} bond lengths agreed very well with the crystallographic value of \ce{Na5W_{14}O_{44}} phase.\cite{Triantafyllou1999a} The 107 \si{cm^{-1}} peak was probably caused by \ce{Na-O} bond.
 % Na5 raman fitting
@@
 \end{table}
-For a comprehensive comparison purpose, the Raman fingerprints of various tungsten oxides and tungstate is shown in Table.~\ref{tab:woram2}. 
+For a comprehensive comparison purpose, the Raman fingerprints of various tungsten oxides and tungstate was shown in Table~\ref{tab:woram2}. 
 \begin{table}[htb]
@@
 Heated at elevated temperatures, the W precursor, quartz tube, and quartz boat were three possible sources for Na.
-The sodium concentration in 3N source was 20 ppm as provided by vendor.\footnote{Due to the non-uniform distribution of foreign elements, detection of sodium by EDX is possible although the concentration is below the limit of typical EDX capacity.} The Na concentrations in quartz tube and quartz boat (GE 214 quartz, Wilmad Labglass) were 1 ppm and 0.7 ppm, respectively.
+The sodium concentration in 3N source was about 20 ppm, as provided by vendor.\footnote{Due to the non-uniform distribution of foreign elements, detection of sodium by EDX is possible although the concentration is below the limit of typical EDX capacity.} The Na concentrations in quartz tube and quartz boat (GE 214 quartz, Wilmad Labglass) were 1 ppm and 0.7 ppm, respectively.
 To verify the major source of Na content coming from 3N powder, control experiments were employed by using W source with higher purities (4N5 or 5N).
-These ultra-high purity W sources produced pure tungsten oxide deposition and no Na content was detected by EDX.
+These ultra-high purity W sources produced pure tungsten oxide deposition, and no Na content was detected by EDX.
 These results verified the Na content was mainly from the 3N W powders.
-In the OT growth experiments, the W source was first slowly oxidized at 1000 \si{\degreeCelsius} with 1 sccm \ce{O2} and the oxidized source was then evaporated producing \ce{WO3} and other sub-stoichiometric tungsten oxide vapors.
+In the non-seeded growth experiments, the W source was first slowly oxidized at 1000 \si{\degreeCelsius} with 1 sccm \ce{O2}, and then the oxidized source was evaporated producing \ce{WO3} and other sub-stoichiometric tungsten oxide vapors.
 The tungsten oxide vapors produced this way were limited by the slow oxidation, as indicated by
@@
 \item only the top layer of the tungsten source was oxidized showing a dark blue color after growth.
-\end{enumerate*} Due to its low concentration, the exact composition of the Na content in the tungsten source is difficult to probe.
-However, the evaporation rate of the Na content is expected to be high when heated at 1000 \si{\degreeCelsius}.
-This assumption is supported by the observation that no Na was found in the deposition along the whole substrate in control experiments using the used 3N W source.
-Put it in another way, this means that the majority of Na content was already evaporated in previous experiment.
-Hence, despite of its low concentration in the source, the total amount of Na-based vapors produced during the growth was significant, resulting in the dominance of sodium tungsten oxide phases in the nanowire growth region.
+\end{enumerate*} Due to its low concentration, the exact composition of the Na content in the tungsten source was difficult to probe.
+However, the evaporation rate of the Na content was expected to be high when heated at 1000 \si{\degreeCelsius}.
+This assumption wais supported by the observation that no Na was found in the deposition along the whole substrate in control experiments using the used 3N W source.
+Put it in another way, this observation indicated that the majority of Na content was already evaporated in previous experiment.
+Hence, despite of its low concentration in the source, the total amount of Na-based vapors produced during the growth could be significant, resulting in the dominance of sodium tungsten oxide phases in the nanowire growth region.
 
@@
 
-As shown by the photograph in Fig.~\ref{fig:nawoxser}a, for a series of growth performed in the same reaction chamber, the morphology of the nanowires changes with the increase of growth number.
+As shown by the photograph in Fig.~\ref{fig:nawoxser}a, for a series of growth performed in the same reaction chamber, the morphology of the nanowires changed with the increase of growth number.
 Three growth zones of nanowires can be identified on basis of the coverage and density of the nanowires, as delimited by the vertical guide line.
 The growth Zone I was located at high temperature end ranging from 660 to 520 \si{\degreeCelsius}, Zone II was from 520 to 470 \si{\degreeCelsius}, and Zone III from 470 to 420 \si{\degreeCelsius}.
-Detailed morphological changes are depicted in Fig.~\ref{fig:nawoxsemall}.
+Detailed morphological changes were depicted in Fig.~\ref{fig:nawoxsemall}.
 \begin{figure}[htb]
@@
 With growth number increased to 3 (Fig.~\ref{fig:nawoxsemall}d-f) and 5 (Fig.~\ref{fig:nawoxsemall}g-i), the coverage, density, and length of the nanowires increased in all three zones.
-Zone I saw the most significant morphology changes as shown by Fig.~\ref{fig:nawoxser}a and Fig.~\ref{fig:nawoxsemall}g.
+Zone I saw the most significant morphology changes, as shown by Fig.~\ref{fig:nawoxser}a and Fig.~\ref{fig:nawoxsemall}g.
 After the fifth growth in the same reaction chamber, the deposition of ultra-long nanowires almost covered all three zones.
@@
 EDX study revealed the variation of Na concentration in the deposition with the growth number.
-Fig.~\ref{fig:nawoxser}b shows the variation of the Na/W ratios with the increase of growth number at different nanowire growth zones.
+Fig.~\ref{fig:nawoxser}b show the variation of the Na/W ratios with the increase of growth number at different nanowire growth zones.
 Generally, the Na/W ratios at all growth zones increased with the increase of growth number.
@@
 A mechanism of residue deposition enhanced growth was proposed to explain the morphology evolution of the nanowires with the growth number.
-Since the CVD setup employed in this thesis is a hot-wall system, deposition formed on the substrate surface as well as on the inner wall of the reaction chamber in the growth area.
-Residue deposition was found on the quartz tube which can be distinguished by the color change on the quartz tube after each growth.
+Since the CVD setup employed in this thesis was a hot-wall system, deposition formed on the substrate surface as well as on the inner wall of the reaction chamber in the growth area.
+Residue deposition was found on the quartz tube, which can be distinguished by the color change on the quartz tube after each growth.
 With the increase of growth number for the same reaction chamber, the residue deposition on the inner wall of the tube also increased.
-If a clean quartz tube free of any residue deposition is used as the reaction chamber, the vapors are supplied only from the source material forming deposition in the growth area with lower temperature (as shown by the schematics in Fig.~\ref{fig:nawoxsch}a).
-When a quartz tube with residue deposition from previous depositions is used repeatedly as the reaction chamber, the residue deposition heated at growth temperature will also produce vapor locally.
-Therefore, the vapors from both the source materials and the local residue deposition will result in an enhanced growth of nanowires (Fig.~\ref{fig:nawoxsch}b).
+If a clean quartz tube free of any residue deposition was used as the reaction chamber, the vapors were supplied only from the source material forming deposition in the growth area with lower temperature (as shown by the schematics in Fig.~\ref{fig:nawoxsch}a).
+When a quartz tube with residue deposition from previous depositions was used repeatedly as the reaction chamber, the residue deposition heated at growth temperature could also produce vapor locally; therefore, the vapors from both the source materials and the local residue deposition would result in an enhanced growth of nanowires (Fig.~\ref{fig:nawoxsch}b).
 To prove this hypothesis, control experiments were performed utilizing a quartz tube used multiple times previously (e.g.
 a growth number of 9).
-The experiments were carried out without any source materials while other growth parameters remain the same.
+The experiments were carried out without any source materials while other growth parameters remained the same.
 Similar nanowires were found on the substrate in the nanowire growth zones.
@@
 \end{figure}
+
 The general trend of Na/W ratios with the growth number can also be explained by the aforementioned effect of residue deposition.
 The sodium contents from the residue deposition will join the new Na contents from the W source forming deposition.
-Fig.~\ref{fig:nawoxxrd} displays the XRD spectra of a series of specimens with the growth number increases from 1 to 5.
-The XRD spectra reveal the relative concentration dynamics of the three phases as the growth number increases.
-Compared to the \ce{WO3} phase, the \ce{Na5W_{14}O_{44}} and the \ce{Na2W4O_{13}} phases increase significantly as the growth number increase from 1 to 5.
-And in the 5th growth, \ce{Na2W4O_{13}} become the dominated phase compared to the other two phases.
-These results are consistent with the SEM observation (Fig.~\ref{fig:nawoxsemall}) and the composition change from the EDX measurements (Fig.~\ref{fig:nawoxser}b).
-Details XRD indices assignment is summarized in Table~\ref{tbl:wo3xrd}.
+Fig.~\ref{fig:nawoxxrd} displayed the XRD spectra of a series of specimens with the growth number increases from 1 to 5.
+The XRD spectra revealed the relative concentration dynamics of the three phases as the growth number increases.
+Compared to the \ce{WO3} phase, the \ce{Na5W_{14}O_{44}} and the \ce{Na2W4O_{13}} phases increased significantly as the growth number increased from 1 to 5.
+And in the 5th growth, \ce{Na2W4O_{13}} became the dominated phase in comparison to the other two phases.
+These results were consistent with the SEM observation (Fig.~\ref{fig:nawoxsemall}) and the composition change from the EDX measurements (Fig.~\ref{fig:nawoxser}b).
+Details XRD indices assignment was summarized in Table~\ref{tbl:wo3xrd}.
 
@@
 The sample was prepared on a quartz substrate, which is transparent from 300 to 1300 nm.
-SEM images (not shown) found dense NWs array growth similar to those on \ce{SiO2}-Si substrates, indicating the residue effect is not sensitive to the substrate.
+SEM images (not shown) found dense NWs array growth similar to those on \ce{SiO2}-Si substrates, indicating the residue effect was not sensitive to the substrate.
 %051412 sample
@@
 \end{figure}
-The transmission (Fig.~\ref{fig:nauv}) was about 70\% above 400nm, and began to drop significantly for shorter wavelength.
-This variation was also identified in the diffuse reflection spectrum in Fig.~\ref{fig:nadrs}, where the reflection reached to a maximum of 16\% at 390 nm.
-One difference is the DRS increased from 1300 nm to 400nm, presumably due to the inverse scattering intensity with NW dimension of 300 nm.
+The transmission (Fig.~\ref{fig:nauv}) stood at about 70\% above 400nm and began to drop significantly for shorter wavelength.
+This variation was also identified in the diffuse reflection spectrum (DRS) in Fig.~\ref{fig:nadrs}, where the reflection reached to a maximum of 16\% at 390 nm.
+One difference was the DRS increased from 1300 nm to 400nm, presumably due to the inverse scattering intensity with NW dimension of 300 nm.
 The calculated absorption was shown in Fig.~\ref{fig:nauv}, suggesting an energy gap edge at about 380 nm.
-This is consistent with the observed white sample color; however, the conductivity of \ce{Na5W14O44} has not been investigated experimentally.
-Based on the electron sum rule, the sodium tungsten oxide can be cast into \ce{Na5W_1^{5+}W_{13}^{6+}O44}, which indicates the W atom state is quite close to that in \ce{WO3}.
-More investigation is needed to vigorously determined the electronic transport properties of \ce{Na5W14O44} NWs.
+This was consistent with the observed white sample color; however, the conductivity of \ce{Na5W14O44} has not been investigated experimentally.
+Based on the electron sum rule, the sodium tungsten oxide can be cast into \ce{Na5W_1^{5+}W_{13}^{6+}O44}, which indicated the W ion valence states were quite close to that in \ce{WO3}.
+Further investigation is needed to vigorously determined the electronic transport properties of \ce{Na5W14O44} NWs.
 
-Typical morphologies of ordinary transport growth using other powders are shown in Fig.~\ref{fig:wox3n5} and Fig.~\ref{fig:wox4n5}, respectively.
-The common feature of these samples is the dominance of islands growth in upstream end and layers growth in downstream end.
-The exact dimension still shows some minor difference, particularly in low temperature region.
-The deposition with 4N5 and 5N have much smaller grain size than that with 3N5 powder.
+Typical morphologies of non-seeded growth using other powders were shown in Fig.~\ref{fig:wox3n5} and Fig.~\ref{fig:wox4n5}, respectively.
+The common feature of these samples was the dominance of islands growth in upstream end and layers growth in downstream end.
+The exact dimension still show some minor difference, particularly in the low temperature region.
+The deposition with 4N5 and 5N powders had much smaller grain size than that with 3N5 powders.
 % 3N5 powder growth
@@
 \end{figure}
-It is worth pointing out that there are some NWs growth in low temperature end associated with 4N5 growth(Fig.~\ref{fig:wox4n5}c), although not in large scale.
+It was worth pointing out that there were some NWs growth in low temperature end associated with 4N5 growth(Fig.~\ref{fig:wox4n5}c), although not in large scale.
 
@@
 
-As mentioned in Sec.~\ref{sec:nawox}, growth using higher purity tungsten powders primarily produces thin film deposition, and growth using 3N powder is plagued with the impurity effect producing sodium tungsten oxide NW instead of tungsten oxide NW.
+As mentioned in Sec.~\ref{sec:nawox}, growth using higher purity tungsten powders primarily produced thin film deposition; and growth using 3N powder was plagued with the impurity effect producing sodium tungsten oxide NW instead of tungsten oxide NW.
 New growth method was thus explored to obtain \ce{WO3} NWs.
@@
 
-Understanding the oxidation of tungsten powder is the key to obtain high yield in seeded growth.
-Oxidation of tungsten have been investigated under diverse conditions, such as at elevated temperature (\textgreater 1100 \si{\degreeCelsius}) and oxygen pressure on the order of Torr,\cite{Gulbransen1960} and at temperatures ranging from 20 to 500 \si{\degreeCelsius} under atmosphere pressure.\cite{Warren1996} \ce{WO_x} NWs were readily found when tungsten (foil, wire, or powder) is oxidized under various conditions.\cite{Zhu1999,Karuppanan2007,Hsieh2010} However the study on tungsten powder oxidation behavior between intermediate temperature range and under low pressure is still rare.
+Understanding the oxidation of tungsten powder was the key to obtain high yield in seeded growth.
+Oxidation of tungsten had been investigated under diverse conditions, such as at elevated temperature (\textgreater 1100 \si{\degreeCelsius}) and oxygen pressure on the order of Torr,\cite{Gulbransen1960} and at temperatures ranging from 20 to 500 \si{\degreeCelsius} under atmosphere pressure.\cite{Warren1996} \ce{WO_x} NWs were readily found when tungsten (foil, wire, or powder) was oxidized under various conditions.\cite{Zhu1999,Karuppanan2007,Hsieh2010} However, the study on tungsten powder oxidation behavior between intermediate temperature range and under low pressure was still rare.
 This thesis studied the oxidation of tungsten powders with diverse size within temperature range from 500 to 1000 \si{\degreeCelsius} and under several mTorr oxygen partial pressure.
-It was illustrated that using tungsten powder as seed is an economic approach to obtain high yield of \ce{WO3} nanowires at relatively lower temperature.
-It was also demonstrated that there was an optimal tungsten powder size under current experimental conditions for seeded growth.
-This observation will provide some insight on the role of tungsten powder as source material in CVD growth of \ce{WO_x}.
+It was illustrated that using tungsten powder as seed was an economic approach to obtain high yield of \ce{WO3} nanowires at relatively lower temperature.
+It was also demonstrated that there was an optimal tungsten powder size under current experimental conditions for the seeded growth.
+This observation provided some insight on the role of tungsten powder as source material in CVD growth of \ce{WO_x}.
 
-Commercial available tungsten powders with different size are usually associated with purity variation as well.
+Commercial available tungsten powders with different size were usually associated with purity variation as well.
 Four kinds of tungsten powders were used as precursor to prepare \ce{WO3} NWs, as already summarized in Table~\ref{tab:powder}.
 The dimensions of tungsten powder were obtained by measuring the average size in SEM graphs.
-A systematic investigation was performed on the oxidation behavior of tungsten powder to evaluate the temperature effect, size-dependence and influence of oxygen partial pressure.
+A systematic investigation was performed on the oxidation behavior of tungsten powder to evaluate the temperature effect, size-dependence, and influence of oxygen partial pressure.
 
@@
 When temperature was increased to 600 \si{\degreeCelsius}, 3N powder started to crack with longer NWs on the isolated surface.
-Further increase of temperature lead to irregular shapes of tungsten power and aggregation of NWs, giving rise to the nanorods and bunched or bundled structures.
+Further increase of temperature led to irregular shapes of tungsten power and aggregation of NWs, giving rise to the nanorods and bunched or bundled structures.
 It could be determined from the morphology variation that the optimal seeded growth temperature for 3N powder was in the range of 600 to 650 \si{\degreeCelsius}.
@@
 Fig.~\ref{fig:pdsize} depicted the oxidation of different sizes of tungsten powder under the same experimental conditions.
-In contrast to the morphology of 3N powder shown in Fig.~\ref{fig:pdtemp}, 3N5 powder surface is primarily covered with sub-micron particles as well as some short tiny NWs; whereas 4N5 and 5N powder were thoroughly oxidized, showing branched flowers feature.
+In contrast to the morphology of 3N powder shown in Fig.~\ref{fig:pdtemp}, 3N5 powder surface was primarily covered with sub-micron particles as well as some short tiny NWs; whereas 4N5 and 5N powder were thoroughly oxidized, showing branched flowers feature.
 This dramatic difference could be explained in terms of surface energy and oxygen diffusion.
-With smaller dimension, the increased surface-to-volume ratio and short diffusion path both lower the energy barrier of oxidation.\cite{tungsten1999} It was logical to deduce that higher temperature or increased oxygen level might favor the NWs formation on 3N5 powder.
-When it comes to seeded growth, however, the powder size distribution was an important factor to give uniform NWs deposition.
-Since the size distribution of 3N powder is more uniform than that of 3N5 powder, this study used the former as seeds.
+With smaller dimension, the increased surface-to-volume ratio and short diffusion path both lowered the energy barrier of oxidation.\cite{tungsten1999} It was logical to deduce that higher temperature or increased oxygen level might favored the NWs formation on 3N5 powder.
+When it came to seeded growth, however, the powder size distribution was an important factor to give uniform NWs deposition.
+Since the size distribution of 3N powder was more uniform than that of 3N5 powder, this study used the former as seeds.
 % seed optimal
@@
 Fig.~\ref{fig:pdoxy} depicted the morphology change of 3N powder with respect to varied oxygen partial pressure.
-When the oxygen flow is lower than 3 sccm, 3N powder almost stayed as the same, with cracks separating the dense layer of NWs.
-When oxygen flow is increased to 10 sccm, the 3N powder exemplified an enlarged version of that for 4N5 or 5N powder under 1 sccm oxygen flow.
+When the oxygen flow was lower than 3 sccm, 3N powder almost stayed as the same with cracks separating the dense layer of NWs.
+When oxygen flow was increased to 10 sccm, the 3N powder exemplified an enlarged version of that for 4N5 or 5N powder under 1 sccm oxygen flow.
 This observation again supported the surface energy explanation.
 
-With all above oxidation experiments, favorable conditions for local growth of NWs were extracted to perform seeded growth.
-The seeded growth was performed by placing high purity tungsten powders (4N5 or 5N) in heating zone and receiving substrate with 3N tungsten powders in downstream location where the temperature was about 600 \si{\degreeCelsius}.
-The temperature profile and source and substrate locations remain essentially the same as in Fig.~\ref{fig:wogrow} except the presence of 3N powder on substrate.
-In all experiments, tungsten powders were uniformly distributed by sliding two pieces of substrates and the growth time was kept at 4 h.
+With all above oxidation experiments, favorable conditions for local growth of NWs were extracted to perform the seeded growth.
+The growth was performed by placing high purity tungsten powders (4N5 or 5N) in center heating zone and substrate with 3N tungsten powders in downstream location, where the temperature was about 600 \si{\degreeCelsius}.
+The temperature profile, source, and substrate locations remained essentially the same as in Fig.~\ref{fig:wogrow} except the presence of 3N powder on substrate.
+In all experiments, tungsten powders were uniformly distributed by sliding two pieces of substrates, and the growth time was kept at 4 h.
 % sg sem
@@
 \end{figure}
-As shown in Fig.~\ref{fig:sgb}, dense NWs array was obtained on tungsten powder seeds with individual wires of length up to 10 $\mu$m and diameter about 50 to 200 nm, according to the measurements made in the close-up view.
+As shown in Fig.~\ref{fig:sgb}, a dense NWs array was obtained on tungsten powder seeds with individual wires of length up to 10 $\mu$m and diameter about 50 to 200 nm, according to the measurements made in the close-up view.
 Each tungsten powder stood as independent growth site (Fig.~\ref{fig:sga}) with island-layer growth on the substrates, a common feature without using tungsten powder as seed under current experimental conditions.
@@
 
-Fig.~\ref{fig:sgxrd} is the XRD spectrum of one typical sample.
-The peaks under circular symbol were identified to be the monoclinic \ce{WO3} phase (ICDD PDF 01-083-0950, \emph{a}=7.30084 \AA, \emph{b}=7.53889 \AA, \emph{c}=7.6896 \AA, $\beta$=90.89$^\circ$), while the peak under the triangular symbol was indexed to cubic tungsten phase (ICDD PDF 04-16-3405, \emph{a}=3.157 \AA), in agreement with the EDX analysis (Fig.~\ref{fig:woedx}).
-This means that during the \ce{WO3} seeded growth of 4 h heating at 1000 \si{\degreeCelsius}, the tungsten powder in downstream low temperature region (600-700 \si{\degreeCelsius}) is not entirely oxidized.
+Fig.~\ref{fig:sgxrd} displayed the XRD spectrum of one typical sample.
+The peaks under circular symbol were identified to be the monoclinic \ce{WO3} phase (ICDD PDF 01-083-0950, \emph{a}=7.3008 \AA, \emph{b}=7.5388 \AA, \emph{c}=7.6896 \AA, $\beta$=90.89$^\circ$), while the peak under the triangular symbol was indexed to cubic tungsten phase (ICDD PDF 04-16-3405, \emph{a}=3.157 \AA), in agreement with the EDX analysis (Fig.~\ref{fig:woedx}).
+This indicated during the \ce{WO3} seeded growth of 4 h heating at 1000 \si{\degreeCelsius}, the tungsten powder in the low temperature region (600-700 \si{\degreeCelsius}) was not entirely oxidized.
 Micro-Raman scattering spectroscopy was performed on the as-synthesized sample as well.
-During Raman examination, the laser spot was carefully focused onto the NWs on powders and several inspections on different positions were observed to ensure the reproductivity of spectra data.
-As shown in Fig.~\ref{fig:sgram}, five distinct bands were well resolved, with peaks located at 131, 265, 327, 711 and 803 \si{cm^{-1}}, respectively.
-This pattern was typical features of \ce{WO3}, consistent with previous study.\cite{Salje1975a,Dixit1986} The high background level probably arises from the metallic core.
+During Raman examination, the laser spot was carefully focused onto the NWs on powders, and several inspections on different positions were observed to ensure the reproductivity of spectra data.
+As shown in Fig.~\ref{fig:sgram}, five distinct bands were well resolved with peaks located at 131, 265, 327, 711, and 803 \si{cm^{-1}}, respectively.
+This pattern was typical features of \ce{WO3}, in consistent with previous study.\cite{Salje1975a,Dixit1986} The high background level probably arose from the metallic core.
 % sg tem
@@
 TEM specimen was prepared by using carbon grid to slightly scratch the as-grown sample.
-Fig.~\ref{fig:woseedtem1} shows the feature of majority NWs.
-The growth direction is determined to be perpendicular to (002) plane.
-The streaking in SEAD pattern presumably arises from stacking defaults during \ce{WO3} NW growth.
+Fig.~\ref{fig:woseedtem1} show the feature of majority NWs.
+The growth direction was determined to be perpendicular to (002) plane.
+The streaking in \gls{saed} pattern presumably stemmed from stacking defaults during \ce{WO3} NW growth.
 This study also found some NWs exhibit high crystalline quality, as revealed by the TEM analysis in Fig.~\ref{fig:woseedtem2}.
-The NW grew normal to (002) plane with a measured lattice spacing of 3.79 \AA, which is favorably compared to the XRD peak at $23.07^\circ$ (7.7103 \AA).
-The sharp SEAD pattern and clear phase contrast in HRTEM demonstrated are both strong evidence of good crystallinity.
-This formation indicated current growth parameters have promising potential to obtain highly crystalline \ce{WO3} NWs in large scale.
+The NW grew normal to (002) plane with a measured lattice spacing of 3.79 \si{\angstrom}, which was favorably compared to the XRD peak at $23.07^\circ$ (7.7103 \si{\angstrom}).
+The sharp \gls{saed} pattern and clear phase contrast in HRTEM demonstrated strong evidence of good crystallinity.
+This formation indicated current growth parameters could have promising potential to obtain highly crystalline \ce{WO3} NWs in large scale.
 
@@
 
-In regarding to the formation of NWs on tungsten powder itself, this study assumes the driving force is related to interfacial strain between W and \ce{WO_x}.
-Oxidation of tungsten proceed slowly at room temperature and an oxide layer of 100 \si{\angstrom} was found on the surface of tungsten foils.\cite{Warren1996} The tungsten powder used in current study would be covered by a thin oxide layer as well.
-During oxidation, different oxidation rates exist for different crystallographic orientations on the tungsten powder.
-Oxidation occurring at boundaries and defects are preferred thermodynamically.\cite{You2010} Compressive strain will gradually accumulate at the tungsten oxide/tungsten interface, which might limit the diffusion rate of oxygen at temperature lower than 500 \si{\degreeCelsius}.\cite{tungsten1999} At elevated temperature, cracks will primarily occur, as observed in Fig.~\ref{fig:pdtemp}.
-When heated up, tungsten and the oxide shell will probably relax the strain by converting into sub-stoichiometric NWs, a similar process as suggested by \citeauthor{Klinke2005} in the chemically induced strain growth of tungsten oxide NWs.\cite{Klinke2005} It is worth noting that tungsten oxide nanowires could also formed when \ce{WO3} is reduced.\cite{Sarin1975} The elongation of \ce{WO_x} is thermodynamically favorable during the conversion from metallic tungsten to tungsten oxide as well.
+In regarding to the formation of NWs on tungsten powder itself, this study assumed the driving force was related to interfacial strain between W and \ce{WO_x}.
+Oxidation of tungsten proceeded slowly at room temperature and an oxide layer of 100 \si{\angstrom} was found on the surface of tungsten foils.\cite{Warren1996} The tungsten powder used in current study would be covered by a thin oxide layer as well.
+During oxidation, different oxidation rates existed for different crystallographic orientations on the tungsten powder.
+Oxidation occurring at boundaries and defects were thermodynamically preferred.\cite{You2010} Compressive strain gradually accumulated at the tungsten oxide/tungsten interface, which might limit the diffusion rate of oxygen at temperature lower than 500 \si{\degreeCelsius}.\cite{tungsten1999} At elevated temperature, cracks primarily occurred, as observed in Fig.~\ref{fig:pdtemp}.
+When heated up, tungsten and the oxide shell probably relaxed the strain by converting into sub-stoichiometric NWs, a similar process as suggested by \citeauthor{Klinke2005} in the chemically induced strain growth of tungsten oxide NWs.\cite{Klinke2005} It is worth noting that tungsten oxide nanowires could also formed when \ce{WO3} was reduced.\cite{Sarin1975} The elongation of \ce{WO_x} was thermodynamically favorable during the conversion from metallic tungsten to tungsten oxide as well.
 Local evaporation-condensation process might also contribute to the formation of NWs on tungsten powder.
 
-The enhanced yield of NWs obtained via seeded growth could be explained by a vapor-solid (VS) mechanism.
-External supply of growth species will condense onto the powders and substrate simultaneously, promoting the elongation of NWs on power as well as resulting island-layer growth on substrate.
+The enhanced yield of NWs obtained via the seeded growth could be explained by a vapor-solid (VS) mechanism.
+External supply of growth species condensed onto the powders and substrate simultaneously, promoting the elongation of NWs on power as well as resulting island-layer growth on substrate.
 The local NW density in oxidation experiment was much higher than that of seeded growth.
-It is reasonable to presume that during seeded growth, several NWs in a small region on powder will coalescence, as evidenced by the bundled structures.
-At last, the author would like to point out that when low purity tungsten powder (3N) was used as source, sodium tungsten oxide nanowires were found to be dominant in the final product.
-The details have been published.\cite{Sheng2014} It seems surprising that when 3N powder was used as seeds, only \ce{WO3} nanowires were obtained.
+It was reasonable to presume that during the seeded growth, several NWs in a small region on powder coalesced, as evidenced by the bundled structures.
+At last, the author would like to point out that when low purity tungsten powder (3N) was used as source, sodium tungsten oxide nanowires were found to be dominant in the final phase.
+The details have been published.\cite{Sheng2014} It seemed surprising that when 3N powder was used as seeds, only \ce{WO3} nanowires were obtained.
 This result was attributed to the lower temperature and significantly reduced amount of 3N powder used in the seeded growth, compared with the conditions used in Ref.\cite{Sheng2014}.
-The source material in seeded growth is not limited to high purity tungsten powder.
+The source material in the seeded growth is not limited to high purity tungsten powder.
 Instead, any material that could produce appropriate growth vapor could be employed, indicating the versatility of this approach.
@@
 \end{figure}
-As shown in Sec.~\ref{sec:nawox}, ordinary transport growth using high purity W power mostly leads to thin film growth on one substrate of 1 inch long.
-However, it was found that when two shorter substrates were closely placed together, the \ce{WO3} NW yield was significantly enhanced in the second substrate located in lower temperature region.
-For instance, substrate 1 (Sub1) is located at 6.75 to 7 inch (Fig.~\ref{fig:wogrow} horizontal axis on page~\pageref{fig:wogrow}), and substrate 2 (sub2) is placed in close vicinity of downstream end of sub1.
-W source moves to 5 inch, and 0.3 sccm \ce{O2} is used to reduce the \ce{WO_x} vapor pressure.
-Deposition on sub1 is characterized by thin film, similar to those shown in Fig.~\ref{fig:wox4n5}b.
-However, deposition on sub2 (Fig.~\ref{fig:fg1}) is in sharp contrast to that shown in Fig.~\ref{fig:wox4n5}c, although they are both located in the low temperature region of reaction chamber.
-The NW density is dramatically increased.
-The NWs have length about 1 to 2 $\mu$m and diameter about 200 nm.
-Close-up view (inset of Fig.~\ref{fig:fg2}) shows the NWs have clear facets, implying its high crystalline quality.
+As shown in Sec.~\ref{sec:nawox}, the non-seeded growth using high purity W powers mostly led to thin film growth on the substrate of 1 inch long.
+In contrast, it was found that when two shorter substrates were closely placed together, the \ce{WO3} NW yield was significantly enhanced in the second substrate located in lower temperature region.
+For instance, substrate 1 (Sub1) was located at 6.75 to 7 inch (Fig.~\ref{fig:wogrow} horizontal axis on page~\pageref{fig:wogrow}), and substrate 2 (sub2) was placed in close vicinity of downstream end of sub1.
+W source was moved to 5 inch, and 0.3 sccm \ce{O2} was used to reduce the \ce{WO_x} vapor pressure.
+Deposition on sub1 was characterized by thin film, similar to those shown in Fig.~\ref{fig:wox4n5}b.
+However, deposition on sub2 (Fig.~\ref{fig:fg1}) was in sharp contrast to that shown in Fig.~\ref{fig:wox4n5}c, although they were both located in the low temperature region of reaction chamber.
+The NW density was dramatically increased when two separate substrates were employed.
+The NWs had length about 1 to 2 $\mu$m and diameter about 200 nm.
+Close-up view (inset of Fig.~\ref{fig:fg2}) shows the NWs exhibited sharp facets, implying its high crystalline quality.
 
 The growth mechanism here can be explained by aforementioned VS process as well.
-Both local flow and temperature play an vital role in the formation of dense NW array.
-Splitting one substrate into two presumably introduces some fluctuation in the vapor flow.
-It is well known that in lamellar flow region, there is a velocity boundary above the side wall.
-In spite of the high crystalline quality, the \ce{WO3} is not long enough and yield is limited by the evaporation of source materials; therefore this approach is not seriously pursued in this study.
+Both local flow and temperature played an vital role in the formation of dense NW array.
+Splitting one substrate into two presumably introduced some fluctuation in the vapor flow.
+In spite of the high crystalline quality, the \ce{WO3} was not long enough, and the yield was limited by the evaporation of source materials; therefore this approach was not seriously pursued in this study.
 
@@
 \ce{Na5W14O44} NW was first reported from this study; the crystal structure was investigated in details, and HRTEM images were obtained.
-Besides, the Raman vibrational spectroscopy of \ce{Na5W14O44} was also revealed.
-The presence of sodium tungsten oxide phase indicates that the CVD growth of \ce{WO3} is extremely sensitive to Na contents.
+Besides, the Raman vibrational spectroscopy of \ce{Na5W14O44} was also identified.
+The presence of sodium tungsten oxide phase indicated that the CVD growth of \ce{WO3} was extremely sensitive to Na contents.
 The insight of \ce{WO3} growth kinetics we have gained from this study could help establish a systematic connection between the interaction of transition metal oxide and alkali metal ions, thereby turning this deleterious effect into a beneficial approach of controlled growth.
-In fact, favorable results have been observed on both \ce{WO3} and \ce{MoO3} 1D nanostructures syntheses using NaOH treated Si substrates.
-Details will be presented in Chapter 4 and 6.
+In fact, favorable results has been observed on both \ce{WO3} and \ce{MoO3} 1D nanostructures syntheses using NaOH treated Si substrates.
+Details will be presented in Chapter 4 and 6, respectively.
 Moreover, two alternative approaches of \ce{WO3} NWs were also attempted, and the seeded growth method proved effective for large scale growth.

### 2015-02-08 ch-wox/part1.tex
walked in to exchange opinions with Advr, and walking out with his on wox and moox
grammar overhaul, tense, clause, ISBN

@@
 Intense research interest was rekindled by the discovery of \gls{ec} effect in \citeyear{Granqvist1993}.\cite{Granqvist1993}  Nano-engineering \ce{WO_x} bring more possibility and flexibility to its already rich characteristics, therefore resulting in research efforts spanning multiple fields in the scientific community.
-Besides smart window based on \gls{ec} effect, tungsten oxides are also well investigated for several other significant applications: photoelectrochemical cell for solar energy conversion and storage, photocatalysis for hydrogen evolution reaction, chemical and biological sensing based on gasochromic effect.
+Besides smart window based on \gls{ec} effect, tungsten oxides are also well investigated for several other significant applications: photoelectrochemical cell for solar energy conversion and storage, photocatalysis for hydrogen evolution reaction, and chemical and biological sensing based on gasochromic effect.
 In addition, a few young fields are not thoroughly explored: field emission, optical storage, thermo-electricity, ferro-electricity, and superconductivity.
 
-In this chapter, a literature review on tungsten oxides and sodium tungsten oxides will be given first, with focus on technological applications, crystal structures, and synthesis approaches.
+In this chapter, a literature review on tungsten oxides and sodium tungsten oxides is introduced first, with focus on technological applications, crystal structures, and synthesis approaches.
 Several growth methods were explored in this study to investigate the crystallographic dynamics of tungsten oxides and sodium tungsten oxides nanostructures.
@@
 A representative lattice structure is illustrated in Fig.~\ref{fig:wo3oct}.
+\begin{figure}[htb]
+\centering
+\includegraphics[width=0.4\textwidth]{octwo3.jpg}
+\caption[Octahedra model of \ce{WO3}]{Octahedra model of \ce{WO3}}
+\label{fig:wo3oct}
+\end{figure}
 These distorted \ce{WO6} octahedra adapt different tilting angles in different phases and edge-sharing octahedra also arise. 
@@
 \end{table}
-The temperature-dependent phase transition and corresponding lattice constants in bulk form is summarized in Table~\ref{tab:wo3phase}.\cite{Zheng2011} And a firm assignation of space group to monoclinic phases are still in debate.\cite{Chatten2005} It is noticed that the lattice parameters obtained via \emph{ab initio} calculation closely match the experimental values.\cite{Migas2010a} The phase transition scenarios in nanostructured \ce{WO3} are supposed to be more sophisticated.
+The temperature-dependent phase transition and corresponding lattice constants in bulk form is summarized in Table~\ref{tab:wo3phase}.\cite{Zheng2011} \ce{WO3} in monoclinic phase is favored in room temperature; however, a firm assignation of space group to monoclinic phases are still in debate.\cite{Chatten2005} It is noticed that the lattice parameters obtained via \emph{ab initio} calculation closely match the experimental values.\cite{Migas2010a} The phase transition scenarios in nanostructured \ce{WO3} are supposed to be more sophisticated.
 Within Gibbs-Thomson framework, one can generally expect lower transition temperature than their bulk counterparts due to enhanced surface energy.
 Temperature-dependent Raman spectroscopy provided support for this deduction.\cite{Boulova2002}
-\begin{figure}[htb]
-\centering
-\includegraphics[width=0.4\textwidth]{octwo3.jpg}
-\caption[Octahedra model of \ce{WO3}]{Octahedra model of \ce{WO3}}
-\label{fig:wo3oct}
-\end{figure}
 
@@
 Besides \ce{WO3}, tungsten oxide exists in a series of sub-stoichiometric states.
-The \ce{W_nO_{3n-1}} ($n \geq 2$) exhibit $\{ 001 \}$ CS structure.
+The \ce{W_nO_{3n-1}} ($n \geq 2$) exhibit $\{ 001 \}$ \gls{cs} structure.
 Chemical formula corresponding to n=2, 3, 4, 5 and 6 are \ce{W2O5=WO_{2.5}}, \ce{W3O8=W_{2.67}}, \ce{W4O_{11}=WO_{2.75}}, \ce{W5O_{14}=WO_{2.8}}, and \ce{W6O_{17}=WO_{2.83}}, which indicates the existence of a oxygen deficient plane at every $n$ row.
@@
 Moreover, the oxygen deficient planes could extend along directions other than $\{ 001 \}$.
-For instance, the $\{ 102 \}$ CS planes appears in \ce{WO_x} where $x$ is within 2.93 to 2.98, and  the $\{ 103 \}$ CS planes for $x$ within 2.87 to 2.93.\cite{Sloan1999} The enhancement arises from the structure composed of a conductive layer and an insulating layer that are laminated therein.\cite{Shingaya2013} In \ce{WO_x} nanorods, the oxygen deficient planes are conductive, each having atomic thickness and separated by several nm of \ce{WO3} layers.
+For instance, the $\{ 102 \}$ CS planes appears in \ce{WO_x} where $x$ is within 2.93 to 2.98, and  the $\{ 103 \}$ CS planes for $x$ within 2.87 to 2.93.\cite{Sloan1999} In \ce{WO_x} nanorods, the oxygen deficient planes are conductive, each having atomic thickness and separated by several nm of \ce{WO3} layers.
 Localized surface plasmons could possibly exist on these conductive planes.
@@
 The concept of polaron was first proposed by Landau in 1933.
-In ionic or highly polar crystals, such as II-VI semiconductors, alkali halides and transition metal oxides, the Coulomb interaction between a conduction electron and the lattice ions results in a strong electron-phonon coupling.
+In ionic or highly polar crystals, such as II-VI semiconductors, alkali halides, and transition metal oxides, the Coulomb interaction between a conduction electron and the lattice ions results in a strong electron-phonon coupling.
 A new quasi-particle, virtual phonon, can be defined corresponding to the effect of electron pulling nearby positive ions towards it and pushing nearby negative ions away.
@@
 This local distortion and the electron together is equivalent to a new elementary exciton of the crystal, and is named as polaron} the intercalation of \ce{M^+} (M = H, \ce{Li}, or Na) ions into \ce{WO3} films is accompanied with the formation of small polarons ($r_p$ comparable to unit cell size) and formal reduction of some \ce{W^{6+}} sites to \ce{W^{5+}}, as depicted in Eq.~\ref{eq:ec}.
-During the intercalation process, the \ce{M^+} ions enter into these vacant sites.\cite{Hepel2008} Coloration occurs when electron transition occurs from the hole polaron band to the electron polaron band.
 \begin{align}\label{eq:ec}
@@
 \end{align}
+During the intercalation process, the \ce{M^+} ions enter into these vacant sites.\cite{Hepel2008} Coloration occurs when electron transition occurs from the hole polaron band to the electron polaron band.
 And the polaron binding energy ($E_p$) is given by
@@
 \end{align}
-where $\epsilon_\infty$ and $\epsilon_{st}$ are optical and static dielectric constants respectively, and polaron radius $r_p$, which specifies how far the lattice distortion extends, is related to polaron density $N_p$ by $r_p = \frac{1}{2}\sqrt[3]{\pi/6N_p}$.
+where $\epsilon_\infty$ and $\epsilon_{st}$ are optical and static dielectric constants, respectively, and polaron radius $r_p$, which specifies how far the lattice distortion extends, is related to polaron density $N_p$ by $r_p = \frac{1}{2}\sqrt[3]{\pi/6N_p}$.
 However, the polaron model has difficulty in estimating $r_p$.
@@
 When one electron is removed from this level, $V_O^0$ is converted to $V_O^+$.
-The positively charged vacancy exerts coulombic repulsion to the nearest W-ions, which results in a displacement of the neighboring W-ions and an upward shift of the defect level into the bandgap, thereby creating a color center.
+The positively charged vacancy exerts Coulombic repulsion to the nearest W-ions, which results in a displacement of the neighboring W-ions and an upward shift of the defect level into the bandgap, thereby creating a color center.
 The optical transition from $V_O^+$ to $V_O^{2+}$ (a state within the conduction band) contributes to coloration.\cite{Deb2008}
 
-So the polaron and color center models both agree on that \ce{W^{5+}} and its transition is responsible for the coloration, but disagree on how this \ce{W^{5+}} state and the corresponding energy levels are created (foreign ion reduction in polaron model and oxygen vacancy in color center model).
+So the polaron and color center models both agree on that \ce{W^{5+}} and its transition is responsible for the coloration; but disagree on how this \ce{W^{5+}} state and the corresponding energy levels are created (foreign ion reduction in polaron model and oxygen vacancy in color center model).
 A modified polaron model is proposed to include \ce{W^{4+}} states in host lattice.
@@
 But there is a disagreement on the final states.
-Double injection supports the formation of tungsten bronze \ce{H_xWO3} while color center model insists on the inward diffusion of oxygen vacancy and outward diffusion of water molecules.
-Both have been substantiated experimentally.
-Therefore the exact mechanism in \ce{WO_x} still requires further investigation.
+Double injection model supports the formation of tungsten bronze \ce{H_xWO3} while color center model insists on the inward diffusion of oxygen vacancy and outward diffusion of water molecules.
+Both have been substantiated experimentally;\cite{Zhu2010} therefore, the exact mechanism in \ce{WO_x} still requires further investigation.
 
-\subsection{Review of Synthesis Methods}\label{sec:woxgrowth}
+\subsection{Review of Synthesis Methods of Tungsten Oxides}\label{sec:woxgrowth}
 
-As the chemical formula \ce{WO3} suggested, the most straightforward way is heating metallic tungsten in various forms,\cite{Zhou2005a,Cao2009,Hsieh2010} i.e., powders, foils and wires.
+As the chemical formula \ce{WO3} suggested, the most straightforward way is heating metallic tungsten (W) in various forms,\cite{Zhou2005a,Cao2009,Hsieh2010} i.e., powders, foils, and wires.
 Actually \ce{WO_x} \glspl{nw}\footnote{$x$ is between 2 and 3} were observed when directly heating W wires.\cite{Gu2002a} Due to the extreme high melting point of W, it requires very high temperature (say, above 1100 \si{\degreeCelsius}) to produce large amount of growth species.
 Therefore scalable growth seems difficult at low temperature range unless other activation mechanisms are used.
-The DC current heating proved to be a route with potential large yield.
-Tungsten wire or filament is connected to a current source, and substrate is positioned in proximity to the heated W wire.\cite{Lingfei2006,Thangala2007,Chang2007} Tungsten oxides powder can also been used as precursor to prepare \ce{WO_{x}} \glspl{nw}.\cite{Huang2008a,Wang2009} Hydrogen-containing agents (i.e.
+The dc current heating proved to be a route with potential large yield, where tungsten wire or filament was connected to a current source, and substrate was positioned in proximity to the heated W wire.\cite{Lingfei2006,Thangala2007,Chang2007} Tungsten oxides powder can also been used as precursor to prepare \ce{WO_{x}} \glspl{nw}.\cite{Huang2008a,Wang2009} Hydrogen-containing agents (i.e.
 water, \ce{H2}, or methane\cite{Klinke2005}) were often involved into the reaction.\cite{Baek2007,Karuppanan2007} The potential benefit is \ce{WO3} has a much lower melting point ($\approx 1470$ \si{\degreeCelsius}) than that of metallic tungsten.
 
-In contrast, organometallic decomposition is another feasible method.
-\citeauthor{Pol2005} obtained \ce{W18O49} nanorods by thermal dissociation of \ce{WO(OMe)4} at 700 \si{\degreeCelsius}, and \ce{WO3} by further annealing at 500 \si{\degreeCelsius} in air atmosphere.\cite{Pol2005} Spray pyrolysis is a typical aerosol-assisted \gls{cvd} technique.
-Typical process flow is: the precursor solution is pumped to an atomizer, and then sprayed through the carrier gas as a fine mist of very small droplets onto heated substrates.
+Meanwhile, organometallic decomposition is another feasible method.
+\citeauthor{Pol2005} obtained \ce{W18O49} nanorods by thermal dissociation of \ce{WO(OMe)4} at 700 \si{\degreeCelsius} and \ce{WO3} by further annealing at 500 \si{\degreeCelsius} in air atmosphere.\cite{Pol2005} Spray pyrolysis is a typical aerosol-assisted \gls{cvd} technique.
+Typical process flow is: the precursor solution is pumped to an atomizer and then sprayed through the carrier gas as a fine mist of very small droplets onto heated substrates.
 Subsequently the droplets undergo evaporation, solute condensation, and thermal decomposition, which then result in film formation.\cite{Zheng2011} Main reactions include:
@@
 
-Hydrothermal method has been an important route to synthesize a diversity of nanomaterials.
+Besides, hydrothermal method has been an important route to synthesize a diversity of nanomaterials.
 Preparation of \ce{WO_{3-x}} has also been demonstrated hydrothermally.\cite{Lee2003,Gu2007} Usually, the precursor (\ce{H2WO4}) is mixed with other reactants (sulfides or certain organic acid) in solution and pH value is adjusted as another control degree of freedom.
-Then the solution is transferred into a sealed container (i.e.
+Then, the solution is transferred into a sealed container (i.e.
 Teflon autoclave) and maintained at elevated temperature ($120 \sim 300$ \si{\degreeCelsius}) for tens of hours.
-Finally the product is separated from the solution and dried, layered \ce{WO3.nH2O} flakes are usual products.
+Finally, the product is separated from the solution and dried, layered \ce{WO3.nH2O} flakes are usual products.
 A brief summary of representative synthesis methods is shown in Table~\ref{tab:wox}.

### 2015-03-09 FrontMatter/Abstract.tex
front matter finalized

@@
 
-This dissertation consists of three main parts, each centering on \ce{WO3}, \ce{MoO3}, and \ce{WS2}-\ce{WO3}, respectively.
+This dissertation consists of three main parts, each centering on \ce{WO3}, \ce{MoO3}, and \ce{WO3}-\ce{WS2}, respectively.
 Systematical investigation of the \ce{WO3} nanostructure prepared by the CVD method with tungsten powders as precursor led to the following accomplishments:
 \begin{enumerate*}[label=\itshape\alph*\upshape)]
-\item the discovery of \ce{Na5W14O44} nanowires;
+\item the discovery of \ce{Na5W14O44} nanowires (NWs);
 \item a knowledge of the delicate role of sodium in tungsten source powders; and
-\item a seeded growth method to produce high quality \ce{WO3} nanowires.
-\end{enumerate*} Enlightened by the intricate interactions between sodium content and tungsten oxide, this dissertation extended the vapor-liquid-solid strategy into \ce{MoO3} 1D nanostructure growth and discovered two morphologies of \ce{MoO3}: ultra-longbelts and microtowers.
-Careful observation in extensive experiments identified the catalytic role of sodium hydroxide during the growth of \ce{MoO3} and readily proved that the catalytic behavior also exists with other alkali-based metal contents.
-The third part of this work moved the investigation center from growth to property characterization.
-A novel TEM-Raman integrated study was performed on \ce{WS2}-\ce{WO3} core-shell NWs, allowing for the observation of high resolution TEM imaging, Raman spectroscopy, and photoluminescence spectroscopy on individual nanowires.
-The single-walled \ce{WS2} tubular nanostructure was first identified.
-The combined results further illustrated the existence of \ce{WS2} wall number dependent Raman fingerprints on resonant Raman spectra.
+\item a seeded growth method to produce high quality \ce{WO3} NWs.
+\end{enumerate*} Enlightened by the intricate interactions between sodium content and tungsten oxide, this dissertation extended the vapor-liquid-solid strategy in to \ce{MoO3} 1D nanostructure growth and discovered two morphologies of \ce{MoO3}: long nano-belts and micro-towers.
+Careful observation in extensive experiments identified the catalytic role of sodium hydroxide during the growth of \ce{MoO3} and readily proved that the catalytic behavior also exists with other alkali metal compounds.
+The third part of this work moved the investigation center from growth to structure and property characterization.
+A novel integrated structure-property (transmission electron microscopy-Raman spectroscopy, TEM-Raman) study was performed on \ce{WO3}-\ce{WS2} core-shell NWs, allowing for the observation of high resolution TEM imaging, Raman spectroscopy, and photoluminescence spectroscopy on individual nanowires.
+The TEM-Raman combined results further illustrated that the profiles of resonant Raman spectra exhibit strong dependence on the wall number of \ce{WS2}.
+This Raman fingerprints can provide a rapid approach for the optical identification of few-walled \ce{WS2} tubular structures.
 

### 2015-03-09 FrontMatter/FrontMatter.tex
front matter finalized

@@
 I appreciate the financial supports of GASP in UNC Charlotte, the research assistantship from National Science Foundation (DMR-1006547), and the teaching assistantship from Physics and Optical Science department.
-I also appreciate the Center for Optoelectronics and Optical Communications at UNC Charlotte for the support in multiuser facilities.
+I also appreciate the Department of Mechanical Engineering and Engineering Science and the Center for Optoelectronics and Optical Communications at UNC Charlotte for supports in multiuser facilities.
 I would also like to thank all my friends and/or research partners I have met in Charlotte: Dr.
@@
 \begin{flushright}
-
+\vspace{2in}
 \emph{Sheng, Tao}
 
-\emph{January 2015}
+January 2015
 
-\emph{Charlotte, NC}
+Charlotte, NC
 

### 2015-03-09 misc/SI_thesis.tex
update on mwe files

@@
 Thermal evaporation process sensitive to the concentration of oxygen in growth system, influencing not only the volatility of source materials but also the stoichiometry of vapor phase.\cite{Dai2002}
+
+self-nucleation from vapor of new crystals, new liquid drops and 2D monolayers on a saturated crystal face requires supersaturations of the vapor by factors of 10, 5, and 1.5 respectively; the presence of dislocation, however, breaks the need for fresh 2D nucleation.
+perfect metal exhibits 1E+8 dislocation lines each square centimeter.\cite{Frank1949}
+
+solid-solid wetting for \ce{MoO3}, \ce{WO3}, and \ce{V2O5} spreading.\cite{Leyrer1988} Experimental evidence supports the oxyhydroxide are intermediates in the surface chemical transformation of these oxides into surface polyoxoanions in the presence of \ce{H2O} vapor.
+The spreading occurs independent of polymolybdate formation and in the absence of \ce{H2O} vapor; the solid-solid wetting driven by a gradient of the surface free energy.
+Gas form transport is discarded as the dominanting mechanism.
+
+\ce{MoO3} wet \ce{Al2O3} and \ce{TiO2} but not \ce{SiO2}; \ce{MoO3} reacts with \ce{Al2O3} in solid state to form \ce{Al2(MoO4)3} and with \ce{TiO2} to form \ce{Ti(MoO4)2}, yet reaction with \ce{SiO2} not reported.
+
+1D review. show more exotic phenomena, spin-charge separation. Au-Si NW growth terminate as Au, not a Au-Si alloy.\cite{Hu1999}
+
+an order-of-magnitude estimate, to a lesser extent,
 
@@
 
+Basic operations and several growth recipes using the home-built cvd system are included in Appendix.
+
+the TEM specimen was prepared either by directly scratching the as-synthesized sample using TEM grid (Cu, lacy carbon, 300 mesh), or dispersed into aqueous or organic solutions, then drop-cast onto TEM grid.
+
+The enhancement arises from the structure composed of a conductive layer and an insulating layer that are laminated therein.\cite{Shingaya2013}
+
+It is well known that in lamellar flow region, there is a velocity boundary above the side wall.
+
+Raman band assignment for \ce{A2MO4} is well grounded.
+Alkali metal cations with octahedral coordination occur below 230 cm$^{-1}$.
+For \ce{A2M_nO_{3n+1}}, exact assignment is not available yet due to the complicated \ce{MO6} octahedra.
+
+Based on the vls process, it is known that a eutectic state is the key to promote preferred growth direction
+The melting of \ce{Na2MoO4} was highly possible when taking into account of its size as well.\cite{Bruggemann1997}
+
+\begin{itemize}
+
+\item When no Mo powder was used while growth was performed in an old tube or oxygen flow is limited to a extreme small value, circular particle-like solid were found and Mo, Na and O were detected, suggesting the existence of VLS mechanism.
+Using Mo coated substrate and subsequent NaOH treatment, similar particles formation was repeated.
+No discernible XRD pattern emerged, illustrating the amorphous nature of liquid catalyst.
+\item 30 min growth: belts growth begin (500 microns long, grow rate is estimated to be 0.5 $\mu$ m/s), tower structures show up as well, but much less than belt.
+Two kinds of belts found, tapering and non-tapering.
+The former one seems to have particles mostly associated with sidewalls of the top part.
+\item In reduced time or less oxygen supply growth, Na-containing site was found located onto the sidewall of belts instead of the usual expected tip.
+XRD pattern indicated the existence of \ce{Na_xMoO3} phase.
+And \ce{MoO3} XRD pattern is dominated by (0k0) peaks, indicating a 2D layer-by-layer growth with lateral rate exceeding that of axial direction.
+\item 2 h growth: there are crossed tapering belts at downstream boundary, with more than one particle located along the interface of two perpendicular belts, EDX confirmed high Na content.
+
+\end{itemize}
+
+people used chamber pot when there was no running water system. 
+This difference presumably vanished when nanotube diameter exceeded 100 nm.
+considering the integration into current microelectronic process, which was found higher for film prepared without an intermediate Ni coating
+
+This thesis then conjectured that the substrate cleaning in Ref.\cite{Peimyoo2013} should be similar to that in Ref.\cite{VanderZande2013}, yet the source-to-substrate layout and growth pressure were still needed to be optimized with respect to the home-built CVD apparatus.
+No 1L vs nL statistic is available.
+
+15 optical modes e allowed assuming 6 atoms in primitive cell.
+
 \section{MB}
@@
 
+\ce{WS2} exciton binding energy 0.71 eV , exciton A of 2 eV and B of 2.4 eV from direct band gap at K valley of the BZ. \cite{Zhu2014a}
+
+photocarrier relaxation pathway in TMDC by Monte-Carlo simulation.\cite{Kozawa2014} the excitation at K point, the path way and radiative emission channels are related to band nesting.
+
+Substrate effects on Raman and PL of TMDC.\cite{Buscema2014} \ce{MoS2} PL on Au is not quenched for 1L.
+
+Si work function, 4.83 eV throughout most of the doping range.\cite{Allen1962} be open to reinterpretation; work function $\psi$ is determined using the Kelvin contact potential difference method against a metal reference.
+$\psi_m$ is determined by a photoelectric measurement.
+
+1T \ce{WS2} hydrogen evolution.\cite{Voiry2013a}
+
+\ce{WS2} nanotube has been studied because of the strong lubricant;  
+The sulfurization of tungsten oxide, proved as a high yield approach, has been studied throughly for preparing \ce{WS2} nanotubes.
+Few wall \ce{WS2} can be used to obtain nanoribbon.
+The properties of \ce{WS2} nanotube can help to understand the confinement in \ce{WS2} nanoribbon.
+
+The growth design, emphasizing the absence of \ce{H2};
+
 \ce{WS2} NIR photocatalysis.\cite{Sang2014}
 
-\ce{WS2} hydrogen evolution,\cite{Voiry2013a}
+\ce{WS2} hydrogen evolution can be achieved by using large potential and expensive Pt-based catalysts.
+Finding inexpensive replacement would enable large scale HER applications.\cite{Voiry2013a} \ce{WS2} nanosheets exfoliated by chemical reaction, and 1T (octahedral) phase is associated with the enhanced electrocatalytic activity.
+Energy barrier from 1T to 2H transformation is calculated to be 0.95 eV, explained why 1T is stable in ambient environment.
+
+aqueous suspension, de-aerated with Ar.
+
+TCO band alignment.\cite{Klein2010} The energy band alignment between TCO and organic materials is governed by vacuum level to a large extent; whereas the alignment with inorganic materials is modfied by the interficial dipole significantly.
+
+Work function (minus of the Fermi level wrt vacuum) of two contributions: electrical work for passing the intrinsic surface dipole layer and the other one is equivalent to the chemical potential $\mu$ of the electrons in the bulk material, measured with respect to the vacuum in absence of a dipole layer on the surface.\cite{Gerischer1983} Different crystallographic orientation surfaces have different dipoles.
+The Fermi level position relative to the vacuum level therefore depends on the surface structure.
+
+Charge separation and the geometrical influence.
+catalytic activity is associated to the oxygen vacancy, substoichiometry, or plasmon.
+\ce{WO3} nanosheet carrier density derived from UV-Vis using Drude model $\omega_p = \sqrt{\frac{N_e e^2}{\epsilon_0 m_e}}$ and from Mott-Schottky measurement.
+PL data of \ce{WO3-x} obtained using 360 nm excitation.\cite{Yan2015}
+
+\ce{MoS2} FET.\cite{Li2015}
+
+(Good writing) Hot carriers generation and collection device bansed on TCO.\cite{Gong2014a} Metal-SC contact as Schottky photodetector, where hot electron generated in metal and was injected into SC.
+ITO-\ce{Al2O3}-Au, where e in Au traverse 5 nm \ce{Al2O3}.
+
+alternatively, hot electrons, carrier cooling, losing kinetics energy to lattice, phonon emission.
 
@@
 \]
+
+How the large exciton binding energy affect the optical properties in TMDC. out-of-plane acoustic (ZA), \cite{Zhang2015tmdc}
+
+In ambient environment, \ce{MoS2} oxidized into oxides when $T > 350$ \si{\degreeCelsius}.\cite{Su2014a}
+
+For Raman, the total scattered intensity $I(\lambda)$ is 
+\[
+I(\lambda) = \int_0^d |F_{abs}(\lambda_0,x)\cdot F_{sc}(\lambda, x)|dx
+\]
+where $F_{abs}$ can be found in the ESI of ref.\cite{Buscema2014}. The enhancement factor is hereby defined as the ratio of intensity between free standing layer and substrate-specfic layer.
+
+Raman and PL of \ce{MoS2} on dielectric and conducting substrates.
+514 nm, 20 $\mu$m aperture, 0.5 \si{cm^{-1}} resolution, 0.25 mW power, and 10 s integration time.
+\cite{Buscema2014} The substrate-dependent interferometric stacking does not perturb the peak emission wavelength but strongly influences the emission intensity.
+\ce{SiO2} charge impurity induced doping, leading to enhanced electron density, is proposed to explain the softening of A1g mode on \ce{SiO2}.
+
+metallic sub affect PL by additional non-radiative path for exciton recombination, such as charge transfer and dipole-dipole interaction.
+But on Au \ce{MoS2} PL is enhanced compared to that on \ce{SiO2} after normalization.
+Charged exciton results in PL in redshifted wavelength.
 

### 2015-03-09 misc/paper.tex
update on mwe files

@@
 
-In energy band structure of $E-k$, the zero energy is chosen at the top of VB, so the $E$ here should be chemical potential, \cite{Sze2006} 
-When defining the Fermi level, the follow integral is used
-\[
-n = \int_{E_C}^\infty N(E)f(E)dE
-\]
-So the Fermi level is again compared to the VBM.
-
-The ionization energy of acceptor is measured against valence band edge;
-zero electron or hole current requires $\frac{dE_F}{dx} = 0$.
-
-Deviation of SC-Metal barrier due to 1) interface layer, 2) surface state, and 3) image force.
-
 \url{http://physics.stackexchange.com/questions/70341/fermi-level-alignment-and-electrochemical-potential-between-two-metals?rq=1}
@@
 
-Basic operations and several growth recipes using the home-built \gls{cvd} system are included in Appendix.
+\section{sze ssp}
+\subsection{review of semiconductor}
+zincblende structure: two interpenetrating fcc lattices; wurtzite structure: two interpenetrating hexagonal lattices.
+band structure, that is energy-momentum relationship, is usually obtained by solving the Schrodinger equations in one electron approximation.
 
-the TEM specimen was prepared either by directly scratching the as-synthesized sample using TEM grid (Cu, lacy carbon, 300 mesh), or dispersed into aqueous or organic solutions, then drop-cast onto TEM grid.
+In energy band structure of $E-k$, the zero energy is chosen at the top of VB, so the $E$ here should be chemical potential.\cite{Sze2006} The electron energy is conventionally defined to be positive when measured upward from $E_c$; the hole energy is positive when measured downward from $E_v$.
+When defining the Fermi level, the follow integral is used
+\[
+n = \int_{E_C}^\infty N(E)f(E)dE
+\]
+So the Fermi level is again compared to the VBM. DOS $N(E)$ is approximated by the density near the bottom of conduction band;
 
-The enhancement arises from the structure composed of a conductive layer and an insulating layer that are laminated therein.\cite{Shingaya2013}
+The ionization energy of acceptor is measured against valence band edge;
+zero electron or hole current requires $\frac{dE_F}{dx} = 0$.
 
-It is well known that in lamellar flow region, there is a velocity boundary above the side wall.
+Deviation of SC-Metal barrier due to 1) interface layer, 2) surface state, and 3) image force.
 
-Raman band assignment for \ce{A2MO4} is well grounded.
-Alkali metal cations with octahedral coordination occur below 230 cm$^{-1}$.
-For \ce{A2M_nO_{3n+1}}, exact assignment is not available yet due to the complicated \ce{MO6} octahedra.
+\subsection{metal-SC contacts}
 
-Based on the \gls{vls} process, it is known that a eutectic state is the key to promote preferred growth direction
-The melting of \ce{Na2MoO4} was highly possible when taking into account of its size as well.\cite{Bruggemann1997}
+Schottky suggested that potential barrier could arise from stable space charges alone.
 
-\item When no Mo powder was used while growth was performed in an old tube or oxygen flow is limited to a extreme small value, circular particle-like solid were found and Mo, Na and O were detected, suggesting the existence of VLS mechanism.
-Using Mo coated substrate and subsequent NaOH treatment, similar particles formation was repeated.
-No discernible XRD pattern emerged, illustrating the amorphous nature of liquid catalyst.
-\item 30 min growth: belts growth begin (500 microns long, grow rate is estimated to be 0.5 $\mu$ m/s), tower structures show up as well, but much less than belt.
-Two kinds of belts found, tapering and non-tapering.
-The former one seems to have particles mostly associated with sidewalls of the top part.
-\item In reduced time or less oxygen supply growth, Na-containing site was found located onto the sidewall of belts instead of the usual expected tip.
-XRD pattern indicated the existence of \ce{Na_xMoO3} phase.
-And \ce{MoO3} XRD pattern is dominated by (0k0) peaks, indicating a 2D layer-by-layer growth with lateral rate exceeding that of axial direction.
-\item 2 h growth: there are crossed tapering belts at downstream boundary, with more than one particle located along the interface of two perpendicular belts, EDX confirmed high Na content.
+contact potential means the potential difference between the work functions.
 
-people used chamber pot when there was no running water system. 
-This difference presumably vanished when nanotube diameter exceeded 100 nm.
-considering the integration into current microelectronic process, which was found higher for film prepared without an intermediate Ni coating
+Covalent SC surface has high peak density of surface states, and the neutral level is about one-third of the bandgap from valence-band edge.
+ForIII-V compounds, the pinning of surface Fermi level occurs, leading to the barrier height independent of metal work function,
 
-This thesis then conjectured that the substrate cleaning in Ref.\cite{Peimyoo2013} should be similar to that in Ref.\cite{VanderZande2013}, yet the source-to-substrate layout and growth pressure were still needed to be optimized with respect to the home-built CVD apparatus.
-No 1L vs nL statistic is available.
-
-15 optical modes e allowed assuming 6 atoms in primitive cell.
+For ionic SC, the barrier height depends strongly on the metal.

### 2015-03-09 ch-intro/ch-instr.tex
ch 1, ch 2 post reviewing

@@
 A detailed description is given to the \gls{cvd} system.
-Other sample and substrate preparation methods are also briefly introduced.
+General sample and substrate preparation methods are also briefly introduced.
 For mature processes and techniques, the contents are limited to the extent where experienced material researchers could repeat the experiments performed here.
@@
 (a) Photograph of reaction chamber.
-(b) Sketch of CVD system, where A1: quartz tube; B1: bubbler; C1-2: gas cylinders; E1: mechanical pump; H1-2: ceramic heater; MFC: flow controller; P1: pressure gauge; V1-4: needle valves; V5-7: butterfly valves.}
+(b) Sketch of CVD system, where A1: quartz tube; B1: bubbler; C1-2: gas cylinders; E1: mechanical pump; H1-2: ceramic heater; MFC: mass flow controller; P1: pressure gauge; V1-4: needle valves; V5-7: butterfly valves.}
 \label{fig:ch2cvd}
@@
 On the hot substrate, adatoms diffuse and do not settle down until finding an appropriate location where equilibrium is favored.
-Detailed growth conditions will be introduced in the corresponding chapters.
+Detailed growth conditions will be introduced in the corresponding experimental section of Chapter 3, 4, and 5.
 \subsection{Substrates Treatments}\label{ch2sub}
 
-Silicon (Si) and 1 $\mu$m silicon dioxides on Si wafer (\ce{SiO2}-Si) (University Wafer Inc.) were primarily used, and other substrates were also employed, i.e.
+Silicon (Si) and 1 $\mu$m silicon dioxides on Si wafer (\ce{SiO2}-Si) (University Wafer Inc.) were primarily used.
+Other substrates were also employed, i.e.
 Mica\footnote{\ce{K(Al2)(Si3Al)O10(OH)2}}, glass (Fisher Scientific, microscope slide, 12-549),\footnote{Typical composition is 72.6\% \ce{SiO2}, 0.8\% \ce{B2O3}, 1.7\% \ce{Al2O3}, 4.6\% \ce{CaO}, 3.6\% \ce{MgO} and 15.2\% \ce{Na2O}} and stainless steel.
-Si and \ce{SiO2}-Si substrates were first cut into rectangular pieces of certain size and then ultrasonically cleaned (Branson 1510R-MTH) with acetone and alcohol for about 15 min, each followed by blow-drying with nitrogen gas.
+Si and \ce{SiO2}-Si substrates were first cut into rectangular pieces and then ultrasonically cleaned (Branson 1510R-MTH) with acetone and alcohol for about 15 min, each followed by blow-drying with nitrogen gas.
 After solution cleaning, the substrate surface is usually hydrophobic.
@@
 In this study, secondary electron images were mainly used to reveal the morphology of the samples.
-Unless otherwise noticed, the SEM images were acquired using 10 kV acceleration voltage, 10 mm working distance, and 30 spot size.
+Unless otherwise noted, the SEM images were acquired using 10 kV acceleration voltage, 10 mm working distance, and 30 spot size.
 
@@
 Akin to the electron-materials interaction introduced in Sec.~\ref{sec:sem}, various signals are generated when the thin specimen is radiated by electron beam.
-Besides the \gls{saed} pattern and \gls{hrtem} imaging, other TEM based techniques include \gls{cbed}, EDX, \gls{eels} and \gls{cl}, etc; therefore, TEM is essentially a signal-generating and detecting tool.\cite{Williams2009} Fundamental physics of electron is needed to obtain a comprehensive understanding of these TEM related techniques, and only a brief summary is given here.
+Besides the \gls{saed} pattern and \gls{hrtem} imaging, other TEM based techniques include \gls{cebd}, EDX, \gls{eels} and \gls{cl}, etc; therefore, TEM is essentially a signal-generating and detecting tool.\cite{Williams2009} Fundamental physics of electron scattering is needed to obtain a comprehensive understanding of these TEM related techniques, and only a brief summary is given here.
 
@@
 \end{table}
-This small deviation angle determines the way of secondary signal usage in TEM.
-In analog to the diffraction-limited resolution in conventional lens optics, the ultimate resolved point distance in TEM should be on the order of electron wavelength used, which is 0.025 \si{\angstrom} at 200 kV.
-However, it is generally more difficult to manipulate electron with magnetic field than do photon with dielectric lens.
-The current resolving power in TEM is on the order of 1.0 \si{\angstrom} without correction of the spherical aberration.
+This small scattering angle determines the way of secondary signal usage in TEM.
+In analogy to the diffraction-limited resolution in conventional lens optics, the ultimate resolved point distance in TEM should be on the order of electron wavelength used, which is 0.025 \si{\angstrom} at 200 kV.
+Without correction of the spherical aberration, the current resolving power in TEM is on the order of 1.0 \si{\angstrom}.
 The nominal resolution of JEM-2100 is 2.3 \si{\angstrom}.
-On the other hand, it is much easier to fine tune the power (focal length) of lens in TEM than in conventional optics.
-This capacity enables other observation approaches that would be rather difficult, if not impossible, to be realized in lens optics, such as \gls{saed} pattern.
+Nevertheless, it is much easier to fine tune the power (focal length) of lens in TEM than in conventional optics.
+This capacity enables other observation approaches that would be rather difficult, if not impossible, to be realized in lens optics, such as generating \gls{saed} pattern.
 

### 2015-03-09 ch-intro/ch-intro.tex
ch 1, ch 2 post reviewing

@@
 \begin{align}
-4\ce{h^+} +  \ce{H2O} &\rightarrow \ce{O2} + 4\ce{H^+} \label{eq:hervb}\\
+4\ce{h^+} +  2\ce{H2O} &\rightarrow \ce{O2} + 4\ce{H^+} \label{eq:hervb}\\
 4\ce{H^+} +  4e^- &\rightarrow 2\ce{H2} \label{eq:hercb}
@@
 \item surface energy state, thereby band structure modification;
-\item quantum confinement effect when exciton size is smaller then physical dimension; and
+\item quantum confinement effect; and
 \item different charge-separation and transport mechanism.
@@
 
-In regarding to the contents of this study, electrochromic applications based on \gls{tmo} nanowires will benefit from the reduced diffusion depth by eliminating the deficiency of ions accumulation in amorphous oxide thin film devices, which in turn leads to shorter response time and higher coloration efficiency.\cite{Huang2008a,Scherer2012} And photocatalytic applications using \gls{tmo} nanostructures could harvest the huge surface area on which unsaturated bond reside, thereby enabling a much higher efficiency.\cite{Mills1993,Merki2011,Chen2011b}
+In regarding to the contents of this study, electrochromic applications based on \gls{tmo} nanowires will benefit from the reduced diffusion depth by eliminating the deficiency of ions accumulation in amorphous oxide thin film devices, which in turn leads to shorter response time and higher coloration efficiency.\cite{Huang2008a,Scherer2012} And photocatalytic applications using \gls{tmo} nanostructures could harvest the huge surface area on which unsaturated bonds reside, thereby enabling a much higher efficiency.\cite{Mills1993,Merki2011,Chen2011b}
 
-To make fully use of the nano-engineering, one must just be as aware of the limitations as one is of its advantages; for example, an obvious disadvantage is the difficulty of device fabrication using nanomaterials due to the size and requirements of new integration process.
-There also exist some uncertainty as to the energy band modification present in nanostructures, which could be either useful or not depending on the application scenario.\cite{Wang2012} With this explained, the dissertation moves on to the objective and scope section.
+To fully use nano-engineering, one must just be as aware of the limitations as one is of its advantages; for example, an obvious disadvantage is the difficulty of device fabrication using nanomaterials due to the size and requirements of new integration processes.
+There also exist some uncertainty as to the energy band modification present in nanostructures, which could be either useful or not depending on the application.\cite{Wang2012}
 
 \section{Scope and Dissertation Outline}
-To fully harvest the advantages of these \gls{tmo} and \gls{tmdc} one-dimensional nanomaterials, a scalable growth method and a comprehensive understanding towards the growth-structure-property relation must be established in the first place.
+To fully harvest the advantages of these \gls{tmo} and \gls{tmdc} one-dimensional nanomaterials, a scalable growth method and a comprehensive understanding of the growth-structure-property relation must be established in the first place.
 This study primarily focuses on the \ce{WO3} and \ce{MoO3} nanostructure synthesis, the growth mechanism study, crystal structures characterization, and optical properties measurement.
@@
 The materials studied in this dissertation are tungsten oxides (\ce{WO3}), molybdenum oxides (\ce{MoO3}),and tungsten disulfide (\ce{WS2}).
-Experimental tools will be introduced in Chapter 2, including the CVD apparatus and substrate treatments for growth and electron microscopes and optical spectrometers for characterization.
+Experimental tools will be mentioned in Chapter 2, including the CVD apparatus and substrate treatments for growth, electron microscopes and optical spectrometers for characterization.
 Chapter 3 is devoted to tungsten oxides (\ce{WO3}) and sodium tungsten oxides (\ce{Na5W14O44}) nanowires, where the role of sodium in metallic tungsten precursors are thoroughly investigated; a potentially scalable growth method is also developed.
@@
 Emphasis will be placed on the characterization of individual \ce{WO3}-\ce{WS2} core-shell \gls{nw}.
-At last, this dissertation is closed with summary and future work.
+This dissertation is concluded with summary and future work.

### 2015-03-09 ch-moox/moox.tex
ch 4 post reviewing

@@
 
-In this work, a new growth mechanism of molybdenum oxide (\ce{MoO3}) 1D structures was discovered, highlighted by \ce{MoO3} long nanobelts and micro-scale towers.
+In this work, a new growth mechanism of molybdenum oxide (\ce{MoO3}) 1D structures was discovered, manifest as \ce{MoO3} long nanobelts and micro-towers.
 The samples were synthesized using a group of alkali metal based catalysts, including \ce{NaOH}, \ce{KI}, and \ce{Na2CO3}.
-In contrast to the sole axial growth found in the conventional catalyst-assisted growth, two different growth modes were observed for the \ce{MoO3} 1D growth here: transverse growth and axial growth.
-In the transverse mode, the 1D structures grew perpendicularly to the catalyst-deposition interface with catalyst particles on the side surfaces; whereas in the axial mode, the crystal grew along the catalyst-deposition axis.
-The growth modes were explained by a modified \gls{vss} mechanism, and the growth kinetics were explored in details.
+In contrast to the sole axial growth found in the conventional catalyst-assisted process, two different growth modes were observed for the 1D \ce{MoO3} deposition: transverse and axial growth.
+In the transverse mode, the 1D structures grew parallel to the catalyst-deposition interface with catalyst particles on the side surfaces; whereas in the axial mode, the crystal grew perpendicularly to the catalyst-deposition interface.
+The growth modes were explained by a modified \gls{vss} mechanism, and the growth kinetics were explored in detail.
 
@@
 Emphasis will be placed on morphological and crystal structure characterization of 1D \ce{MoO3} nanostructures and the verification of proposed VSS mechanism.
-This chapter is concluded with a summary of VSS growth and preliminary results on morphology controlled \ce{MoO3} nanostructures.
+This chapter concludes with a summary of VSS growth and preliminary results on morphology controlled \ce{MoO3} nanostructures.
 
@@
 Molybdenum oxide (\ce{MoO3}) crystallizes in three phases: orthorhombic $\alpha$-\ce{MoO3}, monoclinic $\beta$-\ce{MoO3}, and the metastable hexagonal h-\ce{MoO3}.\citep{Deb1968,Fibers2007} $\alpha$-\ce{MoO3} phase (hereafter \ce{MoO3}) exhibits anisotropic structure with strong bonding along [001] and [100] direction while van der Waals interaction along [010] direction.\cite{He2003} Due to this unique structure, \ce{MoO3} has been found to have several important properties and a wide range of technological applications, such as electrochromism and photochromism,\cite{Yao1992} lubricants,\cite{Sheehan1996} photocatalysts,\cite{Chen2010} and gas sensor, including \ce{CO},\cite{Comini2005} \ce{NO2},\cite{Taurino2006} \ce{H2},\cite{Sha2009} and ethanol.\cite{Choopun} Moreover, other features arise when nanoscale \ce{MoO3} is specifically prepared, e.g.
-field emission.\citep{Li2002d,Zhou2003b}  As a layered hosting material, \ce{MoO3} can be further modified by intercalating with alkali ions\citep{Spahr1995,Li2006b,Hu2011} and even divalent ion.\cite{Sian2005} This structural richness has enabled improved performance in Li-ion\cite{Mai2007} and sodium-ion battery.\cite{Hariharan2013} In combination with \ce{TiO2} forming a core-shell structure, these nanoparitcles were reported to lower the photon absorption energy of \ce{TiO2}.\cite{Elder2000} When \ce{MoO3} was combined with Ag as layered structure, transparent conducting behavior was observed.\cite{Nguyen2012} In addition, \ce{MoO3} has been a good precursor for preparing other useful materials, such as \ce{MoS2} fullerene\cite{Li2003c} and few layer \ce{MoS2}.\cite{Lin2012} Recently, 2D atomic layers attracts intensive research efforts, and \ce{MoO3} can be an important member in fabricating the van der Waals heterostructures.\cite{Geim2013}
+field emission.\citep{Li2002d,Zhou2003b}  As a layered hosting material, \ce{MoO3} can be further modified by intercalating with alkali ions\citep{Spahr1995,Li2006b,Hu2011} and even divalent ion.\cite{Sian2005} This structural richness has enabled improved performance in Li-ion\cite{Mai2007} and sodium-ion batteries.\cite{Hariharan2013} In combination with \ce{TiO2} forming a core-shell structure, these nanoparitcles were reported to lower the photon absorption energy of \ce{TiO2}.\cite{Elder2000} When \ce{MoO3} was combined with Ag as layered structure, transparent conducting behavior was observed.\cite{Nguyen2012} In addition, \ce{MoO3} has been a good precursor for preparing other useful materials, such as \ce{MoS2} fullerene\cite{Li2003c} and few layer \ce{MoS2}.\cite{Lin2012} Recently, 2D atomic layers attract intensive research efforts, and \ce{MoO3} can be used in fabricating the van der Waals heterostructures.\cite{Geim2013}
 
@@
 Researchers have been exploring a variety of methods to synthesize different \ce{MoO3} nanostructures.
-Only a brief introduction will be given here, since these efforts has been well documented in several review articles.\cite{He2003} Most of these methods can be categorized into two groups: solution-based hydrothermal procedures \citep{Li2002b,Xia2006,Li2006a,Camacho-Bragado2006} and chemical vapor deposition approaches.\citep{Zeng1998,Li2002c,Li2002d,Zhou2003b,Fibers2007,Yan2009} Both methods have its own merits.
-Hydrothermal process usually needs lower temperature(\textless 300 \si{\degreeCelsius}), but the duration is usually long, and the sample requires several post-growth processing steps; whereas vapor deposition demands relatively high temperature (\textgreater 500 \si{\degreeCelsius}) yet a shorter time.
+Only a brief introduction will be given here, since these efforts has been well documented in several review articles.\cite{He2003} Most of these methods can be categorized into two groups: solution-based hydrothermal procedures \citep{Li2002b,Xia2006,Li2006a,Camacho-Bragado2006} and chemical vapor deposition approaches.\citep{Zeng1998,Li2002c,Li2002d,Zhou2003b,Fibers2007,Yan2009} Both methods have their own merits.
+Hydrothermal process usually needs lower temperature(\textless 300 \si{\degreeCelsius}), but the reaction often requires tens of hours, and the sample requires several post-growth processing steps; whereas vapor deposition demands relatively high temperature (\textgreater 500 \si{\degreeCelsius}) with a few hours reaction time.
 Both methods are scalable for industrial applications.
 However, the hydrothermal treatment seems to allow more  nanostructures control than does the vapor deposition method.
-Nanobelts,\cite{Li2002b} helical nanosheets, nanoflowers, prims-like rods,\cite{Li2006a} and nanoribbons\cite{Camacho-Bragado2006} were obtained by the former one while nanoflakes,\cite{Chen2009} nanobelts,\cite{Hu2009} and nanowires\citep{Zhou2003b,Chen2011b} dominated the product morphology for the latter one.
+Nanobelts,\cite{Li2002b} helical nanosheets, nanoflowers, nanorods,\cite{Li2006a} and nanoribbons\cite{Camacho-Bragado2006} were obtained by the former one while nanoflakes,\cite{Chen2009} nanobelts,\cite{Hu2009} and nanowires\citep{Zhou2003b,Chen2011b} dominated the product morphology for the latter one.
 The assistance of Au catalyst in vapor deposition only altered the orientation\cite{Yan2009} or served as preferred nucleation sites\cite{Cai2011} without producing new \ce{MoO3} structures.
@@
 
-Silicon substrates was first cleaned according to the procedures stated in Sec.~\ref{ch2sub} on page~\pageref{ch2sub} and directly used in non-catalyst-assisted experiment.
+Silicon substrate was first cleaned according to the procedures stated in Sec.~\ref{ch2sub} on page~\pageref{ch2sub} and directly used in non-catalyst-assisted experiment.
 In catalyst-assisted growth, hydrophilic Si substrates were first drop-cast with \ce{NaOH} (or \ce{KI}, \ce{Na2CO3}) solution (54 $\mu$L 10 mM) and then air dried in a chemical fume hood before experiment.
@@
 For \ce{MoO3} non-catalytic growth, this study observed micro-flakes morphology, as shown in Fig.~\ref{fig:mosisem}.
-Most flakes exhibited rectangular shape with average thickness of one micron and standard deviation $\sigma_D$ of $0.34 \mu$m.
+Most flakes exhibited rectangular shape with average thickness of one micrometer and standard deviation $\sigma_D$ of $0.34$ $\mu$m.
 % sem in (31210-31510) batches
@@
 \end{figure}
-The Raman spectrum of the as-synthesized specimen also closely matched \ce{MoO3} features in previous studies.\cite{Dixit1986,Silveira2012} During m-Raman measurement, the laser spot was carefully focused onto the \ce{MoO3} flakes, and several inspections on different positions were observed to ensure the reproductivity of spectra data.
+The Raman spectrum of the as-synthesized specimen also closely matched \ce{MoO3} features observed in previous studies.\cite{Dixit1986,Silveira2012} During m-Raman measurement, the laser spot was carefully focused onto the \ce{MoO3} flakes, and several inspections on different positions were observed to ensure the reproductivity of spectra data.
 As shown in Fig.~\ref{fig:moram}, 14 distinct bands were well resolved.
@@
 The 819 \si{cm^{-1}} peak arose from doubly coordinated oxygen stretching mode between two octahedral.
-The 996 \si{cm^{-1}} peak was from unshared oxygen stretching mode.\cite{Siciliano2009} The Rama symmetry assignment was summarized in Table~\ref{tab:moram}.
+The 996 \si{cm^{-1}} peak was from unshared oxygen stretching mode.\cite{Siciliano2009} The Raman symmetry assignment is summarized in Table~\ref{tab:moram}.
 % raman assign
@@
 
-All growth time of samples prepared in Sec.~\ref{sec:naohsi} was 2 h, the same as that in Sec.~\ref{sec:nonsi}.
+All samples in Sec.~\ref{sec:naohsi} were grown for 2 h, the same as that in Sec.~\ref{sec:nonsi}.
 The only difference in growth conditions from Sec.~\ref{sec:nonsi} was the Si substrate treatment.
@@
 The Raman spectra of sodium molybdates was featured with multiple strong peaks located between 800 and 1000 \si{cm^{-1}}, which was referred as high-frequency region hereafter.
-\ce{MoO3} phase show two peaks in this region with the strongest one at about 820 \si{cm^{-1}}; \ce{Na2Mo2O7} phase exhibited four peaks in this region with the strongest one moving to 937 \si{cm^{-1}}, whereas \ce{Na2Mo4O13} phase show even more peaks in the high-frequency region with a doublet at 962 and 970 \si{cm^{-1}}, respectively.\cite{Schofield2005,Saraiva2011} As predicted by the phase diagram (Fig.~\ref{fig:ch4pd}), Raman spectra identified \ce{Na2Mo2O7} phase in the 0.1 sccm growth (Fig.~\ref{fig:ch4oxy}b), and \ce{Na2Mo4O13} phase on the particles in the rest three growths (Fig.~\ref{fig:ch4oxy}e, h, and k).
+\ce{MoO3} phase show two peaks in this region with the strongest one at about 820 \si{cm^{-1}}; \ce{Na2Mo2O7} phase exhibited four peaks in this region with the strongest one moving to 937 \si{cm^{-1}}, whereas \ce{Na2Mo4O13} phase show even more peaks in the high-frequency region with a doublet at 962 and 970 \si{cm^{-1}}, respectively.\cite{Schofield2005,Saraiva2011} As predicted by the phase diagram (Fig.~\ref{fig:ch4pd}), Raman spectra identified \ce{Na2Mo2O7} phase in the 0.1 sccm growth (Fig.~\ref{fig:ch4oxy}b), and \ce{Na2Mo4O13} phase on the particles in the other three growths (Fig.~\ref{fig:ch4oxy}e, h, and k).
 This observation supported the previous hypothesis about the reaction sequences on NaOH-Si substrate (Formula~\ref{eq:pd}).
@@
 The morphologies of second series experiment at constant \ce{O2} flow and varied growth time were shown in Fig.~\ref{fig:ch4ev}.
-The 15 min and 30 min growth show that dense arrays of \ce{MoO3} forked nanoplates with a length of hundreds of microns covering the substrate areas at different temperatures.
+The 15 min and 30 min growth show that dense arrays of \ce{MoO3} forked nanoplates with a length of hundreds of micrometers covering the substrate areas at different temperatures.
 With the increase of the growth time, these nanoplates kept growing and became larger, longer, and denser.
@@
 To reveal the growth mechanisms for the long 1D structures in the second stage, specimens were carefully examined to locate the catalyst particles.
-Small catalyst particles ranging from several hundred nanometers to several microns were found at different locations of these long 1D structures.
-As shown in Fig.~\ref{fig:ch4edx1} and Fig.~\ref{fig:ch4edx2}, EDX element analysis confirmed the presence of Na, Mo, and O in these particles, indicating the particles were sodium molybdate catalysts.
+Small catalyst particles ranging from several hundred nanometers to several micrometers were found at different locations of these long 1D structures.
+As shown in Fig.~\ref{fig:ch4edx1} and Fig.~\ref{fig:ch4edx2}, EDX element analysis confirmed the presence of Na, Mo, and O in these particles, suggesting the particles were sodium molybdate catalysts.
 
@@
 It could be of difficulty to observe the sodium molybdate particles on the as-synthesized belts and towers due to the following two factors, one is the consumption of catalysts, such as evaporation; the other is the unpredictable location of the catalyst.
-Unlike the conventional \gls{vls} growth where the catalysts were predominantly found at the tip of 1D nanostructures, the catalyst in current study were mostly found at the side wall of long nanobelts, and the location could be on the tip or several microns away from the tip.
+Unlike the conventional \gls{vls} growth where the catalysts were predominantly found at the tip of 1D nanostructures, the catalyst in this study were mostly found at the side wall of long nanobelts, and the location could be on the tip or several microns away from the tip.
 As for the microtowers, it was even rare to observe Na element.
@@
 Some belt-like growth was visible on reaction chamber walls, suggesting the evaporation and transport of \ce{Na_xMoO3} vapor phase;
-\item Using NaOH treated hydrophobic substrates, dense tower array growth was found along the edge areas or molten periphery of particles, where 5 min growth already show the initial stage of tower with diameter about 1 $\mu$ m, which increased to 10 $\mu$ m in prolonged growth.
+\item Using NaOH treated hydrophobic substrates, dense tower array growth was found along the edge areas or molten periphery of particles, where 5 min growth already show the initial stage of tower with diameter about 1 $\mu$ m, which increased to 10 $\mu$ m with prolonged growth.
 \end{enumerate}
@@
 \item Because of the evaporation, the catalyst particles may become too small to be detected.
-Some particles could even disappeared terminating the catalyzed growth, which may explain the growth of the microtowers with a flat top.
+Some particles could even have disappeared terminating the catalyzed growth, which may explain the growth of the microtowers with a flat top.
 \end{enumerate*} The evaporation and nucleation of catalyst not only promoted the growth of the 1D structures in the second stage growth, they also shaped the morphologies of these 1D structures.
@@
 In analogy to the \ce{Na2MoO4}-\ce{MoO3} binary phase diagram, other alkali metals, such as Li and K, could also form A-Mo-O alloy at elevated temperature.
-This fact allows for the usage of a variety of alkali metal based material as catalyst to promote \gls{vls} or \gls{vss} growth of \ce{MoO3}.
-Two group of experiments have been performed in this study; the first one used \ce{KI} and \ce{Na2CO3} treated Si substrate and the second one used alkali metal ions containing substrate, including ITO/glass, glass, and mica.
+This has potential for using a variety of alkali metal based material as catalysta to promote \gls{vls} or \gls{vss} growth of \ce{MoO3}.
+Two groups of experiments have been performed in this study; the first one used \ce{KI} and \ce{Na2CO3} treated Si substrate and the second one used alkali metal ions containing substrate, including ITO/glass, glass, and mica.
 Fig.~\ref{fig:ch4al1}a-b show the long belt growth on KI treated Si substrate and the forked plate growth on \ce{Na2CO3} treated Si, respectively.
@@
 
-Fig.~\ref{fig:ch4al2}a-c illustrated microtowers grown on ITO glass, sword-shape belts on glass, and nanoblets growth on mica, respectively.
+Fig.~\ref{fig:ch4al2}a-c illustrated microtowers grown on ITO glass, sword-shape belts on glass, and nanobelts growth on mica, respectively.
 The towers on ITO glass exhibited stacking features.
@@
 Considering the adjusted ratio, Na contents should be much more when using glass substrate than using NaOH-Si substrate.
-Another important factor was the evaporation of sodium molybdates.
-However, few relevant report could be found in literature.
-Only one was reported by \citeauthor{Kazenas2010}.\cite{Kazenas2010} The partial pressure of \ce{Na2MoO4} was calculated to be 0.2 mTorr at 800 \si{\degreeCelsius} and $3.5\times 10^{-3}$ mTorr at 670 \si{\degreeCelsius}.\footnote{$\log P(atm)= -13794/T + 6.19$}
+Another important factor was the evaporation of sodium molybdates; however, only one relevant report by \citeauthor{Kazenas2010} could be found in literature.\cite{Kazenas2010} The partial pressure of \ce{Na2MoO4} was calculated to be 0.2 mTorr at 800 \si{\degreeCelsius} and $3.5\times 10^{-3}$ mTorr at 670 \si{\degreeCelsius}.\footnote{$\log P(atm)= -13794/T + 6.19$}
 
@@
 The optical properties of the as-grown specimen were evaluated using \gls{drs} method.
-Fig.~\ref{fig:modrs} show the hemisphere diffuse reflection spectrum from 800 nm to 250 nm, where the diffuse reflection $R_{dff}$ kept increasing from 27\% to 33\% when incident wavelength scanned from 800nm to about 400 nm; then, $R_{dff}$ dropped sharply to 15\% between 400 nm and 300 nm.
+Fig.~\ref{fig:modrs} show the hemisphere diffuse reflection spectrum from 800 nm to 250 nm, where the diffuse reflection $R_{dff}$ kept increasing from 27\% to 33\% when incident wavelength scanned from 800 nm to about 400 nm; then, $R_{dff}$ dropped sharply to 15\% between 400 nm and 300 nm.
 The KMT function fitting was used to estimated the energy gap, as displayed in Fig.~\ref{fig:mokmt}.
@@
 Another reflection peak was found at 260 nm, illustrating there is more complex electronic band structures for \ce{MoO3} above 4 eV.
-As a comparison, the estimated energy gap and results from previous studies was summarized in Table~\ref{tab:mobg}.
+As a comparison, the estimated energy gap and results from previous studies is summarized in Table~\ref{tab:mobg}.
 \begin{table}[htb]
@@
 In this chapter, a new growth model of \ce{MoO3} using alkali metal ions as catalysts was discovered and investigated in depth.
-The growth kinetics was closely inspected using a series of controlled experiments.
+The growth kinetics were closely inspected using a series of controlled experiments.
 A modified vapor-solid-solid mechanism was proposed and favorably verified.

### 2015-03-09 ch-wox/ch-wox.tex
ch 3 post reviewing

@@
 
-\section{Results and Discussion on 1D WO$_3$ Nanowire}
+\section{Results and Discussion on Tungsten Oxide Nanowires}
 \subsection{Tungsten Oxides: Impurities and Residual Effects}\label{sec:nawox}
@@
 Four kinds of tungsten powder sources were used, and the sodium impurity effect was throughly studied.
-\ce{Na5W14O44} NW was first reported from this study; the crystal structure was investigated in details, and HRTEM images were obtained.
+\ce{Na5W14O44} NW was first reported from this study; the crystal structure was investigated in detail, and HRTEM images were obtained.
 Besides, the Raman vibrational spectroscopy of \ce{Na5W14O44} was also identified.

### 2015-03-09 ch-wox/part1.tex
ch 3 post reviewing

@@
 The \ce{W_nO_{3n-1}} ($n \geq 2$) exhibit $\{ 001 \}$ \gls{cs} structure.
-Chemical formula corresponding to n=2, 3, 4, 5 and 6 are \ce{W2O5=WO_{2.5}}, \ce{W3O8=W_{2.67}}, \ce{W4O_{11}=WO_{2.75}}, \ce{W5O_{14}=WO_{2.8}}, and \ce{W6O_{17}=WO_{2.83}}, which indicates the existence of a oxygen deficient plane at every $n$ row.
+Chemical formula corresponding to n=2, 3, 4, 5 and 6 are \ce{W2O5=WO_{2.5}}, \ce{W3O8=WO_{2.67}}, \ce{W4O_{11}=WO_{2.75}}, \ce{W5O_{14}=WO_{2.8}}, and \ce{W6O_{17}=WO_{2.83}}, which indicates the existence of a oxygen deficient plane at every $n$ row.
 Actually the value $x$ in \ce{WO_x} could almost continuously vary within a range of 2.5 to 3.
@@
 On basis of this property, \gls{ecd} of tremendous energy saving potential is conceptualized and some products have already been commercialized (i.e.
-smart window\footnote{"We did a case study in five cities, and the average savings in commercial buildings are about 25 percent of the heating, ventilation, and air-conditioning energy use annually," says CEO of View, Inc.}), although the materials used is not clear.
+smart window\footnote{"We did a case study in five cities, and the average savings in commercial buildings are about 25 percent of the heating, ventilation, and air-conditioning energy use annually," said CEO of View, Inc.}), although the materials used is not clear.
 
-In the past decades, tons of works have been devoted to understanding the chromogenic phenomena in \ce{WO3}. Several key results were highlighted as reviewed in Ref.\cite{Deb2008}:
+In the past decades, substantial works have been devoted to understanding the chromogenic phenomena in \ce{WO3}. Several key results were highlighted as reviewed in Ref.\cite{Deb2008}:
 \begin{itemize}
@@
 As the chemical formula \ce{WO3} suggested, the most straightforward way is heating metallic tungsten (W) in various forms,\cite{Zhou2005a,Cao2009,Hsieh2010} i.e., powders, foils, and wires.
-Actually \ce{WO_x} \glspl{nw}\footnote{$x$ is between 2 and 3} were observed when directly heating W wires.\cite{Gu2002a} Due to the extreme high melting point of W, it requires very high temperature (say, above 1100 \si{\degreeCelsius}) to produce large amount of growth species.
+Actually \ce{WO_x} \glspl{nw}\footnote{$x$ is between 2 and 3} were observed when directly heating W wires.\cite{Gu2002a} Due to the extreme high melting point of W, it requires high temperature (say, above 1100 \si{\degreeCelsius}) to produce large amount of growth species.
 Therefore scalable growth seems difficult at low temperature range unless other activation mechanisms are used.

### 2015-03-17 ch-intro/ch-intro.tex
post review step -2

@@
 \includegraphics[width=0.5\textwidth]{blackbody1.pdf}
-\caption[Spectral radiance of blackbody at 0, 50 and 100 \si{\degreeCelsius} predicated by Planck's Law]{Spectral radiance of blackbody at 0, 50 and 100 \si{\degreeCelsius} predicated by Planck's Law.}
+\caption[Spectral radiance of blackbody at 0, 50 and 100 \si{\degreeCelsius}]{Spectral radiance of blackbody at 0, 50 and 100 \si{\degreeCelsius} predicated by Planck's Law.}
 \label{fig:introbb}
@@
 
-In regarding to the contents of this study, electrochromic applications based on \gls{tmo} nanowires will benefit from the reduced diffusion depth by eliminating the deficiency of ions accumulation in amorphous oxide thin film devices, which in turn leads to shorter response time and higher coloration efficiency.\cite{Huang2008a,Scherer2012} And photocatalytic applications using \gls{tmo} nanostructures could harvest the huge surface area on which unsaturated bonds reside, thereby enabling a much higher efficiency.\cite{Mills1993,Merki2011,Chen2011b}
-
-To fully use nano-engineering, one must just be as aware of the limitations as one is of its advantages; for example, an obvious disadvantage is the difficulty of device fabrication using nanomaterials due to the size and requirements of new integration processes.
+In regarding to the contents of this study, electrochromic applications based on \gls{tmo} nanowires will benefit from the reduced diffusion depth by eliminating the deficiency of ions accumulation in amorphous oxide thin film devices, which in turn leads to shorter response time and higher coloration efficiency.\cite{Huang2008a,Scherer2012} And photocatalytic applications using \gls{tmo} nanostructures could harvest the huge surface area on which unsaturated bonds reside, thereby enabling a much higher efficiency.\cite{Mills1993,Merki2011,Chen2011b} To fully use nano-engineering, one must just be as aware of the limitations as one is of its advantages; for example, an obvious disadvantage is the difficulty of device fabrication using nanomaterials due to the size and requirements of new integration processes.
 There also exist some uncertainty as to the energy band modification present in nanostructures, which could be either useful or not depending on the application.\cite{Wang2012}

### 2015-03-17 ch-moox/moox.tex
post review step -2

@@
 \includegraphics[width=0.9\textwidth]{MoO3_SEM_a.jpg}
-\caption[Effect of alkali metal based catalysts on the morphology of \ce{MoO3} depositions]{Effect of alkali metal based catalysts on the morphology of \ce{MoO3} depositions: (a) SEM image of rectangular nanoplates grown without catalysts.
+\caption[Effect of alkali metal based catalysts on \ce{MoO3} depositions]{Effect of alkali metal based catalysts on the morphology of \ce{MoO3} depositions: (a) SEM image of rectangular nanoplates grown without catalysts.
 (b-f) SEM images of different morphologies grown with NaOH catalysts: (b) nanobelts grown on top of dense array of nanoplates,(c) close-up view of the forked nanoplates from an area indicated by the square in Fig.~\ref{fig:ch4sem2by3}, (d) long nanobelts, (e) side-view of ultra-long microbelts, and (f) side-view of microtowers.
@@
 \centering
-\caption{Comparison of Raman shift (\si{cm^{-1}}) of sodium molybdates and molybdenum oxide}\label{tb:moo3ram}
+\caption[Raman shift of sodium molybdates and molybdenum oxide]{Comparison of Raman shift (\si{cm^{-1}}) of sodium molybdates and molybdenum oxide}\label{tb:moo3ram}
 \begin{tabular}{lllllllll}
@@
 \includegraphics[width=0.9\textwidth]{mooe_sem_ev}
-\caption[Growth evolution of the second stage of catalyst-assisted growth of \ce{MoO3} 1D structures]{Growth evolution of the second stage of catalyst-assisted growth of \ce{MoO3} 1D structures: SEM images of the deposition at different growth temperatures with growth time of row 1: 15 min, row 2: 30 min, row 3: 60 min, and row 4: 90 min.}
+\caption[Evolution of the second stage on \ce{MoO3} growth]{Growth evolution of the second stage of catalyst-assisted growth of \ce{MoO3} 1D structures: SEM images of the deposition at different growth temperatures with growth time of row 1: 15 min, row 2: 30 min, row 3: 60 min, and row 4: 90 min.}
 \label{fig:ch4ev}
@@
 \includegraphics[width=0.5\textwidth]{MoO3_SFig_EDX}
-\caption[SEM images and EDS spectra identifying the location, morphology, and composition of the catalyst particles on the nanobelt structures]{SEM images and EDS spectra identifying the location, morphology, and composition of the catalyst particles on the nanobelt structures: (a-b) a catalyst particle (I) in the middle of a nanobelt (II), (c-d) two catalyst particles (I and II) leading the growth of two perpendicular nanobelts.}
+\caption[Identifying the catalyst particles on the nanobelt structures]{SEM images and EDS spectra identifying the location, morphology, and composition of the catalyst particles on the nanobelt structures: (a-b) a catalyst particle (I) in the middle of a nanobelt (II), (c-d) two catalyst particles (I and II) leading the growth of two perpendicular nanobelts.}
 \label{fig:ch4edx1}
@@
 \includegraphics[width=0.5\textwidth]{MoO3_SFig_EDX_tower}
-\caption[SEM images and EDS spectra for identifying the location, morphology, and composition of the catalysts on the microtower structures]{SEM images and EDS spectra for identifying the location, morphology, and composition of the catalysts on the microtower structures: (a-b) a tiny catalyst particle (I) on top of a small cone shaped microtower (II), and (c-d) a catalyst particle (III) on a large and short microtower (IV).}
+\caption[Identifying the catalysts on the microtower structures]{SEM images and EDS spectra for identifying the location, morphology, and composition of the catalysts on the microtower structures: (a-b) a tiny catalyst particle (I) on top of a small cone shaped microtower (II), and (c-d) a catalyst particle (III) on a large and short microtower (IV).}
 \label{fig:ch4edx2}

### 2015-03-17 ch-tms/tms.tex
post review step -2

@@
 This study leverages a home-built micromanipulator apparatus to transfer the nanostructures from growth substrates to TEM grids.
-This transferring technique has allowed for correlating TEM and micro-Raman measurement on individual \ce{WO3}-\ce{WS2} core-shell nanowire and enhancing the understanding of structure-property relations, which would otherwise be blurred in conventional ensemble averaged methods.
-\ce{WO3}-\ce{WS2} heterostructure was chosen due to its potential applications in photocatalysis and hydrogen evolution.\cite{DiPaola1999,Chen2011b}
+This transferring technique has allowed for correlating TEM and micro-Raman measurement on individual \ce{WO3}-\ce{WS2} core-shell nanowires and enhancing the understanding of structure-property relations, which would otherwise be blurred in conventional ensemble averaged methods.
+\ce{WO3}-\ce{WS2} heterostructure was chosen due to its potential applications in photocatalysis and hydrogen evolution reaction.\cite{DiPaola1999,Chen2011b}
 
@@
 The \ce{WO3}-\ce{WS2} core-shell nanowires were fabricated using a sulfurization process based on the \ce{WO3} NWs prepared from the seeded growth method in Chapter~3, Sec.~\ref{sec:sgfg}.
-For the sake of completeness, schematic layout of the two-step growth were illustrated in Fig.~\ref{fig:ch5grow}, including the seeded growth and subsequent sulfurization process.
+For the sake of completeness, schematic layout of the two-step growth is illustrated in Fig.~\ref{fig:ch5grow}, including the seeded growth and subsequent sulfurization process.
 % cvd NW growth
@@
 \includegraphics[width=0.5\textwidth]{cs_growth_lbd}
-\caption[Schematic diagrams of seeded growth of \ce{WO3} NW and sulfurization process]{Schematic diagrams of (a) seeded growth of \ce{WO3} NW and (b) sulfurization process. }
+\caption[Schematic diagrams of two-step synthesis process]{Schematic diagrams of (a) seeded growth of \ce{WO3} NW and (b) sulfurization process. }
 \label{fig:ch5grow}
@@
 \section{Results and Discussion}
-\subsection{Ensemble Measurements on Core-Shell NWs Array}
+\subsection{Ensemble Measurements on Core-Shell Nanowires Array}
 
@@
 \includegraphics[width=0.7\textwidth]{ws2_sem_edx_labeled}
-\caption[Morphology and composition analysis on the as-synthesized \ce{WO3}-\ce{WS2} core-shell structures]{Morphology and composition analysis on the as-synthesized \ce{WO3}-\ce{WS2} core-shell structures.
+\caption[Morphology and composition analysis on the core-shell structures]{Morphology and composition analysis on the as-synthesized \ce{WO3}-\ce{WS2} core-shell structures.
 (a) Low magnification and (b) high magnification SEM images showing the NWs morphologies after sulfurization.
@@
 \includegraphics[width=0.7\textwidth]{cs_tem_g3_lbd}
-\caption[HRTEM imaging on one tapered core-shell nanowire showing fluctuation of layer numbers]{HRTEM imaging on one tapered core-shell nanowire showing fluctuation of layer numbers.}
+\caption[HRTEM imaging on one tapered core-shell nanowire]{HRTEM imaging on one tapered core-shell nanowire showing fluctuation of layer numbers.}
 \label{fig:ch5ws2tem4}
@@
 \includegraphics[width=0.7\textwidth]{core-shell_void_growth}
-\caption[HRTEM imaging on one core-shell nanowire showing consumed core]{HRTEM imaging on one core-shell nanowire showing consumed core.}
+\caption[HRTEM imaging on one nanowire showing consumed core]{HRTEM imaging on one core-shell nanowire showing consumed core.}
 \label{fig:ch5ws2tem2}
@@
 
-\subsection{TEM-Raman Integrated Study on Individual NW}\label{tms:raman}
+\subsection{An Integrated TEM-Raman Study on Individual Nanowire}\label{tms:raman}
 
@@
 \subfloat[]{\label{fig:stk3}\includegraphics[width=0.30\textwidth]{stacking3}}
-\caption[Optical reflectance simulation on three different \ce{WS2} layer stacking configurations]{Optical reflectance simulation on three different \ce{WS2} layer stacking configurations.}
+\caption[Optical reflectance simulation on three stacking configurations]{Optical reflectance simulation on three  \ce{WS2} layer stacking configurations.}
 \label{fig:ch5ws2stk}
@@
 \includegraphics[width=0.7\textwidth]{ws2_sio2_all}
-\caption[Raman spectrum acquired on the middle spot of core-shell NW (inset) using 532 nm.
-The $x$ axis is in logarithmic scale]{Raman spectrum acquired on the middle spot of core-shell NW (inset) using 532 nm.
-The $x$ axis is in logarithmic scale.}
+\caption[Raman spectrum on the middle spot of core-shell NW]{Raman spectrum acquired on the middle spot of core-shell NW (inset) using 532 nm. The $x$ axis is in logarithmic scale.}
 \label{fig:ws2ramall}
@@
 \includegraphics[width=0.5\textwidth]{ws2_sio2_all_blue}
-\caption[Raman spectrum acquired on the middle spot of core-shell NW shown in the inset of Fig.~\ref{fig:ws2ramall}]{Raman spectrum acquired on the middle spot of core-shell NW shown in the inset of Fig.~\ref{fig:ws2ramall}.}
+\caption[Raman spectrum acquired on the middle spot]{Raman spectrum acquired on the middle spot of core-shell NW shown in the inset of Fig.~\ref{fig:ws2ramall}.}
 \label{fig:ws2ramblue}
@@
 \subfloat[]{\label{fig:blue}\includegraphics[width=0.45\textwidth]{ws2_sio2_raman_blue}}
-\caption[Raman scattering from (a) 532 nm and (b) 441 nm excitation scanned along the core-shell NW]{Raman scattering from (a) 532 nm and (b) 441 nm excitation scanned along the core-shell NW.}
+\caption[Raman scattering from two excitation wavelength]{Raman scattering from (a) 532 nm and (b) 441 nm excitation scanned along the core-shell NW.}
 \label{fig:ws2ram3site}
@@
 Sodium impurity effect in tungsten powder source was revealed, and the formation of \ce{Na5W14O44} nanowire was first reported.
-Partially enlightened by this discovery, a new VSS growth mechanism of \ce{MoO3} was found, and the growth dynamics was systematically probed.
+Partially enlightened by this discovery, a new VSS growth mechanism of \ce{MoO3} was hypothesized, and the growth dynamics was systematically probed.
 Comprehensive electron microscopy characterizations were performed on both \ce{WO3} and \ce{MoO3}.
@@
 As an example, preliminary results of \ce{WO3} NWs growth using \ce{NaOH} treated Si substrate and controlled \ce{MoO3} 1D nanostructures growth on glass were presented in Sec.~\ref{sec:nawo} and Sec.~\ref{sec:mogls}, respectively.
-
-Besides, seeded growth of \ce{WO3} was demonstrated to be an effective and scalable approach for obtaining single crystalline 1D \ce{WO3} NWs.
+Seeded growth of \ce{WO3} was demonstrated to be an effective and scalable approach for obtaining single crystalline 1D \ce{WO3} NWs.
 Based on these \ce{WO3} nanowires, \ce{WO3}-\ce{WS2} heterostructure was synthesized using a simple sulfurization process, and single-walled \ce{WS2} tubular core-shell nanowire was observed.
@@
 
-\section{Preliminary results of NaOH WO$_3$ growth}\label{sec:nawo}
+\section{Preliminary Results on Catalytic Growth of Tungsten Oxide}\label{sec:nawo}
 The growth conditions almost remained the same as that of the non-seeded \ce{WO3} growth except that the substrate were located at 7.5 inch (refer to page~\pageref{sec:woxnonseed} for details).
@@
 \includegraphics[width=0.5\textwidth]{naoh-wo3_edx}
-\caption[Composition analysis on \ce{NaOH} \ce{WO3} growth NWs identifying small fraction Na content]{Composition analysis on \ce{NaOH} \ce{WO3} growth NWs identifying small fraction Na content.}
+\caption[Composition analysis on \ce{NaOH} \ce{WO3} growth NWs]{Composition analysis on \ce{NaOH} \ce{WO3} growth NWs identifying small fraction Na content.}
 \label{fig:naohwedx}
@@
 
-\section{Preliminary results of MoO$_3$ growth on glass}\label{sec:mogls}
+\section{Preliminary Results on Molybdenum Oxide Growth Using Glass}\label{sec:mogls}
 
@@
 700    &  10   & 60  &   particle almost all on tip of belts, many towers \\
-800    &  1    & 15  &   tens $\mu$m belt with sharp edge(100 nm thick, and 1micro wide) dominates\\
+800    &  1    & 15  &   tens $\mu$m belts with sharp edge (100 nm thick and 1 micrometer wide) dominate\\
 800    &  1    & 60  &   exhibiting ITO features, particles on tips of belt, many tower like structures\\
@@
 %raman data on moo3 glass available
+
 For future work, the author suggested several following perspectives:

### 2015-03-17 ch-tms/tmspart.tex
post review step -2

@@
 \section{Introduction}
-\subsection{Properties and Applications of WS$_2$}
+\subsection{Properties and Applications of Tungsten Disulfide}
 Tungsten disulfide (\ce{WS2}) is a group VI dichalcogenide semiconductor compound.
@@
 Two other crystal structures were found in man-made \ce{WS2}, i.e.
-1T and 3R, where 3R can be prepared by bromine (Br) chemical vapor transport (CVT) method \cite{Schutte1987} and 1T was generally found in alkaline intercalated \ce{WS2}.\cite{Yang1996a, Enyashin2011} As a reference, the lattice dimensions of \ce{MoS2} and \ce{WS2} were summarized in Table~\ref{tab:ms2lattice}.
+1T and 3R, where 3R can be prepared by bromine (Br) chemical vapor transport (CVT) method \cite{Schutte1987} and 1T was generally found in alkaline intercalated \ce{WS2}.\cite{Yang1996a, Enyashin2011} As a reference, the lattice dimensions of \ce{MoS2} and \ce{WS2} are summarized in Table~\ref{tab:ms2lattice}.
 %lattice
@@
 
-\subsection{Review of Synthesis Methods of WS$_2$}
+\subsection{Review of Synthesis Methods of Tungsten Disulfide}
 Shortly after the discovery of \gls{cnt} in 1991,\cite{Iijima1991} its transition metal dichalcogenides (TMDC) counterparts, i.e.
@@
 All these methods can be applied to the growth of TMDC few layer structures, directly or with some modifications.
-Among all the members of TMDC nanotubes, \ce{WS2} and \ce{MoS2} NTs were probably the most well investigated.\cite{Homyonfer1997,Tenne1998,Frey1998,Frey1999,Rothschild2000,Zak2000} The reaction mechanism of \ce{WO3} with \ce{H2}/\ce{H2S} was thoroughly studied,\cite{Feldman1998} and high yield synthesis approach has been established.\cite{Margolin2004} For \ce{WO3} nanoparticles precursor, it was found that the simultaneous reduction and sulfurization was essential for encapsulation of fullerene like \ce{WS2} structures from the oxide nanoparticles.
+Among all the members of TMDC nanotubes, \ce{WS2} and \ce{MoS2} NTs were probably the most well investigated.\cite{Homyonfer1997,Tenne1998,Frey1998,Frey1999,Rothschild2000,Zak2000} The reaction mechanism of \ce{WO3} with \ce{H2}/\ce{H2S} was thoroughly studied,\cite{Feldman1998} and a high yield synthesis approach has been established.\cite{Margolin2004} For \ce{WO3} nanoparticles precursor, it was found that the simultaneous reduction and sulfurization was essential for encapsulation of fullerene like \ce{WS2} structures from the oxide nanoparticles.
 During the sulfurization process, remaining oxide core was gradually reduced and transformed into an ordered superlattice of $\{ 001 \}$ \gls{cs} planes.
@@
 For precursor of \ce{WO3} nanowires, \citeauthor{Feldman1996} proposed that TMDC nanotubes growth began with the reduced \ce{WO3} phases, in particular \ce{W_{18}O_{49}}.\cite{Feldman1996} It is worth noting that \ce{MS2} can be prepared by direct sulfurization from its oxides phase, but reaction \cee{MO3 + Se \rightarrow MSe2} will not proceed unless other reducing agents, e.g.
-\ce{H2}, are used simultaneously.\cite{Tsirlina1998} This fact highlights that sulfur is rather radical at elevated temperature.
+\ce{H2}, are used simultaneously.\cite{Tsirlina1998} This fact highlights that sulfur is chemically radical at elevated temperature.
 
@@
 Parallel with the scenario of CNT and graphene, TMDC few layer structures have attracted intensive research efforts recently.
-These atomic TMDC layers exhibited many appealing features, i.e., indirect-to-direct band gap transition,\cite{Splendiani2010} and became a promising candidate in energy harvesting, optoelectronics, and photocatalytic applications.
+These atomic TMDC layers exhibits many appealing features, i.e., indirect-to-direct band gap transition,\cite{Splendiani2010} and became a promising candidate in energy harvesting, optoelectronics, and photocatalytic applications.
 For scientific research purpose, exfoliation by liquid\cite{Smith2011} or mechanical methods\cite{Lee2010a} can provide sufficient materials, yet CVD synthesis of thickness controllable 2D TMDC is stills highly desired, which holds the greatest potential for high yield production of \ce{MS2}.
@@
 The substrate and \ce{MoO3} source distance was critical in determining the growth density.
-The synthesis strategy in Refs.\cite{Lee2013,Lee2012b} was briefly mentioned as well, where \gls{ptas} treated substrate was found to promote the deposition, while KCl treated substrates did not; small carrier gas flow was preferred (1 sccm \ce{N2}).
+The synthesis strategy in Refs.\cite{Lee2013,Lee2012b} was briefly mentioned as well, where perylene-3,4,9,10-tetracarboxylic acid tetrapotassium salt (PTAS) treated substrate was found to promote the deposition, while KCl treated substrates did not; small carrier gas flow was preferred (1 sccm \ce{N2}).
 It was also noted that the \ce{MoS2} flakes morphology seemed more uniform in Ref\cite{VanderZande2013} than that in Ref\cite{Lee2012b}.
@@
 
-\subsection{Raman on WS$_2$: Bulk, Few Layer and Nanotube}\label{sec:ntram}
+\subsection{Raman on Tungsten Disulfide: Bulk, Few Layer, and Nanotube}\label{sec:ntram}
 
@@
 The enhancement of the total Raman cross section at excitonic resonance in which excitons served as the intermediate state was stronger compared to that of interband resonance.
-The strong enhancement at excitonic resonance was attributed to the characteristics of excitons in layered materials such as large binding energy, enhanced oscillator strength, and small damping constant.\cite{Zhao2013} \citeauthor{Chung1998} grew \ce{WS2} film using \ce{W(CO)6} and \ce{H2S} precursor.\cite{Chung1998} Raman spectra ($\lambda=632 nm$) on films with non-parallel orientation revealed the presence of shoulder mode under $A_{1g}$, which was assigned to \gls{la} and \gls{ta} phonon coupling.
+The strong enhancement at excitonic resonance was attributed to the characteristics of excitons in layered materials such as large binding energy, enhanced oscillator strength, and small damping constant.\cite{Zhao2013} \citeauthor{Chung1998} grew \ce{WS2} film using \ce{W(CO)6} and \ce{H2S} precursor.\cite{Chung1998} Raman spectra ($\lambda=632$ nm) on films with non-parallel orientation revealed the presence of shoulder mode under $A_{1g}$, which was assigned to \gls{la} and \gls{ta} phonon coupling.
 This coupling process stemmed from disorder-activated zone boundary phonons.

### 2015-03-17 ch-wox/ch-wox.tex
post review step -2

@@
 Two growth configurations were explored, namely non-seeded growth and seeded growth.
+
 % Tungsten powders size and purity
@@
 
-\subsection{Non-seeded growth}\label{sec:woxnonseed}
+\subsection{Non-seeded Growth}\label{sec:woxnonseed}
 
@@
 
-\subsection{Seeded growth}
+\subsection{Seeded Growth}
 In the seeded growth, additional tungsten powders were used on the substrate serving as local seed, on which a dense \ce{WO3} NW array grew.
@@
 With this degree of freedom included, the primary features of the deposition and the associated parameters were summarized in Table~\ref{tab:wot}.
-% \ce{WO_x} ordinary transport results
+%
 \begin{table}[htb]
@@
 Heated at elevated temperatures, the W precursor, quartz tube, and quartz boat were three possible sources for Na.
-The sodium concentration in 3N source was about 20 ppm, as provided by vendor.\footnote{Due to the non-uniform distribution of foreign elements, detection of sodium by EDX is possible although the concentration is below the limit of typical EDX capacity.} The Na concentrations in quartz tube and quartz boat (GE 214 quartz, Wilmad Labglass) were 1 ppm and 0.7 ppm, respectively.
+The sodium concentration in 3N source was about 20 ppm, as provided by vendor.\footnote{Owing to the non-uniform distribution of foreign elements, detection of sodium by EDX is possible although the concentration is below the capacity limit of typical EDX.} The Na concentrations in quartz tube and quartz boat (GE 214 quartz, Wilmad Labglass) were 1 ppm and 0.7 ppm, respectively.
 To verify the major source of Na content coming from 3N powder, control experiments were employed by using W source with higher purities (4N5 or 5N).
@@
 \includegraphics[width=0.8\textwidth]{wox_xrd_series}
-\caption[XRD spectra of the as-synthesized specimen with the increase of growth number from 1 to 5]{XRD spectra of the as-synthesized specimen with the increase of growth number from 1 to 5.}
+\caption[XRD spectra of the as-synthesized specimen]{XRD spectra of the as-synthesized specimen with the increase of growth number from 1 to 5.}
 \label{fig:nawoxxrd}
@@
 \includegraphics[width=0.5\textwidth]{naxwo_xrd_low}
-\caption{Low angle scan of XRD pattern on the as-grown sodium tungsten oxide sample}
+\caption[Low angle XRD pattern on the as-grown sodium tungsten oxide]{Low angle scan of XRD pattern on the as-grown sodium tungsten oxide sample}
 \label{fig:naxrdlow}
@@
 \subfloat[]{\label{fig:nadrs}\includegraphics[width=0.45\textwidth]{uvvis_naxwo2}}
-\caption[UV-Vis and \gls{drs} of \ce{Na5W14O44} NWs on quartz]{UV-Vis and DRS of \ce{Na5W14O44} NWs on quartz: (a) Optical transmission and (b) diffuse reflection spectra.}
+\caption[UV-Vis and DRS of \ce{Na5W14O44} NWs on quartz]{UV-Vis and DRS of \ce{Na5W14O44} NWs on quartz: (a) Optical transmission and (b) diffuse reflection spectra.}
 \label{fig:ch3naxuvvis}

### 2015-03-17 ch-wox/part1.tex
post review step -2

@@
 In addition, a few young fields are not thoroughly explored: field emission, optical storage, thermo-electricity, ferro-electricity, and superconductivity.
-
 In this chapter, a literature review on tungsten oxides and sodium tungsten oxides is introduced first, with focus on technological applications, crystal structures, and synthesis approaches.
@@
 A representative lattice structure is illustrated in Fig.~\ref{fig:wo3oct}.
+These distorted \ce{WO6} octahedra adapt different tilting angles in different phases and edge-sharing octahedra also arise.
+
+The temperature-dependent phase transition and corresponding lattice constants in bulk form is summarized in Table~\ref{tab:wo3phase}.\cite{Zheng2011} \ce{WO3} in monoclinic phase is favored in room temperature; however, a firm assignation of space group to monoclinic phases are still in debate.\cite{Chatten2005} It is noticed that the lattice parameters obtained via \emph{ab initio} calculation closely match the experimental values.\cite{Migas2010a} The phase transition scenarios in nanostructured \ce{WO3} are supposed to be more sophisticated.
+Within Gibbs-Thomson framework, one can generally expect lower transition temperature than their bulk counterparts due to enhanced surface energy.
+Temperature-dependent Raman spectroscopy provided support for this deduction.\cite{Boulova2002}
 \begin{figure}[htb]
@@
 \end{figure}
-These distorted \ce{WO6} octahedra adapt different tilting angles in different phases and edge-sharing octahedra also arise. 
+
+\ce{WO3} is a wide gap n-type semiconductor with valence band top featuring $2p$ states of oxygen and conduction band bottom arising primarily from $5d$ states of tungsten with some mixing of oxygen $2p$ states.\cite{Gillet2004} \citeauthor{Migas2010a} maintained there is essentially identical band dispersion near the gap region in case of $\epsilon$-\ce{WO3}, $\delta$-\ce{WO3}, $\gamma$-\ce{WO3} and $\beta$-\ce{WO3}.\cite{Migas2010a} When there is oxygen vacancy, the Fermi level moves into the conduction band and the gap shrinks by about 0.5 eV.
+\citeauthor{Migas2010a} also pointed out the flat bands at \gls{vbm} and \gls{cbm} could lead to poor transport of holes and electrons, thus may compromising the function in photoelectrochemical cells.
+
+Besides \ce{WO3}, tungsten oxide exists in a series of sub-stoichiometric states.
+The \ce{W_nO_{3n-1}} ($n \geq 2$) exhibit $\{ 001 \}$ \gls{cs} structure.
+Chemical formula corresponding to n=2, 3, 4, 5 and 6 are \ce{W2O5=WO_{2.5}}, \ce{W3O8=WO_{2.67}}, \ce{W4O_{11}=WO_{2.75}}, \ce{W5O_{14}=WO_{2.8}}, and \ce{W6O_{17}=WO_{2.83}}, which indicates the existence of a oxygen deficient plane at every $n$ row.
+Actually the value $x$ in \ce{WO_x} could almost continuously vary within a range of 2.5 to 3.
+\ce{W_{18}O_{49}=\ce{WO_{2.72}}} is an exception without $\{ 001 \}$ CS structure.
+Moreover, the oxygen deficient planes could extend along directions other than $\{ 001 \}$.
+For instance, the $\{ 102 \}$ CS planes appears in \ce{WO_x} where $x$ is within 2.93 to 2.98, and  the $\{ 103 \}$ CS planes for $x$ within 2.87 to 2.93.\cite{Sloan1999} In \ce{WO_x} nanorods, the oxygen deficient planes are conductive, each having atomic thickness and separated by several nm of \ce{WO3} layers.
+Localized surface plasmons could possibly exist on these conductive planes.
+Therefore \gls{sers} applies and single molecule Raman scattering using individual tungsten oxide nanorod has been demonstrated.\cite{Shingaya2013}
 % wo3 phases
@@
 \end{table}
-The temperature-dependent phase transition and corresponding lattice constants in bulk form is summarized in Table~\ref{tab:wo3phase}.\cite{Zheng2011} \ce{WO3} in monoclinic phase is favored in room temperature; however, a firm assignation of space group to monoclinic phases are still in debate.\cite{Chatten2005} It is noticed that the lattice parameters obtained via \emph{ab initio} calculation closely match the experimental values.\cite{Migas2010a} The phase transition scenarios in nanostructured \ce{WO3} are supposed to be more sophisticated.
-Within Gibbs-Thomson framework, one can generally expect lower transition temperature than their bulk counterparts due to enhanced surface energy.
-Temperature-dependent Raman spectroscopy provided support for this deduction.\cite{Boulova2002}
-
-\ce{WO3} is a wide gap n-type semiconductor with valence band top featuring $2p$ states of oxygen and conduction band bottom arising primarily from $5d$ states of tungsten with some mixing of oxygen $2p$ states.\cite{Gillet2004} \citeauthor{Migas2010a} maintained there is essentially identical band dispersion near the gap region in case of $\epsilon$-\ce{WO3}, $\delta$-\ce{WO3}, $\gamma$-\ce{WO3} and $\beta$-\ce{WO3}.\cite{Migas2010a} When there is oxygen vacancy, the Fermi level moves into the conduction band and the gap shrinks by about 0.5 eV.
-\citeauthor{Migas2010a} also pointed out the flat bands at \gls{vbm} and \gls{cbm} could lead to poor transport of holes and electrons, thus may compromising the function in photoelectrochemical cells.
-
-Besides \ce{WO3}, tungsten oxide exists in a series of sub-stoichiometric states.
-The \ce{W_nO_{3n-1}} ($n \geq 2$) exhibit $\{ 001 \}$ \gls{cs} structure.
-Chemical formula corresponding to n=2, 3, 4, 5 and 6 are \ce{W2O5=WO_{2.5}}, \ce{W3O8=WO_{2.67}}, \ce{W4O_{11}=WO_{2.75}}, \ce{W5O_{14}=WO_{2.8}}, and \ce{W6O_{17}=WO_{2.83}}, which indicates the existence of a oxygen deficient plane at every $n$ row.
-Actually the value $x$ in \ce{WO_x} could almost continuously vary within a range of 2.5 to 3.
-\ce{W_{18}O_{49}=\ce{WO_{2.72}}} is an exception without $\{ 001 \}$ CS structure.
-Moreover, the oxygen deficient planes could extend along directions other than $\{ 001 \}$.
-For instance, the $\{ 102 \}$ CS planes appears in \ce{WO_x} where $x$ is within 2.93 to 2.98, and  the $\{ 103 \}$ CS planes for $x$ within 2.87 to 2.93.\cite{Sloan1999} In \ce{WO_x} nanorods, the oxygen deficient planes are conductive, each having atomic thickness and separated by several nm of \ce{WO3} layers.
-Localized surface plasmons could possibly exist on these conductive planes.
-Therefore \gls{sers} applies and single molecule Raman scattering using individual tungsten oxide nanorod has been demonstrated.\cite{Shingaya2013}
-
 Tungsten oxides were probably best known for the electrochromic effect, meaning the coloration (deep blue) and bleaching (transparent) states of \ce{WO3} are reversibly switched upon forward and backward voltage, and the coloration or bleached states remain after disconnecting the voltage.

### 2015-03-17 main.tex
SI info inserted into main text
after format review, bold font in figure caption removed, frontmatter spacing fixed
intro writing after format review
figure caption fixed, proof reading and introduction chapter done
SI papers reading
post review step -2

@@
 \documentclass[12pt,oneside]{book}
-   \usepackage{uncc-thesis} % uncc format specification seems this style should be loaded before other packages
+   \usepackage{unccx} % uncc format specification seems this style should be loaded before other packages
    \input{package_iff.tex} % additonal packages and tweaking
    \input{./FrontMatter/abbre}
-   \makeglossaries
+
 \begin{document}
@@
    \include{./ch-intro/ch-intro}
-    %\include{./ch-intro/ch-instr}
-   % \include{./ch-wox/ch-wox}
-   % \include{./ch-moox/moox} % no tex needed, otherwise there is error
-   % \include{./ch-tms/tms}
-\appendix
+   \include{./ch-intro/ch-instr}
+   \include{./ch-wox/ch-wox}
+   \include{./ch-moox/moox} % no tex needed, otherwise there is error
+   \include{./ch-tms/tms}
+
+%\appendix
   % \glsaddallunused
-    \include{./BackMatter/app1}
+   %\include{./BackMatter/app1}
    %\include{./BackMatter/app2}
@@
 \end{document}
+
+should check how other template deals with before after section skip
+ the belowcaptionskip is \the\belowcaptionskip, and the above is \the\abovecaptionskip, the intextsep is \the\intextsep. and the baselineskip is \the\baselineskip.

### 2015-03-17 misc/paper.tex
post review step -2

@@
 For ionic SC, the barrier height depends strongly on the metal.
+
+\section{Solid State Chemistry}
+
+strain is linearly proportional to the magnitude of stress. 
+\[
+\sigma = E \epsilon
+\]
+where strain has no units, $E$, directly related to the strength of the bonds, is Young's modulus.
+
+Poisson's ratio
+\[
+\nu = - \frac{\partial\epsilon_y}{\partial\epsilon_x}
+\]
+
+Strain energy $E_v = 1/2\sigma\epsilon$.
+
+\textbf{thermodynamics of surfaces} Competition between adopting the lowest energy (internal energy) and adopting an energy state that is more probable (entropy) dictates the ...
+
+Gibbs energy change reflect this point
+\[
+\Delta G= \Delta H - T\Delta S = \Delta H - kT\Delta ln\phi
+\]
+
+Surface energy in unit of energy per area
+\[
+\gamma = \frac{\partial G}{\partial A}_{T,P}
+\]
+
+Energy required to break bonds to increase the area. Increase surface area means increasing the number of unsaturated atoms.
+
+Surface molecular density of many simple crystals is of the order $1\times 10^{15}$.
+
+Surface tension and surface energy can be used interchangeably for liquids but not for solids.
+
+\[
+\tau = \frac{\partial(\gamma A)}{\partial A}|_{T,P} = \gamma + A\frac{\partial(\gamma)}{\partial A}|_{T,P}
+\]
+
+like dissolves like.
+
+Formation of alloy requires:
+\begin{itemize}
+\item crystal structure criteria: two metallic elements can only be fully soluble in one another if each has the same crystal structure
+\item Atomic radii criteria: 
+\item valency criteria: a metal will dissolve a metal of higher valency to a greater extent than one of lower valency.
+\end{itemize}
+
+Boron: electron deficient bonds.
+
+An electron in orbits define by quantum numbers, n, l, m, and spin.
+
+\begin{enumerate}
+\item n = 1, 2, 3, K, L, M shell
+\item l angular momentum, 0, 1, 2, 3, s, p, d, f orbit
+\item m magnetic number, $\pm l$
+\item s $\pm 1/2$
+\end{enumerate}
+
+metallic bonding, Van der Waals bonding,
+
+covalent, electron-pair bond, can be attributed to the complex mutual attraction of two positively charged nuclei by the shared pair of electrons.
+The resulting electron pair with its zero spin momentum interacts less strongly with its surroundings than do two independent electrons.
+
+The evidence of hydrogen molecule.
+
+\ce{H^{\sigma +}}-\ce{Cl^{\delta -}}, polar bond and permanent dipole moment,
+
+potential energy lowering (more difficult to remove one electron from two nearby nuclei than from one),
+
+Secondary bonding involves:
+\begin{itemize}
+\item dipole-dipole interaction
+\item dipole-induced dipole interaction
+\item London Dispersion Forces (existence even in system of no permanent dipole), temporary dipole, fluctuating dipole interaction
+\item Hydrogen bonding
+\end{itemize}
+
+Metal specific heat, restrictions as to the number of electrons with identical energy.
+
+Energy band theory proposed by Bloch is a molecular-orbital model of metallic crystals: the orbitals characteristic of the whole crystal are obtained as linear combinations of the atomic orbitals of the individual atoms.
+
+LCAO (linear combination of atomic orbitals) the total number of molecular orbital states is always the same as the total number of original atomic states (conservation of electronic states).
+
+phase: the stability of different states of aggregations.
+
+phase diagrams:
+
+eutectic has four meaning:
+\begin{enumerate}
+\item reversible, isothermal reaction
+\item the composition of the alloy which undergoes the reversible reaction
+\item the temperature at which the eutectic reaction occurs
+\item one of the specific microstructures formed by the reaction
+\end{enumerate}
+
+vapor pressure of S at 400 K is ca. 0.1 Torr. 30 sccm Ar pressure 200 mTorr. Mean free path of sulfur molecules estimated as 
+\[
+\lambda = 5\times 10^{-3}/0.3 = 166 
+\]
+in unit of $\mu$m. The diameter of tube is 2.54 mm, and therefore average collision number is 15.
+
+\section{thin films}
+\subsection{epitaxy}
+
+extended single-crystal film formation on top of a crystalline substrate.
+left laboratory and assume importance in device processing.
+Homoepitaxy: Si, because epilayer is freer of defects, can be doped independently.
+Heteroepitaxy: \ce{AlAs} on \ce{GaAs}, heteroepitaxial film.
+Interfacial bond straining, Grow an epitaxial film on top of an amorphous sub: Si on inculator, i.e., \ce{SiO2}.
+Selvedge, relax in such a way as to preserve the symmetry parallel to the surface but not normal to it.
+Give unit meshes corresponding to a two-dimensional surface.
+(100) $P(2\times 1)$ overlayer where P indicates the unit cell is primitive, and $b_1 = 2 a_1, b_2 = a_2$.
+(100) $R45^{\circ}(\sqrt{2}\times 2\sqrt{2})$.
+The reciprocal lattice appears as the visible image in diffraction patterns.
+These patterns can serve as the basis, on which complex pattern is built.
+
+$(HKL)\parallel(hkl);[UVW]\parallel[uvw]$ to define the epitaxial geometry. lattice-strained but defect-free (commensurate) epitaxy, dislocation-relaxed (discommensurate).
+
+Five defect categories:
+\begin{enumerate}
+\item propagation of defects from sub. into the epitaxial layer. Today the sub are largely dislocation-free, with the absence of grain boundaries or twins. 
+\item stacking faults: common in GaAs on Si 
+\item precipitate due to supersaturation of impurities. 
+\item low-angle grain boundaries and twins.
+\item formation of misfit dislocations
+\end{enumerate}
+
+Silicon-based heteroepitaxy,
+
+\ce{WO3} LEED, surface unit mesh,
+
+\section{Si Photonics}
+
+Active Si modulator: a low-loss phase-shifting mechanism based on refractive index change.\cite{Soref1987} $\delta\alpha$ and $\delta$n related by KKR.
+Electroabsorption means $\delta\alpha$ versus $E$ field, which arise from field-induced tunneling b/w VB and CB states (Franz-Keldysh effect).
+
+carrier effects on optical property
+\begin{itemize}
+\item free carrier absorption
+\item bandfilling leading to blueshift of absorption
+\item Coulombic interaction of carriers with impurities leading to redshift.
+\end{itemize}
+In crystalline Si, absorption redshift is observed, indicating Coulombic effect acting stronger than bandfilling.
+
+$n$ will increase when carriers are depleted from doped materials; the index will decrease when carries are injected.
+The modulation is polarization independent.
+depletion mode is expected to offer picoseconds range response time.
+The response in practice is limited by the RC constants.
+
+DWDM for Si photonics. \cite{Narasimha2007} Three cascaded interferometer are continuously tuned by maximizing the output power from each channel using an iterative algorithm.
+
+test: electrical probe station, surface-normal optical interface (grating couplers)
+
+mode-size converter, weak guided optical mode in glass fiber and a typical mode size of 8$\mu$m; large index contrast in Si wg and small mode size.
+power budget.\cite{Moerman1997} high alignment and increased packaging cost.
+
+\begin{table}[htb]
+\centering
+\caption{Materials in Si photonics}
+\begin{tabular}{lcp{3in}r}
+\toprule
+Composition & Function &  Property & Ref   \\
+\midrule
+Si          &    &   direct gap 3.4 eV,     &    \\
+Si          &  waveguide  &   $n=3.47$@1550 nm,     &    \\
+Si          &  modulator  &  $\chi^{(2)}$ 122 pm/V  &    \\
+\ce{LiNbO3} &  modulator  &  $\chi^{(2)}$ 360 pm/V  &    \\
+InP         &  detector  &   footprint 50 $\mu m^2$, 33 GHz        &    \\
+SiGe        &  detector    &  0.7 eV, up to 1.7 $\mu$m        &    \\
+cobalt salicide  &     &         &    \\
+\bottomrule
+\end{tabular}
+\end{table}
+
+\begin{table}[htb]
+\centering
+\caption{Detector in Si photonics}
+\begin{tabular}{lccr}
+\toprule
+structure & quantum efficiency &  response time & noise   \\
+\midrule
+Schottky metal-SC-metal &   low$^a$     &           &  5 nA  \\
+p-i-n                   &    &    & 100 pA to 1 nA  \\
+avalanche               &    &    &    \\
+III-V              &    &    &  low   \\
+\bottomrule
+\end{tabular}
+a: due to leakage photon flux
+
+\end{table}
+
+metal bonding between III-V and SOI, butt-joint coupling, Si of thickness 1.5 $\mu$m for polarization insensitive? wafer scale co-processed III-V and Si, SiGe-on-SOI for detector.
+
+what metal, epitaxy or not; dimension parameters,
+
+mode size, effective index, 2D field solver,
+
+SOI to reduce parasitic device capacitance, SOS (silicon on sapphire) for RF applications. challenges: metrology to probe buried oxide layer, and differential stress in the topmost silicon layer;
+
+\section{vocabulary}
+
+model also is applicable to ..., more probable,
+
+Proof-of-concept device
+Expansion of functionality set

### 2015-03-29 ch-moox/moox.tex
Final

@@
 Only a brief introduction will be given here, since these efforts has been well documented in several review articles.\cite{He2003} Most of these methods can be categorized into two groups: solution-based hydrothermal procedures \citep{Li2002b,Xia2006,Li2006a,Camacho-Bragado2006} and chemical vapor deposition approaches.\citep{Zeng1998,Li2002c,Li2002d,Zhou2003b,Fibers2007,Yan2009} Both methods have their own merits.
-Hydrothermal process usually needs lower temperature(\textless 300 \si{\degreeCelsius}), but the reaction often requires tens of hours, and the sample requires several post-growth processing steps; whereas vapor deposition demands relatively high temperature (\textgreater 500 \si{\degreeCelsius}) with a few hours reaction time.
+Hydrothermal process usually needs lower temperature (\textless 300 \si{\degreeCelsius}), but the reaction often requires tens of hours, and the sample requires several post-growth processing steps; whereas vapor deposition demands relatively high temperature (\textgreater 500 \si{\degreeCelsius}) with a few hours reaction time.
 Both methods are scalable for industrial applications.
@@
 \end{table}
-In a typical catalytic synthesis (Fig.~\ref{fig:mooxgrowth}), about 2 g molybdenum powders were loaded into the uniform heating zone, and the sealed chamber was first pumped down to 10 mTorr. 
+In a typical catalytic synthesis (Fig.~\ref{fig:mooxgrowth}), molybdenum powders were loaded at the center of  the reaction chamber with the receiving substrate placed at the downstream.
+The reaction chamber was first pumped down to $\sim$10 mTorr, and then brought up to $\sim$200 mTorr with 10 sccm \ce{O2} and 10 sccm Ar.
 % cvd layout
@@
 \end{figure}
-Oxygen flow, varying between 0.1 sccm to 10 sccm, was then admitted from the upstream inlet.
-With 10 sccm UHP Ar as carrier gas, the overall pressure reached about 200 mTorr.
-The heating temperature was ramped up to 800 \si{\degreeCelsius} in 30 min and lasted for 15 to 120 min.
-At last, the heating power was turned off, and the chamber was allowed to naturally cool to room temperature.
-The substrate was placed in downstream location where the temperature was about 350 to 650 \si{\degreeCelsius} according to open air temperature profile.
+The heating temperature at the center was ramped up to 800 \si{\degreeCelsius} in 30 min and lasted for 120 min.
+Then the heating power was turned off, and the chamber was allowed to naturally cool to room temperature.
+During the growth, the growth temperature along the substrate was about 620 \si{\degreeCelsius} to 300 \si{\degreeCelsius} according to the temperature profile measured at atmospheric pressure.
 Non-catalytic growth shared the same procedure except the NaOH treatment on Si substrates.
@@
 \end{figure}
-The Raman spectrum of the as-synthesized specimen also closely matched \ce{MoO3} features observed in previous studies.\cite{Dixit1986,Silveira2012} During m-Raman measurement, the laser spot was carefully focused onto the \ce{MoO3} flakes, and several inspections on different positions were observed to ensure the reproductivity of spectra data.
+The Raman spectrum of the as-synthesized specimen also closely matched \ce{MoO3} features observed in previous studies.\cite{Dixit1986,Silveira2012} During measurement, the laser spot was carefully focused onto the \ce{MoO3} flakes, and several inspections on different positions were observed to ensure the reproductivity of spectra data.
 As shown in Fig.~\ref{fig:moram}, 14 distinct bands were well resolved.
@@
 Previous study in our group had found that \ce{MoO3} deposition on ITO glass exhibited new morphologies that were not observed on Si substrates under the same growth conditions, yet the mechanism was not well investigated.\cite{predeep2011} A list of composition difference between glass and Si substrate show the additional elements of Na, K, and Ca, \emph{etc} in glass.
-Since the concentration of Na is highest among these extra elements, it is most likely to induce the new morphology growth.
-Therefore, a \gls{vls} mechanism may exist for the \ce{MoO3} growth when alkali metal ions are involved.
+Since the concentration of Na is highest among these extra elements, it is most likely that Na content induced the new morphology growth.
+Therefore, a \gls{vls} or analogous mechanism may exist for the \ce{MoO3} growth when alkali metal ions are involved.
 To provide a proper context, \gls{vls} process is briefly introduced here.
@@
 The melting point of \ce{Na2MoO4} is 687 \si{\degreeCelsius}.
-Based on the open air temperature profile (Fig.~\ref{fig:mooxgrowth}), the substrate was located in temperature zone between 650 and 350 \si{\degreeCelsius}.
+Based on the open air temperature profile (Fig.~\ref{fig:mooxgrowth}), the substrate was located in temperature zone between 620 \si{\degreeCelsius} and 300 \si{\degreeCelsius}.
+Since the growth temperature range for \ce{MoO3} (525 \si{\degreeCelsius} to 300 \si{\degreeCelsius}) deposition was mainly below the lowest eutectic temperature of 507  \si{\degreeCelsius}, the majority growth of \ce{MoO3} can be explained as a \gls{vss} process, which is analogous to the VLS process except that the catalysts remain as solid particles.
 The actual temperature distribution during growth was different from ambient measurement due to the pressure change and thermal conduction along the Si substrate.
-It was difficult to acquire the accurate temperatures along the substrate; however, by considering the flow rate, the actual temperature should be higher than that predicted by open air measurement.\cite{Subannajui2010} The continuous supply of \ce{MoO3} growth species pushed the phase evolution towards high \ce{MoO3} molar ratio end, with $n$ in \ce{Na2O.nMoO3} increasing from 1 to 4.
-Each site of \ce{Na2MoO4} continued absorb incoming \ce{MoO3}, forming a swelling particle.
+It was difficult to acquire the accurate temperatures along the substrate; however, by considering the flow rate, the actual temperature should be higher than that predicted by open air measurement.\cite{Subannajui2010} Thus, \gls{vls} mechanism cannot be ruled out completely.
+The continuous supply of \ce{MoO3} growth species pushed the phase evolution towards high \ce{MoO3} molar ratio end, with $n$ in \ce{Na2O.nMoO3} increasing from 1 to 4.
+Each site of \ce{Na2MoO4} continued absorb incoming \ce{MoO3} growth species.
 \ce{MoO3} precipitated from these seeds when a critical supersaturation concentration was reached, which was about 75\% in unit of mole according to Fig.~\ref{fig:ch4pd}.
@@
 
-\emph{The reaction on NaOH-Si substrate follows the phase diagram, and \ce{Na2Mo4O13} serves as the catalyst promoting various 1D \ce{MoO3} growth.}
+\emph{The reaction on NaOH-Si substrate follows the phase diagram, and \ce{Na2Mo4O13} serves as the catalyst promoting various 1D \ce{MoO3} growth in a VSS mechanism.}
 
@@
 \centering
-\includegraphics[width=0.9\textwidth]{mooe_sem_ev}
-\caption[Evolution of the second stage on \ce{MoO3} growth]{Growth evolution of the second stage of catalyst-assisted growth of \ce{MoO3} 1D structures: SEM images of the deposition at different growth temperatures with growth time of row 1: 15 min, row 2: 30 min, row 3: 60 min, and row 4: 90 min.}
+\includegraphics[width=0.9\textwidth]{moo3_sem_ev}
+\caption[Evolution of the second stage on \ce{MoO3} growth]{Growth evolution of the second stage of catalyst-assisted growth of \ce{MoO3} 1D structures: SEM images of the deposition with growth time of (a-d) 15 min, (e-h) 30 min, (i-l) 60 min, and (m-p) 90 min at growth temperature of 525 \si{\degreeCelsius}, 445 \si{\degreeCelsius}, 390 \si{\degreeCelsius}, and 340 \si{\degreeCelsius}, respectively.}
 \label{fig:ch4ev}
@@
 Although the exact phase (liquid or solid) of \ce{Na2Mo4O13} was not known yet in current study, it can be deduced that the \ce{Na2Mo4O13} existed as an active site for the adsorption of incoming \ce{MoO3} growth species.
-When the catalyst was smaller than some critical size, there is no preferred growth direction.
-This changed when the precipitated solid exceeded certain critical dimension, and the morphology evolution was then determined by the relative size of already formed solid and the associated catalyst.
 Several pathways could occur after the accommodation of \ce{MoO3} vapor and supersaturation.
@@
 Meanwhile, the \gls{vs} process is not suppressed and \ce{MoO3} adatoms could directly condense on \ce{MoO3} surface.
-
 \begin{figure}[htb]
@@
 \end{figure}
-
 Some unique features of \ce{MoO3} must be taken into consideration to properly evaluate the dominate pathway(s).
@@
 First, the reduction in catalyst size may induce the tapering.
-Due to the evaporation, the size of the catalyst particles can shrink during the growth resulting in the tapered growth.
+Owing to the evaporation, the size of the catalyst particles can shrink during the growth resulting in the tapered growth.
 The \gls{vs} growth on the side surfaces was another possible mechanism, which promoted the radial growth of the 1D structures forming the tapered shape.
@@
 
-\subsection{Growth on Alkali Metal Containing Substrates}\label{sec:glass}
+\subsection{Growth with Other Alkali Metal Catalysts}\label{sec:glass}
 In analogy to the \ce{Na2MoO4}-\ce{MoO3} binary phase diagram, other alkali metals, such as Li and K, could also form A-Mo-O alloy at elevated temperature.
@@
 \centering
-\caption[Mass transport of sodium ions in silica glass]{Mass transport of sodium ions in silica glass, with diffusion coefficient in unit of \si{cm^2\per\second}}\label{tab:mona}
+\caption[Mass transport of sodium ions in silica glass]{Mass transport of sodium ions in silica glass, with diffusion coefficient in unit of \si{cm^2\per\second}.}\label{tab:mona}
 \begin{tabular}{lcr}
@@
 \cite{Deb1968}   & 2.80  & $E\perp c_0$ & single crystal \\
-\cite{Julien1995} & 2.8$\sim$ 3.2 & NA & films\\
+\cite{Julien1995} & 2.8$\sim$3.2 & NA & films\\
  this work  & 3.2  & NA & nanoflakes\\

### 2015-03-29 ch-tms/tms.tex
Final

@@
 After pumping down, the reaction chamber was flushed two times to expel residual air.
-A cold trap filled with liquid nitrogen in downstream was used to collect possible sulfur precipitation.
+A cold trap filled with liquid nitrogen in downstream was used to collect possible sulfur condensation.
 Then, the furnace was heated to 750 \si{\degreeCelsius} in 30 min, held for 15 min, and allowed to naturally cool down to room temperature.
@@
 
-Due to this small spacing, TEM was primarily utilized to observe the detailed morphology of \ce{WO3}-\ce{WS2} core-shell NWs.
+Owing to this small spacing, TEM was primarily utilized to observe the detailed morphology of \ce{WO3}-\ce{WS2} core-shell NWs.
 Fig.~\ref{fig:ch5ws2tem1}c and d show HRTEM imaging on typical tip and body region of the core-shell NW, respectively.
 A comparison with the pre-sulfurization specimen (Fig.~\ref{fig:woseedtem2} on page~\pageref{fig:woseedtem2}) readily revealed the formation of core-shell morphology after sulfurization.
-The measured layer spacing of 6.5 \si{\angstrom} appeared slightly larger than bulk 2H-\ce{WS2} value of 6.16 \si{\angstrom}, but matched well with the XRD result in Fig.~\ref{fig:ch5ws2xrd}.
+The measured wall spacing of 6.5 \si{\angstrom} appeared slightly larger than bulk 2H-\ce{WS2} value of 6.16 \si{\angstrom}, but matched well with the XRD result in Fig.~\ref{fig:ch5ws2xrd}.
 The sharp contrast in core region also proved the lattice structure of \ce{WO3} was not seriously distorted upon sulfurization.
@@
 \caption[HRTEM imaging before and after sulfurization]{HRTEM imaging before and after sulfurization illustrating the presence of core-shell structure.
-(a) Low magnification and (b) HRTEM images on \ce{WO3} NW specimen from seeded growth;  HRTEM images on the core-shell nanowire of (c) tip region and (d) body region showing layer number variation.
+(a) Low magnification and (b) HRTEM images on \ce{WO3} NW specimen from seeded growth;  HRTEM images on the core-shell nanowire of (c) tip region and (d) body region showing wall number variation.
 The contrast between (b) and (d) readily identify the formation of core-shell structure.
@@
 
-After examining dozens of core-shell NWs, this study found the \ce{WS2} layer number at NW tip was usually the largest, reaching more than ten, and the layer number decreased to one along the NW body; but there also existed some layer number fluctuation and shape modification.
-Fig.~\ref{fig:ch5ws2tem3} show a smooth transition of \ce{WS2} layer number on the tip region of one NW.
-The layer number was about 7 on the tip corner, gradually decreased from 4 to 3 along the NW body, and stopped at 2 layers.
-Closer observation indicated the layer spacing was not quite uniform in the tip area, probably due to the complex curvature and bending.
+After examining dozens of core-shell NWs, this study found the \ce{WS2} wall number at NW tip was usually the largest, reaching more than ten, and the wall number decreased to one along the NW body; but there also existed some wall number fluctuation and shape modification.
+Fig.~\ref{fig:ch5ws2tem3} show a smooth transition of \ce{WS2} wall number on the tip region of one NW.
+The wall number was about 7 on the tip corner, gradually decreased from 4 to 3 along the NW body, and stopped at 2 walls.
+Closer observation indicated the wall spacing was not quite uniform in the tip area, probably due to the complex curvature and bending.
 \ce{WS2} fullerene also show similar structures.
-Since the closing of the tip region could be of great complexity and the induced strain could modify Raman signal considerably, the TEM-Raman integrated measurement in this study focused on the body region of the core-shell NWs with smooth transition layer number.
+Since the closing of the tip region could be of great complexity and the induced strain could modify Raman signal considerably, the TEM-Raman integrated measurement in this study focused on the body region of the core-shell NWs with smooth transition wall number.
 % coreshell tem
@@
 This tapering probably arose from the sulfurization process but could be also due to the parent \ce{WO3} NW.
-The diameter varied from about 200 nm to 15 nm, and the \ce{WS2} layer number also changed in a nonlinear manner.
+The diameter varied from about 200 nm to 15 nm, and the \ce{WS2} wall number also changed in a nonlinear manner.
 On some turning region, the \ce{WS2} seemed penetrating into the body of primary \ce{WO3} NW.
@@
 \includegraphics[width=0.7\textwidth]{cs_tem_g3_lbd}
-\caption[HRTEM imaging on one tapered core-shell nanowire]{HRTEM imaging on one tapered core-shell nanowire showing fluctuation of layer numbers.}
+\caption[HRTEM imaging on one tapered core-shell nanowire]{HRTEM imaging on one tapered core-shell nanowire showing fluctuation of wall numbers.}
 \label{fig:ch5ws2tem4}
@@
 The growth mechanism of \ce{WS2} nanotubes from oxides has been thoroughly studied,\cite{Feldman1998} and it was generally agreed that the sulfurization of \ce{WO3} was a diffusion limited reaction.\cite{Feldman1996} It was also suggested that the core \ce{WO3} NWs became non-stoichiometric phases upon sulfurization.\cite{Feldman1996,ZAK2009} This study recognized this possibility but also considered two factors different from previous studies: one was the usage of sulfur as precursor instead of \ce{H2} and/or \ce{H2S} as in previous reports, which accelerated the reduction of \ce{WO3} significantly due to the formation of \ce{H2O}; the other was the short reaction time and light degree of sulfurization, which probably would not distort the \ce{WO3} lattice significantly, as evidenced by the XRD and HRTEM analysis in this section.
-The sulfurization dynamic was then proposed as following in this thesis: the tips of \ce{WO3} NWs exhibited greater crystalline disorder, and \ce{WS2} layers on tips were folded at least along two axes, resulting a higher density of defects and thus a higher sulfurization rate; while the folding along NW body was quasi-one dimensional, subsequently the sulfurization rate could be lower.
-Besides, sulfurization could also be initiated from the NW body, presumably due to the presence of surface defects.
-As a result, this led to the uneven \ce{WS2} layer number distribution along the core-shell NWs.
+The sulfurization dynamic was then proposed as following: The tips of the NWs exposed directly to the sulfur vapors resulting in a high sulfurization rate.
+On the other hand,  sulfurizaiton along the NWs is limited by the diffusion of the sulfur vapors through the dense NWs array.
+Therefore, the \ce{WS2} wall number is not uniform along the as-grown core-shell NWs.
 
@@
 An exception was shown in Fig.~\ref{fig:ch5ws2tem2}.
-Note the rectangular area show abrupt termination of one \ce{WS2} layer, which was tentatively attributed to stacking fault in this study.
+Note the rectangular area show abrupt termination of one \ce{WS2} wall, indicating a formation of dislocation.
 
@@
 \end{figure}
-The transferred NWs were first examined using TEM to identify the \ce{WS2} layers configuration and the associated geometrical orientation.
+The transferred NWs were first examined using TEM to identify the \ce{WS2} wall configuration and the associated geometrical orientation.
 Then, the core-shell NWs on TEM grids were probed under Raman in a location-resolved manner.
-Only those core-shell NWs exhibiting relative smooth \ce{WS2} wall number transition were used in subsequent Raman measurement (wall number and layer number were used interchangeably in this work, but note that 1 wall is not equal to 1 layer due to the tubular structure).
+Only those core-shell NWs exhibiting relative smooth \ce{WS2} wall number\footnote{wall number and layer number were used interchangeably in this work, but note that 1 wall is not equal to 1 layer due to the tubular structure} transition were used in subsequent Raman measurement.
 To perform TEM and Raman analysis on individual NWs, this study placed one NW only in each cell of the TEM grid (65 $\times$ 65 $\mu$m).
@@
 (e) Raman spectra acquired from the same core-shell NWs supported on TEM grids, indicating a sharp contrast between the in-plane and out-of-plane vibrations.
-Notice that the Raman spectra primarily arise from the outer \ce{WS2} shell, and only weak Raman shift at about 800 \si{cm^{-1}} were observed at some bare core region (not shown here).}
+Note that the Raman spectra primarily arise from the outer \ce{WS2} shell, and only weak Raman shift at about 800 \si{cm^{-1}} were observed at some bare core region (not shown here).}
 \label{fig:ch5ws2ram}
@@
 Rigid analysis of the Raman spectra must be performed to reach solid conclusion.
-Hence, multi-peak Lorentzian fitting was employed on the spectra in Fig.~\ref{fig:ch5ws2ram}e, and the result for 1 layer \ce{WS2} core-shell NW was displayed in Fig.~\ref{fig:ch5ws2ml}.
+Hence, multi-peak Lorentzian fitting was employed on the spectra in Fig.~\ref{fig:ch5ws2ram}e, and the result for one wall \ce{WS2} core-shell NW was displayed in Fig.~\ref{fig:ch5ws2ml}.
 The de-convolution peaks compared favorably with original Raman spectrum, and similar operation were used for other three spectra.
-Fig.~\ref{fig:ch5ws2pr} show the layer number dependence on three group of intensity ratios extracted from apparent value, de-convoluted height, and integrated intensity, respectively.
-Similar trend was found among all three set of data, though the integrated intensity appeared more sensitive towards layer No variation.
-For a qualitative purpose, the apparent intensity ratio $I_{E/A}$ between in-plane E band ($E_{2g}^1+2LA$) and out-of-plane A band ($A_{1g}+B_{1u}$) was used as a quick criterion to distinguish \ce{WS2} few layer in this study.
+Fig.~\ref{fig:ch5ws2pr} show the wall number dependence on three group of intensity ratios extracted from apparent value, de-convoluted height, and integrated intensity, respectively.
+Similar trend was found among all three set of data, though the integrated intensity appeared more sensitive towards wall number variation.
+For a qualitative purpose, the apparent intensity ratio $I_{E/A}$ between in-plane E band ($E_{2g}^1+2LA$) and out-of-plane A band ($A_{1g}+B_{1u}$) was used as a quick criterion to distinguish \ce{WS2} few wall in this study.
 % fig Raman TEM
@@
 \subfloat[]{\label{fig:ch5ws2pr}\includegraphics[width=0.45\textwidth]{ws2_peak_ratio}}
-\caption[Multi-peak Lorentzian fitting on core-shell NWs]{(a) Multi-peak Lorentzian fitting on core-shell NWs, and (b) Layer number dependence on averaged intensity ratio between the in-plane and out-of-plane Raman bands.}
+\caption[Multi-peak Lorentzian fitting on core-shell NWs]{(a) Multi-peak Lorentzian fitting on core-shell NWs, and (b) wall number dependence on averaged intensity ratio between the in-plane and out-of-plane Raman bands.}
 \label{fig:ch5ws2prl}
 \end{figure}
-$I_{E/A}$ was then extracted to correlate with layer number variation on tens of core-shell NWs.
-As shown in Fig.~\ref{fig:ch5ws2ramap}, the mapping of \ce{WS2} layer dependent $I_{E/A}$ almost followed the same trend in Fig.~\ref{fig:ch5ws2pr} with some variation attributed to the core-shell NW diameter difference.
+$I_{E/A}$ was then extracted to correlate with wall number variation on tens of core-shell NWs.
+As shown in Fig.~\ref{fig:ch5ws2ramap}, the mapping of \ce{WS2} wall dependent $I_{E/A}$ almost followed the same trend in Fig.~\ref{fig:ch5ws2pr} with some variation attributed to the core-shell NW diameter difference.
 \begin{figure}[htb]
@@
 \includegraphics[width=0.6\textwidth]{ws2_ratio_map}
-\caption[Mapping on the \ce{WS2} layer dependent intensity ratio]{Mapping on the \ce{WS2} layer dependent intensity ratio.
+\caption[Mapping on the \ce{WS2} wall dependent intensity ratio]{Mapping on the \ce{WS2} wall dependent intensity ratio.
 The Raman spectra were acquired on individual NW suspended on 300 mesh lacey C TEM grid.}
@@
 \end{figure}
-The intensity ratio $I_{E/A}$ decreased monotonically with the increase of \ce{WS2} wall number, a similar trend as observed on 2D few layer \ce{WS2},\cite{Berkdemir2013} and the exact value of $I_{E/A}$ show modest difference with 2D sheet, which could be attributed to the suspended configuration of current core-shell NWs specimen and the presence of \ce{WO3} core.
+The intensity ratio $I_{E/A}$ decreased monotonically with the increase of \ce{WS2} wall number, a similar trend as observed on two-dimensional (2D) few layer \ce{WS2},\cite{Berkdemir2013} and the exact value of $I_{E/A}$ show modest difference with 2D sheet, which could be attributed to the suspended configuration of current core-shell NWs specimen and the presence of \ce{WO3} core.
 Furthermore, these results indicated that $I_{E/A} > 2$ for single-walled \ce{WS2} core-shell NW, and when the \ce{WS2} wall number was about 3, $I_{E/A}=1$.
@@
 \subfloat[]{\label{fig:stk3}\includegraphics[width=0.30\textwidth]{stacking3}}
-\caption[Optical reflectance simulation on three stacking configurations]{Optical reflectance simulation on three  \ce{WS2} layer stacking configurations.}
+\caption[Optical reflectance simulation on three stacking configurations]{Optical reflectance simulation on three  \ce{WS2} wall stacking configurations.}
 \label{fig:ch5ws2stk}
@@
 Using 532 nm excitation, the multi-phonon resonant feature was clearly resolved.
-A broad PL peak was also observed with center at 628 nm and FWHM of 23 nm, corresponding to a photon energy of 1.974 eV with width of 72 meV.
+A broad \gls{pl} peak was also observed with center at 628 nm and FWHM of 23 nm, corresponding to a photon energy of 1.974 eV with width of 72 meV.
 % ws2/wo3 on sio2,1 
@@
 \end{figure}
-Another feature was the presence of three peaks centering at 1860, 3695, and 5500 \si{cm^{-1}}, respectively, where the latter two were probably the secondary and third overtone of the first peak.
-It was confirmed that this three peaks belonged to Raman shift instead of PL, since similar peaks were observed using different excitation wavelength of 441 nm and 532 nm.
+Another feature was the presence of three peaks centering at 1860, 3695, and 5500 \si{cm^{-1}}, respectively, where the latter two were probably the secondary and third overtones of the first peak.
+It was confirmed that this three peaks belonged to Raman shift instead of \gls{pl}, since similar peaks were observed using different excitation wavelength of 441 nm and 532 nm.
 The origin of this peak family was still under research, and one possible candidate was the \ce{C=O} bonding, which presumably came from the carbon impurity in tungsten powders as seeds.
@@
 \end{figure}
-Three Raman sites were chosen to probe possible layer variation using both 532 and 441 nm excitation with the naming displayed in the inset of Fig.~\ref{fig:ws2ramall}.
+
+Three Raman sites were chosen to probe possible wall variation using both 532 and 441 nm excitation with the naming displayed in the inset of Fig.~\ref{fig:ws2ramall}.
 The Raman patterns were shown in Fig.~\ref{fig:ws2ram3site}a-b.
@@
 In contrast, the on-resonance profile in Fig.~\ref{fig:ws2ram3site}a exhibited much richer spectra.
-The shoulder mode at tip2 spectrum was a manifestation of $B_{1u}$ mode from curved \ce{WS2} layer.
-According to previous analysis, the apparent ratio between in-plane and out-of-plane vibration indicated site tip2 had multi-wall \ce{WS2}, and the other two possibly had few-walled \ce{WS2}.
+The shoulder mode at tip2 spectrum was a manifestation of $B_{1u}$ mode from curved \ce{WS2} wall.
+According to previous analysis, the apparent ratio between in-plane and out-of-plane vibration indicated site tip2 had multi-wall \ce{WS2}, and the other two possibly had few-wall \ce{WS2}.
 \begin{figure}[htb]
@@
 \end{figure}
-This predication was confirmed by the associated PL measurement displayed in Fig.~\ref{fig:ws2plgreen}.
+This predication was confirmed by the associated \gls{pl} measurement displayed in Fig.~\ref{fig:ws2plgreen}.
 Strong luminescent peaks were found at site mid and tip1, and an extremely weak peak were found from site tip2.
-The PL peaks centered at 1.958 and 1.934 eV for mid and tip1, respectively.
+The \gls{pl} peaks centered at 1.958 and 1.934 eV for mid and tip1, respectively.
 The second and third order peaks also show up on all three Raman sites.
@@
 The present work in this chapter, to some extent, circumvented this limitation by leveraging a home-built micromanipulator apparatus to transfer the nanostructures between TEM grids and other desired substrates.
-Considerable insight on the \ce{WO3}-\ce{WS2} core-shell nanostructures was obtained: few-layer, even single-layer tubular \ce{WS2} nanostructure was observed with \ce{WO3} core; layer dependent Raman spectra were studied at on-resonance and off-resonance conditions; the fingerprint of few-layer \ce{WS2} was revealed; and photoluminescence from core-shell NWs was identified.
+Considerable insight on the \ce{WO3}-\ce{WS2} core-shell nanostructures was obtained: few-wall, even single-wall tubular \ce{WS2} nanostructure were observed with \ce{WO3} cores; wall number dependent Raman spectra were studied at on-resonance and off-resonance conditions; the fingerprint of few-wall \ce{WS2} was revealed; and photoluminescence from core-shell NWs was identified.
 These results held great values to the application of \ce{WO3}-\ce{WS2} heterostrucutres in photocatalysis and photoelectrochemical applications.
@@
 More important, a TEM-Raman integrated approach was tested aiming at providing a location-resolved map between crystal structure and optical properties.
-As a result, layer number dependence of Raman spectra on \ce{WS2} tubular nanostructure was fingerprinted, and direct band gap \gls{pl} from \ce{WS2} tubular structure was observed.
+As a result, wall number dependence of Raman spectra on \ce{WS2} tubular nanostructure was fingerprinted, and direct band gap \gls{pl} from \ce{WS2} tubular structure was observed.
 These results indicated a broad space for band structure tuning of \ce{WO3}-\ce{WS2}.
@@
 \includegraphics[width=0.7\textwidth]{naohwo3_sem.jpg}
-\caption[SEM characterization of \ce{NaOH} \ce{WO3} growth]{SEM characterization of \ce{NaOH} \ce{WO3} growth.
-(a) Low-magnification SEM graphs showing dense \ce{WO3} NWs.
-(b) A high magnification view showing thin NW growth.}
+\caption[SEM characterization of \ce{NaOH} catalyzed \ce{WO3} growth]{SEM characterization of \ce{NaOH} catalyzed \ce{WO3} growth.
+(a) Low-magnification SEM graphs showing dense \ce{WO3} NWs, and (b) a high magnification view showing thin NW growth.}
 \label{fig:naohwsem}
@@
 \includegraphics[width=0.5\textwidth]{naoh-wo3_edx}
-\caption[Composition analysis on \ce{NaOH} \ce{WO3} growth NWs]{Composition analysis on \ce{NaOH} \ce{WO3} growth NWs identifying small fraction Na content.}
+\caption[Composition analysis on \ce{NaOH} catalyzed \ce{WO3} growth NWs]{Composition analysis on \ce{NaOH} catalyzed \ce{WO3} growth NWs identifying small fraction Na content.}
 \label{fig:naohwedx}
@@
 \subfloat[]{\label{fig:nawram}\includegraphics[width=0.45\textwidth]{naoh-wo3_raman}}
-\caption[Characterization of \ce{NaOH} \ce{WO3} NWs: XRD and Raman]{Characterization of \ce{NaOH} \ce{WO3} NWs: XRD and Raman.
+\caption[Characterization of \ce{NaOH} catalyzed \ce{WO3} NWs: XRD and Raman]{Characterization of \ce{NaOH} catalyzed \ce{WO3} NWs: XRD and Raman.
 (a) XRD pattern of the as-prepared sample, and (b) Raman spectrum on NWs region.}
@@
 Another small hump was also observed at 946 \si{cm^{-1}}.
-This Raman spectrum deviated from typical features of \ce{WO3},\cite{Salje1975a,Dixit1986} but matched well with \ce{WO3.H2O} in one previous study;\cite{Daniel1987} however, the XRD pattern did not reveal tungsten oxide hydrates feature.\footnote{ICDD PDF 04-011-1708, \emph{a}=7.35 \si{\angstrom}, \emph{b}=12.5 \si{\angstrom}, \emph{c}=7.70 \si{\angstrom}} Further analysis was therefore required to confirm the exact phase of \ce{NaOH} \ce{WO3} NWs.\cite{Azimirad2009a}
+This Raman spectrum deviated from typical features of \ce{WO3},\cite{Salje1975a,Dixit1986} but matched well with \ce{WO3.H2O} in one previous study;\cite{Daniel1987} (also see Table.~\ref{tab:woram2} on page.~\pageref{tab:woram2}) however, the XRD pattern did not reveal tungsten oxide hydrates feature.\footnote{ICDD PDF 04-011-1708, \emph{a}=7.35 \si{\angstrom}, \emph{b}=12.5 \si{\angstrom}, \emph{c}=7.70 \si{\angstrom}} Further analysis was therefore required to confirm the exact phase of \ce{NaOH} catalyzed \ce{WO3} NWs.\cite{Azimirad2009a}
 
@@
 \centering
-\includegraphics[width=0.7\textwidth]{naoh_wo3_tem.jpg}
-\caption[Characterization of \ce{NaOH} \ce{WO3}: TEM]{TEM Characterization of \ce{NaOH} \ce{WO3}: (a) TEM image of one nanowire with diameter ca.
+\includegraphics[width=0.6\textwidth]{naoh_wo3_tem.jpg}
+\caption[Characterization of \ce{NaOH} catalyzed \ce{WO3}: TEM]{TEM Characterization of \ce{NaOH} catalyzed \ce{WO3}: (a) TEM image of one nanowire with diameter ca.
 20 nm, and (b) HRTEM images on the tip region showing absence of catalytic particle.}

### 2015-03-29 ch-tms/tmspart.tex
Final

@@
 The substrates were thoroughly cleaned.
-It was mentioned that separate sulfur heating improved the PL uniformity.
+It was mentioned that separate sulfur heating improved the \gls{pl} uniformity.
 Sulfurization mechanism study of \ce{WO3} suggested \ce{W^{6+}} cannot be directly reduce to \ce{W^{4+}} in \ce{WS2}.\cite{VanderVlies2002,VanderVlies2002a} Tungsten oxysulfides was necessary as an intermediate phase.
 
-\citeauthor{Peimyoo2013} prepared \ce{WS2} on \ce{SiO2}-Si using \ce{WO3} powder and sulfur at 800 \si{\degreeCelsius}, aiming at the light emission studies to clarify several contradictory reports.\cite{Peimyoo2013} Uniform PL intensity was found on the triangular \ce{WS2} flakes, in contrast to previous edge enhanced PL\cite{Berkdemir2013}.
+\citeauthor{Peimyoo2013} prepared \ce{WS2} on \ce{SiO2}-Si using \ce{WO3} powder and sulfur at 800 \si{\degreeCelsius}, aiming at the light emission studies to clarify several contradictory reports.\cite{Peimyoo2013} Uniform \gls{pl} intensity was found on the triangular \ce{WS2} flakes, in contrast to previous edge enhanced \gls{pl}\cite{Berkdemir2013}.
 Raman spectra (532 nm) fit included $E_{2g}^1(M)$ mode at 343 cm$^{-1}$, according to the phonon dispersion calculation \cite{Molina-Sanchez2011} and experimental observation.\cite{Zeng2013a,Zhao2013,Lee2013} However, none of these experimental reports specifically mentioned $E_{2g}^1(M)$ mode.
@@
 Raman spectra indicated a universal down-shift of $A_{1g}$ peak (1L from 418 \si{cm^{-1}} on \ce{SiO2}-Si to 416.4 \si{cm^{-1}} on sapphire).
-PL signal of \ce{WS2} on \ce{SiO2}-Si was stronger than that on sapphire.
+\gls{pl} signal of \ce{WS2} on \ce{SiO2}-Si was stronger than that on sapphire.
 The visibility of \ce{WS2} on \ce{Al2O3} was poor.

### 2015-03-29 ch-wox/ch-wox.tex
Final

@@
 
-In a typical non-seeded experiment (Fig.~\ref{fig:wogrow}), about 2 g tungsten powder was positioned in the upstream end of a quartz boat, and downstream about 2.5 inch the substrate was stationed. 
+In a typical non-seeded experiment (Fig.~\ref{fig:wogrow}), about 2 g tungsten powder (3N) was positioned in the upstream end of a quartz boat, and downstream about 2.5 inch the substrate was stationed.
 % cvd NW growth
@@
 To study the growth mechanism, controlled experiments were performed on the oxidation of the tungsten seed particles dispersed on the substrate.
-In a typical oxidation experiment, tungsten powders were loaded into the uniform heating zone, and the sealed chamber was pumped down to an ultimate pressure of $\sim8$ mTorr.
+In a typical oxidation experiment, tungsten powders were loaded into the uniform heating zone at the center of the chamber, and the sealed chamber was pumped down to an ultimate pressure of $\sim8$ mTorr.
 Then oxygen flow, varying between 1 sccm to 10 sccm, was admitted from the upstream inlet.
@@
 With this degree of freedom included, the primary features of the deposition and the associated parameters were summarized in Table~\ref{tab:wot}.
-%
 \begin{table}[htb]
 \centering
-\caption{\ce{WO_x} ordinary transport results}\label{tab:wot}
+\caption{\ce{WO3} non-seeded growth summary}\label{tab:wot}
 \begin{tabular}{lp{2in}p{2in}r}
@@
 \end{table}
-
 The change of metallic W source after growth carries important information about the growth.
@@
 \centering
-\includegraphics[width=0.6\textwidth]{pd_before.jpg}
+\includegraphics[width=0.5\textwidth]{pd_before.jpg}
 \caption[SEM images of W powder before growth]{SEM images of W powder before growth for (a) 3N, (b) 3N5, (c) 4N5 and (d) 5N, respectively.}
@@
 \centering
-\includegraphics[width=0.6\textwidth]{pd_after.jpg}
+\includegraphics[width=0.5\textwidth]{pd_after.jpg}
 \caption[SEM images of W powder after growth]{SEM images of W powder after growth for (a) 3N, (b) 3N5, (c) 4N5 and (d) 5N. }
@@
 
-The sodium contents in 3N powders fundamentally changed the deposition in ordinary transport growth.
+The sodium contents in 3N powders fundamentally changed the deposition in the non-seeded growth.
 Typical morphologies of the as-synthesized nanostructures grown on a \ce{SiO2}-Si substrate were shown in Fig.~\ref{fig:nawoxsemedx}a.
@@
 Micro-Raman spectroscopy was also carried out at room temperature in ambient atmosphere to confirm the phases of the microplates and ultra-long nanowires.
-Fig.~\ref{fig:nawoxram}a show the m-Raman spectrum of the microplates.
+Fig.~\ref{fig:nawoxram}a show the Raman spectrum of the microplates.
 The Raman lines at 949, 794-777, 366-263 \si{cm^{-1}} closely matched the reported \ce{Na2W4O_{13}} Raman shift.\cite{Fomichev1992} The Raman spectrum from the ultra-long nanowires was shown in Fig.~\ref{fig:nawoxram}b.
@@
 \end{table}
-For a comprehensive comparison purpose, the Raman fingerprints of various tungsten oxides and tungstate was shown in Table~\ref{tab:woram2}. 
+For a purpose of comprehensive comparison, the Raman fingerprints of various tungsten oxides and tungstate were listed in Table~\ref{tab:woram2}. 
 \begin{table}[htb]
@@
 The sodium concentration in 3N source was about 20 ppm, as provided by vendor.\footnote{Owing to the non-uniform distribution of foreign elements, detection of sodium by EDX is possible although the concentration is below the capacity limit of typical EDX.} The Na concentrations in quartz tube and quartz boat (GE 214 quartz, Wilmad Labglass) were 1 ppm and 0.7 ppm, respectively.
-To verify the major source of Na content coming from 3N powder, control experiments were employed by using W source with higher purities (4N5 or 5N).
+To verify the major source of Na content, control experiments were employed by using W source with higher purities (4N5 or 5N).
 These ultra-high purity W sources produced pure tungsten oxide deposition, and no Na content was detected by EDX.
@@
 \item only the top layer of the tungsten source was oxidized showing a dark blue color after growth.
-\end{enumerate*} Due to its low concentration, the exact composition of the Na content in the tungsten source was difficult to probe.
-However, the evaporation rate of the Na content was expected to be high when heated at 1000 \si{\degreeCelsius}.
-This assumption wais supported by the observation that no Na was found in the deposition along the whole substrate in control experiments using the used 3N W source.
+\end{enumerate*} Owing to its low concentration, the exact composition of the Na content in the tungsten source was difficult to probe; however, the evaporation rate of the Na content was expected to be high when heated at 1000 \si{\degreeCelsius}.
+This assumption was supported by the observation that no Na was found in the deposition along the whole substrate in control experiments using the used 3N W source.
 Put it in another way, this observation indicated that the majority of Na content was already evaporated in previous experiment.
@@
 The deposition with 4N5 and 5N powders had much smaller grain size than that with 3N5 powders.
-% 3N5 powder growth
+% 3N5 powder growth 082712
 \begin{figure}[htb]
@@
 \includegraphics[width=0.9\textwidth]{wox3n5.jpg}
-\caption[SEM images of \ce{WO3} growth using 3N5 powder]{SEM images of \ce{WO3} growth using 3N5 powder showing the morphology variation from (a) high temperature, (b) intermediate temperature, to (c) low temperature.}
+\caption[SEM images of \ce{WO3} growth using 3N5 powder]{SEM images of \ce{WO3} growth using 3N5 powder showing the morphology variation at (a) 736 \si{\degreeCelsius}, (b) 590 \si{\degreeCelsius}, and (c) 400 \si{\degreeCelsius}.}
 \label{fig:wox3n5}
@@
 \includegraphics[width=0.9\textwidth]{wox4n5.jpg}
-\caption[SEM images of \ce{WO3} growth using 4N5 powder]{SEM images of \ce{WO3} growth using 4N5 powder showing the morphology variation from (a) high temperature and (b) intermediate temperature, to (c) low temperature.
-Growth with 5N powders have almost the same morphology with that of 4N5, and is not shown hereby.}
+\caption[SEM images of \ce{WO3} growth using 4N5 powder]{SEM images of \ce{WO3} growth using 4N5 powder showing the morphology variation at (a) 870 \si{\degreeCelsius} and (b) 750 \si{\degreeCelsius}, and (c) 408 \si{\degreeCelsius}.
+Growth with 5N powders exhibited almost the same morphology as that of 4N5 and is not shown hereby.}
 \label{fig:wox4n5}
@@
 Four kinds of tungsten powders were used as precursor to prepare \ce{WO3} NWs, as already summarized in Table~\ref{tab:powder}.
-The dimensions of tungsten powder were obtained by measuring the average size in SEM graphs.
+The dimensions of tungsten powder were obtained by measuring the average size in SEM micrographs.
 A systematic investigation was performed on the oxidation behavior of tungsten powder to evaluate the temperature effect, size-dependence, and influence of oxygen partial pressure.
@@
 Fig.~\ref{fig:pdtemp} illustrated the effect of temperature on the morphological change and surface nanowires formation of 3N powder.
-At 500 \si{\degreeCelsius}, most tungsten powder retained its original shape and a layer of tiny dense NWs begun to grow.
+At 500 \si{\degreeCelsius}, most tungsten powder retained its original shape and a layer of tiny dense NWs began to grow.
 When temperature was increased to 600 \si{\degreeCelsius}, 3N powder started to crack with longer NWs on the isolated surface.
@@
 This dramatic difference could be explained in terms of surface energy and oxygen diffusion.
-With smaller dimension, the increased surface-to-volume ratio and short diffusion path both lowered the energy barrier of oxidation.\cite{tungsten1999} It was logical to deduce that higher temperature or increased oxygen level might favored the NWs formation on 3N5 powder.
-When it came to seeded growth, however, the powder size distribution was an important factor to give uniform NWs deposition.
-Since the size distribution of 3N powder was more uniform than that of 3N5 powder, this study used the former as seeds.
+With smaller dimension, the increased surface-to-volume ratio and short diffusion path both lowered the energy barrier of oxidation.\cite{tungsten1999} When it came to seeded growth, however, the powder size distribution was an important factor to give uniform NWs deposition.
+Since the size distribution of 3N powder was more uniform than that of 3N5 powder (Fig.~\ref{fig:pdbefore}), this study used the former as seeds.
 % seed optimal
@@
 When oxygen flow was increased to 10 sccm, the 3N powder exemplified an enlarged version of that for 4N5 or 5N powder under 1 sccm oxygen flow.
-This observation again supported the surface energy explanation.
+This observation again was supported by the surface energy explanation.
 
@@
 As shown in Fig.~\ref{fig:sgb}, a dense NWs array was obtained on tungsten powder seeds with individual wires of length up to 10 $\mu$m and diameter about 50 to 200 nm, according to the measurements made in the close-up view.
-Each tungsten powder stood as independent growth site (Fig.~\ref{fig:sga}) with island-layer growth on the substrates, a common feature without using tungsten powder as seed under current experimental conditions.
+Each tungsten powder stood as independent growth site (Fig.~\ref{fig:sga}) with film growth on the substrates, a common feature without using tungsten powder as seed under current experimental conditions.
 It was occasionally observed that NWs growth was initiated adjacent some tungsten powders.
@@
 It is also found that the diameter of NWs decrease as the distance between powders and upstream edge increases.
-This is a combination effect of lower temperature and reduced \ce{WOx} growth species supply.
-Similar phenomena were observed in other studies.
-\citeauthor{Thangala2007} reported that a decrease in NW density with increasing substrate temperature, and an increase of NW density with increasing partial pressure of oxygen.\cite{Thangala2007}
+This is a combination effect of lower temperature and reduced \ce{WO_x} growth species supply.
 
@@
 \includegraphics[width=0.5\textwidth]{wo3_seed_edx}
-\caption[Composition analysis on seeded growth \ce{WO3} NWs]{Composition analysis on seeded growth \ce{WO3} NWs. EDX spectroscopy on seeded growth \ce{WO3} NWs.}
+\caption[Composition analysis on the \ce{WO3} NWs from the seeded growth]{Composition analysis on the \ce{WO3} NWs from the seeded growth with EDX.}
 \label{fig:woedx}
 \end{figure}
-\gls{edx} analysis on the seeded growth \ce{WO3} NWs is shown in Fig.~\ref{fig:woedx}.
+\gls{edx} analysis on the \ce{WO3} NWs from the seeded growth is shown in Fig.~\ref{fig:woedx}.
 Only W and O elements were detected on the NW array.
-The background level from 3 to 8 keV was a manifestation of the continuous components of W X-ray spectrum.
+The background level from 3 to 8 KeV was a manifestation of the continuous components of X-ray spectrum.
 
@@
 \caption[Characterization of seeded growth \ce{WO3}: XRD and Raman]{Characterization of seeded growth \ce{WO3}: XRD and Raman.
-(a) XRD pattern of as-prepared sample indicating the \ce{WO3} phase and the presence of metallic core.
-(b) Raman spectrum on NWs region showing the feature of \ce{WO3}.}
+(a) XRD pattern of as-prepared sample indicating the \ce{WO3} phase and the presence of metallic core, and (b) Raman spectrum on NWs region showing the feature of \ce{WO3}.}
 \label{fig:woseedxrd}
@@
 The enhanced yield of NWs obtained via the seeded growth could be explained by a vapor-solid (VS) mechanism.
-External supply of growth species condensed onto the powders and substrate simultaneously, promoting the elongation of NWs on power as well as resulting island-layer growth on substrate.
+External supply of growth species condensed onto the powders and substrate simultaneously, promoting the elongation of NWs on powers as well as resulting film growth on substrates.
 The local NW density in oxidation experiment was much higher than that of seeded growth.
@@
 \caption[Characterization of flow growth \ce{WO3}: SEM]{Characterization of flow growth \ce{WO3}: SEM.
-(a) Low magnification SEM image showing dense array of NWs (b) High magnification SEM image of NWs grew out of layer and close-up view on individual wire.}
+(a) Low magnification SEM image showing dense array of NWs, and (b) High magnification SEM image of NWs grew out of layer and close-up view on individual wire.}
 \label{fig:wogrowsf}
@@
 In contrast, it was found that when two shorter substrates were closely placed together, the \ce{WO3} NW yield was significantly enhanced in the second substrate located in lower temperature region.
-For instance, substrate 1 (Sub1) was located at 6.75 to 7 inch (Fig.~\ref{fig:wogrow} horizontal axis on page~\pageref{fig:wogrow}), and substrate 2 (sub2) was placed in close vicinity of downstream end of sub1.
+For instance, substrate 1 (sub1) was located at 6.75 to 7 inch (Fig.~\ref{fig:wogrow} horizontal axis on page~\pageref{fig:wogrow}), and substrate 2 (sub2) was placed in close vicinity of downstream end of sub1.
 W source was moved to 5 inch, and 0.3 sccm \ce{O2} was used to reduce the \ce{WO_x} vapor pressure.
@@
 The NW density was dramatically increased when two separate substrates were employed.
-The NWs had length about 1 to 2 $\mu$m and diameter about 200 nm.
+The NWs had length about 1 $\mu$m to 2 $\mu$m and diameter about 200 nm.
 Close-up view (inset of Fig.~\ref{fig:fg2}) shows the NWs exhibited sharp facets, implying its high crystalline quality.

### 2015-03-29 ch-wox/part1.tex
Final

@@
 Localized surface plasmons could possibly exist on these conductive planes.
-Therefore \gls{sers} applies and single molecule Raman scattering using individual tungsten oxide nanorod has been demonstrated.\cite{Shingaya2013}
+Therefore, \gls{sers} applies and single molecule Raman scattering using individual tungsten oxide nanorod has been demonstrated.\cite{Shingaya2013}
 % wo3 phases
@@
 
-Therefore another model in analogy to the F-color center is proposed.
+Therefore, another model in analogy to the F-color center was proposed.
 Color center model assumes the presence of oxygen vacancy $V_O^0$ is associated with \ce{W^{4+}} or 2\ce{W^{5+}} states.
@@
 
-So the polaron and color center models both agree on that \ce{W^{5+}} and its transition is responsible for the coloration; but disagree on how this \ce{W^{5+}} state and the corresponding energy levels are created (foreign ion reduction in polaron model and oxygen vacancy in color center model).
+The polaron and color center models both agree on that \ce{W^{5+}} and its transition is responsible for the coloration; but disagree on how this \ce{W^{5+}} state and the corresponding energy levels are created (foreign ion reduction in polaron model and oxygen vacancy in color center model).
 A modified polaron model is proposed to include \ce{W^{4+}} states in host lattice.

### 2015-03-29 main.tex
Final

@@
 
+Similar phenomena were observed in other studies.
+\citeauthor{Thangala2007} reported that a decrease in NW density with increasing substrate temperature, and an increase of NW density with increasing partial pressure of oxygen.\cite{Thangala2007}
+
+When the catalyst was smaller than some critical size, there is no preferred growth direction.
+This changed when the precipitated solid exceeded certain critical dimension, and the morphology evolution was then determined by the relative size of already formed solid and the associated catalyst.
+
+forming a swelling particle
+
+ the tips of \ce{WO3} NWs exhibited greater crystalline disorder, and \ce{WS2} layers on tips were folded at least along two axes, resulting a higher density of defects and thus a higher sulfurization rate; while the folding along NW body was quasi-one dimensional, subsequently the sulfurization rate could be lower.
+Besides, sulfurization could also be initiated from the NW body, presumably due to the presence of surface defects.
+As a result, this led to the uneven \ce{WS2} layer number distribution along the core-shell NWs.
+
+which was tentatively attributed to stacking fault in this study.
+
 should check how other template deals with before after section skip

### 2015-03-29 misc/paper.tex
Final

@@
 
+taper design beam propagation method and FDTD,\cite{Almeida2003} mode field resides in the \ce{SiO2} cladding region,
+
+Low temp. oxygen-plasma assisted wafer bonding for hybrid Si laser.\cite{Park2005} Process:
+\begin{enumerate}
+\item \ce{SiO2} mask layer formation on SOI by 2 h at 1050 C
+\item Silicon rib waveguide by inductively coupled plasma etching with \ce{Cl2}/\ce{BCl3}
+\item cleaning
+\item oxygen-plasma assisted wafer bonding: annealing at 300 C, 1.5 MPa for 12 h
+\item InP removal by HCl at 250 C
+\item diced, polished, and coated with \ce{SiO2}/\ce{Ta2O5}
+\item n-contact: Ni/AuGe/Ni/Au
+\item p-contact: Pd/Ti/Pd/Au
+\end{enumerate}
+
+Electrically pumped hybrid Si laser.\cite{Fang2006} 0.5 mW fiber coupled power and 70 C operating temp.
+for commercial transmitters.
+yield dominated by waveguide chipping and bond delamination during facets polishing.
+
+DFB Si laser.\cite{Fang2008}
+
+\begin{enumerate}
+\item grating formation: 50 nm PECVD \ce{SiO2} patterned with e-beam lithography and inductively coupled plasma dry etching; 
+\item 
+\end{enumerate}
+
+Hybrid laser development history.\cite{Bowers2010} 650 C bonding led to cracks.
+300 C plasma-activated approach with vertical outgassing channel.
+Cleaving yielded stepped facets due to incorrect orientation of silicon.
+current could not be passed through the bonded interface due to thin oxide layer formation increasing the junction resistance.
+DFB laser were important because they removed the need for polished facets and enable single wavelength operation capability that is needed in DWDM.
+
+design principles:
+\begin{enumerate}
+\item taper angle small to prevent coupling from low order mode to high order ones.
+\item 
+\item 
+\end{enumerate}
+
+wg on SOI.\cite{Kurdi1988} high density of carriers reduces the refraction index.
+SOI formation: high dose of oxygen ions implantation ($10^{18}$ ions/cm2) on sub.
+held at a temp.
+range of 450 to 600 C; abbreviated as SIMOX.
+postannealing at a temperature $T>1250$ C, defect densities can be as low as $10^5$ cm-2 when SIMOX samples annealed at $T=1300$ C.
+The top layer Si thickness can be increased by a subsequent epitaxial growth.
+For 200 nm top Si, the loss of TE0 mode is 1 dB/cm when \ce{SiO2} thickness reached 500 nm.
+High order modes suffer orders of magnitude higher attenuation.
+
+InP electrical conductivity tuning by proton bombardment.\cite{Boudinov2001} Carrier trap center creation and thermal activation.
+
+Single-mode SOI wg.\cite{Vivien2002} birefringence either due to effective index difference or group index difference between TE and TM modes.
+$n_g = n_{eff} - \lambda \frac{\partial n_{eff}}{\partial\lambda}$.
+
+Plasma-Assisted InP-Si bonding.\cite{Pasquariello2002} Gallium arsenide, indium phosphide.
+bonding thermally mismatched materials cause degradation.
+thermal stress.
+wafer bonding requires surface roughness below 1 nm.
+eutectic bonding as alternative, indium-gold eutectic bonding.
+use Pd to form an ohmic contact in between InP and Si or GaAs.
+Anodic bonding; Hydrophilic wafer bonding; Hydrophobic surface obtained on HF treated InP and Si, and HCl or \ce{NH4OH} treated GaAs.
+Fluorine may be still on the surfaces.
+
+Plasma is a partially ionized gas with equal charges.
+Electron are more mobile, thus the plasma potential is always positive.
+An ion current formed between the plasma and the chamber wall.
+Oxygen plasma is attractive for surface pretreatment in wafer bonding since it is efficient in removing hydrocarbon and water related species.
+
+Pressure of 0.25 MPa on 2 inch wafer, nearly 50 kg.
+
+Short cavity length DFB laser on Si with high efficiency, direct modulation.\cite{Zhang2014d} First order grating on Si defined with e-beam lithography; transmission line measurement for n- and p-contact resistance.
+grating pitch.
+Low thermal conductivity of BOX layer.
+12.5 GB/s with 3 dB eye diagram demonstrated.
+
+A path to PIC. \cite{Bowers2014}
+\begin{enumerate}
+\item III-V chips bonded on Si.
+\item epitaxial growth of III-V layers on Si using buffer layers (Ge or strained supperlattices); however, this dislocation filter layers are absorptive and thick, limiting the efficient coupling into Si wg.
+\item a 
+\end{enumerate}
+
 \begin{table}[htb]
@@
 InP         &  detector  &   footprint 50 $\mu m^2$, 33 GHz        &    \\
+InP         & gain medium  &   thermal $4.8\times 10^{-6}$ K        &    \\
+Si         &  sub  &   thermal $2.6\times 10^{-6}$ K        &    \\
 SiGe        &  detector    &  0.7 eV, up to 1.7 $\mu$m        &    \\
@@
 
+\subsection{EAM thesis}
+
+Frequency chirping from directly modulated lasers, where the pulse becomes broadening after transmitting through a dispersive fiber.
+External modulation also show chirping, but at a much lower magnitude.
+Time division multiplexing: Optical TDM, mode-locking source, time delay, the return-to-zero signal requires double bandwidth than do the non-return-to-zero signal.
+Electrical TDM.
+
+\begin{itemize}
+\item Electro-optic effect: change of refraction index by E field
+\item Electroabsorption: change of absorption in the presence of E field. Franz-Keldysh effect in bulk and quantum confined Stark effect in QW. 
+\item FK effect: below-bandgap photon-assisted tunneling of electrons from VB to CB. In bulk materials with E field applied, exciton ionization occurs predominately.
+\item QCSE: when E field applies, optical absorption redshift, and exciton remains due to the large binding energy in QW. 
+\end{itemize}
+
+Using traveling wave electrode configuration, the reflection at the load end is diminished significantly, thus bypassing the RC limitation.
+Increasing well thickness leads to stronger QCSE and a lower driving voltage.
+The QW has to be designed with an absorption edge just slightly shorter than operation wavelength, such as 1490 nm for 1550 operation; a closer wavelength causes higher residual absorption without bias, and a shorter wavelength requires larger bias voltage.
+
+Heavy hole transitions related to absorption of TE; and light hole related to TM. 
+Heavy- and light-hole degeneracy is sufficient to ensure the polarization insensitivity of absorption for MQW using QCSE. Photo-generated holes accumulated in the wells, screening the applied field.
+
+Traveling wave electrode design: carrier sweep out time and optical-electrical group velocity mismatch.
+
+Transmission line. three modes in microstrip: dielectric quasi-TEM mode, skin-effect mode and slow-wave mode.
+
+mesa, epoxy,
+
+ref 30
+
+\begin{table}[htb]
+\centering
+\caption{Comparison of modulator}
+\begin{tabular}{cccc}
+\toprule
+Material   & Voltage &  Bandwidth   & Remarks   \\
+           & (V)     &  (GHz)      &    \\
+\midrule
+\ce{LiNbO3}&  3-5     &  40   &    EO MZ      \\
+InP, MQW   &  2-4     &  10   &    EO MZ      \\
+InGaAs   &  1.5-3     &  30   &    EAM        \\
+\bottomrule
+\end{tabular}
+\end{table}
+
+\section{edx nanoelectronics}
+
+Previously, diffusive random walk; current flow in nanoscale: ballistic, resistance calculation depending on the device length vs. mean free path. resistance associated with voltage drop.
+
+Entropy driven process and mechanics force driven;
+
+\[
+G = \frac{q^2}{h}M\times\frac{\lambda}{L+ \lambda} \text{Ballistic conductance}
+\]
+
+positive voltage lower the electrochemical potential by amount of $qV$. conductance occurs only near the Fermi level. Current flow driven by E field?
+
+Ballistic: no lost of momentum. Elastic: no lost of energy?  
+For low bias (small than kT), conductance approximately as
+\[
+G = \int_{-\infty}^{+\infty} dE -\frac{\partial f_0}{\partial E}G(E)
+\]
+
 \section{vocabulary}
 
-model also is applicable to ..., more probable,
+model also is applicable to ..., more probable, material degradation,
 
@@
 Expansion of functionality set
+
+You can't make a silk purse out of a sow's ear

### 2015-04-23 misc/paper.tex
mwe update

@@
 
-\ce{H^{\sigma +}}-\ce{Cl^{\delta -}}, polar bond and permanent dipole moment,
+\cee{H^{\sigma +}}-\cee{Cl^{\delta -}}, polar bond and permanent dipole moment,
 
@@
 
+\section{EM thesis}
+
+Time domain and parallel distributed integral equation techniques for full--wave microelectronics simulation.\cite{Yang2005a}
+
+time domain integral equations; Modified Nodal Analysis; multi-level low-rank decomposition algorithm;
+
+Surface-based TDIE: incorporating skins effects without volumetric meshing; volume current?
+
+Scalar potential produced on electrically small terminals will be equal to the circuit potential of the circuit node.
+
+edge-based Rao-Wilton-Glisson spatial basis functions: triangular discretization of surface S.
+
 \section{edx nanoelectronics}
@@
 
+\section{metrology}
+
+Coordinate measurement techniques (CMT).\cite{Goch1990} $L_2$-norm inaccurate in computational fitting of measured points, where Tschebyscheff-norm should be applied.
+\citeauthor{Goch1990} proposed a universal algorithm based on both $L_2$-norm and T-norm.
+
+reference coordinate system (RCS); coordinate measuring machine (CMM); workpiece-related coordinate system (WCS);
+
+\[
+Q_G = (\sum_{i=1}^n [d(x_i, x_S)]^2)^{1/2}
+\]
+and
+
+\[
+Q_T = {sup \atop x_i\in W_I} |d(\vec{x_i}, \vec{x_S})|
+\]
+
+subscript $i(I)$ for measured point(surface); subscript $s(S)$ for nominal point(surface).
+
 \section{vocabulary}
@@
 You can't make a silk purse out of a sow's ear
+
+\subsection{headline and elevator speech}
+
+Aligning with customer priorities
+Addressing power sensitive markets
+Application benefit, use-case
+Is projected /Is positioned
+Is here to stay
+Offer the best path towards
+Cost-effective
